### 2013-05-17 anthropomorphism.tex
Initial commit from Julia

%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a general template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2010/09/16
%
% Copy it to a new file with a new name and use it as the basis
% for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% First comes an example EPS file -- just ignore it and
% proceed on the \documentclass line
% your LaTeX will extract the file if required
\begin{filecontents*}{example.eps}
%!PS-Adobe-3.0 EPSF-3.0
%%BoundingBox: 19 19 221 221
%%CreationDate: Mon Sep 29 1997
%%Creator: programmed by hand (JK)
%%EndComments
gsave
newpath
  20 20 moveto
  20 220 lineto
  220 220 lineto
  220 20 lineto
closepath
2 setlinewidth
gsave
  .4 setgray fill
grestore
stroke
grestore
\end{filecontents*}
%
\RequirePackage{fix-cm}
%
%\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
%\documentclass[smallextended]{svjour3}       % onecolumn (second format)
\documentclass[twocolumn]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{graphicx}
%
\usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
\usepackage{color, soul}
\usepackage{url}
\usepackage[numbers, square, comma, sort&compress]{natbib}
\usepackage{multirow}
% insert here the call for the packages your document requires
%\usepackage{latexsym}
% etc.
%
% please place your own definitions here and don't use \def but
% \newcommand{}{}
%
% Insert the name of "your journal" with
\journalname{Int J Soc Robot}
%

\newcommand{\eg}{{\textit{e.g.~}}}
\newcommand{\etal}{{\textit{et al.~}}}
\newcommand{\ie}{{\textit{i.e.~}}}

\hyphenation{com-mon-ly}

\begin{document}

\title{On the Dynamics of Anthropomorphism in Robotics
\thanks{This research was supported by the Swiss National Science Foundation through the National Centre of Competence in Research Robotics.}
}
\subtitle{}

%\titlerunning{Short form of title}        % if too long for running head

\author{Julia Fink         \and
        S\'{e}verin Lemaignan     \and
        Pierre Dillenbourg  %etc.
}

%\authorrunning{Short form of author list} % if too long for running head

\institute{J. Fink \and S. Lemaignan \and P. Dillenbourg \at
              Computer-Human Interaction in Learning and Instruction (CHILI) \\
              Ecole Polytechnique F\'{e}d\'{e}rale de Lausanne (EPFL) \\
              Rolex Learning Center, Station 20 \\
              CH-1015 Lausanne \\
              Switzerland \\
              Tel.: +41-21-693-2274\\
              Fax: +41-21-693-6070\\
              \email{julia.fink@epfl.ch}           %  \\
%             \emph{Present address:} of F. Author  %  if needed
           \and
           S. Lemaignan \at
              \email{severin.lemaignan@epfl.ch}
		   \and
           P. Dillenbourg \at
              \email{pierre.dillenbourg@epfl.ch}
}

\date{Received: date / Accepted: date}
% The correct dates will be entered by the editor

\maketitle

\begin{abstract}

	While anthropomorphism in robotics is a commonly discussed trait of human-robot interaction (HRI), it is paradoxically an overlooked research topic. This article attempts first at providing a comprehensive synthesis of the social phenomenon of \textit{attributing human characteristics to robots}. It draws on social sciences and psychology, as well as on a critical survey of existing literature in the HRI community, to ground the concept of \textit{anthropomorphism}. We further present different kinds of \textit{anthropomorphic design} of robots and outline their role in social robotics. We then propose to go beyond the traditional perception of anthropomorphism as a static feature. We suggest to understand anthropomorphism as a dynamic, context-dependent process. This also provides an account of the so-called \textit{novelty effect}. To this end, we introduce an initial function of anthropomorphism that models the phenomenon along three interaction phases. Our function is supported by results of a long-term study that we conducted in a real human environment.

%	This article synthesizes the social phenomenon of attributing human characteristics to robots, and illustrates the role of human-like form and human social behavior cues in the design of robots. We draw on backgrounds from social sciences and psychology to first provide a common ground for the understanding of  anthropomorphism. The theoretical background is featured by an overview of different kinds of anthropomorphic design in robots. We also provide a comprehensive summary and critical comparison of findings from experiments studying anthropomorphism in human-robot interaction. Finally, we propose to understand anthropomorphism as a dynamic phenomenon which is not only determined by 1) \textit{individual characteristics} of the human user, and 2) the \textit{anthropomorphic design of the robot}, but might also be impacted by 3) \textit{dynamics}, such as \textit{time} and the \textit{context of use}. Consequently, we propose different levels of anthropomorphism that might shift with increased time of interaction and the context of use of a robot.

\keywords{
	Anthropomorphism \and
	Design \and    
    Human-Robot Interaction \and
    Social Issues in Robotics \and
    Acceptance of Robots}
% \PACS{PACS code1 \and PACS code2 \and more}
% \subclass{MSC code1 \and MSC code2 \and more}
\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
%
%				INTRODUCTION
%
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Anthropomorphic Design and Anthropomorphism}
\label{intro}

	 Since the very beginning of robotics, there has been a trend of making robots human-like. Personal robots are designed with more or less human-like shapes or characteristics, and are able to use and react to human social behavior, such as facial expressions or nonverbal gestures. We call this design approach \textbf{anthropomorphic design}, which hereafter refers to human-like \hl{(life-like?)} characteristics in a robot (realized in its shape, behavior, interaction, etc.). Even though this design principle is not exclusive for robots, the topic has received remarkable attention in the domain of (social) robotics. On one hand, human-like design of robots seems to be beneficial from a technical viewpoint: for finding efficient solutions in the technical and mechanical development of a robot (e.g. bio-inspired robots) in order to optimally fit the robot into our to humans adapted physical space. On the other hand, human-like characteristics in a robot also concern the social space, the acceptance of a robot, as well as how people perceive it, form expectations toward it, and in turn treat it. A robot that looks and acts like a human raises different expectations than a functionally designed robot \hl{[REF]}. The anthropomorphic design of robots is thus a crucial aspect for the study of acceptance of robots in daily life and in the domain of social robotics in general.

	Why does anthropomorphic design seem to be so popular in HRI? Amongst others, a human-like shape and human-social characteristics of a robot aim to enable effective and natural interaction between humans and robots. As robots are generally something unfamiliar and new to humans, the underlying argumentation is that when a robot has a human-like shape and displays human social cues, it is easier for people to interact with it. A robot's anthropomorphic design suggests to the human user to understand and treat it to some extend similar to a human, thus in a social manner. This behavior has been extensively studied in HCI and is explained by the \emph{Media Equation Theory}, which states that people's interactions with computers, television, and new media are fundamentally social and natural, just like interactions in real life \cite{reeves_media_1996}. Since robots are physically embodied agents, it is consequently very likely that people respond socially to them. The anthropomorphic design in a robot further encourages a person to ascribe / attribute human characteristics to it (e.g. intention, emotions, personality). To this end, anthropomorphic design of robots aims to make the system understandable, thus predictable, and acceptable. The conclusion builds on the assumption that humans prefer to interact with machines (and robots) in the same way they interact with humans \cite{fong_survey_2003} because they are familiar to these kind of interactions. The implicit social mechanism which is exploited, is called \textbf{anthropomorphism}. It describes the phenomenon of a person ascribing human-like characteristics (e.g. beliefs, intentions, personality) to a non-human artifact, such as a robot. Anthropomorphism also concerns a person's reasoning about a non-human agent as if that agent were human-like (\textit{i.e.} a cognitive process without the action of making a verbal statement with attribution, for instance). In robotics, this social phenomenon is enhanced by using anthropomorphic forms in the design of robots, thus these two aspects are closely related to each other.

	As in the near future it is likely that a growing number of social robots will be deployed in everyday environments, the analysis and understanding of anthropomorphism and related social dynamics in HRI becomes increasingly important.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
%
%				ANTAGONISM
%
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{The Antagonism of Anthropomorphic Design}
\label{sec:2}

	In the first place, robotics seems to benefit from anthropomorphic design and people's tendency to anthropomorphize robots. However, there is the other side: a not yet very well defined thin line separates acceptable human-like forms in robots from creepy artificial \textit{almost} human-like appearing robots. The underlying theory for this viewpoint is stated as the \textit{Uncanny Valley} \cite{mori_uncanny_1970} which suggests that artificial human-like forms are only acceptable up to a certain degree but lead to reluctance if they fail in trying to attain human-likeness \hl{cross-ref to later and figure}. The usage of different kinds of anthropomorphic forms in robots is still controversially discussed. Some developers and researchers clearly oppose human-like forms in robots but rather suggest animal-like shapes or caricature-like appearance. Another sensitive aspect is that with robots to closely resemble a human, also ethical issues arise. For instance, we need to consider how far we actually want an \textit{artificial agent} to resemble ourselves and how far it should act `artificially socially' toward humans, and what happens as soon as it is considered a \textit{moral agent} \cite{sullins_when_2006}. Using \textit{socially interactive robots} in contexts involving elderly care or rehabilitation for disabled / handicapped persons, autistic children is also a controversially discussed topic \cite{robins_robots_2005}.

	Literature on anthropomorphism (in robotics) is quite diverse and one strives hard to extract a coherent conclusion. There is no commonly accepted definition about the terms used and the terminology is not clear. However the terms \textit{anthropomorphic or human-like are often used as if their meanings are clear and agreed upon"} \cite{persson_anthropomorphism_2000}. Consequently, Duffy \cite{duffy_anthropomorphism_2002} argues that terms might even be misused. For instance, some researchers refer to \textit{"the robot's level of anthropomorphism"} \cite{bartneck_is_2007}, however, others argue that anthropomorphism emerges in the \textit{interaction} between the technology and the user, thus a system or an artifact does not "contain anthropomorphism" \textit{per se} \cite{persson_anthropomorphism_2000}. Further, robotics is a multi-disciplinary field and researchers from very different domains might have diverse or even contradictory understandings of anthropomorphism. Epley \textit{et al.} \cite{epley_seeing_2007} notice that despite the fact that anthropomorphism in the perception of non-human agents is commonly observed, it is poorly understood. The phenomenon itself has been found to be very complex but sometimes subtle and hard to study. Another constraint that limits the reliability of some findings is, that most experiments on anthropomorphism are conducted in controlled lab-settings during short-term interactions. This experimental setting (short term and laboratory context) can be critical when studying a social phenomenon like anthropomorphism and possibly lead to over-interpretations. Some studies also seem to contrast two or more different anthropomorphic and mechanical systems that might not be appropriate for comparison under the given context and research question. \hl{say more}

	To sum it up, while anthropomorphism in robotics is a commonly discussed and studied trait of human-robot interaction (HRI), we think it is paradoxically an overlooked research topic. The understanding of anthropomorphism in robotics seems to not take into account the wide range of phenomena that it encompasses. The traditional understanding of anthropomorphism in robotics to date, considers two main factors that account for the social phenomenon: the characteristics of \textbf{1) the robot's design} (degree of human-likeness) and the psychological determinants in \textbf{2) the human user} (see \cite{epley_seeing_2007}). It has been shown that both these factors can facilitate or hinder anthropomorphism. We propose to go beyond this traditional perception of anthropomorphism as a static feature of HRI. Based on Persson \textit{et al.}'s \cite{persson_anthropomorphism_2000} argumentation that anthropomorphism is a multi-layered phenomenon which arises in different levels, we suggest to understand anthropomorphism as a dynamic, context-dependent process. To this end, we apply Persson \textit{et al.}'s six levels on anthropomorphism to HRI and introduce three interaction phases. These interaction phases of anthropomorphism reflect also the results of a long-term study that we conducted in a real human environment and provide an account of the so-called \textit{novelty effect}. Consequently, we would like to draw attention to two \textit{dynamics in anthropomorphism}, namely, the context of use, and the fact of getting used to a system over time. We propose to add these two aspects as a third factor, the characteristics of \textbf{3) the interaction} (time and space), to the existing two accounts of anthropomorphism (robot and user).

	We would further like to review and discuss research on anthropomorphism in robotics and human-like design of robots. We first provide a comprehensive understanding of the phenomenon drawing on theories from developmental psychology and cognitive sciences. We then present the trends of different kinds of anthropomorphic forms in robots and discuss their role in social robotics. The article integrates related work from human-robot interaction studies, reporting on findings from experiments with human subjects interacting with and evaluating various types of systems. We try to give a coherent view on the topic, outline similarities and antithetic findings, and contribute to a better understanding of anthropomorphism in robotics, and the acceptance of human-like characteristics in robots. We also aim to constructively discuss anthropomorphic design of personal and socially interactive robots.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
%
%				ANTHROPOMORPHISM: EXPLANATIONS & BACKGROUND
%
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Anthropomorphism as a Social Phenomenon}
\label{sec:3}

	The term \textbf{anthropomorphism} is used in different senses throughout natural sciences, psychology, Human-Computer Interaction, and Human-Robot Interaction \cite{duffy_anthropomorphism_2003}. There is no single accepted definition. Originally, anthropomorphism comes from the Greek \textit{`anthropos'} for `man' (or `human') and \textit{`morphe'} for `form/structure' (or `shape'). It can be understood as people's tendency to think of objects as if they had human characteristics, and consequently, attribute / ascribe specific human characteristics to these non-human entities and artifacts (including animals, and robots) \cite{duffy_anthropomorphism_2003,schmitz_concepts_2011}. Apart from anthropomorphism there is also \textbf{animism}, the \textit{"attribution of life to the nonliving"} \hl{in Schmitz 2011, cite Piaget original text!}. Often synonymously used to animism is \textbf{zoomorphism}, which describes the case when non-lifelike objects are associated with animalistic attributes, excluding human-specific traits. Both anthropomorphism and zoomorphism can be embraced by the concept of \textbf{life-likeness}. \footnote{The inverse process, dehumanization \cite{haslam_dehumanization:_2006}, or mechanomorphism \cite{caporael_anthropomorphism_1986} also exists.}

	Commonly, anthropomorphism can also be understood as \textbf{humanization} or \textbf{personification} of anything other than a human being. The phenomenon of personifying something has ancient roots, \textit{e.g.} in mythology but also in storytelling. Already in prehistoric artworks and illustrations zoomorphic (animal-shaped) or anthropomorphic shapes were used to represent natural forces or great spirits, for instance. A more recent example is Milo Winter's illustration from 1919, \textit{"The North Wind and the Sun"} (Figure \ref{fig:1}), in which both north wind and sun are given a human face (anthropomorphized). Similarly, when parents explain their children about nature, they tend to use anthropomorphisms, \textit{e.g.} saying the skies would cry when it rains. More generally, a possible explanation for why people anthropomorphize is that by doing so, the subject is made graspable, understandable, somehow predictable, and one could feel more empathetic toward it. For instance, people commonly anthropomorphize their pets, ascribing mental states, intentions or feelings to them \cite{eddy_attribution_1993}. Interestingly, pet-ownership seems to have a significant impact on human-robot interaction: several studies suggest that pet-owners are more likely to anthropomorphize technologies and robots than non pet-owners \hl{references!}.

 \begin{figure}
% Use the relevant command to insert your figure file.
% For example, with the graphicx package use
  \includegraphics[scale=0.91]{north-wind.jpg}
  \includegraphics[scale=0.91]{sun.jpg}
% figure caption is below the figure
 \caption{Milo Winter illustration of Aesop Fable \textit{The North Wind and the Sun}, 1919; both natural forces wind and sun are anthropomorphized with a human face; picture source: wikipedia}
 \label{fig:1}       % Give a unique label
 \end{figure}

\subsection{Explanations for Anthropomorphism}
\label{sec:3.1}

	According to Lee \textit{et al.} \cite{lee_human_2005}, there are two main perspectives in explaining people's tendency to anthropomorphize. The first one explains anthropomorphism from the design of the artifact (anthropomorphic form in the design). It assumes that humans directly respond to life-like or social cues that an object or system emits, without thoughtful mental processing, by simply applying stereotypes and heuristics to it. In fact, from early childhood on, humans are inherently well-trained to perceive life \cite{epley_seeing_2007}. Schmitz \cite{schmitz_concepts_2011} describes that within the visual scope of design, the outer appearance can have an important impact on the overall perception of an object. The basic assumption here is that if an artifact appears much like a human it is likely to be treated similar to a human. If this explanation of anthropomorphism is correct, people may respond automatically to social cues emitted by a robot, and apply human-human social schemas and norms to these interactions.

	The second perspective applies a human-centered, cognitive viewpoint where anthropomorphism is described through people's specific mental model they construct about how an artifact works the way it does. According to v. Foerster \hl{ref} \textit{"we anthropomorphize because it allows us to explain things we do not understand in terms that we do understand, and what we understand best is ourselves as human beings"} \cite{hegel_understanding_2008}. This is consistent with the \hl{familiarity thesis (18)} \cite{hegel_understanding_2008} which claims we understand the world based upon a mental model of the world that we are most familiar with. Consequently, people tend to thoughtfully develop a mental model of agents in their environment and make inferences about it based on what is familiar to them. This point of view implicitly builds on a person's ability to attribute mental states to oneself and others, which is called \textit{Theory of Mind}. A theory of  mind for other agents enables us to attribute intentionality to those agents \cite{leslie_pretense_1987,admoni_multi-category_2012}. If a system behaves much like a human being (e.g. emits a human voice), people's mental model of the system's behavior may approach their mental model of humans, though the model may differ in some important aspects \hl{ref? Schmitz?}. In turn, people's estimation of a robot's `knowledge' and its capabilities / abilities affects the way they relate to it. Research examined the validity of the mental model concept with various kinds of robots \cite{schmitz_concepts_2011,kiesler_mental_2002}. Findings suggest that people tend to hold richer mental models about anthropomorphic robots in contrast to mechanic ones \cite{kiesler_mental_2002}.

\hl{here or later? : familiarity thesis does probably not hold after one get's acquantained with a robot.}

\subsection{Insights from Social and Developmental Psychology}
\label{sec:3.2}

	To understand the social phenomenon of anthropomorphism better, it makes sense to take a look at studies and explanations from (developmental) psychology. The phenomenon of attributing intentions and \hl{animacy} to simple shapes based on motion has been intensively studied in (developmental) psychology. Two famous studies on the perception of and attribution to simple things have been done in the mid 1940s: Heider and Simmel's work on the \textit{attribution theory} \cite{heider_experimental_1944} and Michotte's studies on \textit{the perception of causality} \cite{michotte_perception_1963}. In both experiments, participants viewed animations of simple shapes, such as circles or triangles (see Figure \ref{fig:2}). Asked to describe what they observed, interestingly, most people developed elaborate stories, attributing motivations, emotions and relationships between the objects.

\begin{figure}\centering
% Use the relevant command to insert your figure file.
% For example, with the graphicx package use
  \includegraphics[scale=0.6]{heider-simmel_animation.jpeg}
% figure caption is below the figure
 \caption{Fritz Heider and Mary-Ann Simmel's animated film to study people's tendency to attribute animacy and intention to simple shapes; \textit{An experimental study of apparent behaviour}, 1944}
 \label{fig:2}       % Give a unique label
 \end{figure}

	What is a person's motivation to attribute human characteristics to simple geometric shapes, or more sophisticated, anthropomorphic shapes, animated or not? Irrespective of the artifact's characteristics, there are psychological theories to explain the phenomenon. An interesting recent psychological theory of anthropomorphism (also related to robotics) is provided by Epley, Waytz, and Cacioppo \cite{epley_seeing_2007}. The authors established a three-factor theory of when people are likely to anthropomorphize based on psychological determinants. Namely, the theory suggests that some people are more likely to anthropomorphize when:

\begin{itemize}
	\item anthropocentric knowledge is accessible and applicable to the artifact (\textit{elicited agent knowledge}),
	\item they are motivated to explain and understand the behavior of other agents (\textit{effectance motivation}), and
	\item they have the desire for social contact and affiliation (\textit{social motivation}).
\end{itemize}

	Epley \textit{et al.} describe that \textit{elicited agent knowledge} is a \textbf{cognitive determinant  of anthropomorphism} which is understood as the activation of knowledge about humans (or the self) when making inferences about non-human agents. One basic reasons for this are a person's physical constraints of being a human and nothing else. Consequently, one has no other experience than the self and in turn people tend to make inferences about others' mental states by relying inordinately on their own mental states. \footnote{Using one's own mental states and characteristics as a guide when reasoning about other humans is ego-centrism; when reasoning about non-human agents is anthropomorphism. See Epley, 2007 \textit{et al.} \cite{epley_seeing_2007}} Also empirical findings suggest that knowledge about humans in general, or self-knowledge in particular, is likely to serve as a readily accessible base for induction when reasoning about non-human agents. This tendency is usually stronger in young children and decreases with cognitive development and the learning to distinguish the self from other humans, and non-human agents.

	Both \textit{effectance} and \textit{sociality} are \textbf{motivational determinants of anthropomorphism}. \textit{Effectance} is understood as the motivation to interact effectively in one's environment: understand, predict, \hl{reduce uncertainty (this feeds again our hypothesis that as soon as a robot is not uncertain anymore, there is no need to keep on anthropomorphizing it)} about one's environment and the agents that inhabit it. According to Epley \textit{et al.}, anthropomorphism serves as one way to reduce uncertainty and increase comprehension of events in one's environment. They mention for instance, children (as they are in their early stages of life) appear to be more likely to anthropomorphize than adults, as they might feel more uncertain within their environment.
	\textit{Sociality} describes the motivation for social contact, social connection, and social approval from other agents. Importantly for anthropomorphism, this social connection appears to be satisfied by connections with \hl{ \textit{"two of the most commonly anthropomorphized hon-human agents, namely pets and religious agents"}} \cite{epley_seeing_2007}. According to Epley \textit{et al.}, the motivation of being socially connected increases the tendency to anthropomorphize non-human agents because first sociality motivation increases the tendency to perceive human-like characteristics and traits even in non-human agents, and second it increases the tendency to search for sources of social connection in one's environment. Consequently, the authors suggest \textit{"[...] those who are chronically lonely should be more likely to anthropomorphize nonhuman agents than those who are more chronically connected"}.

	\hl{BRIDGE}

\subsection{Anthropomorphism in Robotics}
\label{sec:3.3}

	Anthropomorphism is a commonly observed phenomenon in human-robot interaction. Studies showed that there are people who directly talk to their robot (even if it does not recognize speech), give it a name, greet it, wonder about its intentions or actions \cite{eyssel_anthropomorphic_2010,fink_anthropomorphic_2012,forlizzi_how_2007,fussell_how_2008,kiesler_anthropomorphic_2008}. It has frequently been described that people ascribe intentions or emotions to their domestic robot, such as to a Roomba vacuum-cleaning robot \cite{krumm_my_2007,sung_robots_2009} or their AIBO robotic dog \cite{friedman_hardware_2003}. However, people's tendency to anthropomorphize technologies has not only been observed with robots but described earlier in human-computer interaction and related to digital agents \cite{reeves_media_1996, nass_anthropocentrism_1995}. Though, the phenomenon seems to be more coined in human-robot interaction than in other human-machine interaction fields. What makes anthropomorphism special in robotics, is probably related to the (unique) characteristics of robots in contrast to other technologies. Robots are embodied, physical agents, autonomously acting right next to us, and able to respond intelligently to us and the environment. These are factors that seem to facilitate anthropomorphism, due to the nature of the phenomenon and its origins itself. In robotics, anthropomorphism is further encouraged through specific anthropomorphic design of a robot. But what is the interest, which underlies the efforts of enhancing anthropomorphism through specific anthropomorphic design in robots? Why does anthropomorphism seem to be so important in robotics? There is no one single answer to this question but certainly, developers and designers have discovered that anthropomorphism seems to be beneficial for human-robot relations, especially with socially interactive robots \cite{fong_survey_2003}. More concretely, it has been found that the appearance and function of a \hl{product (research in marketing?)}) impacts how people perceive it, interact with it, and build long-term relations with it \cite{bartneck_shaping_2004}. Consequently, the domain of (social) robotics tries to exploit this fact by enhancing anthropomorphism through anthropomorphic robots: \textit{"Applying anthropomorphism or zoomorphism changes the way how users try to understand and make sense of a [system] by projecting everyday \hl{expectations} of human and animalistic life onto it."} \cite{schmitz_concepts_2011}. Studies have further shown that perceived similarity between the user and the robot influences the intense of the participants' attributions towards the robot. Thus, anthropomorphism plays an important role in the design of robots as it is strongly related to the perception of intelligence, fun, the attribution of intentions and thus the predictability of the robot \hl{which ref??}.

%	Duffy defines anthropomorphism as "the tendency to attribute human characteristics to inanimate objects, animals and others with a view to helping rationalise their actions." \cite{duffy_anthropomorphism_2003}. This definition directly tries to give an explanation for why people tend to anthropomorphize robots, namely, in order to rationalize their actions, which seems to be effective as long as the robot is not very familiar to the human interaction partner. \hl{familiarity aspect LATER} Attributing familiar human-like qualities to a robot can serve to make the robot more familiar, explainable, or predictable \cite{epley_seeing_2007}. Further Duffy argues that anthropomorphism includes "attributing cognitive or emotional states to something based on observation." \cite{duffy_anthropomorphism_2003} \hl{BRIDGE, explain better} This is important for the acceptance of socially interactive robots \cite{fong_survey_2003} in daily life environments. As robots have to deal with people's acceptance to become useful devices and collaboration partners for humans, anthropomorphic robot design is amongst other reasons used to make people anthropomorphize (or socialize) the robot, treat it socially, act empathetical toward it.

	"[...] the experiment demonstrates that human beings implicitly attribute human-like qualities, such as mental states, to nonhuman agents. This finding was evident on a neurophysiological level as well as behavioural level." \cite{hegel_understanding_2008}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
%
%				HUMAN-LIKE DESIGN IN ROBOTS
%
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Human-like Design in Robots}
\label{sec:4}

	Anthropomorphic design means an imitation of human form (or natural form, in a broader understanding) \cite{disalvo_seduction_2003}. Concepts of anthropomorphic or other life-like forms can be found in a variety of interactive objects and effects of this design approach are studied in disciplines such as affective computing, tangible interaction or industrial design. In a robot, anthropomorphic design can be realized in \textit{1)} a robot's physical (visible) form / shape (embodiment / appearance), \textit{2)} its behavior (e.g. motion), and \textit{3)} the kind of interaction / communication (e.g. modality) that it enables or triggers. Especially socially interactive robots often make use of `human social' behavior cues, such as express / perceive emotions, communicate with high-level dialogue, learn / recognize models of other agents, establish / maintain social relationships, use natural cues (gaze, gestures, etc.), exhibit distinctive personality and character, or learn / develop social competencies \cite{fong_survey_2003}.

\subsection{Human-like embodiment (form / shape)}
\label{sec:4.1}

	The degree of human-like shape in a robot, also its morphological similarity, is the extent to which a non-human agent's observable features look human-like. \cite{epley_seeing_2007} Fong \textit{et al.} classify four categories of a robot's aesthetic form: \cite{fong_survey_2003}

\begin{itemize}
	\item anthropomorphic: structurally and functionally similar to a human
	\item zoomorphic: imitation of forms of living creatures, e.g. animal or pet design
	\item caricatured: using a character or caricature form, e.g. inspired from animation
	\item functional: reflecting the task a robot should perform
\end{itemize}

	For some robots, it seems to be difficult to assign them to only one of these categories. How to categorize, for instance, a mainly functional robot which has only a human-like head? It is also interesting that each of the four categories follows specific design principles to fulfill different goals. For instance, zoomorphic robots seem to help creating a "companionship" relation (e.g. similar to the owner-pet relation), whereas the anthropomorphic design seems to foster rather a human-social relation between the robot and the human and also tries to give the impression of the robot being a more sophisticated interaction partner \cite{disalvo_all_2002,fong_survey_2003,kiesler_mental_2002}. Accordingly, a robot's functionality should be reflected in it's design because it strongly impacts what kind of expectations people have of the robot \hl{ref, matching hypothesis}: \textit{"The device's visual appearance will often shape first impressions and can therefore play a considerable role in establishing first expectations."} \cite{schmitz_concepts_2011} What however is the best design for a multi-purpose robot that not only vacuums floors but also aims to interact socially with the user? This seems to be a fundamental question in HRI and the design of robots. Interestingly, it has been observed that body parts of a robot that are associated with senses could indicate that the robot is capable of perceiving the corresponding modality (e.g. eyes suggest seeing and ears hearing, respectively. \cite{schmitz_concepts_2011} Schmitz calls this notion \textbf{anthropomorphic affordances}, which describe affordances of an artifact that are impacted by its anthropomorphic shape and suggest to a user a  specific action or interaction. Consequently, if a more human-like shaped robot leads to higher expectations from the user side, it seems to be exeptionally difficult at this moment, to build a satisfying anthropomorphic robot. Moreover, there are also practical affordances that a robot's shape brings along. A legged robot is supposed to be able to walk and climb stairs whereas a wheeled one would probably not be able to do so. \hl{Sullivan: form follows funtion!}

\subsection{Human-like behavior}
\label{sec:4.2}

	Besides anthropomorphic shape, also a robot's behavior, e.g. the particular way of how it moves, can be human-inspired (which is in fact often defined by its morphology). According to Epley \textit{et al.} \textit{"at least two dimensions of similarity seem particularly important for anthropomorphism to occur -- similarity in motion and similarity in morphology"} \cite{epley_seeing_2007}. Similarity in motion might not only be walking on two feet but also the speed of movements of a robot, which when adapted to a human, have a positive effect on the usability and perception of the robot from the user cite \hl{ref!!}. The aspect is less important for robots in automation (e.g. assembly lines, production) which usually do not directly interact with humans.

	Another aspect of human-like behavior in robots is autonomy and pro-activity. Schmitz argues that both can be a fundamental strategy in order to evoke anthropomorphic / zoomorphic interpretation \cite{schmitz_concepts_2011} \hl{ref 33}. \hl{more on autonomy and pro-activity, transparency}

	"On a next level, \textbf{stereotypical behaviour}, which expresses e.g. shyness of curiosity, addresses more complex processes but adds essentially to anthropomorphic strategies [38] [46]." \cite{schmitz_concepts_2011}

	\hl{Severin: mention the need to be "complete enough not to be predictable" --> toys that are predictable are quickly boring and humans are really good at identifying simple logical behaviors. / Julia: role of uselessness in robots, surprise factor}

\subsection{Human-like interaction / communication}
\label{sec:4.3}

	"The mere \textbf{presence of voice} is another strong trigger for anthropomorphic perception \hl{(33)}, irrespective of contents and sounds." \cite{schmitz_concepts_2011}

	"Besides speech, the acoustic channel can be used to deliver alternative feedback that resembles \textbf{life-like, physiological sounds or haptics} instead of conventional feedback, for example pulse, breath, snore or cough [...]." \cite{schmitz_concepts_2011}

Others: proxemics

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
%
%				DOES ANTHROPOMORPHISM MAKE ROBOTS MORE SOCIAL?
%
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Does anthropomorphism make robots more social?}
\label{sec:5}

	In general, it is suggested that increasing human-likeness of a robot	 will lead to more perceived \textit{affinity} from the human side \cite{mori_uncanny_1970}. This theoretical concept is also supported by psychological determinants of perceiving human-likeness in something non-human: \textit{"the more similar in appearance, the more people are likely to use themselves as a source of induction and anthropomorphize these nonhuman agents"} \cite{epley_seeing_2007}. Further, empirical studies have shown that robots with human-like forms can enhance social responses from humans which in turn can have a positive impact on acceptance \cite{venkatesh_theoretical_2000,duffy_anthropomorphism_2003,goetz_cooperation_2002}.  People responded more positively to an artifact that displayed human-like behavioral characteristics (emotions, facial expression) in contrast to a purely functional design \cite{eyssel_anthropomorphic_2010,krach_can_2008,reeves_media_1996,riek_how_2009}. Overall, these results suggest that human-like features in robots enhance anthropomorphism, and in turn create a social view toward the robot.

	"The anthropomorphic design of human-machine interfaces is inevitable. The important criterion is to seek a balance between people's expectations and the machines capabilities." \cite{duffy_anthropomorphism_2002}

	"What is the ideal set of human features that could supplement and augment a robots  social functionality?" \cite{duffy_anthropomorphism_2002}

	Though, the 'anthropomorphic design principle" seems beneficial, it also raises ethical issues and has been reviewed critically in terms of acceptance. How far do we want a robot to resemble a human or act like a human?

	Findings that support anthropomorphic form in robots because they found people respond with anthropomorphizing these kind of robots, and in turn act more social toward them or accept them more easily:

	\hl{empathy --> check Iolanda's paper}

\subsection{Socially interactive robots}
\label{sec:5.1}

Evaluation and classification of social robots

\subsection{Too much human-likeness?}
\label{sec:5.2}

\begin{figure}\centering
% Use the relevant command to insert your figure file.
% For example, with the graphicx package use
  \includegraphics[scale=0.6]{uncanny-valley.jpg}
% figure caption is below the figure
 \caption{Mashiro Mori, illustration of the \textit{Uncanny Valley}, originally from 1970; picture from a manuscript version of \cite{mori_uncanny_2012}}
 \label{fig:2}       % Give a unique label
 \end{figure}

	The \textit{Uncanny Valley} hypothesis \cite{mori_uncanny_1970} models people's reactions to technologies that resemble a human too close while still not being one (see Figure). The theory hypothesizes that a person's response to a human-like robot would abruptly shift from empathy to revulsion as it approached, but failed to attain, a lifelike appearance \cite{mori_uncanny_1970}. Starting with low degrees of anthropomorphic cues in a robot, humans seem to readily accept and prefer them compared to purely mechanical robots. In general, one can say that up to a certain (yet not very well defined) degree, the more human-like the robot, the more affection it can engender through familiar communication references.

	when slowly increasing its human-likeness, the more affection

The idea of the hypothesis follows Freud's description of the uncanny (a translation from the German word `unheimlich') \hl{ref Freud, The Uncanny}: "it derives its terror not from something externally alien or unknown but - on the contrary - from something strangely familiar which defeats our efforts to separate ourselves from it". \cite{hegel_understanding_2008}

	Also: Simulation Theory

	Findings that oppose anthropomorphic design in robots as people respond negatively to it:

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
%
%				SKEPTICAL REVIEW OF ANTHROPOMORPHISM IN HRI
%
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Does anthropomorphism make robots more social?}
\label{sec:6}

We believe that the prevalent mostly observed anthropomorphic stances in short-term experiments do not fully embrace this complex social phenomenon. For instance, when reading through literature on anthropomorphism in robotics one can get the impression that it is taken as a given fact that once people attribute human characteristics to a robot, they will always keep on doing so.

	short term

	lab context

	fake comparison of different robots that are not appropriate for comparison

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
%
%				OUR MODEL
%
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Initial Model of the Dynamics of Anthropomorphism}
\label{sec:7}

In this section we outline the essence of our initial model of the dynamics of anthropomorphism. This work is still in progress. The ideas we discuss are still incomplete, and their implications for the design of (social) robots and human-robot interaction are still quite speculative. Nonetheless, we believe that even our initial model, incomplete as it is, provides lessons for the understanding and study of anthropomorphism in robotics. However, we view this paper as only setting the stage for further research, realizing full well that it raises many more questions than it answers.

We propose to go beyond the traditional perception of anthropomorphism in robotics as a static feature.  We rather suggest to understand anthropomorphism in HRI as a dynamic, and context-dependent process, which is likely to change over time and with growing user experience with the robot (which we assume comes along with a familiarization and better understanding of the robot). This viewpoint considers the so called \textit{novelty effect} which has been observed during long-term studies with innovative technologies and robots. In the following, we present our understanding of the dynamics of anthropomorphism and try to model this process as a function of time and growing experience.

\subsection{The Initial Capital of Anthropomorphism}
\label{sec:7.1}

	Initially, there is a given potential that a robot will be anthropomorphized. Our proposed function of anthropomorphism starts with this what we call \textit{initial capital} of anthropomorphism (ICA) at time point = 0, which describes the first (imagined) contact to the robot. This time point can temporally be before the first real physical interaction with the robot, for instance, when a person learns about the existence of vacuum-cleaning robots (\textit{e.g.} when one sees an advertisement of the robot, or discusses about it with a friend). In this phase of "pre-interaction", people form initial expectations toward the robot and imagine how they will use / interact with it, before they actually start interacting with it in real. Therefore, the time point = 0 can be understood as user experience = 0. \hl{[pre-adoption, rogers]} How can we hypothetically quantify the ICA? We argue, that the potential to anthropomorphize a robot is mainly determined by three factors, which we would like to introduce as the "Three P's":

\begin{enumerate}

	\item The \textbf{personality} of the human user: Psychological characteristics / determinants that influence a person's tendency to anthropomorphize artifacts, see \cite{epley_seeing_2007}.

	\item The human user's \textbf{perception} of the robot: Characteristics of the robot's form, behavior, and interaction modalities (anthropomorphic design), see \cite{fong_survey_2003}.

	\item The real or imagined \textbf{purpose} of the robot: The task context and role in which the robot is used / experienced (environmental context), see \cite{joosse_what_2013}.

\end{enumerate}

	The ICA builds the sum of some hypothetical values for the "Three P's" and ranges between the theoretical values of 0 and 1.
	For \textbf{personality}, we suggest to apply Epley \textit{et al.}'s psychological \textit{"Three Factory Theory"} of anthropomorphism. For instance, children generally tend to anthropomorphize objects more than adults. Also, a person who lacks social connection is said to be more likely to anthropomorphize. Both aspects would increase the ICA.
	For \textbf{perception}, we understand that a robot that follows an anthropomorphic design (e.g. NAO) leads to a higher ICA than a rather functional robot (e.g. Roomba). Also, a robot that displays facial expressions would increase the ICA. However, \hl{as discussed before} a classification of the "amount" of anthropomorphic design in a robot, as for instance suggested by Fong \textit{et al.} \cite{fong_survey_2003}, can be difficult.
	For \textbf{purpose}, we propose that the real or imagined context in which a robot is used, impacts how far the robot will be attributed human-social characteristics. We	draw on findings such as presented in Joosse \textit{et al.}. The authors showed that when the same robot (NAO) is used in a different task context (cleaning task \textit{vs.} tour guide), this influences the perception of the "personality" of the robot. In general, we think that a robot which is (imagined to be) used in a social, entertaining or playful context leads to a higher ICA than a robot which is used for a serious task (security, rescue, etc.). This idea receives support from \hl{XX (Kiesler / Goetz?)} work that revealed that people prefer a serious robot for serious tasks and a less serious robot for more playful tasks \hl{REF}. Also, we suggest that the environmental context in which people experience and interact with the robot impacts the ICA. When several people who might be friends interact simultaneously with the robot this might lead to an increased ICA \hl{study: people are more emotional when watching TV in company than when watching TV on their own}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
%
%				DISCUSSION
%
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Discussion}
\label{sec:8}

\subsection{Effect of Context of Use and Purpose of the Robot}
\label{sec:8.1}
Frederic: role of uselessness

\begin{description}
	\item[\textbf{Hypothesis 1}] A person's tendency to anthropomorphize a robot is impacted by the context of use and purpose of the robot. A social context and purpose of the robot increases anthropomorphism. \textit{(context and purpose of the robot)}
\end{description}

\subsection{Effect of Time and Familiarization}
\label{sec:8.2}

	The \textit{context of use} is related to the purpose (and functionality) of the robot and influences the user interaction experience. With \textit{time}, we refer to long-term interaction with the robot, which is related to what has been described as 'novelty effect' but also accounts for the user getting used to the robot. Consequently, we propose that anthropomorphism is not static but likely to change, due to what we call \textit{dynamics}, in space and time.

	As outlined in section \hl{XX}, the tendency to anthropomorphize is motivated by a person's wish to make sense of an agent which might be difficult to understand (in its functionality or behavior, for instance). In turn, a user might ascribe intentions or emotions to the system because the systems output was unexpected for the user. Based on this explanation, we estimate that when the user has familiarized herself / himself with the system, thus reached the point of when the system is usable and explainable, the tendency to anthropomorphize decreases. Therefore, our second hypothesis is as follows:

\begin{description}
	\item[\textbf{Hypothesis 2}] A person's tendency to anthropomorphize a robot decreases over time and with growing experience the person has with the robot. \textit{(familiarize oneself with the robot)}
\end{description}

Given our first hypothesis from above, this might not hold over all contexts; more concretely, probably not in a social context of usage.

	Smart innovative devices, such as personal domestic robots, might demand from a human user spontaneous usage of an unfamiliar system. Such situations will require that a user should be able to build up a mental model quickly, which particularly holds for novice users \cite{schmitz_concepts_2011}.

	Eddy \textit{et aél.} points out that familiarity increases the tendency to anthropomorphize \cite{eddy_attribution_1993}.

	"As shown in several psychological experiments [13,24] and pointed out by Watt [25], familiarity may also ease social acceptance and even tend to increase people's tendency to anthropomorphize [16]." \cite{duffy_anthropomorphism_2003}

\subsection{Personal characteristic effects in anthropomorphizing}
\label{sec:8.3}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
%
%				CONCLUSION
%
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Conclusion}
\label{sec:9}

	Anthropomorphism is a social phenomenon, which seems to be natural on one side and very complex on the other side. It is a mechanism within oneself that makes a human observer think and treat a non-human agent as if it would have some human (social) characteristics, and ascribe to it intentions, emotions, or thoughts, for instance. In accordance with other researchers, we also think that the term is sometimes misused or misunderstood \cite{duffy_anthropomorphism_2002}. Concerning robotics, we do not think that we can speak of anthropomorphism when a person simply refers to physical parts of a robot using terms that describe a human body, such as arm, head, fingers, etc.. We believe that this is not anthropomorphism in its true sense because the person might simply take advantage of the physically resembling shape instead of truly ascribing human (social) characteristics to the robot.

%\subsection{Subsection title}
%\label{sec:X.X}
%as required. Don't forget to give each section
%and subsection a unique label (see Sect.~\ref{sec:1}).
%\paragraph{Paragraph headings} Use paragraph headings as needed.
%\begin{equation}
%a^2+b^2=c^2
%\end{equation}

% For one-column wide figures use
% \begin{figure}
% Use the relevant command to insert your figure file.
% For example, with the graphicx package use
%  \includegraphics{example.jpg}
% figure caption is below the figure
% \caption{Please write your figure caption here}
% \label{fig:1}       % Give a unique label
% \end{figure}
%
% For two-column wide figures use
% \begin{figure*}
% Use the relevant command to insert your figure file.
% For example, with the graphicx package use
%  \includegraphics[width=0.75\textwidth]{example.eps}
% figure caption is below the figure
% \caption{Please write your figure caption here}
% \label{fig:2}       % Give a unique label
% \end{figure*}
%

\begin{acknowledgements}
AJung Moon, Aude Billard.\\
\end{acknowledgements}

% BibTeX users please use one of
 \bibliographystyle{spbasic}      % basic style, author-year citations
%\bibliographystyle{elsart-harv}
%\bibliographystyle{spmpsci}      % mathematics and physical sciences
%\bibliographystyle{spphys}       % APS-like style for physics
\bibliography{anthropomorphism}   % name your BibTeX data base

%\begin{thebibliography}{42}
%\providecommand{\natexlab}[1]{#1}
%\providecommand{\url}[1]{{#1}}
%\providecommand{\urlprefix}{URL }
%\expandafter\ifx\csname urlstyle\endcsname\relax
%  \providecommand{\doi}[1]{DOI~\discretionary{}{}{}#1}\else
%  \providecommand{\doi}{DOI~\discretionary{}{}{}\begingroup
%  \urlstyle{rm}\Url}\fi
%\providecommand{\eprint}[2][]{\url{#2}}
%
%
%\bibitem[{Young et~al(2008)Young, Hawkins, Sharlin, and
%  Igarashi}]{young_toward_2008}
%Young JE, Hawkins R, Sharlin E, Igarashi T (2008) Toward acceptable domestic
%  robots: Applying insights from social psychology. International Journal of
%  Social Robotics 1(1):95--108
%
%
%\end{thebibliography}

% Non-BibTeX users please use
% \begin{thebibliography}{}
%
% and use \bibitem to create references. Consult the Instructions
% for authors for reference list style.
%
% \bibitem{RefJ}
% Format for Journal Reference
% Author, Article title, Journal, Volume, page numbers (year)
% Format for books
% \bibitem{RefB}
% Author, Book title, page numbers. Publisher, place (year)
% etc
% \end{thebibliography}

%\paragraph{ }
%\begin{description}
$\newline$

\textbf{Julia Fink} is a PhD student in Human-Robot Interaction at EPFL. Her work focusses on the analysis of interaction, user experience and acceptance of robots in domestic spaces. She has a multi-disciplinary background in Media, Technology, Communication, and Interaction Studies. \\

\textbf{Dr. S\'{e}verin Lemaignan} is a postdoctoral researcher at EPFL. ...  \\

\textbf{Prof. Pierre Dillenbourg} is professor of learning technologies at EPFL. Former teacher in elementary school, he graduated in educational science (University of Mons, Belgium). He obtained a PhD in computer science from the University of Lancaster (UK), in the field of educational applications of artificial intelligence.  His work covers various domains of computer-supported collaborative learning (CSCL), ranging from novel interfaces for face-to-face collaboration (interactive furniture, tangibles, paper computing) to more cognitive projects on dual eye tracking.
%\end{description}

\end{document}
% end of file template.tex

### 2013-05-17 anthropomorphism.tex
Remove the creation of the sample EPS file in .tex preamble
Moved figures to there own directory
Added the figure 'Dynamics of anthropomorphism'

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-% First comes an example EPS file -- just ignore it and
-% proceed on the \documentclass line
-% your LaTeX will extract the file if required
-\begin{filecontents*}{example.eps}
-%!PS-Adobe-3.0 EPSF-3.0
-%%BoundingBox: 19 19 221 221
-%%CreationDate: Mon Sep 29 1997
-%%Creator: programmed by hand (JK)
-%%EndComments
-gsave
-newpath
-  20 20 moveto
-  20 220 lineto
-  220 220 lineto
-  220 20 lineto
-closepath
-2 setlinewidth
-gsave
-  .4 setgray fill
-grestore
-stroke
-grestore
-\end{filecontents*}
-%
 \RequirePackage{fix-cm}
@@
 \usepackage{graphicx}
+\graphicspath{{figs/}}
+\usepackage{tikz}
+\usetikzlibrary{shapes}
 %
+\usepackage{amsmath} 
 \usepackage{mathptmx}      % use Times fonts if available on your TeX system
@@
 
+\begin{figure*}[htb]
+\centering
+
+\begin{tikzpicture}
+
+% background shading
+\path[fill=gray!20] (0,0) rectangle (0.6,5.5);
+\path[fill=gray!50] (0.6,0) rectangle (5.2,5.5);
+\path[fill=gray!20] (5.2,0) rectangle (9.8,5.5);
+\draw(0,5.5) node[anchor=south west] {\scriptsize \sc Initialization};
+\draw(3,5.5) node[anchor=south] {\scriptsize \sc Familiarization};
+\draw(7.5,5.5) node[anchor=south] {\scriptsize \sc Stabilization};
+% horizontal axis
+\draw[->] (0,0) -- (10,0) node[anchor=north] {$t$};
+\draw(5,-0.1) node[anchor=north] {\scriptsize Duration of interaction};
+
+% vertical axis
+\draw[->] (0,0) -- (0,6) node[anchor=east] {};
+\draw(-0.8,3) node[rotate=90,anchor=south] {\scriptsize Normalized level of anthropomorphism};
+
+\draw (-0.05, 3) -- (0.05, 3) node[anchor=east] {\scriptsize $\text{ICA}_{\mathcal B}$};
+\draw (-0.05, 4.1) -- (0.05, 4.1) node[anchor=east] {\scriptsize $\text{ICA}_{\mathcal A}$};
+\draw (-0.05, 0.6) -- (0.05, 0.6) node[anchor=east] {\scriptsize $\text{ICA}_{\mathcal C}$};
+
+% vertical axis - end
+\draw[->] (9.8,0) -- (9.8,2) node[anchor=east] {};
+\draw (9.8, 0.8) node[anchor=west] {\scriptsize SLA$_\mathcal{E}$};
+\draw (9.8, 1.4) node[anchor=west] {\scriptsize SLA$_\mathcal{D}$};
+\draw (9.8, .2) node[anchor=west] {\scriptsize SLA$_\mathcal{F}$};
+
+\draw[<-] (0.65,5) -- (0.8,5.2) node[anchor=east] {};
+\draw (0.9,5.3) node[anchor=west] {\tiny \it novelty effect};
+
+\draw[dotted] (0, 5) -- (6.2,5);
+\draw[dotted] (0, 3) -- (6.2,3);
+\draw[<->] (6.1,3) -- (6.1,5) node[anchor=east] {};
+\draw (6.2,4) node[rotate=90, anchor=north] {\tiny Expectation mismatch};
+
+\draw[<-] (1.7,4.4) -- (3.2,4.1) node[anchor=east] {};
+\draw[<-] (2.85,3.3) -- (3.2,4.1) node[anchor=east] {};
+\draw (3.2,4.1) node[anchor=west] {\tiny \it disruptive behaviors};
+%%%%%
+%% CURVES
+%%%%
+\begin{scope}[yscale=-1,shift={(-0.125,-0.4)}]
+
+% output of inkscape2tikz
+\path[draw=black]
+    (0.1250,-2.5620) .. controls (0.1451,-3.7193) and (0.4645,-4.5602) ..
+    (0.7044,-4.5633) .. controls (0.8413,-4.5633) and (0.9599,-4.5104) ..
+    (1.0794,-4.3971) .. controls (1.1989,-4.2841) and (1.3191,-4.1185) ..
+    (1.4588,-3.9181) .. controls (1.5287,-3.8183) and (1.5610,-4.1413) ..
+    (1.6381,-4.1420) .. controls (1.7378,-4.1420) and (1.6515,-3.6434) ..
+    (1.9554,-3.2280) .. controls (2.1466,-2.9667) and (2.3889,-2.7023) ..
+    (2.6819,-2.4292) .. controls (2.7551,-2.3607) and (2.7727,-2.8119) ..
+    (2.8771,-2.8180) .. controls (2.9742,-2.8180) and (2.9594,-2.2108) ..
+    (3.1665,-2.0209) .. controls (3.3340,-1.8673) and (3.5379,-1.7527) ..
+    (3.7508,-1.6236) .. controls (5.8366,-0.4852) and (8.0977,-0.2106) ..
+    (10.1250,-0.1860);
+\path[draw=black, dashed]
+    (0.1250,-3.6924) .. controls (0.1103,-4.0298) and (0.4645,-4.5602) .. 
+    (0.7044,-4.5633)
+    (3.7508,-1.6236) .. controls (4.9579,-0.9555) and (8.1358,-0.8261) .. 
+    (10.1250,-0.7946);
+\path[draw=black,dashed]
+    (0.1250,-0.1953) .. controls (0.1804,-3.3871) and (0.4645,-4.5602) .. 
+    (0.7044,-4.5633) .. controls (0.8413,-4.5633) and (0.9599,-4.5104) .. 
+    (1.0794,-4.3971)
+    (3.7508,-1.6236) .. controls (4.7654,-0.8505) and (6.5955,0.3538) .. 
+    (10.1250,0.4062);
+
+\end{scope}
+
+\end{tikzpicture}
+
+\caption{Dynamics of anthropomorphism. We distinguish three main phases:
+\emph{initialization}, \emph{familiarization} and \emph{stabilization}. In the
+pre-interaction phase, users build an \emph{initial capital of
+anthropomorphism} (ICA). Once the interaction starts, the level of
+anthropomorphism increases due to the \emph{novelty effect}, and then decreases
+to reach a \emph{stabilized level of anthropomorphism} (SLA).
+During the interaction, unpredicted behaviors of the robot (\emph{disruptive
+behaviors}) locally increase the level of anthropomorphism.}
+\label{fig|dynamics}
+\end{figure*}
+
 In this section we outline the essence of our initial model of the dynamics of anthropomorphism.

### 2013-05-17 anthropomorphism.tex
Added figure on cognitive phases

@@
 behaviors}) locally increase the level of anthropomorphism.}
-\label{fig|dynamics}
+\label{fig:dynamics}
 \end{figure*}
@@
 \label{sec:8}
+
+\subsection{Anthropomorphism and Cognitive Models}
+\label{sec:cognitivemodel}
+
+\begin{figure}[htb]
+\centering
+%\resizebox{\linewidth}{!}{
+\begin{tikzpicture}[scale=0.8, transform shape]
+\baselineskip=8pt
+
+% horizontal axis
+\draw[->] (0,0) -- (10,0) node[anchor=north] {$t$};
+% labels
+\draw   (2,0) node[anchor=north] {Phase I}
+        (5,0) node[anchor=north] {Phase II}
+        (8,0) node[anchor=north] {Phase III};
+
+\draw[dotted] (3.5, -0.5) -- (3.5,6);
+\draw[dotted] (6.5, -0.5) -- (6.5,6);
+
+% vertical axis
+\draw[-|] (0,0) -- (0,6) node[anchor=east] {};
+% Us
+\draw[thick] (0,0) -- (1,2) -- (3,2) -- (4,4) -- (6,4) -- (7,6) -- (10,6);
+
+\draw (2.2,2) node[align=center] {\scriptsize{sub-cognitive}\\\scriptsize{anthropomorphism}}; %label
+\draw (5,3.85) node[align=center] {\scriptsize{projection of existing}\\\scriptsize{mental models}\\\scriptsize{\it (familiarity)}}; %label
+\draw (8.5,5.85) node[align=center] {\scriptsize{adapted mental model} \\ $\to$ \scriptsize{adapted interaction}\\\scriptsize{\it (antropomorphic or not)}}; %label
+
+\draw (2.2,1) node[align=left] {\tiny{\it observation (shape, motion, sound)}}; %label
+\draw (5.2,3) node[align=left] {\tiny \it observation (interactive behaviour) \\ \tiny \it or short interaction}; %label
+\draw (7.8,5) node[align=left] {\tiny \it contextualized interaction}; %label
+
+\end{tikzpicture}
+%}
+\caption{The three cognitive phases of anthropomorphism: Phase I is the instinctive,
+sub-cognitive identification of living peers. {\it Empathy} [TO DISCUSS] is characteristic
+of this stage. After longer observation or short, uncontextualized interaction
+(typically, a lab environment), the user enters Phase II: the user projects a
+mental model he/she is already familiar with onto the robot. This leads to
+expectation regarding the cognitive abilities of the robot. After longer {\it
+contextualized} interaction (typically, at home), the user enters Phase III of
+anthropomorphism: the user recomposes an accurate mental model of the robot,
+based on experience. This leads to adapted interaction modalities, that may
+still be anthropomorphic, or not.}
+\label{fig:cognitivemodel}
+\end{figure}
+
+Figure~\ref{fig:cognitivemodel} offers a cognitive perspective on the dynamics
+of anthropomorphism presented in the previous section.
 

### 2013-05-17 anthropomorphism.tex
Added section on disruptive behaviors

@@
 \usepackage{multirow}
-% insert here the call for the packages your document requires
-%\usepackage{latexsym}
-% etc.
-%
-% please place your own definitions here and don't use \def but
-% \newcommand{}{}
-%
-% Insert the name of "your journal" with
+\usepackage{array}
+
+\usepackage[draft]{fixme}
+
 \journalname{Int J Soc Robot}
-%
 
@@
 
-	Eddy \textit{et aél.} points out that familiarity increases the tendency to anthropomorphize \cite{eddy_attribution_1993}.
+	Eddy \textit{et al.} points out that familiarity increases the tendency to anthropomorphize \cite{eddy_attribution_1993}.
 
@@
 \label{sec:8.3}
+
+\subsection{Role of disruptive behaviors}
+\label{sec:disruptive}
+
+Common observation of naive people (children or adults) interacting with robots
+shows that unexpected behaviors of the robot has a notable impact on
+interaction.
+
+During a normal interaction with the robot, the user iteratively refine its own
+model of the behavior of the robot. As explained in previous sections, as the
+user improves its model of the robot actions, it also improves its ability to predict
+the actions and thus, the user tends to anthropomorphize less.
+
+We emit the hypothesis that an unexpected robot behavior leads the user to
+suddently restate its behavioral model of the robot and will temporarly lead to
+an increase of the level of anthropomorphism (see the spikes on
+Figure~\ref{fig:dynamics}).
+
+\begin{figure}
+\begin{center}
+    \begin{tabular}{ | >{\centering\arraybackslash}m{1.5cm} | >{\centering\arraybackslash}m{2cm} | >{\centering\arraybackslash}m{2cm} |}
+    \hline
+     & Unplanned by the robot & Planned by the robot \\ \hline
+    Perceived as non-intentional & case I  & case IIIa  \\ \hline
+    Perceived as intentional &  case IIIb & case II  \\ \hline
+    \end{tabular}
+\end{center}
+\caption{
+    Behaviors of the robot that are unexpected by the user may be intentional
+    (the robot has planned the behavior) or not (typically, a failure:
+    misdetection, bug,...). Independently of that, the behavior may be
+    \emph{perceived} by the user as intentional or not.}
+\label{fig:perceptionUnexpectedBehavior}
+\end{figure}
+
+When talking about \emph{unexpected robot behaviors}, several distinct cases
+must be considered, summarized in Table~\ref{fig:perceptionUnexpectedBehavior}.
+
+If the unexpected behavior is not planned, and perceived as such by the human
+(case I), the human can interpret that the robot is faillible. If the robot
+explicitly states its failure (for instance, by saying ``I'm lost!''), the
+behavior is then called \emph{transparent} \fixme{cite here, Julia?}, and the
+user may besides hypothesize that the robot has \emph{introspective}
+capabilities, which in turn may leads to higher anthropomorphism level.  On the
+contrary, if the robot shows no sign of recognizing its own failure, the user
+may ascribe a lower level of anthropomorphism to the robot.
+
+In case II, the robot voluntary executes a behavior that is unexpected by the
+human, and the human perceives it rightfully as an \emph{intentional} behavior.
+For instance, the human asks the robot to go somewhere, and the robot refuses,
+saying ``I do not want to go there''. In that case, we expect to see an
+increase of anthropomorphism attribution due to the human ascribing
+intentionality to the robot.
+
+Case IIIa and IIIb correspond to misinterpretations of the robot behavior. Case
+IIIb may actually lead to increased level of anthropomorphism since the human
+will (wrongfully) attribute intentionality to the robot, while case IIIa is
+expected to lead to a lower anthropomorphism level.  However, in those two
+cases, the next occurrence of an expected behavior, if correctly interpreted
+(case I or II), is likely to lead to stronger effects due to a larger delta
+between expectations and actual observed behavior.
+
+%% experience -> unexpected behaviour should not impact the interaction child-robot BEFORE the theory of mind is established!
 

### 2013-05-21 anthropomorphism.tex
new paragraph to introduce our model

@@
 
-We propose to go beyond the traditional perception of anthropomorphism in robotics as a static feature.
-We rather suggest to understand anthropomorphism in HRI as a dynamic, and context-dependent process, which is likely to change over time and with growing user experience with the robot (which we assume comes along with a familiarization and better understanding of the robot).
-This viewpoint considers the so called \textit{novelty effect} which has been observed during long-term studies with innovative technologies and robots.
-In the following, we present our understanding of the dynamics of anthropomorphism and try to model this process as a function of time and growing experience.
+We propose to go beyond the traditional perception of anthropomorphism in robotics as a static feature that once observed during a short-term interaction reflects a sustaining social effect.
+So far, the HRI community has not investigated how anthropomorphism in human-robot interactions evolves over time (during the process of adopting a robot, for instance).
+However, based on an extensive literature review and our own work, we believe that the social phenomenon will not always be the same but evolve over time, with growing interaction and experience with the robot.
+We would like to present an extension to the understanding of anthropomorphism in HRI which takes time / interaction / experience / familiarization into account.
+Consequently, we suggest to understand anthropomorphism in HRI as a dynamic process, which is likely to change over time and with growing user experience with the robot (which we assume comes along with a familiarization and better understanding of the robot).
+This viewpoint also considers the so called \textit{novelty effect} which has been observed during long-term studies with innovative technologies and robots.
+In the following, we present our understanding of the dynamics of anthropomorphism and try to model this process as a function of time and growing experience (see Figure \ref{fig:dynamics}).
 

### 2013-05-21 anthropomorphism.tex
new figure and new text multi-layered anthropomorphism

@@
 \usepackage{array}
+\usepackage{fixltx2e}
+\usepackage{textcomp}
 
@@
 Consequently, Duffy \cite{duffy_anthropomorphism_2002} argues that terms might even be misused.
-For instance, some researchers refer to \textit{"the robot's level of anthropomorphism"} \cite{bartneck_is_2007}, however, others argue that anthropomorphism emerges in the \textit{interaction} between the technology and the user, thus a system or an artifact does not "contain anthropomorphism" \textit{per se} \cite{persson_anthropomorphism_2000}.
+For instance, some researchers refer to \textit{"the robot's level of anthropomorphism"} \cite{bartneck_is_2007}, however, others argue that anthropomorphism emerges in the \textit{interaction} between the technology and the user, thus a system or an artifact does not "contain anthropomorphism" \textit{per se} \cite{persson_anthropomorphism_2000} but only gives rise to the process of anthropomorphizing in a given user and situation.
 Further, robotics is a multi-disciplinary field and researchers from very different domains might have diverse or even contradictory understandings of anthropomorphism.
@@
 This finding was evident on a neurophysiological level as well as behavioural level." \cite{hegel_understanding_2008}
+
+\subsection{Anthropomorphism as a multi-layered phenomenon}
+\label{sec:3.4}
+
+Anthropomorphism can also be viewed as an \textit{experience} that arises in the \textit{interaction} between a set of user expectations and external reality \cite{persson_anthropomorphism_2000}, (see Figure)
+
+an \textit{understanding} of complex -- not necessarily human -- patterns of behavior in the world, in order to make sense of it: \textit{"Anthropomorphism is a way of simplifying and thereby making sense of the environment by projecting a host of expectations about human life onto aspects of that environment."} \cite{persson_anthropomorphism_2000}
+Persson \textit{et al.} explored anthropomorphism triggered by computer interfaces and system and we believe their perspective on anthropomorphism could also be applied in HRI.
+The authors suggest that the social phenomenon is not only one single process but that it involves several levels, \textit{e.g.} primitive psychology, folk-psychology, social stereotypes, and emotional anthropomorphism.
+We would like to take up the proposition to discriminate different levels of anthropomorphism, since each has its own characteristics and involves specific types of user expectations.
+This differentiation could allow to draw inferences on the human-robot relationship from the observed level of anthropomorphism.
+
+\begin{figure}\centering
+% Use the relevant command to insert your figure file.
+% For example, with the graphicx package use
+  \includegraphics[scale=0.42]{persson_anthropomorphism.png}
+% figure caption is below the figure
+ \caption{Anthropomorphism emerges in the (real or imagined) interaction between robot and user; illustration taken from \cite{persson_anthropomorphism_2000} \hl{maybe we don't put the figure here, it was just to illustrate what I mean}}
+ \label{fig:2}       % Give a unique label
+ \end{figure}
 
@@
 	Initially, there is a given potential that a robot will be anthropomorphized.
-Our proposed function of anthropomorphism starts with this what we call \textit{initial capital} of anthropomorphism (ICA) at time point = 0, which describes the first (imagined) contact to the robot.
-This time point can temporally be before the first real physical interaction with the robot, for instance, when a person learns about the existence of vacuum-cleaning robots (\textit{e.g.} when one sees an advertisement of the robot, or discusses about it with a friend).
-In this phase of "pre-interaction", people form initial expectations toward the robot and imagine how they will use / interact with it, before they actually start interacting with it in real.
-Therefore, the time point = 0 can be understood as user experience = 0.
-\hl{[pre-adoption, rogers]} How can we hypothetically quantify the ICA?
-We argue, that the potential to anthropomorphize a robot is mainly determined by three factors, which we would like to introduce as the "Three P's":
+Our proposed function to model the dynamics of anthropomorphism starts with this what we call \textit{initial capital of anthropomorphism} (ICA) at time point $t_{0}$, which describes the first (real or imagined) contact to the robot (see Figure \ref{fig:dynamics}).
+Time point $t_{0}$ can temporally be before the first real physical interaction with the robot, for instance, when a person learns about the existence of vacuum-cleaning robots and imagines using one (\textit{e.g.} when one watches an advertisement of the robot, or observes one at a trade show).
+In this stage of "pre-interaction", people form initial expectations toward the robot and imagine how they will use / interact with it.
+Time point $t_{0}$ can be understood as duration of interaction = 0 and user experience = 0.
+How can we hypothetically quantify the ICA on a normalized scale of anthropomorphism?
+For this, we suggest, what we call the \textit{"Three P's"}.
+These are three main factors that \textit{a priori} determine the potential to anthropomorphize a robot:
 
@@
 
-	The ICA builds the sum of some hypothetical values for the "Three P's" and ranges between the theoretical values of 0 and 1.
+	The ICA comprises some hypothetical values for each of the \textit{"Three P's"}, such that different ICA values can be obtained, given the robot, human user, and environmental context.
 	For \textbf{personality}, we suggest to apply Epley \textit{et al.}'s psychological \textit{"Three Factory Theory"} of anthropomorphism.
@@
 Both aspects would increase the ICA.
+This means that, one and the same robot used in a different context or by a different user, can lead to a different ICA.
+
 	For \textbf{perception}, we understand that a robot that follows an anthropomorphic design (e.g.
@@
 However, \hl{as discussed before} a classification of the "amount" of anthropomorphic design in a robot, as for instance suggested by Fong \textit{et al.} \cite{fong_survey_2003}, can be difficult.
+
 	For \textbf{purpose}, we propose that the real or imagined context in which a robot is used, impacts how far the robot will be attributed human-social characteristics.
@@
 When several people who might be friends interact simultaneously with the robot this might lead to an increased ICA \hl{study: people are more emotional when watching TV in company than when watching TV on their own}.
+
+\subsection{Anthropomorphism during Initialization Phase}
+\label{sec:7.2}
+
+(\textit{INITIALIZATION})
+
+\subsection{Anthropomorphism during Familiarization Phase}
+\label{sec:7.3}
+
+\subsection{Anthropomorphism during Stabilization Phase}
+\label{sec:7.4}
 

### 2013-05-22 anthropomorphism.tex
Moved paragraph on the limit of our model to the discussion introduction

@@
 
-\section{Initial Model of the Dynamics of Anthropomorphism}
-\label{sec:7}
+\section{A Model of the Dynamics of Anthropomorphism}
+\label{sec:dynamics_model}
 
@@
 
-In this section we outline the essence of our initial model of the dynamics of anthropomorphism.
-This work is still in progress.
-The ideas we discuss are still incomplete, and their implications for the design of (social) robots and human-robot interaction are still quite speculative.
-Nonetheless, we believe that even our initial model, incomplete as it is, provides lessons for the understanding and study of anthropomorphism in robotics.
-However, we view this paper as only setting the stage for further research, realizing full well that it raises many more questions than it answers.
-
 We propose to go beyond the traditional perception of anthropomorphism in robotics as a static feature that once observed during a short-term interaction reflects a sustaining social effect.
@@
 \section{Discussion}
-\label{sec:8}
+\label{sec:discussion}
+
+The model of anthropomorphism we propose is still a work in progress. In
+particular, its implications regarding the design of (social) robots and
+human-robot interaction are still to be refined.
+
+In this section, we discuss more speculative aspects and hypothesis that follow
+from the model. These aspects would require further investigation and
+experimental support to be validated.
 

### 2013-05-22 anthropomorphism.tex
Rewrite intro of model + added section to introduce the 3 phases

@@
 \section{Anthropomorphic Design and Anthropomorphism}
-\label{intro}
+\label{sec:intro}
 
@@
 The conclusion builds on the assumption that humans prefer to interact with machines (and robots) in the same way they interact with humans \cite{fong_survey_2003} because they are familiar to these kind of interactions.
-The implicit social mechanism which is exploited, is called \textbf{anthropomorphism}.
+\hl{The implicit social mechanism which is exploited, is called \textbf{anthropomorphism}}\fxfatal{Discuss also \emph{anthropomorphic effects} as the observable part of anthropomorphism}.
 It describes the phenomenon of a person ascribing human-like characteristics (e.g.
@@
 \draw[->] (0,0) -- (0,6) node[anchor=east] {};
-\draw(-0.8,3) node[rotate=90,anchor=south] {\scriptsize Normalized level of anthropomorphism};
+\draw(-0.8,3) node[rotate=90,anchor=south] {\scriptsize Normalized level of anthropomorphic effects};
 
@@
 
-We propose to go beyond the traditional perception of anthropomorphism in robotics as a static feature that once observed during a short-term interaction reflects a sustaining social effect.
-So far, the HRI community has not investigated how anthropomorphism in human-robot interactions evolves over time (during the process of adopting a robot, for instance).
-However, based on an extensive literature review and our own work, we believe that the social phenomenon will not always be the same but evolve over time, with growing interaction and experience with the robot.
-We would like to present an extension to the understanding of anthropomorphism in HRI which takes time / interaction / experience / familiarization into account.
-Consequently, we suggest to understand anthropomorphism in HRI as a dynamic process, which is likely to change over time and with growing user experience with the robot (which we assume comes along with a familiarization and better understanding of the robot).
-This viewpoint also considers the so called \textit{novelty effect} which has been observed during long-term studies with innovative technologies and robots.
-In the following, we present our understanding of the dynamics of anthropomorphism and try to model this process as a function of time and growing experience (see Figure \ref{fig:dynamics}).
-
-\subsection{The Initial Capital of Anthropomorphism}
-\label{sec:7.1}
+So far, the HRI community has not much investigated how anthropomorphism in
+human-robot interactions evolves over time (during the process of
+\emph{adopting} a robot, for instance): we propose to go beyond the traditional
+perception of anthropomorphism in robotics as a static feature that once
+observed during a short-term interaction reflects a sustaining social effect.
+Based on an extensive literature review and our own work \fxfatal{Summarize
+these findings in a specific section!}, we believe that the social phenomenon
+is not always be the same but evolve over time, along with growing interaction
+and experience with the robot.
+
+The model of anthropomorphism we propose (Figure~\ref{fig:dynamics}) represents
+how the level of anthropomorphic effects (\ie observable manifestations of
+anthropomorphism, as defined at section~\ref{sec:intro}) evolves over a
+long-term human-robot interaction. By long-term interaction, we mean direct
+(non-mediated), repeated interaction with the same robot, over (at least) several
+days. The nature of the interaction (goal-directed, entertainment,...) may vary.
+
+The model takes into account the duration of the interaction, the nature of the
+interaction, as well as acquired experience and familiarization mechanisms: We
+also propose to formally introduce a so-called \emph{novelty effect} that
+models the first phase of human-robot interaction, and during which specific
+anthropomorphic effect are observed.
+
+\subsection{Three phases}
+\label{sec:phases}
+
+We distinguish three main phases that describe the evolution of the
+anthorpomorphic effects in a long-term human-robot interaction. They are
+depicted in different shades on Figure~\ref{fig:dynamics}.
+
+First, the \emph{initialization} phase. During this short phase (from a couple
+of seconds to a couple of hours), we observe an increased level of
+antrophomorphism, from an \emph{initial capital of anthropomorphism}
+(detailled in the next section) and a peak of antropomorphic manifestations
+that correspond to the maximum of the \emph{novelty effect}.
+Section~\ref{sec:initialization} details this first phase.
+
+The second phase, \emph{familiarization}, lasts longer (up to several days) and
+models the process of the human getting acquainted to the robot: by observation
+and interaction, the human builds a model of the robot's behaviour that allows
+him/her to predict the robot's actions. We observe a decrease of
+anthropomorphic effects during this phase, that we explain by the acquired
+ability to predict the behaviour of the robot: the initial apparent behavioural
+complexity vanishes, and the robot is considered more and more as a machine.
+Section~\ref{sec:familiarization} discusses the second phase.
+
+The last phase is the \emph{stabilization} phase. The level of anthrpomorphic
+effects tends to stabilize over a longer time, to reach a \emph{stabilized
+level of anthropomorphism} (SLA). The SLA may be null (no anthropomorphic
+effects observed anymore), but it may also remain at an higher level.  This
+third phase, as well as the \emph{stabilized level of anthropomorphism}, are
+discussed in section~\ref{sec:stabilization} below.
+
+\subsection{Initial Capital of Anthropomorphism}
+\label{sec:ica}
 
@@
 \subsection{Anthropomorphism during Initialization Phase}
-\label{sec:7.2}
-
-(\textit{INITIALIZATION})
+\label{sec:initialization}
+
+\paragraph{The Novelty Effect}
+\label{sec:noveltyeffect}
 
 \subsection{Anthropomorphism during Familiarization Phase}
-\label{sec:7.3}
+\label{sec:familiarization}
+
+\paragraph{Disruptive Behaviours}
 
 \subsection{Anthropomorphism during Stabilization Phase}
-\label{sec:7.4}
+\label{sec:stabilization}
+
+\paragraph{Stabilized Level of Anthropomorphism (SLA)}
 

### 2013-05-22 anthropomorphism.tex
Fixed some figure duplicated labels

@@
 Two famous studies on the perception of and attribution to simple things have been done in the mid 1940s: Heider and Simmel's work on the \textit{attribution theory} \cite{heider_experimental_1944} and Michotte's studies on \textit{the perception of causality} \cite{michotte_perception_1963}.
-In both experiments, participants viewed animations of simple shapes, such as circles or triangles (see Figure \ref{fig:2}).
+In both experiments, participants viewed animations of simple shapes, such as circles or triangles (see Figure \ref{fig:animacy_attribution}).
 Asked to describe what they observed, interestingly, most people developed elaborate stories, attributing motivations, emotions and relationships between the objects.
@@
  \caption{Fritz Heider and Mary-Ann Simmel's animated film to study people's tendency to attribute animacy and intention to simple shapes; \textit{An experimental study of apparent behaviour}, 1944}
- \label{fig:2}       % Give a unique label
+ \label{fig:animacy_attribution}       % Give a unique label
  \end{figure}
@@
  \caption{Anthropomorphism emerges in the (real or imagined) interaction between robot and user; illustration taken from \cite{persson_anthropomorphism_2000} \hl{maybe we don't put the figure here, it was just to illustrate what I mean}}
- \label{fig:2}       % Give a unique label
+ \label{fig:anthropomorphism_and_interaction}       % Give a unique label
  \end{figure}
@@
  \caption{Mashiro Mori, illustration of the \textit{Uncanny Valley}, originally from 1970; picture from a manuscript version of \cite{mori_uncanny_2012}}
- \label{fig:2}       % Give a unique label
+ \label{fig:uncanny_valley}       % Give a unique label
  \end{figure}

### 2013-05-22 anthropomorphism.tex
Work on the 'cognitive model of anthropomorphism' section

@@
 	"[...] the experiment demonstrates that human beings implicitly attribute human-like qualities, such as mental states, to nonhuman agents.
-This finding was evident on a neurophysiological level as well as behavioural level." \cite{hegel_understanding_2008}
+This finding was evident on a neurophysiological level as well as behavioral level." \cite{hegel_understanding_2008}
 
@@
 
-	"On a next level, \textbf{stereotypical behaviour}, which expresses e.g.
+	"On a next level, \textbf{stereotypical behavior}, which expresses e.g.
 shyness of curiosity, addresses more complex processes but adds essentially to anthropomorphic strategies [38] [46]." \cite{schmitz_concepts_2011}
@@
 models the process of the human getting acquainted to the robot: by observation
-and interaction, the human builds a model of the robot's behaviour that allows
+and interaction, the human builds a model of the robot's behavior that allows
 him/her to predict the robot's actions. We observe a decrease of
 anthropomorphic effects during this phase, that we explain by the acquired
-ability to predict the behaviour of the robot: the initial apparent behavioural
+ability to predict the behavior of the robot: the initial apparent behavioral
 complexity vanishes, and the robot is considered more and more as a machine.
@@
 
-\paragraph{Disruptive Behaviours}
+\paragraph{Disruptive behaviors}
+\ref{sec:disruptive}
+
+\paragraph{Expectation mismatch}
 
@@
 \paragraph{Stabilized Level of Anthropomorphism (SLA)}
+
+\fxnote{Note that ICA and SLA are NOT correlated}
 
@@
 \draw (2.2,1) node[align=left] {\tiny{\it observation (shape, motion, sound)}}; %label
-\draw (5.2,3) node[align=left] {\tiny \it observation (interactive behaviour) \\ \tiny \it or short interaction}; %label
+\draw (5.2,3) node[align=left] {\tiny \it observation (interactive behavior) \\ \tiny \it or short interaction}; %label
 \draw (7.8,5) node[align=left] {\tiny \it contextualized interaction}; %label
@@
 
+The first cognitive phase we identify that contribute to anthropomorphism is
+actually \emph{pre-cognitive}.\fxfatal{Complete that. Reference to the pleo
+paper}.
+
+After a longer observation period (typically including complete action
+sequences of the robot) or short interaction (touching, short talk like
+greetings), the human enters the cognitive phase II: in this phase, the human
+starts to build a behavioral and cognitive model of the robot that would
+support both the observed and imagined capabilities of the robot. Based on the
+\emph{familiarity thesis}\fxfatal{citation!}, we suggest that the human first
+projects onto the robot mental models of similar agents he/she is already
+familiar with. This may range from animals to adults, through pets and
+children. We hypothesise that the nature of the projected mental model, as well
+as how deep the human engage in this projection, are driven by the same
+parameters as we presented for the \emph{initial capital of anthropomorphism}
+(section~\ref{sec:ica}, p.\pageref{sec:ica}).
+
+We identify a further transition to the cognitive phase III after a
+\emph{contextualized} interaction. A \emph{contextualized} interaction is
+\emph{explicitly purposeful} (the purpose of the interaction, be it purely
+entertainment, is explicit and conscious for the human), and takes place in an
+environment that fosters a stronger cognitive (and possibly affective)
+commitment from the human in the interaction (typically, at home). During this
+interaction, the human iteratively restate and reshape its behavioral and
+mental model of the robot (\emph{how does the robot react to such and such
+situation/input? what does the robot knows about me? about itself? about our
+environment? what can the robot learn?}, etc.).
+
+This mental process heavily depends on the human understanding of the robot
+inner working, as well as his/her own tendency to anthropomorphize (the
+\emph{personality} in ICA factor), but at this stage, the \emph{perception} of
+the robot (its shape for instance) and its intended \emph{purpose} play only a
+minor role. It is mostly a human-centric process.
+
+\paragraph{Relation to the model of anthropomorphism} It must be noted that the
+three cognitive phases we introduce here do not match the
+\emph{initialization}, \emph{familiarization} and \emph{stabilization} phases
+introduced at~\ref{sec:phases}: in particular, cognitive phases I and II are
+both included in the \emph{initialization} phase of the anthropomorphism model.
+
+Sub-cognitive anthropomorphism typically \emph{initiates} the novelty effect by
+rapidly engaging the human in the interaction through this initial projected
+\emph{agency}, whereas cognitive phase II (projection of familiar mental
+models) supports the novelty effect by inducing beliefs that the robot is set
+up with possibly complex cognitive abilities.
+
+The cognitive phase II also overlaps with the \emph{Familiarization} phase: as
+(s)he get used to the robot, we hypothesize the human restate and adapt its
+cognitive model of the robot by iteratively reshaping pre-existant, familiar
+models until it provides a satisfying support to explain and justify the
+observed robot behavior.
+
+A \emph{stable level of anthropomorphism} is reached when the adaptation
+process depicted in cognitive phase III reached a stable state, \ie the human
+experience with the robot is correctly supported by the cognitive model the
+human has built.
+
+\paragraph{Limits} This discussion on the cognitive correlates of the dynamics
+of anthropomorphism are speculative, and only indirectly supported by
+experimental evidence. New experiences need to be designed to specifically test
+these hypothesis.\fxnote{...}
+
 \subsection{Effect of Context of Use and Purpose of the Robot}
@@
 suddently restate its behavioral model of the robot and will temporarly lead to
-an increase of the level of anthropomorphism (see the spikes on
+an increase of the level of anthropomorphism (depicted by the spikes on
 Figure~\ref{fig:dynamics}).
@@
 
-%% experience -> unexpected behaviour should not impact the interaction child-robot BEFORE the theory of mind is established!
+%% experience -> unexpected behavior should not impact the interaction child-robot BEFORE the theory of mind is established!
 

### 2013-05-22 anthropomorphism.tex
Cite Rosenthal-von der Putten on fMRI + emotional reaction
While here, enable support for UTF8

@@
 %
+
+\usepackage[utf8x]{inputenc}
+\usepackage[T1]{fontenc}
+
 \usepackage{graphicx}
@@
 The first cognitive phase we identify that contribute to anthropomorphism is
-actually \emph{pre-cognitive}.\fxfatal{Complete that. Reference to the pleo
-paper}.
+actually \emph{pre-cognitive}. In~\cite{Rosenthal-vonderPutten2013Neural},
+Rosenthal-von der Pütten et al. investigated the neural correlates of emotional
+reactions of human towards robot or other human that showed comparable
+responses. \fxfatal{Complete that. Reference to the pleo paper}.
 

### 2013-05-22 anthropomorphism.tex
Completed my biography

@@
 
-\textbf{Julia Fink} is a PhD student in Human-Robot Interaction at EPFL.
-Her work focusses on the analysis of interaction, user experience and acceptance of robots in domestic spaces.
-She has a multi-disciplinary background in Media, Technology, Communication, and Interaction Studies.
-\\
-
-\textbf{Dr. S\'{e}verin Lemaignan} is a postdoctoral researcher at EPFL. ...  \\
-
-\textbf{Prof.
-Pierre Dillenbourg} is professor of learning technologies at EPFL.
-Former teacher in elementary school, he graduated in educational science (University of Mons, Belgium).
-He obtained a PhD in computer science from the University of Lancaster (UK), in the field of educational applications of artificial intelligence.
-His work covers various domains of computer-supported collaborative learning (CSCL), ranging from novel interfaces for face-to-face collaboration (interactive furniture, tangibles, paper computing) to more cognitive projects on dual eye tracking.
+\textbf{Julia Fink} is a PhD student in Human-Robot Interaction at EPFL. Her
+work focuses on the analysis of interaction, user experience and acceptance of
+robots in domestic spaces. She has a multi-disciplinary background in Media,
+Technology, Communication, and Interaction Studies. \\
+
+\textbf{Dr. Séverin Lemaignan} is a postdoctoral researcher at EPFL. His work
+focuses on robotics and its application to education and learning, with an
+emphasis on human-robot interaction. He obtained in 2012 a PhD from the
+CNRS/LAAS (France) and the Technical University of Munich (Germany) in
+cognitive robotics, and has a background both in mechanical engineering and
+education sciences.\\
+
+\textbf{Prof. Pierre Dillenbourg} is professor of learning technologies at
+EPFL. Former teacher in elementary school, he graduated in educational science
+(University of Mons, Belgium). He obtained a PhD in computer science from the
+University of Lancaster (UK), in the field of educational applications of
+artificial intelligence.  His work covers various domains of computer-supported
+collaborative learning (CSCL), ranging from novel interfaces for face-to-face
+collaboration (interactive furniture, tangibles, paper computing) to more
+cognitive projects on dual eye tracking.
 %\end{description}

### 2013-05-23 anthropomorphism.tex
Switch to Journal of Human-Robot Interaction template
You may need to install texlive-bibtex-extra to get the APA bibliography style

--- 2013-05-22 anthropomorphism.tex
@@
-%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
-%
-% This is a general template file for the LaTeX package SVJour3
-% for Springer journals.          Springer Heidelberg 2010/09/16
-%
-% Copy it to a new file with a new name and use it as the basis
-% for your article. Delete % signs as needed.
-%
-% This template includes a few options for different layouts and
-% content for various journals. Please consult a previous issue of
-% your journal as needed.
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\RequirePackage{fix-cm}
-%
-%\documentclass{svjour3}                     % onecolumn (standard format)
-%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
-%\documentclass[smallextended]{svjour3}       % onecolumn (second format)
-\documentclass[twocolumn]{svjour3}          % twocolumn
-%
-\smartqed  % flush right qed marks, e.g. at end of proof
-%
-
+\documentclass[lettersize, apacite, twoside, HRI]{apa_HRI}
+\usepackage{times} % Required package for HRI journal format
+
+% UTF8 support
 \usepackage[utf8x]{inputenc}
@@
 \usepackage[draft]{fixme}
-
-\journalname{Int J Soc Robot}
+\rightheader{Journal of Human-Robot Interaction}
+\leftheader{Fink et al.}
 
@@
 
-\begin{document}
-
 \title{On the Dynamics of Anthropomorphism in Robotics
-\thanks{This research was supported by the Swiss National Science Foundation through the National Centre of Competence in Research Robotics.}
 }
-\subtitle{}
-
-%\titlerunning{Short form of title}        % if too long for running head
-
-\author{Julia Fink         \and
-        S\'{e}verin Lemaignan     \and
-        Pierre Dillenbourg  %etc.
+
+\author{Julia Fink, Séverin Lemaignan, Pierre Dillenbourg}
+\affiliation{ Computer-Human Interaction in Learning and Instruction (CHILI) \\
+              Ecole Polytechnique Fédérale de Lausanne (EPFL) \\
+              CH-1015 Lausanne, Switzerland
 }
-
-%\authorrunning{Short form of author list} % if too long for running head
-
-\institute{J. Fink \and S. Lemaignan \and P. Dillenbourg \at
-              Computer-Human Interaction in Learning and Instruction (CHILI) \\
-              Ecole Polytechnique F\'{e}d\'{e}rale de Lausanne (EPFL) \\
-              Rolex Learning Center, Station 20 \\
-              CH-1015 Lausanne \\
-              Switzerland \\
-              Tel.: +41-21-693-2274\\
-              Fax: +41-21-693-6070\\
-              \email{julia.fink@epfl.ch}           %  \\
-%             \emph{Present address:} of F. Author  %  if needed
-           \and
-           S. Lemaignan \at
-              \email{severin.lemaignan@epfl.ch}
-		   \and
-           P. Dillenbourg \at
-              \email{pierre.dillenbourg@epfl.ch}
-}
-
-\date{Received: date / Accepted: date}
-% The correct dates will be entered by the editor
-
-\maketitle
-
-\begin{abstract}
-
-	While anthropomorphism in robotics is a commonly discussed trait of human-robot interaction (HRI), it is paradoxically an overlooked research topic.
+\abstract{While anthropomorphism in robotics is a commonly discussed trait of human-robot interaction (HRI), it is paradoxically an overlooked research topic.
 This article attempts first at providing a comprehensive synthesis of the social phenomenon of \textit{attributing human characteristics to robots}.
@@
 To this end, we introduce an initial function of anthropomorphism that models the phenomenon along three interaction phases.
-Our function is supported by results of a long-term study that we conducted in a real human environment.
-
-%	This article synthesizes the social phenomenon of attributing human characteristics to robots, and illustrates the role of human-like form and human social behavior cues in the design of robots.
-We draw on backgrounds from social sciences and psychology to first provide a common ground for the understanding of  anthropomorphism.
-The theoretical background is featured by an overview of different kinds of anthropomorphic design in robots.
-We also provide a comprehensive summary and critical comparison of findings from experiments studying anthropomorphism in human-robot interaction.
-Finally, we propose to understand anthropomorphism as a dynamic phenomenon which is not only determined by 1) \textit{individual characteristics} of the human user, and 2) the \textit{anthropomorphic design of the robot}, but might also be impacted by 3) \textit{dynamics}, such as \textit{time} and the \textit{context of use}.
-Consequently, we propose different levels of anthropomorphism that might shift with increased time of interaction and the context of use of a robot.
-
-\keywords{
-	Anthropomorphism \and
-	Design \and    
-    Human-Robot Interaction \and
-    Social Issues in Robotics \and
-    Acceptance of Robots}
-% \PACS{PACS code1 \and PACS code2 \and more}
-% \subclass{MSC code1 \and MSC code2 \and more}
-\end{abstract}
+Our function is supported by results of a long-term study that we conducted in a real human environment.}
+
+\keywords{Anthropomorphism, Design, Human-Robot Interaction, Social Issues in Robotics, Acceptance of Robots}
+
+\begin{document}
+\maketitle
 
@@
 
-%\subsection{Subsection title}
-%\label{sec:X.X}
-%as required. Don't forget to give each section
-%and subsection a unique label (see Sect.~\ref{sec:1}).
-%\paragraph{Paragraph headings} Use paragraph headings as needed.
-%\begin{equation}
-%a^2+b^2=c^2
-%\end{equation}
-
-% For one-column wide figures use
-% \begin{figure}
-% Use the relevant command to insert your figure file.
-% For example, with the graphicx package use
-%  \includegraphics{example.jpg}
-% figure caption is below the figure
-% \caption{Please write your figure caption here}
-% \label{fig:1}       % Give a unique label
-% \end{figure}
-%
-% For two-column wide figures use
-% \begin{figure*}
-% Use the relevant command to insert your figure file.
-% For example, with the graphicx package use
-%  \includegraphics[width=0.75\textwidth]{example.eps}
-% figure caption is below the figure
-% \caption{Please write your figure caption here}
-% \label{fig:2}       % Give a unique label
-% \end{figure*}
-%
-
-\begin{acknowledgements}
+\section*{Acknowledgements}
 AJung Moon, Aude Billard.\\
-\end{acknowledgements}
-
-% BibTeX users please use one of
- \bibliographystyle{spbasic}      % basic style, author-year citations
-%\bibliographystyle{elsart-harv}
-%\bibliographystyle{spmpsci}      % mathematics and physical sciences
-%\bibliographystyle{spphys}       % APS-like style for physics
+
+This research was supported by the Swiss National Science Foundation through
+the National Centre of Competence in Research Robotics.
+
+\section{Bibliography}
 \bibliography{anthropomorphism}   % name your BibTeX data base
 
-%\begin{thebibliography}{42}
-%\providecommand{\natexlab}[1]{#1}
-%\providecommand{\url}[1]{{#1}}
-%\providecommand{\urlprefix}{URL }
-%\expandafter\ifx\csname urlstyle\endcsname\relax
-%  \providecommand{\doi}[1]{DOI~\discretionary{}{}{}#1}\else
-%  \providecommand{\doi}{DOI~\discretionary{}{}{}\begingroup
-%  \urlstyle{rm}\Url}\fi
-%\providecommand{\eprint}[2][]{\url{#2}}
-%
-%
-%\bibitem[{Young et~al(2008)Young, Hawkins, Sharlin, and
-%  Igarashi}]{young_toward_2008}
-%Young JE, Hawkins R, Sharlin E, Igarashi T (2008) Toward acceptable domestic
-%  robots: Applying insights from social psychology. International Journal of
-%  Social Robotics 1(1):95--108
-%
-%
-%\end{thebibliography}
-
-% Non-BibTeX users please use
-% \begin{thebibliography}{}
-%
-% and use \bibitem to create references. Consult the Instructions
-% for authors for reference list style.
-%
-% \bibitem{RefJ}
-% Format for Journal Reference
-% Author, Article title, Journal, Volume, page numbers (year)
-% Format for books
-% \bibitem{RefB}
-% Author, Book title, page numbers. Publisher, place (year)
-% etc
-% \end{thebibliography}
-
-%\paragraph{ }
-%\begin{description}
-$\newline$
-
-\textbf{Julia Fink} is a PhD student in Human-Robot Interaction at EPFL.
-Her work focusses on the analysis of interaction, user experience and acceptance of robots in domestic spaces.
-She has a multi-disciplinary background in Media, Technology, Communication, and Interaction Studies.
-\\
-
-\textbf{Dr. S\'{e}verin Lemaignan} is a postdoctoral researcher at EPFL. ...  \\
-
-\textbf{Prof.
-Pierre Dillenbourg} is professor of learning technologies at EPFL.
-Former teacher in elementary school, he graduated in educational science (University of Mons, Belgium).
-He obtained a PhD in computer science from the University of Lancaster (UK), in the field of educational applications of artificial intelligence.
-His work covers various domains of computer-supported collaborative learning (CSCL), ranging from novel interfaces for face-to-face collaboration (interactive furniture, tangibles, paper computing) to more cognitive projects on dual eye tracking.
-%\end{description}
-
+\hrule
+\vspace*{.1in}
+Authors' names and contact information: Julia Fink {\tt julia.fink@epfl.ch}, Séverin Lemaignan {\tt severin.lemaignan@epfl.ch}, Pierre Dillenbourg {\tt pierre.dillenbourg@epfl.ch}, CHILI Lab, EPFL, Lausanne, Switzerland.
 \end{document}
-% end of file template.tex

### 2013-05-23 anthropomorphism.tex
Explain the 'normalized level' on the model diagram

@@
 
+The model uses a \emph{normalized} level of anthropomorphic effects: because
+anthropomorphic effects are not quantified on an absolute scale, we present
+them as a normalized value, that span from a minimum (no anthropomorphic
+effects) to a maximum (corresponding to the novelty effect peak on
+Figure~\ref{fig:dynamics}). The actual maximum value of anthropomorphic effects
+is strongly correlated to the human, the robot and other factors we introduce
+below. Hence, the model we propose only focuses on the general \emph{shape} of
+the level of antropomorphism over time, \ie the general dynamics of
+anthropomorphism.
+
 The model takes into account the duration of the interaction, the nature of the

### 2013-05-24 anthropomorphism.tex
refinements (typos etc), new bib

@@
 observed during a short-term interaction reflects a sustaining social effect.
-Based on an extensive literature review and our own work \fxfatal{Summarize
-these findings in a specific section!}, we believe that the social phenomenon
-is not always be the same but evolve over time, along with growing interaction
-and experience with the robot.
+Based on an extensive literature review \cite{fink_anthropomorphism_2012} and \hl{our own work} \fxfatal{Summarize
+these findings in a specific section!}, we believe that anthropomorphic effects in HRI are not always the same but evolve over time, along with growing interaction
+and experience with the robot, similar to how relationships among people evolve over time \hl{(cite Hinde, 1988)}.
+In fact, Kanda \textit{et al.} \cite{kanda_interactive_2004} also hypothesized that people's attitude toward technological artifacts and their relationship with them would evolve over time, and they were among the first who described \textit{novelty effects} during a long-term study with an interactive robot in a school.
 
@@
 how the level of anthropomorphic effects (\ie observable manifestations of
-anthropomorphism, as defined at section~\ref{sec:intro}) evolves over a
+anthropomorphism, as defined in section~\ref{sec:intro}) evolves over a
 long-term human-robot interaction. By long-term interaction, we mean direct
 (non-mediated), repeated interaction with the same robot, over (at least) several
-days. The nature of the interaction (goal-directed, entertainment,...) may vary.
+days. The nature of the interaction (goal-directed, entertainment, etc.) may vary.
 
@@
 below. Hence, the model we propose only focuses on the general \emph{shape} of
-the level of antropomorphism over time, \ie the general dynamics of
+the level of anthropomorphism over time, \ie the general dynamics of
 anthropomorphism.
@@
 We distinguish three main phases that describe the evolution of the
-anthorpomorphic effects in a long-term human-robot interaction. They are
+anthropomorphic effects in a long-term human-robot interaction. They are
 depicted in different shades on Figure~\ref{fig:dynamics}.
@@
 of seconds to a couple of hours), we observe an increased level of
-antrophomorphism, from an \emph{initial capital of anthropomorphism}
-(detailled in the next section) and a peak of antropomorphic manifestations
-that correspond to the maximum of the \emph{novelty effect}.
+anthropomorphism, from an \emph{initial capital of anthropomorphism}
+(detailed in the next section) and a peak of anthropomorphic manifestations
+that corresponds to the maximum of the \emph{novelty effect}.
 Section~\ref{sec:initialization} details this first phase.
@@
 ability to predict the behavior of the robot: the initial apparent behavioral
-complexity vanishes, and the robot is considered more and more as a machine.
+complexity vanishes, and the robot is considered more and more as \hl{a machine (Julia: I would rather say "a tool")}.
 Section~\ref{sec:familiarization} discusses the second phase.
@@
 level of anthropomorphism} (SLA). The SLA may be null (no anthropomorphic
-effects observed anymore), but it may also remain at an higher level.  This
+effects observed anymore), but it may also remain at a higher level.  This
 third phase, as well as the \emph{stabilized level of anthropomorphism}, are
@@
 For this, we suggest, what we call the \textit{"Three P's"}.
-These are three main factors that \textit{a priori} determine the potential to anthropomorphize a robot:
+These are three main factors that \textit{a priori} determine the potential that a robot will be anthropomorphized:
 
@@
 	The ICA comprises some hypothetical values for each of the \textit{"Three P's"}, such that different ICA values can be obtained, given the robot, human user, and environmental context.
-	For \textbf{personality}, we suggest to apply Epley \textit{et al.}'s psychological \textit{"Three Factory Theory"} of anthropomorphism.
+
+	For \textbf{personality}, we suggest to apply Epley \textit{et al.}'s \cite{epley_seeing_2007} psychological \textit{"Three Factor Theory"} of anthropomorphism.
 For instance, children generally tend to anthropomorphize objects more than adults.
@@
 Both aspects would increase the ICA.
-This means that, one and the same robot used in a different context or by a different user, can lead to a different ICA.
+This means that, one and the same robot used by a different user, can lead to a different ICA.
 
@@
 Roomba).
-Also, a robot that displays facial expressions would increase the ICA.
+Also, a robot that is able to display facial expressions would increase the ICA.
 However, \hl{as discussed before} a classification of the "amount" of anthropomorphic design in a robot, as for instance suggested by Fong \textit{et al.} \cite{fong_survey_2003}, can be difficult.
+Nevertheless, the important aspect is how the robot appears to the user, e.g.
+human-like or machine-like.
+Studies have shown that an anthropomorphic robot is perceived differently to a non-anthropomorphic robot.
 
-	For \textbf{purpose}, we propose that the real or imagined context in which a robot is used, impacts how far the robot will be attributed human-social characteristics.
+	For \textbf{purpose}, we propose that the real or imagined context in which a robot is used and the interaction that it brings along, impacts how far the robot will be attributed human-like characteristics.
 We	draw on findings such as presented in Joosse \textit{et al.}.
@@
 
-In this section, we discuss more speculative aspects and hypothesis that follow
+In this section, we discuss more speculative aspects and hypotheses that follow
 from the model. These aspects would require further investigation and
@@
 The first cognitive phase we identify that contribute to anthropomorphism is
-actually \emph{pre-cognitive}. In~\cite{Rosenthal-vonderPutten2013Neural},
-Rosenthal-von der Pütten et al. investigated the neural correlates of emotional
+actually \emph{pre-cognitive}. Rosenthal-von der Pütten \textit{et al.} \cite{rosenthal-vonderputten_experimental_2013} investigated the neural correlates of emotional
 reactions of human towards robot or other human that showed comparable
-responses. \fxfatal{Complete that. Reference to the pleo paper}.
+responses. \fxfatal{Complete that. Reference to the pleo paper}
 
@@
 familiar with. This may range from animals to adults, through pets and
-children. We hypothesise that the nature of the projected mental model, as well
-as how deep the human engage in this projection, are driven by the same
+children. We hypothesize that the nature of the projected mental model, as well
+as how deep the human engages in this projection, might be driven by the same
 parameters as we presented for the \emph{initial capital of anthropomorphism}
@@
 interaction, the human iteratively restate and reshape its behavioral and
-mental model of the robot (\emph{how does the robot react to such and such
-situation/input? what does the robot knows about me? about itself? about our
-environment? what can the robot learn?}, etc.).
+mental model of the robot (\emph{How does the robot react to such and such
+situation/input? What does the robot know about me? About itself? About our
+environment? What can the robot learn?}, etc.).
 
-This mental process heavily depends on the human understanding of the robot
+This mental process heavily depends on the human understanding of the robot's
 inner working, as well as his/her own tendency to anthropomorphize (the
@@
 
-The cognitive phase II also overlaps with the \emph{Familiarization} phase: as
+The cognitive phase II also overlaps with the \emph{familiarization} phase: as
 (s)he get used to the robot, we hypothesize the human restate and adapt its
-cognitive model of the robot by iteratively reshaping pre-existant, familiar
+cognitive model of the robot by iteratively reshaping pre-existent, familiar
 models until it provides a satisfying support to explain and justify the
@@
 	The \textit{context of use} is related to the purpose (and functionality) of the robot and influences the user interaction experience.
-With \textit{time}, we refer to long-term interaction with the robot, which is related to what has been described as 'novelty effect' but also accounts for the user getting used to the robot.
+With \textit{time}, we refer to long-term interaction with the robot, which is related to what has been described as \textit{novelty effect} but also accounts for the user getting used to the robot.
 Consequently, we propose that anthropomorphism is not static but likely to change, due to what we call \textit{dynamics}, in space and time.
@@
 Common observation of naive people (children or adults) interacting with robots
-shows that unexpected behaviors of the robot has a notable impact on
-interaction.
+shows that unexpected behaviors of the robot can have a notable impact on
+interaction. \hl{cite literature, e.g. cheating robot, disagreeing, disobeying, HRI2013 paper}
 
-During a normal interaction with the robot, the user iteratively refine its own
+During a normal interaction with the robot, the user iteratively refines his/her own
 model of the behavior of the robot. As explained in previous sections, as the
-user improves its model of the robot actions, it also improves its ability to predict
+user improves his/her model of the robot's actions, he/she also improves the ability to predict
 the actions and thus, the user tends to anthropomorphize less.
 
-We emit the hypothesis that an unexpected robot behavior leads the user to
-suddently restate its behavioral model of the robot and will temporarly lead to
+We emit the hypothesis that an unexpected robot behavior might lead the user to
+suddenly restate his/her behavioral model of the robot and will temporarily lead to
 an increase of the level of anthropomorphism (depicted by the spikes on
@@
 If the unexpected behavior is not planned, and perceived as such by the human
-(case I), the human can interpret that the robot is faillible. If the robot
+(case I), the human can interpret that the robot is able to fail. If the robot
 explicitly states its failure (for instance, by saying ``I'm lost!''), the
-behavior is then called \emph{transparent} \fixme{cite here, Julia?}, and the
+behavior is then called \emph{transparent} \fixme{cite here, Julia?} \hl{(literature on transparency)}, and the
 user may besides hypothesize that the robot has \emph{introspective}
-capabilities, which in turn may leads to higher anthropomorphism level.  On the
+capabilities \hl{(what is this?)}, which in turn may leads to higher anthropomorphism level.  On the
 contrary, if the robot shows no sign of recognizing its own failure, the user
@@
 Case IIIa and IIIb correspond to misinterpretations of the robot behavior. Case
-IIIb may actually lead to increased level of anthropomorphism since the human
+IIIb may actually lead to an increased level of anthropomorphism since the human
 will (wrongfully) attribute intentionality to the robot, while case IIIa is
@@
 (case I or II), is likely to lead to stronger effects due to a larger delta
-between expectations and actual observed behavior.
+between expectations and actual observed behavior. \hl{(we actually assume that anthropomorphism can be radically changing and be a very spontaneous "reaction".)}
 

### 2013-05-31 dynamics-anthropomorphism.tex
Renaming {anthropomorphism->dynamics-anthropomorphism}
Shorten first part of the paper + misc formatting

--- 2013-05-24 anthropomorphism.tex
@@
 }
-\abstract{While anthropomorphism in robotics is a commonly discussed trait of human-robot interaction (HRI), it is paradoxically an overlooked research topic.
-This article attempts first at providing a comprehensive synthesis of the social phenomenon of \textit{attributing human characteristics to robots}.
-It draws on social sciences and psychology, as well as on a critical survey of existing literature in the HRI community, to ground the concept of \textit{anthropomorphism}.
-We further present different kinds of \textit{anthropomorphic design} of robots and outline their role in social robotics.
+\abstract{While anthropomorphism in robotics is a commonly discussed trait of HRI, it is paradoxically an overlooked research topic.
+This article attempts first at providing a comprehensive synthesis of the social phenomenon of \textit{perceiving human-like characteristics in non-human agents and attributing those characteristics to robots}.
+We draw on social sciences and psychology, as well as on a critical survey of existing literature in the HRI community, to ground the concept of \textit{anthropomorphism}.
+We further briefly present different kinds of \textit{anthropomorphic design} of robots and outline their role in social robotics.
 We then propose to go beyond the traditional perception of anthropomorphism as a static feature.
-We suggest to understand anthropomorphism as a dynamic, context-dependent process.
+We suggest to understand anthropomorphism as a dynamic, context-dependent process, which changes over time.
 This also provides an account of the so-called \textit{novelty effect}.
@@
 
-\section{Anthropomorphic Design and Anthropomorphism}
+\section{Anthropomorphism}
 \label{sec:intro}
 
-	 Since the very beginning of robotics, there has been a trend of making robots human-like.
-Personal robots are designed with more or less human-like shapes or characteristics, and are able to use and react to human social behavior, such as facial expressions or nonverbal gestures.
-We call this design approach \textbf{anthropomorphic design}, which hereafter refers to human-like \hl{(life-like?)} characteristics in a robot (realized in its shape, behavior, interaction, etc.).
-Even though this design principle is not exclusive for robots, the topic has received remarkable attention in the domain of (social) robotics.
-On one hand, human-like design of robots seems to be beneficial from a technical viewpoint: for finding efficient solutions in the technical and mechanical development of a robot (e.g.
-bio-inspired robots) in order to optimally fit the robot into our to humans adapted physical space.
-On the other hand, human-like characteristics in a robot also concern the social space, the acceptance of a robot, as well as how people perceive it, form expectations toward it, and in turn treat it.
-A robot that looks and acts like a human raises different expectations than a functionally designed robot \hl{[REF]}.
-The anthropomorphic design of robots is thus a crucial aspect for the study of acceptance of robots in daily life and in the domain of social robotics in general.
+%DEFINITION OF ANTHROPOMORPHISM
 
-     Why does anthropomorphic design seem to be so popular in HRI?
-Amongst others, a human-like shape and human-social characteristics of a robot aim to enable effective and natural interaction between humans and robots.
-As robots are generally something unfamiliar and new to humans, the underlying argumentation is that when a robot has a human-like shape and displays human social cues, it is easier for people to interact with it.
-A robot's anthropomorphic design suggests to the human user to understand and treat it to some extend similar to a human, thus in a social manner.
-This behavior has been extensively studied in HCI and is explained by the \emph{Media Equation Theory}, which states that people's interactions with computers, television, and new media are fundamentally social and natural, just like interactions in real life \cite{reeves_media_1996}.
-Since robots are physically embodied agents, it is consequently very likely that people respond socially to them.
-The anthropomorphic design in a robot further encourages a person to ascribe / attribute human characteristics to it (e.g.
-intention, emotions, personality).
-To this end, anthropomorphic design of robots aims to make the system understandable, thus predictable, and acceptable.
-The conclusion builds on the assumption that humans prefer to interact with machines (and robots) in the same way they interact with humans \cite{fong_survey_2003} because they are familiar to these kind of interactions.
-\hl{The implicit social mechanism which is exploited, is called \textbf{anthropomorphism}}\fxfatal{Discuss also \emph{anthropomorphic effects} as the observable part of anthropomorphism}.
-It describes the phenomenon of a person ascribing human-like characteristics (e.g.
-beliefs, intentions, personality) to a non-human artifact, such as a robot.
-Anthropomorphism also concerns a person's reasoning about a non-human agent as if that agent were human-like (\textit{i.e.} a cognitive process without the action of making a verbal statement with attribution, for instance).
-In robotics, this social phenomenon is enhanced by using anthropomorphic forms in the design of robots, thus these two aspects are closely related to each other.
+	The essence of anthropomorphism is perceiving human-like characteristics in either real or imagined non-human agents.
+According to Epley \textit{et al.} \cite{epley_when_2008}, these human-like characteristics may include physical appearance (such as a religious agent believed to look human-like), emotional states perceived to be uniquely human, or inner mental states and motivations.
+Real or imagined non-human agents can be "anything that acts--or is believed to act--with apparent independence, including non-human animals, natural forces, religious agents, technological gadgets, or mechanical devices".
+Such anthropomorphic representations are important determinants of how a person behaves towards these agents, or how a person may behave in light of these agents.
 
-	As in the near future it is likely that a growing number of social robots will be deployed in everyday environments, the analysis and understanding of anthropomorphism and related social dynamics in HRI becomes increasingly important.
+%ANTHROPOMORPHISM AS SUBJECT IN HCI AND HRI
+
+	In this context, anthropomorphism has received remarkable attention in the study of humans interacting with artificial entities, and has been a subject in Human-Computer Interaction (HCI), and Human-Robot Interaction (HRI).
+Following the \textit{Media Equation}, it has been described that people mindlessly react socially to computers \cite{reeves_media_1996}.
+The phenomenon has also been observed with virtual characters \hl{cite [50, 100] in rosenthal-von der P{\"u}tten (2013)}, and more recent studies investigated how far people ascribe personality or intentions to artificial agents \hl{references} and whether they show empathetic behavior toward robots \cite{rosenthal-vonderputten_experimental_2013}.
+The common base for this research is the assumption that humans perceive or react to a non-human agent or artifact as somewhat similar to a human.
+
+%CONTROVERSAL UNDERSTANDINGS OF ANTHROPOMORPHISM
+
+	However, not everything labeled as "anthropomorphism" really is anthropomorphism.	It is true that there are several different, partially even conflicting understandings of anthropomorphism, across and within disciplines \cite{duffy_anthropomorphism_2002}.
+Epley \textit{et al.} \cite{epley_when_2008} try to narrow down and clarify the understanding of anthropomorphism (in psychology) by explaining what it is \textit{not}.
+The authors list four things that anthropomorphism does not include: First, anthropomorphism does not include behavioral descriptions of observable actions.
+Anthropomorphism requires going beyond what is directly observable.
+Second, anthropomorphism does not merely entail animism, as animate life is not a uniquely human-like characteristic.
+Third, anthropomorphism does not include any requirement of reasoned or reflective endorsement of an inference (\hl{the strength of anthropomorphic inferences can vary} \footnote{for further explanation the reader may refer the original work \cite{epley_when_2008}.}).	Finally, anthropomorphism is not necessarily inaccurate.
+A psychological theory should take this (in)accuracy in anthropomorphism into account and predict variability in the tendency to perceive human-like traits in non-human agents.
+
+%ANTHROPOMOPRHIC DESIGN
+
+	Anthropomorphism represents just one of many examples of induction whereby "people reason about an unknown stimulus based on a better-known representation of a related stimulus" \cite{epley_when_2008}, in this case reasoning about a non-human agent based on representation of the self or humans.
+At this point, anthropomorphic design enters the stage.
+The anthropomorphic design of a robot encourages people to reason about this unfamiliar system as if it were a human.
+To increase this tendency, robots are designed with anthropomorphic forms (human-like forms or lifelike forms, in the broader sense), or are able to display and use human-social behavior.
 
@@
 %
-%				ANTAGONISM
+%				XXX
 %
@@
 
-\section{The Antagonism of Anthropomorphic Design}
-\label{sec:2}
-
-	In the first place, robotics seems to benefit from anthropomorphic design and people's tendency to anthropomorphize robots.
-However, there is the other side: a not yet very well defined thin line separates acceptable human-like forms in robots from creepy artificial \textit{almost} human-like appearing robots.
-The underlying theory for this viewpoint is stated as the \textit{Uncanny Valley} \cite{mori_uncanny_1970} which suggests that artificial human-like forms are only acceptable up to a certain degree but lead to reluctance if they fail in trying to attain human-likeness \hl{cross-ref to later and figure}.
-The usage of different kinds of anthropomorphic forms in robots is still controversially discussed.
-Some developers and researchers clearly oppose human-like forms in robots but rather suggest animal-like shapes or caricature-like appearance.
-Another sensitive aspect is that with robots to closely resemble a human, also ethical issues arise.
-For instance, we need to consider how far we actually want an \textit{artificial agent} to resemble ourselves and how far it should act `artificially socially' toward humans, and what happens as soon as it is considered a \textit{moral agent} \cite{sullins_when_2006}.
-Using \textit{socially interactive robots} in contexts involving elderly care or rehabilitation for disabled / handicapped persons, autistic children is also a controversially discussed topic \cite{robins_robots_2005}.
-
-	Literature on anthropomorphism (in robotics) is quite diverse and one strives hard to extract a coherent conclusion.
-There is no commonly accepted definition about the terms used and the terminology is not clear.
-However the terms \textit{anthropomorphic or human-like are often used as if their meanings are clear and agreed upon"} \cite{persson_anthropomorphism_2000}.
-Consequently, Duffy \cite{duffy_anthropomorphism_2002} argues that terms might even be misused.
-For instance, some researchers refer to \textit{"the robot's level of anthropomorphism"} \cite{bartneck_is_2007}, however, others argue that anthropomorphism emerges in the \textit{interaction} between the technology and the user, thus a system or an artifact does not "contain anthropomorphism" \textit{per se} \cite{persson_anthropomorphism_2000} but only gives rise to the process of anthropomorphizing in a given user and situation.
-Further, robotics is a multi-disciplinary field and researchers from very different domains might have diverse or even contradictory understandings of anthropomorphism.
-Epley \textit{et al.} \cite{epley_seeing_2007} notice that despite the fact that anthropomorphism in the perception of non-human agents is commonly observed, it is poorly understood.
-The phenomenon itself has been found to be very complex but sometimes subtle and hard to study.
-Another constraint that limits the reliability of some findings is, that most experiments on anthropomorphism are conducted in controlled lab-settings during short-term interactions.
-This experimental setting (short term and laboratory context) can be critical when studying a social phenomenon like anthropomorphism and possibly lead to over-interpretations.
-Some studies also seem to contrast two or more different anthropomorphic and mechanical systems that might not be appropriate for comparison under the given context and research question.
-\hl{say more}
-
-	To sum it up, while anthropomorphism in robotics is a commonly discussed and studied trait of human-robot interaction (HRI), we think it is paradoxically an overlooked research topic.
-The understanding of anthropomorphism in robotics seems to not take into account the wide range of phenomena that it encompasses.
-The traditional understanding of anthropomorphism in robotics to date, considers two main factors that account for the social phenomenon: the characteristics of \textbf{1) the robot's design} (degree of human-likeness) and the psychological determinants in \textbf{2) the human user} (see \cite{epley_seeing_2007}).
-It has been shown that both these factors can facilitate or hinder anthropomorphism.
-We propose to go beyond this traditional perception of anthropomorphism as a static feature of HRI.
-Based on Persson \textit{et al.}'s \cite{persson_anthropomorphism_2000} argumentation that anthropomorphism is a multi-layered phenomenon which arises in different levels, we suggest to understand anthropomorphism as a dynamic, context-dependent process.
-To this end, we apply Persson \textit{et al.}'s six levels on anthropomorphism to HRI and introduce three interaction phases.
-These interaction phases of anthropomorphism reflect also the results of a long-term study that we conducted in a real human environment and provide an account of the so-called \textit{novelty effect}.
-Consequently, we would like to draw attention to two \textit{dynamics in anthropomorphism}, namely, the context of use, and the fact of getting used to a system over time.
-We propose to add these two aspects as a third factor, the characteristics of \textbf{3) the interaction} (time and space), to the existing two accounts of anthropomorphism (robot and user).
-
-	We would further like to review and discuss research on anthropomorphism in robotics and human-like design of robots.
-We first provide a comprehensive understanding of the phenomenon drawing on theories from developmental psychology and cognitive sciences.
-We then present the trends of different kinds of anthropomorphic forms in robots and discuss their role in social robotics.
-The article integrates related work from human-robot interaction studies, reporting on findings from experiments with human subjects interacting with and evaluating various types of systems.
-We try to give a coherent view on the topic, outline similarities and antithetic findings, and contribute to a better understanding of anthropomorphism in robotics, and the acceptance of human-like characteristics in robots.
-We also aim to constructively discuss anthropomorphic design of personal and socially interactive robots.
+\section{XXX}
+\label{sec:}
 
@@
 \section{Anthropomorphism as a Social Phenomenon}
-\label{sec:3}
+\label{sec:origins-anthropomorphism}
 
@@
 
- \begin{figure}
+ \begin{figure}\centering
 % Use the relevant command to insert your figure file.
@@
 \subsection{Explanations for Anthropomorphism}
-\label{sec:3.1}
+\label{sec:explanations}
 
@@
 \subsection{Insights from Social and Developmental Psychology}
-\label{sec:3.2}
+\label{sec:psychological-factors}
 
@@
 
-	\hl{BRIDGE}
-
 \subsection{Anthropomorphism in Robotics}
-\label{sec:3.3}
+\label{sec:anthropomorphism-robotics}
 
@@
 
-%	Duffy defines anthropomorphism as "the tendency to attribute human characteristics to inanimate objects, animals and others with a view to helping rationalise their actions." \cite{duffy_anthropomorphism_2003}.
-This definition directly tries to give an explanation for why people tend to anthropomorphize robots, namely, in order to rationalize their actions, which seems to be effective as long as the robot is not very familiar to the human interaction partner.
-\hl{familiarity aspect LATER} Attributing familiar human-like qualities to a robot can serve to make the robot more familiar, explainable, or predictable \cite{epley_seeing_2007}.
-Further Duffy argues that anthropomorphism includes "attributing cognitive or emotional states to something based on observation." \cite{duffy_anthropomorphism_2003} \hl{BRIDGE, explain better} This is important for the acceptance of socially interactive robots \cite{fong_survey_2003} in daily life environments.
-As robots have to deal with people's acceptance to become useful devices and collaboration partners for humans, anthropomorphic robot design is amongst other reasons used to make people anthropomorphize (or socialize) the robot, treat it socially, act empathetical toward it.
-
-	"[...] the experiment demonstrates that human beings implicitly attribute human-like qualities, such as mental states, to nonhuman agents.
-This finding was evident on a neurophysiological level as well as behavioral level." \cite{hegel_understanding_2008}
-
-\subsection{Anthropomorphism as a multi-layered phenomenon}
-\label{sec:3.4}
-
-Anthropomorphism can also be viewed as an \textit{experience} that arises in the \textit{interaction} between a set of user expectations and external reality \cite{persson_anthropomorphism_2000}, (see Figure)
-
-an \textit{understanding} of complex -- not necessarily human -- patterns of behavior in the world, in order to make sense of it: \textit{"Anthropomorphism is a way of simplifying and thereby making sense of the environment by projecting a host of expectations about human life onto aspects of that environment."} \cite{persson_anthropomorphism_2000}
-Persson \textit{et al.} explored anthropomorphism triggered by computer interfaces and system and we believe their perspective on anthropomorphism could also be applied in HRI.
-The authors suggest that the social phenomenon is not only one single process but that it involves several levels, \textit{e.g.} primitive psychology, folk-psychology, social stereotypes, and emotional anthropomorphism.
-We would like to take up the proposition to discriminate different levels of anthropomorphism, since each has its own characteristics and involves specific types of user expectations.
-This differentiation could allow to draw inferences on the human-robot relationship from the observed level of anthropomorphism.
-
-\begin{figure}\centering
-% Use the relevant command to insert your figure file.
-% For example, with the graphicx package use
-  \includegraphics[scale=0.42]{persson_anthropomorphism.png}
-% figure caption is below the figure
- \caption{Anthropomorphism emerges in the (real or imagined) interaction between robot and user; illustration taken from \cite{persson_anthropomorphism_2000} \hl{maybe we don't put the figure here, it was just to illustrate what I mean}}
- \label{fig:anthropomorphism_and_interaction}       % Give a unique label
- \end{figure}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %
-%				HUMAN-LIKE DESIGN IN ROBOTS
-%
-%
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Human-like Design in Robots}
-\label{sec:4}
-
-	Anthropomorphic design means an imitation of human form (or natural form, in a broader understanding) \cite{disalvo_seduction_2003}.
-Concepts of anthropomorphic or other life-like forms can be found in a variety of interactive objects and effects of this design approach are studied in disciplines such as affective computing, tangible interaction or industrial design.
-In a robot, anthropomorphic design can be realized in \textit{1)} a robot's physical (visible) form / shape (embodiment / appearance), \textit{2)} its behavior (e.g.
-motion), and \textit{3)} the kind of interaction / communication (e.g.
-modality) that it enables or triggers.
-Especially socially interactive robots often make use of `human social' behavior cues, such as express / perceive emotions, communicate with high-level dialogue, learn / recognize models of other agents, establish / maintain social relationships, use natural cues (gaze, gestures, etc.), exhibit distinctive personality and character, or learn / develop social competencies \cite{fong_survey_2003}.
-
-\subsection{Human-like embodiment (form / shape)}
-\label{sec:4.1}
-
-	The degree of human-like shape in a robot, also its morphological similarity, is the extent to which a non-human agent's observable features look human-like.
-\cite{epley_seeing_2007} Fong \textit{et al.} classify four categories of a robot's aesthetic form: \cite{fong_survey_2003}
-
-\begin{itemize}
-	\item anthropomorphic: structurally and functionally similar to a human
-	\item zoomorphic: imitation of forms of living creatures, e.g. animal or pet design
-	\item caricatured: using a character or caricature form, e.g. inspired from animation
-	\item functional: reflecting the task a robot should perform
-\end{itemize}
-
-	For some robots, it seems to be difficult to assign them to only one of these categories.
-How to categorize, for instance, a mainly functional robot which has only a human-like head?
-It is also interesting that each of the four categories follows specific design principles to fulfill different goals.
-For instance, zoomorphic robots seem to help creating a "companionship" relation (e.g.
-similar to the owner-pet relation), whereas the anthropomorphic design seems to foster rather a human-social relation between the robot and the human and also tries to give the impression of the robot being a more sophisticated interaction partner \cite{disalvo_all_2002,fong_survey_2003,kiesler_mental_2002}.
-Accordingly, a robot's functionality should be reflected in it's design because it strongly impacts what kind of expectations people have of the robot \hl{ref, matching hypothesis}: \textit{"The device's visual appearance will often shape first impressions and can therefore play a considerable role in establishing first expectations."} \cite{schmitz_concepts_2011} What however is the best design for a multi-purpose robot that not only vacuums floors but also aims to interact socially with the user?
-This seems to be a fundamental question in HRI and the design of robots.
-Interestingly, it has been observed that body parts of a robot that are associated with senses could indicate that the robot is capable of perceiving the corresponding modality (e.g.
-eyes suggest seeing and ears hearing, respectively.
-\cite{schmitz_concepts_2011} Schmitz calls this notion \textbf{anthropomorphic affordances}, which describe affordances of an artifact that are impacted by its anthropomorphic shape and suggest to a user a  specific action or interaction.
-Consequently, if a more human-like shaped robot leads to higher expectations from the user side, it seems to be exeptionally difficult at this moment, to build a satisfying anthropomorphic robot.
-Moreover, there are also practical affordances that a robot's shape brings along.
-A legged robot is supposed to be able to walk and climb stairs whereas a wheeled one would probably not be able to do so.
-\hl{Sullivan: form follows funtion!}
-
-\subsection{Human-like behavior}
-\label{sec:4.2}
-
-	Besides anthropomorphic shape, also a robot's behavior, e.g.
-the particular way of how it moves, can be human-inspired (which is in fact often defined by its morphology).
-According to Epley \textit{et al.} \textit{"at least two dimensions of similarity seem particularly important for anthropomorphism to occur -- similarity in motion and similarity in morphology"} \cite{epley_seeing_2007}.
-Similarity in motion might not only be walking on two feet but also the speed of movements of a robot, which when adapted to a human, have a positive effect on the usability and perception of the robot from the user cite \hl{ref!!}.
-The aspect is less important for robots in automation (e.g.
-assembly lines, production) which usually do not directly interact with humans.
-
-	Another aspect of human-like behavior in robots is autonomy and pro-activity.
-Schmitz argues that both can be a fundamental strategy in order to evoke anthropomorphic / zoomorphic interpretation \cite{schmitz_concepts_2011} \hl{ref 33}.
-\hl{more on autonomy and pro-activity, transparency}
-
-	"On a next level, \textbf{stereotypical behavior}, which expresses e.g.
-shyness of curiosity, addresses more complex processes but adds essentially to anthropomorphic strategies [38] [46]." \cite{schmitz_concepts_2011}
-
-	\hl{Severin: mention the need to be "complete enough not to be predictable" --> toys that are predictable are quickly boring and humans are really good at identifying simple logical behaviors.
-/ Julia: role of uselessness in robots, surprise factor}
-
-\subsection{Human-like interaction / communication}
-\label{sec:4.3}
-
-	"The mere \textbf{presence of voice} is another strong trigger for anthropomorphic perception \hl{(33)}, irrespective of contents and sounds." \cite{schmitz_concepts_2011}
-
-	"Besides speech, the acoustic channel can be used to deliver alternative feedback that resembles \textbf{life-like, physiological sounds or haptics} instead of conventional feedback, for example pulse, breath, snore or cough [...]." \cite{schmitz_concepts_2011}
-
-Others: proxemics
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-%
-%
-%				DOES ANTHROPOMORPHISM MAKE ROBOTS MORE SOCIAL?
-%
-%
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Does anthropomorphism make robots more social?}
-\label{sec:5}
-
-	In general, it is suggested that increasing human-likeness of a robot	 will lead to more perceived \textit{affinity} from the human side \cite{mori_uncanny_1970}.
-This theoretical concept is also supported by psychological determinants of perceiving human-likeness in something non-human: \textit{"the more similar in appearance, the more people are likely to use themselves as a source of induction and anthropomorphize these nonhuman agents"} \cite{epley_seeing_2007}.
-Further, empirical studies have shown that robots with human-like forms can enhance social responses from humans which in turn can have a positive impact on acceptance \cite{venkatesh_theoretical_2000,duffy_anthropomorphism_2003,goetz_cooperation_2002}.
-People responded more positively to an artifact that displayed human-like behavioral characteristics (emotions, facial expression) in contrast to a purely functional design \cite{eyssel_anthropomorphic_2010,krach_can_2008,reeves_media_1996,riek_how_2009}.
-Overall, these results suggest that human-like features in robots enhance anthropomorphism, and in turn create a social view toward the robot.
-
-	"The anthropomorphic design of human-machine interfaces is inevitable.
-The important criterion is to seek a balance between people's expectations and the machines capabilities." \cite{duffy_anthropomorphism_2002}
-
-	"What is the ideal set of human features that could supplement and augment a robots  social functionality?" \cite{duffy_anthropomorphism_2002}
-
-	Though, the 'anthropomorphic design principle" seems beneficial, it also raises ethical issues and has been reviewed critically in terms of acceptance.
-How far do we want a robot to resemble a human or act like a human?
-
-	Findings that support anthropomorphic form in robots because they found people respond with anthropomorphizing these kind of robots, and in turn act more social toward them or accept them more easily:
-
-	\hl{empathy --> check Iolanda's paper}
-
-\subsection{Socially interactive robots}
-\label{sec:5.1}
-
-Evaluation and classification of social robots
-
-\subsection{Too much human-likeness?}
-\label{sec:5.2}
-
-\begin{figure}\centering
-% Use the relevant command to insert your figure file.
-% For example, with the graphicx package use
-  \includegraphics[scale=0.6]{uncanny-valley.jpg}
-% figure caption is below the figure
- \caption{Mashiro Mori, illustration of the \textit{Uncanny Valley}, originally from 1970; picture from a manuscript version of \cite{mori_uncanny_2012}}
- \label{fig:uncanny_valley}       % Give a unique label
- \end{figure}
-
-	The \textit{Uncanny Valley} hypothesis \cite{mori_uncanny_1970} models people's reactions to technologies that resemble a human too close while still not being one (see Figure).
-The theory hypothesizes that a person's response to a human-like robot would abruptly shift from empathy to revulsion as it approached, but failed to attain, a lifelike appearance \cite{mori_uncanny_1970}.
-Starting with low degrees of anthropomorphic cues in a robot, humans seem to readily accept and prefer them compared to purely mechanical robots.
-In general, one can say that up to a certain (yet not very well defined) degree, the more human-like the robot, the more affection it can engender through familiar communication references.
-
-	when slowly increasing its human-likeness, the more affection
-
-The idea of the hypothesis follows Freud's description of the uncanny (a translation from the German word `unheimlich') \hl{ref Freud, The Uncanny}: "it derives its terror not from something externally alien or unknown but - on the contrary - from something strangely familiar which defeats our efforts to separate ourselves from it".
-\cite{hegel_understanding_2008}
-
-	Also: Simulation Theory
-
-	Findings that oppose anthropomorphic design in robots as people respond negatively to it:
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-%
-%
-%				SKEPTICAL REVIEW OF ANTHROPOMORPHISM IN HRI
-%
-%
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Does anthropomorphism make robots more social?}
-\label{sec:6}
-
-We believe that the prevalent mostly observed anthropomorphic stances in short-term experiments do not fully embrace this complex social phenomenon.
-For instance, when reading through literature on anthropomorphism in robotics one can get the impression that it is taken as a given fact that once people attribute human characteristics to a robot, they will always keep on doing so.
-
-	short term
-
-	lab context
-
-	fake comparison of different robots that are not appropriate for comparison
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-%
-%
-%				OUR MODEL
+%				DYNAMICS OF ANTHROPOMORPHISM
 %
@@
 
+\subsection{Why is anthropomorphism likely to change over time?}
+\label{sec:whychanges}
+
+Why do we think that anthropomorphic inferences are likely to change over time and with growing experience a person has with a robot?
+The underlying process in anthropomorphism is understood as reasoning about and perceiving something non-human, and unknown or unfamiliar based on one's representation of the familiar and well-known concept of being human (or one-self).
+The basic operations underlying inductive inference are the acquisition of knowledge, the activation or elicitation of knowledge, and the application of activated knowledge at the time of the judgment \cite{epley_when_2008}.
+According to Epley \textit{et al.}, the application includes attempts to correct, adjust, or integrate less accessible information into a more automatically activated default representation.
+This process can be seen as a process of correction, and thus, it is often insufficient leaving final judgments biased in the direction of the initially activated representation.
+As a person's knowledge base changes / evolves constantly with newly acquired things, or growing experiences with a robot, etc., it is likely that the "need to anthropomorphize" a robot decreases over time.
+First, because of the evolved knowledge about it, and second because one has familiarized oneself with it.
+Consequently, the robot should become more predictable and more familiar to the human user and inferences about it can be made based on the acquired knowledge.
+
+\subsection{Model of anthropomorphism over time}
+\label{sec:modelintro}
+
 So far, the HRI community has not much investigated how anthropomorphism in
@@
 	Initially, there is a given potential that a robot will be anthropomorphized.
-Our proposed function to model the dynamics of anthropomorphism starts with this what we call \textit{initial capital of anthropomorphism} (ICA) at time point $t_{0}$, which describes the first (real or imagined) contact to the robot (see Figure \ref{fig:dynamics}).
+But what are the determinants of anthropomorphism?
+It has been shown that some \textit{people} anthropomorphism more than others, some \textit{situations} induce anthropomorphism more than others, that \textit{children} tend to anthropomorphize more than adults, and some \textit{cultures} are notorious for their anthropomorphic religions and worldviews \cite{epley_when_2008}.
+Our proposed function to model the dynamics of anthropomorphism tries to take these variances into account and starts with what we call \textit{initial capital of anthropomorphism} (ICA) at time point $t_{0}$.
+The ICA describes the first (real or imagined) contact to a robot (see Figure \ref{fig:dynamics}).
 Time point $t_{0}$ can temporally be before the first real physical interaction with the robot, for instance, when a person learns about the existence of vacuum-cleaning robots and imagines using one (\textit{e.g.} when one watches an advertisement of the robot, or observes one at a trade show).
@@
 How can we hypothetically quantify the ICA on a normalized scale of anthropomorphism?
-For this, we suggest, what we call the \textit{"Three P's"}.
-These are three main factors that \textit{a priori} determine the potential that a robot will be anthropomorphized:
+For this, we suggest three main factors that \textit{a priori} determine the potential that a robot will be anthropomorphized:
 
@@
 
-	\item The \textbf{personality} of the human user: Psychological characteristics / determinants that influence a person's tendency to anthropomorphize artifacts, see \cite{epley_seeing_2007}.
+	\item Human-centered factor: The \textbf{personality} and individual traits of the human user: Psychological characteristics / determinants that influence a person's tendency to anthropomorphize artifacts, see \cite{epley_seeing_2007}.
+Also other individual traits and demographic aspects are comprised (\textit{e.g.} age, gender, cultural background, professional background).
 
-	\item The human user's \textbf{perception} of the robot: Characteristics of the robot's form, behavior, and interaction modalities (anthropomorphic design), see \cite{fong_survey_2003}.
+	\item Robot-centered factor: The robot's \textbf{design} and how it appears to the human user: Characteristics of the robot's form, behavior, and interaction modalities (anthropomorphic design), see \cite{fong_survey_2003}.
 
-	\item The real or imagined \textbf{purpose} of the robot: The task context and role in which the robot is used / experienced (environmental context), see \cite{joosse_what_2013}.
+	\item Situation-centered factor: The real or imagined \textbf{purpose} of the robot, including the situational context in which it is used: The task context and role in which the robot is used / experienced (environmental context), see \cite{joosse_what_2013}.
 
@@
 
-	The ICA comprises some hypothetical values for each of the \textit{"Three P's"}, such that different ICA values can be obtained, given the robot, human user, and environmental context.
+	The ICA comprises some hypothetical values for each of these three factors, such that different ICA values can be obtained, given the robot, human user, and environmental context.
 
@@
 
-	For \textbf{perception}, we understand that a robot that follows an anthropomorphic design (e.g.
+	For \textbf{design}, we understand that a robot that follows an anthropomorphic design (e.g.
 NAO) leads to a higher ICA than a rather functional robot (e.g.
@@
 \section{Bibliography}
-\bibliography{anthropomorphism}   % name your BibTeX data base
+\bibliography{dynamics-anthropomorphism}   % name your BibTeX data base
 
 \hrule
+
 \vspace*{.1in}

### 2013-06-26 dynamics-anthropomorphism.tex
Amended the introduction

@@
 }
-\abstract{While anthropomorphism in robotics is a commonly discussed trait of HRI, it is paradoxically an overlooked research topic.
-This article attempts first at providing a comprehensive synthesis of the social phenomenon of \textit{perceiving human-like characteristics in non-human agents and attributing those characteristics to robots}.
-We draw on social sciences and psychology, as well as on a critical survey of existing literature in the HRI community, to ground the concept of \textit{anthropomorphism}.
-We further briefly present different kinds of \textit{anthropomorphic design} of robots and outline their role in social robotics.
-We then propose to go beyond the traditional perception of anthropomorphism as a static feature.
-We suggest to understand anthropomorphism as a dynamic, context-dependent process, which changes over time.
-This also provides an account of the so-called \textit{novelty effect}.
-To this end, we introduce an initial function of anthropomorphism that models the phenomenon along three interaction phases.
-Our function is supported by results of a long-term study that we conducted in a real human environment.}
+
+\abstract{While anthropomorphism in robotics is a commonly discussed trait of
+HRI, it is paradoxically an overlooked research topic. This article
+attempts first at providing a comprehensive synthesis of the social
+phenomenon of \textit{perceiving human-like characteristics in non-human
+agents and attributing those characteristics to robots}. We draw on
+social sciences and psychology, as well as on a critical survey of
+existing literature in the HRI community, to ground the concept of
+\textit{anthropomorphism}. We further briefly present different kinds
+of \textit{anthropomorphic design} of robots and outline their role in
+social robotics\fxfatal{do we really do?}. We then suggest to go beyond the traditional
+perception of anthropomorphism as a static feature of a system: we propose to
+understand anthropomorphism as a dynamic, non-monotonic and
+context-dependent process, which evolves over time and accounts for
+special events like the so-called \textit{novelty effect}. To this end,
+we introduce a model of anthropomorphism that analyzes the phenomenon
+along three interaction phases. These findings are supported by a long-term
+study conducted in a real human environment.}
 

### 2013-06-26 dynamics-anthropomorphism.tex
Proof-reading, added several 'fixme' all over the place

@@
 Real or imagined non-human agents can be "anything that acts--or is believed to act--with apparent independence, including non-human animals, natural forces, religious agents, technological gadgets, or mechanical devices".
-Such anthropomorphic representations are important determinants of how a person behaves towards these agents, or how a person may behave in light of these agents.
+Such anthropomorphic representations are important determinants of how a person behaves towards these agents, or how a person may behave in light\fxnote{in light?} of these agents.
 
@@
 
-	In this context, anthropomorphism has received remarkable attention in the study of humans interacting with artificial entities, and has been a subject in Human-Computer Interaction (HCI), and Human-Robot Interaction (HRI).
+In this context, anthropomorphism has received remarkable attention\fxnote{contradict with intro} in the study of humans interacting with artificial entities, and has been a subject in Human-Computer Interaction (HCI) and Human-Robot Interaction (HRI).
 Following the \textit{Media Equation}, it has been described that people mindlessly react socially to computers \cite{reeves_media_1996}.
-The phenomenon has also been observed with virtual characters \hl{cite [50, 100] in rosenthal-von der P{\"u}tten (2013)}, and more recent studies investigated how far people ascribe personality or intentions to artificial agents \hl{references} and whether they show empathetic behavior toward robots \cite{rosenthal-vonderputten_experimental_2013}.
+The phenomenon has also been observed with virtual characters \hl{cite [50, 100] in rosenthal-von der P{\"u}tten (2013)}, and more recent studies investigated how far people ascribe personality or intentions to artificial agents \hl{references}\fxnote{Rosenthal is not enough?} and whether they show empathetic behavior toward robots \cite{rosenthal-vonderputten_experimental_2013}.
 The common base for this research is the assumption that humans perceive or react to a non-human agent or artifact as somewhat similar to a human.
+
+We furthermore use in this article \emph{anthropomorphic effects} to denote the
+observable correlates of anthropomorphism. These include, amongst others,
+verbal behaviors (like the use of pronouns ``he/she''), kinesics (like hugging
+the robot) or anticipation of certain robot's actions.
 
@@
 
-	However, not everything labeled as "anthropomorphism" really is anthropomorphism.	It is true that there are several different, partially even conflicting understandings of anthropomorphism, across and within disciplines \cite{duffy_anthropomorphism_2002}.
-Epley \textit{et al.} \cite{epley_when_2008} try to narrow down and clarify the understanding of anthropomorphism (in psychology) by explaining what it is \textit{not}.
+However, not everything colloquially labeled as \emph{anthropomorphism} really is anthropomorphism.
+Different, even partially conflicting, understandings of anthropomorphism exist across and within disciplines \cite{duffy_anthropomorphism_2002}.
+Epley \textit{et al.} \cite{epley_when_2008} try to narrow down and clarify the understanding of anthropomorphism in psychology by explaining what it is \textit{not}.
 The authors list four things that anthropomorphism does not include: First, anthropomorphism does not include behavioral descriptions of observable actions.
@@
 Third, anthropomorphism does not include any requirement of reasoned or reflective endorsement of an inference (\hl{the strength of anthropomorphic inferences can vary} \footnote{for further explanation the reader may refer the original work \cite{epley_when_2008}.}).	Finally, anthropomorphism is not necessarily inaccurate.
-A psychological theory should take this (in)accuracy in anthropomorphism into account and predict variability in the tendency to perceive human-like traits in non-human agents.
+A psychological theory should take this (in)accuracy in anthropomorphism into account and predict variability in the tendency to perceive human-like traits in non-human agents\fxfatal{End of paragraph is unclear.
+We need to reformulate}.
 
@@
 Anthropomorphism represents just one of many examples of induction whereby "people reason about an unknown stimulus based on a better-known representation of a related stimulus" \cite{epley_when_2008}, in this case reasoning about a non-human agent based on representation of the self or humans.
-At this point, anthropomorphic design enters the stage.
-The anthropomorphic design of a robot encourages people to reason about this unfamiliar system as if it were a human.
+This supports the usual role we assign to anthropomorphism in robotics: the anthropomorphic design of a robot encourages people to reason about this unfamiliar system \emph{as if} it was a human.
 To increase this tendency, robots are designed with anthropomorphic forms (human-like forms or lifelike forms, in the broader sense), or are able to display and use human-social behavior.
@@
 The term \textbf{anthropomorphism} is used in different senses throughout natural sciences, psychology, Human-Computer Interaction, and Human-Robot Interaction \cite{duffy_anthropomorphism_2003}.
-There is no single accepted definition.
+There is no single accepted definition\fxfatal{already said before}.
 Originally, anthropomorphism comes from the Greek \textit{`anthropos'} for `man' (or `human') and \textit{`morphe'} for `form/structure' (or `shape').
@@
 Both anthropomorphism and zoomorphism can be embraced by the concept of \textbf{life-likeness}.
-\footnote{The inverse process, dehumanization \cite{haslam_dehumanization:_2006}, or mechanomorphism \cite{caporael_anthropomorphism_1986} also exists.}
+\footnote{The inverse process would be called dehumanization \cite{haslam_dehumanization:_2006}, or mechanomorphism \cite{caporael_anthropomorphism_1986}.}
 
@@
 The phenomenon of personifying something has ancient roots, \textit{e.g.} in mythology but also in storytelling.
-Already in prehistoric artworks and illustrations zoomorphic (animal-shaped) or anthropomorphic shapes were used to represent natural forces or great spirits, for instance.
+In prehistoric artworks and illustrations, zoomorphic (animal-shaped) or anthropomorphic shapes were already used to represent natural forces or great spirits, for instance.
 A more recent example is Milo Winter's illustration from 1919, \textit{"The North Wind and the Sun"} (Figure \ref{fig:1}), in which both north wind and sun are given a human face (anthropomorphized).
 Similarly, when parents explain their children about nature, they tend to use anthropomorphisms, \textit{e.g.} saying the skies would cry when it rains.
-More generally, a possible explanation for why people anthropomorphize is that by doing so, the subject is made graspable, understandable, somehow predictable, and one could feel more empathetic toward it.
+More generally, an explanation for why people anthropomorphize is that by doing so, the subject is made \emph{graspable}, \emph{understandable}, \emph{predictable}, and one feel \emph{more empathetic} toward it\fxnote{important part.
+Emphasize this 4 facets, eg by saying we build on top of them}.
 For instance, people commonly anthropomorphize their pets, ascribing mental states, intentions or feelings to them \cite{eddy_attribution_1993}.
@@
 
+\fxfatal{inconsistency: we already give explanations for anthropomorphism in previous paragraph...}
 	According to Lee \textit{et al.} \cite{lee_human_2005}, there are two main perspectives in explaining people's tendency to anthropomorphize.
@@
 Schmitz \cite{schmitz_concepts_2011} describes that within the visual scope of design, the outer appearance can have an important impact on the overall perception of an object.
-The basic assumption here is that if an artifact appears much like a human it is likely to be treated similar to a human.
+The basic assumption here is that if an artifact appears much like a human, it is likely to be treated similar to a human.
 If this explanation of anthropomorphism is correct, people may respond automatically to social cues emitted by a robot, and apply human-human social schemas and norms to these interactions.
@@
 Consequently, people tend to thoughtfully develop a mental model of agents in their environment and make inferences about it based on what is familiar to them.
-This point of view implicitly builds on a person's ability to attribute mental states to oneself and others, which is called \textit{Theory of Mind}.
+This point of view implicitly builds on a person's ability to attribute mental states to oneself and others, which is called \textit{Theory of Mind}~\cite{Premack1978}.
 A theory of  mind for other agents enables us to attribute intentionality to those agents \cite{leslie_pretense_1987,admoni_multi-category_2012}.
-If a system behaves much like a human being (e.g.
-emits a human voice), people's mental model of the system's behavior may approach their mental model of humans, though the model may differ in some important aspects \hl{ref?
+If a system behaves much like a human being (\eg emits a human voice), people's mental model of the system's behavior may approach their mental model of humans, though the model may differ in some important aspects \hl{ref?
 Schmitz?}.
-In turn, people's estimation of a robot's `knowledge' and its capabilities / abilities affects the way they relate to it.
-Research examined the validity of the mental model concept with various kinds of robots \cite{schmitz_concepts_2011,kiesler_mental_2002}.
+In turn, people's estimation of a robot's knowledge model and its capabilities affects the way they relate to it.
+Previous research examined the validity of the mental model concept with various kinds of robots \cite{schmitz_concepts_2011,kiesler_mental_2002}.
 Findings suggest that people tend to hold richer mental models about anthropomorphic robots in contrast to mechanic ones \cite{kiesler_mental_2002}.
@@
 
-	To understand the social phenomenon of anthropomorphism better, it makes sense to take a look at studies and explanations from (developmental) psychology.
-The phenomenon of attributing intentions and \hl{animacy} to simple shapes based on motion has been intensively studied in (developmental) psychology.
+	To understand the social phenomenon of anthropomorphism better, it makes sense to take a look at studies and explanations from developmental psychology.
+The phenomenon of attributing intentions and \hl{animacy} to simple shapes based on motion has been intensively studied in developmental psychology.
 Two famous studies on the perception of and attribution to simple things have been done in the mid 1940s: Heider and Simmel's work on the \textit{attribution theory} \cite{heider_experimental_1944} and Michotte's studies on \textit{the perception of causality} \cite{michotte_perception_1963}.
@@
  \caption{Fritz Heider and Mary-Ann Simmel's animated film to study people's tendency to attribute animacy and intention to simple shapes; \textit{An experimental study of apparent behaviour}, 1944}
+ \fxnote{wrap text around this figure?}
  \label{fig:animacy_attribution}       % Give a unique label
@@
 One basic reasons for this are a person's physical constraints of being a human and nothing else.
-Consequently, one has no other experience than the self and in turn people tend to make inferences about others' mental states by relying inordinately on their own mental states.
+Consequently, one has no other experience than the self and in turn people tend to make inferences about others' mental states by relying inordinately on their own mental state.
 \footnote{Using one's own mental states and characteristics as a guide when reasoning about other humans is ego-centrism; when reasoning about non-human agents is anthropomorphism.
@@
     Both \textit{effectance} and \textit{sociality} are \textbf{motivational determinants of anthropomorphism}.
-\textit{Effectance} is understood as the motivation to interact effectively in one's environment: understand, predict, \hl{reduce uncertainty (this feeds again our hypothesis that as soon as a robot is not uncertain anymore, there is no need to keep on anthropomorphizing it)} about one's environment and the agents that inhabit it.
+\textit{Effectance} is understood as the motivation to interact effectively in one's environment: understand, predict, \hl{reduce uncertainty (this feeds again our hypothesis that as soon as a robot is not uncertain anymore, there is no need to keep on anthropomorphizing it)}\fxfatal{important!
+move/copy that to the 'model' section or discussion} about one's environment and the agents that inhabit it.
 According to Epley \textit{et al.}, anthropomorphism serves as one way to reduce uncertainty and increase comprehension of events in one's environment.
 They mention for instance, children (as they are in their early stages of life) appear to be more likely to anthropomorphize than adults, as they might feel more uncertain within their environment.
+
 	\textit{Sociality} describes the motivation for social contact, social connection, and social approval from other agents.
-Importantly for anthropomorphism, this social connection appears to be satisfied by connections with \hl{ \textit{"two of the most commonly anthropomorphized hon-human agents, namely pets and religious agents"}} \cite{epley_seeing_2007}.
+Importantly for anthropomorphism, this social connection appears to be satisfied by connections with \hl{ \textit{"two of the most commonly anthropomorphized non-human agents, namely pets and religious agents"}} \cite{epley_seeing_2007}.
 According to Epley \textit{et al.}, the motivation of being socially connected increases the tendency to anthropomorphize non-human agents because first sociality motivation increases the tendency to perceive human-like characteristics and traits even in non-human agents, and second it increases the tendency to search for sources of social connection in one's environment.
@@
 It has frequently been described that people ascribe intentions or emotions to their domestic robot, such as to a Roomba vacuum-cleaning robot \cite{krumm_my_2007,sung_robots_2009} or their AIBO robotic dog \cite{friedman_hardware_2003}.
-However, people's tendency to anthropomorphize technologies has not only been observed with robots but described earlier in human-computer interaction and related to digital agents \cite{reeves_media_1996, nass_anthropocentrism_1995}.
-Though, the phenomenon seems to be more coined in human-robot interaction than in other human-machine interaction fields.
-What makes anthropomorphism special in robotics, is probably related to the (unique) characteristics of robots in contrast to other technologies.
-Robots are embodied, physical agents, autonomously acting right next to us, and able to respond intelligently to us and the environment.
-These are factors that seem to facilitate anthropomorphism, due to the nature of the phenomenon and its origins itself.
-In robotics, anthropomorphism is further encouraged through specific anthropomorphic design of a robot.
-But what is the interest, which underlies the efforts of enhancing anthropomorphism through specific anthropomorphic design in robots?
+People's tendency to anthropomorphize technologies has besides been described earlier in human-computer interaction and related to digital agents \cite{reeves_media_1996, nass_anthropocentrism_1995}.
+Though, the phenomenon seems to be more coined in human-robot interaction than in other human-machine interaction fields, which is probably related to the embodied nature of robots.
+They are physical agents, autonomously acting right next to us, and also designed to interact intelligently with us and the environment.
+Besides, anthropomorphism may be further supported by a specific anthropomorphic \emph{design}.
+But what is the motivation which underlies the efforts of enhancing anthropomorphism through specific anthropomorphic design in robots?
 Why does anthropomorphism seem to be so important in robotics?
@@
 More concretely, it has been found that the appearance and function of a \hl{product (research in marketing?)}) impacts how people perceive it, interact with it, and build long-term relations with it \cite{bartneck_shaping_2004}.
-Consequently, the domain of (social) robotics tries to exploit this fact by enhancing anthropomorphism through anthropomorphic robots: \textit{"Applying anthropomorphism or zoomorphism changes the way how users try to understand and make sense of a [system] by projecting everyday \hl{expectations} of human and animalistic life onto it."} \cite{schmitz_concepts_2011}.
-Studies have further shown that perceived similarity between the user and the robot influences the intense of the participants' attributions towards the robot.
+Consequently, the domain of (social) robotics tries to exploit this fact by enhancing anthropomorphism through anthropomorphic robots: \textit{"Applying anthropomorphism or zoomorphism changes the way how users try to understand and make sense of a [system] by projecting everyday \hl{expectations} of human and animalistic life onto it."} \cite{schmitz_concepts_2011}\fxfatal{paragraph a bit confusing...}.
+Studies have further shown that perceived similarity between the user and the robot influences the intensity of the participants' attributions towards the robot.
 Thus, anthropomorphism plays an important role in the design of robots as it is strongly related to the perception of intelligence, fun, the attribution of intentions and thus the predictability of the robot \hl{which ref??}.
@@
 
-\begin{tikzpicture}
+\begin{tikzpicture}[scale=1.2]
 
@@
 \caption{Dynamics of anthropomorphism. We distinguish three main phases:
-\emph{initialization}, \emph{familiarization} and \emph{stabilization}. In the
-pre-interaction phase, users build an \emph{initial capital of
-anthropomorphism} (ICA). Once the interaction starts, the level of
-anthropomorphism increases due to the \emph{novelty effect}, and then decreases
-to reach a \emph{stabilized level of anthropomorphism} (SLA).
-During the interaction, unpredicted behaviors of the robot (\emph{disruptive
-behaviors}) locally increase the level of anthropomorphism.}
+\emph{initialization}, \emph{familiarization} and \emph{stabilization},
+preceded by a \emph{pre-interaction} phase. In the pre-interaction phase,
+users build an \emph{initial capital of anthropomorphism} (ICA). Once the
+interaction starts, the level of anthropomorphism increases due to the
+\emph{novelty effect}, and then decreases to reach a \emph{stabilized level
+of anthropomorphism} (SLA).  During the interaction, unpredicted behaviors
+of the robot (\emph{disruptive behaviors}) may lead to local increase of the
+level of anthropomorphism.}
+
 \label{fig:dynamics}
@@
 
-Why do we think that anthropomorphic inferences are likely to change over time and with growing experience a person has with a robot?
+Why do we think that anthropomorphic projections are likely to change over time and with growing experience a person has with a robot?
 The underlying process in anthropomorphism is understood as reasoning about and perceiving something non-human, and unknown or unfamiliar based on one's representation of the familiar and well-known concept of being human (or one-self).
@@
 Consequently, the robot should become more predictable and more familiar to the human user and inferences about it can be made based on the acquired knowledge.
+/fxfatal{confusing paragraph...needs reformulation. Could also be turned into a section introduction instead of a subsection}
 
@@
 observed during a short-term interaction reflects a sustaining social effect.
-Based on an extensive literature review \cite{fink_anthropomorphism_2012} and \hl{our own work} \fxfatal{Summarize
+Based on an extensive literature review previously published~\cite{fink_anthropomorphism_2012} and \hl{our own work} \fxfatal{Summarize
 these findings in a specific section!}, we believe that anthropomorphic effects in HRI are not always the same but evolve over time, along with growing interaction
@@
 long-term human-robot interaction. By long-term interaction, we mean direct
-(non-mediated), repeated interaction with the same robot, over (at least) several
-days. The nature of the interaction (goal-directed, entertainment, etc.) may vary.
+(non-mediated), repeated interaction with the same robot, over at least several
+days. The nature of the interaction (goal-directed, entertainment, etc.) may
+however vary.
 
-The model uses a \emph{normalized} level of anthropomorphic effects: because
-anthropomorphic effects are not quantified on an absolute scale, we present
-them as a normalized value, that span from a minimum (no anthropomorphic
-effects) to a maximum (corresponding to the novelty effect peak on
-Figure~\ref{fig:dynamics}). The actual maximum value of anthropomorphic effects
-is strongly correlated to the human, the robot and other factors we introduce
-below. Hence, the model we propose only focuses on the general \emph{shape} of
-the level of anthropomorphism over time, \ie the general dynamics of
-anthropomorphism.
+Anthropomorphism is quantified by a \emph{normalized level of anthropomorphic
+effects}: because anthropomorphic effects are not quantified on an absolute
+scale, we present them as a normalized value, that spans from a minimum (no
+anthropomorphic effects) to a maximum (corresponding to the novelty effect peak
+on Figure~\ref{fig:dynamics}). The actual maximum value of anthropomorphic
+effects depends on each unique combinations of human, robot and several other
+factors we introduce below, and thus varies. The general \emph{shape} of the
+model remains however the same and depicts the level of anthropomorphism over
+time, \ie the general dynamics of anthropomorphism.
 
 The model takes into account the duration of the interaction, the nature of the
-interaction, as well as acquired experience and familiarization mechanisms: We
-also propose to formally introduce a so-called \emph{novelty effect} that
-models the first phase of human-robot interaction, and during which specific
-anthropomorphic effect are observed.
+interaction, as well as acquired experience and familiarization mechanisms. We
+also formally introduce a so-called \emph{novelty effect} that
+models the first phase of human-robot interaction, during which a specific
+increase of anthropomorphic interactions is observed.
 
@@
 anthropomorphism, from an \emph{initial capital of anthropomorphism}
-(detailed in the next section) and a peak of anthropomorphic manifestations
+(detailed in the next section) to a peak of anthropomorphic manifestations
 that corresponds to the maximum of the \emph{novelty effect}.
@@
 ability to predict the behavior of the robot: the initial apparent behavioral
-complexity vanishes, and the robot is considered more and more as \hl{a machine (Julia: I would rather say "a tool")}.
+complexity vanishes, and the robot is considered more and more as a tool.
 Section~\ref{sec:familiarization} discusses the second phase.
 
-The last phase is the \emph{stabilization} phase. The level of anthrpomorphic
+The last phase is the \emph{stabilization} phase. The level of anthropomorphic
 effects tends to stabilize over a longer time, to reach a \emph{stabilized
@@
 
-	Initially, there is a given potential that a robot will be anthropomorphized.
-But what are the determinants of anthropomorphism?
+A robot has an initial potential of being anthropomorphized.
 It has been shown that some \textit{people} anthropomorphism more than others, some \textit{situations} induce anthropomorphism more than others, that \textit{children} tend to anthropomorphize more than adults, and some \textit{cultures} are notorious for their anthropomorphic religions and worldviews \cite{epley_when_2008}.
-Our proposed function to model the dynamics of anthropomorphism tries to take these variances into account and starts with what we call \textit{initial capital of anthropomorphism} (ICA) at time point $t_{0}$.
-The ICA describes the first (real or imagined) contact to a robot (see Figure \ref{fig:dynamics}).
-Time point $t_{0}$ can temporally be before the first real physical interaction with the robot, for instance, when a person learns about the existence of vacuum-cleaning robots and imagines using one (\textit{e.g.} when one watches an advertisement of the robot, or observes one at a trade show).
+Our model of anthropomorphism takes these determinants into account and initializes the level of anthropomorphic interactions between a human and a robot to a value that we call \textit{initial capital of anthropomorphism} (ICA on Figure~\ref{fig:dynamics}).
+The ICA describes the first (real or imagined) contact to a robot.
+Time point $t_{0}$ can be temporally before the first real physical interaction with the robot, for instance, when a person learns about the existence of vacuum-cleaning robots and imagines using one (\eg when one watches an advertisement of the robot, or observes one at a trade show).
 In this stage of "pre-interaction", people form initial expectations toward the robot and imagine how they will use / interact with it.
 Time point $t_{0}$ can be understood as duration of interaction = 0 and user experience = 0.
-How can we hypothetically quantify the ICA on a normalized scale of anthropomorphism?
-For this, we suggest three main factors that \textit{a priori} determine the potential that a robot will be anthropomorphized:
+We build the ICA on three main factors that \textit{a priori} determine the potential that a robot will be anthropomorphized:
 
@@
 
-	\item Human-centered factor: The \textbf{personality} and individual traits of the human user: Psychological characteristics / determinants that influence a person's tendency to anthropomorphize artifacts, see \cite{epley_seeing_2007}.
-Also other individual traits and demographic aspects are comprised (\textit{e.g.} age, gender, cultural background, professional background).
+    \item \emph{Human-centered factor}: The \textbf{personality} and individual traits of the human user: Psychological characteristics / determinants that influence a person's tendency to anthropomorphize artifacts~\cite{epley_seeing_2007}.
+Other individual traits and demographic aspects are comprised (\textit{e.g.} age, gender, cultural background, professional background).
 
-	\item Robot-centered factor: The robot's \textbf{design} and how it appears to the human user: Characteristics of the robot's form, behavior, and interaction modalities (anthropomorphic design), see \cite{fong_survey_2003}.
+    \item \emph{Robot-centered factor}: The robot's \textbf{design} and how it appears to the human user.
+Characteristics of the robot's form, behavior, and interaction modalities (anthropomorphic design)~\cite{fong_survey_2003}.
 
-	\item Situation-centered factor: The real or imagined \textbf{purpose} of the robot, including the situational context in which it is used: The task context and role in which the robot is used / experienced (environmental context), see \cite{joosse_what_2013}.
+    \item \emph{Situation-centered factor}: The real or imagined \textbf{purpose} of the robot, including the situational context in which it is used.
+The task context and role in which the robot is used / experienced (environmental context)~\cite{joosse_what_2013}.
 
@@
 
-	The ICA comprises some hypothetical values for each of these three factors, such that different ICA values can be obtained, given the robot, human user, and environmental context.
+The ICA comprises some hypothetical values for each of these three factors, such that different ICA values can be obtained, given the robot, human user, and environmental context\fxfatal{??}.
 
@@
 
-	For \textbf{design}, we understand that a robot that follows an anthropomorphic design (e.g.
-NAO) leads to a higher ICA than a rather functional robot (e.g.
-Roomba).
+    For \textbf{design}, we understand that a robot that follows an anthropomorphic design (\eg NAO) leads to a higher ICA than a rather functional robot (\eg Roomba).
 Also, a robot that is able to display facial expressions would increase the ICA.
 However, \hl{as discussed before} a classification of the "amount" of anthropomorphic design in a robot, as for instance suggested by Fong \textit{et al.} \cite{fong_survey_2003}, can be difficult.
-Nevertheless, the important aspect is how the robot appears to the user, e.g.
-human-like or machine-like.
-Studies have shown that an anthropomorphic robot is perceived differently to a non-anthropomorphic robot.
+Nevertheless, the important aspect is how the robot appears to the user, \eg human-like or machine-like.
+Studies have shown that an anthropomorphic robot is perceived differently to a non-anthropomorphic robot\fxfatal{...this sentence sounds strange like that.
+Need references or better integration in the paragraph}.
 
-	For \textbf{purpose}, we propose that the real or imagined context in which a robot is used and the interaction that it brings along, impacts how far the robot will be attributed human-like characteristics.
-We	draw on findings such as presented in Joosse \textit{et al.}.
+    By \textbf{purpose} we suggest that the real or imagined context in which a robot is used and the interaction that it brings along, impacts how far the robot will be attributed human-like characteristics.
+We	draw on findings such as presented in Joosse \textit{et al.}\fxfatal{reference?}.
 The authors showed that when the same robot (NAO) is used in a different task context (cleaning task \textit{vs.} tour guide), this influences the perception of the "personality" of the robot.
-In general, we think that a robot which is (imagined to be) used in a social, entertaining or playful context leads to a higher ICA than a robot which is used for a serious task (security, rescue, etc.).
+In general, we think that a robot which is imagined to be used in a social, entertaining or playful context leads to a higher ICA than a robot which is used for a serious task (security, rescue, etc.).
 This idea receives support from \hl{XX (Kiesler / Goetz?)} work that revealed that people prefer a serious robot for serious tasks and a less serious robot for more playful tasks \hl{REF}.
@@
 In this section, we discuss more speculative aspects and hypotheses that follow
-from the model. These aspects would require further investigation and
-experimental support to be validated.
+from the model. These aspects would benefit further investigations and
+experimental support.
 
@@
 %\resizebox{\linewidth}{!}{
-\begin{tikzpicture}[scale=0.8, transform shape]
+\begin{tikzpicture}[scale=1.2, transform shape]
 \baselineskip=8pt
@@
 sequences of the robot) or short interaction (touching, short talk like
-greetings), the human enters the cognitive phase II: in this phase, the human
-starts to build a behavioral and cognitive model of the robot that would
-support both the observed and imagined capabilities of the robot. Based on the
-\emph{familiarity thesis}\fxfatal{citation!}, we suggest that the human first
-projects onto the robot mental models of similar agents he/she is already
-familiar with. This may range from animals to adults, through pets and
-children. We hypothesize that the nature of the projected mental model, as well
-as how deep the human engages in this projection, might be driven by the same
-parameters as we presented for the \emph{initial capital of anthropomorphism}
-(section~\ref{sec:ica}, p.\pageref{sec:ica}).
+greetings), we suggest the human enters the cognitive \emph{phase II}: in this
+phase, the human starts to build a behavioral and cognitive model of the robot
+that would support both the observed and imagined capabilities of the robot.
+The \emph{familiarity thesis}\fxfatal{citation!} would support the idea that
+the human first projects onto the robot mental models of similar agents he/she
+is already familiar with. This may range from animals to human adults, through
+pets and children. We hypothesize that the nature of the projected mental
+model, as well as how deep the human engages in this projection, might be
+driven by the same parameters as we presented for the \emph{initial capital of
+anthropomorphism} (section~\ref{sec:ica}).
 
-We identify a further transition to the cognitive phase III after a
+We identify a further transition to the cognitive \emph{phase III} after a
 \emph{contextualized} interaction. A \emph{contextualized} interaction is
@@
 \emph{personality} in ICA factor), but at this stage, the \emph{perception} of
-the robot (its shape for instance) and its intended \emph{purpose} play only a
-minor role. It is mostly a human-centric process.
+the robot (its shape for instance) and its intended \emph{purpose} play a less
+important role. It is mostly a human-centric process.
+
+The result of this third phase is an iteratively adapted cognitive model of the
+robot.
 
@@
 Sub-cognitive anthropomorphism typically \emph{initiates} the novelty effect by
-rapidly engaging the human in the interaction through this initial projected
+rapidly engaging the human in the interaction through an initial projected
 \emph{agency}, whereas cognitive phase II (projection of familiar mental
@@
 The cognitive phase II also overlaps with the \emph{familiarization} phase: as
-(s)he get used to the robot, we hypothesize the human restate and adapt its
+(s)he get used to the robot, we hypothesize the human restates and adapts its
 cognitive model of the robot by iteratively reshaping pre-existent, familiar
@@
     Perceived as non-intentional & case I  & case IIIa  \\ \hline
-    Perceived as intentional &  case IIIb & case II  \\ \hline
+    Perceived as intentional &  case IIIb & case II \\
+    \hline
     \end{tabular}
@@
 When talking about \emph{unexpected robot behaviors}, several distinct cases
-must be considered, summarized in Table~\ref{fig:perceptionUnexpectedBehavior}.
+must however be considered, summarized in Table~\ref{fig:perceptionUnexpectedBehavior}.
 

### 2013-07-01 dynamics-anthropomorphism.tex
Re-introduced many part of the original intro by Julia
Partially revert a30995f1849a1efe6a92de7ed6f513762e1801c5

@@
 
-\usepackage[draft]{fixme}
+\usepackage[draft, nomargin, marginclue, footnote]{fixme}
+\fxsetup{targetlayout=color}
+
 \rightheader{Journal of Human-Robot Interaction}
@@
 Real or imagined non-human agents can be "anything that acts--or is believed to act--with apparent independence, including non-human animals, natural forces, religious agents, technological gadgets, or mechanical devices".
-Such anthropomorphic representations are important determinants of how a person behaves towards these agents, or how a person may behave in light\fxnote{in light?} of these agents.
+Such anthropomorphic representations are important determinants of how a person behaves towards these agents, or how a person may behave \fxnote*{in light?}{in light} of these agents.
 
@@
 
-In this context, anthropomorphism has received remarkable attention\fxnote{contradict with intro} in the study of humans interacting with artificial entities, and has been a subject in Human-Computer Interaction (HCI) and Human-Robot Interaction (HRI).
+In this context, anthropomorphism has received \fxnote*{contradict with intro}{remarkable attention} in the study of humans interacting with artificial entities, and has been a subject in Human-Computer Interaction (HCI) and Human-Robot Interaction (HRI).
 Following the \textit{Media Equation}, it has been described that people mindlessly react socially to computers \cite{reeves_media_1996}.
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-%
-%
-%				XXX
-%
-%
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\paragraph{Anthropomorphism in robotics} Literature on anthropomorphism in robotics is quite diverse and one strives hard to extract a coherent conclusion.
+There is no commonly accepted definition about the terms used and the terminology is not clear.
+However the terms \textit{anthropomorphic or human-like are often used as if their meanings are clear and agreed upon"} \cite{persson_anthropomorphism_2000}.
+Consequently, Duffy \cite{duffy_anthropomorphism_2002} argues that terms might even be misused.
+For instance, some researchers refer to \textit{"the robot's level of anthropomorphism"} \cite{bartneck_is_2007}, however, others argue that anthropomorphism emerges in the \textit{interaction} between the technology and the user, thus a system or an artifact does not "contain anthropomorphism" \textit{per se} \cite{persson_anthropomorphism_2000} but only gives rise to the process of anthropomorphizing in a given user and situation.
+Further, robotics is a multi-disciplinary field and researchers from very different domains might have diverse or even contradictory understandings of anthropomorphism.
+Epley \textit{et al.} \cite{epley_seeing_2007} notice that despite the fact that anthropomorphism in the perception of non-human agents is commonly observed, it is poorly understood.
+The phenomenon itself has been found to be very complex but sometimes subtle and hard to study.
+Another constraint that limits the reliability of some findings is, that most experiments on anthropomorphism are conducted in controlled lab-settings during short-term interactions.
+This experimental setting (short term and laboratory context) can be critical when studying a social phenomenon like anthropomorphism and possibly lead to over-interpretations.
+Some studies also seem to contrast two or more different anthropomorphic and mechanical systems that might not be appropriate for comparison under the given context and research question.
+\hl{say more}
 
-\section{XXX}
-\label{sec:}
+To sum it up, while anthropomorphism in robotics is a commonly discussed and studied trait of human-robot interaction, we think it is paradoxically an overlooked research topic.
+The understanding of anthropomorphism in robotics seems to not take into account the wide range of phenomena that it encompasses.
+The traditional understanding of anthropomorphism in robotics to date considers two main factors that account for the social phenomenon: the characteristics of \textbf{1) the robot's design} (degree of human-likeness) and the psychological determinants in \textbf{2) the human user} (see \cite{epley_seeing_2007}).
+It has been shown that both these factors can facilitate or hinder anthropomorphism.
+We propose to go beyond this traditional perception of anthropomorphism as a static feature of HRI: Based on Persson \textit{et al.}'s~\cite{persson_anthropomorphism_2000} argumentation that anthropomorphism is a multi-layered phenomenon which arises in different levels, we suggest to understand anthropomorphism as a \emph{dynamic}, \emph{context-dependent} process.
+To this end, we apply Persson \textit{et al.}'s six levels on anthropomorphism to HRI and introduce three \emph{interaction phases}.
+These interaction phases of anthropomorphism reflect also the results of a long-term study that we conducted in a real human environment and provide an account of the so-called \textit{novelty effect}.
+We also draw attention to two new determinants of anthropomorphism, namely, the context of use and the fact of getting used to a system over time.
+We propose to add these two aspects as a third factor, the characteristics of \textbf{3) the interaction} (time and space), to the previous two factors of anthropomorphism (robot and user).
+
+%% -> Commented out the overview as it does not match what we actually present... maybe we need a new one?
+% We would further like to review and discuss research on anthropomorphism in robotics and human-like design of robots.
+We first provide a comprehensive understanding of the phenomenon drawing on theories from developmental psychology and cognitive sciences.
+We then present the trends of different kinds of anthropomorphic forms in robots and discuss their role in social robotics.
+The article integrates related work from human-robot interaction studies, reporting on findings from experiments with human subjects interacting with and evaluating various types of systems.
+We try to give a coherent view on the topic, outline similarities and antithetic findings, and contribute to a better understanding of anthropomorphism in robotics, and the acceptance of human-like characteristics in robots.
+We also aim to constructively discuss anthropomorphic design of personal and socially interactive robots.
 
@@
 The term \textbf{anthropomorphism} is used in different senses throughout natural sciences, psychology, Human-Computer Interaction, and Human-Robot Interaction \cite{duffy_anthropomorphism_2003}.
-There is no single accepted definition\fxfatal{already said before}.
 Originally, anthropomorphism comes from the Greek \textit{`anthropos'} for `man' (or `human') and \textit{`morphe'} for `form/structure' (or `shape').
@@
 Findings suggest that people tend to hold richer mental models about anthropomorphic robots in contrast to mechanic ones \cite{kiesler_mental_2002}.
-
-\hl{here or later? : familiarity thesis does probably not hold after one get's acquantained with a robot.}
+Later in this article, we may however come to question this result for longer human-robot interactions, after one get's acquantained with the robot's behaviour.
 
@@
 Studies showed that there are people who directly talk to their robot (even if it does not recognize speech), give it a name, greet it, wonder about its intentions or actions \cite{eyssel_anthropomorphic_2010,fink_anthropomorphic_2012,forlizzi_how_2007,fussell_how_2008,kiesler_anthropomorphic_2008}.
-It has frequently been described that people ascribe intentions or emotions to their domestic robot, such as to a Roomba vacuum-cleaning robot \cite{krumm_my_2007,sung_robots_2009} or their AIBO robotic dog \cite{friedman_hardware_2003}.
+It has frequently been described that people ascribe intentions or emotions to their domestic robot, such as to a Roomba vacuum-cleaning robot \cite{krumm_my_2007,sung_robots_2009} or the AIBO robotic dog \cite{friedman_hardware_2003}.
 People's tendency to anthropomorphize technologies has besides been described earlier in human-computer interaction and related to digital agents \cite{reeves_media_1996, nass_anthropocentrism_1995}.
-Though, the phenomenon seems to be more coined in human-robot interaction than in other human-machine interaction fields, which is probably related to the embodied nature of robots.
+Though, the phenomenon seems to be more coined in human-robot interaction than in other human-machine interaction fields, due to the embodied nature of robots.
 They are physical agents, autonomously acting right next to us, and also designed to interact intelligently with us and the environment.
@@
 Thus, anthropomorphism plays an important role in the design of robots as it is strongly related to the perception of intelligence, fun, the attribution of intentions and thus the predictability of the robot \hl{which ref??}.
+
+"[...] the experiment demonstrates that human beings implicitly attribute human-like qualities, such as mental states, to nonhuman agents.
+This finding was evident on a neurophysiological level as well as behavioral level." \cite{hegel_understanding_2008}\fxwarning{What to do with this quote?
+'neuro' level maybe interesting?}
+
+\subsection{Anthropomorphism as a multi-layered phenomenon}
+\label{sec:3.4}
+
+Anthropomorphism can also be viewed as an \textit{experience} that arises in the \textit{interaction} between a set of user expectations and external reality \cite{persson_anthropomorphism_2000}, (Figure~\ref{fig:anthropomorphism_and_interaction}).
+Persson \textit{et al.} suggest that the social phenomenon involves several levels, like primitive psychology, folk-psychology, social stereotypes, and emotional anthropomorphism.
+
+\begin{figure}[ht!]\centering
+% Use the relevant command to insert your figure file.
+% For example, with the graphicx package use
+  \includegraphics[scale=0.42]{persson_anthropomorphism.png}
+% figure caption is below the figure
+ \caption{Anthropomorphism emerges in the (real or imagined) interaction between robot and user; illustration taken from \cite{persson_anthropomorphism_2000} \hl{maybe we don't put the figure here, it was just to illustrate what I mean}}
+ \label{fig:anthropomorphism_and_interaction}       % Give a unique label
+ \end{figure}
+
+We would like to take up the proposition to discriminate different levels of anthropomorphism, since each has its own characteristics and involves specific types of user expectations.
+This differentiation could allow to draw inferences on the human-robot relationship from the observed level of anthropomorphism.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+%
+%
+%				DOES ANTHROPOMORPHISM MAKE ROBOTS MORE SOCIAL?
+%
+%
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Does anthropomorphism make robots more social?}
+\label{sec:more_social}
+
+	In general, it is suggested that increasing human-likeness of a robot	 will lead to more perceived \textit{affinity} from the human side \cite{mori_uncanny_1970}.
+This theoretical concept is also supported by psychological determinants of perceiving human-likeness in something non-human: \textit{"the more similar in appearance, the more people are likely to use themselves as a source of induction and anthropomorphize these nonhuman agents"} \cite{epley_seeing_2007}.
+Further, empirical studies have shown that robots with human-like forms can enhance social responses from humans which in turn can have a positive impact on acceptance \cite{venkatesh_theoretical_2000,duffy_anthropomorphism_2003,goetz_cooperation_2002}.
+People responded more positively to an artifact that displayed human-like behavioral characteristics (emotions, facial expression) in contrast to a purely functional design \cite{eyssel_anthropomorphic_2010,krach_can_2008,reeves_media_1996,riek_how_2009}.
+Overall, these results suggest that human-like features in robots enhance anthropomorphism, and in turn create a social view toward the robot.
+
+Well known from the HRI community, we may mention the other side of human-like behaviours and appearance: a not yet very well defined thin line separates acceptable human-like forms in robots from creepy artificial \textit{almost} human-like appearing robots.
+The underlying theory for this viewpoint is stated as the \textit{Uncanny Valley} \cite{mori_uncanny_1970} which suggests that artificial human-like forms are only acceptable up to a certain degree but lead to reluctance if they fail in trying to attain human-likeness \hl{cross-ref to later and figure}.
+
+The theory (Figure~\ref{fig:uncanny_valley}) hypothesizes that a person's response to a human-like robot would abruptly shift from empathy to revulsion as it approached, but failed to attain, a lifelike appearance \cite{mori_uncanny_1970}.
+Starting with low degrees of anthropomorphic cues in a robot, humans seem to readily accept and prefer them compared to purely mechanical robots.
+In general, one can say that up to a certain (yet not very well defined) degree, the more human-like the robot, the more affection it can engender through familiar communication references.
+
+\begin{figure}\centering
+% Use the relevant command to insert your figure file.
+% For example, with the graphicx package use
+  \includegraphics[scale=0.6]{uncanny-valley.jpg}
+% figure caption is below the figure
+ \caption{Mashiro Mori, illustration of the \textit{Uncanny Valley}, originally from 1970; picture from a manuscript version of \cite{mori_uncanny_2012}}
+ \label{fig:uncanny_valley}       % Give a unique label
+ \end{figure}
+
+Another sensitive aspect is that with robots that closely resemble humans, ethical issues arise.
+For instance, we need to consider how far we actually want an \textit{artificial agent} to resemble ourselves and how far it should act `artificially socially' toward humans, and what happens as soon as it is considered a \textit{moral agent} \cite{sullins_when_2006}.
+Using \textit{socially interactive robots} in contexts involving elderly care or rehabilitation for disabled / handicapped persons, autistic children is also a controversially discussed topic \cite{robins_robots_2005}.
+
+	when slowly increasing its human-likeness, the more affection
+
+The idea of the hypothesis follows Freud's description of the uncanny (a translation from the German word `unheimlich') \hl{ref Freud, The Uncanny}: "it derives its terror not from something externally alien or unknown but - on the contrary - from something strangely familiar which defeats our efforts to separate ourselves from it".
+\cite{hegel_understanding_2008}
+
+	Also: Simulation Theory
+
+	"The anthropomorphic design of human-machine interfaces is inevitable.
+The important criterion is to seek a balance between people's expectations and the machines capabilities." \cite{duffy_anthropomorphism_2002}
+
+	"What is the ideal set of human features that could supplement and augment a robots  social functionality?" \cite{duffy_anthropomorphism_2002}
+
+	Though, the 'anthropomorphic design principle" seems beneficial, it also raises ethical issues and has been reviewed critically in terms of acceptance.
+How far do we want a robot to resemble a human or act like a human?
+
+	Findings that support anthropomorphic form in robots because they found people respond with anthropomorphizing these kind of robots, and in turn act more social toward them or accept them more easily:
+
+	\hl{empathy --> check Iolanda's paper}
 

### 2013-07-01 dynamics-anthropomorphism.tex
Fixed layout of the disruptive behaviours table

@@
 
-\begin{figure}
-\begin{center}
-    \begin{tabular}{ | >{\centering\arraybackslash}m{1.5cm} | >{\centering\arraybackslash}m{2cm} | >{\centering\arraybackslash}m{2cm} |}
-    \hline
+\begin{figure}\footnotesize
+    \begin{tabular}{  >{\centering\arraybackslash}m{2cm} | >{\centering\arraybackslash}m{2cm} | >{\centering\arraybackslash}m{2cm} }
      & Unplanned by the robot & Planned by the robot \\ \hline
     Perceived as non-intentional & case I  & case IIIa  \\ \hline
-    Perceived as intentional &  case IIIb & case II \\
-    \hline
+    Perceived as intentional &  case IIIb & case II 
     \end{tabular}
-\end{center}
 \caption{

### 2013-07-01 dynamics-anthropomorphism.tex
Detail what 'introspective' means

@@
 user may besides hypothesize that the robot has \emph{introspective}
-capabilities \hl{(what is this?)}, which in turn may leads to higher anthropomorphism level.  On the
-contrary, if the robot shows no sign of recognizing its own failure, the user
-may ascribe a lower level of anthropomorphism to the robot.
+capabilities (it can reflect on its own internal state), which in turn may
+leads to higher anthropomorphism level.  On the contrary, if the robot shows no
+sign of recognizing its own failure, the user may ascribe a lower level of
+anthropomorphism to the robot.
 

### 2013-07-01 dynamics-anthropomorphism.tex
WIP on the Familiarization phase

@@
 
+\emph{Familiarization}, in this context, means \emph{to get acquainted with}:
+it is not to be confused with the \emph{familiarity thesis} that relates to the
+projection of already known cognitive models onto the robot. We discuss this
+aspect at section~\ref{sec:cognitivemodel}.
+
+The \emph{familiarization phase} starts at the peak of the \emph{novelty
+effect}: anthropomorphic effects are at their maximum, the user thinks (s)he is
+\emph{potentially} facing an agent endowed with ``human-level intelligence'' to
+take McCarthy's words.
+
+This is a transient state that vanishes as soon as the human observe that the
+behaviour of the robot is \emph{predictable} and possibly \emph{deceptive} (for
+instance, it talks but does not understand when we talk to him; it has eyes but
+does not recognize everyday objects I show to him; etc.).
+
 \paragraph{Disruptive behaviors}
-\ref{sec:disruptive}
+
+The model also represents \emph{disruptive behaviors} as local
+increases of anthropomorphic effects in the familiarization phase (and at a
+lesser extend, in the stabilization phase) (Figure~\ref{fig:dynamics}).
+
+By \emph{disruptive behaviors}, we mean any behavior exhibited by the robot
+that is unexpected by the user: for instance, a robot may usually follow always
+the same route to go to two different places in a house, and suddenly change
+the route. The actual underlying reason may span from a bug to the detection of
+a new possible obstacle, but as long as this reason is not immediately
+understood by the user, we count the behavior as \emph{disruptive}.
+
+Section~\ref{sec:disruptive} propose a typology of disruptive behaviors and
+discusses the possible consequences on the level of anthropomorphism, which may
+both increase if the user perceives (rightfully or not) a form of
+intentionality, or decrease if the unexpected behavior is perceived as a
+failure.
 
 \paragraph{Expectation mismatch}
+
+Besides, we propose to call \emph{expectation mismatch} the delta between the
+initial capital of anthropomorphism for a given tuple (user, robot, context)
+and the anthropomorphism peak of novelty effect (Figure~\ref{fig:dynamics}).
+\fixme{Need to rediscuss what this delta actually represent...}
 

### 2013-07-08 dynamics-anthropomorphism.tex
Rewrite/complete section on familiarization

--- 2013-07-01 dynamics-anthropomorphism.tex
@@
 
+\emph{Familiarization}, in this context, means \emph{to get acquainted with}.
+It is not to be confused with the \emph{familiarity thesis} that relates to the
+projection of already known cognitive models onto the robot. We discuss this other
+aspect at section~\ref{sec:cognitivemodel}.
+
+The \emph{familiarization phase} starts at the peak of the \emph{novelty
+effect}: anthropomorphic effects are at their maximum, the user thinks (s)he is
+potentially facing an agent aiming at ``human-level intelligence'' (to take
+McCarthy's words). This is a transient state that quickly vanishes, and the
+projected anthropomorphism then starts to decrease while the human observes and
+recognizes that the behaviour of the robot is generally \emph{predictable} and
+possibly \emph{deceptive} (for instance, it talks but does not understand when
+we talk ; it has eyes but does not recognize everyday objects we show ; etc.).
+
 \paragraph{Disruptive behaviors}
-\ref{sec:disruptive}
+
+By \emph{disruptive behaviors}, we mean any behavior exhibited by the robot
+that is unexpected by the user: for instance, a robot may usually follow always
+the same route to go to two different places in a house, and suddenly change
+the route. The actual underlying reason may span from a bug to the detection of
+a new possible obstacle, but as long as this reason is not immediately
+intelligible to the user, the behavior counts as \emph{disruptive}.
+
+Our model represents \emph{disruptive behaviors} as local increases of
+anthropomorphic effects in the familiarization phase (and at a lesser extend,
+in the stabilization phase) (Figure~\ref{fig:dynamics}): because such behaviors
+are unexpected, a human observer interprets them as the result of a richer
+deliberative process.
+
+This is however to modulate depending on the real and percieved reasons of the
+unexpected behavior.  Section~\ref{sec:disruptive} discusses more in depth the
+mental correlates of disruptive behaviors. It proposes a typology that relates
+them to the anthropomorphism they induce. It may increase if the user perceives
+(rightfully or not) a form of intentionality, as well as decrease if the
+unexpected behavior is perceived as a failure.
 
 \paragraph{Expectation mismatch}
+
+Besides, we propose to call \emph{expectation mismatch} the delta between the
+initial capital of anthropomorphism for a given tuple (user, robot, context)
+and the anthropomorphism peak of novelty effect (Figure~\ref{fig:dynamics}).
+\fixme{Need to rediscuss what this delta actually represent...}
 

### 2013-07-08 dynamics-anthropomorphism.tex
Added a section in discussion on experimental cues of anthropomorphism

@@
 
+\subsection{Behavioral cues of anthropomorphism}
+\label{sec:behavioralcues}
+
+Our model suggests to analyze anthropomorphism based on a \emph{relative and
+normalized level of anthropomorphic effects} instead of an absolute
+quantitative assessment of anthropomorphic evidences. Similarly we introduce
+two specific \emph{abstract} levels of anthropomorphism, the \emph{Initial
+Capital of Anthropomorphism} and the \emph{Stabilized Level of
+Anthropomorphism}: while we discuss the factors on which those values are
+build, we did not formally investigated the experimental cues or evidences
+that would allow to actually quantify those levels.
+
+This is explained by the intricacy and interdependency of those behaviors.
+Their correct identification and interpretation rely on psychosomatic cues that
+the authors did not investigate.
+
+A formal methodology for the assessment of anthropomorphic effects in HRI, as
+well as a typology of these effects is still to be devised.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2013-07-08 dynamics-anthropomorphism.tex
Use hyperref package to generate PDF index
[wip] First pass on Anthropomorphism during Stabilization Phase

@@
 \usepackage{textcomp}
+
+\usepackage[bookmarks]{hyperref}
 
@@
 factors we introduce below, and thus varies. The general \emph{shape} of the
-model remains however the same and depicts the level of anthropomorphism over
+model remains however the same and depicts the evolution of anthropomorphism over
 time, \ie the general dynamics of anthropomorphism.
@@
 
-This is however to modulate depending on the real and percieved reasons of the
+This is however to be modulated depending on the real and percieved reasons of the
 unexpected behavior.  Section~\ref{sec:disruptive} discusses more in depth the
@@
 
+If, after the familiarization phase, no anthropomorphic effects are observed
+anymore, the \emph{Stabilized Level of Anthropomorphism} is zero. This can either be interpreted as the user
+considering the robot as merely a tool, or as a consequence of no interactions
+taking place anymore with the robot (robot not used)\fxwarning{reference to the
+roomba experiment}.
+
 \paragraph{Stabilized Level of Anthropomorphism (SLA)}
 
-\fxnote{Note that ICA and SLA are NOT correlated}
+The \emph{Stabilized Level of Anthropomorphism} (SLA on
+Figure~\ref{fig:dynamics}) describes the long-term lasting level of
+anthropomorphism.  Like the ICA, the SLA has a unique value per triplet
+(\emph{human}, \emph{robot}, \emph{context of interaction}).
+
+We suggested that the ICA is built on three factors (section~\ref{sec:ica}):
+user's \emph{personality}, robot's \emph{design} and interaction \emph{purpose}
+(or \emph{interaction context}). The user's personality and the context of use
+do also influence the SLA. In particular, it appears that the user's level of
+acquaintance with technologies plays an important role in long-term tendency to
+anthropomophize (people more familiar with technology understand, and hence
+predict, better the behavior of the robot, which in turn lead them more
+frequently to ultimately consider the robot as a simple tool).
+
+The robot's design, on the other hand, plays a more subtle role: lasting
+anthropomorphic effects have been observed on non-anthropomorphic robots (like
+the iRobot Roomba or the military iRobot PackBot\footnote{Rodney Brooks has
+reported in keynotes that occasionaly soldiers would give a name to
+\emph{their} PackBot and require it to be repared instead of being replaced by
+another one in case of incident.}), and on the contrary, anthropomorphic
+designs can lead to higher expectation deceptions, resulting in the robot not
+being used anymore.
+
+Note that the \emph{Initial Capital of Anthropomorphism} and the
+\emph{Stabilized Level of Anthropomorphism} are generally not correlated: one
+individual may have high expectations (high ICA), and get disappointed by the
+actual abilities of the robots, down to considering it as a simple machine/tool
+(low SLA), while another one with the same high ICA may, for instance, create
+lasting affective bonds with the robot, and keep anthropomorphizing it (high
+SLA).
 

### 2013-07-11 dynamics-anthropomorphism.tex
refinements in the first sections

@@
 \abstract{While anthropomorphism in robotics is a commonly discussed trait of
-HRI, it is paradoxically an overlooked research topic. This article
+HRI, it paradoxically lacks formal grounds. This article
 attempts first at providing a comprehensive synthesis of the social
@@
 existing literature in the HRI community, to ground the concept of
-\textit{anthropomorphism}. We further briefly present different kinds
-of \textit{anthropomorphic design} of robots and outline their role in
-social robotics\fxfatal{do we really do?}. We then suggest to go beyond the traditional
+\textit{anthropomorphism}. We then suggest to go beyond the traditional
 perception of anthropomorphism as a static feature of a system: we propose to
@@
 context-dependent process, which evolves over time and accounts for
-special events like the so-called \textit{novelty effect}. To this end,
+special events such as the so-called \textit{novelty effect}. To this end,
 we introduce a model of anthropomorphism that analyzes the phenomenon
@@
 
-The essence of anthropomorphism is perceiving human-like characteristics in either real or imagined non-human agents.
-According to Epley \textit{et al.} \cite{epley_when_2008}, these human-like characteristics may include physical appearance (such as a religious agent believed to look human-like), emotional states perceived to be uniquely human, or inner mental states and motivations.
-Real or imagined non-human agents can be "anything that acts--or is believed to act--with apparent independence, including non-human animals, natural forces, religious agents, technological gadgets, or mechanical devices".
-Such anthropomorphic representations are important determinants of how a person behaves towards these agents, or how a person may behave \fxnote*{in light?}{in light} of these agents.
+The essence of anthropomorphism is the perception of human-like characteristics in either real or imagined non-human agents.
+According to Epley \textit{et al.} \cite{epley_when_2008}, these human-like characteristics may include physical appearance, emotional states perceived to be uniquely human, or inner mental states and motivations.
+Real or imagined non-human agents can be "anything that acts -- or is believed to act -- with apparent independence, including non-human animals, natural forces, religious agents, technological gadgets, or mechanical devices".
+Such anthropomorphic representations are important determinants of how a person perceives and in turn behaves towards these agents, or how a person may behave in light of these agents \cite{epley_when_2008}.
 
@@
 
-In this context, anthropomorphism has received \fxnote*{contradict with intro}{remarkable attention} in the study of humans interacting with artificial entities, and has been a subject in Human-Computer Interaction (HCI) and Human-Robot Interaction (HRI).
-Following the \textit{Media Equation}, it has been described that people mindlessly react socially to computers \cite{reeves_media_1996}.
-The phenomenon has also been observed with virtual characters \hl{cite [50, 100] in rosenthal-von der P{\"u}tten (2013)}, and more recent studies investigated how far people ascribe personality or intentions to artificial agents \hl{references}\fxnote{Rosenthal is not enough?} and whether they show empathetic behavior toward robots \cite{rosenthal-vonderputten_experimental_2013}.
+Phenomenons related to anthropomorphism -- along with questions such as "how much human do we perceive in the non-human" or "how human-like do we treat non-human artifacts" (and why?) -- have received remarkable attention in the domains of Human-Computer Interaction (HCI) and Human-Robot Interaction (HRI): the study of humans interacting with an artificial system / machine.
+Following the \textit{Media Equation}, it has been described that people mindlessly react socially to computers \cite{reeves_media_1996} and may even attribute human (social) characteristics to their artificial counterpart.
+The phenomenon has also been observed with virtual characters \hl{cite [50, 100] in rosenthal-von der P{\"u}tten (2013)}, and more recent studies investigated how far people ascribe personality or intentions to artificial emobdied agents or whether they show empathetic behavior toward robots \cite{rosenthal-vonderputten_experimental_2013}.
 The common base for this research is the assumption that humans perceive or react to a non-human agent or artifact as somewhat similar to a human.
 
-We furthermore use in this article \emph{anthropomorphic effects} to denote the
-observable correlates of anthropomorphism. These include, amongst others,
-verbal behaviors (like the use of pronouns ``he/she''), kinesics (like hugging
-the robot) or anticipation of certain robot's actions.
+In this article we will use the term \emph{anthropomorphic effect} to denote observable correlates of anthropomorphism. With these we include, amongst others,
+verbal utterances (such as direct speech or the use of pronouns "he/she"), (social) gestures (such as a hug, waving, deictic gestures) or \hl{anticipation of certain actions of an agent [what??]}.
 
@@
 Second, anthropomorphism does not merely entail animism, as animate life is not a uniquely human-like characteristic.
-Third, anthropomorphism does not include any requirement of reasoned or reflective endorsement of an inference (\hl{the strength of anthropomorphic inferences can vary} \footnote{for further explanation the reader may refer the original work \cite{epley_when_2008}.}).	Finally, anthropomorphism is not necessarily inaccurate.
-A psychological theory should take this (in)accuracy in anthropomorphism into account and predict variability in the tendency to perceive human-like traits in non-human agents\fxfatal{End of paragraph is unclear.
-We need to reformulate}.
+Third, anthropomorphism does not include any requirement of reasoned or reflective endorsement of an inference (\hl{the strength of anthropomorphic inferences can vary} \footnote{for further explanation the reader may refer to the original work \cite{epley_when_2008}.}).	Finally, anthropomorphism is not necessarily inaccurate.
+A psychological theory should take this (in)accuracy in anthropomorphism into account and predict variability in the tendency to perceive human-like traits in non-human agents.
+In conclusion, it has been noted that anthropomorphism is a very complex phenomenon - in itself, its understanding, and when studying it.
+A common formal ground is missing; however, it is important to be clear about what exactly we mean when using the term anthropomorphism.
 
-%ANTHROPOMOPRHIC DESIGN
+\paragraph{Anthropomorphism in robotics \hl{[I think this first paragraph should go somewhere else, later probably]}}
 
-Anthropomorphism represents just one of many examples of induction whereby "people reason about an unknown stimulus based on a better-known representation of a related stimulus" \cite{epley_when_2008}, in this case reasoning about a non-human agent based on representation of the self or humans.
+Anthropomorphism represents just one of many examples of induction whereby "people reason about an unknown stimulus based on a better-known representation of a related stimulus" \cite{epley_when_2008}, in this case reasoning about a non-human agent based on representation of the self or other humans.
 This supports the usual role we assign to anthropomorphism in robotics: the anthropomorphic design of a robot encourages people to reason about this unfamiliar system \emph{as if} it was a human.
-To increase this tendency, robots are designed with anthropomorphic forms (human-like forms or lifelike forms, in the broader sense), or are able to display and use human-social behavior.
+To increase this tendency, robots are designed with anthropomorphic forms (human-like or lifelike forms, in the broader sense), or are able to display and use human-social cues when interacting with humans.\\
 
-\paragraph{Anthropomorphism in robotics} Literature on anthropomorphism in robotics is quite diverse and one strives hard to extract a coherent conclusion.
-There is no commonly accepted definition about the terms used and the terminology is not clear.
-However the terms \textit{anthropomorphic or human-like are often used as if their meanings are clear and agreed upon"} \cite{persson_anthropomorphism_2000}.
-Consequently, Duffy \cite{duffy_anthropomorphism_2002} argues that terms might even be misused.
-For instance, some researchers refer to \textit{"the robot's level of anthropomorphism"} \cite{bartneck_is_2007}, however, others argue that anthropomorphism emerges in the \textit{interaction} between the technology and the user, thus a system or an artifact does not "contain anthropomorphism" \textit{per se} \cite{persson_anthropomorphism_2000} but only gives rise to the process of anthropomorphizing in a given user and situation.
-Further, robotics is a multi-disciplinary field and researchers from very different domains might have diverse or even contradictory understandings of anthropomorphism.
-Epley \textit{et al.} \cite{epley_seeing_2007} notice that despite the fact that anthropomorphism in the perception of non-human agents is commonly observed, it is poorly understood.
-The phenomenon itself has been found to be very complex but sometimes subtle and hard to study.
-Another constraint that limits the reliability of some findings is, that most experiments on anthropomorphism are conducted in controlled lab-settings during short-term interactions.
+Literature on anthropomorphism in robotics is quite diverse and one strives hard to extract a coherent conclusion.
+One reason for this might be that robotics is a multi-disciplinary field and researchers from very different domains might integrate diverse or even contradictory understandings of the phenomenon.
+Despite the fact that there is no commonly accepted definition of anthropomorphism in robotics, and also the terminology is not clear, the terms \textit{anthropomorphic} or \textit{human-like} are often used as if their meanings were clear and agreed upon \cite{persson_anthropomorphism_2000}.
+Duffy \cite{duffy_anthropomorphism_2002} even argues that the terms might be misused.
+For instance, some researchers refer to \textit{"the robot's level of anthropomorphism"} \cite{bartneck_is_2007}, whereas others argue that the system or artifact itself does not "contain anthropomorphism" \textit{per se} but only gives rise to the process of anthropomorphizing in a given user and situation.
+Consequently, anthropomorphism emerges in the \textit{interaction} between the technology and the user \cite{persson_anthropomorphism_2000}.
+
+Paradoxically, anthropomorphism in the perception of non-human agents (such as robots) is commonly observed but at the same time poorly understood \cite{epley_seeing_2007}.
+Why?
+The phenomenon itself has been found to be very complex.
+Still, it can sometimes also be subtle and as such hard to study.
+What might also account for the rather poor (or controversial) understanding of anthropomorphism in robotics, is the limited reliability of some findings (or interpretations) from experiments investigating anthropomorphism.
+Most of these experiments are conducted in controlled lab-settings during short-term human-robot interactions.
 This experimental setting (short term and laboratory context) can be critical when studying a social phenomenon like anthropomorphism and possibly lead to over-interpretations.

### 2013-07-12 dynamics-anthropomorphism.tex
changes

@@
 
-Literature on anthropomorphism in robotics is quite diverse and one strives hard to extract a coherent conclusion.
-One reason for this might be that robotics is a multi-disciplinary field and researchers from very different domains might integrate diverse or even contradictory understandings of the phenomenon.
-Despite the fact that there is no commonly accepted definition of anthropomorphism in robotics, and also the terminology is not clear, the terms \textit{anthropomorphic} or \textit{human-like} are often used as if their meanings were clear and agreed upon \cite{persson_anthropomorphism_2000}.
-Duffy \cite{duffy_anthropomorphism_2002} even argues that the terms might be misused.
+Literature on anthropomorphism (the social phenomenon) in robotics as well as on anthropomorphic design of robots is quite diverse and one strives hard to extract a coherent conclusion.
+One reason for this might be that robotics is a multi-disciplinary field and researchers from very different domains might integrate diverse or even contradictory understandings, or simply refer to different things.
+However, despite the fact that there is no commonly accepted definition, and also the terminology is not clear, the terms \textit{anthropomorphism}, \textit{anthropomorphic} or \textit{human-like} are often used as if their meanings were clear and agreed upon \cite{persson_anthropomorphism_2000}.
+Duffy \cite{duffy_anthropomorphism_2002} argues that these terms might even be misused (in accordance with \cite{epley_when_2008}).
 For instance, some researchers refer to \textit{"the robot's level of anthropomorphism"} \cite{bartneck_is_2007}, whereas others argue that the system or artifact itself does not "contain anthropomorphism" \textit{per se} but only gives rise to the process of anthropomorphizing in a given user and situation.
-Consequently, anthropomorphism emerges in the \textit{interaction} between the technology and the user \cite{persson_anthropomorphism_2000}.
+Consequently, Persson \textit{et al.} conclude that anthropomorphism emerges in the \textit{interaction} between the technology and the user \cite{persson_anthropomorphism_2000}.
+\hl{[In this article, we accept this latter viewpoint and would like to clearly distinguish between the term \textit{anthropomorphism} as a social phenomenon and \textit{anthropomorphic} as a specific design.
+This however, is not yet a definition of what exactly both terms refer to.
+Still, we acknowledge that both terms can refer to different levels or types; which we will outline later.]}
 
-Paradoxically, anthropomorphism in the perception of non-human agents (such as robots) is commonly observed but at the same time poorly understood \cite{epley_seeing_2007}.
-Why?
-The phenomenon itself has been found to be very complex.
-Still, it can sometimes also be subtle and as such hard to study.
-What might also account for the rather poor (or controversial) understanding of anthropomorphism in robotics, is the limited reliability of some findings (or interpretations) from experiments investigating anthropomorphism.
-Most of these experiments are conducted in controlled lab-settings during short-term human-robot interactions.
-This experimental setting (short term and laboratory context) can be critical when studying a social phenomenon like anthropomorphism and possibly lead to over-interpretations.
-Some studies also seem to contrast two or more different anthropomorphic and mechanical systems that might not be appropriate for comparison under the given context and research question.
+Paradoxically, human's tendency to anthropomorphize non-human agents (such as robots) is commonly observed but at the same time it is rather poorly understood \cite{epley_seeing_2007}.
+There might be several reasons.
+First, probably because the phenomenon itself has been found to be very complex though sometimes subtle and as such hard to study.
+Second, the rather poor (or controversial) understanding, might also be due to the limited reliability of some findings (or interpretations) from experiments investigating anthropomorphism.
+Most of the experiments that investigate anthropomorphism in robotics are conducted in controlled lab-settings during short-term human-robot interactions.
+This experimental setting can be critical when studying a social phenomenon like anthropomorphism and possibly lead to over-interpretations.
+Some studies (e.g.
+exploring characteristics of the "uncanny valley") also seem to contrast two or more different anthropomorphic or mechanical systems that might not be appropriate for comparison given the complex context.
+Others might also use empirical methods inappropriate for the given research question which leads to inaccurate results.
 \hl{say more}
 
-To sum it up, while anthropomorphism in robotics is a commonly discussed and studied trait of human-robot interaction, we think it is paradoxically an overlooked research topic.
+To sum it up, while anthropomorphism in robotics is a commonly discussed and studied trait of human-robot interaction, we think it paradoxically lacks a formal ground and unified understanding.
 The understanding of anthropomorphism in robotics seems to not take into account the wide range of phenomena that it encompasses.

### 2013-08-15 dynamics-anthropomorphism.tex
Merge of changes operated in HRI version

@@
 existing literature in the HRI community, to ground the concept of
-\textit{anthropomorphism}. We then suggest to go beyond the traditional
+\textit{anthropomorphism}. Supported by extensive literature review
+and long-term field studies, we suggest to go beyond the traditional
 perception of anthropomorphism as a static feature of a system: we propose to
-understand anthropomorphism as a dynamic, non-monotonic and
-context-dependent process, which evolves over time and accounts for
-special events such as the so-called \textit{novelty effect}. To this end,
-we introduce a model of anthropomorphism that analyzes the phenomenon
-along three interaction phases. These findings are supported by a long-term
-study conducted in a real human environment.}
+understand anthropomorphism as a dynamic, non-monotonic and context-dependent
+process, which evolves over time and accounts for special events such as the
+so-called \textit{novelty effect}. To this end, we introduce a model of
+anthropomorphism that analyzes the phenomenon along three interaction phases,
+and we discuss cognitive interpretations that follow.
 
@@
 observed during a short-term interaction reflects a sustaining social effect.
-Based on an extensive literature review previously published~\cite{fink_anthropomorphism_2012} and \hl{our own work} \fxfatal{Summarize
-these findings in a specific section!}, we believe that anthropomorphic effects in HRI are not always the same but evolve over time, along with growing interaction
-and experience with the robot, similar to how relationships among people evolve over time \hl{(cite Hinde, 1988)}.
-In fact, Kanda \textit{et al.} \cite{kanda_interactive_2004} also hypothesized that people's attitude toward technological artifacts and their relationship with them would evolve over time, and they were among the first who described \textit{novelty effects} during a long-term study with an interactive robot in a school.
+Based on an extensive literature review previously
+published~\cite{fink_anthropomorphism_2012} and field
+experiements~\fixme{cites!}, we believe that anthropomorphic effects in HRI are
+not always the same but evolve over time, along with growing interaction and
+experience with the robot, similar to how relationships among people evolve
+over time \fixme{(cite Hinde, 1988)}. In fact, Kanda \textit{et al.}
+\cite{kanda_interactive_2004} also hypothesized that people's attitude toward
+technological artifacts and their relationship with them would evolve over
+time, and they were among the first who described \textit{novelty effects}
+during a long-term study with an interactive robot in a school.
 
@@
 long-term human-robot interaction. By long-term interaction, we mean direct
-(non-mediated), repeated interaction with the same robot, over at least several
-days. The nature of the interaction (goal-directed, entertainment, etc.) may
+(non-mediated), repeated interaction with the same robot, over a long period of
+time. The nature of the interaction (goal-directed, entertainment, etc.) may
 however vary.
@@
 
-\subsection{Initial Capital of Anthropomorphism}
+\subsection{Initialization Phase}
+\label{sec:initialization}
+
+\paragraph{Initial Capital of Anthropomorphism}
 \label{sec:ica}
 
-A robot has an initial potential of being anthropomorphized.
-It has been shown that some \textit{people} anthropomorphism more than others, some \textit{situations} induce anthropomorphism more than others, that \textit{children} tend to anthropomorphize more than adults, and some \textit{cultures} are notorious for their anthropomorphic religions and worldviews \cite{epley_when_2008}.
-Our model of anthropomorphism takes these determinants into account and initializes the level of anthropomorphic interactions between a human and a robot to a value that we call \textit{initial capital of anthropomorphism} (ICA on Figure~\ref{fig:dynamics}).
-The ICA describes the first (real or imagined) contact to a robot.
-Time point $t_{0}$ can be temporally before the first real physical interaction with the robot, for instance, when a person learns about the existence of vacuum-cleaning robots and imagines using one (\eg when one watches an advertisement of the robot, or observes one at a trade show).
-In this stage of "pre-interaction", people form initial expectations toward the robot and imagine how they will use / interact with it.
-Time point $t_{0}$ can be understood as duration of interaction = 0 and user experience = 0.
-We build the ICA on three main factors that \textit{a priori} determine the potential that a robot will be anthropomorphized:
+A robot has an initial potential of being anthropomorphized. It has been shown
+that some \textit{people} anthropomorphism more than others, some
+\textit{situations} induce anthropomorphism more than others, that
+\textit{children} tend to anthropomorphize more than adults, and some
+\textit{cultures} are notorious for their anthropomorphic religions and
+worldviews \cite{epley_when_2008}. Our model of anthropomorphism takes these
+determinants into account and initializes the level of anthropomorphic
+interactions between a human and a robot to a value that we call
+\textit{initial capital of anthropomorphism} (ICA on
+Figure~\ref{fig:dynamics}). The ICA describes the first (real or imagined)
+contact to a robot. In this stage of "pre-interaction", people form initial
+expectations toward the robot and imagine how they will use / interact with it.
+
+We build the ICA on three main factors that \textit{a priori} determine the
+potential that a robot will be anthropomorphized:
 
@@
 
-    \item \emph{Human-centered factor}: The \textbf{personality} and individual traits of the human user: Psychological characteristics / determinants that influence a person's tendency to anthropomorphize artifacts~\cite{epley_seeing_2007}.
-Other individual traits and demographic aspects are comprised (\textit{e.g.} age, gender, cultural background, professional background).
-
-    \item \emph{Robot-centered factor}: The robot's \textbf{design} and how it appears to the human user.
-Characteristics of the robot's form, behavior, and interaction modalities (anthropomorphic design)~\cite{fong_survey_2003}.
-
-    \item \emph{Situation-centered factor}: The real or imagined \textbf{purpose} of the robot, including the situational context in which it is used.
-The task context and role in which the robot is used / experienced (environmental context)~\cite{joosse_what_2013}.
+    \item \emph{Human-centered factor}: The \textbf{personality} and individual
+        traits of the human user: Psychological characteristics / determinants
+        that influence a person's tendency to anthropomorphize
+        artifacts~\cite{epley_seeing_2007}. Other individual traits and
+        demographic aspects are comprised (\eg age, gender, cultural
+        background, professional background).
+
+    \item \emph{Robot-centered factor}: The robot's \textbf{design} and how it
+        appears to the human user. Characteristics of the robot's form,
+        behavior, and interaction modalities (anthropomorphic
+        design)~\cite{fong_survey_2003}.
+
+    \item \emph{Situation-centered factor}: The real or imagined
+        \textbf{purpose} of the robot, including the situational context in
+        which it is used. The task context and role in which the robot is used
+        / experienced (environmental context)~\cite{joosse_what_2013}.
 
@@
 
-    By \textbf{purpose} we suggest that the real or imagined context in which a robot is used and the interaction that it brings along, impacts how far the robot will be attributed human-like characteristics.
-We	draw on findings such as presented in Joosse \textit{et al.}\fxfatal{reference?}.
-The authors showed that when the same robot (NAO) is used in a different task context (cleaning task \textit{vs.} tour guide), this influences the perception of the "personality" of the robot.
-In general, we think that a robot which is imagined to be used in a social, entertaining or playful context leads to a higher ICA than a robot which is used for a serious task (security, rescue, etc.).
-This idea receives support from \hl{XX (Kiesler / Goetz?)} work that revealed that people prefer a serious robot for serious tasks and a less serious robot for more playful tasks \hl{REF}.
-Also, we suggest that the environmental context in which people experience and interact with the robot impacts the ICA.
-When several people who might be friends interact simultaneously with the robot this might lead to an increased ICA \hl{study: people are more emotional when watching TV in company than when watching TV on their own}.
-
-\subsection{Anthropomorphism during Initialization Phase}
-\label{sec:initialization}
+By \textbf{purpose} we suggest that the real or imagined context in which a
+robot is used and the interaction that it brings along, impacts how far the
+robot will be attributed human-like characteristics. We draw on findings such
+as presented in Joosse \textit{et al.}~\cite{joosse_what_2013}. The authors showed
+that when the same robot (NAO) is used in a different task context (cleaning
+task \textit{vs.} tour guide), this influences the perception of the
+"personality" of the robot. In general, we think that a robot which is imagined
+to be used in a social, entertaining or playful context leads to a higher ICA
+than a robot which is used for a routine or focused task (security, rescue, etc.). This
+idea receives support from \fixme{XX (Kiesler / Goetz?)} work that revealed
+that people prefer a serious robot for serious tasks and a less serious robot
+for more playful tasks \fixme{REF}. Also, we suggest that the environmental
+context in which people experience and interact with the robot impacts the ICA.
+When several people who might be friends interact simultaneously with the robot
+this might lead to an increased ICA \fixme{study: people are more emotional
+when watching TV in company than when watching TV on their own}.
 
@@
 
-\subsection{Anthropomorphism during Familiarization Phase}
+TDB
+
+\subsection{Familiarization Phase}
 \label{sec:familiarization}
@@
 in the stabilization phase) (Figure~\ref{fig:dynamics}): because such behaviors
-are unexpected, a human observer interprets them as the result of a richer
-deliberative process.
+are unexpected, a human observer may interpret them as the result of a richer
+deliberative process, which in turn leads to the supposition of complex
+cognitive skills
 
@@
 
-\subsection{Anthropomorphism during Stabilization Phase}
+\subsection{Stabilization Phase}
 \label{sec:stabilization}
 
+The last phase is the \emph{stabilization} phase. The level of anthropomorphic
+effects tends to stabilize over a longer time, to reach a \emph{stabilized
+level of anthropomorphism} (SLA).
+
 If, after the familiarization phase, no anthropomorphic effects are observed
-anymore, the \emph{Stabilized Level of Anthropomorphism} is zero. This can either be interpreted as the user
-considering the robot as merely a tool, or as a consequence of no interactions
-taking place anymore with the robot (robot not used)\fxwarning{reference to the
-roomba experiment}.
+anymore, the \emph{Stabilized Level of Anthropomorphism} is zero. This can
+be interpreted as the user interacting with the robot in a routine way, without
+projecting anymore human-like traits on the robot.
 
@@
 \emph{Stabilized Level of Anthropomorphism} are generally not correlated: one
-individual may have high expectations (high ICA), and get disappointed by the
-actual abilities of the robots, down to considering it as a simple machine/tool
+individual may have high potential of anthropomorphizing (high ICA) at first
+sight of a good-looking humanoid robot, and get disappointed by the actual
+abilities of the robots, down to routine, non-anthropomorphic, interactions
 (low SLA), while another one with the same high ICA may, for instance, create
-lasting affective bonds with the robot, and keep anthropomorphizing it (high
-SLA).
+lasting affective bonds with the same robot, and keep anthropomorphizing it
+(higher SLA).
 
@@
 
-\subsection{Anthropomorphism and Cognitive Models}
+\section{Cognitive Interpretations}
 \label{sec:cognitivemodel}
+
+\paragraph{Explanations for anthropomorphism}
+
+Anthropomorphism represents just one of many examples of induction whereby
+``people reason about an unknown stimulus based on a better-known representation
+of a related stimulus"~\cite{epley_when_2008}, in this case reasoning about a
+non-human agent based on representation of the self or other humans.
+
+According to Lee \textit{et al.} \cite{lee_human_2005},
+there are two main perspectives in explaining people's tendency to
+anthropomorphize. The first one explains anthropomorphism from the design of
+the artifact (anthropomorphic form in the design). It assumes that humans
+directly respond to life-like or social cues that an object or system emits,
+without thoughtful mental processing, by simply applying stereotypes and
+heuristics to it. In fact, from early childhood on, humans are inherently
+well-trained to perceive life \cite{epley_seeing_2007}. Schmitz
+\cite{schmitz_concepts_2011} describes that within the visual scope of design,
+the outer appearance can have an important impact on the overall perception of
+an object. The basic assumption here is that if an artifact appears much like a
+human, it is likely to be treated similar to a human. If this explanation of
+anthropomorphism is correct, people may respond automatically to social cues
+emitted by a robot, and apply human-human social schemas and norms to these
+interactions.
+
+The second perspective applies a human-centered, cognitive viewpoint where
+anthropomorphism is described through people's specific mental model they
+construct about how an artifact works the way it does. According to v.
+Foerster \fixme{ref} \textit{``we anthropomorphize because it allows us to
+explain things we do not understand in terms that we do understand, and what we
+understand best is ourselves as human beings"}~\cite{hegel_understanding_2008}.
+This is consistent with the \emph{familiarity
+thesis}~\cite{hegel_understanding_2008} which claims we understand the world
+based upon a mental model of the world that we are most familiar with.
+Consequently, people tend to thoughtfully develop a mental model of agents in
+their environment and make inferences about it based on what is familiar to
+them. This point of view implicitly builds on a person's ability to attribute
+mental states to oneself and others (\ie the availability of a \emph{theory of
+mind}~\cite{Premack1978a}). A theory of  mind for other agents enables us to
+attribute intentionality to those agents
+\cite{leslie_pretense_1987,admoni_multi-category_2012}. Previous research
+examined the validity of the mental model concept with various kinds of robots
+\cite{schmitz_concepts_2011,kiesler_mental_2002}. Findings suggest that people
+tend to hold richer mental models about anthropomorphic robots in contrast to
+mechanic ones \cite{kiesler_mental_2002}.
 
@@
 \caption{The three cognitive phases of anthropomorphism: Phase I is the instinctive,
-sub-cognitive identification of living peers. {\it Empathy} [TO DISCUSS] is characteristic
+sub-cognitive identification of living peers. {\it Empathy} is characteristic
 of this stage. After longer observation or short, uncontextualized interaction
 (typically, a lab environment), the user enters Phase II: the user projects a
-mental model he/she is already familiar with onto the robot. This leads to
-expectation regarding the cognitive abilities of the robot. After longer {\it
+mental model he/she is already familiar with onto the robot. After longer {\it
 contextualized} interaction (typically, at home), the user enters Phase III of
@@
 
-Figure~\ref{fig:cognitivemodel} offers a cognitive perspective on the dynamics
-of anthropomorphism presented in the previous section.
+\paragraph{Building cognitive models over time}
+
+Building on these previous researches, Figure~\ref{fig:cognitivemodel} offers a
+cognitive perspective on the dynamics of anthropomorphism presented in the
+previous section.
 
 The first cognitive phase we identify that contribute to anthropomorphism is
-actually \emph{pre-cognitive}. Rosenthal-von der Pütten \textit{et al.} \cite{rosenthal-vonderputten_experimental_2013} investigated the neural correlates of emotional
-reactions of human towards robot or other human that showed comparable
-responses. \fxfatal{Complete that. Reference to the pleo paper}
+actually \emph{pre-cognitive}. This is supported by studies like Rosenthal-von
+der Pütten \textit{et al.}~\cite{rosenthal-vonderputten_experimental_2013} that
+investigated the neural correlates of emotional reactions of human towards
+robot.
 
@@
 that would support both the observed and imagined capabilities of the robot.
-The \emph{familiarity thesis}\fxfatal{citation!} would support the idea that
+The \emph{familiarity thesis} would support the idea that
 the human first projects onto the robot mental models of similar agents he/she
-is already familiar with. This may range from animals to human adults, through
-pets and children. We hypothesize that the nature of the projected mental
+is already familiar with (ranging from animals to human adults, through
+pets and children). We hypothesize that the nature of the projected mental
 model, as well as how deep the human engages in this projection, might be
@@
 \end{description}
+
+\subsection{Impact of the behavioral complexity of robots}
+
+TBD. Most experiments are carried with robots exhibiting relatively simple
+behaviors. In our model, the maximum level of anthropomorphism is reached with
+the novelty effect, and then decrease. Can we go \emph{over} the novelty effect
+if the robot exhibit more complex behaviors?
+
+\subsection{Segmentation of interaction phases}
+
+TBD
+
+\subsection{Behavioral cues of anthropomorphism}
+\label{sec:behavioralcues}
+
+Our model suggests to analyze anthropomorphism based on a \emph{relative and
+normalized level of anthropomorphic effects} instead of an absolute
+quantitative assessment of anthropomorphic evidences. Similarly we introduce
+two specific \emph{abstract} levels of anthropomorphism, the \emph{Initial
+Capital of Anthropomorphism} and the \emph{Stabilized Level of
+Anthropomorphism}: while we discuss the factors on which those values are
+build, we did not formally investigated the experimental cues or evidences
+that would allow to actually quantify those levels.
+
+The intricacy and interdependency of those behaviors make them difficult to
+quantify.  Their systematic identification and interpretation rely on
+psychosomatic cues that the authors did not investigate.
+
+A formal methodology for the assessment of anthropomorphic effects in HRI, as
+well as a typology of these effects is still to be formally devised.
 
@@
 
-\subsection{Behavioral cues of anthropomorphism}
-\label{sec:behavioralcues}
-
-Our model suggests to analyze anthropomorphism based on a \emph{relative and
-normalized level of anthropomorphic effects} instead of an absolute
-quantitative assessment of anthropomorphic evidences. Similarly we introduce
-two specific \emph{abstract} levels of anthropomorphism, the \emph{Initial
-Capital of Anthropomorphism} and the \emph{Stabilized Level of
-Anthropomorphism}: while we discuss the factors on which those values are
-build, we did not formally investigated the experimental cues or evidences
-that would allow to actually quantify those levels.
-
-This is explained by the intricacy and interdependency of those behaviors.
-Their correct identification and interpretation rely on psychosomatic cues that
-the authors did not investigate.
-
-A formal methodology for the assessment of anthropomorphic effects in HRI, as
-well as a typology of these effects is still to be devised.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \section{Conclusion}
-\label{sec:9}
-
-	Anthropomorphism is a social phenomenon, which seems to be natural on one side and very complex on the other side.
-It is a mechanism within oneself that makes a human observer think and treat a non-human agent as if it would have some human (social) characteristics, and ascribe to it intentions, emotions, or thoughts, for instance.
-In accordance with other researchers, we also think that the term is sometimes misused or misunderstood \cite{duffy_anthropomorphism_2002}.
-Concerning robotics, we do not think that we can speak of anthropomorphism when a person simply refers to physical parts of a robot using terms that describe a human body, such as arm, head, fingers, etc..
-We believe that this is not anthropomorphism in its true sense because the person might simply take advantage of the physically resembling shape instead of truly ascribing human (social) characteristics to the robot.
+\label{sec:conclusion}
+
+Anthropomorphism is a social phenomenon which seems to be natural on one side
+and very complex on the other side. It is a mechanism within oneself that makes
+a human observer think and treat a non-human agent as if it would have some
+human (social) characteristics, and ascribe to it intentions, emotions, or
+thoughts, for instance. Understanding the reasons and modalities of
+anthropomorphism is thus of prime importance to build a successful and lasting
+human-robot interaction.
+
+Anthropomorphism is traditionally empirically understood as the combination of
+the anthropomorphic design of a robot and the psychological determinants of the
+user. We have found out that the duration and context of the interaction is a
+third factor that plays a key role. In this article, we propose a new formal
+model of anthropomorphism that accounts for these three factors and also
+explicits the dynamics of anthromorphism. We introduce the concepts of
+\emph{initial} and \emph{stabilized levels of anthropomorphism} as compound
+factors to characterize the profile of a given anthropomorphic interaction.
+
+The article also discusses the cognitive correlates of anthropomorphism. We
+proposes to identify three cognitive phases corresponding to successive
+refinements of the mental models of the robot that the user builds during the
+interaction. We show how these phases relate to observable anthorpomorphic
+behaviours, and how they evolve over time.
+
+While not definitive, we hope that this contribution consolidates the
+scientific grounds of anthropomorphism, and provides support for further
+research on long-term acceptance of robots in human environments.
 
 \section*{Acknowledgements}
-AJung Moon, Aude Billard.\\
+
+We would like to acknowledge here the fruitful discussions with A Jung Moon and
+Aude Billard.\\
 

### 2014-01-21 dynamics-anthropomorphism.tex
Imported changes from 'Anthropomorphism and cognition' HRI workshop

@@
 
+\subsection{Why is anthropomorphism likely to change over time?}
+\label{sec:whychanges}
+
+Why do we think that anthropomorphic projections are likely to change over time and with growing experience a person has with a robot?
+The underlying process in anthropomorphism is understood as reasoning about and perceiving something non-human, and unknown or unfamiliar based on one's representation of the familiar and well-known concept of being human (or one-self).
+The basic operations underlying inductive inference are the acquisition of knowledge, the activation or elicitation of knowledge, and the application of activated knowledge at the time of the judgment \cite{epley_when_2008}.
+According to Epley \textit{et al.}, the application includes attempts to correct, adjust, or integrate less accessible information into a more automatically activated default representation.
+This process can be seen as a process of correction, and thus, it is often insufficient leaving final judgments biased in the direction of the initially activated representation.
+As a person's knowledge base changes / evolves constantly with newly acquired things, or growing experiences with a robot, etc., it is likely that the "need to anthropomorphize" a robot decreases over time.
+First, because of the evolved knowledge about it, and second because one has familiarized oneself with it.
+Consequently, the robot should become more predictable and more familiar to the human user and inferences about it can be made based on the acquired knowledge.
+/fxfatal{confusing paragraph...needs reformulation. Could also be turned into a section introduction instead of a subsection}
+
+\subsection{Model of anthropomorphism over time}
+\label{sec:modelintro}
+
+So far, the HRI community has not much investigated how anthropomorphism in
+human-robot interactions evolves over time (during the process of
+\emph{adopting} a robot, for instance): we propose to go beyond the traditional
+perception of anthropomorphism in robotics as a static feature that once
+observed during a short-term interaction reflects a sustaining social effect.
+Based on an extensive literature review previously
+published~\cite{fink_anthropomorphism_2012} and field
+experiements~\fixme{cites!}, we believe that anthropomorphic effects in HRI are
+not always the same but evolve over time, along with growing interaction and
+experience with the robot, similar to how relationships among people evolve
+over time \fixme{(cite Hinde, 1988)}. In fact, Kanda \textit{et al.}
+\cite{kanda_interactive_2004} also hypothesized that people's attitude toward
+technological artifacts and their relationship with them would evolve over
+time, and they were among the first who described \textit{novelty effects}
+during a long-term study with an interactive robot in a school.
+
+The phenomenological model of anthropomorphism we propose (Figure~\ref{fig:dynamics},~\cite{lemaignan2014dynamics}) represents
+how the level of anthropomorphic effects (\ie observable manifestations of
+anthropomorphism, as defined in section~\ref{sec:intro}) evolves over a
+long-term human-robot interaction. By long-term interaction, we mean direct
+(non-mediated), repeated interaction with the same robot, over a long period of
+time.
+
+In this model, anthropomorphism is quantified by a \emph{normalized level of
+anthropomorphic effects}: because anthropomorphic effects are not quantified on
+an absolute scale, we present them as a normalized value, that spans from a
+minimum (no anthropomorphic effects) to a maximum (corresponding to the novelty
+effect peak on Figure~\ref{fig:dynamics}). The actual maximum value of
+anthropomorphic effects depends on each unique combination of human, robot and
+several other factors we introduce below, and thus varies. The general
+\emph{shape} of the model remains however the same and depicts the evolution of
+anthropomorphism over time, \ie the general dynamics of anthropomorphism.
+
+The model takes into account the duration of the interaction, the nature of the
+interaction, as well as acquired experience and familiarization mechanisms. We
+also formally introduce a so-called \emph{novelty effect} that models the first
+phase of human-robot interaction, during which a specific increase of
+anthropomorphic interactions is observed. We focus on \emph{long-term
+interaction}, \ie direct (non-mediated), repeated interaction with the same
+robot, over an extended period of time (typically longer than a week). The nature 
+of the interaction (goal-directed, entertainment, etc.) may
+however vary.
+
 \begin{figure*}[htb]
@@
 \draw(0,5.5) node[anchor=south west] {\scriptsize \sc Initialization};
-\draw(3,5.5) node[anchor=south] {\scriptsize \sc Familiarization};
+\draw(4,5.5) node[anchor=south] {\scriptsize \sc Familiarization};
 \draw(7.5,5.5) node[anchor=south] {\scriptsize \sc Stabilization};
@@
 
-\draw (-0.05, 3) -- (0.05, 3) node[anchor=east] {\scriptsize $\text{ICA}_{\mathcal B}$};
-\draw (-0.05, 4.1) -- (0.05, 4.1) node[anchor=east] {\scriptsize $\text{ICA}_{\mathcal A}$};
-\draw (-0.05, 0.6) -- (0.05, 0.6) node[anchor=east] {\scriptsize $\text{ICA}_{\mathcal C}$};
+\draw (-0.05, 3) -- (0.05, 3) node[anchor=east] {\scriptsize ICA$_{\mathcal B}$};
+\draw (-0.05, 4.1) -- (0.05, 4.1) node[anchor=east] {\scriptsize ICA$_{\mathcal A}$};
+\draw (-0.05, 0.6) -- (0.05, 0.6) node[anchor=east] {\scriptsize ICA$_{\mathcal C}$};
 
@@
 
-\caption{Dynamics of anthropomorphism. We distinguish three main phases:
+\caption{The dynamics of anthropomorphism. We distinguish three main phases:
 \emph{initialization}, \emph{familiarization} and \emph{stabilization},
@@
 interaction starts, the level of anthropomorphism increases due to the
-\emph{novelty effect}, and then decreases to reach a \emph{stabilized level
+\emph{novelty effect}~\cite{kanda_interactive_2004}, and then decreases to reach a \emph{stabilized level
 of anthropomorphism} (SLA).  During the interaction, unpredicted behaviors
@@
 \end{figure*}
-
-\subsection{Why is anthropomorphism likely to change over time?}
-\label{sec:whychanges}
-
-Why do we think that anthropomorphic projections are likely to change over time and with growing experience a person has with a robot?
-The underlying process in anthropomorphism is understood as reasoning about and perceiving something non-human, and unknown or unfamiliar based on one's representation of the familiar and well-known concept of being human (or one-self).
-The basic operations underlying inductive inference are the acquisition of knowledge, the activation or elicitation of knowledge, and the application of activated knowledge at the time of the judgment \cite{epley_when_2008}.
-According to Epley \textit{et al.}, the application includes attempts to correct, adjust, or integrate less accessible information into a more automatically activated default representation.
-This process can be seen as a process of correction, and thus, it is often insufficient leaving final judgments biased in the direction of the initially activated representation.
-As a person's knowledge base changes / evolves constantly with newly acquired things, or growing experiences with a robot, etc., it is likely that the "need to anthropomorphize" a robot decreases over time.
-First, because of the evolved knowledge about it, and second because one has familiarized oneself with it.
-Consequently, the robot should become more predictable and more familiar to the human user and inferences about it can be made based on the acquired knowledge.
-/fxfatal{confusing paragraph...needs reformulation. Could also be turned into a section introduction instead of a subsection}
-
-\subsection{Model of anthropomorphism over time}
-\label{sec:modelintro}
-
-So far, the HRI community has not much investigated how anthropomorphism in
-human-robot interactions evolves over time (during the process of
-\emph{adopting} a robot, for instance): we propose to go beyond the traditional
-perception of anthropomorphism in robotics as a static feature that once
-observed during a short-term interaction reflects a sustaining social effect.
-Based on an extensive literature review previously
-published~\cite{fink_anthropomorphism_2012} and field
-experiements~\fixme{cites!}, we believe that anthropomorphic effects in HRI are
-not always the same but evolve over time, along with growing interaction and
-experience with the robot, similar to how relationships among people evolve
-over time \fixme{(cite Hinde, 1988)}. In fact, Kanda \textit{et al.}
-\cite{kanda_interactive_2004} also hypothesized that people's attitude toward
-technological artifacts and their relationship with them would evolve over
-time, and they were among the first who described \textit{novelty effects}
-during a long-term study with an interactive robot in a school.
-
-The model of anthropomorphism we propose (Figure~\ref{fig:dynamics}) represents
-how the level of anthropomorphic effects (\ie observable manifestations of
-anthropomorphism, as defined in section~\ref{sec:intro}) evolves over a
-long-term human-robot interaction. By long-term interaction, we mean direct
-(non-mediated), repeated interaction with the same robot, over a long period of
-time. The nature of the interaction (goal-directed, entertainment, etc.) may
-however vary.
-
-Anthropomorphism is quantified by a \emph{normalized level of anthropomorphic
-effects}: because anthropomorphic effects are not quantified on an absolute
-scale, we present them as a normalized value, that spans from a minimum (no
-anthropomorphic effects) to a maximum (corresponding to the novelty effect peak
-on Figure~\ref{fig:dynamics}). The actual maximum value of anthropomorphic
-effects depends on each unique combinations of human, robot and several other
-factors we introduce below, and thus varies. The general \emph{shape} of the
-model remains however the same and depicts the evolution of anthropomorphism over
-time, \ie the general dynamics of anthropomorphism.
-
-The model takes into account the duration of the interaction, the nature of the
-interaction, as well as acquired experience and familiarization mechanisms. We
-also formally introduce a so-called \emph{novelty effect} that
-models the first phase of human-robot interaction, during which a specific
-increase of anthropomorphic interactions is observed.
 
@@
 
-A robot has an initial potential of being anthropomorphized. It has been shown
-that some \textit{people} anthropomorphism more than others, some
+The \emph{initial capital of anthropomorphism} describes the initial potential
+for the robot to be anthropomorphized by the human user in a given situation.
+This potential depends on several factors. It has been shown, for instance, that
+some \textit{people} tend to anthropomorphize more than others, that some
 \textit{situations} induce anthropomorphism more than others, that
-\textit{children} tend to anthropomorphize more than adults, and some
+\textit{children} tend to anthropomorphize more than adults, and that some
 \textit{cultures} are notorious for their anthropomorphic religions and
-worldviews \cite{epley_when_2008}. Our model of anthropomorphism takes these
-determinants into account and initializes the level of anthropomorphic
-interactions between a human and a robot to a value that we call
-\textit{initial capital of anthropomorphism} (ICA on
-Figure~\ref{fig:dynamics}). The ICA describes the first (real or imagined)
-contact to a robot. In this stage of "pre-interaction", people form initial
-expectations toward the robot and imagine how they will use / interact with it.
-
-We build the ICA on three main factors that \textit{a priori} determine the
+worldviews~\cite{epley_when_2008}. Also the shape and design of the robot play a
+role, and the context in which the interaction takes place. Our model of
+anthropomorphism takes these determinants into account and initializes the level
+of anthropomorphic interactions between a human and a robot to a value that we
+call \emph{initial capital of anthropomorphism} (ICA). The ICA describes the
+first (real or imagined) contact to a robot. In this stage of pre-interaction,
+people form initial expectations toward the robot and imagine how they will use
+it / interact with it.
+
+We build the ICA on three main factors that \emph{a priori} determine the
 potential that a robot will be anthropomorphized:
@@
         \textbf{purpose} of the robot, including the situational context in
-        which it is used. The task context and role in which the robot is used
-        / experienced (environmental context)~\cite{joosse_what_2013}.
+        which it is used, as well as the task context and role in which the robot is
+		used / experienced (environmental context)~\cite{joosse_what_2013}.
 
@@
 
-By \textbf{purpose} we suggest that the real or imagined context in which a
-robot is used and the interaction that it brings along, impacts how far the
-robot will be attributed human-like characteristics. We draw on findings such
-as presented in Joosse \textit{et al.}~\cite{joosse_what_2013}. The authors showed
-that when the same robot (NAO) is used in a different task context (cleaning
-task \textit{vs.} tour guide), this influences the perception of the
-"personality" of the robot. In general, we think that a robot which is imagined
-to be used in a social, entertaining or playful context leads to a higher ICA
-than a robot which is used for a routine or focused task (security, rescue, etc.). This
-idea receives support from \fixme{XX (Kiesler / Goetz?)} work that revealed
-that people prefer a serious robot for serious tasks and a less serious robot
-for more playful tasks \fixme{REF}. Also, we suggest that the environmental
-context in which people experience and interact with the robot impacts the ICA.
-When several people who might be friends interact simultaneously with the robot
-this might lead to an increased ICA \fixme{study: people are more emotional
-when watching TV in company than when watching TV on their own}.
+By taking the \textbf{purpose} of a robot into account, we suggest that the real
+or imagined context in which a robot is used and the interaction that this usage
+brings along, impacts how far the robot will be attributed human-like
+characteristics. We draw on findings such as presented in Joosse
+\etal~\cite{joosse_what_2013}. The authors showed for instance that when the
+same robot (NAO) is used in a different task context (cleaning task \emph{vs.}
+tour guide), users ascribe different ``personalities'' to the robot. In general,
+a robot which is imagined to be used in a social, entertaining or playful
+context leads to a higher ICA than a robot which is used for a routine or
+focused task (security, rescue, etc.). This idea also receives support from
+Goetz \& Kiesler's work that revealed that people prefer a serious robot for
+serious tasks and a less serious robot for more playful
+tasks~\cite{goetz_cooperation_2002, goetz_matching_2003}. Also, we suggest that
+the environmental context in which people experience and interact with the robot
+impacts the ICA. For instance, several friends interacting simultaneously with
+the robot might lead to increased ICAs, due to increased human-human social
+interactions (the robot might be perceived to be part of the social interaction,
+and in turn attributed human-like qualities)~\cite{baxter2013do}.
 
@@
 
-We suggested that the ICA is built on three factors (section~\ref{sec:ica}):
-user's \emph{personality}, robot's \emph{design} and interaction \emph{purpose}
-(or \emph{interaction context}). The user's personality and the context of use
-do also influence the SLA. In particular, it appears that the user's level of
-acquaintance with technologies plays an important role in long-term tendency to
-anthropomophize (people more familiar with technology understand, and hence
-predict, better the behavior of the robot, which in turn lead them more
-frequently to ultimately consider the robot as a simple tool).
-
-The robot's design, on the other hand, plays a more subtle role: lasting
+We proposed that the ICA is built on three factors: user's \emph{personality},
+robot's \emph{design} and interaction \emph{purpose} (or \emph{interaction
+context}). The user's personality and the context of use do also influence the
+SLA. In particular, it appears that the user's level of acquaintance with
+technologies plays an important role in long-term tendency to
+anthropomophize~\cite{fink_living_2013} (people more familiar with technology
+understand, and hence predict, better the behavior of the robot, which in turn
+leads them more frequently to ultimately consider the robot as a simple tool).
+
+The robot's design, on the other hand, plays a more subtle role, and strong
+initial anthropomorphic design does not mandate high SLA: lasting
 anthropomorphic effects have been observed on non-anthropomorphic robots (like
-the iRobot Roomba or the military iRobot PackBot\footnote{Rodney Brooks has
-reported in keynotes that occasionaly soldiers would give a name to
-\emph{their} PackBot and require it to be repared instead of being replaced by
-another one in case of incident.}), and on the contrary, anthropomorphic
-designs can lead to higher expectation deceptions, resulting in the robot not
-being used anymore.
+the iRobot Roomba~\cite{fink_living_2013} or the military iRobot
+PackBot\footnote{Rodney Brooks has reported in keynotes that occasionally
+soldiers would give a name to \emph{their} PackBot and require it to be repaired
+instead of being replaced by another one in case of incident.}), and on the
+contrary, anthropomorphic designs can lead to higher expectation deceptions,
+resulting in the robot not being used anymore.
 
@@
 abilities of the robots, down to routine, non-anthropomorphic, interactions
-(low SLA), while another one with the same high ICA may, for instance, create
-lasting affective bonds with the same robot, and keep anthropomorphizing it
+(low SLA), while another user with the same high ICA may, for instance, creates
+lasting affective bonds with the same robot, and keeps anthropomorphizing it
 (higher SLA).
@@
 
-\paragraph{Explanations for anthropomorphism}
+\begin{figure}[htb]
+\centering
+%\resizebox{\linewidth}{!}{
+\begin{tikzpicture}[scale=1.2, transform shape]
+\baselineskip=8pt
+
+% horizontal axis
+\draw[->] (0,0) -- (10,0) node[anchor=north] {$t$};
+% labels
+\draw   (2,0) node[anchor=north] {Phase I}
+        (5,0) node[anchor=north] {Phase II}
+        (8,0) node[anchor=north] {Phase III};
+
+\draw[dotted] (3.5, -0.5) -- (3.5,6);
+\draw[dotted] (6.5, -0.5) -- (6.5,6);
+
+% vertical axis
+\draw[-|] (0,0) -- (0,6) node[anchor=east] {};
+% Us
+\draw[thick] (0,0) -- (1,2) -- (3,2) -- (4,4) -- (6,4) -- (7,6) -- (10,6);
+
+\draw (2.2,2) node[align=center] {\scriptsize{sub-cognitive}\\\scriptsize{anthropomorphism}}; %label
+\draw (5,3.85) node[align=center] {\scriptsize{projection of existing}\\\scriptsize{mental models}\\\scriptsize{\it (familiarity)}}; %label
+\draw (8.5,5.85) node[align=center] {\scriptsize{adapted mental model} \\ $\to$ \scriptsize{adapted interaction}\\\scriptsize{\it (antropomorphic or not)}}; %label
+
+\draw (2.2,1) node[align=left] {\tiny{\it observation (shape, motion, sound)}}; %label
+\draw (5.2,3) node[align=left] {\tiny \it observation (interactive behavior) \\ \tiny \it or short interaction}; %label
+\draw (7.8,5) node[align=left] {\tiny \it contextualized interaction}; %label
+
+\end{tikzpicture}
+%}
+\caption{The three cognitive phases of anthropomorphism: Phase I is the instinctive,
+sub-cognitive identification of living peers. {\it Empathy} is characteristic
+of this stage. After longer observation or short, non-contextualized interaction
+(typically, a lab environment), the user enters Phase II: the user projects a
+mental model he/she is already familiar with onto the robot. After longer {\it
+contextualized} interaction (typically, at home), the user enters Phase III of
+anthropomorphism: the user recomposes an accurate mental model of the robot,
+based on experience. This leads to adapted interaction modalities, that may
+still be anthropomorphic, or not.}
+\label{fig:cognitivemodel}
+\end{figure}
+
+We provide in this section a tentative interpretation of anthropomorphism in
+terms of cognitive correlates. We warmly welcome the feedback and
+comments from both the cognitive sciences and robotics communities to further
+discuss these findings.
+
+We propose three different cognitive phases (Figure~\ref{fig:cognitivemodel}),
+which do not directly match the previously presented three phases of
+anthropomorphism but are still related.
+
+\subsection{Explanations for anthropomorphism}
 
@@
 
-According to Lee \textit{et al.} \cite{lee_human_2005},
-there are two main perspectives in explaining people's tendency to
-anthropomorphize. The first one explains anthropomorphism from the design of
-the artifact (anthropomorphic form in the design). It assumes that humans
+According to Lee \etal~\cite{lee_human_2005}, there are two main perspectives in
+explaining people's tendency to anthropomorphize. First one explains
+anthropomorphism from the design of the artifact. It assumes that humans
 directly respond to life-like or social cues that an object or system emits,
@@
 anthropomorphism is described through people's specific mental model they
-construct about how an artifact works the way it does. According to v.
-Foerster \fixme{ref} \textit{``we anthropomorphize because it allows us to
-explain things we do not understand in terms that we do understand, and what we
-understand best is ourselves as human beings"}~\cite{hegel_understanding_2008}.
-This is consistent with the \emph{familiarity
-thesis}~\cite{hegel_understanding_2008} which claims we understand the world
-based upon a mental model of the world that we are most familiar with.
+construct about how an artifact works the way it does.  We then
+anthropomorphize because it allows us to explain things we do not understand in
+terms that we do understand, and what we understand best is ourselves as human
+beings. This is consistent with the \emph{familiarity
+thesis}~\cite{hegel_understanding_2008} which claims that we understand the
+world based upon a mental model of the world that we are most familiar with.
 Consequently, people tend to thoughtfully develop a mental model of agents in
 their environment and make inferences about it based on what is familiar to
-them. This point of view implicitly builds on a person's ability to attribute
-mental states to oneself and others (\ie the availability of a \emph{theory of
-mind}~\cite{Premack1978a}). A theory of  mind for other agents enables us to
-attribute intentionality to those agents
+them -- humans and human behavior, for instance.  This point of view implicitly
+builds on a person's ability to attribute mental states to oneself and others
+(\ie the availability of a \emph{theory of mind}~\cite{premack1978does} -- the
+link between a tendency to anthropomorphize and the engagement in the
+attribution of mental states to other humans has been recently demonstrated at
+the brain level in~\cite{cullen2013individual}). A theory of mind for other
+agents enables us to attribute intentionality to those agents
 \cite{leslie_pretense_1987,admoni_multi-category_2012}. Previous research
@@
 \cite{schmitz_concepts_2011,kiesler_mental_2002}. Findings suggest that people
-tend to hold richer mental models about anthropomorphic robots in contrast to
+tend to hold richer mental models of anthropomorphic robots in contrast to
 mechanic ones \cite{kiesler_mental_2002}.
 
-\begin{figure}[htb]
-\centering
-%\resizebox{\linewidth}{!}{
-\begin{tikzpicture}[scale=1.2, transform shape]
-\baselineskip=8pt
-
-% horizontal axis
-\draw[->] (0,0) -- (10,0) node[anchor=north] {$t$};
-% labels
-\draw   (2,0) node[anchor=north] {Phase I}
-        (5,0) node[anchor=north] {Phase II}
-        (8,0) node[anchor=north] {Phase III};
-
-\draw[dotted] (3.5, -0.5) -- (3.5,6);
-\draw[dotted] (6.5, -0.5) -- (6.5,6);
-
-% vertical axis
-\draw[-|] (0,0) -- (0,6) node[anchor=east] {};
-% Us
-\draw[thick] (0,0) -- (1,2) -- (3,2) -- (4,4) -- (6,4) -- (7,6) -- (10,6);
-
-\draw (2.2,2) node[align=center] {\scriptsize{sub-cognitive}\\\scriptsize{anthropomorphism}}; %label
-\draw (5,3.85) node[align=center] {\scriptsize{projection of existing}\\\scriptsize{mental models}\\\scriptsize{\it (familiarity)}}; %label
-\draw (8.5,5.85) node[align=center] {\scriptsize{adapted mental model} \\ $\to$ \scriptsize{adapted interaction}\\\scriptsize{\it (antropomorphic or not)}}; %label
-
-\draw (2.2,1) node[align=left] {\tiny{\it observation (shape, motion, sound)}}; %label
-\draw (5.2,3) node[align=left] {\tiny \it observation (interactive behavior) \\ \tiny \it or short interaction}; %label
-\draw (7.8,5) node[align=left] {\tiny \it contextualized interaction}; %label
-
-\end{tikzpicture}
-%}
-\caption{The three cognitive phases of anthropomorphism: Phase I is the instinctive,
-sub-cognitive identification of living peers. {\it Empathy} is characteristic
-of this stage. After longer observation or short, uncontextualized interaction
-(typically, a lab environment), the user enters Phase II: the user projects a
-mental model he/she is already familiar with onto the robot. After longer {\it
-contextualized} interaction (typically, at home), the user enters Phase III of
-anthropomorphism: the user recomposes an accurate mental model of the robot,
-based on experience. This leads to adapted interaction modalities, that may
-still be anthropomorphic, or not.}
-\label{fig:cognitivemodel}
-\end{figure}
-
-\paragraph{Building cognitive models over time}
-
-Building on these previous researches, Figure~\ref{fig:cognitivemodel} offers a
-cognitive perspective on the dynamics of anthropomorphism presented in the
-previous section.
-
-The first cognitive phase we identify that contribute to anthropomorphism is
-actually \emph{pre-cognitive}. This is supported by studies like Rosenthal-von
-der Pütten \textit{et al.}~\cite{rosenthal-vonderputten_experimental_2013} that
-investigated the neural correlates of emotional reactions of human towards
-robot.
-
-After a longer observation period (typically including complete action
-sequences of the robot) or short interaction (touching, short talk like
-greetings), we suggest the human enters the cognitive \emph{phase II}: in this
-phase, the human starts to build a behavioral and cognitive model of the robot
-that would support both the observed and imagined capabilities of the robot.
-The \emph{familiarity thesis} would support the idea that
-the human first projects onto the robot mental models of similar agents he/she
-is already familiar with (ranging from animals to human adults, through
-pets and children). We hypothesize that the nature of the projected mental
+\subsection{Cognitive Processes and Phases}
+
+The main underlying cognitive process in anthropomorphism is understood as
+perceiving and reasoning about something non-human and unfamiliar based on one's
+representation of the familiar and well-known concept of being
+human~\cite{epley_when_2008}. This led us to interpret the phases of
+anthropomorphic interactions as parallel cognitive phases
+(Figure~\ref{fig:cognitivemodel}).
+
+The so-called \emph{phase I} is the instinctive, pre-cognitive identification of
+living peers. That humans tend to anthropomorphize robots intuitively in this
+pre-cognitive way
+is supported by studies done by Rosenthal-von der Pütten
+\textit{et al.}~\cite{rosenthal-vonderputten_experimental_2013} who investigated
+the neural correlates of emotional reactions of humans towards a robot. {\it
+Empathy} is characteristic of this stage~\cite{rosenthalvonderPutten2013neural}.
+Anthropomorphism at this pre-cognitive stage might also be mediated by the
+human's mirror neurons system (neurons that fire both during execution of
+specific goal-oriented action and during the viewing of action directed toward
+the same goal~\cite{Rizzolatti1996, Kilner2009}) by allowing for a mapping of
+the robot's goal-directed actions into the human own motor
+repertoire~\cite{Gallese1998, Wolpert2003, cullen2013individual}.
+
+After a longer observation period (typically including complete action sequences
+of the robot) or short interaction (touching, short talk like greetings), we
+suggest the human enters the cognitive \emph{phase II}: in this phase, the human
+starts building a behavioral and cognitive model of the robot that would support
+both the observed and imagined capabilities of the robot.  The \emph{familiarity
+thesis}~\cite{hegel_understanding_2008} supports the idea that the human
+first projects onto the robot mental models of similar agents he/she is already
+familiar with (ranging from animals to human adults, to pets and children). We 
+hypothesize that the nature of the projected mental
 model, as well as how deep the human engages in this projection, might be
-driven by the same parameters as we presented for the \emph{initial capital of
+driven by the same parameters as we mentioned for the \emph{initial capital of
 anthropomorphism} (section~\ref{sec:ica}).
 
-We identify a further transition to the cognitive \emph{phase III} after a
-\emph{contextualized} interaction. A \emph{contextualized} interaction is
-\emph{explicitly purposeful} (the purpose of the interaction, be it purely
-entertainment, is explicit and conscious for the human), and takes place in an
-environment that fosters a stronger cognitive (and possibly affective)
-commitment from the human in the interaction (typically, at home). During this
-interaction, the human iteratively restate and reshape its behavioral and
-mental model of the robot (\emph{How does the robot react to such and such
-situation/input? What does the robot know about me? About itself? About our
-environment? What can the robot learn?}, etc.).
-
-This mental process heavily depends on the human understanding of the robot's
+The cognitive \emph{phase III} occurs after a \emph{contextualized} interaction.
+A \emph{contextualized} interaction is \emph{explicitly purposeful} (the purpose
+of the interaction, be it purely entertainment, is explicit and conscious to the
+human), and takes place in an environment that fosters a stronger cognitive (and
+possibly affective/social) commitment from the human in the interaction
+(typically, at home). During this interaction, the human iteratively restates
+and reshapes his/her behavioral and mental model of the robot (\emph{How does
+the robot react to such and such situation/input?  What does the robot know
+about me? About itself? About our environment? What can the robot learn?}, etc.).
+
+This mental process depends on the human understanding of the robot's
 inner working, as well as his/her own tendency to anthropomorphize (the
-\emph{personality} in ICA factor), but at this stage, the \emph{perception} of
-the robot (its shape for instance) and its intended \emph{purpose} play a less
-important role. It is mostly a human-centric process.
-
-The result of this third phase is an iteratively adapted cognitive model of the
-robot.
-
-\paragraph{Relation to the model of anthropomorphism} It must be noted that the
-three cognitive phases we introduce here do not match the
-\emph{initialization}, \emph{familiarization} and \emph{stabilization} phases
-introduced at~\ref{sec:phases}: in particular, cognitive phases I and II are
-both included in the \emph{initialization} phase of the anthropomorphism model.
-
-Sub-cognitive anthropomorphism typically \emph{initiates} the novelty effect by
-rapidly engaging the human in the interaction through an initial projected
-\emph{agency}, whereas cognitive phase II (projection of familiar mental
-models) supports the novelty effect by inducing beliefs that the robot is set
-up with possibly complex cognitive abilities.
-
-The cognitive phase II also overlaps with the \emph{familiarization} phase: as
-(s)he get used to the robot, we hypothesize the human restates and adapts its
+\emph{personality} in ICA factor), but at this
+stage, the \emph{perception} of the robot (its shape for instance) and its
+intended \emph{purpose} play a less important role. It is mostly a human-centric
+process.  The result of this third phase would be an iteratively adapted
+cognitive model of the robot.
+
+\subsection{Relation to the model of anthropomorphism}
+
+These cognitive phases overlap but do not exactly match the
+\emph{Initialization}, \emph{Familiarization} and \emph{Stabilization} phases
+introduced in our model of the dynamics of anthropomorphism. In particular,
+cognitive phases I and II are both included in the \emph{initialization} phase
+of the anthropomorphism model. Sub-cognitive anthropomorphism typically
+\emph{initiates} the novelty effect by rapidly engaging the human in the
+interaction through an initial projected agency, whereas cognitive phase II
+(projection of familiar mental models) supports the novelty effect by inducing
+beliefs that the robot is set up with possibly complex cognitive abilities.
+
+The cognitive phase III also overlaps with the \emph{familiarization} phase: as
+the human gets used to the robot, we hypothesize one restates and adapts its
 cognitive model of the robot by iteratively reshaping pre-existent, familiar
@@
 
-A \emph{stable level of anthropomorphism} is reached when the adaptation
-process depicted in cognitive phase III reached a stable state, \ie the human
-experience with the robot is correctly supported by the cognitive model the
-human has built.
+A \emph{stable level of anthropomorphism} is reached when the adaptation process
+depicted in cognitive phase III reached a stable state, \ie the user's experience
+with the robot is correctly supported by the cognitive model he/she has
+built.
 
@@
 
+\section{Discussion}
+
+This interpretation of anthropomorphism in terms of cognitive correlates
+opens questions that we hope could be fruitfully discussed during the workshop.
+By adopting both a cognitive and a dynamic perspective on the anthropomorphic
+bonds that establish between a robot and a human during an interaction, 
+some observations can be raised.
+
+For instance, we propose that the human \emph{adapts} iteratively to the robot
+by restating its cognitive model of the robot. Could our two models be
+conversely relied on to have the robot itself iteratively adapting its
+behaviour? In particular, we hypothesize that the so-called novelty effect
+represents a peak in anthropomorphic manifestations, followed by mostly
+deception-driven refinements of the cognitive behavioural model of the robot.
+Could we imagine that the robot pro-actively \emph{verbalises} its own limits,
+in a timely manner (likely before the end of the novely effect). And how would this
+affect the cognitive models built by the human?
+
+One related question we plan to elaborate on is the effects of \emph{mutual
+explicitation of the mental model of the other agent}: a human and a robot
+interact on a given task, and after a while, we interrupt the task and ask each
+of the agents to explicit the mental model it has built of its partner
+(emotional state, beliefs, intentions, etc.). Depending on the cognitive phase
+the two agents are in, we may expect varying accuracy levels in the produced
+mental models.
+
+Another question raised by these models relates to their transposition to
+human-human interaction: while concepts like \emph{novelty effect} are not
+directly meaningful when analyzing human-human interaction, insights from
+cognitive sciences (and in particular social psychology) regarding how we, as
+humans, cope with unexpected behaviours from peers, or on the dynamics of
+mental model refinements, could bring interesting perspectives with possible
+applications to better manage long-term human-robot interactions.
+
 \section{Conclusion}
@@
 
-Anthropomorphism is traditionally empirically understood as the combination of
+While anthropomorphism is traditionally empirically understood as the interactions between
 the anthropomorphic design of a robot and the psychological determinants of the
-user. We have found out that the duration and context of the interaction is a
-third factor that plays a key role. In this article, we propose a new formal
+user, it appears that the duration and context of the
+interaction are also key factors, and that anthropomorphism needs to be
+understood as a dynamic phenomenon. In this article, we propose a new formal
 model of anthropomorphism that accounts for these three factors and also
@@
 refinements of the mental models of the robot that the user builds during the
-interaction. We show how these phases relate to observable anthorpomorphic
-behaviours, and how they evolve over time.
-
-While not definitive, we hope that this contribution consolidates the
-scientific grounds of anthropomorphism, and provides support for further
-research on long-term acceptance of robots in human environments.
+interaction. We show how these phases relate to observable anthropomorphic
+effects, and how they evolve over time.
+
+While subject to discussion and further extensions, we hope that this
+contribution consolidates the scientific grounds of anthropomorphism, and
+provides support for a better understanding of long-term acceptance of robots
+in human environments.
 

### 2014-01-21 dynamics-anthropomorphism.tex
Wrapped lines to 80 chars

@@
 and we discuss cognitive interpretations that follow.
+}
 
@@
 
-The essence of anthropomorphism is the perception of human-like characteristics in either real or imagined non-human agents.
-According to Epley \textit{et al.} \cite{epley_when_2008}, these human-like characteristics may include physical appearance, emotional states perceived to be uniquely human, or inner mental states and motivations.
-Real or imagined non-human agents can be "anything that acts -- or is believed to act -- with apparent independence, including non-human animals, natural forces, religious agents, technological gadgets, or mechanical devices".
-Such anthropomorphic representations are important determinants of how a person perceives and in turn behaves towards these agents, or how a person may behave in light of these agents \cite{epley_when_2008}.
+The essence of anthropomorphism is the perception of human-like characteristics
+in either real or imagined non-human agents. According to Epley \textit{et al.}
+\cite{epley_when_2008}, these human-like characteristics may include physical
+appearance, emotional states perceived to be uniquely human, or inner mental
+states and motivations. Real or imagined non-human agents can be "anything that
+acts -- or is believed to act -- with apparent independence, including non-human
+animals, natural forces, religious agents, technological gadgets, or mechanical
+devices". Such anthropomorphic representations are important determinants of how
+a person perceives and in turn behaves towards these agents, or how a person may
+behave in light of these agents \cite{epley_when_2008}.
 
@@
 
-Phenomenons related to anthropomorphism -- along with questions such as "how much human do we perceive in the non-human" or "how human-like do we treat non-human artifacts" (and why?) -- have received remarkable attention in the domains of Human-Computer Interaction (HCI) and Human-Robot Interaction (HRI): the study of humans interacting with an artificial system / machine.
-Following the \textit{Media Equation}, it has been described that people mindlessly react socially to computers \cite{reeves_media_1996} and may even attribute human (social) characteristics to their artificial counterpart.
-The phenomenon has also been observed with virtual characters \hl{cite [50, 100] in rosenthal-von der P{\"u}tten (2013)}, and more recent studies investigated how far people ascribe personality or intentions to artificial emobdied agents or whether they show empathetic behavior toward robots \cite{rosenthal-vonderputten_experimental_2013}.
-The common base for this research is the assumption that humans perceive or react to a non-human agent or artifact as somewhat similar to a human.
-
-In this article we will use the term \emph{anthropomorphic effect} to denote observable correlates of anthropomorphism. With these we include, amongst others,
-verbal utterances (such as direct speech or the use of pronouns "he/she"), (social) gestures (such as a hug, waving, deictic gestures) or \hl{anticipation of certain actions of an agent [what??]}.
+Phenomenons related to anthropomorphism -- along with questions such as "how
+much human do we perceive in the non-human" or "how human-like do we treat
+non-human artifacts" (and why?) -- have received remarkable attention in the
+domains of Human-Computer Interaction (HCI) and Human-Robot Interaction (HRI):
+the study of humans interacting with an artificial system / machine. Following
+the \textit{Media Equation}, it has been described that people mindlessly react
+socially to computers \cite{reeves_media_1996} and may even attribute human
+(social) characteristics to their artificial counterpart. The phenomenon has
+also been observed with virtual characters \hl{cite [50, 100] in rosenthal-von
+der P{\"u}tten (2013)}, and more recent studies investigated how far people
+ascribe personality or intentions to artificial emobdied agents or whether they
+show empathetic behavior toward robots
+\cite{rosenthal-vonderputten_experimental_2013}. The common base for this
+research is the assumption that humans perceive or react to a non-human agent or
+artifact as somewhat similar to a human.
+
+In this article we will use the term \emph{anthropomorphic effect} to denote
+observable correlates of anthropomorphism. With these we include, amongst
+others, verbal utterances (such as direct speech or the use of pronouns
+"he/she"), (social) gestures (such as a hug, waving, deictic gestures) or
+\hl{anticipation of certain actions of an agent [what??]}.
 
@@
 
-However, not everything colloquially labeled as \emph{anthropomorphism} really is anthropomorphism.
-Different, even partially conflicting, understandings of anthropomorphism exist across and within disciplines \cite{duffy_anthropomorphism_2002}.
-Epley \textit{et al.} \cite{epley_when_2008} try to narrow down and clarify the understanding of anthropomorphism in psychology by explaining what it is \textit{not}.
-The authors list four things that anthropomorphism does not include: First, anthropomorphism does not include behavioral descriptions of observable actions.
-Anthropomorphism requires going beyond what is directly observable.
-Second, anthropomorphism does not merely entail animism, as animate life is not a uniquely human-like characteristic.
-Third, anthropomorphism does not include any requirement of reasoned or reflective endorsement of an inference (\hl{the strength of anthropomorphic inferences can vary} \footnote{for further explanation the reader may refer to the original work \cite{epley_when_2008}.}).	Finally, anthropomorphism is not necessarily inaccurate.
-A psychological theory should take this (in)accuracy in anthropomorphism into account and predict variability in the tendency to perceive human-like traits in non-human agents.
-In conclusion, it has been noted that anthropomorphism is a very complex phenomenon - in itself, its understanding, and when studying it.
-A common formal ground is missing; however, it is important to be clear about what exactly we mean when using the term anthropomorphism.
+However, not everything colloquially labeled as \emph{anthropomorphism} really
+is anthropomorphism. Different, even partially conflicting, understandings of
+anthropomorphism exist across and within disciplines
+\cite{duffy_anthropomorphism_2002}. Epley \textit{et al.} \cite{epley_when_2008}
+try to narrow down and clarify the understanding of anthropomorphism in
+psychology by explaining what it is \textit{not}. The authors list four things
+that anthropomorphism does not include: First, anthropomorphism does not include
+behavioral descriptions of observable actions. Anthropomorphism requires going
+beyond what is directly observable. Second, anthropomorphism does not merely
+entail animism, as animate life is not a uniquely human-like characteristic.
+Third, anthropomorphism does not include any requirement of reasoned or
+reflective endorsement of an inference (\hl{the strength of anthropomorphic
+inferences can vary} \footnote{for further explanation the reader may refer to
+the original work \cite{epley_when_2008}.}).	Finally, anthropomorphism is not
+necessarily inaccurate. A psychological theory should take this (in)accuracy in
+anthropomorphism into account and predict variability in the tendency to
+perceive human-like traits in non-human agents.  In conclusion, it has been
+noted that anthropomorphism is a very complex phenomenon - in itself, its
+understanding, and when studying it. A common formal ground is missing; however,
+it is important to be clear about what exactly we mean when using the term
+anthropomorphism.
 
@@
 
-Anthropomorphism represents just one of many examples of induction whereby "people reason about an unknown stimulus based on a better-known representation of a related stimulus" \cite{epley_when_2008}, in this case reasoning about a non-human agent based on representation of the self or other humans.
-This supports the usual role we assign to anthropomorphism in robotics: the anthropomorphic design of a robot encourages people to reason about this unfamiliar system \emph{as if} it was a human.
-To increase this tendency, robots are designed with anthropomorphic forms (human-like or lifelike forms, in the broader sense), or are able to display and use human-social cues when interacting with humans.\\
-
-Literature on anthropomorphism (the social phenomenon) in robotics as well as on anthropomorphic design of robots is quite diverse and one strives hard to extract a coherent conclusion.
-One reason for this might be that robotics is a multi-disciplinary field and researchers from very different domains might integrate diverse or even contradictory understandings, or simply refer to different things.
-However, despite the fact that there is no commonly accepted definition, and also the terminology is not clear, the terms \textit{anthropomorphism}, \textit{anthropomorphic} or \textit{human-like} are often used as if their meanings were clear and agreed upon \cite{persson_anthropomorphism_2000}.
-Duffy \cite{duffy_anthropomorphism_2002} argues that these terms might even be misused (in accordance with \cite{epley_when_2008}).
-For instance, some researchers refer to \textit{"the robot's level of anthropomorphism"} \cite{bartneck_is_2007}, whereas others argue that the system or artifact itself does not "contain anthropomorphism" \textit{per se} but only gives rise to the process of anthropomorphizing in a given user and situation.
-Consequently, Persson \textit{et al.} conclude that anthropomorphism emerges in the \textit{interaction} between the technology and the user \cite{persson_anthropomorphism_2000}.
-\hl{[In this article, we accept this latter viewpoint and would like to clearly distinguish between the term \textit{anthropomorphism} as a social phenomenon and \textit{anthropomorphic} as a specific design.
-This however, is not yet a definition of what exactly both terms refer to.
-Still, we acknowledge that both terms can refer to different levels or types; which we will outline later.]}
-
-Paradoxically, human's tendency to anthropomorphize non-human agents (such as robots) is commonly observed but at the same time it is rather poorly understood \cite{epley_seeing_2007}.
-There might be several reasons.
-First, probably because the phenomenon itself has been found to be very complex though sometimes subtle and as such hard to study.
-Second, the rather poor (or controversial) understanding, might also be due to the limited reliability of some findings (or interpretations) from experiments investigating anthropomorphism.
-Most of the experiments that investigate anthropomorphism in robotics are conducted in controlled lab-settings during short-term human-robot interactions.
-This experimental setting can be critical when studying a social phenomenon like anthropomorphism and possibly lead to over-interpretations.
-Some studies (e.g.
-exploring characteristics of the "uncanny valley") also seem to contrast two or more different anthropomorphic or mechanical systems that might not be appropriate for comparison given the complex context.
-Others might also use empirical methods inappropriate for the given research question which leads to inaccurate results.
-\hl{say more}
-
-To sum it up, while anthropomorphism in robotics is a commonly discussed and studied trait of human-robot interaction, we think it paradoxically lacks a formal ground and unified understanding.
-The understanding of anthropomorphism in robotics seems to not take into account the wide range of phenomena that it encompasses.
-The traditional understanding of anthropomorphism in robotics to date considers two main factors that account for the social phenomenon: the characteristics of \textbf{1) the robot's design} (degree of human-likeness) and the psychological determinants in \textbf{2) the human user} (see \cite{epley_seeing_2007}).
-It has been shown that both these factors can facilitate or hinder anthropomorphism.
-We propose to go beyond this traditional perception of anthropomorphism as a static feature of HRI: Based on Persson \textit{et al.}'s~\cite{persson_anthropomorphism_2000} argumentation that anthropomorphism is a multi-layered phenomenon which arises in different levels, we suggest to understand anthropomorphism as a \emph{dynamic}, \emph{context-dependent} process.
-To this end, we apply Persson \textit{et al.}'s six levels on anthropomorphism to HRI and introduce three \emph{interaction phases}.
-These interaction phases of anthropomorphism reflect also the results of a long-term study that we conducted in a real human environment and provide an account of the so-called \textit{novelty effect}.
-We also draw attention to two new determinants of anthropomorphism, namely, the context of use and the fact of getting used to a system over time.
-We propose to add these two aspects as a third factor, the characteristics of \textbf{3) the interaction} (time and space), to the previous two factors of anthropomorphism (robot and user).
+Anthropomorphism represents just one of many examples of induction whereby
+"people reason about an unknown stimulus based on a better-known representation
+of a related stimulus" \cite{epley_when_2008}, in this case reasoning about a
+non-human agent based on representation of the self or other humans. This
+supports the usual role we assign to anthropomorphism in robotics: the
+anthropomorphic design of a robot encourages people to reason about this
+unfamiliar system \emph{as if} it was a human. To increase this tendency, robots
+are designed with anthropomorphic forms (human-like or lifelike forms, in the
+broader sense), or are able to display and use human-social cues when
+interacting with humans.\\
+
+Literature on anthropomorphism (the social phenomenon) in robotics as well as on
+anthropomorphic design of robots is quite diverse and one strives hard to
+extract a coherent conclusion. One reason for this might be that robotics is a
+multi-disciplinary field and researchers from very different domains might
+integrate diverse or even contradictory understandings, or simply refer to
+different things. However, despite the fact that there is no commonly accepted
+definition, and also the terminology is not clear, the terms
+\textit{anthropomorphism}, \textit{anthropomorphic} or \textit{human-like} are
+often used as if their meanings were clear and agreed upon
+\cite{persson_anthropomorphism_2000}. Duffy \cite{duffy_anthropomorphism_2002}
+argues that these terms might even be misused (in accordance with
+\cite{epley_when_2008}). For instance, some researchers refer to \textit{"the
+robot's level of anthropomorphism"} \cite{bartneck_is_2007}, whereas others
+argue that the system or artifact itself does not "contain anthropomorphism"
+\textit{per se} but only gives rise to the process of anthropomorphizing in a
+given user and situation. Consequently, Persson \textit{et al.} conclude that
+anthropomorphism emerges in the \textit{interaction} between the technology and
+the user \cite{persson_anthropomorphism_2000}.  \hl{[In this article, we accept
+this latter viewpoint and would like to clearly distinguish between the term
+\textit{anthropomorphism} as a social phenomenon and \textit{anthropomorphic} as
+a specific design. This however, is not yet a definition of what exactly both
+terms refer to. Still, we acknowledge that both terms can refer to different
+levels or types; which we will outline later.]}
+
+Paradoxically, human's tendency to anthropomorphize non-human agents (such as
+robots) is commonly observed but at the same time it is rather poorly understood
+\cite{epley_seeing_2007}. There might be several reasons. First, probably
+because the phenomenon itself has been found to be very complex though sometimes
+subtle and as such hard to study. Second, the rather poor (or controversial)
+understanding, might also be due to the limited reliability of some findings (or
+interpretations) from experiments investigating anthropomorphism. Most of the
+experiments that investigate anthropomorphism in robotics are conducted in
+controlled lab-settings during short-term human-robot interactions. This
+experimental setting can be critical when studying a social phenomenon like
+anthropomorphism and possibly lead to over-interpretations. Some studies (e.g.
+exploring characteristics of the "uncanny valley") also seem to contrast two or
+more different anthropomorphic or mechanical systems that might not be
+appropriate for comparison given the complex context. Others might also use
+empirical methods inappropriate for the given research question which leads to
+inaccurate results. \hl{say more}
+
+To sum it up, while anthropomorphism in robotics is a commonly discussed and
+studied trait of human-robot interaction, we think it paradoxically lacks a
+formal ground and unified understanding. The understanding of anthropomorphism
+in robotics seems to not take into account the wide range of phenomena that it
+encompasses. The traditional understanding of anthropomorphism in robotics to
+date considers two main factors that account for the social phenomenon: the
+characteristics of \textbf{1) the robot's design} (degree of human-likeness) and
+the psychological determinants in \textbf{2) the human user} (see
+\cite{epley_seeing_2007}). It has been shown that both these factors can
+facilitate or hinder anthropomorphism. We propose to go beyond this traditional
+perception of anthropomorphism as a static feature of HRI: Based on Persson
+\textit{et al.}'s~\cite{persson_anthropomorphism_2000} argumentation that
+anthropomorphism is a multi-layered phenomenon which arises in different levels,
+we suggest to understand anthropomorphism as a \emph{dynamic},
+\emph{context-dependent} process. To this end, we apply Persson \textit{et
+al.}'s six levels on anthropomorphism to HRI and introduce three
+\emph{interaction phases}. These interaction phases of anthropomorphism reflect
+also the results of a long-term study that we conducted in a real human
+environment and provide an account of the so-called \textit{novelty effect}. We
+also draw attention to two new determinants of anthropomorphism, namely, the
+context of use and the fact of getting used to a system over time. We propose to
+add these two aspects as a third factor, the characteristics of \textbf{3) the
+interaction} (time and space), to the previous two factors of anthropomorphism
+(robot and user).
 
 %% -> Commented out the overview as it does not match what we actually present... maybe we need a new one?
-% We would further like to review and discuss research on anthropomorphism in robotics and human-like design of robots.
-We first provide a comprehensive understanding of the phenomenon drawing on theories from developmental psychology and cognitive sciences.
-We then present the trends of different kinds of anthropomorphic forms in robots and discuss their role in social robotics.
-The article integrates related work from human-robot interaction studies, reporting on findings from experiments with human subjects interacting with and evaluating various types of systems.
-We try to give a coherent view on the topic, outline similarities and antithetic findings, and contribute to a better understanding of anthropomorphism in robotics, and the acceptance of human-like characteristics in robots.
-We also aim to constructively discuss anthropomorphic design of personal and socially interactive robots.
+% We would further like to review and discuss research on anthropomorphism in
+% robotics and human-like design of robots. We first provide a comprehensive
+% understanding of the phenomenon drawing on theories from developmental
+% psychology and cognitive sciences. We then present the trends of different
+% kinds of anthropomorphic forms in robots and discuss their role in social
+% robotics. The article integrates related work from human-robot interaction
+% studies, reporting on findings from experiments with human subjects
+% interacting with and evaluating various types of systems. We try to give a
+% coherent view on the topic, outline similarities and antithetic findings, and
+% contribute to a better understanding of anthropomorphism in robotics, and the
+% acceptance of human-like characteristics in robots. We also aim to
+% constructively discuss anthropomorphic design of personal and socially
+% interactive robots.
 
@@
 
-The term \textbf{anthropomorphism} is used in different senses throughout natural sciences, psychology, Human-Computer Interaction, and Human-Robot Interaction \cite{duffy_anthropomorphism_2003}.
-Originally, anthropomorphism comes from the Greek \textit{`anthropos'} for `man' (or `human') and \textit{`morphe'} for `form/structure' (or `shape').
-It can be understood as people's tendency to think of objects as if they had human characteristics, and consequently, attribute / ascribe specific human characteristics to these non-human entities and artifacts (including animals, and robots) \cite{duffy_anthropomorphism_2003,schmitz_concepts_2011}.
-Apart from anthropomorphism there is also \textbf{animism}, the \textit{"attribution of life to the nonliving"} \hl{in Schmitz 2011, cite Piaget original text!}.
-Often synonymously used to animism is \textbf{zoomorphism}, which describes the case when non-lifelike objects are associated with animalistic attributes, excluding human-specific traits.
-Both anthropomorphism and zoomorphism can be embraced by the concept of \textbf{life-likeness}.
-\footnote{The inverse process would be called dehumanization \cite{haslam_dehumanization:_2006}, or mechanomorphism \cite{caporael_anthropomorphism_1986}.}
-
-Commonly, anthropomorphism can also be understood as \textbf{humanization} or \textbf{personification} of anything other than a human being.
-The phenomenon of personifying something has ancient roots, \textit{e.g.} in mythology but also in storytelling.
-In prehistoric artworks and illustrations, zoomorphic (animal-shaped) or anthropomorphic shapes were already used to represent natural forces or great spirits, for instance.
-A more recent example is Milo Winter's illustration from 1919, \textit{"The North Wind and the Sun"} (Figure \ref{fig:1}), in which both north wind and sun are given a human face (anthropomorphized).
-Similarly, when parents explain their children about nature, they tend to use anthropomorphisms, \textit{e.g.} saying the skies would cry when it rains.
-More generally, an explanation for why people anthropomorphize is that by doing so, the subject is made \emph{graspable}, \emph{understandable}, \emph{predictable}, and one feel \emph{more empathetic} toward it\fxnote{important part.
-Emphasize this 4 facets, eg by saying we build on top of them}.
-For instance, people commonly anthropomorphize their pets, ascribing mental states, intentions or feelings to them \cite{eddy_attribution_1993}.
-Interestingly, pet-ownership seems to have a significant impact on human-robot interaction: several studies suggest that pet-owners are more likely to anthropomorphize technologies and robots than non pet-owners \hl{references!}.
+The term \textbf{anthropomorphism} is used in different senses throughout
+natural sciences, psychology, Human-Computer Interaction, and Human-Robot
+Interaction \cite{duffy_anthropomorphism_2003}. Originally, anthropomorphism
+comes from the Greek \textit{`anthropos'} for `man' (or `human') and
+\textit{`morphe'} for `form/structure' (or `shape'). It can be understood as
+people's tendency to think of objects as if they had human characteristics, and
+consequently, attribute / ascribe specific human characteristics to these
+non-human entities and artifacts (including animals, and robots)
+\cite{duffy_anthropomorphism_2003,schmitz_concepts_2011}. Apart from
+anthropomorphism there is also \textbf{animism}, the \textit{"attribution of
+life to the nonliving"} \hl{in Schmitz 2011, cite Piaget original text!}. Often
+synonymously used to animism is \textbf{zoomorphism}, which describes the case
+when non-lifelike objects are associated with animalistic attributes, excluding
+human-specific traits. Both anthropomorphism and zoomorphism can be embraced by
+the concept of \textbf{life-likeness}. \footnote{The inverse process would be
+called dehumanization \cite{haslam_dehumanization:_2006}, or mechanomorphism
+\cite{caporael_anthropomorphism_1986}.}
+
+Commonly, anthropomorphism can also be understood as \textbf{humanization} or
+\textbf{personification} of anything other than a human being. The phenomenon of
+personifying something has ancient roots, \textit{e.g.} in mythology but also in
+storytelling. In prehistoric artworks and illustrations, zoomorphic
+(animal-shaped) or anthropomorphic shapes were already used to represent natural
+forces or great spirits, for instance. A more recent example is Milo Winter's
+illustration from 1919, \textit{"The North Wind and the Sun"} (Figure
+\ref{fig:1}), in which both north wind and sun are given a human face
+(anthropomorphized). Similarly, when parents explain their children about
+nature, they tend to use anthropomorphisms, \textit{e.g.} saying the skies would
+cry when it rains. More generally, an explanation for why people
+anthropomorphize is that by doing so, the subject is made \emph{graspable},
+\emph{understandable}, \emph{predictable}, and one feel \emph{more empathetic}
+toward it\fxnote{important part. Emphasize this 4 facets, eg by saying we build
+on top of them}. For instance, people commonly anthropomorphize their pets,
+ascribing mental states, intentions or feelings to them
+\cite{eddy_attribution_1993}. Interestingly, pet-ownership seems to have a
+significant impact on human-robot interaction: several studies suggest that
+pet-owners are more likely to anthropomorphize technologies and robots than non
+pet-owners \hl{references!}.
 
@@
 \fxfatal{inconsistency: we already give explanations for anthropomorphism in previous paragraph...}
-	According to Lee \textit{et al.} \cite{lee_human_2005}, there are two main perspectives in explaining people's tendency to anthropomorphize.
-The first one explains anthropomorphism from the design of the artifact (anthropomorphic form in the design).
-It assumes that humans directly respond to life-like or social cues that an object or system emits, without thoughtful mental processing, by simply applying stereotypes and heuristics to it.
-In fact, from early childhood on, humans are inherently well-trained to perceive life \cite{epley_seeing_2007}.
-Schmitz \cite{schmitz_concepts_2011} describes that within the visual scope of design, the outer appearance can have an important impact on the overall perception of an object.
-The basic assumption here is that if an artifact appears much like a human, it is likely to be treated similar to a human.
-If this explanation of anthropomorphism is correct, people may respond automatically to social cues emitted by a robot, and apply human-human social schemas and norms to these interactions.
-
-    The second perspective applies a human-centered, cognitive viewpoint where anthropomorphism is described through people's specific mental model they construct about how an artifact works the way it does.
-According to v.
-Foerster \hl{ref} \textit{"we anthropomorphize because it allows us to explain things we do not understand in terms that we do understand, and what we understand best is ourselves as human beings"} \cite{hegel_understanding_2008}.
-This is consistent with the \hl{familiarity thesis (18)} \cite{hegel_understanding_2008} which claims we understand the world based upon a mental model of the world that we are most familiar with.
-Consequently, people tend to thoughtfully develop a mental model of agents in their environment and make inferences about it based on what is familiar to them.
-This point of view implicitly builds on a person's ability to attribute mental states to oneself and others, which is called \textit{Theory of Mind}~\cite{Premack1978}.
-A theory of  mind for other agents enables us to attribute intentionality to those agents \cite{leslie_pretense_1987,admoni_multi-category_2012}.
-If a system behaves much like a human being (\eg emits a human voice), people's mental model of the system's behavior may approach their mental model of humans, though the model may differ in some important aspects \hl{ref?
-Schmitz?}.
-In turn, people's estimation of a robot's knowledge model and its capabilities affects the way they relate to it.
-Previous research examined the validity of the mental model concept with various kinds of robots \cite{schmitz_concepts_2011,kiesler_mental_2002}.
-Findings suggest that people tend to hold richer mental models about anthropomorphic robots in contrast to mechanic ones \cite{kiesler_mental_2002}.
-Later in this article, we may however come to question this result for longer human-robot interactions, after one get's acquantained with the robot's behaviour.
+According to Lee \textit{et al.} \cite{lee_human_2005}, there are two main
+perspectives in explaining people's tendency to anthropomorphize. The first
+one explains anthropomorphism from the design of the artifact
+(anthropomorphic form in the design). It assumes that humans directly
+respond to life-like or social cues that an object or system emits, without
+thoughtful mental processing, by simply applying stereotypes and heuristics
+to it. In fact, from early childhood on, humans are inherently well-trained
+to perceive life \cite{epley_seeing_2007}. Schmitz
+\cite{schmitz_concepts_2011} describes that within the visual scope of
+design, the outer appearance can have an important impact on the overall
+perception of an object. The basic assumption here is that if an artifact
+appears much like a human, it is likely to be treated similar to a human. If
+this explanation of anthropomorphism is correct, people may respond
+automatically to social cues emitted by a robot, and apply human-human
+social schemas and norms to these interactions.
+
+The second perspective applies a human-centered, cognitive viewpoint where
+anthropomorphism is described through people's specific mental model they
+construct about how an artifact works the way it does. According to v.
+Foerster \hl{ref} \textit{"we anthropomorphize because it allows us to
+explain things we do not understand in terms that we do understand, and what
+we understand best is ourselves as human beings"}
+\cite{hegel_understanding_2008}. This is consistent with the \hl{familiarity
+thesis (18)} \cite{hegel_understanding_2008} which claims we understand the
+world based upon a mental model of the world that we are most familiar with.
+Consequently, people tend to thoughtfully develop a mental model of agents in
+their environment and make inferences about it based on what is familiar to
+them. This point of view implicitly builds on a person's ability to attribute
+mental states to oneself and others, which is called \textit{Theory of
+Mind}~\cite{Premack1978}. A theory of  mind for other agents enables us to
+attribute intentionality to those agents
+\cite{leslie_pretense_1987,admoni_multi-category_2012}. If a system behaves much
+like a human being (\eg emits a human voice), people's mental model of the
+system's behavior may approach their mental model of humans, though the model
+may differ in some important aspects \hl{ref? Schmitz?}. In turn, people's
+estimation of a robot's knowledge model and its capabilities affects the way
+they relate to it. Previous research examined the validity of the mental model
+concept with various kinds of robots
+\cite{schmitz_concepts_2011,kiesler_mental_2002}. Findings suggest that people
+tend to hold richer mental models about anthropomorphic robots in contrast to
+mechanic ones \cite{kiesler_mental_2002}. Later in this article, we may however
+come to question this result for longer human-robot interactions, after one
+get's acquantained with the robot's behaviour.
 
@@
 
-	To understand the social phenomenon of anthropomorphism better, it makes sense to take a look at studies and explanations from developmental psychology.
-The phenomenon of attributing intentions and \hl{animacy} to simple shapes based on motion has been intensively studied in developmental psychology.
-Two famous studies on the perception of and attribution to simple things have been done in the mid 1940s: Heider and Simmel's work on the \textit{attribution theory} \cite{heider_experimental_1944} and Michotte's studies on \textit{the perception of causality} \cite{michotte_perception_1963}.
-In both experiments, participants viewed animations of simple shapes, such as circles or triangles (see Figure \ref{fig:animacy_attribution}).
-Asked to describe what they observed, interestingly, most people developed elaborate stories, attributing motivations, emotions and relationships between the objects.
+To understand the social phenomenon of anthropomorphism better, it makes sense
+to take a look at studies and explanations from developmental psychology. The
+phenomenon of attributing intentions and \hl{animacy} to simple shapes based on
+motion has been intensively studied in developmental psychology. Two famous
+studies on the perception of and attribution to simple things have been done in
+the mid 1940s: Heider and Simmel's work on the \textit{attribution theory}
+\cite{heider_experimental_1944} and Michotte's studies on \textit{the perception
+of causality} \cite{michotte_perception_1963}. In both experiments, participants
+viewed animations of simple shapes, such as circles or triangles (see Figure
+\ref{fig:animacy_attribution}). Asked to describe what they observed,
+interestingly, most people developed elaborate stories, attributing motivations,
+emotions and relationships between the objects.
 
@@
 
-	What is a person's motivation to attribute human characteristics to simple geometric shapes, or more sophisticated, anthropomorphic shapes, animated or not?
-Irrespective of the artifact's characteristics, there are psychological theories to explain the phenomenon.
-An interesting recent psychological theory of anthropomorphism (also related to robotics) is provided by Epley, Waytz, and Cacioppo \cite{epley_seeing_2007}.
-The authors established a three-factor theory of when people are likely to anthropomorphize based on psychological determinants.
-Namely, the theory suggests that some people are more likely to anthropomorphize when:
+What is a person's motivation to attribute human characteristics to simple
+geometric shapes, or more sophisticated, anthropomorphic shapes, animated or
+not? Irrespective of the artifact's characteristics, there are psychological
+theories to explain the phenomenon. An interesting recent psychological theory
+of anthropomorphism (also related to robotics) is provided by Epley, Waytz, and
+Cacioppo \cite{epley_seeing_2007}. The authors established a three-factor theory
+of when people are likely to anthropomorphize based on psychological
+determinants. Namely, the theory suggests that some people are more likely to
+anthropomorphize when:
 
@@
 
-	Epley \textit{et al.} describe that \textit{elicited agent knowledge} is a \textbf{cognitive determinant  of anthropomorphism} which is understood as the activation of knowledge about humans (or the self) when making inferences about non-human agents.
-One basic reasons for this are a person's physical constraints of being a human and nothing else.
-Consequently, one has no other experience than the self and in turn people tend to make inferences about others' mental states by relying inordinately on their own mental state.
-\footnote{Using one's own mental states and characteristics as a guide when reasoning about other humans is ego-centrism; when reasoning about non-human agents is anthropomorphism.
-See Epley, 2007 \textit{et al.} \cite{epley_seeing_2007}} Also empirical findings suggest that knowledge about humans in general, or self-knowledge in particular, is likely to serve as a readily accessible base for induction when reasoning about non-human agents.
-This tendency is usually stronger in young children and decreases with cognitive development and the learning to distinguish the self from other humans, and non-human agents.
-
-    Both \textit{effectance} and \textit{sociality} are \textbf{motivational determinants of anthropomorphism}.
-\textit{Effectance} is understood as the motivation to interact effectively in one's environment: understand, predict, \hl{reduce uncertainty (this feeds again our hypothesis that as soon as a robot is not uncertain anymore, there is no need to keep on anthropomorphizing it)}\fxfatal{important!
-move/copy that to the 'model' section or discussion} about one's environment and the agents that inhabit it.
-According to Epley \textit{et al.}, anthropomorphism serves as one way to reduce uncertainty and increase comprehension of events in one's environment.
-They mention for instance, children (as they are in their early stages of life) appear to be more likely to anthropomorphize than adults, as they might feel more uncertain within their environment.
-
-	\textit{Sociality} describes the motivation for social contact, social connection, and social approval from other agents.
-Importantly for anthropomorphism, this social connection appears to be satisfied by connections with \hl{ \textit{"two of the most commonly anthropomorphized non-human agents, namely pets and religious agents"}} \cite{epley_seeing_2007}.
-According to Epley \textit{et al.}, the motivation of being socially connected increases the tendency to anthropomorphize non-human agents because first sociality motivation increases the tendency to perceive human-like characteristics and traits even in non-human agents, and second it increases the tendency to search for sources of social connection in one's environment.
-Consequently, the authors suggest \textit{"[...] those who are chronically lonely should be more likely to anthropomorphize nonhuman agents than those who are more chronically connected"}.
+Epley \textit{et al.} describe that \textit{elicited agent knowledge} is a
+\textbf{cognitive determinant  of anthropomorphism} which is understood as the
+activation of knowledge about humans (or the self) when making inferences about
+non-human agents. One basic reasons for this are a person's physical constraints
+of being a human and nothing else. Consequently, one has no other experience
+than the self and in turn people tend to make inferences about others' mental
+states by relying inordinately on their own mental state. \footnote{Using one's
+own mental states and characteristics as a guide when reasoning about other
+humans is ego-centrism; when reasoning about non-human agents is
+anthropomorphism. See Epley, 2007 \textit{et al.} \cite{epley_seeing_2007}} Also
+empirical findings suggest that knowledge about humans in general, or
+self-knowledge in particular, is likely to serve as a readily accessible base
+for induction when reasoning about non-human agents. This tendency is usually
+stronger in young children and decreases with cognitive development and the
+learning to distinguish the self from other humans, and non-human agents.
+
+Both \textit{effectance} and \textit{sociality} are \textbf{motivational
+determinants of anthropomorphism}. \textit{Effectance} is understood as the
+motivation to interact effectively in one's environment: understand, predict,
+\hl{reduce uncertainty (this feeds again our hypothesis that as soon as a robot
+is not uncertain anymore, there is no need to keep on anthropomorphizing
+it)}\fxfatal{important! move/copy that to the 'model' section or discussion}
+about one's environment and the agents that inhabit it. According to Epley
+\textit{et al.}, anthropomorphism serves as one way to reduce uncertainty and
+increase comprehension of events in one's environment. They mention for
+instance, children (as they are in their early stages of life) appear to be more
+likely to anthropomorphize than adults, as they might feel more uncertain within
+their environment.
+
+\textit{Sociality} describes the motivation for social contact, social
+connection, and social approval from other agents. Importantly for
+anthropomorphism, this social connection appears to be satisfied by connections
+with \hl{ \textit{"two of the most commonly anthropomorphized non-human agents,
+namely pets and religious agents"}} \cite{epley_seeing_2007}. According to Epley
+\textit{et al.}, the motivation of being socially connected increases the
+tendency to anthropomorphize non-human agents because first sociality motivation
+increases the tendency to perceive human-like characteristics and traits even in
+non-human agents, and second it increases the tendency to search for sources of
+social connection in one's environment. Consequently, the authors suggest
+\textit{"[...] those who are chronically lonely should be more likely to
+anthropomorphize nonhuman agents than those who are more chronically
+connected"}.
 
@@
 Anthropomorphism is a commonly observed phenomenon in human-robot interaction.
-Studies showed that there are people who directly talk to their robot (even if it does not recognize speech), give it a name, greet it, wonder about its intentions or actions \cite{eyssel_anthropomorphic_2010,fink_anthropomorphic_2012,forlizzi_how_2007,fussell_how_2008,kiesler_anthropomorphic_2008}.
-It has frequently been described that people ascribe intentions or emotions to their domestic robot, such as to a Roomba vacuum-cleaning robot \cite{krumm_my_2007,sung_robots_2009} or the AIBO robotic dog \cite{friedman_hardware_2003}.
-People's tendency to anthropomorphize technologies has besides been described earlier in human-computer interaction and related to digital agents \cite{reeves_media_1996, nass_anthropocentrism_1995}.
-Though, the phenomenon seems to be more coined in human-robot interaction than in other human-machine interaction fields, due to the embodied nature of robots.
-They are physical agents, autonomously acting right next to us, and also designed to interact intelligently with us and the environment.
-Besides, anthropomorphism may be further supported by a specific anthropomorphic \emph{design}.
-But what is the motivation which underlies the efforts of enhancing anthropomorphism through specific anthropomorphic design in robots?
-Why does anthropomorphism seem to be so important in robotics?
-There is no one single answer to this question but certainly, developers and designers have discovered that anthropomorphism seems to be beneficial for human-robot relations, especially with socially interactive robots \cite{fong_survey_2003}.
-More concretely, it has been found that the appearance and function of a \hl{product (research in marketing?)}) impacts how people perceive it, interact with it, and build long-term relations with it \cite{bartneck_shaping_2004}.
-Consequently, the domain of (social) robotics tries to exploit this fact by enhancing anthropomorphism through anthropomorphic robots: \textit{"Applying anthropomorphism or zoomorphism changes the way how users try to understand and make sense of a [system] by projecting everyday \hl{expectations} of human and animalistic life onto it."} \cite{schmitz_concepts_2011}\fxfatal{paragraph a bit confusing...}.
-Studies have further shown that perceived similarity between the user and the robot influences the intensity of the participants' attributions towards the robot.
-Thus, anthropomorphism plays an important role in the design of robots as it is strongly related to the perception of intelligence, fun, the attribution of intentions and thus the predictability of the robot \hl{which ref??}.
-
-"[...] the experiment demonstrates that human beings implicitly attribute human-like qualities, such as mental states, to nonhuman agents.
-This finding was evident on a neurophysiological level as well as behavioral level." \cite{hegel_understanding_2008}\fxwarning{What to do with this quote?
-'neuro' level maybe interesting?}
+Studies showed that there are people who directly talk to their robot (even if
+it does not recognize speech), give it a name, greet it, wonder about its
+intentions or actions
+\cite{eyssel_anthropomorphic_2010,fink_anthropomorphic_2012,forlizzi_how_2007,fussell_how_2008,kiesler_anthropomorphic_2008}.
+It has frequently been described that people ascribe intentions or emotions to
+their domestic robot, such as to a Roomba vacuum-cleaning robot
+\cite{krumm_my_2007,sung_robots_2009} or the AIBO robotic dog
+\cite{friedman_hardware_2003}. People's tendency to anthropomorphize
+technologies has besides been described earlier in human-computer interaction
+and related to digital agents \cite{reeves_media_1996,
+nass_anthropocentrism_1995}. Though, the phenomenon seems to be more coined in
+human-robot interaction than in other human-machine interaction fields, due to
+the embodied nature of robots. They are physical agents, autonomously acting
+right next to us, and also designed to interact intelligently with us and the
+environment. Besides, anthropomorphism may be further supported by a specific
+anthropomorphic \emph{design}. But what is the motivation which underlies the
+efforts of enhancing anthropomorphism through specific anthropomorphic design in
+robots? Why does anthropomorphism seem to be so important in robotics? There is
+no one single answer to this question but certainly, developers and designers
+have discovered that anthropomorphism seems to be beneficial for human-robot
+relations, especially with socially interactive robots \cite{fong_survey_2003}.
+More concretely, it has been found that the appearance and function of a
+\hl{product (research in marketing?)}) impacts how people perceive it, interact
+with it, and build long-term relations with it \cite{bartneck_shaping_2004}.
+Consequently, the domain of (social) robotics tries to exploit this fact by
+enhancing anthropomorphism through anthropomorphic robots: \textit{"Applying
+anthropomorphism or zoomorphism changes the way how users try to understand and
+make sense of a [system] by projecting everyday \hl{expectations} of human and
+animalistic life onto it."} \cite{schmitz_concepts_2011}\fxfatal{paragraph a bit
+confusing...}. Studies have further shown that perceived similarity between the
+user and the robot influences the intensity of the participants' attributions
+towards the robot. Thus, anthropomorphism plays an important role in the design
+of robots as it is strongly related to the perception of intelligence, fun, the
+attribution of intentions and thus the predictability of the robot \hl{which
+ref??}.
+
+"[...] the experiment demonstrates that human beings implicitly attribute
+human-like qualities, such as mental states, to nonhuman agents. This finding
+was evident on a neurophysiological level as well as behavioral level."
+\cite{hegel_understanding_2008}\fxwarning{What to do with this quote? 'neuro'
+level maybe interesting?}
 
@@
 
-Anthropomorphism can also be viewed as an \textit{experience} that arises in the \textit{interaction} between a set of user expectations and external reality \cite{persson_anthropomorphism_2000}, (Figure~\ref{fig:anthropomorphism_and_interaction}).
-Persson \textit{et al.} suggest that the social phenomenon involves several levels, like primitive psychology, folk-psychology, social stereotypes, and emotional anthropomorphism.
+Anthropomorphism can also be viewed as an \textit{experience} that arises in the
+\textit{interaction} between a set of user expectations and external reality
+\cite{persson_anthropomorphism_2000},
+(Figure~\ref{fig:anthropomorphism_and_interaction}). Persson \textit{et al.}
+suggest that the social phenomenon involves several levels, like primitive
+psychology, folk-psychology, social stereotypes, and emotional anthropomorphism.
 
@@
 % figure caption is below the figure
- \caption{Anthropomorphism emerges in the (real or imagined) interaction between robot and user; illustration taken from \cite{persson_anthropomorphism_2000} \hl{maybe we don't put the figure here, it was just to illustrate what I mean}}
+ \caption{Anthropomorphism emerges in the (real or imagined) interaction between
+ robot and user; illustration taken from \cite{persson_anthropomorphism_2000}
+ \hl{maybe we don't put the figure here, it was just to illustrate what I mean}}
+
  \label{fig:anthropomorphism_and_interaction}       % Give a unique label
@@
 
-We would like to take up the proposition to discriminate different levels of anthropomorphism, since each has its own characteristics and involves specific types of user expectations.
-This differentiation could allow to draw inferences on the human-robot relationship from the observed level of anthropomorphism.
+We would like to take up the proposition to discriminate different levels of
+anthropomorphism, since each has its own characteristics and involves specific
+types of user expectations. This differentiation could allow to draw inferences
+on the human-robot relationship from the observed level of anthropomorphism.
 
@@
 
-	In general, it is suggested that increasing human-likeness of a robot	 will lead to more perceived \textit{affinity} from the human side \cite{mori_uncanny_1970}.
-This theoretical concept is also supported by psychological determinants of perceiving human-likeness in something non-human: \textit{"the more similar in appearance, the more people are likely to use themselves as a source of induction and anthropomorphize these nonhuman agents"} \cite{epley_seeing_2007}.
-Further, empirical studies have shown that robots with human-like forms can enhance social responses from humans which in turn can have a positive impact on acceptance \cite{venkatesh_theoretical_2000,duffy_anthropomorphism_2003,goetz_cooperation_2002}.
-People responded more positively to an artifact that displayed human-like behavioral characteristics (emotions, facial expression) in contrast to a purely functional design \cite{eyssel_anthropomorphic_2010,krach_can_2008,reeves_media_1996,riek_how_2009}.
-Overall, these results suggest that human-like features in robots enhance anthropomorphism, and in turn create a social view toward the robot.
-
-Well known from the HRI community, we may mention the other side of human-like behaviours and appearance: a not yet very well defined thin line separates acceptable human-like forms in robots from creepy artificial \textit{almost} human-like appearing robots.
-The underlying theory for this viewpoint is stated as the \textit{Uncanny Valley} \cite{mori_uncanny_1970} which suggests that artificial human-like forms are only acceptable up to a certain degree but lead to reluctance if they fail in trying to attain human-likeness \hl{cross-ref to later and figure}.
-
-The theory (Figure~\ref{fig:uncanny_valley}) hypothesizes that a person's response to a human-like robot would abruptly shift from empathy to revulsion as it approached, but failed to attain, a lifelike appearance \cite{mori_uncanny_1970}.
-Starting with low degrees of anthropomorphic cues in a robot, humans seem to readily accept and prefer them compared to purely mechanical robots.
-In general, one can say that up to a certain (yet not very well defined) degree, the more human-like the robot, the more affection it can engender through familiar communication references.
+In general, it is suggested that increasing human-likeness of a robot	 will
+lead to more perceived \textit{affinity} from the human side
+\cite{mori_uncanny_1970}. This theoretical concept is also supported by
+psychological determinants of perceiving human-likeness in something non-human:
+\textit{"the more similar in appearance, the more people are likely to use
+themselves as a source of induction and anthropomorphize these nonhuman agents"}
+\cite{epley_seeing_2007}. Further, empirical studies have shown that robots with
+human-like forms can enhance social responses from humans which in turn can have
+a positive impact on acceptance
+\cite{venkatesh_theoretical_2000,duffy_anthropomorphism_2003,goetz_cooperation_2002}.
+People responded more positively to an artifact that displayed human-like
+behavioral characteristics (emotions, facial expression) in contrast to a purely
+functional design
+\cite{eyssel_anthropomorphic_2010,krach_can_2008,reeves_media_1996,riek_how_2009}.
+Overall, these results suggest that human-like features in robots enhance
+anthropomorphism, and in turn create a social view toward the robot.
+
+Well known from the HRI community, we may mention the other side of human-like
+behaviours and appearance: a not yet very well defined thin line separates
+acceptable human-like forms in robots from creepy artificial \textit{almost}
+human-like appearing robots. The underlying theory for this viewpoint is stated
+as the \textit{Uncanny Valley} \cite{mori_uncanny_1970} which suggests that
+artificial human-like forms are only acceptable up to a certain degree but lead
+to reluctance if they fail in trying to attain human-likeness \hl{cross-ref to
+later and figure}.
+
+The theory (Figure~\ref{fig:uncanny_valley}) hypothesizes that a person's
+response to a human-like robot would abruptly shift from empathy to revulsion as
+it approached, but failed to attain, a lifelike appearance
+\cite{mori_uncanny_1970}. Starting with low degrees of anthropomorphic cues in a
+robot, humans seem to readily accept and prefer them compared to purely
+mechanical robots. In general, one can say that up to a certain (yet not very
+well defined) degree, the more human-like the robot, the more affection it can
+engender through familiar communication references.
 
@@
 % figure caption is below the figure
- \caption{Mashiro Mori, illustration of the \textit{Uncanny Valley}, originally from 1970; picture from a manuscript version of \cite{mori_uncanny_2012}}
+ \caption{Mashiro Mori, illustration of the \textit{Uncanny Valley}, originally
+ from 1970; picture from a manuscript version of \cite{mori_uncanny_2012}}
+
  \label{fig:uncanny_valley}       % Give a unique label
@@
 
-Another sensitive aspect is that with robots that closely resemble humans, ethical issues arise.
-For instance, we need to consider how far we actually want an \textit{artificial agent} to resemble ourselves and how far it should act `artificially socially' toward humans, and what happens as soon as it is considered a \textit{moral agent} \cite{sullins_when_2006}.
-Using \textit{socially interactive robots} in contexts involving elderly care or rehabilitation for disabled / handicapped persons, autistic children is also a controversially discussed topic \cite{robins_robots_2005}.
+Another sensitive aspect is that with robots that closely resemble humans,
+ethical issues arise. For instance, we need to consider how far we actually want
+an \textit{artificial agent} to resemble ourselves and how far it should act
+`artificially socially' toward humans, and what happens as soon as it is
+considered a \textit{moral agent} \cite{sullins_when_2006}. Using
+\textit{socially interactive robots} in contexts involving elderly care or
+rehabilitation for disabled / handicapped persons, autistic children is also a
+controversially discussed topic \cite{robins_robots_2005}.
 
@@
 
-The idea of the hypothesis follows Freud's description of the uncanny (a translation from the German word `unheimlich') \hl{ref Freud, The Uncanny}: "it derives its terror not from something externally alien or unknown but - on the contrary - from something strangely familiar which defeats our efforts to separate ourselves from it".
-\cite{hegel_understanding_2008}
+The idea of the hypothesis follows Freud's description of the uncanny (a
+translation from the German word `unheimlich') \hl{ref Freud, The Uncanny}: "it
+derives its terror not from something externally alien or unknown but - on the
+contrary - from something strangely familiar which defeats our efforts to
+separate ourselves from it". \cite{hegel_understanding_2008}
 
@@
 
-	"The anthropomorphic design of human-machine interfaces is inevitable.
-The important criterion is to seek a balance between people's expectations and the machines capabilities." \cite{duffy_anthropomorphism_2002}
-
-	"What is the ideal set of human features that could supplement and augment a robots  social functionality?" \cite{duffy_anthropomorphism_2002}
-
-	Though, the 'anthropomorphic design principle" seems beneficial, it also raises ethical issues and has been reviewed critically in terms of acceptance.
-How far do we want a robot to resemble a human or act like a human?
-
-	Findings that support anthropomorphic form in robots because they found people respond with anthropomorphizing these kind of robots, and in turn act more social toward them or accept them more easily:
+"The anthropomorphic design of human-machine interfaces is inevitable. The
+important criterion is to seek a balance between people's expectations and the
+machines capabilities." \cite{duffy_anthropomorphism_2002}
+
+"What is the ideal set of human features that could supplement and augment a
+robots  social functionality?" \cite{duffy_anthropomorphism_2002}
+
+Though, the 'anthropomorphic design principle" seems beneficial, it also raises
+ethical issues and has been reviewed critically in terms of acceptance. How far
+do we want a robot to resemble a human or act like a human?
+
+Findings that support anthropomorphic form in robots because they found people
+respond with anthropomorphizing these kind of robots, and in turn act more
+social toward them or accept them more easily:
 
@@
 
-Why do we think that anthropomorphic projections are likely to change over time and with growing experience a person has with a robot?
-The underlying process in anthropomorphism is understood as reasoning about and perceiving something non-human, and unknown or unfamiliar based on one's representation of the familiar and well-known concept of being human (or one-self).
-The basic operations underlying inductive inference are the acquisition of knowledge, the activation or elicitation of knowledge, and the application of activated knowledge at the time of the judgment \cite{epley_when_2008}.
-According to Epley \textit{et al.}, the application includes attempts to correct, adjust, or integrate less accessible information into a more automatically activated default representation.
-This process can be seen as a process of correction, and thus, it is often insufficient leaving final judgments biased in the direction of the initially activated representation.
-As a person's knowledge base changes / evolves constantly with newly acquired things, or growing experiences with a robot, etc., it is likely that the "need to anthropomorphize" a robot decreases over time.
-First, because of the evolved knowledge about it, and second because one has familiarized oneself with it.
-Consequently, the robot should become more predictable and more familiar to the human user and inferences about it can be made based on the acquired knowledge.
-/fxfatal{confusing paragraph...needs reformulation. Could also be turned into a section introduction instead of a subsection}
+Why do we think that anthropomorphic projections are likely to change over time
+and with growing experience a person has with a robot? The underlying process in
+anthropomorphism is understood as reasoning about and perceiving something
+non-human, and unknown or unfamiliar based on one's representation of the
+familiar and well-known concept of being human (or one-self). The basic
+operations underlying inductive inference are the acquisition of knowledge, the
+activation or elicitation of knowledge, and the application of activated
+knowledge at the time of the judgment \cite{epley_when_2008}. According to Epley
+\textit{et al.}, the application includes attempts to correct, adjust, or
+integrate less accessible information into a more automatically activated
+default representation. This process can be seen as a process of correction, and
+thus, it is often insufficient leaving final judgments biased in the direction
+of the initially activated representation. As a person's knowledge base changes
+/ evolves constantly with newly acquired things, or growing experiences with a
+robot, etc., it is likely that the "need to anthropomorphize" a robot decreases
+over time. First, because of the evolved knowledge about it, and second because
+one has familiarized oneself with it. Consequently, the robot should become more
+predictable and more familiar to the human user and inferences about it can be
+made based on the acquired knowledge.  /fxfatal{confusing paragraph...needs
+reformulation. Could also be turned into a section introduction instead of a
+subsection}
 
@@
 
-The phenomenological model of anthropomorphism we propose (Figure~\ref{fig:dynamics},~\cite{lemaignan2014dynamics}) represents
-how the level of anthropomorphic effects (\ie observable manifestations of
+The phenomenological model of anthropomorphism we propose
+(Figure~\ref{fig:dynamics},~\cite{lemaignan2014dynamics}) represents how the
+level of anthropomorphic effects (\ie observable manifestations of
 anthropomorphism, as defined in section~\ref{sec:intro}) evolves over a
@@
     interaction starts, the level of anthropomorphism increases due to the
-\emph{novelty effect}~\cite{kanda_interactive_2004}, and then decreases to reach a \emph{stabilized level
-of anthropomorphism} (SLA).  During the interaction, unpredicted behaviors
-of the robot (\emph{disruptive behaviors}) may lead to local increase of the
-level of anthropomorphism.}
+    \emph{novelty effect}~\cite{kanda_interactive_2004}, and then decreases to
+    reach a \emph{stabilized level of anthropomorphism} (SLA).  During the
+    interaction, unpredicted behaviors of the robot (\emph{disruptive behaviors})
+    may lead to local increase of the level of anthropomorphism.}
 
@@
         artifacts~\cite{epley_seeing_2007}. Other individual traits and
-        demographic aspects are comprised (\eg age, gender, cultural
-        background, professional background).
+        demographic aspects are comprised (\eg age, gender, cultural background,
+        professional background).
 
@@
         \textbf{purpose} of the robot, including the situational context in
-        which it is used, as well as the task context and role in which the robot is
-		used / experienced (environmental context)~\cite{joosse_what_2013}.
+        which it is used, as well as the task context and role in which the
+        robot is used / experienced (environmental
+        context)~\cite{joosse_what_2013}.
 
@@
 
-The ICA comprises some hypothetical values for each of these three factors, such that different ICA values can be obtained, given the robot, human user, and environmental context\fxfatal{??}.
-
-	For \textbf{personality}, we suggest to apply Epley \textit{et al.}'s \cite{epley_seeing_2007} psychological \textit{"Three Factor Theory"} of anthropomorphism.
-For instance, children generally tend to anthropomorphize objects more than adults.
-Also, a person who lacks social connection is said to be more likely to anthropomorphize.
-Both aspects would increase the ICA.
-This means that, one and the same robot used by a different user, can lead to a different ICA.
-
-    For \textbf{design}, we understand that a robot that follows an anthropomorphic design (\eg NAO) leads to a higher ICA than a rather functional robot (\eg Roomba).
-Also, a robot that is able to display facial expressions would increase the ICA.
-However, \hl{as discussed before} a classification of the "amount" of anthropomorphic design in a robot, as for instance suggested by Fong \textit{et al.} \cite{fong_survey_2003}, can be difficult.
-Nevertheless, the important aspect is how the robot appears to the user, \eg human-like or machine-like.
-Studies have shown that an anthropomorphic robot is perceived differently to a non-anthropomorphic robot\fxfatal{...this sentence sounds strange like that.
+The ICA comprises some hypothetical values for each of these three factors, such
+that different ICA values can be obtained, given the robot, human user, and
+environmental context\fxfatal{??}.
+
+For \textbf{personality}, we suggest to apply Epley \textit{et al.}'s
+\cite{epley_seeing_2007} psychological \textit{"Three Factor Theory"} of
+anthropomorphism. For instance, children generally tend to anthropomorphize
+objects more than adults. Also, a person who lacks social connection is said to
+be more likely to anthropomorphize. Both aspects would increase the ICA. This
+means that, one and the same robot used by a different user, can lead to a
+different ICA.
+
+For \textbf{design}, we understand that a robot that follows an anthropomorphic
+design (\eg NAO) leads to a higher ICA than a rather functional robot (\eg
+Roomba). Also, a robot that is able to display facial expressions would increase
+the ICA. However, \hl{as discussed before} a classification of the "amount" of
+anthropomorphic design in a robot, as for instance suggested by Fong \textit{et
+al.} \cite{fong_survey_2003}, can be difficult. Nevertheless, the important
+aspect is how the robot appears to the user, \eg human-like or machine-like.
+Studies have shown that an anthropomorphic robot is perceived differently to a
+non-anthropomorphic robot\fxfatal{...this sentence sounds strange like that.
 Need references or better integration in the paragraph}.
@@
 sight of a good-looking humanoid robot, and get disappointed by the actual
-abilities of the robots, down to routine, non-anthropomorphic, interactions
-(low SLA), while another user with the same high ICA may, for instance, creates
+abilities of the robots, down to routine, non-anthropomorphic, interactions (low
+SLA), while another user with the same high ICA may, for instance, creates
 lasting affective bonds with the same robot, and keeps anthropomorphizing it
@@
 A \emph{stable level of anthropomorphism} is reached when the adaptation process
-depicted in cognitive phase III reached a stable state, \ie the user's experience
-with the robot is correctly supported by the cognitive model he/she has
-built.
+depicted in cognitive phase III reached a stable state, \ie the user's
+experience with the robot is correctly supported by the cognitive model he/she
+has built.
 
@@
 \begin{description}
-	\item[\textbf{Hypothesis 1}] A person's tendency to anthropomorphize a robot is impacted by the context of use and purpose of the robot.
-A social context and purpose of the robot increases anthropomorphism.
+    \item[\textbf{Hypothesis 1}] A person's tendency to anthropomorphize a robot
+        is impacted by the context of use and purpose of the robot. A social
+        context and purpose of the robot increases anthropomorphism.
         \textit{(context and purpose of the robot)}
+
 \end{description}
@@
 
-	The \textit{context of use} is related to the purpose (and functionality) of the robot and influences the user interaction experience.
-With \textit{time}, we refer to long-term interaction with the robot, which is related to what has been described as \textit{novelty effect} but also accounts for the user getting used to the robot.
-Consequently, we propose that anthropomorphism is not static but likely to change, due to what we call \textit{dynamics}, in space and time.
-
-	As outlined in section \hl{XX}, the tendency to anthropomorphize is motivated by a person's wish to make sense of an agent which might be difficult to understand (in its functionality or behavior, for instance).
-In turn, a user might ascribe intentions or emotions to the system because the systems output was unexpected for the user.
-Based on this explanation, we estimate that when the user has familiarized herself / himself with the system, thus reached the point of when the system is usable and explainable, the tendency to anthropomorphize decreases.
-Therefore, our second hypothesis is as follows:
+The \textit{context of use} is related to the purpose (and functionality) of the
+robot and influences the user interaction experience. With \textit{time}, we
+refer to long-term interaction with the robot, which is related to what has been
+described as \textit{novelty effect} but also accounts for the user getting used
+to the robot. Consequently, we propose that anthropomorphism is not static but
+likely to change, due to what we call \textit{dynamics}, in space and time.
+
+As outlined in section \hl{XX}, the tendency to anthropomorphize is motivated by
+a person's wish to make sense of an agent which might be difficult to understand
+(in its functionality or behavior, for instance). In turn, a user might ascribe
+intentions or emotions to the system because the systems output was unexpected
+for the user. Based on this explanation, we estimate that when the user has
+familiarized herself / himself with the system, thus reached the point of when
+the system is usable and explainable, the tendency to anthropomorphize
+decreases. Therefore, our second hypothesis is as follows:
 
@@
 
-Given our first hypothesis from above, this might not hold over all contexts; more concretely, probably not in a social context of usage.
-
-	Smart innovative devices, such as personal domestic robots, might demand from a human user spontaneous usage of an unfamiliar system.
-Such situations will require that a user should be able to build up a mental model quickly, which particularly holds for novice users \cite{schmitz_concepts_2011}.
-
-	Eddy \textit{et al.} points out that familiarity increases the tendency to anthropomorphize \cite{eddy_attribution_1993}.
-
-	"As shown in several psychological experiments [13,24] and pointed out by Watt [25], familiarity may also ease social acceptance and even tend to increase people's tendency to anthropomorphize [16]." \cite{duffy_anthropomorphism_2003}
+Given our first hypothesis from above, this might not hold over all contexts;
+more concretely, probably not in a social context of usage.
+
+Smart innovative devices, such as personal domestic robots, might demand from a
+human user spontaneous usage of an unfamiliar system. Such situations will
+require that a user should be able to build up a mental model quickly, which
+particularly holds for novice users \cite{schmitz_concepts_2011}.
+
+Eddy \textit{et al.} points out that familiarity increases the tendency to
+anthropomorphize \cite{eddy_attribution_1993}.
+
+"As shown in several psychological experiments [13,24] and pointed out by Watt
+[25], familiarity may also ease social acceptance and even tend to increase
+people's tendency to anthropomorphize [16]." \cite{duffy_anthropomorphism_2003}
 
@@
 shows that unexpected behaviors of the robot can have a notable impact on
-interaction. \hl{cite literature, e.g. cheating robot, disagreeing, disobeying, HRI2013 paper}
-
-During a normal interaction with the robot, the user iteratively refines his/her own
-model of the behavior of the robot. As explained in previous sections, as the
-user improves his/her model of the robot's actions, he/she also improves the ability to predict
-the actions and thus, the user tends to anthropomorphize less.
+interaction. \hl{cite literature, e.g. cheating robot, disagreeing, disobeying,
+HRI2013 paper}
+
+During a normal interaction with the robot, the user iteratively refines his/her
+own model of the behavior of the robot. As explained in previous sections, as
+the user improves his/her model of the robot's actions, he/she also improves the
+ability to predict the actions and thus, the user tends to anthropomorphize
+less.
 
 We emit the hypothesis that an unexpected robot behavior might lead the user to
-suddenly restate his/her behavioral model of the robot and will temporarily lead to
-an increase of the level of anthropomorphism (depicted by the spikes on
+suddenly restate his/her behavioral model of the robot and will temporarily lead
+to an increase of the level of anthropomorphism (depicted by the spikes on
 Figure~\ref{fig:dynamics}).
@@
 When talking about \emph{unexpected robot behaviors}, several distinct cases
-must however be considered, summarized in Table~\ref{fig:perceptionUnexpectedBehavior}.
+must however be considered, summarized in
+Table~\ref{fig:perceptionUnexpectedBehavior}.
 
@@
 explicitly states its failure (for instance, by saying ``I'm lost!''), the
-behavior is then called \emph{transparent} \fixme{cite here, Julia?} \hl{(literature on transparency)}, and the
-user may besides hypothesize that the robot has \emph{introspective}
-capabilities (it can reflect on its own internal state), which in turn may
-leads to higher anthropomorphism level.  On the contrary, if the robot shows no
-sign of recognizing its own failure, the user may ascribe a lower level of
-anthropomorphism to the robot.
+behavior is then called \emph{transparent} \fixme{cite here, Julia?}
+\hl{(literature on transparency)}, and the user may besides hypothesize that the
+robot has \emph{introspective} capabilities (it can reflect on its own internal
+state), which in turn may leads to higher anthropomorphism level.  On the
+contrary, if the robot shows no sign of recognizing its own failure, the user
+may ascribe a lower level of anthropomorphism to the robot.
 
@@
 For instance, the human asks the robot to go somewhere, and the robot refuses,
-saying ``I do not want to go there''. In that case, we expect to see an
-increase of anthropomorphism attribution due to the human ascribing
-intentionality to the robot.
+saying ``I do not want to go there''. In that case, we expect to see an increase
+of anthropomorphism attribution due to the human ascribing intentionality to the
+robot.
 
@@
 (case I or II), is likely to lead to stronger effects due to a larger delta
-between expectations and actual observed behavior. \hl{(we actually assume that anthropomorphism can be radically changing and be a very spontaneous "reaction".)}
+between expectations and actual observed behavior. \hl{(we actually assume that
+anthropomorphism can be radically changing and be a very spontaneous
+"reaction".)}
 
@@
 
-This interpretation of anthropomorphism in terms of cognitive correlates
-opens questions that we hope could be fruitfully discussed during the workshop.
-By adopting both a cognitive and a dynamic perspective on the anthropomorphic
-bonds that establish between a robot and a human during an interaction, 
-some observations can be raised.
+This interpretation of anthropomorphism in terms of cognitive correlates opens
+questions that we hope could be fruitfully discussed during the workshop.  By
+adopting both a cognitive and a dynamic perspective on the anthropomorphic bonds
+that establish between a robot and a human during an interaction, some
+observations can be raised.
 
@@
 Could we imagine that the robot pro-actively \emph{verbalises} its own limits,
-in a timely manner (likely before the end of the novely effect). And how would this
-affect the cognitive models built by the human?
+in a timely manner (likely before the end of the novely effect). And how would
+this affect the cognitive models built by the human?
 
@@
 cognitive sciences (and in particular social psychology) regarding how we, as
-humans, cope with unexpected behaviours from peers, or on the dynamics of
-mental model refinements, could bring interesting perspectives with possible
+humans, cope with unexpected behaviours from peers, or on the dynamics of mental
+model refinements, could bring interesting perspectives with possible
 applications to better manage long-term human-robot interactions.
@@
 
-While anthropomorphism is traditionally empirically understood as the interactions between
-the anthropomorphic design of a robot and the psychological determinants of the
-user, it appears that the duration and context of the
+While anthropomorphism is traditionally empirically understood as the
+interactions between the anthropomorphic design of a robot and the psychological
+determinants of the user, it appears that the duration and context of the
 interaction are also key factors, and that anthropomorphism needs to be
@@
 contribution consolidates the scientific grounds of anthropomorphism, and
-provides support for a better understanding of long-term acceptance of robots
-in human environments.
+provides support for a better understanding of long-term acceptance of robots in
+human environments.
 
@@
 We would like to acknowledge here the fruitful discussions with A Jung Moon and
-Aude Billard.\\
+Aude Billard.
 

### 2014-03-10 paper.tex
Updated the template to Frontiers model

--- 2014-01-21 dynamics-anthropomorphism.tex
@@
-\documentclass[lettersize, apacite, twoside, HRI]{apa_HRI}
-\usepackage{times} % Required package for HRI journal format
-
-% UTF8 support
-\usepackage[utf8x]{inputenc}
-\usepackage[T1]{fontenc}
+\documentclass{frontiersSCNS} % for Science articles
+
+%\usepackage[utf8x]{inputenc}
+%\usepackage[T1]{fontenc}
+
+%\usepackage[english]{babel}
 
@@
 \usepackage{url}
-\usepackage[numbers, square, comma, sort&compress]{natbib}
 \usepackage{multirow}
@@
 
-\rightheader{Journal of Human-Robot Interaction}
-\leftheader{Fink et al.}
-
 \newcommand{\eg}{{\textit{e.g.~}}}
@@
 
-\title{On the Dynamics of Anthropomorphism in Robotics
-}
-
-\author{Julia Fink, Séverin Lemaignan, Pierre Dillenbourg}
-\affiliation{ Computer-Human Interaction in Learning and Instruction (CHILI) \\
-              Ecole Polytechnique Fédérale de Lausanne (EPFL) \\
-              CH-1015 Lausanne, Switzerland
-}
+% Leave a blank line between paragraphs in stead of using \\
+
+\copyrightyear{}
+\pubyear{}
+
+\def\journal{Cognitive Science}%%% write here for which journal %%%
+\def\DOI{}
+\def\articleType{Research Article}
+\def\keyFont{\fontsize{8}{11}\helveticabold }
+\def\firstAuthorLast{Fink {et~al.}} %use et al only if is more than 1 author
+\def\Authors{Julia Fink\,$^{*}$, S\'{e}verin Lemaignan\, Claire Braboszcz and Pierre Dillenbourg}
+\def\Address{Computer-Human Interaction in Learning and Instruction (CHILI) \\ Ecole Polytechnique F\'{e}d\'{e}rale de Lausanne (EPFL) \\ CH-1015 Lausanne, Switzerland}
+\def\corrAuthor{Julia Fink \vspace{1mm}}
+\def\corrAddress{EPFL - CHILI, RLC D1 740, Station 20, CH-1015 Lausanne, Switzerland}
+\def\corrEmail{julia.fink@epfl.ch}
+
+\begin{document}
+\onecolumn
+\firstpage{1}
+
+\title[Dynamics of Anthropomorphism]{Dynamics of Anthropomorphic Effects in Human-Robot Interaction}
+\author[\firstAuthorLast ]{\Authors}
+\address{}
+\correspondance{}
+\extraAuth{}
+\topic{The Uncanny Valley Hypothesis and Beyond}% If your article is part of a Research Topic, please indicate here which.
+
+\maketitle
 
@@
 
-\keywords{Anthropomorphism, Design, Human-Robot Interaction, Social Issues in Robotics, Acceptance of Robots}
-
-\begin{document}
-\maketitle
+%\keywords{Anthropomorphism, Design, Human-Robot Interaction, Social Issues in Robotics, Acceptance of Robots}
 
@@
 
-\paragraph{Anthropomorphism in robotics \hl{[I think this first paragraph should go somewhere else, later probably]}}
+\paragraph{Anthropomorphism in robotics}
+\hl{[I think this first paragraph should go somewhere else, later probably]}
 
@@
 
-\begin{description}
+\begin{itemize}
     \item[\textbf{Hypothesis 1}] A person's tendency to anthropomorphize a robot
@@
 
-\end{description}
+\end{itemize}
 
@@
 
-\begin{description}
+\begin{itemize}
 	\item[\textbf{Hypothesis 2}] A person's tendency to anthropomorphize a robot decreases over time and with growing experience the person has with the robot.
 \textit{(familiarize oneself with the robot)}
-\end{description}
+\end{itemize}
 
@@
 \section{Bibliography}
+
+\bibliographystyle{frontiersinSCNS&ENG} % for Science and Engineering articles
 \bibliography{dynamics-anthropomorphism}   % name your BibTeX data base
 
-\hrule
-
-\vspace*{.1in}
-Authors' names and contact information: Julia Fink {\tt julia.fink@epfl.ch}, Séverin Lemaignan {\tt severin.lemaignan@epfl.ch}, Pierre Dillenbourg {\tt pierre.dillenbourg@epfl.ch}, CHILI Lab, EPFL, Lausanne, Switzerland.
 \end{document}

### 2014-03-11 paper.tex
Julia tried to mess up the structure a bit ...

@@
 %
-%				INTRODUCTION
+%		INTRODUCTION & OVERVIEW
 %
@@
 
-\section{Anthropomorphism}
+% JULIA: brief problem definition / issue, motivation, objectives, contribution ...
+
+\vspace{2cm}
+\section{Introduction and Overview}
 \label{sec:intro}
@@
 der P{\"u}tten (2013)}, and more recent studies investigated how far people
-ascribe personality or intentions to artificial emobdied agents or whether they
+ascribe personality or intentions to artificial embodied agents or whether they
 show empathetic behavior toward robots
@@
 
-\paragraph{Anthropomorphism in robotics}
-\hl{[I think this first paragraph should go somewhere else, later probably]}
-
-Anthropomorphism represents just one of many examples of induction whereby
-"people reason about an unknown stimulus based on a better-known representation
-of a related stimulus" \cite{epley_when_2008}, in this case reasoning about a
-non-human agent based on representation of the self or other humans. This
-supports the usual role we assign to anthropomorphism in robotics: the
-anthropomorphic design of a robot encourages people to reason about this
-unfamiliar system \emph{as if} it was a human. To increase this tendency, robots
-are designed with anthropomorphic forms (human-like or lifelike forms, in the
-broader sense), or are able to display and use human-social cues when
-interacting with humans.\\
-
-Literature on anthropomorphism (the social phenomenon) in robotics as well as on
-anthropomorphic design of robots is quite diverse and one strives hard to
-extract a coherent conclusion. One reason for this might be that robotics is a
-multi-disciplinary field and researchers from very different domains might
-integrate diverse or even contradictory understandings, or simply refer to
-different things. However, despite the fact that there is no commonly accepted
-definition, and also the terminology is not clear, the terms
-\textit{anthropomorphism}, \textit{anthropomorphic} or \textit{human-like} are
-often used as if their meanings were clear and agreed upon
-\cite{persson_anthropomorphism_2000}. Duffy \cite{duffy_anthropomorphism_2002}
-argues that these terms might even be misused (in accordance with
-\cite{epley_when_2008}). For instance, some researchers refer to \textit{"the
-robot's level of anthropomorphism"} \cite{bartneck_is_2007}, whereas others
-argue that the system or artifact itself does not "contain anthropomorphism"
-\textit{per se} but only gives rise to the process of anthropomorphizing in a
-given user and situation. Consequently, Persson \textit{et al.} conclude that
-anthropomorphism emerges in the \textit{interaction} between the technology and
-the user \cite{persson_anthropomorphism_2000}.  \hl{[In this article, we accept
-this latter viewpoint and would like to clearly distinguish between the term
-\textit{anthropomorphism} as a social phenomenon and \textit{anthropomorphic} as
-a specific design. This however, is not yet a definition of what exactly both
-terms refer to. Still, we acknowledge that both terms can refer to different
-levels or types; which we will outline later.]}
-
-Paradoxically, human's tendency to anthropomorphize non-human agents (such as
-robots) is commonly observed but at the same time it is rather poorly understood
-\cite{epley_seeing_2007}. There might be several reasons. First, probably
-because the phenomenon itself has been found to be very complex though sometimes
-subtle and as such hard to study. Second, the rather poor (or controversial)
-understanding, might also be due to the limited reliability of some findings (or
-interpretations) from experiments investigating anthropomorphism. Most of the
-experiments that investigate anthropomorphism in robotics are conducted in
-controlled lab-settings during short-term human-robot interactions. This
-experimental setting can be critical when studying a social phenomenon like
-anthropomorphism and possibly lead to over-interpretations. Some studies (e.g.
-exploring characteristics of the "uncanny valley") also seem to contrast two or
-more different anthropomorphic or mechanical systems that might not be
-appropriate for comparison given the complex context. Others might also use
-empirical methods inappropriate for the given research question which leads to
-inaccurate results. \hl{say more}
-
-To sum it up, while anthropomorphism in robotics is a commonly discussed and
-studied trait of human-robot interaction, we think it paradoxically lacks a
-formal ground and unified understanding. The understanding of anthropomorphism
-in robotics seems to not take into account the wide range of phenomena that it
-encompasses. The traditional understanding of anthropomorphism in robotics to
-date considers two main factors that account for the social phenomenon: the
-characteristics of \textbf{1) the robot's design} (degree of human-likeness) and
-the psychological determinants in \textbf{2) the human user} (see
-\cite{epley_seeing_2007}). It has been shown that both these factors can
-facilitate or hinder anthropomorphism. We propose to go beyond this traditional
-perception of anthropomorphism as a static feature of HRI: Based on Persson
-\textit{et al.}'s~\cite{persson_anthropomorphism_2000} argumentation that
-anthropomorphism is a multi-layered phenomenon which arises in different levels,
-we suggest to understand anthropomorphism as a \emph{dynamic},
-\emph{context-dependent} process. To this end, we apply Persson \textit{et
-al.}'s six levels on anthropomorphism to HRI and introduce three
-\emph{interaction phases}. These interaction phases of anthropomorphism reflect
-also the results of a long-term study that we conducted in a real human
-environment and provide an account of the so-called \textit{novelty effect}. We
-also draw attention to two new determinants of anthropomorphism, namely, the
-context of use and the fact of getting used to a system over time. We propose to
-add these two aspects as a third factor, the characteristics of \textbf{3) the
-interaction} (time and space), to the previous two factors of anthropomorphism
-(robot and user).
-
-%% -> Commented out the overview as it does not match what we actually present... maybe we need a new one?
-% We would further like to review and discuss research on anthropomorphism in
-% robotics and human-like design of robots. We first provide a comprehensive
-% understanding of the phenomenon drawing on theories from developmental
-% psychology and cognitive sciences. We then present the trends of different
-% kinds of anthropomorphic forms in robots and discuss their role in social
-% robotics. The article integrates related work from human-robot interaction
-% studies, reporting on findings from experiments with human subjects
-% interacting with and evaluating various types of systems. We try to give a
-% coherent view on the topic, outline similarities and antithetic findings, and
-% contribute to a better understanding of anthropomorphism in robotics, and the
-% acceptance of human-like characteristics in robots. We also aim to
-% constructively discuss anthropomorphic design of personal and socially
-% interactive robots.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %
-%				ANTHROPOMORPHISM: EXPLANATIONS & BACKGROUND
+%		PART 1: WHAT OTHERS DID AND WE ALREADY KNOW ABOUT ANTHROPOMORPHISM
 %
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Anthropomorphism as a Social Phenomenon}
-\label{sec:origins-anthropomorphism}
+%
+% JULIA: there will be 4-5 subsections
+%	1) anthropomorphism as a social phenomenon, definitions, origins, etc.
+%	2) anthropomorphism as a consequence of anthropomorphic / life-like design
+%	3) the link to robotics and HRI, mention the uncanny valley theory ...
+%	4) however: we suggest anthropomorphism is more than a static feature ...
+%
+%
+
+\vspace{2cm}
+\section{Anthropomorphism}
+\label{sec:anthropomorphism}
+
+\hl{bridge sentence}
+
+\subsection*{Anthropomorphism as a Social Phenomenon}
+\label{sec:social-phenomenon}
 
@@
 
-\subsection{Explanations for Anthropomorphism}
+\paragraph{Explanations for Anthropomorphism}
 \label{sec:explanations}
@@
 \fxfatal{inconsistency: we already give explanations for anthropomorphism in previous paragraph...}
+
+Anthropomorphism represents just one of many examples of induction whereby
+``people reason about an unknown stimulus based on a better-known representation
+of a related stimulus"~\cite{epley_when_2008}, in this case reasoning about a
+non-human agent based on representation of the self or other humans.
+
+According to Lee \etal~\cite{lee_human_2005}, there are two main perspectives in
+explaining people's tendency to anthropomorphize. First one explains
+anthropomorphism from the design of the artifact. It assumes that humans
+directly respond to life-like or social cues that an object or system emits,
+without thoughtful mental processing, by simply applying stereotypes and
+heuristics to it. In fact, from early childhood on, humans are inherently
+well-trained to perceive life \cite{epley_seeing_2007}. Schmitz
+\cite{schmitz_concepts_2011} describes that within the visual scope of design,
+the outer appearance can have an important impact on the overall perception of
+an object. The basic assumption here is that if an artifact appears much like a
+human, it is likely to be treated similar to a human. If this explanation of
+anthropomorphism is correct, people may respond automatically to social cues
+emitted by a robot, and apply human-human social schemas and norms to these
+interactions.
+
+The second perspective applies a human-centered, cognitive viewpoint where
+anthropomorphism is described through people's specific mental model they
+construct about how an artifact works the way it does.  We then
+anthropomorphize because it allows us to explain things we do not understand in
+terms that we do understand, and what we understand best is ourselves as human
+beings. This is consistent with the \emph{familiarity
+thesis}~\cite{hegel_understanding_2008} which claims that we understand the
+world based upon a mental model of the world that we are most familiar with.
+Consequently, people tend to thoughtfully develop a mental model of agents in
+their environment and make inferences about it based on what is familiar to
+them -- humans and human behavior, for instance.  This point of view implicitly
+builds on a person's ability to attribute mental states to oneself and others
+(\ie the availability of a \emph{theory of mind}~\cite{premack1978does} -- the
+link between a tendency to anthropomorphize and the engagement in the
+attribution of mental states to other humans has been recently demonstrated at
+the brain level in~\cite{cullen2013individual}). A theory of mind for other
+agents enables us to attribute intentionality to those agents
+\cite{leslie_pretense_1987,admoni_multi-category_2012}. Previous research
+examined the validity of the mental model concept with various kinds of robots
+\cite{schmitz_concepts_2011,kiesler_mental_2002}. Findings suggest that people
+tend to hold richer mental models of anthropomorphic robots in contrast to
+mechanic ones \cite{kiesler_mental_2002}.
+
 According to Lee \textit{et al.} \cite{lee_human_2005}, there are two main
@@
 
-\subsection{Insights from Social and Developmental Psychology}
+\paragraph{Insights from Social and Developmental Psychology}
 \label{sec:psychological-factors}
@@
 
-\subsection{Anthropomorphism in Robotics}
+\subsection*{Anthropomorphic Design Principle}
+\label{sec:anthropomorphic-design}
+
+\hl{check if we really need this section ... maybe yes because it is important for the uncanny valley hypothesis}
+
+In general, it is suggested that increasing human-likeness of a robot	 will
+lead to more perceived \textit{affinity} from the human side
+\cite{mori_uncanny_1970}. This theoretical concept is also supported by
+psychological determinants of perceiving human-likeness in something non-human:
+\textit{"the more similar in appearance, the more people are likely to use
+themselves as a source of induction and anthropomorphize these nonhuman agents"}
+\cite{epley_seeing_2007}. Further, empirical studies have shown that robots with
+human-like forms can enhance social responses from humans which in turn can have
+a positive impact on acceptance
+\cite{venkatesh_theoretical_2000,duffy_anthropomorphism_2003,goetz_cooperation_2002}.
+People responded more positively to an artifact that displayed human-like
+behavioral characteristics (emotions, facial expression) in contrast to a purely
+functional design
+\cite{eyssel_anthropomorphic_2010,krach_can_2008,reeves_media_1996,riek_how_2009}.
+Overall, these results suggest that human-like features in robots enhance
+anthropomorphism, and in turn create a social view toward the robot.
+
+Well known from the HRI community, we may mention the other side of human-like
+behaviours and appearance: a not yet very well defined thin line separates
+acceptable human-like forms in robots from creepy artificial \textit{almost}
+human-like appearing robots. The underlying theory for this viewpoint is stated
+as the \textit{Uncanny Valley} \cite{mori_uncanny_1970} which suggests that
+artificial human-like forms are only acceptable up to a certain degree but lead
+to reluctance if they fail in trying to attain human-likeness \hl{cross-ref to
+later and figure}.
+
+The theory (Figure~\ref{fig:uncanny_valley}) hypothesizes that a person's
+response to a human-like robot would abruptly shift from empathy to revulsion as
+it approached, but failed to attain, a lifelike appearance
+\cite{mori_uncanny_1970}. Starting with low degrees of anthropomorphic cues in a
+robot, humans seem to readily accept and prefer them compared to purely
+mechanical robots. In general, one can say that up to a certain (yet not very
+well defined) degree, the more human-like the robot, the more affection it can
+engender through familiar communication references.
+
+\begin{figure}\centering
+% Use the relevant command to insert your figure file.
+% For example, with the graphicx package use
+  \includegraphics[scale=0.6]{uncanny-valley.jpg}
+% figure caption is below the figure
+ \caption{Mashiro Mori, illustration of the \textit{Uncanny Valley}, originally
+ from 1970; picture from a manuscript version of \cite{mori_uncanny_2012}}
+
+ \label{fig:uncanny_valley}       % Give a unique label
+ \end{figure}
+
+Another sensitive aspect is that with robots that closely resemble humans,
+ethical issues arise. For instance, we need to consider how far we actually want
+an \textit{artificial agent} to resemble ourselves and how far it should act
+`artificially socially' toward humans, and what happens as soon as it is
+considered a \textit{moral agent} \cite{sullins_when_2006}. Using
+\textit{socially interactive robots} in contexts involving elderly care or
+rehabilitation for disabled / handicapped persons, autistic children is also a
+controversially discussed topic \cite{robins_robots_2005}.
+
+when slowly increasing its human-likeness, the more affection
+
+The idea of the hypothesis follows Freud's description of the uncanny (a
+translation from the German word `unheimlich') \hl{ref Freud, The Uncanny}: "it
+derives its terror not from something externally alien or unknown but - on the
+contrary - from something strangely familiar which defeats our efforts to
+separate ourselves from it". \cite{hegel_understanding_2008}
+
+	Also: Simulation Theory
+
+"The anthropomorphic design of human-machine interfaces is inevitable. The
+important criterion is to seek a balance between people's expectations and the
+machines capabilities." \cite{duffy_anthropomorphism_2002}
+
+"What is the ideal set of human features that could supplement and augment a
+robots  social functionality?" \cite{duffy_anthropomorphism_2002}
+
+Though, the 'anthropomorphic design principle" seems beneficial, it also raises
+ethical issues and has been reviewed critically in terms of acceptance. How far
+do we want a robot to resemble a human or act like a human?
+
+Findings that support anthropomorphic form in robots because they found people
+respond with anthropomorphizing these kind of robots, and in turn act more
+social toward them or accept them more easily:
+
+	\hl{empathy --> check Iolanda's paper}
+
+\subsection*{Anthropomorphism in Robotics and Human-Robot Interaction}
 \label{sec:anthropomorphism-robotics}
@@
 
-\subsection{Anthropomorphism as a multi-layered phenomenon}
-\label{sec:3.4}
+Anthropomorphism represents just one of many examples of induction whereby
+"people reason about an unknown stimulus based on a better-known representation
+of a related stimulus" \cite{epley_when_2008}, in this case reasoning about a
+non-human agent based on representation of the self or other humans. This
+supports the usual role we assign to anthropomorphism in robotics: the
+anthropomorphic design of a robot encourages people to reason about this
+unfamiliar system \emph{as if} it was a human. To increase this tendency, robots
+are designed with anthropomorphic forms (human-like or lifelike forms, in the
+broader sense), or are able to display and use human-social cues when
+interacting with humans.\\
+
+Literature on anthropomorphism (the social phenomenon) in robotics as well as on
+anthropomorphic design of robots is quite diverse and one strives hard to
+extract a coherent conclusion. One reason for this might be that robotics is a
+multi-disciplinary field and researchers from very different domains might
+integrate diverse or even contradictory understandings, or simply refer to
+different things. However, despite the fact that there is no commonly accepted
+definition, and also the terminology is not clear, the terms
+\textit{anthropomorphism}, \textit{anthropomorphic} or \textit{human-like} are
+often used as if their meanings were clear and agreed upon
+\cite{persson_anthropomorphism_2000}. Duffy \cite{duffy_anthropomorphism_2002}
+argues that these terms might even be misused (in accordance with
+\cite{epley_when_2008}). For instance, some researchers refer to \textit{"the
+robot's level of anthropomorphism"} \cite{bartneck_is_2007}, whereas others
+argue that the system or artifact itself does not "contain anthropomorphism"
+\textit{per se} but only gives rise to the process of anthropomorphizing in a
+given user and situation. Consequently, Persson \textit{et al.} conclude that
+anthropomorphism emerges in the \textit{interaction} between the technology and
+the user \cite{persson_anthropomorphism_2000}.  \hl{[In this article, we accept
+this latter viewpoint and would like to clearly distinguish between the term
+\textit{anthropomorphism} as a social phenomenon and \textit{anthropomorphic} as
+a specific design. This however, is not yet a definition of what exactly both
+terms refer to. Still, we acknowledge that both terms can refer to different
+levels or types; which we will outline later.]}
+
+Paradoxically, human's tendency to anthropomorphize non-human agents (such as
+robots) is commonly observed but at the same time it is rather poorly understood
+\cite{epley_seeing_2007}. There might be several reasons. First, probably
+because the phenomenon itself has been found to be very complex though sometimes
+subtle and as such hard to study. Second, the rather poor (or controversial)
+understanding, might also be due to the limited reliability of some findings (or
+interpretations) from experiments investigating anthropomorphism. Most of the
+experiments that investigate anthropomorphism in robotics are conducted in
+controlled lab-settings during short-term human-robot interactions. This
+experimental setting can be critical when studying a social phenomenon like
+anthropomorphism and possibly lead to over-interpretations. Some studies (e.g.
+exploring characteristics of the "uncanny valley") also seem to contrast two or
+more different anthropomorphic or mechanical systems that might not be
+appropriate for comparison given the complex context. Others might also use
+empirical methods inappropriate for the given research question which leads to
+inaccurate results. \hl{say more}
+
+To sum it up, while anthropomorphism in robotics is a commonly discussed and
+studied trait of human-robot interaction, we think it paradoxically lacks a
+formal ground and unified understanding. The understanding of anthropomorphism
+in robotics seems to not take into account the wide range of phenomena that it
+encompasses. The traditional understanding of anthropomorphism in robotics to
+date considers two main factors that account for the social phenomenon: the
+characteristics of \textbf{1) the robot's design} (degree of human-likeness) and
+the psychological determinants in \textbf{2) the human user} (see
+\cite{epley_seeing_2007}). It has been shown that both these factors can
+facilitate or hinder anthropomorphism. We propose to go beyond this traditional
+perception of anthropomorphism as a static feature of HRI: Based on Persson
+\textit{et al.}'s~\cite{persson_anthropomorphism_2000} argumentation that
+anthropomorphism is a multi-layered phenomenon which arises in different levels,
+we suggest to understand anthropomorphism as a \emph{dynamic},
+\emph{context-dependent} process. To this end, we apply Persson \textit{et
+al.}'s six levels on anthropomorphism to HRI and introduce three
+\emph{interaction phases}. These interaction phases of anthropomorphism reflect
+also the results of a long-term study that we conducted in a real human
+environment and provide an account of the so-called \textit{novelty effect}. We
+also draw attention to two new determinants of anthropomorphism, namely, the
+context of use and the fact of getting used to a system over time. We propose to
+add these two aspects as a third factor, the characteristics of \textbf{3) the
+interaction} (time and space), to the previous two factors of anthropomorphism
+(robot and user).
+
+%% -> Commented out the overview as it does not match what we actually present... maybe we need a new one?
+% We would further like to review and discuss research on anthropomorphism in
+% robotics and human-like design of robots. We first provide a comprehensive
+% understanding of the phenomenon drawing on theories from developmental
+% psychology and cognitive sciences. We then present the trends of different
+% kinds of anthropomorphic forms in robots and discuss their role in social
+% robotics. The article integrates related work from human-robot interaction
+% studies, reporting on findings from experiments with human subjects
+% interacting with and evaluating various types of systems. We try to give a
+% coherent view on the topic, outline similarities and antithetic findings, and
+% contribute to a better understanding of anthropomorphism in robotics, and the
+% acceptance of human-like characteristics in robots. We also aim to
+% constructively discuss anthropomorphic design of personal and socially
+% interactive robots.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+%
+%
+%				PART 2: OUR IDEAS -- A DYNAMIC PHENOMENON
+%
+%
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+% SEVERIN & JULIA: there will be 2-3 subsections in which we present our ideas:
+% 	1) anthropomorphism is a multi-factor phenomenon (the figure with the several factors)
+%	2) anthropomorphism is dynamic (the dynamic curve model)
+%
+%
+
+\vspace{2cm}
+\section{Anthropomorphism as a multi-factor phenomenon that evolves over time}
+\label{sec:our-ideas}
+
+\hl{bridge sentence}
+
+\subsection*{Multiple factors of anthropomorphism}
+\label{sec:multi-factors}
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-%
-%
-%				DOES ANTHROPOMORPHISM MAKE ROBOTS MORE SOCIAL?
-%
-%
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Does anthropomorphism make robots more social?}
-\label{sec:more_social}
-
-In general, it is suggested that increasing human-likeness of a robot	 will
-lead to more perceived \textit{affinity} from the human side
-\cite{mori_uncanny_1970}. This theoretical concept is also supported by
-psychological determinants of perceiving human-likeness in something non-human:
-\textit{"the more similar in appearance, the more people are likely to use
-themselves as a source of induction and anthropomorphize these nonhuman agents"}
-\cite{epley_seeing_2007}. Further, empirical studies have shown that robots with
-human-like forms can enhance social responses from humans which in turn can have
-a positive impact on acceptance
-\cite{venkatesh_theoretical_2000,duffy_anthropomorphism_2003,goetz_cooperation_2002}.
-People responded more positively to an artifact that displayed human-like
-behavioral characteristics (emotions, facial expression) in contrast to a purely
-functional design
-\cite{eyssel_anthropomorphic_2010,krach_can_2008,reeves_media_1996,riek_how_2009}.
-Overall, these results suggest that human-like features in robots enhance
-anthropomorphism, and in turn create a social view toward the robot.
-
-Well known from the HRI community, we may mention the other side of human-like
-behaviours and appearance: a not yet very well defined thin line separates
-acceptable human-like forms in robots from creepy artificial \textit{almost}
-human-like appearing robots. The underlying theory for this viewpoint is stated
-as the \textit{Uncanny Valley} \cite{mori_uncanny_1970} which suggests that
-artificial human-like forms are only acceptable up to a certain degree but lead
-to reluctance if they fail in trying to attain human-likeness \hl{cross-ref to
-later and figure}.
-
-The theory (Figure~\ref{fig:uncanny_valley}) hypothesizes that a person's
-response to a human-like robot would abruptly shift from empathy to revulsion as
-it approached, but failed to attain, a lifelike appearance
-\cite{mori_uncanny_1970}. Starting with low degrees of anthropomorphic cues in a
-robot, humans seem to readily accept and prefer them compared to purely
-mechanical robots. In general, one can say that up to a certain (yet not very
-well defined) degree, the more human-like the robot, the more affection it can
-engender through familiar communication references.
-
-\begin{figure}\centering
-% Use the relevant command to insert your figure file.
-% For example, with the graphicx package use
-  \includegraphics[scale=0.6]{uncanny-valley.jpg}
-% figure caption is below the figure
- \caption{Mashiro Mori, illustration of the \textit{Uncanny Valley}, originally
- from 1970; picture from a manuscript version of \cite{mori_uncanny_2012}}
-
- \label{fig:uncanny_valley}       % Give a unique label
- \end{figure}
-
-Another sensitive aspect is that with robots that closely resemble humans,
-ethical issues arise. For instance, we need to consider how far we actually want
-an \textit{artificial agent} to resemble ourselves and how far it should act
-`artificially socially' toward humans, and what happens as soon as it is
-considered a \textit{moral agent} \cite{sullins_when_2006}. Using
-\textit{socially interactive robots} in contexts involving elderly care or
-rehabilitation for disabled / handicapped persons, autistic children is also a
-controversially discussed topic \cite{robins_robots_2005}.
-
-when slowly increasing its human-likeness, the more affection
-
-The idea of the hypothesis follows Freud's description of the uncanny (a
-translation from the German word `unheimlich') \hl{ref Freud, The Uncanny}: "it
-derives its terror not from something externally alien or unknown but - on the
-contrary - from something strangely familiar which defeats our efforts to
-separate ourselves from it". \cite{hegel_understanding_2008}
-
-	Also: Simulation Theory
-
-"The anthropomorphic design of human-machine interfaces is inevitable. The
-important criterion is to seek a balance between people's expectations and the
-machines capabilities." \cite{duffy_anthropomorphism_2002}
-
-"What is the ideal set of human features that could supplement and augment a
-robots  social functionality?" \cite{duffy_anthropomorphism_2002}
-
-Though, the 'anthropomorphic design principle" seems beneficial, it also raises
-ethical issues and has been reviewed critically in terms of acceptance. How far
-do we want a robot to resemble a human or act like a human?
-
-Findings that support anthropomorphic form in robots because they found people
-respond with anthropomorphizing these kind of robots, and in turn act more
-social toward them or accept them more easily:
-
-	\hl{empathy --> check Iolanda's paper}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-%
-%
-%				DYNAMICS OF ANTHROPOMORPHISM
-%
-%
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{A Model of the Dynamics of Anthropomorphism}
-\label{sec:dynamics_model}
-
-\subsection{Why is anthropomorphism likely to change over time?}
-\label{sec:whychanges}
+\subsection*{A Model of the Dynamics of Anthropomorphism}
+\label{sec:dynamics-model}
+
+\paragraph{Why is anthropomorphism likely to change over time?}
+\hl{maybe we need to move this paragraph to PART 3}
 
@@
 subsection}
-
-\subsection{Model of anthropomorphism over time}
-\label{sec:modelintro}
 
@@
 
-\subsection{Three phases}
+\subsection*{Three phases}
 \label{sec:phases}
@@
 
-\subsection{Initialization Phase}
+\subsection*{Initialization Phase}
 \label{sec:initialization}
@@
 
-\subsection{Familiarization Phase}
+\subsection*{Familiarization Phase}
 \label{sec:familiarization}
@@
 
-\subsection{Stabilization Phase}
+\subsection*{Stabilization Phase}
 \label{sec:stabilization}
@@
 %
-%				DISCUSSION
+%		PART 3: EXPLANATIONS -- COGNITIVE CORRELATES, NEUROSCIENCE VIEW
 %
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Discussion}
-\label{sec:discussion}
-
-The model of anthropomorphism we propose is still a work in progress. In
-particular, its implications regarding the design of (social) robots and
-human-robot interaction are still to be refined.
+%
+% CLAIRE & SEVERIN:
+%
+%
+
+\vspace{2cm}
+\section{Cognitive Correlates and Neuroscience Perspective}
+\label{sec:cognition-neuroscience}
 
@@
 
-\section{Cognitive Interpretations}
-\label{sec:cognitivemodel}
+\subsection*{Cognitive Interpretations}
+\label{sec:cognitive-model}
 
@@
 
-\subsection{Explanations for anthropomorphism}
-
-Anthropomorphism represents just one of many examples of induction whereby
-``people reason about an unknown stimulus based on a better-known representation
-of a related stimulus"~\cite{epley_when_2008}, in this case reasoning about a
-non-human agent based on representation of the self or other humans.
-
-According to Lee \etal~\cite{lee_human_2005}, there are two main perspectives in
-explaining people's tendency to anthropomorphize. First one explains
-anthropomorphism from the design of the artifact. It assumes that humans
-directly respond to life-like or social cues that an object or system emits,
-without thoughtful mental processing, by simply applying stereotypes and
-heuristics to it. In fact, from early childhood on, humans are inherently
-well-trained to perceive life \cite{epley_seeing_2007}. Schmitz
-\cite{schmitz_concepts_2011} describes that within the visual scope of design,
-the outer appearance can have an important impact on the overall perception of
-an object. The basic assumption here is that if an artifact appears much like a
-human, it is likely to be treated similar to a human. If this explanation of
-anthropomorphism is correct, people may respond automatically to social cues
-emitted by a robot, and apply human-human social schemas and norms to these
-interactions.
-
-The second perspective applies a human-centered, cognitive viewpoint where
-anthropomorphism is described through people's specific mental model they
-construct about how an artifact works the way it does.  We then
-anthropomorphize because it allows us to explain things we do not understand in
-terms that we do understand, and what we understand best is ourselves as human
-beings. This is consistent with the \emph{familiarity
-thesis}~\cite{hegel_understanding_2008} which claims that we understand the
-world based upon a mental model of the world that we are most familiar with.
-Consequently, people tend to thoughtfully develop a mental model of agents in
-their environment and make inferences about it based on what is familiar to
-them -- humans and human behavior, for instance.  This point of view implicitly
-builds on a person's ability to attribute mental states to oneself and others
-(\ie the availability of a \emph{theory of mind}~\cite{premack1978does} -- the
-link between a tendency to anthropomorphize and the engagement in the
-attribution of mental states to other humans has been recently demonstrated at
-the brain level in~\cite{cullen2013individual}). A theory of mind for other
-agents enables us to attribute intentionality to those agents
-\cite{leslie_pretense_1987,admoni_multi-category_2012}. Previous research
-examined the validity of the mental model concept with various kinds of robots
-\cite{schmitz_concepts_2011,kiesler_mental_2002}. Findings suggest that people
-tend to hold richer mental models of anthropomorphic robots in contrast to
-mechanic ones \cite{kiesler_mental_2002}.
-
-\subsection{Cognitive Processes and Phases}
+\subsection*{Cognitive Processes and Phases}
 
@@
 
-\subsection{Relation to the model of anthropomorphism}
+\subsection*{Relation to the model of anthropomorphism}
 
@@
 
-\subsection{Effect of Context of Use and Purpose of the Robot}
-\label{sec:8.1}
-Frederic: role of uselessness
-
 \begin{itemize}
-    \item[\textbf{Hypothesis 1}] A person's tendency to anthropomorphize a robot
+    \item \textbf{Hypothesis 1} A person's tendency to anthropomorphize a robot
         is impacted by the context of use and purpose of the robot. A social
@@
         \textit{(context and purpose of the robot)}
-
+	\item \textbf{Hypothesis 2} A person's tendency to anthropomorphize a robot decreases over time and with growing experience the person has with the robot.
+\textit{(familiarize oneself with the robot)}
 \end{itemize}
 
-\subsection{Impact of the behavioral complexity of robots}
+\subsection*{Impact of the behavioral complexity of robots}
 
@@
 
-\subsection{Segmentation of interaction phases}
+\subsection*{Segmentation of interaction phases}
 
@@
 
-\subsection{Behavioral cues of anthropomorphism}
+\subsection*{Behavioral cues of anthropomorphism}
 \label{sec:behavioralcues}
@@
 
-\subsection{Effect of Time and Familiarization}
-\label{sec:8.2}
+\subsection*{Effect of Time and Familiarization}
 
@@
 \begin{itemize}
-	\item[\textbf{Hypothesis 2}] A person's tendency to anthropomorphize a robot decreases over time and with growing experience the person has with the robot.
+	\item \textbf{Hypothesis 2} A person's tendency to anthropomorphize a robot decreases over time and with growing experience the person has with the robot.
 \textit{(familiarize oneself with the robot)}
@@
 
-\subsection{Personal characteristic effects in anthropomorphizing}
-\label{sec:8.3}
-
-\subsection{Role of disruptive behaviors}
+\subsection*{Role of disruptive behaviors}
 \label{sec:disruptive}
@@
 %
-%				CONCLUSION
+%				DISCUSSION + FUTURE WORK
 %
@@
 
+% JULIA & SEVERIN: how to measure / quantify anthropomorphism ...
+% CLAIRE: FMRI study idea
+
+\vspace{2cm}
 \section{Discussion}
+\label{sec:discussion}
+
+The model of anthropomorphism we propose is still a work in progress. In
+particular, its implications regarding the design of (social) robots and
+human-robot interaction are still to be refined.
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+%
+%
+%				CONCLUSIONS
+%
+%
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% JULIA & SEVERIN
+
+\vspace{2cm}
 \section{Conclusion}
@@
 model of anthropomorphism that accounts for these three factors and also
-explicits the dynamics of anthromorphism. We introduce the concepts of
+explicits the dynamics of anthropomorphism. We introduce the concepts of
 \emph{initial} and \emph{stabilized levels of anthropomorphism} as compound
@@
 
-\section*{Acknowledgements}
-
-We would like to acknowledge here the fruitful discussions with A Jung Moon and
+\vspace{2cm}
+\section*{Acknowledgments}
+
+We would like to acknowledge the fruitful discussions with A Jung Moon and
 Aude Billard.
@@
 
-\section{Bibliography}
+\vspace{2cm}
+\section*{Bibliography}
 

### 2014-03-12 paper.tex
Fixed Frontiers template issues
use begin{abstract}...end{abstract} instead of abstract{...}

While here, restore section numbering.

@@
 
-\abstract{While anthropomorphism in robotics is a commonly discussed trait of
+\begin{abstract}
+
+While anthropomorphism in robotics is a commonly discussed trait of
 HRI, it paradoxically lacks formal grounds. This article
@@
 and we discuss cognitive interpretations that follow.
-}
-
-%\keywords{Anthropomorphism, Design, Human-Robot Interaction, Social Issues in Robotics, Acceptance of Robots}
+
+\tiny
+ \keyFont{ \section{Keywords:} Anthropomorphism, Design, Human-Robot Interaction, Social Issues in Robotics, Acceptance of Robots}
+
+\end{abstract}
 
@@
 
-\subsection*{Anthropomorphism as a Social Phenomenon}
+\subsection{Anthropomorphism as a Social Phenomenon}
 \label{sec:social-phenomenon}
@@
 
-\subsection*{Anthropomorphic Design Principle}
+\subsection{Anthropomorphic Design Principle}
 \label{sec:anthropomorphic-design}
@@
 
-\subsection*{Anthropomorphism in Robotics and Human-Robot Interaction}
+\subsection{Anthropomorphism in Robotics and Human-Robot Interaction}
 \label{sec:anthropomorphism-robotics}
@@
 
-\subsection*{Multiple factors of anthropomorphism}
+\subsection{Multiple factors of anthropomorphism}
 \label{sec:multi-factors}
@@
 
-\subsection*{A Model of the Dynamics of Anthropomorphism}
+\subsection{A Model of the Dynamics of Anthropomorphism}
 \label{sec:dynamics-model}
@@
 
-\subsection*{Three phases}
+\subsection{Three phases}
 \label{sec:phases}
@@
 
-\subsection*{Initialization Phase}
+\subsection{Initialization Phase}
 \label{sec:initialization}
@@
 
-\subsection*{Familiarization Phase}
+\subsection{Familiarization Phase}
 \label{sec:familiarization}
@@
 
-\subsection*{Stabilization Phase}
+\subsection{Stabilization Phase}
 \label{sec:stabilization}
@@
 
-\subsection*{Cognitive Interpretations}
+\subsection{Cognitive Interpretations}
 \label{sec:cognitive-model}
@@
 
-\subsection*{Cognitive Processes and Phases}
+\subsection{Cognitive Processes and Phases}
 
@@
 
-\subsection*{Relation to the model of anthropomorphism}
+\subsection{Relation to the model of anthropomorphism}
 
@@
 
-\subsection*{Impact of the behavioral complexity of robots}
+\subsection{Impact of the behavioral complexity of robots}
 
@@
 
-\subsection*{Segmentation of interaction phases}
+\subsection{Segmentation of interaction phases}
 
@@
 
-\subsection*{Behavioral cues of anthropomorphism}
+\subsection{Behavioral cues of anthropomorphism}
 \label{sec:behavioralcues}
@@
 
-\subsection*{Effect of Time and Familiarization}
+\subsection{Effect of Time and Familiarization}
 
@@
 
-\subsection*{Role of disruptive behaviors}
+\subsection{Role of disruptive behaviors}
 \label{sec:disruptive}
@@
 \vspace{2cm}
-\section*{Acknowledgments}
+\section{Acknowledgments}
 
@@
 \vspace{2cm}
-\section*{Bibliography}
+\section{Bibliography}
 

### 2014-03-12 paper.tex
template issues
mainly intro and overview modifications ... to start with something

@@
+%\documentclass{frontiersENG} % for Engineering articles
 \documentclass{frontiersSCNS} % for Science articles
+%\documentclass{frontiersMED} % for Medicine articles
+%\documentclass{frontiersFPHY} % for Physics articles
 
@@
 \def\firstAuthorLast{Fink {et~al.}} %use et al only if is more than 1 author
-\def\Authors{Julia Fink\,$^{*}$, S\'{e}verin Lemaignan\, Claire Braboszcz and Pierre Dillenbourg}
+\def\Authors{Julia Fink\,$^{*}$, S\'{e}verin Lemaignan, Claire Braboszcz and Pierre Dillenbourg}
 \def\Address{Computer-Human Interaction in Learning and Instruction (CHILI) \\ Ecole Polytechnique F\'{e}d\'{e}rale de Lausanne (EPFL) \\ CH-1015 Lausanne, Switzerland}
@@
 anthropomorphism that analyzes the phenomenon along three interaction phases,
-and we discuss cognitive interpretations that follow.
+and we discuss cognitive interpretations that follow. \hl{(Julia: probably the abstract needs to be refined once we finished writing the paper)}
 
@@
 
-\vspace{2cm}
 \section{Introduction and Overview}
@@
 
-%DEFINITION OF ANTHROPOMORPHISM
-
-The essence of anthropomorphism is the perception of human-like characteristics
-in either real or imagined non-human agents. According to Epley \textit{et al.}
-\cite{epley_when_2008}, these human-like characteristics may include physical
-appearance, emotional states perceived to be uniquely human, or inner mental
-states and motivations. Real or imagined non-human agents can be "anything that
-acts -- or is believed to act -- with apparent independence, including non-human
-animals, natural forces, religious agents, technological gadgets, or mechanical
-devices". Such anthropomorphic representations are important determinants of how
-a person perceives and in turn behaves towards these agents, or how a person may
-behave in light of these agents \cite{epley_when_2008}.
-
-%ANTHROPOMORPHISM AS SUBJECT IN HCI AND HRI
-
-Phenomenons related to anthropomorphism -- along with questions such as "how
-much human do we perceive in the non-human" or "how human-like do we treat
-non-human artifacts" (and why?) -- have received remarkable attention in the
-domains of Human-Computer Interaction (HCI) and Human-Robot Interaction (HRI):
-the study of humans interacting with an artificial system / machine. Following
-the \textit{Media Equation}, it has been described that people mindlessly react
-socially to computers \cite{reeves_media_1996} and may even attribute human
-(social) characteristics to their artificial counterpart. The phenomenon has
-also been observed with virtual characters \hl{cite [50, 100] in rosenthal-von
-der P{\"u}tten (2013)}, and more recent studies investigated how far people
-ascribe personality or intentions to artificial embodied agents or whether they
-show empathetic behavior toward robots
-\cite{rosenthal-vonderputten_experimental_2013}. The common base for this
-research is the assumption that humans perceive or react to a non-human agent or
-artifact as somewhat similar to a human.
-
-In this article we will use the term \emph{anthropomorphic effect} to denote
-observable correlates of anthropomorphism. With these we include, amongst
-others, verbal utterances (such as direct speech or the use of pronouns
-"he/she"), (social) gestures (such as a hug, waving, deictic gestures) or
-\hl{anticipation of certain actions of an agent [what??]}.
-
-%CONTROVERSAL UNDERSTANDINGS OF ANTHROPOMORPHISM
-
-However, not everything colloquially labeled as \emph{anthropomorphism} really
-is anthropomorphism. Different, even partially conflicting, understandings of
-anthropomorphism exist across and within disciplines
-\cite{duffy_anthropomorphism_2002}. Epley \textit{et al.} \cite{epley_when_2008}
-try to narrow down and clarify the understanding of anthropomorphism in
-psychology by explaining what it is \textit{not}. The authors list four things
-that anthropomorphism does not include: First, anthropomorphism does not include
-behavioral descriptions of observable actions. Anthropomorphism requires going
-beyond what is directly observable. Second, anthropomorphism does not merely
-entail animism, as animate life is not a uniquely human-like characteristic.
-Third, anthropomorphism does not include any requirement of reasoned or
-reflective endorsement of an inference (\hl{the strength of anthropomorphic
-inferences can vary} \footnote{for further explanation the reader may refer to
-the original work \cite{epley_when_2008}.}).	Finally, anthropomorphism is not
-necessarily inaccurate. A psychological theory should take this (in)accuracy in
-anthropomorphism into account and predict variability in the tendency to
-perceive human-like traits in non-human agents.  In conclusion, it has been
-noted that anthropomorphism is a very complex phenomenon - in itself, its
-understanding, and when studying it. A common formal ground is missing; however,
-it is important to be clear about what exactly we mean when using the term
-anthropomorphism.
+The essence of anthropomorphism is the perception of human-like characteristics in either real or imagined non-human agents.
+In human-robot interaction (HRI), anthropomorphism is a commonly observed phenomenon: people tend to ascribe human-like characteristics to robots, and they are willing to treat and react to robots as if they were human-social counterparts.
+The HRI and social robotics literature is full of various kinds of studies showing how humans readily interact in a social fashion with robots -- despite the fact that robots are not humans.
+In our own work on human-robot interaction analysis, we also observed anthropomorphism.
+However, we found qualitative differences and dynamics in how participants anthropomorphized and socially related to the robots used in our studies, which were mostly conducted in natural settings with normal people.
+More concretely, we found that anthropomorphism was not only based on how much the robot resembles a human (anthropomorphic design) but that it was determined by multiple factors, including the individual characteristics of the human user, and the context of use.
+We also found that anthropomorphism changed over time with growing experience of the user with the system.
+By trying to understand these variances and dynamics in anthropomorphism, we reviewed related work from the HRI domain and social robotics.
+Despite the fact that there is a vast amount of literature on anthropomorphism in HRI, we did not come across findings that were similar to ours and described how anthropomorphism would evolve over time.
+Instead, we found ourselves confronted with diverse and partially contradictory understandings of anthropomorphism.
+We also had the impression that the reported data were sometimes over-interpreted or obtained in settings and in a way that we believe do not give enough consideration to the complex nature of anthropomorphism.\footnote{As anthropomorphism emerges from an interaction between a human and a non-human agent, we believe that showing pictures of different kinds of robots and then using questionnaires to measure anthropomorphism is somehow limited.
+In the discussion section \ref{sec:discussion} we discuss what tools and measurements could be used to study anthropomorphism and its dynamics in interaction studies in real-world environments.} However, we found support for the observed variances and dynamics in anthropomorphism in literature from social psychology, cognitive science, and neuroscience.
+As these domains are also relevant in for HRI, we believe it is valid to use theories from these domains for interpreting our results and to report this.
+
+In this article, we would like to share our somehow critical but constructive considerations on anthropomorphism in robotics.
+Thereby, we contribute to a refined understanding of this complex phenomenon related to interactions between humans and robots.
+In accordance with theories from other domains, we propose that anthropomorphism is determined and affected by multiple factors.
+Based on this multi-factor understanding, and the findings from our work, we suggest an initial model that we call "dynamics of anthropomorphism" that serves to describe how anthropomorphism evolves over time.
+We then present a cognitive and neuroscience perspective on anthropomorphism to consolidate this model.
+Finally, we discuss alternative ways how anthropomorphism in HRI can be studied and measured, as this is an important questions.
 
@@
 
-\vspace{2cm}
 \section{Anthropomorphism}
@@
 
-\hl{bridge sentence}
+Anthropomorphism is an interesting social phenomenon because it tells us something about the relation between the human who anthropomorphizes, and the non-human agent that is anthropomorphized.
+Though commonly observed, it appears controversial at the same time that humans tend to perceive human-like physical appearance (\eg faces), emotional states, or inner mental states and motivations in non-human agents\footnote{According to \cite{epley_when_2008}, a non-human agent can be anything that acts -- or is believed to act -- with apparent independence.}, such as animals, natural forces, religious agents, technological gadgets, or mechanical devices \citep{epley_when_2008}.
+
+Anthropomorphism and related questions such as "how much human do we perceive in the non-human" or "how human-like do we treat and interact with non-human artifacts" (and why?) have received remarkable attention across several domains.\footnote{Especially in human-pet relations and human-machine relations, anthropomorphism is frequently studied.}
+
+In this section we will first clarify the terminology used.
+We present anthropomorphism as a social phenomenon and propose to use another term, namely anthropomorphic form, to refer to the human-inspired design of artifacts.
 
@@
 \label{sec:anthropomorphism-robotics}
+
+Following research in human-computer interaction (HCI) the \textit{Media Equation} \citep{reeves_media_1996} describes that people mindlessly react socially to their computer and may even attribute human (social) characteristics to it.
+The phenomenon has also been observed with virtual characters, and artificial embodied agents, such as robots.
+For instance, recent studies found that people tend to ascribe personality and intentions to robots \hl(REFS) and that they show empathetic behavior toward robots \cite{rosenthal-vonderputten_experimental_2013}.
+To subsume it, there is a growing body of literature that describes anthropomorphism in HCI and HRI.
+
+However, not everything colloquially labeled as \emph{anthropomorphism} really is anthropomorphism.
+Different, even partially conflicting understandings of anthropomorphism exist across and within disciplines \cite{duffy_anthropomorphism_2002}.
+\cite{epley_when_2008} try to narrow down and clarify the understanding of anthropomorphism in psychology by explaining what it is \textit{not}.
+The authors list four things
+that anthropomorphism does not include: First, anthropomorphism does not include
+behavioral descriptions of observable actions. Anthropomorphism requires going
+beyond what is directly observable. Second, anthropomorphism does not merely
+entail animism, as animate life is not a uniquely human-like characteristic.
+Third, anthropomorphism does not include any requirement of reasoned or
+reflective endorsement of an inference (\hl{the strength of anthropomorphic
+inferences can vary} \footnote{for further explanation the reader may refer to
+the original work \cite{epley_when_2008}.}).	Finally, anthropomorphism is not
+necessarily inaccurate. A psychological theory should take this (in)accuracy in
+anthropomorphism into account and predict variability in the tendency to
+perceive human-like traits in non-human agents.  In conclusion, it has been
+noted that anthropomorphism is a very complex phenomenon - in itself, its
+understanding, and when studying it. A common formal ground is missing; however,
+it is important to be clear about what exactly we mean when using the term
+anthropomorphism.
+
+How a person relates to an agent further determines how she perceives and in turn behaves towards the agent, or how she may behave in light of this agent \cite{epley_when_2008}.
 
@@
 
-\vspace{2cm}
 \section{Anthropomorphism as a multi-factor phenomenon that evolves over time}
@@
 \label{sec:multi-factors}
+
+In this article we will use the term \emph{anthropomorphic effect} to denote
+observable correlates of anthropomorphism. With these we include, amongst
+others, verbal utterances (such as direct speech or the use of pronouns
+"he/she"), (social) gestures (such as a hug, waving, deictic gestures) or
+\hl{anticipation of certain actions of an agent [what??]}.
 
@@
 
-\vspace{2cm}
 \section{Cognitive Correlates and Neuroscience Perspective}
@@
 
-\vspace{2cm}
 \section{Discussion}
@@
 
-\vspace{2cm}
 \section{Conclusion}
@@
 
-\vspace{2cm}
 \section{Acknowledgments}

### 2014-03-13 paper.tex
anthropomorphism definitions etc.

--- 2014-03-12 paper.tex
@@
 
-%DEFINITION OF ANTHROPOMORPHISM
-
-The essence of anthropomorphism is the perception of human-like characteristics
-in either real or imagined non-human agents. According to Epley \textit{et al.}
-\cite{epley_when_2008}, these human-like characteristics may include physical
-appearance, emotional states perceived to be uniquely human, or inner mental
-states and motivations. Real or imagined non-human agents can be "anything that
-acts -- or is believed to act -- with apparent independence, including non-human
-animals, natural forces, religious agents, technological gadgets, or mechanical
-devices". Such anthropomorphic representations are important determinants of how
-a person perceives and in turn behaves towards these agents, or how a person may
-behave in light of these agents \cite{epley_when_2008}.
-
-%ANTHROPOMORPHISM AS SUBJECT IN HCI AND HRI
-
-Phenomenons related to anthropomorphism -- along with questions such as "how
-much human do we perceive in the non-human" or "how human-like do we treat
-non-human artifacts" (and why?) -- have received remarkable attention in the
-domains of Human-Computer Interaction (HCI) and Human-Robot Interaction (HRI):
-the study of humans interacting with an artificial system / machine. Following
-the \textit{Media Equation}, it has been described that people mindlessly react
-socially to computers \cite{reeves_media_1996} and may even attribute human
-(social) characteristics to their artificial counterpart. The phenomenon has
-also been observed with virtual characters \hl{cite [50, 100] in rosenthal-von
-der P{\"u}tten (2013)}, and more recent studies investigated how far people
-ascribe personality or intentions to artificial embodied agents or whether they
-show empathetic behavior toward robots
-\cite{rosenthal-vonderputten_experimental_2013}. The common base for this
-research is the assumption that humans perceive or react to a non-human agent or
-artifact as somewhat similar to a human.
-
-In this article we will use the term \emph{anthropomorphic effect} to denote
-observable correlates of anthropomorphism. With these we include, amongst
-others, verbal utterances (such as direct speech or the use of pronouns
-"he/she"), (social) gestures (such as a hug, waving, deictic gestures) or
-\hl{anticipation of certain actions of an agent [what??]}.
-
-%CONTROVERSAL UNDERSTANDINGS OF ANTHROPOMORPHISM
-
-However, not everything colloquially labeled as \emph{anthropomorphism} really
-is anthropomorphism. Different, even partially conflicting, understandings of
-anthropomorphism exist across and within disciplines
-\cite{duffy_anthropomorphism_2002}. Epley \textit{et al.} \cite{epley_when_2008}
-try to narrow down and clarify the understanding of anthropomorphism in
-psychology by explaining what it is \textit{not}. The authors list four things
-that anthropomorphism does not include: First, anthropomorphism does not include
-behavioral descriptions of observable actions. Anthropomorphism requires going
-beyond what is directly observable. Second, anthropomorphism does not merely
-entail animism, as animate life is not a uniquely human-like characteristic.
-Third, anthropomorphism does not include any requirement of reasoned or
-reflective endorsement of an inference (\hl{the strength of anthropomorphic
-inferences can vary} \footnote{for further explanation the reader may refer to
-the original work \cite{epley_when_2008}.}).	Finally, anthropomorphism is not
-necessarily inaccurate. A psychological theory should take this (in)accuracy in
-anthropomorphism into account and predict variability in the tendency to
-perceive human-like traits in non-human agents.  In conclusion, it has been
-noted that anthropomorphism is a very complex phenomenon - in itself, its
-understanding, and when studying it. A common formal ground is missing; however,
-it is important to be clear about what exactly we mean when using the term
-anthropomorphism.
+The essence of anthropomorphism is the perception of human-like characteristics in either real or imagined non-human agents.
+In Human-Robot Interaction (HRI), anthropomorphism is a commonly observed phenomenon: people tend to ascribe human-like characteristics to robots, and they are willing to treat and react to robots as if they were human-social counterparts.
+The HRI and social robotics literature is full of various kinds of studies showing how humans readily interact in a social fashion with robots -- despite the fact that robots are not humans.
+In our own studies on HRI analysis in real-world settings, we also observed anthropomorphism.
+However, we found qualitative differences and dynamics over time in how participants anthropomorphized and related to the robots used in our studies.
+More concretely, we found that anthropomorphism was not only based on how much the robot resembles a human (anthropomorphic design) but that it was determined by multiple factors, including individual characteristics of the human user, and the context of use, for instance.
+We also found that anthropomorphism changed over time with growing experience of the user with the system.
+By trying to understand these variances and dynamics in anthropomorphism, we reviewed related work from the HRI domain and social robotics.
+Despite the fact that there is a vast amount of literature on anthropomorphism in HRI, we were surprised to find that other studies do not describe similar variances or dynamics.
+Instead, we came across diverse and partially conflicting understandings of anthropomorphism.
+We also had the impression that the reported data were sometimes over-interpreted (probably due to the confusion of what exactly anthropomorphism is) or obtained in settings and assessed in ways that we believe do not give enough consideration to the complex nature of anthropomorphism.\footnote{As anthropomorphism emerges from an interaction between a human and a non-human agent, we believe that showing pictures of different kinds of robots and then using questionnaires to measure anthropomorphism is somehow limited.
+In the discussion in section \ref{sec:discussion} we discuss what tools and measurements could be used to study anthropomorphism and its dynamics in interaction studies in real-world environments.} However, when reviewing literature from social psychology, cognitive science, and neuroscience, we found support for the variances and dynamics in anthropomorphism that we observed in our studies.
+As HRI integrates many disciplines, we think that it is valid to use theories from these related domains for interpreting our results and that it is relevant to report on this integration.
+
+In this article, we would like to share some critical but constructive considerations on anthropomorphism in robotics.
+Thereby, we contribute to the understanding of this complex phenomenon related to HRI.
+In accordance with theories from other related domains, we propose that anthropomorphism is determined and affected by multiple factors, and we show how this can impact the user experience and acceptance of robots in daily life environments.
+We further suggest an initial model that we call ``dynamics of anthropomorphism'' that serves to describe how anthropomorphism evolves and shapes the interaction over time.
+We illustrate our idea with empirical findings from several HRI studies that we conducted in natural environments.
+We then present a cognitive and neuroscience perspective on anthropomorphism to consolidate our considerations and the observed dynamics.
+Finally, we discuss alternative ways to measure anthropomorphism in HRI, as this is a critical aspect of gaining a better understanding of it.
 
@@
 
-\hl{bridge sentence}
+In this section we will clarify the terminology that we use as we have found conflicting understandings of the term ``anthropomorphism'' in the related literature.
+We first present anthropomorphism as a social phenomenon.
+Then we propose to use another term, namely ``anthropomorphic form'', to refer to the human-inspired design of artifacts.
+Finally, we focus on anthropomorphism in Human-Robot Interaction, as it naturally brings together (and needs to question) the usage of an anthropomorphic design of robots and its consequences for the interaction with the human user.
 
@@
 
-The term \textbf{anthropomorphism} is used in different senses throughout
-natural sciences, psychology, Human-Computer Interaction, and Human-Robot
-Interaction \cite{duffy_anthropomorphism_2003}. Originally, anthropomorphism
-comes from the Greek \textit{`anthropos'} for `man' (or `human') and
-\textit{`morphe'} for `form/structure' (or `shape'). It can be understood as
-people's tendency to think of objects as if they had human characteristics, and
-consequently, attribute / ascribe specific human characteristics to these
-non-human entities and artifacts (including animals, and robots)
-\cite{duffy_anthropomorphism_2003,schmitz_concepts_2011}. Apart from
-anthropomorphism there is also \textbf{animism}, the \textit{"attribution of
-life to the nonliving"} \hl{in Schmitz 2011, cite Piaget original text!}. Often
-synonymously used to animism is \textbf{zoomorphism}, which describes the case
-when non-lifelike objects are associated with animalistic attributes, excluding
-human-specific traits. Both anthropomorphism and zoomorphism can be embraced by
-the concept of \textbf{life-likeness}. \footnote{The inverse process would be
-called dehumanization \cite{haslam_dehumanization:_2006}, or mechanomorphism
-\cite{caporael_anthropomorphism_1986}.}
+Anthropomorphism is an interesting phenomenon because it tells us something about the relationship between the human who anthropomorphizes, and the non-human agent which is anthropomorphized.
+Though commonly observed, it appears controversial, at the same time, that humans tend to perceive human-like physical appearance (\eg faces), emotional states, or inner mental states and motivations in non-human agents such as animals, natural forces, religious agents, technological gadgets, or mechanical devices \citep{epley_when_2008}.\footnote{According to \cite{epley_when_2008}, a non-human agent can be anything that acts -- or is believed to act -- with apparent independence.}  Anthropomorphism has received remarkable attention across several domains, such as natural sciences, psychology, Human-Computer Interaction, and Human-Robot Interaction.
+However, the term is used in different senses throughout these disciplines \citep{duffy_anthropomorphism_2003} which makes it difficult to synthesize findings.
+
+Originally, \textbf{anthropomorphism} comes from the Greek \textit{`anthropos'} for `man' (or `human') and \textit{`morphe'} for `form / structure' (or `shape').
+It can generally be understood as people's tendency to perceive a non-human agent as if it had some human characteristics.
+In turn, how a person perceives an agent further determines how she relates to and behaves towards the agent, or how she may behave in light of this agent \citep{epley_when_2008}.
+By this, anthropomorphism can be seen as a special kind of relationship between the human and the non-human agent.
+This relationship is often characterized by the fact that the human attributes or ascribes uniquely human characteristics to the non-human entity or artifact.
+The most prominently anthropomorphized non-human agents are probably animals and robots \citep{duffy_anthropomorphism_2003,schmitz_concepts_2011}.
+
+Apart from anthropomorphism there exists also \textbf{animism}, which can be understood as the \textit{"attribution of life to the nonliving"} \hl{in Schmitz 2011, cite Piaget original text!}.
+Using this definition, animism differs in two main aspects from anthropomorphism:
+First, the property which is ascribed differs: it is not human-unique but applies to all living beings (life-likeness).
+For instance, attributing life-likeness to a stone must not necessarily be labeled as anthropomorphism, since being alive is not a human unique property but applies to all living beings.
+The second difference comes from the instance (or better things) to which life is attributed: all living entities are excluded in this definition.
+In other words, pets as non-human but living beings can only be anthropomorphized (because they are not human) but not animized (because they are already alive).
+Often synonymously used to animism is the term \textbf{zoomorphism}, which applies to the cases when non-lifelike instances / things are associated with animalistic attributes, excluding human-specific traits.
+Both anthropomorphism and zoomorphism can be embraced by the concept of \textbf{life-likeness}.
+\footnote{The inverse process would be called dehumanization \cite{haslam_dehumanization:_2006}, or mechanomorphism \cite{caporael_anthropomorphism_1986}.}
 
@@
 \label{sec:anthropomorphism-robotics}
+
+Following research in Human-Computer Interaction (HCI) the \textit{Media Equation} \citep{reeves_media_1996} describes that people mindlessly react socially to their computer and may even attribute human (social) characteristics to it.
+The phenomenon has also been observed with virtual characters, and artificial embodied agents, such as robots.
+For instance, recent studies found that people tend to ascribe personality and intentions to robots \hl(REFS) and that they show empathetic behavior toward robots \cite{rosenthal-vonderputten_experimental_2013}.
+To subsume it, there is a growing body of literature that describes anthropomorphism in HCI and HRI.
+
+However, not everything colloquially labeled as \emph{anthropomorphism} really is anthropomorphism.
+Different, even partially conflicting understandings of anthropomorphism exist across and within disciplines \cite{duffy_anthropomorphism_2002}.
+\cite{epley_when_2008} try to narrow down and clarify the understanding of anthropomorphism in psychology by explaining what it is \textit{not}.
+The authors list four things
+that anthropomorphism does not include: First, anthropomorphism does not include
+behavioral descriptions of observable actions. Anthropomorphism requires going
+beyond what is directly observable. Second, anthropomorphism does not merely
+entail animism, as animate life is not a uniquely human-like characteristic.
+Third, anthropomorphism does not include any requirement of reasoned or
+reflective endorsement of an inference (\hl{the strength of anthropomorphic
+inferences can vary} \footnote{for further explanation the reader may refer to
+the original work \cite{epley_when_2008}.}).	Finally, anthropomorphism is not
+necessarily inaccurate. A psychological theory should take this (in)accuracy in
+anthropomorphism into account and predict variability in the tendency to
+perceive human-like traits in non-human agents.  In conclusion, it has been
+noted that anthropomorphism is a very complex phenomenon - in itself, its
+understanding, and when studying it. A common formal ground is missing; however,
+it is important to be clear about what exactly we mean when using the term
+anthropomorphism.
 

### 2014-03-13 paper.tex
new bib item first section about anthropomorphism definitions

@@
 
-In this section we will clarify the terminology that we use as we have found conflicting understandings of the term ``anthropomorphism'' in the related literature.
+In this section we will try to create a common ground in the understanding of anthropomorphism since we have found conflicting definitions of the term.
 We first present anthropomorphism as a social phenomenon.
@@
 Anthropomorphism is an interesting phenomenon because it tells us something about the relationship between the human who anthropomorphizes, and the non-human agent which is anthropomorphized.
-Though commonly observed, it appears controversial, at the same time, that humans tend to perceive human-like physical appearance (\eg faces), emotional states, or inner mental states and motivations in non-human agents such as animals, natural forces, religious agents, technological gadgets, or mechanical devices \citep{epley_when_2008}.\footnote{According to \cite{epley_when_2008}, a non-human agent can be anything that acts -- or is believed to act -- with apparent independence.}  Anthropomorphism has received remarkable attention across several domains, such as natural sciences, psychology, Human-Computer Interaction, and Human-Robot Interaction.
+Though commonly observed, it appears controversial, at the same time, that humans tend to perceive human-like physical appearance (\eg faces), emotional states, or inner mental states and motivations in non-human agents such as animals, natural forces, religious agents, technological gadgets, or mechanical devices \citep{epley_when_2008}.\footnote{According to \cite{epley_when_2008}, a non-human agent can be anything that acts -- or is believed to act -- with apparent independence.}  Anthropomorphism is one of not so many other topics that has received remarkable attention across various different domains, such as natural sciences, developmental and social psychology, Human-Computer Interaction (HCI), and Human-Robot Interaction (HRI).
 However, the term is used in different senses throughout these disciplines \citep{duffy_anthropomorphism_2003} which makes it difficult to synthesize findings.
 
-Originally, \textbf{anthropomorphism} comes from the Greek \textit{`anthropos'} for `man' (or `human') and \textit{`morphe'} for `form / structure' (or `shape').
-It can generally be understood as people's tendency to perceive a non-human agent as if it had some human characteristics.
+Originally, the term \textbf{anthropomorphism} comes from the Greek \textit{`anthropos'} for `man' (or `human') and \textit{`morphe'} for `form / structure' (or `shape').
+Anthropomorphism is generally understood as people's tendency to perceive a non-human agent as if it had some human characteristics or traits.
 In turn, how a person perceives an agent further determines how she relates to and behaves towards the agent, or how she may behave in light of this agent \citep{epley_when_2008}.
-By this, anthropomorphism can be seen as a special kind of relationship between the human and the non-human agent.
-This relationship is often characterized by the fact that the human attributes or ascribes uniquely human characteristics to the non-human entity or artifact.
+As such, anthropomorphism can be seen as a special kind of relationship between a human interacting with a non-human agent.
+This anthropomorphic relationship is often characterized by the fact that the human attributes or ascribes human-unique characteristics to the non-human agent.
+Since anthropomorphism becomes observable through these attributions, some definitions claim that anthropomorphism is not the perception but rather the attribution of human attributes to non-human agents, and name thoughts, emotions, and intentions as examples.
 The most prominently anthropomorphized non-human agents are probably animals and robots \citep{duffy_anthropomorphism_2003,schmitz_concepts_2011}.
 
-Apart from anthropomorphism there exists also \textbf{animism}, which can be understood as the \textit{"attribution of life to the nonliving"} \hl{in Schmitz 2011, cite Piaget original text!}.
-Using this definition, animism differs in two main aspects from anthropomorphism:
-First, the property which is ascribed differs: it is not human-unique but applies to all living beings (life-likeness).
-For instance, attributing life-likeness to a stone must not necessarily be labeled as anthropomorphism, since being alive is not a human unique property but applies to all living beings.
-The second difference comes from the instance (or better things) to which life is attributed: all living entities are excluded in this definition.
-In other words, pets as non-human but living beings can only be anthropomorphized (because they are not human) but not animized (because they are already alive).
+Apart from anthropomorphism there also exists the term \textbf{animism}, which can be defined as the attribution of life to the nonliving.\footnote{The study of animism was pioneered by \hl{Piaget} in the 1920s with his work on child's conception of the  world and of the living.
+He found that children tend to regard many inanimate objects as capable of sensations, emotions and intentions, and called this view `animism'.
+Since then, children's inferences about the world have been studied intensively and it has been found that especially younger children (according to \hl{Piaget} up to the age of about 10 years) tend to interpret physical phenomena in terms of intention on the part of the inanimate subject, for instance \textit{``the sun is hot because it wants to make people warm''}.
+However, there is an agreement that children's views and concepts of living, animal, and plant evolve as they grow up.} Using this definition, animism differs in two main aspects from anthropomorphism:
+First, the property which is ascribed differs: life-likeness is not human-unique but applies to all living beings.
+The second difference between anthropomorphism and animism stems from the agent (or better artifact) to which life is attributed.
+Living beings (most importantly animals) are naturally excluded from being animized.
+Consequently, while animals can be anthropomorphized (perceived to have human unique characteristics), they cannot be animized as they are already living beings.
+(Similarly to the fact that humans cannot be anthropomorphized as they are already humans.)
 Often synonymously used to animism is the term \textbf{zoomorphism}, which applies to the cases when non-lifelike instances / things are associated with animalistic attributes, excluding human-specific traits.
-Both anthropomorphism and zoomorphism can be embraced by the concept of \textbf{life-likeness}.
-\footnote{The inverse process would be called dehumanization \cite{haslam_dehumanization:_2006}, or mechanomorphism \cite{caporael_anthropomorphism_1986}.}
-
-Commonly, anthropomorphism can also be understood as \textbf{humanization} or
-\textbf{personification} of anything other than a human being. The phenomenon of
-personifying something has ancient roots, \textit{e.g.} in mythology but also in
-storytelling. In prehistoric artworks and illustrations, zoomorphic
-(animal-shaped) or anthropomorphic shapes were already used to represent natural
-forces or great spirits, for instance. A more recent example is Milo Winter's
-illustration from 1919, \textit{"The North Wind and the Sun"} (Figure
-\ref{fig:1}), in which both north wind and sun are given a human face
-(anthropomorphized). Similarly, when parents explain their children about
-nature, they tend to use anthropomorphisms, \textit{e.g.} saying the skies would
-cry when it rains. More generally, an explanation for why people
-anthropomorphize is that by doing so, the subject is made \emph{graspable},
-\emph{understandable}, \emph{predictable}, and one feel \emph{more empathetic}
-toward it\fxnote{important part. Emphasize this 4 facets, eg by saying we build
-on top of them}. For instance, people commonly anthropomorphize their pets,
-ascribing mental states, intentions or feelings to them
-\cite{eddy_attribution_1993}. Interestingly, pet-ownership seems to have a
-significant impact on human-robot interaction: several studies suggest that
-pet-owners are more likely to anthropomorphize technologies and robots than non
-pet-owners \hl{references!}.
+Both anthropomorphism and animism / zoomorphism can be embraced by the concept of \textbf{life-likeness}.
+
+There exist also inverse phenomenons to anthropomorphism, which can be found in the literature as \textbf{dehumanization} \citep{haslam_dehumanization:_2006}, and \textbf{mechanomorphism} \citep{caporael_anthropomorphism_1986}.
+However, we do not treat these phenomenons here.
 
@@
 
+To illustrate better how anthropomorphism differs from attributions of animacy or life-likeness, it is worth looking at paraphrases and examples of it.
+That is to say, anthropomorphism can alternatively be understood as \textbf{humanization} or \textbf{personification} of anything other than a human being.
+Personification has ancient roots, \eg in mythology but also in storytelling.
+Anthropomorphism was also used to describe and be able to predict natural forces or anticipate great spirits, for instance.
+An illustration of an anthropomorphism related to nature is shown in Figure \ref{fig:1}.
+In this Milo Winter (1919) drawing \textit{"The North Wind and the Sun"}, both north wind and sun are given a human face.
+
 \paragraph{Explanations for Anthropomorphism}
@@
 
-\fxfatal{inconsistency: we already give explanations for anthropomorphism in previous paragraph...}
-
-Anthropomorphism represents just one of many examples of induction whereby
-``people reason about an unknown stimulus based on a better-known representation
-of a related stimulus"~\cite{epley_when_2008}, in this case reasoning about a
-non-human agent based on representation of the self or other humans.
-
-According to Lee \etal~\cite{lee_human_2005}, there are two main perspectives in
-explaining people's tendency to anthropomorphize. First one explains
-anthropomorphism from the design of the artifact. It assumes that humans
-directly respond to life-like or social cues that an object or system emits,
-without thoughtful mental processing, by simply applying stereotypes and
-heuristics to it. In fact, from early childhood on, humans are inherently
-well-trained to perceive life \cite{epley_seeing_2007}. Schmitz
-\cite{schmitz_concepts_2011} describes that within the visual scope of design,
-the outer appearance can have an important impact on the overall perception of
-an object. The basic assumption here is that if an artifact appears much like a
-human, it is likely to be treated similar to a human. If this explanation of
-anthropomorphism is correct, people may respond automatically to social cues
-emitted by a robot, and apply human-human social schemas and norms to these
-interactions.
-
-The second perspective applies a human-centered, cognitive viewpoint where
-anthropomorphism is described through people's specific mental model they
-construct about how an artifact works the way it does.  We then
-anthropomorphize because it allows us to explain things we do not understand in
-terms that we do understand, and what we understand best is ourselves as human
-beings. This is consistent with the \emph{familiarity
-thesis}~\cite{hegel_understanding_2008} which claims that we understand the
-world based upon a mental model of the world that we are most familiar with.
-Consequently, people tend to thoughtfully develop a mental model of agents in
-their environment and make inferences about it based on what is familiar to
-them -- humans and human behavior, for instance.  This point of view implicitly
-builds on a person's ability to attribute mental states to oneself and others
-(\ie the availability of a \emph{theory of mind}~\cite{premack1978does} -- the
-link between a tendency to anthropomorphize and the engagement in the
-attribution of mental states to other humans has been recently demonstrated at
-the brain level in~\cite{cullen2013individual}). A theory of mind for other
-agents enables us to attribute intentionality to those agents
-\cite{leslie_pretense_1987,admoni_multi-category_2012}. Previous research
-examined the validity of the mental model concept with various kinds of robots
-\cite{schmitz_concepts_2011,kiesler_mental_2002}. Findings suggest that people
-tend to hold richer mental models of anthropomorphic robots in contrast to
-mechanic ones \cite{kiesler_mental_2002}.
-
-According to Lee \textit{et al.} \cite{lee_human_2005}, there are two main
-perspectives in explaining people's tendency to anthropomorphize. The first
-one explains anthropomorphism from the design of the artifact
-(anthropomorphic form in the design). It assumes that humans directly
-respond to life-like or social cues that an object or system emits, without
-thoughtful mental processing, by simply applying stereotypes and heuristics
-to it. In fact, from early childhood on, humans are inherently well-trained
-to perceive life \cite{epley_seeing_2007}. Schmitz
-\cite{schmitz_concepts_2011} describes that within the visual scope of
-design, the outer appearance can have an important impact on the overall
-perception of an object. The basic assumption here is that if an artifact
-appears much like a human, it is likely to be treated similar to a human. If
-this explanation of anthropomorphism is correct, people may respond
-automatically to social cues emitted by a robot, and apply human-human
-social schemas and norms to these interactions.
-
-The second perspective applies a human-centered, cognitive viewpoint where
-anthropomorphism is described through people's specific mental model they
-construct about how an artifact works the way it does. According to v.
-Foerster \hl{ref} \textit{"we anthropomorphize because it allows us to
-explain things we do not understand in terms that we do understand, and what
-we understand best is ourselves as human beings"}
-\cite{hegel_understanding_2008}. This is consistent with the \hl{familiarity
-thesis (18)} \cite{hegel_understanding_2008} which claims we understand the
-world based upon a mental model of the world that we are most familiar with.
-Consequently, people tend to thoughtfully develop a mental model of agents in
-their environment and make inferences about it based on what is familiar to
-them. This point of view implicitly builds on a person's ability to attribute
-mental states to oneself and others, which is called \textit{Theory of
-Mind}~\cite{Premack1978}. A theory of  mind for other agents enables us to
-attribute intentionality to those agents
-\cite{leslie_pretense_1987,admoni_multi-category_2012}. If a system behaves much
-like a human being (\eg emits a human voice), people's mental model of the
-system's behavior may approach their mental model of humans, though the model
-may differ in some important aspects \hl{ref? Schmitz?}. In turn, people's
-estimation of a robot's knowledge model and its capabilities affects the way
-they relate to it. Previous research examined the validity of the mental model
-concept with various kinds of robots
-\cite{schmitz_concepts_2011,kiesler_mental_2002}. Findings suggest that people
-tend to hold richer mental models about anthropomorphic robots in contrast to
-mechanic ones \cite{kiesler_mental_2002}. Later in this article, we may however
-come to question this result for longer human-robot interactions, after one
-get's acquantained with the robot's behaviour.
+But why do people anthropomorphize?
+One general reason is that by anthropomorphizing the non-human subject, it is made more \emph{graspable}, \emph{understandable}, \emph{predictable}, and one can feel \emph{more empathetic} toward it, and possible anticipate the subject's behavior.
+\fxnote{important part.
+Emphasize this 4 facets, eg by saying we build on top of them} For instance, people commonly anthropomorphize their pets, ascribing mental states, intentions or feelings to them\footnote{Interestingly, pet-ownership seems to have a significant impact on human-robot interaction: several studies suggest that pet-owners are more likely to anthropomorphize technologies and robots than non pet-owners} \cite{eddy_attribution_1993}.
+But what are the motivations behind this, generally speaking?
+
+Anthropomorphism represents just one of many examples of induction whereby ``people reason about an unknown stimulus based on a better-known representation of a related stimulus"~\cite{epley_when_2008}, in this case reasoning about a non-human agent based on representation of the self or other humans.
+\hl{Julia: this needs to go somewhere else ...}
+
+According to \cite{lee_human_2005}, there are two main perspectives in explaining people's tendency to anthropomorphize.
+
+First one explains anthropomorphism from ascertainable parts / the design of the non-human agent.
+This perspective assumes that humans directly respond to life-like or social cues that an object or system emits, without thoughtful mental processing, by simply applying stereotypes and heuristics to it.
+In fact, from early childhood on, humans are inherently well-trained to perceive life \citep{epley_seeing_2007}.
+\cite{schmitz_concepts_2011} describes that within the visual scope of design, the outer appearance of an object can have an important impact on how it is overall perceived.
+The basic assumption here is that if an artifact somehow resembles a human, it is likely to be treated similar to a human.
+If this explanation of anthropomorphism is correct, people may respond automatically to social cues emitted by an artificial embodied agent such as a robot, and apply human-human social schemas and norms to the occurring interactions.
+
+\hl{Julia: change the order of the two explanations! that makes more sense in terms of previous paragraph and anth form as following paragraph}
+
+The second perspective applies a human-centered, cognitive viewpoint where anthropomorphism is described through people's specific mental model they construct about how an artifact works the way it does.
+We then anthropomorphize because it allows us to explain things we do not understand in terms that we do understand, and what we understand best is ourselves as human beings.
+This is consistent with the \emph{familiarity thesis}~\cite{hegel_understanding_2008} which claims that we understand the world based upon a mental model of the world that we are most familiar with.
+Consequently, people tend to thoughtfully develop a mental model of agents in their environment and make inferences about it based on what is familiar to them -- humans and human behavior, for instance.
+This point of view implicitly builds on a person's ability to attribute mental states to oneself and others, which is called \textit{Theory of Mind}~\cite{Premack1978}.
+The link between a tendency to anthropomorphize and the engagement in the attribution of mental states to other humans has been recently demonstrated at the brain level in~\cite{cullen2013individual}.
+A theory of mind for other agents enables us to attribute intentionality to those agents \cite{leslie_pretense_1987,admoni_multi-category_2012}.
+If a system behaves much like a human being (\eg emits a human voice), people's mental model of the system's behavior may approach their mental model of humans, though the model may differ in some important aspects.
+In turn, people's estimation of a robot's knowledge model and its capabilities affects the way they relate to it.
+Previous research examined the validity of the mental model concept with various kinds of robots \cite{schmitz_concepts_2011,kiesler_mental_2002}.
+Findings suggest that people tend to hold richer mental models of anthropomorphic robots in contrast to mechanic ones \cite{kiesler_mental_2002}.
+Later in this article, we may however come to question this result for longer human-robot interactions, after one get's acquainted with the robot's behavior.
 
@@
 \hl{check if we really need this section ... maybe yes because it is important for the uncanny valley hypothesis}
+
+Anthropomorphic forms based on  have already in prehistoric artworks and illustrations, anthropomorphic (but sometimes also animal-shaped) characters
 
@@
 
-However, not everything colloquially labeled as \emph{anthropomorphism} really is anthropomorphism.
-Different, even partially conflicting understandings of anthropomorphism exist across and within disciplines \cite{duffy_anthropomorphism_2002}.
+However, not everything colloquially labeled as \emph{anthropomorphism} really is anthropomorphism.\footnote{For instance, it is not always clear whether a person (may it be an adult or a child) who gives and anthropomorphic response, believes that the other agent really thinks or acts like a human or whether she is using anthropomorphism in a metaphoric sense.\citep{leeds_childrens_1992}} Different, even partially conflicting understandings of anthropomorphism exist across and within disciplines \cite{duffy_anthropomorphism_2002}.
 \cite{epley_when_2008} try to narrow down and clarify the understanding of anthropomorphism in psychology by explaining what it is \textit{not}.

### 2014-03-14 paper.tex
section 1 complete, section 2 on-going

@@
 \hyphenation{com-mon-ly}
+\hyphenation{an-thro-po-mor-phism}
+\hyphenation{an-thro-po-mor-phic}
 
@@
 
-\section{Introduction and Overview}
+\section{Introduction and overview}
 \label{sec:intro}
@@
 Instead, we came across diverse and partially conflicting understandings of anthropomorphism.
-We also had the impression that the reported data were sometimes over-interpreted (probably due to the confusion of what exactly anthropomorphism is) or obtained in settings and assessed in ways that we believe do not give enough consideration to the complex nature of anthropomorphism.\footnote{As anthropomorphism emerges from an interaction between a human and a non-human agent, we believe that showing pictures of different kinds of robots and then using questionnaires to measure anthropomorphism is somehow limited.
-In the discussion in section \ref{sec:discussion} we discuss what tools and measurements could be used to study anthropomorphism and its dynamics in interaction studies in real-world environments.} However, when reviewing literature from social psychology, cognitive science, and neuroscience, we found support for the variances and dynamics in anthropomorphism that we observed in our studies.
+We also had the impression that the reported data were sometimes over-interpreted (probably due to the confusion of what exactly anthropomorphism is) or obtained in settings and assessed in ways that we believe do not give enough consideration to the complex nature of anthropomorphism.
+However, when reviewing literature from social psychology, cognitive science, and neuroscience, we found support for the variances and dynamics in anthropomorphism that we observed in our studies.
 As HRI integrates many disciplines, we think that it is valid to use theories from these related domains for interpreting our results and that it is relevant to report on this integration.
@@
 
-\subsection{Anthropomorphism as a Social Phenomenon}
-\label{sec:social-phenomenon}
+%\subsection{What is anthropomorphism?}
+%\label{sec:social-phenomenon}
 
@@
 
-Apart from anthropomorphism there also exists the term \textbf{animism}, which can be defined as the attribution of life to the nonliving.\footnote{The study of animism was pioneered by \hl{Piaget} in the 1920s with his work on child's conception of the  world and of the living.
+Apart from anthropomorphism there also exists the term \textbf{animism}, which can be defined as the attribution of life to the nonliving.
+The study of animism was pioneered by Piaget in the 1920s with his work on \textit{The Child's Conception of the  World}.
 He found that children tend to regard many inanimate objects as capable of sensations, emotions and intentions, and called this view `animism'.
-Since then, children's inferences about the world have been studied intensively and it has been found that especially younger children (according to \hl{Piaget} up to the age of about 10 years) tend to interpret physical phenomena in terms of intention on the part of the inanimate subject, for instance \textit{``the sun is hot because it wants to make people warm''}.
-However, there is an agreement that children's views and concepts of living, animal, and plant evolve as they grow up.} Using this definition, animism differs in two main aspects from anthropomorphism:
+Since then, children's inferences about the world have been studied intensively.
+However, there is an agreement that children's views and concepts of living, animal, and plant evolve as they grow up.
+Using this definition, animism differs in two main aspects from anthropomorphism:
 First, the property which is ascribed differs: life-likeness is not human-unique but applies to all living beings.
@@
 
- \begin{figure}\centering
+ \begin{figure}[b]\centering
 % Use the relevant command to insert your figure file.
 % For example, with the graphicx package use
-  \includegraphics[scale=0.91]{north-wind.jpg}
-  \includegraphics[scale=0.91]{sun.jpg}
+  \includegraphics[scale=1]{north-wind.jpg}
+  \includegraphics[scale=1]{sun.jpg}
 % figure caption is below the figure
  \caption{Milo Winter illustration of Aesop Fable \textit{The North Wind and the Sun}, 1919; both natural forces wind and sun are anthropomorphized with a human face; picture source: wikipedia}
- \label{fig:1}       % Give a unique label
+ \label{fig:north-wind-sun}       % Give a unique label
  \end{figure}
@@
 Anthropomorphism was also used to describe and be able to predict natural forces or anticipate great spirits, for instance.
-An illustration of an anthropomorphism related to nature is shown in Figure \ref{fig:1}.
+An illustration of an anthropomorphism related to nature is shown in Figure \ref{fig:north-wind-sun}.
 In this Milo Winter (1919) drawing \textit{"The North Wind and the Sun"}, both north wind and sun are given a human face.
 
-\paragraph{Explanations for Anthropomorphism}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+%
+%
+%		WHY DO PEOPLE ANTHROPOMORPHIZE?
+%
+%
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section*{Why do people anthropomorphize?}
 \label{sec:explanations}
@@
 But why do people anthropomorphize?
-One general reason is that by anthropomorphizing the non-human subject, it is made more \emph{graspable}, \emph{understandable}, \emph{predictable}, and one can feel \emph{more empathetic} toward it, and possible anticipate the subject's behavior.
-\fxnote{important part.
-Emphasize this 4 facets, eg by saying we build on top of them} For instance, people commonly anthropomorphize their pets, ascribing mental states, intentions or feelings to them\footnote{Interestingly, pet-ownership seems to have a significant impact on human-robot interaction: several studies suggest that pet-owners are more likely to anthropomorphize technologies and robots than non pet-owners} \cite{eddy_attribution_1993}.
-But what are the motivations behind this, generally speaking?
-
-Anthropomorphism represents just one of many examples of induction whereby ``people reason about an unknown stimulus based on a better-known representation of a related stimulus"~\cite{epley_when_2008}, in this case reasoning about a non-human agent based on representation of the self or other humans.
-\hl{Julia: this needs to go somewhere else ...}
-
-According to \cite{lee_human_2005}, there are two main perspectives in explaining people's tendency to anthropomorphize.
-
-First one explains anthropomorphism from ascertainable parts / the design of the non-human agent.
+First and foremost, it needs to be mentioned that anthropomorphism is a fairly complex phenomenon.
+Paradoxically, there is a huge and diverse body of literature on it but nevertheless, it seems that anthropomorphism is still not very well understood (especially in more recent fields like HRI).
+
+One common reason for anthropomorphism is that by perceiving some human-like characteristics in the non-human agent, this agent is made more \emph{graspable}, \emph{understandable}, \emph{predictable}, and one can feel \emph{more empathetic} toward it, and possibly one can then anticipate the agent's behavior.
+These are central motivations when trying to explain anthropomorphism, and we will come back to them in more detail later on.
+It is described that for the just mentioned reasons, people commonly anthropomorphize their pets, by ascribing mental states, intentions or feelings to them\footnote{Interestingly, pet-ownership seems to have a significant impact on human-robot interaction: several studies suggest that pet-owners are more likely to anthropomorphize technologies and robots than non pet-owners} \cite{eddy_attribution_1993}.
+But how can these motivations behind anthropomorphism be explained?
+
+It is important to keep in mind that anthropomorphism as a social phenomenon arises in an interaction \citep{persson_anthropomorphism_2000}, and thus includes at least two interaction partners (the human and the real or imagined non-human agent).
+Therefore, one can also take two main perspectives on explaining it \citep{lee_human_2005}: a human-centered, and an artifact-centered.
+We briefly outline both views in the following.
+It has to be kept in mind that both perspectives are inseparable; they apply at the same time, and we would like to present them here just as two different viewpoints on the same kind of phenomenon.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+%
+%
+%		HUMAN-CENTERED PERSPECTIVE: SOCIAL PHENOMENON
+%
+%
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{A human-centered perspective on anthropomorphism}
+
+The human-centered perspective builds on research from developmental and social psychology as well as cognitive sciences.
+In the following, we present what we found in reviewing this literature: (1) a line of research in developmental psychology that studies the attribution of animacy; (2) a line of research in more cognitive sciences that studies the cognitive processes that underlie anthropomorphism, and (3) a theory that explains anthropomorphism based on psychological factors~\citep{epley_seeing_2007}.
+All three branches apply a human-centered perspective on anthropomorphism.
+
+\paragraph*{Developmental psychology research on the attribution of animacy and intention}
+
+The phenomenon of attributing animacy and intentions to nonliving objects such as simple shapes has been intensively studied in developmental psychology.
+As mentioned earlier, Piaget found that children tend to ascribe life to the nonliving.
+They also tend to interpret physical phenomena in terms of intention on the part of the non-human subject.
+For instance children are likely to argue that \textit{``the sun is hot because it wants to make people warm''} \citep{leeds_childrens_1992}.
+In this example it is in fact questionable whether children really anthropomorphize the sun (believing that it has an intention) or whether they are using anthropomorphism in a metaphoric sense (because their conceptions of the world and of the living are not yet fully formed).
+Later however, two famous experiments by \cite{heider_experimental_1944} and \cite{michotte_perception_1963} showed that also adult participants attribute animacy and intention to simple things and shapes based on motion.\footnote{For more details, the reader may refer to the ``attribution theory''.} In both experiments, participants viewed animations of simple shapes, such as circles or triangles (see Figure \ref{fig:animacy_attribution}).
+Asked to describe what they observed, most people developed elaborate stories, attributing motivations, emotions and relationships between the objects.
+
+\begin{figure}[h]\centering
+% Use the relevant command to insert your figure file.
+% For example, with the graphicx package use
+  \includegraphics[scale=0.6]{heider-simmel_animation.jpeg}
+% figure caption is below the figure
+ \caption{Fritz Heider and Mary-Ann Simmel's animated film to study people's tendency to attribute animacy and intention to simple shapes; \textit{An experimental study of apparent behavior}, 1944}
+ \fxnote{wrap text around this figure?}
+ \label{fig:animacy_attribution}       % Give a unique label
+ \end{figure}
+
+Summing it up, it seems that there is a natural, relatively spontaneous reaction that makes a person attribute animacy and intention to moving shapes, even when there is no similarity of the shape to a human.
+This tendency to animize / anthropomorphize is already developed (and even more distinct) in infants and children.\footnote{\hl{Julia: I think we should mention this also in the anthropomorphic design section; as movements / motions as one of the most basic "lifelike" cues.}}
+
+\paragraph*{Cognitive science research and the mental model theory (Theory of Mind)}
+
+Anthropomorphism and similar phenomenons can also be understood as a thoughtful process of induction whereby \textit{``people reason about an unknown stimulus based on a better-known representation of a related stimulus"}~\citep{epley_when_2008}.
+In the case of anthropomorphism this means a person's reasoning about a non-human agent based on the representation of the self or other humans.
+The general assumption here is that all other agents (and entities) but oneself are \textit{``unknown''} (because we can only be our self).
+A central construct of this perspective is the so-called \textit{mental model} that a person has (and builds) of the agents she is reasoning about and interacting with.
+The specific mental model we have about an artifact / agent basically explains how this artifact / agent works the way it does.
+But how can we explain the phenomenon that a person uses a human-inspired mental model to explain the actions of a non-human (unknown) agent?
+Well, what we know and understand best is ourselves as human beings (the mental model that we have of our self and other humans).
+So by applying a similar mental model (or parts of it) to the unknown agent, we seek to be able to explain this unknown agent.
+This view is consistent with the \emph{familiarity thesis}~\citep{hegel_understanding_2008} which claims that we understand the world based upon a mental model of the world that we are most familiar with.
+Also, the mental model (human-centered perspective) is supported by \cite{epley_seeing_2007} \textit{Three Factor Theory} which applies a social psychology view, and will be presented in the next paragraph.
+
+In sum, this branch of research suggests that anthropomorphism implies that people thoughtfully develop a mental model of agents in their environment and that they make inferences about these agents based on what is familiar to them -- themselves, humans and human behavior.
+This understanding builds on a person's ability to attribute mental states to oneself and others, which is called \textit{Theory of Mind}~\cite{Premack1978}.
+A theory of mind for other agents enables us to attribute intentionality to those agents \cite{leslie_pretense_1987,admoni_multi-category_2012}.
+The link between this tendency to thoughtfully anthropomorphize and the engagement in the attribution of mental states to other humans has recently also been demonstrated at the brain level~\citep{cullen2013individual}.
+
+\paragraph*{The mental model theory in human-robot interaction}
+
+Mental models have also been studied in HRI.
+Starting point for this research is the assumption that if a system behaves much like a human being (\eg a robot that emits a human voice), people's mental model of the system's behavior may approach their mental model of humans (though the model may differ in some important aspects).
+In turn, people's estimation of an agent's knowledge model and its capabilities affects the way they relate to it.
+This holds important implications for the resulting interaction with the system, the user experience, and the acceptance.
+Previous research examined the validity of the mental model concept with various kinds of robots \cite{schmitz_concepts_2011,kiesler_mental_2002}.
+Findings suggest that people tend to hold richer mental models of anthropomorphic robots in contrast to mechanic ones \cite{kiesler_mental_2002}.
+\footnote{\hl{Later in this article, we may however come to question how far this result is based on expectations from the human user side, which are likely to be refined after continued interaction, and after the user gets acquainted with the robot's behavior.}} \hl{Julia:leave this paragraph here or put it later in the HRI section??}
+
+\paragraph*{Social psychology research: a 3-factor theory of anthropomorphism}
+\label{sec:psychological-factors}
+
+Social psychology offers interesting theories that can be applied to understand people's motivation to anthropomorphize.
+Irrespective of the artifact's characteristics, several psychological determinants have been found to explain a person's tendency to anthropomorphize.
+\cite{epley_seeing_2007} present a ``3-factor theory'' of when people are likely to anthropomorphize based on psychological determinants.
+Namely, the theory suggests that some people are more likely to anthropomorphize when:
+
+\begin{itemize}
+	\item anthropocentric knowledge is accessible and applicable to the artifact (\textit{elicited agent knowledge}),
+	\item they are motivated to explain and understand the behavior of other agents (\textit{effectance motivation}), and
+	\item they have the desire for social contact and affiliation (\textit{social motivation}).
+\end{itemize}
+
+\cite{epley_seeing_2007} describe that \textit{elicited agent knowledge} is a \textbf{cognitive determinant of anthropomorphism} which is understood as the activation of knowledge about humans (or the self) when making inferences about non-human agents.
+One basic reasons for this are a person's physical constraints of being a human and nothing else.
+Consequently, one has no other experience than the self and in turn people tend to make inferences about others' mental states by relying inordinately on their own mental state.
+\footnote{Using one's own mental states and characteristics as a guide when reasoning about other humans is ego-centrism; when reasoning about non-human agents is anthropomorphism.
+See \cite{epley_seeing_2007}} Also empirical findings suggest that knowledge about humans in general, or self-knowledge in particular, is likely to serve as a readily accessible base for induction when reasoning about non-human agents.
+This tendency is usually stronger in young children and decreases with cognitive development and the learning to distinguish the self from other humans, and non-human agents.
+
+Both \textit{effectance} and \textit{sociality} are \textbf{motivational determinants of anthropomorphism}.
+\textit{Effectance} is understood as the motivation to interact effectively in one's environment: understand, predict, \hl{reduce uncertainty (this feeds again our hypothesis that as soon as a robot is not uncertain anymore, there is no need to keep on anthropomorphizing it)}\fxfatal{important!
+move/copy that to the 'model' section or discussion} about one's environment and the agents that inhabit it.
+According to \cite{epley_seeing_2007}, anthropomorphism serves as one way to reduce uncertainty and increase comprehension of events in one's environment.
+They mention for instance, children (as they are in their early stages of life) appear to be more likely to anthropomorphize than adults, as they might feel more uncertain within their environment.
+
+\textit{Sociality} describes the motivation for social contact, social connection, and social approval from other agents.
+Importantly for anthropomorphism, this social connection appears to be satisfied by connections with \hl{\textit{"two of the most commonly anthropomorphized non-human agents, namely pets and religious agents"}} \cite{epley_seeing_2007}.
+According to \cite{epley_seeing_2007}, the motivation of being socially connected increases the tendency to anthropomorphize non-human agents because first sociality motivation increases the tendency to perceive human-like characteristics and traits even in non-human agents, and second it increases the tendency to search for sources of social connection in one's environment.
+Consequently, the authors suggest \textit{"[...] those who are chronically lonely should be more likely to anthropomorphize nonhuman agents than those who are more chronically connected"}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+%
+%
+%		ARTIFACT-CENTERED PERSPECTIVE: ANTHROPOMORPHIC DESIGN
+%
+%
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{An artifact-centered perspective on anthropomorphism}
+\label{sec:anthropomorphic-design}
+
+In contrast to the human-centered perspective, the artifact-centered perspective explains anthropomorphism from the ascertainable parts / the design of the non-human agent.
+
 This perspective assumes that humans directly respond to life-like or social cues that an object or system emits, without thoughtful mental processing, by simply applying stereotypes and heuristics to it.
@@
 If this explanation of anthropomorphism is correct, people may respond automatically to social cues emitted by an artificial embodied agent such as a robot, and apply human-human social schemas and norms to the occurring interactions.
-
-\hl{Julia: change the order of the two explanations! that makes more sense in terms of previous paragraph and anth form as following paragraph}
-
-The second perspective applies a human-centered, cognitive viewpoint where anthropomorphism is described through people's specific mental model they construct about how an artifact works the way it does.
-We then anthropomorphize because it allows us to explain things we do not understand in terms that we do understand, and what we understand best is ourselves as human beings.
-This is consistent with the \emph{familiarity thesis}~\cite{hegel_understanding_2008} which claims that we understand the world based upon a mental model of the world that we are most familiar with.
-Consequently, people tend to thoughtfully develop a mental model of agents in their environment and make inferences about it based on what is familiar to them -- humans and human behavior, for instance.
-This point of view implicitly builds on a person's ability to attribute mental states to oneself and others, which is called \textit{Theory of Mind}~\cite{Premack1978}.
-The link between a tendency to anthropomorphize and the engagement in the attribution of mental states to other humans has been recently demonstrated at the brain level in~\cite{cullen2013individual}.
-A theory of mind for other agents enables us to attribute intentionality to those agents \cite{leslie_pretense_1987,admoni_multi-category_2012}.
-If a system behaves much like a human being (\eg emits a human voice), people's mental model of the system's behavior may approach their mental model of humans, though the model may differ in some important aspects.
-In turn, people's estimation of a robot's knowledge model and its capabilities affects the way they relate to it.
-Previous research examined the validity of the mental model concept with various kinds of robots \cite{schmitz_concepts_2011,kiesler_mental_2002}.
-Findings suggest that people tend to hold richer mental models of anthropomorphic robots in contrast to mechanic ones \cite{kiesler_mental_2002}.
-Later in this article, we may however come to question this result for longer human-robot interactions, after one get's acquainted with the robot's behavior.
-
-\paragraph{Insights from Social and Developmental Psychology}
-\label{sec:psychological-factors}
-
-To understand the social phenomenon of anthropomorphism better, it makes sense
-to take a look at studies and explanations from developmental psychology. The
-phenomenon of attributing intentions and \hl{animacy} to simple shapes based on
-motion has been intensively studied in developmental psychology. Two famous
-studies on the perception of and attribution to simple things have been done in
-the mid 1940s: Heider and Simmel's work on the \textit{attribution theory}
-\cite{heider_experimental_1944} and Michotte's studies on \textit{the perception
-of causality} \cite{michotte_perception_1963}. In both experiments, participants
-viewed animations of simple shapes, such as circles or triangles (see Figure
-\ref{fig:animacy_attribution}). Asked to describe what they observed,
-interestingly, most people developed elaborate stories, attributing motivations,
-emotions and relationships between the objects.
-
-\begin{figure}\centering
-% Use the relevant command to insert your figure file.
-% For example, with the graphicx package use
-  \includegraphics[scale=0.6]{heider-simmel_animation.jpeg}
-% figure caption is below the figure
- \caption{Fritz Heider and Mary-Ann Simmel's animated film to study people's tendency to attribute animacy and intention to simple shapes; \textit{An experimental study of apparent behaviour}, 1944}
- \fxnote{wrap text around this figure?}
- \label{fig:animacy_attribution}       % Give a unique label
- \end{figure}
-
-What is a person's motivation to attribute human characteristics to simple
-geometric shapes, or more sophisticated, anthropomorphic shapes, animated or
-not? Irrespective of the artifact's characteristics, there are psychological
-theories to explain the phenomenon. An interesting recent psychological theory
-of anthropomorphism (also related to robotics) is provided by Epley, Waytz, and
-Cacioppo \cite{epley_seeing_2007}. The authors established a three-factor theory
-of when people are likely to anthropomorphize based on psychological
-determinants. Namely, the theory suggests that some people are more likely to
-anthropomorphize when:
-
-\begin{itemize}
-	\item anthropocentric knowledge is accessible and applicable to the artifact (\textit{elicited agent knowledge}),
-	\item they are motivated to explain and understand the behavior of other agents (\textit{effectance motivation}), and
-	\item they have the desire for social contact and affiliation (\textit{social motivation}).
-\end{itemize}
-
-Epley \textit{et al.} describe that \textit{elicited agent knowledge} is a
-\textbf{cognitive determinant  of anthropomorphism} which is understood as the
-activation of knowledge about humans (or the self) when making inferences about
-non-human agents. One basic reasons for this are a person's physical constraints
-of being a human and nothing else. Consequently, one has no other experience
-than the self and in turn people tend to make inferences about others' mental
-states by relying inordinately on their own mental state. \footnote{Using one's
-own mental states and characteristics as a guide when reasoning about other
-humans is ego-centrism; when reasoning about non-human agents is
-anthropomorphism. See Epley, 2007 \textit{et al.} \cite{epley_seeing_2007}} Also
-empirical findings suggest that knowledge about humans in general, or
-self-knowledge in particular, is likely to serve as a readily accessible base
-for induction when reasoning about non-human agents. This tendency is usually
-stronger in young children and decreases with cognitive development and the
-learning to distinguish the self from other humans, and non-human agents.
-
-Both \textit{effectance} and \textit{sociality} are \textbf{motivational
-determinants of anthropomorphism}. \textit{Effectance} is understood as the
-motivation to interact effectively in one's environment: understand, predict,
-\hl{reduce uncertainty (this feeds again our hypothesis that as soon as a robot
-is not uncertain anymore, there is no need to keep on anthropomorphizing
-it)}\fxfatal{important! move/copy that to the 'model' section or discussion}
-about one's environment and the agents that inhabit it. According to Epley
-\textit{et al.}, anthropomorphism serves as one way to reduce uncertainty and
-increase comprehension of events in one's environment. They mention for
-instance, children (as they are in their early stages of life) appear to be more
-likely to anthropomorphize than adults, as they might feel more uncertain within
-their environment.
-
-\textit{Sociality} describes the motivation for social contact, social
-connection, and social approval from other agents. Importantly for
-anthropomorphism, this social connection appears to be satisfied by connections
-with \hl{ \textit{"two of the most commonly anthropomorphized non-human agents,
-namely pets and religious agents"}} \cite{epley_seeing_2007}. According to Epley
-\textit{et al.}, the motivation of being socially connected increases the
-tendency to anthropomorphize non-human agents because first sociality motivation
-increases the tendency to perceive human-like characteristics and traits even in
-non-human agents, and second it increases the tendency to search for sources of
-social connection in one's environment. Consequently, the authors suggest
-\textit{"[...] those who are chronically lonely should be more likely to
-anthropomorphize nonhuman agents than those who are more chronically
-connected"}.
-
-\subsection{Anthropomorphic Design Principle}
-\label{sec:anthropomorphic-design}
-
-\hl{check if we really need this section ... maybe yes because it is important for the uncanny valley hypothesis}
 
@@
 	\hl{empathy --> check Iolanda's paper}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+%
+%
+%		PART 1.3: ANTHROPOMORPHISM IN HRI / SOCIAL ROBOTICS
+%
+%
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 cognitive sciences (and in particular social psychology) regarding how we, as
-humans, cope with unexpected behaviours from peers, or on the dynamics of mental
+humans, cope with unexpected behaviors from peers, or on the dynamics of mental
 model refinements, could bring interesting perspectives with possible
 applications to better manage long-term human-robot interactions.
+
+\paragraph*{How to measure anthropomorphism?}
+
+As anthropomorphism emerges from an interaction between a human and a non-human agent, we believe that showing pictures of different kinds of robots and then using questionnaires to measure anthropomorphism is somehow limited.
+We discuss what tools and measurements could be used to study anthropomorphism and its dynamics in interaction studies in real-world environments.
 
@@
 
-We would like to acknowledge the fruitful discussions with A Jung Moon and
-Aude Billard.
-
-This research was supported by the Swiss National Science Foundation through
-the National Centre of Competence in Research Robotics.
-
-\vspace{2cm}
+This research was supported by the Swiss National Science Foundation through the National Centre of Competence in Research Robotics.
+
 \section{Bibliography}

### 2014-03-18 paper.tex
Added a section on measuring anthropomorphism

@@
 \newcommand{\ie}{{\textit{i.e.~}}}
+\newcommand{\etc}{{\textit{etc.~}}}
 
@@
 \def\firstAuthorLast{Fink {et~al.}} %use et al only if is more than 1 author
-\def\Authors{Julia Fink\,$^{*}$, S\'{e}verin Lemaignan, Claire Braboszcz and Pierre Dillenbourg}
-\def\Address{Computer-Human Interaction in Learning and Instruction (CHILI) \\ Ecole Polytechnique F\'{e}d\'{e}rale de Lausanne (EPFL) \\ CH-1015 Lausanne, Switzerland}
+\def\Authors{Julia Fink\,$^{1*}$, S\'{e}verin Lemaignan$^{1}$, Claire Braboszcz$^{2}$ and Pierre Dillenbourg$^{1}$}
+\def\Address{$^{1}$Computer-Human Interaction in Learning and Instruction (CHILI) \\ Ecole Polytechnique F\'{e}d\'{e}rale de Lausanne (EPFL) \\ CH-1015 Lausanne, Switzerland \\
+\vspace{0.25cm}
+$^{2}$Laboratory for Neurology and Imaging of Cognition (LabNIC) \\
+Universit\'{e} de Gen\`{e}ve \\ CH-1211 Gen\`{e}ve, Switzerland 
+}
 \def\corrAuthor{Julia Fink \vspace{1mm}}
@@
 
-\section{Introduction and overview}
+\section*{Introduction and overview}
 \label{sec:intro}
@@
 
-In this article, we would like to share some critical but constructive considerations on anthropomorphism in robotics.
-Thereby, we contribute to the understanding of this complex phenomenon related to HRI.
-In accordance with theories from other related domains, we propose that anthropomorphism is determined and affected by multiple factors, and we show how this can impact the user experience and acceptance of robots in daily life environments.
-We further suggest an initial model that we call ``dynamics of anthropomorphism'' that serves to describe how anthropomorphism evolves and shapes the interaction over time.
+In this article, we would like to share some critical but constructive considerations on anthropomorphism in robotics and HRI.
+Thereby, we contribute to a better understanding of this complex phenomenon related to robots.
+In Section \ref{sec:anthropomorphism} we would first like to give an overview of how anthropomorphism can be defined, and then, in Section \ref{sec:explanations} present explanations to the question why people anthropomorphize, with a focus on anthropomorphism as a social phenomenon in HRI and the trend to design human-like robots.
+Then, based on these reviews of theories and concepts from related domains, in Section \ref{sec:multi-factors} we propose that anthropomorphism is determined and affected by multiple factors.
+We outline how anthropomorphism as a multi-factor phenomenon can impact the user experience and acceptance of robots in daily life environments.
+Next, in Section \ref{sec:dynamics-model} we suggest that anthropomorphism changes over time, and describe these changes in an initial model that we call ``Dynamics of Anthropomorphism''.
 We illustrate our idea with empirical findings from several HRI studies that we conducted in natural environments.
-We then present a cognitive and neuroscience perspective on anthropomorphism to consolidate our considerations and the observed dynamics.
-Finally, we discuss alternative ways to measure anthropomorphism in HRI, as this is a critical aspect of gaining a better understanding of it.
+In Section \ref{sec:cognition-neuroscience} we present a cognitive and neuroscience perspective on anthropomorphism to consolidate our considerations and the observed dynamics.
+Next, Section \ref{sec:discussion} considers limitations in our approach and we discuss existing and alternative ways to measure anthropomorphism in HRI.
+Finally, in Section \ref{sec:conclusion} we conclude this article.
 
@@
 Then we propose to use another term, namely ``anthropomorphic form'', to refer to the human-inspired design of artifacts.
-Finally, we focus on anthropomorphism in Human-Robot Interaction, as it naturally brings together (and needs to question) the usage of an anthropomorphic design of robots and its consequences for the interaction with the human user.
+Finally, we focus on both anthropomorphism and anthropomorphic design in human-robot interaction / robotics, as here both topics are brought together naturally.
 
@@
 Anthropomorphism is an interesting phenomenon because it tells us something about the relationship between the human who anthropomorphizes, and the non-human agent which is anthropomorphized.
-Though commonly observed, it appears controversial, at the same time, that humans tend to perceive human-like physical appearance (\eg faces), emotional states, or inner mental states and motivations in non-human agents such as animals, natural forces, religious agents, technological gadgets, or mechanical devices \citep{epley_when_2008}.\footnote{According to \cite{epley_when_2008}, a non-human agent can be anything that acts -- or is believed to act -- with apparent independence.}  Anthropomorphism is one of not so many other topics that has received remarkable attention across various different domains, such as natural sciences, developmental and social psychology, Human-Computer Interaction (HCI), and Human-Robot Interaction (HRI).
-However, the term is used in different senses throughout these disciplines \citep{duffy_anthropomorphism_2003} which makes it difficult to synthesize findings.
+Though commonly observed, it appears controversial, at the same time, that humans tend to perceive human-like physical appearance (\eg faces), emotional states, or inner mental states and motivations in non-human agents such as animals, natural forces, religious agents, technological gadgets, or mechanical devices \citep{epley_when_2008}.\footnote{According to \cite{epley_when_2008}, a non-human agent can be anything that acts -- or is believed to act -- with apparent independence.}  Anthropomorphism has received remarkable attention across various different domains, such as natural sciences, developmental and social psychology, Human-Computer Interaction (HCI), and Human-Robot Interaction (HRI).
 
@@
 
-There exist also inverse phenomenons to anthropomorphism, which can be found in the literature as \textbf{dehumanization} \citep{haslam_dehumanization:_2006}, and \textbf{mechanomorphism} \citep{caporael_anthropomorphism_1986}.
-However, we do not treat these phenomenons here.
+There exists also the inverse phenomenon to anthropomorphism, which can be found in the literature as \textbf{dehumanization} \citep{haslam_dehumanization:_2006}, or \textbf{mechanomorphism} \citep{caporael_anthropomorphism_1986}.
+We do not treat this here.
 
@@
 
+\paragraph*{Diverse understandings of anthropomorphism\\ \\}
+
+Anthropomorphism is used in different senses throughout different disciplines \citep{duffy_anthropomorphism_2003} which makes it difficult to synthesize findings.
+Depending on which understanding of anthropomorphism is applied, not everything colloquially labeled as \emph{anthropomorphism} really is anthropomorphism.\footnote{For instance, it is not always clear whether a person (may it be an adult or a child) who gives and anthropomorphic response, believes that the other agent really thinks or acts like a human or whether she is using anthropomorphism in a metaphoric sense.\citep{leeds_childrens_1992}} We need to be clear about what we mean by anthropomorphism because at the moment, there are different, even partially conflicting understandings of anthropomorphism, not only across but also within disciplines \cite{duffy_anthropomorphism_2002}.
+In particular, in the multi-disciplinary field of HRI, anthropomorphism is understood and interpreted in such a variety of ways that it is almost impossible to bring together and compare the research work done.
+In turn, it seems that the understanding of anthropomorphism in HRI has not improved much over the last decade but has only become more diverse (which is ok, too, but certainly a deeper understanding and common grounds would be convenient).
+
+How can we narrow down the understanding of anthropomorphism?
+From a psychology point of view \cite{epley_when_2008} try to clarify anthropomorphism by explaining what it is \textit{not}, and we think this approach could also help researchers in HRI and robotics.
+\cite{epley_when_2008} list four effects that anthropomorphism does not include:
+(1) First, anthropomorphism does not include behavioral descriptions of observable actions. Anthropomorphism requires going beyond what is directly observable.
+(2) Second, anthropomorphism does not merely entail animism, as animate life is not a uniquely human-like characteristic.
+(3) Third, anthropomorphism does not include any requirement of reasoned or reflective endorsement of an inference.\footnote{\hl{(the strength of anthropomorphic inferences can vary)}}
+(4) Finally, anthropomorphism is not necessarily inaccurate.
+A psychological theory should take this (in)accuracy in anthropomorphism into account and predict variability in the tendency to perceive human-like traits in non-human agents.\footnote{For more details, the reader may refer to the original work \citep{epley_when_2008}.}
+
+Not only \cite{epley_when_2008} and \cite{duffy_anthropomorphism_2002} but also others have noticed that anthropomorphism is a very complex phenomenon - in itself, in how it can be understood, and when studying it.
+A common formal ground is missing so far; however, it is important to be clear about what exactly we mean when using the term anthropomorphism.
+
+\hl{(maybe here Persson: anthropomorphism as a multi-layered phenomenon)}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\section*{Why do people anthropomorphize?}
+\section{Why do people anthropomorphize?}
 \label{sec:explanations}
@@
 
-It is important to keep in mind that anthropomorphism as a social phenomenon arises in an interaction \citep{persson_anthropomorphism_2000}, and thus includes at least two interaction partners (the human and the real or imagined non-human agent).
-Therefore, one can also take two main perspectives on explaining it \citep{lee_human_2005}: a human-centered, and an artifact-centered.
+Anthropomorphism as a social phenomenon arises in an interaction \citep{persson_anthropomorphism_2000}, and thus includes at least two interaction partners (the human and the real or imagined non-human agent).
+Therefore, one can take two main perspectives on explaining it \citep{lee_human_2005}: a human-centered, and an artifact-centered.
 We briefly outline both views in the following.
@@
 
-\paragraph*{Developmental psychology research on the attribution of animacy and intention}
+\paragraph*{Developmental psychology research on the attribution of animacy and intention\\ \\}
 
@@
 
-\paragraph*{Cognitive science research and the mental model theory (Theory of Mind)}
+\paragraph*{Cognitive science research and the mental model theory (Theory of Mind)\\ \\}
 
@@
 This view is consistent with the \emph{familiarity thesis}~\citep{hegel_understanding_2008} which claims that we understand the world based upon a mental model of the world that we are most familiar with.
-Also, the mental model (human-centered perspective) is supported by \cite{epley_seeing_2007} \textit{Three Factor Theory} which applies a social psychology view, and will be presented in the next paragraph.
+Also, the mental model (human-centered perspective) is supported by \cite{epley_seeing_2007} \textit{Three Factor Theory} which applies a social psychology view, and will be presented later in this section.
 
 In sum, this branch of research suggests that anthropomorphism implies that people thoughtfully develop a mental model of agents in their environment and that they make inferences about these agents based on what is familiar to them -- themselves, humans and human behavior.
-This understanding builds on a person's ability to attribute mental states to oneself and others, which is called \textit{Theory of Mind}~\cite{Premack1978}.
-A theory of mind for other agents enables us to attribute intentionality to those agents \cite{leslie_pretense_1987,admoni_multi-category_2012}.
-The link between this tendency to thoughtfully anthropomorphize and the engagement in the attribution of mental states to other humans has recently also been demonstrated at the brain level~\citep{cullen2013individual}.
-
-\paragraph*{The mental model theory in human-robot interaction}
+This understanding builds on a person's ability to attribute mental states to oneself and others, which is called \textit{Theory of Mind}~\citep{Premack1978}.
+A theory of mind for other agents enables us to attribute intentionality to those agents \citep{leslie_pretense_1987,admoni_multi-category_2012}.
+The link between this tendency to thoughtfully anthropomorphize and the engagement in the attribution of mental states to other humans were recently demonstrated at the brain level~\citep{cullen2013individual}.
+
+%\paragraph*{The mental model theory in human-robot interaction\\ \\}
 
@@
 Previous research examined the validity of the mental model concept with various kinds of robots \cite{schmitz_concepts_2011,kiesler_mental_2002}.
-Findings suggest that people tend to hold richer mental models of anthropomorphic robots in contrast to mechanic ones \cite{kiesler_mental_2002}.
-\footnote{\hl{Later in this article, we may however come to question how far this result is based on expectations from the human user side, which are likely to be refined after continued interaction, and after the user gets acquainted with the robot's behavior.}} \hl{Julia:leave this paragraph here or put it later in the HRI section??}
-
-\paragraph*{Social psychology research: a 3-factor theory of anthropomorphism}
+Findings suggest that people tend to hold richer mental models of anthropomorphic robots in contrast to mechanic ones \cite{kiesler_mental_2002}.\footnote{\hl{Later in this article, we may however come to question how far this result is based on expectations from the human user side, which are likely to be refined after continued interaction, and after the user gets acquainted with the robot's behavior.}} \hl{Julia:leave this paragraph here or put it later in the HRI section??}
+
+\paragraph*{Social psychology research: a 3-factor theory of anthropomorphism\\ \\}
 \label{sec:psychological-factors}
@@
 
-\begin{itemize}
+\begin{enumerate}
 	\item anthropocentric knowledge is accessible and applicable to the artifact (\textit{elicited agent knowledge}),
@@
 	\item they have the desire for social contact and affiliation (\textit{social motivation}).
-\end{itemize}
-
-\cite{epley_seeing_2007} describe that \textit{elicited agent knowledge} is a \textbf{cognitive determinant of anthropomorphism} which is understood as the activation of knowledge about humans (or the self) when making inferences about non-human agents.
-One basic reasons for this are a person's physical constraints of being a human and nothing else.
+\end{enumerate}
+
+The first factor (\textit{elicited agent knowledge}) is a \textbf{cognitive determinant of anthropomorphism} and based on the idea that a person builds a mental model (theory of mind) of the other agent.
+\cite{epley_seeing_2007} suggest that the process of making inferences about non-human agents is based on the activation of knowledge about humans (or the self).
+As mentioned before, when a person builds a mental model of the other (unfamiliar) agent, the question here is why does she draw on knowledge about other humans / herself and not on something else?
+One basic reasons for this is a person's physical constraints of being a human and nothing else.
 Consequently, one has no other experience than the self and in turn people tend to make inferences about others' mental states by relying inordinately on their own mental state.
-\footnote{Using one's own mental states and characteristics as a guide when reasoning about other humans is ego-centrism; when reasoning about non-human agents is anthropomorphism.
+\footnote{Using one's own mental states and characteristics as a guide when reasoning about other humans is called ego-centrism.
+In contrast, when using self-knowledge (or knowledge about humans in general) when reasoning about non-human agents, this is called anthropomorphism.
 See \cite{epley_seeing_2007}} Also empirical findings suggest that knowledge about humans in general, or self-knowledge in particular, is likely to serve as a readily accessible base for induction when reasoning about non-human agents.
@@
 
-Both \textit{effectance} and \textit{sociality} are \textbf{motivational determinants of anthropomorphism}.
-\textit{Effectance} is understood as the motivation to interact effectively in one's environment: understand, predict, \hl{reduce uncertainty (this feeds again our hypothesis that as soon as a robot is not uncertain anymore, there is no need to keep on anthropomorphizing it)}\fxfatal{important!
-move/copy that to the 'model' section or discussion} about one's environment and the agents that inhabit it.
-According to \cite{epley_seeing_2007}, anthropomorphism serves as one way to reduce uncertainty and increase comprehension of events in one's environment.
-They mention for instance, children (as they are in their early stages of life) appear to be more likely to anthropomorphize than adults, as they might feel more uncertain within their environment.
-
-\textit{Sociality} describes the motivation for social contact, social connection, and social approval from other agents.
-Importantly for anthropomorphism, this social connection appears to be satisfied by connections with \hl{\textit{"two of the most commonly anthropomorphized non-human agents, namely pets and religious agents"}} \cite{epley_seeing_2007}.
-According to \cite{epley_seeing_2007}, the motivation of being socially connected increases the tendency to anthropomorphize non-human agents because first sociality motivation increases the tendency to perceive human-like characteristics and traits even in non-human agents, and second it increases the tendency to search for sources of social connection in one's environment.
-Consequently, the authors suggest \textit{"[...] those who are chronically lonely should be more likely to anthropomorphize nonhuman agents than those who are more chronically connected"}.
+Both the second factor \textit{effectance} and the third factor \textit{sociality} are \textbf{motivational determinants of anthropomorphism}.
+\textit{Effectance} is understood a person's motivation to interact effectively in one's environment.
+That means, a person is motivated to be able to understand, predict, and reduce uncertainty \footnote{\hl{(this feeds again our hypothesis that as soon as a robot is not uncertain anymore, there is no need to keep on anthropomorphizing it)}}\fxfatal{important!
+move/copy that to the 'model' section or discussion} about her environment and the agents that inhabit it.
+According to \cite{epley_seeing_2007}, \textit{effectance motivation} can lead to anthropomorphism, since anthropomorphism serves as one way to reduce uncertainty and to increase comprehension of events in one's environment.
+Again, also according this factor it can be argued that children are more likely to anthropomorphize than adults.
+As children are in their early stages of life, they are likely to feel more uncertain within their environment, and consequently tend to anthropomorphize more.
+
+The third factor \textit{sociality} describes a person's motivation for social contact, social connection, and social approval from other agents.
+In lack of social connections to other humans (\etc friends, family, colleagues), a person is more likely to compensate these social connections by anthropomorphizing non-human agents.
+In other words \textit{"[...] those who are chronically lonely should be more likely to anthropomorphize nonhuman agents than those who are more chronically connected"} \citep{epley_seeing_2007}.
+Importantly for anthropomorphism, this social connection often appears to be satisfied by connections with \textit{"two of the most commonly anthropomorphized non-human agents, namely pets and religious agents"} \citep{epley_seeing_2007}.
+Thus, the motivation of being socially connected increases the tendency to anthropomorphize non-human agents because first sociality motivation increases the tendency to perceive human-like characteristics and traits even in non-human agents, and second it increases the tendency to search for sources of social connection in one's environment.
 
@@
 In contrast to the human-centered perspective, the artifact-centered perspective explains anthropomorphism from the ascertainable parts / the design of the non-human agent.
-
-This perspective assumes that humans directly respond to life-like or social cues that an object or system emits, without thoughtful mental processing, by simply applying stereotypes and heuristics to it.
-In fact, from early childhood on, humans are inherently well-trained to perceive life \citep{epley_seeing_2007}.
-\cite{schmitz_concepts_2011} describes that within the visual scope of design, the outer appearance of an object can have an important impact on how it is overall perceived.
+One could think of changing the direction of the causality: here, it is the non-human artifact that encourages the human to anthropomorphize it -- in the human-centered perspective our argument was in the opposite direction, the human was motivated to anthropomorphize the non-human artifact).
+As already mentioned, both these views go hand in hand.
+
+The artifact-centered perspective assumes that humans directly respond to life-like and social cues that the non-human artifact or system emits, without thoughtful mental processing, by simply applying stereotypes and heuristics to it.
+In fact, from early childhood on, humans are inherently well-trained to perceive life \citep{epley_seeing_2007}, and to respond to social cues, such as facial expressions, social gestures, turn-taking.
+\cite{schmitz_concepts_2011} describes that within the visual scope of design, the outer appearance of an object can have an important impact on how it is overall perceived (how it appears to the human).
+This fact is exploited in design.
 The basic assumption  here is that if an artifact somehow resembles a human, it is likely to be treated similar to a human.
 If this explanation of anthropomorphism is correct, people may respond automatically to social cues emitted by an artificial embodied agent such as a robot, and apply human-human social schemas and norms to the occurring interactions.
-
-Anthropomorphic forms based on  have already in prehistoric artworks and illustrations, anthropomorphic (but sometimes also animal-shaped) characters
-
-In general, it is suggested that increasing human-likeness of a robot	 will
-lead to more perceived \textit{affinity} from the human side
-\cite{mori_uncanny_1970}. This theoretical concept is also supported by
-psychological determinants of perceiving human-likeness in something non-human:
-\textit{"the more similar in appearance, the more people are likely to use
-themselves as a source of induction and anthropomorphize these nonhuman agents"}
-\cite{epley_seeing_2007}. Further, empirical studies have shown that robots with
-human-like forms can enhance social responses from humans which in turn can have
-a positive impact on acceptance
-\cite{venkatesh_theoretical_2000,duffy_anthropomorphism_2003,goetz_cooperation_2002}.
-People responded more positively to an artifact that displayed human-like
-behavioral characteristics (emotions, facial expression) in contrast to a purely
-functional design
-\cite{eyssel_anthropomorphic_2010,krach_can_2008,reeves_media_1996,riek_how_2009}.
-Overall, these results suggest that human-like features in robots enhance
-anthropomorphism, and in turn create a social view toward the robot.
-
-Well known from the HRI community, we may mention the other side of human-like
-behaviours and appearance: a not yet very well defined thin line separates
-acceptable human-like forms in robots from creepy artificial \textit{almost}
-human-like appearing robots. The underlying theory for this viewpoint is stated
-as the \textit{Uncanny Valley} \cite{mori_uncanny_1970} which suggests that
-artificial human-like forms are only acceptable up to a certain degree but lead
-to reluctance if they fail in trying to attain human-likeness \hl{cross-ref to
-later and figure}.
-
-The theory (Figure~\ref{fig:uncanny_valley}) hypothesizes that a person's
-response to a human-like robot would abruptly shift from empathy to revulsion as
-it approached, but failed to attain, a lifelike appearance
-\cite{mori_uncanny_1970}. Starting with low degrees of anthropomorphic cues in a
-robot, humans seem to readily accept and prefer them compared to purely
-mechanical robots. In general, one can say that up to a certain (yet not very
-well defined) degree, the more human-like the robot, the more affection it can
-engender through familiar communication references.
+(However, at the same time, the human-like design of things also raises expectations from the human user side, to which we will come back later in more detail.)
+
+\paragraph*{Anthropomorphic designs\\ \\}
+
+An imitation of human form (or in a broader sense also animal and natural) form is called \textit{``anthropomorphic design''} or \textit{``anthropomorphic form''} -- but \textit{not anthropomorphism}.\footnote{We suggest to use these two different terms - \textit{anthropomorphism} and \textit{anthropomorphic form} - in order to highlight that they are not the same.
+In short, anthropomorphism refers to the social phenomenon, the human's tendency to perceive human-likeness in non human-like agents, while anthropomorphic form refers to the design of the agent / artifact.} The use of anthropomorphic (human-like) form in the design of non-human things is as old as people's tendency to anthropomorphize.
+Anthropomorphic (and also animal-shaped) forms were used already in prehistoric artworks and illustrations, and they have a long-standing tradition in the design of daily life artifacts and in general \citep{guthrie_bottles_2000}.
+The principle of human-like form has received remarkable attention in respect to the design of robots, on which we will focus in the next paragraph.
+
+Using the term \textit{``form''} to describe the design of an artifact, we refer not only to the shape of an artifact (how the artifact looks like) but to the total expression of the product \citep{bartneck_shaping_2004}.
+\cite{disalvo_hug:_2003} argues that \textit{form} includes a product's physical shape, materials, and behavioral qualities.
+Latter aspect is of special importance for interactive systems that show some degree of autonomy (independence).
+
+\paragraph*{Anthropomorphic form in robotics - Uncanny Valley Hypothesis\\ \\}
+
+Several categories of anthropomorphic form can be classified, but there is no common agreement on the borders and transitions between these categories: anthropomorphic, zoomorphic, caricatured, functional \citep{fong_survey_2003}.
+However, a classification makes sense because different user reactions are expected.
+According to \cite{bartneck_shaping_2004}, the appearance and function of a product, whether it is an appliance or a humanoid robot, affects the way that people perceive it, interact with it, and build long-term relationships with it.
+In general, it is suggested that increasing human-likeness of a robot will lead to more perceived \textit{affinity} from the human side \citep{mori_uncanny_1970}.
+This theoretical concept is also supported by psychological determinants of perceiving human-likeness in something non-human: \textit{"the more similar in appearance, the more people are likely to use themselves as a source of induction and anthropomorphize these nonhuman agents"} \citep{epley_seeing_2007}.
+Further, empirical studies have shown that robots with human-like forms can enhance social responses from humans which in turn can have a positive impact on acceptance \citep{duffy_anthropomorphism_2003,goetz_cooperation_2002,venkatesh_theoretical_2000}.
+People responded more positively to an artifact that displayed human-like behavioral characteristics (emotions, facial expression) in contrast to a purely functional design \citep{eyssel_anthropomorphic_2010,krach_can_2008,reeves_media_1996,riek_how_2009}.
+Overall, these results suggest that human-like features in robots enhance anthropomorphism, and in turn create a social view toward the robot.
 
@@
 % For example, with the graphicx package use
-  \includegraphics[scale=0.6]{uncanny-valley.jpg}
+  \includegraphics[scale=0.75]{uncanny-valley.jpg}
 % figure caption is below the figure
- \caption{Mashiro Mori, illustration of the \textit{Uncanny Valley}, originally
- from 1970; picture from a manuscript version of \cite{mori_uncanny_2012}}
-
+ \caption{Mashiro Mori, illustration of the \textit{Uncanny Valley} hypothesis.
+The curve models the user's perceived affinity with the artifact, as its human likeness is increased.
+Up to a certain (not yet defined) point, a person perceives more affinity in a more human-like agent; however with an abrupt shift towards a negative perception as soon as the agent surpasses this point, of resembling a human too closely but not fully.
+Originally from 1970; picture from a manuscript version of \cite{mori_uncanny_2012}}
  \label{fig:uncanny_valley}       % Give a unique label
@@
 
-Another sensitive aspect is that with robots that closely resemble humans,
-ethical issues arise. For instance, we need to consider how far we actually want
-an \textit{artificial agent} to resemble ourselves and how far it should act
-`artificially socially' toward humans, and what happens as soon as it is
-considered a \textit{moral agent} \cite{sullins_when_2006}. Using
-\textit{socially interactive robots} in contexts involving elderly care or
-rehabilitation for disabled / handicapped persons, autistic children is also a
-controversially discussed topic \cite{robins_robots_2005}.
-
-when slowly increasing its human-likeness, the more affection
-
-The idea of the hypothesis follows Freud's description of the uncanny (a
-translation from the German word `unheimlich') \hl{ref Freud, The Uncanny}: "it
-derives its terror not from something externally alien or unknown but - on the
-contrary - from something strangely familiar which defeats our efforts to
-separate ourselves from it". \cite{hegel_understanding_2008}
-
-	Also: Simulation Theory
-
-"The anthropomorphic design of human-machine interfaces is inevitable. The
-important criterion is to seek a balance between people's expectations and the
-machines capabilities." \cite{duffy_anthropomorphism_2002}
-
-"What is the ideal set of human features that could supplement and augment a
-robots  social functionality?" \cite{duffy_anthropomorphism_2002}
-
-Though, the 'anthropomorphic design principle" seems beneficial, it also raises
-ethical issues and has been reviewed critically in terms of acceptance. How far
-do we want a robot to resemble a human or act like a human?
-
-Findings that support anthropomorphic form in robots because they found people
-respond with anthropomorphizing these kind of robots, and in turn act more
-social toward them or accept them more easily:
-
-	\hl{empathy --> check Iolanda's paper}
+However, there is the other side of using human-like forms in the design of robots: a not yet very well defined thin line separates acceptable human-like forms in robots from creepy artificial \textit{almost} human-like appearing robots.
+The underlying theory for this viewpoint is stated as the \textit{Uncanny Valley} \cite{mori_uncanny_1970} (see Figure \ref{fig:uncanny_valley}).
+The theory hypothesizes that artificial human-like forms are only acceptable up to a certain degree but lead to reluctance if they fail in trying to attain human-likeness.
+Consequently, it is assumed that a person's response to a human-like robot would abruptly shift from empathy to revulsion as the robot's form approached, but failed to attain a lifelike appearance.
+Naturally, humans are very skilled and also sensitive when it comes to identifying if there is \hl{``something wrong''} in the counterpart-- may the difference be even subtle.
+First, starting with low degrees of anthropomorphic cues in a robot, humans seem to readily accept and prefer these forms compared to purely mechanical robots.
+A possible explanation for this is that humans tend to apply the same communication references to anthropomorphic systems that they would use with other humans.
+However, as the anthropomorphic form also increases people's expectation of the agent, and further artificial systems are (not yet) able to mimic human movements, or human social cues in an acceptable way, the pretended human but artificial agent is more than just disappointing for the human -- it appears uncanny\footnote{The idea of the Uncanny Valley hypothesis follow Freud's description of the uncanny (a translation from the German word \textit{``unheimlich'')}.
+Something uncanny \textit{"derives its terror not from something externally alien or unknown but -- on the contrary -- from something strangely familiar which defeats our efforts to separate ourselves from it"} cited after \cite{hegel_understanding_2008}.} and evokes reluctance, the so-called \textit{"uncanny valley"}.
+
+Of course, there is no one good answer to the question how to not fall in the uncanny valley when designing an anthropomorphic system.
+Equipping a system with some anthropomorphic forms seems to be inevitable \cite{duffy_anthropomorphism_2002} in the advancement of human-machine interfaces and sociable robots \citep{breazeal_sociable_2000}.
+However, we agree that \textit{"the important criterion is to seek a balance between people's expectations and the machines capabilities"} \citep{duffy_anthropomorphism_2002}.
+
+Another critical point with the use of human-like form in artificial agents are ethical aspects.
+For instance, we need to consider how far we actually want an \textit{artificial agent} to resemble a human -- or ourself.
+Even though we do not discuss these aspects in this article, we think the HRI / robotics community needs to consider questions of how far an artificial agent should act ``as if it would be social'' toward humans.
+What implications does an anthropomorphic design of robots have?
+What happens as soon as the artificial agent is considered a \textit{moral agent} \cite{sullins_when_2006}?
+Using \textit{socially interactive robots} in contexts involving elderly care or rehabilitation for disabled / handicapped persons, autistic children is a controversially discussed topic \cite{robins_robots_2005}.
+
+% Simulation Theory
+
+% Findings that support anthropomorphic form in robots because they found people respond with anthropomorphizing these kind of robots, and in turn act more social toward them or accept them more easily:	empathy --> check Iolanda's paper
 
@@
 
-Following research in Human-Computer Interaction (HCI) the \textit{Media Equation} \citep{reeves_media_1996} describes that people mindlessly react socially to their computer and may even attribute human (social) characteristics to it.
-The phenomenon has also been observed with virtual characters, and artificial embodied agents, such as robots.
-For instance, recent studies found that people tend to ascribe personality and intentions to robots \hl(REFS) and that they show empathetic behavior toward robots \cite{rosenthal-vonderputten_experimental_2013}.
-To subsume it, there is a growing body of literature that describes anthropomorphism in HCI and HRI.
-
-However, not everything colloquially labeled as \emph{anthropomorphism} really is anthropomorphism.\footnote{For instance, it is not always clear whether a person (may it be an adult or a child) who gives and anthropomorphic response, believes that the other agent really thinks or acts like a human or whether she is using anthropomorphism in a metaphoric sense.\citep{leeds_childrens_1992}} Different, even partially conflicting understandings of anthropomorphism exist across and within disciplines \cite{duffy_anthropomorphism_2002}.
-\cite{epley_when_2008} try to narrow down and clarify the understanding of anthropomorphism in psychology by explaining what it is \textit{not}.
-The authors list four things
-that anthropomorphism does not include: First, anthropomorphism does not include
-behavioral descriptions of observable actions. Anthropomorphism requires going
-beyond what is directly observable. Second, anthropomorphism does not merely
-entail animism, as animate life is not a uniquely human-like characteristic.
-Third, anthropomorphism does not include any requirement of reasoned or
-reflective endorsement of an inference (\hl{the strength of anthropomorphic
-inferences can vary} \footnote{for further explanation the reader may refer to
-the original work \cite{epley_when_2008}.}).	Finally, anthropomorphism is not
-necessarily inaccurate. A psychological theory should take this (in)accuracy in
-anthropomorphism into account and predict variability in the tendency to
-perceive human-like traits in non-human agents.  In conclusion, it has been
-noted that anthropomorphism is a very complex phenomenon - in itself, its
-understanding, and when studying it. A common formal ground is missing; however,
-it is important to be clear about what exactly we mean when using the term
-anthropomorphism.
+While the previous sections presented anthropomorphism more generally, this section focuses on how anthropomorphism is understood and has been studied in human robot interaction / social robotics.
+Our aim here is to give a rough overview of the diverse and partially conflicting interpretations of anthropomorphism in HRI, and critically review some previous work.
+
+Most work that studies anthropomorphism in HRI builds on the famous work of \cite{reeves_media_1996} in HCI.
+In the so-called \textit{Media Equation}, the authors describe that people mindlessly react socially to their computer and that they tend to even attribute human (social) characteristics to it.
+Then, with emerging new interactive technologies and systems, anthropomorphism has also been observed with digital / virtual characters \citep{reeves_media_1996,
+nass_anthropocentrism_1995}, and later also with artificial embodied agents, such as robots.
+For instance, recent studies found that people tend to ascribe personality and intentions to robots \hl{(REFS)} and that they show empathetic behavior toward robots \cite{rosenthal-vonderputten_experimental_2013}.
+Summing it up, there is a huge and constantly growing body of literature that describes anthropomorphism in HCI and HRI.
+Despite the phenomenon is well studied, we still know rather little about it, so that at conferences and symposiums, anthropomorphism is still a ``hot topic''; however, at the same time theories related to anthropomorphism, such as the \textit{``Uncanny Valley''} are controversially discussed.
+
+\paragraph*{Studies on anthropomorphism in HRI\\ \\}
 
 Anthropomorphism is a commonly observed phenomenon in human-robot interaction.
-Studies showed that there are people who directly talk to their robot (even if
-it does not recognize speech), give it a name, greet it, wonder about its
-intentions or actions
-\cite{eyssel_anthropomorphic_2010,fink_anthropomorphic_2012,forlizzi_how_2007,fussell_how_2008,kiesler_anthropomorphic_2008}.
-It has frequently been described that people ascribe intentions or emotions to
-their domestic robot, such as to a Roomba vacuum-cleaning robot
-\cite{krumm_my_2007,sung_robots_2009} or the AIBO robotic dog
-\cite{friedman_hardware_2003}. People's tendency to anthropomorphize
-technologies has besides been described earlier in human-computer interaction
-and related to digital agents \cite{reeves_media_1996,
-nass_anthropocentrism_1995}. Though, the phenomenon seems to be more coined in
-human-robot interaction than in other human-machine interaction fields, due to
-the embodied nature of robots. They are physical agents, autonomously acting
-right next to us, and also designed to interact intelligently with us and the
-environment. Besides, anthropomorphism may be further supported by a specific
-anthropomorphic \emph{design}. But what is the motivation which underlies the
-efforts of enhancing anthropomorphism through specific anthropomorphic design in
-robots? Why does anthropomorphism seem to be so important in robotics? There is
-no one single answer to this question but certainly, developers and designers
-have discovered that anthropomorphism seems to be beneficial for human-robot
-relations, especially with socially interactive robots \cite{fong_survey_2003}.
-More concretely, it has been found that the appearance and function of a
-\hl{product (research in marketing?)}) impacts how people perceive it, interact
-with it, and build long-term relations with it \cite{bartneck_shaping_2004}.
-Consequently, the domain of (social) robotics tries to exploit this fact by
-enhancing anthropomorphism through anthropomorphic robots: \textit{"Applying
-anthropomorphism or zoomorphism changes the way how users try to understand and
-make sense of a [system] by projecting everyday \hl{expectations} of human and
-animalistic life onto it."} \cite{schmitz_concepts_2011}\fxfatal{paragraph a bit
-confusing...}. Studies have further shown that perceived similarity between the
-user and the robot influences the intensity of the participants' attributions
-towards the robot. Thus, anthropomorphism plays an important role in the design
-of robots as it is strongly related to the perception of intelligence, fun, the
-attribution of intentions and thus the predictability of the robot \hl{which
-ref??}.
-
-"[...] the experiment demonstrates that human beings implicitly attribute
-human-like qualities, such as mental states, to nonhuman agents. This finding
-was evident on a neurophysiological level as well as behavioral level."
-\cite{hegel_understanding_2008}\fxwarning{What to do with this quote? 'neuro'
-level maybe interesting?}
-
-Anthropomorphism represents just one of many examples of induction whereby
-"people reason about an unknown stimulus based on a better-known representation
-of a related stimulus" \cite{epley_when_2008}, in this case reasoning about a
-non-human agent based on representation of the self or other humans. This
-supports the usual role we assign to anthropomorphism in robotics: the
-anthropomorphic design of a robot encourages people to reason about this
-unfamiliar system \emph{as if} it was a human. To increase this tendency, robots
-are designed with anthropomorphic forms (human-like or lifelike forms, in the
-broader sense), or are able to display and use human-social cues when
-interacting with humans.\\
+Various studies have shown that people directly talk to their robot (even if it does not recognize speech), give it a name, greet it, or wonder about its intentions and actions as if it were a human \citep{eyssel_anthropomorphic_2010,fink_anthropomorphic_2012,forlizzi_how_2007,fussell_how_2008,kiesler_anthropomorphic_2008}.
+It has frequently been described that people ascribe intentions or emotions to their domestic robot, such as to a Roomba vacuum-cleaning robot \citep{krumm_my_2007,sung_robots_2009} or the AIBO robotic dog \citep{friedman_hardware_2003}.
+Though people's tendency to anthropomorphize non-human agents has already been described in HCI and related to digital agents; however the phenomenon seems to be more coined in HRI.
+There are several reasons for this, which mostly concern the unique characteristics of robots.
+First of all, robots are embodied / physical agents that are sharing the same space with us. 
+Further, robots act autonomously and are able to respond intelligently to us and the environment.
+Then, there is the design aspect, which has already been outlined in Section \ref{sec:anthropomorphic-design}.
+Thus, anthropomorphism may be further supported by a specific anthropomorphic \emph{design}.
+
+But what is the motivation which underlies the efforts of enhancing anthropomorphism through specific anthropomorphic design in robots?
+Why does anthropomorphism seem to be so important in robotics?
+There is no one single answer to this question but certainly, developers and designers have discovered that anthropomorphism seems to be beneficial for human-robot relations, especially with socially interactive robots \cite{fong_survey_2003}.
+
+More concretely, it has been found that the appearance and function of a impacts how people perceive it, interact with it, and build long-term relations with it \cite{bartneck_shaping_2004}.
+Consequently, the domain of (social) robotics tries to exploit this fact by enhancing anthropomorphism through anthropomorphic robots: \textit{"Applying anthropomorphism or zoomorphism changes the way how users try to understand and make sense of a [system] by projecting everyday \hl{expectations} of human and animalistic life onto it."} \cite{schmitz_concepts_2011}\fxfatal{paragraph a bit
+confusing...}.
+
+Studies have further shown that perceived similarity between the user and the robot influences the intensity of the participants' attributions towards the robot.
+Thus, anthropomorphism plays an important role in the design of robots as it is strongly related to the perception of intelligence, fun, the attribution of intentions and thus the predictability of the robot \hl{which ref??}.
+
+"[...] the experiment demonstrates that human beings implicitly attribute human-like qualities, such as mental states, to nonhuman agents.
+This finding was evident on a neuro-physiological level as well as behavioral level." \cite{hegel_understanding_2008}\fxwarning{What to do with this quote?
+'neuro' level maybe interesting?}
+
+Anthropomorphism represents just one of many examples of induction whereby "people reason about an unknown stimulus based on a better-known representation of a related stimulus" \cite{epley_when_2008}, in this case reasoning about a non-human agent based on representation of the self or other humans.
+This supports the usual role we assign to anthropomorphism in robotics: the anthropomorphic design of a robot encourages people to reason about this unfamiliar system \emph{as if} it was a human.
+To increase this tendency, robots are designed with anthropomorphic forms (human-like or lifelike forms, in the broader sense), or are able to display and use human-social cues when interacting with humans.\\
 
@@
 
-\section{Anthropomorphism as a multi-factor phenomenon that evolves over time}
-\label{sec:our-ideas}
-
-\hl{bridge sentence}
-
-\subsection{Multiple factors of anthropomorphism}
+\section{Anthropomorphism as a multi-factor phenomenon ...}
 \label{sec:multi-factors}
@@
 
-\subsection{A Model of the Dynamics of Anthropomorphism}
+\section{... that evolves over time}
 \label{sec:dynamics-model}
@@
 published~\cite{fink_anthropomorphism_2012} and field
-experiements~\fixme{cites!}, we believe that anthropomorphic effects in HRI are
+experiments~\fixme{cites!}, we believe that anthropomorphic effects in HRI are
 not always the same but evolve over time, along with growing interaction and
 experience with the robot, similar to how relationships among people evolve
-over time \fixme{(cite Hinde, 1988)}. In fact, Kanda \textit{et al.}
-\cite{kanda_interactive_2004} also hypothesized that people's attitude toward
-technological artifacts and their relationship with them would evolve over
-time, and they were among the first who described \textit{novelty effects}
-during a long-term study with an interactive robot in a school.
+over time \fixme{(cite Hinde, 1988)}. In fact, \cite{kanda_interactive_2004}
+also hypothesized that people's attitude toward technological artifacts and
+their relationship with them would evolve over time, and they were among the
+first who described \emph{novelty effects} during a long-term study with an
+interactive robot in a school.
+
+\subsection{Measuring anthropomorphism}
+
+Measuring anthropomorphism is challenging because the phenomenon is partialy
+unconscious, its mediation is largely subject-dependent, and we found the
+phenomenon generally difficult to verbalize for users.
+
+To reduce subjectivity and still accurately account for psychological effects,
+it appears necessary to interleave quantitative and qualitative assessments of
+anthropomorphic effects.
+
+We present in this section the methodology and techniques we have relied on to
+assess anthropomorphic projections in two unrelated studies, the Roomba
+experiment~\cite{fink_living_2013}, and the Dominos experiment.
+
+\paragraph{Quantitative assessment of anthropomorphism} Quantitative data are
+acquired by systematic annotations of human- robot interactions on video records
+of the experiments. Six classes of interactions were identified as reflecting
+active commitment of the users in the interaction (gestures, touches, talk to
+the robot, show something to the robot, misbehave, look at the experimenter
+because worried by the robot's behavior)
+
+\paragraph{Qualitative assessment of anthropomorphism} The main tools for
+qualitative measurement of anthropomorphic effect are questionnaires. We have
+explored both Likert-scale and open questions.
+
+\subsubsection{The Roomba experiment}
+
+\begin{figure*}[htb]
+\centering
+
+\begin{tikzpicture}[scale=0.5, y = 2cm]
+%axis
+\draw (0,0) -- coordinate (x axis mid) (20,0);
+\draw (0,0) -- coordinate (y axis mid) (0,7);
+%ticks
+\foreach \x in {0,4,...,20}
+    \draw (\x,1pt) -- (\x,-3pt);
+\foreach \y in {1,...,7} 
+    \draw[black!20] (20,\y) -- (-3pt,\y);
+\foreach \y in {1,...,7} 
+    \draw (-3pt, \y) node[anchor=east] {\y}; 
+%labels
+\node[below=0.8cm] at (x axis mid) {People's perception ($\sigma=15$)};
+\node at (2, -0.4) {\tiny expectations};
+\node[align=center] at (6, -0.4) {\tiny after\\ \tiny first usage};
+\node[align=center] at (10, -0.4) {\tiny after\\ \tiny 2 weeks};
+\node[align=center] at (14, -0.4) {\tiny after\\ \tiny 2 months};
+\node[align=center] at (18, -0.4) {\tiny after\\ \tiny 6 months};
+
+\draw[dashed, black!50] (6,0) -- (6,7) node[sloped, below, pos=0.25] {\tiny novelty effect};
+
+\draw[ultra thick, red!50] (2,5.6) -- (6,6.1) -- (10,6.3) -- (14,6.3) -- (18,6.1) node at (15,6.5) {\tiny \it ease of use};
+\draw[ultra thick, purple] (2,4.9) -- (6,5.2) -- (10,5.1) -- (14,4.5) -- (18,4.2) node at (3,4.7) {\tiny \it usefulness};
+\draw[ultra thick, blue!50] (2,4) -- (6,4.1) -- (10,4.6) -- (14,4.1) -- (18,4.3) node at (16,4) {\tiny \it fun};
+\draw[ultra thick, green!50] (2,3.9) -- (6,4.1) -- (10,4.2) -- (14,3.8) -- (18,3.3) node at (19,3.5) {\tiny \it intelligence};
+\draw[ultra thick, orange] (2,3.5) -- (6,4.2) -- (10,4) -- (14,3.2) -- (18,2.8) node at (14,2.7) {\tiny \it impact};
+
+\draw[ultra thick, dashed] (2,5.2) -- (6,5.2) -- (10,5) -- (14,4.9) -- (18,4.5) node at (14,5.3) {\tiny \it overall};
+
+\end{tikzpicture}
+
+\caption{User perception of the Roomba robot over a 6 month period
+($\sigma=15$).}
+
+\label{roomba-perception}
+\end{figure*}
+
+\subsubsection{The Ranger experiment}
+
+Questionnaires are analyzed such as points are 
+attributed for key answers, leading to a 
+qualitative score:
+
+\begin{itemize}
+    \item Spontaneously ascribe feelings or states (2 points) {\it Robot is
+        hungry, tired}
+    \item Ascribe ``own will'' (1--3 points) {\it Robot could leave room, does not
+        always obey, could do a b\^{e}tise...}
+    \item View robot as friend (1 point)
+    \item Ascribe cognitive abilities (0.5--1 point) {\it Robot is able to see,
+        able to hear}
+    \item Belief robot has feelings (2 points)
+    \item Give anthropomorphic reasons for
+        \begin{itemize}
+            \item not leaving robot alone (1--3 points) {\it Would be sad when
+                left alone}
+            \item misbehavior (1 point) {\it Robot wants to make a tour, doesn’t
+                like to play any longer}
+        \end{itemize}
+\end{itemize}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.6\columnwidth]{ranger-interactions-per-runs}
+    \caption{Quantitative assessment: here, six interactions modalities have
+        been selected: showing something to the robot ({\tt show}), talking to
+        the robot ({\tt talk}), touching it ({\tt touch}), misbehaving (like
+        shaking it, {\tt mis}), deictic interactions ({\tt ges}), and looking
+        for exterior help by looking at the experimenter ({\tt look}). In each
+        of the 14 experimental runs, we annotate and count the number of
+        occurences of each of these interactions.  Highlighted runs 2.3, 2.4,
+        2.7 and 2.8 correspond to unexpected robot behaviours: we observe peaks
+        of interactions everytime the robot's behaviour changes from expected to
+        unexpected or from unexpected to expected.}
+
+    \label{interactions-per-run}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.6\columnwidth]{ranger-interactions-vs-qualitative-score}
+    \caption{We found a significant negative correlation ($p=0.048$) between the
+    number of interactions and the qualitative anthropomorphic projections
+    ($\sigma=13$).}
+    \label{qualitative-score}
+\end{figure}
+
+\subsection{A Model of the Dynamics of Anthropomorphism}
+\label{sec:dynamics-model}
+
+\paragraph{Why is anthropomorphism likely to change over time?}
+\hl{maybe we need to move this paragraph to PART 3}
+
+\subsection{A Model of the Dynamics of Anthropomorphism}
 
@@
 
-\section{Acknowledgments}
+\section*{Acknowledgments}
 
@@
 
-\section{Bibliography}
+%\section{Bibliography}
 

### 2014-03-18 paper.tex
{Dynamics of Anth... -> The Dynamics of ...}
Moved the Factors of anthropo to end of section 2
Minor sections/subsections fixing
refinements sections 1 and 2

@@
 published~\cite{fink_anthropomorphism_2012} and field
-experiments~\fixme{cites!}, we believe that anthropomorphic effects in HRI are
+experiements~\fixme{cites!}, we believe that anthropomorphic effects in HRI are
 not always the same but evolve over time, along with growing interaction and
 experience with the robot, similar to how relationships among people evolve
-over time \fixme{(cite Hinde, 1988)}. In fact, \cite{kanda_interactive_2004}
-also hypothesized that people's attitude toward technological artifacts and
-their relationship with them would evolve over time, and they were among the
-first who described \emph{novelty effects} during a long-term study with an
-interactive robot in a school.
-
-\subsection{Measuring anthropomorphism}
-
-Measuring anthropomorphism is challenging because the phenomenon is partialy
-unconscious, its mediation is largely subject-dependent, and we found the
-phenomenon generally difficult to verbalize for users.
-
-To reduce subjectivity and still accurately account for psychological effects,
-it appears necessary to interleave quantitative and qualitative assessments of
-anthropomorphic effects.
-
-We present in this section the methodology and techniques we have relied on to
-assess anthropomorphic projections in two unrelated studies, the Roomba
-experiment~\cite{fink_living_2013}, and the Dominos experiment.
-
-\paragraph{Quantitative assessment of anthropomorphism} Quantitative data are
-acquired by systematic annotations of human- robot interactions on video records
-of the experiments. Six classes of interactions were identified as reflecting
-active commitment of the users in the interaction (gestures, touches, talk to
-the robot, show something to the robot, misbehave, look at the experimenter
-because worried by the robot's behavior)
-
-\paragraph{Qualitative assessment of anthropomorphism} The main tools for
-qualitative measurement of anthropomorphic effect are questionnaires. We have
-explored both Likert-scale and open questions.
-
-\subsubsection{The Roomba experiment}
-
-\begin{figure*}[htb]
-\centering
-
-\begin{tikzpicture}[scale=0.5, y = 2cm]
-%axis
-\draw (0,0) -- coordinate (x axis mid) (20,0);
-\draw (0,0) -- coordinate (y axis mid) (0,7);
-%ticks
-\foreach \x in {0,4,...,20}
-    \draw (\x,1pt) -- (\x,-3pt);
-\foreach \y in {1,...,7} 
-    \draw[black!20] (20,\y) -- (-3pt,\y);
-\foreach \y in {1,...,7} 
-    \draw (-3pt, \y) node[anchor=east] {\y}; 
-%labels
-\node[below=0.8cm] at (x axis mid) {People's perception ($\sigma=15$)};
-\node at (2, -0.4) {\tiny expectations};
-\node[align=center] at (6, -0.4) {\tiny after\\ \tiny first usage};
-\node[align=center] at (10, -0.4) {\tiny after\\ \tiny 2 weeks};
-\node[align=center] at (14, -0.4) {\tiny after\\ \tiny 2 months};
-\node[align=center] at (18, -0.4) {\tiny after\\ \tiny 6 months};
-
-\draw[dashed, black!50] (6,0) -- (6,7) node[sloped, below, pos=0.25] {\tiny novelty effect};
-
-\draw[ultra thick, red!50] (2,5.6) -- (6,6.1) -- (10,6.3) -- (14,6.3) -- (18,6.1) node at (15,6.5) {\tiny \it ease of use};
-\draw[ultra thick, purple] (2,4.9) -- (6,5.2) -- (10,5.1) -- (14,4.5) -- (18,4.2) node at (3,4.7) {\tiny \it usefulness};
-\draw[ultra thick, blue!50] (2,4) -- (6,4.1) -- (10,4.6) -- (14,4.1) -- (18,4.3) node at (16,4) {\tiny \it fun};
-\draw[ultra thick, green!50] (2,3.9) -- (6,4.1) -- (10,4.2) -- (14,3.8) -- (18,3.3) node at (19,3.5) {\tiny \it intelligence};
-\draw[ultra thick, orange] (2,3.5) -- (6,4.2) -- (10,4) -- (14,3.2) -- (18,2.8) node at (14,2.7) {\tiny \it impact};
-
-\draw[ultra thick, dashed] (2,5.2) -- (6,5.2) -- (10,5) -- (14,4.9) -- (18,4.5) node at (14,5.3) {\tiny \it overall};
-
-\end{tikzpicture}
-
-\caption{User perception of the Roomba robot over a 6 month period
-($\sigma=15$).}
-
-\label{roomba-perception}
-\end{figure*}
-
-\subsubsection{The Ranger experiment}
-
-Questionnaires are analyzed such as points are 
-attributed for key answers, leading to a 
-qualitative score:
-
-\begin{itemize}
-    \item Spontaneously ascribe feelings or states (2 points) {\it Robot is
-        hungry, tired}
-    \item Ascribe ``own will'' (1--3 points) {\it Robot could leave room, does not
-        always obey, could do a b\^{e}tise...}
-    \item View robot as friend (1 point)
-    \item Ascribe cognitive abilities (0.5--1 point) {\it Robot is able to see,
-        able to hear}
-    \item Belief robot has feelings (2 points)
-    \item Give anthropomorphic reasons for
-        \begin{itemize}
-            \item not leaving robot alone (1--3 points) {\it Would be sad when
-                left alone}
-            \item misbehavior (1 point) {\it Robot wants to make a tour, doesn’t
-                like to play any longer}
-        \end{itemize}
-\end{itemize}
-
-\begin{figure}
-    \centering
-    \includegraphics[width=0.6\columnwidth]{ranger-interactions-per-runs}
-    \caption{Quantitative assessment: here, six interactions modalities have
-        been selected: showing something to the robot ({\tt show}), talking to
-        the robot ({\tt talk}), touching it ({\tt touch}), misbehaving (like
-        shaking it, {\tt mis}), deictic interactions ({\tt ges}), and looking
-        for exterior help by looking at the experimenter ({\tt look}). In each
-        of the 14 experimental runs, we annotate and count the number of
-        occurences of each of these interactions.  Highlighted runs 2.3, 2.4,
-        2.7 and 2.8 correspond to unexpected robot behaviours: we observe peaks
-        of interactions everytime the robot's behaviour changes from expected to
-        unexpected or from unexpected to expected.}
-
-    \label{interactions-per-run}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \includegraphics[width=0.6\columnwidth]{ranger-interactions-vs-qualitative-score}
-    \caption{We found a significant negative correlation ($p=0.048$) between the
-    number of interactions and the qualitative anthropomorphic projections
-    ($\sigma=13$).}
-    \label{qualitative-score}
-\end{figure}
-
-\subsection{A Model of the Dynamics of Anthropomorphism}
-\label{sec:dynamics-model}
-
-\paragraph{Why is anthropomorphism likely to change over time?}
-\hl{maybe we need to move this paragraph to PART 3}
+over time \fixme{(cite Hinde, 1988)}. In fact, Kanda \textit{et al.}
+\cite{kanda_interactive_2004} also hypothesized that people's attitude toward
+technological artifacts and their relationship with them would evolve over
+time, and they were among the first who described \textit{novelty effects}
+during a long-term study with an interactive robot in a school.
 

### 2014-03-18 paper.tex
Added a comment of the figure 'qualitative score vs interactions'

--- 2014-03-18 paper.tex
@@
 
-\title[Dynamics of Anthropomorphism]{Dynamics of Anthropomorphic Effects in Human-Robot Interaction}
+\title[The Dynamics of Anthropomorphism]{The Dynamics of Anthropomorphic Effects in Human-Robot Interaction}
 \author[\firstAuthorLast ]{\Authors}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-%
-%
-%				PART 2: OUR IDEAS -- A DYNAMIC PHENOMENON
-%
-%
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-% SEVERIN & JULIA: there will be 2-3 subsections in which we present our ideas:
-% 	1) anthropomorphism is a multi-factor phenomenon (the figure with the several factors)
-%	2) anthropomorphism is dynamic (the dynamic curve model)
-%
-%
-
-\section{Anthropomorphism as a multi-factor phenomenon ...}
+\subsection{Summary: Anthropomorphism as a multi-factor phenomenon}
 \label{sec:multi-factors}
@@
 
-\section{... that evolves over time}
-\label{sec:dynamics-model}
-
-\paragraph{Why is anthropomorphism likely to change over time?}
-\hl{maybe we need to move this paragraph to PART 3}
+\begin{figure}
+    \centering
+    \includegraphics[width=0.6\columnwidth]{factors}
+    \caption{}
+    \label{factors}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+%
+%
+%				PART 2: OUR IDEAS -- A DYNAMIC PHENOMENON
+%
+%
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+% SEVERIN & JULIA: there will be 2-3 subsections in which we present our ideas:
+% 	1) anthropomorphism is a multi-factor phenomenon (the figure with the several factors)
+%	2) anthropomorphism is dynamic (the dynamic curve model)
+%
+%
+
+\section{Anthropomorphism: a dynamic phenomenon}
+\label{sec:our-ideas}
 
@@
 
-Measuring anthropomorphism is challenging because the phenomenon is partialy
-unconscious, its mediation is largely subject-dependent, and we found the
+Measuring anthropomorphism is challenging because the phenomenon is partially
+unconscious, its mediation is largely subject-dependent\fxnote{Should we put
+here different interaction profiles from the Ranger study?}, and we found the
 phenomenon generally difficult to verbalize for users.
@@
                 left alone}
-            \item misbehavior (1 point) {\it Robot wants to make a tour, doesn’t
+            \item misbehavior (1 point) {\it Robot wants to make a tour, doesn't
                 like to play any longer}
@@
         of the 14 experimental runs, we annotate and count the number of
-        occurences of each of these interactions.  Highlighted runs 2.3, 2.4,
+        occurrences of each of these interactions.  Highlighted runs 2.3, 2.4,
         2.7 and 2.8 correspond to unexpected robot behaviours: we observe peaks
-        of interactions everytime the robot's behaviour changes from expected to
+        of interactions every time the robot's behaviour changes from expected to
         unexpected or from unexpected to expected.}
@@
 \end{figure}
+
+Fig.~\ref{qualitative-score} plots the qualitative vs quantitative assessment of
+anthropomorphic effects during the \emph{Dominos} experiment: the correlation is
+negative. The more the children interacted with the robot, the less they
+projected anthropomorphic traits on the robot. We also note a remarkable cluster
+of seven groups of children who did not interact much with the robot, but had a
+strongly anthropomorphic perception of the robot. This may initially look
+counter-intuitive (one could hypothesize that the more playful the children are
+with the robot, the more likely they are to consider it as a friend/pet/lively
+being) and we discuss at section~\ref{sec:cognition-neuroscience} possible
+cognitive explanations.
 
@@
 
-\subsection{Initialization Phase}
+\subsubsection{Initialization Phase}
 \label{sec:initialization}
@@
 
-\subsection{Familiarization Phase}
+\subsubsection{Familiarization Phase}
 \label{sec:familiarization}
@@
 
-\subsection{Stabilization Phase}
+\subsubsection{Stabilization Phase}
 \label{sec:stabilization}

### 2014-03-18 paper.tex
Fixed again subsectionning
Moved section on Disruptive behaviours to section on Dynamics of Anthropo
Split the section on Measuring anthropo into the introduction ('few results from the field') and the discussion 'measuring anthropo')

@@
 
-\section*{Introduction and overview}
+\section{Introduction and overview}
 \label{sec:intro}
 
-The essence of anthropomorphism is the perception of human-like characteristics in either real or imagined non-human agents.
-In Human-Robot Interaction (HRI), anthropomorphism is a commonly observed phenomenon: people tend to ascribe human-like characteristics to robots, and they are willing to treat and react to robots as if they were human-social counterparts.
-The HRI and social robotics literature is full of various kinds of studies showing how humans readily interact in a social fashion with robots -- despite the fact that robots are not humans.
-In our own studies on HRI analysis in real-world settings, we also observed anthropomorphism.
-However, we found qualitative differences and dynamics over time in how participants anthropomorphized and related to the robots used in our studies.
-More concretely, we found that anthropomorphism was not only based on how much the robot resembles a human (anthropomorphic design) but that it was determined by multiple factors, including individual characteristics of the human user, and the context of use, for instance.
-We also found that anthropomorphism changed over time with growing experience of the user with the system.
-By trying to understand these variances and dynamics in anthropomorphism, we reviewed related work from the HRI domain and social robotics.
-Despite the fact that there is a vast amount of literature on anthropomorphism in HRI, we were surprised to find that other studies do not describe similar variances or dynamics.
-Instead, we came across diverse and partially conflicting understandings of anthropomorphism.
-We also had the impression that the reported data were sometimes over-interpreted (probably due to the confusion of what exactly anthropomorphism is) or obtained in settings and assessed in ways that we believe do not give enough consideration to the complex nature of anthropomorphism.
-However, when reviewing literature from social psychology, cognitive science, and neuroscience, we found support for the variances and dynamics in anthropomorphism that we observed in our studies.
-As HRI integrates many disciplines, we think that it is valid to use theories from these related domains for interpreting our results and that it is relevant to report on this integration.
-
-In this article, we would like to share some critical but constructive considerations on anthropomorphism in robotics and HRI.
-Thereby, we contribute to a better understanding of this complex phenomenon related to robots.
-In Section \ref{sec:anthropomorphism} we would first like to give an overview of how anthropomorphism can be defined, and then, in Section \ref{sec:explanations} present explanations to the question why people anthropomorphize, with a focus on anthropomorphism as a social phenomenon in HRI and the trend to design human-like robots.
-Then, based on these reviews of theories and concepts from related domains, in Section \ref{sec:multi-factors} we propose that anthropomorphism is determined and affected by multiple factors.
-We outline how anthropomorphism as a multi-factor phenomenon can impact the user experience and acceptance of robots in daily life environments.
-Next, in Section \ref{sec:dynamics-model} we suggest that anthropomorphism changes over time, and describe these changes in an initial model that we call ``Dynamics of Anthropomorphism''.
-We illustrate our idea with empirical findings from several HRI studies that we conducted in natural environments.
-In Section \ref{sec:cognition-neuroscience} we present a cognitive and neuroscience perspective on anthropomorphism to consolidate our considerations and the observed dynamics.
-Next, Section \ref{sec:discussion} considers limitations in our approach and we discuss existing and alternative ways to measure anthropomorphism in HRI.
-Finally, in Section \ref{sec:conclusion} we conclude this article.
+The essence of anthropomorphism is the perception of human-like characteristics
+in either real or imagined non-human agents. In Human-Robot Interaction (HRI),
+anthropomorphism is a commonly observed phenomenon: people tend to ascribe
+human-like characteristics to robots, and they are willing to treat and react to
+robots as if they were human-social counterparts. The HRI and social robotics
+literature is full of various kinds of studies showing how humans readily
+interact in a social fashion with robots -- despite the fact that robots are not
+humans. In our own studies on HRI analysis in real-world settings, we also
+observed anthropomorphism. However, we found qualitative differences and
+dynamics over time in how participants anthropomorphized and related to the
+robots used in our studies. More concretely, we found that anthropomorphism was
+not only based on how much the robot resembles a human (anthropomorphic design)
+but that it was determined by multiple factors, including individual
+characteristics of the human user, and the context of use, for instance. We also
+found that anthropomorphism changed over time with growing experience of the
+user with the system. By trying to understand these variances and dynamics in
+anthropomorphism, we reviewed related work from the HRI domain and social
+robotics. Despite the fact that there is a vast amount of literature on
+anthropomorphism in HRI, we were surprised to find that other studies do not
+describe similar variances or dynamics. Instead, we came across diverse and
+partially conflicting understandings of anthropomorphism. We also had the
+impression that the reported data were sometimes over-interpreted (probably due
+to the confusion of what exactly anthropomorphism is) or obtained in settings
+and assessed in ways that we believe do not give enough consideration to the
+complex nature of anthropomorphism. However, when reviewing literature from
+social psychology, cognitive science, and neuroscience, we found support for the
+variances and dynamics in anthropomorphism that we observed in our studies. As
+HRI integrates many disciplines, we think that it is valid to use theories from
+these related domains for interpreting our results and that it is relevant to
+report on this integration.
+
+In this article, we would like to share some critical but constructive
+considerations on anthropomorphism in robotics and HRI. Thereby, we contribute
+to a better understanding of this complex phenomenon related to robots. In
+Section \ref{sec:anthropomorphism} we would first like to give an overview of
+how anthropomorphism can be defined, and then, in Section \ref{sec:explanations}
+present explanations to the question why people anthropomorphize, with a focus
+on anthropomorphism as a social phenomenon in HRI and the trend to design
+human-like robots. Then, based on these reviews of theories and concepts from
+related domains, in Section \ref{sec:multi-factors} we propose that
+anthropomorphism is determined and affected by multiple factors. We outline how
+anthropomorphism as a multi-factor phenomenon can impact the user experience and
+acceptance of robots in daily life environments. Next, in Section
+\ref{sec:dynamics-model} we suggest that anthropomorphism changes over time, and
+describe these changes in an initial model that we call ``Dynamics of
+Anthropomorphism''. We illustrate our idea with empirical findings from several
+HRI studies that we conducted in natural environments. In Section
+\ref{sec:cognition-neuroscience} we present a cognitive and neuroscience
+perspective on anthropomorphism to consolidate our considerations and the
+observed dynamics. Next, Section \ref{sec:discussion} considers limitations in
+our approach and we discuss existing and alternative ways to measure
+anthropomorphism in HRI. Finally, in Section \ref{sec:conclusion} we conclude
+this article.
+
+\subsection{A few results from the field}
+
+\subsubsection{The Roomba experiment}
+
+\begin{figure*}[htb]
+\centering
+
+\begin{tikzpicture}[scale=0.5, y = 2cm]
+%axis
+\draw (0,0) -- coordinate (x axis mid) (20,0);
+\draw (0,0) -- coordinate (y axis mid) (0,7);
+%ticks
+\foreach \x in {0,4,...,20}
+    \draw (\x,1pt) -- (\x,-3pt);
+\foreach \y in {1,...,7} 
+    \draw[black!20] (20,\y) -- (-3pt,\y);
+\foreach \y in {1,...,7} 
+    \draw (-3pt, \y) node[anchor=east] {\y}; 
+%labels
+\node[below=0.8cm] at (x axis mid) {People's perception ($\sigma=15$)};
+\node at (2, -0.4) {\tiny expectations};
+\node[align=center] at (6, -0.4) {\tiny after\\ \tiny first usage};
+\node[align=center] at (10, -0.4) {\tiny after\\ \tiny 2 weeks};
+\node[align=center] at (14, -0.4) {\tiny after\\ \tiny 2 months};
+\node[align=center] at (18, -0.4) {\tiny after\\ \tiny 6 months};
+
+\draw[dashed, black!50] (6,0) -- (6,7) node[sloped, below, pos=0.25] {\tiny novelty effect};
+
+\draw[ultra thick, red!50] (2,5.6) -- (6,6.1) -- (10,6.3) -- (14,6.3) -- (18,6.1) node at (15,6.5) {\tiny \it ease of use};
+\draw[ultra thick, purple] (2,4.9) -- (6,5.2) -- (10,5.1) -- (14,4.5) -- (18,4.2) node at (3,4.7) {\tiny \it usefulness};
+\draw[ultra thick, blue!50] (2,4) -- (6,4.1) -- (10,4.6) -- (14,4.1) -- (18,4.3) node at (16,4) {\tiny \it fun};
+\draw[ultra thick, green!50] (2,3.9) -- (6,4.1) -- (10,4.2) -- (14,3.8) -- (18,3.3) node at (19,3.5) {\tiny \it intelligence};
+\draw[ultra thick, orange] (2,3.5) -- (6,4.2) -- (10,4) -- (14,3.2) -- (18,2.8) node at (14,2.7) {\tiny \it impact};
+
+\draw[ultra thick, dashed] (2,5.2) -- (6,5.2) -- (10,5) -- (14,4.9) -- (18,4.5) node at (14,5.3) {\tiny \it overall};
+
+\end{tikzpicture}
+
+\caption{User perception of the Roomba robot over a 6 month period
+($\sigma=15$).}
+
+\label{roomba-perception}
+\end{figure*}
+
+\subsubsection{The Ranger experiment}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.6\columnwidth]{ranger-interactions-per-runs}
+    \caption{Quantitative assessment: here, six interactions modalities have
+        been selected: showing something to the robot ({\tt show}), talking to
+        the robot ({\tt talk}), touching it ({\tt touch}), misbehaving (like
+        shaking it, {\tt mis}), deictic interactions ({\tt ges}), and looking
+        for exterior help by looking at the experimenter ({\tt look}). In each
+        of the 14 experimental runs, we annotate and count the number of
+        occurrences of each of these interactions.  Highlighted runs 2.3, 2.4,
+        2.7 and 2.8 correspond to unexpected robot behaviours: we observe peaks
+        of interactions every time the robot's behaviour changes from expected to
+        unexpected or from unexpected to expected.}
+
+    \label{interactions-per-run}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.6\columnwidth]{ranger-interactions-vs-qualitative-score}
+    \caption{We found a significant negative correlation ($p=0.048$) between the
+    number of interactions and the qualitative anthropomorphic projections
+    ($\sigma=13$).}
+    \label{qualitative-score}
+\end{figure}
+
+Figure~\ref{qualitative-score} plots the qualitative vs quantitative assessment of
+anthropomorphic effects during the \emph{Dominos} experiment: the correlation is
+negative. The more the children interacted with the robot, the less they
+projected anthropomorphic traits on the robot. We also note a remarkable cluster
+of seven groups of children who did not interact much with the robot, but had a
+strongly anthropomorphic perception of the robot. This may initially look
+counter-intuitive (one could hypothesize that the more playful the children are
+with the robot, the more likely they are to consider it as a friend/pet/lively
+being) and we discuss at section~\ref{sec:cognition-neuroscience} possible
+cognitive explanations.
+
+\subsection{Towards an understanding of anthropomorphism}
+
+\fxnote{state here our main research hypothesis}
+\fxnote{state here our main contributions}
+\fxnote{Introduce the remainder of the paper}
 
@@
 
-\section{Why do people anthropomorphize?}
+\subsection{Why do people anthropomorphize?}
 \label{sec:explanations}
@@
 
-\subsection{Measuring anthropomorphism}
-
-Measuring anthropomorphism is challenging because the phenomenon is partially
-unconscious, its mediation is largely subject-dependent\fxnote{Should we put
-here different interaction profiles from the Ranger study?}, and we found the
-phenomenon generally difficult to verbalize for users.
-
-To reduce subjectivity and still accurately account for psychological effects,
-it appears necessary to interleave quantitative and qualitative assessments of
-anthropomorphic effects.
-
-We present in this section the methodology and techniques we have relied on to
-assess anthropomorphic projections in two unrelated studies, the Roomba
-experiment~\cite{fink_living_2013}, and the Dominos experiment.
-
-\paragraph{Quantitative assessment of anthropomorphism} Quantitative data are
-acquired by systematic annotations of human- robot interactions on video records
-of the experiments. Six classes of interactions were identified as reflecting
-active commitment of the users in the interaction (gestures, touches, talk to
-the robot, show something to the robot, misbehave, look at the experimenter
-because worried by the robot's behavior)
-
-\paragraph{Qualitative assessment of anthropomorphism} The main tools for
-qualitative measurement of anthropomorphic effect are questionnaires. We have
-explored both Likert-scale and open questions.
-
-\subsubsection{The Roomba experiment}
-
-\begin{figure*}[htb]
-\centering
-
-\begin{tikzpicture}[scale=0.5, y = 2cm]
-%axis
-\draw (0,0) -- coordinate (x axis mid) (20,0);
-\draw (0,0) -- coordinate (y axis mid) (0,7);
-%ticks
-\foreach \x in {0,4,...,20}
-    \draw (\x,1pt) -- (\x,-3pt);
-\foreach \y in {1,...,7} 
-    \draw[black!20] (20,\y) -- (-3pt,\y);
-\foreach \y in {1,...,7} 
-    \draw (-3pt, \y) node[anchor=east] {\y}; 
-%labels
-\node[below=0.8cm] at (x axis mid) {People's perception ($\sigma=15$)};
-\node at (2, -0.4) {\tiny expectations};
-\node[align=center] at (6, -0.4) {\tiny after\\ \tiny first usage};
-\node[align=center] at (10, -0.4) {\tiny after\\ \tiny 2 weeks};
-\node[align=center] at (14, -0.4) {\tiny after\\ \tiny 2 months};
-\node[align=center] at (18, -0.4) {\tiny after\\ \tiny 6 months};
-
-\draw[dashed, black!50] (6,0) -- (6,7) node[sloped, below, pos=0.25] {\tiny novelty effect};
-
-\draw[ultra thick, red!50] (2,5.6) -- (6,6.1) -- (10,6.3) -- (14,6.3) -- (18,6.1) node at (15,6.5) {\tiny \it ease of use};
-\draw[ultra thick, purple] (2,4.9) -- (6,5.2) -- (10,5.1) -- (14,4.5) -- (18,4.2) node at (3,4.7) {\tiny \it usefulness};
-\draw[ultra thick, blue!50] (2,4) -- (6,4.1) -- (10,4.6) -- (14,4.1) -- (18,4.3) node at (16,4) {\tiny \it fun};
-\draw[ultra thick, green!50] (2,3.9) -- (6,4.1) -- (10,4.2) -- (14,3.8) -- (18,3.3) node at (19,3.5) {\tiny \it intelligence};
-\draw[ultra thick, orange] (2,3.5) -- (6,4.2) -- (10,4) -- (14,3.2) -- (18,2.8) node at (14,2.7) {\tiny \it impact};
-
-\draw[ultra thick, dashed] (2,5.2) -- (6,5.2) -- (10,5) -- (14,4.9) -- (18,4.5) node at (14,5.3) {\tiny \it overall};
-
-\end{tikzpicture}
-
-\caption{User perception of the Roomba robot over a 6 month period
-($\sigma=15$).}
-
-\label{roomba-perception}
-\end{figure*}
-
-\subsubsection{The Ranger experiment}
-
-Questionnaires are analyzed such as points are 
-attributed for key answers, leading to a 
-qualitative score:
-
-\begin{itemize}
-    \item Spontaneously ascribe feelings or states (2 points) {\it Robot is
-        hungry, tired}
-    \item Ascribe ``own will'' (1--3 points) {\it Robot could leave room, does not
-        always obey, could do a b\^{e}tise...}
-    \item View robot as friend (1 point)
-    \item Ascribe cognitive abilities (0.5--1 point) {\it Robot is able to see,
-        able to hear}
-    \item Belief robot has feelings (2 points)
-    \item Give anthropomorphic reasons for
-        \begin{itemize}
-            \item not leaving robot alone (1--3 points) {\it Would be sad when
-                left alone}
-            \item misbehavior (1 point) {\it Robot wants to make a tour, doesn't
-                like to play any longer}
-        \end{itemize}
-\end{itemize}
-
-\begin{figure}
-    \centering
-    \includegraphics[width=0.6\columnwidth]{ranger-interactions-per-runs}
-    \caption{Quantitative assessment: here, six interactions modalities have
-        been selected: showing something to the robot ({\tt show}), talking to
-        the robot ({\tt talk}), touching it ({\tt touch}), misbehaving (like
-        shaking it, {\tt mis}), deictic interactions ({\tt ges}), and looking
-        for exterior help by looking at the experimenter ({\tt look}). In each
-        of the 14 experimental runs, we annotate and count the number of
-        occurrences of each of these interactions.  Highlighted runs 2.3, 2.4,
-        2.7 and 2.8 correspond to unexpected robot behaviours: we observe peaks
-        of interactions every time the robot's behaviour changes from expected to
-        unexpected or from unexpected to expected.}
-
-    \label{interactions-per-run}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \includegraphics[width=0.6\columnwidth]{ranger-interactions-vs-qualitative-score}
-    \caption{We found a significant negative correlation ($p=0.048$) between the
-    number of interactions and the qualitative anthropomorphic projections
-    ($\sigma=13$).}
-    \label{qualitative-score}
-\end{figure}
-
-Fig.~\ref{qualitative-score} plots the qualitative vs quantitative assessment of
-anthropomorphic effects during the \emph{Dominos} experiment: the correlation is
-negative. The more the children interacted with the robot, the less they
-projected anthropomorphic traits on the robot. We also note a remarkable cluster
-of seven groups of children who did not interact much with the robot, but had a
-strongly anthropomorphic perception of the robot. This may initially look
-counter-intuitive (one could hypothesize that the more playful the children are
-with the robot, the more likely they are to consider it as a friend/pet/lively
-being) and we discuss at section~\ref{sec:cognition-neuroscience} possible
-cognitive explanations.
-
 \subsection{A Model of the Dynamics of Anthropomorphism}
@@
 
+\subsection{Role of disruptive behaviors}
+\label{sec:disruptive}
+
+Common observation of naive people (children or adults) interacting with robots
+shows that unexpected behaviors of the robot can have a notable impact on
+interaction. \hl{cite literature, e.g. cheating robot, disagreeing, disobeying,
+HRI2013 paper}
+
+During a normal interaction with the robot, the user iteratively refines his/her
+own model of the behavior of the robot. As explained in previous sections, as
+the user improves his/her model of the robot's actions, he/she also improves the
+ability to predict the actions and thus, the user tends to anthropomorphize
+less.
+
+We emit the hypothesis that an unexpected robot behavior might lead the user to
+suddenly restate his/her behavioral model of the robot and will temporarily lead
+to an increase of the level of anthropomorphism (depicted by the spikes on
+Figure~\ref{fig:dynamics}).
+
+\begin{figure}\footnotesize
+    \centering
+    \begin{tabular}{  >{\centering\arraybackslash}m{2cm} | >{\centering\arraybackslash}m{2cm} | >{\centering\arraybackslash}m{2cm} }
+     & Unplanned by the robot & Planned by the robot \\ \hline
+    Perceived as non-intentional & case I  & case IIIa  \\ \hline
+    Perceived as intentional &  case IIIb & case II 
+    \end{tabular}
+\caption{
+    Behaviors of the robot that are unexpected by the user may be intentional
+    (the robot has planned the behavior) or not (typically, a failure:
+    misdetection, bug,...). Independently of that, the behavior may be
+    \emph{perceived} by the user as intentional or not.}
+\label{fig:perceptionUnexpectedBehavior}
+\end{figure}
+
+When talking about \emph{unexpected robot behaviors}, several distinct cases
+must however be considered, summarized in
+Table~\ref{fig:perceptionUnexpectedBehavior}.
+
+If the unexpected behavior is not planned, and perceived as such by the human
+(case I), the human can interpret that the robot is able to fail. If the robot
+explicitly states its failure (for instance, by saying ``I'm lost!''), the
+behavior is then called \emph{transparent} \fixme{cite here, Julia?}
+\hl{(literature on transparency)}, and the user may besides hypothesize that the
+robot has \emph{introspective} capabilities (it can reflect on its own internal
+state), which in turn may leads to higher anthropomorphism level.  On the
+contrary, if the robot shows no sign of recognizing its own failure, the user
+may ascribe a lower level of anthropomorphism to the robot.
+
+In case II, the robot voluntary executes a behavior that is unexpected by the
+human, and the human perceives it rightfully as an \emph{intentional} behavior.
+For instance, the human asks the robot to go somewhere, and the robot refuses,
+saying ``I do not want to go there''. In that case, we expect to see an increase
+of anthropomorphism attribution due to the human ascribing intentionality to the
+robot.
+
+Case IIIa and IIIb correspond to misinterpretations of the robot behavior. Case
+IIIb may actually lead to an increased level of anthropomorphism since the human
+will (wrongfully) attribute intentionality to the robot, while case IIIa is
+expected to lead to a lower anthropomorphism level.  However, in those two
+cases, the next occurrence of an expected behavior, if correctly interpreted
+(case I or II), is likely to lead to stronger effects due to a larger delta
+between expectations and actual observed behavior. \hl{(we actually assume that
+anthropomorphism can be radically changing and be a very spontaneous
+"reaction".)}
+
+%% experience -> unexpected behavior should not impact the interaction child-robot BEFORE the theory of mind is established!
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\subsection{Role of disruptive behaviors}
-\label{sec:disruptive}
-
-Common observation of naive people (children or adults) interacting with robots
-shows that unexpected behaviors of the robot can have a notable impact on
-interaction. \hl{cite literature, e.g. cheating robot, disagreeing, disobeying,
-HRI2013 paper}
-
-During a normal interaction with the robot, the user iteratively refines his/her
-own model of the behavior of the robot. As explained in previous sections, as
-the user improves his/her model of the robot's actions, he/she also improves the
-ability to predict the actions and thus, the user tends to anthropomorphize
-less.
-
-We emit the hypothesis that an unexpected robot behavior might lead the user to
-suddenly restate his/her behavioral model of the robot and will temporarily lead
-to an increase of the level of anthropomorphism (depicted by the spikes on
-Figure~\ref{fig:dynamics}).
-
-\begin{figure}\footnotesize
-    \begin{tabular}{  >{\centering\arraybackslash}m{2cm} | >{\centering\arraybackslash}m{2cm} | >{\centering\arraybackslash}m{2cm} }
-     & Unplanned by the robot & Planned by the robot \\ \hline
-    Perceived as non-intentional & case I  & case IIIa  \\ \hline
-    Perceived as intentional &  case IIIb & case II 
-    \end{tabular}
-\caption{
-    Behaviors of the robot that are unexpected by the user may be intentional
-    (the robot has planned the behavior) or not (typically, a failure:
-    misdetection, bug,...). Independently of that, the behavior may be
-    \emph{perceived} by the user as intentional or not.}
-\label{fig:perceptionUnexpectedBehavior}
-\end{figure}
-
-When talking about \emph{unexpected robot behaviors}, several distinct cases
-must however be considered, summarized in
-Table~\ref{fig:perceptionUnexpectedBehavior}.
-
-If the unexpected behavior is not planned, and perceived as such by the human
-(case I), the human can interpret that the robot is able to fail. If the robot
-explicitly states its failure (for instance, by saying ``I'm lost!''), the
-behavior is then called \emph{transparent} \fixme{cite here, Julia?}
-\hl{(literature on transparency)}, and the user may besides hypothesize that the
-robot has \emph{introspective} capabilities (it can reflect on its own internal
-state), which in turn may leads to higher anthropomorphism level.  On the
-contrary, if the robot shows no sign of recognizing its own failure, the user
-may ascribe a lower level of anthropomorphism to the robot.
-
-In case II, the robot voluntary executes a behavior that is unexpected by the
-human, and the human perceives it rightfully as an \emph{intentional} behavior.
-For instance, the human asks the robot to go somewhere, and the robot refuses,
-saying ``I do not want to go there''. In that case, we expect to see an increase
-of anthropomorphism attribution due to the human ascribing intentionality to the
-robot.
-
-Case IIIa and IIIb correspond to misinterpretations of the robot behavior. Case
-IIIb may actually lead to an increased level of anthropomorphism since the human
-will (wrongfully) attribute intentionality to the robot, while case IIIa is
-expected to lead to a lower anthropomorphism level.  However, in those two
-cases, the next occurrence of an expected behavior, if correctly interpreted
-(case I or II), is likely to lead to stronger effects due to a larger delta
-between expectations and actual observed behavior. \hl{(we actually assume that
-anthropomorphism can be radically changing and be a very spontaneous
-"reaction".)}
-
-%% experience -> unexpected behavior should not impact the interaction child-robot BEFORE the theory of mind is established!
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-This interpretation of anthropomorphism in terms of cognitive correlates opens
-questions that we hope could be fruitfully discussed during the workshop.  By
-adopting both a cognitive and a dynamic perspective on the anthropomorphic bonds
-that establish between a robot and a human during an interaction, some
+\subsection{General observations}
+
+By adopting both a cognitive and a dynamic perspective on the anthropomorphic
+bonds that establish between a robot and a human during an interaction, some
 observations can be raised.
@@
 
-\paragraph*{How to measure anthropomorphism?}
-
-As anthropomorphism emerges from an interaction between a human and a non-human agent, we believe that showing pictures of different kinds of robots and then using questionnaires to measure anthropomorphism is somehow limited.
-We discuss what tools and measurements could be used to study anthropomorphism and its dynamics in interaction studies in real-world environments.
+\subsection{Measuring anthropomorphism}
+
+\fxwarning{To be completed/rephrased into a discussion}
+
+Measuring anthropomorphism is challenging because the phenomenon is partially
+unconscious, its mediation is largely subject-dependent\fxnote{Should we put
+here different interaction profiles from the Ranger study?}, and we found the
+phenomenon generally difficult to verbalize for users.
+
+To reduce subjectivity and still accurately account for psychological effects,
+it appears necessary to interleave quantitative and qualitative assessments of
+anthropomorphic effects.
+
+We present in this section the methodology and techniques we have relied on to
+assess anthropomorphic projections in two unrelated studies, the Roomba
+experiment~\cite{fink_living_2013}, and the Dominos experiment.
+
+\paragraph{Quantitative assessment of anthropomorphism} Quantitative data are
+acquired by systematic annotations of human- robot interactions on video records
+of the experiments. Six classes of interactions were identified as reflecting
+active commitment of the users in the interaction (gestures, touches, talk to
+the robot, show something to the robot, misbehave, look at the experimenter
+because worried by the robot's behavior)
+
+\paragraph{Qualitative assessment of anthropomorphism} The main tools for
+qualitative measurement of anthropomorphic effect are questionnaires. We have
+explored both Likert-scale and open questions. In the Dominos experiment,
+questionnaires were analyzed such as points are attributed for key answers,
+leading to a qualitative score:
+
+\begin{itemize}
+    \item Spontaneously ascribe feelings or states (2 points) {\it Robot is
+        hungry, tired}
+    \item Ascribe ``own will'' (1--3 points) {\it Robot could leave room, does not
+        always obey, could do a b\^{e}tise...}
+    \item View robot as friend (1 point)
+    \item Ascribe cognitive abilities (0.5--1 point) {\it Robot is able to see,
+        able to hear}
+    \item Belief robot has feelings (2 points)
+    \item Give anthropomorphic reasons for
+        \begin{itemize}
+            \item not leaving robot alone (1--3 points) {\it Would be sad when
+                left alone}
+            \item misbehavior (1 point) {\it Robot wants to make a tour, doesn't
+                like to play any longer}
+        \end{itemize}
+\end{itemize}
 

### 2014-03-18 paper.tex
Imported section on novelty effect for previous HRI paper

@@
 
-TDB
+To illustrate how the novelty of a robot can evoke anthropomorphic effects, we
+present an example from our long-term ethnographic study with Roomba vacuum
+cleaning robots in households. The observed scenario describes how an elderly
+woman (71 years, living on her own with a little dog in a small row house) was
+setting up and using the robot for the first time for about 10 minutes.
+
+The woman (E.) is reading aloud parts of the "quick start manual": \emph{"When
+Roomba senses dirt, the blue dirt detect light is lit and Roomba cleans more
+intensely in that area."} She laughs and turns to the robot, talking directly to
+it \emph{"Today you can light up darling!"}. E. carries Roomba to the entrance
+door and puts it on the floor [floor type: tiles, partially covered with little
+Persian carpets], she explains \emph{"It has to start from here, this is where
+you enter the house!"}. After pressing the CLEAN button, the robot quickly gets
+stuck with the carpet in the entrance hall, consequently it reports error 1 [
+two-tone "Uh-Oh" sound followed by a narrated voice that starts off with "Error
+1"]. E. is very surprised \emph{"What, it is even talking to me?"}, lifts the
+robot off and puts it back for cleaning. At several occasions, while watching
+how the robot moves around and cleans, E. makes compliments to the robot:
+\emph{"Nice!"} or \emph{"Good job!"} or \emph{"Bravo!"}. Once, when Roomba turns
+right in front of some crumbs on the kitchen floor and moves away without
+cleaning them up, E. says: \emph{"There you forgot something, what is with over
+there? Look, there you still have something to clean up!"}, and she points at
+where she wants Roomba to go. Further, she uses directing gestures and tells the
+robot: \emph{"No, go this way! Come over here!"}. The woman keeps observing the
+robot and wonders about its "intentions", asking it directly: \emph{"Why do you
+leave the kitchen? There is still something there on the fringe!"}. E. turns to
+the experimenter, and tells her: \emph{"She [the robot] loves the hall!"}.
+
+Besides this behavior of generally anthropomorphizing the robot, we observe the
+following concrete instances as anthropomorphic effects in this scenario:
+talking directly to the robot, or asking it questions (though it doesn't
+recognize speech); giving it nick-names or ascribing a gender (\emph{"darling"}
+/ \emph{"she"}); praising the robot (\emph{"Good job!"}); using pointing
+gestures toward the robot, or try to direct it around with commands; attributing
+a personal preference / intention to the robot (\emph{"she loves the hall!"}).
+
+During the following visits at the woman's place, she did not talk to the robot
+anymore, and generally behaved in a less anthropomorphizing way. This is why we
+suspect the observed effects were due to the novelty of the robot.
 

### 2014-03-18 paper.tex
Reshaped the diagram of cognitive phases

@@
 %\resizebox{\linewidth}{!}{
-\begin{tikzpicture}[scale=1.2, transform shape]
+\begin{tikzpicture}
 \baselineskip=8pt
 
-% horizontal axis
-\draw[->] (0,0) -- (10,0) node[anchor=north] {$t$};
-% labels
-\draw   (2,0) node[anchor=north] {Phase I}
-        (5,0) node[anchor=north] {Phase II}
-        (8,0) node[anchor=north] {Phase III};
-
-\draw[dotted] (3.5, -0.5) -- (3.5,6);
-\draw[dotted] (6.5, -0.5) -- (6.5,6);
-
-% vertical axis
-\draw[-|] (0,0) -- (0,6) node[anchor=east] {};
+\path[fill=gray!20] (0,0) rectangle (10.5,2);
+\path[fill=gray!50] (0,2) rectangle (10.5,4);
+\path[fill=gray!20] (0,4) rectangle (10.5,6);
+
+\draw (-0.3,1) node[rotate=90] {Level 1}
+      (-0.3,3) node[rotate=90] {Level 2}
+      (-0.3,5) node[rotate=90] {Level 3};
+
+\draw[->] (0,0) -- (11,0) node[anchor=north] {$t$};
+\draw[-|] (0,0) -- (0,6.5) node[anchor=east] {};
 % Us
-\draw[thick] (0,0) -- (1,2) -- (3,2) -- (4,4) -- (6,4) -- (7,6) -- (10,6);
-
-\draw (2.2,2) node[align=center] {\scriptsize{sub-cognitive}\\\scriptsize{anthropomorphism}}; %label
-\draw (5,3.85) node[align=center] {\scriptsize{projection of existing}\\\scriptsize{mental models}\\\scriptsize{\it (familiarity)}}; %label
-\draw (8.5,5.85) node[align=center] {\scriptsize{adapted mental model} \\ $\to$ \scriptsize{adapted interaction}\\\scriptsize{\it (antropomorphic or not)}}; %label
-
-\draw (2.2,1) node[align=left] {\tiny{\it observation (shape, motion, sound)}}; %label
-\draw (5.2,3) node[align=left] {\tiny \it observation (interactive behavior) \\ \tiny \it or short interaction}; %label
-\draw (7.8,5) node[align=left] {\tiny \it contextualized interaction}; %label
+\draw[ultra thick, ->] (0,0) -- (1,2) -- (3,2) -- (4,4) -- (6,4) -- (7,6) --
+(9.5,6);
+\draw[ultra thick, dashed, ->] (3,2) -- (9.5,2);
+\draw[ultra thick, dashed, ->] (6,4) -- (9.5,4);
+
+\draw (11,1) node[align=left, anchor=west]{\scriptsize pre-cognitive\\\scriptsize anthropomorphism}; %label
+
+\draw (11,3) node[align=left, anchor=west] {\scriptsize{projection of existing}\\\scriptsize{mental models}\\\scriptsize{\it (familiarity)}}; %label
+
+\draw (11,5) node[align=left, anchor=west] {\scriptsize{adapted mental
+model} \\ $\to$ \scriptsize{adapted interaction}\\\scriptsize{\it (anthropomorphic or not)}}; %label
+
+\draw[dashed,->] (1,0.1) to[bend right] (2,1.9)  node at (4.5,1) {\tiny{\it observation (shape, motion, sound)}}; %label
+
+\draw[dashed,->] (4,2.1) to[bend right] (5,3.9)  node[align=left] at (7.5,3) {\tiny \it observation (interactive behavior) \\ \tiny \it or short interaction}; %label
+
+\draw[dashed,->] (7,4.1) to[bend right] (8,5.9)  node[align=left] at (9,5)
+{\tiny \it contextualized\\ \tiny \it interaction}; %label
 
@@
 %}
-\caption{The three cognitive phases of anthropomorphism: Phase I is the instinctive,
+\caption{The three cognitive levels of anthropomorphism: Level 1 is the instinctive,
 sub-cognitive identification of living peers. {\it Empathy} is characteristic
 of this stage. After longer observation or short, non-contextualized interaction
-(typically, a lab environment), the user enters Phase II: the user projects a
+(typically, a lab environment), the user reaches Level 2: the user projects a
 mental model he/she is already familiar with onto the robot. After longer {\it
-contextualized} interaction (typically, at home), the user enters Phase III of
+contextualized} interaction (typically, at home), the user enters Level 3 of
 anthropomorphism: the user recomposes an accurate mental model of the robot,

### 2014-03-19 paper.tex
minor changes

@@
 Then we propose to use another term, namely ``anthropomorphic form'', to refer to the human-inspired design of artifacts.
-Finally, we focus on both anthropomorphism and anthropomorphic design in human-robot interaction / robotics, as here both topics are brought together naturally.
+Finally, we focus on both anthropomorphism and anthropomorphic design in human-robot interaction / robotics, as in these domains both topics are brought together naturally.
+\hl{(adjust according to the section)}
 
@@
 Anthropomorphism is an interesting phenomenon because it tells us something about the relationship between the human who anthropomorphizes, and the non-human agent which is anthropomorphized.
-Though commonly observed, it appears controversial, at the same time, that humans tend to perceive human-like physical appearance (\eg faces), emotional states, or inner mental states and motivations in non-human agents such as animals, natural forces, religious agents, technological gadgets, or mechanical devices \citep{epley_when_2008}.\footnote{According to \cite{epley_when_2008}, a non-human agent can be anything that acts -- or is believed to act -- with apparent independence.}  Anthropomorphism has received remarkable attention across various different domains, such as natural sciences, developmental and social psychology, Human-Computer Interaction (HCI), and Human-Robot Interaction (HRI).
+Though commonly observed, it appears controversial, at the same time, that humans tend to \hl{\textit{``see something human in the non-human''}}.
+
+Humans tend to perceive human-like characteristics such as physical appearance, emotional states, or inner mental states and motivations in non-human agents that do not have these characteristics themselves, such as animals, natural forces, religious agents, technological gadgets, or mechanical devices \citep{epley_when_2008}.\footnote{According to \cite{epley_when_2008}, a non-human agent can be anything that acts -- or is believed to act -- with apparent independence.}  Anthropomorphism has received remarkable attention across various different domains, such as natural sciences, developmental and social psychology, Human-Computer Interaction (HCI), and Human-Robot Interaction (HRI).
 
@@
 As such, anthropomorphism can be seen as a special kind of relationship between a human interacting with a non-human agent.
-This anthropomorphic relationship is often characterized by the fact that the human attributes or ascribes human-unique characteristics to the non-human agent.
+This anthropomorphic relationship is often characterized by the fact that the human attributes human-unique characteristics to the non-human agent.
 Since anthropomorphism becomes observable through these attributions, some definitions claim that anthropomorphism is not the perception but rather the attribution of human attributes to non-human agents, and name thoughts, emotions, and intentions as examples.
@@
 
-Not only \cite{epley_when_2008} and \cite{duffy_anthropomorphism_2002} but also others have noticed that anthropomorphism is a very complex phenomenon - in itself, in how it can be understood, and when studying it.
+Not only \cite{epley_when_2008} and \cite{duffy_anthropomorphism_2002} but also others have noticed that anthropomorphism is a very complex phenomenon -- itself and in how it can be understood.
+This holds implications for the study of anthropomorphism (to what we will come back later in this article \hl{(REF to studying / measuring anthropomorphism)}.
 A common formal ground is missing so far; however, it is important to be clear about what exactly we mean when using the term anthropomorphism.

### 2014-03-19 paper.tex
new bib item, new introduction (adapted to the structure: studies - anthropomorphic design - anthropomorphism ...)

@@
 
+\subsection*{\hl{Intro when start with anthropomorphic design}}
+The Uncanny Valley hypothesis \citep{mori_uncanny_1970} proposes that human-like designs of objects and non-human agents evoke a positive feeling of affinity in the human observer / user, which in turn reflects the experience of emotional engagement with and feelings of empathy for the non-human agent \citep{cheetham_human_2011}.
+This convenient positive effect of so-called \textbf{anthropomorphic design} is exploited in the design of artificial agents (\eg digital characters, robots) in order to foster people's acceptance of these agents, and to enable effective (human-like and human-social) interaction.
+However, at a certain point (not very well defined, probably due to the various dimensions of human likeness) as the non-human agent approaches but fails to closely resemble a human, the evoked valence in the human user suddenly turns into a negative uncanny feeling of what \cite{mori_uncanny_1970} describes as disgust and revulsion.
+The Uncanny Valley hypothesis further predicts that when the non-human agent appears to the human so realistic that it is not distinguishable from a human and in fact perceived to be human, the effect is again a positive one, reflecting feelings and engagement that are similar as those evoked by a human-human interaction.
+
+Besides a feeling of affinity, and empathy, one of the resulting (and  more or less desired) effects of the anthropomorphic design of artificial agents (up to the first positive peak) is the human user's perception of human-likeness in the non-human agent.
+This phenomenon is labeled as \textbf{anthropomorphism}.
+There are various reasons and explanations for why people tend to anthropomorphize non-human agents.
+In general, as anthropomorphism emerges in a (real or imagined) interaction \citep{persson_anthropomorphism_2000} between at least two players (the human who anthropomorphizes and the non-human agent which is anthropomorphized) there are also two main perspectives on the phenomenon: a human-centered (cognitive, psychological) and artifact-centered (design) one.
+The Uncanny Valley hypothesis can be categorized as being part of latter, artifact-centered approach to understand anthropomorphism.
+
+We investigated anthropomorphism in several human-robot interaction studies that were carried out with real embodied robots, mostly in the real-world.\footnote{Note that the main purpose of these studies was not to analyze in detail the effect of human-likeness in a robot on the user's perception of and interaction with the robot.} We
+% now copy-pasted from alternative intro part
+found qualitative differences and
+dynamics over time in how participants anthropomorphized and related to the
+robots used in our studies. More concretely, we found that anthropomorphism was
+not only based on how much the robot resembles a human (anthropomorphic design)
+but that it was determined by multiple factors, including individual
+characteristics of the human user, and the context of use, for instance. We also
+found that anthropomorphism changed over time with growing experience of the
+user with the system. By trying to understand these variances and dynamics in
+anthropomorphism, we reviewed related work from the HRI domain and social
+robotics. Despite the fact that there is a vast amount of literature on
+anthropomorphism in HRI, we were surprised to find that other studies do not
+describe similar variances or dynamics. Instead, we came across diverse and
+partially conflicting understandings of anthropomorphism. We also had the
+impression that the reported data were sometimes over-interpreted (probably due
+to the confusion of what exactly anthropomorphism is) or obtained in settings
+and assessed in ways that we believe do not give enough consideration to the
+complex nature of anthropomorphism. However, when reviewing literature from
+social psychology, cognitive science, and neuroscience, we found support for the
+variances and dynamics in anthropomorphism that we observed in our studies. As
+HRI integrates many disciplines, we think that it is valid to use theories from
+these related domains for interpreting our results and that it is relevant to
+report on this integration.
+
+\subsection*{\hl{Intro when start with anthropomorphism}}
 The essence of anthropomorphism is the perception of human-like characteristics
@@
 humans. In our own studies on HRI analysis in real-world settings, we also
-observed anthropomorphism. However, we found qualitative differences and
+observed anthropomorphism. However, we
+%
+found qualitative differences and
 dynamics over time in how participants anthropomorphized and related to the

### 2014-03-19 paper.tex
refined intro

--- 2014-03-19 paper.tex
@@
 
-The essence of anthropomorphism is the perception of human-like characteristics
-in either real or imagined non-human agents. In Human-Robot Interaction (HRI),
-anthropomorphism is a commonly observed phenomenon: people tend to ascribe
-human-like characteristics to robots, and they are willing to treat and react to
-robots as if they were human-social counterparts. The HRI and social robotics
-literature is full of various kinds of studies showing how humans readily
-interact in a social fashion with robots -- despite the fact that robots are not
-humans. In our own studies on HRI analysis in real-world settings, we also
-observed anthropomorphism. However, we found qualitative differences and
-dynamics over time in how participants anthropomorphized and related to the
-robots used in our studies. More concretely, we found that anthropomorphism was
-not only based on how much the robot resembles a human (anthropomorphic design)
-but that it was determined by multiple factors, including individual
-characteristics of the human user, and the context of use, for instance. We also
-found that anthropomorphism changed over time with growing experience of the
-user with the system. By trying to understand these variances and dynamics in
-anthropomorphism, we reviewed related work from the HRI domain and social
-robotics. Despite the fact that there is a vast amount of literature on
-anthropomorphism in HRI, we were surprised to find that other studies do not
-describe similar variances or dynamics. Instead, we came across diverse and
-partially conflicting understandings of anthropomorphism. We also had the
-impression that the reported data were sometimes over-interpreted (probably due
-to the confusion of what exactly anthropomorphism is) or obtained in settings
-and assessed in ways that we believe do not give enough consideration to the
-complex nature of anthropomorphism. However, when reviewing literature from
-social psychology, cognitive science, and neuroscience, we found support for the
-variances and dynamics in anthropomorphism that we observed in our studies. As
-HRI integrates many disciplines, we think that it is valid to use theories from
-these related domains for interpreting our results and that it is relevant to
-report on this integration.
-
-In this article, we would like to share some critical but constructive
-considerations on anthropomorphism in robotics and HRI. Thereby, we contribute
-to a better understanding of this complex phenomenon related to robots. In
-Section \ref{sec:anthropomorphism} we would first like to give an overview of
-how anthropomorphism can be defined, and then, in Section \ref{sec:explanations}
-present explanations to the question why people anthropomorphize, with a focus
-on anthropomorphism as a social phenomenon in HRI and the trend to design
-human-like robots. Then, based on these reviews of theories and concepts from
-related domains, in Section \ref{sec:multi-factors} we propose that
-anthropomorphism is determined and affected by multiple factors. We outline how
-anthropomorphism as a multi-factor phenomenon can impact the user experience and
-acceptance of robots in daily life environments. Next, in Section
-\ref{sec:dynamics-model} we suggest that anthropomorphism changes over time, and
-describe these changes in an initial model that we call ``Dynamics of
-Anthropomorphism''. We illustrate our idea with empirical findings from several
-HRI studies that we conducted in natural environments. In Section
-\ref{sec:cognition-neuroscience} we present a cognitive and neuroscience
-perspective on anthropomorphism to consolidate our considerations and the
-observed dynamics. Next, Section \ref{sec:discussion} considers limitations in
-our approach and we discuss existing and alternative ways to measure
-anthropomorphism in HRI. Finally, in Section \ref{sec:conclusion} we conclude
-this article.
+%{Intro when start with anthropomorphic design}
+The Uncanny Valley hypothesis \citep{mori_uncanny_1970} proposes that human-like designs of objects and non-human agents evoke a positive feeling of affinity in the human observer / user, which in turn reflects the experience of emotional engagement with and feelings of empathy for the non-human agent \citep{cheetham_human_2011}.
+The positive effect of so-called \textbf{anthropomorphic form} is exploited in the design of artificial agents (\eg digital characters, robots) for several reasons.
+Amongst others, anthropomorphic design should serve to elicit this positive valence as it is predicted in the Uncanny Valley hypothesis, and it should further foster people's acceptance of these artificial agents, and enable effective (human-like and especially human-social) interaction.
+However, at a certain point as the non-human agent approaches but fails to closely resemble a human, the evoked valence in the human user suddenly turns into a negative uncanny feeling of what \cite{mori_uncanny_1970} describes as disgust and revulsion.
+This, in turn, might lead to rejection of the non-human but human-like agent.
+The Uncanny Valley hypothesis predicts that with further increasing the human-likeness of the non-human agent such that it appears so realistic that it is not distinguishable from a human but perceived to be human, the effect is again a positive one, reflecting feelings and engagement that are similar as those evoked by a human-human interaction.
+Of course, roboticists and developers try to avoid ``falling'' into this Uncanny Valley with their human-like designs of artificial agents.
+Consequently, there is a considerable research effort into better understanding and defining the boundaries of anthropomorphic design.
+However, findings have been inconsistent \citep{cheetham_human_2011}.
+
+A phenomenon that is often studied related to the human-like design of robots is \textbf{anthropomorphism}.
+Besides a feeling of affinity, and empathy, anthropomorphism can be understood as being one of the resulting (and  more or less desired) effects of the anthropomorphic design of artificial agents (up to the first positive peak).
+The essence of anthropomorphism is the human user's perception of human-likeness in the non-human agent.
+Logically, anthropomorphism is said to be enhanced with increased human-like design of the agent.
+There are various other reasons and explanations for why people tend to anthropomorphize non-human agents.
+In general, as anthropomorphism emerges in a (real or imagined) interaction \citep{persson_anthropomorphism_2000} between at least two players (the human who anthropomorphizes and the non-human agent which is anthropomorphized) there are also two main perspectives on the phenomenon: an artifact-centered (design) and a human-centered (cognitive, psychological) one.
+The Uncanny Valley hypothesis can be categorized as being part of first, artifact-centered approach, to understand anthropomorphism.
+
+We observed anthropomorphism in several short- and long-term human-robot interaction studies that we carried out with embodied robots, mostly in real-world settings.\footnote{Note that it was not the main purpose of these studies to analyze in detail the effect of human-likeness in a robot on the user's perception of and interaction with the robot.} There is not much research that investigates anthropomorphism based on real interaction between a human and a robot, and above all in a natural setting and over an extended period of time.
+Our data suggest that there are qualitative differences and dynamics over time in how participants relate to different types of robots.
+More concretely, we found that how human-like people perceived and interacted with the robot was not only based on how much the robot resembled a human (mostly in its behavioral cues)
+but that this was determined by multiple factors, including individual
+characteristics of the human user but also the context of use, for instance. Interestingly, our findings also suggest that anthropomorphism is likely to change over time with growing experience of the
+user with the system.
+
+Based on these observations and an extensive literature review, we would like to propose a model that accounts for variances and dynamics in anthropomorphism.
+This model of the ``Dynamics of Anthropomorphism'' considers variances in respect to multiple factors, including the human user, the anthropomorphic design of the non-human agent, the context of use, and the interaction experience (time).
+
+Thereby, we would like to extend the current understanding of anthropomorphism in robotics and human-robot interaction.
+
+%{Intro when start with anthropomorphism}
+%The essence of anthropomorphism is the perception of human-like characteristics
+%in either real or imagined non-human agents. In Human-Robot Interaction (HRI),
+%anthropomorphism is a commonly observed phenomenon: people tend to ascribe
+%human-like characteristics to robots, and they are willing to treat and react to
+%robots as if they were human-social counterparts. The HRI and social robotics
+%literature is full of various kinds of studies showing how humans readily
+%interact in a social fashion with robots -- despite the fact that robots are not
+%humans. In our own studies on HRI analysis in real-world settings, we also
+%observed anthropomorphism. However, we found qualitative differences and
+%dynamics over time in how participants anthropomorphized and related to the
+%robots used in our studies. More concretely, we found that anthropomorphism was
+%not only based on how much the robot resembles a human (anthropomorphic design)
+%but that it was determined by multiple factors, including individual
+%characteristics of the human user but also the context of use, for instance. We also
+%found that anthropomorphism changed over time with growing experience of the
+%user with the system. By trying to understand these variances and dynamics in
+%anthropomorphism, we reviewed related work from the HRI domain and social
+%robotics. Despite the fact that there is a vast amount of literature on
+%anthropomorphism in HRI, we were surprised to find that other studies do not
+%describe similar variances or dynamics. Instead, we came across diverse and
+%partially conflicting understandings of anthropomorphism. We also had the
+%impression that the reported data were sometimes over-interpreted (probably due
+%to the confusion of what exactly anthropomorphism is) or obtained in settings
+%and assessed in ways that we believe do not give enough consideration to the
+%complex nature of anthropomorphism. However, when reviewing literature from
+%social psychology, cognitive science, and neuroscience, we found support for the
+%variances and dynamics in anthropomorphism that we observed in our studies. As
+%HRI integrates many disciplines, we think that it is valid to use theories from
+%these related domains for interpreting our results and that it is relevant to
+%report on this integration.
+%
+%In this article, we would like to share some critical but constructive
+%considerations on anthropomorphism in robotics and HRI. Thereby, we contribute
+%to a better understanding of this complex phenomenon related to robots. In
+%Section \ref{sec:anthropomorphism} we would first like to give an overview of
+%how anthropomorphism can be defined, and then, in Section \ref{sec:explanations}
+%present explanations to the question why people anthropomorphize, with a focus
+%on anthropomorphism as a social phenomenon in HRI and the trend to design
+%human-like robots. Then, based on these reviews of theories and concepts from
+%related domains, in Section \ref{sec:multi-factors} we propose that
+%anthropomorphism is determined and affected by multiple factors. We outline how
+%anthropomorphism as a multi-factor phenomenon can impact the user experience and
+%acceptance of robots in daily life environments. Next, in Section
+%\ref{sec:dynamics-model} we suggest that anthropomorphism changes over time, and
+%describe these changes in an initial model that we call ``Dynamics of
+%Anthropomorphism''. We illustrate our idea with empirical findings from several
+%HRI studies that we conducted in natural environments. In Section
+%\ref{sec:cognition-neuroscience} we present a cognitive and neuroscience
+%perspective on anthropomorphism to consolidate our considerations and the
+%observed dynamics. Next, Section \ref{sec:discussion} considers limitations in
+%our approach and we discuss existing and alternative ways to measure
+%anthropomorphism in HRI. Finally, in Section \ref{sec:conclusion} we conclude
+%this article.
 

### 2014-03-19 paper.tex
new intro and overview completed

@@
 The positive effect of so-called \textbf{anthropomorphic form} is exploited in the design of artificial agents (\eg digital characters, robots) for several reasons.
-Amongst others, anthropomorphic design should serve to elicit this positive valence as it is predicted in the Uncanny Valley hypothesis, and it should further foster people's acceptance of these artificial agents, and enable effective (human-like and especially human-social) interaction.
+Amongst others, anthropomorphic design should serve to evoke a positive valence as the Uncanny Valley hypothesis suggests, which in turn should foster people's acceptance of the artificial agent, and enable effective (human-like and especially human-social) interaction.
 However, at a certain point as the non-human agent approaches but fails to closely resemble a human, the evoked valence in the human user suddenly turns into a negative uncanny feeling of what \cite{mori_uncanny_1970} describes as disgust and revulsion.
@@
 Of course, roboticists and developers try to avoid ``falling'' into this Uncanny Valley with their human-like designs of artificial agents.
-Consequently, there is a considerable research effort into better understanding and defining the boundaries of anthropomorphic design.
+Consequently, there is a considerable research effort into better understanding the boundaries of anthropomorphic design and their effect on the interaction and experience.
 However, findings have been inconsistent \citep{cheetham_human_2011}.
@@
 In general, as anthropomorphism emerges in a (real or imagined) interaction \citep{persson_anthropomorphism_2000} between at least two players (the human who anthropomorphizes and the non-human agent which is anthropomorphized) there are also two main perspectives on the phenomenon: an artifact-centered (design) and a human-centered (cognitive, psychological) one.
-The Uncanny Valley hypothesis can be categorized as being part of first, artifact-centered approach, to understand anthropomorphism.
-
-We observed anthropomorphism in several short- and long-term human-robot interaction studies that we carried out with embodied robots, mostly in real-world settings.\footnote{Note that it was not the main purpose of these studies to analyze in detail the effect of human-likeness in a robot on the user's perception of and interaction with the robot.} There is not much research that investigates anthropomorphism based on real interaction between a human and a robot, and above all in a natural setting and over an extended period of time.
-Our data suggest that there are qualitative differences and dynamics over time in how participants relate to different types of robots.
-More concretely, we found that how human-like people perceived and interacted with the robot was not only based on how much the robot resembled a human (mostly in its behavioral cues)
+The Uncanny Valley hypothesis can be categorized as being part of first, artifact-centered approach, to understand anthropomorphism.\\
+
+We observed anthropomorphism in several short- and long-term human-robot interaction studies that we carried out with embodied robots, mostly in real-world settings.
+There is not much research that investigates anthropomorphism based on real interaction between a human and a robot, and above all in natural settings and over extended periods of time.
+
+Our data suggest that there are qualitative differences and dynamics over time in how humans relate to different types of robots.
+More concretely, we found that people's perception of human-likeness in the robot and in turn their human-social engagement with the robot was not only based on how much the robot resembled a human (mostly in its behavioral cues)
 but that this was determined by multiple factors, including individual
-characteristics of the human user but also the context of use, for instance. Interestingly, our findings also suggest that anthropomorphism is likely to change over time with growing experience of the
+characteristics of the human user but also the context of use, for instance.
+Interestingly, our findings also suggest that how far people anthropomorphize a robot is likely to change over time with growing experience of the
 user with the system.
@@
 Based on these observations and an extensive literature review, we would like to propose a model that accounts for variances and dynamics in anthropomorphism.
-This model of the ``Dynamics of Anthropomorphism'' considers variances in respect to multiple factors, including the human user, the anthropomorphic design of the non-human agent, the context of use, and the interaction experience (time).
-
-Thereby, we would like to extend the current understanding of anthropomorphism in robotics and human-robot interaction.
+This model of the \textit{``Dynamics of Anthropomorphism''} considers several impact factors, including the human user, the anthropomorphic design of the non-human agent, the context of use, and the interaction experience (time).
+With this initial model, we would like to extend the current understanding of anthropomorphism in robotics and human-robot interaction.
+This might in turn lead to a discussion about the short- and long-term benefits and other effects of the human-like (anthropomorphic) design of robots and other artificial agents.\\
+
+The remainder of this article is organized as follows. 
+First, in Section \ref{sec:overview-studies}, we give a brief overview on the various studies that we conducted to investigate anthropomorphism, namely (1) the Roomba study, (2) the Forum study, (3) the Ranger domino study.
+As an outcome of these studies, we propose two main research hypotheses related to anthropomorphism.
+Next, in Section \ref{sec:anthropomorphism} we investigate these hypotheses by synthesizing literature on anthropomorphism.
+This should also serve to establish a common ground.
+We first explore an artifact-centered perspective and briefly outline how the human-like design of agents can encourage anthropomorphism.
+Then, we explore a human-centered perspective by integrating theories from cognitive science, developmental and social psychology that serve to explain anthropomorphism.
+At the end of this section we bring both perspectives together and interpret that anthropomorphism is a multi-factor phenomenon.
+Based on the two previous sections, we propose an initial model of the \textit{``Dynamics of Anthropomorphism''} in Section \ref{sec:dynamics-model}.
+This model describes the variances and dynamics of people's tendency to anthropomorphize an artificial agent, such as a robot.
+Next, in Section \ref{sec:cognition-neuroscience} we present a cognitive and neuroscience perspective on anthropomorphism to consolidate our considerations and the proposed model.
+This will be followed by a discussion about the limitations of our approach (Section \ref{sec:discussion}). Further, we debate existing and alternative ways to measure
+anthropomorphism in human-robot interactions.
+Finally, Section \ref{sec:conclusion} concludes this article and offers starting points for further research on anthropomorphism and the effect of the human-like design approach in robotics.
 
@@
 
-\subsection{A few results from the field}
-
-\subsubsection{The Roomba experiment}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+%
+%
+%		OVERVIEW ON OUR STUDIES
+%
+%
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{A few results from the field}
+\label{sec:overview-studies}
+
+In this section we give a brief overview of the studies that we conducted to investigate anthropomorphism.
+Note that it was not the main purpose of these studies to analyze in detail the effect of different dimensions human-likeness of a robot on the user's perception of and interaction with the robot.
+Each of these studies
+
+The strong points
+
+\subsection{Roomba study: how people live with a vacuum cleaning robot}
 
@@
 
-\subsubsection{The Ranger experiment}
+\subsection{Forum study: using anthropomorphic language to describe a robot}
+
+\hl{Julia: I think we should also include this study}
+
+\subsection{Ranger domino study: effect of unexpected robot behavior}
 
@@
 \fxnote{state here our main contributions}
-\fxnote{Introduce the remainder of the paper}
 

### 2014-03-19 paper.tex
added new figure, completed intro, started to describe Roomba study

@@
 Note that it was not the main purpose of these studies to analyze in detail the effect of different dimensions human-likeness of a robot on the user's perception of and interaction with the robot.
-Each of these studies
-
-The strong points
+Each of these studies were motivated also by other research questions, and we encourage the reader to refer to our other main publications about these studies for more details.
 
 \subsection{Roomba study: how people live with a vacuum cleaning robot}
+
+We openly explored interactions between human users and a domestic service robot in a 6-months lasting ethnographic study in nine households to which we gave a commercially available vacuum cleaning robot (iRobot's Roomba).\footnote{This study is published in \cite{fink_living_2013}.} Hereafter, we refer to this study as the "Roomba study".
+
+We can report on several findings related to anthropomorphism and the anthropomorphic design of robots.
+The gathered data for these aspects include qualitative observations, semi-structured interviews, and also quantitative assessments of various aspects of human-robot interaction.
+The Roomba study is one of very few long-term human-robot interaction studies in the domestic environment.
+
+In the following, we present findings in respect of two aspects:
+First, we qualitatively describe what kinds of anthropomorphic interactions between participants and the robot were observed and outline how these interactions evolved over time.
+Second, we present people's perception of human-likeness and social capabilities of the robot and how this perception changed over time.
+
+\subsubsection{Anthropomorphic interactions with the robot}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.6\columnwidth]{roomba-activities.png}
+    \caption{This bar chart shows how many of the 9 households carried out different kinds of activities with and related to the robot over a period of 6 months.
+Activities included using the robot for \texttt{cleaning}, \texttt{watching} the robot for fun, giving a \texttt{demo} of the robot to guests / visitors, taking a \texttt{photo/video} of the robot, \texttt{personalizing} the robot, giving a \texttt{name} to the robot, \texttt{talking} to the robot, \texttt{playing} with the robot, \texttt{hacking} the robot, having a \texttt{conversation} about the robot, making \texttt{adjustments} to the home due to the robot.
+Participants were asked to report on these activities at 3 time points after the robot was deployed in their home: after 2 weeks, after 2 months, and after 6 months.
+\hl{(strangely, in the pdf version of this graph the bars were not displayed!)}}
+
+    \label{fig:roomba-activities}
+\end{figure}
+
+\subsubsection{Perception of human-like characteristics of the robot}
 

### 2014-03-20 paper.tex
Work on introduction

--- 2014-03-19 paper.tex
@@
 
-\section{Introduction and overview}
+\section{Introduction}
 \label{sec:intro}
@@
 %{Intro when start with anthropomorphic design}
-The Uncanny Valley hypothesis \citep{mori_uncanny_1970} proposes that human-like designs of objects and non-human agents evoke a positive feeling of affinity in the human observer / user, which in turn reflects the experience of emotional engagement with and feelings of empathy for the non-human agent \citep{cheetham_human_2011}.
-The positive effect of so-called \textbf{anthropomorphic form} is exploited in the design of artificial agents (\eg digital characters, robots) for several reasons.
-Amongst others, anthropomorphic design should serve to evoke a positive valence as the Uncanny Valley hypothesis suggests, which in turn should foster people's acceptance of the artificial agent, and enable effective (human-like and especially human-social) interaction.
-However, at a certain point as the non-human agent approaches but fails to closely resemble a human, the evoked valence in the human user suddenly turns into a negative uncanny feeling of what \cite{mori_uncanny_1970} describes as disgust and revulsion.
-This, in turn, might lead to rejection of the non-human but human-like agent.
-The Uncanny Valley hypothesis predicts that with further increasing the human-likeness of the non-human agent such that it appears so realistic that it is not distinguishable from a human but perceived to be human, the effect is again a positive one, reflecting feelings and engagement that are similar as those evoked by a human-human interaction.
-Of course, roboticists and developers try to avoid ``falling'' into this Uncanny Valley with their human-like designs of artificial agents.
-Consequently, there is a considerable research effort into better understanding the boundaries of anthropomorphic design and their effect on the interaction and experience.
-However, findings have been inconsistent \citep{cheetham_human_2011}.
-
-A phenomenon that is often studied related to the human-like design of robots is \textbf{anthropomorphism}.
-Besides a feeling of affinity, and empathy, anthropomorphism can be understood as being one of the resulting (and  more or less desired) effects of the anthropomorphic design of artificial agents (up to the first positive peak).
-The essence of anthropomorphism is the human user's perception of human-likeness in the non-human agent.
-Logically, anthropomorphism is said to be enhanced with increased human-like design of the agent.
-There are various other reasons and explanations for why people tend to anthropomorphize non-human agents.
-In general, as anthropomorphism emerges in a (real or imagined) interaction \citep{persson_anthropomorphism_2000} between at least two players (the human who anthropomorphizes and the non-human agent which is anthropomorphized) there are also two main perspectives on the phenomenon: an artifact-centered (design) and a human-centered (cognitive, psychological) one.
-The Uncanny Valley hypothesis can be categorized as being part of first, artifact-centered approach, to understand anthropomorphism.\\
-
-We observed anthropomorphism in several short- and long-term human-robot interaction studies that we carried out with embodied robots, mostly in real-world settings.
-There is not much research that investigates anthropomorphism based on real interaction between a human and a robot, and above all in natural settings and over extended periods of time.
-
-Our data suggest that there are qualitative differences and dynamics over time in how humans relate to different types of robots.
-More concretely, we found that people's perception of human-likeness in the robot and in turn their human-social engagement with the robot was not only based on how much the robot resembled a human (mostly in its behavioral cues)
-but that this was determined by multiple factors, including individual
-characteristics of the human user but also the context of use, for instance.
-Interestingly, our findings also suggest that how far people anthropomorphize a robot is likely to change over time with growing experience of the
-user with the system.
-
-Based on these observations and an extensive literature review, we would like to propose a model that accounts for variances and dynamics in anthropomorphism.
-This model of the \textit{``Dynamics of Anthropomorphism''} considers several impact factors, including the human user, the anthropomorphic design of the non-human agent, the context of use, and the interaction experience (time).
-With this initial model, we would like to extend the current understanding of anthropomorphism in robotics and human-robot interaction.
-This might in turn lead to a discussion about the short- and long-term benefits and other effects of the human-like (anthropomorphic) design of robots and other artificial agents.\\
-
-The remainder of this article is organized as follows. 
-First, in Section \ref{sec:overview-studies}, we give a brief overview on the various studies that we conducted to investigate anthropomorphism, namely (1) the Roomba study, (2) the Forum study, (3) the Ranger domino study.
-As an outcome of these studies, we propose two main research hypotheses related to anthropomorphism.
-Next, in Section \ref{sec:anthropomorphism} we investigate these hypotheses by synthesizing literature on anthropomorphism.
-This should also serve to establish a common ground.
-We first explore an artifact-centered perspective and briefly outline how the human-like design of agents can encourage anthropomorphism.
-Then, we explore a human-centered perspective by integrating theories from cognitive science, developmental and social psychology that serve to explain anthropomorphism.
-At the end of this section we bring both perspectives together and interpret that anthropomorphism is a multi-factor phenomenon.
-Based on the two previous sections, we propose an initial model of the \textit{``Dynamics of Anthropomorphism''} in Section \ref{sec:dynamics-model}.
-This model describes the variances and dynamics of people's tendency to anthropomorphize an artificial agent, such as a robot.
-Next, in Section \ref{sec:cognition-neuroscience} we present a cognitive and neuroscience perspective on anthropomorphism to consolidate our considerations and the proposed model.
-This will be followed by a discussion about the limitations of our approach (Section \ref{sec:discussion}). Further, we debate existing and alternative ways to measure
-anthropomorphism in human-robot interactions.
-Finally, Section \ref{sec:conclusion} concludes this article and offers starting points for further research on anthropomorphism and the effect of the human-like design approach in robotics.
-
-%{Intro when start with anthropomorphism}
-%The essence of anthropomorphism is the perception of human-like characteristics
-%in either real or imagined non-human agents. In Human-Robot Interaction (HRI),
-%anthropomorphism is a commonly observed phenomenon: people tend to ascribe
-%human-like characteristics to robots, and they are willing to treat and react to
-%robots as if they were human-social counterparts. The HRI and social robotics
-%literature is full of various kinds of studies showing how humans readily
-%interact in a social fashion with robots -- despite the fact that robots are not
-%humans. In our own studies on HRI analysis in real-world settings, we also
-%observed anthropomorphism. However, we found qualitative differences and
-%dynamics over time in how participants anthropomorphized and related to the
-%robots used in our studies. More concretely, we found that anthropomorphism was
-%not only based on how much the robot resembles a human (anthropomorphic design)
-%but that it was determined by multiple factors, including individual
-%characteristics of the human user but also the context of use, for instance. We also
-%found that anthropomorphism changed over time with growing experience of the
-%user with the system. By trying to understand these variances and dynamics in
-%anthropomorphism, we reviewed related work from the HRI domain and social
-%robotics. Despite the fact that there is a vast amount of literature on
-%anthropomorphism in HRI, we were surprised to find that other studies do not
-%describe similar variances or dynamics. Instead, we came across diverse and
-%partially conflicting understandings of anthropomorphism. We also had the
-%impression that the reported data were sometimes over-interpreted (probably due
-%to the confusion of what exactly anthropomorphism is) or obtained in settings
-%and assessed in ways that we believe do not give enough consideration to the
-%complex nature of anthropomorphism. However, when reviewing literature from
-%social psychology, cognitive science, and neuroscience, we found support for the
-%variances and dynamics in anthropomorphism that we observed in our studies. As
-%HRI integrates many disciplines, we think that it is valid to use theories from
-%these related domains for interpreting our results and that it is relevant to
-%report on this integration.
-%
-%In this article, we would like to share some critical but constructive
-%considerations on anthropomorphism in robotics and HRI. Thereby, we contribute
-%to a better understanding of this complex phenomenon related to robots. In
-%Section \ref{sec:anthropomorphism} we would first like to give an overview of
-%how anthropomorphism can be defined, and then, in Section \ref{sec:explanations}
-%present explanations to the question why people anthropomorphize, with a focus
-%on anthropomorphism as a social phenomenon in HRI and the trend to design
-%human-like robots. Then, based on these reviews of theories and concepts from
-%related domains, in Section \ref{sec:multi-factors} we propose that
-%anthropomorphism is determined and affected by multiple factors. We outline how
-%anthropomorphism as a multi-factor phenomenon can impact the user experience and
-%acceptance of robots in daily life environments. Next, in Section
-%\ref{sec:dynamics-model} we suggest that anthropomorphism changes over time, and
-%describe these changes in an initial model that we call ``Dynamics of
-%Anthropomorphism''. We illustrate our idea with empirical findings from several
-%HRI studies that we conducted in natural environments. In Section
-%\ref{sec:cognition-neuroscience} we present a cognitive and neuroscience
-%perspective on anthropomorphism to consolidate our considerations and the
-%observed dynamics. Next, Section \ref{sec:discussion} considers limitations in
-%our approach and we discuss existing and alternative ways to measure
-%anthropomorphism in HRI. Finally, in Section \ref{sec:conclusion} we conclude
-%this article.
+The Uncanny Valley hypothesis \citep{mori_uncanny_1970} proposes that human-like
+designs of objects and non-human agents evoke a positive feeling of affinity in
+the human observer / user, which in turn reflects the experience of emotional
+engagement with and feelings of empathy for the non-human agent
+\citep{cheetham_human_2011}. The positive effect of so-called
+\textbf{anthropomorphic form} is exploited in the design of artificial agents
+(\eg digital characters, robots) for several reasons. Amongst others,
+anthropomorphic design should serve to evoke a positive valence as the Uncanny
+Valley hypothesis suggests, which in turn should foster people's acceptance of
+the artificial agent, and enable effective (human-like and especially
+human-social) interaction.  However, at a certain point as the non-human agent
+approaches but fails to closely resemble a human, the evoked valence in the
+human user suddenly turns into a negative uncanny feeling of what
+\cite{mori_uncanny_1970} describes as disgust and revulsion. This, in turn,
+might lead to rejection of the non-human but human-like agent.  The Uncanny
+Valley hypothesis predicts that with further increasing the human-likeness of
+the non-human agent such that it appears so realistic that it is not
+distinguishable from a human but perceived to be human, the effect is again a
+positive one, reflecting feelings and engagement that are similar as those
+evoked by a human-human interaction.  Of course, roboticists and developers try
+to avoid ``falling'' into this Uncanny Valley with their human-like designs of
+artificial agents. Consequently, there is a considerable research effort into
+better understanding the boundaries of anthropomorphic design and their effect
+on the interaction and experience. However, findings have been inconsistent
+\citep{cheetham_human_2011}.
+
+A phenomenon that is often studied related to the human-like design of robots is
+\textbf{anthropomorphism}. Besides a feeling of affinity, and empathy,
+anthropomorphism can be understood as being one of the resulting (and  more or
+less desired) effects of the anthropomorphic design of artificial agents (up to
+the first positive peak). The essence of anthropomorphism is the human user's
+perception of human-likeness in the non-human agent. Logically, anthropomorphism
+is said to be enhanced with increased human-like design of the agent. There are
+various other reasons and explanations for why people tend to anthropomorphize
+non-human agents. In general, as anthropomorphism emerges in a (real or
+imagined) interaction \citep{persson_anthropomorphism_2000} between at least two
+players (the human who anthropomorphizes and the non-human agent which is
+anthropomorphized) there are also two main perspectives on the phenomenon: an
+artifact-centered (design) and a human-centered (cognitive, psychological) one.
+The Uncanny Valley hypothesis can be categorized as being part of first,
+artifact-centered approach, to understand anthropomorphism.\\
+
+We observed anthropomorphism in several short- and long-term human-robot
+interaction studies that we carried out with embodied robots, mostly in
+real-world settings. There is not much research that investigates
+anthropomorphism based on real interaction between a human and a robot, and
+above all in natural settings and over extended periods of time.
+
+Our data suggest that there are qualitative differences and dynamics over time
+in how humans relate to different types of robots. More concretely, we found
+that people's perception of human-likeness in the robot and in turn their
+human-social engagement with the robot was not only based on how much the robot
+resembled a human (mostly in its behavioral cues) but that this was determined
+by multiple factors, including individual characteristics of the human user but
+also the context of use, for instance. Interestingly, our findings also suggest
+that how far people anthropomorphize a robot is likely to change over time with
+growing experience of the user with the system.
+
+Based on these observations and an extensive literature review, we would like to
+propose a model that accounts for variances and dynamics in anthropomorphism.
+This model of the \textit{``Dynamics of Anthropomorphism''} considers several
+impact factors, including the human user, the anthropomorphic design of the
+non-human agent, the context of use, and the interaction experience (time). With
+this initial model, we would like to extend the current understanding of
+anthropomorphism in robotics and human-robot interaction. This might in turn
+lead to a discussion about the short- and long-term benefits and other effects
+of the human-like (anthropomorphic) design of robots and other artificial
+agents.\\
+
+\subsection{A few results from the field}
+
+To support the reflection, it may be useful to consider a few experimental
+results. Figure~\ref{roomba-perception} gives a first perspective on how naive
+users perceive robots over a long period of time. Here, \emph{Roomba} robots
+were given to nine household for a 6 months period. The aim was to explore how
+people use and perceive the robot over time, and how they generally live with
+the Roomba in their home. At various time points, users were asked to rated
+their perception of different features of the robot on a 7-Likert scale. As
+Figure~\ref{roomba-perception} shows, some features remained stable over time
+(\emph{ease of use} and \emph{fun}), and other decreased: the perceived
+\emph{usefulness}, \emph{intelligence} and \emph{impact} on their household.
+\emph{intelligence} and \emph{impact} reflect the cognitive engagement of the
+user towards the machine: we can assume that one do not care to engage in a
+(cognitive) interaction with an artifact perceived as non-intelligent and with
+no impact on his/her life. Even if one can argue that the Roomba is not designed
+to foster interaction, the question is raised: how to sustain engagement between
+a robot and a human over a long period of time? And, as a pre-requisite, do we
+actually understand the psychological phenomenon, and can we effectively account
+for the dynamics of these interactions?
+
+Those questions are certainly not new, but paradoxically, while anthropomorphism
+in robotics is a commonly discussed and studied trait of human-robot
+interaction, it appears it lacks a formal ground and unified understanding to
+take into account the wide range of phenomena that it encompasses.
+
+\subsection{Towards a formal understanding of anthropomorphism}
+
+\fxnote{state here our main research hypothesis}
+\fxnote{state here our main contributions}
+
+So far, the HRI community has not much investigated how anthropomorphism in
+human-robot interactions evolves over time (during the process of
+\emph{adopting} a robot, for instance). Anthropomorphism is traditionally
+perceived in robotics as a static feature that once observed during a
+short-term interaction reflects a sustaining social effect.  Based on an
+literature review previously published~\cite{fink_anthropomorphism_2012}, a
+long-term field study in a natural environment~\cite{fink_living_2013}, as well
+as two on-going child-robot experiments, we believe that anthropomorphic
+effects do evolve over time in non-monotonic ways, and play a central role in
+sustaining engagement in human-robot interaction.
+
+We propose to formalize these dynamic effects into a model that we call the
+\emph{dynamics of anthropomorphism}. We hope that it may support further
+discussions and reflections on how anthropomorphism impacts human-robot
+interaction on the long run, and also foster research on the affective bonds
+induced by anthropomorphic projections on robots.
+
+As such, we propose to represent how the level of anthropomorphic effects (\ie
+observable manifestations of anthropomorphism) evolves over a long-term
+human-robot interaction (Figure~\ref{fig:dynamics}). By long-term interaction,
+we mean direct (non-mediated), repeated interaction with the same robot, over
+an extended period of time (typically longer than a week).
+
+In this article, we would like to share some critical but constructive
+considerations on anthropomorphism in robotics and HRI. Thereby, we contribute
+to a better understanding of this complex phenomenon related to robots.
+
+The remainder of this article is organized as follows.  First, in Section
+\ref{sec:overview-studies}, we give a brief overview on the various studies that
+we conducted to investigate anthropomorphism, namely (1) the Roomba study, (2)
+the Forum study, (3) the Ranger domino study. As an outcome of these studies, we
+propose two main research hypotheses related to anthropomorphism.  Next, in
+Section \ref{sec:anthropomorphism} we investigate these hypotheses by
+synthesizing literature on anthropomorphism. This should also serve to establish
+a common ground. We first explore an artifact-centered perspective and briefly
+outline how the human-like design of agents can encourage anthropomorphism.
+Then, we explore a human-centered perspective by integrating theories from
+cognitive science, developmental and social psychology that serve to explain
+anthropomorphism. At the end of this section we bring both perspectives together
+and interpret that anthropomorphism is a multi-factor phenomenon.  Based on the
+two previous sections, we propose an initial model of the \textit{``Dynamics of
+Anthropomorphism''} in Section \ref{sec:our-ideas}. This model describes the
+variances and dynamics of people's tendency to anthropomorphize an artificial
+agent, such as a robot.  Next, in Section \ref{sec:cognition-neuroscience} we
+present a cognitive and neuroscience perspective on anthropomorphism to
+consolidate our considerations and the proposed model.  This will be followed by
+a discussion about the limitations of our approach (Section
+\ref{sec:discussion}). Further, we debate existing and alternative ways to
+measure anthropomorphism in human-robot interactions.  Finally, Section
+\ref{sec:conclusion} concludes this article and offers starting points for
+further research on anthropomorphism and the effect of the human-like design
+approach in robotics.
 
@@
 
-\section{A few results from the field}
+\section{Studying anthropomorphism}
 \label{sec:overview-studies}
 
-In this section we give a brief overview of the studies that we conducted to investigate anthropomorphism.
-Note that it was not the main purpose of these studies to analyze in detail the effect of different dimensions human-likeness of a robot on the user's perception of and interaction with the robot.
-Each of these studies
-
-The strong points
+In this section we give a brief overview of the studies that we conducted to
+investigate anthropomorphism in human-robot interaction. Note that it was not
+the main purpose of these studies to analyze in detail the effect of different
+dimensions human-likeness of a robot on the user's perception of and interaction
+with the robot. Each of these studies were motivated also by other research
+questions, and we encourage the reader to refer to our other main publications
+about these studies for more details.
 
@@
 
-\begin{figure*}[htb]
+We openly explored long-term interactions between human users and a domestic
+service robot in a 6-months lasting ethnographic study. We gave a commercially
+available vacuum cleaning robot (iRobot's Roomba, see Figure
+\ref{fig:aibo-roomba-ipad} middle) to nine households in the French speaking
+part of Switzerland. The fairly diverse sample of households consisted of 2
+single homes, 1 couple, and 6 families with children in their home. In total,
+this summed up to 30 participants: 15 adults (26-71 years old, mean age 43.6
+years), and 15 children (6 months to 18 years old). During the 6 months, each
+household was visited 5 times to conduct interviews and make field observations
+in the households. Moreover, during several weeks, households were asked to fill
+in a diary to report the usage of the robot and other cleaning activities.
+\footnote{This study is published in \cite{fink_living_2013}.} Hereafter, we
+refer to this study as the "Roomba study".
+
+%The main goal of this study was to explore how households live with a vacuum
+%cleaning robot over an extended period of time. We wanted to analyze how the
+%usage of and interaction with the robot evolve over time, and to identify
+%adoption phases as well as factors that impact on the long-term acceptance of
+%service robots in homes.
+
+From the Roomba study, we can report on several findings related to
+anthropomorphism and the anthropomorphic design of robots.
+%The gathered data for these aspects include qualitative observations,
+%semi-structured interviews, and also quantitative assessments of various
+%aspects of human-robot interaction.
+The Roomba study is one of very few long-term human-robot interaction studies in
+the domestic environment.
+
+In the following, we present findings in respect of two aspects: First, we
+qualitatively describe what kinds of anthropomorphic interactions between
+participants and the robot were observed and outline how these interactions
+evolved over time.  Second, we present people's perception of human-likeness and
+social capabilities of the robot and how this perception changed over
+time.\footnote{\hl{note that these two different kinds of data
+(behavior/interaction and perception) already show that we try to measure
+anthropomorphism from these two angles!}}
+
+\subsubsection{Anthropomorphic interactions with the robot\\}
+
+It has been described in several previous studies of the Roomba that users tend
+to engage in a variety of non-cleaning activities associated with the robot,
+including, but not limited to, naming, ascribing personality and gender
+\citep{forlizzi_service_2006,forlizzi_how_2007,krumm_my_2007,sung_domestic_2010}.
+\cite{sung_housewives_2008} carried out a survey among 379 Roomba users to
+investigate how common these activities are. The authors concluded that overall,
+respondents had relatively low rates of treating Roomba as a living entity.
+
+In our long-term study of the Roomba in homes, we found that it was mostly
+during the initial phase with the robot that some (rather few) people tended to
+interact in an anthropomorphic or human-social way with their vacuum cleaning
+robot.  Overall, our data suggest that the anthropomorphic effect and the social
+impact of a functional robot on a household is rather marginal.
+%There were just few instances of people anthropomorphizing the robot and
+%interacting with it in a human-social way. More importantly, overall, these
+%anthropomorphic interactions with the robot did not last but seemed to be
+%somehow related to the novelty of the robot.
+
+We categorized several interactions and actions with the robot as
+anthropomorphic or human-social (in a broader sense). 
+%Examples of what we categorized as somehow social and anthropomorphic
+%(human-like) interactions with the robot include \textit{watching} the robot
+%for fun, giving a \textit{demo} of the robot to guests / visitors, taking a
+%\textit{photo/video} of the robot, \textit{personalizing} the robot, giving a
+%\textit{name} to the robot, \textit{talking} to the robot using direct speech,
+%\textit{playing} with the robot, and making \textit{adjustments} to the home
+%due to the robot. 
+Figure \ref{fig:roomba-activities}) shows how many of the 9 households engaged
+in these activities during the 6 months when the study was conducted.
+
+\begin{figure}
     \centering
+    \includegraphics[width=0.5\columnwidth]{roomba-activities.png}
+    \caption{Activities with the robot over time, n = 9 households. This bar
+        chart shows how many of the 9 households carried out different kinds of
+        anthropomorphic / social activities with and related to the robot at 3
+        time points during 6 months. Activities include \texttt{watching} the
+        robot for fun, giving a \texttt{demo} of the robot to guests / visitors,
+        \texttt{personalizing} the robot, giving a \texttt{name} to the robot,
+        \texttt{talking} to the robot, \texttt{playing} with the robot.
+        Participants were asked to report on these activities at 3 time points
+        after the robot was deployed in their home: after 2 weeks, after 2 months,
+        and after 6 months.}
+
+\label{fig:roomba-activities}
+\end{figure}
+
+\paragraph*{Watching the robot for fun.} We categorize watching a robot for fun
+as an entertaining, emotional activity, reflecting a feeling of empathy for the
+robot. In \cite{sung_housewives_2008} survey, 73~\% of the participants reported
+to watch their Roomba running for fun. While in the beginning of our study, also
+a quite high proportion (6 of 9 households) reported to watch the robot for fun,
+after 2 and 6 months the number of households that engaged in this activity
+decreased by half.
+
+\paragraph*{Giving a robot demo to visitors.} It is somehow natural that owners
+of innovative devices show the device to others and ask for their opinion about
+it \citep{rogers_diffusion_1995}. However, this activity suggests that the robot
+is presented as a new part of the household to visitors.
+\cite{sung_domestic_2010} described that a vacuum cleaning robot can serve as a
+mediator and encourage social interaction among people. We categorize giving a
+demo of the robot to visitors / guests as such an activity. During the first 2
+weeks with the robot 8 of 9 households in our study showed their robot to
+others, and still after 2 and 6 months 5 of the households engaged in this
+activity. This number is more or less in accordance with the 57~\% of survey
+respondents who stated to give demonstrations to others
+\citep{sung_housewives_2008}.
+
+%\paragraph*{Taking photos / videos of the robot.} How far taking a photo or
+%video of a robot can be seen as an anthropomorphic interaction is questionable.
+%However, it reflects the fact that the robot is observed by the user who for
+%some reason is motivated to record the event. The number of households that
+%took a photo or video of the robot decreased over time from 5 households in the
+%beginning to 1 household after 6 months.
+
+\paragraph*{Personalizing the robot.} It has been found that people are
+motivated to personalize technology as a form of self-expression (identity
+projection) or when they use a technology a lot and know how to customize it
+(technical identity projection) \citep{blom_personalization:_2000}. Though
+\cite{sung_pimp_2009} found that some Roomba users who were given a
+customization toolkit personalized their Roomba, none of the users in her study
+who was \textit{not} given this toolkit personalized their Roomba. Also in our
+study none of the 9 households engaged in a personalization activity.
+
+\paragraph*{Giving a name to the robot.} Giving a name to an artificial agent
+reflects a certain kind of personal relationship to the agent. By naming a
+robot, it is not anonymous anymore, and might be perceived as a moral agent. As
+such, naming an artificial agent can be classified as anthropomorphizing this
+agent. It further suggests that the agent is talked to directly. Though more
+than 23~\% of the survey participants in \cite{sung_housewives_2008} study
+reported to name their Roomba, only 1 of 9 households in our study did so.
+
+\paragraph*{Talking directly to the robot.} Using direct speech toward an object
+or artificial agent that does not have the ability to recognize and process
+speech (such as verbal comments) or other sound cues, is an interesting
+phenomenon which can be classified as an anthropomorphic interaction. Whereas
+only 11~\% of the survey respondents in \cite{sung_housewives_2008} study
+reported to talk to their robot, around half of the households engaged in this
+activity and the proportion did not notably decrease over time.
+
+\paragraph*{Playing with the robot.} In our study, it were mostly children who
+engaged in playing with the robot, however, most of them stopped doing so after
+some time. The number of household playing with their Roomba decreased from 8
+when asked after 2 weeks with the robot, to 4 households after 2 months, and 1
+household after 6 months. In \cite{sung_housewives_2008} survey, 37~\% of the
+Roomba owners reported to play and experiment with their robot.\\
+
+%\paragraph*{Making adjustments to the home due to the robot.} To help Roomba
+%clean, \cite{sung_housewives_2008} found in an online survey that about half of
+%the 379 participants made physical modifications to their homes. This process
+%is referred to as \textit{roombarization}, and it seems to be a unique aspect
+%of adopting a domestic service robot. In our study, almost all the households
+%made adjustments when they used the robot for the first time in front of us.
+%However, during the first two weeks with the robot, only 3 households reported
+%to have adjusted something due to the robot, and after 6 months it was only 1
+%household that still engaged in this activity. This decrease is, however,
+%logical since after some time most people had done all the necessary
+%adjustments to enable the robot show a good performance.
+
+%\paragraph*{Emerging anthropomorphic interactions.} Another, from our side more
+%unexpected interaction that we would describe as somehow anthropomorphic, is
+%what we call \textit{``collaborative cleaning''} with the robot. In the initial
+%phase of the study, some people spontaneously helped the robot to clean by
+%either picking up crumbs from the floor themselves or pushing it right in front
+%of the robot. Another way of collaborating with the robot we observed was to
+%help it go everywhere by spontaneously putting up the trash bin or the carpet
+%in the bathroom (things that are not just lying around and need to be cleaned
+%up). However, the activity of collaborative cleaning faded out soon, and we
+%suspect it was encouraged by the novelty of the robot.\\
+
+Overall, Figure \ref{fig:roomba-activities} shows that as time goes by, less
+households engage in the before-mentioned non-cleaning activities with the
+vacuum cleaning robot: after 2 weeks, on average, 4.67 of 9 households engage in
+a human-like activity with the robot; after 2 months, the value decreases to
+2.83, and after 6 months to 2.3. Our interpretation is that the nature of
+human-robot interaction changes over time. More concretely, we suspect  that
+anthropomorphic / human-social interactions with the robot become less over
+time, and that only with some people these interactions sustain.
+
+\subsubsection{Perception of anthropomorphic characteristics of the robot\\}
+
+We also studied people's perception of the robot, and how it evolved over time
+(see Figure \ref{fig:roomba-perception}). The main idea was to find out which of
+the perceived attributes could be related to how far the robot was integrated in
+the household as a cleaning tool. Concerning anthropomorphism, we included
+\textit{perceived intelligence} and experienced \textit{fun} when using the
+robot as indicators for the perception of human-likeness in the robot.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.5\columnwidth]{roomba-perception.pdf}
 
@@
 
-\caption{User perception of the Roomba robot over a 6 month period
-($\sigma=15$).}
-
-\label{roomba-perception}
-\end{figure*}
-
-\subsection{Forum study: using anthropomorphic language to describe a robot}
-
-\hl{Julia: I think we should also include this study}
+    \caption{People's perception of the robot over time, n = 15 participants.
+    This line chart shows how people's perception of the robot evolves over
+    time. At 5 time points people were asked to rate the robot according to the
+    following aspects: the perceived \texttt{intelligence} of the robot, the
+    perceived \texttt{usefulness}, the perceived \texttt{ease of use}, how much
+    \texttt{fun} it was to use the robot, how far they found the robot had an
+    \texttt{impact} on their household, and their {overall} impression of it.}
+
+    \label{fig:roomba-perception}
+\end{figure}
+
+\paragraph*{Perceived intelligence.} On a scale from 1-7, people were not sure
+about how intelligent they should expect the robot to be (mean value 3.9). The
+rating did not change much and not significantly over time (average ratings
+between 3.3-4.2) \citep{fink_living_2013}. Interestingly, at all five time
+points, male participants rated the robot as more intelligent (average 4.5) than
+females (average 3.4), however, this difference was not significant. When asked
+why they thought Roomba possesses intelligence, men more often referred to the
+'robot side' of Roomba: its abilities to detect and avoid obstacles, stairs, and
+being able to recharge itself. Contrary, women referred to its rather limited
+vacuuming performance and found it was not as intelligent because \textit{``it
+doesn't see where the dirt is, it sometimes leaves it, it can't be smart!''}.
+This difference in the perception of intelligence of a robot suggests that
+gender,and probably other individual characteristics need to be taken into
+account.
+
+\paragraph*{Experienced fun.} Participants rated the robot as 'somewhat fun'
+(values from 4.0-4.6). There was a qualitative gender difference (not
+significant), in the sense that the experienced fun remained quite stable for
+male participants, whereas it tended to decrease with time for female
+participants. Men described the robot more as a 'fun gadget' than females, who
+referred to it as \textit{``In the end, Roomba is a cleaning tool and it is not
+really fun to use it''}. Again for this aspect, gender seems to play a role in
+how the robot is perceived and experienced.\\
+
+Overall, Figure \ref{fig:roomba-perception} shows that after the first usage of
+the Roomba (T2), most of the perceived constructs slightly decrease (and hence
+are less positively rated) as time goes by. The course is different for the
+perceived \textit{ease of use} of the robot, as participants become more
+experienced with the robot over time. Also, the experienced \textit{fun} does
+not decrease with time.
+
+\subsubsection{Summary Roomba study\\}
+
+In accordance with previous work we also found relatively low rates of users
+treating and perceiving their vacuum cleaning robot as a living (or human-like)
+entity \citep{sung_housewives_2008}. We interpret that it might be the pure
+functional purpose and non human-like form of the Roomba that prevented people
+from anthropomorphizing it. Still, we observed some initial anthropomorphic
+effects, both reflected in interaction with and perception of the robot.
+However, most of the anthropomorphic effects did not last long. \hl{One fairly
+stable human-like interaction with the robot was \textit{talking to the robot},
+despite the fact that the robot was not able to recognize and respond to verbal
+statements.\footnote{important! I think I've seen that finding somewhere else
+when comparing ASIMO to AIBO or so.}}
+
+\subsection{Forum study: using anthropomorphic expressions to describe a robot}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.7\columnwidth]{aibo-roomba-ipad_2.jpg}
+    \caption{The Sony AIBO robotic dog (left), the iRobot Roomba vacuum-cleaning robot (middle), and the Apple Inc.
+iPad tablet computer (right) were compared in terms of how far users of these devices use anthropomorphic expressions in discussions about their technology / robot in online discussion forums.}
+    \label{fig:aibo-roomba-ipad}
+\end{figure}
+
+We investigated the amount and context of anthropomorphic language in three
+online discussion forums about the robotic dog AIBO, the vacuum cleaning robot
+Roomba, and the tablet computer iPad. This was done by means of a content
+analysis of 750 forum posts that were further partitioned in n = 1208 valid
+segments \citep{fink_anthropomorphic_2012}. Hereafter, we refer to this study as
+the "Forum study". The three devices, pictured in Figure
+\ref{fig:aibo-roomba-ipad}, were chosen as they show different designs and
+fulfill different purposes. We would describe (1) AIBO as a zoomorphic /
+pet-like robot that does not have a clear purpose but engages people to play
+with it; (2) Roomba as a mechanical / functional domestic service robot that has
+a practical main purpose (vacuum cleaning) but offers not much of interactivity;
+(3) the iPad as a minimalistic designed interactive (touch-based) technology
+with multiple purposes (both entertainment, and professional / practical use).
+Based on these different characteristics, we made the two following hypotheses
+concerning anthropomorphism:
+
+\begin{enumerate}
+
+    	\item People engage in a more social and human-like way with a robotic pet compared to a functional robot and a tablet computer, therefore there will be a higher amount of anthropomorphic language in the AIBO and Roomba forum, compared to the iPad forum.
+
+    	\item As anthropomorphism can be seen as a certain kind of emotional / social relation to an artifact, there will be more anthropomorphic language in forum posts in which the author describes a relation to the device, compared to discussing technological aspects or how the device is used.
+\end{enumerate}
+
+Similar to how \cite{friedman_hardware_2003} analyzed anthropomorphic language
+in online forums, we coded a segment as anthropomorphic when the respective
+device was described in terms of:
+
+\begin{itemize}
+    \item \textit{Life-likeness}, uch as being alive or having (parts of) a
+        body, \eg \textit{``she can be reborn since you copied her memory
+        stick''};
+
+    \item \textit{Emotional states, empathy} or the technology having a
+        \textit{feeling}, \eg \textit{``oh no, poor AIBO''};
+
+    \item \textit{Gender, personality} or the technology having an
+        \textit{intention}, \eg Roomba \textit{``seems to like to hang around
+        under the sofa''};
+
+    \item When the author gave the technology a \textit{name}, \eg
+        \textit{``whenever I show Java his pink ball''};
+
+    \item Being \textit{socially integrated}, such as being a family member, \eg
+        \textit{``I'm considering adding a Roomba to the family''};
+
+    \item \textit{Metaphorical ways}, \eg Roomba \textit{``sings its victory
+        song when it finishes and docks''}.
+
+\end{itemize}
+
+In the next sections, we present findings in respect of our two hypotheses:
+anthropomorphic language related to the device, and anthropomorphic language
+related to the topic of the forum post.
+
+Overall, our analysis revealed that in all three forums, discussions about
+\textit{technical} aspects of the respective device were most frequent (67.7~\%
+of all 1208 categorized segments). However there were huge differences between
+the three devices: \textit{technical} aspects made up 79.9~\% of the discussion
+in the Roomba forum, compared to 69.9~\% in the AIBO forum, and 55.2~\% in the
+iPad forum. Another fairly frequently discussed topic concerned the
+\textit{usage} of the respective device, thus people describing how and for what
+they use their technology. This topic made up 21.8~\% of all posts, and was most
+frequent in the iPad forum (35.7~\%), followed by the Roomba forum (15.9~\%),
+and the AIBO forum (10.7~\%). Last but not least, we defined \textit{relation}
+as the third topic of interest. Discussions in which people described their
+relation to the respective device made up 10.5~\% of all posts, and was most
+frequent in the AIBO forum (19.4~\%), followed by the iPad forum (9.1~\%), and
+the Roomba forum (4.2~\%). \hl{(if it is getting too much we can leave out this
+paragraph, it's not crucial, and doesn't say anything about anthropomorphism
+directly)}
+
+\subsubsection{Anthropomorphic language related to the device (design)\\}
+
+A statistical analysis revealed a significant difference for the use of
+anthropomorphism across the three devices \citep{fink_anthropomorphic_2012}. In
+accordance with our first hypothesis, the highest amount of anthropomorphic
+language (56.6~\%) was found in the AIBO forum. In contrast, only 11.7~\% and
+respectively 2.2~\% of the segments in the Roomba and the iPad forum contained
+anthropomorphic expressions.  The data suggests that on a subjective scale of
+perceived human-likeness (or rather life-likeness), Roomba is closer to the iPad
+than to the AIBO, at least in matters of how they are described with words. This
+was a bit against our expectation. Still, the Roomba is an autonomous robot that
+can navigate around the house itself, and we expected this property to enhance
+anthropomorphism. We interpret that here, the physical embodiment of the object
+and how far it resembles a life-like entity determine how far the object is
+anthropomorphized, and as such the robotic dog is anthropomorphized more than
+the functionally designed devices.
+
+\subsubsection{Anthropomorphic language related to the topic of conversation\\}
+
+Also in terms of anthropomorphic language related to the topic of conversation,
+a statistical analysis revealed a significant difference
+\citep{fink_anthropomorphic_2012}. The analysis suggests that anthropomorphizing
+happens more when the topic of conversation is \textit{relation}, compared to
+\textit{usage}, and \textit{technical} aspects. This finding is qualitatively
+confirmed when looking at the distribution of anthropomorphic expressions across
+the three topics in the Roomba and iPad forum (with both technologies the
+highest amount of anthropomorphism is in the \textit{relation} topic). However,
+in the AIBO the amount of anthropomorphic segments is highest for the
+\textit{usage} topic.  We interpret that it is the different type of interaction
+/ use context that makes the difference. Contrary to the iPad and the Roomba,
+the AIBO is made to encourage its user in a playful / social interaction, which
+in turn is a typical use context. Furhter, AIBO has the ability to respond
+intelligently to its user and environment, which might also encourage people to
+ascribe human-like abilities to it while interacting with it.
+
+\subsubsection{Summary Forum study\\}
+
+Overall, findings of the content analysis suggest that there are differences in
+people's tendency to use anthropomorphic language, originating form the design
+characteristics of the artifact. Interestingly, not only the physical embodiment
+of the object but also the interaction complexity and purpose of use of the
+object seems to play a role in how far the object is anthropomorphized.
 
 \subsection{Ranger domino study: effect of unexpected robot behavior}
+
+The so-called "Ranger domino study" describes a child-robot interaction study
+that we carried out in a fairly controlled lab setting. One of the goals of this
+study was to investigate the effect of unexpected robot behavior on (1) the
+interaction and engagement with robot, and (2) how far children would ascribe
+human-like abilities (\eg intentions, cognitive abilities) to the robot.
+
+13 groups of each two children (n = 26) who were all between 4-5 years old and
+knew each other, were invited to play for around 20 minutes with the Ranger
+robot toy box \citep{fink2014which} and assemble a domino together. The robot
+was operated by one of the experimenters using the wizard-of-oz technique.
+Ranger was supposed to transport domino tiles between the two children and it
+would do its job correctly for the first 7 domino tiles. Then, however, the
+robot started misbehaving by either \textit{disobeying} to the child
 
@@
 cognitive explanations.
-
-\subsection{Towards an understanding of anthropomorphism}
-
-\fxnote{state here our main research hypothesis}
-\fxnote{state here our main contributions}
 

### 2014-03-20 paper.tex
Roomba study section started, new figure

--- 2014-03-19 paper.tex
@@
 \usepackage{tikz}
+\usepackage{caption}
+\usepackage{subcaption}
+\usepackage{float}
+\floatstyle{plaintop}
 \usetikzlibrary{shapes}
@@
 
-In this section we give a brief overview of the studies that we conducted to investigate anthropomorphism.
+In this section we give a brief overview of the studies that we conducted to investigate anthropomorphism in human-robot interaction.
 Note that it was not the main purpose of these studies to analyze in detail the effect of different dimensions human-likeness of a robot on the user's perception of and interaction with the robot.
-Each of these studies
-
-The strong points
+Each of these studies were motivated also by other research questions, and we encourage the reader to refer to our other main publications about these studies for more details.
 
@@
 
-\begin{figure*}[htb]
+We openly explored long-term interactions between human users and a domestic service robot in a 6-months lasting ethnographic study.
+We gave a commercially available vacuum cleaning robot (iRobot's Roomba) to nine different types of households in the French speaking part of Switzerland.
+The fairly diverse sample of households consisted of 2 single homes, 1 couple, and 6 families with children in their home.
+In total, this summed up to 30 participants: 15 adults (26-71 years old, mean age 43.6 years), and 15 children (6 months to 18 years old).
+During the 6 months, each household was visited 5 times to conduct interviews and make field observations in the households.
+Moreover during several weeks, households were asked to fill in a diary to report the usage of the robot and other cleaning activities.
+
+The main goal of this study was to explore how households live with a vacuum cleaning robot over an extended period of time.
+We wanted to analyze how the usage of and interaction with the robot evolve over time, and to identify adoption phases as well as factors that impact on the long-term acceptance of service robots in homes.
+\footnote{This study is published in \cite{fink_living_2013}.} Hereafter, we refer to this study as the "Roomba study".
+
+From the Roomba study, we can report on several findings related to anthropomorphism and the anthropomorphic design of robots.
+The gathered data for these aspects include qualitative observations, semi-structured interviews, and also quantitative assessments of various aspects of human-robot interaction.
+The Roomba study is one of very few long-term human-robot interaction studies in the domestic environment.
+
+In the following, we present findings in respect of two aspects:
+First, we qualitatively describe what kinds of anthropomorphic interactions between participants and the robot were observed and outline how these interactions evolved over time.
+Second, we present people's perception of human-likeness and social capabilities of the robot and how this perception changed over time.
+
+\subsubsection{Anthropomorphic interactions with the robot}
+
+It has been described in several previous studies of the Roomba \citep{forlizzi_service_2006,forlizzi_how_2007,krumm_my_2007,sung_domestic_2010}, that users tend to engage in a variety of non-cleaning activities associated with the Roomba including, but not limited to, naming, ascribing personality and gender.
+\cite{sung_housewives_2008} carried out a survey among 379 Roomba users to investigate how common these activities are.
+
+We also found that people tend to anthropomorphize or interact socially (in a broader sense) with their vacuum cleaning robot.
+However, our long-term observations suggest that this effect is marginal, and that the social impact of a functional robot on a household seems to be generally overestimated.
+In contrast to the previous work, we found that there were just few instances of people anthropomorphizing the robot and interacting with it in a human-social way.
+More importantly, overall, these anthropomorphic interactions with the robot did not last but seemed to be somehow related to the novelty of the robot.
+
+In terms of how people interacted with the robot, we categorized several interactions and actions with the robot as anthropomorphic or social, in a broader sense.
+Examples of what we categorized as somehow social and anthropomorphic (human-like) interactions with the robot include \textit{watching} the robot for fun, giving a \textit{demo} of the robot to guests / visitors, taking a \textit{photo/video} of the robot, \textit{personalizing} the robot, giving a \textit{name} to the robot, \textit{talking} to the robot using direct speech, \textit{playing} with the robot, and making \textit{adjustments} to the home due to the robot.
+Figure \ref{fig:roomba-activities}) shows how many of the 9 households engaged in what kind of activity with the robot at three different points of time after the robot was deployed in the household.
+
+\paragraph*{Watching the robot for fun.} We categorize watching a robot for fun as an entertaining, social activity, reflecting a feeling of empathy for the robot.
+In \cite{sung_housewives_2008} survey, 73~\% of the participants reported to watch their Roomba running for fun.
+While in the beginning of our study, also a quite high proportion (6 of 9 households) reported to watch the robot for fun, after 2 and 6 months the number of households that engaged in this activity decreased by half.
+
+\paragraph*{Giving a robot demo to visitors.} \cite{sung_domestic_2010} described that a vacuum cleaning robot can serve as a mediator and encourage social interaction among people.
+We categorize giving a demo of the robot to visitors / guest to the household as such an activity.
+During the first 2 weeks with the robot 8 of 9 households in our study showed their robot to others, and still after 2 and 6 months 5 of the households engaged in this activity.
+This number is more or less in accordance with the 57~\% of survey respondents who stated to give demonstrations to others \citep{sung_housewives_2008}.
+
+\paragraph*{Taking photos / videos of the robot.} How far taking a photo or video of a robot can be seen as an anthropomorphic interaction is questionable.
+However, it reflects the fact that the robot is observed by the user who for some reason is motivated to record the event.
+The number of households that took a photo or video of the robot decreased over time from 5 households in the beginning to 1 household after 6 months.
+
+\paragraph*{Personalizing the robot.} It has been found that people are motivated to personalize technology as a form of self-expression (identity projection) or when they use a technology a lot and know how to customize it (technical identity projection) \citep{blom_personalization:_2000}.
+Though \cite{sung_pimp_2009} found that some Roomba users who were given a customization toolkit personalized their Roomba, none of the users in her study who was \textit{not} given this toolkit personalized their Roomba.
+Also in our study none of the 9 households engaged in a personalization activity.
+
+\paragraph*{Giving a name to the robot.} Giving a name to an artificial agent reflects a certain kind of personal relationship to the agent.
+By naming a robot, it is not anonymous anymore, and might be perceived as a moral agent.
+As such, naming an artificial agent can be classified as anthropomorphizing this agent.
+It further suggests that the agent is talked to directly.
+Though more than 23~\% of the survey participants in \cite{sung_housewives_2008} study reported to name their Roomba, only 1 of 9 households in our study did so.
+
+\paragraph*{Talking directly to the robot.} Using direct speech toward an object or artificial agent that does not have the ability to recognize and process speech (such as verbal comments) or other sound cues, is an interesting phenomenon which can be classified as an anthropomorphic interaction.
+Whereas only 11~\% of the survey respondents in \cite{sung_housewives_2008} study reported to talk to their robot, around half of the households engaged in this activity and the proportion did not notably decrease over time.
+
+\paragraph*{Playing with the robot.} In our study, it were mostly children who engaged in playing with the robot, however, most of them stopped doing so after some time.
+The number of household playing with their Roomba decreased from 8 when asked after 2 weeks with the robot, to 4 households after 2 months, and 1 household after 6 months.
+In \cite{sung_housewives_2008} survey, 37~\% of the Roomba owners reported to play and experiment with their robot.
+
+\paragraph*{Making adjustments to the home due to the robot.} To help Roomba clean, \cite{sung_housewives_2008} found in an online survey that about half of the 379 participants made physical modifications to their homes.
+This process is referred to as \textit{roombarization}, and it seems to be a unique aspect of adopting a domestic service robot.
+In our study, almost all the households made adjustments when they used the robot for the first time in front of us.
+However, during the first two weeks with the robot, only 3 households reported to have adjusted something due to the robot, and after 6 months it was only 1 household that still engaged in this activity.
+This decrease is, however, logical since after some time most people had done all the necessary adjustments to enable the robot show a good performance.
+
+\paragraph*{Emerging anthropomorphic interactions.} Another, from our side more unexpected interaction that we would describe as somehow anthropomorphic, is what we call \textit{``collaborative cleaning''} with the robot.
+In the initial phase of the study, some people spontaneously helped the robot to clean by either picking up crumbs from the floor themselves or pushing it right in front of the robot.
+Another way of collaborating with the robot we observed was to help it go everywhere by spontaneously putting up the trash bin or the carpet in the bathroom (things that are not just lying around and need to be cleaned up).
+However, the activity of collaborative cleaning faded out soon, and we suspect it was encouraged by the novelty of the robot.
+
+\subsubsection{Perception of human-like characteristics of the robot}
+
+\begin{figure}[t]
 	\centering
 
-\begin{tikzpicture}[scale=0.5, y = 2cm]
-%axis
-\draw (0,0) -- coordinate (x axis mid) (20,0);
-\draw (0,0) -- coordinate (y axis mid) (0,7);
-%ticks
-\foreach \x in {0,4,...,20}
-    \draw (\x,1pt) -- (\x,-3pt);
-\foreach \y in {1,...,7} 
-    \draw[black!20] (20,\y) -- (-3pt,\y);
-\foreach \y in {1,...,7} 
-    \draw (-3pt, \y) node[anchor=east] {\y}; 
-%labels
-\node[below=0.8cm] at (x axis mid) {People's perception ($\sigma=15$)};
-\node at (2, -0.4) {\tiny expectations};
-\node[align=center] at (6, -0.4) {\tiny after\\ \tiny first usage};
-\node[align=center] at (10, -0.4) {\tiny after\\ \tiny 2 weeks};
-\node[align=center] at (14, -0.4) {\tiny after\\ \tiny 2 months};
-\node[align=center] at (18, -0.4) {\tiny after\\ \tiny 6 months};
-
-\draw[dashed, black!50] (6,0) -- (6,7) node[sloped, below, pos=0.25] {\tiny novelty effect};
-
-\draw[ultra thick, red!50] (2,5.6) -- (6,6.1) -- (10,6.3) -- (14,6.3) -- (18,6.1) node at (15,6.5) {\tiny \it ease of use};
-\draw[ultra thick, purple] (2,4.9) -- (6,5.2) -- (10,5.1) -- (14,4.5) -- (18,4.2) node at (3,4.7) {\tiny \it usefulness};
-\draw[ultra thick, blue!50] (2,4) -- (6,4.1) -- (10,4.6) -- (14,4.1) -- (18,4.3) node at (16,4) {\tiny \it fun};
-\draw[ultra thick, green!50] (2,3.9) -- (6,4.1) -- (10,4.2) -- (14,3.8) -- (18,3.3) node at (19,3.5) {\tiny \it intelligence};
-\draw[ultra thick, orange] (2,3.5) -- (6,4.2) -- (10,4) -- (14,3.2) -- (18,2.8) node at (14,2.7) {\tiny \it impact};
-
-\draw[ultra thick, dashed] (2,5.2) -- (6,5.2) -- (10,5) -- (14,4.9) -- (18,4.5) node at (14,5.3) {\tiny \it overall};
-
-\end{tikzpicture}
-
-\caption{User perception of the Roomba robot over a 6 month period
-($\sigma=15$).}
-
-\label{roomba-perception}
-\end{figure*}
+    \subfloat[activities with the robot over time,\\ n = 9 households]
+    {\label{fig:roomba-activities}
+    \includegraphics[width=8.5cm]{roomba-activities.png}}
+	\subfloat[people's perception of the robot over time,\\ n = 15 participants]    
+	{\label{fig:roomba-perception}
+    \includegraphics[width=8.5cm]{roomba-perception.pdf}}
+
+    \caption{\textbf{Activities with and perception of the robot over time.}\\
+	\textbf{(a)} This bar chart shows how many of the 9 households carried out different kinds of anthropomorphic / social activities with and related to the robot at 3 time points during 6 months.
+Activities include \texttt{watching} the robot for fun, giving a \texttt{demo} of the robot to guests / visitors, taking a \texttt{photo/video} of the robot, \texttt{personalizing} the robot, giving a \texttt{name} to the robot, \texttt{talking} to the robot, \texttt{playing} with the robot, and making \texttt{adjustments} to the home due to the robot.
+Participants were asked to report on these activities at 3 time points after the robot was deployed in their home: after 2 weeks, after 2 months, and after 6 months.\\
+	\textbf{(b)} This line chart shows how people's perception of the robot evolves over time.
+At 5 time points people were asked to rate the robot according to the following aspects: the perceived \texttt{intelligence} of the robot, the perceived \texttt{usefulness}, the perceived \texttt{easy of use}, how much \texttt{fun} it was to use the robot, how far they found the robot had an \texttt{impact} on their household, and their {overall} impression of it.}
+
+\end{figure}
+
+%\begin{figure*}[htb]
+%\centering
+%
+%\begin{tikzpicture}[scale=0.5, y = 2cm]
+%%axis
+%\draw (0,0) -- coordinate (x axis mid) (20,0);
+%\draw (0,0) -- coordinate (y axis mid) (0,7);
+%%ticks
+%\foreach \x in {0,4,...,20}
+%    \draw (\x,1pt) -- (\x,-3pt);
+%\foreach \y in {1,...,7} 
+%    \draw[black!20] (20,\y) -- (-3pt,\y);
+%\foreach \y in {1,...,7} 
+%    \draw (-3pt, \y) node[anchor=east] {\y}; 
+%%labels
+%\node[below=0.8cm] at (x axis mid) {People's perception ($\sigma=15$)};
+%\node at (2, -0.4) {\tiny expectations};
+%\node[align=center] at (6, -0.4) {\tiny after\\ \tiny first usage};
+%\node[align=center] at (10, -0.4) {\tiny after\\ \tiny 2 weeks};
+%\node[align=center] at (14, -0.4) {\tiny after\\ \tiny 2 months};
+%\node[align=center] at (18, -0.4) {\tiny after\\ \tiny 6 months};
+%
+%\draw[dashed, black!50] (6,0) -- (6,7) node[sloped, below, pos=0.25] {\tiny novelty effect};
+%
+%\draw[ultra thick, red!50] (2,5.6) -- (6,6.1) -- (10,6.3) -- (14,6.3) -- (18,6.1) node at (15,6.5) {\tiny \it ease of use};
+%\draw[ultra thick, purple] (2,4.9) -- (6,5.2) -- (10,5.1) -- (14,4.5) -- (18,4.2) node at (3,4.7) {\tiny \it usefulness};
+%\draw[ultra thick, blue!50] (2,4) -- (6,4.1) -- (10,4.6) -- (14,4.1) -- (18,4.3) node at (16,4) {\tiny \it fun};
+%\draw[ultra thick, green!50] (2,3.9) -- (6,4.1) -- (10,4.2) -- (14,3.8) -- (18,3.3) node at (19,3.5) {\tiny \it intelligence};
+%\draw[ultra thick, orange] (2,3.5) -- (6,4.2) -- (10,4) -- (14,3.2) -- (18,2.8) node at (14,2.7) {\tiny \it impact};
+%
+%\draw[ultra thick, dashed] (2,5.2) -- (6,5.2) -- (10,5) -- (14,4.9) -- (18,4.5) node at (14,5.3) {\tiny \it overall};
+%
+%\end{tikzpicture}
+%
+%\caption{User perception of the Roomba robot over a 6 month period
+%($\sigma=15$).}
+%
+%\label{roomba-perception}
+%\end{figure*}
+
+In accordance with \cite{sung_housewives_2008} we also found relatively low rates of users treating and perceiveing their vacuum cleaning robot as a living (or human-like) entity.
+We interpret that it might be the pure functional purpose and non human-like form of the Roomba vacuum cleaning robot that prevented people from anthropomorphizing it.
+Still, we observed some initial anthropomorphic effects, such as collaborative cleaning with the robot, and talking to the robot.
 

### 2014-03-21 paper.tex
refinements Roomba study part

@@
 We openly explored long-term interactions between human users and a domestic service robot in a 6-months lasting ethnographic study.
-We gave a commercially available vacuum cleaning robot (iRobot's Roomba) to nine different types of households in the French speaking part of Switzerland.
+We gave a commercially available vacuum cleaning robot (iRobot's Roomba) to nine households in the French speaking part of Switzerland.
 The fairly diverse sample of households consisted of 2 single homes, 1 couple, and 6 families with children in their home.
@@
 During the 6 months, each household was visited 5 times to conduct interviews and make field observations in the households.
-Moreover during several weeks, households were asked to fill in a diary to report the usage of the robot and other cleaning activities.
-
-The main goal of this study was to explore how households live with a vacuum cleaning robot over an extended period of time.
+Moreover, during several weeks, households were asked to fill in a diary to report the usage of the robot and other cleaning activities.
+\footnote{This study is published in \cite{fink_living_2013}.}
+Hereafter, we refer to this study as the "Roomba study".
+
+%The main goal of this study was to explore how households live with a vacuum cleaning robot over an extended period of time.
 We wanted to analyze how the usage of and interaction with the robot evolve over time, and to identify adoption phases as well as factors that impact on the long-term acceptance of service robots in homes.
-\footnote{This study is published in \cite{fink_living_2013}.} Hereafter, we refer to this study as the "Roomba study".
 
 From the Roomba study, we can report on several findings related to anthropomorphism and the anthropomorphic design of robots.
-The gathered data for these aspects include qualitative observations, semi-structured interviews, and also quantitative assessments of various aspects of human-robot interaction.
+%The gathered data for these aspects include qualitative observations, semi-structured interviews, and also quantitative assessments of various aspects of human-robot interaction.
 The Roomba study is one of very few long-term human-robot interaction studies in the domestic environment.
@@
 First, we qualitatively describe what kinds of anthropomorphic interactions between participants and the robot were observed and outline how these interactions evolved over time.
-Second, we present people's perception of human-likeness and social capabilities of the robot and how this perception changed over time.
-
-\subsubsection{Anthropomorphic interactions with the robot}
-
-It has been described in several previous studies of the Roomba \citep{forlizzi_service_2006,forlizzi_how_2007,krumm_my_2007,sung_domestic_2010}, that users tend to engage in a variety of non-cleaning activities associated with the Roomba including, but not limited to, naming, ascribing personality and gender.
+Second, we present people's perception of human-likeness and social capabilities of the robot and how this perception changed over time.\footnote{\hl{note that these two different kinds of data (behavior/interaction and perception) already show that we try to measure anthropomorphism from these two angles!}}
+
+\subsubsection{Anthropomorphic interactions with the robot\\}
+
+It has been described in several previous studies of the Roomba that users tend to engage in a variety of non-cleaning activities associated with the robot, including, but not limited to, naming, ascribing personality and gender \citep{forlizzi_service_2006,forlizzi_how_2007,krumm_my_2007,sung_domestic_2010}.
 \cite{sung_housewives_2008} carried out a survey among 379 Roomba users to investigate how common these activities are.
-
-We also found that people tend to anthropomorphize or interact socially (in a broader sense) with their vacuum cleaning robot.
-However, our long-term observations suggest that this effect is marginal, and that the social impact of a functional robot on a household seems to be generally overestimated.
-In contrast to the previous work, we found that there were just few instances of people anthropomorphizing the robot and interacting with it in a human-social way.
+The authors concluded that overall, respondents had relatively low rates of treating Roomba as a living entity.
+
+In our long-term study of the Roomba in homes, we found that it was mostly during the initial phase with the robot that some (rather few) people tended to interact in an anthropomorphic or human-social way with their vacuum cleaning robot.
+Overall, our data suggest that the anthropomorphic effect and the social impact of a functional robot on a household is rather marginal.
+%There were just few instances of people anthropomorphizing the robot and interacting with it in a human-social way.
 More importantly, overall, these anthropomorphic interactions with the robot did not last but seemed to be somehow related to the novelty of the robot.
 
-In terms of how people interacted with the robot, we categorized several interactions and actions with the robot as anthropomorphic or social, in a broader sense.
-Examples of what we categorized as somehow social and anthropomorphic (human-like) interactions with the robot include \textit{watching} the robot for fun, giving a \textit{demo} of the robot to guests / visitors, taking a \textit{photo/video} of the robot, \textit{personalizing} the robot, giving a \textit{name} to the robot, \textit{talking} to the robot using direct speech, \textit{playing} with the robot, and making \textit{adjustments} to the home due to the robot.
-Figure \ref{fig:roomba-activities}) shows how many of the 9 households engaged in what kind of activity with the robot at three different points of time after the robot was deployed in the household.
-
-\paragraph*{Watching the robot for fun.} We categorize watching a robot for fun as an entertaining, social activity, reflecting a feeling of empathy for the robot.
+We categorized several interactions and actions with the robot as anthropomorphic or human-social (in a broader sense). 
+%Examples of what we categorized as somehow social and anthropomorphic (human-like) interactions with the robot include \textit{watching} the robot for fun, giving a \textit{demo} of the robot to guests / visitors, taking a \textit{photo/video} of the robot, \textit{personalizing} the robot, giving a \textit{name} to the robot, \textit{talking} to the robot using direct speech, \textit{playing} with the robot, and making \textit{adjustments} to the home due to the robot.
+Figure \ref{fig:roomba-activities}) shows how many of the 9 households engaged in these activities during the 6 months when the study was conducted.
+
+\paragraph*{Watching the robot for fun.} We categorize watching a robot for fun as an entertaining, emotional activity, reflecting a feeling of empathy for the robot.
 In \cite{sung_housewives_2008} survey, 73~\% of the participants reported to watch their Roomba running for fun.
@@
 
-\paragraph*{Giving a robot demo to visitors.} \cite{sung_domestic_2010} described that a vacuum cleaning robot can serve as a mediator and encourage social interaction among people.
-We categorize giving a demo of the robot to visitors / guest to the household as such an activity.
+\paragraph*{Giving a robot demo to visitors.} It is somehow natural that owners of innovative devices show the device to others and ask for their opinion about it \citep{rogers_diffusion_1995}.
+However, this activity suggests that the robot is presented as a new part of the household to visitors.
+\cite{sung_domestic_2010} described that a vacuum cleaning robot can serve as a mediator and encourage social interaction among people.
+We categorize giving a demo of the robot to visitors / guests as such an activity.
 During the first 2 weeks with the robot 8 of 9 households in our study showed their robot to others, and still after 2 and 6 months 5 of the households engaged in this activity.
@@
 
-\paragraph*{Taking photos / videos of the robot.} How far taking a photo or video of a robot can be seen as an anthropomorphic interaction is questionable.
+%\paragraph*{Taking photos / videos of the robot.} How far taking a photo or video of a robot can be seen as an anthropomorphic interaction is questionable.
 However, it reflects the fact that the robot is observed by the user who for some reason is motivated to record the event.
@@
 The number of household playing with their Roomba decreased from 8 when asked after 2 weeks with the robot, to 4 households after 2 months, and 1 household after 6 months.
-In \cite{sung_housewives_2008} survey, 37~\% of the Roomba owners reported to play and experiment with their robot.
-
-\paragraph*{Making adjustments to the home due to the robot.} To help Roomba clean, \cite{sung_housewives_2008} found in an online survey that about half of the 379 participants made physical modifications to their homes.
+In \cite{sung_housewives_2008} survey, 37~\% of the Roomba owners reported to play and experiment with their robot.\\
+
+%\paragraph*{Making adjustments to the home due to the robot.} To help Roomba clean, \cite{sung_housewives_2008} found in an online survey that about half of the 379 participants made physical modifications to their homes.
 This process is referred to as \textit{roombarization}, and it seems to be a unique aspect of adopting a domestic service robot.
@@
 
-\paragraph*{Emerging anthropomorphic interactions.} Another, from our side more unexpected interaction that we would describe as somehow anthropomorphic, is what we call \textit{``collaborative cleaning''} with the robot.
+%\paragraph*{Emerging anthropomorphic interactions.} Another, from our side more unexpected interaction that we would describe as somehow anthropomorphic, is what we call \textit{``collaborative cleaning''} with the robot.
 In the initial phase of the study, some people spontaneously helped the robot to clean by either picking up crumbs from the floor themselves or pushing it right in front of the robot.
 Another way of collaborating with the robot we observed was to help it go everywhere by spontaneously putting up the trash bin or the carpet in the bathroom (things that are not just lying around and need to be cleaned up).
-However, the activity of collaborative cleaning faded out soon, and we suspect it was encouraged by the novelty of the robot.
-
-\subsubsection{Perception of human-like characteristics of the robot}
+However, the activity of collaborative cleaning faded out soon, and we suspect it was encouraged by the novelty of the robot.\\
+
+Overall, Figure \ref{fig:roomba-activities} shows that as time goes by, less households engage in the before-mentioned non-cleaning activities with the vacuum cleaning robot: after 2 weeks, on average, 4.67 of 9 households engage in a human-like activity with the robot; after 2 months, the value decreases to 2.83, and after 6 months to 2.3.
+Our interpretation is that the nature of human-robot interaction changes over time.
+More concretely, we suspect  that anthropomorphic / human-social interactions with the robot become less over time, and that only with some people these interactions sustain.
 
@@
     {\label{fig:roomba-activities}
-    \includegraphics[width=8.5cm]{roomba-activities.png}}
+    \includegraphics[width=8.5cm]{roomba-activities.pdf}}
 	\subfloat[people's perception of the robot over time,\\ n = 15 participants]    
@@
 	\textbf{(a)} This bar chart shows how many of the 9 households carried out different kinds of anthropomorphic / social activities with and related to the robot at 3 time points during 6 months.
-Activities include \texttt{watching} the robot for fun, giving a \texttt{demo} of the robot to guests / visitors, taking a \texttt{photo/video} of the robot, \texttt{personalizing} the robot, giving a \texttt{name} to the robot, \texttt{talking} to the robot, \texttt{playing} with the robot, and making \texttt{adjustments} to the home due to the robot.
+Activities include \texttt{watching} the robot for fun, giving a \texttt{demo} of the robot to guests / visitors, \texttt{personalizing} the robot, giving a \texttt{name} to the robot, \texttt{talking} to the robot, \texttt{playing} with the robot.
 Participants were asked to report on these activities at 3 time points after the robot was deployed in their home: after 2 weeks, after 2 months, and after 6 months.\\
 	\textbf{(b)} This line chart shows how people's perception of the robot evolves over time.
-At 5 time points people were asked to rate the robot according to the following aspects: the perceived \texttt{intelligence} of the robot, the perceived \texttt{usefulness}, the perceived \texttt{easy of use}, how much \texttt{fun} it was to use the robot, how far they found the robot had an \texttt{impact} on their household, and their {overall} impression of it.}
+At 5 time points people were asked to rate the robot according to the following aspects: the perceived \texttt{intelligence} of the robot, the perceived \texttt{usefulness}, the perceived \texttt{ease of use}, how much \texttt{fun} it was to use the robot, how far they found the robot had an \texttt{impact} on their household, and their {overall} impression of it.}
 
@@
 
-In accordance with \cite{sung_housewives_2008} we also found relatively low rates of users treating and perceiveing their vacuum cleaning robot as a living (or human-like) entity.
-We interpret that it might be the pure functional purpose and non human-like form of the Roomba vacuum cleaning robot that prevented people from anthropomorphizing it.
-Still, we observed some initial anthropomorphic effects, such as collaborative cleaning with the robot, and talking to the robot.
+\subsubsection{Perception of anthropomorphic characteristics of the robot\\}
+
+We also studied people's perception of the robot, and how it evolved over time (see Figure \ref{fig:roomba-perception}).
+The main idea was to find out which of the perceived attributes could be related to how far the robot was integrated in the household as a cleaning tool.
+
+Concerning anthropomorphism, we included \textit{perceived intelligence} and experienced \textit{fun} when using the robot as indicators for the perception of human-likeness in the robot.
+
+\paragraph*{Perceived intelligence.} On a scale from 1-7, people were not sure about how intelligent they should expect the robot to be (mean value 3.9).
+The rating did not change much and not significantly over time (average ratings between 3.3-4.2) \citep{fink_living_2013}.
+Interestingly, at all five time points, male participants rated the robot as more intelligent (average 4.5) than females (average 3.4), however, this difference was not significant.
+When asked why they thought Roomba possesses intelligence, men more often referred to the 'robot side' of Roomba: its abilities to detect and avoid obstacles, stairs, and being able to recharge itself.
+Contrary, women referred to its rather limited vacuuming performance and found it was not as intelligent because \textit{``it doesn't see where the dirt is, it sometimes leaves it, it can't be smart!''}.
+This difference in the perception of intelligence of a robot suggests that gender,and probably other individual characteristics need to be taken into account.
+
+\paragraph*{Experienced fun.} Participants rated the robot as 'somewhat fun' (values from 4.0-4.6).
+There was a qualitative gender difference (not significant), in the sense that the experienced fun remained quite stable for male participants, whereas it tended to decrease with time for female participants.
+Men described the robot more as a 'fun gadget' than females, who referred to it as \textit{``In the end, Roomba is a cleaning tool and it is not really fun to use it''}.
+Again for this aspect, gender seems to play a role in how the robot is perceived and experienced.
+
+\subsubsection{Summary Roomba study\\}
+
+In accordance with \cite{sung_housewives_2008} we also found relatively low rates of users treating and perceiving their vacuum cleaning robot as a living (or human-like) entity.
+We interpret that it might be the pure functional purpose and non human-like form of the Roomba that prevented people from anthropomorphizing it.
+Still, we observed some initial anthropomorphic effects, both reflected in interaction with and perception of the robot.
+However, most of the anthropomorphic effects did not last long.
+\hl{One fairly stable human-like interaction with the robot was \textit{talking to the robot}, despite the fact that the robot was not able to recognize and respond to verbal statements.\footnote{important!
+I think I've seen that finding somewhere else when comparing ASIMO to AIBO or so.}}
 
@@
 
-\hl{Julia: I think we should also include this study}
+\hl{Julia: I think we should also include this study ... if it is not getting too much}
 

### 2014-03-21 paper.tex
forum study section started, new figure

@@
 \usepackage{tikz}
-\usepackage{caption}
-\usepackage{subcaption}
-\usepackage{float}
-\floatstyle{plaintop}
+%\usepackage{caption}
+%\usepackage{subcaption}
+%\usepackage{float}
+%\floatstyle{plaintop}
 \usetikzlibrary{shapes}
@@
 At the end of this section we bring both perspectives together and interpret that anthropomorphism is a multi-factor phenomenon.
-Based on the two previous sections, we propose an initial model of the \textit{``Dynamics of Anthropomorphism''} in Section \ref{sec:dynamics-model}.
+Based on the two previous sections, we propose an initial model of the \textit{``Dynamics of Anthropomorphism''} in Section \ref{sec:our-ideas}.
 This model describes the variances and dynamics of people's tendency to anthropomorphize an artificial agent, such as a robot.
@@
 We openly explored long-term interactions between human users and a domestic service robot in a 6-months lasting ethnographic study.
-We gave a commercially available vacuum cleaning robot (iRobot's Roomba) to nine households in the French speaking part of Switzerland.
+We gave a commercially available vacuum cleaning robot (iRobot's Roomba, see Figure \ref{fig:aibo-roomba-ipad} middle) to nine households in the French speaking part of Switzerland.
 The fairly diverse sample of households consisted of 2 single homes, 1 couple, and 6 families with children in their home.
@@
 
+\begin{figure}
+    \centering
+    \includegraphics[width=0.5\columnwidth]{roomba-activities.png}
+    \caption{Activities with the robot over time, n = 9 households.
+This bar chart shows how many of the 9 households carried out different kinds of anthropomorphic / social activities with and related to the robot at 3 time points during 6 months.
+Activities include \texttt{watching} the robot for fun, giving a \texttt{demo} of the robot to guests / visitors, \texttt{personalizing} the robot, giving a \texttt{name} to the robot, \texttt{talking} to the robot, \texttt{playing} with the robot.
+Participants were asked to report on these activities at 3 time points after the robot was deployed in their home: after 2 weeks, after 2 months, and after 6 months.}
+    \label{fig:roomba-activities}
+\end{figure}
+
 \paragraph*{Watching the robot for fun.} We categorize watching a robot for fun as an entertaining, emotional activity, reflecting a feeling of empathy for the robot.
@@
 More concretely, we suspect  that anthropomorphic / human-social interactions with the robot become less over time, and that only with some people these interactions sustain.
-
-\begin{figure}[t]
-	\centering
-
-    \subfloat[activities with the robot over time,\\ n = 9 households]
-    {\label{fig:roomba-activities}
-    \includegraphics[width=8.5cm]{roomba-activities.pdf}}
-	\subfloat[people's perception of the robot over time,\\ n = 15 participants]    
-	{\label{fig:roomba-perception}
-    \includegraphics[width=8.5cm]{roomba-perception.pdf}}
-
-    \caption{\textbf{Activities with and perception of the robot over time.}\\
-	\textbf{(a)} This bar chart shows how many of the 9 households carried out different kinds of anthropomorphic / social activities with and related to the robot at 3 time points during 6 months.
-Activities include \texttt{watching} the robot for fun, giving a \texttt{demo} of the robot to guests / visitors, \texttt{personalizing} the robot, giving a \texttt{name} to the robot, \texttt{talking} to the robot, \texttt{playing} with the robot.
-Participants were asked to report on these activities at 3 time points after the robot was deployed in their home: after 2 weeks, after 2 months, and after 6 months.\\
-	\textbf{(b)} This line chart shows how people's perception of the robot evolves over time.
-At 5 time points people were asked to rate the robot according to the following aspects: the perceived \texttt{intelligence} of the robot, the perceived \texttt{usefulness}, the perceived \texttt{ease of use}, how much \texttt{fun} it was to use the robot, how far they found the robot had an \texttt{impact} on their household, and their {overall} impression of it.}
-
-\end{figure}
 
@@
 The main idea was to find out which of the perceived attributes could be related to how far the robot was integrated in the household as a cleaning tool.
-
 Concerning anthropomorphism, we included \textit{perceived intelligence} and experienced \textit{fun} when using the robot as indicators for the perception of human-likeness in the robot.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.5\columnwidth]{roomba-perception.pdf}
+    \caption{People's perception of the robot over time, n = 15 participants.
+This line chart shows how people's perception of the robot evolves over time.
+At 5 time points people were asked to rate the robot according to the following aspects: the perceived \texttt{intelligence} of the robot, the perceived \texttt{usefulness}, the perceived \texttt{ease of use}, how much \texttt{fun} it was to use the robot, how far they found the robot had an \texttt{impact} on their household, and their {overall} impression of it.}
+    \label{fig:roomba-perception}
+\end{figure}
 
@@
 Men described the robot more as a 'fun gadget' than females, who referred to it as \textit{``In the end, Roomba is a cleaning tool and it is not really fun to use it''}.
-Again for this aspect, gender seems to play a role in how the robot is perceived and experienced.
+Again for this aspect, gender seems to play a role in how the robot is perceived and experienced.\\
+
+Overall, Figure \ref{fig:roomba-perception} shows that after the first usage of the Roomba (T2), most of the perceived constructs slightly decrease (and hence are less positively rated) as time goes by.
+The course is different for the perceived \textit{ease of use} of the robot, as participants become more experienced with the robot over time.
+Also, the experienced \textit{fun} does not decrease with time.
 
@@
 
-In accordance with \cite{sung_housewives_2008} we also found relatively low rates of users treating and perceiving their vacuum cleaning robot as a living (or human-like) entity.
+In accordance with previous work we also found relatively low rates of users treating and perceiving their vacuum cleaning robot as a living (or human-like) entity \citep{sung_housewives_2008}.
 We interpret that it might be the pure functional purpose and non human-like form of the Roomba that prevented people from anthropomorphizing it.
@@
 
-\subsection{Forum study: using anthropomorphic language to describe a robot}
-
-\hl{Julia: I think we should also include this study ... if it is not getting too much}
+\subsection{Forum study: using anthropomorphic expressions to describe a robot}
+
+We investigated the amount and context of anthropomorphic language in three online discussion forums about the robotic dog AIBO, the vacuum cleaning robot Roomba, and the tablet computer iPad.
+This analysis was done by means of a content analysis of 750 forum posts that were further partitioned in n = 1208 valid segments \citep{fink_anthropomorphic_2012}.
+These three devices, pictured in Figure \ref{fig:aibo-roomba-ipad}, were chosen as they show different designs and fulfill different purposes.
+We would describe (1) AIBO as a zoomorphic / pet-like robot that does not have a clear purpose but engages people to play with it; (2) Roomba as a mechanical / functional domestic service robot that has a practical main purpose (vacuum cleaning) but offers not much of interactivity; (3) the iPad as a minimalistic designed interactive (touch-based) technology with multiple purposes (both entertainment, and professional / practical use).
+Based on these different characteristics, we made the two following hypotheses concerning anthropomorphism:
+
+\begin{enumerate}
+	\item People engage in a more social and human-like way with a robotic pet compared to a functional robot and a tablet computer, therefore there will be a higher amount of anthropomorphic language in the AIBO and Roomba forum, compared to the iPad forum.
+	\item As anthropomorphism can be seen as a certain kind of emotional / social relation to an artifact, there will be more anthropomorphic language in forum posts in which the author describes a relation to the device, compared to discussing technological aspects or how the device is used.
+\end{enumerate}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.7\columnwidth]{aibo-roomba-ipad_2.jpg}
+    \caption{The Sony AIBO robotic dog (left), the iRobot Roomba vacuum-cleaning robot (middle), and the Apple Inc.
+iPad tablet computer (right) were compared in terms of how far users of these devices use anthropomorphic expressions in discussions about their technology / robot in online discussion forums.}
+    \label{fig:aibo-roomba-ipad}
+\end{figure}
 

### 2014-03-21 paper.tex
Forum study part complete

@@
 
-We investigated the amount and context of anthropomorphic language in three online discussion forums about the robotic dog AIBO, the vacuum cleaning robot Roomba, and the tablet computer iPad.
-This analysis was done by means of a content analysis of 750 forum posts that were further partitioned in n = 1208 valid segments \citep{fink_anthropomorphic_2012}.
-These three devices, pictured in Figure \ref{fig:aibo-roomba-ipad}, were chosen as they show different designs and fulfill different purposes.
-We would describe (1) AIBO as a zoomorphic / pet-like robot that does not have a clear purpose but engages people to play with it; (2) Roomba as a mechanical / functional domestic service robot that has a practical main purpose (vacuum cleaning) but offers not much of interactivity; (3) the iPad as a minimalistic designed interactive (touch-based) technology with multiple purposes (both entertainment, and professional / practical use).
-Based on these different characteristics, we made the two following hypotheses concerning anthropomorphism:
-
-\begin{enumerate}
-	\item People engage in a more social and human-like way with a robotic pet compared to a functional robot and a tablet computer, therefore there will be a higher amount of anthropomorphic language in the AIBO and Roomba forum, compared to the iPad forum.
-	\item As anthropomorphism can be seen as a certain kind of emotional / social relation to an artifact, there will be more anthropomorphic language in forum posts in which the author describes a relation to the device, compared to discussing technological aspects or how the device is used.
-\end{enumerate}
-
 \begin{figure}
@@
 \end{figure}
+
+We investigated the amount and context of anthropomorphic language in three online discussion forums about the robotic dog AIBO, the vacuum cleaning robot Roomba, and the tablet computer iPad.
+This was done by means of a content analysis of 750 forum posts that were further partitioned in n = 1208 valid segments \citep{fink_anthropomorphic_2012}.
+Hereafter, we refer to this study as the "Forum study".
+The three devices, pictured in Figure \ref{fig:aibo-roomba-ipad}, were chosen as they show different designs and fulfill different purposes.
+We would describe (1) AIBO as a zoomorphic / pet-like robot that does not have a clear purpose but engages people to play with it; (2) Roomba as a mechanical / functional domestic service robot that has a practical main purpose (vacuum cleaning) but offers not much of interactivity; (3) the iPad as a minimalistic designed interactive (touch-based) technology with multiple purposes (both entertainment, and professional / practical use).
+Based on these different characteristics, we made the two following hypotheses concerning anthropomorphism:
+
+\begin{enumerate}
+	\item People engage in a more social and human-like way with a robotic pet compared to a functional robot and a tablet computer, therefore there will be a higher amount of anthropomorphic language in the AIBO and Roomba forum, compared to the iPad forum.
+	\item As anthropomorphism can be seen as a certain kind of emotional / social relation to an artifact, there will be more anthropomorphic language in forum posts in which the author describes a relation to the device, compared to discussing technological aspects or how the device is used.
+\end{enumerate}
+
+Similar to how \cite{friedman_hardware_2003} analyzed anthropomorphic language in online forums, we coded a segment as anthropomorphic when the respective device was described in terms of:
+
+\begin{itemize}
+	\item \textit{Life-likeness}, uch as being alive or having (parts of) a body, \eg \textit{``she can be reborn since you copied her memory stick''};
+	\item \textit{Emotional states} or the technology having a feeling, \eg \textit{``oh no, poor AIBO''};
+	\item \textit{Gender, personality} or the technology having an \textit{intention}, \eg Roomba \textit{``seems to like to hang around under the sofa''};
+	\item When the author gave the technology a \textit{name}, \eg \textit{``whenever I show Java his pink ball''};
+	\item Being \textit{socially integrated}, such as being a family member, \eg \textit{``I'm considering adding a Roomba to the family''};
+	\item \textit{Metaphorical ways}, \eg Roomba \textit{``sings its victory song when it finishes and docks''}.
+\end{itemize}
+
+In the next sections, we present findings in respect of our two hypotheses: anthropomorphic language related to the device, and anthropomorphic language related to the topic of the forum post.
+
+Overall, our analysis revealed that in all three forums, discussions about \textit{technical} aspects of the respective device were most frequent (67.7~\% of all 1208 categorized segments).
+However there were huge differences between the three devices: \textit{technical} aspects made up 79.9~\% of the discussion in the Roomba forum, compared to 69.9~\% in the AIBO forum, and 55.2~\% in the iPad forum.
+Another fairly frequently discussed topic concerned the \textit{usage} of the respective device, thus people describing how and for what they use their technology.
+This topic made up 21.8~\% of all posts, and was most frequent in the iPad forum (35.7~\%), followed by the Roomba forum (15.9~\%), and the AIBO forum (10.7~\%).
+Last but not least, we defined \textit{relation} as the third topic of interest.
+Discussions in which people described their relation to the respective device made up 10.5~\% of all posts, and was most frequent in the AIBO forum (19.4~\%), followed by the iPad forum (9.1~\%), and the Roomba forum (4.2~\%).
+\hl{(if it is getting too much we can leave out this paragraph, it's not crucial, and doesn't say anything about anthropomorphism directly)}
+
+\subsubsection{Anthropomorphic language related to the device (design)\\}
+
+A statistical analysis revealed a significant difference for the use of anthropomorphism across the three devices \citep{fink_anthropomorphic_2012}.
+In accordance with our first hypothesis, the highest amount of anthropomorphic language (56.6~\%) was found in the AIBO forum.
+In contrast, only 11.7~\% and respectively 2.2~\% of the segments in the Roomba and the iPad forum contained anthropomorphic expressions.
+The data suggests that on a subjective scale of perceived human-likeness (or rather life-likeness), Roomba is closer to the iPad than to the AIBO, at least in matters of how they are described with words.
+This was a bit against our expectation.
+Still, the Roomba is an autonomous robot that can navigate around the house itself, and we expected this property to enhance anthropomorphism.
+We interpret that here, the physical embodiment of the object and how far it resembles a life-like entity determine how far the object is anthropomorphized, and as such the robotic dog is anthropomorphized more than the functionally designed devices.
+
+\subsubsection{Anthropomorphic language related to the topic of conversation\\}
+
+Also in terms of anthropomorphic language related to the topic of conversation, a statistical analysis revealed a significant difference \citep{fink_anthropomorphic_2012}.
+The analysis suggests that anthropomorphizing happens more when the topic of conversation is \textit{relation}, compared to \textit{usage}, and \textit{technical} aspects.
+This finding is qualitatively confirmed when looking at the distribution of anthropomorphic expressions across the three topics in the Roomba and iPad forum (with both technologies the highest amount of anthropomorphism is in the \textit{relation} topic).
+However, in the AIBO the amount of anthropomorphic segments is highest for the \textit{usage} topic.
+We interpret that it is the different type of interaction / use context that makes the difference.
+Contrary to the iPad and the Roomba, the AIBO is made to encourage its user in a playful / social interaction, which in turn is a typical use context.
+Furhter, AIBO has the ability to respond intelligently to its user and environment, which might also encourage people to ascribe human-like abilities to it while interacting with it.
+
+\subsubsection{Summary Forum study\\}
+
+Overall, findings of the content analysis suggest that there are differences in people's tendency to use anthropomorphic language, originating form the design characteristics of the artifact.
+Interestingly, not only the physical embodiment of the object but also the interaction complexity and purpose of use of the object seems to play a role in how far the object is anthropomorphized.
 

### 2014-03-21 paper.tex
Line wrapping at 80 char + bring back roomba perception fig

@@
 \usepackage{tikz}
-%\usepackage{caption}
-%\usepackage{subcaption}
-%\usepackage{float}
-%\floatstyle{plaintop}
 \usetikzlibrary{shapes}
@@
 %{Intro when start with anthropomorphic design}
-The Uncanny Valley hypothesis \citep{mori_uncanny_1970} proposes that human-like designs of objects and non-human agents evoke a positive feeling of affinity in the human observer / user, which in turn reflects the experience of emotional engagement with and feelings of empathy for the non-human agent \citep{cheetham_human_2011}.
-The positive effect of so-called \textbf{anthropomorphic form} is exploited in the design of artificial agents (\eg digital characters, robots) for several reasons.
-Amongst others, anthropomorphic design should serve to evoke a positive valence as the Uncanny Valley hypothesis suggests, which in turn should foster people's acceptance of the artificial agent, and enable effective (human-like and especially human-social) interaction.
-However, at a certain point as the non-human agent approaches but fails to closely resemble a human, the evoked valence in the human user suddenly turns into a negative uncanny feeling of what \cite{mori_uncanny_1970} describes as disgust and revulsion.
-This, in turn, might lead to rejection of the non-human but human-like agent.
-The Uncanny Valley hypothesis predicts that with further increasing the human-likeness of the non-human agent such that it appears so realistic that it is not distinguishable from a human but perceived to be human, the effect is again a positive one, reflecting feelings and engagement that are similar as those evoked by a human-human interaction.
-Of course, roboticists and developers try to avoid ``falling'' into this Uncanny Valley with their human-like designs of artificial agents.
-Consequently, there is a considerable research effort into better understanding the boundaries of anthropomorphic design and their effect on the interaction and experience.
-However, findings have been inconsistent \citep{cheetham_human_2011}.
-
-A phenomenon that is often studied related to the human-like design of robots is \textbf{anthropomorphism}.
-Besides a feeling of affinity, and empathy, anthropomorphism can be understood as being one of the resulting (and  more or less desired) effects of the anthropomorphic design of artificial agents (up to the first positive peak).
-The essence of anthropomorphism is the human user's perception of human-likeness in the non-human agent.
-Logically, anthropomorphism is said to be enhanced with increased human-like design of the agent.
-There are various other reasons and explanations for why people tend to anthropomorphize non-human agents.
-In general, as anthropomorphism emerges in a (real or imagined) interaction \citep{persson_anthropomorphism_2000} between at least two players (the human who anthropomorphizes and the non-human agent which is anthropomorphized) there are also two main perspectives on the phenomenon: an artifact-centered (design) and a human-centered (cognitive, psychological) one.
-The Uncanny Valley hypothesis can be categorized as being part of first, artifact-centered approach, to understand anthropomorphism.\\
-
-We observed anthropomorphism in several short- and long-term human-robot interaction studies that we carried out with embodied robots, mostly in real-world settings.
-There is not much research that investigates anthropomorphism based on real interaction between a human and a robot, and above all in natural settings and over extended periods of time.
-
-Our data suggest that there are qualitative differences and dynamics over time in how humans relate to different types of robots.
-More concretely, we found that people's perception of human-likeness in the robot and in turn their human-social engagement with the robot was not only based on how much the robot resembled a human (mostly in its behavioral cues)
-but that this was determined by multiple factors, including individual
-characteristics of the human user but also the context of use, for instance.
-Interestingly, our findings also suggest that how far people anthropomorphize a robot is likely to change over time with growing experience of the
-user with the system.
-
-Based on these observations and an extensive literature review, we would like to propose a model that accounts for variances and dynamics in anthropomorphism.
-This model of the \textit{``Dynamics of Anthropomorphism''} considers several impact factors, including the human user, the anthropomorphic design of the non-human agent, the context of use, and the interaction experience (time).
-With this initial model, we would like to extend the current understanding of anthropomorphism in robotics and human-robot interaction.
-This might in turn lead to a discussion about the short- and long-term benefits and other effects of the human-like (anthropomorphic) design of robots and other artificial agents.\\
-
-The remainder of this article is organized as follows. 
-First, in Section \ref{sec:overview-studies}, we give a brief overview on the various studies that we conducted to investigate anthropomorphism, namely (1) the Roomba study, (2) the Forum study, (3) the Ranger domino study.
-As an outcome of these studies, we propose two main research hypotheses related to anthropomorphism.
-Next, in Section \ref{sec:anthropomorphism} we investigate these hypotheses by synthesizing literature on anthropomorphism.
-This should also serve to establish a common ground.
-We first explore an artifact-centered perspective and briefly outline how the human-like design of agents can encourage anthropomorphism.
-Then, we explore a human-centered perspective by integrating theories from cognitive science, developmental and social psychology that serve to explain anthropomorphism.
-At the end of this section we bring both perspectives together and interpret that anthropomorphism is a multi-factor phenomenon.
-Based on the two previous sections, we propose an initial model of the \textit{``Dynamics of Anthropomorphism''} in Section \ref{sec:our-ideas}.
-This model describes the variances and dynamics of people's tendency to anthropomorphize an artificial agent, such as a robot.
-Next, in Section \ref{sec:cognition-neuroscience} we present a cognitive and neuroscience perspective on anthropomorphism to consolidate our considerations and the proposed model.
-This will be followed by a discussion about the limitations of our approach (Section \ref{sec:discussion}). Further, we debate existing and alternative ways to measure
-anthropomorphism in human-robot interactions.
-Finally, Section \ref{sec:conclusion} concludes this article and offers starting points for further research on anthropomorphism and the effect of the human-like design approach in robotics.
+The Uncanny Valley hypothesis \citep{mori_uncanny_1970} proposes that human-like
+designs of objects and non-human agents evoke a positive feeling of affinity in
+the human observer / user, which in turn reflects the experience of emotional
+engagement with and feelings of empathy for the non-human agent
+\citep{cheetham_human_2011}. The positive effect of so-called
+\textbf{anthropomorphic form} is exploited in the design of artificial agents
+(\eg digital characters, robots) for several reasons. Amongst others,
+anthropomorphic design should serve to evoke a positive valence as the Uncanny
+Valley hypothesis suggests, which in turn should foster people's acceptance of
+the artificial agent, and enable effective (human-like and especially
+human-social) interaction.  However, at a certain point as the non-human agent
+approaches but fails to closely resemble a human, the evoked valence in the
+human user suddenly turns into a negative uncanny feeling of what
+\cite{mori_uncanny_1970} describes as disgust and revulsion. This, in turn,
+might lead to rejection of the non-human but human-like agent.  The Uncanny
+Valley hypothesis predicts that with further increasing the human-likeness of
+the non-human agent such that it appears so realistic that it is not
+distinguishable from a human but perceived to be human, the effect is again a
+positive one, reflecting feelings and engagement that are similar as those
+evoked by a human-human interaction.  Of course, roboticists and developers try
+to avoid ``falling'' into this Uncanny Valley with their human-like designs of
+artificial agents. Consequently, there is a considerable research effort into
+better understanding the boundaries of anthropomorphic design and their effect
+on the interaction and experience. However, findings have been inconsistent
+\citep{cheetham_human_2011}.
+
+A phenomenon that is often studied related to the human-like design of robots is
+\textbf{anthropomorphism}. Besides a feeling of affinity, and empathy,
+anthropomorphism can be understood as being one of the resulting (and  more or
+less desired) effects of the anthropomorphic design of artificial agents (up to
+the first positive peak). The essence of anthropomorphism is the human user's
+perception of human-likeness in the non-human agent. Logically, anthropomorphism
+is said to be enhanced with increased human-like design of the agent. There are
+various other reasons and explanations for why people tend to anthropomorphize
+non-human agents. In general, as anthropomorphism emerges in a (real or
+imagined) interaction \citep{persson_anthropomorphism_2000} between at least two
+players (the human who anthropomorphizes and the non-human agent which is
+anthropomorphized) there are also two main perspectives on the phenomenon: an
+artifact-centered (design) and a human-centered (cognitive, psychological) one.
+The Uncanny Valley hypothesis can be categorized as being part of first,
+artifact-centered approach, to understand anthropomorphism.\\
+
+We observed anthropomorphism in several short- and long-term human-robot
+interaction studies that we carried out with embodied robots, mostly in
+real-world settings. There is not much research that investigates
+anthropomorphism based on real interaction between a human and a robot, and
+above all in natural settings and over extended periods of time.
+
+Our data suggest that there are qualitative differences and dynamics over time
+in how humans relate to different types of robots. More concretely, we found
+that people's perception of human-likeness in the robot and in turn their
+human-social engagement with the robot was not only based on how much the robot
+resembled a human (mostly in its behavioral cues) but that this was determined
+by multiple factors, including individual characteristics of the human user but
+also the context of use, for instance. Interestingly, our findings also suggest
+that how far people anthropomorphize a robot is likely to change over time with
+growing experience of the user with the system.
+
+Based on these observations and an extensive literature review, we would like to
+propose a model that accounts for variances and dynamics in anthropomorphism.
+This model of the \textit{``Dynamics of Anthropomorphism''} considers several
+impact factors, including the human user, the anthropomorphic design of the
+non-human agent, the context of use, and the interaction experience (time). With
+this initial model, we would like to extend the current understanding of
+anthropomorphism in robotics and human-robot interaction. This might in turn
+lead to a discussion about the short- and long-term benefits and other effects
+of the human-like (anthropomorphic) design of robots and other artificial
+agents.\\
+
+The remainder of this article is organized as follows.  First, in Section
+\ref{sec:overview-studies}, we give a brief overview on the various studies that
+we conducted to investigate anthropomorphism, namely (1) the Roomba study, (2)
+the Forum study, (3) the Ranger domino study. As an outcome of these studies, we
+propose two main research hypotheses related to anthropomorphism.  Next, in
+Section \ref{sec:anthropomorphism} we investigate these hypotheses by
+synthesizing literature on anthropomorphism. This should also serve to establish
+a common ground. We first explore an artifact-centered perspective and briefly
+outline how the human-like design of agents can encourage anthropomorphism.
+Then, we explore a human-centered perspective by integrating theories from
+cognitive science, developmental and social psychology that serve to explain
+anthropomorphism. At the end of this section we bring both perspectives together
+and interpret that anthropomorphism is a multi-factor phenomenon.  Based on the
+two previous sections, we propose an initial model of the \textit{``Dynamics of
+Anthropomorphism''} in Section \ref{sec:our-ideas}. This model describes the
+variances and dynamics of people's tendency to anthropomorphize an artificial
+agent, such as a robot.  Next, in Section \ref{sec:cognition-neuroscience} we
+present a cognitive and neuroscience perspective on anthropomorphism to
+consolidate our considerations and the proposed model.  This will be followed by
+a discussion about the limitations of our approach (Section
+\ref{sec:discussion}). Further, we debate existing and alternative ways to
+measure anthropomorphism in human-robot interactions.  Finally, Section
+\ref{sec:conclusion} concludes this article and offers starting points for
+further research on anthropomorphism and the effect of the human-like design
+approach in robotics.
 
@@
 
-In this section we give a brief overview of the studies that we conducted to investigate anthropomorphism in human-robot interaction.
-Note that it was not the main purpose of these studies to analyze in detail the effect of different dimensions human-likeness of a robot on the user's perception of and interaction with the robot.
-Each of these studies were motivated also by other research questions, and we encourage the reader to refer to our other main publications about these studies for more details.
+In this section we give a brief overview of the studies that we conducted to
+investigate anthropomorphism in human-robot interaction. Note that it was not
+the main purpose of these studies to analyze in detail the effect of different
+dimensions human-likeness of a robot on the user's perception of and interaction
+with the robot. Each of these studies were motivated also by other research
+questions, and we encourage the reader to refer to our other main publications
+about these studies for more details.
 
@@
 
-We openly explored long-term interactions between human users and a domestic service robot in a 6-months lasting ethnographic study.
-We gave a commercially available vacuum cleaning robot (iRobot's Roomba, see Figure \ref{fig:aibo-roomba-ipad} middle) to nine households in the French speaking part of Switzerland.
-The fairly diverse sample of households consisted of 2 single homes, 1 couple, and 6 families with children in their home.
-In total, this summed up to 30 participants: 15 adults (26-71 years old, mean age 43.6 years), and 15 children (6 months to 18 years old).
-During the 6 months, each household was visited 5 times to conduct interviews and make field observations in the households.
-Moreover, during several weeks, households were asked to fill in a diary to report the usage of the robot and other cleaning activities.
-\footnote{This study is published in \cite{fink_living_2013}.}
-Hereafter, we refer to this study as the "Roomba study".
-
-%The main goal of this study was to explore how households live with a vacuum cleaning robot over an extended period of time.
-We wanted to analyze how the usage of and interaction with the robot evolve over time, and to identify adoption phases as well as factors that impact on the long-term acceptance of service robots in homes.
-
-From the Roomba study, we can report on several findings related to anthropomorphism and the anthropomorphic design of robots.
-%The gathered data for these aspects include qualitative observations, semi-structured interviews, and also quantitative assessments of various aspects of human-robot interaction.
-The Roomba study is one of very few long-term human-robot interaction studies in the domestic environment.
-
-In the following, we present findings in respect of two aspects:
-First, we qualitatively describe what kinds of anthropomorphic interactions between participants and the robot were observed and outline how these interactions evolved over time.
-Second, we present people's perception of human-likeness and social capabilities of the robot and how this perception changed over time.\footnote{\hl{note that these two different kinds of data (behavior/interaction and perception) already show that we try to measure anthropomorphism from these two angles!}}
+We openly explored long-term interactions between human users and a domestic
+service robot in a 6-months lasting ethnographic study. We gave a commercially
+available vacuum cleaning robot (iRobot's Roomba, see Figure
+\ref{fig:aibo-roomba-ipad} middle) to nine households in the French speaking
+part of Switzerland. The fairly diverse sample of households consisted of 2
+single homes, 1 couple, and 6 families with children in their home. In total,
+this summed up to 30 participants: 15 adults (26-71 years old, mean age 43.6
+years), and 15 children (6 months to 18 years old). During the 6 months, each
+household was visited 5 times to conduct interviews and make field observations
+in the households. Moreover, during several weeks, households were asked to fill
+in a diary to report the usage of the robot and other cleaning activities.
+\footnote{This study is published in \cite{fink_living_2013}.} Hereafter, we
+refer to this study as the "Roomba study".
+
+%The main goal of this study was to explore how households live with a vacuum
+%cleaning robot over an extended period of time. We wanted to analyze how the
+%usage of and interaction with the robot evolve over time, and to identify
+%adoption phases as well as factors that impact on the long-term acceptance of
+%service robots in homes.
+
+From the Roomba study, we can report on several findings related to
+anthropomorphism and the anthropomorphic design of robots.
+%The gathered data for these aspects include qualitative observations,
+%semi-structured interviews, and also quantitative assessments of various
+%aspects of human-robot interaction.
+The Roomba study is one of very few long-term human-robot interaction studies in
+the domestic environment.
+
+In the following, we present findings in respect of two aspects: First, we
+qualitatively describe what kinds of anthropomorphic interactions between
+participants and the robot were observed and outline how these interactions
+evolved over time.  Second, we present people's perception of human-likeness and
+social capabilities of the robot and how this perception changed over
+time.\footnote{\hl{note that these two different kinds of data
+(behavior/interaction and perception) already show that we try to measure
+anthropomorphism from these two angles!}}
 
@@
 
-It has been described in several previous studies of the Roomba that users tend to engage in a variety of non-cleaning activities associated with the robot, including, but not limited to, naming, ascribing personality and gender \citep{forlizzi_service_2006,forlizzi_how_2007,krumm_my_2007,sung_domestic_2010}.
-\cite{sung_housewives_2008} carried out a survey among 379 Roomba users to investigate how common these activities are.
-The authors concluded that overall, respondents had relatively low rates of treating Roomba as a living entity.
-
-In our long-term study of the Roomba in homes, we found that it was mostly during the initial phase with the robot that some (rather few) people tended to interact in an anthropomorphic or human-social way with their vacuum cleaning robot.
-Overall, our data suggest that the anthropomorphic effect and the social impact of a functional robot on a household is rather marginal.
-%There were just few instances of people anthropomorphizing the robot and interacting with it in a human-social way.
-More importantly, overall, these anthropomorphic interactions with the robot did not last but seemed to be somehow related to the novelty of the robot.
-
-We categorized several interactions and actions with the robot as anthropomorphic or human-social (in a broader sense). 
-%Examples of what we categorized as somehow social and anthropomorphic (human-like) interactions with the robot include \textit{watching} the robot for fun, giving a \textit{demo} of the robot to guests / visitors, taking a \textit{photo/video} of the robot, \textit{personalizing} the robot, giving a \textit{name} to the robot, \textit{talking} to the robot using direct speech, \textit{playing} with the robot, and making \textit{adjustments} to the home due to the robot.
-Figure \ref{fig:roomba-activities}) shows how many of the 9 households engaged in these activities during the 6 months when the study was conducted.
+It has been described in several previous studies of the Roomba that users tend
+to engage in a variety of non-cleaning activities associated with the robot,
+including, but not limited to, naming, ascribing personality and gender
+\citep{forlizzi_service_2006,forlizzi_how_2007,krumm_my_2007,sung_domestic_2010}.
+\cite{sung_housewives_2008} carried out a survey among 379 Roomba users to
+investigate how common these activities are. The authors concluded that overall,
+respondents had relatively low rates of treating Roomba as a living entity.
+
+In our long-term study of the Roomba in homes, we found that it was mostly
+during the initial phase with the robot that some (rather few) people tended to
+interact in an anthropomorphic or human-social way with their vacuum cleaning
+robot.  Overall, our data suggest that the anthropomorphic effect and the social
+impact of a functional robot on a household is rather marginal.
+%There were just few instances of people anthropomorphizing the robot and
+%interacting with it in a human-social way. More importantly, overall, these
+%anthropomorphic interactions with the robot did not last but seemed to be
+%somehow related to the novelty of the robot.
+
+We categorized several interactions and actions with the robot as
+anthropomorphic or human-social (in a broader sense). 
+%Examples of what we categorized as somehow social and anthropomorphic
+%(human-like) interactions with the robot include \textit{watching} the robot
+%for fun, giving a \textit{demo} of the robot to guests / visitors, taking a
+%\textit{photo/video} of the robot, \textit{personalizing} the robot, giving a
+%\textit{name} to the robot, \textit{talking} to the robot using direct speech,
+%\textit{playing} with the robot, and making \textit{adjustments} to the home
+%due to the robot. 
+Figure \ref{fig:roomba-activities}) shows how many of the 9 households engaged
+in these activities during the 6 months when the study was conducted.
 
@@
     \includegraphics[width=0.5\columnwidth]{roomba-activities.png}
-    \caption{Activities with the robot over time, n = 9 households.
-This bar chart shows how many of the 9 households carried out different kinds of anthropomorphic / social activities with and related to the robot at 3 time points during 6 months.
-Activities include \texttt{watching} the robot for fun, giving a \texttt{demo} of the robot to guests / visitors, \texttt{personalizing} the robot, giving a \texttt{name} to the robot, \texttt{talking} to the robot, \texttt{playing} with the robot.
-Participants were asked to report on these activities at 3 time points after the robot was deployed in their home: after 2 weeks, after 2 months, and after 6 months.}
+    \caption{Activities with the robot over time, n = 9 households. This bar
+        chart shows how many of the 9 households carried out different kinds of
+        anthropomorphic / social activities with and related to the robot at 3
+        time points during 6 months. Activities include \texttt{watching} the
+        robot for fun, giving a \texttt{demo} of the robot to guests / visitors,
+        \texttt{personalizing} the robot, giving a \texttt{name} to the robot,
+        \texttt{talking} to the robot, \texttt{playing} with the robot.
+        Participants were asked to report on these activities at 3 time points
+        after the robot was deployed in their home: after 2 weeks, after 2 months,
+        and after 6 months.}
+
 \label{fig:roomba-activities}
@@
 
-\paragraph*{Watching the robot for fun.} We categorize watching a robot for fun as an entertaining, emotional activity, reflecting a feeling of empathy for the robot.
-In \cite{sung_housewives_2008} survey, 73~\% of the participants reported to watch their Roomba running for fun.
-While in the beginning of our study, also a quite high proportion (6 of 9 households) reported to watch the robot for fun, after 2 and 6 months the number of households that engaged in this activity decreased by half.
-
-\paragraph*{Giving a robot demo to visitors.} It is somehow natural that owners of innovative devices show the device to others and ask for their opinion about it \citep{rogers_diffusion_1995}.
-However, this activity suggests that the robot is presented as a new part of the household to visitors.
-\cite{sung_domestic_2010} described that a vacuum cleaning robot can serve as a mediator and encourage social interaction among people.
-We categorize giving a demo of the robot to visitors / guests as such an activity.
-During the first 2 weeks with the robot 8 of 9 households in our study showed their robot to others, and still after 2 and 6 months 5 of the households engaged in this activity.
-This number is more or less in accordance with the 57~\% of survey respondents who stated to give demonstrations to others \citep{sung_housewives_2008}.
-
-%\paragraph*{Taking photos / videos of the robot.} How far taking a photo or video of a robot can be seen as an anthropomorphic interaction is questionable.
-However, it reflects the fact that the robot is observed by the user who for some reason is motivated to record the event.
-The number of households that took a photo or video of the robot decreased over time from 5 households in the beginning to 1 household after 6 months.
-
-\paragraph*{Personalizing the robot.} It has been found that people are motivated to personalize technology as a form of self-expression (identity projection) or when they use a technology a lot and know how to customize it (technical identity projection) \citep{blom_personalization:_2000}.
-Though \cite{sung_pimp_2009} found that some Roomba users who were given a customization toolkit personalized their Roomba, none of the users in her study who was \textit{not} given this toolkit personalized their Roomba.
-Also in our study none of the 9 households engaged in a personalization activity.
-
-\paragraph*{Giving a name to the robot.} Giving a name to an artificial agent reflects a certain kind of personal relationship to the agent.
-By naming a robot, it is not anonymous anymore, and might be perceived as a moral agent.
-As such, naming an artificial agent can be classified as anthropomorphizing this agent.
-It further suggests that the agent is talked to directly.
-Though more than 23~\% of the survey participants in \cite{sung_housewives_2008} study reported to name their Roomba, only 1 of 9 households in our study did so.
-
-\paragraph*{Talking directly to the robot.} Using direct speech toward an object or artificial agent that does not have the ability to recognize and process speech (such as verbal comments) or other sound cues, is an interesting phenomenon which can be classified as an anthropomorphic interaction.
-Whereas only 11~\% of the survey respondents in \cite{sung_housewives_2008} study reported to talk to their robot, around half of the households engaged in this activity and the proportion did not notably decrease over time.
-
-\paragraph*{Playing with the robot.} In our study, it were mostly children who engaged in playing with the robot, however, most of them stopped doing so after some time.
-The number of household playing with their Roomba decreased from 8 when asked after 2 weeks with the robot, to 4 households after 2 months, and 1 household after 6 months.
-In \cite{sung_housewives_2008} survey, 37~\% of the Roomba owners reported to play and experiment with their robot.\\
-
-%\paragraph*{Making adjustments to the home due to the robot.} To help Roomba clean, \cite{sung_housewives_2008} found in an online survey that about half of the 379 participants made physical modifications to their homes.
-This process is referred to as \textit{roombarization}, and it seems to be a unique aspect of adopting a domestic service robot.
-In our study, almost all the households made adjustments when they used the robot for the first time in front of us.
-However, during the first two weeks with the robot, only 3 households reported to have adjusted something due to the robot, and after 6 months it was only 1 household that still engaged in this activity.
-This decrease is, however, logical since after some time most people had done all the necessary adjustments to enable the robot show a good performance.
-
-%\paragraph*{Emerging anthropomorphic interactions.} Another, from our side more unexpected interaction that we would describe as somehow anthropomorphic, is what we call \textit{``collaborative cleaning''} with the robot.
-In the initial phase of the study, some people spontaneously helped the robot to clean by either picking up crumbs from the floor themselves or pushing it right in front of the robot.
-Another way of collaborating with the robot we observed was to help it go everywhere by spontaneously putting up the trash bin or the carpet in the bathroom (things that are not just lying around and need to be cleaned up).
-However, the activity of collaborative cleaning faded out soon, and we suspect it was encouraged by the novelty of the robot.\\
-
-Overall, Figure \ref{fig:roomba-activities} shows that as time goes by, less households engage in the before-mentioned non-cleaning activities with the vacuum cleaning robot: after 2 weeks, on average, 4.67 of 9 households engage in a human-like activity with the robot; after 2 months, the value decreases to 2.83, and after 6 months to 2.3.
-Our interpretation is that the nature of human-robot interaction changes over time.
-More concretely, we suspect  that anthropomorphic / human-social interactions with the robot become less over time, and that only with some people these interactions sustain.
-
-%\begin{figure*}[htb]
-%\centering
-%
-%\begin{tikzpicture}[scale=0.5, y = 2cm]
-%%axis
-%\draw (0,0) -- coordinate (x axis mid) (20,0);
-%\draw (0,0) -- coordinate (y axis mid) (0,7);
-%%ticks
-%\foreach \x in {0,4,...,20}
-%    \draw (\x,1pt) -- (\x,-3pt);
-%\foreach \y in {1,...,7} 
-%    \draw[black!20] (20,\y) -- (-3pt,\y);
-%\foreach \y in {1,...,7} 
-%    \draw (-3pt, \y) node[anchor=east] {\y}; 
-%%labels
-%\node[below=0.8cm] at (x axis mid) {People's perception ($\sigma=15$)};
-%\node at (2, -0.4) {\tiny expectations};
-%\node[align=center] at (6, -0.4) {\tiny after\\ \tiny first usage};
-%\node[align=center] at (10, -0.4) {\tiny after\\ \tiny 2 weeks};
-%\node[align=center] at (14, -0.4) {\tiny after\\ \tiny 2 months};
-%\node[align=center] at (18, -0.4) {\tiny after\\ \tiny 6 months};
-%
-%\draw[dashed, black!50] (6,0) -- (6,7) node[sloped, below, pos=0.25] {\tiny novelty effect};
-%
-%\draw[ultra thick, red!50] (2,5.6) -- (6,6.1) -- (10,6.3) -- (14,6.3) -- (18,6.1) node at (15,6.5) {\tiny \it ease of use};
-%\draw[ultra thick, purple] (2,4.9) -- (6,5.2) -- (10,5.1) -- (14,4.5) -- (18,4.2) node at (3,4.7) {\tiny \it usefulness};
-%\draw[ultra thick, blue!50] (2,4) -- (6,4.1) -- (10,4.6) -- (14,4.1) -- (18,4.3) node at (16,4) {\tiny \it fun};
-%\draw[ultra thick, green!50] (2,3.9) -- (6,4.1) -- (10,4.2) -- (14,3.8) -- (18,3.3) node at (19,3.5) {\tiny \it intelligence};
-%\draw[ultra thick, orange] (2,3.5) -- (6,4.2) -- (10,4) -- (14,3.2) -- (18,2.8) node at (14,2.7) {\tiny \it impact};
-%
-%\draw[ultra thick, dashed] (2,5.2) -- (6,5.2) -- (10,5) -- (14,4.9) -- (18,4.5) node at (14,5.3) {\tiny \it overall};
-%
-%\end{tikzpicture}
-%
-%\caption{User perception of the Roomba robot over a 6 month period
-%($\sigma=15$).}
-%
-%\label{roomba-perception}
-%\end{figure*}
+\paragraph*{Watching the robot for fun.} We categorize watching a robot for fun
+as an entertaining, emotional activity, reflecting a feeling of empathy for the
+robot. In \cite{sung_housewives_2008} survey, 73~\% of the participants reported
+to watch their Roomba running for fun. While in the beginning of our study, also
+a quite high proportion (6 of 9 households) reported to watch the robot for fun,
+after 2 and 6 months the number of households that engaged in this activity
+decreased by half.
+
+\paragraph*{Giving a robot demo to visitors.} It is somehow natural that owners
+of innovative devices show the device to others and ask for their opinion about
+it \citep{rogers_diffusion_1995}. However, this activity suggests that the robot
+is presented as a new part of the household to visitors.
+\cite{sung_domestic_2010} described that a vacuum cleaning robot can serve as a
+mediator and encourage social interaction among people. We categorize giving a
+demo of the robot to visitors / guests as such an activity. During the first 2
+weeks with the robot 8 of 9 households in our study showed their robot to
+others, and still after 2 and 6 months 5 of the households engaged in this
+activity. This number is more or less in accordance with the 57~\% of survey
+respondents who stated to give demonstrations to others
+\citep{sung_housewives_2008}.
+
+%\paragraph*{Taking photos / videos of the robot.} How far taking a photo or
+%video of a robot can be seen as an anthropomorphic interaction is questionable.
+%However, it reflects the fact that the robot is observed by the user who for
+%some reason is motivated to record the event. The number of households that
+%took a photo or video of the robot decreased over time from 5 households in the
+%beginning to 1 household after 6 months.
+
+\paragraph*{Personalizing the robot.} It has been found that people are
+motivated to personalize technology as a form of self-expression (identity
+projection) or when they use a technology a lot and know how to customize it
+(technical identity projection) \citep{blom_personalization:_2000}. Though
+\cite{sung_pimp_2009} found that some Roomba users who were given a
+customization toolkit personalized their Roomba, none of the users in her study
+who was \textit{not} given this toolkit personalized their Roomba. Also in our
+study none of the 9 households engaged in a personalization activity.
+
+\paragraph*{Giving a name to the robot.} Giving a name to an artificial agent
+reflects a certain kind of personal relationship to the agent. By naming a
+robot, it is not anonymous anymore, and might be perceived as a moral agent. As
+such, naming an artificial agent can be classified as anthropomorphizing this
+agent. It further suggests that the agent is talked to directly. Though more
+than 23~\% of the survey participants in \cite{sung_housewives_2008} study
+reported to name their Roomba, only 1 of 9 households in our study did so.
+
+\paragraph*{Talking directly to the robot.} Using direct speech toward an object
+or artificial agent that does not have the ability to recognize and process
+speech (such as verbal comments) or other sound cues, is an interesting
+phenomenon which can be classified as an anthropomorphic interaction. Whereas
+only 11~\% of the survey respondents in \cite{sung_housewives_2008} study
+reported to talk to their robot, around half of the households engaged in this
+activity and the proportion did not notably decrease over time.
+
+\paragraph*{Playing with the robot.} In our study, it were mostly children who
+engaged in playing with the robot, however, most of them stopped doing so after
+some time. The number of household playing with their Roomba decreased from 8
+when asked after 2 weeks with the robot, to 4 households after 2 months, and 1
+household after 6 months. In \cite{sung_housewives_2008} survey, 37~\% of the
+Roomba owners reported to play and experiment with their robot.\\
+
+%\paragraph*{Making adjustments to the home due to the robot.} To help Roomba
+%clean, \cite{sung_housewives_2008} found in an online survey that about half of
+%the 379 participants made physical modifications to their homes. This process
+%is referred to as \textit{roombarization}, and it seems to be a unique aspect
+%of adopting a domestic service robot. In our study, almost all the households
+%made adjustments when they used the robot for the first time in front of us.
+%However, during the first two weeks with the robot, only 3 households reported
+%to have adjusted something due to the robot, and after 6 months it was only 1
+%household that still engaged in this activity. This decrease is, however,
+%logical since after some time most people had done all the necessary
+%adjustments to enable the robot show a good performance.
+
+%\paragraph*{Emerging anthropomorphic interactions.} Another, from our side more
+%unexpected interaction that we would describe as somehow anthropomorphic, is
+%what we call \textit{``collaborative cleaning''} with the robot. In the initial
+%phase of the study, some people spontaneously helped the robot to clean by
+%either picking up crumbs from the floor themselves or pushing it right in front
+%of the robot. Another way of collaborating with the robot we observed was to
+%help it go everywhere by spontaneously putting up the trash bin or the carpet
+%in the bathroom (things that are not just lying around and need to be cleaned
+%up). However, the activity of collaborative cleaning faded out soon, and we
+%suspect it was encouraged by the novelty of the robot.\\
+
+Overall, Figure \ref{fig:roomba-activities} shows that as time goes by, less
+households engage in the before-mentioned non-cleaning activities with the
+vacuum cleaning robot: after 2 weeks, on average, 4.67 of 9 households engage in
+a human-like activity with the robot; after 2 months, the value decreases to
+2.83, and after 6 months to 2.3. Our interpretation is that the nature of
+human-robot interaction changes over time. More concretely, we suspect  that
+anthropomorphic / human-social interactions with the robot become less over
+time, and that only with some people these interactions sustain.
 
@@
 
-We also studied people's perception of the robot, and how it evolved over time (see Figure \ref{fig:roomba-perception}).
-The main idea was to find out which of the perceived attributes could be related to how far the robot was integrated in the household as a cleaning tool.
-Concerning anthropomorphism, we included \textit{perceived intelligence} and experienced \textit{fun} when using the robot as indicators for the perception of human-likeness in the robot.
+We also studied people's perception of the robot, and how it evolved over time
+(see Figure \ref{fig:roomba-perception}). The main idea was to find out which of
+the perceived attributes could be related to how far the robot was integrated in
+the household as a cleaning tool. Concerning anthropomorphism, we included
+\textit{perceived intelligence} and experienced \textit{fun} when using the
+robot as indicators for the perception of human-likeness in the robot.
 
@@
     \includegraphics[width=0.5\columnwidth]{roomba-perception.pdf}
+
+    \begin{tikzpicture}[scale=0.5, y = 2cm]
+    %axis
+    \draw (0,0) -- coordinate (x axis mid) (20,0);
+    \draw (0,0) -- coordinate (y axis mid) (0,7);
+    %ticks
+    \foreach \x in {0,4,...,20}
+        \draw (\x,1pt) -- (\x,-3pt);
+    \foreach \y in {1,...,7} 
+        \draw[black!20] (20,\y) -- (-3pt,\y);
+    \foreach \y in {1,...,7} 
+        \draw (-3pt, \y) node[anchor=east] {\y}; 
+    %labels
+    \node[below=0.8cm] at (x axis mid) {People's perception ($\sigma=15$)};
+    \node at (2, -0.4) {\tiny expectations};
+    \node[align=center] at (6, -0.4) {\tiny after\\ \tiny first usage};
+    \node[align=center] at (10, -0.4) {\tiny after\\ \tiny 2 weeks};
+    \node[align=center] at (14, -0.4) {\tiny after\\ \tiny 2 months};
+    \node[align=center] at (18, -0.4) {\tiny after\\ \tiny 6 months};
+
+    \draw[dashed, black!50] (6,0) -- (6,7) node[sloped, below, pos=0.25] {\tiny novelty effect};
+
+    \draw[ultra thick, red!50] (2,5.6) -- (6,6.1) -- (10,6.3) -- (14,6.3) -- (18,6.1) node at (15,6.5) {\tiny \it ease of use};
+    \draw[ultra thick, purple] (2,4.9) -- (6,5.2) -- (10,5.1) -- (14,4.5) -- (18,4.2) node at (3,4.7) {\tiny \it usefulness};
+    \draw[ultra thick, blue!50] (2,4) -- (6,4.1) -- (10,4.6) -- (14,4.1) -- (18,4.3) node at (16,4) {\tiny \it fun};
+    \draw[ultra thick, green!50] (2,3.9) -- (6,4.1) -- (10,4.2) -- (14,3.8) -- (18,3.3) node at (19,3.5) {\tiny \it intelligence};
+    \draw[ultra thick, orange] (2,3.5) -- (6,4.2) -- (10,4) -- (14,3.2) -- (18,2.8) node at (14,2.7) {\tiny \it impact};
+
+    \draw[ultra thick, dashed] (2,5.2) -- (6,5.2) -- (10,5) -- (14,4.9) -- (18,4.5) node at (14,5.3) {\tiny \it overall};
+
+    \end{tikzpicture}
+
     \caption{People's perception of the robot over time, n = 15 participants.
-This line chart shows how people's perception of the robot evolves over time.
-At 5 time points people were asked to rate the robot according to the following aspects: the perceived \texttt{intelligence} of the robot, the perceived \texttt{usefulness}, the perceived \texttt{ease of use}, how much \texttt{fun} it was to use the robot, how far they found the robot had an \texttt{impact} on their household, and their {overall} impression of it.}
+    This line chart shows how people's perception of the robot evolves over
+    time. At 5 time points people were asked to rate the robot according to the
+    following aspects: the perceived \texttt{intelligence} of the robot, the
+    perceived \texttt{usefulness}, the perceived \texttt{ease of use}, how much
+    \texttt{fun} it was to use the robot, how far they found the robot had an
+    \texttt{impact} on their household, and their {overall} impression of it.}
+
     \label{fig:roomba-perception}
@@
 
-\paragraph*{Perceived intelligence.} On a scale from 1-7, people were not sure about how intelligent they should expect the robot to be (mean value 3.9).
-The rating did not change much and not significantly over time (average ratings between 3.3-4.2) \citep{fink_living_2013}.
-Interestingly, at all five time points, male participants rated the robot as more intelligent (average 4.5) than females (average 3.4), however, this difference was not significant.
-When asked why they thought Roomba possesses intelligence, men more often referred to the 'robot side' of Roomba: its abilities to detect and avoid obstacles, stairs, and being able to recharge itself.
-Contrary, women referred to its rather limited vacuuming performance and found it was not as intelligent because \textit{``it doesn't see where the dirt is, it sometimes leaves it, it can't be smart!''}.
-This difference in the perception of intelligence of a robot suggests that gender,and probably other individual characteristics need to be taken into account.
-
-\paragraph*{Experienced fun.} Participants rated the robot as 'somewhat fun' (values from 4.0-4.6).
-There was a qualitative gender difference (not significant), in the sense that the experienced fun remained quite stable for male participants, whereas it tended to decrease with time for female participants.
-Men described the robot more as a 'fun gadget' than females, who referred to it as \textit{``In the end, Roomba is a cleaning tool and it is not really fun to use it''}.
-Again for this aspect, gender seems to play a role in how the robot is perceived and experienced.\\
-
-Overall, Figure \ref{fig:roomba-perception} shows that after the first usage of the Roomba (T2), most of the perceived constructs slightly decrease (and hence are less positively rated) as time goes by.
-The course is different for the perceived \textit{ease of use} of the robot, as participants become more experienced with the robot over time.
-Also, the experienced \textit{fun} does not decrease with time.
+\paragraph*{Perceived intelligence.} On a scale from 1-7, people were not sure
+about how intelligent they should expect the robot to be (mean value 3.9). The
+rating did not change much and not significantly over time (average ratings
+between 3.3-4.2) \citep{fink_living_2013}. Interestingly, at all five time
+points, male participants rated the robot as more intelligent (average 4.5) than
+females (average 3.4), however, this difference was not significant. When asked
+why they thought Roomba possesses intelligence, men more often referred to the
+'robot side' of Roomba: its abilities to detect and avoid obstacles, stairs, and
+being able to recharge itself. Contrary, women referred to its rather limited
+vacuuming performance and found it was not as intelligent because \textit{``it
+doesn't see where the dirt is, it sometimes leaves it, it can't be smart!''}.
+This difference in the perception of intelligence of a robot suggests that
+gender,and probably other individual characteristics need to be taken into
+account.
+
+\paragraph*{Experienced fun.} Participants rated the robot as 'somewhat fun'
+(values from 4.0-4.6). There was a qualitative gender difference (not
+significant), in the sense that the experienced fun remained quite stable for
+male participants, whereas it tended to decrease with time for female
+participants. Men described the robot more as a 'fun gadget' than females, who
+referred to it as \textit{``In the end, Roomba is a cleaning tool and it is not
+really fun to use it''}. Again for this aspect, gender seems to play a role in
+how the robot is perceived and experienced.\\
+
+Overall, Figure \ref{fig:roomba-perception} shows that after the first usage of
+the Roomba (T2), most of the perceived constructs slightly decrease (and hence
+are less positively rated) as time goes by. The course is different for the
+perceived \textit{ease of use} of the robot, as participants become more
+experienced with the robot over time. Also, the experienced \textit{fun} does
+not decrease with time.
 
@@
 
-In accordance with previous work we also found relatively low rates of users treating and perceiving their vacuum cleaning robot as a living (or human-like) entity \citep{sung_housewives_2008}.
-We interpret that it might be the pure functional purpose and non human-like form of the Roomba that prevented people from anthropomorphizing it.
-Still, we observed some initial anthropomorphic effects, both reflected in interaction with and perception of the robot.
-However, most of the anthropomorphic effects did not last long.
-\hl{One fairly stable human-like interaction with the robot was \textit{talking to the robot}, despite the fact that the robot was not able to recognize and respond to verbal statements.\footnote{important!
-I think I've seen that finding somewhere else when comparing ASIMO to AIBO or so.}}
+In accordance with previous work we also found relatively low rates of users
+treating and perceiving their vacuum cleaning robot as a living (or human-like)
+entity \citep{sung_housewives_2008}. We interpret that it might be the pure
+functional purpose and non human-like form of the Roomba that prevented people
+from anthropomorphizing it. Still, we observed some initial anthropomorphic
+effects, both reflected in interaction with and perception of the robot.
+However, most of the anthropomorphic effects did not last long. \hl{One fairly
+stable human-like interaction with the robot was \textit{talking to the robot},
+despite the fact that the robot was not able to recognize and respond to verbal
+statements.\footnote{important! I think I've seen that finding somewhere else
+when comparing ASIMO to AIBO or so.}}
 
@@
 
-We investigated the amount and context of anthropomorphic language in three online discussion forums about the robotic dog AIBO, the vacuum cleaning robot Roomba, and the tablet computer iPad.
-This was done by means of a content analysis of 750 forum posts that were further partitioned in n = 1208 valid segments \citep{fink_anthropomorphic_2012}.
-Hereafter, we refer to this study as the "Forum study".
-The three devices, pictured in Figure \ref{fig:aibo-roomba-ipad}, were chosen as they show different designs and fulfill different purposes.
-We would describe (1) AIBO as a zoomorphic / pet-like robot that does not have a clear purpose but engages people to play with it; (2) Roomba as a mechanical / functional domestic service robot that has a practical main purpose (vacuum cleaning) but offers not much of interactivity; (3) the iPad as a minimalistic designed interactive (touch-based) technology with multiple purposes (both entertainment, and professional / practical use).
-Based on these different characteristics, we made the two following hypotheses concerning anthropomorphism:
+We investigated the amount and context of anthropomorphic language in three
+online discussion forums about the robotic dog AIBO, the vacuum cleaning robot
+Roomba, and the tablet computer iPad. This was done by means of a content
+analysis of 750 forum posts that were further partitioned in n = 1208 valid
+segments \citep{fink_anthropomorphic_2012}. Hereafter, we refer to this study as
+the "Forum study". The three devices, pictured in Figure
+\ref{fig:aibo-roomba-ipad}, were chosen as they show different designs and
+fulfill different purposes. We would describe (1) AIBO as a zoomorphic /
+pet-like robot that does not have a clear purpose but engages people to play
+with it; (2) Roomba as a mechanical / functional domestic service robot that has
+a practical main purpose (vacuum cleaning) but offers not much of interactivity;
+(3) the iPad as a minimalistic designed interactive (touch-based) technology
+with multiple purposes (both entertainment, and professional / practical use).
+Based on these different characteristics, we made the two following hypotheses
+concerning anthropomorphism:
 
 \begin{enumerate}
+
     	\item People engage in a more social and human-like way with a robotic pet compared to a functional robot and a tablet computer, therefore there will be a higher amount of anthropomorphic language in the AIBO and Roomba forum, compared to the iPad forum.
+
     	\item As anthropomorphism can be seen as a certain kind of emotional / social relation to an artifact, there will be more anthropomorphic language in forum posts in which the author describes a relation to the device, compared to discussing technological aspects or how the device is used.
@@
 
-Similar to how \cite{friedman_hardware_2003} analyzed anthropomorphic language in online forums, we coded a segment as anthropomorphic when the respective device was described in terms of:
+Similar to how \cite{friedman_hardware_2003} analyzed anthropomorphic language
+in online forums, we coded a segment as anthropomorphic when the respective
+device was described in terms of:
 
 \begin{itemize}
-	\item \textit{Life-likeness}, uch as being alive or having (parts of) a body, \eg \textit{``she can be reborn since you copied her memory stick''};
-	\item \textit{Emotional states} or the technology having a feeling, \eg \textit{``oh no, poor AIBO''};
-	\item \textit{Gender, personality} or the technology having an \textit{intention}, \eg Roomba \textit{``seems to like to hang around under the sofa''};
-	\item When the author gave the technology a \textit{name}, \eg \textit{``whenever I show Java his pink ball''};
-	\item Being \textit{socially integrated}, such as being a family member, \eg \textit{``I'm considering adding a Roomba to the family''};
-	\item \textit{Metaphorical ways}, \eg Roomba \textit{``sings its victory song when it finishes and docks''}.
+    \item \textit{Life-likeness}, uch as being alive or having (parts of) a
+        body, \eg \textit{``she can be reborn since you copied her memory
+        stick''};
+
+    \item \textit{Emotional states, empathy} or the technology having a
+        \textit{feeling}, \eg \textit{``oh no, poor AIBO''};
+
+    \item \textit{Gender, personality} or the technology having an
+        \textit{intention}, \eg Roomba \textit{``seems to like to hang around
+        under the sofa''};
+
+    \item When the author gave the technology a \textit{name}, \eg
+        \textit{``whenever I show Java his pink ball''};
+
+    \item Being \textit{socially integrated}, such as being a family member, \eg
+        \textit{``I'm considering adding a Roomba to the family''};
+
+    \item \textit{Metaphorical ways}, \eg Roomba \textit{``sings its victory
+        song when it finishes and docks''}.
+
 \end{itemize}
 
-In the next sections, we present findings in respect of our two hypotheses: anthropomorphic language related to the device, and anthropomorphic language related to the topic of the forum post.
-
-Overall, our analysis revealed that in all three forums, discussions about \textit{technical} aspects of the respective device were most frequent (67.7~\% of all 1208 categorized segments).
-However there were huge differences between the three devices: \textit{technical} aspects made up 79.9~\% of the discussion in the Roomba forum, compared to 69.9~\% in the AIBO forum, and 55.2~\% in the iPad forum.
-Another fairly frequently discussed topic concerned the \textit{usage} of the respective device, thus people describing how and for what they use their technology.
-This topic made up 21.8~\% of all posts, and was most frequent in the iPad forum (35.7~\%), followed by the Roomba forum (15.9~\%), and the AIBO forum (10.7~\%).
-Last but not least, we defined \textit{relation} as the third topic of interest.
-Discussions in which people described their relation to the respective device made up 10.5~\% of all posts, and was most frequent in the AIBO forum (19.4~\%), followed by the iPad forum (9.1~\%), and the Roomba forum (4.2~\%).
-\hl{(if it is getting too much we can leave out this paragraph, it's not crucial, and doesn't say anything about anthropomorphism directly)}
+In the next sections, we present findings in respect of our two hypotheses:
+anthropomorphic language related to the device, and anthropomorphic language
+related to the topic of the forum post.
+
+Overall, our analysis revealed that in all three forums, discussions about
+\textit{technical} aspects of the respective device were most frequent (67.7~\%
+of all 1208 categorized segments). However there were huge differences between
+the three devices: \textit{technical} aspects made up 79.9~\% of the discussion
+in the Roomba forum, compared to 69.9~\% in the AIBO forum, and 55.2~\% in the
+iPad forum. Another fairly frequently discussed topic concerned the
+\textit{usage} of the respective device, thus people describing how and for what
+they use their technology. This topic made up 21.8~\% of all posts, and was most
+frequent in the iPad forum (35.7~\%), followed by the Roomba forum (15.9~\%),
+and the AIBO forum (10.7~\%). Last but not least, we defined \textit{relation}
+as the third topic of interest. Discussions in which people described their
+relation to the respective device made up 10.5~\% of all posts, and was most
+frequent in the AIBO forum (19.4~\%), followed by the iPad forum (9.1~\%), and
+the Roomba forum (4.2~\%). \hl{(if it is getting too much we can leave out this
+paragraph, it's not crucial, and doesn't say anything about anthropomorphism
+directly)}
 
@@
 
-A statistical analysis revealed a significant difference for the use of anthropomorphism across the three devices \citep{fink_anthropomorphic_2012}.
-In accordance with our first hypothesis, the highest amount of anthropomorphic language (56.6~\%) was found in the AIBO forum.
-In contrast, only 11.7~\% and respectively 2.2~\% of the segments in the Roomba and the iPad forum contained anthropomorphic expressions.
-The data suggests that on a subjective scale of perceived human-likeness (or rather life-likeness), Roomba is closer to the iPad than to the AIBO, at least in matters of how they are described with words.
-This was a bit against our expectation.
-Still, the Roomba is an autonomous robot that can navigate around the house itself, and we expected this property to enhance anthropomorphism.
-We interpret that here, the physical embodiment of the object and how far it resembles a life-like entity determine how far the object is anthropomorphized, and as such the robotic dog is anthropomorphized more than the functionally designed devices.
+A statistical analysis revealed a significant difference for the use of
+anthropomorphism across the three devices \citep{fink_anthropomorphic_2012}. In
+accordance with our first hypothesis, the highest amount of anthropomorphic
+language (56.6~\%) was found in the AIBO forum. In contrast, only 11.7~\% and
+respectively 2.2~\% of the segments in the Roomba and the iPad forum contained
+anthropomorphic expressions.  The data suggests that on a subjective scale of
+perceived human-likeness (or rather life-likeness), Roomba is closer to the iPad
+than to the AIBO, at least in matters of how they are described with words. This
+was a bit against our expectation. Still, the Roomba is an autonomous robot that
+can navigate around the house itself, and we expected this property to enhance
+anthropomorphism. We interpret that here, the physical embodiment of the object
+and how far it resembles a life-like entity determine how far the object is
+anthropomorphized, and as such the robotic dog is anthropomorphized more than
+the functionally designed devices.
 
@@
 
-Also in terms of anthropomorphic language related to the topic of conversation, a statistical analysis revealed a significant difference \citep{fink_anthropomorphic_2012}.
-The analysis suggests that anthropomorphizing happens more when the topic of conversation is \textit{relation}, compared to \textit{usage}, and \textit{technical} aspects.
-This finding is qualitatively confirmed when looking at the distribution of anthropomorphic expressions across the three topics in the Roomba and iPad forum (with both technologies the highest amount of anthropomorphism is in the \textit{relation} topic).
-However, in the AIBO the amount of anthropomorphic segments is highest for the \textit{usage} topic.
-We interpret that it is the different type of interaction / use context that makes the difference.
-Contrary to the iPad and the Roomba, the AIBO is made to encourage its user in a playful / social interaction, which in turn is a typical use context.
-Furhter, AIBO has the ability to respond intelligently to its user and environment, which might also encourage people to ascribe human-like abilities to it while interacting with it.
+Also in terms of anthropomorphic language related to the topic of conversation,
+a statistical analysis revealed a significant difference
+\citep{fink_anthropomorphic_2012}. The analysis suggests that anthropomorphizing
+happens more when the topic of conversation is \textit{relation}, compared to
+\textit{usage}, and \textit{technical} aspects. This finding is qualitatively
+confirmed when looking at the distribution of anthropomorphic expressions across
+the three topics in the Roomba and iPad forum (with both technologies the
+highest amount of anthropomorphism is in the \textit{relation} topic). However,
+in the AIBO the amount of anthropomorphic segments is highest for the
+\textit{usage} topic.  We interpret that it is the different type of interaction
+/ use context that makes the difference. Contrary to the iPad and the Roomba,
+the AIBO is made to encourage its user in a playful / social interaction, which
+in turn is a typical use context. Furhter, AIBO has the ability to respond
+intelligently to its user and environment, which might also encourage people to
+ascribe human-like abilities to it while interacting with it.
 
@@
 
-Overall, findings of the content analysis suggest that there are differences in people's tendency to use anthropomorphic language, originating form the design characteristics of the artifact.
-Interestingly, not only the physical embodiment of the object but also the interaction complexity and purpose of use of the object seems to play a role in how far the object is anthropomorphized.
+Overall, findings of the content analysis suggest that there are differences in
+people's tendency to use anthropomorphic language, originating form the design
+characteristics of the artifact. Interestingly, not only the physical embodiment
+of the object but also the interaction complexity and purpose of use of the
+object seems to play a role in how far the object is anthropomorphized.
 
 \subsection{Ranger domino study: effect of unexpected robot behavior}
+
+The so-called "Ranger domino study" describes a child-robot interaction study
+that we carried out in a fairly controlled lab setting. One of the goals of this
+study was to investigate the effect of unexpected robot behavior on (1) the
+interaction and engagement with robot, and (2) how far children would ascribe
+human-like abilities (\eg intentions, cognitive abilities) to the robot.
+
+13 groups of each two children (n = 26) who were all between 4-5 years old and
+knew each other, were invited to play for around 20 minutes with the Ranger
+robot toy box \citep{fink2014which} and assemble a domino together. The robot
+was operated by one of the experimenters using the wizard-of-oz technique.
+Ranger was supposed to transport domino tiles between the two children and it
+would do its job correctly for the first 7 domino tiles. Then, however, the
+robot started misbehaving by either \textit{disobeying} to the child
 

### 2014-03-21 paper.tex
latest changes in the domino study part

--- 2014-03-21 paper.tex
@@
 	\item \textit{Life-likeness}, uch as being alive or having (parts of) a body, \eg \textit{``she can be reborn since you copied her memory stick''};
-	\item \textit{Emotional states} or the technology having a feeling, \eg \textit{``oh no, poor AIBO''};
+	\item \textit{Emotional states, empathy} or the technology having a \textit{feeling}, \eg \textit{``oh no, poor AIBO''};
 	\item \textit{Gender, personality} or the technology having an \textit{intention}, \eg Roomba \textit{``seems to like to hang around under the sofa''};
@@
 \subsection{Ranger domino study: effect of unexpected robot behavior}
+
+The so-called "Ranger domino study" describes a child-robot interaction study that we carried out in a fairly controlled lab setting.
+One of the goals of this study was to investigate the effect of unexpected robot behavior on (1) the interaction and engagement with robot, and (2) how far children would ascribe human-like abilities (\eg intentions, cognitive abilities) to the robot.
+13 groups of each two children (n = 26) who were all between 4-5 years old and knew each other, were invited to play for around 20 minutes with the Ranger robot toy box \citep{fink2014which} and assemble a domino together.
+The robot was operated by one of the experimenters using the wizard-of-oz technique.
+Ranger was supposed to transport domino tiles between the two children and it would do its job correctly for the first 7 domino tiles.
+Then, however, the robot started misbehaving by either \textit{disobeying} to the child
 

### 2014-03-21 paper.tex
Introduced notation A(R,H,C,t) + updated fig dynamics of anthropo

--- 2014-03-21 paper.tex
@@
 \usetikzlibrary{shapes}
+\usetikzlibrary{svg.path}
 %
@@
 \newcommand{\etc}{{\textit{etc.~}}}
+
+\usepackage{xifthen}% provides \isempty test
+
+% use either \Ant or \Ant[R,H,C,...]
+\newcommand{\Ant}[1][]{%
+      \ifthenelse{\isempty{#1}}%
+        {$\mathcal{A}$}
+        {$\mathcal{A}(#1)$}
+}
+
+% for use inside a math environment
+\newcommand{\ant}[1][]{%
+      \ifthenelse{\isempty{#1}}%
+        {\mathcal{A}}
+        {\mathcal{A}(#1)}
+}
+\newcommand{\ICA}{{$\mathcal{A}_0$~}}
+\newcommand{\SLA}{{$\mathcal{A}_\infty$~}}
+\newcommand{\sla}{{\mathcal{A}_\infty}}
+\newcommand{\AntMax}{{$\mathcal{A}_{max}$~}}
 
@@
 A phenomenon that is often studied related to the human-like design of robots is
-\textbf{anthropomorphism}. Besides a feeling of affinity, and empathy,
+\textbf{anthropomorphism} (noted \Ant in this paper). Besides a feeling of affinity, and empathy,
 anthropomorphism can be understood as being one of the resulting (and  more or
@@
 agents.\\
+
+\subsection{A few results from the field}
+
+To support the reflection, it may be useful to consider a few experimental
+results. Figure~\ref{roomba-perception} gives a first perspective on how naive
+users perceive robots over a long period of time. Here, \emph{Roomba} robots
+were given to nine household for a 6 months period. The aim was to explore how
+people use and perceive the robot over time, and how they generally live with
+the Roomba in their home. At various time points, users were asked to rated
+their perception of different features of the robot on a 7-Likert scale. As
+Figure~\ref{roomba-perception} shows, some features remained stable over time
+(\emph{ease of use} and \emph{fun}), and other decreased: the perceived
+\emph{usefulness}, \emph{intelligence} and \emph{impact} on their household.
+\emph{intelligence} and \emph{impact} reflect the cognitive engagement of the
+user towards the machine: we can assume that one do not care to engage in a
+(cognitive) interaction with an artifact perceived as non-intelligent and with
+no impact on his/her life. Even if one can argue that the Roomba is not designed
+to foster interaction, the question is raised: how to sustain engagement between
+a robot and a human over a long period of time? And, as a pre-requisite, do we
+actually understand the psychological phenomenon, and can we effectively account
+for the dynamics of these interactions?
+
+Those questions are certainly not new, but paradoxically, while anthropomorphism
+in robotics is a commonly discussed and studied trait of human-robot
+interaction, it appears it lacks a formal ground and unified understanding to
+take into account the wide range of phenomena that it encompasses.
+
+\subsection{Towards a formal understanding of anthropomorphism}
+
+\fxnote{state here our main research hypothesis}
+\fxnote{state here our main contributions}
+
+So far, the HRI community has not much investigated how anthropomorphism in
+human-robot interactions evolves over time (during the process of
+\emph{adopting} a robot, for instance). Anthropomorphism is traditionally
+perceived in robotics as a static feature that once observed during a
+short-term interaction reflects a sustaining social effect.  Based on an
+literature review previously published~\cite{fink_anthropomorphism_2012}, a
+long-term field study in a natural environment~\cite{fink_living_2013}, as well
+as two on-going child-robot experiments, we believe that anthropomorphic
+effects do evolve over time in non-monotonic ways, and play a central role in
+sustaining engagement in human-robot interaction.
+
+We propose to formalize these dynamic effects into a model that we call the
+\emph{dynamics of anthropomorphism}. We hope that it may support further
+discussions and reflections on how anthropomorphism impacts human-robot
+interaction on the long run, and also foster research on the affective bonds
+induced by anthropomorphic projections on robots.
+
+As such, we propose to represent how the level of anthropomorphic effects (\ie
+observable manifestations of anthropomorphism) evolves over a long-term
+human-robot interaction (Figure~\ref{fig:dynamics}). By long-term interaction,
+we mean direct (non-mediated), repeated interaction with the same robot, over
+an extended period of time (typically longer than a week).
+
+In this article, we would like to share some critical but constructive
+considerations on anthropomorphism in robotics and HRI. Thereby, we contribute
+to a better understanding of this complex phenomenon related to robots.
 
@@
 
-%{Intro when start with anthropomorphism}
-%The essence of anthropomorphism is the perception of human-like characteristics
-%in either real or imagined non-human agents. In Human-Robot Interaction (HRI),
-%anthropomorphism is a commonly observed phenomenon: people tend to ascribe
-%human-like characteristics to robots, and they are willing to treat and react to
-%robots as if they were human-social counterparts. The HRI and social robotics
-%literature is full of various kinds of studies showing how humans readily
-%interact in a social fashion with robots -- despite the fact that robots are not
-%humans. In our own studies on HRI analysis in real-world settings, we also
-%observed anthropomorphism. However, we found qualitative differences and
-%dynamics over time in how participants anthropomorphized and related to the
-%robots used in our studies. More concretely, we found that anthropomorphism was
-%not only based on how much the robot resembles a human (anthropomorphic design)
-%but that it was determined by multiple factors, including individual
-%characteristics of the human user but also the context of use, for instance. We also
-%found that anthropomorphism changed over time with growing experience of the
-%user with the system. By trying to understand these variances and dynamics in
-%anthropomorphism, we reviewed related work from the HRI domain and social
-%robotics. Despite the fact that there is a vast amount of literature on
-%anthropomorphism in HRI, we were surprised to find that other studies do not
-%describe similar variances or dynamics. Instead, we came across diverse and
-%partially conflicting understandings of anthropomorphism. We also had the
-%impression that the reported data were sometimes over-interpreted (probably due
-%to the confusion of what exactly anthropomorphism is) or obtained in settings
-%and assessed in ways that we believe do not give enough consideration to the
-%complex nature of anthropomorphism. However, when reviewing literature from
-%social psychology, cognitive science, and neuroscience, we found support for the
-%variances and dynamics in anthropomorphism that we observed in our studies. As
-%HRI integrates many disciplines, we think that it is valid to use theories from
-%these related domains for interpreting our results and that it is relevant to
-%report on this integration.
-%
-%In this article, we would like to share some critical but constructive
-%considerations on anthropomorphism in robotics and HRI. Thereby, we contribute
-%to a better understanding of this complex phenomenon related to robots. In
-%Section \ref{sec:anthropomorphism} we would first like to give an overview of
-%how anthropomorphism can be defined, and then, in Section \ref{sec:explanations}
-%present explanations to the question why people anthropomorphize, with a focus
-%on anthropomorphism as a social phenomenon in HRI and the trend to design
-%human-like robots. Then, based on these reviews of theories and concepts from
-%related domains, in Section \ref{sec:multi-factors} we propose that
-%anthropomorphism is determined and affected by multiple factors. We outline how
-%anthropomorphism as a multi-factor phenomenon can impact the user experience and
-%acceptance of robots in daily life environments. Next, in Section
-%\ref{sec:dynamics-model} we suggest that anthropomorphism changes over time, and
-%describe these changes in an initial model that we call ``Dynamics of
-%Anthropomorphism''. We illustrate our idea with empirical findings from several
-%HRI studies that we conducted in natural environments. In Section
-%\ref{sec:cognition-neuroscience} we present a cognitive and neuroscience
-%perspective on anthropomorphism to consolidate our considerations and the
-%observed dynamics. Next, Section \ref{sec:discussion} considers limitations in
-%our approach and we discuss existing and alternative ways to measure
-%anthropomorphism in HRI. Finally, in Section \ref{sec:conclusion} we conclude
-%this article.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\section{A few results from the field}
+\section{Studying anthropomorphism}
 \label{sec:overview-studies}
@@
     \centering
-    \includegraphics[width=0.5\columnwidth]{roomba-perception.pdf}
 
@@
 
+The notation \Ant[R,H,C,t] reflects these multiple factors: we suggest here that
+anthropomorphism is a function of a vector of robot's traits $R = \{r_0,...,r_n\}$, a vector human
+determinants $H = \{h_0,...,h_n\}$, a set of interaction situations that build a
+an interaction context $C = \{s_0,...,s_n\}$, and the duration of the
+interaction itself, $t$.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \subsection{A Model of the Dynamics of Anthropomorphism}
-\label{sec:dynamics-model}
-
-\paragraph{Why is anthropomorphism likely to change over time?}
-\hl{maybe we need to move this paragraph to PART 3}
-
-\subsection{A Model of the Dynamics of Anthropomorphism}
 
@@
 
+While the model primarily considers \emph{long-term interaction} -- direct
+(non-mediated), repeated interaction with the same robot, over an extended
+period of time (typically longer than a week) --, we also formally introduce a
+so-called \emph{novelty effect}~\cite{kanda_interactive_2004} that models the
+first phase of human-robot interaction, during which a specific increase of
+anthropomorphic interactions is observed.
+
 In this model, anthropomorphism is quantified by a \emph{normalized level of
@@
 an absolute scale, we present them as a normalized value, that spans from a
-minimum (no anthropomorphic effects) to a maximum (corresponding to the novelty
-effect peak on Figure~\ref{fig:dynamics}). The actual maximum value of
+minimum (no anthropomorphic effects: $\ant=0$) to a maximum (noted \AntMax, with
+$t_{max} = \operatorname{arg\,max}_t \, \ant[t]$). We also discuss at
+section~\ref{measuring} possible methodologies for the quantitative and
+qualitative assessment of anthropomorphic effects.
+
+As pictured on Figure~\ref{fig:dynamics}, we suggest that $t_{max}$ actually
+corresponds to the novelty effect peak. The actual maximum value of
 anthropomorphic effects depends on each unique combination of human, robot and
@@
 
-The model takes into account the duration of the interaction, the nature of the
-interaction, as well as acquired experience and familiarization mechanisms. We
-also formally introduce a so-called \emph{novelty effect} that models the first
-phase of human-robot interaction, during which a specific increase of
-anthropomorphic interactions is observed. We focus on \emph{long-term
-interaction}, \ie direct (non-mediated), repeated interaction with the same
-robot, over an extended period of time (typically longer than a week). The nature 
-of the interaction (goal-directed, entertainment, etc.) may
-however vary.
-
 \begin{figure*}[htb]
@@
 
-\begin{tikzpicture}[scale=1.2]
+\begin{tikzpicture}[scale=1.4]
 
 % background shading
-\path[fill=gray!20] (0,0) rectangle (0.6,5.5);
-\path[fill=gray!50] (0.6,0) rectangle (5.2,5.5);
-\path[fill=gray!20] (5.2,0) rectangle (9.8,5.5);
-\draw(0,5.5) node[anchor=south west] {\scriptsize \sc Initialization};
-\draw(4,5.5) node[anchor=south] {\scriptsize \sc Familiarization};
-\draw(7.5,5.5) node[anchor=south] {\scriptsize \sc Stabilization};
+\path[fill=blue!20] (0,0) rectangle (0.6,5.5);
+\path[fill=green!20] (0.6,0) rectangle (5.2,5.5);
+\path[fill=orange!20] (5.2,0) rectangle (9.8,5.5);
+\draw(0,5.5) node[anchor=south west, rotate=10] {\scriptsize \sc Initialization};
+\draw(2.5,5.5) node[anchor=south west, rotate=10] {\scriptsize \sc Familiarization};
+\draw(6.5,5.5) node[anchor=south west, rotate=10] {\scriptsize \sc Stabilization};
 % horizontal axis
@@
 
-\draw (-0.05, 3) -- (0.05, 3) node[anchor=east] {\scriptsize ICA$_{\mathcal B}$};
-\draw (-0.05, 4.1) -- (0.05, 4.1) node[anchor=east] {\scriptsize ICA$_{\mathcal A}$};
-\draw (-0.05, 0.6) -- (0.05, 0.6) node[anchor=east] {\scriptsize ICA$_{\mathcal C}$};
+\draw (-0.05, 3) -- (0.05, 3) node[anchor=east] {\ICA};
+\draw (-0.05, 5) -- (0.05, 5) node[anchor=east] {\AntMax};
 
@@
 \draw[->] (9.8,0) -- (9.8,2) node[anchor=east] {};
-\draw (9.8, 0.8) node[anchor=west] {\scriptsize SLA$_\mathcal{E}$};
-\draw (9.8, 1.4) node[anchor=west] {\scriptsize SLA$_\mathcal{D}$};
-\draw (9.8, .2) node[anchor=west] {\scriptsize SLA$_\mathcal{F}$};
+\draw (9.8, 0.8) node[anchor=west] {\SLA};
 
 \draw[<-] (0.65,5) -- (0.8,5.2) node[anchor=east] {};
-\draw (0.9,5.3) node[anchor=west] {\tiny \it novelty effect};
+\draw (0.9,5.3) node[anchor=west] {\tiny \it novelty peak};
 
@@
 \draw[<->] (6.1,3) -- (6.1,5) node[anchor=east] {};
-\draw (6.2,4) node[rotate=90, anchor=north] {\tiny Expectation mismatch};
+\draw (6.2,4) node[rotate=90, anchor=north, align=center] {\tiny Expectation\\\tiny mismatch};
 
 \draw[<-] (1.7,4.4) -- (3.2,4.1) node[anchor=east] {};
-\draw[<-] (2.85,3.3) -- (3.2,4.1) node[anchor=east] {};
-\draw (3.2,4.1) node[anchor=west] {\tiny \it disruptive behaviors};
+\draw[<-] (2.85,2.6) -- (3.2,4.1) node[anchor=east] {};
+\draw (3.2,4.1) node[anchor=west, align=center] {\tiny \it disruptive\\ \tiny
+\it behaviors};
 %%%%%
@@
 
-% output of inkscape2tikz
-\path[draw=black]
-    (0.1250,-2.5620) .. controls (0.1451,-3.7193) and (0.4645,-4.5602) ..
-    (0.7044,-4.5633) .. controls (0.8413,-4.5633) and (0.9599,-4.5104) ..
-    (1.0794,-4.3971) .. controls (1.1989,-4.2841) and (1.3191,-4.1185) ..
-    (1.4588,-3.9181) .. controls (1.5287,-3.8183) and (1.5610,-4.1413) ..
-    (1.6381,-4.1420) .. controls (1.7378,-4.1420) and (1.6515,-3.6434) ..
-    (1.9554,-3.2280) .. controls (2.1466,-2.9667) and (2.3889,-2.7023) ..
-    (2.6819,-2.4292) .. controls (2.7551,-2.3607) and (2.7727,-2.8119) ..
-    (2.8771,-2.8180) .. controls (2.9742,-2.8180) and (2.9594,-2.2108) ..
-    (3.1665,-2.0209) .. controls (3.3340,-1.8673) and (3.5379,-1.7527) ..
-    (3.7508,-1.6236) .. controls (5.8366,-0.4852) and (8.0977,-0.2106) ..
-    (10.1250,-0.1860);
-\path[draw=black, dashed]
-    (0.1250,-3.6924) .. controls (0.1103,-4.0298) and (0.4645,-4.5602) .. 
-    (0.7044,-4.5633)
-    (3.7508,-1.6236) .. controls (4.9579,-0.9555) and (8.1358,-0.8261) .. 
-    (10.1250,-0.7946);
-\path[draw=black,dashed]
-    (0.1250,-0.1953) .. controls (0.1804,-3.3871) and (0.4645,-4.5602) .. 
-    (0.7044,-4.5633) .. controls (0.8413,-4.5633) and (0.9599,-4.5104) .. 
-    (1.0794,-4.3971)
-    (3.7508,-1.6236) .. controls (4.7654,-0.8505) and (6.5955,0.3538) .. 
-    (10.1250,0.4062);
+    \draw[ultra thick] svg[scale=1cm] "M 0.125,-2.5619582 c 0.0200733,-1.1573591
+    0.33954391,-1.9982333 0.57940683,-2.0013597 0.13691605,0 0.25550329,0.052908
+    0.37497897,0.1661788 0.119476,0.1130305 0.2396954,0.2786079
+    0.37944,0.4790565 0.069872,0.099803 0.1021612,-0.2231749
+    0.1792538,-0.2238964 0.099707,0 0.013454,0.4985362 0.3173383,0.9139831
+    0.1911917,0.2612926 0.3444354,0.2578391 0.6711932,0.4894291
+    0.2058265,0.1458798 0.1571532,0.9762306 0.2615031,0.9702183 0.097182,0
+    0.083295,-0.3336208 0.4330446,-0.1199242 0.4306401,0.2631203
+    0.216699,0.1355642 0.4296663,0.2647074 2.0858202,1.13836043
+    4.34683,1.41300027 6.3741749,1.43753027";
+
+    \draw[dashed] svg[scale=1cm] "M 0.125,-0.1952939 c 0.0553601,-3.1917862
+    0.33954391,-4.3648976 0.57940683,-4.368024 0.13691605,0 0.25550329,0.052908
+    0.37497897,0.1661788 m 2.6714393,2.7735737 C 4.7653984,-0.85050947
+    6.5955093,0.35382293 10.125,0.4062498";
+
+    \draw[dashed] svg[scale=1cm] "M 0.125,-3.6923825 C 0.1102888,-4.0297903
+    0.46454391,-4.5601915 0.70440683,-4.5633179 M 3.7508251,-1.6235654 C
+    4.9579368,-0.95548345 8.1358175,-0.82609971 10.125,-0.79459549";
 
@@
     preceded by a \emph{pre-interaction} phase. In the pre-interaction phase,
-    users build an \emph{initial capital of anthropomorphism} (ICA). Once the
-    interaction starts, the level of anthropomorphism increases due to the
-    \emph{novelty effect}~\cite{kanda_interactive_2004}, and then decreases to
-    reach a \emph{stabilized level of anthropomorphism} (SLA).  During the
-    interaction, unpredicted behaviors of the robot (\emph{disruptive behaviors})
-    may lead to local increase of the level of anthropomorphism.}
+    users build an \emph{initial capital of anthropomorphism} (ICA, noted \ICA).
+    Once the interaction starts, the level of anthropomorphism increases due to
+    the \emph{novelty effect}, and then decreases to reach a \emph{stabilized
+    level of anthropomorphism} (SLA, noted \SLA). \ICA and \SLA may vary
+    depending on the user, the robot and the context of interaction.  During the
+    interaction, unpredicted behaviors of the robot (\emph{disruptive
+    behaviors}) may lead to local increases or decreases of the level of
+    anthropomorphism.}
 
@@
 of seconds to a couple of hours), we observe an increased level of
-anthropomorphism, from an \emph{initial capital of anthropomorphism}
+anthropomorphism, from an \emph{initial capital of anthropomorphism} \ICA
 (detailed in the next section) to a peak of anthropomorphic manifestations
-that corresponds to the maximum of the \emph{novelty effect}.
+\AntMax that corresponds to the maximum of the \emph{novelty effect}.
 Section~\ref{sec:initialization} details this first phase.
@@
 effects tends to stabilize over a longer time, to reach a \emph{stabilized
-level of anthropomorphism} (SLA). The SLA may be null (no anthropomorphic
+level of anthropomorphism} \SLA. \SLA may be null (no anthropomorphic
 effects observed anymore), but it may also remain at a higher level.  This
@@
 of anthropomorphic interactions between a human and a robot to a value that we
-call \emph{initial capital of anthropomorphism} (ICA). The ICA describes the
+call \emph{initial capital of anthropomorphism}, noted \ICA. \ICA describes the
 first (real or imagined) contact to a robot. In this stage of pre-interaction,
@@
 
-We build the ICA on three main factors that \emph{a priori} determine the
+We build \ICA on three main factors that \emph{a priori} determine the
 potential that a robot will be anthropomorphized:
@@
 
-The ICA comprises some hypothetical values for each of these three factors, such
-that different ICA values can be obtained, given the robot, human user, and
+\ICA comprises some hypothetical values for each of these three factors, such
+that different \ICA values can be obtained, given the robot, human user, and
 environmental context\fxfatal{??}.
@@
 objects more than adults. Also, a person who lacks social connection is said to
-be more likely to anthropomorphize. Both aspects would increase the ICA. This
+be more likely to anthropomorphize. Both aspects would increase \ICA. This
 means that, one and the same robot used by a different user, can lead to a
-different ICA.
+different \ICA.
 
 For \textbf{design}, we understand that a robot that follows an anthropomorphic
-design (\eg NAO) leads to a higher ICA than a rather functional robot (\eg
+design (\eg NAO) leads to a higher \ICA than a rather functional robot (\eg
 Roomba). Also, a robot that is able to display facial expressions would increase
-the ICA. However, \hl{as discussed before} a classification of the "amount" of
+the \ICA. However, \hl{as discussed before} a classification of the "amount" of
 anthropomorphic design in a robot, as for instance suggested by Fong \textit{et
@@
 a robot which is imagined to be used in a social, entertaining or playful
-context leads to a higher ICA than a robot which is used for a routine or
+context leads to a higher \ICA than a robot which is used for a routine or
 focused task (security, rescue, etc.). This idea also receives support from
@@
 the environmental context in which people experience and interact with the robot
-impacts the ICA. For instance, several friends interacting simultaneously with
-the robot might lead to increased ICAs, due to increased human-human social
-interactions (the robot might be perceived to be part of the social interaction,
-and in turn attributed human-like qualities)~\cite{baxter2013do}.
+impacts the \ICA. For instance, several friends interacting simultaneously with
+the robot might lead to increased \ICA for each of the users, due to increased
+human-human social interactions (the robot might be perceived to be part of the
+social interaction, and in turn attributed human-like
+qualities)~\cite{baxter2013do}.
 
@@
 
-By \emph{disruptive behaviors}, we mean any behavior exhibited by the robot
-that is unexpected by the user: for instance, a robot may usually follow always
-the same route to go to two different places in a house, and suddenly change
-the route. The actual underlying reason may span from a bug to the detection of
-a new possible obstacle, but as long as this reason is not immediately
+By \emph{disruptive behaviors}, we mean any behavior exhibited by the robot that
+is unexpected by the user: for instance, a robot may usually follow always the
+same route to go to two different places in a house, and suddenly change the
+route. The actual underlying reason may span from a bug to the detection of a
+new possible obstacle, but as long as this reason is not immediately
 intelligible to the user, the behavior counts as \emph{disruptive}.
 
-Our model represents \emph{disruptive behaviors} as local increases of
-anthropomorphic effects in the familiarization phase (and at a lesser extend,
-in the stabilization phase) (Figure~\ref{fig:dynamics}): because such behaviors
-are unexpected, a human observer may interpret them as the result of a richer
-deliberative process, which in turn leads to the supposition of complex
-cognitive skills
-
-This is however to be modulated depending on the real and percieved reasons of the
-unexpected behavior.  Section~\ref{sec:disruptive} discusses more in depth the
-mental correlates of disruptive behaviors. It proposes a typology that relates
-them to the anthropomorphism they induce. It may increase if the user perceives
-(rightfully or not) a form of intentionality, as well as decrease if the
-unexpected behavior is perceived as a failure.
+As illustrated on Figure~\ref{fig:dynamics}, our model represents
+\emph{disruptive behaviors} as either local increases or local decreases of
+anthropomorphic effects in the familiarization phase (and at a lesser extend, in
+the stabilization phase): because such behaviors are unexpected, a human
+observer may interpret them either as the result of a richer deliberative
+process, which in turn leads to the supposition of complex cognitive skills, or
+conversely as a failure, reminding the human that the robot is ``just a
+machine''. Section~\ref{sec:disruptive} discusses more in depth the impact of
+the user's perception of disruptive behaviours, and their cognitive correlates.
 
@@
 effects tends to stabilize over a longer time, to reach a \emph{stabilized
-level of anthropomorphism} (SLA).
+level of anthropomorphism}, noted \SLA.
 
 If, after the familiarization phase, no anthropomorphic effects are observed
-anymore, the \emph{Stabilized Level of Anthropomorphism} is zero. This can
-be interpreted as the user interacting with the robot in a routine way, without
-projecting anymore human-like traits on the robot.
-
-\paragraph{Stabilized Level of Anthropomorphism (SLA)}
-
-The \emph{Stabilized Level of Anthropomorphism} (SLA on
-Figure~\ref{fig:dynamics}) describes the long-term lasting level of
-anthropomorphism.  Like the ICA, the SLA has a unique value per triplet
-(\emph{human}, \emph{robot}, \emph{context of interaction}).
-
-We proposed that the ICA is built on three factors: user's \emph{personality},
+anymore, $\sla = 0$. This can be interpreted as the user interacting with the
+robot in a routine way, without projecting anymore human-like traits on the
+robot.
+
+\paragraph{Stabilized Level of Anthropomorphism}
+
+The \emph{Stabilized Level of Anthropomorphism} describes the long-term lasting level of
+anthropomorphism.
+
+We proposed that \ICA is built on three factors: user's \emph{personality},
 robot's \emph{design} and interaction \emph{purpose} (or \emph{interaction
-context}). The user's personality and the context of use do also influence the
-SLA. In particular, it appears that the user's level of acquaintance with
+context}). The user's personality and the context of use do also influence \SLA.
+In particular, it appears that the user's level of acquaintance with
 technologies plays an important role in long-term tendency to
@@
 The robot's design, on the other hand, plays a more subtle role, and strong
-initial anthropomorphic design does not mandate high SLA: lasting
+initial anthropomorphic design does not mandate high \SLA: lasting
 anthropomorphic effects have been observed on non-anthropomorphic robots (like
@@
 \emph{Stabilized Level of Anthropomorphism} are generally not correlated: one
-individual may have high potential of anthropomorphizing (high ICA) at first
+individual may have high potential of anthropomorphizing (high \ICA) at first
 sight of a good-looking humanoid robot, and get disappointed by the actual
 abilities of the robots, down to routine, non-anthropomorphic, interactions (low
-SLA), while another user with the same high ICA may, for instance, creates
+\SLA), while another user with the same high \ICA may, for instance, creates
 lasting affective bonds with the same robot, and keeps anthropomorphizing it
-(higher SLA).
+(higher \SLA).
 
@@
 \subsection{Measuring anthropomorphism}
+\label{measuring}
 

### 2014-03-21 paper.tex
Cleaned up sec 5, moved some stuff to discussion, {phases->levels}

@@
 
-The so-called \emph{phase I} is the instinctive, pre-cognitive identification of
+The so-called \emph{level 1} is the instinctive, pre-cognitive identification of
 living peers. That humans tend to anthropomorphize robots intuitively in this
@@
 of the robot) or short interaction (touching, short talk like greetings), we
-suggest the human enters the cognitive \emph{phase II}: in this phase, the human
+suggest the human reaches the cognitive \emph{level 2}: in this phase, the human
 starts building a behavioral and cognitive model of the robot that would support
@@
 
-The cognitive \emph{phase III} occurs after a \emph{contextualized} interaction.
+The cognitive \emph{level 3} is reached after a \emph{contextualized} interaction.
 A \emph{contextualized} interaction is \emph{explicitly purposeful} (the purpose
@@
 
-These cognitive phases overlap but do not exactly match the
+These cognitive levels overlap but do not exactly match the
 \emph{Initialization}, \emph{Familiarization} and \emph{Stabilization} phases
 introduced in our model of the dynamics of anthropomorphism. In particular,
-cognitive phases I and II are both included in the \emph{initialization} phase
+the cognitive levels 1 and 2 are both included in the \emph{initialization} phase
 of the anthropomorphism model. Sub-cognitive anthropomorphism typically
 \emph{initiates} the novelty effect by rapidly engaging the human in the
-interaction through an initial projected agency, whereas cognitive phase II
+interaction through an initial projected agency, whereas cognitive level 2
 (projection of familiar mental models) supports the novelty effect by inducing
@@
 
-The cognitive phase III also overlaps with the \emph{familiarization} phase: as
+The cognitive level 3 also overlaps with the \emph{Familiarization} phase: as
 the human gets used to the robot, we hypothesize one restates and adapts its
@@
 A \emph{stable level of anthropomorphism} is reached when the adaptation process
-depicted in cognitive phase III reached a stable state, \ie the user's
+depicted in the cognitive level 3 reached a stable state, \ie the user's
 experience with the robot is correctly supported by the cognitive model he/she
@@
 
-\paragraph{Limits} This discussion on the cognitive correlates of the dynamics
-of anthropomorphism are speculative, and only indirectly supported by
-experimental evidence. New experiences need to be designed to specifically test
-these hypothesis.\fxnote{...}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+%
+%
+%				DISCUSSION + FUTURE WORK
+%
+%
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% JULIA & SEVERIN: how to measure / quantify anthropomorphism ...
+% CLAIRE: FMRI study idea
+
+\section{Discussion}
+\label{sec:discussion}
+
+The model of anthropomorphism we propose is still a work in progress. In
+particular, its implications regarding the design of (social) robots and
+human-robot interaction are still to be refined.
+
+\subsection{Effect of Time and Familiarization}
+
+\fixme{Discuss here the general findings of the paper: the global shape of the
+model of the dynamics, ...}
+
+The \textit{context of use} is related to the purpose (and functionality) of the
+robot and influences the user interaction experience. With \textit{time}, we
+refer to long-term interaction with the robot, which is related to what has been
+described as \textit{novelty effect} but also accounts for the user getting used
+to the robot. Consequently, we propose that anthropomorphism is not static but
+likely to change, due to what we call \textit{dynamics}, in space and time.
+
+As outlined in section \hl{XX}, the tendency to anthropomorphize is motivated by
+a person's wish to make sense of an agent which might be difficult to understand
+(in its functionality or behavior, for instance). In turn, a user might ascribe
+intentions or emotions to the system because the systems output was unexpected
+for the user. Based on this explanation, we estimate that when the user has
+familiarized herself / himself with the system, thus reached the point of when
+the system is usable and explainable, the tendency to anthropomorphize
+decreases. Therefore, our second hypothesis is as follows:
 
@@
 
-\subsection{Impact of the behavioral complexity of robots}
-
-TBD. Most experiments are carried with robots exhibiting relatively simple
-behaviors. In our model, the maximum level of anthropomorphism is reached with
-the novelty effect, and then decrease. Can we go \emph{over} the novelty effect
-if the robot exhibit more complex behaviors?
-
-\subsection{Segmentation of interaction phases}
-
-TBD
-
-\subsection{Behavioral cues of anthropomorphism}
-\label{sec:behavioralcues}
-
-Our model suggests to analyze anthropomorphism based on a \emph{relative and
-normalized level of anthropomorphic effects} instead of an absolute
-quantitative assessment of anthropomorphic evidences. Similarly we introduce
-two specific \emph{abstract} levels of anthropomorphism, the \emph{Initial
-Capital of Anthropomorphism} and the \emph{Stabilized Level of
-Anthropomorphism}: while we discuss the factors on which those values are
-build, we did not formally investigated the experimental cues or evidences
-that would allow to actually quantify those levels.
-
-The intricacy and interdependency of those behaviors make them difficult to
-quantify.  Their systematic identification and interpretation rely on
-psychosomatic cues that the authors did not investigate.
-
-A formal methodology for the assessment of anthropomorphic effects in HRI, as
-well as a typology of these effects is still to be formally devised.
-
-\subsection{Effect of Time and Familiarization}
-
-The \textit{context of use} is related to the purpose (and functionality) of the
-robot and influences the user interaction experience. With \textit{time}, we
-refer to long-term interaction with the robot, which is related to what has been
-described as \textit{novelty effect} but also accounts for the user getting used
-to the robot. Consequently, we propose that anthropomorphism is not static but
-likely to change, due to what we call \textit{dynamics}, in space and time.
-
-As outlined in section \hl{XX}, the tendency to anthropomorphize is motivated by
-a person's wish to make sense of an agent which might be difficult to understand
-(in its functionality or behavior, for instance). In turn, a user might ascribe
-intentions or emotions to the system because the systems output was unexpected
-for the user. Based on this explanation, we estimate that when the user has
-familiarized herself / himself with the system, thus reached the point of when
-the system is usable and explainable, the tendency to anthropomorphize
-decreases. Therefore, our second hypothesis is as follows:
-
-\begin{itemize}
-	\item \textbf{Hypothesis 2} A person's tendency to anthropomorphize a robot decreases over time and with growing experience the person has with the robot.
-\textit{(familiarize oneself with the robot)}
-\end{itemize}
-
 Given our first hypothesis from above, this might not hold over all contexts;
@@
 people's tendency to anthropomorphize [16]." \cite{duffy_anthropomorphism_2003}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-%
-%
-%				DISCUSSION + FUTURE WORK
-%
-%
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% JULIA & SEVERIN: how to measure / quantify anthropomorphism ...
-% CLAIRE: FMRI study idea
-
-\section{Discussion}
-\label{sec:discussion}
-
-The model of anthropomorphism we propose is still a work in progress. In
-particular, its implications regarding the design of (social) robots and
-human-robot interaction are still to be refined.
 
@@
 of the agents to explicit the mental model it has built of its partner
-(emotional state, beliefs, intentions, etc.). Depending on the cognitive phase
+(emotional state, beliefs, intentions, etc.). Depending on the cognitive levels
 the two agents are in, we may expect varying accuracy levels in the produced
@@
 
+\subsection{Sustaining long-term interaction}
+
+\paragraph{Impact of the behavioral complexity of robots}
+
+To remain tractable, most experiments, and even more when they investigate
+long-term interactions, are carried with robots exhibiting relatively simple
+behaviors. In our model, the maximum level of anthropomorphism \AntMax is
+reached at the end of the novelty effect, and then decrease. A natural question
+is whether we can design robots such as \AntMax remains high, possibly higher
+than $\ant[t_{novelty~peak}]$ (note that to know if sustaining strong
+anthropomorphic interaction is desirable is entirely another question).
+
+Intuitively, the behavioral complexity of the robot, and in particular, the ability
+for the robot to evolve over time and adapt its behavior to the user as the user
+familiarizes itself with the robot (\ie, \emph{co-familiarize}), seems to play a
+key role.
+
+...
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 The article also discusses the cognitive correlates of anthropomorphism. We
-proposes to identify three cognitive phases corresponding to successive
+proposes to identify three cognitive levels corresponding to successive
 refinements of the mental models of the robot that the user builds during the
-interaction. We show how these phases relate to observable anthropomorphic
+interaction. We show how these levels relate to observable anthropomorphic
 effects, and how they evolve over time.

### 2014-03-24 paper.tex
modifications Ranger domino study, structure anthropomorphism section

--- 2014-03-21 paper.tex
@@
 \usetikzlibrary{shapes}
-\usetikzlibrary{svg.path}
 %
@@
 \newcommand{\etc}{{\textit{etc.~}}}
-
-\usepackage{xifthen}% provides \isempty test
-
-% use either \Ant or \Ant[R,H,C,...]
-\newcommand{\Ant}[1][]{%
-      \ifthenelse{\isempty{#1}}%
-        {$\mathcal{A}$}
-        {$\mathcal{A}(#1)$}
-}
-
-% for use inside a math environment
-\newcommand{\ant}[1][]{%
-      \ifthenelse{\isempty{#1}}%
-        {\mathcal{A}}
-        {\mathcal{A}(#1)}
-}
-\newcommand{\ICA}{{$\mathcal{A}_0$~}}
-\newcommand{\SLA}{{$\mathcal{A}_\infty$~}}
-\newcommand{\sla}{{\mathcal{A}_\infty}}
-\newcommand{\AntMax}{{$\mathcal{A}_{max}$~}}
 
@@
 
-While anthropomorphism in robotics is a commonly discussed trait of
-HRI, it paradoxically lacks formal grounds. This article
-attempts first at providing a comprehensive synthesis of the social
-phenomenon of \textit{perceiving human-like characteristics in non-human
-agents and attributing those characteristics to robots}. We draw on
-social sciences and psychology, as well as on a critical survey of
-existing literature in the HRI community, to ground the concept of
-\textit{anthropomorphism}. Supported by extensive literature review
-and long-term field studies, we suggest to go beyond the traditional
-perception of anthropomorphism as a static feature of a system: we propose to
-understand anthropomorphism as a dynamic, non-monotonic and context-dependent
-process, which evolves over time and accounts for special events such as the
-so-called \textit{novelty effect}. To this end, we introduce a model of
-anthropomorphism that analyzes the phenomenon along three interaction phases,
-and we discuss cognitive interpretations that follow. \hl{(Julia: probably the abstract needs to be refined once we finished writing the paper)}
+A phenomenon that is often studied related to the human-like design of 
+robots is anthropomorphism. While people's tendency to perceive human-like 
+characteristics in robots is a commonly discussed trait of 
+human-robot interaction (HRI), the phenomenon paradoxically lacks formal 
+grounds. Based on findings from several empirical studies and a 
+comprehensive synthesis of literature, this article attempts at extending 
+the current understanding of anthropomorphism. In accordance with theories 
+from social psychology, cognitive science, and neuroscience, we suggest to 
+formalize qualitative differences and dynamics over time in how 
+humans anthropomorphize non-human agents. Based on several key factors, 
+namely the 
+design of the non-human agent, the individual characteristics of the human 
+user, and the context of use, we found that anthropomorphism changes in a 
+non-linear way with growing experience of the user with the system. To 
+account for these variances, we propose an initial model that we call 
+\textit{``Dynamics of Anthropomorphism''}. Focusing on human-robot 
+interactions, we present a cognitive interpretation that considers 
+the described dynamics. Finally, we would like to discuss how others can 
+apply our model to measure and describe better the complexity in human's 
+tendency to perceive human-like characteristics in non-human agents.
 
@@
 A phenomenon that is often studied related to the human-like design of robots is
-\textbf{anthropomorphism} (noted \Ant in this paper). Besides a feeling of affinity, and empathy,
+\textbf{anthropomorphism}. Besides a feeling of affinity, and empathy,
 anthropomorphism can be understood as being one of the resulting (and  more or
@@
 The Uncanny Valley hypothesis can be categorized as being part of first,
-artifact-centered approach, to understand anthropomorphism.\\
-
-We observed anthropomorphism in several short- and long-term human-robot
+artifact-centered approach, to understand anthropomorphism.
+
+\subsection{A few results from the field}
+
+To support the reflection, it may be useful to consider a few experimental
+results. We observed anthropomorphism in several short- and long-term human-robot
 interaction studies that we carried out with embodied robots, mostly in
@@
 
-Our data suggest that there are qualitative differences and dynamics over time
-in how humans relate to different types of robots. More concretely, we found
-that people's perception of human-likeness in the robot and in turn their
-human-social engagement with the robot was not only based on how much the robot
-resembled a human (mostly in its behavioral cues) but that this was determined
-by multiple factors, including individual characteristics of the human user but
-also the context of use, for instance. Interestingly, our findings also suggest
-that how far people anthropomorphize a robot is likely to change over time with
-growing experience of the user with the system.
-
-Based on these observations and an extensive literature review, we would like to
-propose a model that accounts for variances and dynamics in anthropomorphism.
-This model of the \textit{``Dynamics of Anthropomorphism''} considers several
-impact factors, including the human user, the anthropomorphic design of the
-non-human agent, the context of use, and the interaction experience (time). With
-this initial model, we would like to extend the current understanding of
-anthropomorphism in robotics and human-robot interaction. This might in turn
-lead to a discussion about the short- and long-term benefits and other effects
-of the human-like (anthropomorphic) design of robots and other artificial
-agents.\\
-
-\subsection{A few results from the field}
-
-To support the reflection, it may be useful to consider a few experimental
-results. Figure~\ref{roomba-perception} gives a first perspective on how naive
-users perceive robots over a long period of time. Here, \emph{Roomba} robots
-were given to nine household for a 6 months period. The aim was to explore how
+Figure~\ref{roomba-perception} gives a first perspective on how naive
+users perceive robots over a long period of time. Here, \emph{Roomba} vacuum cleaning robots
+were given to nine households for a 6-months period. The aim was to explore how
 people use and perceive the robot over time, and how they generally live with
-the Roomba in their home. At various time points, users were asked to rated
-their perception of different features of the robot on a 7-Likert scale. As
+the Roomba in their home. At various time points, users were asked to rate
+their perception of different features of the robot on a 7-point rating scale. As
 Figure~\ref{roomba-perception} shows, some features remained stable over time
-(\emph{ease of use} and \emph{fun}), and other decreased: the perceived
+(\emph{ease of use} and \emph{fun}), and others decreased: the perceived
 \emph{usefulness}, \emph{intelligence} and \emph{impact} on their household.
 \emph{intelligence} and \emph{impact} reflect the cognitive engagement of the
-user towards the machine: we can assume that one do not care to engage in a
+user towards the machine: we can assume that one does not care to engage in a
 (cognitive) interaction with an artifact perceived as non-intelligent and with
@@
 in robotics is a commonly discussed and studied trait of human-robot
-interaction, it appears it lacks a formal ground and unified understanding to
+interaction, it appears that it lacks a formal ground and unified understanding to
 take into account the wide range of phenomena that it encompasses.
@@
 
-\fxnote{state here our main research hypothesis}
-\fxnote{state here our main contributions}
-
 So far, the HRI community has not much investigated how anthropomorphism in
-human-robot interactions evolves over time (during the process of
-\emph{adopting} a robot, for instance). Anthropomorphism is traditionally
-perceived in robotics as a static feature that once observed during a
-short-term interaction reflects a sustaining social effect.  Based on an
-literature review previously published~\cite{fink_anthropomorphism_2012}, a
-long-term field study in a natural environment~\cite{fink_living_2013}, as well
-as two on-going child-robot experiments, we believe that anthropomorphic
-effects do evolve over time in non-monotonic ways, and play a central role in
-sustaining engagement in human-robot interaction.
-
-We propose to formalize these dynamic effects into a model that we call the
-\emph{dynamics of anthropomorphism}. We hope that it may support further
+human-robot interactions evolves over time. In robotics, anthropomorphism is traditionally
+perceived as a static feature triggered by the human-like design of a robot that once observed (during a
+short-term interaction) reflects a sustaining social effect. Based on a previously published
+literature review~\citep{fink_anthropomorphism_2012}, a
+long-term field study in a natural environment~\citep{fink_living_2013}, a 
+content analysis of online discussion 
+forums~\citep{fink_anthropomorphic_2012}, and an on-going child-robot 
+interaction study, we believe that anthropomorphic
+effects are based on several factors, and that they do evolve over time in 
+non-monotonic ways. Moreover, we assume that these variances and dynamics 
+play a central role in sustaining engagement in human-robot interaction.
+
+This article is organized around two main hypothesis that we formulated based on 
+our empirical studies of HRI, and by integrating previous work from several domains.
+
+\begin{itemize}
+    \item \textbf{Hypothesis 1~} A person's tendency to anthropomorphize a robot
+is based on several factors, including (but not limited to) (1) the 
+design of the robot, (2) the personal characteristics of the human user, 
+and (3) the context and situation of use. For instance, a social 
+context and purpose of the robot increase anthropomorphism. 
+\textit{(anthropomorphism as a multi-factor phenomenon)}
+	\item \textbf{Hypothesis 2~} A person's tendency to anthropomorphize a robot 
+evolves in a non-linear way over time and with growing experience that the 
+person has with the robot. For instance, a more experienced user will perceive 
+the robot as more familiar and predictable, and in turn anthropomorphizes the 
+robot less. \textit{(anthropomorphism as a dynamic phenomenon)}
+\end{itemize}
+
+We propose to formalize these variances and dynamic effects into a model that we call the
+\emph{Dynamics of Anthropomorphism}. We hope that it may support further
 discussions and reflections on how anthropomorphism impacts human-robot
@@
 induced by anthropomorphic projections on robots.
-
-As such, we propose to represent how the level of anthropomorphic effects (\ie
+Through our model, we propose to represent how the level of anthropomorphic effects (\ie
 observable manifestations of anthropomorphism) evolves over a long-term
@@
 
-In this article, we would like to share some critical but constructive
-considerations on anthropomorphism in robotics and HRI. Thereby, we contribute
-to a better understanding of this complex phenomenon related to robots.
+%In this article, we would further like to share some critical but constructive
+%considerations on anthropomorphism in robotics and HRI. Thereby, we contribute
+%to a better understanding of this complex phenomenon related to robots.
 
@@
 we conducted to investigate anthropomorphism, namely (1) the Roomba study, (2)
-the Forum study, (3) the Ranger domino study. As an outcome of these studies, we
-propose two main research hypotheses related to anthropomorphism.  Next, in
-Section \ref{sec:anthropomorphism} we investigate these hypotheses by
-synthesizing literature on anthropomorphism. This should also serve to establish
-a common ground. We first explore an artifact-centered perspective and briefly
+the Forum study, (3) the Ranger domino study. Next, in Section 
+\ref{sec:anthropomorphism} we aim to establish a common ground in the understanding 
+of anthropomorphism. We first explore an artifact-centered perspective and briefly
 outline how the human-like design of agents can encourage anthropomorphism.
@@
 
-\section{Studying anthropomorphism}
+\section{Studying anthropomorphism in HRI}
 \label{sec:overview-studies}
@@
 We openly explored long-term interactions between human users and a domestic
-service robot in a 6-months lasting ethnographic study. We gave a commercially
+service robot in a 6-months lasting ethnographic study~\citep{fink_living_2013}. 
+We gave a commercially
 available vacuum cleaning robot (iRobot's Roomba, see Figure
-\ref{fig:aibo-roomba-ipad} middle) to nine households in the French speaking
-part of Switzerland. The fairly diverse sample of households consisted of 2
-single homes, 1 couple, and 6 families with children in their home. In total,
-this summed up to 30 participants: 15 adults (26-71 years old, mean age 43.6
-years), and 15 children (6 months to 18 years old). During the 6 months, each
-household was visited 5 times to conduct interviews and make field observations
-in the households. Moreover, during several weeks, households were asked to fill
-in a diary to report the usage of the robot and other cleaning activities.
-\footnote{This study is published in \cite{fink_living_2013}.} Hereafter, we
-refer to this study as the "Roomba study".
-
-%The main goal of this study was to explore how households live with a vacuum
-%cleaning robot over an extended period of time. We wanted to analyze how the
-%usage of and interaction with the robot evolve over time, and to identify
-%adoption phases as well as factors that impact on the long-term acceptance of
-%service robots in homes.
-
-From the Roomba study, we can report on several findings related to
-anthropomorphism and the anthropomorphic design of robots.
-%The gathered data for these aspects include qualitative observations,
-%semi-structured interviews, and also quantitative assessments of various
-%aspects of human-robot interaction.
-The Roomba study is one of very few long-term human-robot interaction studies in
-the domestic environment.
-
+\ref{fig:aibo-roomba-ipad} middle) to nine households. 
+%in the French speaking
+%part of Switzerland. 
+%The fairly diverse sample of households consisted of 2
+%single homes, 1 couple, and 6 families with children in their home. In total,
+%this summed up to 30 participants: 15 adults (26-71 years old, mean age 43.6
+%years), and 15 children (6 months to 18 years old). During the 6 months, each
+%household was visited 5 times to conduct interviews and make field observations
+%in the households. Moreover, during several weeks, households were asked to fill
+%in a diary to report the usage of the robot and other cleaning activities.
+Hereafter, we refer to this study as the ``Roomba study''. It is one of very few 
+long-term human-robot interaction studies in the domestic environment. 
 In the following, we present findings in respect of two aspects: First, we
@@
 
+%The main goal of this study was to explore how households live with a vacuum
+%cleaning robot over an extended period of time. We wanted to analyze how the
+%usage of and interaction with the robot evolve over time, and to identify
+%adoption phases as well as factors that impact on the long-term acceptance of
+%service robots in homes.
+
+%The gathered data for these aspects include qualitative observations,
+%semi-structured interviews, and also quantitative assessments of various
+%aspects of human-robot interaction.
+
 \subsubsection{Anthropomorphic interactions with the robot\\}
@@
 respondents had relatively low rates of treating Roomba as a living entity.  
-
-In our long-term study of the Roomba in homes, we found that it was mostly
-during the initial phase with the robot that some (rather few) people tended to
-interact in an anthropomorphic or human-social way with their vacuum cleaning
-robot.  Overall, our data suggest that the anthropomorphic effect and the social
-impact of a functional robot on a household is rather marginal.
+Similarly, in our long-term study of the Roomba in homes, we found that only few 
+people tended to interact in an anthropomorphic or human-social way with their 
+vacuum cleaning robot and that this effect did not sustain. Overall, our data 
+suggest that the anthropomorphic effect and the social
+impact of a functional robot on a household are rather marginal.
 %There were just few instances of people anthropomorphizing the robot and
@@
 %due to the robot. 
-Figure \ref{fig:roomba-activities}) shows how many of the 9 households engaged
+Figure \ref{fig:roomba-activities} shows how many of the 9 households engaged
 in these activities during the 6 months when the study was conducted.
 
-\begin{figure}
+\begin{figure}[hb]
     \centering
@@
 \textit{perceived intelligence} and experienced \textit{fun} when using the
-robot as indicators for the perception of human-likeness in the robot.
-
-\begin{figure}
+robot as indicators for the perception of human-likeness in the robot.\fixme{JF: Severin, you also mentioned impact as one factor. Please include it here below as another paragraph.}
+
+\begin{figure}[b]
     \centering
-
-    \begin{tikzpicture}[scale=0.5, y = 2cm]
-    %axis
-    \draw (0,0) -- coordinate (x axis mid) (20,0);
-    \draw (0,0) -- coordinate (y axis mid) (0,7);
-    %ticks
-    \foreach \x in {0,4,...,20}
-        \draw (\x,1pt) -- (\x,-3pt);
-    \foreach \y in {1,...,7} 
-        \draw[black!20] (20,\y) -- (-3pt,\y);
-    \foreach \y in {1,...,7} 
-        \draw (-3pt, \y) node[anchor=east] {\y}; 
-    %labels
-    \node[below=0.8cm] at (x axis mid) {People's perception ($\sigma=15$)};
-    \node at (2, -0.4) {\tiny expectations};
-    \node[align=center] at (6, -0.4) {\tiny after\\ \tiny first usage};
-    \node[align=center] at (10, -0.4) {\tiny after\\ \tiny 2 weeks};
-    \node[align=center] at (14, -0.4) {\tiny after\\ \tiny 2 months};
-    \node[align=center] at (18, -0.4) {\tiny after\\ \tiny 6 months};
-
-    \draw[dashed, black!50] (6,0) -- (6,7) node[sloped, below, pos=0.25] {\tiny novelty effect};
-
-    \draw[ultra thick, red!50] (2,5.6) -- (6,6.1) -- (10,6.3) -- (14,6.3) -- (18,6.1) node at (15,6.5) {\tiny \it ease of use};
-    \draw[ultra thick, purple] (2,4.9) -- (6,5.2) -- (10,5.1) -- (14,4.5) -- (18,4.2) node at (3,4.7) {\tiny \it usefulness};
-    \draw[ultra thick, blue!50] (2,4) -- (6,4.1) -- (10,4.6) -- (14,4.1) -- (18,4.3) node at (16,4) {\tiny \it fun};
-    \draw[ultra thick, green!50] (2,3.9) -- (6,4.1) -- (10,4.2) -- (14,3.8) -- (18,3.3) node at (19,3.5) {\tiny \it intelligence};
-    \draw[ultra thick, orange] (2,3.5) -- (6,4.2) -- (10,4) -- (14,3.2) -- (18,2.8) node at (14,2.7) {\tiny \it impact};
-
-    \draw[ultra thick, dashed] (2,5.2) -- (6,5.2) -- (10,5) -- (14,4.9) -- (18,4.5) node at (14,5.3) {\tiny \it overall};
-
-    \end{tikzpicture}
+    \includegraphics[width=0.5\columnwidth]{roomba-perception.pdf}
+
+%    \begin{tikzpicture}[scale=0.5, y = 2cm]
+%    %axis
+%    \draw (0,0) -- coordinate (x axis mid) (20,0);
+%    \draw (0,0) -- coordinate (y axis mid) (0,7);
+%    %ticks
+%    \foreach \x in {0,4,...,20}
+%        \draw (\x,1pt) -- (\x,-3pt);
+%    \foreach \y in {1,...,7} 
+%        \draw[black!20] (20,\y) -- (-3pt,\y);
+%    \foreach \y in {1,...,7} 
+%        \draw (-3pt, \y) node[anchor=east] {\y}; 
+%    %labels
+%    \node[below=0.8cm] at (x axis mid) {People's perception ($\sigma=15$)};
+%    \node at (2, -0.4) {\tiny expectations};
+%    \node[align=center] at (6, -0.4) {\tiny after\\ \tiny first usage};
+%    \node[align=center] at (10, -0.4) {\tiny after\\ \tiny 2 weeks};
+%    \node[align=center] at (14, -0.4) {\tiny after\\ \tiny 2 months};
+%    \node[align=center] at (18, -0.4) {\tiny after\\ \tiny 6 months};
+%
+%    \draw[dashed, black!50] (6,0) -- (6,7) node[sloped, below, pos=0.25] {\tiny novelty effect};
+%
+%    \draw[ultra thick, red!50] (2,5.6) -- (6,6.1) -- (10,6.3) -- (14,6.3) -- (18,6.1) node at (15,6.5) {\tiny \it ease of use};
+%    \draw[ultra thick, purple] (2,4.9) -- (6,5.2) -- (10,5.1) -- (14,4.5) -- (18,4.2) node at (3,4.7) {\tiny \it usefulness};
+%    \draw[ultra thick, blue!50] (2,4) -- (6,4.1) -- (10,4.6) -- (14,4.1) -- (18,4.3) node at (16,4) {\tiny \it fun};
+%    \draw[ultra thick, green!50] (2,3.9) -- (6,4.1) -- (10,4.2) -- (14,3.8) -- (18,3.3) node at (19,3.5) {\tiny \it intelligence};
+%    \draw[ultra thick, orange] (2,3.5) -- (6,4.2) -- (10,4) -- (14,3.2) -- (18,2.8) node at (14,2.7) {\tiny \it impact};
+%
+%    \draw[ultra thick, dashed] (2,5.2) -- (6,5.2) -- (10,5) -- (14,4.9) -- (18,4.5) node at (14,5.3) {\tiny \it overall};
+%
+%    \end{tikzpicture}
 
@@
 \subsection{Forum study: using anthropomorphic expressions to describe a robot}
-
-\begin{figure}
-    \centering
-    \includegraphics[width=0.7\columnwidth]{aibo-roomba-ipad_2.jpg}
-    \caption{The Sony AIBO robotic dog (left), the iRobot Roomba vacuum-cleaning robot (middle), and the Apple Inc.
-iPad tablet computer (right) were compared in terms of how far users of these devices use anthropomorphic expressions in discussions about their technology / robot in online discussion forums.}
-    \label{fig:aibo-roomba-ipad}
-\end{figure}
 
@@
 \begin{enumerate}
-
     	\item People engage in a more social and human-like way with a robotic pet compared to a functional robot and a tablet computer, therefore there will be a higher amount of anthropomorphic language in the AIBO and Roomba forum, compared to the iPad forum.
@@
 \end{enumerate}
+
+\begin{figure}[b]
+    \centering
+    \includegraphics[width=0.5\columnwidth]{aibo-roomba-ipad_2.jpg}
+    \caption{The Sony AIBO robotic dog (left), the iRobot Roomba vacuum-cleaning robot (middle), and the Apple Inc.
+iPad tablet computer (right) were compared in terms of how far users of these devices use anthropomorphic expressions in discussions about their technology / robot in online discussion forums.}
+    \label{fig:aibo-roomba-ipad}
+\end{figure}
 
@@
 \begin{itemize}
-    \item \textit{Life-likeness}, uch as being alive or having (parts of) a
+    \item \textit{Life-likeness}, such as being alive or having (parts of) a
         body, \eg \textit{``she can be reborn since you copied her memory
         stick''};
-
     \item \textit{Emotional states, empathy} or the technology having a
         \textit{feeling}, \eg \textit{``oh no, poor AIBO''};
-
     \item \textit{Gender, personality} or the technology having an
@@
         under the sofa''};
-
     \item When the author gave the technology a \textit{name}, \eg
         \textit{``whenever I show Java his pink ball''};
-
     \item Being \textit{socially integrated}, such as being a family member, \eg
         \textit{``I'm considering adding a Roomba to the family''};
-
     \item \textit{Metaphorical ways}, \eg Roomba \textit{``sings its victory
         song when it finishes and docks''}.
-
 \end{itemize}
 
-In the next sections, we present findings in respect of our two hypotheses:
+In the next paragraphs, we present findings in respect of our two hypotheses:
 anthropomorphic language related to the device, and anthropomorphic language
@@
 
-Overall, our analysis revealed that in all three forums, discussions about
-\textit{technical} aspects of the respective device were most frequent (67.7~\%
-of all 1208 categorized segments). However there were huge differences between
-the three devices: \textit{technical} aspects made up 79.9~\% of the discussion
-in the Roomba forum, compared to 69.9~\% in the AIBO forum, and 55.2~\% in the
-iPad forum. Another fairly frequently discussed topic concerned the
-\textit{usage} of the respective device, thus people describing how and for what
-they use their technology. This topic made up 21.8~\% of all posts, and was most
-frequent in the iPad forum (35.7~\%), followed by the Roomba forum (15.9~\%),
-and the AIBO forum (10.7~\%). Last but not least, we defined \textit{relation}
-as the third topic of interest. Discussions in which people described their
-relation to the respective device made up 10.5~\% of all posts, and was most
-frequent in the AIBO forum (19.4~\%), followed by the iPad forum (9.1~\%), and
-the Roomba forum (4.2~\%). \hl{(if it is getting too much we can leave out this
-paragraph, it's not crucial, and doesn't say anything about anthropomorphism
-directly)}
+%Overall, our analysis revealed that in all three forums, discussions about
+%\textit{technical} aspects of the respective device were most frequent (67.7~\%
+%of all 1208 categorized segments). However there were huge differences between
+%the three devices: \textit{technical} aspects made up 79.9~\% of the discussion
+%in the Roomba forum, compared to 69.9~\% in the AIBO forum, and 55.2~\% in the
+%iPad forum. Another fairly frequently discussed topic concerned the
+%\textit{usage} of the respective device, thus people describing how and for what
+%they use their technology. This topic made up 21.8~\% of all posts, and was most
+%frequent in the iPad forum (35.7~\%), followed by the Roomba forum (15.9~\%),
+%and the AIBO forum (10.7~\%). Last but not least, we defined \textit{relation}
+%as the third topic of interest. Discussions in which people described their
+%relation to the respective device made up 10.5~\% of all posts, and was most
+%frequent in the AIBO forum (19.4~\%), followed by the iPad forum (9.1~\%), and
+%the Roomba forum (4.2~\%). \hl{(if it is getting too much we can leave out this
+%paragraph, it's not crucial, and doesn't say anything about anthropomorphism
+%directly)}
 
@@
 the AIBO is made to encourage its user in a playful / social interaction, which
-in turn is a typical use context. Furhter, AIBO has the ability to respond
+in turn is a typical use context. Further, AIBO has the ability to respond
 intelligently to its user and environment, which might also encourage people to
@@
 13 groups of each two children (n = 26) who were all between 4-5 years old and
-knew each other, were invited to play for around 20 minutes with the Ranger
-robot toy box \citep{fink2014which} and assemble a domino together. The robot
+knew each other, were invited to play with the Ranger
+robot toy box \citep{fink2014which} to assemble a domino together. The robot
 was operated by one of the experimenters using the wizard-of-oz technique.
 Ranger was supposed to transport domino tiles between the two children and it
-would do its job correctly for the first 7 domino tiles. Then, however, the
-robot started misbehaving by either \textit{disobeying} to the child
+would do its job correctly for the first 7 runs, bringing each one domino tile to the child. Then, however, the
+robot started misbehaving by not coming over to the child who was calling the 
+robot. Three different experimental conditions were explored using three different 
+types of misbehavior from the robot side:
+Either the robot was \textit{disobeying} and did not come over at all, or 
+the robot got \textit{lost} on its way to the child, or the robot did a 
+\textit{mistake} by first going in another direction but then turning and 
+coming over to the child who had called it.
+According to these three different types of unexpected robot behavior, we 
+expected to observe variations of how far the children perceived the 
+robot in terms of intentionality, and cognitive abilities.
+
+In respect of anthropomorphism, we analyzed two types of data: children's 
+\textit{interaction} with the robot (\eg do they talk to and use gestures 
+toward the robot?, see Figure \ref{fig:interactions-per-run}), and 
+children's \textit{perception} of the robot (\eg do they believe the 
+robot has an own will, feelings, or is able to understand what they 
+say?). The interaction data was analyzed quantitatively after having 
+annotated the video recordings of the interaction. Children's perception 
+of the robot was analyzed in a qualitative way and processed in a 
+qualitative scale (higher values on that scale indicate more 
+anthropomorphism), see Figure \ref{fig:qualitative-score}.
+
+\subsubsection{Anthropomorphic interactions with the robot\\}
+
+The video recordings of the interaction session in which the children 
+played domino with the partly misbehaving robot were annotated according 
+to a coding scheme that we developed. Amongst others, six different types 
+of active actions / active engagement that a child carried out with the 
+robot were annotated. We understand some of these active engagement 
+actions as anthropomorphic, such as talking directly to the robot or 
+using gestures to the robot. The distribution of the interaction data per 
+run (see Figure \ref{fig:interactions-per-run} suggests that after the 
+robot started misbehaving (and thus became less predictable) children 
+tended to use slightly more active engagement interactions: gestures toward the 
+robot, and to talk more to the robot. Also, they were looking more often at the 
+experimenter, seeking help.
 
@@
     \centering
-    \includegraphics[width=0.6\columnwidth]{ranger-interactions-per-runs}
-    \caption{Quantitative assessment: here, six interactions modalities have
+    \includegraphics[width=0.5\columnwidth]{ranger-interactions-per-runs}
+    \caption{Quantitative assessment: here, six interaction modalities have
         been selected: showing something to the robot ({\tt show}), talking to
         the robot ({\tt talk}), touching it ({\tt touch}), misbehaving (like
-        shaking it, {\tt mis}), deictic interactions ({\tt ges}), and looking
-        for exterior help by looking at the experimenter ({\tt look}). In each
-        of the 14 experimental runs, we annotate and count the number of
+        shaking it, {\tt mis}), using gestures ({\tt ges}), and looking
+        for help by glancing at the experimenter ({\tt look}). In each
+        of the 13 experimental runs, we annotated and counted the number of
         occurrences of each of these interactions. Highlighted runs 2.3, 2.4,
-        2.7 and 2.8 correspond to unexpected robot behaviours: we observe peaks
-        of interactions every time the robot's behaviour changes from expected to
-        unexpected or from unexpected to expected.}
-
-    \label{interactions-per-run}
+        2.7 and 2.8 correspond to unexpected robot behaviors: we observe peaks
+        of interactions every time the robot's behavior changes from expected to
+        unexpected or from unexpected to expected. (n = 26 children)}
+
+    \label{fig:interactions-per-run}
 \end{figure}
+
+\subsubsection{Perception of anthropomorphic characteristics of the robot\\}
+
+First of all, note that it is not at all easy to measure how far 4-5 year old's 
+perceive a robot to have some human-like qualities. We interviewed children about 
+various anthropomorphic traits of the robot, such as: Can the robot feel happy or 
+sad? Some of these questions were inspired by \cite{kahn_jr._robotic_2006}. For 
+each of these anthropomorphic traits questions, we gave a point if the child 
+answered in a positive way (partly reversed, negative way), indicating that the 
+child perceived the robot as somehow human-like. In the end, we summed up all 
+points, to obtain a \textit{qualitative score} for a child's tendency to 
+anthropomorphize the robot.
+
+\subsubsection{Summary Ranger domino study\\}
+
+We were trying to bring both measurements together: the anthropomorphic 
+interactions with the robot and the perception of anthropomorphic characteristics 
+of the robot. By this, we wanted to find out whether both aspects are correlated to 
+each other. A correlation would allow us to answer questions such as: Do children 
+that perceive more human-like characteristics in the robot also interact with it in 
+a more human-like way?
 
@@
     \centering
-    \includegraphics[width=0.6\columnwidth]{ranger-interactions-vs-qualitative-score}
+    \includegraphics[width=0.5\columnwidth]{ranger-interactions-vs-qualitative-score}
     \caption{We found a significant negative correlation ($p=0.048$) between the
-    number of interactions and the qualitative anthropomorphic projections
-    ($\sigma=13$).}
-    \label{qualitative-score}
+    number of interactions and the qualitative anthropomorphic projections. This 
+    suggests that children who interacted more with the robot, anthropomorphized it 
+    less, and \textit{vice versa}. (n = 13 groups)}
+    \label{fig:qualitative-score}
 \end{figure}
 
-Figure~\ref{qualitative-score} plots the qualitative vs quantitative assessment of
-anthropomorphic effects during the \emph{Dominos} experiment: the correlation is
-negative. The more the children interacted with the robot, the less they
+Figure~\ref{fig:qualitative-score} plots the qualitative against the quantitative assessment of
+anthropomorphic effects during the Ranger domino study: the correlation is
+negative. This was a surprise. The more the children interacted with the robot, the less they
 projected anthropomorphic traits on the robot. We also note a remarkable cluster
@@
 with the robot, the more likely they are to consider it as a friend/pet/lively
-being) and we discuss at section~\ref{sec:cognition-neuroscience} possible
-cognitive explanations.
+being). We discuss possible cognitive explanations of this in Section~\ref{sec:cognition-neuroscience}.
 
@@
 
-In this section we will try to create a common ground in the understanding of anthropomorphism since we have found conflicting definitions of the term.
-We first present anthropomorphism as a social phenomenon.
-Then we propose to use another term, namely ``anthropomorphic form'', to refer to the human-inspired design of artifacts.
-Finally, we focus on both anthropomorphism and anthropomorphic design in human-robot interaction / robotics, as in these domains both topics are brought together naturally.
-\hl{(adjust according to the section)}
-
-%\subsection{What is anthropomorphism?}
-%\label{sec:social-phenomenon}
-
-Anthropomorphism is an interesting phenomenon because it tells us something about the relationship between the human who anthropomorphizes, and the non-human agent which is anthropomorphized.
-Though commonly observed, it appears controversial, at the same time, that humans tend to \hl{\textit{``see something human in the non-human''}}.
-
-Humans tend to perceive human-like characteristics such as physical appearance, emotional states, or inner mental states and motivations in non-human agents that do not have these characteristics themselves, such as animals, natural forces, religious agents, technological gadgets, or mechanical devices \citep{epley_when_2008}.\footnote{According to \cite{epley_when_2008}, a non-human agent can be anything that acts -- or is believed to act -- with apparent independence.}  Anthropomorphism has received remarkable attention across various different domains, such as natural sciences, developmental and social psychology, Human-Computer Interaction (HCI), and Human-Robot Interaction (HRI).
-
-Originally, the term \textbf{anthropomorphism} comes from the Greek \textit{`anthropos'} for `man' (or `human') and \textit{`morphe'} for `form / structure' (or `shape').
-Anthropomorphism is generally understood as people's tendency to perceive a non-human agent as if it had some human characteristics or traits.
-In turn, how a person perceives an agent further determines how she relates to and behaves towards the agent, or how she may behave in light of this agent \citep{epley_when_2008}.
-As such, anthropomorphism can be seen as a special kind of relationship between a human interacting with a non-human agent.
-This anthropomorphic relationship is often characterized by the fact that the human attributes human-unique characteristics to the non-human agent.
-Since anthropomorphism becomes observable through these attributions, some definitions claim that anthropomorphism is not the perception but rather the attribution of human attributes to non-human agents, and name thoughts, emotions, and intentions as examples.
-The most prominently anthropomorphized non-human agents are probably animals and robots \citep{duffy_anthropomorphism_2003,schmitz_concepts_2011}.
-
-Apart from anthropomorphism there also exists the term \textbf{animism}, which can be defined as the attribution of life to the nonliving.
-The study of animism was pioneered by Piaget in the 1920s with his work on \textit{The Child's Conception of the  World}.
-He found that children tend to regard many inanimate objects as capable of sensations, emotions and intentions, and called this view `animism'.
-Since then, children's inferences about the world have been studied intensively.
-However, there is an agreement that children's views and concepts of living, animal, and plant evolve as they grow up.
-Using this definition, animism differs in two main aspects from anthropomorphism:
-First, the property which is ascribed differs: life-likeness is not human-unique but applies to all living beings.
-The second difference between anthropomorphism and animism stems from the agent (or better artifact) to which life is attributed.
-Living beings (most importantly animals) are naturally excluded from being animized.
-Consequently, while animals can be anthropomorphized (perceived to have human unique characteristics), they cannot be animized as they are already living beings.
-(Similarly to the fact that humans cannot be anthropomorphized as they are already humans.)
-Often synonymously used to animism is the term \textbf{zoomorphism}, which applies to the cases when non-lifelike instances / things are associated with animalistic attributes, excluding human-specific traits.
-Both anthropomorphism and animism / zoomorphism can be embraced by the concept of \textbf{life-likeness}.
-
-There exists also the inverse phenomenon to anthropomorphism, which can be found in the literature as \textbf{dehumanization} \citep{haslam_dehumanization:_2006}, or \textbf{mechanomorphism} \citep{caporael_anthropomorphism_1986}.
-We do not treat this here.
-
- \begin{figure}[b]\centering
-% Use the relevant command to insert your figure file.
-% For example, with the graphicx package use
-  \includegraphics[scale=1]{north-wind.jpg}
-  \includegraphics[scale=1]{sun.jpg}
-% figure caption is below the figure
- \caption{Milo Winter illustration of Aesop Fable \textit{The North Wind and the Sun}, 1919; both natural forces wind and sun are anthropomorphized with a human face; picture source: wikipedia}
- \label{fig:north-wind-sun}       % Give a unique label
- \end{figure}
-
-To illustrate better how anthropomorphism differs from attributions of animacy or life-likeness, it is worth looking at paraphrases and examples of it.
-That is to say, anthropomorphism can alternatively be understood as \textbf{humanization} or \textbf{personification} of anything other than a human being.
-Personification has ancient roots, \eg in mythology but also in storytelling.
-Anthropomorphism was also used to describe and be able to predict natural forces or anticipate great spirits, for instance.
-An illustration of an anthropomorphism related to nature is shown in Figure \ref{fig:north-wind-sun}.
-In this Milo Winter (1919) drawing \textit{"The North Wind and the Sun"}, both north wind and sun are given a human face.
-
-\paragraph*{Diverse understandings of anthropomorphism\\ \\}
-
-Anthropomorphism is used in different senses throughout different disciplines \citep{duffy_anthropomorphism_2003} which makes it difficult to synthesize findings.
-Depending on which understanding of anthropomorphism is applied, not everything colloquially labeled as \emph{anthropomorphism} really is anthropomorphism.\footnote{For instance, it is not always clear whether a person (may it be an adult or a child) who gives and anthropomorphic response, believes that the other agent really thinks or acts like a human or whether she is using anthropomorphism in a metaphoric sense.\citep{leeds_childrens_1992}} We need to be clear about what we mean by anthropomorphism because at the moment, there are different, even partially conflicting understandings of anthropomorphism, not only across but also within disciplines \cite{duffy_anthropomorphism_2002}.
-In particular, in the multi-disciplinary field of HRI, anthropomorphism is understood and interpreted in such a variety of ways that it is almost impossible to bring together and compare the research work done.
-In turn, it seems that the understanding of anthropomorphism in HRI has not improved much over the last decade but has only become more diverse (which is ok, too, but certainly a deeper understanding and common grounds would be convenient).
-
-How can we narrow down the understanding of anthropomorphism?
-From a psychology point of view \cite{epley_when_2008} try to clarify anthropomorphism by explaining what it is \textit{not}, and we think this approach could also help researchers in HRI and robotics.
-\cite{epley_when_2008} list four effects that anthropomorphism does not include:
-(1) First, anthropomorphism does not include behavioral descriptions of observable actions. Anthropomorphism requires going beyond what is directly observable.
-(2) Second, anthropomorphism does not merely entail animism, as animate life is not a uniquely human-like characteristic.
-(3) Third, anthropomorphism does not include any requirement of reasoned or reflective endorsement of an inference.\footnote{\hl{(the strength of anthropomorphic inferences can vary)}}
-(4) Finally, anthropomorphism is not necessarily inaccurate.
-A psychological theory should take this (in)accuracy in anthropomorphism into account and predict variability in the tendency to perceive human-like traits in non-human agents.\footnote{For more details, the reader may refer to the original work \citep{epley_when_2008}.}
-
-Not only \cite{epley_when_2008} and \cite{duffy_anthropomorphism_2002} but also others have noticed that anthropomorphism is a very complex phenomenon -- itself and in how it can be understood.
-This holds implications for the study of anthropomorphism (to what we will come back later in this article \hl{(REF to studying / measuring anthropomorphism)}.
-A common formal ground is missing so far; however, it is important to be clear about what exactly we mean when using the term anthropomorphism.
-
-\hl{(maybe here Persson: anthropomorphism as a multi-layered phenomenon)}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-%
-%
-%		WHY DO PEOPLE ANTHROPOMORPHIZE?
-%
-%
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Why do people anthropomorphize?}
-\label{sec:explanations}
-
-But why do people anthropomorphize?
-First and foremost, it needs to be mentioned that anthropomorphism is a fairly complex phenomenon.
-Paradoxically, there is a huge and diverse body of literature on it but nevertheless, it seems that anthropomorphism is still not very well understood (especially in more recent fields like HRI).
-
-One common reason for anthropomorphism is that by perceiving some human-like characteristics in the non-human agent, this agent is made more \emph{graspable}, \emph{understandable}, \emph{predictable}, and one can feel \emph{more empathetic} toward it, and possibly one can then anticipate the agent's behavior.
-These are central motivations when trying to explain anthropomorphism, and we will come back to them in more detail later on.
-It is described that for the just mentioned reasons, people commonly anthropomorphize their pets, by ascribing mental states, intentions or feelings to them\footnote{Interestingly, pet-ownership seems to have a significant impact on human-robot interaction: several studies suggest that pet-owners are more likely to anthropomorphize technologies and robots than non pet-owners} \cite{eddy_attribution_1993}.
-But how can these motivations behind anthropomorphism be explained?
-
-Anthropomorphism as a social phenomenon arises in an interaction \citep{persson_anthropomorphism_2000}, and thus includes at least two interaction partners (the human and the real or imagined non-human agent).
-Therefore, one can take two main perspectives on explaining it \citep{lee_human_2005}: a human-centered, and an artifact-centered.
-We briefly outline both views in the following.
-It has to be kept in mind that both perspectives are inseparable; they apply at the same time, and we would like to present them here just as two different viewpoints on the same kind of phenomenon.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-%
-%
-%		HUMAN-CENTERED PERSPECTIVE: SOCIAL PHENOMENON
-%
-%
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{A human-centered perspective on anthropomorphism}
-
-The human-centered perspective builds on research from developmental and social psychology as well as cognitive sciences.
-In the following, we present what we found in reviewing this literature: (1) a line of research in developmental psychology that studies the attribution of animacy; (2) a line of research in more cognitive sciences that studies the cognitive processes that underlie anthropomorphism, and (3) a theory that explains anthropomorphism based on psychological factors~\citep{epley_seeing_2007}.
-All three branches apply a human-centered perspective on anthropomorphism.
-
-\paragraph*{Developmental psychology research on the attribution of animacy and intention\\ \\}
-
-The phenomenon of attributing animacy and intentions to nonliving objects such as simple shapes has been intensively studied in developmental psychology.
-As mentioned earlier, Piaget found that children tend to ascribe life to the nonliving.
-They also tend to interpret physical phenomena in terms of intention on the part of the non-human subject.
-For instance children are likely to argue that \textit{``the sun is hot because it wants to make people warm''} \citep{leeds_childrens_1992}.
-In this example it is in fact questionable whether children really anthropomorphize the sun (believing that it has an intention) or whether they are using anthropomorphism in a metaphoric sense (because their conceptions of the world and of the living are not yet fully formed).
-Later however, two famous experiments by \cite{heider_experimental_1944} and \cite{michotte_perception_1963} showed that also adult participants attribute animacy and intention to simple things and shapes based on motion.\footnote{For more details, the reader may refer to the ``attribution theory''.} In both experiments, participants viewed animations of simple shapes, such as circles or triangles (see Figure \ref{fig:animacy_attribution}).
-Asked to describe what they observed, most people developed elaborate stories, attributing motivations, emotions and relationships between the objects.
-
-\begin{figure}[h]\centering
-% Use the relevant command to insert your figure file.
-% For example, with the graphicx package use
-  \includegraphics[scale=0.6]{heider-simmel_animation.jpeg}
-% figure caption is below the figure
- \caption{Fritz Heider and Mary-Ann Simmel's animated film to study people's tendency to attribute animacy and intention to simple shapes; \textit{An experimental study of apparent behavior}, 1944}
- \fxnote{wrap text around this figure?}
- \label{fig:animacy_attribution}       % Give a unique label
- \end{figure}
-
-Summing it up, it seems that there is a natural, relatively spontaneous reaction that makes a person attribute animacy and intention to moving shapes, even when there is no similarity of the shape to a human.
-This tendency to animize / anthropomorphize is already developed (and even more distinct) in infants and children.\footnote{\hl{Julia: I think we should mention this also in the anthropomorphic design section; as movements / motions as one of the most basic "lifelike" cues.}}
-
-\paragraph*{Cognitive science research and the mental model theory (Theory of Mind)\\ \\}
-
-Anthropomorphism and similar phenomenons can also be understood as a thoughtful process of induction whereby \textit{``people reason about an unknown stimulus based on a better-known representation of a related stimulus"}~\citep{epley_when_2008}.
-In the case of anthropomorphism this means a person's reasoning about a non-human agent based on the representation of the self or other humans.
-The general assumption here is that all other agents (and entities) but oneself are \textit{``unknown''} (because we can only be our self).
-A central construct of this perspective is the so-called \textit{mental model} that a person has (and builds) of the agents she is reasoning about and interacting with.
-The specific mental model we have about an artifact / agent basically explains how this artifact / agent works the way it does.
-But how can we explain the phenomenon that a person uses a human-inspired mental model to explain the actions of a non-human (unknown) agent?
-Well, what we know and understand best is ourselves as human beings (the mental model that we have of our self and other humans).
-So by applying a similar mental model (or parts of it) to the unknown agent, we seek to be able to explain this unknown agent.
-This view is consistent with the \emph{familiarity thesis}~\citep{hegel_understanding_2008} which claims that we understand the world based upon a mental model of the world that we are most familiar with.
-Also, the mental model (human-centered perspective) is supported by \cite{epley_seeing_2007} \textit{Three Factor Theory} which applies a social psychology view, and will be presented later in this section.
-
-In sum, this branch of research suggests that anthropomorphism implies that people thoughtfully develop a mental model of agents in their environment and that they make inferences about these agents based on what is familiar to them -- themselves, humans and human behavior.
-This understanding builds on a person's ability to attribute mental states to oneself and others, which is called \textit{Theory of Mind}~\citep{Premack1978}.
-A theory of mind for other agents enables us to attribute intentionality to those agents \citep{leslie_pretense_1987,admoni_multi-category_2012}.
-The link between this tendency to thoughtfully anthropomorphize and the engagement in the attribution of mental states to other humans were recently demonstrated at the brain level~\citep{cullen2013individual}.
-
-%\paragraph*{The mental model theory in human-robot interaction\\ \\}
-
-Mental models have also been studied in HRI.
-Starting point for this research is the assumption that if a system behaves much like a human being (\eg a robot that emits a human voice), people's mental model of the system's behavior may approach their mental model of humans (though the model may differ in some important aspects).
-In turn, people's estimation of an agent's knowledge model and its capabilities affects the way they relate to it.
-This holds important implications for the resulting interaction with the system, the user experience, and the acceptance.
-Previous research examined the validity of the mental model concept with various kinds of robots \cite{schmitz_concepts_2011,kiesler_mental_2002}.
-Findings suggest that people tend to hold richer mental models of anthropomorphic robots in contrast to mechanic ones \cite{kiesler_mental_2002}.\footnote{\hl{Later in this article, we may however come to question how far this result is based on expectations from the human user side, which are likely to be refined after continued interaction, and after the user gets acquainted with the robot's behavior.}} \hl{Julia:leave this paragraph here or put it later in the HRI section??}
-
-\paragraph*{Social psychology research: a 3-factor theory of anthropomorphism\\ \\}
-\label{sec:psychological-factors}
-
-Social psychology offers interesting theories that can be applied to understand people's motivation to anthropomorphize.
-Irrespective of the artifact's characteristics, several psychological determinants have been found to explain a person's tendency to anthropomorphize.
-\cite{epley_seeing_2007} present a ``3-factor theory'' of when people are likely to anthropomorphize based on psychological determinants.
-Namely, the theory suggests that some people are more likely to anthropomorphize when:
-
-\begin{enumerate}
-	\item anthropocentric knowledge is accessible and applicable to the artifact (\textit{elicited agent knowledge}),
-	\item they are motivated to explain and understand the behavior of other agents (\textit{effectance motivation}), and
-	\item they have the desire for social contact and affiliation (\textit{social motivation}).
-\end{enumerate}
-
-The first factor (\textit{elicited agent knowledge}) is a \textbf{cognitive determinant of anthropomorphism} and based on the idea that a person builds a mental model (theory of mind) of the other agent.
-\cite{epley_seeing_2007} suggest that the process of making inferences about non-human agents is based on the activation of knowledge about humans (or the self).
-As mentioned before, when a person builds a mental model of the other (unfamiliar) agent, the question here is why does she draw on knowledge about other humans / herself and not on something else?
-One basic reasons for this is a person's physical constraints of being a human and nothing else.
-Consequently, one has no other experience than the self and in turn people tend to make inferences about others' mental states by relying inordinately on their own mental state.
-\footnote{Using one's own mental states and characteristics as a guide when reasoning about other humans is called ego-centrism.
-In contrast, when using self-knowledge (or knowledge about humans in general) when reasoning about non-human agents, this is called anthropomorphism.
-See \cite{epley_seeing_2007}} Also empirical findings suggest that knowledge about humans in general, or self-knowledge in particular, is likely to serve as a readily accessible base for induction when reasoning about non-human agents.
-This tendency is usually stronger in young children and decreases with cognitive development and the learning to distinguish the self from other humans, and non-human agents.
-
-Both the second factor \textit{effectance} and the third factor \textit{sociality} are \textbf{motivational determinants of anthropomorphism}.
-\textit{Effectance} is understood a person's motivation to interact effectively in one's environment.
-That means, a person is motivated to be able to understand, predict, and reduce uncertainty \footnote{\hl{(this feeds again our hypothesis that as soon as a robot is not uncertain anymore, there is no need to keep on anthropomorphizing it)}}\fxfatal{important!
-move/copy that to the 'model' section or discussion} about her environment and the agents that inhabit it.
-According to \cite{epley_seeing_2007}, \textit{effectance motivation} can lead to anthropomorphism, since anthropomorphism serves as one way to reduce uncertainty and to increase comprehension of events in one's environment.
-Again, also according this factor it can be argued that children are more likely to anthropomorphize than adults.
-As children are in their early stages of life, they are likely to feel more uncertain within their environment, and consequently tend to anthropomorphize more.
-
-The third factor \textit{sociality} describes a person's motivation for social contact, social connection, and social approval from other agents.
-In lack of social connections to other humans (\etc friends, family, colleagues), a person is more likely to compensate these social connections by anthropomorphizing non-human agents.
-In other words \textit{"[...] those who are chronically lonely should be more likely to anthropomorphize nonhuman agents than those who are more chronically connected"} \citep{epley_seeing_2007}.
-Importantly for anthropomorphism, this social connection often appears to be satisfied by connections with \textit{"two of the most commonly anthropomorphized non-human agents, namely pets and religious agents"} \citep{epley_seeing_2007}.
-Thus, the motivation of being socially connected increases the tendency to anthropomorphize non-human agents because first sociality motivation increases the tendency to perceive human-like characteristics and traits even in non-human agents, and second it increases the tendency to search for sources of social connection in one's environment.
+Anthropomorphism is an interesting phenomenon because it tells us something about 
+the relationship between the human who anthropomorphizes, and the non-human agent 
+which is anthropomorphized. Though commonly observed, it appears controversial, at 
+the same time, that humans tend to \hl{\textit{``see human in the non-
+human''}}. 
+Anthropomorphism as a social phenomenon arises in an interaction 
+\citep{persson_anthropomorphism_2000}, and thus includes at least two interaction 
+partners (the human and the real or imagined non-human agent). Therefore, one can 
+take two main perspectives on explaining it \citep{lee_human_2005}: an artifact-
+centered, and a human-centered. We briefly outline both views in the following. 
+It has to be kept in mind that both perspectives are inseparable; they apply at the 
+same time, and we would like to present them here just as two different viewpoints 
+on the same kind of phenomenon.
+
+In this section we will try to create a common ground in the understanding of 
+anthropomorphism, with a focus on it related to human-robot interaction. 
+First of all, we would like to propose a clarification of terms.
+We call an imitation of human form (or in a broader sense also animal and natural) 
+form \textit{``anthropomorphic design''} or \textit{``anthropomorphic form''} -- 
+but \textit{not anthropomorphism}. Contrary, we call the social phenomenon of 
+people's tendency to perceive human-likeness in non human-like 
+agents \textit{anthropomorphism}.
+
+In the following, we first present an artifact-centered perspective on 
+anthropomorphism, and outline how the human-like 
+design approach (\textit{anthropomorphic form}) is used in robotics to encourage 
+people to interact socially with robots. Then, we apply a human-centered 
+perspective and shed light on \textit{anthropomorphism as a social phenomenon}. We present 
+theories from psychology and cognitive science to explain people's tendency to 
+perceive human-like characteristics in non-human agents. In the end, we synthesize 
+the presented backgrounds and suggest an extended understanding of anthropomorphism 
+as a multi-factor phenomenon.
 
@@
 
-In contrast to the human-centered perspective, the artifact-centered perspective explains anthropomorphism from the ascertainable parts / the design of the non-human agent.
-One could think of changing the direction of the causality: here, it is the non-human artifact that encourages the human to anthropomorphize it -- in the human-centered perspective our argument was in the opposite direction, the human was motivated to anthropomorphize the non-human artifact).
-As already mentioned, both these views go hand in hand.
-
-The artifact-centered perspective assumes that humans directly respond to life-like and social cues that the non-human artifact or system emits, without thoughtful mental processing, by simply applying stereotypes and heuristics to it.
-In fact, from early childhood on, humans are inherently well-trained to perceive life \citep{epley_seeing_2007}, and to respond to social cues, such as facial expressions, social gestures, turn-taking.
-\cite{schmitz_concepts_2011} describes that within the visual scope of design, the outer appearance of an object can have an important impact on how it is overall perceived (how it appears to the human).
-This fact is exploited in design.
-The basic assumption  here is that if an artifact somehow resembles a human, it is likely to be treated similar to a human.
-If this explanation of anthropomorphism is correct, people may respond automatically to social cues emitted by an artificial embodied agent such as a robot, and apply human-human social schemas and norms to the occurring interactions.
-(However, at the same time, the human-like design of things also raises expectations from the human user side, to which we will come back later in more detail.)
-
-\paragraph*{Anthropomorphic designs\\ \\}
-
-An imitation of human form (or in a broader sense also animal and natural) form is called \textit{``anthropomorphic design''} or \textit{``anthropomorphic form''} -- but \textit{not anthropomorphism}.\footnote{We suggest to use these two different terms - \textit{anthropomorphism} and \textit{anthropomorphic form} - in order to highlight that they are not the same.
-In short, anthropomorphism refers to the social phenomenon, the human's tendency to perceive human-likeness in non human-like agents, while anthropomorphic form refers to the design of the agent / artifact.} The use of anthropomorphic (human-like) form in the design of non-human things is as old as people's tendency to anthropomorphize.
-Anthropomorphic (and also animal-shaped) forms were used already in prehistoric artworks and illustrations, and they have a long-standing tradition in the design of daily life artifacts and in general \citep{guthrie_bottles_2000}.
-The principle of human-like form has received remarkable attention in respect to the design of robots, on which we will focus in the next paragraph.
-
-Using the term \textit{``form''} to describe the design of an artifact, we refer not only to the shape of an artifact (how the artifact looks like) but to the total expression of the product \citep{bartneck_shaping_2004}.
-\cite{disalvo_hug:_2003} argues that \textit{form} includes a product's physical shape, materials, and behavioral qualities.
-Latter aspect is of special importance for interactive systems that show some degree of autonomy (independence).
-
-\paragraph*{Anthropomorphic form in robotics - Uncanny Valley Hypothesis\\ \\}
-
-Several categories of anthropomorphic form can be classified, but there is no common agreement on the borders and transitions between these categories: anthropomorphic, zoomorphic, caricatured, functional \citep{fong_survey_2003}.
-However, a classification makes sense because different user reactions are expected.
-According to \cite{bartneck_shaping_2004}, the appearance and function of a product, whether it is an appliance or a humanoid robot, affects the way that people perceive it, interact with it, and build long-term relationships with it.
-In general, it is suggested that increasing human-likeness of a robot will lead to more perceived \textit{affinity} from the human side \citep{mori_uncanny_1970}.
-This theoretical concept is also supported by psychological determinants of perceiving human-likeness in something non-human: \textit{"the more similar in appearance, the more people are likely to use themselves as a source of induction and anthropomorphize these nonhuman agents"} \citep{epley_seeing_2007}.
-Further, empirical studies have shown that robots with human-like forms can enhance social responses from humans which in turn can have a positive impact on acceptance \citep{duffy_anthropomorphism_2003,goetz_cooperation_2002,venkatesh_theoretical_2000}.
-People responded more positively to an artifact that displayed human-like behavioral characteristics (emotions, facial expression) in contrast to a purely functional design \citep{eyssel_anthropomorphic_2010,krach_can_2008,reeves_media_1996,riek_how_2009}.
-Overall, these results suggest that human-like features in robots enhance anthropomorphism, and in turn create a social view toward the robot.
+An artifact-centered perspective explains anthropomorphism from the ascertainable 
+parts / the design of the non-human agent.
+The direction of causality in this view is that the non-human artifact (or certain 
+features of it) encourages the human to anthropomorphize it.
+This perspective assumes that humans directly respond to life-like and social cues 
+that the non-human artifact or system emits, without thoughtful mental processing, 
+by simply applying stereotypes and heuristics to it. In fact, from early childhood 
+on, humans are inherently well-trained to perceive life \citep{epley_seeing_2007}, 
+and to respond to social cues, such as facial expressions, social gestures or turn-
+taking. When first looking at an unknown object, the visual scope of its design, 
+its outer appearance is likely to have an important impact on how the object is 
+overall perceived (how it appears to the human) \citep{schmitz_concepts_2011}.
+
+This fact is exploited in the design of robots and other things. The basic 
+assumption  here is that if an artifact 
+somehow resembles a human, it is likely to be treated similar to a human. If this 
+explanation of anthropomorphism is correct, people may respond automatically to 
+social cues emitted by an artificial embodied agent such as a robot, and apply 
+human-human social schemas and norms to the occurring interactions. \hl{(However, at 
+the same time, the human-like design of things also raises expectations from the 
+human user side, to which we will come back later in more detail.)}
+
+\subsubsection{Anthropomorphic design of robots and the Uncanny Valley hypothesis\\}
+
+%People's tendency to anthropomorphize technologies has been described in HCI 
+%\citep{reeves_media_1996} and related to digital agents; however the phenomenon 
+%seems to be more coined in HRI. There are several reasons for this, one of it stems 
+%from the unique characteristics of robots (their typical design).
+
+The use of anthropomorphic (human-like) form in the design of non-human 
+things is as old as people's tendency to anthropomorphize. Anthropomorphic (and 
+also animal-shaped) forms were used already in prehistoric artworks and 
+illustrations, and they have a long-standing tradition in the design of daily life 
+artifacts and in general \citep{guthrie_bottles_2000}. The principle of human-like 
+form is probably most prominent in the design of robots. But what do we mean by \textit{human-like / anthropomorphic form}?
+
+Using the term \textit{``form''} to describe the design of an artifact, we refer 
+not only to the shape of an artifact (how the artifact looks like) but to the total 
+expression of the product \citep{bartneck_shaping_2004}. \cite{disalvo_hug:_2003} 
+argues that \textit{form} includes a product's physical shape, materials, and 
+behavioral qualities. Latter aspect is of special importance for interactive 
+systems that show some degree of autonomy (independence).
+Several categories of anthropomorphic form can be classified, but there is no 
+common agreement on the borders and transitions between these categories: 
+anthropomorphic, zoomorphic, caricatured, functional \citep{fong_survey_2003}. 
+However, a classification makes sense because different user reactions are 
+expected. According to \cite{bartneck_shaping_2004}, the appearance and function of 
+a product, whether it is an appliance or a humanoid robot, affects the way that 
+people perceive it, interact with it, and build long-term relationships with it.
+The relation between the design of a robot and the user's perception of it, is also formulated in the \textit{Uncanny Valley} hypothesis \citep{mori_uncanny_1970}.
 
@@
 
-However, there is the other side of using human-like forms in the design of robots: a not yet very well defined thin line separates acceptable human-like forms in robots from creepy artificial \textit{almost} human-like appearing robots.
-The underlying theory for this viewpoint is stated as the \textit{Uncanny Valley} \cite{mori_uncanny_1970} (see Figure \ref{fig:uncanny_valley}).
-The theory hypothesizes that artificial human-like forms are only acceptable up to a certain degree but lead to reluctance if they fail in trying to attain human-likeness.
-Consequently, it is assumed that a person's response to a human-like robot would abruptly shift from empathy to revulsion as the robot's form approached, but failed to attain a lifelike appearance.
-Naturally, humans are very skilled and also sensitive when it comes to identifying if there is \hl{``something wrong''} in the counterpart-- may the difference be even subtle.
-First, starting with low degrees of anthropomorphic cues in a robot, humans seem to readily accept and prefer these forms compared to purely mechanical robots.
-A possible explanation for this is that humans tend to apply the same communication references to anthropomorphic systems that they would use with other humans.
-However, as the anthropomorphic form also increases people's expectation of the agent, and further artificial systems are (not yet) able to mimic human movements, or human social cues in an acceptable way, the pretended human but artificial agent is more than just disappointing for the human -- it appears uncanny\footnote{The idea of the Uncanny Valley hypothesis follow Freud's description of the uncanny (a translation from the German word \textit{``unheimlich'')}.
-Something uncanny \textit{"derives its terror not from something externally alien or unknown but -- on the contrary -- from something strangely familiar which defeats our efforts to separate ourselves from it"} cited after \cite{hegel_understanding_2008}.} and evokes reluctance, the so-called \textit{"uncanny valley"}.
-
-Of course, there is no one good answer to the question how to not fall in the uncanny valley when designing an anthropomorphic system.
-Equipping a system with some anthropomorphic forms seems to be inevitable \cite{duffy_anthropomorphism_2002} in the advancement of human-machine interfaces and sociable robots \citep{breazeal_sociable_2000}.
-However, we agree that \textit{"the important criterion is to seek a balance between people's expectations and the machines capabilities"} \citep{duffy_anthropomorphism_2002}.
-
-Another critical point with the use of human-like form in artificial agents are ethical aspects.
-For instance, we need to consider how far we actually want an \textit{artificial agent} to resemble a human -- or ourself.
-Even though we do not discuss these aspects in this article, we think the HRI / robotics community needs to consider questions of how far an artificial agent should act ``as if it would be social'' toward humans.
-What implications does an anthropomorphic design of robots have?
-What happens as soon as the artificial agent is considered a \textit{moral agent} \cite{sullins_when_2006}?
-Using \textit{socially interactive robots} in contexts involving elderly care or rehabilitation for disabled / handicapped persons, autistic children is a controversially discussed topic \cite{robins_robots_2005}.
+In general, it is suggested that increasing human-likeness of a robot will lead to 
+more perceived \textit{affinity} from the human side \citep{mori_uncanny_1970} (see 
+Figure \ref{fig:uncanny_valley}). Humans seem to readily accept and prefer the 
+anthropomorphic form of a robot, when compared to purely mechanical robots. A 
+possible explanation for this is that 
+humans tend to apply the same communication references to anthropomorphic systems 
+that they would use with other humans. This theoretical concept is also supported 
+by psychological determinants of 
+perceiving human-likeness in something non-human: \textit{"the more similar in 
+appearance, the more people are likely to use themselves as a source of induction 
+and anthropomorphize these nonhuman agents"} \citep{epley_seeing_2007}. 
+Also various 
+empirical studies have shown that robots with human-like forms can have a positive 
+effect, as they enhance social 
+responses from humans which in turn can positively impact on acceptance 
+\citep{duffy_anthropomorphism_2003,goetz_cooperation_2002,venkatesh_theoretical_2000}. 
+People responded more positively to an artifact that displayed human-like 
+behavioral characteristics (emotions, facial expression) in contrast to a purely 
+functional design 
+\citep{eyssel_anthropomorphic_2010,krach_can_2008,reeves_media_1996,riek_how_2009}. 
+Overall, these results suggest that human-like features in robots enhance 
+anthropomorphism, and in turn create a social view toward the robot.
+
+However, the anthropomorphic form also 
+increases people's expectations of the agent, and consequently, a very human-like 
+appearing robot is expected to act like a human. But today's artificial systems are 
+not able (yet) to mimic human movements, or human social cues in an acceptable way. 
+The case is that the artificial agent pretends to be human but fails, and this is 
+more than just disappointing for the 
+human -- it appears uncanny and evokes reluctance, the so-called 
+\textit{"uncanny valley"}. The idea of naming this shift and drop from a positive to a negative reaction,
+follows Freud's description of the so-called \textit{uncanny} (a translation from the German word 
+\textit{``unheimlich''}). Controversially, something uncanny \textit{"derives its terror not from 
+something externally alien or unknown but -- on the contrary -- from something 
+strangely familiar which defeats our efforts to separate ourselves from it"} (cited 
+after \cite{hegel_understanding_2008}).
+In other words, humans are very sensitive to the limits of what is familiar to them 
+in a sense of being human. At the same time, humans are naturally very skilled when 
+it comes to identifying what is acceptable as a human and what is a \hl{NACHAHMUNG} 
+of it. Even subtle differences can be crucial -- humans are inherently well trained 
+in identifying if there is \hl{``something strange''} in the familiar.
+Summing it up, a not yet very well defined thin line separates acceptable human-like forms in 
+robots from creepy artificial \textit{almost} human-like appearing robots.
+
+Of course, there is no one good answer to the question how to not fall in the 
+uncanny valley when designing an anthropomorphic system. Equipping a system with 
+some anthropomorphic forms seems to be inevitable 
+\cite{duffy_anthropomorphism_2002} in the advancement of human-machine interfaces 
+and sociable robots \citep{breazeal_sociable_2000}. However, we agree that 
+\textit{"the important criterion is to seek a balance between people's expectations 
+and the machines capabilities"} \citep{duffy_anthropomorphism_2002}.
+
+\hl{(ethical issues, maybe put this rather in the end)}
+Another critical point with the use of human-like form in artificial agents are 
+ethical aspects. For instance, we need to consider how far we actually want an 
+\textit{artificial agent} to resemble a human -- or ourself. Even though we do not 
+discuss these aspects in this article, we think the HRI / robotics community needs 
+to consider questions of how far an artificial agent should act ``as if it would be 
+social'' toward humans. What implications does an anthropomorphic design of robots 
+have? What happens as soon as the artificial agent is considered a \textit{moral 
+agent} \cite{sullins_when_2006}? Using \textit{socially interactive robots} in 
+contexts involving elderly care or rehabilitation for disabled / handicapped 
+persons, autistic children is a controversially discussed topic 
+\cite{robins_robots_2005}.
 
@@
 
-% Findings that support anthropomorphic form in robots because they found people respond with anthropomorphizing these kind of robots, and in turn act more social toward them or accept them more easily:	empathy --> check Iolanda's paper
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-%
-%
-%		PART 1.3: ANTHROPOMORPHISM IN HRI / SOCIAL ROBOTICS
-%
-%
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Anthropomorphism in Robotics and Human-Robot Interaction}
+%Findings that support anthropomorphic form in robots because they found people 
+%respond with anthropomorphizing these kind of robots, and in turn act more social 
+%toward them or accept them more easily:	empathy --> check Iolanda's paper
+
+\subsubsection{Anthropomorphism in Robotics and Human-Robot Interaction\\}
 \label{sec:anthropomorphism-robotics}
 
-While the previous sections presented anthropomorphism more generally, this section focuses on how anthropomorphism is understood and has been studied in human robot interaction / social robotics.
-Our aim here is to give a rough overview of the diverse and partially conflicting interpretations of anthropomorphism in HRI, and critically review some previous work.
+\hl{Julia: I need to work on this section ...}
+
+%While the previous sections presented anthropomorphism more generally, this 
+%section focuses on how anthropomorphism is understood and has been studied in human 
+%robot interaction / social robotics. Our aim here is to give a rough overview of 
+%the diverse and partially conflicting interpretations of anthropomorphism in HRI, 
+%and critically review some previous work.
 
@@
 In the so-called \textit{Media Equation}, the authors describe that people mindlessly react socially to their computer and that they tend to even attribute human (social) characteristics to it.
-Then, with emerging new interactive technologies and systems, anthropomorphism has also been observed with digital / virtual characters \citep{reeves_media_1996,
-nass_anthropocentrism_1995}, and later also with artificial embodied agents, such as robots.
-For instance, recent studies found that people tend to ascribe personality and intentions to robots \hl{(REFS)} and that they show empathetic behavior toward robots \cite{rosenthal-vonderputten_experimental_2013}.
+Apart from computers, anthropomorphism has also been observed with digital / virtual characters \citep{reeves_media_1996,
+nass_anthropocentrism_1995}, and as more interactive technologies and systems emerged, also with artificial embodied agents, such as robots.
+
+In human-robot interaction anthropomorphism is a commonly observed phenomenon, however, findings have been inconsistent, and in turn, anthropomorphic designs of robots are controversially discussed.
+
+For instance, recent studies found that people tend to ascribe personality and intentions to robots \hl{(REFS)} and that they show empathetic behavior toward robots \citep{rosenthal-vonderputten_experimental_2013}.
 Summing it up, there is a huge and constantly growing body of literature that describes anthropomorphism in HCI and HRI.
@@
 
-\paragraph*{Studies on anthropomorphism in HRI\\ \\}
-
-Anthropomorphism is a commonly observed phenomenon in human-robot interaction.
-Various studies have shown that people directly talk to their robot (even if it does not recognize speech), give it a name, greet it, or wonder about its intentions and actions as if it were a human \citep{eyssel_anthropomorphic_2010,fink_anthropomorphic_2012,forlizzi_how_2007,fussell_how_2008,kiesler_anthropomorphic_2008}.
-It has frequently been described that people ascribe intentions or emotions to their domestic robot, such as to a Roomba vacuum-cleaning robot \citep{krumm_my_2007,sung_robots_2009} or the AIBO robotic dog \citep{friedman_hardware_2003}.
-Though people's tendency to anthropomorphize non-human agents has already been described in HCI and related to digital agents; however the phenomenon seems to be more coined in HRI.
-There are several reasons for this, which mostly concern the unique characteristics of robots.
-First of all, robots are embodied / physical agents that are sharing the same space with us. 
-Further, robots act autonomously and are able to respond intelligently to us and the environment.
-Then, there is the design aspect, which has already been outlined in Section \ref{sec:anthropomorphic-design}.
-Thus, anthropomorphism may be further supported by a specific anthropomorphic \emph{design}.
+%Various studies have shown that people directly talk to their robot (even if it 
+%does not recognize speech), give it a name, greet it, or wonder about its 
+%intentions and actions as if it were a human 
+%\citep{eyssel_anthropomorphic_2010,fink_anthropomorphic_2012,forlizzi_how_2007,fussell_how_2008,kiesler_anthropomorphic_2008}.
+%It has frequently been described that people ascribe intentions or emotions to 
+%their domestic robot, such as to a Roomba vacuum-cleaning robot 
+%\citep{krumm_my_2007,sung_robots_2009} or the AIBO robotic dog 
+%\citep{friedman_hardware_2003}.
 
@@
 inaccurate results. \hl{say more}
+
+%% -> Commented out the overview as it does not match what we actually present... maybe we need a new one?
+% We would further like to review and discuss research on anthropomorphism in
+% robotics and human-like design of robots. We first provide a comprehensive
+% understanding of the phenomenon drawing on theories from developmental
+% psychology and cognitive sciences. We then present the trends of different
+% kinds of anthropomorphic forms in robots and discuss their role in social
+% robotics. The article integrates related work from human-robot interaction
+% studies, reporting on findings from experiments with human subjects
+% interacting with and evaluating various types of systems. We try to give a
+% coherent view on the topic, outline similarities and antithetic findings, and
+% contribute to a better understanding of anthropomorphism in robotics, and the
+% acceptance of human-like characteristics in robots. We also aim to
+% constructively discuss anthropomorphic design of personal and socially
+% interactive robots.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+%
+%
+%		HUMAN-CENTERED PERSPECTIVE: SOCIAL PHENOMENON
+%
+%
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{A human-centered perspective on anthropomorphism}
+
+In contrast to the artifact-centered perspective, in the human-centered perspective the argumentation is, that the human is motivated to anthropomorphize the non-human artifact).
+As already mentioned, both these views go hand in hand.
+
+Humans tend to perceive human-like characteristics such as physical appearance, emotional states, or inner mental states and motivations in non-human agents that do not have these characteristics themselves, such as animals, natural forces, religious agents, technological gadgets, or mechanical devices \citep{epley_when_2008}.\footnote{According to \cite{epley_when_2008}, a non-human agent can be anything that acts -- or is believed to act -- with apparent independence.}  Anthropomorphism has received remarkable attention across various different domains, such as natural sciences, developmental and social psychology, Human-Computer Interaction (HCI), and Human-Robot Interaction (HRI).
+
+Originally, the term \textbf{anthropomorphism} comes from the Greek \textit{`anthropos'} for `man' (or `human') and \textit{`morphe'} for `form / structure' (or `shape').
+Anthropomorphism is generally understood as people's tendency to perceive a non-human agent as if it had some human characteristics or traits.
+In turn, how a person perceives an agent further determines how she relates to and behaves towards the agent, or how she may behave in light of this agent \citep{epley_when_2008}.
+As such, anthropomorphism can be seen as a special kind of relationship between a human interacting with a non-human agent.
+This anthropomorphic relationship is often characterized by the fact that the human attributes human-unique characteristics to the non-human agent.
+Since anthropomorphism becomes observable through these attributions, some definitions claim that anthropomorphism is not the perception but rather the attribution of human attributes to non-human agents, and name thoughts, emotions, and intentions as examples.
+The most prominently anthropomorphized non-human agents are probably animals and robots \citep{duffy_anthropomorphism_2003,schmitz_concepts_2011}.
+
+Apart from anthropomorphism there also exists the term \textbf{animism}, which can be defined as the attribution of life to the nonliving.
+The study of animism was pioneered by Piaget in the 1920s with his work on \textit{The Child's Conception of the  World}.
+He found that children tend to regard many inanimate objects as capable of sensations, emotions and intentions, and called this view `animism'.
+Since then, children's inferences about the world have been studied intensively.
+However, there is an agreement that children's views and concepts of living, animal, and plant evolve as they grow up.
+Using this definition, animism differs in two main aspects from anthropomorphism:
+First, the property which is ascribed differs: life-likeness is not human-unique but applies to all living beings.
+The second difference between anthropomorphism and animism stems from the agent (or better artifact) to which life is attributed.
+Living beings (most importantly animals) are naturally excluded from being animized.
+Consequently, while animals can be anthropomorphized (perceived to have human unique characteristics), they cannot be animized as they are already living beings.
+(Similarly to the fact that humans cannot be anthropomorphized as they are already humans.)
+Often synonymously used to animism is the term \textbf{zoomorphism}, which applies to the cases when non-lifelike instances / things are associated with animalistic attributes, excluding human-specific traits.
+Both anthropomorphism and animism / zoomorphism can be embraced by the concept of \textbf{life-likeness}.
+
+There exists also the inverse phenomenon to anthropomorphism, which can be found in the literature as \textbf{dehumanization} \citep{haslam_dehumanization:_2006}, or \textbf{mechanomorphism} \citep{caporael_anthropomorphism_1986}.
+We do not treat this here.
+
+ \begin{figure}[b]\centering
+% Use the relevant command to insert your figure file.
+% For example, with the graphicx package use
+  \includegraphics[scale=1]{north-wind.jpg}
+  \includegraphics[scale=1]{sun.jpg}
+% figure caption is below the figure
+ \caption{Milo Winter illustration of Aesop Fable \textit{The North Wind and the Sun}, 1919; both natural forces wind and sun are anthropomorphized with a human face; picture source: wikipedia}
+ \label{fig:north-wind-sun}       % Give a unique label
+ \end{figure}
+
+To illustrate better how anthropomorphism differs from attributions of animacy or life-likeness, it is worth looking at paraphrases and examples of it.
+That is to say, anthropomorphism can alternatively be understood as \textbf{humanization} or \textbf{personification} of anything other than a human being.
+Personification has ancient roots, \eg in mythology but also in storytelling.
+Anthropomorphism was also used to describe and be able to predict natural forces or anticipate great spirits, for instance.
+An illustration of an anthropomorphism related to nature is shown in Figure \ref{fig:north-wind-sun}.
+In this Milo Winter (1919) drawing \textit{"The North Wind and the Sun"}, both north wind and sun are given a human face.
+
+\subsubsection{Diverse understandings of anthropomorphism\\}
+
+Amongst others, one reason for this might be that there exist several understandings of what anthropomorphism is \hl{(REF Peter Ruijten, HRI 2014.)}
+
+Anthropomorphism is used in different senses throughout different disciplines \citep{duffy_anthropomorphism_2003} which makes it difficult to synthesize findings.
+Depending on which understanding of anthropomorphism is applied, not everything colloquially labeled as \emph{anthropomorphism} really is anthropomorphism.\footnote{For instance, it is not always clear whether a person (may it be an adult or a child) who gives and anthropomorphic response, believes that the other agent really thinks or acts like a human or whether she is using anthropomorphism in a metaphoric sense.\citep{leeds_childrens_1992}} We need to be clear about what we mean by anthropomorphism because at the moment, there are different, even partially conflicting understandings of anthropomorphism, not only across but also within disciplines \cite{duffy_anthropomorphism_2002}.
+In particular, in the multi-disciplinary field of HRI, anthropomorphism is understood and interpreted in such a variety of ways that it is almost impossible to bring together and compare the research work done.
+In turn, it seems that the understanding of anthropomorphism in HRI has not improved much over the last decade but has only become more diverse (which is ok, too, but certainly a deeper understanding and common grounds would be convenient).
+
+How can we narrow down the understanding of anthropomorphism?
+From a psychology point of view \cite{epley_when_2008} try to clarify anthropomorphism by explaining what it is \textit{not}, and we think this approach could also help researchers in HRI and robotics.
+\cite{epley_when_2008} list four effects that anthropomorphism does not include:
+(1) First, anthropomorphism does not include behavioral descriptions of observable actions. Anthropomorphism requires going beyond what is directly observable.
+(2) Second, anthropomorphism does not merely entail animism, as animate life is not a uniquely human-like characteristic.
+(3) Third, anthropomorphism does not include any requirement of reasoned or reflective endorsement of an inference.\footnote{\hl{(the strength of anthropomorphic inferences can vary)}}
+(4) Finally, anthropomorphism is not necessarily inaccurate.
+A psychological theory should take this (in)accuracy in anthropomorphism into account and predict variability in the tendency to perceive human-like traits in non-human agents.\footnote{For more details, the reader may refer to the original work \citep{epley_when_2008}.}
+
+Not only \cite{epley_when_2008} and \cite{duffy_anthropomorphism_2002} but also others have noticed that anthropomorphism is a very complex phenomenon -- itself and in how it can be understood.
+This holds implications for the study of anthropomorphism (to what we will come back later in this article \hl{(REF to studying / measuring anthropomorphism)}.
+A common formal ground is missing so far; however, it is important to be clear about what exactly we mean when using the term anthropomorphism.
+
+\hl{(maybe here Persson: anthropomorphism as a multi-layered phenomenon)}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+%
+%
+%		WHY DO PEOPLE ANTHROPOMORPHIZE?
+%
+%
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsubsection{Why do people anthropomorphize?\\}
+\label{sec:explanations}
+
+But why do people anthropomorphize?
+First and foremost, it needs to be mentioned that anthropomorphism is a fairly complex phenomenon.
+Paradoxically, there is a huge and diverse body of literature on it but nevertheless, it seems that anthropomorphism is still not very well understood (especially in more recent fields like HRI).
+
+One common reason for anthropomorphism is that by perceiving some human-like characteristics in the non-human agent, this agent is made more \emph{graspable}, \emph{understandable}, \emph{predictable}, and one can feel \emph{more empathetic} toward it, and possibly one can then anticipate the agent's behavior.
+These are central motivations when trying to explain anthropomorphism, and we will come back to them in more detail later on.
+It is described that for the just mentioned reasons, people commonly anthropomorphize their pets, by ascribing mental states, intentions or feelings to them\footnote{Interestingly, pet-ownership seems to have a significant impact on human-robot interaction: several studies suggest that pet-owners are more likely to anthropomorphize technologies and robots than non pet-owners} \cite{eddy_attribution_1993}.
+But how can these motivations behind anthropomorphism be explained?
+
+The human-centered perspective builds on research from developmental and social psychology as well as cognitive sciences.
+In the following, we present what we found in reviewing this literature: (1) a line of research in developmental psychology that studies the attribution of animacy; (2) a line of research in more cognitive sciences that studies the cognitive processes that underlie anthropomorphism, and (3) a theory that explains anthropomorphism based on psychological factors~\citep{epley_seeing_2007}.
+All three branches apply a human-centered perspective on anthropomorphism.
+
+\paragraph*{Developmental psychology research on the attribution of animacy and intention\\ \\}
+
+The phenomenon of attributing animacy and intentions to nonliving objects such as simple shapes has been intensively studied in developmental psychology.
+As mentioned earlier, Piaget found that children tend to ascribe life to the nonliving.
+They also tend to interpret physical phenomena in terms of intention on the part of the non-human subject.
+For instance children are likely to argue that \textit{``the sun is hot because it wants to make people warm''} \citep{leeds_childrens_1992}.
+In this example it is in fact questionable whether children really anthropomorphize the sun (believing that it has an intention) or whether they are using anthropomorphism in a metaphoric sense (because their conceptions of the world and of the living are not yet fully formed).
+Later however, two famous experiments by \cite{heider_experimental_1944} and \cite{michotte_perception_1963} showed that also adult participants attribute animacy and intention to simple things and shapes based on motion.\footnote{For more details, the reader may refer to the ``attribution theory''.} In both experiments, participants viewed animations of simple shapes, such as circles or triangles (see Figure \ref{fig:animacy_attribution}).
+Asked to describe what they observed, most people developed elaborate stories, attributing motivations, emotions and relationships between the objects.
+
+\begin{figure}[h]\centering
+% Use the relevant command to insert your figure file.
+% For example, with the graphicx package use
+  \includegraphics[scale=0.6]{heider-simmel_animation.jpeg}
+% figure caption is below the figure
+ \caption{Fritz Heider and Mary-Ann Simmel's animated film to study people's tendency to attribute animacy and intention to simple shapes; \textit{An experimental study of apparent behavior}, 1944}
+ \fxnote{wrap text around this figure?}
+ \label{fig:animacy_attribution}       % Give a unique label
+ \end{figure}
+
+Summing it up, it seems that there is a natural, relatively spontaneous reaction that makes a person attribute animacy and intention to moving shapes, even when there is no similarity of the shape to a human.
+This tendency to animize / anthropomorphize is already developed (and even more distinct) in infants and children.\footnote{\hl{Julia: I think we should mention this also in the anthropomorphic design section; as movements / motions as one of the most basic "lifelike" cues.}}
+
+\paragraph*{Cognitive science research and the mental model theory (Theory of Mind)\\ \\}
+
+Anthropomorphism and similar phenomenons can also be understood as a thoughtful process of induction whereby \textit{``people reason about an unknown stimulus based on a better-known representation of a related stimulus"}~\citep{epley_when_2008}.
+In the case of anthropomorphism this means a person's reasoning about a non-human agent based on the representation of the self or other humans.
+The general assumption here is that all other agents (and entities) but oneself are \textit{``unknown''} (because we can only be our self).
+A central construct of this perspective is the so-called \textit{mental model} that a person has (and builds) of the agents she is reasoning about and interacting with.
+The specific mental model we have about an artifact / agent basically explains how this artifact / agent works the way it does.
+But how can we explain the phenomenon that a person uses a human-inspired mental model to explain the actions of a non-human (unknown) agent?
+Well, what we know and understand best is ourselves as human beings (the mental model that we have of our self and other humans).
+So by applying a similar mental model (or parts of it) to the unknown agent, we seek to be able to explain this unknown agent.
+This view is consistent with the \emph{familiarity thesis}~\citep{hegel_understanding_2008} which claims that we understand the world based upon a mental model of the world that we are most familiar with.
+Also, the mental model (human-centered perspective) is supported by \cite{epley_seeing_2007} \textit{Three Factor Theory} which applies a social psychology view, and will be presented later in this section.
+
+In sum, this branch of research suggests that anthropomorphism implies that people thoughtfully develop a mental model of agents in their environment and that they make inferences about these agents based on what is familiar to them -- themselves, humans and human behavior.
+This understanding builds on a person's ability to attribute mental states to oneself and others, which is called \textit{Theory of Mind}~\citep{Premack1978}.
+A theory of mind for other agents enables us to attribute intentionality to those agents \citep{leslie_pretense_1987,admoni_multi-category_2012}.
+The link between this tendency to thoughtfully anthropomorphize and the engagement in the attribution of mental states to other humans were recently demonstrated at the brain level~\citep{cullen2013individual}.
+
+%\paragraph*{The mental model theory in human-robot interaction\\ \\}
+
+Mental models have also been studied in HRI.
+Starting point for this research is the assumption that if a system behaves much like a human being (\eg a robot that emits a human voice), people's mental model of the system's behavior may approach their mental model of humans (though the model may differ in some important aspects).
+In turn, people's estimation of an agent's knowledge model and its capabilities affects the way they relate to it.
+This holds important implications for the resulting interaction with the system, the user experience, and the acceptance.
+Previous research examined the validity of the mental model concept with various kinds of robots \cite{schmitz_concepts_2011,kiesler_mental_2002}.
+Findings suggest that people tend to hold richer mental models of anthropomorphic robots in contrast to mechanic ones \cite{kiesler_mental_2002}.\footnote{\hl{Later in this article, we may however come to question how far this result is based on expectations from the human user side, which are likely to be refined after continued interaction, and after the user gets acquainted with the robot's behavior.}} \hl{Julia:leave this paragraph here or put it later in the HRI section??}
+
+\paragraph*{Social psychology research: a 3-factor theory of anthropomorphism\\ \\}
+\label{sec:psychological-factors}
+
+Social psychology offers interesting theories that can be applied to understand people's motivation to anthropomorphize.
+Irrespective of the artifact's characteristics, several psychological determinants have been found to explain a person's tendency to anthropomorphize.
+\cite{epley_seeing_2007} present a ``3-factor theory'' of when people are likely to anthropomorphize based on psychological determinants.
+Namely, the theory suggests that some people are more likely to anthropomorphize when:
+
+\begin{enumerate}
+	\item anthropocentric knowledge is accessible and applicable to the artifact (\textit{elicited agent knowledge}),
+	\item they are motivated to explain and understand the behavior of other agents (\textit{effectance motivation}), and
+	\item they have the desire for social contact and affiliation (\textit{social motivation}).
+\end{enumerate}
+
+The first factor (\textit{elicited agent knowledge}) is a \textbf{cognitive determinant of anthropomorphism} and based on the idea that a person builds a mental model (theory of mind) of the other agent.
+\cite{epley_seeing_2007} suggest that the process of making inferences about non-human agents is based on the activation of knowledge about humans (or the self).
+As mentioned before, when a person builds a mental model of the other (unfamiliar) agent, the question here is why does she draw on knowledge about other humans / herself and not on something else?
+One basic reasons for this is a person's physical constraints of being a human and nothing else.
+Consequently, one has no other experience than the self and in turn people tend to make inferences about others' mental states by relying inordinately on their own mental state.
+\footnote{Using one's own mental states and characteristics as a guide when reasoning about other humans is called ego-centrism.
+In contrast, when using self-knowledge (or knowledge about humans in general) when reasoning about non-human agents, this is called anthropomorphism.
+See \cite{epley_seeing_2007}} Also empirical findings suggest that knowledge about humans in general, or self-knowledge in particular, is likely to serve as a readily accessible base for induction when reasoning about non-human agents.
+This tendency is usually stronger in young children and decreases with cognitive development and the learning to distinguish the self from other humans, and non-human agents.
+
+Both the second factor \textit{effectance} and the third factor \textit{sociality} are \textbf{motivational determinants of anthropomorphism}.
+\textit{Effectance} is understood a person's motivation to interact effectively in one's environment.
+That means, a person is motivated to be able to understand, predict, and reduce uncertainty \footnote{\hl{(this feeds again our hypothesis that as soon as a robot is not uncertain anymore, there is no need to keep on anthropomorphizing it)}}\fxfatal{important!
+move/copy that to the 'model' section or discussion} about her environment and the agents that inhabit it.
+According to \cite{epley_seeing_2007}, \textit{effectance motivation} can lead to anthropomorphism, since anthropomorphism serves as one way to reduce uncertainty and to increase comprehension of events in one's environment.
+Again, also according this factor it can be argued that children are more likely to anthropomorphize than adults.
+As children are in their early stages of life, they are likely to feel more uncertain within their environment, and consequently tend to anthropomorphize more.
+
+The third factor \textit{sociality} describes a person's motivation for social contact, social connection, and social approval from other agents.
+In lack of social connections to other humans (\etc friends, family, colleagues), a person is more likely to compensate these social connections by anthropomorphizing non-human agents.
+In other words \textit{"[...] those who are chronically lonely should be more likely to anthropomorphize nonhuman agents than those who are more chronically connected"} \citep{epley_seeing_2007}.
+Importantly for anthropomorphism, this social connection often appears to be satisfied by connections with \textit{"two of the most commonly anthropomorphized non-human agents, namely pets and religious agents"} \citep{epley_seeing_2007}.
+Thus, the motivation of being socially connected increases the tendency to anthropomorphize non-human agents because first sociality motivation increases the tendency to perceive human-like characteristics and traits even in non-human agents, and second it increases the tendency to search for sources of social connection in one's environment.
+
+\subsection{Summary: Anthropomorphism as a multi-factor phenomenon}
+\label{sec:multi-factors}
 
@@
 
-%% -> Commented out the overview as it does not match what we actually present... maybe we need a new one?
-% We would further like to review and discuss research on anthropomorphism in
-% robotics and human-like design of robots. We first provide a comprehensive
-% understanding of the phenomenon drawing on theories from developmental
-% psychology and cognitive sciences. We then present the trends of different
-% kinds of anthropomorphic forms in robots and discuss their role in social
-% robotics. The article integrates related work from human-robot interaction
-% studies, reporting on findings from experiments with human subjects
-% interacting with and evaluating various types of systems. We try to give a
-% coherent view on the topic, outline similarities and antithetic findings, and
-% contribute to a better understanding of anthropomorphism in robotics, and the
-% acceptance of human-like characteristics in robots. We also aim to
-% constructively discuss anthropomorphic design of personal and socially
-% interactive robots.
-
-\subsection{Summary: Anthropomorphism as a multi-factor phenomenon}
-\label{sec:multi-factors}
-
 In this article we will use the term \emph{anthropomorphic effect} to denote
@@
 \end{figure}
-
-The notation \Ant[R,H,C,t] reflects these multiple factors: we suggest here that
-anthropomorphism is a function of a vector of robot's traits $R = \{r_0,...,r_n\}$, a vector human
-determinants $H = \{h_0,...,h_n\}$, a set of interaction situations that build a
-an interaction context $C = \{s_0,...,s_n\}$, and the duration of the
-interaction itself, $t$.
 
@@
 \subsection{A Model of the Dynamics of Anthropomorphism}
+\label{sec:dynamics-model}
+
+\paragraph{Why is anthropomorphism likely to change over time?}
+\hl{maybe we need to move this paragraph to PART 3}
+
+\subsection{A Model of the Dynamics of Anthropomorphism}
 
@@
 
-While the model primarily considers \emph{long-term interaction} -- direct
-(non-mediated), repeated interaction with the same robot, over an extended
-period of time (typically longer than a week) --, we also formally introduce a
-so-called \emph{novelty effect}~\cite{kanda_interactive_2004} that models the
-first phase of human-robot interaction, during which a specific increase of
-anthropomorphic interactions is observed.
-
 In this model, anthropomorphism is quantified by a \emph{normalized level of
@@
 an absolute scale, we present them as a normalized value, that spans from a
-minimum (no anthropomorphic effects: $\ant=0$) to a maximum (noted \AntMax, with
-$t_{max} = \operatorname{arg\,max}_t \, \ant[t]$). We also discuss at
-section~\ref{measuring} possible methodologies for the quantitative and
-qualitative assessment of anthropomorphic effects.
-
-As pictured on Figure~\ref{fig:dynamics}, we suggest that $t_{max}$ actually
-corresponds to the novelty effect peak. The actual maximum value of
+minimum (no anthropomorphic effects) to a maximum (corresponding to the novelty
+effect peak on Figure~\ref{fig:dynamics}). The actual maximum value of
 anthropomorphic effects depends on each unique combination of human, robot and
@@
 
-\begin{figure*}[htb]
-\centering
-
-\begin{tikzpicture}[scale=1.4]
-
-% background shading
-\path[fill=blue!20] (0,0) rectangle (0.6,5.5);
-\path[fill=green!20] (0.6,0) rectangle (5.2,5.5);
-\path[fill=orange!20] (5.2,0) rectangle (9.8,5.5);
-\draw(0,5.5) node[anchor=south west, rotate=10] {\scriptsize \sc Initialization};
-\draw(2.5,5.5) node[anchor=south west, rotate=10] {\scriptsize \sc Familiarization};
-\draw(6.5,5.5) node[anchor=south west, rotate=10] {\scriptsize \sc Stabilization};
-% horizontal axis
-\draw[->] (0,0) -- (10,0) node[anchor=north] {$t$};
-\draw(5,-0.1) node[anchor=north] {\scriptsize Duration of interaction};
-
-% vertical axis
-\draw[->] (0,0) -- (0,6) node[anchor=east] {};
-\draw(-0.8,3) node[rotate=90,anchor=south] {\scriptsize Normalized level of anthropomorphic effects};
-
-\draw (-0.05, 3) -- (0.05, 3) node[anchor=east] {\ICA};
-\draw (-0.05, 5) -- (0.05, 5) node[anchor=east] {\AntMax};
-
-% vertical axis - end
-\draw[->] (9.8,0) -- (9.8,2) node[anchor=east] {};
-\draw (9.8, 0.8) node[anchor=west] {\SLA};
-
-\draw[<-] (0.65,5) -- (0.8,5.2) node[anchor=east] {};
-\draw (0.9,5.3) node[anchor=west] {\tiny \it novelty peak};
-
-\draw[dotted] (0, 5) -- (6.2,5);
-\draw[dotted] (0, 3) -- (6.2,3);
-\draw[<->] (6.1,3) -- (6.1,5) node[anchor=east] {};
-\draw (6.2,4) node[rotate=90, anchor=north, align=center] {\tiny Expectation\\\tiny mismatch};
-
-\draw[<-] (1.7,4.4) -- (3.2,4.1) node[anchor=east] {};
-\draw[<-] (2.85,2.6) -- (3.2,4.1) node[anchor=east] {};
-\draw (3.2,4.1) node[anchor=west, align=center] {\tiny \it disruptive\\ \tiny
-\it behaviors};
+The model takes into account the duration of the interaction, the nature of the
+interaction, as well as acquired experience and familiarization mechanisms. We
+also formally introduce a so-called \emph{novelty effect} that models the first
+phase of human-robot interaction, during which a specific increase of
+anthropomorphic interactions is observed. We focus on \emph{long-term
+interaction}, \ie direct (non-mediated), repeated interaction with the same
+robot, over an extended period of time (typically longer than a week). The nature 
+of the interaction (goal-directed, entertainment, etc.) may
+however vary.
+
+%\begin{figure*}[htb]
+%\centering
+%
+%
+%\begin{tikzpicture}[scale=1.2]
+%
+%% background shading
+%\path[fill=gray!20] (0,0) rectangle (0.6,5.5);
+%\path[fill=gray!50] (0.6,0) rectangle (5.2,5.5);
+%\path[fill=gray!20] (5.2,0) rectangle (9.8,5.5);
+%\draw(0,5.5) node[anchor=south west] {\scriptsize \sc Initialization};
+%\draw(4,5.5) node[anchor=south] {\scriptsize \sc Familiarization};
+%\draw(7.5,5.5) node[anchor=south] {\scriptsize \sc Stabilization};
+%% horizontal axis
+%\draw[->] (0,0) -- (10,0) node[anchor=north] {$t$};
+%\draw(5,-0.1) node[anchor=north] {\scriptsize Duration of interaction};
+%
+%
+%% vertical axis
+%\draw[->] (0,0) -- (0,6) node[anchor=east] {};
+%\draw(-0.8,3) node[rotate=90,anchor=south] {\scriptsize Normalized level of anthropomorphic effects};
+%
+%\draw (-0.05, 3) -- (0.05, 3) node[anchor=east] {\scriptsize ICA$_{\mathcal B}$};
+%\draw (-0.05, 4.1) -- (0.05, 4.1) node[anchor=east] {\scriptsize ICA$_{\mathcal A}$};
+%\draw (-0.05, 0.6) -- (0.05, 0.6) node[anchor=east] {\scriptsize ICA$_{\mathcal C}$};
+%
+%% vertical axis - end
+%\draw[->] (9.8,0) -- (9.8,2) node[anchor=east] {};
+%\draw (9.8, 0.8) node[anchor=west] {\scriptsize SLA$_\mathcal{E}$};
+%\draw (9.8, 1.4) node[anchor=west] {\scriptsize SLA$_\mathcal{D}$};
+%\draw (9.8, .2) node[anchor=west] {\scriptsize SLA$_\mathcal{F}$};
+%
+%
+%\draw[<-] (0.65,5) -- (0.8,5.2) node[anchor=east] {};
+%\draw (0.9,5.3) node[anchor=west] {\tiny \it novelty effect};
+%
+%
+%\draw[dotted] (0, 5) -- (6.2,5);
+%\draw[dotted] (0, 3) -- (6.2,3);
+%\draw[<->] (6.1,3) -- (6.1,5) node[anchor=east] {};
+%\draw (6.2,4) node[rotate=90, anchor=north] {\tiny Expectation mismatch};
+%
+%\draw[<-] (1.7,4.4) -- (3.2,4.1) node[anchor=east] {};
+%\draw[<-] (2.85,3.3) -- (3.2,4.1) node[anchor=east] {};
+%\draw (3.2,4.1) node[anchor=west] {\tiny \it disruptive behaviors};
+%%%%%%
+%%% CURVES
 %%%%%
-%% CURVES
-%%%%
-\begin{scope}[yscale=-1,shift={(-0.125,-0.4)}]
-
-    \draw[ultra thick] svg[scale=1cm] "M 0.125,-2.5619582 c 0.0200733,-1.1573591
-    0.33954391,-1.9982333 0.57940683,-2.0013597 0.13691605,0 0.25550329,0.052908
-    0.37497897,0.1661788 0.119476,0.1130305 0.2396954,0.2786079
-    0.37944,0.4790565 0.069872,0.099803 0.1021612,-0.2231749
-    0.1792538,-0.2238964 0.099707,0 0.013454,0.4985362 0.3173383,0.9139831
-    0.1911917,0.2612926 0.3444354,0.2578391 0.6711932,0.4894291
-    0.2058265,0.1458798 0.1571532,0.9762306 0.2615031,0.9702183 0.097182,0
-    0.083295,-0.3336208 0.4330446,-0.1199242 0.4306401,0.2631203
-    0.216699,0.1355642 0.4296663,0.2647074 2.0858202,1.13836043
-    4.34683,1.41300027 6.3741749,1.43753027";
-
-    \draw[dashed] svg[scale=1cm] "M 0.125,-0.1952939 c 0.0553601,-3.1917862
-    0.33954391,-4.3648976 0.57940683,-4.368024 0.13691605,0 0.25550329,0.052908
-    0.37497897,0.1661788 m 2.6714393,2.7735737 C 4.7653984,-0.85050947
-    6.5955093,0.35382293 10.125,0.4062498";
-
-    \draw[dashed] svg[scale=1cm] "M 0.125,-3.6923825 C 0.1102888,-4.0297903
-    0.46454391,-4.5601915 0.70440683,-4.5633179 M 3.7508251,-1.6235654 C
-    4.9579368,-0.95548345 8.1358175,-0.82609971 10.125,-0.79459549";
-
-\end{scope}
-
-\end{tikzpicture}
-
-\caption{The dynamics of anthropomorphism. We distinguish three main phases:
-    \emph{initialization}, \emph{familiarization} and \emph{stabilization},
-    preceded by a \emph{pre-interaction} phase. In the pre-interaction phase,
-    users build an \emph{initial capital of anthropomorphism} (ICA, noted \ICA).
-    Once the interaction starts, the level of anthropomorphism increases due to
-    the \emph{novelty effect}, and then decreases to reach a \emph{stabilized
-    level of anthropomorphism} (SLA, noted \SLA). \ICA and \SLA may vary
-    depending on the user, the robot and the context of interaction.  During the
-    interaction, unpredicted behaviors of the robot (\emph{disruptive
-    behaviors}) may lead to local increases or decreases of the level of
-    anthropomorphism.}
-
-\label{fig:dynamics}
-\end{figure*}
+%\begin{scope}[yscale=-1,shift={(-0.125,-0.4)}]
+%
+%% output of inkscape2tikz
+%\path[draw=black]
+%    (0.1250,-2.5620) .. controls (0.1451,-3.7193) and (0.4645,-4.5602) ..
+%    (0.7044,-4.5633) .. controls (0.8413,-4.5633) and (0.9599,-4.5104) ..
+%    (1.0794,-4.3971) .. controls (1.1989,-4.2841) and (1.3191,-4.1185) ..
+%    (1.4588,-3.9181) .. controls (1.5287,-3.8183) and (1.5610,-4.1413) ..
+%    (1.6381,-4.1420) .. controls (1.7378,-4.1420) and (1.6515,-3.6434) ..
+%    (1.9554,-3.2280) .. controls (2.1466,-2.9667) and (2.3889,-2.7023) ..
+%    (2.6819,-2.4292) .. controls (2.7551,-2.3607) and (2.7727,-2.8119) ..
+%    (2.8771,-2.8180) .. controls (2.9742,-2.8180) and (2.9594,-2.2108) ..
+%    (3.1665,-2.0209) .. controls (3.3340,-1.8673) and (3.5379,-1.7527) ..
+%    (3.7508,-1.6236) .. controls (5.8366,-0.4852) and (8.0977,-0.2106) ..
+%    (10.1250,-0.1860);
+%\path[draw=black, dashed]
+%    (0.1250,-3.6924) .. controls (0.1103,-4.0298) and (0.4645,-4.5602) .. 
+%    (0.7044,-4.5633)
+%    (3.7508,-1.6236) .. controls (4.9579,-0.9555) and (8.1358,-0.8261) .. 
+%    (10.1250,-0.7946);
+%\path[draw=black,dashed]
+%    (0.1250,-0.1953) .. controls (0.1804,-3.3871) and (0.4645,-4.5602) .. 
+%    (0.7044,-4.5633) .. controls (0.8413,-4.5633) and (0.9599,-4.5104) .. 
+%    (1.0794,-4.3971)
+%    (3.7508,-1.6236) .. controls (4.7654,-0.8505) and (6.5955,0.3538) .. 
+%    (10.1250,0.4062);
+%
+%\end{scope}
+%
+%\end{tikzpicture}
+%
+%\caption{The dynamics of anthropomorphism. We distinguish three main phases:
+%    \emph{initialization}, \emph{familiarization} and \emph{stabilization},
+%    preceded by a \emph{pre-interaction} phase. In the pre-interaction phase,
+%    users build an \emph{initial capital of anthropomorphism} (ICA). Once the
+%    interaction starts, the level of anthropomorphism increases due to the
+%    \emph{novelty effect}~\cite{kanda_interactive_2004}, and then decreases to
+%    reach a \emph{stabilized level of anthropomorphism} (SLA).  During the
+%    interaction, unpredicted behaviors of the robot (\emph{disruptive behaviors})
+%    may lead to local increase of the level of anthropomorphism.}
+%
+%\label{fig:dynamics}
+%\end{figure*}
 
@@
 of seconds to a couple of hours), we observe an increased level of
-anthropomorphism, from an \emph{initial capital of anthropomorphism} \ICA
+anthropomorphism, from an \emph{initial capital of anthropomorphism}
 (detailed in the next section) to a peak of anthropomorphic manifestations
-\AntMax that corresponds to the maximum of the \emph{novelty effect}.
+that corresponds to the maximum of the \emph{novelty effect}.
 Section~\ref{sec:initialization} details this first phase.
@@
 effects tends to stabilize over a longer time, to reach a \emph{stabilized
-level of anthropomorphism} \SLA. \SLA may be null (no anthropomorphic
+level of anthropomorphism} (SLA). The SLA may be null (no anthropomorphic
 effects observed anymore), but it may also remain at a higher level.  This
@@
 of anthropomorphic interactions between a human and a robot to a value that we
-call \emph{initial capital of anthropomorphism}, noted \ICA. \ICA describes the
+call \emph{initial capital of anthropomorphism} (ICA). The ICA describes the
 first (real or imagined) contact to a robot. In this stage of pre-interaction,
@@
 
-We build \ICA on three main factors that \emph{a priori} determine the
+We build the ICA on three main factors that \emph{a priori} determine the
 potential that a robot will be anthropomorphized:
@@
 
-\ICA comprises some hypothetical values for each of these three factors, such
-that different \ICA values can be obtained, given the robot, human user, and
+The ICA comprises some hypothetical values for each of these three factors, such
+that different ICA values can be obtained, given the robot, human user, and
 environmental context\fxfatal{??}.
@@
 objects more than adults. Also, a person who lacks social connection is said to
-be more likely to anthropomorphize. Both aspects would increase \ICA. This
+be more likely to anthropomorphize. Both aspects would increase the ICA. This
 means that, one and the same robot used by a different user, can lead to a
-different \ICA.
+different ICA.
 
 For \textbf{design}, we understand that a robot that follows an anthropomorphic
-design (\eg NAO) leads to a higher \ICA than a rather functional robot (\eg
+design (\eg NAO) leads to a higher ICA than a rather functional robot (\eg
 Roomba). Also, a robot that is able to display facial expressions would increase
-the \ICA. However, \hl{as discussed before} a classification of the "amount" of
+the ICA. However, \hl{as discussed before} a classification of the "amount" of
 anthropomorphic design in a robot, as for instance suggested by Fong \textit{et
@@
 a robot which is imagined to be used in a social, entertaining or playful
-context leads to a higher \ICA than a robot which is used for a routine or
+context leads to a higher ICA than a robot which is used for a routine or
 focused task (security, rescue, etc.). This idea also receives support from
@@
 the environmental context in which people experience and interact with the robot
-impacts the \ICA. For instance, several friends interacting simultaneously with
-the robot might lead to increased \ICA for each of the users, due to increased
-human-human social interactions (the robot might be perceived to be part of the
-social interaction, and in turn attributed human-like
-qualities)~\cite{baxter2013do}.
+impacts the ICA. For instance, several friends interacting simultaneously with
+the robot might lead to increased ICAs, due to increased human-human social
+interactions (the robot might be perceived to be part of the social interaction,
+and in turn attributed human-like qualities)~\cite{baxter2013do}.
 
@@
 
-By \emph{disruptive behaviors}, we mean any behavior exhibited by the robot that
-is unexpected by the user: for instance, a robot may usually follow always the
-same route to go to two different places in a house, and suddenly change the
-route. The actual underlying reason may span from a bug to the detection of a
-new possible obstacle, but as long as this reason is not immediately
+By \emph{disruptive behaviors}, we mean any behavior exhibited by the robot
+that is unexpected by the user: for instance, a robot may usually follow always
+the same route to go to two different places in a house, and suddenly change
+the route. The actual underlying reason may span from a bug to the detection of
+a new possible obstacle, but as long as this reason is not immediately
 intelligible to the user, the behavior counts as \emph{disruptive}.
 
-As illustrated on Figure~\ref{fig:dynamics}, our model represents
-\emph{disruptive behaviors} as either local increases or local decreases of
-anthropomorphic effects in the familiarization phase (and at a lesser extend, in
-the stabilization phase): because such behaviors are unexpected, a human
-observer may interpret them either as the result of a richer deliberative
-process, which in turn leads to the supposition of complex cognitive skills, or
-conversely as a failure, reminding the human that the robot is ``just a
-machine''. Section~\ref{sec:disruptive} discusses more in depth the impact of
-the user's perception of disruptive behaviours, and their cognitive correlates.
+Our model represents \emph{disruptive behaviors} as local increases of
+anthropomorphic effects in the familiarization phase (and at a lesser extend,
+in the stabilization phase) (Figure~\ref{fig:dynamics}): because such behaviors
+are unexpected, a human observer may interpret them as the result of a richer
+deliberative process, which in turn leads to the supposition of complex
+cognitive skills
+
+This is however to be modulated depending on the real and percieved reasons of the
+unexpected behavior.  Section~\ref{sec:disruptive} discusses more in depth the
+mental correlates of disruptive behaviors. It proposes a typology that relates
+them to the anthropomorphism they induce. It may increase if the user perceives
+(rightfully or not) a form of intentionality, as well as decrease if the
+unexpected behavior is perceived as a failure.
 
@@
 effects tends to stabilize over a longer time, to reach a \emph{stabilized
-level of anthropomorphism}, noted \SLA.
+level of anthropomorphism} (SLA).
 
 If, after the familiarization phase, no anthropomorphic effects are observed
-anymore, $\sla = 0$. This can be interpreted as the user interacting with the
-robot in a routine way, without projecting anymore human-like traits on the
-robot.
-
-\paragraph{Stabilized Level of Anthropomorphism}
-
-The \emph{Stabilized Level of Anthropomorphism} describes the long-term lasting level of
-anthropomorphism.
-
-We proposed that \ICA is built on three factors: user's \emph{personality},
+anymore, the \emph{Stabilized Level of Anthropomorphism} is zero. This can
+be interpreted as the user interacting with the robot in a routine way, without
+projecting anymore human-like traits on the robot.
+
+\paragraph{Stabilized Level of Anthropomorphism (SLA)}
+
+The \emph{Stabilized Level of Anthropomorphism} (SLA on
+Figure~\ref{fig:dynamics}) describes the long-term lasting level of
+anthropomorphism.  Like the ICA, the SLA has a unique value per triplet
+(\emph{human}, \emph{robot}, \emph{context of interaction}).
+
+We proposed that the ICA is built on three factors: user's \emph{personality},
 robot's \emph{design} and interaction \emph{purpose} (or \emph{interaction
-context}). The user's personality and the context of use do also influence \SLA.
-In particular, it appears that the user's level of acquaintance with
+context}). The user's personality and the context of use do also influence the
+SLA. In particular, it appears that the user's level of acquaintance with
 technologies plays an important role in long-term tendency to
@@
 The robot's design, on the other hand, plays a more subtle role, and strong
-initial anthropomorphic design does not mandate high \SLA: lasting
+initial anthropomorphic design does not mandate high SLA: lasting
 anthropomorphic effects have been observed on non-anthropomorphic robots (like
@@
 \emph{Stabilized Level of Anthropomorphism} are generally not correlated: one
-individual may have high potential of anthropomorphizing (high \ICA) at first
+individual may have high potential of anthropomorphizing (high ICA) at first
 sight of a good-looking humanoid robot, and get disappointed by the actual
 abilities of the robots, down to routine, non-anthropomorphic, interactions (low
-\SLA), while another user with the same high \ICA may, for instance, creates
+SLA), while another user with the same high ICA may, for instance, creates
 lasting affective bonds with the same robot, and keeps anthropomorphizing it
-(higher \SLA).
+(higher SLA).
 
@@
 
-\begin{figure}[htb]
-\centering
-%\resizebox{\linewidth}{!}{
-\begin{tikzpicture}
-\baselineskip=8pt
-
-\path[fill=gray!20] (0,0) rectangle (10.5,2);
-\path[fill=gray!50] (0,2) rectangle (10.5,4);
-\path[fill=gray!20] (0,4) rectangle (10.5,6);
-
-\draw (-0.3,1) node[rotate=90] {Level 1}
-      (-0.3,3) node[rotate=90] {Level 2}
-      (-0.3,5) node[rotate=90] {Level 3};
-
-\draw[->] (0,0) -- (11,0) node[anchor=north] {$t$};
-\draw[-|] (0,0) -- (0,6.5) node[anchor=east] {};
-% Us
-\draw[ultra thick, ->] (0,0) -- (1,2) -- (3,2) -- (4,4) -- (6,4) -- (7,6) --
-(9.5,6);
-\draw[ultra thick, dashed, ->] (3,2) -- (9.5,2);
-\draw[ultra thick, dashed, ->] (6,4) -- (9.5,4);
-
-\draw (11,1) node[align=left, anchor=west]{\scriptsize pre-cognitive\\\scriptsize anthropomorphism}; %label
-
-\draw (11,3) node[align=left, anchor=west] {\scriptsize{projection of existing}\\\scriptsize{mental models}\\\scriptsize{\it (familiarity)}}; %label
-
-\draw (11,5) node[align=left, anchor=west] {\scriptsize{adapted mental
-model} \\ $\to$ \scriptsize{adapted interaction}\\\scriptsize{\it (anthropomorphic or not)}}; %label
-
-\draw[dashed,->] (1,0.1) to[bend right] (2,1.9)  node at (4.5,1) {\tiny{\it observation (shape, motion, sound)}}; %label
-
-\draw[dashed,->] (4,2.1) to[bend right] (5,3.9)  node[align=left] at (7.5,3) {\tiny \it observation (interactive behavior) \\ \tiny \it or short interaction}; %label
-
-\draw[dashed,->] (7,4.1) to[bend right] (8,5.9)  node[align=left] at (9,5)
-{\tiny \it contextualized\\ \tiny \it interaction}; %label
-
-\end{tikzpicture}
-%}
-\caption{The three cognitive levels of anthropomorphism: Level 1 is the instinctive,
-sub-cognitive identification of living peers. {\it Empathy} is characteristic
-of this stage. After longer observation or short, non-contextualized interaction
-(typically, a lab environment), the user reaches Level 2: the user projects a
-mental model he/she is already familiar with onto the robot. After longer {\it
-contextualized} interaction (typically, at home), the user enters Level 3 of
-anthropomorphism: the user recomposes an accurate mental model of the robot,
-based on experience. This leads to adapted interaction modalities, that may
-still be anthropomorphic, or not.}
-\label{fig:cognitivemodel}
-\end{figure}
+%\begin{figure}[htb]
+%\centering
+%%\resizebox{\linewidth}{!}{
+%\begin{tikzpicture}
+%\baselineskip=8pt
+%
+%\path[fill=gray!20] (0,0) rectangle (10.5,2);
+%\path[fill=gray!50] (0,2) rectangle (10.5,4);
+%\path[fill=gray!20] (0,4) rectangle (10.5,6);
+%
+%\draw (-0.3,1) node[rotate=90] {Level 1}
+%      (-0.3,3) node[rotate=90] {Level 2}
+%      (-0.3,5) node[rotate=90] {Level 3};
+%
+%\draw[->] (0,0) -- (11,0) node[anchor=north] {$t$};
+%\draw[-|] (0,0) -- (0,6.5) node[anchor=east] {};
+%% Us
+%\draw[ultra thick, ->] (0,0) -- (1,2) -- (3,2) -- (4,4) -- (6,4) -- (7,6) --
+%(9.5,6);
+%\draw[ultra thick, dashed, ->] (3,2) -- (9.5,2);
+%\draw[ultra thick, dashed, ->] (6,4) -- (9.5,4);
+%
+%\draw (11,1) node[align=left, anchor=west]{\scriptsize pre-cognitive\\\scriptsize anthropomorphism}; %label
+%
+%\draw (11,3) node[align=left, anchor=west] {\scriptsize{projection of existing}\\\scriptsize{mental models}\\\scriptsize{\it (familiarity)}}; %label
+%
+%\draw (11,5) node[align=left, anchor=west] {\scriptsize{adapted mental
+%model} \\ $\to$ \scriptsize{adapted interaction}\\\scriptsize{\it (anthropomorphic or not)}}; %label
+%
+%
+%\draw[dashed,->] (1,0.1) to[bend right] (2,1.9)  node at (4.5,1) {\tiny{\it observation (shape, motion, sound)}}; %label
+%
+%\draw[dashed,->] (4,2.1) to[bend right] (5,3.9)  node[align=left] at (7.5,3) {\tiny \it observation (interactive behavior) \\ \tiny \it or short interaction}; %label
+%
+%\draw[dashed,->] (7,4.1) to[bend right] (8,5.9)  node[align=left] at (9,5)
+%{\tiny \it contextualized\\ \tiny \it interaction}; %label
+%
+%\end{tikzpicture}
+%%}
+%\caption{The three cognitive levels of anthropomorphism: Level 1 is the instinctive,
+%sub-cognitive identification of living peers. {\it Empathy} is characteristic
+%of this stage. After longer observation or short, non-contextualized interaction
+%(typically, a lab environment), the user reaches Level 2: the user projects a
+%mental model he/she is already familiar with onto the robot. After longer {\it
+%contextualized} interaction (typically, at home), the user enters Level 3 of
+%anthropomorphism: the user recomposes an accurate mental model of the robot,
+%based on experience. This leads to adapted interaction modalities, that may
+%still be anthropomorphic, or not.}
+%\label{fig:cognitivemodel}
+%\end{figure}
 
@@
 
-\begin{itemize}
-    \item \textbf{Hypothesis 1} A person's tendency to anthropomorphize a robot
-        is impacted by the context of use and purpose of the robot. A social
-        context and purpose of the robot increases anthropomorphism.
-        \textit{(context and purpose of the robot)}
-	\item \textbf{Hypothesis 2} A person's tendency to anthropomorphize a robot decreases over time and with growing experience the person has with the robot.
-\textit{(familiarize oneself with the robot)}
-\end{itemize}
-
 \subsection{Impact of the behavioral complexity of robots}
@@
 \subsection{Measuring anthropomorphism}
-\label{measuring}
 
@@
 
+Our data suggest that there are qualitative differences and dynamics over time
+in how humans relate to different types of robots. More concretely, we found
+that people's perception of human-likeness in the robot and in turn their
+human-social engagement with the robot was not only based on how much the robot
+resembled a human (mostly in its behavioral cues) but that this was determined
+by multiple factors, including individual characteristics of the human user but
+also the context of use, for instance. Interestingly, our findings also suggest
+that how far people anthropomorphize a robot is likely to change over time with
+growing experience of the user with the system.
+
+Based on these observations and an extensive literature review, we would like to
+propose a model that accounts for variances and dynamics in anthropomorphism.
+This model of the \textit{``Dynamics of Anthropomorphism''} considers several
+impact factors, including the human user, the anthropomorphic design of the
+non-human agent, the context of use, and the interaction experience (time). With
+this initial model, we would like to extend the current understanding of
+anthropomorphism in robotics and human-robot interaction. This might in turn
+lead to a discussion about the short- and long-term benefits and other effects
+of the human-like (anthropomorphic) design of robots and other artificial
+agents.
+
 Anthropomorphism is a social phenomenon which seems to be natural on one side

### 2014-03-24 paper.tex

@@
 \subsection{Towards a formal understanding of anthropomorphism}
+
+\fxnote{state here our main research hypothesis}
+\fxnote{state here our main contributions}
 
@@
 
+From the Roomba study, we can report on several findings related to
+anthropomorphism and the anthropomorphic design of robots.
 %The gathered data for these aspects include qualitative observations,
@@
 %aspects of human-robot interaction.
+The Roomba study is one of very few long-term human-robot interaction studies in
+the domestic environment.
+
+In the following, we present findings in respect of two aspects: First, we
+qualitatively describe what kinds of anthropomorphic interactions between
+participants and the robot were observed and outline how these interactions
+evolved over time.  Second, we present people's perception of human-likeness and
+social capabilities of the robot and how this perception changed over
+time.\footnote{\hl{note that these two different kinds of data
+(behavior/interaction and perception) already show that we try to measure
+anthropomorphism from these two angles!}}
 
@@
 
-%    \begin{tikzpicture}[scale=0.5, y = 2cm]
-%    %axis
-%    \draw (0,0) -- coordinate (x axis mid) (20,0);
-%    \draw (0,0) -- coordinate (y axis mid) (0,7);
-%    %ticks
-%    \foreach \x in {0,4,...,20}
-%        \draw (\x,1pt) -- (\x,-3pt);
-%    \foreach \y in {1,...,7} 
-%        \draw[black!20] (20,\y) -- (-3pt,\y);
-%    \foreach \y in {1,...,7} 
-%        \draw (-3pt, \y) node[anchor=east] {\y}; 
-%    %labels
-%    \node[below=0.8cm] at (x axis mid) {People's perception ($\sigma=15$)};
-%    \node at (2, -0.4) {\tiny expectations};
-%    \node[align=center] at (6, -0.4) {\tiny after\\ \tiny first usage};
-%    \node[align=center] at (10, -0.4) {\tiny after\\ \tiny 2 weeks};
-%    \node[align=center] at (14, -0.4) {\tiny after\\ \tiny 2 months};
-%    \node[align=center] at (18, -0.4) {\tiny after\\ \tiny 6 months};
-%
-%    \draw[dashed, black!50] (6,0) -- (6,7) node[sloped, below, pos=0.25] {\tiny novelty effect};
-%
-%    \draw[ultra thick, red!50] (2,5.6) -- (6,6.1) -- (10,6.3) -- (14,6.3) -- (18,6.1) node at (15,6.5) {\tiny \it ease of use};
-%    \draw[ultra thick, purple] (2,4.9) -- (6,5.2) -- (10,5.1) -- (14,4.5) -- (18,4.2) node at (3,4.7) {\tiny \it usefulness};
-%    \draw[ultra thick, blue!50] (2,4) -- (6,4.1) -- (10,4.6) -- (14,4.1) -- (18,4.3) node at (16,4) {\tiny \it fun};
-%    \draw[ultra thick, green!50] (2,3.9) -- (6,4.1) -- (10,4.2) -- (14,3.8) -- (18,3.3) node at (19,3.5) {\tiny \it intelligence};
-%    \draw[ultra thick, orange] (2,3.5) -- (6,4.2) -- (10,4) -- (14,3.2) -- (18,2.8) node at (14,2.7) {\tiny \it impact};
-%
-%    \draw[ultra thick, dashed] (2,5.2) -- (6,5.2) -- (10,5) -- (14,4.9) -- (18,4.5) node at (14,5.3) {\tiny \it overall};
-%
-%    \end{tikzpicture}
+    \begin{tikzpicture}[scale=0.5, y = 2cm]
+    %axis
+    \draw (0,0) -- coordinate (x axis mid) (20,0);
+    \draw (0,0) -- coordinate (y axis mid) (0,7);
+    %ticks
+    \foreach \x in {0,4,...,20}
+        \draw (\x,1pt) -- (\x,-3pt);
+    \foreach \y in {1,...,7} 
+        \draw[black!20] (20,\y) -- (-3pt,\y);
+    \foreach \y in {1,...,7} 
+        \draw (-3pt, \y) node[anchor=east] {\y}; 
+    %labels
+    \node[below=0.8cm] at (x axis mid) {People's perception ($\sigma=15$)};
+    \node at (2, -0.4) {\tiny expectations};
+    \node[align=center] at (6, -0.4) {\tiny after\\ \tiny first usage};
+    \node[align=center] at (10, -0.4) {\tiny after\\ \tiny 2 weeks};
+    \node[align=center] at (14, -0.4) {\tiny after\\ \tiny 2 months};
+    \node[align=center] at (18, -0.4) {\tiny after\\ \tiny 6 months};
+
+    \draw[dashed, black!50] (6,0) -- (6,7) node[sloped, below, pos=0.25] {\tiny novelty effect};
+
+    \draw[ultra thick, red!50] (2,5.6) -- (6,6.1) -- (10,6.3) -- (14,6.3) -- (18,6.1) node at (15,6.5) {\tiny \it ease of use};
+    \draw[ultra thick, purple] (2,4.9) -- (6,5.2) -- (10,5.1) -- (14,4.5) -- (18,4.2) node at (3,4.7) {\tiny \it usefulness};
+    \draw[ultra thick, blue!50] (2,4) -- (6,4.1) -- (10,4.6) -- (14,4.1) -- (18,4.3) node at (16,4) {\tiny \it fun};
+    \draw[ultra thick, green!50] (2,3.9) -- (6,4.1) -- (10,4.2) -- (14,3.8) -- (18,3.3) node at (19,3.5) {\tiny \it intelligence};
+    \draw[ultra thick, orange] (2,3.5) -- (6,4.2) -- (10,4) -- (14,3.2) -- (18,2.8) node at (14,2.7) {\tiny \it impact};
+
+    \draw[ultra thick, dashed] (2,5.2) -- (6,5.2) -- (10,5) -- (14,4.9) -- (18,4.5) node at (14,5.3) {\tiny \it overall};
+
+    \end{tikzpicture}
 
@@
 \subsection{Forum study: using anthropomorphic expressions to describe a robot}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.7\columnwidth]{aibo-roomba-ipad_2.jpg}
+    \caption{The Sony AIBO robotic dog (left), the iRobot Roomba vacuum-cleaning robot (middle), and the Apple Inc.
+iPad tablet computer (right) were compared in terms of how far users of these devices use anthropomorphic expressions in discussions about their technology / robot in online discussion forums.}
+    \label{fig:aibo-roomba-ipad}
+\end{figure}
 
@@
 \begin{enumerate}
+
     	\item People engage in a more social and human-like way with a robotic pet compared to a functional robot and a tablet computer, therefore there will be a higher amount of anthropomorphic language in the AIBO and Roomba forum, compared to the iPad forum.
@@
         stick''};
+
     \item \textit{Emotional states, empathy} or the technology having a
         \textit{feeling}, \eg \textit{``oh no, poor AIBO''};
+
     \item \textit{Gender, personality} or the technology having an
@@
         under the sofa''};
+
     \item When the author gave the technology a \textit{name}, \eg
         \textit{``whenever I show Java his pink ball''};
+
     \item Being \textit{socially integrated}, such as being a family member, \eg
         \textit{``I'm considering adding a Roomba to the family''};
+
     \item \textit{Metaphorical ways}, \eg Roomba \textit{``sings its victory
         song when it finishes and docks''}.
+
 \end{itemize}
@@
 
+Anthropomorphism as a social phenomenon arises in an interaction \citep{persson_anthropomorphism_2000}, and thus includes at least two interaction partners (the human and the real or imagined non-human agent).
+Therefore, one can take two main perspectives on explaining it \citep{lee_human_2005}: a human-centered, and an artifact-centered.
+We briefly outline both views in the following.
+It has to be kept in mind that both perspectives are inseparable; they apply at the same time, and we would like to present them here just as two different viewpoints on the same kind of phenomenon.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+%
+%
+%		HUMAN-CENTERED PERSPECTIVE: SOCIAL PHENOMENON
+%
+%
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{A human-centered perspective on anthropomorphism}
+
 The human-centered perspective builds on research from developmental and social psychology as well as cognitive sciences.
@@
 Thus, the motivation of being socially connected increases the tendency to anthropomorphize non-human agents because first sociality motivation increases the tendency to perceive human-like characteristics and traits even in non-human agents, and second it increases the tendency to search for sources of social connection in one's environment.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+%
+%
+%		ARTIFACT-CENTERED PERSPECTIVE: ANTHROPOMORPHIC DESIGN
+%
+%
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{An artifact-centered perspective on anthropomorphism}
+\label{sec:anthropomorphic-design}
 
@@
 
+%% -> Commented out the overview as it does not match what we actually present... maybe we need a new one?
+% We would further like to review and discuss research on anthropomorphism in
+% robotics and human-like design of robots. We first provide a comprehensive
+% understanding of the phenomenon drawing on theories from developmental
+% psychology and cognitive sciences. We then present the trends of different
+% kinds of anthropomorphic forms in robots and discuss their role in social
+% robotics. The article integrates related work from human-robot interaction
+% studies, reporting on findings from experiments with human subjects
+% interacting with and evaluating various types of systems. We try to give a
+% coherent view on the topic, outline similarities and antithetic findings, and
+% contribute to a better understanding of anthropomorphism in robotics, and the
+% acceptance of human-like characteristics in robots. We also aim to
+% constructively discuss anthropomorphic design of personal and socially
+% interactive robots.
+
+\subsection{Summary: Anthropomorphism as a multi-factor phenomenon}
+\label{sec:multi-factors}
+
 In this article we will use the term \emph{anthropomorphic effect} to denote
@@
 \end{figure}
+
+The notation \Ant[R,H,C,t] reflects these multiple factors: we suggest here that
+anthropomorphism is a function of a vector of robot's traits $R = \{r_0,...,r_n\}$, a vector human
+determinants $H = \{h_0,...,h_n\}$, a set of interaction situations that build a
+an interaction context $C = \{s_0,...,s_n\}$, and the duration of the
+interaction itself, $t$.
 
@@
 
-%\begin{figure*}[htb]
-%\centering
-%
-%
-%\begin{tikzpicture}[scale=1.2]
-%
-%% background shading
-%\path[fill=gray!20] (0,0) rectangle (0.6,5.5);
-%\path[fill=gray!50] (0.6,0) rectangle (5.2,5.5);
-%\path[fill=gray!20] (5.2,0) rectangle (9.8,5.5);
-%\draw(0,5.5) node[anchor=south west] {\scriptsize \sc Initialization};
-%\draw(4,5.5) node[anchor=south] {\scriptsize \sc Familiarization};
-%\draw(7.5,5.5) node[anchor=south] {\scriptsize \sc Stabilization};
-%% horizontal axis
-%\draw[->] (0,0) -- (10,0) node[anchor=north] {$t$};
-%\draw(5,-0.1) node[anchor=north] {\scriptsize Duration of interaction};
-%
-%
-%% vertical axis
-%\draw[->] (0,0) -- (0,6) node[anchor=east] {};
-%\draw(-0.8,3) node[rotate=90,anchor=south] {\scriptsize Normalized level of anthropomorphic effects};
-%
-%\draw (-0.05, 3) -- (0.05, 3) node[anchor=east] {\scriptsize ICA$_{\mathcal B}$};
-%\draw (-0.05, 4.1) -- (0.05, 4.1) node[anchor=east] {\scriptsize ICA$_{\mathcal A}$};
-%\draw (-0.05, 0.6) -- (0.05, 0.6) node[anchor=east] {\scriptsize ICA$_{\mathcal C}$};
-%
-%% vertical axis - end
-%\draw[->] (9.8,0) -- (9.8,2) node[anchor=east] {};
-%\draw (9.8, 0.8) node[anchor=west] {\scriptsize SLA$_\mathcal{E}$};
-%\draw (9.8, 1.4) node[anchor=west] {\scriptsize SLA$_\mathcal{D}$};
-%\draw (9.8, .2) node[anchor=west] {\scriptsize SLA$_\mathcal{F}$};
-%
-%
-%\draw[<-] (0.65,5) -- (0.8,5.2) node[anchor=east] {};
-%\draw (0.9,5.3) node[anchor=west] {\tiny \it novelty effect};
-%
-%
-%\draw[dotted] (0, 5) -- (6.2,5);
-%\draw[dotted] (0, 3) -- (6.2,3);
-%\draw[<->] (6.1,3) -- (6.1,5) node[anchor=east] {};
-%\draw (6.2,4) node[rotate=90, anchor=north] {\tiny Expectation mismatch};
-%
-%\draw[<-] (1.7,4.4) -- (3.2,4.1) node[anchor=east] {};
-%\draw[<-] (2.85,3.3) -- (3.2,4.1) node[anchor=east] {};
-%\draw (3.2,4.1) node[anchor=west] {\tiny \it disruptive behaviors};
-%%%%%%
-%%% CURVES
+\begin{figure*}[htb]
+\centering
+
+\begin{tikzpicture}[scale=1.4]
+
+% background shading
+\path[fill=blue!20] (0,0) rectangle (0.6,5.5);
+\path[fill=green!20] (0.6,0) rectangle (5.2,5.5);
+\path[fill=orange!20] (5.2,0) rectangle (9.8,5.5);
+\draw(0,5.5) node[anchor=south west, rotate=10] {\scriptsize \sc Initialization};
+\draw(2.5,5.5) node[anchor=south west, rotate=10] {\scriptsize \sc Familiarization};
+\draw(6.5,5.5) node[anchor=south west, rotate=10] {\scriptsize \sc Stabilization};
+% horizontal axis
+\draw[->] (0,0) -- (10,0) node[anchor=north] {$t$};
+\draw(5,-0.1) node[anchor=north] {\scriptsize Duration of interaction};
+
+% vertical axis
+\draw[->] (0,0) -- (0,6) node[anchor=east] {};
+\draw(-0.8,3) node[rotate=90,anchor=south] {\scriptsize Normalized level of anthropomorphic effects};
+
+\draw (-0.05, 3) -- (0.05, 3) node[anchor=east] {\ICA};
+\draw (-0.05, 5) -- (0.05, 5) node[anchor=east] {\AntMax};
+
+% vertical axis - end
+\draw[->] (9.8,0) -- (9.8,2) node[anchor=east] {};
+\draw (9.8, 0.8) node[anchor=west] {\SLA};
+
+\draw[<-] (0.65,5) -- (0.8,5.2) node[anchor=east] {};
+\draw (0.9,5.3) node[anchor=west] {\tiny \it novelty peak};
+
+\draw[dotted] (0, 5) -- (6.2,5);
+\draw[dotted] (0, 3) -- (6.2,3);
+\draw[<->] (6.1,3) -- (6.1,5) node[anchor=east] {};
+\draw (6.2,4) node[rotate=90, anchor=north, align=center] {\tiny Expectation\\\tiny mismatch};
+
+\draw[<-] (1.7,4.4) -- (3.2,4.1) node[anchor=east] {};
+\draw[<-] (2.85,2.6) -- (3.2,4.1) node[anchor=east] {};
+\draw (3.2,4.1) node[anchor=west, align=center] {\tiny \it disruptive\\ \tiny
+\it behaviors};
 %%%%%
-%\begin{scope}[yscale=-1,shift={(-0.125,-0.4)}]
-%
-%% output of inkscape2tikz
-%\path[draw=black]
-%    (0.1250,-2.5620) .. controls (0.1451,-3.7193) and (0.4645,-4.5602) ..
-%    (0.7044,-4.5633) .. controls (0.8413,-4.5633) and (0.9599,-4.5104) ..
-%    (1.0794,-4.3971) .. controls (1.1989,-4.2841) and (1.3191,-4.1185) ..
-%    (1.4588,-3.9181) .. controls (1.5287,-3.8183) and (1.5610,-4.1413) ..
-%    (1.6381,-4.1420) .. controls (1.7378,-4.1420) and (1.6515,-3.6434) ..
-%    (1.9554,-3.2280) .. controls (2.1466,-2.9667) and (2.3889,-2.7023) ..
-%    (2.6819,-2.4292) .. controls (2.7551,-2.3607) and (2.7727,-2.8119) ..
-%    (2.8771,-2.8180) .. controls (2.9742,-2.8180) and (2.9594,-2.2108) ..
-%    (3.1665,-2.0209) .. controls (3.3340,-1.8673) and (3.5379,-1.7527) ..
-%    (3.7508,-1.6236) .. controls (5.8366,-0.4852) and (8.0977,-0.2106) ..
-%    (10.1250,-0.1860);
-%\path[draw=black, dashed]
-%    (0.1250,-3.6924) .. controls (0.1103,-4.0298) and (0.4645,-4.5602) .. 
-%    (0.7044,-4.5633)
-%    (3.7508,-1.6236) .. controls (4.9579,-0.9555) and (8.1358,-0.8261) .. 
-%    (10.1250,-0.7946);
-%\path[draw=black,dashed]
-%    (0.1250,-0.1953) .. controls (0.1804,-3.3871) and (0.4645,-4.5602) .. 
-%    (0.7044,-4.5633) .. controls (0.8413,-4.5633) and (0.9599,-4.5104) .. 
-%    (1.0794,-4.3971)
-%    (3.7508,-1.6236) .. controls (4.7654,-0.8505) and (6.5955,0.3538) .. 
-%    (10.1250,0.4062);
-%
-%\end{scope}
-%
-%\end{tikzpicture}
-%
-%\caption{The dynamics of anthropomorphism. We distinguish three main phases:
-%    \emph{initialization}, \emph{familiarization} and \emph{stabilization},
-%    preceded by a \emph{pre-interaction} phase. In the pre-interaction phase,
-%    users build an \emph{initial capital of anthropomorphism} (ICA). Once the
-%    interaction starts, the level of anthropomorphism increases due to the
-%    \emph{novelty effect}~\cite{kanda_interactive_2004}, and then decreases to
-%    reach a \emph{stabilized level of anthropomorphism} (SLA).  During the
-%    interaction, unpredicted behaviors of the robot (\emph{disruptive behaviors})
-%    may lead to local increase of the level of anthropomorphism.}
-%
-%\label{fig:dynamics}
-%\end{figure*}
+%% CURVES
+%%%%
+\begin{scope}[yscale=-1,shift={(-0.125,-0.4)}]
+
+    \draw[ultra thick] svg[scale=1cm] "M 0.125,-2.5619582 c 0.0200733,-1.1573591
+    0.33954391,-1.9982333 0.57940683,-2.0013597 0.13691605,0 0.25550329,0.052908
+    0.37497897,0.1661788 0.119476,0.1130305 0.2396954,0.2786079
+    0.37944,0.4790565 0.069872,0.099803 0.1021612,-0.2231749
+    0.1792538,-0.2238964 0.099707,0 0.013454,0.4985362 0.3173383,0.9139831
+    0.1911917,0.2612926 0.3444354,0.2578391 0.6711932,0.4894291
+    0.2058265,0.1458798 0.1571532,0.9762306 0.2615031,0.9702183 0.097182,0
+    0.083295,-0.3336208 0.4330446,-0.1199242 0.4306401,0.2631203
+    0.216699,0.1355642 0.4296663,0.2647074 2.0858202,1.13836043
+    4.34683,1.41300027 6.3741749,1.43753027";
+
+    \draw[dashed] svg[scale=1cm] "M 0.125,-0.1952939 c 0.0553601,-3.1917862
+    0.33954391,-4.3648976 0.57940683,-4.368024 0.13691605,0 0.25550329,0.052908
+    0.37497897,0.1661788 m 2.6714393,2.7735737 C 4.7653984,-0.85050947
+    6.5955093,0.35382293 10.125,0.4062498";
+
+    \draw[dashed] svg[scale=1cm] "M 0.125,-3.6923825 C 0.1102888,-4.0297903
+    0.46454391,-4.5601915 0.70440683,-4.5633179 M 3.7508251,-1.6235654 C
+    4.9579368,-0.95548345 8.1358175,-0.82609971 10.125,-0.79459549";
+
+\end{scope}
+
+\end{tikzpicture}
+
+\caption{The dynamics of anthropomorphism. We distinguish three main phases:
+    \emph{initialization}, \emph{familiarization} and \emph{stabilization},
+    preceded by a \emph{pre-interaction} phase. In the pre-interaction phase,
+    users build an \emph{initial capital of anthropomorphism} (ICA, noted \ICA).
+    Once the interaction starts, the level of anthropomorphism increases due to
+    the \emph{novelty effect}, and then decreases to reach a \emph{stabilized
+    level of anthropomorphism} (SLA, noted \SLA). \ICA and \SLA may vary
+    depending on the user, the robot and the context of interaction.  During the
+    interaction, unpredicted behaviors of the robot (\emph{disruptive
+    behaviors}) may lead to local increases or decreases of the level of
+    anthropomorphism.}
+
+\label{fig:dynamics}
+\end{figure*}
 
@@
 
-%\begin{figure}[htb]
-%\centering
-%%\resizebox{\linewidth}{!}{
-%\begin{tikzpicture}
-%\baselineskip=8pt
-%
-%\path[fill=gray!20] (0,0) rectangle (10.5,2);
-%\path[fill=gray!50] (0,2) rectangle (10.5,4);
-%\path[fill=gray!20] (0,4) rectangle (10.5,6);
-%
-%\draw (-0.3,1) node[rotate=90] {Level 1}
-%      (-0.3,3) node[rotate=90] {Level 2}
-%      (-0.3,5) node[rotate=90] {Level 3};
-%
-%\draw[->] (0,0) -- (11,0) node[anchor=north] {$t$};
-%\draw[-|] (0,0) -- (0,6.5) node[anchor=east] {};
-%% Us
-%\draw[ultra thick, ->] (0,0) -- (1,2) -- (3,2) -- (4,4) -- (6,4) -- (7,6) --
-%(9.5,6);
-%\draw[ultra thick, dashed, ->] (3,2) -- (9.5,2);
-%\draw[ultra thick, dashed, ->] (6,4) -- (9.5,4);
-%
-%\draw (11,1) node[align=left, anchor=west]{\scriptsize pre-cognitive\\\scriptsize anthropomorphism}; %label
-%
-%\draw (11,3) node[align=left, anchor=west] {\scriptsize{projection of existing}\\\scriptsize{mental models}\\\scriptsize{\it (familiarity)}}; %label
-%
-%\draw (11,5) node[align=left, anchor=west] {\scriptsize{adapted mental
-%model} \\ $\to$ \scriptsize{adapted interaction}\\\scriptsize{\it (anthropomorphic or not)}}; %label
-%
-%
-%\draw[dashed,->] (1,0.1) to[bend right] (2,1.9)  node at (4.5,1) {\tiny{\it observation (shape, motion, sound)}}; %label
-%
-%\draw[dashed,->] (4,2.1) to[bend right] (5,3.9)  node[align=left] at (7.5,3) {\tiny \it observation (interactive behavior) \\ \tiny \it or short interaction}; %label
-%
-%\draw[dashed,->] (7,4.1) to[bend right] (8,5.9)  node[align=left] at (9,5)
-%{\tiny \it contextualized\\ \tiny \it interaction}; %label
-%
-%\end{tikzpicture}
-%%}
-%\caption{The three cognitive levels of anthropomorphism: Level 1 is the instinctive,
-%sub-cognitive identification of living peers. {\it Empathy} is characteristic
-%of this stage. After longer observation or short, non-contextualized interaction
-%(typically, a lab environment), the user reaches Level 2: the user projects a
-%mental model he/she is already familiar with onto the robot. After longer {\it
-%contextualized} interaction (typically, at home), the user enters Level 3 of
-%anthropomorphism: the user recomposes an accurate mental model of the robot,
-%based on experience. This leads to adapted interaction modalities, that may
-%still be anthropomorphic, or not.}
-%\label{fig:cognitivemodel}
-%\end{figure}
+\begin{figure}[htb]
+\centering
+%\resizebox{\linewidth}{!}{
+\begin{tikzpicture}
+\baselineskip=8pt
+
+\path[fill=gray!20] (0,0) rectangle (10.5,2);
+\path[fill=gray!50] (0,2) rectangle (10.5,4);
+\path[fill=gray!20] (0,4) rectangle (10.5,6);
+
+\draw (-0.3,1) node[rotate=90] {Level 1}
+      (-0.3,3) node[rotate=90] {Level 2}
+      (-0.3,5) node[rotate=90] {Level 3};
+
+\draw[->] (0,0) -- (11,0) node[anchor=north] {$t$};
+\draw[-|] (0,0) -- (0,6.5) node[anchor=east] {};
+% Us
+\draw[ultra thick, ->] (0,0) -- (1,2) -- (3,2) -- (4,4) -- (6,4) -- (7,6) --
+(9.5,6);
+\draw[ultra thick, dashed, ->] (3,2) -- (9.5,2);
+\draw[ultra thick, dashed, ->] (6,4) -- (9.5,4);
+
+\draw (11,1) node[align=left, anchor=west]{\scriptsize pre-cognitive\\\scriptsize anthropomorphism}; %label
+
+\draw (11,3) node[align=left, anchor=west] {\scriptsize{projection of existing}\\\scriptsize{mental models}\\\scriptsize{\it (familiarity)}}; %label
+
+\draw (11,5) node[align=left, anchor=west] {\scriptsize{adapted mental
+model} \\ $\to$ \scriptsize{adapted interaction}\\\scriptsize{\it (anthropomorphic or not)}}; %label
+
+\draw[dashed,->] (1,0.1) to[bend right] (2,1.9)  node at (4.5,1) {\tiny{\it observation (shape, motion, sound)}}; %label
+
+\draw[dashed,->] (4,2.1) to[bend right] (5,3.9)  node[align=left] at (7.5,3) {\tiny \it observation (interactive behavior) \\ \tiny \it or short interaction}; %label
+
+\draw[dashed,->] (7,4.1) to[bend right] (8,5.9)  node[align=left] at (9,5)
+{\tiny \it contextualized\\ \tiny \it interaction}; %label
+
+\end{tikzpicture}
+%}
+\caption{The three cognitive levels of anthropomorphism: Level 1 is the instinctive,
+sub-cognitive identification of living peers. {\it Empathy} is characteristic
+of this stage. After longer observation or short, non-contextualized interaction
+(typically, a lab environment), the user reaches Level 2: the user projects a
+mental model he/she is already familiar with onto the robot. After longer {\it
+contextualized} interaction (typically, at home), the user enters Level 3 of
+anthropomorphism: the user recomposes an accurate mental model of the robot,
+based on experience. This leads to adapted interaction modalities, that may
+still be anthropomorphic, or not.}
+\label{fig:cognitivemodel}
+\end{figure}
 
@@
 
-\paragraph{Limits} This discussion on the cognitive correlates of the dynamics
-of anthropomorphism are speculative, and only indirectly supported by
-experimental evidence. New experiences need to be designed to specifically test
-these hypothesis.\fxnote{...}
-
-\subsection{Impact of the behavioral complexity of robots}
-
-TBD. Most experiments are carried with robots exhibiting relatively simple
-behaviors. In our model, the maximum level of anthropomorphism is reached with
-the novelty effect, and then decrease. Can we go \emph{over} the novelty effect
-if the robot exhibit more complex behaviors?
-
-\subsection{Segmentation of interaction phases}
-
-TBD
-
-\subsection{Behavioral cues of anthropomorphism}
-\label{sec:behavioralcues}
-
-Our model suggests to analyze anthropomorphism based on a \emph{relative and
-normalized level of anthropomorphic effects} instead of an absolute
-quantitative assessment of anthropomorphic evidences. Similarly we introduce
-two specific \emph{abstract} levels of anthropomorphism, the \emph{Initial
-Capital of Anthropomorphism} and the \emph{Stabilized Level of
-Anthropomorphism}: while we discuss the factors on which those values are
-build, we did not formally investigated the experimental cues or evidences
-that would allow to actually quantify those levels.
-
-The intricacy and interdependency of those behaviors make them difficult to
-quantify.  Their systematic identification and interpretation rely on
-psychosomatic cues that the authors did not investigate.
-
-A formal methodology for the assessment of anthropomorphic effects in HRI, as
-well as a typology of these effects is still to be formally devised.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+%
+%
+%				DISCUSSION + FUTURE WORK
+%
+%
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% JULIA & SEVERIN: how to measure / quantify anthropomorphism ...
+% CLAIRE: FMRI study idea
+
+\section{Discussion}
+\label{sec:discussion}
+
+The model of anthropomorphism we propose is still a work in progress. In
+particular, its implications regarding the design of (social) robots and
+human-robot interaction are still to be refined.
 
 \subsection{Effect of Time and Familiarization}
+
+\fixme{Discuss here the general findings of the paper: the global shape of the
+model of the dynamics, ...}
 
@@
 \begin{itemize}
+    \item \textbf{Hypothesis 1} A person's tendency to anthropomorphize a robot
+        is impacted by the context of use and purpose of the robot. A social
+        context and purpose of the robot increases anthropomorphism.
+        \textit{(context and purpose of the robot)}
 	\item \textbf{Hypothesis 2} A person's tendency to anthropomorphize a robot decreases over time and with growing experience the person has with the robot.

### 2014-03-24 paper.tex
tried to do the merging ... not sure everything went fine :)

@@
 
-Figure~\ref{roomba-perception} gives a first perspective on how naive
+Figure~\ref{fig:roomba-perception} gives a first perspective on how naive
 users perceive robots over a long period of time. Here, \emph{Roomba} vacuum cleaning robots
@@
 their perception of different features of the robot on a 7-point rating scale. As
-Figure~\ref{roomba-perception} shows, some features remained stable over time
+Figure~\ref{fig:roomba-perception} shows, some features remained stable over time
 (\emph{ease of use} and \emph{fun}), and others decreased: the perceived
@@
 \subsection{Towards a formal understanding of anthropomorphism}
-
-\fxnote{state here our main research hypothesis}
-\fxnote{state here our main contributions}
 
@@
 
-From the Roomba study, we can report on several findings related to
-anthropomorphism and the anthropomorphic design of robots.
-%The gathered data for these aspects include qualitative observations,
-%semi-structured interviews, and also quantitative assessments of various
-%aspects of human-robot interaction.
-The Roomba study is one of very few long-term human-robot interaction studies in
-the domestic environment.
-
-In the following, we present findings in respect of two aspects: First, we
-qualitatively describe what kinds of anthropomorphic interactions between
-participants and the robot were observed and outline how these interactions
-evolved over time.  Second, we present people's perception of human-likeness and
-social capabilities of the robot and how this perception changed over
-time.\footnote{\hl{note that these two different kinds of data
-(behavior/interaction and perception) already show that we try to measure
-anthropomorphism from these two angles!}}
-
 \subsubsection{Anthropomorphic interactions with the robot\\}
@@
 
-    \begin{tikzpicture}[scale=0.5, y = 2cm]
-    %axis
-    \draw (0,0) -- coordinate (x axis mid) (20,0);
-    \draw (0,0) -- coordinate (y axis mid) (0,7);
-    %ticks
-    \foreach \x in {0,4,...,20}
-        \draw (\x,1pt) -- (\x,-3pt);
-    \foreach \y in {1,...,7} 
-        \draw[black!20] (20,\y) -- (-3pt,\y);
-    \foreach \y in {1,...,7} 
-        \draw (-3pt, \y) node[anchor=east] {\y}; 
-    %labels
-    \node[below=0.8cm] at (x axis mid) {People's perception ($\sigma=15$)};
-    \node at (2, -0.4) {\tiny expectations};
-    \node[align=center] at (6, -0.4) {\tiny after\\ \tiny first usage};
-    \node[align=center] at (10, -0.4) {\tiny after\\ \tiny 2 weeks};
-    \node[align=center] at (14, -0.4) {\tiny after\\ \tiny 2 months};
-    \node[align=center] at (18, -0.4) {\tiny after\\ \tiny 6 months};
-
-    \draw[dashed, black!50] (6,0) -- (6,7) node[sloped, below, pos=0.25] {\tiny novelty effect};
-
-    \draw[ultra thick, red!50] (2,5.6) -- (6,6.1) -- (10,6.3) -- (14,6.3) -- (18,6.1) node at (15,6.5) {\tiny \it ease of use};
-    \draw[ultra thick, purple] (2,4.9) -- (6,5.2) -- (10,5.1) -- (14,4.5) -- (18,4.2) node at (3,4.7) {\tiny \it usefulness};
-    \draw[ultra thick, blue!50] (2,4) -- (6,4.1) -- (10,4.6) -- (14,4.1) -- (18,4.3) node at (16,4) {\tiny \it fun};
-    \draw[ultra thick, green!50] (2,3.9) -- (6,4.1) -- (10,4.2) -- (14,3.8) -- (18,3.3) node at (19,3.5) {\tiny \it intelligence};
-    \draw[ultra thick, orange] (2,3.5) -- (6,4.2) -- (10,4) -- (14,3.2) -- (18,2.8) node at (14,2.7) {\tiny \it impact};
-
-    \draw[ultra thick, dashed] (2,5.2) -- (6,5.2) -- (10,5) -- (14,4.9) -- (18,4.5) node at (14,5.3) {\tiny \it overall};
-
-    \end{tikzpicture}
+%    \begin{tikzpicture}[scale=0.5, y = 2cm]
+%    %axis
+%    \draw (0,0) -- coordinate (x axis mid) (20,0);
+%    \draw (0,0) -- coordinate (y axis mid) (0,7);
+%    %ticks
+%    \foreach \x in {0,4,...,20}
+%        \draw (\x,1pt) -- (\x,-3pt);
+%    \foreach \y in {1,...,7} 
+%        \draw[black!20] (20,\y) -- (-3pt,\y);
+%    \foreach \y in {1,...,7} 
+%        \draw (-3pt, \y) node[anchor=east] {\y}; 
+%    %labels
+%    \node[below=0.8cm] at (x axis mid) {People's perception (n = 15)};
+%    \node at (2, -0.4) {\tiny expectations};
+%    \node[align=center] at (6, -0.4) {\tiny after\\ \tiny first usage};
+%    \node[align=center] at (10, -0.4) {\tiny after\\ \tiny 2 weeks};
+%    \node[align=center] at (14, -0.4) {\tiny after\\ \tiny 2 months};
+%    \node[align=center] at (18, -0.4) {\tiny after\\ \tiny 6 months};
+%
+%    \draw[dashed, black!50] (6,0) -- (6,7) node[sloped, below, pos=0.25] {\tiny novelty effect};
+%
+%    \draw[ultra thick, red!50] (2,5.6) -- (6,6.1) -- (10,6.3) -- (14,6.3) -- (18,6.1) node at (15,6.5) {\tiny \it ease of use};
+%    \draw[ultra thick, purple] (2,4.9) -- (6,5.2) -- (10,5.1) -- (14,4.5) -- (18,4.2) node at (3,4.7) {\tiny \it usefulness};
+%    \draw[ultra thick, blue!50] (2,4) -- (6,4.1) -- (10,4.6) -- (14,4.1) -- (18,4.3) node at (16,4) {\tiny \it fun};
+%    \draw[ultra thick, green!50] (2,3.9) -- (6,4.1) -- (10,4.2) -- (14,3.8) -- (18,3.3) node at (19,3.5) {\tiny \it intelligence};
+%    \draw[ultra thick, orange] (2,3.5) -- (6,4.2) -- (10,4) -- (14,3.2) -- (18,2.8) node at (14,2.7) {\tiny \it impact};
+%
+%    \draw[ultra thick, dashed] (2,5.2) -- (6,5.2) -- (10,5) -- (14,4.9) -- (18,4.5) node at (14,5.3) {\tiny \it overall};
+%
+%    \end{tikzpicture}
 
@@
 effects, both reflected in interaction with and perception of the robot.
-However, most of the anthropomorphic effects did not last long. \hl{One fairly
+However, most of the anthropomorphic effects did not last long. One fairly
 stable human-like interaction with the robot was \textit{talking to the robot},
 despite the fact that the robot was not able to recognize and respond to verbal
-statements.\footnote{important! I think I've seen that finding somewhere else
-when comparing ASIMO to AIBO or so.}}
+statements.
 
@@
 
-\begin{figure}
-    \centering
-    \includegraphics[width=0.7\columnwidth]{aibo-roomba-ipad_2.jpg}
-    \caption{The Sony AIBO robotic dog (left), the iRobot Roomba vacuum-cleaning robot (middle), and the Apple Inc.
+%\begin{figure}
+%    \centering
+%    \includegraphics[width=0.7\columnwidth]{aibo-roomba-ipad_2.jpg}
+%    \caption{The Sony AIBO robotic dog (left), the iRobot Roomba vacuum-cleaning robot (middle), and the Apple Inc.
 iPad tablet computer (right) were compared in terms of how far users of these devices use anthropomorphic expressions in discussions about their technology / robot in online discussion forums.}
-    \label{fig:aibo-roomba-ipad}
-\end{figure}
+%    \label{fig:aibo-roomba-ipad}
+%\end{figure}
 
@@
 \begin{enumerate}
-
     	\item People engage in a more social and human-like way with a robotic pet compared to a functional robot and a tablet computer, therefore there will be a higher amount of anthropomorphic language in the AIBO and Roomba forum, compared to the iPad forum.
-
     	\item As anthropomorphism can be seen as a certain kind of emotional / social relation to an artifact, there will be more anthropomorphic language in forum posts in which the author describes a relation to the device, compared to discussing technological aspects or how the device is used.
@@
         stick''};
-
     \item \textit{Emotional states, empathy} or the technology having a
         \textit{feeling}, \eg \textit{``oh no, poor AIBO''};
-
     \item \textit{Gender, personality} or the technology having an
@@
         under the sofa''};
-
     \item When the author gave the technology a \textit{name}, \eg
         \textit{``whenever I show Java his pink ball''};
-
     \item Being \textit{socially integrated}, such as being a family member, \eg
         \textit{``I'm considering adding a Roomba to the family''};
-
     \item \textit{Metaphorical ways}, \eg Roomba \textit{``sings its victory
         song when it finishes and docks''}.
-
 \end{itemize}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-%
-%
-%		WHY DO PEOPLE ANTHROPOMORPHIZE?
-%
-%
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \subsubsection{Why do people anthropomorphize?\\}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-%
-%
-%		HUMAN-CENTERED PERSPECTIVE: SOCIAL PHENOMENON
-%
-%
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{A human-centered perspective on anthropomorphism}
-
 The human-centered perspective builds on research from developmental and social psychology as well as cognitive sciences.
@@
 
-\paragraph*{Developmental psychology research on the attribution of animacy and intention\\ \\}
+\paragraph*{Developmental psychology research on the attribution of animacy and intention\\}
 
@@
 
-\paragraph*{Cognitive science research and the mental model theory (Theory of Mind)\\ \\}
+\paragraph*{Cognitive science research and the mental model theory (Theory of Mind)\\}
 
@@
 
-\paragraph*{Social psychology research: a 3-factor theory of anthropomorphism\\ \\}
+\paragraph*{Social psychology research: a 3-factor theory of anthropomorphism\\}
 \label{sec:psychological-factors}
@@
 %
-%		ARTIFACT-CENTERED PERSPECTIVE: ANTHROPOMORPHIC DESIGN
+%		ANTHROPOMORPHISM AS A MULTI-FACTOR PHENOMENON
 %
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{An artifact-centered perspective on anthropomorphism}
-\label{sec:anthropomorphic-design}
 
@@
 
-\subsection{Summary: Anthropomorphism as a multi-factor phenomenon}
-\label{sec:multi-factors}
-
 In this article we will use the term \emph{anthropomorphic effect} to denote
@@
 
-\paragraph{Why is anthropomorphism likely to change over time?}
-\hl{maybe we need to move this paragraph to PART 3}
-
-\subsection{A Model of the Dynamics of Anthropomorphism}
-
 The phenomenological model of anthropomorphism we propose

### 2014-03-24 paper.tex
fine tuning after merging

--- 2014-03-24 paper.tex
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% JULIA: brief problem definition / issue, motivation, objectives, contribution ...
 
@@
 
-\begin{figure}[hb]
+\begin{figure}
     \centering
@@
 
-\begin{figure}[b]
+\begin{figure}
     \centering
-    \includegraphics[width=0.5\columnwidth]{roomba-perception.pdf}
+%    \includegraphics[width=0.5\columnwidth]{roomba-perception.pdf}
 
@@
     %labels
-    \node[below=0.8cm] at (x axis mid) {People's perception ($\sigma=15$)};
+    \node[below=0.8cm] at (x axis mid) {People's perception (n = 15)};
     \node at (2, -0.4) {\tiny expectations};
@@
 effects, both reflected in interaction with and perception of the robot.
-However, most of the anthropomorphic effects did not last long. \hl{One fairly
+However, most of the anthropomorphic effects did not last long. One fairly
 stable human-like interaction with the robot was \textit{talking to the robot},
 despite the fact that the robot was not able to recognize and respond to verbal
-statements.\footnote{important! I think I've seen that finding somewhere else
-when comparing ASIMO to AIBO or so.}}
+statements.
 
 \subsection{Forum study: using anthropomorphic expressions to describe a robot}
-
-\begin{figure}
-    \centering
-    \includegraphics[width=0.7\columnwidth]{aibo-roomba-ipad_2.jpg}
-    \caption{The Sony AIBO robotic dog (left), the iRobot Roomba vacuum-cleaning robot (middle), and the Apple Inc.
-iPad tablet computer (right) were compared in terms of how far users of these devices use anthropomorphic expressions in discussions about their technology / robot in online discussion forums.}
-    \label{fig:aibo-roomba-ipad}
-\end{figure}
 
@@
 
-\begin{figure}[b]
+\begin{figure}
     \centering
@@
     \caption{The Sony AIBO robotic dog (left), the iRobot Roomba vacuum-cleaning robot (middle), and the Apple Inc.
-iPad tablet computer (right) were compared in terms of how far users of these devices use anthropomorphic expressions in discussions about their technology / robot in online discussion forums.}
+iPad tablet computer (right) were compared in terms of how far users of these devices use anthropomorphic expressions in online discussion forums about their technology / robot.}
     \label{fig:aibo-roomba-ipad}
@@
 people's tendency to use anthropomorphic language, originating form the design
-characteristics of the artifact. Interestingly, not only the physical embodiment
+characteristics of the artifact. A pet-like robot encourages people to use more 
+anthropomorphic expressions when discussing about it in an online forum. However, 
+the difference might also be related to other factors that we did not analyze 
+here (\eg. author's characteristics). Our analysis further shows that the design 
+of the robot seems to more important than the topic of the discussion. 
+Interestingly, not only the physical embodiment
 of the object but also the interaction complexity and purpose of use of the
@@
 which is anthropomorphized. Though commonly observed, it appears controversial, at 
-the same time, that humans tend to \hl{\textit{``see human in the non-
-human''}}. 
+the same time, that humans tend to \textit{``see human in the non-
+human''} \citep{epley_seeing_2007}. 
 Anthropomorphism as a social phenomenon arises in an interaction 
@@
 
-More concretely, it has been found that the appearance and function of a impacts how people perceive it, interact with it, and build long-term relations with it \cite{bartneck_shaping_2004}.
-Consequently, the domain of (social) robotics tries to exploit this fact by enhancing anthropomorphism through anthropomorphic robots: \textit{"Applying anthropomorphism or zoomorphism changes the way how users try to understand and make sense of a [system] by projecting everyday \hl{expectations} of human and animalistic life onto it."} \cite{schmitz_concepts_2011}\fxfatal{paragraph a bit
-confusing...}.
+The domain of (social) robotics tries to exploit this fact by enhancing anthropomorphism through anthropomorphic robots: \textit{"Applying anthropomorphism or zoomorphism changes the way how users try to understand and make sense of a [system] by projecting everyday \hl{expectations} of human and animalistic life onto it."} \cite{schmitz_concepts_2011}.
 

### 2014-03-25 paper.tex
minor refinements, figures side by side

--- 2014-03-24 paper.tex
@@
 \usepackage{textcomp}
+
+\usepackage{caption}
+\usepackage{subcaption}
+\usepackage{float}
+\floatstyle{plaintop}
 
@@
 
-\begin{figure}[hb]
+%\begin{figure}
+%    \centering
+%    \includegraphics[width=0.5\columnwidth]{roomba-activities.png}
+%    \caption{Activities with the robot over time, n = 9 households. This bar
+%        chart shows how many of the 9 households carried out different kinds of
+%        anthropomorphic / social activities with and related to the robot at 3
+%        time points during 6 months. Activities include \texttt{watching} the
+%        robot for fun, giving a \texttt{demo} of the robot to guests / visitors,
+%        \texttt{personalizing} the robot, giving a \texttt{name} to the robot,
+%        \texttt{talking} to the robot, \texttt{playing} with the robot.
+%        Participants were asked to report on these activities at 3 time points
+%        after the robot was deployed in their home: after 2 weeks, after 2 months,
+%        and after 6 months.} 
+%
+%\label{fig:roomba-activities}
+%\end{figure}
+
+\begin{figure}
         \centering
-    \includegraphics[width=0.5\columnwidth]{roomba-activities.png}
-    \caption{Activities with the robot over time, n = 9 households. This bar
+        \begin{subfigure}[b]{0.48\columnwidth}
+                \includegraphics[width=\textwidth]{roomba-activities.png}
+                \caption{Roomba activities}
+                \label{fig:roomba-activities}
+        \end{subfigure}%
+        ~ %add desired spacing between images, e. g. ~, \quad, \qquad etc.
+          %(or a blank line to force the subfigure onto a new line)
+        \begin{subfigure}[b]{0.48\columnwidth}
+                \includegraphics[width=\textwidth]{roomba-perception.pdf}
+                \caption{Roomba perception}
+                \label{fig:roomba-perception}
+        \end{subfigure}
+        \caption{\textbf{The Roomba study: Long-term interaction with a robot.\\}
+    \textbf{a)} Activities with the robot over time, n = 9 households. This bar
         chart shows how many of the 9 households carried out different kinds of
@@
         after the robot was deployed in their home: after 2 weeks, after 2 months,
-        and after 6 months.}
-
-\label{fig:roomba-activities}
+        and after 6 months.\\
+	\textbf{b)} People's perception of the robot over time, n = 15 participants.
+    		This line chart shows how people's perception of the robot evolves over
+    		time. At 5 time points people were asked to rate the robot according to the
+    		following aspects: the perceived \texttt{intelligence} of the robot, the
+    		perceived \texttt{usefulness}, the perceived \texttt{ease of use}, how much
+    		\texttt{fun} it was to use the robot, how far they found the robot had an
+    		\texttt{impact} on their household, and their {overall} impression of it.}
+    		\label{fig:roomba-study}
 \end{figure}
@@
 
-\begin{figure}[b]
-    \centering
-    \includegraphics[width=0.5\columnwidth]{roomba-perception.pdf}
+%\begin{figure}
+%    \centering
+%    \includegraphics[width=0.5\columnwidth]{roomba-perception.pdf}
 
@@
 
-    \caption{People's perception of the robot over time, n = 15 participants.
-    This line chart shows how people's perception of the robot evolves over
-    time. At 5 time points people were asked to rate the robot according to the
-    following aspects: the perceived \texttt{intelligence} of the robot, the
-    perceived \texttt{usefulness}, the perceived \texttt{ease of use}, how much
-    \texttt{fun} it was to use the robot, how far they found the robot had an
-    \texttt{impact} on their household, and their {overall} impression of it.}
-
-    \label{fig:roomba-perception}
-\end{figure}
+%    \caption{People's perception of the robot over time, n = 15 participants.
+%    This line chart shows how people's perception of the robot evolves over
+%    time. At 5 time points people were asked to rate the robot according to the
+%    following aspects: the perceived \texttt{intelligence} of the robot, the
+%    perceived \texttt{usefulness}, the perceived \texttt{ease of use}, how much
+%    \texttt{fun} it was to use the robot, how far they found the robot had an
+%    \texttt{impact} on their household, and their {overall} impression of it.}
+%
+%    \label{fig:roomba-perception}
+%\end{figure}
 
@@
 \subsection{Forum study: using anthropomorphic expressions to describe a robot}
-
-%\begin{figure}
-%    \centering
-%    \includegraphics[width=0.7\columnwidth]{aibo-roomba-ipad_2.jpg}
-%    \caption{The Sony AIBO robotic dog (left), the iRobot Roomba vacuum-cleaning robot (middle), and the Apple Inc.
-iPad tablet computer (right) were compared in terms of how far users of these devices use anthropomorphic expressions in discussions about their technology / robot in online discussion forums.}
-%    \label{fig:aibo-roomba-ipad}
-%\end{figure}
 
@@
 \end{enumerate}
-
-\begin{figure}[b]
-    \centering
-    \includegraphics[width=0.5\columnwidth]{aibo-roomba-ipad_2.jpg}
-    \caption{The Sony AIBO robotic dog (left), the iRobot Roomba vacuum-cleaning robot (middle), and the Apple Inc.
-iPad tablet computer (right) were compared in terms of how far users of these devices use anthropomorphic expressions in discussions about their technology / robot in online discussion forums.}
-    \label{fig:aibo-roomba-ipad}
-\end{figure}
 
@@
 
+\begin{figure}[b]
+    \centering
+    \includegraphics[width=0.5\columnwidth]{aibo-roomba-ipad_2.jpg}
+    \caption{The Sony AIBO robotic dog (left), the iRobot Roomba vacuum-cleaning robot (middle), and the Apple Inc.
+iPad tablet computer (right) were compared in terms of how far users of these devices use anthropomorphic expressions in online discussion forums about their technology / robot.}
+    \label{fig:aibo-roomba-ipad}
+\end{figure}
+
 %Overall, our analysis revealed that in all three forums, discussions about
@@
 
+\begin{figure}
+        \centering
+        \begin{subfigure}[b]{0.48\columnwidth}
+                \includegraphics[width=\textwidth]{ranger-interactions-per-runs}
+                \caption{Interactions per run}
+                \label{fig:interactions-per-run}
+        \end{subfigure}%
+        ~ %add desired spacing between images, e. g. ~, \quad, \qquad etc.
+          %(or a blank line to force the subfigure onto a new line)
+        \begin{subfigure}[b]{0.48\columnwidth}
+                \includegraphics[width=\textwidth]{ranger-interactions-vs-qualitative-score}
+                \caption{Qualitative score by interactions}
+                \label{fig:qualitative-score}
+        \end{subfigure}
+        \caption{\textbf{The Ranger domino study: Child-robot interaction.}\\
+    \textbf{a)} Quantitative assessment: here, six interaction modalities have
+        been selected: showing something to the robot ({\tt show}), talking to
+        the robot ({\tt talk}), touching it ({\tt touch}), misbehaving (like
+        shaking it, {\tt mis}), using gestures ({\tt ges}), and looking
+        for help by glancing at the experimenter ({\tt look}). In each
+        of the 13 experimental runs, we annotated and counted the number of
+        occurrences of each of these interactions. Highlighted runs 2.3, 2.4,
+        2.7 and 2.8 correspond to unexpected robot behaviors: we observe peaks
+        of interactions every time the robot's behavior changes from expected to
+        unexpected or from unexpected to expected. (n = 26 children)\\
+	\textbf{b)} We found a significant negative correlation ($p=0.048$) between the
+    number of interactions and the qualitative anthropomorphic projections. This 
+    suggests that children who interacted more with the robot, anthropomorphized it 
+	less, and \textit{vice versa}. (n = 13 groups)}
+    		\label{fig:Ranger-domino}
+\end{figure}
+
 \subsubsection{Anthropomorphic interactions with the robot\\}
@@
 
-\begin{figure}
-    \centering
-    \includegraphics[width=0.5\columnwidth]{ranger-interactions-per-runs}
-    \caption{Quantitative assessment: here, six interaction modalities have
-        been selected: showing something to the robot ({\tt show}), talking to
-        the robot ({\tt talk}), touching it ({\tt touch}), misbehaving (like
-        shaking it, {\tt mis}), using gestures ({\tt ges}), and looking
-        for help by glancing at the experimenter ({\tt look}). In each
-        of the 13 experimental runs, we annotated and counted the number of
-        occurrences of each of these interactions. Highlighted runs 2.3, 2.4,
-        2.7 and 2.8 correspond to unexpected robot behaviors: we observe peaks
-        of interactions every time the robot's behavior changes from expected to
-        unexpected or from unexpected to expected. (n = 26 children)}
-
-    \label{fig:interactions-per-run}
-\end{figure}
+%\begin{figure}
+%    \centering
+%    \includegraphics[width=0.5\columnwidth]{ranger-interactions-per-runs}
+%    \caption{Quantitative assessment: here, six interaction modalities have
+%        been selected: showing something to the robot ({\tt show}), talking to
+%        the robot ({\tt talk}), touching it ({\tt touch}), misbehaving (like
+%        shaking it, {\tt mis}), using gestures ({\tt ges}), and looking
+%        for help by glancing at the experimenter ({\tt look}). In each
+%        of the 13 experimental runs, we annotated and counted the number of
+%        occurrences of each of these interactions. Highlighted runs 2.3, 2.4,
+%        2.7 and 2.8 correspond to unexpected robot behaviors: we observe peaks
+%        of interactions every time the robot's behavior changes from expected to
+%        unexpected or from unexpected to expected. (n = 26 children)}
+%
+%    \label{fig:interactions-per-run}
+%\end{figure}
 
@@
 
-\begin{figure}
-    \centering
-    \includegraphics[width=0.5\columnwidth]{ranger-interactions-vs-qualitative-score}
-    \caption{We found a significant negative correlation ($p=0.048$) between the
-    number of interactions and the qualitative anthropomorphic projections. This 
-    suggests that children who interacted more with the robot, anthropomorphized it 
-    less, and \textit{vice versa}. (n = 13 groups)}
-    \label{fig:qualitative-score}
-\end{figure}
+%\begin{figure}
+%    \centering
+%    \includegraphics[width=0.5\columnwidth]{ranger-interactions-vs-qualitative-score}
+%    \caption{We found a significant negative correlation ($p=0.048$) between the
+%    number of interactions and the qualitative anthropomorphic projections. This 
+%    suggests that children who interacted more with the robot, anthropomorphized it 
+%    less, and \textit{vice versa}. (n = 13 groups)}
+%    \label{fig:qualitative-score}
+%\end{figure}
 
@@
 which is anthropomorphized. Though commonly observed, it appears controversial, at 
-the same time, that humans tend to \hl{\textit{``see human in the non-
-human''}}. 
+the same time, that humans tend to \textit{``see human in the non-
+human''} \citep{epley_seeing_2007}. 
 Anthropomorphism as a social phenomenon arises in an interaction 
 \citep{persson_anthropomorphism_2000}, and thus includes at least two interaction 
-partners (the human and the real or imagined non-human agent). Therefore, one can 
-take two main perspectives on explaining it \citep{lee_human_2005}: an artifact-
-centered, and a human-centered. We briefly outline both views in the following. 
+partners: the human and the real or imagined non-human agent. Therefore, one can 
+take two main perspectives on explaining anthropomorphism \citep{lee_human_2005}: a human-centered and an artifact-centered. We briefly outline both views in the following. 
 It has to be kept in mind that both perspectives are inseparable; they apply at the 
 same time, and we would like to present them here just as two different viewpoints 
-on the same kind of phenomenon.
-
-In this section we will try to create a common ground in the understanding of 
-anthropomorphism, with a focus on it related to human-robot interaction. 
+on the same phenomenon.
+
+By doing so, this section tries to create a common ground in the understanding of 
+anthropomorphism, with a focus on the design of robots and human-robot interaction. 
 First of all, we would like to propose a clarification of terms.
-We call an imitation of human form (or in a broader sense also animal and natural) 
-form \textit{``anthropomorphic design''} or \textit{``anthropomorphic form''} -- 
-but \textit{not anthropomorphism}. Contrary, we call the social phenomenon of 
-people's tendency to perceive human-likeness in non human-like 
-agents \textit{anthropomorphism}.
-
-In the following, we first present an artifact-centered perspective on 
-anthropomorphism, and outline how the human-like 
-design approach (\textit{anthropomorphic form}) is used in robotics to encourage 
-people to interact socially with robots. Then, we apply a human-centered 
+In short, we propose to use two different terms, in order to differentiate between the human-like design of a non-human agent, and the perception of human-likeness in a non-human agent.
+We use the terms \textit{``anthropomorphic design''} and \textit{``anthropomorphic 
+form''} interchangeably to refer to an imitation of human form (or in a broader sense 
+also animal and natural) in the design of objects and artificial agents. We propose to 
+\textit{not} refer to this as \textit{anthropomorphism}.
+Because we use \textit{anthropomorphism} to refer to the social phenomenon of 
+people's tendency to perceive human-likeness in non human-like agents. This is an important differentiation.
+
+In the following, we first present an artifact-centered perspective on anthropomorphism, and outline how 
+the human-like design approach (\textit{anthropomorphic form}) is used in robotics to encourage 
+people to interact in a social way with robots. Then, we apply a human-centered 
 perspective and shed light on \textit{anthropomorphism as a social phenomenon}. We present 
@@
 parts / the design of the non-human agent.
-The direction of causality in this view is that the non-human artifact (or certain 
-features of it) encourages the human to anthropomorphize it.
+The direction of causality in this view is that the non-human artifact (or a certain 
+feature of it) encourages the human to anthropomorphize the artifact / agent.
 This perspective assumes that humans directly respond to life-like and social cues 
-that the non-human artifact or system emits, without thoughtful mental processing, 
+that the non-human agent or system emits, without thoughtful mental processing, 
 by simply applying stereotypes and heuristics to it. In fact, from early childhood 
@@
 in a sense of being human. At the same time, humans are naturally very skilled when 
-it comes to identifying what is acceptable as a human and what is a \hl{NACHAHMUNG} 
+it comes to identifying what is acceptable as a human and what is an imitation 
 of it. Even subtle differences can be crucial -- humans are inherently well trained 

### 2014-03-25 paper.tex
changes in anthropomorphism - artifact-centered section

@@
 that the non-human agent or system emits, without thoughtful mental processing, 
-by simply applying stereotypes and heuristics to it. In fact, from early childhood 
+by simply applying stereotypes and heuristics to it. Humans naturally react to specific 
+cues. This is natural because, for instance, from early childhood 
 on, humans are inherently well-trained to perceive life \citep{epley_seeing_2007}, 
-and to respond to social cues, such as facial expressions, social gestures or turn-
-taking. When first looking at an unknown object, the visual scope of its design, 
-its outer appearance is likely to have an important impact on how the object is 
-overall perceived (how it appears to the human) \citep{schmitz_concepts_2011}.
-
-This fact is exploited in the design of robots and other things. The basic 
+or to respond to social cues, such as facial expressions, social gestures or turn-
+taking. 
+These cues can be of various senses and modalities. One of the most important aspects 
+is the outer appearance of the unknown agent or artifact. \cite{schmitz_concepts_2011} 
+argues that an agent's outer appearance is likely to have an important impact on how 
+the object is overall perceived (how it appears to the human). Thus, if a robot looks much like a human, it appears to be like a human, and is perceived accordingly.
+
+This fact is exploited in the design of robots and other things. Again, the basic 
 assumption here is that if an artifact 
 somehow resembles a human, it is likely to be treated similar to a human. If this 
-explanation of anthropomorphism is correct, people may respond automatically to 
+explanation of anthropomorphism is correct, people may respond automatically also to 
 social cues emitted by an artificial embodied agent such as a robot, and apply 
@@
 human user side, to which we will come back later in more detail.)}
+The human-like design of robots implies various consequences, of which we will present some in the following.
 
@@
 
-The use of anthropomorphic (human-like) form in the design of non-human 
-things is as old as people's tendency to anthropomorphize. Anthropomorphic (and 
-also animal-shaped) forms were used already in prehistoric artworks and 
-illustrations, and they have a long-standing tradition in the design of daily life 
-artifacts and in general \citep{guthrie_bottles_2000}. The principle of human-like 
-form is probably most prominent in the design of robots. But what do we mean by \textit{human-like / anthropomorphic form}?
-
+What do we mean by \textit{human-like / anthropomorphic form}?
 Using the term \textit{``form''} to describe the design of an artifact, we refer 
@@
 anthropomorphic, zoomorphic, caricatured, functional \citep{fong_survey_2003}.
-However, a classification makes sense because different user reactions are 
-expected. According to \cite{bartneck_shaping_2004}, the appearance and function of 
-a product, whether it is an appliance or a humanoid robot, affects the way that 
-people perceive it, interact with it, and build long-term relationships with it.
-The relation between the design of a robot and the user's perception of it, is also formulated in the \textit{Uncanny Valley} hypothesis \citep{mori_uncanny_1970}.
+
+The use of anthropomorphic (human-like) form in the design of non-human 
+things is as old as people's tendency to anthropomorphize. Anthropomorphic (and 
+also animal-shaped) forms were used already in prehistoric artworks and 
+illustrations, and they have a long-standing tradition in the design of daily life 
+artifacts and in general \citep{guthrie_bottles_2000}. The principle of human-like 
+form is probably most prominent in the design of robots, due to several reasons. 
+However, it has been controversially discussed since the early 1970ies, related to 
+\cite{mori_uncanny_1970} theory of the \texit{Uncanny Valley}, see Figure \ref{fig:uncanny_valley}.
+
+The underlying crucial point about the design are the implications that it holds, and the 
+suggestions for interactions that it makes to the user. In other words, the appearance 
+and function of a product, whether it is an appliance or a humanoid robot, affects the 
+way that people perceive it, interact with it, and build long-term relationships with 
+it \cite{bartneck_shaping_2004}. The relation between the design of a robot and the 
+user's perception of it, is also formulated in the \textit{Uncanny Valley} hypothesis \citep{mori_uncanny_1970}.
 
@@
 
-In general, it is suggested that increasing human-likeness of a robot will lead to 
+Despite the fact that the Uncanny Valley theory was more a working hypothesis and not 
+meant to be empirically examined \citep{cheetham_human_2011}, it has been studied quite 
+extensively. However, results are inconsistent. We try to give a short overview (not 
+exclusive) on work related to HRI and robotics in the following.
+
+\subsubsection{How people perceive and interact with human-like robots\\}
+\label{sec:anthropomorphism-robotics}
+
+Most work that studies how far human users treat robots as social agents, builds on the 
+famous work of \cite{reeves_media_1996} in HCI. In the so-called \textit{Media 
+Equation}, the authors describe that people mindlessly react in a social way to their computer 
+and that they tend to even attribute human (social) characteristics to it -- despite 
+the fact that a computer does not have human-like characteristics. Apart from 
+computers, anthropomorphism has also been observed with digital / virtual characters 
+\citep{reeves_media_1996,nass_anthropocentrism_1995}, and artificial embodied agents, 
+such as robots. In short, one can say that with robots, and human-like robots in 
+particular, anthropomorphism is a commonly observed phenomenon. However, the 
+anthropomorphic design approach in robotics is controversially discussed.
+
+But what are the motivations which underlie the efforts of enhancing anthropomorphism through specific anthropomorphic design in robots?
+Why are anthropomorphic forms so distinct and at the same time controversial in robotics?
+There is no one single answer to this question.
+
+\hl{human-likeness has a positive effect\\}
+
+On one hand, developers and designers have discovered that human-like robots may better match the affordances that our to humans adapted world brings along.
+Also.
+anthropomorphic form and people's resulting consequence to anthropomorphize, appears to be generally beneficial for human-robot relations, especially with socially interactive robots \cite{fong_survey_2003}.
+Consequently, the domain of (social) robotics tries to exploit this fact by enhancing anthropomorphism through anthropomorphic robots: \textit{"Applying anthropomorphism or zoomorphism changes the way how users try to understand and make sense of a [system] by projecting everyday \hl{expectations} of human and animalistic life onto it."} \cite{schmitz_concepts_2011}.
+
+In general, it is suggested that increasing the human-likeness of a robot (up to a 
+certain threshold) will lead to 
 more perceived \textit{affinity} from the human side \citep{mori_uncanny_1970} (see 
@@
 humans tend to apply the same communication references to anthropomorphic systems 
-that they would use with other humans. This theoretical concept is also supported 
+that they would use with other humans, and this is what they are familiar with and feel comfortable about. This theoretical concept is also supported 
 by psychological determinants of 
@@
 appearance, the more people are likely to use themselves as a source of induction 
-and anthropomorphize these nonhuman agents"} \citep{epley_seeing_2007}. 
-Also various 
+and anthropomorphize these nonhuman agents"} \citep{epley_seeing_2007}. (We will come back to this later, in Section \ref{sec:explanations}).
+
+Studies have further shown that perceived similarity between the user and the robot influences the intensity of the participants' attributions towards the robot.
+Thus,the anthropomorphic design of a robot impacts the user's perception of the robot, and how far the user is likely to attribute and experience qualities such as intelligence, fun, or intentions in the robot.
+
+"[...] the experiment demonstrates that human beings implicitly attribute human-like qualities, such as mental states, to nonhuman agents.
+This finding was evident on a neuro-physiological level as well as behavioral level." \cite{hegel_understanding_2008}\fxwarning{What to do with this quote?
+'neuro' level maybe interesting?}
+
+Various 
 empirical studies have shown that robots with human-like forms can have a positive 
@@
 anthropomorphism, and in turn create a social view toward the robot.
+
+\hl{human-likeness has a negative effect\\}
 
@@
 
-\subsubsection{Anthropomorphism in Robotics and Human-Robot Interaction\\}
-\label{sec:anthropomorphism-robotics}
-
-\hl{Julia: I need to work on this section ...}
-
-%While the previous sections presented anthropomorphism more generally, this 
-%section focuses on how anthropomorphism is understood and has been studied in human 
-%robot interaction / social robotics. Our aim here is to give a rough overview of 
-%the diverse and partially conflicting interpretations of anthropomorphism in HRI, 
-%and critically review some previous work.
-
-Most work that studies anthropomorphism in HRI builds on the famous work of \cite{reeves_media_1996} in HCI.
-In the so-called \textit{Media Equation}, the authors describe that people mindlessly react socially to their computer and that they tend to even attribute human (social) characteristics to it.
-Apart from computers, anthropomorphism has also been observed with digital / virtual characters \citep{reeves_media_1996,
-nass_anthropocentrism_1995}, and as more interactive technologies and systems emerged, also with artificial embodied agents, such as robots.
-
-In human-robot interaction anthropomorphism is a commonly observed phenomenon, however, findings have been inconsistent, and in turn, anthropomorphic designs of robots are controversially discussed.
-
-For instance, recent studies found that people tend to ascribe personality and intentions to robots \hl{(REFS)} and that they show empathetic behavior toward robots \citep{rosenthal-vonderputten_experimental_2013}.
-Summing it up, there is a huge and constantly growing body of literature that describes anthropomorphism in HCI and HRI.
-Despite the phenomenon is well studied, we still know rather little about it, so that at conferences and symposiums, anthropomorphism is still a ``hot topic''; however, at the same time theories related to anthropomorphism, such as the \textit{``Uncanny Valley''} are controversially discussed.
+%For instance, recent studies found that people tend to ascribe personality and 
+%intentions to robots \hl{(REFS)} and that they show empathetic behavior toward robots 
+%\citep{rosenthal-vonderputten_experimental_2013}. Summing it up, there is a huge and 
+%constantly growing body of literature that describes anthropomorphism in HCI and HRI. 
+%Despite the phenomenon is well studied, we still know rather little about it, so that 
+%at conferences and symposiums, anthropomorphism is still a ``hot topic''; however, at 
+%the same time theories related to anthropomorphism, such as the \textit{``Uncanny 
+%Valley''} are controversially discussed.
 
@@
 %\citep{friedman_hardware_2003}.
-
-But what is the motivation which underlies the efforts of enhancing anthropomorphism through specific anthropomorphic design in robots?
-Why does anthropomorphism seem to be so important in robotics?
-There is no one single answer to this question but certainly, developers and designers have discovered that anthropomorphism seems to be beneficial for human-robot relations, especially with socially interactive robots \cite{fong_survey_2003}.
-
-The domain of (social) robotics tries to exploit this fact by enhancing anthropomorphism through anthropomorphic robots: \textit{"Applying anthropomorphism or zoomorphism changes the way how users try to understand and make sense of a [system] by projecting everyday \hl{expectations} of human and animalistic life onto it."} \cite{schmitz_concepts_2011}.
-
-Studies have further shown that perceived similarity between the user and the robot influences the intensity of the participants' attributions towards the robot.
-Thus, anthropomorphism plays an important role in the design of robots as it is strongly related to the perception of intelligence, fun, the attribution of intentions and thus the predictability of the robot \hl{which ref??}.
-
-"[...] the experiment demonstrates that human beings implicitly attribute human-like qualities, such as mental states, to nonhuman agents.
-This finding was evident on a neuro-physiological level as well as behavioral level." \cite{hegel_understanding_2008}\fxwarning{What to do with this quote?
-'neuro' level maybe interesting?}
 
@@
 \subsection{A human-centered perspective on anthropomorphism}
+\label{sec:human-centered}
 

### 2014-03-25 paper.tex
Rephrase first section of introduction
Should emphazise the importance of a broader look at anthropomorphism

@@
 
-%{Intro when start with anthropomorphic design}
 The Uncanny Valley hypothesis \citep{mori_uncanny_1970} proposes that human-like
@@
 engagement with and feelings of empathy for the non-human agent
-\citep{cheetham_human_2011}. The positive effect of so-called
-\textbf{anthropomorphic form} is exploited in the design of artificial agents
+\citep{cheetham_human_2011}\fxfatal{uncanny valley is not about positive
+feeling!}. The positive effect of so-called \textbf{anthropomorphic form} is
+exploited in the design of artificial agents
 (\eg digital characters, robots) for several reasons. Amongst others,
@@
 to avoid ``falling'' into this Uncanny Valley with their human-like designs of
-artificial agents. Consequently, there is a considerable research effort into
-better understanding the boundaries of anthropomorphic design and their effect
-on the interaction and experience. However, findings have been inconsistent
-\citep{cheetham_human_2011}.
-
-A phenomenon that is often studied related to the human-like design of robots is
-\textbf{anthropomorphism} (noted \Ant in this paper). Besides a feeling of affinity, and empathy,
-anthropomorphism can be understood as being one of the resulting (and  more or
-less desired) effects of the anthropomorphic design of artificial agents (up to
-the first positive peak). The essence of anthropomorphism is the human user's
-perception of human-likeness in the non-human agent. Logically, anthropomorphism
-is said to be enhanced with increased human-like design of the agent. There are
-various other reasons and explanations for why people tend to anthropomorphize
-non-human agents. In general, as anthropomorphism emerges in a (real or
-imagined) interaction \citep{persson_anthropomorphism_2000} between at least two
-players (the human who anthropomorphizes and the non-human agent which is
-anthropomorphized) there are also two main perspectives on the phenomenon: an
-artifact-centered (design) and a human-centered (cognitive, psychological) one.
-The Uncanny Valley hypothesis can be categorized as being part of first,
-artifact-centered approach, to understand anthropomorphism.
+artificial agents. Consequently, there is a considerable research effort to
+better understand the boundaries of anthropomorphic design and their effects
+on the interaction and experience. To date, findings have been however
+inconsistent \citep{cheetham_human_2011}.
+
+Along this line, this article aims at fostering a better understanding of
+anthropomorphism (noted \Ant in this paper) by considering the phenomenon
+\textbf{as a whole}: robotics researchers often tend to believe that
+anthropomorphism only describes a static set of human-like features of a robot
+(like shape, speech capabilities, facial expressions, etc.). We refer to these
+characteristics as the \emph{anthropomorphic design} of the
+robot~\cite{fink_anthropomorphism_2012}. But \emph{anthropomorphism} in general
+refers to the larger \emph{social phenomenon} that emerges from the (real or
+imagined) \emph{interaction} between a robot and a
+user~\citep{persson_anthropomorphism_2000}. According to~\cite{epley_when_2008},
+this includes for instance emotional states, motivations, intentions
+\emph{ascribed by the user} to the robot. As such, the dynamic and
+socio-cognitive dimensions of anthropomorphism are essential to understand the
+complex bonds that human users build with the robots.
 

### 2014-03-25 paper.tex
Completed section 'A few result from the field' in intro
Still wondering if the referenced figures should not be moved there as well

@@
 results. We observed anthropomorphism in several short- and long-term human-robot
-interaction studies that we carried out with embodied robots, mostly in
-real-world settings. There is not much research that investigates
-anthropomorphism based on real interaction between a human and a robot, and
-above all in natural settings and over extended periods of time.
-
-Figure~\ref{fig:roomba-perception} gives a first perspective on how naive
-users perceive robots over a long period of time. Here, \emph{Roomba} vacuum cleaning robots
-were given to nine households for a 6-months period. The aim was to explore how
-people use and perceive the robot over time, and how they generally live with
-the Roomba in their home. At various time points, users were asked to rate
-their perception of different features of the robot on a 7-point rating scale. As
-Figure~\ref{fig:roomba-perception} shows, some features remained stable over time
-(\emph{ease of use} and \emph{fun}), and others decreased: the perceived
-\emph{usefulness}, \emph{intelligence} and \emph{impact} on their household.
-\emph{intelligence} and \emph{impact} reflect the cognitive engagement of the
-user towards the machine: we can assume that one does not care to engage in a
-(cognitive) interaction with an artifact perceived as non-intelligent and with
-no impact on his/her life. Even if one can argue that the Roomba is not designed
-to foster interaction, the question is raised: how to sustain engagement between
-a robot and a human over a long period of time? And, as a pre-requisite, do we
-actually understand the psychological phenomenon, and can we effectively account
-for the dynamics of these interactions?
+interaction studies that we carried out with embodied robots, both in
+ecologically valid real-world environments and controlled lab settings. Those
+experiments are presented in details in section~\ref{sec:overview-studies}. We
+only highlight here some qualitative results in order to trigger some initial
+thoughts.
+
+Figures~\ref{fig:roomba-activities} and~\ref{fig:roomba-perception} (on
+page~\pageref{fig:roomba-perception}) give a first perspective on how naive
+users interact and perceive robots over a long period of time. Here,
+\emph{Roomba} vacuum cleaning robots were given to nine households for a
+6-months period. The aim was to explore how people use and perceive the robot
+over time, and how they generally live with the Roomba in their home. At various
+time points, users were asked to rate their perception of different features of
+the robot on a 7-point rating scale. As Figure~\ref{fig:roomba-perception}
+shows, some features remained stable over time (\emph{ease of use} and
+\emph{fun}), and others decreased: the perceived \emph{usefulness},
+\emph{intelligence} and \emph{impact} on their household.  \emph{intelligence}
+and \emph{impact} reflect the cognitive engagement of the user towards the
+machine: we can assume that one does not care to engage in a (cognitive)
+interaction with an artifact perceived as non-intelligent and with no impact on
+his/her life (and the level of activity pictured on
+Figure~\ref{fig:roomba-activities} qualitatively confirms this intuition). Even
+if one can argue that the Roomba is not designed to foster interaction, it
+raises a first question: how to sustain engagement between a robot and a human
+over a long period of time? And, as a pre-requisite to answer, do we actually
+understand the psychological phenomenon, and can we effectively account for the
+dynamics of these interactions?
 
 Those questions are certainly not new, but paradoxically, while anthropomorphism
-in robotics is a commonly discussed and studied trait of human-robot
-interaction, it appears that it lacks a formal ground and unified understanding to
-take into account the wide range of phenomena that it encompasses.
+in robotics is a commonly discussed trait of human-robot interaction, it appears
+that we lack formal grounds and models that would account for the long-term
+dynamics of these interactions.
+
+Figure~\ref{fig:qualitative-score} (page~\pageref{fig:qualitative-score}) calls
+for other initial remarks. This diagram comes from a study where 13 pairs of
+children (4-5 years old) played for about 20 minutes a Domino game with a robot
+(the robot was tasked to carry domino pieces from one child to the other). The
+$x$-axis represents the number of social interactions between the children and
+the robot (like talking or showing objects), based on video annotations. On the
+$y$-axis, we have a synthetic qualitative measurement of anthropomorphic
+projections based on two questionnaires. The correlation between both these
+values is significantly \emph{negative}: the more the children engaged into
+interaction, the less prone to anthropomorphic projections they were. This
+diagram also highlights an interesting cluster of children who did not interact
+much with the robot, and still reported a strong anthropomorphic perception of
+the robot.
+
+These results may seem counter-intuitive at first sight, and illustrate that the
+mechanisms that relate anthropomorphism to adoption and engagement are
+non-trivial. In section~\ref{sec:cognition-neuroscience}, we sketch a model of
+the cognitive correlates of anthropomorphism that partially account for these
+results.
 

### 2014-03-25 paper.tex
Completed rewrite of introduction

@@
 \floatstyle{plaintop}
+
+\usepackage{paralist} % inparaenum
 
@@
 
-So far, the HRI community has not much investigated how anthropomorphism in
-human-robot interactions evolves over time. In robotics, anthropomorphism is traditionally
-perceived as a static feature triggered by the human-like design of a robot that once observed (during a
-short-term interaction) reflects a sustaining social effect. Based on a previously published
-literature review~\citep{fink_anthropomorphism_2012}, a
-long-term field study in a natural environment~\citep{fink_living_2013}, a 
-content analysis of online discussion 
-forums~\citep{fink_anthropomorphic_2012}, and an on-going child-robot 
-interaction study, we believe that anthropomorphic
-effects are based on several factors, and that they do evolve over time in 
-non-monotonic ways. Moreover, we assume that these variances and dynamics 
-play a central role in sustaining engagement in human-robot interaction.
-
-This article is organized around two main hypothesis that we formulated based on 
-our empirical studies of HRI, and by integrating previous work from several domains.
-
-\begin{itemize}
-    \item \textbf{Hypothesis 1~} A person's tendency to anthropomorphize a robot
+These first remarks lead to the main question we attempt to address in this
+article: how can we understand \emph{anthropomorphism} as a whole, and in such a
+way that is support improved human-robot interactions?
+
+Based on an extensive literature review~\citep{fink_anthropomorphism_2012},
+several field and lab studies~\citep{ fink_anthropomorphic_2012,
+fink_living_2013, fink2014which, lemaignan2014dynamics} and insights from the
+cognitive neurosciences, we propose to discuss anthropomorphism from three
+complementary perspectives.
+
+First, we would like to clarify what anthropomorphism actually \emph{means}:
+besides the \emph{artifact-centered} understanding of anthropomorphism, it
+seems important to explicit the human and social factors of anthropomorphism.
+
+Then, we propose a model to understand how anthropomorphism evolves over time.
+These dynamics are non-monotonic, and psychological factors like the
+\emph{novelty effect} play here a key role.
+
+Finally, we adopt a third perspective on anthropomorphism by investigating its
+\emph{cognitive correlates}. Several studies previously showed that we build
+instinctive bonds with robots as soon as we attribute animacy, and we also know
+from social psychology some of the mechanisms that lead to
+\emph{familiarization}. We attempt here to ``connect the dots'', in order to
+build a practical model of the cognitive stages we encounter in human-robot
+interaction.
+
+\paragraph{Two hypotheses} Our research question also translates to two
+hypotheses, which structure the reflections of this article:
+
+\begin{enumerate}
+
+\item A person's tendency to anthropomorphize a robot
     is based on several factors, including (but not limited to) (1) the
     design of the robot, (2) the personal characteristics of the human user,
-and (3) the context and situation of use. For instance, a social 
-context and purpose of the robot increase anthropomorphism. 
-\textit{(anthropomorphism as a multi-factor phenomenon)}
-	\item \textbf{Hypothesis 2~} A person's tendency to anthropomorphize a robot 
+    and (3) the context and situation of use. For instance, a social context
+    and purpose of the robot increase anthropomorphism: \textit{anthropomorphism
+    as a multi-factor phenomenon}.
+
+\item A person's tendency to anthropomorphize a robot
     evolves in a non-linear way over time and with growing experience that the
-person has with the robot. For instance, a more experienced user will perceive 
-the robot as more familiar and predictable, and in turn anthropomorphizes the 
-robot less. \textit{(anthropomorphism as a dynamic phenomenon)}
-\end{itemize}
-
-We propose to formalize these variances and dynamic effects into a model that we call the
-\emph{Dynamics of Anthropomorphism}. We hope that it may support further
-discussions and reflections on how anthropomorphism impacts human-robot
-interaction on the long run, and also foster research on the affective bonds
-induced by anthropomorphic projections on robots.
-Through our model, we propose to represent how the level of anthropomorphic effects (\ie
-observable manifestations of anthropomorphism) evolves over a long-term
-human-robot interaction (Figure~\ref{fig:dynamics}). By long-term interaction,
-we mean direct (non-mediated), repeated interaction with the same robot, over
-an extended period of time (typically longer than a week).
-
-%In this article, we would further like to share some critical but constructive
-%considerations on anthropomorphism in robotics and HRI. Thereby, we contribute
-%to a better understanding of this complex phenomenon related to robots.
+    person has with the robot. For instance, a more experienced user will
+    perceive the robot as more familiar and predictable, and in turn
+    anthropomorphizes the robot less: \textit{anthropomorphism as a dynamic
+    phenomenon}.
+
+\end{enumerate}
+
+\subsection{Article overview}
+
+\begin{inparaenum}[\itshape 1)\upshape]
 
@@
 \ref{sec:overview-studies}, we give a brief overview on the various studies that
-we conducted to investigate anthropomorphism, namely (1) the Roomba study, (2)
-the Forum study, (3) the Ranger domino study. Next, in Section 
-\ref{sec:anthropomorphism} we aim to establish a common ground in the understanding 
-of anthropomorphism. We first explore an artifact-centered perspective and briefly
-outline how the human-like design of agents can encourage anthropomorphism.
-Then, we explore a human-centered perspective by integrating theories from
-cognitive science, developmental and social psychology that serve to explain
-anthropomorphism. At the end of this section we bring both perspectives together
-and interpret that anthropomorphism is a multi-factor phenomenon.  Based on the
-two previous sections, we propose an initial model of the \textit{``Dynamics of
-Anthropomorphism''} in Section \ref{sec:our-ideas}. This model describes the
-variances and dynamics of people's tendency to anthropomorphize an artificial
-agent, such as a robot.  Next, in Section \ref{sec:cognition-neuroscience} we
-present a cognitive and neuroscience perspective on anthropomorphism to
-consolidate our considerations and the proposed model.  This will be followed by
-a discussion about the limitations of our approach (Section
-\ref{sec:discussion}). Further, we debate existing and alternative ways to
-measure anthropomorphism in human-robot interactions.  Finally, Section
-\ref{sec:conclusion} concludes this article and offers starting points for
-further research on anthropomorphism and the effect of the human-like design
-approach in robotics.
+we conducted to investigate anthropomorphism, namely \item the Roomba study,
+\item the Forum study, \item the Ranger domino study. Next, Section
+\ref{sec:anthropomorphism} aims to establish a common ground in the
+understanding of anthropomorphism. We first explore an artifact-centered
+perspective and briefly outline how the human-like design of agents can
+encourage anthropomorphism.  Then, we explore a human-centered perspective
+by integrating theories from cognitive science, developmental and social
+psychology that serve to explain anthropomorphism. At the end of this
+section we bring both perspectives together and interpret that
+anthropomorphism is a multi-factor phenomenon.  Based on the two previous
+sections, Section~\ref{sec:our-ideas} introduces an initial model of the
+\textit{dynamics of anthropomorphism}. This model describes the variances
+and dynamics of people's tendency to anthropomorphize an artificial agent,
+such as a robot.  Then Section \ref{sec:cognition-neuroscience} presents a
+cognitive and neuroscience perspective on anthropomorphism to consolidate
+our considerations and the proposed model.  This is followed by a discussion
+about the limitations of our approach (Section \ref{sec:discussion}) and the
+existing and alternative ways to measure anthropomorphism in human-robot
+interactions.  Finally, Section \ref{sec:conclusion} concludes this article
+and offers starting points for further research on anthropomorphism and the
+effect of the human-like design approach in robotics.
+
+\end{inparaenum}
 

### 2014-03-25 paper.tex
Moved back the section on Disruptive behavior to Sec Cognitive Correlates
This discussion on disrptive behavior actually relies on the cognitive
interpretations of anthropomorphism, so better have it there.
Tuning of the model of the Dynamics + {expectation mismatch -> attractiveness delta}

@@
 
+\newcommand{\AntNorm}[1][]{%
+      \ifthenelse{\isempty{#1}}%
+      {$\widehat{\mathcal{A}}$}
+      {$\widehat{\mathcal{A}}(#1)$}
+}
+
 % for use inside a math environment
@@
 }
+
+\newcommand{\antNorm}[1][]{%
+      \ifthenelse{\isempty{#1}}%
+      {\widehat{\mathcal{A}}}
+      {\widehat{\mathcal{A}}(#1)}
+}
+
 \newcommand{\ICA}{{$\mathcal{A}_0$~}}
@@
 \newcommand{\AntMax}{{$\mathcal{A}_{max}$~}}
+\newcommand{\antMax}{{\mathcal{A}_{max}}}
 
@@
 The phenomenological model of anthropomorphism we propose
-(Figure~\ref{fig:dynamics},~\cite{lemaignan2014dynamics}) represents how the
-level of anthropomorphic effects (\ie observable manifestations of
+(Figure~\ref{fig:dynamics}~\citep{lemaignan2014dynamics}) represents how the
+level of anthropomorphic effects~\Ant[R,H,C,t] (\ie observable manifestations of
 anthropomorphism, as defined in section~\ref{sec:intro}) evolves over a
-long-term human-robot interaction. By long-term interaction, we mean direct
-(non-mediated), repeated interaction with the same robot, over a long period of
-time.
+long-term human-robot interaction.
 
@@
 (non-mediated), repeated interaction with the same robot, over an extended
-period of time (typically longer than a week) --, we also formally introduce a
+period of time (typically longer than a week), we also formally introduce a
 so-called \emph{novelty effect}~\cite{kanda_interactive_2004} that models the
@@
 In this model, anthropomorphism is quantified by a \emph{normalized level of
-anthropomorphic effects}: because anthropomorphic effects are not quantified on
-an absolute scale, we present them as a normalized value, that spans from a
-minimum (no anthropomorphic effects: $\ant=0$) to a maximum (noted \AntMax, with
-$t_{max} = \operatorname{arg\,max}_t \, \ant[t]$). We also discuss at
-section~\ref{measuring} possible methodologies for the quantitative and
+anthropomorphic effects} $\antNorm[R,H,C,t] = \frac{\ant[R,H,C,t]}{\antMax}$: because anthropomorphic effects are
+not quantified on an absolute scale, we present them as a normalized value, that
+spans from a minimum (no anthropomorphic effects: $\ant=0$) to a maximum (noted
+\AntMax, with $t_{max} = \operatorname{arg\,max}_t \, \ant[t]$). For readability
+reasons, we however omit the hat on \Ant in the following sections. We discuss
+at section~\ref{measuring} possible methodologies for the quantitative and
 qualitative assessment of anthropomorphic effects.
@@
 \draw[->] (0,0) -- (0,6) node[anchor=east] {};
-\draw(-0.8,3) node[rotate=90,anchor=south] {\scriptsize Normalized level of anthropomorphic effects};
+\draw(-0.8,3) node[rotate=90,anchor=south] {\scriptsize Anthropomorphic effects};
 
@@
 
+\draw[dashed] (0.6, 0) -- (0.6,5.1);
+\draw (0.6,0) node[anchor=north] {$t_{max}$};
+
 \draw[dotted] (0, 5) -- (6.2,5);
 \draw[dotted] (0, 3) -- (6.2,3);
-\draw[<->] (6.1,3) -- (6.1,5) node[anchor=east] {};
-\draw (6.2,4) node[rotate=90, anchor=north, align=center] {\tiny Expectation\\\tiny mismatch};
+\draw[<->] (6.1,3) -- (6.1,5) node[sloped, above, midway] {$\Delta_{a}$};
 
@@
 \label{sec:noveltyeffect}
+
+\fxfatal{Julia, do you have smthg to provide an initial account of what the
+novelty effect is?}
 
@@
 
+\paragraph{Attractiveness Delta}
+
+Besides, we propose to call \emph{attractiveness delta}, noted $\Delta_{a}$, the
+difference between the initial capital of anthropomorphism \ICA for a given tuple (user,
+robot, context) and the anthropomorphism peak \AntMax (Figure~\ref{fig:dynamics}).
+This can be interpreted as the initial \emph{excitement} over the robot, or how
+much a user tend to increase his/her anthropomorphic engagement when he/she
+starts to actually interact with the robot.
+
 \subsubsection{Familiarization Phase}
@@
 
-\paragraph{Expectation mismatch}
-
-Besides, we propose to call \emph{expectation mismatch} the delta between the
-initial capital of anthropomorphism for a given tuple (user, robot, context)
-and the anthropomorphism peak of novelty effect (Figure~\ref{fig:dynamics}).
-\fixme{Need to rediscuss what this delta actually represent...}
-
 \subsubsection{Stabilization Phase}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+%
+%
+%		PART 3: EXPLANATIONS -- COGNITIVE CORRELATES, NEUROSCIENCE VIEW
+%
+%
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+% CLAIRE & SEVERIN:
+%
+%
+
+\section{Cognitive Correlates and Neuroscience Perspective}
+\label{sec:cognition-neuroscience}
+
+In this section, we discuss more speculative aspects and hypotheses that follow
+from the model. These aspects would benefit further investigations and
+experimental support.
+
+\subsection{Cognitive Interpretations}
+\label{sec:cognitive-model}
+
+\begin{figure}[htb]
+\centering
+%\resizebox{\linewidth}{!}{
+\begin{tikzpicture}
+\baselineskip=8pt
+
+\path[fill=gray!20] (0,0) rectangle (10.5,2);
+\path[fill=gray!50] (0,2) rectangle (10.5,4);
+\path[fill=gray!20] (0,4) rectangle (10.5,6);
+
+\draw (-0.3,1) node[rotate=90] {Level 1}
+      (-0.3,3) node[rotate=90] {Level 2}
+      (-0.3,5) node[rotate=90] {Level 3};
+
+\draw[->] (0,0) -- (11,0) node[anchor=north] {$t$};
+\draw[-|] (0,0) -- (0,6.5) node[anchor=east] {};
+% Us
+\draw[ultra thick, ->] (0,0) -- (1,2) -- (3,2) -- (4,4) -- (6,4) -- (7,6) --
+(9.5,6);
+\draw[ultra thick, dashed, ->] (3,2) -- (9.5,2);
+\draw[ultra thick, dashed, ->] (6,4) -- (9.5,4);
+
+\draw (11,1) node[align=left, anchor=west]{\scriptsize pre-cognitive\\\scriptsize anthropomorphism}; %label
+
+\draw (11,3) node[align=left, anchor=west] {\scriptsize{projection of existing}\\\scriptsize{mental models}\\\scriptsize{\it (familiarity)}}; %label
+
+\draw (11,5) node[align=left, anchor=west] {\scriptsize{adapted mental
+model} \\ $\to$ \scriptsize{adapted interaction}\\\scriptsize{\it (anthropomorphic or not)}}; %label
+
+\draw[dashed,->] (1,0.1) to[bend right] (2,1.9)  node at (4.5,1) {\tiny{\it observation (shape, motion, sound)}}; %label
+
+\draw[dashed,->] (4,2.1) to[bend right] (5,3.9)  node[align=left] at (7.5,3) {\tiny \it observation (interactive behavior) \\ \tiny \it or short interaction}; %label
+
+\draw[dashed,->] (7,4.1) to[bend right] (8,5.9)  node[align=left] at (9,5)
+{\tiny \it contextualized\\ \tiny \it interaction}; %label
+
+\end{tikzpicture}
+%}
+\caption{The three cognitive levels of anthropomorphism: Level 1 is the instinctive,
+sub-cognitive identification of living peers. {\it Empathy} is characteristic
+of this stage. After longer observation or short, non-contextualized interaction
+(typically, a lab environment), the user reaches Level 2: the user projects a
+mental model he/she is already familiar with onto the robot. After longer {\it
+contextualized} interaction (typically, at home), the user enters Level 3 of
+anthropomorphism: the user recomposes an accurate mental model of the robot,
+based on experience. This leads to adapted interaction modalities, that may
+still be anthropomorphic, or not.}
+\label{fig:cognitivemodel}
+\end{figure}
+
+We provide in this section a tentative interpretation of anthropomorphism in
+terms of cognitive correlates. We warmly welcome the feedback and
+comments from both the cognitive sciences and robotics communities to further
+discuss these findings.
+
+We propose three different cognitive phases (Figure~\ref{fig:cognitivemodel}),
+which do not directly match the previously presented three phases of
+anthropomorphism but are still related.
+
+\subsection{Cognitive Processes and Phases}
+
+The main underlying cognitive process in anthropomorphism is understood as
+perceiving and reasoning about something non-human and unfamiliar based on one's
+representation of the familiar and well-known concept of being
+human~\cite{epley_when_2008}. This led us to interpret the phases of
+anthropomorphic interactions as parallel cognitive phases
+(Figure~\ref{fig:cognitivemodel}).
+
+The so-called \emph{level 1} is the instinctive, pre-cognitive identification of
+living peers. That humans tend to anthropomorphize robots intuitively in this
+pre-cognitive way
+is supported by studies done by Rosenthal-von der Pütten
+\textit{et al.}~\cite{rosenthal-vonderputten_experimental_2013} who investigated
+the neural correlates of emotional reactions of humans towards a robot. {\it
+Empathy} is characteristic of this stage~\cite{rosenthalvonderPutten2013neural}.
+Anthropomorphism at this pre-cognitive stage might also be mediated by the
+human's mirror neurons system (neurons that fire both during execution of
+specific goal-oriented action and during the viewing of action directed toward
+the same goal~\cite{Rizzolatti1996, Kilner2009}) by allowing for a mapping of
+the robot's goal-directed actions into the human own motor
+repertoire~\cite{Gallese1998, Wolpert2003, cullen2013individual}.
+
+After a longer observation period (typically including complete action sequences
+of the robot) or short interaction (touching, short talk like greetings), we
+suggest the human reaches the cognitive \emph{level 2}: in this phase, the human
+starts building a behavioral and cognitive model of the robot that would support
+both the observed and imagined capabilities of the robot.  The \emph{familiarity
+thesis}~\cite{hegel_understanding_2008} supports the idea that the human
+first projects onto the robot mental models of similar agents he/she is already
+familiar with (ranging from animals to human adults, to pets and children). We 
+hypothesize that the nature of the projected mental
+model, as well as how deep the human engages in this projection, might be
+driven by the same parameters as we mentioned for the \emph{initial capital of
+anthropomorphism} (section~\ref{sec:ica}).
+
+The cognitive \emph{level 3} is reached after a \emph{contextualized} interaction.
+A \emph{contextualized} interaction is \emph{explicitly purposeful} (the purpose
+of the interaction, be it purely entertainment, is explicit and conscious to the
+human), and takes place in an environment that fosters a stronger cognitive (and
+possibly affective/social) commitment from the human in the interaction
+(typically, at home). During this interaction, the human iteratively restates
+and reshapes his/her behavioral and mental model of the robot (\emph{How does
+the robot react to such and such situation/input?  What does the robot know
+about me? About itself? About our environment? What can the robot learn?}, etc.).
+
+This mental process depends on the human understanding of the robot's
+inner working, as well as his/her own tendency to anthropomorphize (the
+\emph{personality} in ICA factor), but at this
+stage, the \emph{perception} of the robot (its shape for instance) and its
+intended \emph{purpose} play a less important role. It is mostly a human-centric
+process.  The result of this third phase would be an iteratively adapted
+cognitive model of the robot.
+
+\subsection{Relation to the dynamics of anthropomorphism}
+
+These cognitive levels overlap over time but do not exactly match the
+\emph{Initialization}, \emph{Familiarization} and \emph{Stabilization} phases
+introduced in our model of the dynamics of anthropomorphism. In particular,
+the cognitive levels 1 and 2 are both included in the \emph{initialization} phase
+of the anthropomorphism model. Sub-cognitive anthropomorphism typically
+\emph{initiates} the novelty effect by rapidly engaging the human in the
+interaction through an initial projected agency, whereas cognitive level 2
+(projection of familiar mental models) supports the novelty effect by inducing
+beliefs that the robot is set up with possibly complex cognitive abilities.
+
+The cognitive level 3 also overlaps with the \emph{Familiarization} phase: as
+the human gets used to the robot, we hypothesize one restates and adapts its
+cognitive model of the robot by iteratively reshaping pre-existent, familiar
+models until it provides a satisfying support to explain and justify the
+observed robot behavior.
+
+A \emph{stable level of anthropomorphism} is reached when the adaptation process
+depicted in the cognitive level 3 reached a stable state, \ie the user's
+experience with the robot is correctly supported by the cognitive model he/she
+has built.
+
 \subsection{Role of disruptive behaviors}
 \label{sec:disruptive}
+
+A cognitive interpretation of anthropomorphism also allows to better interpret
+the role of unexpected robot behaviors, that we are \emph{disruptive} in regard
+to the cognitive process of building a mental model of the robot.
 
@@
 %% experience -> unexpected behavior should not impact the interaction child-robot BEFORE the theory of mind is established!
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-%
-%
-%		PART 3: EXPLANATIONS -- COGNITIVE CORRELATES, NEUROSCIENCE VIEW
-%
-%
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-% CLAIRE & SEVERIN:
-%
-%
-
-\section{Cognitive Correlates and Neuroscience Perspective}
-\label{sec:cognition-neuroscience}
-
-In this section, we discuss more speculative aspects and hypotheses that follow
-from the model. These aspects would benefit further investigations and
-experimental support.
-
-\subsection{Cognitive Interpretations}
-\label{sec:cognitive-model}
-
-\begin{figure}[htb]
-\centering
-%\resizebox{\linewidth}{!}{
-\begin{tikzpicture}
-\baselineskip=8pt
-
-\path[fill=gray!20] (0,0) rectangle (10.5,2);
-\path[fill=gray!50] (0,2) rectangle (10.5,4);
-\path[fill=gray!20] (0,4) rectangle (10.5,6);
-
-\draw (-0.3,1) node[rotate=90] {Level 1}
-      (-0.3,3) node[rotate=90] {Level 2}
-      (-0.3,5) node[rotate=90] {Level 3};
-
-\draw[->] (0,0) -- (11,0) node[anchor=north] {$t$};
-\draw[-|] (0,0) -- (0,6.5) node[anchor=east] {};
-% Us
-\draw[ultra thick, ->] (0,0) -- (1,2) -- (3,2) -- (4,4) -- (6,4) -- (7,6) --
-(9.5,6);
-\draw[ultra thick, dashed, ->] (3,2) -- (9.5,2);
-\draw[ultra thick, dashed, ->] (6,4) -- (9.5,4);
-
-\draw (11,1) node[align=left, anchor=west]{\scriptsize pre-cognitive\\\scriptsize anthropomorphism}; %label
-
-\draw (11,3) node[align=left, anchor=west] {\scriptsize{projection of existing}\\\scriptsize{mental models}\\\scriptsize{\it (familiarity)}}; %label
-
-\draw (11,5) node[align=left, anchor=west] {\scriptsize{adapted mental
-model} \\ $\to$ \scriptsize{adapted interaction}\\\scriptsize{\it (anthropomorphic or not)}}; %label
-
-\draw[dashed,->] (1,0.1) to[bend right] (2,1.9)  node at (4.5,1) {\tiny{\it observation (shape, motion, sound)}}; %label
-
-\draw[dashed,->] (4,2.1) to[bend right] (5,3.9)  node[align=left] at (7.5,3) {\tiny \it observation (interactive behavior) \\ \tiny \it or short interaction}; %label
-
-\draw[dashed,->] (7,4.1) to[bend right] (8,5.9)  node[align=left] at (9,5)
-{\tiny \it contextualized\\ \tiny \it interaction}; %label
-
-\end{tikzpicture}
-%}
-\caption{The three cognitive levels of anthropomorphism: Level 1 is the instinctive,
-sub-cognitive identification of living peers. {\it Empathy} is characteristic
-of this stage. After longer observation or short, non-contextualized interaction
-(typically, a lab environment), the user reaches Level 2: the user projects a
-mental model he/she is already familiar with onto the robot. After longer {\it
-contextualized} interaction (typically, at home), the user enters Level 3 of
-anthropomorphism: the user recomposes an accurate mental model of the robot,
-based on experience. This leads to adapted interaction modalities, that may
-still be anthropomorphic, or not.}
-\label{fig:cognitivemodel}
-\end{figure}
-
-We provide in this section a tentative interpretation of anthropomorphism in
-terms of cognitive correlates. We warmly welcome the feedback and
-comments from both the cognitive sciences and robotics communities to further
-discuss these findings.
-
-We propose three different cognitive phases (Figure~\ref{fig:cognitivemodel}),
-which do not directly match the previously presented three phases of
-anthropomorphism but are still related.
-
-\subsection{Cognitive Processes and Phases}
-
-The main underlying cognitive process in anthropomorphism is understood as
-perceiving and reasoning about something non-human and unfamiliar based on one's
-representation of the familiar and well-known concept of being
-human~\cite{epley_when_2008}. This led us to interpret the phases of
-anthropomorphic interactions as parallel cognitive phases
-(Figure~\ref{fig:cognitivemodel}).
-
-The so-called \emph{level 1} is the instinctive, pre-cognitive identification of
-living peers. That humans tend to anthropomorphize robots intuitively in this
-pre-cognitive way
-is supported by studies done by Rosenthal-von der Pütten
-\textit{et al.}~\cite{rosenthal-vonderputten_experimental_2013} who investigated
-the neural correlates of emotional reactions of humans towards a robot. {\it
-Empathy} is characteristic of this stage~\cite{rosenthalvonderPutten2013neural}.
-Anthropomorphism at this pre-cognitive stage might also be mediated by the
-human's mirror neurons system (neurons that fire both during execution of
-specific goal-oriented action and during the viewing of action directed toward
-the same goal~\cite{Rizzolatti1996, Kilner2009}) by allowing for a mapping of
-the robot's goal-directed actions into the human own motor
-repertoire~\cite{Gallese1998, Wolpert2003, cullen2013individual}.
-
-After a longer observation period (typically including complete action sequences
-of the robot) or short interaction (touching, short talk like greetings), we
-suggest the human reaches the cognitive \emph{level 2}: in this phase, the human
-starts building a behavioral and cognitive model of the robot that would support
-both the observed and imagined capabilities of the robot.  The \emph{familiarity
-thesis}~\cite{hegel_understanding_2008} supports the idea that the human
-first projects onto the robot mental models of similar agents he/she is already
-familiar with (ranging from animals to human adults, to pets and children). We 
-hypothesize that the nature of the projected mental
-model, as well as how deep the human engages in this projection, might be
-driven by the same parameters as we mentioned for the \emph{initial capital of
-anthropomorphism} (section~\ref{sec:ica}).
-
-The cognitive \emph{level 3} is reached after a \emph{contextualized} interaction.
-A \emph{contextualized} interaction is \emph{explicitly purposeful} (the purpose
-of the interaction, be it purely entertainment, is explicit and conscious to the
-human), and takes place in an environment that fosters a stronger cognitive (and
-possibly affective/social) commitment from the human in the interaction
-(typically, at home). During this interaction, the human iteratively restates
-and reshapes his/her behavioral and mental model of the robot (\emph{How does
-the robot react to such and such situation/input?  What does the robot know
-about me? About itself? About our environment? What can the robot learn?}, etc.).
-
-This mental process depends on the human understanding of the robot's
-inner working, as well as his/her own tendency to anthropomorphize (the
-\emph{personality} in ICA factor), but at this
-stage, the \emph{perception} of the robot (its shape for instance) and its
-intended \emph{purpose} play a less important role. It is mostly a human-centric
-process.  The result of this third phase would be an iteratively adapted
-cognitive model of the robot.
-
-\subsection{Relation to the model of anthropomorphism}
-
-These cognitive levels overlap but do not exactly match the
-\emph{Initialization}, \emph{Familiarization} and \emph{Stabilization} phases
-introduced in our model of the dynamics of anthropomorphism. In particular,
-the cognitive levels 1 and 2 are both included in the \emph{initialization} phase
-of the anthropomorphism model. Sub-cognitive anthropomorphism typically
-\emph{initiates} the novelty effect by rapidly engaging the human in the
-interaction through an initial projected agency, whereas cognitive level 2
-(projection of familiar mental models) supports the novelty effect by inducing
-beliefs that the robot is set up with possibly complex cognitive abilities.
-
-The cognitive level 3 also overlaps with the \emph{Familiarization} phase: as
-the human gets used to the robot, we hypothesize one restates and adapts its
-cognitive model of the robot by iteratively reshaping pre-existent, familiar
-models until it provides a satisfying support to explain and justify the
-observed robot behavior.
-
-A \emph{stable level of anthropomorphism} is reached when the adaptation process
-depicted in the cognitive level 3 reached a stable state, \ie the user's
-experience with the robot is correctly supported by the cognitive model he/she
-has built.
 

### 2014-03-25 paper.tex
new bib item and anthropomorphic design section almost done

@@
 The Uncanny Valley hypothesis \citep{mori_uncanny_1970} proposes that human-like
-designs of objects and non-human agents evoke a positive feeling of affinity in
-the human observer / user, which in turn reflects the experience of emotional
-engagement with and feelings of empathy for the non-human agent
-\citep{cheetham_human_2011}\fxfatal{uncanny valley is not about positive
-feeling!}. The positive effect of so-called \textbf{anthropomorphic form} is
-exploited in the design of artificial agents
+designs of objects and non-human agents can evoke both positive and negative feelings 
+of affinity in the human observer / user. Positive feelings reflect the experience of 
+emotional engagement with and feelings of empathy for the non-human agent
+\citep{cheetham_human_2011}. The positive effect of so-called
+\textbf{anthropomorphic form} is exploited in the design of artificial agents
 (\eg digital characters, robots) for several reasons. Amongst others,
@@
 An artifact-centered perspective explains anthropomorphism from the ascertainable 
-parts / the design of the non-human agent.
-The direction of causality in this view is that the non-human artifact (or a certain 
-feature of it) encourages the human to anthropomorphize the artifact / agent.
-This perspective assumes that humans directly respond to life-like and social cues 
-that the non-human agent or system emits, without thoughtful mental processing, 
-by simply applying stereotypes and heuristics to it. Humans naturally react to specific 
-cues. This is natural because, for instance, from early childhood 
-on, humans are inherently well-trained to perceive life \citep{epley_seeing_2007}, 
-or to respond to social cues, such as facial expressions, social gestures or turn-
-taking. 
-These cues can be of various senses and modalities. One of the most important aspects 
-is the outer appearance of the unknown agent or artifact. \cite{schmitz_concepts_2011} 
-argues that an agent's outer appearance is likely to have an important impact on how 
-the object is overall perceived (how it appears to the human). Thus, if a robot looks much like a human, it appears to be like a human, and is perceived accordingly.
-
-This fact is exploited in the design of robots and other things. Again, the basic 
-assumption here is that if an artifact 
-somehow resembles a human, it is likely to be treated similar to a human. If this 
-explanation of anthropomorphism is correct, people may respond automatically also to 
-social cues emitted by an artificial embodied agent such as a robot, and apply 
-human-human social schemas and norms to the occurring interactions. \hl{(However, at 
-the same time, the human-like design of things also raises expectations from the 
-human user side, to which we will come back later in more detail.)}
-The human-like design of robots implies various consequences, of which we will present some in the following.
-
-\subsubsection{Anthropomorphic design of robots and the Uncanny Valley hypothesis\\}
-
-%People's tendency to anthropomorphize technologies has been described in HCI 
-%\citep{reeves_media_1996} and related to digital agents; however the phenomenon 
-%seems to be more coined in HRI. There are several reasons for this, one of it stems 
-%from the unique characteristics of robots (their typical design).
-
-What do we mean by \textit{human-like / anthropomorphic form}?
+parts / the form of the non-human agent, namely the anthropomorphic design of it.
 Using the term \textit{``form''} to describe the design of an artifact, we refer 
@@
 anthropomorphic, zoomorphic, caricatured, functional \citep{fong_survey_2003}.
-
-The use of anthropomorphic (human-like) form in the design of non-human 
-things is as old as people's tendency to anthropomorphize. Anthropomorphic (and 
-also animal-shaped) forms were used already in prehistoric artworks and 
-illustrations, and they have a long-standing tradition in the design of daily life 
-artifacts and in general \citep{guthrie_bottles_2000}. The principle of human-like 
-form is probably most prominent in the design of robots, due to several reasons. 
-However, it has been controversially discussed since the early 1970ies, related to 
-\cite{mori_uncanny_1970} theory of the \texit{Uncanny Valley}, see Figure \ref{fig:uncanny_valley}.
-
-The underlying crucial point about the design are the implications that it holds, and the 
-suggestions for interactions that it makes to the user. In other words, the appearance 
-and function of a product, whether it is an appliance or a humanoid robot, affects the 
-way that people perceive it, interact with it, and build long-term relationships with 
-it \cite{bartneck_shaping_2004}. The relation between the design of a robot and the 
-user's perception of it, is also formulated in the \textit{Uncanny Valley} hypothesis \citep{mori_uncanny_1970}.
+The use of nature-inspired and in particular anthropomorphic (human-like) form in the 
+design of non-human things is as old and manifold as people's tendency to anthropomorphize. 
+Anthropomorphic (and also animal-shaped) forms were used already in prehistoric 
+artworks and illustrations, and they have a long-standing tradition in design in 
+general, and with respect of the design of daily life things, in particular 
+\citep{norman_design_1988,guthrie_bottles_2000}.
+
+The direction of causality in the artifact-centered view is that the non-human artifact 
+(or a certain feature of it) encourages the human to anthropomorphize the artifact / 
+agent. This perspective assumes that humans directly respond to life-like and social 
+cues that the non-human agent or system emits, without thoughtful mental processing, 
+by simply applying stereotypes and heuristics to it, and in turn apply 
+human-human social schemas and norms to the occurring interactions.
+This view is acceptable since humans naturally react to specific 
+cues. From early childhood 
+on, humans are inherently well-trained to perceive life \citep{epley_seeing_2007}, 
+or to respond to social cues, such as facial expressions, social gestures or turn-taking. 
+One has to keep in mind that these cues are of various senses and modalities in human-
+human interaction, and consequently human-like design also addresses several senses. 
+One of the most outstanding aspects is probably the outer appearance of an agent or 
+artifact (in particular when it is unknown or unfamiliar). \cite{schmitz_concepts_2011} 
+argues that an agent's outer appearance is likely to have an important impact on how 
+the object is overall perceived. Consequently, if a robot's outer form resembles a 
+human, the robot is likely to be treated similar to a human \hl{(\eg eye-contact is 
+established or the robot is greeted)}.
+
+People's natural reaction to anthropomorphic design is exploited in the design of 
+robots (in particular, social or also called \textit{sociable} robots 
+\citep{breazeal_sociable_2000}) and other things, however, consequences can be both of 
+positive and negative nature, which makes anthropomorphic form an interesting subject 
+of study.
+
+\subsubsection{How people perceive and interact with human-like robots\\}
+\label{sec:anthropomorphism-robotics}
+
+Most work that studies how far human users treat robots as social agents, builds on the 
+famous work of \cite{reeves_media_1996} in HCI. In the so-called \textit{Media 
+Equation}, the authors describe that people mindlessly react in a social way to their computer 
+and that they tend to even attribute human (social) characteristics to it -- despite 
+the fact that a computer does not have human-like characteristics. Apart from 
+computers, anthropomorphism has also been observed with digital / virtual characters 
+\citep{reeves_media_1996,nass_anthropocentrism_1995}, and artificial embodied agents, 
+such as robots. In short, one can say that with robots, and human-like robots in 
+particular, anthropomorphism is a commonly observed phenomenon. 
+But what are the motivations which underlie the efforts of enhancing anthropomorphism 
+through specific anthropomorphic design in robots? Why are anthropomorphic forms so 
+distinct and at the same time controversial in robotics? There is no one single answer 
+to these questions.
+
+The underlying central point about the human-like design of robots lies in the 
+implications that this design holds, and the suggestions for interactions that
+it makes to the human user. 
+In other words, the appearance 
+and function of a product, whether it is an appliance or a humanoid robot, affects how 
+people perceive it, interact with it, and build long-term relationships with 
+it \cite{bartneck_shaping_2004}. 
+The principle of human-like form is probably most prominent in the design of robots, 
+due to several reasons, such as to foster efficient interaction and increase 
+acceptance. An anthropomorphic design of a robot encourages people to reason about this 
+unfamiliar system \emph{as if} it was a human. To increase this tendency, robots are 
+designed with anthropomorphic (or lifelike) forms, or are able to display and use 
+human-social cues when interacting with humans.
+However, anthropomorphic robot designs have been controversially discussed and received 
+remarkable attention since the early 1970ies, related to \cite{mori_uncanny_1970} 
+theory of the \textit{Uncanny Valley}, see Figure \ref{fig:uncanny_valley}.
 
@@
 
-\subsubsection{How people perceive and interact with human-like robots\\}
-\label{sec:anthropomorphism-robotics}
-
-Most work that studies how far human users treat robots as social agents, builds on the 
-famous work of \cite{reeves_media_1996} in HCI. In the so-called \textit{Media 
-Equation}, the authors describe that people mindlessly react in a social way to their computer 
-and that they tend to even attribute human (social) characteristics to it -- despite 
-the fact that a computer does not have human-like characteristics. Apart from 
-computers, anthropomorphism has also been observed with digital / virtual characters 
-\citep{reeves_media_1996,nass_anthropocentrism_1995}, and artificial embodied agents, 
-such as robots. In short, one can say that with robots, and human-like robots in 
-particular, anthropomorphism is a commonly observed phenomenon. However, the 
-anthropomorphic design approach in robotics is controversially discussed.
-
-But what are the motivations which underlie the efforts of enhancing anthropomorphism through specific anthropomorphic design in robots?
-Why are anthropomorphic forms so distinct and at the same time controversial in robotics?
-There is no one single answer to this question.
-
-\hl{human-likeness has a positive effect\\}
-
-On one hand, developers and designers have discovered that human-like robots may better match the affordances that our to humans adapted world brings along.
-Also.
-anthropomorphic form and people's resulting consequence to anthropomorphize, appears to be generally beneficial for human-robot relations, especially with socially interactive robots \cite{fong_survey_2003}.
-Consequently, the domain of (social) robotics tries to exploit this fact by enhancing anthropomorphism through anthropomorphic robots: \textit{"Applying anthropomorphism or zoomorphism changes the way how users try to understand and make sense of a [system] by projecting everyday \hl{expectations} of human and animalistic life onto it."} \cite{schmitz_concepts_2011}.
+\paragraph*{Anthropomorphic form can be advantageous for HRI\\}
+
+On one hand, developers and designers have discovered that human-like robots may better 
+match the affordances that our to humans adapted world brings along. Also, up to a 
+certain point, anthropomorphic form as it increases anthropomorphism,
+appears to be generally beneficial for human-robot relations, especially with socially 
+interactive robots \cite{fong_survey_2003}. Consequently, the domain of (social) 
+robotics tries to exploit this fact by enhancing anthropomorphism through 
+anthropomorphic robots: Applying anthropomorphism or zoomorphism changes the 
+way how users try to understand and make sense of a system by projecting everyday 
+\hl{expectations} of human and animalistic life onto it. \cite{schmitz_concepts_2011}.
 
@@
 
-\hl{human-likeness has a negative effect\\}
-
-However, the anthropomorphic form also 
+Anthropomorphism represents just one of many examples of induction whereby "people reason about an unknown stimulus based on a better-known representation of a related stimulus" \cite{epley_when_2008}, in this case reasoning about a non-human agent based on representation of the self or other humans.
+
+\paragraph*{Anthropomorphic form can be disadvantageous for HRI\\}
+
+The anthropomorphic form also 
 increases people's expectations of the agent, and consequently, a very human-like 
-appearing robot is expected to act like a human. But today's artificial systems are 
-not able (yet) to mimic human movements, or human social cues in an acceptable way. 
+appearing robot is not only perceived but also expected to act like a human. However, today's artificial systems are 
+not able (yet) to well mimic human movements, or human social cues in an acceptable way. 
 The case is that the artificial agent pretends to be human but fails, and this is 
@@
 
-\hl{(ethical issues, maybe put this rather in the end)}
-Another critical point with the use of human-like form in artificial agents are 
-ethical aspects. For instance, we need to consider how far we actually want an 
-\textit{artificial agent} to resemble a human -- or ourself. Even though we do not 
-discuss these aspects in this article, we think the HRI / robotics community needs 
-to consider questions of how far an artificial agent should act ``as if it would be 
-social'' toward humans. What implications does an anthropomorphic design of robots 
-have? What happens as soon as the artificial agent is considered a \textit{moral 
-agent} \cite{sullins_when_2006}? Using \textit{socially interactive robots} in 
-contexts involving elderly care or rehabilitation for disabled / handicapped 
-persons, autistic children is a controversially discussed topic 
-\cite{robins_robots_2005}.
-
 % Simulation Theory
@@
 %intentions to robots \hl{(REFS)} and that they show empathetic behavior toward robots 
-%\citep{rosenthal-vonderputten_experimental_2013}. Summing it up, there is a huge and 
-%constantly growing body of literature that describes anthropomorphism in HCI and HRI. 
-%Despite the phenomenon is well studied, we still know rather little about it, so that 
-%at conferences and symposiums, anthropomorphism is still a ``hot topic''; however, at 
-%the same time theories related to anthropomorphism, such as the \textit{``Uncanny 
-%Valley''} are controversially discussed.
+%\citep{rosenthal-vonderputten_experimental_2013}.
 
@@
 
-Anthropomorphism represents just one of many examples of induction whereby "people reason about an unknown stimulus based on a better-known representation of a related stimulus" \cite{epley_when_2008}, in this case reasoning about a non-human agent based on representation of the self or other humans.
-This supports the usual role we assign to anthropomorphism in robotics: the anthropomorphic design of a robot encourages people to reason about this unfamiliar system \emph{as if} it was a human.
-To increase this tendency, robots are designed with anthropomorphic forms (human-like or lifelike forms, in the broader sense), or are able to display and use human-social cues when interacting with humans.\\
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+%
+%
+%		HUMAN-CENTERED PERSPECTIVE: SOCIAL PHENOMENON
+%
+%
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{A human-centered perspective on anthropomorphism}
+\label{sec:human-centered}
+
+In contrast to the artifact-centered perspective, in the human-centered perspective the argumentation is, that the human is motivated to anthropomorphize the non-human artifact).
+As already mentioned, both these views go hand in hand.
+
+Humans tend to perceive human-like characteristics such as physical appearance, emotional states, or inner mental states and motivations in non-human agents that do not have these characteristics themselves, such as animals, natural forces, religious agents, technological gadgets, or mechanical devices \citep{epley_when_2008}.\footnote{According to \cite{epley_when_2008}, a non-human agent can be anything that acts -- or is believed to act -- with apparent independence.}  Anthropomorphism has received remarkable attention across various different domains, such as natural sciences, developmental and social psychology, Human-Computer Interaction (HCI), and Human-Robot Interaction (HRI).
+
+Originally, the term \textbf{anthropomorphism} comes from the Greek \textit{`anthropos'} for `man' (or `human') and \textit{`morphe'} for `form / structure' (or `shape').
+Anthropomorphism is generally understood as people's tendency to perceive a non-human agent as if it had some human characteristics or traits.
+In turn, how a person perceives an agent further determines how she relates to and behaves towards the agent, or how she may behave in light of this agent \citep{epley_when_2008}.
+As such, anthropomorphism can be seen as a special kind of relationship between a human interacting with a non-human agent.
+This anthropomorphic relationship is often characterized by the fact that the human attributes human-unique characteristics to the non-human agent.
+Since anthropomorphism becomes observable through these attributions, some definitions claim that anthropomorphism is not the perception but rather the attribution of human attributes to non-human agents, and name thoughts, emotions, and intentions as examples.
+The most prominently anthropomorphized non-human agents are probably animals and robots \citep{duffy_anthropomorphism_2003,schmitz_concepts_2011}.
+
+Apart from anthropomorphism there also exists the term \textbf{animism}, which can be defined as the attribution of life to the nonliving.
+The study of animism was pioneered by Piaget in the 1920s with his work on \textit{The Child's Conception of the  World}.
+He found that children tend to regard many inanimate objects as capable of sensations, emotions and intentions, and called this view `animism'.
+Since then, children's inferences about the world have been studied intensively.
+However, there is an agreement that children's views and concepts of living, animal, and plant evolve as they grow up.
+Using this definition, animism differs in two main aspects from anthropomorphism:
+First, the property which is ascribed differs: life-likeness is not human-unique but applies to all living beings.
+The second difference between anthropomorphism and animism stems from the agent (or better artifact) to which life is attributed.
+Living beings (most importantly animals) are naturally excluded from being animized.
+Consequently, while animals can be anthropomorphized (perceived to have human unique characteristics), they cannot be animized as they are already living beings.
+(Similarly to the fact that humans cannot be anthropomorphized as they are already humans.)
+Often synonymously used to animism is the term \textbf{zoomorphism}, which applies to the cases when non-lifelike instances / things are associated with animalistic attributes, excluding human-specific traits.
+Both anthropomorphism and animism / zoomorphism can be embraced by the concept of \textbf{life-likeness}.
+
+There exists also the inverse phenomenon to anthropomorphism, which can be found in the literature as \textbf{dehumanization} \citep{haslam_dehumanization:_2006}, or \textbf{mechanomorphism} \citep{caporael_anthropomorphism_1986}.
+We do not treat this here.
+
+ \begin{figure}[b]\centering
+% Use the relevant command to insert your figure file.
+% For example, with the graphicx package use
+  \includegraphics[scale=1]{north-wind.jpg}
+  \includegraphics[scale=1]{sun.jpg}
+% figure caption is below the figure
+ \caption{Milo Winter illustration of Aesop Fable \textit{The North Wind and the Sun}, 1919; both natural forces wind and sun are anthropomorphized with a human face; picture source: wikipedia}
+ \label{fig:north-wind-sun}       % Give a unique label
+ \end{figure}
+
+To illustrate better how anthropomorphism differs from attributions of animacy or life-
+likeness, it is worth looking at paraphrases and examples of it. That is to say, 
+anthropomorphism can alternatively be understood as \textbf{humanization} or 
+\textbf{personification} of anything other than a human being. Personification has 
+ancient roots, \eg in mythology but also in storytelling. Anthropomorphism was also 
+used to describe and be able to predict natural forces or anticipate great spirits, for 
+instance. An illustration of an anthropomorphism related to nature is shown in Figure 
+\ref{fig:north-wind-sun}. In this Milo Winter (1919) drawing \textit{"The North Wind 
+and the Sun"}, both north wind and sun are given a human face.
+
+\subsubsection{Diverse understandings of anthropomorphism\\}
+
+Amongst others, one reason for this might be that there exist several understandings of what anthropomorphism is \hl{(REF Peter Ruijten, HRI 2014.)}
 
@@
 
-%% -> Commented out the overview as it does not match what we actually present... maybe we need a new one?
-% We would further like to review and discuss research on anthropomorphism in
-% robotics and human-like design of robots. We first provide a comprehensive
-% understanding of the phenomenon drawing on theories from developmental
-% psychology and cognitive sciences. We then present the trends of different
-% kinds of anthropomorphic forms in robots and discuss their role in social
-% robotics. The article integrates related work from human-robot interaction
-% studies, reporting on findings from experiments with human subjects
-% interacting with and evaluating various types of systems. We try to give a
-% coherent view on the topic, outline similarities and antithetic findings, and
-% contribute to a better understanding of anthropomorphism in robotics, and the
-% acceptance of human-like characteristics in robots. We also aim to
-% constructively discuss anthropomorphic design of personal and socially
-% interactive robots.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-%
-%
-%		HUMAN-CENTERED PERSPECTIVE: SOCIAL PHENOMENON
-%
-%
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{A human-centered perspective on anthropomorphism}
-\label{sec:human-centered}
-
-In contrast to the artifact-centered perspective, in the human-centered perspective the argumentation is, that the human is motivated to anthropomorphize the non-human artifact).
-As already mentioned, both these views go hand in hand.
-
-Humans tend to perceive human-like characteristics such as physical appearance, emotional states, or inner mental states and motivations in non-human agents that do not have these characteristics themselves, such as animals, natural forces, religious agents, technological gadgets, or mechanical devices \citep{epley_when_2008}.\footnote{According to \cite{epley_when_2008}, a non-human agent can be anything that acts -- or is believed to act -- with apparent independence.}  Anthropomorphism has received remarkable attention across various different domains, such as natural sciences, developmental and social psychology, Human-Computer Interaction (HCI), and Human-Robot Interaction (HRI).
-
-Originally, the term \textbf{anthropomorphism} comes from the Greek \textit{`anthropos'} for `man' (or `human') and \textit{`morphe'} for `form / structure' (or `shape').
-Anthropomorphism is generally understood as people's tendency to perceive a non-human agent as if it had some human characteristics or traits.
-In turn, how a person perceives an agent further determines how she relates to and behaves towards the agent, or how she may behave in light of this agent \citep{epley_when_2008}.
-As such, anthropomorphism can be seen as a special kind of relationship between a human interacting with a non-human agent.
-This anthropomorphic relationship is often characterized by the fact that the human attributes human-unique characteristics to the non-human agent.
-Since anthropomorphism becomes observable through these attributions, some definitions claim that anthropomorphism is not the perception but rather the attribution of human attributes to non-human agents, and name thoughts, emotions, and intentions as examples.
-The most prominently anthropomorphized non-human agents are probably animals and robots \citep{duffy_anthropomorphism_2003,schmitz_concepts_2011}.
-
-Apart from anthropomorphism there also exists the term \textbf{animism}, which can be defined as the attribution of life to the nonliving.
-The study of animism was pioneered by Piaget in the 1920s with his work on \textit{The Child's Conception of the  World}.
-He found that children tend to regard many inanimate objects as capable of sensations, emotions and intentions, and called this view `animism'.
-Since then, children's inferences about the world have been studied intensively.
-However, there is an agreement that children's views and concepts of living, animal, and plant evolve as they grow up.
-Using this definition, animism differs in two main aspects from anthropomorphism:
-First, the property which is ascribed differs: life-likeness is not human-unique but applies to all living beings.
-The second difference between anthropomorphism and animism stems from the agent (or better artifact) to which life is attributed.
-Living beings (most importantly animals) are naturally excluded from being animized.
-Consequently, while animals can be anthropomorphized (perceived to have human unique characteristics), they cannot be animized as they are already living beings.
-(Similarly to the fact that humans cannot be anthropomorphized as they are already humans.)
-Often synonymously used to animism is the term \textbf{zoomorphism}, which applies to the cases when non-lifelike instances / things are associated with animalistic attributes, excluding human-specific traits.
-Both anthropomorphism and animism / zoomorphism can be embraced by the concept of \textbf{life-likeness}.
-
-There exists also the inverse phenomenon to anthropomorphism, which can be found in the literature as \textbf{dehumanization} \citep{haslam_dehumanization:_2006}, or \textbf{mechanomorphism} \citep{caporael_anthropomorphism_1986}.
-We do not treat this here.
-
- \begin{figure}[b]\centering
-% Use the relevant command to insert your figure file.
-% For example, with the graphicx package use
-  \includegraphics[scale=1]{north-wind.jpg}
-  \includegraphics[scale=1]{sun.jpg}
-% figure caption is below the figure
- \caption{Milo Winter illustration of Aesop Fable \textit{The North Wind and the Sun}, 1919; both natural forces wind and sun are anthropomorphized with a human face; picture source: wikipedia}
- \label{fig:north-wind-sun}       % Give a unique label
- \end{figure}
-
-To illustrate better how anthropomorphism differs from attributions of animacy or life-likeness, it is worth looking at paraphrases and examples of it.
-That is to say, anthropomorphism can alternatively be understood as \textbf{humanization} or \textbf{personification} of anything other than a human being.
-Personification has ancient roots, \eg in mythology but also in storytelling.
-Anthropomorphism was also used to describe and be able to predict natural forces or anticipate great spirits, for instance.
-An illustration of an anthropomorphism related to nature is shown in Figure \ref{fig:north-wind-sun}.
-In this Milo Winter (1919) drawing \textit{"The North Wind and the Sun"}, both north wind and sun are given a human face.
-
-\subsubsection{Diverse understandings of anthropomorphism\\}
-
-Amongst others, one reason for this might be that there exist several understandings of what anthropomorphism is \hl{(REF Peter Ruijten, HRI 2014.)}
-
-Anthropomorphism is used in different senses throughout different disciplines \citep{duffy_anthropomorphism_2003} which makes it difficult to synthesize findings.
-Depending on which understanding of anthropomorphism is applied, not everything colloquially labeled as \emph{anthropomorphism} really is anthropomorphism.\footnote{For instance, it is not always clear whether a person (may it be an adult or a child) who gives and anthropomorphic response, believes that the other agent really thinks or acts like a human or whether she is using anthropomorphism in a metaphoric sense.\citep{leeds_childrens_1992}} We need to be clear about what we mean by anthropomorphism because at the moment, there are different, even partially conflicting understandings of anthropomorphism, not only across but also within disciplines \cite{duffy_anthropomorphism_2002}.
-In particular, in the multi-disciplinary field of HRI, anthropomorphism is understood and interpreted in such a variety of ways that it is almost impossible to bring together and compare the research work done.
-In turn, it seems that the understanding of anthropomorphism in HRI has not improved much over the last decade but has only become more diverse (which is ok, too, but certainly a deeper understanding and common grounds would be convenient).
+Anthropomorphism is used in different senses throughout different disciplines 
+\citep{duffy_anthropomorphism_2003} which makes it difficult to synthesize findings. 
+Depending on which understanding of anthropomorphism is applied, not everything 
+colloquially labeled as \emph{anthropomorphism} really is anthropomorphism.
+\footnote{For instance, it is not always clear whether a person (may it be an adult or 
+a child) who gives and anthropomorphic response, believes that the other agent really 
+thinks or acts like a human or whether she is using anthropomorphism in a metaphoric 
+sense.\citep{leeds_childrens_1992}} We need to be clear about what we mean by 
+anthropomorphism because at the moment, there are different, even partially conflicting 
+understandings of anthropomorphism, not only across but also within disciplines 
+\cite{duffy_anthropomorphism_2002}. In particular, in the multi-disciplinary field of 
+HRI, anthropomorphism is understood and interpreted in such a variety of ways that it 
+is almost impossible to bring together and compare the research work done. In turn, it 
+seems that the understanding of anthropomorphism in HRI has not improved much over the last decade but has only become more diverse (which is ok, too, but certainly a deeper 
+understanding and common grounds would be convenient).
 
@@
 
-\paragraph{Attractiveness Delta}
-
-Besides, we propose to call \emph{attractiveness delta}, noted $\Delta_{a}$, the
-difference between the initial capital of anthropomorphism \ICA for a given tuple (user,
-robot, context) and the anthropomorphism peak \AntMax (Figure~\ref{fig:dynamics}).
-This can be interpreted as the initial \emph{excitement} over the robot, or how
-much a user tend to increase his/her anthropomorphic engagement when he/she
-starts to actually interact with the robot.
-
 \subsubsection{Familiarization Phase}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-%
-%
-%				DISCUSSION + FUTURE WORK
-%
-%
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% JULIA & SEVERIN: how to measure / quantify anthropomorphism ...
-% CLAIRE: FMRI study idea
-
-\section{Discussion}
-\label{sec:discussion}
+\subsection{Limitations}
 
@@
 conversely relied on to have the robot itself iteratively adapting its
-behaviour? In particular, we hypothesize that the so-called novelty effect
+behavior? In particular, we hypothesize that the so-called novelty effect
 represents a peak in anthropomorphic manifestations, followed by mostly
-deception-driven refinements of the cognitive behavioural model of the robot.
-Could we imagine that the robot pro-actively \emph{verbalises} its own limits,
-in a timely manner (likely before the end of the novely effect). And how would
+deception-driven refinements of the cognitive behavioral model of the robot.
+Could we imagine that the robot pro-actively \emph{verbalizes} its own limits,
+in a timely manner (likely before the end of the novelty effect). And how would
 this affect the cognitive models built by the human?
@@
 \fxwarning{To be completed/rephrased into a discussion}
+
+\citep{ruijten_introducing_2014}
 
@@
 
+\subsection{Ethical aspects of anthropomorphism and human-like form of robots}
+
+% our message kind of is that it would be favorable to sustain anthropomorphism over 
+% extended periods of time ... however, this is ethically questionable, when thinking 
+% of emotional bonding with an artificial agent, etc. --> we sould elaborate on this a % bit
+
+Another critical point with the use of human-like form in artificial agents are 
+ethical aspects. For instance, we need to consider how far we actually want an 
+\textit{artificial agent} to resemble a human -- or ourself. Even though we do not 
+discuss these aspects in this article, we think the HRI / robotics community needs 
+to consider questions of how far an artificial agent should act ``as if it would be 
+social'' toward humans. What implications does an anthropomorphic design of robots 
+have? What happens as soon as the artificial agent is considered a \textit{moral 
+agent} \cite{sullins_when_2006}? Using \textit{socially interactive robots} in 
+contexts involving elderly care or rehabilitation for disabled / handicapped 
+persons, autistic children is a controversially discussed topic 
+\cite{robins_robots_2005}.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2014-03-25 paper.tex
just started working on part 5- mirror neurons and robots

--- 2014-03-25 paper.tex
@@
 \floatstyle{plaintop}
-
-\usepackage{paralist} % inparaenum
 
@@
 
+%{Intro when start with anthropomorphic design}
 The Uncanny Valley hypothesis \citep{mori_uncanny_1970} proposes that human-like
@@
 engagement with and feelings of empathy for the non-human agent
-\citep{cheetham_human_2011}\fxfatal{uncanny valley is not about positive
-feeling!}. The positive effect of so-called \textbf{anthropomorphic form} is
-exploited in the design of artificial agents
+\citep{cheetham_human_2011}. The positive effect of so-called
+\textbf{anthropomorphic form} is exploited in the design of artificial agents
 (\eg digital characters, robots) for several reasons. Amongst others,
@@
 to avoid ``falling'' into this Uncanny Valley with their human-like designs of
-artificial agents. Consequently, there is a considerable research effort to
-better understand the boundaries of anthropomorphic design and their effects
-on the interaction and experience. To date, findings have been however
-inconsistent \citep{cheetham_human_2011}.
-
-Along this line, this article aims at fostering a better understanding of
-anthropomorphism (noted \Ant in this paper) by considering the phenomenon
-\textbf{as a whole}: robotics researchers often tend to believe that
-anthropomorphism only describes a static set of human-like features of a robot
-(like shape, speech capabilities, facial expressions, etc.). We refer to these
-characteristics as the \emph{anthropomorphic design} of the
-robot~\cite{fink_anthropomorphism_2012}. But \emph{anthropomorphism} in general
-refers to the larger \emph{social phenomenon} that emerges from the (real or
-imagined) \emph{interaction} between a robot and a
-user~\citep{persson_anthropomorphism_2000}. According to~\cite{epley_when_2008},
-this includes for instance emotional states, motivations, intentions
-\emph{ascribed by the user} to the robot. As such, the dynamic and
-socio-cognitive dimensions of anthropomorphism are essential to understand the
-complex bonds that human users build with the robots.
+artificial agents. Consequently, there is a considerable research effort into
+better understanding the boundaries of anthropomorphic design and their effect
+on the interaction and experience. However, findings have been inconsistent
+\citep{cheetham_human_2011}.
+
+A phenomenon that is often studied related to the human-like design of robots is
+\textbf{anthropomorphism} (noted \Ant in this paper). Besides a feeling of affinity, and empathy,
+anthropomorphism can be understood as being one of the resulting (and  more or
+less desired) effects of the anthropomorphic design of artificial agents (up to
+the first positive peak). The essence of anthropomorphism is the human user's
+perception of human-likeness in the non-human agent. Logically, anthropomorphism
+is said to be enhanced with increased human-like design of the agent. There are
+various other reasons and explanations for why people tend to anthropomorphize
+non-human agents. In general, as anthropomorphism emerges in a (real or
+imagined) interaction \citep{persson_anthropomorphism_2000} between at least two
+players (the human who anthropomorphizes and the non-human agent which is
+anthropomorphized) there are also two main perspectives on the phenomenon: an
+artifact-centered (design) and a human-centered (cognitive, psychological) one.
+The Uncanny Valley hypothesis can be categorized as being part of first,
+artifact-centered approach, to understand anthropomorphism.
 
@@
 results. We observed anthropomorphism in several short- and long-term human-robot
-interaction studies that we carried out with embodied robots, both in
-ecologically valid real-world environments and controlled lab settings. Those
-experiments are presented in details in section~\ref{sec:overview-studies}. We
-only highlight here some qualitative results in order to trigger some initial
-thoughts.
-
-Figures~\ref{fig:roomba-activities} and~\ref{fig:roomba-perception} (on
-page~\pageref{fig:roomba-perception}) give a first perspective on how naive
-users interact and perceive robots over a long period of time. Here,
-\emph{Roomba} vacuum cleaning robots were given to nine households for a
-6-months period. The aim was to explore how people use and perceive the robot
-over time, and how they generally live with the Roomba in their home. At various
-time points, users were asked to rate their perception of different features of
-the robot on a 7-point rating scale. As Figure~\ref{fig:roomba-perception}
-shows, some features remained stable over time (\emph{ease of use} and
-\emph{fun}), and others decreased: the perceived \emph{usefulness},
-\emph{intelligence} and \emph{impact} on their household.  \emph{intelligence}
-and \emph{impact} reflect the cognitive engagement of the user towards the
-machine: we can assume that one does not care to engage in a (cognitive)
-interaction with an artifact perceived as non-intelligent and with no impact on
-his/her life (and the level of activity pictured on
-Figure~\ref{fig:roomba-activities} qualitatively confirms this intuition). Even
-if one can argue that the Roomba is not designed to foster interaction, it
-raises a first question: how to sustain engagement between a robot and a human
-over a long period of time? And, as a pre-requisite to answer, do we actually
-understand the psychological phenomenon, and can we effectively account for the
-dynamics of these interactions?
+interaction studies that we carried out with embodied robots, mostly in
+real-world settings. There is not much research that investigates
+anthropomorphism based on real interaction between a human and a robot, and
+above all in natural settings and over extended periods of time.
+
+Figure~\ref{fig:roomba-perception} gives a first perspective on how naive
+users perceive robots over a long period of time. Here, \emph{Roomba} vacuum cleaning robots
+were given to nine households for a 6-months period. The aim was to explore how
+people use and perceive the robot over time, and how they generally live with
+the Roomba in their home. At various time points, users were asked to rate
+their perception of different features of the robot on a 7-point rating scale. As
+Figure~\ref{fig:roomba-perception} shows, some features remained stable over time
+(\emph{ease of use} and \emph{fun}), and others decreased: the perceived
+\emph{usefulness}, \emph{intelligence} and \emph{impact} on their household.
+\emph{intelligence} and \emph{impact} reflect the cognitive engagement of the
+user towards the machine: we can assume that one does not care to engage in a
+(cognitive) interaction with an artifact perceived as non-intelligent and with
+no impact on his/her life. Even if one can argue that the Roomba is not designed
+to foster interaction, the question is raised: how to sustain engagement between
+a robot and a human over a long period of time? And, as a pre-requisite, do we
+actually understand the psychological phenomenon, and can we effectively account
+for the dynamics of these interactions?
 
 Those questions are certainly not new, but paradoxically, while anthropomorphism
-in robotics is a commonly discussed trait of human-robot interaction, it appears
-that we lack formal grounds and models that would account for the long-term
-dynamics of these interactions.
-
-Figure~\ref{fig:qualitative-score} (page~\pageref{fig:qualitative-score}) calls
-for other initial remarks. This diagram comes from a study where 13 pairs of
-children (4-5 years old) played for about 20 minutes a Domino game with a robot
-(the robot was tasked to carry domino pieces from one child to the other). The
-$x$-axis represents the number of social interactions between the children and
-the robot (like talking or showing objects), based on video annotations. On the
-$y$-axis, we have a synthetic qualitative measurement of anthropomorphic
-projections based on two questionnaires. The correlation between both these
-values is significantly \emph{negative}: the more the children engaged into
-interaction, the less prone to anthropomorphic projections they were. This
-diagram also highlights an interesting cluster of children who did not interact
-much with the robot, and still reported a strong anthropomorphic perception of
-the robot.
-
-These results may seem counter-intuitive at first sight, and illustrate that the
-mechanisms that relate anthropomorphism to adoption and engagement are
-non-trivial. In section~\ref{sec:cognition-neuroscience}, we sketch a model of
-the cognitive correlates of anthropomorphism that partially account for these
-results.
+in robotics is a commonly discussed and studied trait of human-robot
+interaction, it appears that it lacks a formal ground and unified understanding to
+take into account the wide range of phenomena that it encompasses.
 
@@
 
-These first remarks lead to the main question we attempt to address in this
-article: how can we understand \emph{anthropomorphism} as a whole, and in such a
-way that is support improved human-robot interactions?
-
-Based on an extensive literature review~\citep{fink_anthropomorphism_2012},
-several field and lab studies~\citep{ fink_anthropomorphic_2012,
-fink_living_2013, fink2014which, lemaignan2014dynamics} and insights from the
-cognitive neurosciences, we propose to discuss anthropomorphism from three
-complementary perspectives.
-
-First, we would like to clarify what anthropomorphism actually \emph{means}:
-besides the \emph{artifact-centered} understanding of anthropomorphism, it
-seems important to explicit the human and social factors of anthropomorphism.
-
-Then, we propose a model to understand how anthropomorphism evolves over time.
-These dynamics are non-monotonic, and psychological factors like the
-\emph{novelty effect} play here a key role.
-
-Finally, we adopt a third perspective on anthropomorphism by investigating its
-\emph{cognitive correlates}. Several studies previously showed that we build
-instinctive bonds with robots as soon as we attribute animacy, and we also know
-from social psychology some of the mechanisms that lead to
-\emph{familiarization}. We attempt here to ``connect the dots'', in order to
-build a practical model of the cognitive stages we encounter in human-robot
-interaction.
-
-\paragraph{Two hypotheses} Our research question also translates to two
-hypotheses, which structure the reflections of this article:
-
-\begin{enumerate}
-
-\item A person's tendency to anthropomorphize a robot
+So far, the HRI community has not much investigated how anthropomorphism in
+human-robot interactions evolves over time. In robotics, anthropomorphism is traditionally
+perceived as a static feature triggered by the human-like design of a robot that once observed (during a
+short-term interaction) reflects a sustaining social effect. Based on a previously published
+literature review~\citep{fink_anthropomorphism_2012}, a
+long-term field study in a natural environment~\citep{fink_living_2013}, a 
+content analysis of online discussion 
+forums~\citep{fink_anthropomorphic_2012}, and an on-going child-robot 
+interaction study, we believe that anthropomorphic
+effects are based on several factors, and that they do evolve over time in 
+non-monotonic ways. Moreover, we assume that these variances and dynamics 
+play a central role in sustaining engagement in human-robot interaction.
+
+This article is organized around two main hypothesis that we formulated based on 
+our empirical studies of HRI, and by integrating previous work from several domains.
+
+\begin{itemize}
+    \item \textbf{Hypothesis 1~} A person's tendency to anthropomorphize a robot
 is based on several factors, including (but not limited to) (1) the 
 design of the robot, (2) the personal characteristics of the human user, 
-    and (3) the context and situation of use. For instance, a social context
-    and purpose of the robot increase anthropomorphism: \textit{anthropomorphism
-    as a multi-factor phenomenon}.
-
-\item A person's tendency to anthropomorphize a robot
+and (3) the context and situation of use. For instance, a social 
+context and purpose of the robot increase anthropomorphism. 
+\textit{(anthropomorphism as a multi-factor phenomenon)}
+	\item \textbf{Hypothesis 2~} A person's tendency to anthropomorphize a robot 
 evolves in a non-linear way over time and with growing experience that the 
-    person has with the robot. For instance, a more experienced user will
-    perceive the robot as more familiar and predictable, and in turn
-    anthropomorphizes the robot less: \textit{anthropomorphism as a dynamic
-    phenomenon}.
-
-\end{enumerate}
-
-\subsection{Article overview}
-
-\begin{inparaenum}[\itshape 1)\upshape]
+person has with the robot. For instance, a more experienced user will perceive 
+the robot as more familiar and predictable, and in turn anthropomorphizes the 
+robot less. \textit{(anthropomorphism as a dynamic phenomenon)}
+\end{itemize}
+
+We propose to formalize these variances and dynamic effects into a model that we call the
+\emph{Dynamics of Anthropomorphism}. We hope that it may support further
+discussions and reflections on how anthropomorphism impacts human-robot
+interaction on the long run, and also foster research on the affective bonds
+induced by anthropomorphic projections on robots.
+Through our model, we propose to represent how the level of anthropomorphic effects (\ie
+observable manifestations of anthropomorphism) evolves over a long-term
+human-robot interaction (Figure~\ref{fig:dynamics}). By long-term interaction,
+we mean direct (non-mediated), repeated interaction with the same robot, over
+an extended period of time (typically longer than a week).
+
+%In this article, we would further like to share some critical but constructive
+%considerations on anthropomorphism in robotics and HRI. Thereby, we contribute
+%to a better understanding of this complex phenomenon related to robots.
 
@@
 \ref{sec:overview-studies}, we give a brief overview on the various studies that
-we conducted to investigate anthropomorphism, namely \item the Roomba study,
-\item the Forum study, \item the Ranger domino study. Next, Section
-\ref{sec:anthropomorphism} aims to establish a common ground in the
-understanding of anthropomorphism. We first explore an artifact-centered
-perspective and briefly outline how the human-like design of agents can
-encourage anthropomorphism.  Then, we explore a human-centered perspective
-by integrating theories from cognitive science, developmental and social
-psychology that serve to explain anthropomorphism. At the end of this
-section we bring both perspectives together and interpret that
-anthropomorphism is a multi-factor phenomenon.  Based on the two previous
-sections, Section~\ref{sec:our-ideas} introduces an initial model of the
-\textit{dynamics of anthropomorphism}. This model describes the variances
-and dynamics of people's tendency to anthropomorphize an artificial agent,
-such as a robot.  Then Section \ref{sec:cognition-neuroscience} presents a
-cognitive and neuroscience perspective on anthropomorphism to consolidate
-our considerations and the proposed model.  This is followed by a discussion
-about the limitations of our approach (Section \ref{sec:discussion}) and the
-existing and alternative ways to measure anthropomorphism in human-robot
-interactions.  Finally, Section \ref{sec:conclusion} concludes this article
-and offers starting points for further research on anthropomorphism and the
-effect of the human-like design approach in robotics.
-
-\end{inparaenum}
+we conducted to investigate anthropomorphism, namely (1) the Roomba study, (2)
+the Forum study, (3) the Ranger domino study. Next, in Section 
+\ref{sec:anthropomorphism} we aim to establish a common ground in the understanding 
+of anthropomorphism. We first explore an artifact-centered perspective and briefly
+outline how the human-like design of agents can encourage anthropomorphism.
+Then, we explore a human-centered perspective by integrating theories from
+cognitive science, developmental and social psychology that serve to explain
+anthropomorphism. At the end of this section we bring both perspectives together
+and interpret that anthropomorphism is a multi-factor phenomenon.  Based on the
+two previous sections, we propose an initial model of the \textit{``Dynamics of
+Anthropomorphism''} in Section \ref{sec:our-ideas}. This model describes the
+variances and dynamics of people's tendency to anthropomorphize an artificial
+agent, such as a robot.  Next, in Section \ref{sec:cognition-neuroscience} we
+present a cognitive and neuroscience perspective on anthropomorphism to
+consolidate our considerations and the proposed model.  This will be followed by
+a discussion about the limitations of our approach (Section
+\ref{sec:discussion}). Further, we debate existing and alternative ways to
+measure anthropomorphism in human-robot interactions.  Finally, Section
+\ref{sec:conclusion} concludes this article and offers starting points for
+further research on anthropomorphism and the effect of the human-like design
+approach in robotics.
 
@@
 that the non-human agent or system emits, without thoughtful mental processing, 
-by simply applying stereotypes and heuristics to it. Humans naturally react to specific 
-cues. This is natural because, for instance, from early childhood 
+by simply applying stereotypes and heuristics to it. In fact, from early childhood 
 on, humans are inherently well-trained to perceive life \citep{epley_seeing_2007}, 
-or to respond to social cues, such as facial expressions, social gestures or turn-
-taking. 
-These cues can be of various senses and modalities. One of the most important aspects 
-is the outer appearance of the unknown agent or artifact. \cite{schmitz_concepts_2011} 
-argues that an agent's outer appearance is likely to have an important impact on how 
-the object is overall perceived (how it appears to the human). Thus, if a robot looks much like a human, it appears to be like a human, and is perceived accordingly.
-
-This fact is exploited in the design of robots and other things. Again, the basic 
+and to respond to social cues, such as facial expressions, social gestures or turn-
+taking. When first looking at an unknown object, the visual scope of its design, 
+its outer appearance is likely to have an important impact on how the object is 
+overall perceived (how it appears to the human) \citep{schmitz_concepts_2011}.
+
+This fact is exploited in the design of robots and other things. The basic 
 assumption  here is that if an artifact 
 somehow resembles a human, it is likely to be treated similar to a human. If this 
-explanation of anthropomorphism is correct, people may respond automatically also to 
+explanation of anthropomorphism is correct, people may respond automatically to 
 social cues emitted by an artificial embodied agent such as a robot, and apply 
@@
 human user side, to which we will come back later in more detail.)}
-The human-like design of robots implies various consequences, of which we will present some in the following.
 
@@
 
-What do we mean by \textit{human-like / anthropomorphic form}?
+The use of anthropomorphic (human-like) form in the design of non-human 
+things is as old as people's tendency to anthropomorphize. Anthropomorphic (and 
+also animal-shaped) forms were used already in prehistoric artworks and 
+illustrations, and they have a long-standing tradition in the design of daily life 
+artifacts and in general \citep{guthrie_bottles_2000}. The principle of human-like 
+form is probably most prominent in the design of robots. But what do we mean by \textit{human-like / anthropomorphic form}?
+
 Using the term \textit{``form''} to describe the design of an artifact, we refer 
@@
 anthropomorphic, zoomorphic, caricatured, functional \citep{fong_survey_2003}. 
-
-The use of anthropomorphic (human-like) form in the design of non-human 
-things is as old as people's tendency to anthropomorphize. Anthropomorphic (and 
-also animal-shaped) forms were used already in prehistoric artworks and 
-illustrations, and they have a long-standing tradition in the design of daily life 
-artifacts and in general \citep{guthrie_bottles_2000}. The principle of human-like 
-form is probably most prominent in the design of robots, due to several reasons. 
-However, it has been controversially discussed since the early 1970ies, related to 
-\cite{mori_uncanny_1970} theory of the \texit{Uncanny Valley}, see Figure \ref{fig:uncanny_valley}.
-
-The underlying crucial point about the design are the implications that it holds, and the 
-suggestions for interactions that it makes to the user. In other words, the appearance 
-and function of a product, whether it is an appliance or a humanoid robot, affects the 
-way that people perceive it, interact with it, and build long-term relationships with 
-it \cite{bartneck_shaping_2004}. The relation between the design of a robot and the 
-user's perception of it, is also formulated in the \textit{Uncanny Valley} hypothesis \citep{mori_uncanny_1970}.
+However, a classification makes sense because different user reactions are 
+expected. According to \cite{bartneck_shaping_2004}, the appearance and function of 
+a product, whether it is an appliance or a humanoid robot, affects the way that 
+people perceive it, interact with it, and build long-term relationships with it.
+The relation between the design of a robot and the user's perception of it, is also formulated in the \textit{Uncanny Valley} hypothesis \citep{mori_uncanny_1970}.
 
@@
 
-Despite the fact that the Uncanny Valley theory was more a working hypothesis and not 
-meant to be empirically examined \citep{cheetham_human_2011}, it has been studied quite 
-extensively. However, results are inconsistent. We try to give a short overview (not 
-exclusive) on work related to HRI and robotics in the following.
-
-\subsubsection{How people perceive and interact with human-like robots\\}
-\label{sec:anthropomorphism-robotics}
-
-Most work that studies how far human users treat robots as social agents, builds on the 
-famous work of \cite{reeves_media_1996} in HCI. In the so-called \textit{Media 
-Equation}, the authors describe that people mindlessly react in a social way to their computer 
-and that they tend to even attribute human (social) characteristics to it -- despite 
-the fact that a computer does not have human-like characteristics. Apart from 
-computers, anthropomorphism has also been observed with digital / virtual characters 
-\citep{reeves_media_1996,nass_anthropocentrism_1995}, and artificial embodied agents, 
-such as robots. In short, one can say that with robots, and human-like robots in 
-particular, anthropomorphism is a commonly observed phenomenon. However, the 
-anthropomorphic design approach in robotics is controversially discussed.
-
-But what are the motivations which underlie the efforts of enhancing anthropomorphism through specific anthropomorphic design in robots?
-Why are anthropomorphic forms so distinct and at the same time controversial in robotics?
-There is no one single answer to this question.
-
-\hl{human-likeness has a positive effect\\}
-
-On one hand, developers and designers have discovered that human-like robots may better match the affordances that our to humans adapted world brings along.
-Also.
-anthropomorphic form and people's resulting consequence to anthropomorphize, appears to be generally beneficial for human-robot relations, especially with socially interactive robots \cite{fong_survey_2003}.
-Consequently, the domain of (social) robotics tries to exploit this fact by enhancing anthropomorphism through anthropomorphic robots: \textit{"Applying anthropomorphism or zoomorphism changes the way how users try to understand and make sense of a [system] by projecting everyday \hl{expectations} of human and animalistic life onto it."} \cite{schmitz_concepts_2011}.
-
-In general, it is suggested that increasing the human-likeness of a robot (up to a 
-certain threshold) will lead to 
+In general, it is suggested that increasing human-likeness of a robot will lead to 
 more perceived \textit{affinity} from the human side \citep{mori_uncanny_1970} (see 
@@
 humans tend to apply the same communication references to anthropomorphic systems 
-that they would use with other humans, and this is what they are familiar with and feel comfortable about. This theoretical concept is also supported 
+that they would use with other humans. This theoretical concept is also supported 
 by psychological determinants of 
@@
 appearance, the more people are likely to use themselves as a source of induction 
-and anthropomorphize these nonhuman agents"} \citep{epley_seeing_2007}. (We will come back to this later, in Section \ref{sec:explanations}).
-
-Studies have further shown that perceived similarity between the user and the robot influences the intensity of the participants' attributions towards the robot.
-Thus,the anthropomorphic design of a robot impacts the user's perception of the robot, and how far the user is likely to attribute and experience qualities such as intelligence, fun, or intentions in the robot.
-
-"[...] the experiment demonstrates that human beings implicitly attribute human-like qualities, such as mental states, to nonhuman agents.
-This finding was evident on a neuro-physiological level as well as behavioral level." \cite{hegel_understanding_2008}\fxwarning{What to do with this quote?
-'neuro' level maybe interesting?}
-
-Various 
+and anthropomorphize these nonhuman agents"} \citep{epley_seeing_2007}. 
+Also various 
 empirical studies have shown that robots with human-like forms can have a positive 
@@
 anthropomorphism, and in turn create a social view toward the robot.
-
-\hl{human-likeness has a negative effect\\}
 
@@
 
-%For instance, recent studies found that people tend to ascribe personality and 
-%intentions to robots \hl{(REFS)} and that they show empathetic behavior toward robots 
-%\citep{rosenthal-vonderputten_experimental_2013}. Summing it up, there is a huge and 
-%constantly growing body of literature that describes anthropomorphism in HCI and HRI. 
-%Despite the phenomenon is well studied, we still know rather little about it, so that 
-%at conferences and symposiums, anthropomorphism is still a ``hot topic''; however, at 
-%the same time theories related to anthropomorphism, such as the \textit{``Uncanny 
-%Valley''} are controversially discussed.
+\subsubsection{Anthropomorphism in Robotics and Human-Robot Interaction\\}
+\label{sec:anthropomorphism-robotics}
+
+\hl{Julia: I need to work on this section ...}
+
+%While the previous sections presented anthropomorphism more generally, this 
+%section focuses on how anthropomorphism is understood and has been studied in human 
+%robot interaction / social robotics. Our aim here is to give a rough overview of 
+%the diverse and partially conflicting interpretations of anthropomorphism in HRI, 
+%and critically review some previous work.
+
+Most work that studies anthropomorphism in HRI builds on the famous work of \cite{reeves_media_1996} in HCI.
+In the so-called \textit{Media Equation}, the authors describe that people mindlessly react socially to their computer and that they tend to even attribute human (social) characteristics to it.
+Apart from computers, anthropomorphism has also been observed with digital / virtual characters \citep{reeves_media_1996,
+nass_anthropocentrism_1995}, and as more interactive technologies and systems emerged, also with artificial embodied agents, such as robots.
+
+In human-robot interaction anthropomorphism is a commonly observed phenomenon, however, findings have been inconsistent, and in turn, anthropomorphic designs of robots are controversially discussed.
+
+For instance, recent studies found that people tend to ascribe personality and intentions to robots \hl{(REFS)} and that they show empathetic behavior toward robots \citep{rosenthal-vonderputten_experimental_2013}.
+Summing it up, there is a huge and constantly growing body of literature that describes anthropomorphism in HCI and HRI.
+Despite the phenomenon is well studied, we still know rather little about it, so that at conferences and symposiums, anthropomorphism is still a ``hot topic''; however, at the same time theories related to anthropomorphism, such as the \textit{``Uncanny Valley''} are controversially discussed.
 
@@
 %\citep{friedman_hardware_2003}.
+
+But what is the motivation which underlies the efforts of enhancing anthropomorphism through specific anthropomorphic design in robots?
+Why does anthropomorphism seem to be so important in robotics?
+There is no one single answer to this question but certainly, developers and designers have discovered that anthropomorphism seems to be beneficial for human-robot relations, especially with socially interactive robots \cite{fong_survey_2003}.
+
+The domain of (social) robotics tries to exploit this fact by enhancing anthropomorphism through anthropomorphic robots: \textit{"Applying anthropomorphism or zoomorphism changes the way how users try to understand and make sense of a [system] by projecting everyday \hl{expectations} of human and animalistic life onto it."} \cite{schmitz_concepts_2011}.
+
+Studies have further shown that perceived similarity between the user and the robot influences the intensity of the participants' attributions towards the robot.
+Thus, anthropomorphism plays an important role in the design of robots as it is strongly related to the perception of intelligence, fun, the attribution of intentions and thus the predictability of the robot \hl{which ref??}.
+
+"[...] the experiment demonstrates that human beings implicitly attribute human-like qualities, such as mental states, to nonhuman agents.
+This finding was evident on a neuro-physiological level as well as behavioral level." \cite{hegel_understanding_2008}\fxwarning{What to do with this quote?
+'neuro' level maybe interesting?}
 
@@
 \subsection{A human-centered perspective on anthropomorphism}
-\label{sec:human-centered}
 
@@
 the robot's goal-directed actions into the human own motor
-repertoire~\cite{Gallese1998, Wolpert2003, cullen2013individual}.
+repertoire~\cite{Gallese1998, Wolpert2003, cullen2013individual}. Interestingly
+\citet{Gazzola2007} have found no significant difference in the activation of
+the mirror neurons system during the observation of an industrial robot or of a
+human performing the same action, supporting the hypothesis that the goal of the
+action is more important than its kinematics to activate mirror neurons.
 

### 2014-03-25 paper.tex
new changes in anthropomorphic design section ... almost done

--- 2014-03-25 paper.tex
@@
 computers, anthropomorphism has also been observed with digital / virtual characters 
-\citep{reeves_media_1996,nass_anthropocentrism_1995}, and artificial embodied agents, 
-such as robots. In short, one can say that with robots, and human-like robots in 
+\citep{von_der_putten_it_2010}, and artificial embodied agents, 
+such as robots \citep{rosenthal-vonderputten_experimental_2013}. 
+In short, one can say that with robots, and human-like robots in 
 particular, anthropomorphism is a commonly observed phenomenon. 
@@
 On one hand, developers and designers have discovered that human-like robots may better 
-match the affordances that our to humans adapted world brings along. Also, up to a 
-certain point, anthropomorphic form as it increases anthropomorphism,
-appears to be generally beneficial for human-robot relations, especially with socially 
-interactive robots \cite{fong_survey_2003}. Consequently, the domain of (social) 
-robotics tries to exploit this fact by enhancing anthropomorphism through 
-anthropomorphic robots: Applying anthropomorphism or zoomorphism changes the 
-way how users try to understand and make sense of a system by projecting everyday 
-\hl{expectations} of human and animalistic life onto it. \cite{schmitz_concepts_2011}.
-
+match the affordances that this to humans adapted world brings along. 
 In general, it is suggested that increasing the human-likeness of a robot (up to a 
@@
 more perceived \textit{affinity} from the human side \citep{mori_uncanny_1970} (see 
-Figure \ref{fig:uncanny_valley}). Humans seem to readily accept and prefer the 
-anthropomorphic form of a robot, when compared to purely mechanical robots. A 
-possible explanation for this is that 
-humans tend to apply the same communication references to anthropomorphic systems 
-that they would use with other humans, and this is what they are familiar with and feel comfortable about. This theoretical concept is also supported 
-by psychological determinants of 
-perceiving human-likeness in something non-human: \textit{"the more similar in 
+Figure \ref{fig:uncanny_valley}).
+This further increases anthropomorphism, and as such
+appears to be beneficial for human-robot relations, especially with socially 
+interactive robots \cite{fong_survey_2003}. Consequently, the domain of (social) 
+robotics tries to exploit this by using
+anthropomorphic forms in robots.
+Humans seem to readily accept and prefer the 
+anthropomorphic form of a robot (up to a certain point), when compared to purely mechanical 
+robots. A possible explanation for this is that perceiving a system as
+human-like (or also pet-like) compared to machine-like changes the 
+way how users try to understand and make sense of this system. The reason for this is 
+because humans tend to project everyday 
+\hl{expectations} of human and animalistic life onto artificial agents that use 
+anthropomorphic (or zoomorphic) forms \cite{schmitz_concepts_2011}. 
+Both cognitive science 
+and social psychology can provide explanations for this process of projection. The basic idea 
+is that \textit{"the more similar in 
 appearance, the more people are likely to use themselves as a source of induction 
-and anthropomorphize these nonhuman agents"} \citep{epley_seeing_2007}. (We will come back to this later, in Section \ref{sec:explanations}).
-
-Studies have further shown that perceived similarity between the user and the robot influences the intensity of the participants' attributions towards the robot.
-Thus,the anthropomorphic design of a robot impacts the user's perception of the robot, and how far the user is likely to attribute and experience qualities such as intelligence, fun, or intentions in the robot.
-
-"[...] the experiment demonstrates that human beings implicitly attribute human-like qualities, such as mental states, to nonhuman agents.
-This finding was evident on a neuro-physiological level as well as behavioral level." \cite{hegel_understanding_2008}\fxwarning{What to do with this quote?
-'neuro' level maybe interesting?}
-
-Various 
-empirical studies have shown that robots with human-like forms can have a positive 
-effect, as they enhance social 
+and anthropomorphize these nonhuman agents"} \citep{epley_seeing_2007}. Studies have further 
+shown that perceived similarity between the user and the robot influences the intensity of 
+the participants' attributions towards the robot. Thus,the anthropomorphic design of a robot 
+impacts the user's perception of the robot, and how far the user is likely to attribute and 
+experience qualities such as intelligence, fun, or intentions in the robot.
+(We will come back to this more thoughtful reaction to anthropomorphic forms, in more detail 
+later, in Section \ref{sec:human-centered}).
+
+In short, the central point for the design of sociable robots is that 
+humans tend to apply the same communication references to anthropomorphic robots 
+that they would use with other humans, which in turn enhances feeling familiar and 
+comfortable when interacting with the otherwise unknown system.
+This positive effect has been shown in various 
+empirical studies. It has been found that robots with human-like forms can enhance social 
 responses from humans which in turn can positively impact on acceptance 
@@
 
-Anthropomorphism represents just one of many examples of induction whereby "people reason about an unknown stimulus based on a better-known representation of a related stimulus" \cite{epley_when_2008}, in this case reasoning about a non-human agent based on representation of the self or other humans.
+%Anthropomorphism represents just one of many examples of induction whereby "people reason about an unknown stimulus based on a better-known representation of a related stimulus" \cite{epley_when_2008}, in this case reasoning about a non-human agent based on representation of the self or other humans.
+
+Mental models have also been studied in HRI.
+Starting point for this research is the assumption that if a system behaves much like a human being (\eg a robot that emits a human voice), people's mental model of the system's behavior may approach their mental model of humans (though the model may differ in some important aspects).
+In turn, people's estimation of an agent's knowledge model and its capabilities affects the way they relate to it.
+This holds important implications for the resulting interaction with the system, the user experience, and the acceptance.
+Previous research examined the validity of the mental model concept with various kinds of robots \cite{schmitz_concepts_2011,kiesler_mental_2002}.
+Findings suggest that people tend to hold richer mental models of anthropomorphic robots in contrast to mechanic ones \cite{kiesler_mental_2002}.\footnote{\hl{Later in this article, we may however come to question how far this result is based on expectations from the human user side, which are likely to be refined after continued interaction, and after the user gets acquainted with the robot's behavior.}} \hl{Julia:leave this paragraph here or put it later in the HRI section??}
 
@@
 This view is consistent with the \emph{familiarity thesis}~\citep{hegel_understanding_2008} which claims that we understand the world based upon a mental model of the world that we are most familiar with.
-Also, the mental model (human-centered perspective) is supported by \cite{epley_seeing_2007} \textit{Three Factor Theory} which applies a social psychology view, and will be presented later in this section.
+The authors found that human beings implicitly attribute human-like qualities, such as mental states, to nonhuman agents.
+This finding was evident on a neuro-physiological level as well as behavioral level.
+\footnote{\hl{Ha!
+This says that anthropomorphism can also occur on a behavioral level, yes!
+:)}} Also, the mental model (human-centered perspective) is supported by \cite{epley_seeing_2007} \textit{Three Factor Theory} which applies a social psychology view, and will be presented later in this section.
 
@@
 The link between this tendency to thoughtfully anthropomorphize and the engagement in the attribution of mental states to other humans were recently demonstrated at the brain level~\citep{cullen2013individual}.
-
-%\paragraph*{The mental model theory in human-robot interaction\\ \\}
-
-Mental models have also been studied in HRI.
-Starting point for this research is the assumption that if a system behaves much like a human being (\eg a robot that emits a human voice), people's mental model of the system's behavior may approach their mental model of humans (though the model may differ in some important aspects).
-In turn, people's estimation of an agent's knowledge model and its capabilities affects the way they relate to it.
-This holds important implications for the resulting interaction with the system, the user experience, and the acceptance.
-Previous research examined the validity of the mental model concept with various kinds of robots \cite{schmitz_concepts_2011,kiesler_mental_2002}.
-Findings suggest that people tend to hold richer mental models of anthropomorphic robots in contrast to mechanic ones \cite{kiesler_mental_2002}.\footnote{\hl{Later in this article, we may however come to question how far this result is based on expectations from the human user side, which are likely to be refined after continued interaction, and after the user gets acquainted with the robot's behavior.}} \hl{Julia:leave this paragraph here or put it later in the HRI section??}
 

### 2014-03-26 paper.tex
Solved bib conflicts + use Latex special chars

@@
 
-In sum, this branch of research suggests that anthropomorphism implies that people thoughtfully develop a mental model of agents in their environment and that they make inferences about these agents based on what is familiar to them -- themselves, humans and human behavior.
-This understanding builds on a person's ability to attribute mental states to oneself and others, which is called \textit{Theory of Mind}~\citep{Premack1978}.
-A theory of mind for other agents enables us to attribute intentionality to those agents \citep{leslie_pretense_1987,admoni_multi-category_2012}.
-The link between this tendency to thoughtfully anthropomorphize and the engagement in the attribution of mental states to other humans were recently demonstrated at the brain level~\citep{cullen2013individual}.
+In sum, this branch of research suggests that anthropomorphism implies that
+people thoughtfully develop a mental model of agents in their environment and
+that they make inferences about these agents based on what is familiar to them
+-- themselves, humans and human behavior. This understanding builds on a
+person's ability to attribute mental states to oneself and others, which is
+called \textit{Theory of Mind}~\citep{premack1978does}. A theory of mind for
+other agents enables us to attribute intentionality to those agents
+\citep{leslie_pretense_1987,admoni_multi-category_2012}. The link between this
+tendency to thoughtfully anthropomorphize and the engagement in the attribution
+of mental states to other humans were recently demonstrated at the brain
+level~\citep{cullen2013individual}.
 

### 2014-03-26 paper.tex
anthropomorphic design section DONE (almost)

@@
 Along this line, this article aims at fostering a better understanding of
-anthropomorphism (noted \Ant in this paper) by considering the phenomenon
+\textbf{anthropomorphism} (noted \Ant in this paper) by considering the phenomenon
 \textbf{as a whole}: robotics researchers often tend to believe that
@@
 match the affordances that this to humans adapted world brings along. 
-In general, it is suggested that increasing the human-likeness of a robot (up to a 
-certain threshold) will lead to 
+Apart from this, it is suggested that increasing the human-likeness of a robot (up to a 
+certain threshold) will generally lead to 
 more perceived \textit{affinity} from the human side \citep{mori_uncanny_1970} (see 
@@
 way how users try to understand and make sense of this system. The reason for this is 
-because humans tend to project everyday 
+that humans tend to project everyday 
 \hl{expectations} of human and animalistic life onto artificial agents that use 
@@
 experience qualities such as intelligence, fun, or intentions in the robot.
-(We will come back to this more thoughtful reaction to anthropomorphic forms, in more detail 
-later, in Section \ref{sec:human-centered}).
-
-In short, the central point for the design of sociable robots is that 
+However, this is not a natural spontaneous reaction to anthropomorphic form but already a thoughtful process (investigated as the process of forming a \textit{mental model}), which will be treated in more detail later, in Section \ref{sec:human-centered}).
+
+In short, the central point in using anthropomorphic design in sociable robots is that 
 humans tend to apply the same communication references to anthropomorphic robots 
@@
 
-Mental models have also been studied in HRI.
-Starting point for this research is the assumption that if a system behaves much like a human being (\eg a robot that emits a human voice), people's mental model of the system's behavior may approach their mental model of humans (though the model may differ in some important aspects).
-In turn, people's estimation of an agent's knowledge model and its capabilities affects the way they relate to it.
-This holds important implications for the resulting interaction with the system, the user experience, and the acceptance.
-Previous research examined the validity of the mental model concept with various kinds of robots \cite{schmitz_concepts_2011,kiesler_mental_2002}.
-Findings suggest that people tend to hold richer mental models of anthropomorphic robots in contrast to mechanic ones \cite{kiesler_mental_2002}.\footnote{\hl{Later in this article, we may however come to question how far this result is based on expectations from the human user side, which are likely to be refined after continued interaction, and after the user gets acquainted with the robot's behavior.}} \hl{Julia:leave this paragraph here or put it later in the HRI section??}
-
 \paragraph*{Anthropomorphic form can be disadvantageous for HRI\\}
@@
 appearing robot is not only perceived but also expected to act like a human. However, today's artificial systems are 
-not able (yet) to well mimic human movements, or human social cues in an acceptable way. 
+not able (yet) to mimic well human movements, or human social cues in an acceptable way. 
 The case is that the artificial agent pretends to be human but fails, and this is 
@@
 something externally alien or unknown but -- on the contrary -- from something 
-strangely familiar which defeats our efforts to separate ourselves from it"} (cited 
-after \cite{hegel_understanding_2008}).
+strangely familiar which defeats our efforts to separate ourselves from it"} (v. Foerster, cited after \cite{hegel_understanding_2008}).
 In other words, humans are very sensitive to the limits of what is familiar to them 
@@
 
-There exists also the inverse phenomenon to anthropomorphism, which can be found in the literature as \textbf{dehumanization} \citep{haslam_dehumanization:_2006}, or \textbf{mechanomorphism} \citep{caporael_anthropomorphism_1986}.
-We do not treat this here.
-
- \begin{figure}[b]\centering
-% Use the relevant command to insert your figure file.
-% For example, with the graphicx package use
-  \includegraphics[scale=1]{north-wind.jpg}
-  \includegraphics[scale=1]{sun.jpg}
-% figure caption is below the figure
- \caption{Milo Winter illustration of Aesop Fable \textit{The North Wind and the Sun}, 1919; both natural forces wind and sun are anthropomorphized with a human face; picture source: wikipedia}
- \label{fig:north-wind-sun}       % Give a unique label
- \end{figure}
-
 To illustrate better how anthropomorphism differs from attributions of animacy or life-
@@
 \textbf{personification} of anything other than a human being. Personification has 
-ancient roots, \eg in mythology but also in storytelling. Anthropomorphism was also 
-used to describe and be able to predict natural forces or anticipate great spirits, for 
-instance. An illustration of an anthropomorphism related to nature is shown in Figure 
-\ref{fig:north-wind-sun}. In this Milo Winter (1919) drawing \textit{"The North Wind 
-and the Sun"}, both north wind and sun are given a human face.
+ancient roots, \eg in mythology but also in storytelling. For instance, anthropomorphism was also 
+used to describe and be able to predict natural forces or anticipate great spirits.
+
+There exists also the inverse phenomenon to anthropomorphism, which can be found in the literature as \textbf{dehumanization} \citep{haslam_dehumanization:_2006}, or \textbf{mechanomorphism} \citep{caporael_anthropomorphism_1986}.
+We do not treat this here.
+
+% \begin{figure}[b]\centering
+%% Use the relevant command to insert your figure file.
+%% For example, with the graphicx package use
+%  \includegraphics[scale=1]{north-wind.jpg}
+%  \includegraphics[scale=1]{sun.jpg}
+%% figure caption is below the figure
+% \caption{Milo Winter illustration of Aesop Fable \textit{The North Wind and the Sun}, 1919; both natural forces wind and sun are anthropomorphized with a human face; picture source: wikipedia}
+% \label{fig:north-wind-sun}       % Give a unique label
+% \end{figure}
+
+%An illustration of an anthropomorphism related to nature is shown in Figure 
+%\ref{fig:north-wind-sun}. In this Milo Winter (1919) drawing \textit{"The North Wind 
+%and the Sun"}, both north wind and sun are given a human face.
 
@@
 
-Amongst others, one reason for this might be that there exist several understandings of what anthropomorphism is \hl{(REF Peter Ruijten, HRI 2014.)}
-
 Literature on anthropomorphism (the social phenomenon) in robotics as well as on
-anthropomorphic design of robots is quite diverse and one strives hard to
-extract a coherent conclusion. One reason for this might be that robotics is a
-multi-disciplinary field and researchers from very different domains might
+anthropomorphic design of robots is quite diverse. There exist different understandings of what anthropomorphism is, and consequently, one strives hard to
+extract a coherent conclusion.
+
+One reason for why anthropomorphism is defined in different ways might be that it
+is a concept that is studied in very different domains that might each
 integrate diverse or even contradictory understandings, or simply refer to
-different things. However, despite the fact that there is no commonly accepted
+different things.
+However, one conflict is that, despite the fact that there is no commonly accepted
 definition, and also the terminology is not clear, the terms
@@
 anthropomorphism emerges in the \textit{interaction} between the technology and
-the user \cite{persson_anthropomorphism_2000}.  \hl{[In this article, we accept
-this latter viewpoint and would like to clearly distinguish between the term
-\textit{anthropomorphism} as a social phenomenon and \textit{anthropomorphic} as
-a specific design. This however, is not yet a definition of what exactly both
-terms refer to. Still, we acknowledge that both terms can refer to different
-levels or types; which we will outline later.]}
+the user \cite{persson_anthropomorphism_2000}. We will come back to this view later, in the summary of this section (Subsection \ref{sec:multi-factors}).
 
@@
 
+Similarly \cite{ruijten_introducing_2014} argues that anthropomorphism
+
 How can we narrow down the understanding of anthropomorphism?
@@
 In the case of anthropomorphism this means a person's reasoning about a non-human agent based on the representation of the self or other humans.
-The general assumption here is that all other agents (and entities) but oneself are \textit{``unknown''} (because we can only be our self).
 A central construct of this perspective is the so-called \textit{mental model} that a person has (and builds) of the agents she is reasoning about and interacting with.
-The specific mental model we have about an artifact / agent basically explains how this artifact / agent works the way it does.
-But how can we explain the phenomenon that a person uses a human-inspired mental model to explain the actions of a non-human (unknown) agent?
-Well, what we know and understand best is ourselves as human beings (the mental model that we have of our self and other humans).
-So by applying a similar mental model (or parts of it) to the unknown agent, we seek to be able to explain this unknown agent.
-This view is consistent with the \emph{familiarity thesis}~\citep{hegel_understanding_2008} which claims that we understand the world based upon a mental model of the world that we are most familiar with.
-The authors found that human beings implicitly attribute human-like qualities, such as mental states, to nonhuman agents.
+The specific mental model we have about an artifact / agent basically explains (in our individual way to ourselves) how this artifact / agent works the way it does.
+There are two central aspects here, when looking at the quote from \citep{epley_when_2008} above.
+\textit{(1)} First, one assumption is that the user is not familiar with the other agent.
+This is basically true for all other agents (and entities) but oneself because we can only be our self.
+This view is also consistent with the \emph{familiarity thesis}~\citep{hegel_understanding_2008} which claims that we understand the world based upon a mental model of the world that we are most familiar with (our self).
+Thus, we can best use our self as source of induction when reasoning about other agents.
+However, in case we would like to understand the behavior of a spider, we would probably not use our mental model of a human (or our self) simply because we do not have many things in common with a spider.
+And this is the second central aspect here.
+\textit{(2)} Second, one assumption is based oj the anthropomorphic design of the other agent (see Section \ref{sec:anthropomorphic-design}): if the agent behaves (appears) much like a human being (\eg a robot that emits a human voice), people's mental model of the agent's behavior is likely to approach their mental model of humans (though the model may differ in some important aspects).
+
+This cognitive viewpoint on anthropomorphism is important because people's estimation of an agent's knowledge model and its capabilities affects the way they relate to it.
+This holds important implications for the resulting interaction with the system, the user experience, and the acceptance.
+Previous research examined the validity of the mental model concept with various kinds of robots \cite{schmitz_concepts_2011,kiesler_mental_2002}.
+Findings suggest that people tend to hold richer mental models of anthropomorphic robots in contrast to mechanic ones \cite{kiesler_mental_2002}.\footnote{\hl{Later in this article, we may however come to question how far this result is based on expectations from the human user side, which are likely to be refined after continued interaction, and after the user gets acquainted with the robot's behavior.}} A similar finding is described in \cite{hegel_understanding_2008}.
+In a user study, the authors found that participants implicitly attributed human-like qualities, such as mental states, to their non-human interaction partner.
 This finding was evident on a neuro-physiological level as well as behavioral level.
@@
 This says that anthropomorphism can also occur on a behavioral level, yes!
-:)}} Also, the mental model (human-centered perspective) is supported by \cite{epley_seeing_2007} \textit{Three Factor Theory} which applies a social psychology view, and will be presented later in this section.
+:)}}
 

### 2014-03-26 paper.tex
diverse understandings of anthropomorphism

@@
 
-Literature on anthropomorphism (the social phenomenon) in robotics as well as on
-anthropomorphic design of robots is quite diverse. There exist different understandings of what anthropomorphism is, and consequently, one strives hard to
-extract a coherent conclusion.
-
-One reason for why anthropomorphism is defined in different ways might be that it
+Literature on anthropomorphism is quite diverse. There exist different understandings of what 
+anthropomorphism is. 
+One reason for this might be that anthropomorphism
 is a concept that is studied in very different domains that might each
@@
 different things.
-However, one conflict is that, despite the fact that there is no commonly accepted
-definition, and also the terminology is not clear, the terms
+However, the conflict is that, despite the fact that there is no commonly accepted
+definition, the terms
 \textit{anthropomorphism}, \textit{anthropomorphic} or \textit{human-like} are
 often used as if their meanings were clear and agreed upon
-\cite{persson_anthropomorphism_2000}. Duffy \cite{duffy_anthropomorphism_2002}
-argues that these terms might even be misused (in accordance with
-\cite{epley_when_2008}). For instance, some researchers refer to \textit{"the
+\citep{persson_anthropomorphism_2000}. Duffy \cite{duffy_anthropomorphism_2002} and \cite{epley_when_2008}
+argue that these terms might even be misused. For instance, some researchers refer to \textit{"the
 robot's level of anthropomorphism"} \cite{bartneck_is_2007}, whereas others
-argue that the system or artifact itself does not "contain anthropomorphism"
-\textit{per se} but only gives rise to the process of anthropomorphizing in a
-given user and situation. Consequently, Persson \textit{et al.} conclude that
+disagree to such a statement because they argue that the system or artifact itself does not \textit{"contain anthropomorphism" per se} but only gives rise to the process of anthropomorphizing in a
+given user and situation. Consequently, \cite{persson_anthropomorphism_2000} conclude that
 anthropomorphism emerges in the \textit{interaction} between the technology and
-the user \cite{persson_anthropomorphism_2000}. We will come back to this view later, in the summary of this section (Subsection \ref{sec:multi-factors}).
-
-Paradoxically, human's tendency to anthropomorphize non-human agents (such as
-robots) is commonly observed but at the same time it is rather poorly understood
-\cite{epley_seeing_2007}. There might be several reasons. First, probably
-because the phenomenon itself has been found to be very complex though sometimes
-subtle and as such hard to study. Second, the rather poor (or controversial)
-understanding, might also be due to the limited reliability of some findings (or
-interpretations) from experiments investigating anthropomorphism. Most of the
+the user, and has to be understood as such. 
+We will come back to this view later, in the summary of this section (Subsection \ref{sec:multi-factors}).
+
+Paradoxically, while human's tendency to anthropomorphize is commonly observed it is 
+at the same time still rather poorly understood
+\cite{epley_seeing_2007}. The phenomenon itself has been found to be very complex though sometimes
+subtle and as such hard to study.
+Also, the methods and measurements applied to study anthropomorphism appear insufficient, when applying a holistic understanding of anthropomorphism emerging from an interaction between a human user and a robot, for instance.
+Our point here is that to study a phenomenon as complex as anthropomorphism, we believe that one needs to take into account many factors (see Section \ref{sec:multi-factors}), besides looking at the human-like design of the artifact.
+However, most of the
 experiments that investigate anthropomorphism in robotics are conducted in
 controlled lab-settings during short-term human-robot interactions. This
-experimental setting can be critical when studying a social phenomenon like
-anthropomorphism and possibly lead to over-interpretations. Some studies (e.g.
+experimental setting can be critical for studying
+anthropomorphism and findings might possibly lead to interpretations that would not be generalizable to natural settings or real interaction scenarios.\footnote{For instance, some studies are about showing pictures of different robots to human subjects and then asking them how "human-like" they would rate these robots.
+What points of reference do the participants have in this setting?
+What can you really tell from a picture?
+I found that some normal people totally misinterpret the size / height of a robot, when it is not indicated.
+Also, when showing only pictures, movements, behaviors, materials, and so forth are totally disregarded.
+However, these aspects are also crucial to assess how "human-like" a robot appears.
+Last but not least, it has been found that "human-likeness" is a quite diverse and abstract term that includes many things.
+Instead of asking such a big question, \cite{kahn_jr._robotic_2006} suggest to ask for more concrete constructs that are typical or unique of the concept of "human-likeness", such as being hungry or feeling guilty.
+For instance, \cite{ruijten_introducing_2014} propose a 25 concrete questions to measure anthropomorphism along a scale that accounts for lower and higher levels of it.
+\hl{(let's move this to the measurement section at the end.)}}
+Some studies (e.g.
 exploring characteristics of the "uncanny valley") also seem to contrast two or
@@
 
-Similarly \cite{ruijten_introducing_2014} argues that anthropomorphism
-
 How can we narrow down the understanding of anthropomorphism?
@@
 Not only \cite{epley_when_2008} and \cite{duffy_anthropomorphism_2002} but also others have noticed that anthropomorphism is a very complex phenomenon -- itself and in how it can be understood.
-This holds implications for the study of anthropomorphism (to what we will come back later in this article \hl{(REF to studying / measuring anthropomorphism)}.
+This raises question how to study and operationalize anthropomorphism in an appropriate way (see Section \ref{sec:measuring}}.
 A common formal ground is missing so far; however, it is important to be clear about what exactly we mean when using the term anthropomorphism.
@@
 \hl{(maybe here Persson: anthropomorphism as a multi-layered phenomenon)}
+
+Similarly \cite{ruijten_introducing_2014} argues that anthropomorphism
 
@@
 
-In sum, this branch of research suggests that anthropomorphism implies that
-people thoughtfully develop a mental model of agents in their environment and
-that they make inferences about these agents based on what is familiar to them
--- themselves, humans and human behavior. This understanding builds on a
-person's ability to attribute mental states to oneself and others, which is
-called \textit{Theory of Mind}~\citep{premack1978does}. A theory of mind for
-other agents enables us to attribute intentionality to those agents
-\citep{leslie_pretense_1987,admoni_multi-category_2012}. The link between this
-tendency to thoughtfully anthropomorphize and the engagement in the attribution
-of mental states to other humans were recently demonstrated at the brain
-level~\citep{cullen2013individual}.
+In sum, this branch of research suggests that anthropomorphism implies that people thoughtfully develop a mental model of agents in their environment and that they make inferences about these agents based on what is familiar to them -- themselves, humans and human behavior.
+This understanding builds on a person's ability to attribute mental states to oneself and others, which is called \textit{Theory of Mind}~\citep{Premack1978}.
+A theory of mind for other agents enables us to attribute intentionality to those agents \citep{leslie_pretense_1987,admoni_multi-category_2012}.
+The link between this tendency to thoughtfully anthropomorphize and the engagement in the attribution of mental states to other humans were recently demonstrated at the brain level~\citep{cullen2013individual}.
 
@@
 \subsection{Measuring anthropomorphism}
-\label{measuring}
+\label{sec:measuring}
 

### 2014-03-26 paper.tex
sections 1, 2, 3 are so far complete (first robust draft)

@@
 social capabilities of the robot and how this perception changed over
-time.\footnote{\hl{note that these two different kinds of data
-(behavior/interaction and perception) already show that we try to measure
-anthropomorphism from these two angles!}}
+time.
+
+%\footnote{\hl{note that these two different kinds of data
+%(behavior/interaction and perception) already show that we try to measure
+%anthropomorphism from these two angles!}}
 
@@
 the object is overall perceived. Consequently, if a robot's outer form resembles a 
-human, the robot is likely to be treated similar to a human \hl{(\eg eye-contact is 
-established or the robot is greeted)}.
+human, the robot is likely to be treated similar to a human (\eg eye-contact is 
+established or the robot is greeted).
 
@@
 
-\paragraph*{Anthropomorphic form can be advantageous for HRI\\}
+\subsubsection{Anthropomorphic form can be advantageous for HRI\\}
 
@@
 
-\paragraph*{Anthropomorphic form can be disadvantageous for HRI\\}
+\subsubsection{Anthropomorphic form can be disadvantageous for HRI\\}
 
@@
 
-Literature on anthropomorphism is quite diverse. There exist different understandings of what 
-anthropomorphism is. 
+Literature on anthropomorphism is quite diverse. There exist different understandings of what anthropomorphism is. 
 One reason for this might be that anthropomorphism
 is a concept that is studied in very different domains that might each
-integrate diverse or even contradictory understandings, or simply refer to
-different things.
-However, the conflict is that, despite the fact that there is no commonly accepted
-definition, the terms
+integrate diverse or even contradictory understandings, or simply refer to different things.
+However, the conflict is, that despite the fact that there is no commonly accepted definition, the terms
 \textit{anthropomorphism}, \textit{anthropomorphic} or \textit{human-like} are
@@
 
-Paradoxically, while human's tendency to anthropomorphize is commonly observed it is 
+Another paradox is that, while human's tendency to anthropomorphize is commonly observed, it is 
 at the same time still rather poorly understood
 \cite{epley_seeing_2007}. The phenomenon itself has been found to be very complex though sometimes
-subtle and as such hard to study.
-Also, the methods and measurements applied to study anthropomorphism appear insufficient, when applying a holistic understanding of anthropomorphism emerging from an interaction between a human user and a robot, for instance.
-Our point here is that to study a phenomenon as complex as anthropomorphism, we believe that one needs to take into account many factors (see Section \ref{sec:multi-factors}), besides looking at the human-like design of the artifact.
-However, most of the
-experiments that investigate anthropomorphism in robotics are conducted in
-controlled lab-settings during short-term human-robot interactions. This
-experimental setting can be critical for studying
-anthropomorphism and findings might possibly lead to interpretations that would not be generalizable to natural settings or real interaction scenarios.\footnote{For instance, some studies are about showing pictures of different robots to human subjects and then asking them how "human-like" they would rate these robots.
-What points of reference do the participants have in this setting?
-What can you really tell from a picture?
-I found that some normal people totally misinterpret the size / height of a robot, when it is not indicated.
-Also, when showing only pictures, movements, behaviors, materials, and so forth are totally disregarded.
-However, these aspects are also crucial to assess how "human-like" a robot appears.
-Last but not least, it has been found that "human-likeness" is a quite diverse and abstract term that includes many things.
-Instead of asking such a big question, \cite{kahn_jr._robotic_2006} suggest to ask for more concrete constructs that are typical or unique of the concept of "human-likeness", such as being hungry or feeling guilty.
-For instance, \cite{ruijten_introducing_2014} propose a 25 concrete questions to measure anthropomorphism along a scale that accounts for lower and higher levels of it.
-\hl{(let's move this to the measurement section at the end.)}}
-Some studies (e.g.
-exploring characteristics of the "uncanny valley") also seem to contrast two or
-more different anthropomorphic or mechanical systems that might not be
-appropriate for comparison given the complex context. Others might also use
-empirical methods inappropriate for the given research question which leads to
-inaccurate results. \hl{say more}
-
-Anthropomorphism is used in different senses throughout different disciplines 
-\citep{duffy_anthropomorphism_2003} which makes it difficult to synthesize findings. 
+subtle and as such hard to study \cite{epley_when_2008,duffy_anthropomorphism_2002}.
+Further, it is not clear how to operationalize anthropomorphism.
+We would like to discuss the challenges of studying and measuring anthropomorphism toward the end of this article, in Section \ref{sec:measuring}.
+
+%Anthropomorphism is used in different senses throughout different disciplines 
+%\citep{duffy_anthropomorphism_2003} which makes it difficult to synthesize findings. 
 Depending on which understanding of anthropomorphism is applied, not everything 
 colloquially labeled as \emph{anthropomorphism} really is anthropomorphism.
-\footnote{For instance, it is not always clear whether a person (may it be an adult or 
+One practical example is that, it is not always clear whether a person (may it be an adult or 
 a child) who gives and anthropomorphic response, believes that the other agent really 
 thinks or acts like a human or whether she is using anthropomorphism in a metaphoric 
-sense.\citep{leeds_childrens_1992}} We need to be clear about what we mean by 
-anthropomorphism because at the moment, there are different, even partially conflicting 
-understandings of anthropomorphism, not only across but also within disciplines 
-\cite{duffy_anthropomorphism_2002}. In particular, in the multi-disciplinary field of 
-HRI, anthropomorphism is understood and interpreted in such a variety of ways that it 
-is almost impossible to bring together and compare the research work done. In turn, it 
-seems that the understanding of anthropomorphism in HRI has not improved much over the last decade but has only become more diverse (which is ok, too, but certainly a deeper 
-understanding and common grounds would be convenient).
-
-How can we narrow down the understanding of anthropomorphism?
+sense.\citep{leeds_childrens_1992}.
+Thus, we need to be clear about what we mean by anthropomorphism.
+
+But how to clarify the understanding of anthropomorphism?
 From a psychology point of view \cite{epley_when_2008} try to clarify anthropomorphism by explaining what it is \textit{not}, and we think this approach could also help researchers in HRI and robotics.
@@
 
-Not only \cite{epley_when_2008} and \cite{duffy_anthropomorphism_2002} but also others have noticed that anthropomorphism is a very complex phenomenon -- itself and in how it can be understood.
-This raises question how to study and operationalize anthropomorphism in an appropriate way (see Section \ref{sec:measuring}}.
-A common formal ground is missing so far; however, it is important to be clear about what exactly we mean when using the term anthropomorphism.
-
-\hl{(maybe here Persson: anthropomorphism as a multi-layered phenomenon)}
-
-Similarly \cite{ruijten_introducing_2014} argues that anthropomorphism
+Similarly to the last point mentioned by \cite{epley_when_2008}, several researchers argue that there might not just be one single type of anthropomorphism but different levels or gradations.
+For instance, \cite{persson_anthropomorphism_2000} proposes to understand anthropomorphism as a multi-layered phenomenon, and suggests that it exists of different levels, namely primitive categorization, primitive psychology, folk-psychology, traits, social roles, and emotional anthropomorphism.
+Correspondingly, \cite{ruijten_introducing_2014} propose to understand anthropomorphism as a continuum ranging from low to high human likeness, and to measure it as such.
 
@@
 In this example it is in fact questionable whether children really anthropomorphize the sun (believing that it has an intention) or whether they are using anthropomorphism in a metaphoric sense (because their conceptions of the world and of the living are not yet fully formed).
-Later however, two famous experiments by \cite{heider_experimental_1944} and \cite{michotte_perception_1963} showed that also adult participants attribute animacy and intention to simple things and shapes based on motion.\footnote{For more details, the reader may refer to the ``attribution theory''.} In both experiments, participants viewed animations of simple shapes, such as circles or triangles (see Figure \ref{fig:animacy_attribution}).
-Asked to describe what they observed, most people developed elaborate stories, attributing motivations, emotions and relationships between the objects.
-
-\begin{figure}[h]\centering
-% Use the relevant command to insert your figure file.
-% For example, with the graphicx package use
-  \includegraphics[scale=0.6]{heider-simmel_animation.jpeg}
-% figure caption is below the figure
- \caption{Fritz Heider and Mary-Ann Simmel's animated film to study people's tendency to attribute animacy and intention to simple shapes; \textit{An experimental study of apparent behavior}, 1944}
- \fxnote{wrap text around this figure?}
- \label{fig:animacy_attribution}       % Give a unique label
- \end{figure}
+Later however, two famous experiments by \cite{heider_experimental_1944} and \cite{michotte_perception_1963} showed that also adult participants attribute animacy and intention to simple things and shapes based on motion.\footnote{For more details, the reader may refer to the ``attribution theory''.} In both experiments, participants viewed animations of simple shapes, such as circles or triangles
+%(see Figure \ref{fig:animacy_attribution})
+. Asked to describe what they observed, most people developed elaborate stories, attributing motivations, emotions and relationships between the objects.
+
+%\begin{figure}[h]\centering
+%% Use the relevant command to insert your figure file.
+%% For example, with the graphicx package use
+%  \includegraphics[scale=0.6]{heider-simmel_animation.jpeg}
+%% figure caption is below the figure
+% \caption{Fritz Heider and Mary-Ann Simmel's animated film to study people's tendency to attribute animacy and intention to simple shapes; \textit{An experimental study of apparent behavior}, 1944}
+% \fxnote{wrap text around this figure?}
+% \label{fig:animacy_attribution}       % Give a unique label
+% \end{figure}
 
@@
 
-To sum it up, while anthropomorphism in robotics is a commonly discussed and
-studied trait of human-robot interaction, we think it paradoxically lacks a
-formal ground and unified understanding. The understanding of anthropomorphism
-in robotics seems to not take into account the wide range of phenomena that it
-encompasses. The traditional understanding of anthropomorphism in robotics to
-date considers two main factors that account for the social phenomenon: the
+To sum it up, while anthropomorphism is a commonly discussed and
+studied trait of human-robot interaction, its the understanding 
+does not seem to take into account the wide range of phenomena that it
+encompasses. To date, the understanding of anthropomorphism in robotics considers  two main factors: the
 characteristics of \textbf{1) the robot's design} (degree of human-likeness) and
 the psychological determinants in \textbf{2) the human user} (see
-\cite{epley_seeing_2007}). It has been shown that both these factors can
-facilitate or hinder anthropomorphism. We propose to go beyond this traditional
-perception of anthropomorphism as a static feature of HRI: Based on Persson
-\textit{et al.}'s~\cite{persson_anthropomorphism_2000} argumentation that
-anthropomorphism is a multi-layered phenomenon which arises in different levels,
-we suggest to understand anthropomorphism as a \emph{dynamic},
-\emph{context-dependent} process. To this end, we apply Persson \textit{et
-al.}'s six levels on anthropomorphism to HRI and introduce three
-\emph{interaction phases}. These interaction phases of anthropomorphism reflect
-also the results of a long-term study that we conducted in a real human
-environment and provide an account of the so-called \textit{novelty effect}. We
-also draw attention to two new determinants of anthropomorphism, namely, the
-context of use and the fact of getting used to a system over time. We propose to
-add these two aspects as a third factor, the characteristics of \textbf{3) the
-interaction} (time and space), to the previous two factors of anthropomorphism
-(robot and user).
+\cite{epley_seeing_2007}). A lot of research has shown that both these factors can
+facilitate or hinder anthropomorphism.
+
+However, based on what we have just presented, we would like to make a note, that there are more than these two factors that impact on anthropomorphism.
+
+Based on the understanding that anthropomorphism represents a specific type of \textit{experience} that arises in the
+\textit{interaction} between a set of user expectations and external reality
+\cite{persson_anthropomorphism_2000}, 
+%(see Figure~\ref{fig:anthropomorphism_and_interaction})
+we propose that
+anthropomorphism is a multi-layered phenomenon which arises in different levels, and is likely to evolve with continued interaction.
+%we suggest to understand anthropomorphism as a \emph{dynamic},
+%\emph{context-dependent} process. To this end, we apply Persson \textit{et
+%al.}'s six levels on anthropomorphism to HRI and introduce three
+%\emph{interaction phases}. These interaction phases of anthropomorphism reflect
+%also the results of a long-term study that we conducted in a real human
+%environment and provide an account of the so-called \textit{novelty effect}.
+
+To this end, we make the following two suggestions:
+
+First, we propose to include two more main factors as determinants of anthropomorphism (besides the robot's design, and the human user's characteristics).
+Namely, these factors are \textbf{3) the context of use} (situation) and the fact of getting used to a system the more and longer one interacts with it, thus becoming familiar with the system over \textbf{4) time}.
+
+%\begin{figure}[ht!]\centering
+%% Use the relevant command to insert your figure file.
+%% For example, with the graphicx package use
+%  \includegraphics[scale=0.42]{persson_anthropomorphism.png}
+%% figure caption is below the figure
+% \caption{Anthropomorphism emerges in the (real or imagined) interaction between
+% robot and user; illustration taken from \cite{persson_anthropomorphism_2000}
+% \hl{maybe we don't put the figure here, it was just to illustrate what I mean}}
+%
+% \label{fig:anthropomorphism_and_interaction}       % Give a unique label
+% \end{figure}
+
+Second, we would like to take up the proposition already made by other researchers (\eg \cite{persson_anthropomorphism_2000,ruijten_introducing_2014}) to not viewing anthropomorphism as being either there or not there, but to discriminate different levels of
+anthropomorphism (low, and high anthropomorphism, for instance).
+This seems to make sense, since each of the four proposed factors has its own characteristics and involves specific
+types of user expectations, for instance. Such a differentiation in the understanding of anthropomorphism could further allow to draw inferences
+on the human-robot relationship based on the observed level of anthropomorphism.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.7\columnwidth]{factors}
+    \caption{Anthropomorphism is a multi-factor phenomenon.
+How far people tend to anthropomorphize a robot is determined by four main factors: the design of the robot $(R)$, the personal characteristics of the human user $(H)$, the situation and context in which the interaction occurs $(C)$, and the amount of time (repeated interaction) that the user spends to familiarize herself with the robot $(t)$.}
+    \label{factors}
+\end{figure}
+
+To facilitate things, we introduce the notation \Ant[R,H,C,t] to reflect these multiple factors: we suggest here that
+anthropomorphism is a function of a vector of robot's traits $R = \{r_0,...,r_n\}$, a vector human
+determinants $H = \{h_0,...,h_n\}$, a set of interaction situations that build
+an interaction context $C = \{s_0,...,s_n\}$, and the duration of the
+interaction itself, $t$.
 
@@
 
-In this article we will use the term \emph{anthropomorphic effect} to denote
-observable correlates of anthropomorphism. With these we include, amongst
-others, verbal utterances (such as direct speech or the use of pronouns
-"he/she"), (social) gestures (such as a hug, waving, deictic gestures) or
-\hl{anticipation of certain actions of an agent [what??]}.
-
-Anthropomorphism can also be viewed as an \textit{experience} that arises in the
-\textit{interaction} between a set of user expectations and external reality
-\cite{persson_anthropomorphism_2000},
-(Figure~\ref{fig:anthropomorphism_and_interaction}). Persson \textit{et al.}
-suggest that the social phenomenon involves several levels, like primitive
-psychology, folk-psychology, social stereotypes, and emotional anthropomorphism.
-
-\begin{figure}[ht!]\centering
-% Use the relevant command to insert your figure file.
-% For example, with the graphicx package use
-  \includegraphics[scale=0.42]{persson_anthropomorphism.png}
-% figure caption is below the figure
- \caption{Anthropomorphism emerges in the (real or imagined) interaction between
- robot and user; illustration taken from \cite{persson_anthropomorphism_2000}
- \hl{maybe we don't put the figure here, it was just to illustrate what I mean}}
-
- \label{fig:anthropomorphism_and_interaction}       % Give a unique label
- \end{figure}
-
-We would like to take up the proposition to discriminate different levels of
-anthropomorphism, since each has its own characteristics and involves specific
-types of user expectations. This differentiation could allow to draw inferences
-on the human-robot relationship from the observed level of anthropomorphism.
-
-\begin{figure}
-    \centering
-    \includegraphics[width=0.6\columnwidth]{factors}
-    \caption{}
-    \label{factors}
-\end{figure}
-
-The notation \Ant[R,H,C,t] reflects these multiple factors: we suggest here that
-anthropomorphism is a function of a vector of robot's traits $R = \{r_0,...,r_n\}$, a vector human
-determinants $H = \{h_0,...,h_n\}$, a set of interaction situations that build a
-an interaction context $C = \{s_0,...,s_n\}$, and the duration of the
-interaction itself, $t$.
+%In this article we will use the term \emph{anthropomorphic effect} to denote
+%observable correlates of anthropomorphism. With these we include, amongst
+%others, verbal utterances (such as direct speech or the use of pronouns
+%"he/she"), (social) gestures (such as a hug, waving, deictic gestures) or
+%\hl{anticipation of certain actions of an agent [what??]}.
+
+% Persson \textit{et al.}
+%suggest that the social phenomenon involves several levels, like primitive
+%psychology, folk-psychology, social stereotypes, and emotional anthropomorphism.
 
@@
 
+Also, the methods and measurements applied to study anthropomorphism appear insufficient, when applying a holistic understanding of anthropomorphism emerging from an interaction between a human user and a robot, for instance.
+Our point here is that to study a phenomenon as complex as anthropomorphism, we believe that one needs to take into account many factors (see Section \ref{sec:multi-factors}), besides looking at the human-like design of the artifact.
+However, most of the
+experiments that investigate anthropomorphism in robotics are conducted in
+controlled lab-settings during short-term human-robot interactions. This
+experimental setting can be critical for studying
+anthropomorphism and findings might possibly lead to interpretations that would not be generalizable to natural settings or real interaction scenarios.
+For instance, some studies are about showing pictures of different robots to human subjects and then asking them how "human-like" they would rate these robots.
+What points of reference do the participants have in this setting?
+What can you really tell from a picture?
+I found that some normal people totally misinterpret the size / height of a robot, when it is not indicated.
+Also, when showing only pictures, movements, behaviors, materials, and so forth are totally disregarded.
+However, these aspects are also crucial to assess how "human-like" a robot appears.
+Last but not least, it has been found that "human-likeness" is a quite diverse and abstract term that includes many things.
+Instead of asking such a big question, \cite{kahn_jr._robotic_2006} suggest to ask for more concrete constructs that are typical or unique of the concept of "human-likeness", such as being hungry or feeling guilty.
+For instance, \cite{ruijten_introducing_2014} propose a 25 concrete questions to measure anthropomorphism along a scale that accounts for lower and higher levels of it.
+Some studies (e.g. exploring characteristics of the "uncanny valley") also seem to contrast two or
+more different anthropomorphic or mechanical systems that might not be
+appropriate for comparison given the complex context.
+
 Measuring anthropomorphism is challenging because the phenomenon is partially

### 2014-03-26 paper.tex
work in progress... review of neuro literature focused on human-robot interaction and some very early attempt to integrate to the model 3 stages

@@
 
-In this section, we discuss more speculative aspects and hypotheses that follow
+In this section we are briefly reviewing results on anthropomorphism from the cognitive neuroscience point of view.
+We then discuss more speculative aspects and hypotheses that follow
 from the model. These aspects would benefit further investigations and
@@
 
-\subsection{Cognitive Interpretations}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%    Review of neuroscience work on robot-based 
+%    anthropomorphism..... may be moved somewhere 
+%    else or dispatched
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%From the human point of view, what are the brain mechanisms that could mediate anthropomorphism towards robots ?
+\subsection{Neuroscience review of anthropomorphic brain mechanisms in human-robot interaction}
+The neuroscientific study of human-robot interaction is still in its infancy.
+So far most studies have used robots as a way to investigate humans behaviour and brain responses to perception of an artefactual agent actions and emotional states but have not really tapped in the study of how a human behaviours and brain processes are influenced by its direct interaction with a robot (add ref, ref).
+We briefly review below the neuroscientific literature relevant to understand the neural basis of anthropomorphism.
+
+%From an early age, humans develop a tendency to explain one's own and others'actions in terms of beliefs, desires and goals called theory of mind or mentalizing allowing the implicit attribution of intentions and other mental states to others \citep{Frith2003}.
+%A system of brain areas have been linked to mentalizing that encompass an anterior region of the medial prefrontal cortex (MPFC), that may be the basis to distinguish between mental and physical states representation, the temporal lobes, that may allow access to social knowledge  and the posterior superior temporal sulctuc (STS), that might be involved in detection of agency \citep{Frith2003}.
+Resonnance behaviors \citep{Rizzolatti1999} are mechanisms by which the brain areas involved in the internal representations of an action, an emotion or a sensation are equally recruited during the perception of another individual performing the same action or experiencing the same emotion or sensation.
+
+\paragraph{Anthropomorphic response to motor behavior \\}
+Resonnance behaviors have first been shown in the motor mirror neurons system, that is a neural network in motor areas that fire both during the execution of specific goal-oriented action and during the viewing of action directed toward the same goal~\cite{Rizzolatti1996, Kilner2009}.
+
+There are good evidence showing that the human brain responds to both human and robotic motion by activating motor mirror neurons \citet{Gazzola2007, oberman_eeg_2007}, stressing that the perceiving the goal of an action is more important than the human-likeness of its kinematic to activate resonnance mechanisms.
+%For example, fMRI study \citet{Gazzola2007} have found no significant difference in the activation of the mirror neurons system during the observation of an industrial robot or of a human performing the same action, suggesting that the goal of the action is more important than its kinematics to activate resonnance mechanisms.
+%mirror neurons
+
+%[At stage 1] We suggest that the human's mirror neuron system is contributing to anthropomorphism by  allowing for a mapping of the robot's goal-directed actions into the human own motor repertoire \cite{Gallese1998, Wolpert2003, cullen2013individual}.
+
+\paragraph{Anthropomorphism and social behaviour}
+In studying emotional perception in a human or a robot face using functional magnetic resonnance imagery (fMRI) \citet{Chaminade2010} found reduced activity in response to the robot stimuli than to the human stimuli in emotional brain areas known to have mirror properties.
+However if the subject was asked to specifically attend to the emotional content of the stimuli, processing the robot facial expresion, but not the human's, elicited a significant increase in the anterior part of the anterior frontal gyrus, a brain area considered as a marker of motor resonnance.
+
+Howver, using electroencephalograpy another study have found that perception of emotions in a non-humanoid robot face affects the early brain processes of emotional expressions and the behavioral response of the participants the same way as did a human face \citep{Dubal2010}.
+
+%\citet{Dubal2010}: using robots with anthropomorphic (eyes, nose, mouth) featres but not human-like (ie.
+wires and cables) the study show effect of emotional state of the robot on early brain processes of emotional expression using ERPs (enhanced P1 in happy vs neutral state).
+
+Finally, individual tendency to anthropomorphize has been related to the grey matter volume of a brain area involved in mentalizing - the attribution of mental states to other human beings \citet{cullen2013individual, Frith2003}.
+
+Thus it seems that the display of resonance mechanisms for social behaviour in a human-robot interaction is less straightforward than for motor behaviour and may dependent more on the internal attitude and cognitive conceptions the human has of the robot.
+%Brain areas involved when attributing mental states to other human seem to be involved also in anthropomorphism .
+Indeed, individual scores of anthropomorphisms have been found to correlate with the grey matter volume of the left temporoparietal junction, a brain area activared during mentalizing \citet{cullen2013individual}
+
+%\paragraph{Emotions/Empathy}
+%Attitude of the human in a human-robot interaction might influence the anthropomorphic quality of the interaction: \citet{Chaminade2010} shows that directing attention towards emotional processing increases the responses to humanoid robot facial expression in the anteriror part of the left anterior frontal gyrus, a neural marker of motor resonnance.
+
+In the following section, we provide a tentative model of anthropomorphism in terms of cognitive correlates.
+We warmly welcome the feedback and comments from both the cognitive sciences and robotics communities to further
+discuss these findings.
+
+\subsection{Cognitive model}
 \label{sec:cognitive-model}
@@
 
-We provide in this section a tentative interpretation of anthropomorphism in
-terms of cognitive correlates. We warmly welcome the feedback and
-comments from both the cognitive sciences and robotics communities to further
-discuss these findings.
-
 We propose three different cognitive phases (Figure~\ref{fig:cognitivemodel}),
@@
 
-\subsection{Cognitive Processes and Phases}
+\subsubsection{Cognitive Processes and Phases}
 
@@
 Empathy} is characteristic of this stage~\cite{rosenthalvonderPutten2013neural}.
-Anthropomorphism at this pre-cognitive stage might also be mediated by the
-human's mirror neurons system (neurons that fire both during execution of
-specific goal-oriented action and during the viewing of action directed toward
-the same goal~\cite{Rizzolatti1996, Kilner2009}) by allowing for a mapping of
-the robot's goal-directed actions into the human own motor
-repertoire~\cite{Gallese1998, Wolpert2003, cullen2013individual}. Interestingly
-\citet{Gazzola2007} have found no significant difference in the activation of
-the mirror neurons system during the observation of an industrial robot or of a
-human performing the same action, supporting the hypothesis that the goal of the
-action is more important than its kinematics to activate mirror neurons.
+Anthropomorphism at this pre-cognitive stage might also be mediated by the motor and emotional resonnance mechanisms at the neuronal level.
 
@@
 anthropomorphism} (section~\ref{sec:ica}).
+At this stage the huma might also change his attitude towards the robot, paying more attention to social cue than to low-level behaviour which may reinforce the resonnance mechanisms.
 
@@
 cognitive model of the robot.
+It is also at this last stage that the human might modified its own abilities to anthropomorphize, having built a full cognitive model of the robot and know being able to attribute internal state to the robot.
 

### 2014-03-27 paper.tex
Following discussion with Claire and Julia, commenting out section 2 on the experimental studies
Kept some of the diagrams for the introduction

@@
 To support the reflection, it may be useful to consider a few experimental
-results. We observed anthropomorphism in several short- and long-term human-robot
-interaction studies that we carried out with embodied robots, both in
-ecologically valid real-world environments and controlled lab settings. Those
-experiments are presented in details in section~\ref{sec:overview-studies}. We
-only highlight here some qualitative results in order to trigger some initial
-thoughts.
-
-Figures~\ref{fig:roomba-activities} and~\ref{fig:roomba-perception} (on
-page~\pageref{fig:roomba-perception}) give a first perspective on how naive
-users interact and perceive robots over a long period of time. Here,
-\emph{Roomba} vacuum cleaning robots were given to nine households for a
-6-months period. The aim was to explore how people use and perceive the robot
-over time, and how they generally live with the Roomba in their home. At various
-time points, users were asked to rate their perception of different features of
-the robot on a 7-point rating scale. As Figure~\ref{fig:roomba-perception}
-shows, some features remained stable over time (\emph{ease of use} and
-\emph{fun}), and others decreased: the perceived \emph{usefulness},
-\emph{intelligence} and \emph{impact} on their household.  \emph{intelligence}
-and \emph{impact} reflect the cognitive engagement of the user towards the
-machine: we can assume that one does not care to engage in a (cognitive)
-interaction with an artifact perceived as non-intelligent and with no impact on
-his/her life (and the level of activity pictured on
+results. We studied anthropomorphism effects in several short- and long-term
+human-robot interaction studies that we carried out with embodied robots, both
+in ecologically valid real-world environments and controlled lab settings. Those
+experiments are presented in details in previously published
+articles~\citep{fink_anthropomorphic_2012, fink_living_2013, fink2014which,
+lemaignan2014dynamics}. We only highlight here a few qualitative results that
+underline the complexity of the phenomenon.
+
+\begin{figure}[h!]
+        \centering
+        \begin{subfigure}[b]{0.48\columnwidth}
+                \includegraphics[width=\textwidth]{roomba-activities.png}
+                \caption{Roomba activities}
+                \label{fig:roomba-activities}
+        \end{subfigure}%
+        ~ %add desired spacing between images, e. g. ~, \quad, \qquad etc.
+          %(or a blank line to force the subfigure onto a new line)
+        \begin{subfigure}[b]{0.48\columnwidth}
+                \includegraphics[width=\textwidth]{roomba-perception.pdf}
+                \caption{Roomba perception}
+                \label{fig:roomba-perception}
+        \end{subfigure}
+    \caption{Usage and perception of the Roomba robot over a 6 months period.}
+    \label{fig:roomba}
+\end{figure}
+
+Figures~\ref{fig:roomba-activities} and~\ref{fig:roomba-perception} give a first
+perspective on how naive users interact and perceive robots over a long period
+of time. Here, \emph{Roomba} vacuum cleaning robots were given to nine
+households for a 6-months period. The aim was to explore how people use and
+perceive the robot over time, and how they generally live with the Roomba in
+their home. At various time points, users were asked to rate their perception of
+different features of the robot on a 7-point rating scale. As
+Figure~\ref{fig:roomba-perception} shows, some features remained stable over
+time (\emph{ease of use} and \emph{fun}), and others decreased: the perceived
+\emph{usefulness}, \emph{intelligence} and \emph{impact} on their household.
+\emph{intelligence} and \emph{impact} reflect the cognitive engagement of the
+user towards the machine: we can assume that one does not care to engage in a
+(cognitive) interaction with an artifact perceived as non-intelligent and with
+no impact on his/her life (and the level of activity pictured on
 Figure~\ref{fig:roomba-activities} qualitatively confirms this intuition). Even
@@
 
-Figure~\ref{fig:qualitative-score} (page~\pageref{fig:qualitative-score}) calls
-for other initial remarks. This diagram comes from a study where 13 pairs of
-children (4-5 years old) played for about 20 minutes a Domino game with a robot
-(the robot was tasked to carry domino pieces from one child to the other). The
-$x$-axis represents the number of social interactions between the children and
-the robot (like talking or showing objects), based on video annotations. On the
-$y$-axis, we have a synthetic qualitative measurement of anthropomorphic
+Figure~\ref{fig:qualitative-score} calls for other initial remarks. This diagram
+comes from a (yet unpublished) study where 13 pairs of children (4-5 years old)
+played for about 20 minutes a Domino game with a robot (the robot was tasked to
+carry domino pieces from one child to the other, Figure~\ref{fig:ranger-expe}).
+The $x$-axis represents the number of social interactions between the children
+and the robot (like talking or showing objects), based on video annotations. On
+the $y$-axis, we have a synthetic qualitative measurement of anthropomorphic
 projections based on two questionnaires. The correlation between both these
@@
 
+\begin{figure}[h!]
+        \centering
+        \begin{subfigure}[t]{0.48\columnwidth}
+                \centering
+                \includegraphics[width=0.6\textwidth]{ranger}
+                \caption{The \emph{Ranger} Dominos experiment}
+                \label{fig:ranger-expe}
+        \end{subfigure}%
+        ~ %add desired spacing between images, e. g. ~, \quad, \qquad etc.
+          %(or a blank line to force the subfigure onto a new line)
+        \begin{subfigure}[t]{0.48\columnwidth}
+            \includegraphics[width=0.9\textwidth]{ranger-interactions-vs-qualitative-score}
+            \caption{Qualitative level of anthropomorphic projections versus
+            actual interactions with the robot}
+            \label{fig:qualitative-score}
+        \end{subfigure}
+        \caption{Level of interaction with a semi-anthropomorphic robot is
+        \emph{not} a predictor of anthropomorphic projections.}
+    \label{fig:ranger}
+\end{figure}
+
 These results may seem counter-intuitive at first sight, and illustrate that the
@@
 Based on an extensive literature review~\citep{fink_anthropomorphism_2012},
-several field and lab studies~\citep{ fink_anthropomorphic_2012,
-fink_living_2013, fink2014which, lemaignan2014dynamics} and insights from the
+several field and lab studies previously mentioned and insights from the
 cognitive neurosciences, we propose to discuss anthropomorphism from three
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-%
-%
-%		OVERVIEW ON OUR STUDIES
-%
-%
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Studying anthropomorphism in HRI}
-\label{sec:overview-studies}
-
-In this section we give a brief overview of the studies that we conducted to
-investigate anthropomorphism in human-robot interaction. Note that it was not
-the main purpose of these studies to analyze in detail the effect of different
-dimensions human-likeness of a robot on the user's perception of and interaction
-with the robot. Each of these studies were motivated also by other research
-questions, and we encourage the reader to refer to our other main publications
-about these studies for more details.
-
-\subsection{Roomba study: how people live with a vacuum cleaning robot}
-
-We openly explored long-term interactions between human users and a domestic
-service robot in a 6-months lasting ethnographic study~\citep{fink_living_2013}. 
-We gave a commercially
-available vacuum cleaning robot (iRobot's Roomba, see Figure
-\ref{fig:aibo-roomba-ipad} middle) to nine households. 
-%in the French speaking
-%part of Switzerland. 
-%The fairly diverse sample of households consisted of 2
-%single homes, 1 couple, and 6 families with children in their home. In total,
-%this summed up to 30 participants: 15 adults (26-71 years old, mean age 43.6
-%years), and 15 children (6 months to 18 years old). During the 6 months, each
-%household was visited 5 times to conduct interviews and make field observations
-%in the households. Moreover, during several weeks, households were asked to fill
-%in a diary to report the usage of the robot and other cleaning activities.
-Hereafter, we refer to this study as the ``Roomba study''. It is one of very few 
-long-term human-robot interaction studies in the domestic environment. 
-In the following, we present findings in respect of two aspects: First, we
-qualitatively describe what kinds of anthropomorphic interactions between
-participants and the robot were observed and outline how these interactions
-evolved over time.  Second, we present people's perception of human-likeness and
-social capabilities of the robot and how this perception changed over
-time.
-
-%\footnote{\hl{note that these two different kinds of data
-%(behavior/interaction and perception) already show that we try to measure
-%anthropomorphism from these two angles!}}
-
-%The main goal of this study was to explore how households live with a vacuum
-%cleaning robot over an extended period of time. We wanted to analyze how the
-%usage of and interaction with the robot evolve over time, and to identify
-%adoption phases as well as factors that impact on the long-term acceptance of
-%service robots in homes.
-
-\subsubsection{Anthropomorphic interactions with the robot\\}
-
-It has been described in several previous studies of the Roomba that users tend
-to engage in a variety of non-cleaning activities associated with the robot,
-including, but not limited to, naming, ascribing personality and gender
-\citep{forlizzi_service_2006,forlizzi_how_2007,krumm_my_2007,sung_domestic_2010}.
-\cite{sung_housewives_2008} carried out a survey among 379 Roomba users to
-investigate how common these activities are. The authors concluded that overall,
-respondents had relatively low rates of treating Roomba as a living entity.  
-Similarly, in our long-term study of the Roomba in homes, we found that only few 
-people tended to interact in an anthropomorphic or human-social way with their 
-vacuum cleaning robot and that this effect did not sustain. Overall, our data 
-suggest that the anthropomorphic effect and the social
-impact of a functional robot on a household are rather marginal.
-%There were just few instances of people anthropomorphizing the robot and
-%interacting with it in a human-social way. More importantly, overall, these
-%anthropomorphic interactions with the robot did not last but seemed to be
-%somehow related to the novelty of the robot.
-
-We categorized several interactions and actions with the robot as
-anthropomorphic or human-social (in a broader sense). 
-%Examples of what we categorized as somehow social and anthropomorphic
-%(human-like) interactions with the robot include \textit{watching} the robot
-%for fun, giving a \textit{demo} of the robot to guests / visitors, taking a
-%\textit{photo/video} of the robot, \textit{personalizing} the robot, giving a
-%\textit{name} to the robot, \textit{talking} to the robot using direct speech,
-%\textit{playing} with the robot, and making \textit{adjustments} to the home
-%due to the robot. 
-Figure \ref{fig:roomba-activities} shows how many of the 9 households engaged
-in these activities during the 6 months when the study was conducted.
-
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%
+%%
+%%
+%%		OVERVIEW ON OUR STUDIES
+%%
+%%
+%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+%\section{Studying anthropomorphism in HRI}
+%\label{sec:overview-studies}
+%
+%In this section we give a brief overview of the studies that we conducted to
+%investigate anthropomorphism in human-robot interaction. Note that it was not
+%the main purpose of these studies to analyze in detail the effect of different
+%dimensions human-likeness of a robot on the user's perception of and interaction
+%with the robot. Each of these studies were motivated also by other research
+%questions, and we encourage the reader to refer to our other main publications
+%about these studies for more details.
+%
+%
+%\subsection{Roomba study: how people live with a vacuum cleaning robot}
+%
+%We openly explored long-term interactions between human users and a domestic
+%service robot in a 6-months lasting ethnographic study~\citep{fink_living_2013}. 
+%We gave a commercially
+%available vacuum cleaning robot (iRobot's Roomba, see Figure
+%\ref{fig:aibo-roomba-ipad} middle) to nine households. 
+%%in the French speaking
+%%part of Switzerland. 
+%%The fairly diverse sample of households consisted of 2
+%%single homes, 1 couple, and 6 families with children in their home. In total,
+%%this summed up to 30 participants: 15 adults (26-71 years old, mean age 43.6
+%%years), and 15 children (6 months to 18 years old). During the 6 months, each
+%%household was visited 5 times to conduct interviews and make field observations
+%%in the households. Moreover, during several weeks, households were asked to fill
+%%in a diary to report the usage of the robot and other cleaning activities.
+%Hereafter, we refer to this study as the ``Roomba study''. It is one of very few 
+%long-term human-robot interaction studies in the domestic environment. 
+%In the following, we present findings in respect of two aspects: First, we
+%qualitatively describe what kinds of anthropomorphic interactions between
+%participants and the robot were observed and outline how these interactions
+%evolved over time.  Second, we present people's perception of human-likeness and
+%social capabilities of the robot and how this perception changed over
+%time.
+%
+%%\footnote{\hl{note that these two different kinds of data
+%%(behavior/interaction and perception) already show that we try to measure
+%%anthropomorphism from these two angles!}}
+%
+%%The main goal of this study was to explore how households live with a vacuum
+%%cleaning robot over an extended period of time. We wanted to analyze how the
+%%usage of and interaction with the robot evolve over time, and to identify
+%%adoption phases as well as factors that impact on the long-term acceptance of
+%%service robots in homes.
+%
+%
+%\subsubsection{Anthropomorphic interactions with the robot\\}
+%
+%It has been described in several previous studies of the Roomba that users tend
+%to engage in a variety of non-cleaning activities associated with the robot,
+%including, but not limited to, naming, ascribing personality and gender
+%\citep{forlizzi_service_2006,forlizzi_how_2007,krumm_my_2007,sung_domestic_2010}.
+%\cite{sung_housewives_2008} carried out a survey among 379 Roomba users to
+%investigate how common these activities are. The authors concluded that overall,
+%respondents had relatively low rates of treating Roomba as a living entity.  
+%Similarly, in our long-term study of the Roomba in homes, we found that only few 
+%people tended to interact in an anthropomorphic or human-social way with their 
+%vacuum cleaning robot and that this effect did not sustain. Overall, our data 
+%suggest that the anthropomorphic effect and the social
+%impact of a functional robot on a household are rather marginal.
+%%There were just few instances of people anthropomorphizing the robot and
+%%interacting with it in a human-social way. More importantly, overall, these
+%%anthropomorphic interactions with the robot did not last but seemed to be
+%%somehow related to the novelty of the robot.
+%
+%We categorized several interactions and actions with the robot as
+%anthropomorphic or human-social (in a broader sense). 
+%%Examples of what we categorized as somehow social and anthropomorphic
+%%(human-like) interactions with the robot include \textit{watching} the robot
+%%for fun, giving a \textit{demo} of the robot to guests / visitors, taking a
+%%\textit{photo/video} of the robot, \textit{personalizing} the robot, giving a
+%%\textit{name} to the robot, \textit{talking} to the robot using direct speech,
+%%\textit{playing} with the robot, and making \textit{adjustments} to the home
+%%due to the robot. 
+%Figure \ref{fig:roomba-activities} shows how many of the 9 households engaged
+%in these activities during the 6 months when the study was conducted. 
+%
+%%\begin{figure}
+%%    \centering
+%%    \includegraphics[width=0.5\columnwidth]{roomba-activities.png}
+%%    \caption{Activities with the robot over time, n = 9 households. This bar
+%%        chart shows how many of the 9 households carried out different kinds of
+%%        anthropomorphic / social activities with and related to the robot at 3
+%%        time points during 6 months. Activities include \texttt{watching} the
+%%        robot for fun, giving a \texttt{demo} of the robot to guests / visitors,
+%%        \texttt{personalizing} the robot, giving a \texttt{name} to the robot,
+%%        \texttt{talking} to the robot, \texttt{playing} with the robot.
+%%        Participants were asked to report on these activities at 3 time points
+%%        after the robot was deployed in their home: after 2 weeks, after 2 months,
+%%        and after 6 months.} 
+%%
+%%\label{fig:roomba-activities}
+%%\end{figure}
+%
 %\begin{figure}
 %        \centering
-%    \includegraphics[width=0.5\columnwidth]{roomba-activities.png}
-%    \caption{Activities with the robot over time, n = 9 households. This bar
+%        \begin{subfigure}[b]{0.48\columnwidth}
+%                \includegraphics[width=\textwidth]{roomba-activities.png}
+%                \caption{Roomba activities}
+%                \label{fig:roomba-activities}
+%        \end{subfigure}%
+%        ~ %add desired spacing between images, e. g. ~, \quad, \qquad etc.
+%          %(or a blank line to force the subfigure onto a new line)
+%        \begin{subfigure}[b]{0.48\columnwidth}
+%                \includegraphics[width=\textwidth]{roomba-perception.pdf}
+%                \caption{Roomba perception}
+%                \label{fig:roomba-perception}
+%        \end{subfigure}
+%        \caption{\textbf{The Roomba study: Long-term interaction with a robot.\\}
+%    \textbf{a)} Activities with the robot over time, n = 9 households. This bar
 %        chart shows how many of the 9 households carried out different kinds of
@@
 %        after the robot was deployed in their home: after 2 weeks, after 2 months,
-%        and after 6 months.} 
-%
-%\label{fig:roomba-activities}
-%\end{figure}
-
-\begin{figure}
-        \centering
-        \begin{subfigure}[b]{0.48\columnwidth}
-                \includegraphics[width=\textwidth]{roomba-activities.png}
-                \caption{Roomba activities}
-                \label{fig:roomba-activities}
-        \end{subfigure}%
-        ~ %add desired spacing between images, e. g. ~, \quad, \qquad etc.
-          %(or a blank line to force the subfigure onto a new line)
-        \begin{subfigure}[b]{0.48\columnwidth}
-                \includegraphics[width=\textwidth]{roomba-perception.pdf}
-                \caption{Roomba perception}
-                \label{fig:roomba-perception}
-        \end{subfigure}
-        \caption{\textbf{The Roomba study: Long-term interaction with a robot.\\}
-    \textbf{a)} Activities with the robot over time, n = 9 households. This bar
-        chart shows how many of the 9 households carried out different kinds of
-        anthropomorphic / social activities with and related to the robot at 3
-        time points during 6 months. Activities include \texttt{watching} the
-        robot for fun, giving a \texttt{demo} of the robot to guests / visitors,
-        \texttt{personalizing} the robot, giving a \texttt{name} to the robot,
-        \texttt{talking} to the robot, \texttt{playing} with the robot.
-        Participants were asked to report on these activities at 3 time points
-        after the robot was deployed in their home: after 2 weeks, after 2 months,
-        and after 6 months.\\
-	\textbf{b)} People's perception of the robot over time, n = 15 participants.
-    		This line chart shows how people's perception of the robot evolves over
-    		time. At 5 time points people were asked to rate the robot according to the
-    		following aspects: the perceived \texttt{intelligence} of the robot, the
-    		perceived \texttt{usefulness}, the perceived \texttt{ease of use}, how much
-    		\texttt{fun} it was to use the robot, how far they found the robot had an
-    		\texttt{impact} on their household, and their {overall} impression of it.}
-    		\label{fig:roomba-study}
-\end{figure}
-
-\paragraph*{Watching the robot for fun.} We categorize watching a robot for fun
-as an entertaining, emotional activity, reflecting a feeling of empathy for the
-robot. In \cite{sung_housewives_2008} survey, 73~\% of the participants reported
-to watch their Roomba running for fun. While in the beginning of our study, also
-a quite high proportion (6 of 9 households) reported to watch the robot for fun,
-after 2 and 6 months the number of households that engaged in this activity
-decreased by half.
-
-\paragraph*{Giving a robot demo to visitors.} It is somehow natural that owners
-of innovative devices show the device to others and ask for their opinion about
-it \citep{rogers_diffusion_1995}. However, this activity suggests that the robot
-is presented as a new part of the household to visitors.
-\cite{sung_domestic_2010} described that a vacuum cleaning robot can serve as a
-mediator and encourage social interaction among people. We categorize giving a
-demo of the robot to visitors / guests as such an activity. During the first 2
-weeks with the robot 8 of 9 households in our study showed their robot to
-others, and still after 2 and 6 months 5 of the households engaged in this
-activity. This number is more or less in accordance with the 57~\% of survey
-respondents who stated to give demonstrations to others
-\citep{sung_housewives_2008}.
-
-%\paragraph*{Taking photos / videos of the robot.} How far taking a photo or
-%video of a robot can be seen as an anthropomorphic interaction is questionable.
-%However, it reflects the fact that the robot is observed by the user who for
-%some reason is motivated to record the event. The number of households that
-%took a photo or video of the robot decreased over time from 5 households in the
-%beginning to 1 household after 6 months.
-
-\paragraph*{Personalizing the robot.} It has been found that people are
-motivated to personalize technology as a form of self-expression (identity
-projection) or when they use a technology a lot and know how to customize it
-(technical identity projection) \citep{blom_personalization:_2000}. Though
-\cite{sung_pimp_2009} found that some Roomba users who were given a
-customization toolkit personalized their Roomba, none of the users in her study
-who was \textit{not} given this toolkit personalized their Roomba. Also in our
-study none of the 9 households engaged in a personalization activity.
-
-\paragraph*{Giving a name to the robot.} Giving a name to an artificial agent
-reflects a certain kind of personal relationship to the agent. By naming a
-robot, it is not anonymous anymore, and might be perceived as a moral agent. As
-such, naming an artificial agent can be classified as anthropomorphizing this
-agent. It further suggests that the agent is talked to directly. Though more
-than 23~\% of the survey participants in \cite{sung_housewives_2008} study
-reported to name their Roomba, only 1 of 9 households in our study did so.
-
-\paragraph*{Talking directly to the robot.} Using direct speech toward an object
-or artificial agent that does not have the ability to recognize and process
-speech (such as verbal comments) or other sound cues, is an interesting
-phenomenon which can be classified as an anthropomorphic interaction. Whereas
-only 11~\% of the survey respondents in \cite{sung_housewives_2008} study
-reported to talk to their robot, around half of the households engaged in this
-activity and the proportion did not notably decrease over time.
-
-\paragraph*{Playing with the robot.} In our study, it were mostly children who
-engaged in playing with the robot, however, most of them stopped doing so after
-some time. The number of household playing with their Roomba decreased from 8
-when asked after 2 weeks with the robot, to 4 households after 2 months, and 1
-household after 6 months. In \cite{sung_housewives_2008} survey, 37~\% of the
-Roomba owners reported to play and experiment with their robot.\\
-
-%\paragraph*{Making adjustments to the home due to the robot.} To help Roomba
-%clean, \cite{sung_housewives_2008} found in an online survey that about half of
-%the 379 participants made physical modifications to their homes. This process
-%is referred to as \textit{roombarization}, and it seems to be a unique aspect
-%of adopting a domestic service robot. In our study, almost all the households
-%made adjustments when they used the robot for the first time in front of us.
-%However, during the first two weeks with the robot, only 3 households reported
-%to have adjusted something due to the robot, and after 6 months it was only 1
-%household that still engaged in this activity. This decrease is, however,
-%logical since after some time most people had done all the necessary
-%adjustments to enable the robot show a good performance.
-
-%\paragraph*{Emerging anthropomorphic interactions.} Another, from our side more
-%unexpected interaction that we would describe as somehow anthropomorphic, is
-%what we call \textit{``collaborative cleaning''} with the robot. In the initial
-%phase of the study, some people spontaneously helped the robot to clean by
-%either picking up crumbs from the floor themselves or pushing it right in front
-%of the robot. Another way of collaborating with the robot we observed was to
-%help it go everywhere by spontaneously putting up the trash bin or the carpet
-%in the bathroom (things that are not just lying around and need to be cleaned
-%up). However, the activity of collaborative cleaning faded out soon, and we
-%suspect it was encouraged by the novelty of the robot.\\
-
-Overall, Figure \ref{fig:roomba-activities} shows that as time goes by, less
-households engage in the before-mentioned non-cleaning activities with the
-vacuum cleaning robot: after 2 weeks, on average, 4.67 of 9 households engage in
-a human-like activity with the robot; after 2 months, the value decreases to
-2.83, and after 6 months to 2.3. Our interpretation is that the nature of
-human-robot interaction changes over time. More concretely, we suspect  that
-anthropomorphic / human-social interactions with the robot become less over
-time, and that only with some people these interactions sustain.
-
-\subsubsection{Perception of anthropomorphic characteristics of the robot\\}
-
-We also studied people's perception of the robot, and how it evolved over time
-(see Figure \ref{fig:roomba-perception}). The main idea was to find out which of
-the perceived attributes could be related to how far the robot was integrated in
-the household as a cleaning tool. Concerning anthropomorphism, we included
-\textit{perceived intelligence} and experienced \textit{fun} when using the
-robot as indicators for the perception of human-likeness in the robot.\fixme{JF: Severin, you also mentioned impact as one factor. Please include it here below as another paragraph.}
-
-%\begin{figure}
-%    \centering
-%    \includegraphics[width=0.5\columnwidth]{roomba-perception.pdf}
-
-%    \begin{tikzpicture}[scale=0.5, y = 2cm]
-%    %axis
-%    \draw (0,0) -- coordinate (x axis mid) (20,0);
-%    \draw (0,0) -- coordinate (y axis mid) (0,7);
-%    %ticks
-%    \foreach \x in {0,4,...,20}
-%        \draw (\x,1pt) -- (\x,-3pt);
-%    \foreach \y in {1,...,7} 
-%        \draw[black!20] (20,\y) -- (-3pt,\y);
-%    \foreach \y in {1,...,7} 
-%        \draw (-3pt, \y) node[anchor=east] {\y}; 
-%    %labels
-%    \node[below=0.8cm] at (x axis mid) {People's perception (n = 15)};
-%    \node at (2, -0.4) {\tiny expectations};
-%    \node[align=center] at (6, -0.4) {\tiny after\\ \tiny first usage};
-%    \node[align=center] at (10, -0.4) {\tiny after\\ \tiny 2 weeks};
-%    \node[align=center] at (14, -0.4) {\tiny after\\ \tiny 2 months};
-%    \node[align=center] at (18, -0.4) {\tiny after\\ \tiny 6 months};
-%
-%    \draw[dashed, black!50] (6,0) -- (6,7) node[sloped, below, pos=0.25] {\tiny novelty effect};
-%
-%    \draw[ultra thick, red!50] (2,5.6) -- (6,6.1) -- (10,6.3) -- (14,6.3) -- (18,6.1) node at (15,6.5) {\tiny \it ease of use};
-%    \draw[ultra thick, purple] (2,4.9) -- (6,5.2) -- (10,5.1) -- (14,4.5) -- (18,4.2) node at (3,4.7) {\tiny \it usefulness};
-%    \draw[ultra thick, blue!50] (2,4) -- (6,4.1) -- (10,4.6) -- (14,4.1) -- (18,4.3) node at (16,4) {\tiny \it fun};
-%    \draw[ultra thick, green!50] (2,3.9) -- (6,4.1) -- (10,4.2) -- (14,3.8) -- (18,3.3) node at (19,3.5) {\tiny \it intelligence};
-%    \draw[ultra thick, orange] (2,3.5) -- (6,4.2) -- (10,4) -- (14,3.2) -- (18,2.8) node at (14,2.7) {\tiny \it impact};
-%
-%    \draw[ultra thick, dashed] (2,5.2) -- (6,5.2) -- (10,5) -- (14,4.9) -- (18,4.5) node at (14,5.3) {\tiny \it overall};
-%
-%    \end{tikzpicture}
-
-%    \caption{People's perception of the robot over time, n = 15 participants.
+%        and after 6 months.\\
+%	\textbf{b)} People's perception of the robot over time, n = 15 participants.
 %    		This line chart shows how people's perception of the robot evolves over
@@
 %    		\texttt{impact} on their household, and their {overall} impression of it.}
-%
-%    \label{fig:roomba-perception}
+%    		\label{fig:roomba-study}
 %\end{figure}
-
-\paragraph*{Perceived intelligence.} On a scale from 1-7, people were not sure
-about how intelligent they should expect the robot to be (mean value 3.9). The
-rating did not change much and not significantly over time (average ratings
-between 3.3-4.2) \citep{fink_living_2013}. Interestingly, at all five time
-points, male participants rated the robot as more intelligent (average 4.5) than
-females (average 3.4), however, this difference was not significant. When asked
-why they thought Roomba possesses intelligence, men more often referred to the
-'robot side' of Roomba: its abilities to detect and avoid obstacles, stairs, and
-being able to recharge itself. Contrary, women referred to its rather limited
-vacuuming performance and found it was not as intelligent because \textit{``it
-doesn't see where the dirt is, it sometimes leaves it, it can't be smart!''}.
-This difference in the perception of intelligence of a robot suggests that
-gender,and probably other individual characteristics need to be taken into
-account.
-
-\paragraph*{Experienced fun.} Participants rated the robot as 'somewhat fun'
-(values from 4.0-4.6). There was a qualitative gender difference (not
-significant), in the sense that the experienced fun remained quite stable for
-male participants, whereas it tended to decrease with time for female
-participants. Men described the robot more as a 'fun gadget' than females, who
-referred to it as \textit{``In the end, Roomba is a cleaning tool and it is not
-really fun to use it''}. Again for this aspect, gender seems to play a role in
-how the robot is perceived and experienced.\\
-
-Overall, Figure \ref{fig:roomba-perception} shows that after the first usage of
-the Roomba (T2), most of the perceived constructs slightly decrease (and hence
-are less positively rated) as time goes by. The course is different for the
-perceived \textit{ease of use} of the robot, as participants become more
-experienced with the robot over time. Also, the experienced \textit{fun} does
-not decrease with time.
-
-\subsubsection{Summary Roomba study\\}
-
-In accordance with previous work we also found relatively low rates of users
-treating and perceiving their vacuum cleaning robot as a living (or human-like)
-entity \citep{sung_housewives_2008}. We interpret that it might be the pure
-functional purpose and non human-like form of the Roomba that prevented people
-from anthropomorphizing it. Still, we observed some initial anthropomorphic
-effects, both reflected in interaction with and perception of the robot.
-However, most of the anthropomorphic effects did not last long. One fairly
-stable human-like interaction with the robot was \textit{talking to the robot},
-despite the fact that the robot was not able to recognize and respond to verbal
-statements.
-
-\subsection{Forum study: using anthropomorphic expressions to describe a robot}
-
-We investigated the amount and context of anthropomorphic language in three
-online discussion forums about the robotic dog AIBO, the vacuum cleaning robot
-Roomba, and the tablet computer iPad. This was done by means of a content
-analysis of 750 forum posts that were further partitioned in n = 1208 valid
-segments \citep{fink_anthropomorphic_2012}. Hereafter, we refer to this study as
-the "Forum study". The three devices, pictured in Figure
-\ref{fig:aibo-roomba-ipad}, were chosen as they show different designs and
-fulfill different purposes. We would describe (1) AIBO as a zoomorphic /
-pet-like robot that does not have a clear purpose but engages people to play
-with it; (2) Roomba as a mechanical / functional domestic service robot that has
-a practical main purpose (vacuum cleaning) but offers not much of interactivity;
-(3) the iPad as a minimalistic designed interactive (touch-based) technology
-with multiple purposes (both entertainment, and professional / practical use).
-Based on these different characteristics, we made the two following hypotheses
-concerning anthropomorphism:
-
-\begin{enumerate}
-    	\item People engage in a more social and human-like way with a robotic pet compared to a functional robot and a tablet computer, therefore there will be a higher amount of anthropomorphic language in the AIBO and Roomba forum, compared to the iPad forum.
-    	\item As anthropomorphism can be seen as a certain kind of emotional / social relation to an artifact, there will be more anthropomorphic language in forum posts in which the author describes a relation to the device, compared to discussing technological aspects or how the device is used.
-\end{enumerate}
-
-Similar to how \cite{friedman_hardware_2003} analyzed anthropomorphic language
-in online forums, we coded a segment as anthropomorphic when the respective
-device was described in terms of:
-
-\begin{itemize}
-    \item \textit{Life-likeness}, such as being alive or having (parts of) a
-        body, \eg \textit{``she can be reborn since you copied her memory
-        stick''};
-    \item \textit{Emotional states, empathy} or the technology having a
-        \textit{feeling}, \eg \textit{``oh no, poor AIBO''};
-    \item \textit{Gender, personality} or the technology having an
-        \textit{intention}, \eg Roomba \textit{``seems to like to hang around
-        under the sofa''};
-    \item When the author gave the technology a \textit{name}, \eg
-        \textit{``whenever I show Java his pink ball''};
-    \item Being \textit{socially integrated}, such as being a family member, \eg
-        \textit{``I'm considering adding a Roomba to the family''};
-    \item \textit{Metaphorical ways}, \eg Roomba \textit{``sings its victory
-        song when it finishes and docks''}.
-\end{itemize}
-
-In the next paragraphs, we present findings in respect of our two hypotheses:
-anthropomorphic language related to the device, and anthropomorphic language
-related to the topic of the forum post.
-
-\begin{figure}[b]
-    \centering
-    \includegraphics[width=0.5\columnwidth]{aibo-roomba-ipad_2.jpg}
-    \caption{The Sony AIBO robotic dog (left), the iRobot Roomba vacuum-cleaning robot (middle), and the Apple Inc.
+%
+%
+%\paragraph*{Watching the robot for fun.} We categorize watching a robot for fun
+%as an entertaining, emotional activity, reflecting a feeling of empathy for the
+%robot. In \cite{sung_housewives_2008} survey, 73~\% of the participants reported
+%to watch their Roomba running for fun. While in the beginning of our study, also
+%a quite high proportion (6 of 9 households) reported to watch the robot for fun,
+%after 2 and 6 months the number of households that engaged in this activity
+%decreased by half. 
+%
+%\paragraph*{Giving a robot demo to visitors.} It is somehow natural that owners
+%of innovative devices show the device to others and ask for their opinion about
+%it \citep{rogers_diffusion_1995}. However, this activity suggests that the robot
+%is presented as a new part of the household to visitors.
+%\cite{sung_domestic_2010} described that a vacuum cleaning robot can serve as a
+%mediator and encourage social interaction among people. We categorize giving a
+%demo of the robot to visitors / guests as such an activity. During the first 2
+%weeks with the robot 8 of 9 households in our study showed their robot to
+%others, and still after 2 and 6 months 5 of the households engaged in this
+%activity. This number is more or less in accordance with the 57~\% of survey
+%respondents who stated to give demonstrations to others
+%\citep{sung_housewives_2008}.
+%
+%%\paragraph*{Taking photos / videos of the robot.} How far taking a photo or
+%%video of a robot can be seen as an anthropomorphic interaction is questionable.
+%%However, it reflects the fact that the robot is observed by the user who for
+%%some reason is motivated to record the event. The number of households that
+%%took a photo or video of the robot decreased over time from 5 households in the
+%%beginning to 1 household after 6 months.
+%
+%\paragraph*{Personalizing the robot.} It has been found that people are
+%motivated to personalize technology as a form of self-expression (identity
+%projection) or when they use a technology a lot and know how to customize it
+%(technical identity projection) \citep{blom_personalization:_2000}. Though
+%\cite{sung_pimp_2009} found that some Roomba users who were given a
+%customization toolkit personalized their Roomba, none of the users in her study
+%who was \textit{not} given this toolkit personalized their Roomba. Also in our
+%study none of the 9 households engaged in a personalization activity.
+%
+%\paragraph*{Giving a name to the robot.} Giving a name to an artificial agent
+%reflects a certain kind of personal relationship to the agent. By naming a
+%robot, it is not anonymous anymore, and might be perceived as a moral agent. As
+%such, naming an artificial agent can be classified as anthropomorphizing this
+%agent. It further suggests that the agent is talked to directly. Though more
+%than 23~\% of the survey participants in \cite{sung_housewives_2008} study
+%reported to name their Roomba, only 1 of 9 households in our study did so. 
+%
+%\paragraph*{Talking directly to the robot.} Using direct speech toward an object
+%or artificial agent that does not have the ability to recognize and process
+%speech (such as verbal comments) or other sound cues, is an interesting
+%phenomenon which can be classified as an anthropomorphic interaction. Whereas
+%only 11~\% of the survey respondents in \cite{sung_housewives_2008} study
+%reported to talk to their robot, around half of the households engaged in this
+%activity and the proportion did not notably decrease over time. 
+%
+%\paragraph*{Playing with the robot.} In our study, it were mostly children who
+%engaged in playing with the robot, however, most of them stopped doing so after
+%some time. The number of household playing with their Roomba decreased from 8
+%when asked after 2 weeks with the robot, to 4 households after 2 months, and 1
+%household after 6 months. In \cite{sung_housewives_2008} survey, 37~\% of the
+%Roomba owners reported to play and experiment with their robot.\\ 
+%
+%%\paragraph*{Making adjustments to the home due to the robot.} To help Roomba
+%%clean, \cite{sung_housewives_2008} found in an online survey that about half of
+%%the 379 participants made physical modifications to their homes. This process
+%%is referred to as \textit{roombarization}, and it seems to be a unique aspect
+%%of adopting a domestic service robot. In our study, almost all the households
+%%made adjustments when they used the robot for the first time in front of us.
+%%However, during the first two weeks with the robot, only 3 households reported
+%%to have adjusted something due to the robot, and after 6 months it was only 1
+%%household that still engaged in this activity. This decrease is, however,
+%%logical since after some time most people had done all the necessary
+%%adjustments to enable the robot show a good performance.
+%
+%%\paragraph*{Emerging anthropomorphic interactions.} Another, from our side more
+%%unexpected interaction that we would describe as somehow anthropomorphic, is
+%%what we call \textit{``collaborative cleaning''} with the robot. In the initial
+%%phase of the study, some people spontaneously helped the robot to clean by
+%%either picking up crumbs from the floor themselves or pushing it right in front
+%%of the robot. Another way of collaborating with the robot we observed was to
+%%help it go everywhere by spontaneously putting up the trash bin or the carpet
+%%in the bathroom (things that are not just lying around and need to be cleaned
+%%up). However, the activity of collaborative cleaning faded out soon, and we
+%%suspect it was encouraged by the novelty of the robot.\\
+%
+%Overall, Figure \ref{fig:roomba-activities} shows that as time goes by, less
+%households engage in the before-mentioned non-cleaning activities with the
+%vacuum cleaning robot: after 2 weeks, on average, 4.67 of 9 households engage in
+%a human-like activity with the robot; after 2 months, the value decreases to
+%2.83, and after 6 months to 2.3. Our interpretation is that the nature of
+%human-robot interaction changes over time. More concretely, we suspect  that
+%anthropomorphic / human-social interactions with the robot become less over
+%time, and that only with some people these interactions sustain.
+%
+%
+%\subsubsection{Perception of anthropomorphic characteristics of the robot\\}
+%
+%We also studied people's perception of the robot, and how it evolved over time
+%(see Figure \ref{fig:roomba-perception}). The main idea was to find out which of
+%the perceived attributes could be related to how far the robot was integrated in
+%the household as a cleaning tool. Concerning anthropomorphism, we included
+%\textit{perceived intelligence} and experienced \textit{fun} when using the
+%robot as indicators for the perception of human-likeness in the robot.\fixme{JF: Severin, you also mentioned impact as one factor. Please include it here below as another paragraph.}
+%
+%%\begin{figure}
+%%    \centering
+%%    \includegraphics[width=0.5\columnwidth]{roomba-perception.pdf}
+%
+%%    \begin{tikzpicture}[scale=0.5, y = 2cm]
+%%    %axis
+%%    \draw (0,0) -- coordinate (x axis mid) (20,0);
+%%    \draw (0,0) -- coordinate (y axis mid) (0,7);
+%%    %ticks
+%%    \foreach \x in {0,4,...,20}
+%%        \draw (\x,1pt) -- (\x,-3pt);
+%%    \foreach \y in {1,...,7} 
+%%        \draw[black!20] (20,\y) -- (-3pt,\y);
+%%    \foreach \y in {1,...,7} 
+%%        \draw (-3pt, \y) node[anchor=east] {\y}; 
+%%    %labels
+%%    \node[below=0.8cm] at (x axis mid) {People's perception (n = 15)};
+%%    \node at (2, -0.4) {\tiny expectations};
+%%    \node[align=center] at (6, -0.4) {\tiny after\\ \tiny first usage};
+%%    \node[align=center] at (10, -0.4) {\tiny after\\ \tiny 2 weeks};
+%%    \node[align=center] at (14, -0.4) {\tiny after\\ \tiny 2 months};
+%%    \node[align=center] at (18, -0.4) {\tiny after\\ \tiny 6 months};
+%%
+%%    \draw[dashed, black!50] (6,0) -- (6,7) node[sloped, below, pos=0.25] {\tiny novelty effect};
+%%
+%%    \draw[ultra thick, red!50] (2,5.6) -- (6,6.1) -- (10,6.3) -- (14,6.3) -- (18,6.1) node at (15,6.5) {\tiny \it ease of use};
+%%    \draw[ultra thick, purple] (2,4.9) -- (6,5.2) -- (10,5.1) -- (14,4.5) -- (18,4.2) node at (3,4.7) {\tiny \it usefulness};
+%%    \draw[ultra thick, blue!50] (2,4) -- (6,4.1) -- (10,4.6) -- (14,4.1) -- (18,4.3) node at (16,4) {\tiny \it fun};
+%%    \draw[ultra thick, green!50] (2,3.9) -- (6,4.1) -- (10,4.2) -- (14,3.8) -- (18,3.3) node at (19,3.5) {\tiny \it intelligence};
+%%    \draw[ultra thick, orange] (2,3.5) -- (6,4.2) -- (10,4) -- (14,3.2) -- (18,2.8) node at (14,2.7) {\tiny \it impact};
+%%
+%%    \draw[ultra thick, dashed] (2,5.2) -- (6,5.2) -- (10,5) -- (14,4.9) -- (18,4.5) node at (14,5.3) {\tiny \it overall};
+%%
+%%    \end{tikzpicture}
+%
+%
+%%    \caption{People's perception of the robot over time, n = 15 participants.
+%%    This line chart shows how people's perception of the robot evolves over
+%%    time. At 5 time points people were asked to rate the robot according to the
+%%    following aspects: the perceived \texttt{intelligence} of the robot, the
+%%    perceived \texttt{usefulness}, the perceived \texttt{ease of use}, how much
+%%    \texttt{fun} it was to use the robot, how far they found the robot had an
+%%    \texttt{impact} on their household, and their {overall} impression of it.}
+%%
+%%    \label{fig:roomba-perception}
+%%\end{figure}
+%
+%\paragraph*{Perceived intelligence.} On a scale from 1-7, people were not sure
+%about how intelligent they should expect the robot to be (mean value 3.9). The
+%rating did not change much and not significantly over time (average ratings
+%between 3.3-4.2) \citep{fink_living_2013}. Interestingly, at all five time
+%points, male participants rated the robot as more intelligent (average 4.5) than
+%females (average 3.4), however, this difference was not significant. When asked
+%why they thought Roomba possesses intelligence, men more often referred to the
+%'robot side' of Roomba: its abilities to detect and avoid obstacles, stairs, and
+%being able to recharge itself. Contrary, women referred to its rather limited
+%vacuuming performance and found it was not as intelligent because \textit{``it
+%doesn't see where the dirt is, it sometimes leaves it, it can't be smart!''}.
+%This difference in the perception of intelligence of a robot suggests that
+%gender,and probably other individual characteristics need to be taken into
+%account.
+%
+%\paragraph*{Experienced fun.} Participants rated the robot as 'somewhat fun'
+%(values from 4.0-4.6). There was a qualitative gender difference (not
+%significant), in the sense that the experienced fun remained quite stable for
+%male participants, whereas it tended to decrease with time for female
+%participants. Men described the robot more as a 'fun gadget' than females, who
+%referred to it as \textit{``In the end, Roomba is a cleaning tool and it is not
+%really fun to use it''}. Again for this aspect, gender seems to play a role in
+%how the robot is perceived and experienced.\\
+%
+%Overall, Figure \ref{fig:roomba-perception} shows that after the first usage of
+%the Roomba (T2), most of the perceived constructs slightly decrease (and hence
+%are less positively rated) as time goes by. The course is different for the
+%perceived \textit{ease of use} of the robot, as participants become more
+%experienced with the robot over time. Also, the experienced \textit{fun} does
+%not decrease with time.
+% 
+%
+%\subsubsection{Summary Roomba study\\}
+%
+%In accordance with previous work we also found relatively low rates of users
+%treating and perceiving their vacuum cleaning robot as a living (or human-like)
+%entity \citep{sung_housewives_2008}. We interpret that it might be the pure
+%functional purpose and non human-like form of the Roomba that prevented people
+%from anthropomorphizing it. Still, we observed some initial anthropomorphic
+%effects, both reflected in interaction with and perception of the robot.
+%However, most of the anthropomorphic effects did not last long. One fairly
+%stable human-like interaction with the robot was \textit{talking to the robot},
+%despite the fact that the robot was not able to recognize and respond to verbal
+%statements.
+%
+%
+%\subsection{Forum study: using anthropomorphic expressions to describe a robot}
+%
+%We investigated the amount and context of anthropomorphic language in three
+%online discussion forums about the robotic dog AIBO, the vacuum cleaning robot
+%Roomba, and the tablet computer iPad. This was done by means of a content
+%analysis of 750 forum posts that were further partitioned in n = 1208 valid
+%segments \citep{fink_anthropomorphic_2012}. Hereafter, we refer to this study as
+%the "Forum study". The three devices, pictured in Figure
+%\ref{fig:aibo-roomba-ipad}, were chosen as they show different designs and
+%fulfill different purposes. We would describe (1) AIBO as a zoomorphic /
+%pet-like robot that does not have a clear purpose but engages people to play
+%with it; (2) Roomba as a mechanical / functional domestic service robot that has
+%a practical main purpose (vacuum cleaning) but offers not much of interactivity;
+%(3) the iPad as a minimalistic designed interactive (touch-based) technology
+%with multiple purposes (both entertainment, and professional / practical use).
+%Based on these different characteristics, we made the two following hypotheses
+%concerning anthropomorphism:
+%
+%\begin{enumerate}
+%    	\item People engage in a more social and human-like way with a robotic pet compared to a functional robot and a tablet computer, therefore there will be a higher amount of anthropomorphic language in the AIBO and Roomba forum, compared to the iPad forum.
+%    	\item As anthropomorphism can be seen as a certain kind of emotional / social relation to an artifact, there will be more anthropomorphic language in forum posts in which the author describes a relation to the device, compared to discussing technological aspects or how the device is used.
+%\end{enumerate}
+%
+%Similar to how \cite{friedman_hardware_2003} analyzed anthropomorphic language
+%in online forums, we coded a segment as anthropomorphic when the respective
+%device was described in terms of:
+%
+%\begin{itemize}
+%    \item \textit{Life-likeness}, such as being alive or having (parts of) a
+%        body, \eg \textit{``she can be reborn since you copied her memory
+%        stick''};
+%    \item \textit{Emotional states, empathy} or the technology having a
+%        \textit{feeling}, \eg \textit{``oh no, poor AIBO''};
+%    \item \textit{Gender, personality} or the technology having an
+%        \textit{intention}, \eg Roomba \textit{``seems to like to hang around
+%        under the sofa''};
+%    \item When the author gave the technology a \textit{name}, \eg
+%        \textit{``whenever I show Java his pink ball''};
+%    \item Being \textit{socially integrated}, such as being a family member, \eg
+%        \textit{``I'm considering adding a Roomba to the family''};
+%    \item \textit{Metaphorical ways}, \eg Roomba \textit{``sings its victory
+%        song when it finishes and docks''}.
+%\end{itemize}
+%
+%In the next paragraphs, we present findings in respect of our two hypotheses:
+%anthropomorphic language related to the device, and anthropomorphic language
+%related to the topic of the forum post.
+%
+%\begin{figure}[b]
+%    \centering
+%    \includegraphics[width=0.5\columnwidth]{aibo-roomba-ipad_2.jpg}
+%    \caption{The Sony AIBO robotic dog (left), the iRobot Roomba vacuum-cleaning robot (middle), and the Apple Inc.
 iPad tablet computer (right) were compared in terms of how far users of these devices use anthropomorphic expressions in online discussion forums about their technology / robot.}
-    \label{fig:aibo-roomba-ipad}
-\end{figure}
-
-%Overall, our analysis revealed that in all three forums, discussions about
-%\textit{technical} aspects of the respective device were most frequent (67.7~\%
-%of all 1208 categorized segments). However there were huge differences between
-%the three devices: \textit{technical} aspects made up 79.9~\% of the discussion
-%in the Roomba forum, compared to 69.9~\% in the AIBO forum, and 55.2~\% in the
-%iPad forum. Another fairly frequently discussed topic concerned the
-%\textit{usage} of the respective device, thus people describing how and for what
-%they use their technology. This topic made up 21.8~\% of all posts, and was most
-%frequent in the iPad forum (35.7~\%), followed by the Roomba forum (15.9~\%),
-%and the AIBO forum (10.7~\%). Last but not least, we defined \textit{relation}
-%as the third topic of interest. Discussions in which people described their
-%relation to the respective device made up 10.5~\% of all posts, and was most
-%frequent in the AIBO forum (19.4~\%), followed by the iPad forum (9.1~\%), and
-%the Roomba forum (4.2~\%). \hl{(if it is getting too much we can leave out this
-%paragraph, it's not crucial, and doesn't say anything about anthropomorphism
-%directly)}
-
-\subsubsection{Anthropomorphic language related to the device (design)\\}
-
-A statistical analysis revealed a significant difference for the use of
-anthropomorphism across the three devices \citep{fink_anthropomorphic_2012}. In
-accordance with our first hypothesis, the highest amount of anthropomorphic
-language (56.6~\%) was found in the AIBO forum. In contrast, only 11.7~\% and
-respectively 2.2~\% of the segments in the Roomba and the iPad forum contained
-anthropomorphic expressions.  The data suggests that on a subjective scale of
-perceived human-likeness (or rather life-likeness), Roomba is closer to the iPad
-than to the AIBO, at least in matters of how they are described with words. This
-was a bit against our expectation. Still, the Roomba is an autonomous robot that
-can navigate around the house itself, and we expected this property to enhance
-anthropomorphism. We interpret that here, the physical embodiment of the object
-and how far it resembles a life-like entity determine how far the object is
-anthropomorphized, and as such the robotic dog is anthropomorphized more than
-the functionally designed devices.
-
-\subsubsection{Anthropomorphic language related to the topic of conversation\\}
-
-Also in terms of anthropomorphic language related to the topic of conversation,
-a statistical analysis revealed a significant difference
-\citep{fink_anthropomorphic_2012}. The analysis suggests that anthropomorphizing
-happens more when the topic of conversation is \textit{relation}, compared to
-\textit{usage}, and \textit{technical} aspects. This finding is qualitatively
-confirmed when looking at the distribution of anthropomorphic expressions across
-the three topics in the Roomba and iPad forum (with both technologies the
-highest amount of anthropomorphism is in the \textit{relation} topic). However,
-in the AIBO the amount of anthropomorphic segments is highest for the
-\textit{usage} topic.  We interpret that it is the different type of interaction
-/ use context that makes the difference. Contrary to the iPad and the Roomba,
-the AIBO is made to encourage its user in a playful / social interaction, which
-in turn is a typical use context. Further, AIBO has the ability to respond
-intelligently to its user and environment, which might also encourage people to
-ascribe human-like abilities to it while interacting with it.
-
-\subsubsection{Summary Forum study\\}
-
-Overall, findings of the content analysis suggest that there are differences in
-people's tendency to use anthropomorphic language, originating form the design
-characteristics of the artifact. A pet-like robot encourages people to use more 
-anthropomorphic expressions when discussing about it in an online forum. However, 
-the difference might also be related to other factors that we did not analyze 
-here (\eg. author's characteristics). Our analysis further shows that the design 
-of the robot seems to more important than the topic of the discussion. 
-Interestingly, not only the physical embodiment
-of the object but also the interaction complexity and purpose of use of the
-object seems to play a role in how far the object is anthropomorphized.
-
-\subsection{Ranger domino study: effect of unexpected robot behavior}
-
-The so-called "Ranger domino study" describes a child-robot interaction study
-that we carried out in a fairly controlled lab setting. One of the goals of this
-study was to investigate the effect of unexpected robot behavior on (1) the
-interaction and engagement with robot, and (2) how far children would ascribe
-human-like abilities (\eg intentions, cognitive abilities) to the robot.
-
-13 groups of each two children (n = 26) who were all between 4-5 years old and
-knew each other, were invited to play with the Ranger
-robot toy box \citep{fink2014which} to assemble a domino together. The robot
-was operated by one of the experimenters using the wizard-of-oz technique.
-Ranger was supposed to transport domino tiles between the two children and it
-would do its job correctly for the first 7 runs, bringing each one domino tile to the child. Then, however, the
-robot started misbehaving by not coming over to the child who was calling the 
-robot. Three different experimental conditions were explored using three different 
-types of misbehavior from the robot side:
-Either the robot was \textit{disobeying} and did not come over at all, or 
-the robot got \textit{lost} on its way to the child, or the robot did a 
-\textit{mistake} by first going in another direction but then turning and 
-coming over to the child who had called it.
-According to these three different types of unexpected robot behavior, we 
-expected to observe variations of how far the children perceived the 
-robot in terms of intentionality, and cognitive abilities.
-
-In respect of anthropomorphism, we analyzed two types of data: children's 
-\textit{interaction} with the robot (\eg do they talk to and use gestures 
-toward the robot?, see Figure \ref{fig:interactions-per-run}), and 
-children's \textit{perception} of the robot (\eg do they believe the 
-robot has an own will, feelings, or is able to understand what they 
-say?). The interaction data was analyzed quantitatively after having 
-annotated the video recordings of the interaction. Children's perception 
-of the robot was analyzed in a qualitative way and processed in a 
-qualitative scale (higher values on that scale indicate more 
-anthropomorphism), see Figure \ref{fig:qualitative-score}.
-
-\begin{figure}
-        \centering
-        \begin{subfigure}[b]{0.48\columnwidth}
-                \includegraphics[width=\textwidth]{ranger-interactions-per-runs}
-                \caption{Interactions per run}
-                \label{fig:interactions-per-run}
-        \end{subfigure}%
-        ~ %add desired spacing between images, e. g. ~, \quad, \qquad etc.
-          %(or a blank line to force the subfigure onto a new line)
-        \begin{subfigure}[b]{0.48\columnwidth}
-                \includegraphics[width=\textwidth]{ranger-interactions-vs-qualitative-score}
-                \caption{Qualitative score by interactions}
-                \label{fig:qualitative-score}
-        \end{subfigure}
-        \caption{\textbf{The Ranger domino study: Child-robot interaction.}\\
-    \textbf{a)} Quantitative assessment: here, six interaction modalities have
-        been selected: showing something to the robot ({\tt show}), talking to
-        the robot ({\tt talk}), touching it ({\tt touch}), misbehaving (like
-        shaking it, {\tt mis}), using gestures ({\tt ges}), and looking
-        for help by glancing at the experimenter ({\tt look}). In each
-        of the 13 experimental runs, we annotated and counted the number of
-        occurrences of each of these interactions. Highlighted runs 2.3, 2.4,
-        2.7 and 2.8 correspond to unexpected robot behaviors: we observe peaks
-        of interactions every time the robot's behavior changes from expected to
-        unexpected or from unexpected to expected. (n = 26 children)\\
-	\textbf{b)} We found a significant negative correlation ($p=0.048$) between the
-    number of interactions and the qualitative anthropomorphic projections. This 
-    suggests that children who interacted more with the robot, anthropomorphized it 
-	less, and \textit{vice versa}. (n = 13 groups)}
-    		\label{fig:Ranger-domino}
-\end{figure}
-
-\subsubsection{Anthropomorphic interactions with the robot\\}
-
-The video recordings of the interaction session in which the children 
-played domino with the partly misbehaving robot were annotated according 
-to a coding scheme that we developed. Amongst others, six different types 
-of active actions / active engagement that a child carried out with the 
-robot were annotated. We understand some of these active engagement 
-actions as anthropomorphic, such as talking directly to the robot or 
-using gestures to the robot. The distribution of the interaction data per 
-run (see Figure \ref{fig:interactions-per-run} suggests that after the 
-robot started misbehaving (and thus became less predictable) children 
-tended to use slightly more active engagement interactions: gestures toward the 
-robot, and to talk more to the robot. Also, they were looking more often at the 
-experimenter, seeking help.
-
+%    \label{fig:aibo-roomba-ipad}
+%\end{figure}
+%
+%%Overall, our analysis revealed that in all three forums, discussions about
+%%\textit{technical} aspects of the respective device were most frequent (67.7~\%
+%%of all 1208 categorized segments). However there were huge differences between
+%%the three devices: \textit{technical} aspects made up 79.9~\% of the discussion
+%%in the Roomba forum, compared to 69.9~\% in the AIBO forum, and 55.2~\% in the
+%%iPad forum. Another fairly frequently discussed topic concerned the
+%%\textit{usage} of the respective device, thus people describing how and for what
+%%they use their technology. This topic made up 21.8~\% of all posts, and was most
+%%frequent in the iPad forum (35.7~\%), followed by the Roomba forum (15.9~\%),
+%%and the AIBO forum (10.7~\%). Last but not least, we defined \textit{relation}
+%%as the third topic of interest. Discussions in which people described their
+%%relation to the respective device made up 10.5~\% of all posts, and was most
+%%frequent in the AIBO forum (19.4~\%), followed by the iPad forum (9.1~\%), and
+%%the Roomba forum (4.2~\%). \hl{(if it is getting too much we can leave out this
+%%paragraph, it's not crucial, and doesn't say anything about anthropomorphism
+%%directly)}
+%
+%
+%\subsubsection{Anthropomorphic language related to the device (design)\\}
+%
+%A statistical analysis revealed a significant difference for the use of
+%anthropomorphism across the three devices \citep{fink_anthropomorphic_2012}. In
+%accordance with our first hypothesis, the highest amount of anthropomorphic
+%language (56.6~\%) was found in the AIBO forum. In contrast, only 11.7~\% and
+%respectively 2.2~\% of the segments in the Roomba and the iPad forum contained
+%anthropomorphic expressions.  The data suggests that on a subjective scale of
+%perceived human-likeness (or rather life-likeness), Roomba is closer to the iPad
+%than to the AIBO, at least in matters of how they are described with words. This
+%was a bit against our expectation. Still, the Roomba is an autonomous robot that
+%can navigate around the house itself, and we expected this property to enhance
+%anthropomorphism. We interpret that here, the physical embodiment of the object
+%and how far it resembles a life-like entity determine how far the object is
+%anthropomorphized, and as such the robotic dog is anthropomorphized more than
+%the functionally designed devices.
+%
+%
+%\subsubsection{Anthropomorphic language related to the topic of conversation\\}
+%
+%Also in terms of anthropomorphic language related to the topic of conversation,
+%a statistical analysis revealed a significant difference
+%\citep{fink_anthropomorphic_2012}. The analysis suggests that anthropomorphizing
+%happens more when the topic of conversation is \textit{relation}, compared to
+%\textit{usage}, and \textit{technical} aspects. This finding is qualitatively
+%confirmed when looking at the distribution of anthropomorphic expressions across
+%the three topics in the Roomba and iPad forum (with both technologies the
+%highest amount of anthropomorphism is in the \textit{relation} topic). However,
+%in the AIBO the amount of anthropomorphic segments is highest for the
+%\textit{usage} topic.  We interpret that it is the different type of interaction
+%/ use context that makes the difference. Contrary to the iPad and the Roomba,
+%the AIBO is made to encourage its user in a playful / social interaction, which
+%in turn is a typical use context. Further, AIBO has the ability to respond
+%intelligently to its user and environment, which might also encourage people to
+%ascribe human-like abilities to it while interacting with it.
+%
+%
+%\subsubsection{Summary Forum study\\}
+%
+%Overall, findings of the content analysis suggest that there are differences in
+%people's tendency to use anthropomorphic language, originating form the design
+%characteristics of the artifact. A pet-like robot encourages people to use more 
+%anthropomorphic expressions when discussing about it in an online forum. However, 
+%the difference might also be related to other factors that we did not analyze 
+%here (\eg. author's characteristics). Our analysis further shows that the design 
+%of the robot seems to more important than the topic of the discussion. 
+%Interestingly, not only the physical embodiment
+%of the object but also the interaction complexity and purpose of use of the
+%object seems to play a role in how far the object is anthropomorphized.
+%
+%
+%\subsection{Ranger domino study: effect of unexpected robot behavior}
+%
+%The so-called "Ranger domino study" describes a child-robot interaction study
+%that we carried out in a fairly controlled lab setting. One of the goals of this
+%study was to investigate the effect of unexpected robot behavior on (1) the
+%interaction and engagement with robot, and (2) how far children would ascribe
+%human-like abilities (\eg intentions, cognitive abilities) to the robot.
+%
+%13 groups of each two children (n = 26) who were all between 4-5 years old and
+%knew each other, were invited to play with the Ranger
+%robot toy box \citep{fink2014which} to assemble a domino together. The robot
+%was operated by one of the experimenters using the wizard-of-oz technique.
+%Ranger was supposed to transport domino tiles between the two children and it
+%would do its job correctly for the first 7 runs, bringing each one domino tile to the child. Then, however, the
+%robot started misbehaving by not coming over to the child who was calling the 
+%robot. Three different experimental conditions were explored using three different 
+%types of misbehavior from the robot side:
+%Either the robot was \textit{disobeying} and did not come over at all, or 
+%the robot got \textit{lost} on its way to the child, or the robot did a 
+%\textit{mistake} by first going in another direction but then turning and 
+%coming over to the child who had called it.
+%According to these three different types of unexpected robot behavior, we 
+%expected to observe variations of how far the children perceived the 
+%robot in terms of intentionality, and cognitive abilities.
+%
+%In respect of anthropomorphism, we analyzed two types of data: children's 
+%\textit{interaction} with the robot (\eg do they talk to and use gestures 
+%toward the robot?, see Figure \ref{fig:interactions-per-run}), and 
+%children's \textit{perception} of the robot (\eg do they believe the 
+%robot has an own will, feelings, or is able to understand what they 
+%say?). The interaction data was analyzed quantitatively after having 
+%annotated the video recordings of the interaction. Children's perception 
+%of the robot was analyzed in a qualitative way and processed in a 
+%qualitative scale (higher values on that scale indicate more 
+%anthropomorphism), see Figure \ref{fig:qualitative-score}.
+%
 %\begin{figure}
 %        \centering
-%    \includegraphics[width=0.5\columnwidth]{ranger-interactions-per-runs}
-%    \caption{Quantitative assessment: here, six interaction modalities have
+%        \begin{subfigure}[b]{0.48\columnwidth}
+%                \includegraphics[width=\textwidth]{ranger-interactions-per-runs}
+%                \caption{Interactions per run}
+%                \label{fig:interactions-per-run}
+%        \end{subfigure}%
+%        ~ %add desired spacing between images, e. g. ~, \quad, \qquad etc.
+%          %(or a blank line to force the subfigure onto a new line)
+%        \begin{subfigure}[b]{0.48\columnwidth}
+%                \includegraphics[width=\textwidth]{ranger-interactions-vs-qualitative-score}
+%                \caption{Qualitative score by interactions}
+%                \label{fig:qualitative-score}
+%        \end{subfigure}
+%        \caption{\textbf{The Ranger domino study: Child-robot interaction.}\\
+%    \textbf{a)} Quantitative assessment: here, six interaction modalities have
 %        been selected: showing something to the robot ({\tt show}), talking to
@@
 %        of interactions every time the robot's behavior changes from expected to
-%        unexpected or from unexpected to expected. (n = 26 children)}
-%
-%    \label{fig:interactions-per-run}
-%\end{figure}
-
-\subsubsection{Perception of anthropomorphic characteristics of the robot\\}
-
-First of all, note that it is not at all easy to measure how far 4-5 year old's 
-perceive a robot to have some human-like qualities. We interviewed children about 
-various anthropomorphic traits of the robot, such as: Can the robot feel happy or 
-sad? Some of these questions were inspired by \cite{kahn_jr._robotic_2006}. For 
-each of these anthropomorphic traits questions, we gave a point if the child 
-answered in a positive way (partly reversed, negative way), indicating that the 
-child perceived the robot as somehow human-like. In the end, we summed up all 
-points, to obtain a \textit{qualitative score} for a child's tendency to 
-anthropomorphize the robot.
-
-\subsubsection{Summary Ranger domino study\\}
-
-We were trying to bring both measurements together: the anthropomorphic 
-interactions with the robot and the perception of anthropomorphic characteristics 
-of the robot. By this, we wanted to find out whether both aspects are correlated to 
-each other. A correlation would allow us to answer questions such as: Do children 
-that perceive more human-like characteristics in the robot also interact with it in 
-a more human-like way?
-
-%\begin{figure}
-%    \centering
-%    \includegraphics[width=0.5\columnwidth]{ranger-interactions-vs-qualitative-score}
-%    \caption{We found a significant negative correlation ($p=0.048$) between the
+%        unexpected or from unexpected to expected. (n = 26 children)\\
+%	\textbf{b)} We found a significant negative correlation ($p=0.048$) between the
 %    number of interactions and the qualitative anthropomorphic projections. This 
@@
 %	less, and \textit{vice versa}. (n = 13 groups)}
-%    \label{fig:qualitative-score}
+%    		\label{fig:Ranger-domino}
 %\end{figure}
-
-Figure~\ref{fig:qualitative-score} plots the qualitative against the quantitative assessment of
-anthropomorphic effects during the Ranger domino study: the correlation is
-negative. This was a surprise. The more the children interacted with the robot, the less they
-projected anthropomorphic traits on the robot. We also note a remarkable cluster
-of seven groups of children who did not interact much with the robot, but had a
-strongly anthropomorphic perception of the robot. This may initially look
-counter-intuitive (one could hypothesize that the more playful the children are
-with the robot, the more likely they are to consider it as a friend/pet/lively
-being). We discuss possible cognitive explanations of this in Section~\ref{sec:cognition-neuroscience}.
+%
+%
+%\subsubsection{Anthropomorphic interactions with the robot\\}
+%
+%The video recordings of the interaction session in which the children 
+%played domino with the partly misbehaving robot were annotated according 
+%to a coding scheme that we developed. Amongst others, six different types 
+%of active actions / active engagement that a child carried out with the 
+%robot were annotated. We understand some of these active engagement 
+%actions as anthropomorphic, such as talking directly to the robot or 
+%using gestures to the robot. The distribution of the interaction data per 
+%run (see Figure \ref{fig:interactions-per-run} suggests that after the 
+%robot started misbehaving (and thus became less predictable) children 
+%tended to use slightly more active engagement interactions: gestures toward the 
+%robot, and to talk more to the robot. Also, they were looking more often at the 
+%experimenter, seeking help. 
+%
+%%\begin{figure}
+%%    \centering
+%%    \includegraphics[width=0.5\columnwidth]{ranger-interactions-per-runs}
+%%    \caption{Quantitative assessment: here, six interaction modalities have
+%%        been selected: showing something to the robot ({\tt show}), talking to
+%%        the robot ({\tt talk}), touching it ({\tt touch}), misbehaving (like
+%%        shaking it, {\tt mis}), using gestures ({\tt ges}), and looking
+%%        for help by glancing at the experimenter ({\tt look}). In each
+%%        of the 13 experimental runs, we annotated and counted the number of
+%%        occurrences of each of these interactions. Highlighted runs 2.3, 2.4,
+%%        2.7 and 2.8 correspond to unexpected robot behaviors: we observe peaks
+%%        of interactions every time the robot's behavior changes from expected to
+%%        unexpected or from unexpected to expected. (n = 26 children)}
+%%
+%%    \label{fig:interactions-per-run}
+%%\end{figure}
+%
+%
+%\subsubsection{Perception of anthropomorphic characteristics of the robot\\}
+%
+%First of all, note that it is not at all easy to measure how far 4-5 year old's 
+%perceive a robot to have some human-like qualities. We interviewed children about 
+%various anthropomorphic traits of the robot, such as: Can the robot feel happy or 
+%sad? Some of these questions were inspired by \cite{kahn_jr._robotic_2006}. For 
+%each of these anthropomorphic traits questions, we gave a point if the child 
+%answered in a positive way (partly reversed, negative way), indicating that the 
+%child perceived the robot as somehow human-like. In the end, we summed up all 
+%points, to obtain a \textit{qualitative score} for a child's tendency to 
+%anthropomorphize the robot.
+%
+%
+%\subsubsection{Summary Ranger domino study\\}
+%
+%We were trying to bring both measurements together: the anthropomorphic 
+%interactions with the robot and the perception of anthropomorphic characteristics 
+%of the robot. By this, we wanted to find out whether both aspects are correlated to 
+%each other. A correlation would allow us to answer questions such as: Do children 
+%that perceive more human-like characteristics in the robot also interact with it in 
+%a more human-like way?
+%
+%
+%%\begin{figure}
+%%    \centering
+%%    \includegraphics[width=0.5\columnwidth]{ranger-interactions-vs-qualitative-score}
+%%    \caption{We found a significant negative correlation ($p=0.048$) between the
+%%    number of interactions and the qualitative anthropomorphic projections. This 
+%%    suggests that children who interacted more with the robot, anthropomorphized it 
+%%    less, and \textit{vice versa}. (n = 13 groups)}
+%%    \label{fig:qualitative-score}
+%%\end{figure}
+%
+%Figure~\ref{fig:qualitative-score} plots the qualitative against the quantitative assessment of
+%anthropomorphic effects during the Ranger domino study: the correlation is
+%negative. This was a surprise. The more the children interacted with the robot, the less they
+%projected anthropomorphic traits on the robot. We also note a remarkable cluster
+%of seven groups of children who did not interact much with the robot, but had a
+%strongly anthropomorphic perception of the robot. This may initially look
+%counter-intuitive (one could hypothesize that the more playful the children are
+%with the robot, the more likely they are to consider it as a friend/pet/lively
+%being). We discuss possible cognitive explanations of this in Section~\ref{sec:cognition-neuroscience}.
+%
+%
+%
 

### 2014-03-27 paper.tex
new bib item new paragraph our model section

@@
 \newcommand{\etc}{{\textit{etc.~}}}
+\newcommand{\vs}{{\textit{vs.~}}}
 
@@
                 \includegraphics[width=0.6\textwidth]{ranger}
-                \caption{The \emph{Ranger} Dominos experiment}
+                \caption{The \emph{Ranger} Domino study}
                 \label{fig:ranger-expe}
@@
 or to respond to social cues, such as facial expressions, social gestures or turn-taking.
+Also \cite{takayama_perspectives_2012} states that humans have a propensity toward particular cues that seem to trigger automatic interpersonal social responses.
 One has to keep in mind that these cues are of various senses and modalities in human-
@@
 
+\hl{Julia: I need to work on this next paragraph but I would like to keep it here as a note}
+
+\textbf{In-the-moment vs. reflective perspectives on agency}\\
+Perception of agency can be treated as anthropomorphism.
+\citep{takayama_perspectives_2012} proposes to differentiate between a \textit{in-the-moment} and \textit{reflective} perspective to better understand how human users perceive agency in robots.\footnote{``The other important distinction between the two perspectives is the \hl{cognitive processes} that they engage.''} According to Takayama, an \textit{in-the-moment} perspective refers to one's most immediate (sometimes visceral) sense in a situation.
+In contrast, a \textit{reflective} perspective refers to one's sense of a situation upon more distanced cogitation and consideration.
+For instance, we reflectively might not perceive agency in a social robot, but it can feel quite differently in the moment of interaction.
+A critical dimension of agency is the perspective from which something seems to have agency.
+\cite{takayama_perspectives_2012} argues that neglecting to separate reflective perspectives from in-the-moment perspectives of agency is one of the major sources of confusion when people talk and write about anthropomorphism.
+There seems to be a disconnection between what people consciously perceive and how they respond to stimuli that they may not consciously perceive.
+That means, in the initial phase of interacting with a novel device \textbf{(initialization)} people might not consciously respond but rather mindlessly \citep{nass_machines_2000}.
+Only after some time of \textbf{familiarization}, they might respond in a more reflective manner.
+This can be illustrated by the fact that people tend to deny interacting with computational systems as if they were people and yet they respond to computers in many ways that are remarkably similar to how they respond to people \citep{reeves_media_1996}.
+\cite{takayama_perspectives_2012} also applies a cognitive viewpoint on the two different perspectives of in-the-moment \vs reflective to illustrate differences.
+She states that in-the-moment perceptions of agency are largely shaped by bottom-up perceptual processes, evoking very immediate responses (\eg to the cues emitted by the artifact's design, see Section \ref{sec:anthropomorphic-design}).
+In contrast, according to Takayama, reflective perceptions are more often shaped by top-down processes because of the nature of reflective thought.
+
 \subsection{A Model of the Dynamics of Anthropomorphism}
@@
 projected anthropomorphism then starts to decrease while the human observes and
-recognizes that the behaviour of the robot is generally \emph{predictable} and
+recognizes that the behavior of the robot is generally \emph{predictable} and
 possibly \emph{deceptive} (for instance, it talks but does not understand when
@@
 machine''. Section~\ref{sec:disruptive} discusses more in depth the impact of
-the user's perception of disruptive behaviours, and their cognitive correlates.
+the user's perception of disruptive behaviors, and their cognitive correlates.
 
@@
 technologies plays an important role in long-term tendency to
-anthropomophize~\cite{fink_living_2013} (people more familiar with technology
+anthropomorphize~\cite{fink_living_2013} (people more familiar with technology
 understand, and hence predict, better the behavior of the robot, which in turn
@@
 The neuroscientific study of human-robot interaction is still in its infancy.
-So far most studies have used robots as a way to investigate humans behaviour and brain responses to perception of an artefactual agent actions and emotional states but have not really tapped in the study of how a human behaviours and brain processes are influenced by its direct interaction with a robot (add ref, ref).
+So far most studies have used robots as a way to investigate humans behavior and brain responses to perception of an artefactual agent actions and emotional states but have not really tapped in the study of how a human behaviors and brain processes are influenced by its direct interaction with a robot (add ref, ref).
 We briefly review below the neuroscientific literature relevant to understand the neural basis of anthropomorphism.
@@
 %A system of brain areas have been linked to mentalizing that encompass an anterior region of the medial prefrontal cortex (MPFC), that may be the basis to distinguish between mental and physical states representation, the temporal lobes, that may allow access to social knowledge  and the posterior superior temporal sulctuc (STS), that might be involved in detection of agency \citep{Frith2003}.
-Resonnance behaviors \citep{Rizzolatti1999} are mechanisms by which the brain areas involved in the internal representations of an action, an emotion or a sensation are equally recruited during the perception of another individual performing the same action or experiencing the same emotion or sensation.
+Resonance behaviors \citep{Rizzolatti1999} are mechanisms by which the brain areas involved in the internal representations of an action, an emotion or a sensation are equally recruited during the perception of another individual performing the same action or experiencing the same emotion or sensation.
 
 \paragraph{Anthropomorphic response to motor behavior \\}
-Resonnance behaviors have first been shown in the motor mirror neurons system, that is a neural network in motor areas that fire both during the execution of specific goal-oriented action and during the viewing of action directed toward the same goal~\cite{Rizzolatti1996, Kilner2009}.
-
-There are good evidence showing that the human brain responds to both human and robotic motion by activating motor mirror neurons \citet{Gazzola2007, oberman_eeg_2007}, stressing that the perceiving the goal of an action is more important than the human-likeness of its kinematic to activate resonnance mechanisms.
+Resonance behaviors have first been shown in the motor mirror neurons system, that is a neural network in motor areas that fire both during the execution of specific goal-oriented action and during the viewing of action directed toward the same goal~\cite{Rizzolatti1996, Kilner2009}.
+
+There are good evidence showing that the human brain responds to both human and robotic motion by activating motor mirror neurons \citet{Gazzola2007, oberman_eeg_2007}, stressing that the perceiving the goal of an action is more important than the human-likeness of its kinematic to activate resonance mechanisms.
 %For example, fMRI study \citet{Gazzola2007} have found no significant difference in the activation of the mirror neurons system during the observation of an industrial robot or of a human performing the same action, suggesting that the goal of the action is more important than its kinematics to activate resonnance mechanisms.
@@
 
-\paragraph{Anthropomorphism and social behaviour}
-In studying emotional perception in a human or a robot face using functional magnetic resonnance imagery (fMRI) \citet{Chaminade2010} found reduced activity in response to the robot stimuli than to the human stimuli in emotional brain areas known to have mirror properties.
-However if the subject was asked to specifically attend to the emotional content of the stimuli, processing the robot facial expresion, but not the human's, elicited a significant increase in the anterior part of the anterior frontal gyrus, a brain area considered as a marker of motor resonnance.
-
-Howver, using electroencephalograpy another study have found that perception of emotions in a non-humanoid robot face affects the early brain processes of emotional expressions and the behavioral response of the participants the same way as did a human face \citep{Dubal2010}.
+\paragraph{Anthropomorphism and social behavior}
+In studying emotional perception in a human or a robot face using functional magnetic resonance imagery (fMRI) \citet{Chaminade2010} found reduced activity in response to the robot stimuli than to the human stimuli in emotional brain areas known to have mirror properties.
+However if the subject was asked to specifically attend to the emotional content of the stimuli, processing the robot facial expression, but not the human's, elicited a significant increase in the anterior part of the anterior frontal gyrus, a brain area considered as a marker of motor resonance.
+
+However, using electroencephalography another study have found that perception of emotions in a non-humanoid robot face affects the early brain processes of emotional expressions and the behavioral response of the participants the same way as did a human face \citep{Dubal2010}.
 
@@
 
-Thus it seems that the display of resonance mechanisms for social behaviour in a human-robot interaction is less straightforward than for motor behaviour and may dependent more on the internal attitude and cognitive conceptions the human has of the robot.
+Thus it seems that the display of resonance mechanisms for social behavior in a human-robot interaction is less straightforward than for motor behavior and may dependent more on the internal attitude and cognitive conceptions the human has of the robot.
 %Brain areas involved when attributing mental states to other human seem to be involved also in anthropomorphism .
@@
 Empathy} is characteristic of this stage~\cite{rosenthalvonderPutten2013neural}.
-Anthropomorphism at this pre-cognitive stage might also be mediated by the motor and emotional resonnance mechanisms at the neuronal level.
+Anthropomorphism at this pre-cognitive stage might also be mediated by the motor and emotional resonance mechanisms at the neuronal level.
 
@@
 anthropomorphism} (section~\ref{sec:ica}).
-At this stage the huma might also change his attitude towards the robot, paying more attention to social cue than to low-level behaviour which may reinforce the resonnance mechanisms.
+At this stage the human might also change his attitude towards the robot, paying more attention to social cue than to low-level behavior which may reinforce the resonance mechanisms.
 
@@
 assess anthropomorphic projections in two unrelated studies, the Roomba
-experiment~\cite{fink_living_2013}, and the Dominos experiment.
+experiment~\cite{fink_living_2013}, and the Domino study.
 
@@
 qualitative measurement of anthropomorphic effect are questionnaires. We have
-explored both Likert-scale and open questions. In the Dominos experiment,
+explored both Likert-scale and open questions. In the Domino study,
 questionnaires were analyzed such as points are attributed for key answers,

### 2014-03-27 paper.tex
integrated neuro stuff in 2.2.2

@@
 
-\paragraph*{Cognitive science research and the mental model theory (Theory of Mind)\\}
+\paragraph*{Cognitive science research, the mental model theory (Theory of Mind)
+and neural correlates of anthropomorphism\\}
 
@@
 Previous research examined the validity of the mental model concept with various kinds of robots \cite{schmitz_concepts_2011,kiesler_mental_2002}.
-Findings suggest that people tend to hold richer mental models of anthropomorphic robots in contrast to mechanic ones \cite{kiesler_mental_2002}.\footnote{\hl{Later in this article, we may however come to question how far this result is based on expectations from the human user side, which are likely to be refined after continued interaction, and after the user gets acquainted with the robot's behavior.}} A similar finding is described in \cite{hegel_understanding_2008}.
-In a user study, the authors found that participants implicitly attributed human-like qualities, such as mental states, to their non-human interaction partner.
-This finding was evident on a neuro-physiological level as well as behavioral level.
-\footnote{\hl{Ha!
-This says that anthropomorphism can also occur on a behavioral level, yes!
-:)}}
-
-In sum, this branch of research suggests that anthropomorphism implies that people thoughtfully develop a mental model of agents in their environment and that they make inferences about these agents based on what is familiar to them -- themselves, humans and human behavior.
-This understanding builds on a person's ability to attribute mental states to oneself and others, which is called \textit{Theory of Mind}~\citep{Premack1978}.
-A theory of mind for other agents enables us to attribute intentionality to those agents \citep{leslie_pretense_1987,admoni_multi-category_2012}.
-The link between this tendency to thoughtfully anthropomorphize and the engagement in the attribution of mental states to other humans were recently demonstrated at the brain level~\citep{cullen2013individual}.
+Findings suggest that people tend to hold richer mental models of anthropomorphic robots in contrast to mechanic ones \cite{kiesler_mental_2002}.\footnote{\hl{Later in this article, we may however come to question how far this result is based on expectations from the human user side, which are likely to be refined after continued interaction, and after the user gets acquainted with the robot's behavior.}}
+A similar finding is described in \cite{hegel_understanding_2008} and
+\citet{krach_can_2008}. In a user study using functional magnetic resonnance
+imagery (fMRI), the authors found that participants
+implicitly attributed human-like qualities, such as mental states, to their
+non-human interaction partner. Indeed, from an early age humans develop a
+tendency to explain one's own and others'actions in terms of beliefs, desires
+and goals,  called \textit{theory of mind}. The theory of mind allows the implicit attribution of
+intentions and other mental states to others \citep{premack1978_does, leslie_pretense_1987, Frith2003}.
+\citet{hegel_understanding_2008} and \citet{krach_can_2008} finding was evident at the behavioral level
+as well as on the neuro-physiological level: the more the human-likeness of the
+artefactual partner increases, the more brain areas associated with theory of
+mind  get activated
+\citep{krach_can_2008}. \footnote{\hl{Ha! This says that anthropomorphism can also occur on a behavioral level, yes! :)}} 
+Implication of human brain area involved in the inference of other's mental
+states has also been shown in response to viewing
+non-anthropomorphic/non-humanoid robotic gadgets whose behaviour
+has been described as unpredictable - but not in response to those whose
+behavior was described as predictable- a finding also found at the behavioral
+level \citep{Waytz2010}.
+Interestingly, the grey matter volume of a brain area related to theory of mind
+has been correlated to individual's score of anthropomorphism
+\citep{cullen2013individual}.
+
+%\paragraph{Mirror neurons and resonnance behaviors \\}
+%
+%Resonnance behaviors \citep{Rizzolatti1999} are mechanisms by which the brain areas involved in the internal representations of an action, an emotion or a sensation are equally recruited during the perception of another individual performing the same action or experiencing the same emotion or sensation.
+%
+%Resonnance behaviors have first been shown in the motor mirror neurons system, that is a neural network in motor areas that fire both during the execution of specific goal-oriented action and during the viewing of action directed toward the same goal~\cite{Rizzolatti1996, Kilner2009}.
+%
+%Interestingly, there are good evidence showing that motor mirror neurons in the
+%human brain respond to both human and robotic motion \citet{Gazzola2007, oberman_eeg_2007}, stressing that perceiving the goal of an action is more important than the human-likeness of its kinematic to activate resonnance mechanisms.
+%%For example, fMRI study \citet{Gazzola2007} have found no significant difference in the activation of the mirror neurons system during the observation of an industrial robot or of a human performing the same action, suggesting that the goal of the action is more important than its kinematics to activate resonnance mechanisms.
+%mirror neurons
+%
+%%[At stage 1] We suggest that the human's mirror neuron system is contributing to anthropomorphism by  allowing for a mapping of the robot's goal-directed actions into the human own motor repertoire \cite{Gallese1998, Wolpert2003, cullen2013individual}.
+%
+%The response of the human brain to a social signal perceived on a robot, such as facial
+%emotional expression is less evident. 
+%
+%In studying emotional perception in a human or a robot face using functional
+%magnetic resonnance imagery (fMRI) \citet{Chaminade2010} found reduced activity
+%in response to the robot stimuli than to the human stimuli in emotional brain
+%areas known to have mirror properties. However if the subject was asked to
+%specifically attend to the emotional content of the stimuli, processing of the
+%robot facial expresion, but not of the human's, elicited a significant increase in the anterior part of the anterior frontal gyrus, a brain area considered as a marker of motor resonnance.
+%
+%Using electroencephalograpy another study have found that perception of emotions in a non-humanoid robot face affects the early brain processes of emotional expressions and the behavioral response of the participants the same way as did a human face \citep{Dubal2010}.
+%
+%
+%
+%
+
+In sum, this branch of research suggests that anthropomorphism implies that
+people thoughtfully develop a mental model of agents in their environment and
+that they make inferences about these agents based on what is familiar to them
+-- themselves, humans and human behavior. This understanding builds on the
+theory of mind,  a
+person's ability to attribute mental states to oneself and others. 
+%A theory of mind for other agents enables us to attribute intentionality to those agents \citep{leslie_pretense_1987,admoni_multi-category_2012}. 
+We briefly reviewed  neuro-physiological evidence of a link between the tendency
+to thoughtfully anthropomorphize and the engagement of brain processes involved
+in the attribution of mental states to other humans. The human-likeness quality
+of the artefactual agent seems to play a role in the involvement of theory of
+mind but also the unpredictable feature of the agent behavior alone seems to be
+sufficient.  
+%were recently demonstrated at the brain level~\citep{cullen2013individual}.
 
@@
 activation or elicitation of knowledge, and the application of activated
-knowledge at the time of the judgment \cite{epley_when_2008}. According to Epley
+knowledge at the time of the judgment \citep{epley_when_2008}. According to Epley
 \textit{et al.}, the application includes attempts to correct, adjust, or
@@
 Based on an extensive literature review previously
-published~\cite{fink_anthropomorphism_2012} and field
+published~\citep{fink_anthropomorphism_2012} and field
 experiments~\fixme{cites!}, we believe that anthropomorphic effects in HRI are
@@
 experience with the robot, similar to how relationships among people evolve
-over time \fixme{(cite Hinde, 1988)}. In fact, \cite{kanda_interactive_2004}
+over time \fixme{(cite Hinde, 1988)}. In fact, \citet{kanda_interactive_2004}
 also hypothesized that people's attitude toward technological artifacts and
@@
 period of time (typically longer than a week), we also formally introduce a
-so-called \emph{novelty effect}~\cite{kanda_interactive_2004} that models the
+so-called \emph{novelty effect}~\citep{kanda_interactive_2004} that models the
 first phase of human-robot interaction, during which a specific increase of
@@
 
-\section{Cognitive Correlates and Neuroscience Perspective}
+\section{Cognitive Model}
 \label{sec:cognition-neuroscience}
 
-In this section we are briefly reviewing results on anthropomorphism from the cognitive neuroscience point of view.
-We then discuss more speculative aspects and hypotheses that follow
+In this section are discussing more speculative aspects and hypotheses that follow
 from the model. These aspects would benefit further investigations and
 experimental support.
-
+%
+
+%In this section we are briefly reviewing results on anthropomorphism from the cognitive neuroscience point of view.
+%We then discuss more speculative aspects and hypotheses that follow
+%from the model. These aspects would benefit further investigations and
+%experimental support.
+%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %From the human point of view, what are the brain mechanisms that could mediate anthropomorphism towards robots ?
-\subsection{Neuroscience review of anthropomorphic brain mechanisms in human-robot interaction}
-The neuroscientific study of human-robot interaction is still in its infancy.
-So far most studies have used robots as a way to investigate humans behavior and brain responses to perception of an artefactual agent actions and emotional states but have not really tapped in the study of how a human behaviors and brain processes are influenced by its direct interaction with a robot (add ref, ref).
-We briefly review below the neuroscientific literature relevant to understand the neural basis of anthropomorphism.
-
-%From an early age, humans develop a tendency to explain one's own and others'actions in terms of beliefs, desires and goals called theory of mind or mentalizing allowing the implicit attribution of intentions and other mental states to others \citep{Frith2003}.
-%A system of brain areas have been linked to mentalizing that encompass an anterior region of the medial prefrontal cortex (MPFC), that may be the basis to distinguish between mental and physical states representation, the temporal lobes, that may allow access to social knowledge  and the posterior superior temporal sulctuc (STS), that might be involved in detection of agency \citep{Frith2003}.
-Resonance behaviors \citep{Rizzolatti1999} are mechanisms by which the brain areas involved in the internal representations of an action, an emotion or a sensation are equally recruited during the perception of another individual performing the same action or experiencing the same emotion or sensation.
-
-\paragraph{Anthropomorphic response to motor behavior \\}
-Resonance behaviors have first been shown in the motor mirror neurons system, that is a neural network in motor areas that fire both during the execution of specific goal-oriented action and during the viewing of action directed toward the same goal~\cite{Rizzolatti1996, Kilner2009}.
-
-There are good evidence showing that the human brain responds to both human and robotic motion by activating motor mirror neurons \citet{Gazzola2007, oberman_eeg_2007}, stressing that the perceiving the goal of an action is more important than the human-likeness of its kinematic to activate resonance mechanisms.
-%For example, fMRI study \citet{Gazzola2007} have found no significant difference in the activation of the mirror neurons system during the observation of an industrial robot or of a human performing the same action, suggesting that the goal of the action is more important than its kinematics to activate resonnance mechanisms.
+%\subsection{Neuroscience review of anthropomorphic brain mechanisms in human-robot interaction}
+%The neuroscientific study of human-robot interaction is still in its infancy.
+So far most studies have used robots as a way to investigate humans behaviour and brain responses to perception of an artefactual agent actions and emotional states but have not really tapped in the study of how a human behaviours and brain processes are influenced by its direct interaction with a robot (add ref, ref).
+%We briefly review below the neuroscientific literature relevant to understand
+%the neural mechanisms that may underly anthropomorphism. 
+%
+%
+%
+%\paragraph{Mirror neurons and resonnance behaviors \\}
+%
+%Resonnance behaviors \citep{Rizzolatti1999} are mechanisms by which the brain areas involved in the internal representations of an action, an emotion or a sensation are equally recruited during the perception of another individual performing the same action or experiencing the same emotion or sensation.
+%
+%Resonnance behaviors have first been shown in the motor mirror neurons system, that is a neural network in motor areas that fire both during the execution of specific goal-oriented action and during the viewing of action directed toward the same goal~\cite{Rizzolatti1996, Kilner2009}.
+%
+%Interestingly, there are good evidence showing that motor mirror neurons in the
+%human brain respond to both human and robotic motion \citet{Gazzola2007, oberman_eeg_2007}, stressing that perceiving the goal of an action is more important than the human-likeness of its kinematic to activate resonnance mechanisms.
+%%For example, fMRI study \citet{Gazzola2007} have found no significant difference in the activation of the mirror neurons system during the observation of an industrial robot or of a human performing the same action, suggesting that the goal of the action is more important than its kinematics to activate resonnance mechanisms.
 %mirror neurons
-
-%[At stage 1] We suggest that the human's mirror neuron system is contributing to anthropomorphism by  allowing for a mapping of the robot's goal-directed actions into the human own motor repertoire \cite{Gallese1998, Wolpert2003, cullen2013individual}.
-
-\paragraph{Anthropomorphism and social behavior}
-In studying emotional perception in a human or a robot face using functional magnetic resonance imagery (fMRI) \citet{Chaminade2010} found reduced activity in response to the robot stimuli than to the human stimuli in emotional brain areas known to have mirror properties.
-However if the subject was asked to specifically attend to the emotional content of the stimuli, processing the robot facial expression, but not the human's, elicited a significant increase in the anterior part of the anterior frontal gyrus, a brain area considered as a marker of motor resonance.
-
-However, using electroencephalography another study have found that perception of emotions in a non-humanoid robot face affects the early brain processes of emotional expressions and the behavioral response of the participants the same way as did a human face \citep{Dubal2010}.
-
-%\citet{Dubal2010}: using robots with anthropomorphic (eyes, nose, mouth) featres but not human-like (ie.
+%
+%%[At stage 1] We suggest that the human's mirror neuron system is contributing to anthropomorphism by  allowing for a mapping of the robot's goal-directed actions into the human own motor repertoire \cite{Gallese1998, Wolpert2003, cullen2013individual}.
+%
+%The response of the human brain to a social signal perceived on a robot, such as facial
+%emotional expression is less evident. 
+%
+%In studying emotional perception in a human or a robot face using functional
+%magnetic resonnance imagery (fMRI) \citet{Chaminade2010} found reduced activity
+%in response to the robot stimuli than to the human stimuli in emotional brain
+%areas known to have mirror properties. However if the subject was asked to
+%specifically attend to the emotional content of the stimuli, processing of the
+%robot facial expresion, but not of the human's, elicited a significant increase in the anterior part of the anterior frontal gyrus, a brain area considered as a marker of motor resonnance.
+%
+%Using electroencephalograpy another study have found that perception of emotions in a non-humanoid robot face affects the early brain processes of emotional expressions and the behavioral response of the participants the same way as did a human face \citep{Dubal2010}.
+%
+%
+%
+%Thus it seems that the display of resonance mechanisms for social behaviour when
+%viewing a robot is less straightforward than for motor behaviour and may dependent more on the internal attitude and cognitive conceptions the human has of the robot. 
+%%Brain areas involved when attributing mental states to other human seem to be involved also in anthropomorphism .
+Indeed, individual scores of anthropomorphisms have been found to correlate with the grey matter volume of the left temporoparietal junction, a brain area activared during mentalizing \citet{cullen2013individual}
+%However, the studies reviewed above show that the human brain can respond
+%equally to a human or a robot stimuli but they do not  directly address the
+%question of anthropomorphism. Indeed, although it can contribute to it, neither
+%activation of mirror neurons system simulating a perceived action nor influence
+%on early brain processies readily imply that the human confers a humanlike mental
+%state to the robot and thus can not be sufficient to infer anthropomorphism 
+%
+%
+%%\citet{Dubal2010}: using robots with anthropomorphic (eyes, nose, mouth) featres but not human-like (ie.
 wires and cables) the study show effect of emotional state of the robot on early brain processes of emotional expression using ERPs (enhanced P1 in happy vs neutral state).
-
-Finally, individual tendency to anthropomorphize has been related to the grey matter volume of a brain area involved in mentalizing - the attribution of mental states to other human beings \citet{cullen2013individual, Frith2003}.
-
-Thus it seems that the display of resonance mechanisms for social behavior in a human-robot interaction is less straightforward than for motor behavior and may dependent more on the internal attitude and cognitive conceptions the human has of the robot.
-%Brain areas involved when attributing mental states to other human seem to be involved also in anthropomorphism .
-Indeed, individual scores of anthropomorphisms have been found to correlate with the grey matter volume of the left temporoparietal junction, a brain area activared during mentalizing \citet{cullen2013individual}
-
-%\paragraph{Emotions/Empathy}
-%Attitude of the human in a human-robot interaction might influence the anthropomorphic quality of the interaction: \citet{Chaminade2010} shows that directing attention towards emotional processing increases the responses to humanoid robot facial expression in the anteriror part of the left anterior frontal gyrus, a neural marker of motor resonnance.
-
-In the following section, we provide a tentative model of anthropomorphism in terms of cognitive correlates.
+%
+%\paragraph{Neural correlates of theory of mind and antropomorphism\\}
+%
+%
+%%From an early age, humans develop a tendency to explain one's own and others'actions in terms of beliefs, desires and goals called theory of mind or mentalizing allowing the implicit attribution of intentions and other mental states to others \citep{Frith2003}.
+%%A system of brain areas have been linked to mentalizing that encompass an anterior region of the medial prefrontal cortex (MPFC), that may be the basis to distinguish between mental and physical states representation, the temporal lobes, that may allow access to social knowledge  and the posterior superior temporal sulctuc (STS), that might be involved in detection of agency \citep{Frith2003}.
+%In a more direct study of anthropomorphism, \citep{cullen2013individual} related
+%participant's scores of tendency to anthropomorphize to the grey matter
+%volume of the left temporal junction, a brain area involved in mentalizing,
+%that is the attribution of mental states to other human beings (theory of mind) \citep{Frith2003}. 
+%
+%Of note, \citet{Waytz2010} showed that the more an artifical agent behaved
+%unpredictably, the more subjects tend to attribute it a mind and the more the
+%ventro medial prefrontal cortex (VMPFC), key area for sociocognitve processes
+%and especially egocentric mentalizing about similar others, gets activated.
+%
+%
+%%\paragraph{Emotions/Empathy}
+%%Attitude of the human in a human-robot interaction might influence the anthropomorphic quality of the interaction: \citet{Chaminade2010} shows that directing attention towards emotional processing increases the responses to humanoid robot facial expression in the anteriror part of the left anterior frontal gyrus, a neural marker of motor resonnance.
+%
+% 
+%
+%
+%In the following section, we provide a tentative model of anthropomorphism in terms of cognitive correlates.
 We warmly welcome the feedback and comments from both the cognitive sciences and robotics communities to further
-discuss these findings.
+%discuss these findings.
+%
+%
 
@@
 Empathy} is characteristic of this stage~\cite{rosenthalvonderPutten2013neural}.
-Anthropomorphism at this pre-cognitive stage might also be mediated by the motor and emotional resonance mechanisms at the neuronal level.
+
+%mediated by the motor and emotional resonnance mechanisms at the neuronal level.
 
@@
 anthropomorphism} (section~\ref{sec:ica}). 
-At this stage the human might also change his attitude towards the robot, paying more attention to social cue than to low-level behavior which may reinforce the resonance mechanisms.
+%At this stage the huma might also change his attitude towards the robot, paying more attention to social cue than to low-level behaviour which may reinforce the resonnance mechanisms.
 
@@
 process.  The result of this third phase would be an iteratively adapted
-cognitive model of the robot.
-It is also at this last stage that the human might modified its own abilities to anthropomorphize, having built a full cognitive model of the robot and know being able to attribute internal state to the robot.
+cognitive model of the robot. It is also at this last stage that the human might
+modified its own abilities to anthropomorphize, having built a full cognitive
+model of the robot and know being able to attribute internal state to the robot
+through his theory of mind.
 
@@
 HRI2013 paper}
+This is supported by the results from \citet{Waitz2010} seen in section
+\ref{sec:explanations} that people attribute more easily anthropomorphic
+features to artefacts when they have unpredictable behaviors.
 

### 2014-03-28 paper.tex
added back the mirror neurons in 2.2.2 and phase 1 and 2 of cog model

@@
 
-%\paragraph{Mirror neurons and resonnance behaviors \\}
-%
-%Resonnance behaviors \citep{Rizzolatti1999} are mechanisms by which the brain areas involved in the internal representations of an action, an emotion or a sensation are equally recruited during the perception of another individual performing the same action or experiencing the same emotion or sensation.
-%
-%Resonnance behaviors have first been shown in the motor mirror neurons system, that is a neural network in motor areas that fire both during the execution of specific goal-oriented action and during the viewing of action directed toward the same goal~\cite{Rizzolatti1996, Kilner2009}.
-%
-%Interestingly, there are good evidence showing that motor mirror neurons in the
-%human brain respond to both human and robotic motion \citet{Gazzola2007, oberman_eeg_2007}, stressing that perceiving the goal of an action is more important than the human-likeness of its kinematic to activate resonnance mechanisms.
-%%For example, fMRI study \citet{Gazzola2007} have found no significant difference in the activation of the mirror neurons system during the observation of an industrial robot or of a human performing the same action, suggesting that the goal of the action is more important than its kinematics to activate resonnance mechanisms.
-%mirror neurons
-%
-%%[At stage 1] We suggest that the human's mirror neuron system is contributing to anthropomorphism by  allowing for a mapping of the robot's goal-directed actions into the human own motor repertoire \cite{Gallese1998, Wolpert2003, cullen2013individual}.
-%
-%The response of the human brain to a social signal perceived on a robot, such as facial
-%emotional expression is less evident. 
-%
-%In studying emotional perception in a human or a robot face using functional
-%magnetic resonnance imagery (fMRI) \citet{Chaminade2010} found reduced activity
-%in response to the robot stimuli than to the human stimuli in emotional brain
-%areas known to have mirror properties. However if the subject was asked to
-%specifically attend to the emotional content of the stimuli, processing of the
-%robot facial expresion, but not of the human's, elicited a significant increase in the anterior part of the anterior frontal gyrus, a brain area considered as a marker of motor resonnance.
-%
-%Using electroencephalograpy another study have found that perception of emotions in a non-humanoid robot face affects the early brain processes of emotional expressions and the behavioral response of the participants the same way as did a human face \citep{Dubal2010}.
-%
-%
-%
+At lower, more automatic, level, robots have been shown to elicit resonnance behaviors in the
+human brain.
+Resonnance behaviors \citep{Rizzolatti1999} are mechanisms by which the brain areas involved in the internal representations of an action, an emotion or a sensation are equally recruited during the perception of another individual performing the same action or experiencing the same emotion or sensation.
+The neurons showing resonnant properties have been called mirror neurons and
+have been found in a wide range of modalities (motor, emotional etc..)
+\fixme{addref}.Seeing a robotic arm reaching for an object activates the motor mirror neurons the same way as for seeing a human arm reaching for the same object
+\citep{Gazzola2007, oberman_eeg_2007}. However, a study of emotion perception
+on a robotic face found reduced activity in emotional brain
+area known to have mirror properties in response to the robotic face compared to
+a human face \citep{Chaminade2010}. Nevertheless, these authors showed that when
+the participants were explicitely instructed to pay attention to the robot's
+emotional expression, motor mirror neurons gets activated.
+Interestingly, using electroencephalography,  it has also been shown that
+emotional behavior elicited by a robot face influences the speed of human
+responses as well as early brain processes the same way as emotional expression
+of a human face did \citep{Dubal2010}.
+
 %
@@
 mind but also the unpredictable feature of the agent behavior alone seems to be
-sufficient.  
+sufficient. Low-level mechanisms of the brain that allow humans to map other's
+motor behaviors into their own repertoire are equally elicited when perceiving a
+robot's action. It is not yet clear whether human are processing emotional
+signal from a robot the same way as they do for human beings. 
 %were recently demonstrated at the brain level~\citep{cullen2013individual}.
@@
 Empathy} is characteristic of this stage~\cite{rosenthalvonderPutten2013neural}.
+It is also at this stage that automatic activation of the human's mirror neurons
+system  in response to viewing the robots action and human automatic emotional
+responses are contributing at a lower level
+to the intuitive anthropomorphization (see Section 2.2.2 \fixme{put ref})
+%We suggest that the human's mirror neuron system is contributing to anthropomorphism by  allowing for a mapping of the robot's goal-directed actions into the human own motor repertoire \cite{Gallese1998, Wolpert2003, cullen2013individual}.
 
@@
 anthropomorphism} (section~\ref{sec:ica}). 
-%At this stage the huma might also change his attitude towards the robot, paying more attention to social cue than to low-level behaviour which may reinforce the resonnance mechanisms.
+At this stage the human might also change his attitude towards the robot, paying more attention to social cue than to low-level behaviour which may reinforce the resonnance mechanisms.
 

### 2014-03-31 paper.tex
new bib item, minor refinements / typos first 5 pages

@@
 
-\title[The Dynamics of Anthropomorphism]{The Dynamics of Anthropomorphic Effects in Human-Robot Interaction}
+\title[The Dynamics of Anthropomorphism]{The Dynamics of Anthropomorphism in Human-Robot Interaction}
 \author[\firstAuthorLast ]{\Authors}
@@
 Valley hypothesis suggests, which in turn should foster people's acceptance of
-the artificial agent, and enable effective (human-like and especially
+the artificial agent, and enable effective (human-like and 
 human-social) interaction.  However, at a certain point as the non-human agent
@@
 \textbf{anthropomorphism} (noted \Ant in this paper) by considering the phenomenon
-\textbf{as a whole}: robotics researchers often tend to believe that
+as a whole: robotics researchers often tend to believe that
 anthropomorphism only describes a static set of human-like features of a robot
@@
 characteristics as the \emph{anthropomorphic design} of the
-robot~\cite{fink_anthropomorphism_2012}. But \emph{anthropomorphism} in general
+robot~\citep{fink_anthropomorphism_2012}. But \emph{anthropomorphism} in general
 refers to the larger \emph{social phenomenon} that emerges from the (real or
@@
 socio-cognitive dimensions of anthropomorphism are essential to understand the
-complex bonds that human users build with the robots.
+complex bonds that human users build with robots.
 
@@
 To support the reflection, it may be useful to consider a few experimental
-results. We studied anthropomorphism effects in several short- and long-term
+results. We studied anthropomorphism in several short- and long-term
 human-robot interaction studies that we carried out with embodied robots, both
@@
         \centering
-        \begin{subfigure}[b]{0.48\columnwidth}
+        \begin{subfigure}[t]{0.48\columnwidth}
                 \includegraphics[width=\textwidth]{roomba-activities.png}
-                \caption{Roomba activities}
+                \caption{Activities related to Roomba, n = 9 households}
                 \label{fig:roomba-activities}
         \end{subfigure}%
-        ~ %add desired spacing between images, e. g. ~, \quad, \qquad etc.
-          %(or a blank line to force the subfigure onto a new line)
-        \begin{subfigure}[b]{0.48\columnwidth}
+        \hspace{0.5cm} 
+        \begin{subfigure}[t]{0.48\columnwidth}
                 \includegraphics[width=\textwidth]{roomba-perception.pdf}
-                \caption{Roomba perception}
+                \caption{People's perception of Roomba, n = 15 participants}
                 \label{fig:roomba-perception}
         \end{subfigure}
-    \caption{Usage and perception of the Roomba robot over a 6 months period.}
+    \caption{Usage and perception of the Roomba vacuum-cleaning robot over a 6 months period.
+Qualitative data suggest that people's activities related to the robot as well as their perception of the robot change over time.
+Overall, a rather low social engagement of the users with the robot, and few perception of human-likeness in the robot were found.}
     \label{fig:roomba}
@@
 (cognitive) interaction with an artifact perceived as non-intelligent and with
-no impact on his/her life (and the level of activity pictured on
+no impact on one's life (and the level of activity pictured in
 Figure~\ref{fig:roomba-activities} qualitatively confirms this intuition). Even
@@
 Those questions are certainly not new, but paradoxically, while anthropomorphism
-in robotics is a commonly discussed trait of human-robot interaction, it appears
+is a commonly discussed trait of human-robot interaction, it appears
 that we lack formal grounds and models that would account for the long-term
@@
 
+\begin{figure}[h!]
+        \centering
+        \begin{subfigure}[b]{0.48\columnwidth}
+                \centering
+                \includegraphics[width=0.75\textwidth]{ranger}
+                \caption{Interaction scenario of the \emph{Ranger} domino study: the robot toy box Ranger transports domino tiles between the two children}
+                \label{fig:ranger-expe}
+        \end{subfigure}%
+        \hspace{0.5cm}
+        \begin{subfigure}[b]{0.48\columnwidth}
+            \includegraphics[width=\textwidth]{ranger-interactions-vs-qualitative-score}
+            \caption{Qualitative level of anthropomorphic projections ($y$-axis) versus the actual interactions with the robot ($x$-axis) are negatively correlated.}
+            \label{fig:qualitative-score}
+        \end{subfigure}
+        \caption{Children`s interactions with the Ranger robot toy box, and their anthropomorphic projections onto the robot.
+Overall, large variations of both children`s behavior and their perception of the robot were found but seemed to be correlated to each other.}
+    \label{fig:ranger}
+\end{figure}
+
+%\fixme{It was written as caption of fig:ranger: ``Level of interaction with a semi-anthropomorphic robot is \emph{not} a predictor of anthropomorphic projections.'' Comment JF: this statement does not make sense to me as we found a significant negative correlation between the two.}
+
 Figure~\ref{fig:qualitative-score} calls for other initial remarks. This diagram
-comes from a (yet unpublished) study where 13 pairs of children (4-5 years old)
-played for about 20 minutes a Domino game with a robot (the robot was tasked to
+shows data from a (yet unpublished) study in which 13 pairs of children (4-5 years old)
+played for about 20 minutes a Domino game with a robot toy box (the robot was tasked to
 carry domino pieces from one child to the other, Figure~\ref{fig:ranger-expe}).
 The $x$-axis represents the number of social interactions between the children
-and the robot (like talking or showing objects), based on video annotations. On
+and the robot (like talking to the robot or showing objects), based on video annotations. On
 the $y$-axis, we have a synthetic qualitative measurement of anthropomorphic
-projections based on two questionnaires. The correlation between both these
+projections onto the robot, based on two interviews with the children. The correlation between both these
 values is significantly \emph{negative}: the more the children engaged into
@@
 
-\begin{figure}[h!]
-        \centering
-        \begin{subfigure}[t]{0.48\columnwidth}
-                \centering
-                \includegraphics[width=0.6\textwidth]{ranger}
-                \caption{The \emph{Ranger} Domino study}
-                \label{fig:ranger-expe}
-        \end{subfigure}%
-        ~ %add desired spacing between images, e. g. ~, \quad, \qquad etc.
-          %(or a blank line to force the subfigure onto a new line)
-        \begin{subfigure}[t]{0.48\columnwidth}
-            \includegraphics[width=0.9\textwidth]{ranger-interactions-vs-qualitative-score}
-            \caption{Qualitative level of anthropomorphic projections versus
-            actual interactions with the robot}
-            \label{fig:qualitative-score}
-        \end{subfigure}
-        \caption{Level of interaction with a semi-anthropomorphic robot is
-        \emph{not} a predictor of anthropomorphic projections.}
-    \label{fig:ranger}
-\end{figure}
-
 These results may seem counter-intuitive at first sight, and illustrate that the
@@
 These first remarks lead to the main question we attempt to address in this
-article: how can we understand \emph{anthropomorphism} as a whole, and in such a
-way that is support improved human-robot interactions?
-
-Based on an extensive literature review~\citep{fink_anthropomorphism_2012},
-several field and lab studies previously mentioned and insights from the
-cognitive neurosciences, we propose to discuss anthropomorphism from three
-complementary perspectives.
-
-First, we would like to clarify what anthropomorphism actually \emph{means}:
-besides the \emph{artifact-centered} understanding of anthropomorphism, it
-seems important to explicit the human and social factors of anthropomorphism.
-
-Then, we propose a model to understand how anthropomorphism evolves over time.
-These dynamics are non-monotonic, and psychological factors like the
+article: how can we understand \emph{anthropomorphism} as a whole, \hl{and in such a
+way that is support improved human-robot interactions?}\fixme{JF: something's wrong with this sentence}
+
+We propose to discuss anthropomorphism from three
+complementary perspectives:
+
+%Based on an extensive literature review~\citep{fink_anthropomorphism_2012},
+%several field and lab studies previously mentioned, and insights from the
+%cognitive neuroscience, we propose to discuss anthropomorphism from three
+%complementary perspectives.
+
+First, by reviewing what anthropomorphism actually \emph{means}:
+besides an \emph{artifact-centered} understanding that explains anthropomorphism from the human-like design of the non-human artifact, it seems important to explicit the social component, namely a \emph{human-centered} understanding, of anthropomorphism.
+
+Second, we propose a model, called the \textit{Dynamics of Anthropomorphism} to understand how anthropomorphism evolves over time ~\citep{lemaignan2014dynamics}.
+These dynamics are non-monotonic, and effects like the
 \emph{novelty effect} play here a key role.
@@
 
-\paragraph{Two hypotheses} Our research question also translates to two
+%\paragraph{Two hypotheses}
+Our research question also translates to two
 hypotheses, which structure the reflections of this article:
@@
 \begin{enumerate} 
-
-\item A person's tendency to anthropomorphize a robot
+\item ~A person's tendency to anthropomorphize a robot
     is based on several factors, including (but not limited to) (1) the
@@
 
-\item A person's tendency to anthropomorphize a robot
+\item ~A person's tendency to anthropomorphize a robot
     evolves in a non-linear way over time and with growing experience that the
@@
 
-\begin{inparaenum}[\itshape 1)\upshape]
-
-The remainder of this article is organized as follows.  First, in Section
-\ref{sec:overview-studies}, we give a brief overview on the various studies that
-we conducted to investigate anthropomorphism, namely \item the Roomba study,
-\item the Forum study, \item the Ranger domino study. Next, Section
-\ref{sec:anthropomorphism} aims to establish a common ground in the
-understanding of anthropomorphism. We first explore an artifact-centered
-perspective and briefly outline how the human-like design of agents can
-encourage anthropomorphism.  Then, we explore a human-centered perspective
-by integrating theories from cognitive science, developmental and social
-psychology that serve to explain anthropomorphism. At the end of this
-section we bring both perspectives together and interpret that
-anthropomorphism is a multi-factor phenomenon.  Based on the two previous
-sections, Section~\ref{sec:our-ideas} introduces an initial model of the
-\textit{dynamics of anthropomorphism}. This model describes the variances
+%\begin{inparaenum}[\itshape 1)\upshape]
+
+The remainder of this article is organized as follows.
+According to the three perspectives that we take, 
+we first (in Section
+%\ref{sec:overview-studies}, we give a brief overview on the various studies that
+%we conducted to investigate anthropomorphism, namely \item the Roomba study,
+%\item the Forum study, \item the Ranger domino study. Next, Section
+\ref{sec:anthropomorphism}) aim to establish a common ground in the
+understanding of anthropomorphism. We review literature from several relevant domains and integrate the different explanations into an understanding of
+anthropomorphism as a multi-factor phenomenon.
+Based on this, Section~\ref{sec:our-ideas} introduces our initial model of the
+\textit{Dynamics of Anthropomorphism}. This model describes the variances
 and dynamics of people's tendency to anthropomorphize an artificial agent,
-such as a robot.  Then Section \ref{sec:cognition-neuroscience} presents a
+such as a robot. 
+Then Section \ref{sec:cognition-neuroscience} presents a
 cognitive and neuroscience perspective on anthropomorphism to consolidate
-our considerations and the proposed model.  This is followed by a discussion
+our considerations and the proposed model.
+This is followed by a discussion
 about the limitations of our approach (Section \ref{sec:discussion}) and the
 existing and alternative ways to measure anthropomorphism in human-robot
-interactions.  Finally, Section \ref{sec:conclusion} concludes this article
+interactions.
+Finally, Section \ref{sec:conclusion} concludes this article
 and offers starting points for further research on anthropomorphism and the
@@
 
-\end{inparaenum}
+%\end{inparaenum}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-% JULIA: there will be 4-5 subsections
-%	1) anthropomorphism as a social phenomenon, definitions, origins, etc.
-%	2) anthropomorphism as a consequence of anthropomorphic / life-like design
-%	3) the link to robotics and HRI, mention the uncanny valley theory ...
-%	4) however: we suggest anthropomorphism is more than a static feature ...
-%
-%
 
@@
 the relationship between the human who anthropomorphizes, and the non-human agent 
-which is anthropomorphized. Though commonly observed, it appears controversial, at 
+which is anthropomorphized. Though commonly observed, it still appears controversial, at 
 the same time, that humans tend to \textit{``see human in the non-
 human''} \citep{epley_seeing_2007}. 
-Anthropomorphism as a social phenomenon arises in an interaction 
-\citep{persson_anthropomorphism_2000}, and thus includes at least two interaction 
-partners: the human and the real or imagined non-human agent. Therefore, one can 
-take two main perspectives on explaining anthropomorphism \citep{lee_human_2005}: a human-centered and an artifact-centered. We briefly outline both views in the following. 
+To shed light on this phenomenon, first of all, we would like to propose a clarification of terms.
+In short, we propose to differentiate between \textbf{anthropomorphic form} to refer to an imitation of human-like form in the \textit{design} of artificial agents, and  \textbf{anthropomorphism} to refer to the social phenomenon of
+people's tendency to \textit{perceive} human-likeness in non human-like agents.
+\citep{fink_anthropomorphism_2012} In the following, we might use the terms \texitit{form} and \textit{design} interchangeably.
+
+As anthropomorphism arises in an interaction between a human and a non-human agent
+\citep{persson_anthropomorphism_2000}, one can also
+take two main perspectives on explaining anthropomorphism \citep{lee_human_2005}: an artifact-centered perspective and a human-centered perspective. 
+We now first present an artifact-centered perspective on anthropomorphism, and outline how 
+robotics uses \textit{anthropomorphic design} to encourage 
+people to interact in a social way with robots.
+Then, we present a human-centered 
+perspective and shed light on \textit{anthropomorphism as a social phenomenon}. We present 
+theories from psychology and cognitive science to explain people's tendency to 
+perceive human-like characteristics in non-human agents.
 It has to be kept in mind that both perspectives are inseparable; they apply at the 
@@
 on the same phenomenon.
-
-By doing so, this section tries to create a common ground in the understanding of 
-anthropomorphism, with a focus on the design of robots and human-robot interaction. 
-First of all, we would like to propose a clarification of terms.
-In short, we propose to use two different terms, in order to differentiate between the human-like design of a non-human agent, and the perception of human-likeness in a non-human agent.
-We use the terms \textit{``anthropomorphic design''} and \textit{``anthropomorphic 
-form''} interchangeably to refer to an imitation of human form (or in a broader sense 
-also animal and natural) in the design of objects and artificial agents. We propose to 
-\textit{not} refer to this as \textit{anthropomorphism}.
-Because we use \textit{anthropomorphism} to refer to the social phenomenon of 
-people's tendency to perceive human-likeness in non human-like agents. This is an important differentiation.
-
-In the following, we first present an artifact-centered perspective on anthropomorphism, and outline how 
-the human-like design approach (\textit{anthropomorphic form}) is used in robotics to encourage 
-people to interact in a social way with robots. Then, we apply a human-centered 
-perspective and shed light on \textit{anthropomorphism as a social phenomenon}. We present 
-theories from psychology and cognitive science to explain people's tendency to 
-perceive human-like characteristics in non-human agents. In the end, we synthesize 
-the presented backgrounds and suggest an extended understanding of anthropomorphism 
+In the end of this section, we synthesize 
+the presented backgrounds into an extended understanding of anthropomorphism 
 as a multi-factor phenomenon.
@@
 An artifact-centered perspective explains anthropomorphism from the ascertainable 
-parts / the form of the non-human agent, namely the anthropomorphic design of it.
-Using the term \textit{``form''} to describe the design of an artifact, we refer 
-not only to the shape of an artifact (how the artifact looks like) but to the total 
-expression of the product \citep{bartneck_shaping_2004}. \cite{disalvo_hug:_2003} 
+parts of the non-human agent, namely the anthropomorphic form of it.
+Using the term \textit{form} to describe the design of an artifact, we refer 
+not only to the shape (how it looks like) but to the total 
+expression of the artifact \citep{bartneck_shaping_2004}. \cite{disalvo_hug:_2003} 
 argues that \textit{form} includes a product's physical shape, materials, and 
-behavioral qualities. Latter aspect is of special importance for interactive 
+behavioral qualities. The behavioral aspect is of special importance for interactive 
 systems that show some degree of autonomy (independence).
@@
 design of non-human things is as old and manifold as people's tendency to anthropomorphize. 
-Anthropomorphic (and also animal-shaped) forms were used already in prehistoric 
-artworks and illustrations, and they have a long-standing tradition in design in 
-general, and with respect of the design of daily life things, in particular 
+Anthropomorphic (and life-like) forms have a long-standing tradition in design in general, and in the design of daily life things, in particular 
 \citep{norman_design_1988,guthrie_bottles_2000}.
+Interestingly, from its very beginning the image of a robot exists as an outstanding challenge to mankind \citep{replicant_????}.
+Starting from when the term \texit{robot} first appeared in a play by Karel \^{C}apek in the 1920ies, robots were man-made beings, created as the \textit{``shadow of man''} (and sometimes resembling a human being in appearance).
 

### 2014-04-01 paper.tex
minor modifications in the first sections and restructuring of 2.2

@@
 designs of objects and non-human agents can evoke both positive and negative feelings 
-of affinity in the human observer / user. Positive feelings reflect the experience of 
+of affinity in the human observer / user. A positive valence reflects the experience of 
 emotional engagement with and feelings of empathy for the non-human agent
-\citep{cheetham_human_2011}. The positive effect of so-called
-\textbf{anthropomorphic form} is exploited in the design of artificial agents
-(\eg digital characters, robots) for several reasons. Amongst others,
-anthropomorphic design should serve to evoke a positive valence as the Uncanny
-Valley hypothesis suggests, which in turn should foster people's acceptance of
-the artificial agent, and enable effective (human-like and 
-human-social) interaction.  However, at a certain point as the non-human agent
+\citep{cheetham_human_2011}. This in turn may lead to an effective (human-like and 
+human-social) interaction with the non-human agent, and increase people's acceptance of
+it. 
+However, at a certain point as the non-human agent
 approaches but fails to closely resemble a human, the evoked valence in the
@@
 \cite{mori_uncanny_1970} describes as disgust and revulsion. This, in turn,
-might lead to rejection of the non-human but human-like agent.  The Uncanny
+might lead to rejection of the non-human agent. The Uncanny
 Valley hypothesis predicts that with further increasing the human-likeness of
@@
 positive one, reflecting feelings and engagement that are similar as those
-evoked by a human-human interaction.  Of course, roboticists and developers try
-to avoid ``falling'' into this Uncanny Valley with their human-like designs of
-artificial agents. Consequently, there is a considerable research effort to
+evoked by a human-human interaction. 
+Of course, developers and designers of artificial agents
+(\eg virtual characters, robots) try to exploit the positive effects of 
+\textbf{anthropomorphic form} and avoid ``falling'' into this Uncanny Valley.
+Consequently, there is a considerable research effort to
 better understand the boundaries of anthropomorphic design and their effects
@@
 
+A phenomenon that is often studied related to the human-like design of objects and 
+artificial agents is \textbf{anthropomorphism}.
 Along this line, this article aims at fostering a better understanding of
-\textbf{anthropomorphism} (noted \Ant in this paper) by considering the phenomenon
-as a whole: robotics researchers often tend to believe that
+anthropomorphism (noted \Ant in this paper) in human-robot interaction 
+by considering the phenomenon
+as a whole. Robotics researchers often tend to believe that
 anthropomorphism only describes a static set of human-like features of a robot
@@
 characteristics as the \emph{anthropomorphic design} of the
-robot~\citep{fink_anthropomorphism_2012}. But \emph{anthropomorphism} in general
-refers to the larger \emph{social phenomenon} that emerges from the (real or
-imagined) \emph{interaction} between a robot and a
-user~\citep{persson_anthropomorphism_2000}. According to~\cite{epley_when_2008},
-this includes for instance emotional states, motivations, intentions
-\emph{ascribed by the user} to the robot. As such, the dynamic and
+robot~\citep{fink_anthropomorphism_2012}, and propose that \emph{anthropomorphism} in 
+general refers to a \emph{social phenomenon} that emerges from the (real or
+imagined) \emph{interaction} between a non-human agent (\eg a robot) and a 
+human~\citep{persson_anthropomorphism_2000}. According to~\cite{epley_when_2008},
+anthropomorphism includes that the human perceives, for instance, emotional states, motivations, or 
+intentions in the non-human agent, and tends to ascribe those qualities to it.
+As such, the dynamic and
 socio-cognitive dimensions of anthropomorphism are essential to understand the
-complex bonds that human users build with robots.
+complex bonds that human users build with artificial agents such as robots.
 
@@
 
-To support the reflection, it may be useful to consider a few experimental
+To support the reflection on variances and dimensions of anthropomorphism, it may be 
+useful to consider a few experimental
 results. We studied anthropomorphism in several short- and long-term
@@
     \caption{Usage and perception of the Roomba vacuum-cleaning robot over a 6 months period.
-Qualitative data suggest that people's activities related to the robot as well as their perception of the robot change over time.
-Overall, a rather low social engagement of the users with the robot, and few perception of human-likeness in the robot were found.}
+Qualitative data suggest that people's activities related to the robot as well as their perception of the robot change over time.}
     \label{fig:roomba}
@@
             \includegraphics[width=\textwidth]{ranger-interactions-vs-qualitative-score}
-            \caption{Qualitative level of anthropomorphic projections ($y$-axis) versus the actual interactions with the robot ($x$-axis) are negatively correlated.}
+            \caption{We found a significant negative correlation ($p=0.048$) between the
+    number of interactions and the qualitative anthropomorphic projections. n = 13 groups}
             \label{fig:qualitative-score}
         \end{subfigure}
-        \caption{Children`s interactions with the Ranger robot toy box, and their anthropomorphic projections onto the robot.
+        \caption{Children`s interaction with Ranger, and their anthropomorphic projections onto the robot.
 Overall, large variations of both children`s behavior and their perception of the robot were found but seemed to be correlated to each other.}
@@
 people's tendency to \textit{perceive} human-likeness in non human-like agents.
-\citep{fink_anthropomorphism_2012} In the following, we might use the terms \texitit{form} and \textit{design} interchangeably.
+\citep{fink_anthropomorphism_2012} In the following, we might use the terms \texit{form} and \textit{design} interchangeably.
 
@@
 take two main perspectives on explaining anthropomorphism \citep{lee_human_2005}: an artifact-centered perspective and a human-centered perspective. 
-We now first present an artifact-centered perspective on anthropomorphism, and outline how 
+We now first present an artifact-centered perspective, and outline how 
 robotics uses \textit{anthropomorphic design} to encourage 
-people to interact in a social way with robots.
+people to interact in a social, human-like way with robots.
 Then, we present a human-centered 
@@
 \citep{norman_design_1988,guthrie_bottles_2000}.
-Interestingly, from its very beginning the image of a robot exists as an outstanding challenge to mankind \citep{replicant_????}.
-Starting from when the term \texit{robot} first appeared in a play by Karel \^{C}apek in the 1920ies, robots were man-made beings, created as the \textit{``shadow of man''} (and sometimes resembling a human being in appearance).
+Interestingly, from its very beginning robots were resembling a human being in their appearance.
+Starting from when the term \texit{robot} first appeared in a play by Karel \^{C}apek in the 1920ies, robots were man-made beings, created as the \textit{``shadow of man''} \citep{replicant_????}.
 
 The direction of causality in the artifact-centered view is that the non-human artifact 
-(or a certain feature of it) encourages the human to anthropomorphize the artifact / 
-agent. This perspective assumes that humans directly respond to life-like and social 
-cues that the non-human agent or system emits, without thoughtful mental processing, 
-by simply applying stereotypes and heuristics to it, and in turn apply 
-human-human social schemas and norms to the occurring interactions.
-This view is acceptable since humans naturally react to specific 
+(or a certain feature of it) encourages the human to anthropomorphize it. 
+This perspective assumes that humans directly (mindlessly) respond to life-like and social 
+cues that the non-human agent or system emits \citep{nass_machines_2000}. Without thoughtful mental processing, 
+humans tend to simply apply stereotypes and heuristics to the non-human agent, and in turn apply human-human social schemas and norms to the occurring interactions.
+\cite{takayama_perspectives_2012} propose to refer to this immediate (sometimes visceral) sense in a situation as \textit{in-the-moment}, compared to a more distanced cogitation and consideration which she calls \textit{reflective}.
+(As this distinction imply different cognitive processes, we will come back to it later, in the human-centered perspective, Section \ref{sec:human-centered}).
+
+The view of people mindlessly reacting in a human-social manner to anthropomorphic forms
+is based on the fact that humans naturally react to specific 
 cues. From early childhood 
@@
 or to respond to social cues, such as facial expressions, social gestures or turn-taking.
-Also \cite{takayama_perspectives_2012} states that humans have a propensity toward particular cues that seem to trigger automatic interpersonal social responses.
-One has to keep in mind that these cues are of various senses and modalities in human-
-human interaction, and consequently human-like design also addresses several senses. 
+Humans have a propensity toward particular cues that seem to trigger automatic interpersonal social responses \citep{takayama_perspectives_2012}.
+One has to keep in mind that in 
+human-human interaction these cues are of various senses and modalities, 
+and consequently human-like design is also realized addressing several senses. 
 One of the most outstanding aspects is probably the outer appearance of an agent or 
@@
 the object is overall perceived. Consequently, if a robot's outer form resembles a 
-human, the robot is likely to be treated similar to a human (\eg eye-contact is 
-established or the robot is greeted).
-
-People's natural reaction to anthropomorphic design is exploited in the design of 
+human, the robot is likely to be treated similar to a human.
+Besides the physical shape of a robot, other more subtle anthropomorphic forms can be found in robots, including human-social behavioral cues (\eg eye-gaze), social gestures (\eg waving), or verbal politeness (\eg greeting, apologizing).
+
+People's natural reaction to these and other anthropomorphic design cues of
 robots (in particular, social or also called \textit{sociable} robots 
-\citep{breazeal_sociable_2000}) and other things, however, consequences can be both of 
-positive and negative nature, which makes anthropomorphic form an interesting subject 
-of study.
+\citep{breazeal_sociable_2000}) are extensively studied.
+This research is of particular interest in human-robot interaction as the consequences of anthropomorphic design can be both of positive and negative nature, and it is yet not clear what exactly it is that makes the difference.
 
@@
 people perceive it, interact with it, and build long-term relationships with 
-it \cite{bartneck_shaping_2004}. 
+it \citep{bartneck_shaping_2004}. 
 The principle of human-like form is probably most prominent in the design of robots, 
@@
 match the affordances that this to humans adapted world brings along. 
-Apart from this, it is suggested that increasing the human-likeness of a robot (up to a 
+Apart from this, it is suggested that an increased human-likeness of a robot (up to a 
 certain threshold) will generally lead to 
@@
 appears to be beneficial for human-robot relations, especially with socially 
-interactive robots \cite{fong_survey_2003}. Consequently, the domain of (social) 
+interactive robots \citep{fong_survey_2003}. Consequently, the domain of (social) 
 robotics tries to exploit this by using
@@
 \hl{expectations} of human and animalistic life onto artificial agents that use 
-anthropomorphic (or zoomorphic) forms \cite{schmitz_concepts_2011}. 
+anthropomorphic (or zoomorphic) forms \citep{schmitz_concepts_2011}. 
 Both cognitive science 
@@
 shown that perceived similarity between the user and the robot influences the intensity of 
-the participants' attributions towards the robot. Thus,the anthropomorphic design of a robot 
+the participants' attributions towards the robot. Thus, the anthropomorphic design of a robot 
 impacts the user's perception of the robot, and how far the user is likely to attribute and 
 experience qualities such as intelligence, fun, or intentions in the robot. 
-However, this is not a natural spontaneous reaction to anthropomorphic form but already a thoughtful process (investigated as the process of forming a \textit{mental model}), which will be treated in more detail later, in Section \ref{sec:human-centered}).
+These experiences mark the transition between an immediate \textit{in-the-moment} and more thoughtful \textit{reflective} \citep{takayama_perspectives_2012} perception of, and interaction with the robot.
+As such, a more human-centered perspective needs to be applied, and we will come back to this in Section \ref{sec:human-centered}.
 
@@
 
+\subsubsection{Why do people anthropomorphize?\\}
+\label{sec:explanations}
+
+But why do people anthropomorphize?
+First and foremost, it needs to be mentioned that anthropomorphism is a fairly complex phenomenon.
+Paradoxically, there is a huge and diverse body of literature on it but nevertheless, it seems that anthropomorphism is still not very well understood (especially in a field as young as HRI).
+
+One common reason for anthropomorphism is that by perceiving some human-like characteristics in the non-human agent, this agent is made more \emph{graspable}, \emph{understandable}, \emph{predictable}, and one can feel \emph{more empathetic} toward it, and possibly one can then anticipate the agent's behavior.
+These are central motivations when trying to explain anthropomorphism, and we will come back to them in more detail later on.
+It is described that for the just mentioned reasons, people commonly anthropomorphize their pets, by ascribing mental states, intentions or feelings to them\footnote{Interestingly, pet-ownership seems to have a significant impact on human-robot interaction: several studies suggest that pet-owners are more likely to anthropomorphize technologies and robots than non pet-owners} \cite{eddy_attribution_1993}.
+But how can these motivations behind anthropomorphism be explained from a human-centered point of view?
+
+%Anthropomorphism as a social phenomenon arises in an interaction \citep{persson_anthropomorphism_2000}, and thus includes at least two interaction partners (the human and the real or imagined non-human agent).
+Therefore, one can take two main perspectives on explaining it \citep{lee_human_2005}: a human-centered, and an artifact-centered.
+We briefly outline both views in the following.
+It has to be kept in mind that both perspectives are inseparable; they apply at the same time, and we would like to present them here just as two different viewpoints on the same kind of phenomenon.
+
+This perspective builds on research from developmental and social psychology as well as cognitive sciences.
+In the following, we present what we found in reviewing this literature: (1) a line of research in developmental psychology that studies the attribution of animacy; (2) a line of research in more cognitive sciences that studies the cognitive processes that underlie anthropomorphism, and (3) a theory that explains anthropomorphism based on psychological factors~\citep{epley_seeing_2007}.
+All three branches apply a human-centered perspective on anthropomorphism.
+
+\paragraph{Developmental psychology research on the attribution of animacy and intention\\}
+
+The phenomenon of attributing animacy and intentions to nonliving objects such as simple shapes has been intensively studied in developmental psychology.
+As mentioned earlier, Piaget found that children tend to ascribe life to the nonliving.
+They also tend to interpret physical phenomena in terms of intention on the part of the non-human subject.
+For instance children are likely to argue that \textit{``the sun is hot because it wants to make people warm''} \citep{leeds_childrens_1992}.
+In this example it is in fact questionable whether children really anthropomorphize the sun (believing that it has an intention) or whether they are using anthropomorphism in a metaphoric sense (because their conceptions of the world and of the living are not yet fully formed).
+Later however, two famous experiments by \cite{heider_experimental_1944} and \cite{michotte_perception_1963} showed that also adult participants attribute animacy and intention to simple things and shapes based on motion.\footnote{For more details, the reader may refer to the ``attribution theory''.} In both experiments, participants viewed animations of simple shapes, such as circles or triangles.
+%(see Figure \ref{fig:animacy_attribution})
+Asked to describe what they observed, most people developed elaborate stories, attributing motivations, emotions and relationships between the objects.
+
+%\begin{figure}[h]\centering
+%% Use the relevant command to insert your figure file.
+%% For example, with the graphicx package use
+%  \includegraphics[scale=0.6]{heider-simmel_animation.jpeg}
+%% figure caption is below the figure
+% \caption{Fritz Heider and Mary-Ann Simmel's animated film to study people's tendency to attribute animacy and intention to simple shapes; \textit{An experimental study of apparent behavior}, 1944}
+% \fxnote{wrap text around this figure?}
+% \label{fig:animacy_attribution}       % Give a unique label
+% \end{figure}
+
+Summing it up, as mentioned earlier, it seems that there is a natural, relatively spontaneous reaction that accounts for people's tendency to attribute animacy and intention to moving shapes, even when there is no similarity of the shape to a human.
+This tendency to animize / anthropomorphize is already developed (and even more distinct) in infants and children.
+Thus besides the anthropomorphic cues emitted by the design of the artifact, also developmental stages, and people's natural reaction play a role how far we interpret movements / motions (as one of the most basic "lifelike" cues), for instance.
+
+\paragraph{Cognitive science research, the mental model theory (Theory of Mind)
+and neural correlates of anthropomorphism\\}
+
+Anthropomorphism and similar phenomenons can also be understood as a thoughtful process of induction whereby \textit{``people reason about an unknown stimulus based on a better-known representation of a related stimulus"}~\citep{epley_when_2008}.
+In the case of anthropomorphism this means a person's reasoning about a non-human agent based on the representation of the self or other humans.
+A central construct of this perspective is the so-called \textit{mental model} that a person has (and builds) of the agents she is reasoning about and interacting with.
+The specific mental model we have about an artifact / agent basically explains (in our individual way to ourselves) how this artifact / agent works the way it does.
+There are two central aspects here, when looking at the quote from \citep{epley_when_2008} above.\\
+\textit{(1)} One assumption is that the user is not familiar with the other agent.
+This is basically true for all other agents (and entities) but oneself because we can only be our self.
+This view is also consistent with the \emph{familiarity thesis}~\citep{hegel_understanding_2008} which claims that we understand the world based upon a mental model of the world that we are most familiar with (our self).
+Thus, we can best use our self as source of induction when reasoning about other agents.
+However, in case we would like to understand the behavior of a spider, we would probably not use our mental model of a human (or our self) simply because we do not have many things in common with a spider.
+And this is the second central aspect here.\\
+\textit{(2)} One other assumption is based on the anthropomorphic design of the other agent (see Section \ref{sec:anthropomorphic-design}): if the agent behaves (appears) much like a human being (\eg a robot that emits a human voice), people's mental model of the agent's behavior is likely to approach their mental model of humans (though the model may differ in some important aspects).
+
+This cognitive viewpoint on anthropomorphism is important because people's estimation of an agent's knowledge model and its capabilities affects the way they relate to it.
+This holds important implications for the resulting interaction with the system, the user experience, and the acceptance.
+Previous research examined the validity of the mental model concept with various kinds of robots \citep{schmitz_concepts_2011,kiesler_mental_2002}.
+Findings suggest that people tend to hold richer mental models of anthropomorphic robots in contrast to mechanic ones \citep{kiesler_mental_2002}.\footnote{\hl{Later in this article, we may however come to question how far this result is based on expectations from the human user side, which are likely to be refined after continued interaction, and after the user gets acquainted with the robot's behavior.}}
+A similar finding is described in \cite{hegel_understanding_2008} and
+\citet{krach_can_2008}. In a user study using functional magnetic resonnance
+imagery (fMRI), the authors found that participants
+implicitly attributed human-like qualities, such as mental states, to their
+non-human interaction partner. Indeed, from an early age humans develop a
+tendency to explain one's own and others'actions in terms of beliefs, desires
+and goals,  called \textit{theory of mind}. The theory of mind allows the implicit attribution of
+intentions and other mental states to others \citep{premack1978does, leslie_pretense_1987, Frith2003}.
+\citet{hegel_understanding_2008} and \citet{krach_can_2008} finding was evident at the behavioral level
+as well as on the neuro-physiological level: the more the human-likeness of the
+artefactual partner increases, the more brain areas associated with theory of
+mind  get activated
+\citep{krach_can_2008}. \footnote{\hl{Ha! This says that anthropomorphism can also occur on a behavioral level, yes! :) so we should also measure anthropomorphism in the behavior.}} 
+Implication of human brain area involved in the inference of others` mental
+states has also been shown in response to viewing
+non-anthropomorphic/non-humanoid robotic gadgets whose behavior
+has been described as unpredictable -- but not in response to those whose
+behavior was described as predictable -- a finding also found at the behavioral
+level \citep{Waytz2010}.
+Interestingly, the grey matter volume of a brain area related to theory of mind
+has been correlated to individual's score of anthropomorphism
+\citep{cullen2013individual}.
+
+At lower, more automatic, level, robots have been shown to elicit resonance behaviors in the
+human brain.
+Resonance behaviors \citep{Rizzolatti1999} are mechanisms by which the brain areas involved in the internal representations of an action, an emotion or a sensation are equally recruited during the perception of another individual performing the same action or experiencing the same emotion or sensation.
+The neurons showing resonant properties have been called mirror neurons and
+have been found in a wide range of modalities (motor, emotional etc..)
+\fixme{addref}. Seeing a robotic arm reaching for an object activates the motor mirror neurons the same way as for seeing a human arm reaching for the same object
+\citep{Gazzola2007, oberman_eeg_2007}. However, a study of emotion perception
+on a robotic face found reduced activity in emotional brain
+area known to have mirror properties in response to the robotic face compared to
+a human face \citep{Chaminade2010}. Nevertheless, these authors showed that when
+the participants were explicitly instructed to pay attention to the robot's
+emotional expression, motor mirror neurons get activated.
+Interestingly, using electroencephalography,  it has also been shown that
+emotional behavior elicited by a robot face influences the speed of human
+responses as well as early brain processes the same way as emotional expression
+of a human face did \citep{Dubal2010}.
+
+%
+
+In sum, this branch of research suggests that anthropomorphism implies that
+people thoughtfully develop a mental model of agents in their environment and
+that they make inferences about these agents based on what is familiar to them
+-- themselves, humans and human behavior. This understanding builds on the
+theory of mind,  a
+person's ability to attribute mental states to oneself and others. 
+%A theory of mind for other agents enables us to attribute intentionality to those agents \citep{leslie_pretense_1987,admoni_multi-category_2012}. 
+We briefly reviewed  neuro-physiological evidence of a link between the tendency
+to thoughtfully anthropomorphize and the engagement of brain processes involved
+in the attribution of mental states to other humans. The human-likeness quality
+of the artefactual agent seems to play a role in the involvement of theory of
+mind but also the unpredictable feature of the agent behavior alone seems to be
+sufficient. Low-level mechanisms of the brain that allow humans to map others`
+motor behaviors into their own repertoire are equally elicited when perceiving a
+robot's action. It is not yet clear whether humans are processing emotional
+signals from a robot the same way as they do for human beings. 
+%were recently demonstrated at the brain level~\citep{cullen2013individual}.
+
+\paragraph{Social psychology research: a 3-factor theory of anthropomorphism\\}
+\label{sec:psychological-factors}
+
+Social psychology offers interesting theories that can be applied to understand people's motivation to anthropomorphize.
+Irrespective of the artifact's characteristics, several psychological determinants have been found to explain a person's tendency to anthropomorphize.
+\cite{epley_seeing_2007} present a ``3-factor theory'' of when people are likely to anthropomorphize based on psychological determinants.
+Namely, the theory suggests that some people are more likely to anthropomorphize when:
+
+\begin{enumerate}
+	\item ~anthropocentric knowledge is accessible and applicable to the artifact (\textit{elicited agent knowledge}),
+	\item ~they are motivated to explain and understand the behavior of other agents (\textit{effectance motivation}), and
+	\item ~they have the desire for social contact and affiliation (\textit{social motivation}).
+\end{enumerate}
+
+The first factor (\textit{elicited agent knowledge}) is a \textbf{cognitive determinant of anthropomorphism} and based on the idea that a person builds a mental model (theory of mind) of the other agent.
+\cite{epley_seeing_2007} suggest that the process of making inferences about non-human agents is based on the activation of knowledge about humans (or the self).
+As mentioned before, when a person builds a mental model of the other (unfamiliar) agent, the question here is why does she draw on knowledge about other humans / herself and not on something else?
+One basic reasons for this is a person's physical constraints of being a human and nothing else.
+Consequently, one has no other experience than the self and in turn people tend to make inferences about others' mental states by relying inordinately on their own mental state.
+\footnote{Using one's own mental states and characteristics as a guide when reasoning about other humans is called ego-centrism.
+In contrast, when using self-knowledge (or knowledge about humans in general) when reasoning about non-human agents, this is called anthropomorphism.
+See \cite{epley_seeing_2007}} Also empirical findings suggest that knowledge about humans in general, or self-knowledge in particular, is likely to serve as a readily accessible base for induction when reasoning about non-human agents.
+This tendency is usually stronger in young children and decreases with cognitive development and the learning to distinguish the self from other humans, and non-human agents.
+
+Both the second factor \textit{effectance} and the third factor \textit{sociality} are \textbf{motivational determinants of anthropomorphism}.
+\textit{Effectance} is understood a person's motivation to interact effectively in one's environment.
+That means, a person is motivated to be able to understand, predict, and reduce uncertainty \footnote{\hl{(this feeds again our hypothesis that as soon as a robot is not uncertain anymore, there is no need to keep on anthropomorphizing it)}}\fxfatal{important!
+move/copy that to the 'model' section or discussion} about her environment and the agents that inhabit it.
+According to \cite{epley_seeing_2007}, \textit{effectance motivation} can lead to anthropomorphism, since anthropomorphism serves as one way to reduce uncertainty and to increase comprehension of events in one's environment.
+Again, also according this factor it can be argued that children are more likely to anthropomorphize than adults.
+As children are in their early stages of life, they are likely to feel more uncertain within their environment, and consequently tend to anthropomorphize more.
+
+The third factor \textit{sociality} describes a person's motivation for social contact, social connection, and social approval from other agents.
+In lack of social connections to other humans (\etc friends, family, colleagues), a person is more likely to compensate these social connections by anthropomorphizing non-human agents.
+In other words \textit{"[...] those who are chronically lonely should be more likely to anthropomorphize nonhuman agents than those who are more chronically connected"} \citep{epley_seeing_2007}.
+Importantly for anthropomorphism, this social connection often appears to be satisfied by connections with \textit{"two of the most commonly anthropomorphized non-human agents, namely pets and religious agents"} \citep{epley_seeing_2007}.
+Thus, the motivation of being socially connected increases the tendency to anthropomorphize non-human agents because first sociality motivation increases the tendency to perceive human-like characteristics and traits even in non-human agents, and second it increases the tendency to search for sources of social connection in one's environment.
+
 \subsubsection{Diverse understandings of anthropomorphism\\}
 
-Literature on anthropomorphism is quite diverse. There exist different understandings of what anthropomorphism is. 
+We have seen that literature on anthropomorphism is quite diverse. We would like to point out that there exist different understandings of what anthropomorphism is. 
 One reason for this might be that anthropomorphism
@@
 
-\subsubsection{Why do people anthropomorphize?\\}
-\label{sec:explanations}
-
-But why do people anthropomorphize?
-First and foremost, it needs to be mentioned that anthropomorphism is a fairly complex phenomenon.
-Paradoxically, there is a huge and diverse body of literature on it but nevertheless, it seems that anthropomorphism is still not very well understood (especially in more recent fields like HRI).
-
-One common reason for anthropomorphism is that by perceiving some human-like characteristics in the non-human agent, this agent is made more \emph{graspable}, \emph{understandable}, \emph{predictable}, and one can feel \emph{more empathetic} toward it, and possibly one can then anticipate the agent's behavior.
-These are central motivations when trying to explain anthropomorphism, and we will come back to them in more detail later on.
-It is described that for the just mentioned reasons, people commonly anthropomorphize their pets, by ascribing mental states, intentions or feelings to them\footnote{Interestingly, pet-ownership seems to have a significant impact on human-robot interaction: several studies suggest that pet-owners are more likely to anthropomorphize technologies and robots than non pet-owners} \cite{eddy_attribution_1993}.
-But how can these motivations behind anthropomorphism be explained?
-
-Anthropomorphism as a social phenomenon arises in an interaction \citep{persson_anthropomorphism_2000}, and thus includes at least two interaction partners (the human and the real or imagined non-human agent).
-Therefore, one can take two main perspectives on explaining it \citep{lee_human_2005}: a human-centered, and an artifact-centered.
-We briefly outline both views in the following.
-It has to be kept in mind that both perspectives are inseparable; they apply at the same time, and we would like to present them here just as two different viewpoints on the same kind of phenomenon.
-
-The human-centered perspective builds on research from developmental and social psychology as well as cognitive sciences.
-In the following, we present what we found in reviewing this literature: (1) a line of research in developmental psychology that studies the attribution of animacy; (2) a line of research in more cognitive sciences that studies the cognitive processes that underlie anthropomorphism, and (3) a theory that explains anthropomorphism based on psychological factors~\citep{epley_seeing_2007}.
-All three branches apply a human-centered perspective on anthropomorphism.
-
-\paragraph*{Developmental psychology research on the attribution of animacy and intention\\}
-
-The phenomenon of attributing animacy and intentions to nonliving objects such as simple shapes has been intensively studied in developmental psychology.
-As mentioned earlier, Piaget found that children tend to ascribe life to the nonliving.
-They also tend to interpret physical phenomena in terms of intention on the part of the non-human subject.
-For instance children are likely to argue that \textit{``the sun is hot because it wants to make people warm''} \citep{leeds_childrens_1992}.
-In this example it is in fact questionable whether children really anthropomorphize the sun (believing that it has an intention) or whether they are using anthropomorphism in a metaphoric sense (because their conceptions of the world and of the living are not yet fully formed).
-Later however, two famous experiments by \cite{heider_experimental_1944} and \cite{michotte_perception_1963} showed that also adult participants attribute animacy and intention to simple things and shapes based on motion.\footnote{For more details, the reader may refer to the ``attribution theory''.} In both experiments, participants viewed animations of simple shapes, such as circles or triangles
-%(see Figure \ref{fig:animacy_attribution})
-. Asked to describe what they observed, most people developed elaborate stories, attributing motivations, emotions and relationships between the objects.
-
-%\begin{figure}[h]\centering
-%% Use the relevant command to insert your figure file.
-%% For example, with the graphicx package use
-%  \includegraphics[scale=0.6]{heider-simmel_animation.jpeg}
-%% figure caption is below the figure
-% \caption{Fritz Heider and Mary-Ann Simmel's animated film to study people's tendency to attribute animacy and intention to simple shapes; \textit{An experimental study of apparent behavior}, 1944}
-% \fxnote{wrap text around this figure?}
-% \label{fig:animacy_attribution}       % Give a unique label
-% \end{figure}
-
-Summing it up, it seems that there is a natural, relatively spontaneous reaction that makes a person attribute animacy and intention to moving shapes, even when there is no similarity of the shape to a human.
-This tendency to animize / anthropomorphize is already developed (and even more distinct) in infants and children.\footnote{\hl{Julia: I think we should mention this also in the anthropomorphic design section; as movements / motions as one of the most basic "lifelike" cues.}}
-
-\paragraph*{Cognitive science research, the mental model theory (Theory of Mind)
-and neural correlates of anthropomorphism\\}
-
-Anthropomorphism and similar phenomenons can also be understood as a thoughtful process of induction whereby \textit{``people reason about an unknown stimulus based on a better-known representation of a related stimulus"}~\citep{epley_when_2008}.
-In the case of anthropomorphism this means a person's reasoning about a non-human agent based on the representation of the self or other humans.
-A central construct of this perspective is the so-called \textit{mental model} that a person has (and builds) of the agents she is reasoning about and interacting with.
-The specific mental model we have about an artifact / agent basically explains (in our individual way to ourselves) how this artifact / agent works the way it does.
-There are two central aspects here, when looking at the quote from \citep{epley_when_2008} above.
-\textit{(1)} First, one assumption is that the user is not familiar with the other agent.
-This is basically true for all other agents (and entities) but oneself because we can only be our self.
-This view is also consistent with the \emph{familiarity thesis}~\citep{hegel_understanding_2008} which claims that we understand the world based upon a mental model of the world that we are most familiar with (our self).
-Thus, we can best use our self as source of induction when reasoning about other agents.
-However, in case we would like to understand the behavior of a spider, we would probably not use our mental model of a human (or our self) simply because we do not have many things in common with a spider.
-And this is the second central aspect here.
-\textit{(2)} Second, one assumption is based oj the anthropomorphic design of the other agent (see Section \ref{sec:anthropomorphic-design}): if the agent behaves (appears) much like a human being (\eg a robot that emits a human voice), people's mental model of the agent's behavior is likely to approach their mental model of humans (though the model may differ in some important aspects).
-
-This cognitive viewpoint on anthropomorphism is important because people's estimation of an agent's knowledge model and its capabilities affects the way they relate to it.
-This holds important implications for the resulting interaction with the system, the user experience, and the acceptance.
-Previous research examined the validity of the mental model concept with various kinds of robots \cite{schmitz_concepts_2011,kiesler_mental_2002}.
-Findings suggest that people tend to hold richer mental models of anthropomorphic robots in contrast to mechanic ones \cite{kiesler_mental_2002}.\footnote{\hl{Later in this article, we may however come to question how far this result is based on expectations from the human user side, which are likely to be refined after continued interaction, and after the user gets acquainted with the robot's behavior.}}
-A similar finding is described in \cite{hegel_understanding_2008} and
-\citet{krach_can_2008}. In a user study using functional magnetic resonnance
-imagery (fMRI), the authors found that participants
-implicitly attributed human-like qualities, such as mental states, to their
-non-human interaction partner. Indeed, from an early age humans develop a
-tendency to explain one's own and others'actions in terms of beliefs, desires
-and goals,  called \textit{theory of mind}. The theory of mind allows the implicit attribution of
-intentions and other mental states to others \citep{premack1978_does, leslie_pretense_1987, Frith2003}.
-\citet{hegel_understanding_2008} and \citet{krach_can_2008} finding was evident at the behavioral level
-as well as on the neuro-physiological level: the more the human-likeness of the
-artefactual partner increases, the more brain areas associated with theory of
-mind  get activated
-\citep{krach_can_2008}. \footnote{\hl{Ha! This says that anthropomorphism can also occur on a behavioral level, yes! :)}} 
-Implication of human brain area involved in the inference of other's mental
-states has also been shown in response to viewing
-non-anthropomorphic/non-humanoid robotic gadgets whose behaviour
-has been described as unpredictable - but not in response to those whose
-behavior was described as predictable- a finding also found at the behavioral
-level \citep{Waytz2010}.
-Interestingly, the grey matter volume of a brain area related to theory of mind
-has been correlated to individual's score of anthropomorphism
-\citep{cullen2013individual}.
-
-At lower, more automatic, level, robots have been shown to elicit resonnance behaviors in the
-human brain.
-Resonnance behaviors \citep{Rizzolatti1999} are mechanisms by which the brain areas involved in the internal representations of an action, an emotion or a sensation are equally recruited during the perception of another individual performing the same action or experiencing the same emotion or sensation.
-The neurons showing resonnant properties have been called mirror neurons and
-have been found in a wide range of modalities (motor, emotional etc..)
-\fixme{addref}.Seeing a robotic arm reaching for an object activates the motor mirror neurons the same way as for seeing a human arm reaching for the same object
-\citep{Gazzola2007, oberman_eeg_2007}. However, a study of emotion perception
-on a robotic face found reduced activity in emotional brain
-area known to have mirror properties in response to the robotic face compared to
-a human face \citep{Chaminade2010}. Nevertheless, these authors showed that when
-the participants were explicitely instructed to pay attention to the robot's
-emotional expression, motor mirror neurons gets activated.
-Interestingly, using electroencephalography,  it has also been shown that
-emotional behavior elicited by a robot face influences the speed of human
-responses as well as early brain processes the same way as emotional expression
-of a human face did \citep{Dubal2010}.
-
-%
-
-In sum, this branch of research suggests that anthropomorphism implies that
-people thoughtfully develop a mental model of agents in their environment and
-that they make inferences about these agents based on what is familiar to them
--- themselves, humans and human behavior. This understanding builds on the
-theory of mind,  a
-person's ability to attribute mental states to oneself and others. 
-%A theory of mind for other agents enables us to attribute intentionality to those agents \citep{leslie_pretense_1987,admoni_multi-category_2012}. 
-We briefly reviewed  neuro-physiological evidence of a link between the tendency
-to thoughtfully anthropomorphize and the engagement of brain processes involved
-in the attribution of mental states to other humans. The human-likeness quality
-of the artefactual agent seems to play a role in the involvement of theory of
-mind but also the unpredictable feature of the agent behavior alone seems to be
-sufficient. Low-level mechanisms of the brain that allow humans to map other's
-motor behaviors into their own repertoire are equally elicited when perceiving a
-robot's action. It is not yet clear whether human are processing emotional
-signal from a robot the same way as they do for human beings. 
-%were recently demonstrated at the brain level~\citep{cullen2013individual}.
-
-\paragraph*{Social psychology research: a 3-factor theory of anthropomorphism\\}
-\label{sec:psychological-factors}
-
-Social psychology offers interesting theories that can be applied to understand people's motivation to anthropomorphize.
-Irrespective of the artifact's characteristics, several psychological determinants have been found to explain a person's tendency to anthropomorphize.
-\cite{epley_seeing_2007} present a ``3-factor theory'' of when people are likely to anthropomorphize based on psychological determinants.
-Namely, the theory suggests that some people are more likely to anthropomorphize when:
-
-\begin{enumerate}
-	\item anthropocentric knowledge is accessible and applicable to the artifact (\textit{elicited agent knowledge}),
-	\item they are motivated to explain and understand the behavior of other agents (\textit{effectance motivation}), and
-	\item they have the desire for social contact and affiliation (\textit{social motivation}).
-\end{enumerate}
-
-The first factor (\textit{elicited agent knowledge}) is a \textbf{cognitive determinant of anthropomorphism} and based on the idea that a person builds a mental model (theory of mind) of the other agent.
-\cite{epley_seeing_2007} suggest that the process of making inferences about non-human agents is based on the activation of knowledge about humans (or the self).
-As mentioned before, when a person builds a mental model of the other (unfamiliar) agent, the question here is why does she draw on knowledge about other humans / herself and not on something else?
-One basic reasons for this is a person's physical constraints of being a human and nothing else.
-Consequently, one has no other experience than the self and in turn people tend to make inferences about others' mental states by relying inordinately on their own mental state.
-\footnote{Using one's own mental states and characteristics as a guide when reasoning about other humans is called ego-centrism.
-In contrast, when using self-knowledge (or knowledge about humans in general) when reasoning about non-human agents, this is called anthropomorphism.
-See \cite{epley_seeing_2007}} Also empirical findings suggest that knowledge about humans in general, or self-knowledge in particular, is likely to serve as a readily accessible base for induction when reasoning about non-human agents.
-This tendency is usually stronger in young children and decreases with cognitive development and the learning to distinguish the self from other humans, and non-human agents.
-
-Both the second factor \textit{effectance} and the third factor \textit{sociality} are \textbf{motivational determinants of anthropomorphism}.
-\textit{Effectance} is understood a person's motivation to interact effectively in one's environment.
-That means, a person is motivated to be able to understand, predict, and reduce uncertainty \footnote{\hl{(this feeds again our hypothesis that as soon as a robot is not uncertain anymore, there is no need to keep on anthropomorphizing it)}}\fxfatal{important!
-move/copy that to the 'model' section or discussion} about her environment and the agents that inhabit it.
-According to \cite{epley_seeing_2007}, \textit{effectance motivation} can lead to anthropomorphism, since anthropomorphism serves as one way to reduce uncertainty and to increase comprehension of events in one's environment.
-Again, also according this factor it can be argued that children are more likely to anthropomorphize than adults.
-As children are in their early stages of life, they are likely to feel more uncertain within their environment, and consequently tend to anthropomorphize more.
-
-The third factor \textit{sociality} describes a person's motivation for social contact, social connection, and social approval from other agents.
-In lack of social connections to other humans (\etc friends, family, colleagues), a person is more likely to compensate these social connections by anthropomorphizing non-human agents.
-In other words \textit{"[...] those who are chronically lonely should be more likely to anthropomorphize nonhuman agents than those who are more chronically connected"} \citep{epley_seeing_2007}.
-Importantly for anthropomorphism, this social connection often appears to be satisfied by connections with \textit{"two of the most commonly anthropomorphized non-human agents, namely pets and religious agents"} \citep{epley_seeing_2007}.
-Thus, the motivation of being socially connected increases the tendency to anthropomorphize non-human agents because first sociality motivation increases the tendency to perceive human-like characteristics and traits even in non-human agents, and second it increases the tendency to search for sources of social connection in one's environment.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \cite{epley_seeing_2007}). A lot of research has shown that both these factors can
-facilitate or hinder anthropomorphism.
+promote or hinder anthropomorphism.
 

### 2014-04-01 paper.tex
small changes in section 2

@@
 
-\section{Anthropomorphism}
+\section{What does Anthropomorphism mean?}
 \label{sec:anthropomorphism}
@@
 In short, we propose to differentiate between \textbf{anthropomorphic form} to refer to an imitation of human-like form in the \textit{design} of artificial agents, and  \textbf{anthropomorphism} to refer to the social phenomenon of
-people's tendency to \textit{perceive} human-likeness in non human-like agents.
-\citep{fink_anthropomorphism_2012} In the following, we might use the terms \texit{form} and \textit{design} interchangeably.
+people's tendency to \textit{perceive} human-likeness in non human-like agents
+\citep{fink_anthropomorphism_2012}. In the following, we might use the terms \texit{form} and \textit{design} interchangeably.
+
+\hl{Julia: I will make a draft of a figure here}
 
@@
 \citep{persson_anthropomorphism_2000}, one can also
-take two main perspectives on explaining anthropomorphism \citep{lee_human_2005}: an artifact-centered perspective and a human-centered perspective. 
+take two main perspectives on explaining anthropomorphism \citep{lee_human_2005}: an artifact-centered perspective and a human-centered perspective.\\ 
 We now first present an artifact-centered perspective, and outline how 
@@
 perspective and shed light on \textit{anthropomorphism as a social phenomenon}. We present 
-theories from psychology and cognitive science to explain people's tendency to 
+theories from developmental psychology, cognitive science, and social psychology to explain people's tendency to 
 perceive human-like characteristics in non-human agents.
@@
 that humans tend to project everyday 
-\hl{expectations} of human and animalistic life onto artificial agents that use 
+expectations of human and animalistic life onto artificial agents that use 
 anthropomorphic (or zoomorphic) forms \citep{schmitz_concepts_2011}. 
@@
 \textit{Effectance} is understood a person's motivation to interact effectively in one's environment.
-That means, a person is motivated to be able to understand, predict, and reduce uncertainty \footnote{\hl{(this feeds again our hypothesis that as soon as a robot is not uncertain anymore, there is no need to keep on anthropomorphizing it)}}\fxfatal{important!
-move/copy that to the 'model' section or discussion} about her environment and the agents that inhabit it.
+That means, a person is motivated to be able to understand, predict, and reduce uncertainty about her environment and the agents that inhabit it.
 According to \cite{epley_seeing_2007}, \textit{effectance motivation} can lead to anthropomorphism, since anthropomorphism serves as one way to reduce uncertainty and to increase comprehension of events in one's environment.
@@
 
-To sum it up, while anthropomorphism is a commonly discussed and
-studied trait of human-robot interaction, its the understanding 
-does not seem to take into account the wide range of phenomena that it
-encompasses. To date, the understanding of anthropomorphism in robotics considers  two main factors: the
+Summing it up, anthropomorphism is a commonly discussed and
+studied trait of human-robot interaction; however its current understanding seems to be stuck in a twofold consideration. Mostly, only two key factors are recognized: the
 characteristics of \textbf{1) the robot's design} (degree of human-likeness) and
@@
 promote or hinder anthropomorphism.
-
-However, based on what we have just presented, we would like to make a note, that there are more than these two factors that impact on anthropomorphism.
-
-Based on the understanding that anthropomorphism represents a specific type of \textit{experience} that arises in the
-\textit{interaction} between a set of user expectations and external reality
-\cite{persson_anthropomorphism_2000}, 
+However, anthropomorphism is a complex process and we think that the current understanding of it does neither seem to fully take into account the wide range of phenomena that it encompasses, nor the multiplicity of factors which determine it.
+This shortcoming and conflict in the understanding of anthropomorphism in HRI has already been denoted by others but we would like to take a first step towards moving forward in this dilemma, and encourage an open dialogue to solve this.
+
+Through applying an understanding that anthropomorphism represents a specific type of \textit{experience} that arises in the
+\textit{interaction} between a set of user expectations and external reality, 
 %(see Figure~\ref{fig:anthropomorphism_and_interaction})
 we propose that
-anthropomorphism is a multi-layered phenomenon which arises in different levels, and is likely to evolve with continued interaction.
+anthropomorphism is a multi-layered phenomenon which arises in different levels \citep{persson_anthropomorphism_2000}, and which is likely to evolve with continued interaction.
 %we suggest to understand anthropomorphism as a \emph{dynamic},
@@
 
-To this end, we make the following two suggestions:
+To this end, and in respect of our research hypotheses, we make the following two suggestions:
 
@@
 
-Second, we would like to take up the proposition already made by other researchers (\eg \cite{persson_anthropomorphism_2000,ruijten_introducing_2014}) to not viewing anthropomorphism as being either there or not there, but to discriminate different levels of
+Second, we would like to take up the proposition already made by other researchers (\eg \cite{persson_anthropomorphism_2000,takayama_perspectives_2012,ruijten_introducing_2014}) to not viewing anthropomorphism as being either there or not there, but to discriminate different levels of
 anthropomorphism (low, and high anthropomorphism, for instance).
@@
 
+With having both before-mentioned aspects in mind (multi-factors that determine anthropomorphism and multi-levels of the observable phenomenon), it becomes clear that anthropomorphism cannot be something fixed, that once observed in a human-robot interaction always remains the same.
+We think, that anthropomorphism evolves and shows dynamics.
+This idea is what we would like to formalize in the next section.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-Why do we think that anthropomorphic projections are likely to change over time
-and with growing experience a person has with a robot? The underlying process in
-anthropomorphism is understood as reasoning about and perceiving something
-non-human, and unknown or unfamiliar based on one's representation of the
-familiar and well-known concept of being human (or one-self). The basic
-operations underlying inductive inference are the acquisition of knowledge, the
-activation or elicitation of knowledge, and the application of activated
-knowledge at the time of the judgment \citep{epley_when_2008}. According to Epley
-\textit{et al.}, the application includes attempts to correct, adjust, or
-integrate less accessible information into a more automatically activated
-default representation. This process can be seen as a process of correction, and
-thus, it is often insufficient leaving final judgments biased in the direction
-of the initially activated representation. As a person's knowledge base changes
-/ evolves constantly with newly acquired things, or growing experiences with a
-robot, etc., it is likely that the "need to anthropomorphize" a robot decreases
-over time. First, because of the evolved knowledge about it, and second because
-one has familiarized oneself with it. Consequently, the robot should become more
-predictable and more familiar to the human user and inferences about it can be
-made based on the acquired knowledge.  /fxfatal{confusing paragraph...needs
-reformulation. Could also be turned into a section introduction instead of a
-subsection}
-
 So far, the HRI community has not much investigated how anthropomorphism in
 human-robot interactions evolves over time (during the process of
-\emph{adopting} a robot, for instance): we propose to go beyond the traditional
-perception of anthropomorphism in robotics as a static feature that once
-observed during a short-term interaction reflects a sustaining social effect.
-Based on an extensive literature review previously
-published~\citep{fink_anthropomorphism_2012} and field
-experiments~\fixme{cites!}, we believe that anthropomorphic effects in HRI are
-not always the same but evolve over time, along with growing interaction and
-experience with the robot, similar to how relationships among people evolve
-over time \fixme{(cite Hinde, 1988)}. In fact, \citet{kanda_interactive_2004}
-also hypothesized that people's attitude toward technological artifacts and
-their relationship with them would evolve over time, and they were among the
-first who described \emph{novelty effects} during a long-term study with an
-interactive robot in a school.
-
-\hl{Julia: I need to work on this next paragraph but I would like to keep it here as a note}
-
-\textbf{In-the-moment vs. reflective perspectives on agency}\\
-Perception of agency can be treated as anthropomorphism.
-\citep{takayama_perspectives_2012} proposes to differentiate between a \textit{in-the-moment} and \textit{reflective} perspective to better understand how human users perceive agency in robots.\footnote{``The other important distinction between the two perspectives is the \hl{cognitive processes} that they engage.''} According to Takayama, an \textit{in-the-moment} perspective refers to one's most immediate (sometimes visceral) sense in a situation.
+\emph{adopting} a robot, for instance). Though conflicts were found, the HRI community more or less accepted viewing anthropomorphism as a static feature that once
+observed during a short-term interaction reflects a sustaining social effect. So far, it was also measured as such. But there are some hints that this is deficient.
+
+For instance, \cite{kanda_interactive_2004} point out that relationships among people evolve over time and similarly, also people’s attitude toward technological artifacts
+and their relationship with them might evolve over time.
+In their study, \cite{kanda_interactive_2004} were also among the first to describe empirically \emph{novelty effects} during a long-term study with an interactive robot in a school.
+
+There are also hints from a more theoretical side, that make us think that anthropomorphism is likely to change over 
+time and with growing experience that a person has with a robot.
+
+%effectance motivation reduces uncertainty and consequently the tendency to anthropomorphize
+For instance, let's have a look at the processes that underlie anthropomorphism.
+In its essence anthropomorphism means reasoning about and perceiving something
+non-human (and unknown or unfamiliar) based on one's representation of the
+familiar and well-known concept of being human (or one-self). According to \citep{epley_when_2008} the basic
+operations that underlie these inductive inferences are the acquisition of knowledge, the
+activation or elicitation of knowledge, and the application of activated
+knowledge at the time of the judgment. By applying knowledge to a given situation / interaction, it is implied that one attempts to correct, adjust, or maybe
+integrate less accessible information into a more automatically activated
+default representation. \cite{epley_when_2008} argues that this process can be seen as a process of correction, and
+thus, it is often insufficient leaving final judgments biased in the direction
+of the initially activated representation. Refinements to the initial representation mean something evolves. This can be due to the fact that a person's knowledge base changes
+constantly with newly acquired things, or growing experiences with a
+robot, \etc. . Consequently, it is likely that the ``need to anthropomorphize'' a robot decreases
+over time (from the human-centered point of view), since the user's knowledge about the robot evolves, and also the user familiarizes herself with the robot. Consequently, the robot should become more
+predictable and more familiar to the human user and inferences about it can be
+made based on the acquired knowledge.
+
+In other words, the argumentation is that humans have a motivation to interact effectively in their environment \textit{(effectance)} \citep{epley_when_2008}.
+This means that humans are motivated to be able to understand and predict the environment and agents around them.
+Through this process, uncertainty is reduced, and consequently, a first unfamiliar robot, can be explained with means that are different from anthropomorphism.
+
+%expectations
+Further,
+
+%\textbf{In-the-moment vs. reflective perspectives on agency}\\
+%Perception of agency can be treated as anthropomorphism.
+%\citep{takayama_perspectives_2012} proposes to differentiate between a \textit{in-the-moment} and \textit{reflective} perspective to better understand how human users perceive agency in robots.\footnote{``The other important distinction between the two perspectives is the \hl{cognitive processes} that they engage.''} According to Takayama, an \textit{in-the-moment} perspective refers to one's most immediate (sometimes visceral) sense in a situation.
 In contrast, a \textit{reflective} perspective refers to one's sense of a situation upon more distanced cogitation and consideration.
@@
 There seems to be a disconnection between what people consciously perceive and how they respond to stimuli that they may not consciously perceive.
-That means, in the initial phase of interacting with a novel device \textbf{(initialization)} people might not consciously respond but rather mindlessly \citep{nass_machines_2000}.
+%That means, in the initial phase of interacting with a novel device \textbf{(initialization)} people might not consciously respond but rather mindlessly \citep{nass_machines_2000}.
 Only after some time of \textbf{familiarization}, they might respond in a more reflective manner.
 This can be illustrated by the fact that people tend to deny interacting with computational systems as if they were people and yet they respond to computers in many ways that are remarkably similar to how they respond to people \citep{reeves_media_1996}.
-\cite{takayama_perspectives_2012} also applies a cognitive viewpoint on the two different perspectives of in-the-moment \vs reflective to illustrate differences.
+%\cite{takayama_perspectives_2012} also applies a cognitive viewpoint on the two different perspectives of in-the-moment \vs reflective to illustrate differences.
 She states that in-the-moment perceptions of agency are largely shaped by bottom-up perceptual processes, evoking very immediate responses (\eg to the cues emitted by the artifact's design, see Section \ref{sec:anthropomorphic-design}).
-In contrast, according to Takayama, reflective perceptions are more often shaped by top-down processes because of the nature of reflective thought.
+%In contrast, according to Takayama, reflective perceptions are more often shaped by top-down processes because of the nature of reflective thought.
 

### 2014-04-01 paper.tex
Typos, formatting in introduction

@@
 \def\Authors{Julia Fink\,$^{1*}$, S\'{e}verin Lemaignan$^{1}$, Claire Braboszcz$^{2}$ and Pierre Dillenbourg$^{1}$}
-\def\Address{$^{1}$Computer-Human Interaction in Learning and Instruction (CHILI) \\ Ecole Polytechnique F\'{e}d\'{e}rale de Lausanne (EPFL) \\ CH-1015 Lausanne, Switzerland \\
+\def\Address{$^{1}$Computer-Human Interaction in Learning and Instruction
+    (CHILI) \\ \'{E}cole Polytechnique F\'{e}d\'{e}rale de Lausanne (EPFL) \\ CH-1015 Lausanne, Switzerland \\
 \vspace{0.25cm}
@@
 
-A phenomenon that is often studied related to the human-like design of 
-robots is anthropomorphism. While people's tendency to perceive human-like 
+Anthropomorphism is a phenomenon that is often studied related to the human-like
+design of robots. While people's tendency to perceive human-like 
 characteristics in robots is a commonly discussed trait of 
@@
 The Uncanny Valley hypothesis \citep{mori_uncanny_1970} proposes that human-like
-designs of objects and non-human agents can evoke both positive and negative feelings 
-of affinity in the human observer / user. A positive valence reflects the experience of 
-emotional engagement with and feelings of empathy for the non-human agent
-\citep{cheetham_human_2011}. This in turn may lead to an effective (human-like and 
-human-social) interaction with the non-human agent, and increase people's acceptance of
-it. 
-However, at a certain point as the non-human agent
-approaches but fails to closely resemble a human, the evoked valence in the
-human user suddenly turns into a negative uncanny feeling of what
+designs of objects and non-human agents can evoke both positive and negative
+feelings of affinity in the human observer / user. A positive valence reflects
+the experience of emotional engagement with and feelings of empathy for the
+non-human agent \citep{cheetham_human_2011}. This in turn may lead to an
+effective (human-like and human-social) interaction with the non-human agent,
+and increase people's acceptance of it.  However, at a certain point, as the
+non-human agent approaches but fails to closely resemble a human, the evoked
+valence in the human user suddenly turns into a negative uncanny feeling of what
 \cite{mori_uncanny_1970} describes as disgust and revulsion. This, in turn,
-might lead to rejection of the non-human agent. The Uncanny
-Valley hypothesis predicts that with further increasing the human-likeness of
-the non-human agent such that it appears so realistic that it is not
-distinguishable from a human but perceived to be human, the effect is again a
-positive one, reflecting feelings and engagement that are similar as those
-evoked by a human-human interaction. 
-Of course, developers and designers of artificial agents
-(\eg virtual characters, robots) try to exploit the positive effects of 
-\textbf{anthropomorphic form} and avoid ``falling'' into this Uncanny Valley.
-Consequently, there is a considerable research effort to
-better understand the boundaries of anthropomorphic design and their effects
-on the interaction and experience. To date, findings have been however
-inconsistent \citep{cheetham_human_2011}.
-
-A phenomenon that is often studied related to the human-like design of objects and 
-artificial agents is \textbf{anthropomorphism}.
-Along this line, this article aims at fostering a better understanding of
-anthropomorphism (noted \Ant in this paper) in human-robot interaction 
-by considering the phenomenon
-as a whole. Robotics researchers often tend to believe that
-anthropomorphism only describes a static set of human-like features of a robot
-(like shape, speech capabilities, facial expressions, etc.). We refer to these
-characteristics as the \emph{anthropomorphic design} of the
-robot~\citep{fink_anthropomorphism_2012}, and propose that \emph{anthropomorphism} in 
-general refers to a \emph{social phenomenon} that emerges from the (real or
-imagined) \emph{interaction} between a non-human agent (\eg a robot) and a 
-human~\citep{persson_anthropomorphism_2000}. According to~\cite{epley_when_2008},
-anthropomorphism includes that the human perceives, for instance, emotional states, motivations, or 
-intentions in the non-human agent, and tends to ascribe those qualities to it.
-As such, the dynamic and
+might lead to rejection of the non-human agent. The Uncanny Valley hypothesis
+predicts that with further increasing of the human-likeness such as it appears
+so realistic that it is not distinguishable from a human and actually perceived
+to be human, the effect is again a positive one, reflecting feelings and
+engagement that are similar as those evoked by a human-human interaction.
+Developers and designers of artificial agents (\eg virtual characters, robots)
+try to exploit the positive effects of \textbf{anthropomorphic form} and avoid
+``falling'' into this Uncanny Valley, and consequently, there is a considerable
+research effort to better understand the boundaries of anthropomorphic design
+and their effects on the interaction and experience. To date, findings have
+remained however inconsistent \citep{cheetham_human_2011}.
+
+A phenomenon that is often studied related to the human-like design of objects
+and artificial agents is \textbf{anthropomorphism}.  Along this line, this
+article aims at fostering a better understanding of anthropomorphism (noted \Ant
+in this paper) in human-robot interaction by considering the phenomenon as a
+whole. Robotics researchers often tend to believe that anthropomorphism only
+describes a static set of human-like features of a robot (like shape, speech
+capabilities or facial expressions). We refer to these characteristics as the
+\emph{anthropomorphic design} of the robot~\citep{fink_anthropomorphism_2012},
+and propose that \emph{anthropomorphism} in general refers to a \emph{social
+phenomenon} that emerges from the (real or imagined) \emph{interaction} between
+a non-human agent (\eg a robot) and a
+human~\citep{persson_anthropomorphism_2000}. According
+to~\cite{epley_when_2008}, anthropomorphism includes that the human perceives,
+for instance, emotional states, motivations, or intentions in the non-human
+agent, and tends to ascribe those qualities to it.  As such, the dynamic and
 socio-cognitive dimensions of anthropomorphism are essential to understand the
@@
 
-To support the reflection on variances and dimensions of anthropomorphism, it may be 
-useful to consider a few experimental
-results. We studied anthropomorphism in several short- and long-term
-human-robot interaction studies that we carried out with embodied robots, both
-in ecologically valid real-world environments and controlled lab settings. Those
-experiments are presented in details in previously published
-articles~\citep{fink_anthropomorphic_2012, fink_living_2013, fink2014which,
-lemaignan2014dynamics}. We only highlight here a few qualitative results that
-underline the complexity of the phenomenon.
+To support the reflection on variances and dimensions of anthropomorphism, it
+may be useful to first consider a few experimental results. We studied
+anthropomorphism in several short- and long-term human-robot interaction studies
+that we carried out with embodied robots, both in ecologically valid real-world
+environments and controlled lab settings. Those experiments are presented in
+details in previously published articles~\citep{fink_anthropomorphic_2012,
+fink_living_2013, fink2014which, lemaignan2014dynamics}. We only highlight
+here a few qualitative results that underline the complexity of the
+phenomenon.
 
@@
                 \includegraphics[width=\textwidth]{roomba-activities.png}
-                \caption{Activities related to Roomba, n = 9 households}
+                \caption{Activities related to Roomba, $n = 9$ households}
                 \label{fig:roomba-activities}
@@
                 \includegraphics[width=\textwidth]{roomba-perception.pdf}
-                \caption{People's perception of Roomba, n = 15 participants}
+                \caption{People's perception of Roomba, $n = 15$ participants}
                 \label{fig:roomba-perception}
         \end{subfigure}
-    \caption{Usage and perception of the Roomba vacuum-cleaning robot over a 6 months period.
-Qualitative data suggest that people's activities related to the robot as well as their perception of the robot change over time.}
+    \caption{Usage and perception of the Roomba vacuum-cleaning robot over a 6
+    months period. Qualitative data suggest that people's activities related to
+    the robot as well as their perception of the robot change over time.}
+
     \label{fig:roomba}
@@
 perceive the robot over time, and how they generally live with the Roomba in
-their home. At various time points, users were asked to rate their perception of
-different features of the robot on a 7-point rating scale. As
+their home. At various points in time, users were asked to rate their perception
+of different features of the robot on a 7-point rating scale. As
 Figure~\ref{fig:roomba-perception} shows, some features remained stable over
@@
 over a long period of time? And, as a pre-requisite to answer, do we actually
-understand the psychological phenomenon, and can we effectively account for the
-dynamics of these interactions?
+understand the underlying psychological phenomenons that explain the decrease of
+interest, and can we effectively account for the dynamics of these phenomenons?
 
 Those questions are certainly not new, but paradoxically, while anthropomorphism
-is a commonly discussed trait of human-robot interaction, it appears
-that we lack formal grounds and models that would account for the long-term
-dynamics of these interactions.
+is a commonly discussed trait of human-robot interaction, it appears that we
+still lack formal grounds and models that would account for the long-term
+dynamics of the interaction.
 
@@
             \caption{We found a significant negative correlation ($p=0.048$) between the
-    number of interactions and the qualitative anthropomorphic projections. n = 13 groups}
+    number of interactions and the qualitative anthropomorphic projections. $n = 13$ groups}
             \label{fig:qualitative-score}
         \end{subfigure}
-        \caption{Children`s interaction with Ranger, and their anthropomorphic projections onto the robot.
-Overall, large variations of both children`s behavior and their perception of the robot were found but seemed to be correlated to each other.}
+        \caption{Children's interaction with Ranger, and their anthropomorphic
+        projections onto the robot. Overall, large variations of both children's
+        behavior and their perception of the robot were found but were
+        correlated to each other.}
+
     \label{fig:ranger}
@@
 
-%\fixme{It was written as caption of fig:ranger: ``Level of interaction with a semi-anthropomorphic robot is \emph{not} a predictor of anthropomorphic projections.'' Comment JF: this statement does not make sense to me as we found a significant negative correlation between the two.}
-
 Figure~\ref{fig:qualitative-score} calls for other initial remarks. This diagram
-shows data from a (yet unpublished) study in which 13 pairs of children (4-5 years old)
-played for about 20 minutes a Domino game with a robot toy box (the robot was tasked to
-carry domino pieces from one child to the other, Figure~\ref{fig:ranger-expe}).
-The $x$-axis represents the number of social interactions between the children
-and the robot (like talking to the robot or showing objects), based on video annotations. On
-the $y$-axis, we have a synthetic qualitative measurement of anthropomorphic
-projections onto the robot, based on two interviews with the children. The correlation between both these
+shows data from a (yet unpublished) study in which 13 pairs of children (4-5
+years old) played for about 20 minutes a Domino game with a robot toy box (the
+robot was tasked to carry domino pieces from one child to the other,
+Figure~\ref{fig:ranger-expe}).  The $x$-axis represents the number of social
+interactions between the children and the robot (like talking to the robot or
+showing objects), based on video annotations. On the $y$-axis, we have a
+synthetic qualitative measurement of anthropomorphic projections onto the robot,
+based on two interviews with the children. The correlation between both these
 values is significantly \emph{negative}: the more the children engaged into
@@
 These first remarks lead to the main question we attempt to address in this
-article: how can we understand \emph{anthropomorphism} as a whole, \hl{and in such a
-way that is support improved human-robot interactions?}\fixme{JF: something's wrong with this sentence}
-
-We propose to discuss anthropomorphism from three
-complementary perspectives:
-
-%Based on an extensive literature review~\citep{fink_anthropomorphism_2012},
-%several field and lab studies previously mentioned, and insights from the
-%cognitive neuroscience, we propose to discuss anthropomorphism from three
-%complementary perspectives.
-
-First, by reviewing what anthropomorphism actually \emph{means}:
-besides an \emph{artifact-centered} understanding that explains anthropomorphism from the human-like design of the non-human artifact, it seems important to explicit the social component, namely a \emph{human-centered} understanding, of anthropomorphism.
-
-Second, we propose a model, called the \textit{Dynamics of Anthropomorphism} to understand how anthropomorphism evolves over time ~\citep{lemaignan2014dynamics}.
-These dynamics are non-monotonic, and effects like the
-\emph{novelty effect} play here a key role.
+article: how can we understand \emph{anthropomorphism} as a whole, and in such a
+way that it supports improved design of human-robot interactions?
+
+To this end, we propose to discuss anthropomorphism from three complementary
+perspectives:
+
+First, by reviewing what anthropomorphism actually \emph{means}: besides an
+\emph{artifact-centered} understanding that explains anthropomorphism from the
+human-like design of the non-human artifact, it seems important to explicit the
+social component, namely a \emph{human-centered} understanding, of
+anthropomorphism.
+
+Second, we propose a model, called the \textit{Dynamics of Anthropomorphism} to
+understand how anthropomorphism evolves over time
+~\citep{lemaignan2014dynamics}.  These dynamics are non-monotonic, and effects
+like the \emph{novelty effect} play here a key role.
 
@@
 
-%\paragraph{Two hypotheses}
 Our research question also translates to two
@@
     and purpose of the robot increase anthropomorphism: \textit{anthropomorphism
-    as a multi-factor phenomenon}.
+    is a multi-factor phenomenon}.
 
@@
     perceive the robot as more familiar and predictable, and in turn
-    anthropomorphizes the robot less: \textit{anthropomorphism as a dynamic
+    anthropomorphizes the robot less: \textit{anthropomorphism is a dynamic
     phenomenon}.
@@
 
-%\begin{inparaenum}[\itshape 1)\upshape]
-
-The remainder of this article is organized as follows.
-According to the three perspectives that we take, 
-we first (in Section
-%\ref{sec:overview-studies}, we give a brief overview on the various studies that
-%we conducted to investigate anthropomorphism, namely \item the Roomba study,
-%\item the Forum study, \item the Ranger domino study. Next, Section
-\ref{sec:anthropomorphism}) aim to establish a common ground in the
-understanding of anthropomorphism. We review literature from several relevant domains and integrate the different explanations into an understanding of
-anthropomorphism as a multi-factor phenomenon.
-Based on this, Section~\ref{sec:our-ideas} introduces our initial model of the
-\textit{Dynamics of Anthropomorphism}. This model describes the variances
-and dynamics of people's tendency to anthropomorphize an artificial agent,
-such as a robot. 
-Then Section \ref{sec:cognition-neuroscience} presents a
-cognitive and neuroscience perspective on anthropomorphism to consolidate
-our considerations and the proposed model.
-This is followed by a discussion
-about the limitations of our approach (Section \ref{sec:discussion}) and the
-existing and alternative ways to measure anthropomorphism in human-robot
-interactions.
-Finally, Section \ref{sec:conclusion} concludes this article
-and offers starting points for further research on anthropomorphism and the
-effect of the human-like design approach in robotics.
-
-%\end{inparaenum}
+The remainder of this article is organized as follows.  According to the three
+perspectives that we take, we first (in Section \ref{sec:anthropomorphism}) aim
+to establish a common ground in the understanding of anthropomorphism. We review
+literature from several relevant domains and integrate the different
+explanations into an understanding of anthropomorphism as a multi-factor
+phenomenon.  Based on this, Section~\ref{sec:our-ideas} introduces our initial
+model of the \textit{Dynamics of Anthropomorphism}. This model describes the
+variances and dynamics of people's tendency to anthropomorphize an artificial
+agent, such as a robot.  Then Section \ref{sec:cognition-neuroscience} presents
+a cognitive and neuroscience perspective on anthropomorphism to consolidate our
+considerations and the proposed model.  This is followed (Section
+\ref{sec:discussion}) by a discussion about the limitations of our approach and
+the existing and alternative ways to measure anthropomorphism in human-robot
+interactions.  Finally, Section \ref{sec:conclusion} concludes this article and
+offers starting points for further research on anthropomorphism and the effect
+of the human-like design approach in robotics.
 
@@
 projection of already known cognitive models onto the robot. We discuss this other
-aspect at section~\ref{sec:cognitivemodel}.
+aspect at section~\ref{sec:cognition-neuroscience}.
 
@@
 HRI2013 paper}
-This is supported by the results from \citet{Waitz2010} seen in section
+This is supported by the results from \citet{Waytz2010} seen in section
 \ref{sec:explanations} that people attribute more easily anthropomorphic

### 2014-04-01 paper.tex
new figure

@@
 
-\section{What does Anthropomorphism mean?}
+\section{Why do humans anthropomorphize?}
 \label{sec:anthropomorphism}
@@
 
-\hl{Julia: I will make a draft of a figure here}
+\begin{figure}[b]
+    \centering
+    \includegraphics[width=0.75\columnwidth]{anthropo.pdf}
+    \caption{what is anthropomorphism? \hl{we need a cool caption for this that includes terms such as factor, element, influence, etc. :-) }}
+
+    \label{fig:anthropofig}
+\end{figure}
 
@@
 However, anthropomorphic robot designs have been controversially discussed and received 
-remarkable attention since the early 1970ies, related to \cite{mori_uncanny_1970} 
-theory of the \textit{Uncanny Valley}, see Figure \ref{fig:uncanny_valley}.
-
-\begin{figure}\centering
-% Use the relevant command to insert your figure file.
-% For example, with the graphicx package use
-  \includegraphics[scale=0.75]{uncanny-valley.jpg}
-% figure caption is below the figure
- \caption{Mashiro Mori, illustration of the \textit{Uncanny Valley} hypothesis.
+remarkable attention since the early 1970ies, related to Mori's
+theory of the \textit{Uncanny Valley} \citep{mori_uncanny_1970}.
+%see Figure \ref{fig:uncanny_valley}.
+
+%\begin{figure}\centering
+%% Use the relevant command to insert your figure file.
+%% For example, with the graphicx package use
+%  \includegraphics[scale=0.75]{uncanny-valley.jpg}
+%% figure caption is below the figure
+% \caption{Mashiro Mori, illustration of the \textit{Uncanny Valley} hypothesis.
 The curve models the user's perceived affinity with the artifact, as its human likeness is increased.
@@
 Originally from 1970; picture from a manuscript version of \cite{mori_uncanny_2012}}
- \label{fig:uncanny_valley}       % Give a unique label
- \end{figure}
+% \label{fig:uncanny_valley}       % Give a unique label
+% \end{figure}
 
@@
 certain threshold) will generally lead to 
-more perceived \textit{affinity} from the human side \citep{mori_uncanny_1970} (see 
-Figure \ref{fig:uncanny_valley}).
+more perceived \textit{affinity} from the human side \citep{mori_uncanny_1970}.
+% (see Figure \ref{fig:uncanny_valley}).
 This further increases anthropomorphism, and as such

### 2014-04-01 paper.tex
small changes section 2

--- 2014-04-01 paper.tex
@@
 human''} \citep{epley_seeing_2007}. 
-To shed light on this phenomenon, first of all, we would like to propose a clarification of terms.
-In short, we propose to differentiate between \textbf{anthropomorphic form} to refer to an imitation of human-like form in the \textit{design} of artificial agents, and  \textbf{anthropomorphism} to refer to the social phenomenon of
-people's tendency to \textit{perceive} human-likeness in non human-like agents
-\citep{fink_anthropomorphism_2012}. In the following, we might use the terms \texit{form} and \textit{design} interchangeably.
-
-\hl{Julia: I will make a draft of a figure here}
+To shed light on this phenomenon as a whole, first of all, we would like to propose a clarification of terms.
+
+\paragraph{Terminology\\}
+
+We propose to use the term \textbf{anthropomorphism} to describe a social phenomenon, which arises in an interaction between a human agent and a non-human agent, \eg a robot (see Figure \ref{fig:anthropofig}).
+The term anthropomorphism can be used to refer to people's tendency to \textit{perceive} human-like characteristics in non-human agents (or artifacts), but also to refer to the observable effect of a person \textit{ascribing} or \textit{attributing} such human-like characteristics to the agent or artifact.
+Further, anthropomorphism might also be observable in a human's behavior / actions toward a non-human agent.
+The common point here is that anthropomorphism is always performed by the human (either in real or imagined).
+
+However, the term anthropomorphism should \textit{not} be used to refer to the design of a non-human agent or artifact.
+This would violate the understanding of anthropomorphism arising in an interaction.
+We propose to use the term  \textbf{anthropomorphic design} to refer to an imitation of human-like form in the \textit{form} of artificial agents.
+(In the following, we might use the terms \textit{form} and \textit{design} interchangeably.)
+
+In literature, this distinction is not always done, which is a major source of confusion.\\
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.75\columnwidth]{anthropo.pdf}
+    \caption{Anthropomorphism is a social phenomenon which arises in an interaction between a human agent and a non-human agent.
+The two agents are the main \textit{players} \hl{(or elements?)} of the interaction, and consequently one can apply two main perspectives when trying to explain anthropomorphism: a human-centered and an artifact-centered perspective (grey triangles).
+There are several person- and artifact-related factors that determine \hl{(or influence / impact on?)} anthropomorphism.
+Further, the context / situation in which the interaction occurs plays a role.}
+
+    \label{fig:anthropofig}
+\end{figure}
 
@@
 \citep{persson_anthropomorphism_2000}, one can also
-take two main perspectives on explaining anthropomorphism \citep{lee_human_2005}: an artifact-centered perspective and a human-centered perspective.\\ 
+take two main \textit{perspectives} when trying to explain why humans anthropomorphize \citep{lee_human_2005}: an artifact-centered perspective and a human-centered perspective (see grey triangles in Figure \ref{fig:anthropofig}).
+
 We now first present an artifact-centered perspective, and outline how 
@@
 \cite{takayama_perspectives_2012} propose to refer to this immediate (sometimes visceral) sense in a situation as \textit{in-the-moment}, compared to a more distanced cogitation and consideration which she calls \textit{reflective}.
-(As this distinction imply different cognitive processes, we will come back to it later, in the human-centered perspective, Section \ref{sec:human-centered}).
+(As this distinction implies different cognitive processes, we will come back to it later, in the human-centered perspective, Section \ref{sec:human-centered}).
 
@@
 These experiences mark the transition between an immediate \textit{in-the-moment} and more thoughtful \textit{reflective} \citep{takayama_perspectives_2012} perception of, and interaction with the robot.
-As such, a more human-centered perspective needs to be applied, and we will come back to this in Section \ref{sec:human-centered}.
+As this distinction is also based on different cognitive processes, a more human-centered / cognitive perspective needs to be applied here, and we will treat this in Section \ref{sec:human-centered}.
 
@@
 A similar finding is described in \cite{hegel_understanding_2008} and
-\citet{krach_can_2008}. In a user study using functional magnetic resonnance
+\cite{krach_can_2008}. In a user study using functional magnetic resonance
 imagery (fMRI), the authors found that participants
@@
 non-human interaction partner. Indeed, from an early age humans develop a
-tendency to explain one's own and others'actions in terms of beliefs, desires
+tendency to explain one's own and others' actions in terms of beliefs, desires
 and goals,  called \textit{theory of mind}. The theory of mind allows the implicit attribution of
-intentions and other mental states to others \citep{premack1978does, leslie_pretense_1987, Frith2003}.
-\citet{hegel_understanding_2008} and \citet{krach_can_2008} finding was evident at the behavioral level
+intentions and other mental states to others \citep{premack1978does,leslie_pretense_1987,Frith2003}.
+The finding of \cite{hegel_understanding_2008} and \cite{krach_can_2008} was evident at the behavioral level
 as well as on the neuro-physiological level: the more the human-likeness of the
@@
 
-\subsubsection{Diverse understandings of anthropomorphism\\}
+\subsubsection{Diverse understandings of anthropomorphism and confusions in the terminology used\\}
 
@@
 Further,
+
+\hl{Julia is working on this section}
 

### 2014-04-01 paper.tex
Proof-reading of section 3 and 4. Many little changes

@@
 \subsection{A few results from the field}
+\label{sec:field-results}
 
@@
 Anthropomorphic (and life-like) forms have a long-standing tradition in design in general, and in the design of daily life things, in particular 
-\citep{norman_design_1988,guthrie_bottles_2000}.
-Interestingly, from its very beginning robots were resembling a human being in their appearance.
-Starting from when the term \texit{robot} first appeared in a play by Karel \^{C}apek in the 1920ies, robots were man-made beings, created as the \textit{``shadow of man''} \citep{replicant_????}.
+\citep{norman_design_1988,guthrie_bottles_2000}. Interestingly, from its very
+beginning robots were resembling a human being in their appearance. Starting
+from when the term \textit{robot} first appeared in a play by Karel \^{C}apek in the 1920ies, robots were man-made beings, created as the \textit{``shadow of man''} \citep{replicant_????}.
 
@@
 human-robot interactions evolves over time (during the process of
-\emph{adopting} a robot, for instance). Though conflicts were found, the HRI community more or less accepted viewing anthropomorphism as a static feature that once
-observed during a short-term interaction reflects a sustaining social effect. So far, it was also measured as such. But there are some hints that this is deficient.
-
-For instance, \cite{kanda_interactive_2004} point out that relationships among people evolve over time and similarly, also people’s attitude toward technological artifacts
-and their relationship with them might evolve over time.
-In their study, \cite{kanda_interactive_2004} were also among the first to describe empirically \emph{novelty effects} during a long-term study with an interactive robot in a school.
-
-There are also hints from a more theoretical side, that make us think that anthropomorphism is likely to change over 
-time and with growing experience that a person has with a robot.
-
-%effectance motivation reduces uncertainty and consequently the tendency to anthropomorphize
-For instance, let's have a look at the processes that underlie anthropomorphism.
-In its essence anthropomorphism means reasoning about and perceiving something
-non-human (and unknown or unfamiliar) based on one's representation of the
-familiar and well-known concept of being human (or one-self). According to \citep{epley_when_2008} the basic
-operations that underlie these inductive inferences are the acquisition of knowledge, the
-activation or elicitation of knowledge, and the application of activated
-knowledge at the time of the judgment. By applying knowledge to a given situation / interaction, it is implied that one attempts to correct, adjust, or maybe
-integrate less accessible information into a more automatically activated
-default representation. \cite{epley_when_2008} argues that this process can be seen as a process of correction, and
-thus, it is often insufficient leaving final judgments biased in the direction
-of the initially activated representation. Refinements to the initial representation mean something evolves. This can be due to the fact that a person's knowledge base changes
-constantly with newly acquired things, or growing experiences with a
-robot, \etc. . Consequently, it is likely that the ``need to anthropomorphize'' a robot decreases
-over time (from the human-centered point of view), since the user's knowledge about the robot evolves, and also the user familiarizes herself with the robot. Consequently, the robot should become more
-predictable and more familiar to the human user and inferences about it can be
-made based on the acquired knowledge.
-
-In other words, the argumentation is that humans have a motivation to interact effectively in their environment \textit{(effectance)} \citep{epley_when_2008}.
-This means that humans are motivated to be able to understand and predict the environment and agents around them.
-Through this process, uncertainty is reduced, and consequently, a first unfamiliar robot, can be explained with means that are different from anthropomorphism.
-
-%expectations
-Further,
-
-\hl{Julia is working on this section}
-
-%\textbf{In-the-moment vs. reflective perspectives on agency}\\
-%Perception of agency can be treated as anthropomorphism.
-%\citep{takayama_perspectives_2012} proposes to differentiate between a \textit{in-the-moment} and \textit{reflective} perspective to better understand how human users perceive agency in robots.\footnote{``The other important distinction between the two perspectives is the \hl{cognitive processes} that they engage.''} According to Takayama, an \textit{in-the-moment} perspective refers to one's most immediate (sometimes visceral) sense in a situation.
-In contrast, a \textit{reflective} perspective refers to one's sense of a situation upon more distanced cogitation and consideration.
-For instance, we reflectively might not perceive agency in a social robot, but it can feel quite differently in the moment of interaction.
-A critical dimension of agency is the perspective from which something seems to have agency.
-\cite{takayama_perspectives_2012} argues that neglecting to separate reflective perspectives from in-the-moment perspectives of agency is one of the major sources of confusion when people talk and write about anthropomorphism.
-There seems to be a disconnection between what people consciously perceive and how they respond to stimuli that they may not consciously perceive.
-%That means, in the initial phase of interacting with a novel device \textbf{(initialization)} people might not consciously respond but rather mindlessly \citep{nass_machines_2000}.
-Only after some time of \textbf{familiarization}, they might respond in a more reflective manner.
-This can be illustrated by the fact that people tend to deny interacting with computational systems as if they were people and yet they respond to computers in many ways that are remarkably similar to how they respond to people \citep{reeves_media_1996}.
-%\cite{takayama_perspectives_2012} also applies a cognitive viewpoint on the two different perspectives of in-the-moment \vs reflective to illustrate differences.
-She states that in-the-moment perceptions of agency are largely shaped by bottom-up perceptual processes, evoking very immediate responses (\eg to the cues emitted by the artifact's design, see Section \ref{sec:anthropomorphic-design}).
-%In contrast, according to Takayama, reflective perceptions are more often shaped by top-down processes because of the nature of reflective thought.
+\emph{adopting} a robot, for instance). Though conflicts were
+found\fxwarning{SL: which conflicts are we talking about?}, the HRI
+community more or less accepted viewing anthropomorphism as a static feature
+that once observed during a short-term interaction reflects a sustaining social
+effect.
+
+\citet{kanda_interactive_2004} point out, however, that relationships among
+people evolve over time and, in a similar manner, one can expect people's attitude toward
+technological artifacts and their relationship with them to evolve as well.
+In their study, \citet{kanda_interactive_2004} were also among the first to
+describe empirically \emph{novelty effects} during a long-term study with an
+interactive robot in a school.
+
+From a theoretical perspective, we also expect anthropomorphism to change over
+time, with growing experience with a robot. As discussed in the previous
+sections, anthropomorphism means in essence \emph{reasoning about and perceiving
+something non-human (and unknown or unfamiliar) based on one's
+representation of the familiar and well-known concept of being human (or
+one-self)}. According to \citet{epley_when_2008}, the basic operations that
+underlie these inductive inferences are the \emph{acquisition of knowledge}, the
+\emph{activation or elicitation of knowledge}, and the \emph{application of
+activated knowledge at the time of the judgment}. By applying knowledge to a
+given situation or interaction, it is implied that one attempts to correct,
+adjust, or maybe integrate less accessible information into a more automatically
+activated default representation. Epley argues that this process can be seen as
+a process of correction, and thus, it is often insufficient leaving final
+judgments biased in the direction of the initially activated representation.
+Refinements to the initial representation mean something evolves. This can be
+due to the fact that a person's knowledge base changes constantly with newly
+acquired things, or growing experiences with a robot. Consequently, it is likely
+that the ``need to anthropomorphize'' a robot decreases over time (from the
+human-centered point of view), since the user's knowledge about the robot
+evolves, and also the user familiarizes herself with the robot. Consequently,
+the robot should become more predictable and more familiar to the human user and
+inferences about it can be made based on the acquired knowledge.\fxwarning{SL:
+Rephrase the last part of this paragraph}
+
+In other words, the argumentation is that humans have a motivation to interact
+effectively in their environment \textit{(effectance)} \citep{epley_when_2008}.
+This means that humans are motivated to be able to understand and predict the
+environment and agents around them. Through this process, uncertainty is
+reduced, and consequently, a first unfamiliar robot, can be explained with means
+that are different from anthropomorphism.\fxwarning{SL: Paragraph unclear to me.
+Rephrase it?}
+
+In the introduction, we reported on a few selected experimental results that
+illustrate how the user tendency to anthropomorphize decreased over time.
+Combined with the extensive discussion on the nature and factors of
+anthropomorphism that we proposed at section~\ref{sec:anthropomorphism}, we
+introduced in the following section a novel qualitative model of the evolution
+of anthropomorphism over time, \ie a model of the dynamics of anthropomorphism.
 
@@
 The phenomenological model of anthropomorphism we propose
-(Figure~\ref{fig:dynamics}~\citep{lemaignan2014dynamics}) represents how the
-level of anthropomorphic effects~\Ant[R,H,C,t] (\ie observable manifestations of
-anthropomorphism, as defined in section~\ref{sec:intro}) evolves over a
-long-term human-robot interaction.
+(Figure~\ref{fig:dynamics},~\citep{lemaignan2014dynamics}) represents how the
+level of anthropomorphic effects~\Ant[R,H,C,t] (\ie the observable
+manifestations of anthropomorphism) evolves over a long-term human-robot
+interaction.
 
@@
 In this model, anthropomorphism is quantified by a \emph{normalized level of
-anthropomorphic effects} $\antNorm[R,H,C,t] = \frac{\ant[R,H,C,t]}{\antMax}$: because anthropomorphic effects are
-not quantified on an absolute scale, we present them as a normalized value, that
-spans from a minimum (no anthropomorphic effects: $\ant=0$) to a maximum (noted
-\AntMax, with $t_{max} = \operatorname{arg\,max}_t \, \ant[t]$). For readability
-reasons, we however omit the hat on \Ant in the following sections. We discuss
-at section~\ref{measuring} possible methodologies for the quantitative and
+anthropomorphic effects} $\antNorm[R,H,C,t] = \frac{\ant[R,H,C,t]}{\antMax}$:
+because anthropomorphic effects are often qualitative and difficult to quantify
+on an absolute scale, we present them as a normalized value, that spans from a
+minimum (no anthropomorphic effects: $\ant=0$) to a maximum (noted \AntMax, with
+$t_{max} = \operatorname{arg\,max}_t \, \ant[t]$). For the sake of readability,
+we will use \Ant in the following sections to refer to the normalized level of
+anthropomorphic effects. Note also that we discuss at
+section~\ref{sec:measuring} possible methodologies for the quantitative and
 qualitative assessment of anthropomorphic effects.
 
-As pictured on Figure~\ref{fig:dynamics}, we suggest that $t_{max}$ actually
-corresponds to the novelty effect peak. The actual maximum value of
-anthropomorphic effects depends on each unique combination of human, robot and
-several other factors we introduce below, and thus varies. The general
+The actual maximum value of anthropomorphic effects depends on each unique
+combination of human, robot and several other factors we introduce below, and
+thus varies (as pictured on Figure~\ref{fig:dynamics}, we suggest besides that
+$t_{max}$ actually corresponds to the novelty effect peak). The general
 \emph{shape} of the model remains however the same and depicts the evolution of
@@
 % background shading
-\path[fill=blue!20] (0,0) rectangle (0.6,5.5);
-\path[fill=green!20] (0.6,0) rectangle (5.2,5.5);
+\path[fill=green!20] (0,0) rectangle (0.6,5.5);
+\path[fill=blue!15] (0.6,0) rectangle (5.2,5.5);
 \path[fill=orange!20] (5.2,0) rectangle (9.8,5.5);
@@
     behaviors}) may lead to local increases or decreases of the level of
-    anthropomorphism.}
+    anthropomorphic effects.}
 
@@
 
+\fxwarning{SL: Mention the pre-interaction phase}
+
 \subsubsection{Initialization Phase}
@@
 
-The \emph{initial capital of anthropomorphism} describes the initial potential
+The \emph{initial capital of anthropomorphism} \ICA describes the initial potential
 for the robot to be anthropomorphized by the human user in a given situation.
-This potential depends on several factors. It has been shown, for instance, that
+This potential depends on several factors, introduced in
+section~\ref{sec:anthropomorphism}. It has been shown, for instance, that
 some \textit{people} tend to anthropomorphize more than others, that some
@@
 \textit{cultures} are notorious for their anthropomorphic religions and
-worldviews~\cite{epley_when_2008}. Also the shape and design of the robot play a
-role, and the context in which the interaction takes place. Our model of
-anthropomorphism takes these determinants into account and initializes the level
-of anthropomorphic interactions between a human and a robot to a value that we
-call \emph{initial capital of anthropomorphism}, noted \ICA. \ICA describes the
-first (real or imagined) contact to a robot. In this stage of pre-interaction,
-people form initial expectations toward the robot and imagine how they will use
-it / interact with it.
-
-We build \ICA on three main factors that \emph{a priori} determine the
-potential that a robot will be anthropomorphized:
+worldviews~\citep{epley_when_2008}. Also the shape and design of the robot play a
+role, like the context in which the interaction takes place. Our model of
+anthropomorphism represents these factors as a compound metric \ICA. As such,
+\ICA describes the level of anthropomorphic projections just prior the first
+(real or imagined) contact to a robot. In this stage of pre-interaction, people
+form initial expectations toward the robot and imagine how they will use it /
+interact with it.
+
+Following the discussion in section~\ref{sec:anthropomorphism}, we build \ICA on
+three main factors that determine \emph{a priori} that a robot
+will be anthropomorphized:
 
@@
 
-    \item \emph{Human-centered factor}: The \textbf{personality} and individual
+    \item ~\emph{Human-centered factor} $S$: The \textbf{personality} and individual
         traits of the human user: Psychological characteristics / determinants
         that influence a person's tendency to anthropomorphize
-        artifacts~\cite{epley_seeing_2007}. Other individual traits and
+        artifacts~\citep{epley_seeing_2007}. Other individual traits and
         demographic aspects are comprised (\eg age, gender, cultural background,
@@
 
-    \item \emph{Robot-centered factor}: The robot's \textbf{design} and how it
+    \item ~\emph{Robot-centered factor} $R$: The robot's \textbf{design} and how it
         appears to the human user. Characteristics of the robot's form,
         behavior, and interaction modalities (anthropomorphic
-        design)~\cite{fong_survey_2003}.
-
-    \item \emph{Situation-centered factor}: The real or imagined
+        design)~\citep{fong_survey_2003}.
+
+    \item ~\emph{Context-centered factor} $C$: The real or imagined
         \textbf{purpose} of the robot, including the situational context in
@@
         robot is used / experienced (environmental
-        context)~\cite{joosse_what_2013}.
+        context)~\citep{joosse_what_2013}.
 
@@
 
-\ICA comprises some hypothetical values for each of these three factors, such
-that different \ICA values can be obtained, given the robot, human user, and
-environmental context\fxfatal{??}.
-
-For \textbf{personality}, we suggest to apply Epley \textit{et al.}'s
-\cite{epley_seeing_2007} psychological \textit{"Three Factor Theory"} of
-anthropomorphism. For instance, children generally tend to anthropomorphize
-objects more than adults. Also, a person who lacks social connection is said to
-be more likely to anthropomorphize. Both aspects would increase \ICA. This
-means that, one and the same robot used by a different user, can lead to a
-different \ICA.
+For \textbf{personality}, we suggest to apply \citet{epley_seeing_2007}
+psychological \textit{3-factor theory} of anthropomorphism. For instance,
+children generally tend to anthropomorphize objects more than adults. Also, a
+person who lacks social connection is said to be more likely to
+anthropomorphize. Both aspects would increase \ICA. This means that, one and the
+same robot used by a different user, can lead to a different \ICA.
 
 For \textbf{design}, we understand that a robot that follows an anthropomorphic
-design (\eg NAO) leads to a higher \ICA than a rather functional robot (\eg
+design (\eg Nao) leads to a higher \ICA than a rather functional robot (\eg
 Roomba). Also, a robot that is able to display facial expressions would increase
-the \ICA. However, \hl{as discussed before} a classification of the "amount" of
-anthropomorphic design in a robot, as for instance suggested by Fong \textit{et
-al.} \cite{fong_survey_2003}, can be difficult. Nevertheless, the important
-aspect is how the robot appears to the user, \eg human-like or machine-like.
-Studies have shown that an anthropomorphic robot is perceived differently to a
-non-anthropomorphic robot\fxfatal{...this sentence sounds strange like that.
-Need references or better integration in the paragraph}.
+the \ICA. Quantify the \emph{level} of anthropomorphic design in a robot, as
+suggested for instance by \citet{fong_survey_2003}, can be difficult.
+Nevertheless, the important aspect is how the robot appears to the user, \eg
+human-like or machine-like.
 
@@
 brings along, impacts how far the robot will be attributed human-like
-characteristics. We draw on findings such as presented in Joosse
-\etal~\cite{joosse_what_2013}. The authors showed for instance that when the
-same robot (NAO) is used in a different task context (cleaning task \emph{vs.}
-tour guide), users ascribe different ``personalities'' to the robot. In general,
-a robot which is imagined to be used in a social, entertaining or playful
+characteristics. We draw on findings such as presented in \citet{joosse_what_2013}. The authors showed for instance that when the
+same robot (Nao) is used in a different task context (cleaning task \emph{vs.}
+tour guide), users ascribe different personalities to the robot. In general,
+a robot which is imagined in a social, entertaining or playful
 context leads to a higher \ICA than a robot which is used for a routine or
@@
 serious tasks and a less serious robot for more playful
-tasks~\cite{goetz_cooperation_2002, goetz_matching_2003}. Also, we suggest that
+tasks~\citep{goetz_cooperation_2002, goetz_matching_2003}. Also, we suggest that
 the environmental context in which people experience and interact with the robot
@@
 social interaction, and in turn attributed human-like
-qualities)~\cite{baxter2013do}.
+qualities~\citep{baxter2013do}).
 
@@
 
-\fxfatal{Julia, do you have smthg to provide an initial account of what the
+\fxfatal{SL: Julia, do you have smthg to provide an initial account of what the
 novelty effect is?}
@@
 
-The woman (E.) is reading aloud parts of the "quick start manual": \emph{"When
+The woman (E.) is reading aloud parts of the ``quick start manual'': \emph{``When
 Roomba senses dirt, the blue dirt detect light is lit and Roomba cleans more
-intensely in that area."} She laughs and turns to the robot, talking directly to
-it \emph{"Today you can light up darling!"}. E. carries Roomba to the entrance
+intensely in that area.''} She laughs and turns to the robot, talking directly to
+it \emph{``Today you can light up darling!''}. E. carries Roomba to the entrance
 door and puts it on the floor [floor type: tiles, partially covered with little
-Persian carpets], she explains \emph{"It has to start from here, this is where
-you enter the house!"}. After pressing the CLEAN button, the robot quickly gets
+Persian carpets], she explains \emph{``It has to start from here, this is where
+you enter the house!''}. After pressing the CLEAN button, the robot quickly gets
 stuck with the carpet in the entrance hall, consequently it reports error 1 [
-two-tone "Uh-Oh" sound followed by a narrated voice that starts off with "Error
-1"]. E. is very surprised \emph{"What, it is even talking to me?"}, lifts the
+two-tone ``Uh-Oh'' sound followed by a narrated voice that starts off with ``Error
+1'']. E. is very surprised \emph{``What, it is even talking to me?''}, lifts the
 robot off and puts it back for cleaning. At several occasions, while watching
 how the robot moves around and cleans, E. makes compliments to the robot:
-\emph{"Nice!"} or \emph{"Good job!"} or \emph{"Bravo!"}. Once, when Roomba turns
+\emph{``Nice!''} or \emph{``Good job!''} or \emph{``Bravo!''}. Once, when Roomba turns
 right in front of some crumbs on the kitchen floor and moves away without
-cleaning them up, E. says: \emph{"There you forgot something, what is with over
-there? Look, there you still have something to clean up!"}, and she points at
-where she wants Roomba to go. Further, she uses directing gestures and tells the
-robot: \emph{"No, go this way! Come over here!"}. The woman keeps observing the
-robot and wonders about its "intentions", asking it directly: \emph{"Why do you
-leave the kitchen? There is still something there on the fringe!"}. E. turns to
-the experimenter, and tells her: \emph{"She [the robot] loves the hall!"}.
+cleaning them up, E. says: \emph{``There you forgot something, what is with over
+there? Look, there you still have something to clean up!''}, and she points at
+where she wants Roomba to go. Further, she uses deictic gestures and tells the
+robot: \emph{``No, go this way! Come over here!''}. The woman keeps observing the
+robot and wonders about its intentions, asking it directly: \emph{``Why do you
+leave the kitchen? There is still something there on the fringe!''}. E. turns to
+the experimenter, and tells her: \emph{``She [the robot] loves the hall!''}.
 
@@
 talking directly to the robot, or asking it questions (though it doesn't
-recognize speech); giving it nick-names or ascribing a gender (\emph{"darling"}
-/ \emph{"she"}); praising the robot (\emph{"Good job!"}); using pointing
+recognize speech); giving it nick-names or ascribing a gender (\emph{``darling''}
+/ \emph{``she''}); praising the robot (\emph{``Good job!''}); using pointing
 gestures toward the robot, or try to direct it around with commands; attributing
-a personal preference / intention to the robot (\emph{"she loves the hall!"}).
+a personal preference / intention to the robot (\emph{``she loves the hall!''}).
 
 During the following visits at the woman's place, she did not talk to the robot
-anymore, and generally behaved in a less anthropomorphizing way. This is why we
-suspect the observed effects were due to the novelty of the robot.
+anymore, and generally behaved in a less anthropomorphizing way. The observed
+effects were likely due to the novelty of the robot.
 
@@
 technologies plays an important role in long-term tendency to
-anthropomorphize~\cite{fink_living_2013} (people more familiar with technology
+anthropomorphize~\citep{fink_living_2013} (people more familiar with technology
 understand, and hence predict, better the behavior of the robot, which in turn
@@
 anthropomorphic effects have been observed on non-anthropomorphic robots (like
-the iRobot Roomba~\cite{fink_living_2013} or the military iRobot
+the iRobot Roomba~\citep{fink_living_2013} or the military iRobot
 PackBot\footnote{Rodney Brooks has reported in keynotes that occasionally
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-% CLAIRE & SEVERIN:
-%
-%
-
-\section{Cognitive Model}
+
+\section{The Cognitive Correlates of Anthropomorphism}
 \label{sec:cognition-neuroscience}
 
-In this section are discussing more speculative aspects and hypotheses that follow
-from the model. These aspects would benefit further investigations and
-experimental support.
-%
-
-%In this section we are briefly reviewing results on anthropomorphism from the cognitive neuroscience point of view.
-%We then discuss more speculative aspects and hypotheses that follow
-%from the model. These aspects would benefit further investigations and
-%experimental support.
+This section provide an initial interpretation of anthropomorphism in
+terms of \emph{cognitive correlates}: how human cognition can explain the
+dynamic nature of our interactions with robots, and what are the main cognitive
+stages upon which researchers can build to design better, deeper human-robot
+interactions.
+
+The next sections introduces a model of the cognitive stages involved in
+human-robot interaction, that can be interpreted in parallel to the model of the
+dynamics of anthropomorphism.
+
+We also discuss two specific aspects: the cognitive impact of disruptive
+behaviors (section~\ref{sec:disruptive}) on mutual modelling, and how our models
+relate to the \emph{In-the-moment} versus \emph{Reflective} perspectives
+introduced by~\citet{takayama_perspectives_2012}.
+
 %
@@
 
-\subsection{Cognitive model}
+\subsection{A Model of the Cognitive Stages of Human-Robot Interaction}
 \label{sec:cognitive-model}
@@
 
-\draw (-0.3,1) node[rotate=90] {Level 1}
-      (-0.3,3) node[rotate=90] {Level 2}
-      (-0.3,5) node[rotate=90] {Level 3};
+\draw (-0.3,1) node[rotate=90] {Stage 1}
+      (-0.3,3) node[rotate=90] {Stage 2}
+      (-0.3,5) node[rotate=90] {Stage 3};
 
@@
 %}
-\caption{The three cognitive levels of anthropomorphism: Level 1 is the instinctive,
+\caption{The three cognitive stages of anthropomorphism: Stage 1 is the instinctive,
 sub-cognitive identification of living peers. {\it Empathy} is characteristic
 of this stage. After longer observation or short, non-contextualized interaction
-(typically, a lab environment), the user reaches Level 2: the user projects a
+(typically, a lab environment), the user reaches Stage 2: the user projects a
 mental model he/she is already familiar with onto the robot. After longer {\it
-contextualized} interaction (typically, at home), the user enters Level 3 of
-anthropomorphism: the user recomposes an accurate mental model of the robot,
+contextualized} interaction (typically, at home), the user enters Stage 3 of
+anthropomorphism: the user composes a custom mental model of the robot,
 based on experience. This leads to adapted interaction modalities, that may
@@
 
-We propose three different cognitive phases (Figure~\ref{fig:cognitivemodel}),
-which do not directly match the previously presented three phases of
-anthropomorphism but are still related.
-
-\subsubsection{Cognitive Processes and Phases}
+We propose three different cognitive stages (Figure~\ref{fig:cognitivemodel}),
+which are related but do not directly match the three phases of
+the model of the dynamics of anthropomorphism.
+
+\subsubsection{Cognitive Processes and Stages}
 
@@
 representation of the familiar and well-known concept of being
-human~\cite{epley_when_2008}. This led us to interpret the phases of
+human~\citep{epley_when_2008}. This led us to interpret the phases of
 anthropomorphic interactions as parallel cognitive phases
@@
 
-The so-called \emph{level 1} is the instinctive, pre-cognitive identification of
-living peers. That humans tend to anthropomorphize robots intuitively in this
-pre-cognitive way
-is supported by studies done by Rosenthal-von der Pütten
-\textit{et al.}~\cite{rosenthal-vonderputten_experimental_2013} who investigated
-the neural correlates of emotional reactions of humans towards a robot. {\it
-Empathy} is characteristic of this stage~\cite{rosenthalvonderPutten2013neural}.
-It is also at this stage that automatic activation of the human's mirror neurons
-system  in response to viewing the robots action and human automatic emotional
-responses are contributing at a lower level
-to the intuitive anthropomorphization (see Section 2.2.2 \fixme{put ref})
-%We suggest that the human's mirror neuron system is contributing to anthropomorphism by  allowing for a mapping of the robot's goal-directed actions into the human own motor repertoire \cite{Gallese1998, Wolpert2003, cullen2013individual}.
+The \emph{stage 1} is the instinctive, pre-cognitive identification of living
+peers. Studies conducted by~\citet{rosenthal-vonderputten_experimental_2013},
+who investigated the neural correlates of emotional reactions of humans towards
+a robot, supports the idea that humans tend to anthropomorphize robots
+intuitively in this pre-cognitive way. {\it Empathy} is characteristic of this
+stage~\citep{rosenthalvonderPutten2013neural}.  It is also at this stage that
+automatic activation of the human's mirror neurons system  in response to
+viewing the robots action and human automatic emotional responses are
+contributing at a lower level to the intuitive anthropomorphization (see Section
+2.2.2 \fixme{put ref}).
+
+%We suggest that the human's mirror neuron system is contributing to
+%anthropomorphism by  allowing for a mapping of the robot's goal-directed
+%actions into the human own motor repertoire \cite{Gallese1998, Wolpert2003,
+%cullen2013individual}.
 
@@
 of the robot) or short interaction (touching, short talk like greetings), we
-suggest the human reaches the cognitive \emph{level 2}: in this phase, the human
+suggest the human reaches the cognitive \emph{stage 2}: in this phase, the human
 starts building a behavioral and cognitive model of the robot that would support
 both the observed and imagined capabilities of the robot.  The \emph{familiarity
-thesis}~\cite{hegel_understanding_2008} supports the idea that the human
-first projects onto the robot mental models of similar agents he/she is already
+thesis}~\cite{hegel_understanding_2008} supports the idea that the human first
+projects onto the robot mental models of similar agents he/she is already
 familiar with (ranging from animals to human adults, to pets and children). We
-hypothesize that the nature of the projected mental
-model, as well as how deep the human engages in this projection, might be
-driven by the same parameters as we mentioned for the \emph{initial capital of
-anthropomorphism} (section~\ref{sec:ica}). 
-At this stage the human might also change his attitude towards the robot, paying more attention to social cue than to low-level behaviour which may reinforce the resonnance mechanisms.
-
-The cognitive \emph{level 3} is reached after a \emph{contextualized} interaction.
+hypothesize that the nature of the projected mental model, as well as how deep
+the human engages in this projection, might be driven by the same parameters as
+we mentioned for the \emph{initial capital of anthropomorphism}
+(section~\ref{sec:ica}).  At this stage the human might also change his attitude
+towards the robot, paying more attention to social cue than to low-level
+behaviour which may reinforce the resonnance mechanisms.
+
+The cognitive \emph{stage 3} is reached after a \emph{contextualized} interaction.
 A \emph{contextualized} interaction is \emph{explicitly purposeful} (the purpose
@@
 modified its own abilities to anthropomorphize, having built a full cognitive
-model of the robot and know being able to attribute internal state to the robot
-through his theory of mind.
+model of the robot and now being able to attribute internal state to the robot
+through his theory of mind\fxwarning{SL: last part not so clear. Rephrase?}.
+
+\fxwarning{SL: mention that the stages are not mutually exclusive and actually
+overlap over time.}
 
@@
 
-These cognitive levels overlap over time but do not exactly match the
+These cognitive stages overlap over time but do not exactly match the
 \emph{Initialization}, \emph{Familiarization} and \emph{Stabilization} phases
 introduced in our model of the dynamics of anthropomorphism. In particular,
-the cognitive levels 1 and 2 are both included in the \emph{initialization} phase
+the cognitive stages 1 and 2 are both included in the \emph{initialization} phase
 of the anthropomorphism model. Sub-cognitive anthropomorphism typically
 \emph{initiates} the novelty effect by rapidly engaging the human in the
-interaction through an initial projected agency, whereas cognitive level 2
+interaction through an initial projected agency, whereas cognitive stage 2
 (projection of familiar mental models) supports the novelty effect by inducing
@@
 
-The cognitive level 3 also overlaps with the \emph{Familiarization} phase: as
-the human gets used to the robot, we hypothesize one restates and adapts its
+The cognitive stage 3 also overlaps with the \emph{Familiarization} phase: as
+the human gets used to the robot, he/she restates and adapts its
 cognitive model of the robot by iteratively reshaping pre-existent, familiar
@@
 A \emph{stable level of anthropomorphism} is reached when the adaptation process
-depicted in the cognitive level 3 reached a stable state, \ie the user's
+depicted in the cognitive stage 3 reached a stable state, \ie the user's
 experience with the robot is correctly supported by the cognitive model he/she
@@
 A cognitive interpretation of anthropomorphism also allows to better interpret
-the role of unexpected robot behaviors, that we are \emph{disruptive} in regard
+the role of unexpected robot behaviors, that are \emph{disruptive} with respect
 to the cognitive process of building a mental model of the robot.
@@
 HRI2013 paper}
-This is supported by the results from \citet{Waitz2010} seen in section
-\ref{sec:explanations} that people attribute more easily anthropomorphic
-features to artefacts when they have unpredictable behaviors.
+This is supported by the results from~\citet{Waytz2010}, mentioned in section
+\ref{sec:explanations}, that show that people attribute more easily
+anthropomorphic features to artefacts when they have unpredictable behaviors.
 
@@
 suddenly restate his/her behavioral model of the robot and will temporarily lead
-to an increase of the level of anthropomorphism (depicted by the spikes on
-Figure~\ref{fig:dynamics}).
+to an increase or decrease of the level of anthropomorphism (depicted by the
+spikes on Figure~\ref{fig:dynamics}).
 
@@
 behavior is then called \emph{transparent} \fixme{cite here, Julia?}
-\hl{(literature on transparency)}, and the user may besides hypothesize that the
+\hl{(literature on transparency)}, and the user may hypothesize that the
 robot has \emph{introspective} capabilities (it can reflect on its own internal
-state), which in turn may leads to higher anthropomorphism level.  On the
+state), which may lead to higher anthropomorphic projections.  On the
 contrary, if the robot shows no sign of recognizing its own failure, the user
@@
 saying ``I do not want to go there''. In that case, we expect to see an increase
-of anthropomorphism attribution due to the human ascribing intentionality to the
+of attribution of anthropomorphism due to the human ascribing intentionality to the
 robot.
@@
 
+\subsection{\emph{In-the-moment} versus \emph{Reflective} perspectives}
+
+\fxwarning{SL: Bridge + integration in the section 4 TDB}
+
+Perception of agency can be treated as anthropomorphism.
+\citep{takayama_perspectives_2012} proposes to differentiate between a
+\textit{in-the-moment} and \textit{reflective} perspective to better understand
+how human users perceive agency in robots.\footnote{``The other important
+distinction between the two perspectives is the \hl{cognitive processes} that
+they engage.''} According to Takayama, an \textit{in-the-moment} perspective
+refers to one's most immediate (sometimes visceral) sense in a situation. In
+contrast, a \textit{reflective} perspective refers to one's sense of a situation
+upon more distanced cogitation and consideration. For instance, we reflectively
+might not perceive agency in a social robot, but it can feel quite differently
+in the moment of interaction. A critical dimension of agency is the perspective
+from which something seems to have agency.  \cite{takayama_perspectives_2012}
+argues that neglecting to separate reflective perspectives from in-the-moment
+perspectives of agency is one of the major sources of confusion when people talk
+and write about anthropomorphism. There seems to be a disconnection between what
+people consciously perceive and how they respond to stimuli that they may not
+consciously perceive.  That means, in the initial phase of interacting with a
+novel device \textbf{(initialization)} people might not consciously respond but
+rather mindlessly \citep{nass_machines_2000}. Only after some time of
+\textbf{familiarization}, they might respond in a more reflective manner. This
+can be illustrated by the fact that people tend to deny interacting with
+computational systems as if they were people and yet they respond to computers
+in many ways that are remarkably similar to how they respond to people
+\citep{reeves_media_1996}.  \cite{takayama_perspectives_2012} also applies a
+cognitive viewpoint on the two different perspectives of in-the-moment \vs
+reflective to illustrate differences. She states that in-the-moment perceptions
+of agency are largely shaped by bottom-up perceptual processes, evoking very
+immediate responses (\eg to the cues emitted by the artifact's design, see
+Section \ref{sec:anthropomorphic-design}).  In contrast, according to Takayama,
+reflective perceptions are more often shaped by top-down processes because of
+the nature of reflective thought.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 of the agents to explicit the mental model it has built of its partner
-(emotional state, beliefs, intentions, etc.). Depending on the cognitive levels
+(emotional state, beliefs, intentions, etc.). Depending on the cognitive stages
 the two agents are in, we may expect varying accuracy levels in the produced
@@
 The article also discusses the cognitive correlates of anthropomorphism. We
-proposes to identify three cognitive levels corresponding to successive
+proposes to identify three cognitive stages corresponding to successive
 refinements of the mental models of the robot that the user builds during the
-interaction. We show how these levels relate to observable anthropomorphic
+interaction. We show how these stages relate to observable anthropomorphic
 effects, and how they evolve over time.

### 2014-04-02 paper.tex
changes in the structure of section 2: split into two sections

@@
 The Uncanny Valley hypothesis \citep{mori_uncanny_1970} proposes that human-like
-designs of objects and non-human agents can evoke both positive and negative feelings 
-of affinity in the human observer / user. A positive valence reflects the experience of 
+designs of objects and non-human agents can evoke both positive and negative feelings in the human observer / user. A positive valence reflects the experience of 
 emotional engagement with and feelings of empathy for the non-human agent
@@
 %
-%		PART 1: WHAT OTHERS DID AND WE ALREADY KNOW ABOUT ANTHROPOMORPHISM
+%		WHAT IS ANTHROPOMORPHISM
 %
@@
 
-\section{Why do humans anthropomorphize?}
-\label{sec:anthropomorphism}
-
-Anthropomorphism is an interesting phenomenon because it tells us something about 
-the relationship between the human who anthropomorphizes, and the non-human agent 
-which is anthropomorphized. Though commonly observed, it still appears controversial, at 
-the same time, that humans tend to \textit{``see human in the non-
-human''} \citep{epley_seeing_2007}. 
-To shed light on this phenomenon as a whole, first of all, we would like to propose a clarification of terms.
-
-\paragraph{Terminology\\}
+\section{Towards a unified understanding: What is anthropomorphism?}
+\label{sec:definitions}
+
+Literature on anthropomorphism is quite diverse.
+We would like to point out that there exist different and partly conflicting definitions of the term anthropomorphism, and that in general, the \textit{terminology} is not clear.
+Probably as a result of this, there also exist different understandings of the \textit{phenomenon} that the term `anthropomorphism' describes.
+ In this section we will first give an overview on the diversity of terms and then try to establish a common ground in the understanding of anthropomorphism (the phenomenon).
+
+\subsection{Overview of the diversity of terms}
+
+Originally, the term \textbf{anthropomorphism} comes from the Greek \textit{anthropos} for `man' (or `human') and \textit{morphe} for `form / structure' (or `shape').
+Anthropomorphism is generally understood as people's tendency to perceive a non-human agent as if it had some human characteristics or traits.
+How a person perceives an agent is crucial, as it further determines how she relates to, and behaves towards the agent, or how she may behave in light of this agent \citep{epley_when_2008}.
+As such, anthropomorphism can be seen as a special kind of relationship between a human interacting with a non-human agent.
+An anthropomorphic relationship is often characterized by the fact that the human attributes human-unique characteristics to the non-human agent.
+Since anthropomorphism becomes observable through these attributions, some definitions claim that anthropomorphism is not the \textit{perception} but rather the \textit{attribution} of human qualities to non-human agents.
+Ascribing thoughts, emotions, and intentions are given as examples, and as the most prominently anthropomorphized non-human agents animals and robots are mentioned \citep{duffy_anthropomorphism_2003,schmitz_concepts_2011}.
+
+Apart from anthropomorphism there also exists the term \textbf{animism}, which can be defined as the attribution of life to the nonliving.
+The study of animism was pioneered by Piaget in the 1920s with his work on \textit{The Child's Conception of the  World}.
+He found that children tend to regard many inanimate objects as capable of sensations, emotions and intentions, and called this view `animism'.
+Since then, children`s inferences about the world have been studied intensively, and there is an agreement that children`s views and concepts of living, animal, and plant evolve as they grow up.
+Often synonymously used to animism is the term \textbf{zoomorphism}, which similarly applies to the cases when non-lifelike instances / artifacts are associated with animalistic attributes, excluding human-specific traits.
+As `being alive' is not a human-unique property but applies to all living beings, the attribution of life may not be labeled as anthropomorphism (in a narrow understanding of it).
+Another possibility to illustrate how anthropomorphism differs from attributions of animacy, is to look at paraphrases of anthropomorphism. That is to say, 
+anthropomorphism can alternatively be understood as \textbf{humanization} or 
+\textbf{personification} of anything other than a human being.\footnote{There exist also the phenomenons inverse to anthropomorphism, which can be found in the literature as \textbf{dehumanization} \citep{haslam_dehumanization:_2006}, or \textbf{mechanomorphism} \citep{caporael_anthropomorphism_1986}.
+However, we do not treat this here.}
+Robots can both be animized and anthropomorphized, but often the difference is not made.
+
+%\hl{can be cut from here ...}
+%
+%Thus, animism and anthropomorphism differ in two main aspects:
+%
+%First, the nature of the properties which can be ascribed to an agent differs.
+Life-likeness is not human-unique but applies to all living beings.
+Thus, \textit{animism} applies to attributions of life-like properties but excludes human-specific traits.
+Contrary, a narrow understanding of \textit{anthropomorphism} would exclude all attributions of life-likeness that are not human-unique, such as `being alive'.
+%  
+%Second, the range of agents to which life-likeness can be attributed differs.
+Naturally, only non-living agents can be animized.
+Thus, whereas non-human but \textit{living} beings (most importantly animals) can be anthropomorphized, they cannot be animized.
+Similarly, humans cannot neither be animized nor anthropomorphized as they are living beings and humans.
+%
+%\hl{... to here}
+
+%Personification has 
+%ancient roots, \eg in mythology but also in storytelling. For instance, anthropomorphism was also 
+%used to describe and be able to predict natural forces or anticipate great spirits.
+
+\subsection{Overview of the diverse understandings of anthropomorphism}
+
+Naturally, conflicts in how terms are used lead to a diversity of understandings of the phenomenon which is described.
+One reason for this might be that anthropomorphism
+is a phenomenon that is studied in very different domains that might each
+integrate their own understanding, or simply use the same term to refer to different things.
+The conflict when reading about anthropomorphism is, that despite the fact that there is no commonly accepted definition, the terms
+\textit{anthropomorphism}, \textit{anthropomorphic} or \textit{human-like} are
+often used as if their meanings were clear and agreed upon
+\citep{persson_anthropomorphism_2000}. It is even
+argued that these terms might be misused \citep{duffy_anthropomorphism_2002,epley_when_2008}.
+For instance, some researchers refer to \textit{``the
+robot's level of anthropomorphism''} \cite{bartneck_is_2007}, whereas others
+disagree to such a statement because they understand that a system or artifact itself does not \textit{``contain anthropomorphism''} but only gives rise to the process of anthropomorphizing in a
+given user and situation. Consequently, \cite{persson_anthropomorphism_2000} conclude that
+anthropomorphism emerges in the \textit{interaction} between the technology and
+the user, and has to be understood as such \hl{(to which we will come back in the next section)}.
+
+Another paradox is that, while human's tendency to anthropomorphize is commonly observed, the phenomenon is 
+at the same time still rather poorly understood
+\cite{epley_seeing_2007}. The phenomenon itself has been found to be very complex though sometimes
+subtle and as such hard to study \cite{duffy_anthropomorphism_2002,epley_when_2008}.
+Further, it is not clear how to operationalize and measure anthropomorphism.
+We would like to discuss the challenges of studying and measuring anthropomorphism toward the end of this article, in Section \ref{sec:measuring}.
+
+%Anthropomorphism is used in different senses throughout different disciplines 
+%\citep{duffy_anthropomorphism_2003} which makes it difficult to synthesize findings. 
+Depending on which definition of anthropomorphism is applied, not everything 
+colloquially labeled as \emph{anthropomorphism} really is anthropomorphism.
+One practical example is that, it is not always clear whether a person (may it be an adult or 
+a child) who gives and anthropomorphic response, believes that the other agent really 
+thinks or acts like a human or whether she is using anthropomorphism in a metaphoric 
+sense \citep{leeds_childrens_1992}.
+Thus, we need to be clear about what we mean when talking about anthropomorphism.
+
+Several attempts have been made to clarify what anthropomorphism is (the phenomenon).
+From a psychology point of view \cite{epley_when_2008} try to clarify things by explaining what anthropomorphism is \textit{not}.
+For instance, in their understanding, anthropomorphism does not include behavioral descriptions of observable actions but it requires going beyond what is directly observable.
+It is further proposed that anthropomorphism does not merely entail \textit{animism}, as animate life is not a \textit{uniquely} human-like characteristic.\footnote{For the whole list and more details, the reader may refer to the original work \citep{epley_when_2008}.}
+
+%The authors list four effects that anthropomorphism does not include:
+%(1) First, anthropomorphism does not include behavioral descriptions of observable actions. Anthropomorphism requires going beyond what is directly observable.
+%(2) Second, anthropomorphism does not merely entail animism, as animate life is not a uniquely human-like characteristic.
+%(3) Third, anthropomorphism does not include any requirement of reasoned or reflective endorsement of an inference.\footnote{\hl{(the strength of anthropomorphic inferences can vary)}}
+%(4) Finally, anthropomorphism is not necessarily inaccurate.
+A psychological theory should take this (in)accuracy in anthropomorphism into account and predict variability in the tendency to perceive human-like traits in non-human agents.
+%% comment Julia: I commented this out because I think this is too complex and too much of detail here.
+
+As human-likeness itself is a huge dimension, some researchers argue that there might not just be one single type of anthropomorphism but different levels or gradations.
+For instance, \cite{persson_anthropomorphism_2000} proposes to understand anthropomorphism as a multi-layered phenomenon, and suggests that it exists of different levels, namely primitive categorization, primitive psychology, folk-psychology, traits, social roles, and emotional anthropomorphism.
+Correspondingly, \cite{ruijten_introducing_2014} propose to understand anthropomorphism as a continuum ranging from low to high human likeness, and to measure it as such (see Section \ref{sec:measuring}).
+
+\subsection{Terminology and understandings used in this article}
 
@@
 This would violate the understanding of anthropomorphism arising in an interaction.
-We propose to use the term  \textbf{anthropomorphic design} to refer to an imitation of human-like form in the \textit{form} of artificial agents.
-(In the following, we might use the terms \textit{form} and \textit{design} interchangeably.)
-
-In literature, this distinction is not always done, which is a major source of confusion.\\
-
-\begin{figure}
-    \centering
-    \includegraphics[width=0.75\columnwidth]{anthropo.pdf}
-    \caption{Anthropomorphism is a social phenomenon which arises in an interaction between a human agent and a non-human agent.
-The two agents are the main \textit{players} \hl{(or elements?)} of the interaction, and consequently one can apply two main perspectives when trying to explain anthropomorphism: a human-centered and an artifact-centered perspective (grey triangles).
-There are several person- and artifact-related factors that determine \hl{(or influence / impact on?)} anthropomorphism.
-Further, the context / situation in which the interaction occurs plays a role.}
-
-    \label{fig:anthropofig}
-\end{figure}
-
-As anthropomorphism arises in an interaction between a human and a non-human agent
-\citep{persson_anthropomorphism_2000}, one can also
-take two main \textit{perspectives} when trying to explain why humans anthropomorphize \citep{lee_human_2005}: an artifact-centered perspective and a human-centered perspective (see grey triangles in Figure \ref{fig:anthropofig}).
-
-We now first present an artifact-centered perspective, and outline how 
-robotics uses \textit{anthropomorphic design} to encourage 
-people to interact in a social, human-like way with robots.
-Then, we present a human-centered 
-perspective and shed light on \textit{anthropomorphism as a social phenomenon}. We present 
-theories from developmental psychology, cognitive science, and social psychology to explain people's tendency to 
-perceive human-like characteristics in non-human agents.
-It has to be kept in mind that both perspectives are inseparable; they apply at the 
-same time, and we would like to present them here just as two different viewpoints 
-on the same phenomenon.
-In the end of this section, we synthesize 
-the presented backgrounds into an extended understanding of anthropomorphism 
-as a multi-factor phenomenon.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-%
-%
-%		ARTIFACT-CENTERED PERSPECTIVE: ANTHROPOMORPHIC DESIGN
-%
-%
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{An artifact-centered perspective on anthropomorphism}
-\label{sec:anthropomorphic-design}
-
-An artifact-centered perspective explains anthropomorphism from the ascertainable 
-parts of the non-human agent, namely the anthropomorphic form of it.
-Using the term \textit{form} to describe the design of an artifact, we refer 
+To refer to an imitation of human-like form in the \textit{form} of artificial agents, we propose to use the term  \textbf{anthropomorphic design}.
+We found that in literature, this distinction is not always done, which is a major source of confusion.
+
+In the following, we might use the terms \textit{form} and \textit{design} interchangeably. Using the term \textit{form} to describe the design of an artifact, we refer 
 not only to the shape (how it looks like) but to the total 
@@
 anthropomorphic, zoomorphic, caricatured, functional \citep{fong_survey_2003}.
-The use of nature-inspired and in particular anthropomorphic (human-like) form in the 
-design of non-human things is as old and manifold as people's tendency to anthropomorphize. 
-Anthropomorphic (and life-like) forms have a long-standing tradition in design in general, and in the design of daily life things, in particular 
-\citep{norman_design_1988,guthrie_bottles_2000}. Interestingly, from its very
-beginning robots were resembling a human being in their appearance. Starting
-from when the term \textit{robot} first appeared in a play by Karel \^{C}apek in the 1920ies, robots were man-made beings, created as the \textit{``shadow of man''} \citep{replicant_????}.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.75\columnwidth]{anthropo.pdf}
+    \caption{Anthropomorphism is a social phenomenon which arises in an interaction between a human agent and a non-human agent.
+The two agents are the main \textit{players} \hl{(or elements?)} of the interaction, and consequently one can apply two main perspectives when trying to explain anthropomorphism: a human-centered and an artifact-centered perspective (grey triangles).
+There are several person- and artifact-related factors that determine \hl{(or influence / impact on?)} anthropomorphism.
+Further, the context / situation in which the interaction occurs plays a role.}
+
+    \label{fig:anthropofig}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+%
+%
+%		WHY DO HUMAN ANTHROPOMORPHIZE
+%
+%
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Why do humans anthropomorphize?}
+\label{sec:anthropomorphism}
+
+Anthropomorphism is an interesting phenomenon because it tells us something about 
+the relationship between the human who anthropomorphizes, and the non-human agent 
+which is anthropomorphized. Though commonly observed, it still appears controversial, at 
+the same time, that humans tend to \textit{``see human in the non-
+human''} \citep{epley_seeing_2007}.
+
+As anthropomorphism arises in an interaction between a human and a non-human agent
+\citep{persson_anthropomorphism_2000}, one can also
+take two main \textit{perspectives} when trying to explain why humans anthropomorphize \citep{lee_human_2005}: an artifact-centered perspective and a human-centered perspective (see grey triangles in Figure \ref{fig:anthropofig}).
+It has to be kept in mind that both perspectives are inseparable; they apply at the
+same time, and we would like to present them here just as two different viewpoints 
+on the same phenomenon.
+
+In the following we will only briefly present the artifact-centered perspective to explain anthropomorphism.
+Then, we provide a more detailed review and synthesis of literature that applies a human-centered perspective to explain anthropomorphism.
+Concretely, we integrate theories from developmental psychology, cognitive science / neuroscience, and social psychology to shed light on the question why humans anthropomorphize.
+
+\paragraph{Artifact-centered perspective on anthropomorphism}
+
+The artifact-centered perspective explains anthropomorphism from the ascertainable 
+parts of the non-human agent, namely the anthropomorphic form of it.
+This research deals with the question how far anthropomorphism can be explained from the design of the artifact.
+Consequently, it is studied how humans perceive and respond to different types of human-like designs of non-human agents.
+One of the most prominent working hypothesis in this research branch is the Uncanny Valley hypothesis \citep{mori_uncanny_1970}.
+In general, it is proposed that human-like designs of robots can evoke both positive and negative feelings in a human user.
 
@@
 \cite{takayama_perspectives_2012} propose to refer to this immediate (sometimes visceral) sense in a situation as \textit{in-the-moment}, compared to a more distanced cogitation and consideration which she calls \textit{reflective}.
-(As this distinction implies different cognitive processes, we will come back to it later, in the human-centered perspective, Section \ref{sec:human-centered}).
-
-The view of people mindlessly reacting in a human-social manner to anthropomorphic forms
-is based on the fact that humans naturally react to specific 
-cues. From early childhood 
-on, humans are inherently well-trained to perceive life \citep{epley_seeing_2007}, 
-or to respond to social cues, such as facial expressions, social gestures or turn-taking.
+As this distinction implies different cognitive processes, we will come back to it later, in section \ref{sec:cognitive-expl}.
+
+%\subsection{An artifact-centered perspective on anthropomorphism}
+%\label{sec:anthropomorphic-design}
+%
+%An artifact-centered perspective 
+%
+%The use of nature-inspired and in particular anthropomorphic (human-like) form in the 
+%design of non-human things is as old and manifold as people's tendency to anthropomorphize. 
+%Anthropomorphic (and life-like) forms have a long-standing tradition in design in general, and in the design of daily life things, in particular 
+%\citep{norman_design_1988,guthrie_bottles_2000}. Interestingly, from its very
+%beginning robots were resembling a human being in their appearance. Starting
+%from when the term \textit{robot} first appeared in a play by Karel \^{C}apek in the 1920ies, robots were man-made beings, created as the \textit{``shadow of man''} \citep{replicant_????}.
+
+%The view of people mindlessly reacting in a human-social manner to anthropomorphic forms
+%is based on the fact that humans naturally react to specific 
+%cues. From early childhood 
+%on, humans are inherently well-trained to perceive life \citep{epley_seeing_2007}, 
+%or to respond to social cues, such as facial expressions, social gestures or turn-taking.
 Humans have a propensity toward particular cues that seem to trigger automatic interpersonal social responses \citep{takayama_perspectives_2012}.
-One has to keep in mind that in 
-human-human interaction these cues are of various senses and modalities, 
-and consequently human-like design is also realized addressing several senses. 
-One of the most outstanding aspects is probably the outer appearance of an agent or 
-artifact (in particular when it is unknown or unfamiliar). \cite{schmitz_concepts_2011} 
-argues that an agent's outer appearance is likely to have an important impact on how 
-the object is overall perceived. Consequently, if a robot's outer form resembles a 
-human, the robot is likely to be treated similar to a human.
+%One has to keep in mind that in 
+%human-human interaction these cues are of various senses and modalities, 
+%and consequently human-like design is also realized addressing several senses. 
+%One of the most outstanding aspects is probably the outer appearance of an agent or 
+%artifact (in particular when it is unknown or unfamiliar). \cite{schmitz_concepts_2011} 
+%argues that an agent's outer appearance is likely to have an important impact on how 
+%the object is overall perceived. Consequently, if a robot's outer form resembles a 
+%human, the robot is likely to be treated similar to a human.
 Besides the physical shape of a robot, other more subtle anthropomorphic forms can be found in robots, including human-social behavioral cues (\eg eye-gaze), social gestures (\eg waving), or verbal politeness (\eg greeting, apologizing).
-
-People's natural reaction to these and other anthropomorphic design cues of
-robots (in particular, social or also called \textit{sociable} robots 
-\citep{breazeal_sociable_2000}) are extensively studied.
+%
+%People's natural reaction to these and other anthropomorphic design cues of
+%robots (in particular, social or also called \textit{sociable} robots 
+%\citep{breazeal_sociable_2000}) are extensively studied.
 This research is of particular interest in human-robot interaction as the consequences of anthropomorphic design can be both of positive and negative nature, and it is yet not clear what exactly it is that makes the difference.
-
-\subsubsection{How people perceive and interact with human-like robots\\}
-\label{sec:anthropomorphism-robotics}
-
-Most work that studies how far human users treat robots as social agents, builds on the 
-famous work of \cite{reeves_media_1996} in HCI. In the so-called \textit{Media 
-Equation}, the authors describe that people mindlessly react in a social way to their computer 
-and that they tend to even attribute human (social) characteristics to it -- despite 
-the fact that a computer does not have human-like characteristics. Apart from 
-computers, anthropomorphism has also been observed with digital / virtual characters 
-\citep{von_der_putten_it_2010}, and artificial embodied agents, 
-such as robots \citep{rosenthal-vonderputten_experimental_2013}. 
-In short, one can say that with robots, and human-like robots in 
-particular, anthropomorphism is a commonly observed phenomenon. 
-But what are the motivations which underlie the efforts of enhancing anthropomorphism 
-through specific anthropomorphic design in robots? Why are anthropomorphic forms so 
-distinct and at the same time controversial in robotics? There is no one single answer 
-to these questions.
-
-The underlying central point about the human-like design of robots lies in the 
-implications that this design holds, and the suggestions for interactions that
-it makes to the human user. 
-In other words, the appearance 
-and function of a product, whether it is an appliance or a humanoid robot, affects how 
-people perceive it, interact with it, and build long-term relationships with 
-it \citep{bartneck_shaping_2004}. 
-The principle of human-like form is probably most prominent in the design of robots, 
-due to several reasons, such as to foster efficient interaction and increase 
-acceptance. An anthropomorphic design of a robot encourages people to reason about this 
-unfamiliar system \emph{as if} it was a human. To increase this tendency, robots are 
-designed with anthropomorphic (or lifelike) forms, or are able to display and use 
-human-social cues when interacting with humans.
-However, anthropomorphic robot designs have been controversially discussed and received 
-remarkable attention since the early 1970ies, related to Mori's
-theory of the \textit{Uncanny Valley} \citep{mori_uncanny_1970}.
-%see Figure \ref{fig:uncanny_valley}.
-
-%\begin{figure}\centering
-%% Use the relevant command to insert your figure file.
-%% For example, with the graphicx package use
-%  \includegraphics[scale=0.75]{uncanny-valley.jpg}
-%% figure caption is below the figure
-% \caption{Mashiro Mori, illustration of the \textit{Uncanny Valley} hypothesis.
+%
+%
+%\subsubsection{How people perceive and interact with human-like robots\\}
+%\label{sec:anthropomorphism-robotics}  
+% 
+%Most work that studies how far human users treat robots as social agents, builds on the 
+%famous work of \cite{reeves_media_1996} in HCI. In the so-called \textit{Media 
+%Equation}, the authors describe that people mindlessly react in a social way to their computer 
+%and that they tend to even attribute human (social) characteristics to it -- despite 
+%the fact that a computer does not have human-like characteristics. Apart from 
+%computers, anthropomorphism has also been observed with digital / virtual characters 
+%\citep{von_der_putten_it_2010}, and artificial embodied agents, 
+%such as robots \citep{rosenthal-vonderputten_experimental_2013}. 
+%In short, one can say that with robots, and human-like robots in 
+%particular, anthropomorphism is a commonly observed phenomenon. 
+%But what are the motivations which underlie the efforts of enhancing anthropomorphism 
+%through specific anthropomorphic design in robots? Why are anthropomorphic forms so 
+%distinct and at the same time controversial in robotics? There is no one single answer 
+%to these questions. 
+% 
+%The underlying central point about the human-like design of robots lies in the 
+%implications that this design holds, and the suggestions for interactions that
+%it makes to the human user. 
+%In other words, the appearance 
+%and function of a product, whether it is an appliance or a humanoid robot, affects how 
+%people perceive it, interact with it, and build long-term relationships with 
+%it \citep{bartneck_shaping_2004}. 
+%The principle of human-like form is probably most prominent in the design of robots, 
+%due to several reasons, such as to foster efficient interaction and increase 
+%acceptance. An anthropomorphic design of a robot encourages people to reason about this 
+%unfamiliar system \emph{as if} it was a human. To increase this tendency, robots are 
+%designed with anthropomorphic (or lifelike) forms, or are able to display and use 
+%human-social cues when interacting with humans.
+%However, anthropomorphic robot designs have been controversially discussed and received 
+%remarkable attention since the early 1970ies, related to Mori's
+%theory of the \textit{Uncanny Valley} \citep{mori_uncanny_1970}.
+%%see Figure \ref{fig:uncanny_valley}.
+%
+%%\begin{figure}\centering
+%%% Use the relevant command to insert your figure file.
+%%% For example, with the graphicx package use
+%%  \includegraphics[scale=0.75]{uncanny-valley.jpg}
+%%% figure caption is below the figure
+%% \caption{Mashiro Mori, illustration of the \textit{Uncanny Valley} hypothesis.
 The curve models the user's perceived affinity with the artifact, as its human likeness is increased.
@@
 Originally from 1970; picture from a manuscript version of \cite{mori_uncanny_2012}}
-% \label{fig:uncanny_valley}       % Give a unique label
-% \end{figure}
-
-Despite the fact that the Uncanny Valley theory was more a working hypothesis and not 
-meant to be empirically examined \citep{cheetham_human_2011}, it has been studied quite 
-extensively. However, results are inconsistent. We try to give a short overview (not 
-exclusive) on work related to HRI and robotics in the following.
-
-\subsubsection{Anthropomorphic form can be advantageous for HRI\\}
-
-On one hand, developers and designers have discovered that human-like robots may better 
-match the affordances that this to humans adapted world brings along. 
-Apart from this, it is suggested that an increased human-likeness of a robot (up to a 
-certain threshold) will generally lead to 
-more perceived \textit{affinity} from the human side \citep{mori_uncanny_1970}.
-% (see Figure \ref{fig:uncanny_valley}).
-This further increases anthropomorphism, and as such
-appears to be beneficial for human-robot relations, especially with socially 
-interactive robots \citep{fong_survey_2003}. Consequently, the domain of (social) 
-robotics tries to exploit this by using
-anthropomorphic forms in robots.
-Humans seem to readily accept and prefer the 
-anthropomorphic form of a robot (up to a certain point), when compared to purely mechanical 
-robots. A possible explanation for this is that perceiving a system as
-human-like (or also pet-like) compared to machine-like changes the 
-way how users try to understand and make sense of this system. The reason for this is 
-that humans tend to project everyday 
-expectations of human and animalistic life onto artificial agents that use 
-anthropomorphic (or zoomorphic) forms \citep{schmitz_concepts_2011}. 
-Both cognitive science 
-and social psychology can provide explanations for this process of projection. The basic idea 
-is that \textit{"the more similar in 
-appearance, the more people are likely to use themselves as a source of induction 
-and anthropomorphize these nonhuman agents"} \citep{epley_seeing_2007}. Studies have further 
-shown that perceived similarity between the user and the robot influences the intensity of 
-the participants' attributions towards the robot. Thus, the anthropomorphic design of a robot 
-impacts the user's perception of the robot, and how far the user is likely to attribute and 
-experience qualities such as intelligence, fun, or intentions in the robot. 
-These experiences mark the transition between an immediate \textit{in-the-moment} and more thoughtful \textit{reflective} \citep{takayama_perspectives_2012} perception of, and interaction with the robot.
+%% \label{fig:uncanny_valley}       % Give a unique label
+%% \end{figure}
+%
+%Despite the fact that the Uncanny Valley theory was more a working hypothesis and not 
+%meant to be empirically examined \citep{cheetham_human_2011}, it has been studied quite 
+%extensively. However, results are inconsistent. We try to give a short overview (not 
+%exclusive) on work related to HRI and robotics in the following. 
+% 
+% 
+%\subsubsection{Anthropomorphic form can be advantageous for HRI\\}
+%
+%On one hand, developers and designers have discovered that human-like robots may better 
+%match the affordances that this to humans adapted world brings along. 
+%Apart from this, it is suggested that an increased human-likeness of a robot (up to a 
+%certain threshold) will generally lead to 
+%more perceived \textit{affinity} from the human side \citep{mori_uncanny_1970}.
+%% (see Figure \ref{fig:uncanny_valley}).
+%This further increases anthropomorphism, and as such
+%appears to be beneficial for human-robot relations, especially with socially 
+%interactive robots \citep{fong_survey_2003}. Consequently, the domain of (social) 
+%robotics tries to exploit this by using
+%anthropomorphic forms in robots.
+%Humans seem to readily accept and prefer the 
+%anthropomorphic form of a robot (up to a certain point), when compared to purely mechanical 
+%robots. A possible explanation for this is that perceiving a system as
+%human-like (or also pet-like) compared to machine-like changes the 
+%way how users try to understand and make sense of this system. The reason for this is 
+%that humans tend to project everyday 
+%expectations of human and animalistic life onto artificial agents that use 
+%anthropomorphic (or zoomorphic) forms \citep{schmitz_concepts_2011}. 
+%Both cognitive science 
+%and social psychology can provide explanations for this process of projection. The basic idea 
+%is that \textit{"the more similar in 
+%appearance, the more people are likely to use themselves as a source of induction 
+%and anthropomorphize these nonhuman agents"} \citep{epley_seeing_2007}. Studies have further 
+%shown that perceived similarity between the user and the robot influences the intensity of 
+%the participants' attributions towards the robot. Thus, the anthropomorphic design of a robot 
+%impacts the user's perception of the robot, and how far the user is likely to attribute and 
+%experience qualities such as intelligence, fun, or intentions in the robot. 
+%These experiences mark the transition between an immediate \textit{in-the-moment} and more thoughtful \textit{reflective} \citep{takayama_perspectives_2012} perception of, and interaction with the robot.
 As this distinction is also based on different cognitive processes, a more human-centered / cognitive perspective needs to be applied here, and we will treat this in Section \ref{sec:human-centered}.
-
-In short, the central point in using anthropomorphic design in sociable robots is that 
-humans tend to apply the same communication references to anthropomorphic robots 
-that they would use with other humans, which in turn enhances feeling familiar and 
-comfortable when interacting with the otherwise unknown system.
-This positive effect has been shown in various 
-empirical studies. It has been found that robots with human-like forms can enhance social 
-responses from humans which in turn can positively impact on acceptance 
-\citep{duffy_anthropomorphism_2003,goetz_cooperation_2002,venkatesh_theoretical_2000}. 
-People responded more positively to an artifact that displayed human-like 
-behavioral characteristics (emotions, facial expression) in contrast to a purely 
-functional design 
-\citep{eyssel_anthropomorphic_2010,krach_can_2008,reeves_media_1996,riek_how_2009}. 
-Overall, these results suggest that human-like features in robots enhance 
-anthropomorphism, and in turn create a social view toward the robot.
-
-%Anthropomorphism represents just one of many examples of induction whereby "people reason about an unknown stimulus based on a better-known representation of a related stimulus" \cite{epley_when_2008}, in this case reasoning about a non-human agent based on representation of the self or other humans.
-
-\subsubsection{Anthropomorphic form can be disadvantageous for HRI\\}
-
-The anthropomorphic form also 
-increases people's expectations of the agent, and consequently, a very human-like 
-appearing robot is not only perceived but also expected to act like a human. However, today's artificial systems are 
-not able (yet) to mimic well human movements, or human social cues in an acceptable way. 
-The case is that the artificial agent pretends to be human but fails, and this is 
-more than just disappointing for the 
-human -- it appears uncanny and evokes reluctance, the so-called 
-\textit{"uncanny valley"}. The idea of naming this shift and drop from a positive to a negative reaction,
-follows Freud's description of the so-called \textit{uncanny} (a translation from the German word 
-\textit{``unheimlich''}). Controversially, something uncanny \textit{"derives its terror not from 
-something externally alien or unknown but -- on the contrary -- from something 
-strangely familiar which defeats our efforts to separate ourselves from it"} (v. Foerster, cited after \cite{hegel_understanding_2008}).
-In other words, humans are very sensitive to the limits of what is familiar to them 
-in a sense of being human. At the same time, humans are naturally very skilled when 
-it comes to identifying what is acceptable as a human and what is an imitation 
-of it. Even subtle differences can be crucial -- humans are inherently well trained 
-in identifying if there is \hl{``something strange''} in the familiar.
-Summing it up, a not yet very well defined thin line separates acceptable human-like forms in 
-robots from creepy artificial \textit{almost} human-like appearing robots.
-
-Of course, there is no one good answer to the question how to not fall in the 
-uncanny valley when designing an anthropomorphic system. Equipping a system with 
-some anthropomorphic forms seems to be inevitable 
-\cite{duffy_anthropomorphism_2002} in the advancement of human-machine interfaces 
-and sociable robots \citep{breazeal_sociable_2000}. However, we agree that 
-\textit{"the important criterion is to seek a balance between people's expectations 
-and the machines capabilities"} \citep{duffy_anthropomorphism_2002}.
+%
+%In short, the central point in using anthropomorphic design in sociable robots is that 
+%humans tend to apply the same communication references to anthropomorphic robots 
+%that they would use with other humans, which in turn enhances feeling familiar and 
+%comfortable when interacting with the otherwise unknown system.
+%This positive effect has been shown in various 
+%empirical studies. It has been found that robots with human-like forms can enhance social 
+%responses from humans which in turn can positively impact on acceptance 
+%\citep{duffy_anthropomorphism_2003,goetz_cooperation_2002,venkatesh_theoretical_2000}. 
+%People responded more positively to an artifact that displayed human-like 
+%behavioral characteristics (emotions, facial expression) in contrast to a purely 
+%functional design 
+%\citep{eyssel_anthropomorphic_2010,krach_can_2008,reeves_media_1996,riek_how_2009}. 
+%Overall, these results suggest that human-like features in robots enhance 
+%anthropomorphism, and in turn create a social view toward the robot.
+%
+% 
+%%Anthropomorphism represents just one of many examples of induction whereby "people reason about an unknown stimulus based on a better-known representation of a related stimulus" \cite{epley_when_2008}, in this case reasoning about a non-human agent based on representation of the self or other humans.
+%
+%
+%\subsubsection{Anthropomorphic form can be disadvantageous for HRI\\}
+%
+%The anthropomorphic form also 
+%increases people's expectations of the agent, and consequently, a very human-like 
+%appearing robot is not only perceived but also expected to act like a human. However, today's artificial systems are 
+%not able (yet) to mimic well human movements, or human social cues in an acceptable way. 
+%The case is that the artificial agent pretends to be human but fails, and this is 
+%more than just disappointing for the 
+%human -- it appears uncanny and evokes reluctance, the so-called 
+%\textit{"uncanny valley"}. The idea of naming this shift and drop from a positive to a negative reaction,
+%follows Freud's description of the so-called \textit{uncanny} (a translation from the German word 
+%\textit{``unheimlich''}). Controversially, something uncanny \textit{"derives its terror not from 
+%something externally alien or unknown but -- on the contrary -- from something 
+%strangely familiar which defeats our efforts to separate ourselves from it"} (v. Foerster, cited after \cite{hegel_understanding_2008}).
+%In other words, humans are very sensitive to the limits of what is familiar to them 
+%in a sense of being human. At the same time, humans are naturally very skilled when 
+%it comes to identifying what is acceptable as a human and what is an imitation 
+%of it. Even subtle differences can be crucial -- humans are inherently well trained 
+%in identifying if there is \hl{``something strange''} in the familiar.
+%Summing it up, a not yet very well defined thin line separates acceptable human-like forms in 
+%robots from creepy artificial \textit{almost} human-like appearing robots.
+%
+% 
+%Of course, there is no one good answer to the question how to not fall in the 
+%uncanny valley when designing an anthropomorphic system. Equipping a system with 
+%some anthropomorphic forms seems to be inevitable 
+%\cite{duffy_anthropomorphism_2002} in the advancement of human-machine interfaces 
+%and sociable robots \citep{breazeal_sociable_2000}. However, we agree that 
+%\textit{"the important criterion is to seek a balance between people's expectations 
+%and the machines capabilities"} \citep{duffy_anthropomorphism_2002}.
 
@@
 
-\subsection{A human-centered perspective on anthropomorphism}
-\label{sec:human-centered}
+%\subsection{A human-centered perspective on anthropomorphism}
+%\label{sec:human-centered}
 
@@
 Humans tend to perceive human-like characteristics such as physical appearance, emotional states, or inner mental states and motivations in non-human agents that do not have these characteristics themselves, such as animals, natural forces, religious agents, technological gadgets, or mechanical devices \citep{epley_when_2008}.\footnote{According to \cite{epley_when_2008}, a non-human agent can be anything that acts -- or is believed to act -- with apparent independence.}  Anthropomorphism has received remarkable attention across various different domains, such as natural sciences, developmental and social psychology, Human-Computer Interaction (HCI), and Human-Robot Interaction (HRI).
-
-Originally, the term \textbf{anthropomorphism} comes from the Greek \textit{`anthropos'} for `man' (or `human') and \textit{`morphe'} for `form / structure' (or `shape').
-Anthropomorphism is generally understood as people's tendency to perceive a non-human agent as if it had some human characteristics or traits.
-In turn, how a person perceives an agent further determines how she relates to and behaves towards the agent, or how she may behave in light of this agent \citep{epley_when_2008}.
-As such, anthropomorphism can be seen as a special kind of relationship between a human interacting with a non-human agent.
-This anthropomorphic relationship is often characterized by the fact that the human attributes human-unique characteristics to the non-human agent.
-Since anthropomorphism becomes observable through these attributions, some definitions claim that anthropomorphism is not the perception but rather the attribution of human attributes to non-human agents, and name thoughts, emotions, and intentions as examples.
-The most prominently anthropomorphized non-human agents are probably animals and robots \citep{duffy_anthropomorphism_2003,schmitz_concepts_2011}.
-
-Apart from anthropomorphism there also exists the term \textbf{animism}, which can be defined as the attribution of life to the nonliving.
-The study of animism was pioneered by Piaget in the 1920s with his work on \textit{The Child's Conception of the  World}.
-He found that children tend to regard many inanimate objects as capable of sensations, emotions and intentions, and called this view `animism'.
-Since then, children's inferences about the world have been studied intensively.
-However, there is an agreement that children's views and concepts of living, animal, and plant evolve as they grow up.
-Using this definition, animism differs in two main aspects from anthropomorphism:
-First, the property which is ascribed differs: life-likeness is not human-unique but applies to all living beings.
-The second difference between anthropomorphism and animism stems from the agent (or better artifact) to which life is attributed.
-Living beings (most importantly animals) are naturally excluded from being animized.
-Consequently, while animals can be anthropomorphized (perceived to have human unique characteristics), they cannot be animized as they are already living beings.
-(Similarly to the fact that humans cannot be anthropomorphized as they are already humans.)
-Often synonymously used to animism is the term \textbf{zoomorphism}, which applies to the cases when non-lifelike instances / things are associated with animalistic attributes, excluding human-specific traits.
-Both anthropomorphism and animism / zoomorphism can be embraced by the concept of \textbf{life-likeness}.
-
-To illustrate better how anthropomorphism differs from attributions of animacy or life-
-likeness, it is worth looking at paraphrases and examples of it. That is to say, 
-anthropomorphism can alternatively be understood as \textbf{humanization} or 
-\textbf{personification} of anything other than a human being. Personification has 
-ancient roots, \eg in mythology but also in storytelling. For instance, anthropomorphism was also 
-used to describe and be able to predict natural forces or anticipate great spirits.
-
-There exists also the inverse phenomenon to anthropomorphism, which can be found in the literature as \textbf{dehumanization} \citep{haslam_dehumanization:_2006}, or \textbf{mechanomorphism} \citep{caporael_anthropomorphism_1986}.
-We do not treat this here.
 
@@
 
-\paragraph{Developmental psychology research on the attribution of animacy and intention\\}
+\subsection{Developmental psychology research on the attribution of animacy and intention}
+\label{sec:developmental-expl}
 
@@
 
-\paragraph{Cognitive science research, the mental model theory (Theory of Mind)
-and neural correlates of anthropomorphism\\}
+\subsection{Cognitive science research, the mental model theory (Theory of Mind)
+and neural correlates of anthropomorphism}
+\label{sec:cognitive-expl}
 
@@
 
-\paragraph{Social psychology research: a 3-factor theory of anthropomorphism\\}
+\subsection{Social psychology research: a 3-factor theory of anthropomorphism}
 \label{sec:psychological-factors}
@@
 Thus, the motivation of being socially connected increases the tendency to anthropomorphize non-human agents because first sociality motivation increases the tendency to perceive human-like characteristics and traits even in non-human agents, and second it increases the tendency to search for sources of social connection in one's environment.
-
-\subsubsection{Diverse understandings of anthropomorphism and confusions in the terminology used\\}
-
-We have seen that literature on anthropomorphism is quite diverse. We would like to point out that there exist different understandings of what anthropomorphism is. 
-One reason for this might be that anthropomorphism
-is a concept that is studied in very different domains that might each
-integrate diverse or even contradictory understandings, or simply refer to different things.
-However, the conflict is, that despite the fact that there is no commonly accepted definition, the terms
-\textit{anthropomorphism}, \textit{anthropomorphic} or \textit{human-like} are
-often used as if their meanings were clear and agreed upon
-\citep{persson_anthropomorphism_2000}. Duffy \cite{duffy_anthropomorphism_2002} and \cite{epley_when_2008}
-argue that these terms might even be misused. For instance, some researchers refer to \textit{"the
-robot's level of anthropomorphism"} \cite{bartneck_is_2007}, whereas others
-disagree to such a statement because they argue that the system or artifact itself does not \textit{"contain anthropomorphism" per se} but only gives rise to the process of anthropomorphizing in a
-given user and situation. Consequently, \cite{persson_anthropomorphism_2000} conclude that
-anthropomorphism emerges in the \textit{interaction} between the technology and
-the user, and has to be understood as such. 
-We will come back to this view later, in the summary of this section (Subsection \ref{sec:multi-factors}).
-
-Another paradox is that, while human's tendency to anthropomorphize is commonly observed, it is 
-at the same time still rather poorly understood
-\cite{epley_seeing_2007}. The phenomenon itself has been found to be very complex though sometimes
-subtle and as such hard to study \cite{epley_when_2008,duffy_anthropomorphism_2002}.
-Further, it is not clear how to operationalize anthropomorphism.
-We would like to discuss the challenges of studying and measuring anthropomorphism toward the end of this article, in Section \ref{sec:measuring}.
-
-%Anthropomorphism is used in different senses throughout different disciplines 
-%\citep{duffy_anthropomorphism_2003} which makes it difficult to synthesize findings. 
-Depending on which understanding of anthropomorphism is applied, not everything 
-colloquially labeled as \emph{anthropomorphism} really is anthropomorphism.
-One practical example is that, it is not always clear whether a person (may it be an adult or 
-a child) who gives and anthropomorphic response, believes that the other agent really 
-thinks or acts like a human or whether she is using anthropomorphism in a metaphoric 
-sense.\citep{leeds_childrens_1992}.
-Thus, we need to be clear about what we mean by anthropomorphism.
-
-But how to clarify the understanding of anthropomorphism?
-From a psychology point of view \cite{epley_when_2008} try to clarify anthropomorphism by explaining what it is \textit{not}, and we think this approach could also help researchers in HRI and robotics.
-\cite{epley_when_2008} list four effects that anthropomorphism does not include:
-(1) First, anthropomorphism does not include behavioral descriptions of observable actions. Anthropomorphism requires going beyond what is directly observable.
-(2) Second, anthropomorphism does not merely entail animism, as animate life is not a uniquely human-like characteristic.
-(3) Third, anthropomorphism does not include any requirement of reasoned or reflective endorsement of an inference.\footnote{\hl{(the strength of anthropomorphic inferences can vary)}}
-(4) Finally, anthropomorphism is not necessarily inaccurate.
-A psychological theory should take this (in)accuracy in anthropomorphism into account and predict variability in the tendency to perceive human-like traits in non-human agents.\footnote{For more details, the reader may refer to the original work \citep{epley_when_2008}.}
-
-Similarly to the last point mentioned by \cite{epley_when_2008}, several researchers argue that there might not just be one single type of anthropomorphism but different levels or gradations.
-For instance, \cite{persson_anthropomorphism_2000} proposes to understand anthropomorphism as a multi-layered phenomenon, and suggests that it exists of different levels, namely primitive categorization, primitive psychology, folk-psychology, traits, social roles, and emotional anthropomorphism.
-Correspondingly, \cite{ruijten_introducing_2014} propose to understand anthropomorphism as a continuum ranging from low to high human likeness, and to measure it as such.
 

### 2014-04-02 paper.tex
resolving the artifact- and human-centered section lenght conflict

@@
 
-\paragraph{Artifact-centered perspective on anthropomorphism}
+\paragraph{Artifact-centered perspective on anthropomorphism\\}
 
@@
 \cite{takayama_perspectives_2012} propose to refer to this immediate (sometimes visceral) sense in a situation as \textit{in-the-moment}, compared to a more distanced cogitation and consideration which she calls \textit{reflective}.
-As this distinction implies different cognitive processes, we will come back to it later, in section \ref{sec:cognitive-expl}.
+As this distinction implies different cognitive processes, it is more approriate to apply a human-centered perspective and we will come back to it later, in section \ref{sec:cognitive-expl}.
 
@@
 
-In contrast to the artifact-centered perspective, in the human-centered perspective the argumentation is, that the human is motivated to anthropomorphize the non-human artifact).
+\paragraph{Human-centered perspective on anthropomorphism}
+
+In contrast to the artifact-centered perspective, in the human-centered perspective the argumentation is, that the human is motivated to anthropomorphize the non-human artifact.
 As already mentioned, both these views go hand in hand.
 
-Humans tend to perceive human-like characteristics such as physical appearance, emotional states, or inner mental states and motivations in non-human agents that do not have these characteristics themselves, such as animals, natural forces, religious agents, technological gadgets, or mechanical devices \citep{epley_when_2008}.\footnote{According to \cite{epley_when_2008}, a non-human agent can be anything that acts -- or is believed to act -- with apparent independence.}  Anthropomorphism has received remarkable attention across various different domains, such as natural sciences, developmental and social psychology, Human-Computer Interaction (HCI), and Human-Robot Interaction (HRI).
+Humans tend to perceive human-like characteristics such as physical appearance, emotional states, or inner mental states and motivations in non-human agents that do not have these characteristics themselves, such as animals, natural forces, religious agents, technological gadgets, or mechanical devices \citep{epley_when_2008}.\footnote{According to \cite{epley_when_2008}, a non-human agent can be anything that acts -- or is believed to act -- with apparent independence.}
+One common reason for anthropomorphism is that by perceiving some human-like characteristics in the non-human agent, this agent is made more \emph{graspable}, \emph{understandable}, \emph{predictable}, and one can feel \emph{more empathetic} toward it, and possibly one can then anticipate the agent's behavior.
+These are central motivations when trying to explain anthropomorphism, and we will come back to them in more detail later on.
+It is described that for the just mentioned reasons, people commonly anthropomorphize their pets, by ascribing mental states, intentions or feelings to them\footnote{Interestingly, pet-ownership seems to have a significant impact on human-robot interaction: several studies suggest that pet-owners are more likely to anthropomorphize technologies and robots than non pet-owners} \cite{eddy_attribution_1993}.
+But how can these motivations behind anthropomorphism be explained from a human-centered point of view?
+
+In the following, we present what we found in reviewing literature that applies a human-centered perspective on anthropomorphism by building on:
+\textit{(1)} a line of research in developmental psychology that studies the attribution of animacy;
+\textit{(2)} a line of research in more cognitive sciences that studies the cognitive processes that underlie anthropomorphism, and
+\textit{(3)} a theory that explains anthropomorphism based on psychological factors.
 
@@
 
-\subsubsection{Why do people anthropomorphize?\\}
-\label{sec:explanations}
-
-But why do people anthropomorphize?
+%\subsubsection{Why do people anthropomorphize?\\}
+%\label{sec:explanations}
+
+%But why do people anthropomorphize?
 First and foremost, it needs to be mentioned that anthropomorphism is a fairly complex phenomenon.
 Paradoxically, there is a huge and diverse body of literature on it but nevertheless, it seems that anthropomorphism is still not very well understood (especially in a field as young as HRI).
-
-One common reason for anthropomorphism is that by perceiving some human-like characteristics in the non-human agent, this agent is made more \emph{graspable}, \emph{understandable}, \emph{predictable}, and one can feel \emph{more empathetic} toward it, and possibly one can then anticipate the agent's behavior.
-These are central motivations when trying to explain anthropomorphism, and we will come back to them in more detail later on.
-It is described that for the just mentioned reasons, people commonly anthropomorphize their pets, by ascribing mental states, intentions or feelings to them\footnote{Interestingly, pet-ownership seems to have a significant impact on human-robot interaction: several studies suggest that pet-owners are more likely to anthropomorphize technologies and robots than non pet-owners} \cite{eddy_attribution_1993}.
-But how can these motivations behind anthropomorphism be explained from a human-centered point of view?
 
@@
 It has to be kept in mind that both perspectives are inseparable; they apply at the same time, and we would like to present them here just as two different viewpoints on the same kind of phenomenon.
-
-This perspective builds on research from developmental and social psychology as well as cognitive sciences.
-In the following, we present what we found in reviewing this literature: (1) a line of research in developmental psychology that studies the attribution of animacy; (2) a line of research in more cognitive sciences that studies the cognitive processes that underlie anthropomorphism, and (3) a theory that explains anthropomorphism based on psychological factors~\citep{epley_seeing_2007}.
-All three branches apply a human-centered perspective on anthropomorphism.
 

### 2014-04-02 paper.tex
started working on summary of section 3 (first 2)

@@
 Summing it up, anthropomorphism is a commonly discussed and
-studied trait of human-robot interaction; however its current understanding seems to be stuck in a twofold consideration. Mostly, only two key factors are recognized: the
-characteristics of \textbf{1) the robot's design} (degree of human-likeness) and
-the psychological determinants in \textbf{2) the human user} (see
-\cite{epley_seeing_2007}). A lot of research has shown that both these factors can
-promote or hinder anthropomorphism.
-However, anthropomorphism is a complex process and we think that the current understanding of it does neither seem to fully take into account the wide range of phenomena that it encompasses, nor the multiplicity of factors which determine it.
-This shortcoming and conflict in the understanding of anthropomorphism in HRI has already been denoted by others but we would like to take a first step towards moving forward in this dilemma, and encourage an open dialogue to solve this.
-
-Through applying an understanding that anthropomorphism represents a specific type of \textit{experience} that arises in the
-\textit{interaction} between a set of user expectations and external reality, 
+studied trait of human-robot interaction; however its current understanding seems to be stuck.
+More concretely, when seeking to understand why anthropomorphism in an interaction between a human and a non-human artifact happens, most attention is given to the artifact and/or to the human.
+We agree that these two are the essential `players' of anthropomorphism (see Figure \ref{fig:anthropofig}).
+Indeed and, as outlined before, research has shown that both the human and the artifact are not only the two players of anthropomorphism but also the two main `factors' that can promote or hinder anthropomorphism.
+
+However, we think that this is not the full story. When agreeing to understand anthropomorphism as a specific type of \textit{experience} that arises in an
+\textit{interaction} between a set of user expectations and the external reality, 
 %(see Figure~\ref{fig:anthropomorphism_and_interaction})
-we propose that
+it becomes clear that this interaction happens in a specific context, with a specific history.
+We think that the context and the history of the interaction (in Figure \ref{fig:factors} denoted as \textit{time}), are two more factors that determine anthropomorphism.
+
+Consequently, we propose a holistic understanding of anthropomorphism as a phenomenon which is determined by multiple factors:
+
+\begin{enumerate}
+
+\item ~the \textbf{characteristics of the robot's design} (degree of anthropomorphic form),
+\item ~the \textbf{psychological determinants in the human user} (see
+\cite{epley_seeing_2007}),
+\item ~the \textbf{characteristics of the context} (situation) in which the interaction occurs, and
+\item ~the fact of the user getting \textbf{familiar with the robot over time} (getting used to a system the more and longer one interacts with it)
+
+\end{enumerate}
+
+Further, we propose that
 anthropomorphism is a multi-layered phenomenon which arises in different levels \citep{persson_anthropomorphism_2000}, and which is likely to evolve with continued interaction.
+
+%However, anthropomorphism is a complex process and we think that the current understanding of it does neither seem to fully take into account the wide range of phenomena that it encompasses, nor the multiplicity of factors which determine it.
+%This shortcoming and conflict in the understanding of anthropomorphism in HRI has already been denoted by others but we would like to take a first step towards moving forward in this dilemma, and encourage an open dialogue to solve this.
+
 %we suggest to understand anthropomorphism as a \emph{dynamic},
@@
 %environment and provide an account of the so-called \textit{novelty effect}.
-
-To this end, and in respect of our research hypotheses, we make the following two suggestions:
-
-First, we propose to include two more main factors as determinants of anthropomorphism (besides the robot's design, and the human user's characteristics).
-Namely, these factors are \textbf{3) the context of use} (situation) and the fact of getting used to a system the more and longer one interacts with it, thus becoming familiar with the system over \textbf{4) time}.
 
@@
 How far people tend to anthropomorphize a robot is determined by four main factors: the design of the robot $(R)$, the personal characteristics of the human user $(H)$, the situation and context in which the interaction occurs $(C)$, and the amount of time (repeated interaction) that the user spends to familiarize herself with the robot $(t)$.}
-    \label{factors}
+    \label{fig:factors}
 \end{figure}

### 2014-04-02 paper.tex
section 3 finished

@@
 However, we think that this is not the full story. When agreeing to understand anthropomorphism as a specific type of \textit{experience} that arises in an
-\textit{interaction} between a set of user expectations and the external reality, 
+\textit{interaction} between a set of user expectations and the external reality \citep{persson_anthropomorphism_2000}, 
 %(see Figure~\ref{fig:anthropomorphism_and_interaction})
@@
 
-Consequently, we propose a holistic understanding of anthropomorphism as a phenomenon which is determined by multiple factors:
+\begin{figure}
+    \centering
+    \includegraphics[width=0.7\columnwidth]{factors}
+    \caption{Anthropomorphism is a multi-factor phenomenon.
+How far people tend to anthropomorphize a robot is determined by four main factors: the design of the robot $(R)$, the personal characteristics of the human user $(H)$, the situation and context in which the interaction occurs $(C)$, and the amount of time (repeated interaction) that the user spends to familiarize herself with the robot $(t)$.}
+    \label{fig:factors}
+\end{figure}
+
+Consequently, we propose a holistic understanding of anthropomorphism as a phenomenon which is determined by multiple factors (see also Figure \ref{fig:factors}):
 
 \begin{enumerate}
-
-\item ~the \textbf{characteristics of the robot's design} (degree of anthropomorphic form),
-\item ~the \textbf{psychological determinants in the human user} (see
+\item ~the characteristics of the \textbf{robot's design} (degree of anthropomorphic form),
+\item ~the psychological determinants in the \textbf{human user} (see
 \cite{epley_seeing_2007}),
-\item ~the \textbf{characteristics of the context} (situation) in which the interaction occurs, and
-\item ~the fact of the user getting \textbf{familiar with the robot over time} (getting used to a system the more and longer one interacts with it)
-
+\item ~the characteristics of the \textbf{context / situation} in which the interaction occurs, and
+\item ~the fact of the user getting familiar with the robot \textbf{over time} (duration of interaction)
 \end{enumerate}
-
-Further, we propose that
-anthropomorphism is a multi-layered phenomenon which arises in different levels \citep{persson_anthropomorphism_2000}, and which is likely to evolve with continued interaction.
 
@@
 
-Second, we would like to take up the proposition already made by other researchers (\eg \cite{persson_anthropomorphism_2000,takayama_perspectives_2012,ruijten_introducing_2014}) to not viewing anthropomorphism as being either there or not there, but to discriminate different levels of
-anthropomorphism (low, and high anthropomorphism, for instance).
-This seems to make sense, since each of the four proposed factors has its own characteristics and involves specific
-types of user expectations, for instance. Such a differentiation in the understanding of anthropomorphism could further allow to draw inferences
-on the human-robot relationship based on the observed level of anthropomorphism.
-
-\begin{figure}
-    \centering
-    \includegraphics[width=0.7\columnwidth]{factors}
-    \caption{Anthropomorphism is a multi-factor phenomenon.
-How far people tend to anthropomorphize a robot is determined by four main factors: the design of the robot $(R)$, the personal characteristics of the human user $(H)$, the situation and context in which the interaction occurs $(C)$, and the amount of time (repeated interaction) that the user spends to familiarize herself with the robot $(t)$.}
-    \label{fig:factors}
-\end{figure}
-
-To facilitate things, we introduce the notation \Ant[R,H,C,t] to reflect these multiple factors: we suggest here that
+When taking into account these multiple factors, a logical consequence seems to be that anthropomorphism is not either there or not there but that it arises in different levels, may they be distinct, having multiple layers \citep{persson_anthropomorphism_2000}.
+or a continuum being describes in low and high anthropomorphism \citep{ruijten_introducing_2014}.
+For instance,
+
+Moreover, we propose that anthropomorphism shows not only variances determined by these four main factors but that -- the fourth factor implies this -- anthropomorphism is likely to evolve over time with continued interaction between the human and the non-human agent.
+
+To facilitate things, we introduce the notation \Ant[R,H,C,t] to bring these multiple factors together. To take into account dynamics over time, we suggest that
 anthropomorphism is a function of a vector of robot's traits $R = \{r_0,...,r_n\}$, a vector human
 determinants $H = \{h_0,...,h_n\}$, a set of interaction situations that build
-an interaction context $C = \{s_0,...,s_n\}$, and the duration of the
+an interaction context $C = \{s_0,...,s_n\}$, and the duration / history of the
 interaction itself, $t$.
@@
 
-With having both before-mentioned aspects in mind (multi-factors that determine anthropomorphism and multi-levels of the observable phenomenon), it becomes clear that anthropomorphism cannot be something fixed, that once observed in a human-robot interaction always remains the same.
-We think, that anthropomorphism evolves and shows dynamics.
-This idea is what we would like to formalize in the next section.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \emph{adopting} a robot, for instance). Though conflicts were
-found\fxwarning{SL: which conflicts are we talking about?}, the HRI
+found in the understanding of what anthropomorphism is, the HRI
 community more or less accepted viewing anthropomorphism as a static feature
 that once observed during a short-term interaction reflects a sustaining social
-effect.
-
-\citet{kanda_interactive_2004} point out, however, that relationships among
+effect. However, if we agree that anthropomorphism arises in an interaction, and thus reflects a specific relation, we cannot accept it as a static phenomenon.
+
+Similarly, \citet{kanda_interactive_2004} point out that relationships among
 people evolve over time and, in a similar manner, one can expect people's attitude toward
 technological artifacts and their relationship with them to evolve as well.
-In their study, \citet{kanda_interactive_2004} were also among the first to
+In their study, \citet{kanda_interactive_2004} were among the first to
 describe empirically \emph{novelty effects} during a long-term study with an
@@
 activated knowledge at the time of the judgment}. By applying knowledge to a
-given situation or interaction, it is implied that one attempts to correct,
+given situation or interaction, one also attempts to correct,
 adjust, or maybe integrate less accessible information into a more automatically
-activated default representation. Epley argues that this process can be seen as
-a process of correction, and thus, it is often insufficient leaving final
-judgments biased in the direction of the initially activated representation.
-Refinements to the initial representation mean something evolves. This can be
-due to the fact that a person's knowledge base changes constantly with newly
-acquired things, or growing experiences with a robot. Consequently, it is likely
-that the ``need to anthropomorphize'' a robot decreases over time (from the
-human-centered point of view), since the user's knowledge about the robot
-evolves, and also the user familiarizes herself with the robot. Consequently,
-the robot should become more predictable and more familiar to the human user and
-inferences about it can be made based on the acquired knowledge.\fxwarning{SL:
-Rephrase the last part of this paragraph}
-
-In other words, the argumentation is that humans have a motivation to interact
+activated default representation.
+%Epley argues that this process can be seen as
+%a process of correction, and thus, it is often insufficient leaving final
+%judgments biased in the direction of the initially activated representation.
+%Refinements to the initial representation mean something evolves.
+This process of refining the applied knowledge are natural because a person's knowledge base changes constantly with newly
+acquired things.
+For instance, a person can acquire new knowledge about a robot when interacting with it.
+With continued interaction with the unknown system also the user's expertise with the system grows, and it can be expected that in turn, the user will become able to better predict the previously unknown system.
+Consequently, as the robot becomes more predictable, there is less uncertainty, and the ``need to anthropomorphize'' the robot decreases (from the
+human-centered point of view).
+
+In other words, humans have a motivation to interact
 effectively in their environment \textit{(effectance)} \citep{epley_when_2008}.
 This means that humans are motivated to be able to understand and predict the
-environment and agents around them. Through this process, uncertainty is
-reduced, and consequently, a first unfamiliar robot, can be explained with means
-that are different from anthropomorphism.\fxwarning{SL: Paragraph unclear to me.
-Rephrase it?}
+environment and the agents around them.
+Thus, a person will seek to become familiar with what is unfamiliar.
+Anthropomorphism is encouraged when an agent is unfamiliar.
+Consequently, in the process of familiarizing oneself with an agent, the tendency to anthropomorphize this agent should decrease.
+
+We can not be sure about how exactly the process of familiarization to an unfamiliar agent (based on continued interaction with the robot) looks like.
+In turn, we can not make a precise statement about how continued interaction decreases anthropomorphism but we suspect there is a link between the two.
 
@@
 anthropomorphism that we proposed at section~\ref{sec:anthropomorphism}, we
-introduced in the following section a novel qualitative model of the evolution
-of anthropomorphism over time, \ie a model of the dynamics of anthropomorphism.
+introduce in the following section a novel qualitative model of the evolution
+of anthropomorphism over time, \ie a model of the \emph{dynamics of anthropomorphism}.
 

### 2014-04-02 paper.tex
moved on to review section 4 (dynamics model)

@@
 (Figure~\ref{fig:dynamics},~\citep{lemaignan2014dynamics}) represents how the
-level of anthropomorphic effects~\Ant[R,H,C,t] (\ie the observable
+level of `anthropomorphic effects'~\Ant[R,H,C,t] (\ie the observable
 manifestations of anthropomorphism) evolves over a long-term human-robot
-interaction.
+interaction.\footnote{We cannot make a precise statement about how long `long-term' interaction has to be to be considered as such.
+It seems to be practical to not speak of `several days' or `weeks' but to rather consider the duration and frequency of the actual interactions with the artifact.
+One could probably call this the `interaction history'.}
 
@@
 
-In this model, anthropomorphism is quantified by a \emph{normalized level of
+In the \emph{Dynamics of Anthropomorphism} model, anthropomorphism is quantified by a \emph{normalized level of
 anthropomorphic effects} $\antNorm[R,H,C,t] = \frac{\ant[R,H,C,t]}{\antMax}$:
@@
 we will use \Ant in the following sections to refer to the normalized level of
-anthropomorphic effects. Note also that we discuss at
-section~\ref{sec:measuring} possible methodologies for the quantitative and
+anthropomorphic effects. Note also that we discuss in
+Section~\ref{sec:measuring} possible methodologies for the quantitative and
 qualitative assessment of anthropomorphic effects.
@@
 The actual maximum value of anthropomorphic effects depends on each unique
-combination of human, robot and several other factors we introduce below, and
-thus varies (as pictured on Figure~\ref{fig:dynamics}, we suggest besides that
-$t_{max}$ actually corresponds to the novelty effect peak). The general
+combination of a human, a robot, a situation and several other factors we introduce below.
+Thus, the maximum value varies according to the specific characteristics of these factors.
+Figure~\ref{fig:dynamics} pictures this maximum value at
+$t_{max}$, which actually corresponds to what we call the novelty effect peak.\footnote{We assume that there is a peak in the human's experiences of the novelty effects of the unfamiliar system.
+Further, we suspect that this novelty peak comes along with the maximum value of anthropomorphic effects.}
+ The general
 \emph{shape} of the model remains however the same and depicts the evolution of
-anthropomorphism over time, \ie the general dynamics of anthropomorphism.
+anthropomorphism over time, \ie the general dynamics of anthropomorphism.\fixme{Last sentence: Do you mean the shape of the curve?
+i would not agree that it remains the same ...
+but say that it shows a general tendency to decrease, however that there might be variations.}
 
@@
     \emph{initialization}, \emph{familiarization} and \emph{stabilization},
-    preceded by a \emph{pre-interaction} phase. In the pre-interaction phase,
-    users build an \emph{initial capital of anthropomorphism} (ICA, noted \ICA).
+    preceded by a \emph{pre-interaction} phase. The pre-interaction phase
+    is characterized through an \emph{initial capital of anthropomorphism} (ICA, noted \ICA).
     Once the interaction starts, the level of anthropomorphism increases due to
@@
     level of anthropomorphism} (SLA, noted \SLA). \ICA and \SLA may vary
-    depending on the user, the robot and the context of interaction.  During the
+    depending on the user (and his/her expectations), the robot and the context of interaction.  During the
     interaction, unpredicted behaviors of the robot (\emph{disruptive
@@
 anthropomorphic effects in a long-term human-robot interaction. They are
-depicted in different shades on Figure~\ref{fig:dynamics}.
+depicted in different shades in Figure~\ref{fig:dynamics}.
 
@@
 third phase, as well as the \emph{stabilized level of anthropomorphism}, are
-discussed in section~\ref{sec:stabilization} below.
+discussed in section~\ref{sec:stabilization}.
 
@@
 This potential depends on several factors, introduced in
-section~\ref{sec:anthropomorphism}. It has been shown, for instance, that
+section~\ref{sec:multi-factors}, see also Figure \ref{fig:factors}. It has been shown, for instance, that
 some \textit{people} tend to anthropomorphize more than others, that some
@@
 worldviews~\citep{epley_when_2008}. Also the shape and design of the robot play a
-role, like the context in which the interaction takes place. Our model of
+role, as well as the context in which the interaction takes place. Our model of
 anthropomorphism represents these factors as a compound metric \ICA. As such,
 \ICA describes the level of anthropomorphic projections just prior the first
-(real or imagined) contact to a robot. In this stage of pre-interaction, people
-form initial expectations toward the robot and imagine how they will use it /
+(real or imagined) interaction with a robot. In this stage of pre-interaction, people
+form \textbf{initial expectations} toward the robot and imagine how they will use it /
 interact with it.
 
-Following the discussion in section~\ref{sec:anthropomorphism}, we build \ICA on
-three main factors that determine \emph{a priori} that a robot
-will be anthropomorphized:
+Taking up on our suggestion to have four main factors that impact on anthropomorphism, we propose that the initial capital of anthropomorphism can be build \emph{a priori}.
+As the \ICA marks the very moment before the first real or imagined contact of the human with the robot, the \textit{interaction history} between the two players is empty; consequently the time factor $t$ is not taken into account when building the \ICA.
+The specific \ICA value reflects how far a robot is likely to be anthropomorphized, based on the following three factors:
 
@@
 
-    \item ~\emph{Human-centered factor} $S$: The \textbf{personality} and individual
+    \item ~\emph{Human factor} $S$: The \textbf{personality} and individual
         traits of the human user: Psychological characteristics / determinants
@@
 
-    \item ~\emph{Robot-centered factor} $R$: The robot's \textbf{design} and how it
+    \item ~\emph{Robot factor} $R$: The robot's \textbf{design} and how it
         appears to the human user. Characteristics of the robot's form,
@@
 
-    \item ~\emph{Context-centered factor} $C$: The real or imagined
+    \item ~\emph{Context factor} $C$: The real or imagined
         \textbf{purpose} of the robot, including the situational context in
@@
 
-For \textbf{personality}, we suggest to apply \citet{epley_seeing_2007}
-psychological \textit{3-factor theory} of anthropomorphism. For instance,
+For \textbf{personality}, we suggest to apply the
+psychological \textit{3-factor theory} of anthropomorphism by \citet{epley_seeing_2007}. For instance,
 children generally tend to anthropomorphize objects more than adults. Also, a
@@
 For \textbf{design}, we understand that a robot that follows an anthropomorphic
-design (\eg Nao) leads to a higher \ICA than a rather functional robot (\eg
+design up to a certain acceptable level (\eg Nao) leads to a higher \ICA than a rather functional robot (\eg
 Roomba). Also, a robot that is able to display facial expressions would increase
-the \ICA. Quantify the \emph{level} of anthropomorphic design in a robot, as
+the \ICA. Quantifying the \emph{level} of anthropomorphic design in a robot, as
 suggested for instance by \citet{fong_survey_2003}, can be difficult.
 Nevertheless, the important aspect is how the robot appears to the user, \eg
-human-like or machine-like.
+human-like or machine-like, acceptable or not-acceptable.\footnote{It becomes clear that the \textit{robot factor} can not be fully separated from the \textit{human factor}.
+The reason for this is that the message that design tries to make, always lies in the eye of the beholder.
+No matter how much effort a designer spends in making the `message' of the artifact's design clear, there is always some scope and creative freedom in how the design is interpreted by the beholder.}
 
 By taking the \textbf{purpose} of a robot into account, we suggest that the real
-or imagined context in which a robot is used and the interaction that this usage
-brings along, impacts how far the robot will be attributed human-like
+or imagined application context of the robot, or in which situation the interaction occurs, impacts how far the robot will be attributed human-like
 characteristics. We draw on findings such as presented in \citet{joosse_what_2013}. The authors showed for instance that when the
@@
 context leads to a higher \ICA than a robot which is used for a routine or
-focused task (security, rescue, etc.). This idea also receives support from
+focused task (security, rescue, etc.).
+This was also found in an analysis of anthropomorphic language in online forum discussions about the AIBO, Roomba, and iPad \citep{fink_anthropomorphic_2012}.
+Regardless of the conversation topic, more anthropomorphic language was found in the AIBO forum.
+However, this was not only due to the zoomorphic (pet-like) shape of AIBO but also due to its  playful purpose.
+The idea that the purpose of a robot are crucial factors, also receives support from
 Goetz \& Kiesler's work that revealed that people prefer a serious robot for

### 2014-04-02 paper.tex
Proof-read section 2.1, 2.2

@@
 Probably as a result of this, there also exist different understandings of the \textit{phenomenon} that the term `anthropomorphism' describes.
- In this section we will first give an overview on the diversity of terms and then try to establish a common ground in the understanding of anthropomorphism (the phenomenon).
-
-\subsection{Overview of the diversity of terms}
-
-Originally, the term \textbf{anthropomorphism} comes from the Greek \textit{anthropos} for `man' (or `human') and \textit{morphe} for `form / structure' (or `shape').
-Anthropomorphism is generally understood as people's tendency to perceive a non-human agent as if it had some human characteristics or traits.
-How a person perceives an agent is crucial, as it further determines how she relates to, and behaves towards the agent, or how she may behave in light of this agent \citep{epley_when_2008}.
-As such, anthropomorphism can be seen as a special kind of relationship between a human interacting with a non-human agent.
-An anthropomorphic relationship is often characterized by the fact that the human attributes human-unique characteristics to the non-human agent.
-Since anthropomorphism becomes observable through these attributions, some definitions claim that anthropomorphism is not the \textit{perception} but rather the \textit{attribution} of human qualities to non-human agents.
-Ascribing thoughts, emotions, and intentions are given as examples, and as the most prominently anthropomorphized non-human agents animals and robots are mentioned \citep{duffy_anthropomorphism_2003,schmitz_concepts_2011}.
-
-Apart from anthropomorphism there also exists the term \textbf{animism}, which can be defined as the attribution of life to the nonliving.
-The study of animism was pioneered by Piaget in the 1920s with his work on \textit{The Child's Conception of the  World}.
-He found that children tend to regard many inanimate objects as capable of sensations, emotions and intentions, and called this view `animism'.
-Since then, children`s inferences about the world have been studied intensively, and there is an agreement that children`s views and concepts of living, animal, and plant evolve as they grow up.
-Often synonymously used to animism is the term \textbf{zoomorphism}, which similarly applies to the cases when non-lifelike instances / artifacts are associated with animalistic attributes, excluding human-specific traits.
-As `being alive' is not a human-unique property but applies to all living beings, the attribution of life may not be labeled as anthropomorphism (in a narrow understanding of it).
-Another possibility to illustrate how anthropomorphism differs from attributions of animacy, is to look at paraphrases of anthropomorphism. That is to say, 
+ In this section we will first give an overview on the diversity of terms and
+ then try to establish a common ground in the understanding of anthropomorphism
+ as a psychological phenomenon.
+
+ \subsection{The lexical field of anthropomorphism}
+
+Originally, the term \textbf{anthropomorphism} comes from the Greek
+\textit{anthropos} for ``man'' (or ``human'') and \textit{morphe} for `form /
+structure' (or `shape'). Anthropomorphism is generally understood as people's
+tendency to perceive a non-human agent as if it had some human characteristics
+or traits. How a person perceives an agent is crucial, as it further determines
+how he/she relates to, and behaves towards the agent, or how he/she may behave in
+light of this agent \citep{epley_when_2008}. An anthropomorphic relationship is
+often characterized by the fact that the human attributes human-unique
+characteristics to the non-human agent. Since anthropomorphism becomes
+observable through these attributions, some definitions claim that
+anthropomorphism is not the \textit{perception} but rather the
+\textit{attribution} of human qualities to non-human agents.  Ascribing
+thoughts, emotions, and intentions are given as examples, and as the most
+prominently anthropomorphized non-human agents, animals and robots are mentioned
+\citep{duffy_anthropomorphism_2003,schmitz_concepts_2011}.
+
+Apart from anthropomorphism, there also exists the term \textbf{animism}, which
+can be defined as the attribution of life to the nonliving. The study of animism
+was pioneered by Piaget in the 1920s with his work on \textit{The Child's
+Conception of the  World}. He found that children tend to regard many inanimate
+objects as capable of sensations, emotions and intentions, and called this view
+``animism''. Since then, children's inferences about the world have been studied
+intensively, and there is an agreement that children's views and concepts of
+living, animal, and plant evolve as they grow up. Often synonymously used to
+animism is the term \textbf{zoomorphism}, which similarly applies to the cases
+when non-lifelike instances / artifacts are associated with animalistic
+attributes, excluding human-specific traits.  As ``being alive'' is not a
+human-unique property but applies to all living beings, the attribution of life
+may not be labeled as anthropomorphism (in a narrow understanding of it).
+Another possibility to illustrate how anthropomorphism differs from attributions
+of animacy is to look at paraphrases of anthropomorphism. That is to say,
 anthropomorphism can alternatively be understood as \textbf{humanization} or
-\textbf{personification} of anything other than a human being.\footnote{There exist also the phenomenons inverse to anthropomorphism, which can be found in the literature as \textbf{dehumanization} \citep{haslam_dehumanization:_2006}, or \textbf{mechanomorphism} \citep{caporael_anthropomorphism_1986}.
-However, we do not treat this here.}
-Robots can both be animized and anthropomorphized, but often the difference is not made.
+\textbf{personification} of anything other than a human being\footnote{There
+exist also the phenomenons inverse to anthropomorphism, which can be found
+in the literature as \textbf{dehumanization}
+\citep{haslam_dehumanization:_2006}, or \textbf{mechanomorphism}
+\citep{caporael_anthropomorphism_1986}.}. Robots can
+both be animized and anthropomorphized, but often the difference is not made.
 
@@
 
-Naturally, conflicts in how terms are used lead to a diversity of understandings of the phenomenon which is described.
-One reason for this might be that anthropomorphism
-is a phenomenon that is studied in very different domains that might each
-integrate their own understanding, or simply use the same term to refer to different things.
-The conflict when reading about anthropomorphism is, that despite the fact that there is no commonly accepted definition, the terms
-\textit{anthropomorphism}, \textit{anthropomorphic} or \textit{human-like} are
-often used as if their meanings were clear and agreed upon
-\citep{persson_anthropomorphism_2000}. It is even
-argued that these terms might be misused \citep{duffy_anthropomorphism_2002,epley_when_2008}.
-For instance, some researchers refer to \textit{``the
-robot's level of anthropomorphism''} \cite{bartneck_is_2007}, whereas others
-disagree to such a statement because they understand that a system or artifact itself does not \textit{``contain anthropomorphism''} but only gives rise to the process of anthropomorphizing in a
-given user and situation. Consequently, \cite{persson_anthropomorphism_2000} conclude that
-anthropomorphism emerges in the \textit{interaction} between the technology and
-the user, and has to be understood as such \hl{(to which we will come back in the next section)}.
-
-Another paradox is that, while human's tendency to anthropomorphize is commonly observed, the phenomenon is 
-at the same time still rather poorly understood
-\cite{epley_seeing_2007}. The phenomenon itself has been found to be very complex though sometimes
-subtle and as such hard to study \cite{duffy_anthropomorphism_2002,epley_when_2008}.
-Further, it is not clear how to operationalize and measure anthropomorphism.
-We would like to discuss the challenges of studying and measuring anthropomorphism toward the end of this article, in Section \ref{sec:measuring}.
+Naturally, conflicts in how terms are used lead to a diversity of understandings
+of the phenomenon which is described.  One reason for this might be that
+anthropomorphism is a phenomenon that is studied in very different domains that
+might each integrate their own understanding, use the same term to refer to
+different things.  Despite the fact that there is no commonly accepted
+definition, the terms \textit{anthropomorphism}, \textit{anthropomorphic} or
+\textit{human-like} are often used as if their meanings were clear and agreed
+upon \citep{persson_anthropomorphism_2000}. It is even argued that these terms
+might be misused \citep{duffy_anthropomorphism_2002,epley_when_2008}.  For
+instance, some researchers refer to \textit{``the robot's level of
+anthropomorphism''} \citep{bartneck_is_2007}, whereas others disagree to such a
+statement because they understand that a system or artifact itself does not
+\textit{``contain anthropomorphism''} but only gives rise to the process of
+anthropomorphizing in a given user and situation. Consequently,
+\cite{persson_anthropomorphism_2000} conclude that anthropomorphism emerges in
+the \textit{interaction} between the technology and the user, and has to be
+understood as such. We come back on this point in the next section.
+
+Another paradox is that, while human's tendency to anthropomorphize is commonly
+observed, the phenomenon is at the same time still rather poorly understood
+\citep{epley_seeing_2007}. The phenomenon itself has been found to be very
+complex, sometimes subtle and as such hard to study
+\citep{duffy_anthropomorphism_2002,epley_when_2008}. Besides, it is not clear
+how to operationalize and measure anthropomorphism (we discuss this question
+toward the end of this article, in Section \ref{sec:measuring}).
 
@@
 colloquially labeled as \emph{anthropomorphism} really is anthropomorphism.
-One practical example is that, it is not always clear whether a person (may it be an adult or 
-a child) who gives and anthropomorphic response, believes that the other agent really 
-thinks or acts like a human or whether she is using anthropomorphism in a metaphoric 
+For example, it is not always clear whether a person (may it be an adult or 
+a child) who gives an anthropomorphic response, believes that the other agent really 
+thinks or acts like a human or whether he/she is using anthropomorphism in a metaphoric 
 sense \citep{leeds_childrens_1992}.
-Thus, we need to be clear about what we mean when talking about anthropomorphism.
-
-Several attempts have been made to clarify what anthropomorphism is (the phenomenon).
-From a psychology point of view \cite{epley_when_2008} try to clarify things by explaining what anthropomorphism is \textit{not}.
-For instance, in their understanding, anthropomorphism does not include behavioral descriptions of observable actions but it requires going beyond what is directly observable.
-It is further proposed that anthropomorphism does not merely entail \textit{animism}, as animate life is not a \textit{uniquely} human-like characteristic.\footnote{For the whole list and more details, the reader may refer to the original work \citep{epley_when_2008}.}
+This call for explicitely stating what we mean when talking about anthropomorphism.
+
+Several attempts have been made to clarify what the psychological phenomenon
+\emph{anthropomorphism} actually is.  From a psychology point of view,
+\citet{epley_when_2008} explain what anthropomorphism is \textit{not}. For
+instance, in their understanding, anthropomorphism does not include behavioral
+descriptions of observable actions but it requires going beyond what is directly
+observable. They also suggest that anthropomorphism does not merely entail
+\textit{animism}, as animate life is not a \textit{uniquely} human-like
+characteristic\footnote{For the whole list and more details, the reader may
+refer to the original work \citep{epley_when_2008}.}.
 
@@
 
-As human-likeness itself is a huge dimension, some researchers argue that there might not just be one single type of anthropomorphism but different levels or gradations.
-For instance, \cite{persson_anthropomorphism_2000} proposes to understand anthropomorphism as a multi-layered phenomenon, and suggests that it exists of different levels, namely primitive categorization, primitive psychology, folk-psychology, traits, social roles, and emotional anthropomorphism.
-Correspondingly, \cite{ruijten_introducing_2014} propose to understand anthropomorphism as a continuum ranging from low to high human likeness, and to measure it as such (see Section \ref{sec:measuring}).
+As human-likeness itself is a huge dimension\fxwarning{SL: huge dimension?},
+some researchers argue that there might not just be one single type of
+anthropomorphism but different levels or gradations. For instance,
+\citet{persson_anthropomorphism_2000} proposes to understand anthropomorphism as
+a multi-layered phenomenon, namely \emph{primitive categorization},
+\emph{primitive psychology}, \emph{folk-psychology}, \emph{traits}, \emph{social
+roles}, and \emph{emotional anthropomorphism}. Correspondingly,
+\citet{ruijten_introducing_2014} propose to understand anthropomorphism as a
+continuum ranging from low to high human likeness, and to measure it as such.
 

### 2014-04-02 paper.tex
new bibitems, some work on the discussion section

@@
 
-\paragraph{Human-centered perspective on anthropomorphism}
+\paragraph{Human-centered perspective on anthropomorphism\\}
 
@@
 
-\subsubsection{Initialization Phase}
+\subsubsection{Initialization Phase\\}
 \label{sec:initialization}
 
-\paragraph{Initial Capital of Anthropomorphism}
+\paragraph{Initial Capital of Anthropomorphism\\}
 \label{sec:ica}
@@
 serious tasks and a less serious robot for more playful
-tasks~\citep{goetz_cooperation_2002, goetz_matching_2003}. Also, we suggest that
+tasks~\citep{goetz_cooperation_2002, goetz_matching_2003}.
+However, what about artificial agents that seem to have no purpose?
+\cite{kaplan_free_2000} discusses the role of uselessness in the design of robots.
+He argues that artificial pets such as the AIBO, have no real purpose, in a sense that they do not provide any kind of service, or, in other words \textit{``they are not doing what you tell them to do''} and \textit{``they might refuse the order of its owner''}.
+It is this very aspect that might increase people's tendency to anthropomorphize the robot.
+According to Kaplan, it is in our daily use language, that we tend to attribute intentions to devices that are not doing their job well.
+For instance, we do not develop any kind of relationship with our computer, washing machine or TV set when they work properly.
+The author argues that it is only when they start dis-functioning, when they show that they can act differently that what we ordered, that we are ready to give them some kind of ``intentionality''.
+
+ Also, we suggest that
 the environmental context in which people experience and interact with the robot
@@
 
-\paragraph{The Novelty Effect}
+\paragraph{The Novelty Effect\\}
 \label{sec:noveltyeffect}
 
-\fxfatal{SL: Julia, do you have smthg to provide an initial account of what the
-novelty effect is?}
+Novelty effects have been described with interactive technologies in general \citep{rogers_diffusion_1995} and also in several long-term HRI studies in workplaces \citep{huttenrauch_fetch-and-carry_2003,mutlu_robots_2008}, in schools and public places \citep{gockley_designing_2005,kanda_interactive_2004,kanda_communication_2005}, or elder care centers \citep{sabelli_conversational_2011}.
+Further, also with domestic robots it has been found that people's interest, engagement, and fascination with the robot decreased over time \citep{fink_living_2013,fernaeus_how_2010,sung_robots_2009}.
 
@@
 present an example from our long-term ethnographic study with Roomba vacuum
-cleaning robots in households. The observed scenario describes how an elderly
+cleaning robots in households \citep{fink_living_2013}. The observed scenario describes how an elderly
 woman (71 years, living on her own with a little dog in a small row house) was
-setting up and using the robot for the first time for about 10 minutes.
+setting up and using the robot for the first time during about 10 minutes.
 
@@
 intensely in that area.''} She laughs and turns to the robot, talking directly to
-it \emph{``Today you can light up darling!''}. E. carries Roomba to the entrance
+it \emph{``Today you can light up darling!''}. E. carries the Roomba to the entrance
 door and puts it on the floor [floor type: tiles, partially covered with little
@@
 stuck with the carpet in the entrance hall, consequently it reports error 1 [
-two-tone ``Uh-Oh'' sound followed by a narrated voice that starts off with ``Error
-1'']. E. is very surprised \emph{``What, it is even talking to me?''}, lifts the
+two-tone \textit{``uh-oh''} sound followed by a narrated voice that starts off with \textit{``error
+1''}]. E. is very surprised \emph{``What, it is even talking to me?''}, she lifts the
 robot off and puts it back for cleaning. At several occasions, while watching
 how the robot moves around and cleans, E. makes compliments to the robot:
-\emph{``Nice!''} or \emph{``Good job!''} or \emph{``Bravo!''}. Once, when Roomba turns
+\emph{``Nice!''} or \emph{``Good job!''} or \emph{``Bravo!''}. Once, when the Roomba turns
 right in front of some crumbs on the kitchen floor and moves away without
-cleaning them up, E. says: \emph{``There you forgot something, what is with over
+cleaning them up, E. says: \emph{``There you forgot something, what about over
 there? Look, there you still have something to clean up!''}, and she points at
-where she wants Roomba to go. Further, she uses deictic gestures and tells the
+where she wants the Roomba to go. Further, she uses deictic gestures and tells the
 robot: \emph{``No, go this way! Come over here!''}. The woman keeps observing the
@@
 / \emph{``she''}); praising the robot (\emph{``Good job!''}); using pointing
-gestures toward the robot, or try to direct it around with commands; attributing
+gestures toward the robot, or trying to direct it around with commands; attributing
 a personal preference / intention to the robot (\emph{``she loves the hall!''}).
 
-During the following visits at the woman's place, she did not talk to the robot
+During the following visits at the woman's place, E. did not talk to the robot
 anymore, and generally behaved in a less anthropomorphizing way. The observed
-effects were likely due to the novelty of the robot.
-
-\subsubsection{Familiarization Phase}
+effects were likely due to the novelty of the robot, and the fact that E. was not familiar with the robot and its behavior.
+As \cite{persson_anthropomorphism_2000} names it: \textit{``Anthropomorphism is a way of making sense of complex behavior in the world around us.''}.
+Thus, as soon as this complexity is reduced, also anthropomorphism might be reduced.
+
+\subsubsection{Familiarization Phase\\}
 \label{sec:familiarization}
 
-\emph{Familiarization}, in this context, means \emph{to get acquainted with}.
+In this context, \emph{familiarization} means \emph{to get acquainted with}.
 It is not to be confused with the \emph{familiarity thesis} that relates to the
@@
 
-\paragraph{Disruptive behaviors}
+\paragraph{Disruptive behaviors\\}
 
@@
 
-As illustrated on Figure~\ref{fig:dynamics}, our model represents
+As illustrated in Figure~\ref{fig:dynamics}, our model represents
 \emph{disruptive behaviors} as either local increases or local decreases of
@@
 
-\subsubsection{Stabilization Phase}
+To illustrate how a disruptive behavior of a robot can evoke anthropomorphic effects, we present again an example from our long-term ethnographic study with Roomba vacuum cleaning robots in households \citep{fink_living_2013}.
+The observed scenario describes how a family (young parents, 26 and 28 years old, with 3 little children, 5 and 4 years, and 6 months old, living in a house with garden on the countryside) were using the robot during the first week.
+
+The father (M.) always lets Roomba clean up the ground floor after the family finishes dinner and they all go upstairs to put the children to bed.
+When the robot would have finished its cleaning cycle, the parents would later just find it docked at its charging station.
+It used to be like this every evening.
+However, one day when the father comes downstairs, Roomba is not at its station.
+He says: \emph{``Hey, Roomba, where are you?
+Why did you not want to got to sleep last night?''}.
+After some searching he found it stuck under the sofa and wondered why this had happened.
+
+What is the observed anthropomorphic effect in this scenario?
+Usually, the father did not talk to the robot or praise it.
+However, now that the robot did something unexpected (it was not at its usual place) he started wondering about its ``intention'' and directly asked the robot for its reasons to not \textit{``go to sleep''}.
+
+\subsubsection{Stabilization Phase\\}
 \label{sec:stabilization}
@@
 
-\paragraph{Stabilized Level of Anthropomorphism}
+\paragraph{Stabilized Level of Anthropomorphism\\}
 
@@
 
+\fixme{JF: Severin, we should at some point mention what the ``expectation mismatch'' is ...
+I haven't found that so far ...
+but I am also not sure about how to explain this.
+I think that, the we already took into account the user's expectations in the human-factor.}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-This section provide an initial interpretation of anthropomorphism in
+This section provides an initial interpretation of anthropomorphism in
 terms of \emph{cognitive correlates}: how human cognition can explain the
@@
 
-The next sections introduces a model of the cognitive stages involved in
+The next sections introduce a model of the cognitive stages involved in
 human-robot interaction, that can be interpreted in parallel to the model of the
@@
 behaviors (section~\ref{sec:disruptive}) on mutual modelling, and how our models
-relate to the \emph{In-the-moment} versus \emph{Reflective} perspectives
+relate to the \emph{in-the-moment} versus \emph{reflective} perspectives
 introduced by~\citet{takayama_perspectives_2012}.
@@
 
-\subsubsection{Cognitive Processes and Stages}
+\subsubsection{Cognitive Processes and Stages\\}
 
@@
 particular, its implications regarding the design of (social) robots and
-human-robot interaction are still to be refined.
-
-\subsection{Effect of Time and Familiarization}
+human-robot interaction are still to be refined but we hope this article helps encourage an open dialogue between those who do research of anthropomorphism.
+
+\subsection{Effect of time / familiarization on anthropomorphism}
 
 \fixme{Discuss here the general findings of the paper: the global shape of the
-model of the dynamics, ...}
-
-The \textit{context of use} is related to the purpose (and functionality) of the
-robot and influences the user interaction experience. With \textit{time}, we
-refer to long-term interaction with the robot, which is related to what has been
+model of the dynamics, ... // JF: yep, I agree, we should also come back to our initial hypotheses}
+
+We have proposed that time, or in other words, the user's familiarization with the non-human agent, models how anthropomorphism evolves over time.
+Our general assumption is that with continued interaction, and in turn growing user experience, the system becomes more predictable and consequently, the user's need to anthropomorphize the agent decreases.
+We would like to discuss this suggestion here.
+
+With \textit{time} as a factor, we
+referred to long-term interaction with the robot, which is related to what has been
 described as \textit{novelty effect} but also accounts for the user getting used
-to the robot. Consequently, we propose that anthropomorphism is not static but
-likely to change, due to what we call \textit{dynamics}, in space and time.
-
-As outlined in section \hl{XX}, the tendency to anthropomorphize is motivated by
+to the robot.
+
+As outlined before, the tendency to anthropomorphize is motivated by
 a person's wish to make sense of an agent which might be difficult to understand
 (in its functionality or behavior, for instance). In turn, a user might ascribe
-intentions or emotions to the system because the systems output was unexpected
+intentions or emotions to the system because the system's output was unexpected
 for the user. Based on this explanation, we estimate that when the user has
@@
 the system is usable and explainable, the tendency to anthropomorphize
-decreases. Therefore, our second hypothesis is as follows:
-
-\begin{itemize}
-    \item \textbf{Hypothesis 1} A person's tendency to anthropomorphize a robot
-        is impacted by the context of use and purpose of the robot. A social
-        context and purpose of the robot increases anthropomorphism.
-        \textit{(context and purpose of the robot)}
-	\item \textbf{Hypothesis 2} A person's tendency to anthropomorphize a robot decreases over time and with growing experience the person has with the robot.
-\textit{(familiarize oneself with the robot)}
-\end{itemize}
-
-Given our first hypothesis from above, this might not hold over all contexts;
-more concretely, probably not in a social context of usage.
-
-Smart innovative devices, such as personal domestic robots, might demand from a
-human user spontaneous usage of an unfamiliar system. Such situations will
-require that a user should be able to build up a mental model quickly, which
-particularly holds for novice users \cite{schmitz_concepts_2011}.
-
-Eddy \textit{et al.} points out that familiarity increases the tendency to
-anthropomorphize \cite{eddy_attribution_1993}.
-
-"As shown in several psychological experiments [13,24] and pointed out by Watt
-[25], familiarity may also ease social acceptance and even tend to increase
-people's tendency to anthropomorphize [16]." \cite{duffy_anthropomorphism_2003}
-
-\subsection{Limitations}
-
-The model of anthropomorphism we propose is still a work in progress. In
-particular, its implications regarding the design of (social) robots and
-human-robot interaction are still to be refined.
+decreases.
+
+However, there exist views that suggest just the opposite, namely, that familiarization with an agent \textit{increases} the tendency to anthropomorphize \citep{eddy_attribution_1993}.
+Similarly, \cite{duffy_anthropomorphism_2003} reports that several psychological experiments and human-robot interaction experiments showed that familiarity may also ease social acceptance and even tend to \textit{increase} people's tendency to anthropomorphize.
+
+Consequently, we have to accept that our model of the \emph{Dynamics of Anthropomorphism} needs to be verified, to see how far our hypotheses can hold.
+In particular, the effect of the user's familiarity with the system needs to be studied over a longer period of time.
+
+%\begin{enumerate} 
+%\item ~A person's tendency to anthropomorphize a robot
+%    is based on several factors, including (but not limited to) (1) the
+%    design of the robot, (2) the personal characteristics of the human user,
+%    and (3) the context and situation of use. For instance, a social context
+%    and purpose of the robot increase anthropomorphism: \textit{anthropomorphism
+%    as a multi-factor phenomenon}.
+%
+%\item ~A person's tendency to anthropomorphize a robot
+%    evolves in a non-linear way over time and with growing experience that the
+%    person has with the robot. For instance, a more experienced user will
+%    perceive the robot as more familiar and predictable, and in turn
+%    anthropomorphizes the robot less: \textit{anthropomorphism as a dynamic
+%    phenomenon}.
+%
+%\end{enumerate}
+
+%
+%Smart innovative devices, such as personal domestic robots, might demand from a
+%human user spontaneous usage of an unfamiliar system. Such situations will
+%require that a user should be able to build up a mental model quickly, which
+%particularly holds for novice users \cite{schmitz_concepts_2011}.
 

### 2014-04-03 paper.tex
Rewritten section 2.3

@@
 
-\subsection{Terminology and understandings used in this article}
-
-We propose to use the term \textbf{anthropomorphism} to describe a social phenomenon, which arises in an interaction between a human agent and a non-human agent, \eg a robot (see Figure \ref{fig:anthropofig}).
-The term anthropomorphism can be used to refer to people's tendency to \textit{perceive} human-like characteristics in non-human agents (or artifacts), but also to refer to the observable effect of a person \textit{ascribing} or \textit{attributing} such human-like characteristics to the agent or artifact.
-Further, anthropomorphism might also be observable in a human's behavior / actions toward a non-human agent.
-The common point here is that anthropomorphism is always performed by the human (either in real or imagined).
-
-However, the term anthropomorphism should \textit{not} be used to refer to the design of a non-human agent or artifact.
-This would violate the understanding of anthropomorphism arising in an interaction.
-To refer to an imitation of human-like form in the \textit{form} of artificial agents, we propose to use the term  \textbf{anthropomorphic design}.
-We found that in literature, this distinction is not always done, which is a major source of confusion.
-
-In the following, we might use the terms \textit{form} and \textit{design} interchangeably. Using the term \textit{form} to describe the design of an artifact, we refer 
-not only to the shape (how it looks like) but to the total 
-expression of the artifact \citep{bartneck_shaping_2004}. \cite{disalvo_hug:_2003} 
-argues that \textit{form} includes a product's physical shape, materials, and 
-behavioral qualities. The behavioral aspect is of special importance for interactive 
-systems that show some degree of autonomy (independence).
-Several categories of anthropomorphic form can be classified, but there is no 
-common agreement on the borders and transitions between these categories: 
-anthropomorphic, zoomorphic, caricatured, functional \citep{fong_survey_2003}.
+\subsection{Our acception of anthropomorphism and related terminology}
+
+We use the term \textbf{anthropomorphism} to describe the \emph{psychological}
+phenomenon, which arises in the \emph{social context} of an interaction between
+a human agent and a non-human agent, in our case, a robot (see Figure
+\ref{fig:anthropofig}). We use this term to refer to both people's tendency to
+\textit{perceive} human-like characteristics, and to the tendency to
+\textit{ascribe} or \textit{attribute} such human-like characteristics to the
+agent or artifact. Besides, we call {\bf anthropomorphic effects} the
+\emph{observable manifestations} of anthropomorphism, \ie the human's behaviors
+and actions toward a non-human agent that reflect the underlying cognitive
+process of anthropomorphizing.
+
+However, we should \textit{not} use the term \emph{anthropomorphism} to refer to
+the design of a non-human agent or artifact. To refer to an imitation of
+human-like form in the \textit{design} of artificial agents, we use the term
+\textbf{anthropomorphic design}. This explicit terminology prevents the commonly
+encountered confusion between anthropomorphism as a psychological, subjective
+phenomenon, and the external, objective factors that \emph{influence} the
+phenomenon itself.
+
+In the following, we might use the terms \emph{form} and \emph{design}
+interchangeably. Note that the terms \textit{form} or {\it design} do not only
+refer to the shape (how it looks like) but to the total expression of the
+artifact~\citep{bartneck_shaping_2004}. \citet{disalvo_hug:_2003} argues that
+\textit{form} includes the physical shape, materials, and behavioral qualities
+of the product. The behavioral aspect is of special importance for interactive
+systems that show some degree of autonomy (independence).  Several categories of
+anthropomorphic form exist, with no common agreement on the borders and
+transitions between those: anthropomorphic, zoomorphic, caricatured, functional
+\citep{fong_survey_2003}.
 
@@
     \includegraphics[width=0.75\columnwidth]{anthropo.pdf}
-    \caption{Anthropomorphism is a social phenomenon which arises in an interaction between a human agent and a non-human agent.
-The two agents are the main \textit{players} \hl{(or elements?)} of the interaction, and consequently one can apply two main perspectives when trying to explain anthropomorphism: a human-centered and an artifact-centered perspective (grey triangles).
-There are several person- and artifact-related factors that determine \hl{(or influence / impact on?)} anthropomorphism.
-Further, the context / situation in which the interaction occurs plays a role.}
+    \caption{Anthropomorphism is a psychological phenomenon which arises in a
+        social context, during an
+    interaction between a human agent and a non-human agent. One can take two main perspectives when trying to explain
+    anthropomorphism: a human-centered and an artifact-centered perspective (grey
+    triangles). Several external factors influence the anthropomorphism
+    phenomenon. Person- and artifact-related ones, but also related to the
+context of use as well as the actual time spend interacting with the robot.}
 

### 2014-04-03 paper.tex
Proof-reading sections 3.1, 3.2, 3.3

@@
 
-The artifact-centered perspective explains anthropomorphism from the ascertainable 
-parts of the non-human agent, namely the anthropomorphic form of it.
-This research deals with the question how far anthropomorphism can be explained from the design of the artifact.
-Consequently, it is studied how humans perceive and respond to different types of human-like designs of non-human agents.
-One of the most prominent working hypothesis in this research branch is the Uncanny Valley hypothesis \citep{mori_uncanny_1970}.
-In general, it is proposed that human-like designs of robots can evoke both positive and negative feelings in a human user.
-
-The direction of causality in the artifact-centered view is that the non-human artifact 
-(or a certain feature of it) encourages the human to anthropomorphize it. 
-This perspective assumes that humans directly (mindlessly) respond to life-like and social 
-cues that the non-human agent or system emits \citep{nass_machines_2000}. Without thoughtful mental processing, 
-humans tend to simply apply stereotypes and heuristics to the non-human agent, and in turn apply human-human social schemas and norms to the occurring interactions.
-\cite{takayama_perspectives_2012} propose to refer to this immediate (sometimes visceral) sense in a situation as \textit{in-the-moment}, compared to a more distanced cogitation and consideration which she calls \textit{reflective}.
-As this distinction implies different cognitive processes, it is more approriate to apply a human-centered perspective and we will come back to it later, in section \ref{sec:cognitive-expl}.
+The artifact-centered perspective explains anthropomorphism from the
+ascertainable parts of the non-human agent, namely the anthropomorphic form of
+it. This section deals with the question how far anthropomorphism can be
+explained from the design of the artifact.  One of the most prominent working
+hypothesis in this field is the Uncanny Valley hypothesis
+\citep{mori_uncanny_1970}. In general, it is proposed that human-like designs of
+robots can evoke both positive and negative feelings in a human user.
+
+The direction of causality in the artifact-centered view goes from the artifact
+to the humans: the artifact (or a certain feature of it) \emph{encourages} the
+human to anthropomorphize it.  This perspective assumes that humans directly
+(mindlessly) respond to life-like and social cues that the non-human agent or
+system emits \citep{nass_machines_2000}. Without thoughtful mental processing,
+humans tend to simply apply stereotypes and heuristics to the non-human agent,
+and in turn apply human-human social schemas and norms to the occurring
+interactions.  \cite{takayama_perspectives_2012} propose to refer to this
+immediate (sometimes visceral) sense in a situation as \textit{in-the-moment},
+compared to a more distanced cogitation and consideration which she calls
+\textit{reflective}. As this distinction implies different cognitive processes,
+it is more approriate to apply a human-centered perspective and we will come
+back to it later, in section \ref{sec:cognitive-expl}.
+
+\fxwarning{SL: maybe add a ref to previous Julia's paper on anthropomorphism?}
 
@@
 
-In contrast to the artifact-centered perspective, in the human-centered perspective the argumentation is, that the human is motivated to anthropomorphize the non-human artifact.
-As already mentioned, both these views go hand in hand.
-
-Humans tend to perceive human-like characteristics such as physical appearance, emotional states, or inner mental states and motivations in non-human agents that do not have these characteristics themselves, such as animals, natural forces, religious agents, technological gadgets, or mechanical devices \citep{epley_when_2008}.\footnote{According to \cite{epley_when_2008}, a non-human agent can be anything that acts -- or is believed to act -- with apparent independence.}
-One common reason for anthropomorphism is that by perceiving some human-like characteristics in the non-human agent, this agent is made more \emph{graspable}, \emph{understandable}, \emph{predictable}, and one can feel \emph{more empathetic} toward it, and possibly one can then anticipate the agent's behavior.
-These are central motivations when trying to explain anthropomorphism, and we will come back to them in more detail later on.
-It is described that for the just mentioned reasons, people commonly anthropomorphize their pets, by ascribing mental states, intentions or feelings to them\footnote{Interestingly, pet-ownership seems to have a significant impact on human-robot interaction: several studies suggest that pet-owners are more likely to anthropomorphize technologies and robots than non pet-owners} \cite{eddy_attribution_1993}.
-But how can these motivations behind anthropomorphism be explained from a human-centered point of view?
+In contrast to the artifact-centered perspective, in the human-centered
+perspective the argumentation is that the human is self-motivated to
+anthropomorphize the non-human artifact. As already mentioned, both these views
+go hand in hand.
+
+Humans tend to perceive human-like characteristics such as physical appearance,
+emotional states, or inner mental states and motivations in non-human agents
+that do not have these characteristics themselves, such as animals, natural
+forces, religious agents, technological gadgets, or mechanical devices
+\citep{epley_when_2008}\footnote{According to \citet{epley_when_2008}, a
+non-human agent can be anything that acts -- or is believed to act -- with
+apparent independence.}. One common reason for anthropomorphism is that by
+perceiving some human-like characteristics in the non-human agent, this agent is
+made more \emph{graspable}, \emph{understandable}, \emph{predictable}, and one
+can feel \emph{more empathetic} toward it, and possibly one can then anticipate
+the agent's behavior. These are central motivations when trying to explain
+anthropomorphism, and we will come back to them in more detail later on.
+\citet{eddy_attribution_1993} explain that, because of these reasons, people
+commonly anthropomorphize their pets, by ascribing mental states, intentions or
+feelings to them\footnote{Interestingly, pet-ownership seems to have a
+significant impact on human-robot interaction: several studies suggest that
+pet-owners are more likely to anthropomorphize technologies and robots than
+non pet-owners}. But how can these motivations behind anthropomorphism be
+explained from a human-centered point of view?
 
@@
 
-The phenomenon of attributing animacy and intentions to nonliving objects such as simple shapes has been intensively studied in developmental psychology.
-As mentioned earlier, Piaget found that children tend to ascribe life to the nonliving.
-They also tend to interpret physical phenomena in terms of intention on the part of the non-human subject.
-For instance children are likely to argue that \textit{``the sun is hot because it wants to make people warm''} \citep{leeds_childrens_1992}.
-In this example it is in fact questionable whether children really anthropomorphize the sun (believing that it has an intention) or whether they are using anthropomorphism in a metaphoric sense (because their conceptions of the world and of the living are not yet fully formed).
-Later however, two famous experiments by \cite{heider_experimental_1944} and \cite{michotte_perception_1963} showed that also adult participants attribute animacy and intention to simple things and shapes based on motion.\footnote{For more details, the reader may refer to the ``attribution theory''.} In both experiments, participants viewed animations of simple shapes, such as circles or triangles.
-%(see Figure \ref{fig:animacy_attribution})
-Asked to describe what they observed, most people developed elaborate stories, attributing motivations, emotions and relationships between the objects.
+The phenomenon of attributing animacy and intentions to nonliving objects such
+as simple shapes has been intensively studied in developmental psychology. As
+mentioned earlier, Piaget found that children tend to ascribe life to the
+nonliving. They also tend to interpret physical phenomena in terms of intention
+on the part of the non-human subject. For instance children are likely to argue
+that \textit{``the sun is hot because it wants to make people warm''}
+\citep{leeds_childrens_1992}. In this example it is in fact questionable whether
+children really anthropomorphize the sun (believing that it has an intention) or
+whether they are using anthropomorphism in a metaphoric sense (because their
+conceptions of the world and of the living are not yet fully formed). Later
+however, two famous experiments by \cite{heider_experimental_1944} and
+\cite{michotte_perception_1963} showed that also adult participants attribute
+animacy and intention to simple things and shapes based on motion. In both
+experiments, participants viewed animations of simple shapes, such as circles or
+triangles. Asked to describe what they observed, most people developed
+elaborate stories, attributing motivations, emotions and relationships between
+the objects\footnote{For more details, the reader may refer to the ``attribution
+theory''.}.
 
@@
 
-Summing it up, as mentioned earlier, it seems that there is a natural, relatively spontaneous reaction that accounts for people's tendency to attribute animacy and intention to moving shapes, even when there is no similarity of the shape to a human.
-This tendency to animize / anthropomorphize is already developed (and even more distinct) in infants and children.
-Thus besides the anthropomorphic cues emitted by the design of the artifact, also developmental stages, and people's natural reaction play a role how far we interpret movements / motions (as one of the most basic "lifelike" cues), for instance.
+As mentioned earlier, it seems that there is a natural, relatively spontaneous
+reaction that accounts for people's tendency to attribute animacy and intention
+to moving shapes, even when there is no similarity of the shape to a human. This
+tendency to animize / anthropomorphize is already developed (and even more
+distinct) in infants and children. Thus besides the anthropomorphic cues emitted
+by the design of the artifact, also developmental stages and people's natural
+reaction play a role how far we interpret movements (as one of the
+most basic ``life-like'' cues) for instance.
 
@@
 
-Anthropomorphism and similar phenomenons can also be understood as a thoughtful process of induction whereby \textit{``people reason about an unknown stimulus based on a better-known representation of a related stimulus"}~\citep{epley_when_2008}.
-In the case of anthropomorphism this means a person's reasoning about a non-human agent based on the representation of the self or other humans.
-A central construct of this perspective is the so-called \textit{mental model} that a person has (and builds) of the agents she is reasoning about and interacting with.
-The specific mental model we have about an artifact / agent basically explains (in our individual way to ourselves) how this artifact / agent works the way it does.
-There are two central aspects here, when looking at the quote from \citep{epley_when_2008} above.\\
-\textit{(1)} One assumption is that the user is not familiar with the other agent.
-This is basically true for all other agents (and entities) but oneself because we can only be our self.
-This view is also consistent with the \emph{familiarity thesis}~\citep{hegel_understanding_2008} which claims that we understand the world based upon a mental model of the world that we are most familiar with (our self).
-Thus, we can best use our self as source of induction when reasoning about other agents.
-However, in case we would like to understand the behavior of a spider, we would probably not use our mental model of a human (or our self) simply because we do not have many things in common with a spider.
-And this is the second central aspect here.\\
-\textit{(2)} One other assumption is based on the anthropomorphic design of the other agent (see Section \ref{sec:anthropomorphic-design}): if the agent behaves (appears) much like a human being (\eg a robot that emits a human voice), people's mental model of the agent's behavior is likely to approach their mental model of humans (though the model may differ in some important aspects).
-
-This cognitive viewpoint on anthropomorphism is important because people's estimation of an agent's knowledge model and its capabilities affects the way they relate to it.
-This holds important implications for the resulting interaction with the system, the user experience, and the acceptance.
-Previous research examined the validity of the mental model concept with various kinds of robots \citep{schmitz_concepts_2011,kiesler_mental_2002}.
-Findings suggest that people tend to hold richer mental models of anthropomorphic robots in contrast to mechanic ones \citep{kiesler_mental_2002}.\footnote{\hl{Later in this article, we may however come to question how far this result is based on expectations from the human user side, which are likely to be refined after continued interaction, and after the user gets acquainted with the robot's behavior.}}
-A similar finding is described in \cite{hegel_understanding_2008} and
-\cite{krach_can_2008}. In a user study using functional magnetic resonance
-imagery (fMRI), the authors found that participants
-implicitly attributed human-like qualities, such as mental states, to their
-non-human interaction partner. Indeed, from an early age humans develop a
-tendency to explain one's own and others' actions in terms of beliefs, desires
-and goals,  called \textit{theory of mind}. The theory of mind allows the implicit attribution of
-intentions and other mental states to others \citep{premack1978does,leslie_pretense_1987,Frith2003}.
-The finding of \cite{hegel_understanding_2008} and \cite{krach_can_2008} was evident at the behavioral level
-as well as on the neuro-physiological level: the more the human-likeness of the
-artefactual partner increases, the more brain areas associated with theory of
-mind  get activated
-\citep{krach_can_2008}. \footnote{\hl{Ha! This says that anthropomorphism can also occur on a behavioral level, yes! :) so we should also measure anthropomorphism in the behavior.}} 
+Anthropomorphism and similar phenomenons can also be understood as a thoughtful
+process of induction whereby \textit{``people reason about an unknown stimulus
+based on a better-known representation of a related
+stimulus"}~\citep{epley_when_2008}. In the case of anthropomorphism this means a
+person's reasoning about a non-human agent based on the representation of the
+self or other humans. A central construct of this perspective is the so-called
+\textit{mental model} that a person has (and builds) of the agents he/she is
+reasoning about and interacting with. The specific mental model we have about an
+artifact / agent basically explains (in our individual way to ourselves) how
+this artifact / agent works the way it does.  There are two central aspects
+here, that derive from the above quote from Epley.
+
+\textit{(1)} One assumption is that the user is not familiar with the other
+agent. This is basically true for all other agents (and entities) but oneself
+because we can only be our self. This view is also consistent with the
+\emph{familiarity thesis}~\citep{hegel_understanding_2008} which claims that we
+understand the world based upon the mental model of the world that we are most
+familiar with (\ie our self). Thus, we can best use our self as source of induction
+when reasoning about other agents. However, in case we would like to understand
+the behavior of a spider, we would probably not use our mental model of a human
+(or our self) simply because we do not have many things in common with a spider.
+And this is the second central aspect here.
+
+\textit{(2)} One other assumption is based on the anthropomorphic design of the
+other agent: if the agent behaves, thus appears, much like a human being (\eg a
+robot that emits a human voice), people's mental model of the agent's behavior
+is likely to approach their mental model of humans (though the model may differ
+in some important aspects).
+
+This cognitive viewpoint on anthropomorphism is important because people's
+estimation of an agent's knowledge model and its capabilities affects the way
+they relate to it. This holds implications for the resulting interaction with
+the system, the user experience, and the acceptance. Previous research examined
+the validity of the mental model concept with various kinds of robots
+\citep{schmitz_concepts_2011,kiesler_mental_2002}. Findings suggest that people
+tend to hold richer mental models of anthropomorphic robots in contrast to
+mechanic ones \citep{kiesler_mental_2002}\footnote{Later in this article,
+we may however come to question how far this result is based on
+expectations from the human user side, which are likely to be refined
+after continued interaction, and after the user gets acquainted with the
+robot's behavior.}. A similar finding is described in
+\cite{hegel_understanding_2008} and \cite{krach_can_2008}. In a user study using
+functional magnetic resonance imagery (fMRI), the authors found that
+participants implicitly attributed human-like qualities, such as mental states,
+to their non-human interaction partner. Indeed, from an early age humans develop
+a tendency to explain one's own and others' actions in terms of beliefs, desires
+and goals,  called \textit{theory of mind}. The theory of mind allows the
+implicit attribution of intentions and other mental states to others
+\citep{premack1978does,leslie_pretense_1987,Frith2003}.  The finding of
+\cite{hegel_understanding_2008} and \cite{krach_can_2008} was evident at the
+behavioral level as well as on the neuro-physiological level: the more the
+human-likeness of the artefactual partner increases, the more brain areas
+associated with theory of mind  get activated \citep{krach_can_2008}.
+\footnote{\hl{Ha! This says that anthropomorphism can also occur on a behavioral
+level, yes! :) so we should also measure anthropomorphism in the behavior.}}
 Implication of human brain area involved in the inference of others` mental
 states has also been shown in response to viewing
-non-anthropomorphic/non-humanoid robotic gadgets whose behavior
-has been described as unpredictable -- but not in response to those whose
-behavior was described as predictable -- a finding also found at the behavioral
-level \citep{Waytz2010}.
-Interestingly, the grey matter volume of a brain area related to theory of mind
-has been correlated to individual's score of anthropomorphism
-\citep{cullen2013individual}.
-
-At lower, more automatic, level, robots have been shown to elicit resonance behaviors in the
-human brain.
-Resonance behaviors \citep{Rizzolatti1999} are mechanisms by which the brain areas involved in the internal representations of an action, an emotion or a sensation are equally recruited during the perception of another individual performing the same action or experiencing the same emotion or sensation.
-The neurons showing resonant properties have been called mirror neurons and
-have been found in a wide range of modalities (motor, emotional etc..)
-\fixme{addref}. Seeing a robotic arm reaching for an object activates the motor mirror neurons the same way as for seeing a human arm reaching for the same object
-\citep{Gazzola2007, oberman_eeg_2007}. However, a study of emotion perception
-on a robotic face found reduced activity in emotional brain
-area known to have mirror properties in response to the robotic face compared to
-a human face \citep{Chaminade2010}. Nevertheless, these authors showed that when
-the participants were explicitly instructed to pay attention to the robot's
-emotional expression, motor mirror neurons get activated.
+non-anthropomorphic/non-humanoid robotic gadgets whose behavior has been
+described as unpredictable -- but not in response to those whose behavior was
+described as predictable -- a finding also found at the behavioral level
+\citep{Waytz2010}.  Interestingly, the grey matter volume of a brain area
+related to theory of mind has been correlated to individual's score of
+anthropomorphism \citep{cullen2013individual}.
+
+At lower, more automatic, level, robots have been shown to elicit resonance
+behaviors in the human brain. Resonance behaviors \citep{Rizzolatti1999} are
+mechanisms by which the brain areas involved in the internal representations of
+an action, an emotion or a sensation are equally recruited during the perception
+of another individual performing the same action or experiencing the same
+emotion or sensation.  The neurons showing resonant properties have been called
+mirror neurons and have been found in a wide range of modalities (motor,
+emotional etc..) \fixme{addref}. Seeing a robotic arm reaching for an object
+activates the motor mirror neurons the same way as for seeing a human arm
+reaching for the same object \citep{Gazzola2007, oberman_eeg_2007}. However, a
+study of emotion perception on a robotic face found reduced activity in
+emotional brain area known to have mirror properties in response to the robotic
+face compared to a human face \citep{Chaminade2010}. Nevertheless, these authors
+showed that when the participants were explicitly instructed to pay attention to
+the robot's emotional expression, motor mirror neurons get activated.
 Interestingly, using electroencephalography,  it has also been shown that
@@
 
-Social psychology offers interesting theories that can be applied to understand people's motivation to anthropomorphize.
-Irrespective of the artifact's characteristics, several psychological determinants have been found to explain a person's tendency to anthropomorphize.
-\cite{epley_seeing_2007} present a ``3-factor theory'' of when people are likely to anthropomorphize based on psychological determinants.
-Namely, the theory suggests that some people are more likely to anthropomorphize when:
+Social psychology, finally, offers theories that apply well to understand
+people's motivation to anthropomorphize. Irrespective of the artifact's
+characteristics, several psychological determinants have been found to explain a
+person's tendency to anthropomorphize. \cite{epley_seeing_2007} present a
+\emph{3-factor theory} of when people are likely to anthropomorphize based on
+psychological determinants. Namely, the theory suggests that some people are
+more likely to anthropomorphize when:
 
@@
 
-The first factor (\textit{elicited agent knowledge}) is a \textbf{cognitive determinant of anthropomorphism} and based on the idea that a person builds a mental model (theory of mind) of the other agent.
-\cite{epley_seeing_2007} suggest that the process of making inferences about non-human agents is based on the activation of knowledge about humans (or the self).
-As mentioned before, when a person builds a mental model of the other (unfamiliar) agent, the question here is why does she draw on knowledge about other humans / herself and not on something else?
-One basic reasons for this is a person's physical constraints of being a human and nothing else.
-Consequently, one has no other experience than the self and in turn people tend to make inferences about others' mental states by relying inordinately on their own mental state.
-\footnote{Using one's own mental states and characteristics as a guide when reasoning about other humans is called ego-centrism.
-In contrast, when using self-knowledge (or knowledge about humans in general) when reasoning about non-human agents, this is called anthropomorphism.
-See \cite{epley_seeing_2007}} Also empirical findings suggest that knowledge about humans in general, or self-knowledge in particular, is likely to serve as a readily accessible base for induction when reasoning about non-human agents.
-This tendency is usually stronger in young children and decreases with cognitive development and the learning to distinguish the self from other humans, and non-human agents.
-
-Both the second factor \textit{effectance} and the third factor \textit{sociality} are \textbf{motivational determinants of anthropomorphism}.
-\textit{Effectance} is understood a person's motivation to interact effectively in one's environment.
-That means, a person is motivated to be able to understand, predict, and reduce uncertainty about her environment and the agents that inhabit it.
-According to \cite{epley_seeing_2007}, \textit{effectance motivation} can lead to anthropomorphism, since anthropomorphism serves as one way to reduce uncertainty and to increase comprehension of events in one's environment.
-Again, also according this factor it can be argued that children are more likely to anthropomorphize than adults.
-As children are in their early stages of life, they are likely to feel more uncertain within their environment, and consequently tend to anthropomorphize more.
+The first factor (\textit{elicited agent knowledge}) is a \emph{cognitive
+determinant} of anthropomorphism and based on the idea that a person builds a
+mental model (theory of mind) of the other agent. \citet{epley_seeing_2007}
+suggest that the process of making inferences about non-human agents is based on
+the activation of knowledge about humans (or the self). As mentioned before,
+when a person builds a mental model of the other (unfamiliar) agent, the
+question here is why does she draw on knowledge about other humans / herself and
+not on something else? One basic reasons for this is a person's physical
+constraints of being a human and nothing else. Consequently, one has no other
+experience than the self and in turn people tend to make inferences about
+others' mental states by relying inordinately on their own mental state
+\footnote{Using one's own mental states and characteristics as a guide when
+reasoning about other humans is called ego-centrism. In contrast, when using
+self-knowledge (or knowledge about humans in general) when reasoning about
+non-human agents, this is called anthropomorphism. See
+\cite{epley_seeing_2007}}.  Also empirical findings suggest that knowledge about
+humans in general, or self-knowledge in particular, is likely to serve as a
+readily accessible base for induction when reasoning about non-human agents.
+This tendency is usually stronger in young children and decreases with cognitive
+development and the learning to distinguish the self from other humans, and
+non-human agents.
+
+Both the second factor \textit{effectance} and the third factor
+\textit{sociality} are \emph{motivational determinants} of anthropomorphism.
+\textit{Effectance} is understood a person's motivation to interact effectively
+in one's environment. That means, a person is motivated to be able to
+understand, predict, and reduce uncertainty about her environment and the agents
+that inhabit it. According to \cite{epley_seeing_2007}, \textit{effectance
+motivation} can lead to anthropomorphism, since anthropomorphism serves as one
+way to reduce uncertainty and to increase comprehension of events in one's
+environment. Again, also according this factor it can be argued that children
+are more likely to anthropomorphize than adults. As children are in their early
+stages of life, they are likely to feel more uncertain within their environment,
+and consequently tend to anthropomorphize more.
 

### 2014-04-04 paper.tex
refined figure anthropomorphism; new bib item; work on sections 4 and 5

@@
 
-As human-likeness itself is a huge dimension\fxwarning{SL: huge dimension?},
+As human-likeness itself is manifold and complex,
 some researchers argue that there might not just be one single type of
@@
     triangles). Several external factors influence the anthropomorphism
-    phenomenon. Person- and artifact-related ones, but also related to the
-context of use as well as the actual time spend interacting with the robot.}
+    phenomenon. Person- and artifact-related characteristics, but also related to the
+context of use as well as the actual time spent interacting with the robot (interaction history).}
 
@@
 
-In the following we will only briefly present the artifact-centered perspective to explain anthropomorphism.
+In the following we will only briefly present the artifact-centered perspective to explain anthropomorphism\footnote{A review of anthropomorphic design of robots can also be found in \cite{fink_anthropomorphism_2012}}.
 Then, we provide a more detailed review and synthesis of literature that applies a human-centered perspective to explain anthropomorphism.
@@
 back to it later, in section \ref{sec:cognitive-expl}.
-
-\fxwarning{SL: maybe add a ref to previous Julia's paper on anthropomorphism?}
 
@@
 associated with theory of mind  get activated \citep{krach_can_2008}.
-\footnote{\hl{Ha! This says that anthropomorphism can also occur on a behavioral
-level, yes! :) so we should also measure anthropomorphism in the behavior.}}
 Implication of human brain area involved in the inference of others` mental
@@
 mirror neurons and have been found in a wide range of modalities (motor,
-emotional etc..) \fixme{addref}. Seeing a robotic arm reaching for an object
+emotional etc.) \fixme{addref}. Seeing a robotic arm reaching for an object
 activates the motor mirror neurons the same way as for seeing a human arm
@@
 \item ~the characteristics of the \textbf{context / situation} in which the interaction occurs, and
-\item ~the fact of the user getting familiar with the robot \textbf{over time} (duration of interaction)
+\item ~the fact of the user getting familiar with the robot \textbf{over time} (duration / history of interaction)
 \end{enumerate}
@@
 Combined with the extensive discussion on the nature and factors of
-anthropomorphism that we proposed at section~\ref{sec:anthropomorphism}, we
+anthropomorphism that we proposed in section~\ref{sec:anthropomorphism}, we
 introduce in the following section a novel qualitative model of the evolution
@@
 \emph{shape} of the model remains however the same and depicts the evolution of
-anthropomorphism over time, \ie the general dynamics of anthropomorphism.\fixme{Last sentence: Do you mean the shape of the curve?
-i would not agree that it remains the same ...
-but say that it shows a general tendency to decrease, however that there might be variations.}
+anthropomorphism over time, \ie the general dynamics of anthropomorphism.\fixme{JF: Last sentence: Do you mean the shape of the curve?
+I would not agree that it remains the same ...
+but say that it shows a general tendency to decrease, however that there might be variations, mostly determined by the 4 factors.}
 
@@
 
-\fxwarning{SL: Mention the pre-interaction phase}
-
 \subsubsection{Initialization Phase\\}
 \label{sec:initialization}
+
+\paragraph{Pre-interaction phase\\}
+\hl{needs to be written, \eg people form expectations \etc and this leads to the ICA (\ICA).}
 
@@
 projection of already known cognitive models onto the robot. We discuss this other
-aspect at section~\ref{sec:cognition-neuroscience}.
+aspect in section~\ref{sec:cognition-neuroscience}.
 
@@
 behaviors (section~\ref{sec:disruptive}) on mutual modelling, and how our models
-relate to the \emph{in-the-moment} versus \emph{reflective} perspectives
-introduced by~\citet{takayama_perspectives_2012}.
+relate to the \emph{in-the-moment} versus \emph{reflective} perspectives on agency in HRI~\citet{takayama_perspectives_2012}.
 
@@
 which are related but do not directly match the three phases of
-the model of the dynamics of anthropomorphism.
+the model of the dynamics of anthropomorphism. Note that these three stages are not mutually exclusive, they may overlap in time.
 
@@
 2.2.2 \fixme{put ref}).
+
+The intuitive anthropomorphization in the cognitive stage 1 might be characteristic of what \cite{takayama_perspectives_2012} calls the \textit{in-the-moment} perspective on agency with a robot compared to the \textit{reflective} perspective (see paragraph ``artifact-centered perspective'' in Section \ref{sec:anthropomorphism}).
+For instance, we reflectively
+might \textit{not} perceive agency in a social robot, but it can feel quite differently
+in the moment of interaction. \cite{takayama_perspectives_2012}
+argues that neglecting to separate reflective perspectives from in-the-moment
+perspectives of agency is one of the major sources of confusion when people talk
+and write about anthropomorphism. There seems to be a disconnection between what
+people consciously perceive and how they respond to stimuli that they may not
+consciously perceive. That means, in the initial phase of interacting with a
+novel device \textit{(initialization)} (see Figure \ref{fig:dynamics}) people might not respond consciously but
+rather mindlessly \citep{nass_machines_2000}, and in turn anthropomorphize more.
+Only after some time of
+\textit{familiarization}, they might respond in a more reflective manner (in turn, the tendency to anthropomorphize might decrease). This
+can be illustrated by the fact that people tend to deny interacting with
+computational systems as if they were people and yet they respond to computers
+in many ways that are remarkably similar to how they respond to people
+\citep{reeves_media_1996}. \cite{takayama_perspectives_2012} also applies a
+cognitive viewpoint on the two different perspectives of in-the-moment \vs
+reflective to illustrate differences. She states that in-the-moment perceptions
+of agency are largely shaped by bottom-up perceptual processes, evoking very
+immediate responses (\eg to the cues emitted by the artifact's design (``artifact-centered perspective''). In contrast, according to Takayama,
+reflective perceptions are more often shaped by top-down processes because of
+the nature of reflective thought.
 
@@
 process.  The result of this third phase would be an iteratively adapted
-cognitive model of the robot. It is also at this last stage that the human might
-modified its own abilities to anthropomorphize, having built a full cognitive
-model of the robot and now being able to attribute internal state to the robot
-through his theory of mind\fxwarning{SL: last part not so clear. Rephrase?}.
-
-\fxwarning{SL: mention that the stages are not mutually exclusive and actually
-overlap over time.}
+cognitive model of the robot. It is also at this last stage that the human might have a
+modified tendency to anthropomorphize, because he/she has built a full cognitive
+model of the robot. Consequently, the human would now be able to attribute appropriate internal states to the robot
+through his/her theory of mind.
 
@@
 shows that unexpected behaviors of the robot can have a notable impact on
-interaction. \hl{cite literature, e.g. cheating robot, disagreeing, disobeying,
-HRI2013 paper}
-This is supported by the results from~\citet{Waytz2010}, mentioned in section
-\ref{sec:explanations}, that show that people attribute more easily
-anthropomorphic features to artefacts when they have unpredictable behaviors.
+interaction. This is supported by the results from~\citet{Waytz2010}, mentioned in section
+\ref{sec:cognitive-expl}, that show that people attribute more easily
+anthropomorphic features to artifacts when they have unpredictable behaviors.
+Also \cite{short_no_2010} found that variations in a robot's behavior (such that it is unexpected) influence people's attribution of mental states and intentionality to a robot.
+Participants who were playing the ``rock-paper-scissors'' game with a robot that tried to cheat (either verbally or in its action), displayed a greater level of social engagement and made greater attributions of mental states.
+However, an unexpected (disruptive) robot behavior might also have a negative effect on user's engagement with the robot.
+For instance, when the user interprets the robot's behavior as a failure, he/she might lose trust in the robot.
+\cite{desai_impact_2013} found that in an interaction scenario, especially early failures of the robot can cause a dramatically lower real-time trust, compared to middle or late drops of reliability of the robot.
 
@@
 to an increase or decrease of the level of anthropomorphism (depicted by the
-spikes on Figure~\ref{fig:dynamics}).
+spikes in Figure~\ref{fig:dynamics}).
 
@@
 explicitly states its failure (for instance, by saying ``I'm lost!''), the
-behavior is then called \emph{transparent} \fixme{cite here, Julia?}
-\hl{(literature on transparency)}, and the user may hypothesize that the
+behavior is then called \emph{transparent} \citep{kim_who_2006}, and the user may hypothesize that the
 robot has \emph{introspective} capabilities (it can reflect on its own internal
@@
 (case I or II), is likely to lead to stronger effects due to a larger delta
-between expectations and actual observed behavior. \hl{(we actually assume that
-anthropomorphism can be radically changing and be a very spontaneous
-"reaction".)}
+between expectations and actual observed behavior.
 
@@
 
-\subsection{\emph{In-the-moment} versus \emph{Reflective} perspectives}
-
-\fxwarning{SL: Bridge + integration in the section 4 TDB}
-
-Perception of agency can be treated as anthropomorphism.
-\citep{takayama_perspectives_2012} proposes to differentiate between a
-\textit{in-the-moment} and \textit{reflective} perspective to better understand
-how human users perceive agency in robots.\footnote{``The other important
-distinction between the two perspectives is the \hl{cognitive processes} that
-they engage.''} According to Takayama, an \textit{in-the-moment} perspective
-refers to one's most immediate (sometimes visceral) sense in a situation. In
-contrast, a \textit{reflective} perspective refers to one's sense of a situation
-upon more distanced cogitation and consideration. For instance, we reflectively
-might not perceive agency in a social robot, but it can feel quite differently
-in the moment of interaction. A critical dimension of agency is the perspective
-from which something seems to have agency.  \cite{takayama_perspectives_2012}
-argues that neglecting to separate reflective perspectives from in-the-moment
-perspectives of agency is one of the major sources of confusion when people talk
-and write about anthropomorphism. There seems to be a disconnection between what
-people consciously perceive and how they respond to stimuli that they may not
-consciously perceive.  That means, in the initial phase of interacting with a
-novel device \textbf{(initialization)} people might not consciously respond but
-rather mindlessly \citep{nass_machines_2000}. Only after some time of
-\textbf{familiarization}, they might respond in a more reflective manner. This
-can be illustrated by the fact that people tend to deny interacting with
-computational systems as if they were people and yet they respond to computers
-in many ways that are remarkably similar to how they respond to people
-\citep{reeves_media_1996}.  \cite{takayama_perspectives_2012} also applies a
-cognitive viewpoint on the two different perspectives of in-the-moment \vs
-reflective to illustrate differences. She states that in-the-moment perceptions
-of agency are largely shaped by bottom-up perceptual processes, evoking very
-immediate responses (\eg to the cues emitted by the artifact's design, see
-Section \ref{sec:anthropomorphic-design}).  In contrast, according to Takayama,
-reflective perceptions are more often shaped by top-down processes because of
-the nature of reflective thought.
+%\subsection{\emph{In-the-moment} versus \emph{Reflective} perspectives}
+%
+%\fxwarning{SL: Bridge + integration in the section 4 TDB}
+%
+%\hl{(we actually assume that
+%anthropomorphism can be radically changing and be a very spontaneous
+%"reaction".)}
 

### 2014-04-04 paper.tex
Re-organize section hierarchy in Section 3

@@
 
-\paragraph{Artifact-centered perspective on anthropomorphism\\}
+\subsection{Artifact-centered perspective on anthropomorphism}
 
@@
 
-\paragraph{Human-centered perspective on anthropomorphism\\}
+\subsection{Human-centered perspective on anthropomorphism}
 
@@
 
-\subsection{Developmental psychology research on the attribution of animacy and intention}
+\subsubsection{Developmental psychology research on the attribution of animacy and intention}
 \label{sec:developmental-expl}
@@
 
-\subsection{Cognitive science research, the mental model theory (Theory of Mind)
+\subsubsection{Cognitive science research, the mental model theory (Theory of Mind)
 and neural correlates of anthropomorphism}
@@
 
-\subsection{Social psychology research: a 3-factor theory of anthropomorphism}
+\subsubsection{Social psychology research: a 3-factor theory of anthropomorphism}
 \label{sec:psychological-factors}

### 2014-04-04 paper.tex
started measuring anthropomorphism paragraph

@@
 instance, some researchers refer to \textit{``the robot's level of
-anthropomorphism''} \citep{bartneck_is_2007}, whereas others disagree to such a
+anthropomorphism''} \citep{bartneck_is_2007,feil-seifer_human-robot_2008}, whereas others disagree to such a
 statement because they understand that a system or artifact itself does not
@@
 
-However, we should \textit{not} use the term \emph{anthropomorphism} to refer to
-the design of a non-human agent or artifact. To refer to an imitation of
-human-like form in the \textit{design} of artificial agents, we use the term
+However, despite the fact that ``anthropomorphism'' literally means ``human form'' we propose that the term should \textit{not} be used to refer to
+the \textit{form / design} of a non-human agent or artifact. To refer to an imitation of
+human-like \textit{form / design} of artificial agents, we propose to use the term
 \textbf{anthropomorphic design}. This explicit terminology prevents the commonly
@@
 
-\fxwarning{To be completed/rephrased into a discussion}
-
-\citep{ruijten_introducing_2014}
+%\fxwarning{To be completed/rephrased into a discussion}
+
+With this extended understanding of anthropomorphism being determined by multiple factors and showing dynamics over time, it also becomes questionable if the metrics and techniques that are currently used to measure anthropomorphism are sufficient.
 

### 2014-04-04 paper.tex
discussion section

@@
 
-\subsubsection{Developmental psychology research on the attribution of animacy and intention}
+\subsubsection{Developmental psychology research on the attribution of animacy and intention\\}
 \label{sec:developmental-expl}
@@
 
-\subsubsection{Cognitive science research, the mental model theory (Theory of Mind)
-and neural correlates of anthropomorphism}
+\subsubsection{Cognitive science research, Theory of Mind, and neural correlates of anthropomorphism\\}
 \label{sec:cognitive-expl}
@@
 
-\subsubsection{Social psychology research: a 3-factor theory of anthropomorphism}
+\subsubsection{Social psychology research: a 3-factor theory of anthropomorphism\\}
 \label{sec:psychological-factors}
@@
 anthropomorphism.
-
 We proposed that \ICA is built on three factors: user's \emph{personality},
@@
 
-\subsection{Effect of time / familiarization on anthropomorphism}
-
 \fixme{Discuss here the general findings of the paper: the global shape of the
 model of the dynamics, ... // JF: yep, I agree, we should also come back to our initial hypotheses}
+
+\subsection{Effect of time / familiarization on anthropomorphism}
 
@@
 
+%Also, the methods and measurements applied to study anthropomorphism appear insufficient, when applying a holistic understanding of anthropomorphism emerging from an interaction between a human user and a robot, for instance.
+Our point here is that to study a phenomenon as complex as anthropomorphism, we believe that one needs to take into account many factors (see Section \ref{sec:multi-factors}), besides looking at the human-like design of the artifact.
+
 With this extended understanding of anthropomorphism being determined by multiple factors and showing dynamics over time, it also becomes questionable if the metrics and techniques that are currently used to measure anthropomorphism are sufficient.
-
-Also, the methods and measurements applied to study anthropomorphism appear insufficient, when applying a holistic understanding of anthropomorphism emerging from an interaction between a human user and a robot, for instance.
-Our point here is that to study a phenomenon as complex as anthropomorphism, we believe that one needs to take into account many factors (see Section \ref{sec:multi-factors}), besides looking at the human-like design of the artifact.
+We would like to discuss two issues: the scenario in which anthropomorphism is measured, and how, with which means it is assessed.
+
+One needs to keep in mind that anthropomorphism arises in an interaction.
+We believe that as such, anthropomorphism can be better understood when studied and measured in a real, direct human-robot interaction compared to a mediated interaction.
+In a direct interaction scenario one could also take the human's behavior into account, as it seems to reflect an anthropomorphic interaction \citep{krach_can_2008,hegel_understanding_2008}.
+Of course, the scenario and measurements used depend on the research questions, so a direct human-robot interaction might not always be preferred.
+
 However, most of the
-experiments that investigate anthropomorphism in robotics are conducted in
-controlled lab-settings during short-term human-robot interactions. This
-experimental setting can be critical for studying
-anthropomorphism and findings might possibly lead to interpretations that would not be generalizable to natural settings or real interaction scenarios.
-For instance, some studies are about showing pictures of different robots to human subjects and then asking them how "human-like" they would rate these robots.
-What points of reference do the participants have in this setting?
-What can you really tell from a picture?
-I found that some normal people totally misinterpret the size / height of a robot, when it is not indicated.
-Also, when showing only pictures, movements, behaviors, materials, and so forth are totally disregarded.
-However, these aspects are also crucial to assess how "human-like" a robot appears.
-Last but not least, it has been found that "human-likeness" is a quite diverse and abstract term that includes many things.
-Instead of asking such a big question, \cite{kahn_jr._robotic_2006} suggest to ask for more concrete constructs that are typical or unique of the concept of "human-likeness", such as being hungry or feeling guilty.
-For instance, \cite{ruijten_introducing_2014} propose a 25 concrete questions to measure anthropomorphism along a scale that accounts for lower and higher levels of it.
-Some studies (e.g. exploring characteristics of the "uncanny valley") also seem to contrast two or
-more different anthropomorphic or mechanical systems that might not be
-appropriate for comparison given the complex context.
-
-Measuring anthropomorphism is challenging because the phenomenon is partially
+experiments that investigate anthropomorphism in HRI are conducted in
+controlled lab-settings during a short-term scenario.
+For instance, pictures or videos of different robots are shown to human subjects who subsequently fill in a questionnaire, to assess how far the different types of robots were perceived human-like.\footnote{It can already be critical to not indicate the height / size of a robot when it is pictured or presented in a video.
+We cannot assume that without any point of reference, lay people estimate correctly the height of ASIMO or Nao, for instance, they might think these humanoid robots are the same size as a Barbie doll.
+Also, when showing a picture, the movements, behaviors, materials of a robot, and so forth are totally disregarded.
+However, these aspects are also crucial features of a robot, impacting how human-like it appears.}
+We think that such
+experimental settings have limitations for studying a social phenomenon like
+anthropomorphism. The critical question is: can anthropomorphism really be measured in a post-interaction closed questionnaire or by rating scales?
+Findings might possibly lead to interpretations that would not be generalizable to natural settings or real interaction scenarios (which is always an issue in social science research).
+
+Regarding the second issue, how and with which means anthropomorphism is measured, the central point is that ``human-likeness'' itself is complex and manifold.
+It as a quite diverse and abstract concept, and instead of asking such a vague question, whether a robot is human-like or not, \cite{kahn_jr._robotic_2006} suggest to ask for more concrete constructs that are typical or unique of the concept of ``human-likeness''.
+For instance, \cite{ruijten_introducing_2014} propose a 25-item questions to measure various concrete aspects of human-likeness.
+Consequently, anthropomorphism can be modeled along a scale that accounts for lower and higher levels of it.
+
+Still, we also feel that measuring anthropomorphism (or social engagement with a robot) is challenging because the phenomenon is partially
 unconscious, its mediation is largely subject-dependent\fxnote{Should we put
@@
 
-We present in this section the methodology and techniques we have relied on to
-assess anthropomorphic projections in two unrelated studies, the Roomba
-experiment~\cite{fink_living_2013}, and the Domino study.
-
-\paragraph{Quantitative assessment of anthropomorphism} Quantitative data are
-acquired by systematic annotations of human- robot interactions on video records
-of the experiments. Six classes of interactions were identified as reflecting
-active commitment of the users in the interaction (gestures, touches, talk to
-the robot, show something to the robot, misbehave, look at the experimenter
-because worried by the robot's behavior)
-
-\paragraph{Qualitative assessment of anthropomorphism} The main tools for
-qualitative measurement of anthropomorphic effect are questionnaires. We have
-explored both Likert-scale and open questions. In the Domino study,
-questionnaires were analyzed such as points are attributed for key answers,
-leading to a qualitative score:
+We present in this section the methodology and techniques that we used to
+assess anthropomorphic projections in the child-robot interaction study, called the Domino study (see Section \ref{sec:field-results}, and Figure \ref{fig:ranger}).
+
+\paragraph{Qualitative and quantitative assessment of anthropomorphism in human's behavior\\}
+
+Anthropomorphism can possibly be observed in how humans behave toward a non-human agent (social human-like engagement).
+Based on video recordings of the Domino experiment, we acquired both quantitative and qualitative behavioral data that reflects anthropomorphism.
+
+Quantitative data are
+acquired by systematic annotations of specific types of actions in the video records of the interaction. Six classes of interactions were identified as reflecting
+active commitment and/or an anthropomorphic interaction of the user: gestures toward the robot, touching the robot, direct talk to
+the robot, showing something to the robot, mistreating the robot (\eg kicking it), and looking at the experimenter because worried by the robot's behavior.
+
+By considering the number of occurrences, the duration, and consequently the frequency of these types of interaction, we can make statements of how far the robot is anthropomorphized in an interaction (based on quantitative data).
+
+We assessed anthropomorphic interactions qualitatively by looking at specific instances of human-social cues in the human's behavior, such as: facial expressions, observable emotional reactions (\eg surprised, high pitch voice or shouting to the robot), eye-contact with the robot, turn-taking gestures, greeting (waving) gestures.
+These are just suggestions of actions that might reflect anthropomorphism.
+These actions partly overlap with the quantitative assessment, however it is generally advisable to combine the two.
+
+\paragraph{Qualitative assessment of anthropomorphism when verbally referring to the robot (reflection)\\}
+
+The main tools for
+qualitative measurement of anthropomorphic effect are questionnaires and semi-structured interviews. We have
+explored both rating-scales in a questionnaire, and open questions in an interview (inspired from \citep{kahn_jr._robotic_2006,weiss_i_2009}).
+In the Domino study, interviews were transcribed and participant's answers to the key questions that were assessing an anthropomorphic projection onto the robot, were analyzed.
+For instance, one question to see how far children would ascribe moral standing to the robot was \emph{``If you had this robot at home, and you were to leave for 2 weeks of holidays, would it be ok to leave the robot alone at home?''}.
+A point for anthropomorphism was counted, when the participant's answer indicated an anthropomorphic view of the robot.
+This process led to a ``qualitative score'' that reflects how far the robot is anthropomorphized.
+We used the following constructs to measure how far the robot is perceived as a human-like agent:
 
 \begin{itemize}
-    \item Spontaneously ascribe feelings or states (2 points) {\it Robot is
+    \item ~Spontaneously ascribe inner states, {\it eg. robot is
         hungry, tired}
-    \item Ascribe ``own will'' (1--3 points) {\it Robot could leave room, does not
+    \item ~Ascribe ``own will'', {\it eg. robot could leave room by itself, does not
         always obey, could do a b\^{e}tise...}
-    \item View robot as friend (1 point)
-    \item Ascribe cognitive abilities (0.5--1 point) {\it Robot is able to see,
+    \item ~Describe robot as friend
+    \item ~Ascribe cognitive abilities, {\it eg. robot is able to see,
         able to hear}
-    \item Belief robot has feelings (2 points)
-    \item Give anthropomorphic reasons for
+    \item ~Belief robot has feelings, {\it eg. robot can be happy or sad}
+    \item ~Give anthropomorphic explanation for
         \begin{itemize}
-            \item not leaving robot alone (1--3 points) {\it Would be sad when
-                left alone}
-            \item misbehavior (1 point) {\it Robot wants to make a tour, doesn't
+            \item ~Why robot can (not) leave room alone {\it eg. it would be sad when left alone}
+            \item ~Misbehavior {\it eg. robot wants to make a tour, doesn't
                 like to play any longer}
@@
 
+One main challenge that robots with applications in daily life contexts face is to sustain long-term interaction.
+
 \paragraph{Impact of the behavioral complexity of robots}
@@
 To remain tractable, most experiments, and even more when they investigate
-long-term interactions, are carried with robots exhibiting relatively simple
+long-term interactions, are carried out with robots exhibiting relatively simple
 behaviors. In our model, the maximum level of anthropomorphism \AntMax is
-reached at the end of the novelty effect, and then decrease. A natural question
+reached at the end of the novelty effect, and then decreases. A natural question
 is whether we can design robots such as \AntMax remains high, possibly higher
@@
 for the robot to evolve over time and adapt its behavior to the user as the user
-familiarizes itself with the robot (\ie, \emph{co-familiarize}), seems to play a
+familiarizes his/herself with the robot (\ie, \emph{co-familiarize}), seems to play a
 key role.
 
-...
+\fixme{JF: Severin, I am not sure what you want to say here.}
 
@@
 
-Another critical point with the use of human-like form in artificial agents are 
-ethical aspects. For instance, we need to consider how far we actually want an 
-\textit{artificial agent} to resemble a human -- or ourself. Even though we do not 
-discuss these aspects in this article, we think the HRI / robotics community needs 
-to consider questions of how far an artificial agent should act ``as if it would be 
-social'' toward humans. What implications does an anthropomorphic design of robots 
-have? What happens as soon as the artificial agent is considered a \textit{moral 
-agent} \cite{sullins_when_2006}? Using \textit{socially interactive robots} in 
-contexts involving elderly care or rehabilitation for disabled / handicapped 
-persons, autistic children is a controversially discussed topic 
-\cite{robins_robots_2005}.
+After all discussion, there remains the question how far a sustained anthropomorphic (human social) interaction between a human and a non-human can be favored, regarding ethical aspects.
+We need to rethink carefully the consequences that emotional bonds between humans and robots can have.
+They might be beneficial on one hand but can also hold negative implications.
+How far should a robot's design encourage us to lastingly project feelings or intentions to it?
+Why should a machine even react to us as if it had emotions?
+Can this be the reality we want to live in?
+What happens as soon as the artificial agent is considered a \textit{moral agent} \cite{sullins_when_2006}?
+Also, the use of \textit{socially interactive robots} in
+contexts involving elderly care or in rehabilitation and with autistic children is a controversially discussed topic 
+\cite{robins_robots_2005}. Do we want robots to comfort us; robots that make us eventually even falling in love with them?
+The anthropomorphic design of robots is critical. Why do we even need this? The HRI / robotics community needs to discuss these and other questions.
 

### 2014-04-07 paper.tex
refinements sections 1,2,3

@@
 
-\title[The Dynamics of Anthropomorphism]{The Dynamics of Anthropomorphism in Human-Robot Interaction}
+\title[Dynamics of Anthropomorphism]{Dynamics of Anthropomorphism in Human-Robot Interaction}
 \author[\firstAuthorLast ]{\Authors}
@@
 A phenomenon that is often studied related to the human-like design of 
-robots is anthropomorphism. While people's tendency to perceive human-like 
-characteristics in robots is a commonly discussed trait of 
-human-robot interaction (HRI), the phenomenon paradoxically lacks formal 
+robots is \textit{anthropomorphism} -- people's tendency to perceive human-like 
+characteristics in non-human agents. While this is a commonly discussed trait of 
+human-robot interaction (HRI), the phenomenon paradoxically appears to lack formal 
 grounds. Based on findings from several empirical studies and a 
@@
 formalize qualitative differences and dynamics over time in how 
-humans anthropomorphize non-human agents. Based on several key factors, 
+humans anthropomorphize non-human agents. We propose several key factors that determine anthropomorphism, 
 namely the 
 design of the non-human agent, the individual characteristics of the human 
-user, and the context of use, we found that anthropomorphism changes in a 
-non-linear way with growing experience of the user with the system. To 
-account for these variances, we propose an initial model that we call 
-\textit{``Dynamics of Anthropomorphism''}. Focusing on human-robot 
-interactions, we present a cognitive interpretation that considers 
-the described dynamics. Finally, we would like to discuss how others can 
-apply our model to measure and describe better the complexity in human's 
+user, and the context of use. An initial model that we call 
+\textit{``Dynamics of Anthropomorphism''} tries to formalize the qualitative changes in anthropomorphism over time. To 
+account for these variances, our model describes the non-linear relationship between anthropomorphic effects of a human-robot interaction and the human user's growing experience with the system.
+We also present a cognitive interpretation that considers 
+these described dynamics. Further, we discuss scenarios and techniques to measure anthropomorphism. Finally, we make suggestions how others can 
+apply our model to better describe the complexity in human's 
 tendency to perceive human-like characteristics in non-human agents.
@@
 it. 
-However, at a certain point as the non-human agent
-approaches but fails to closely resemble a human, the evoked valence in the
-human user suddenly turns into a negative uncanny feeling of what
-\cite{mori_uncanny_1970} describes as disgust and revulsion. This, in turn,
-might lead to rejection of the non-human agent. The Uncanny
-Valley hypothesis predicts that with further increasing the human-likeness of
-the non-human agent such that it appears so realistic that it is not
-distinguishable from a human but perceived to be human, the effect is again a
-positive one, reflecting feelings and engagement that are similar as those
-evoked by a human-human interaction. 
-Of course, developers and designers of artificial agents
-(\eg virtual characters, robots) try to exploit the positive effects of 
-\textbf{anthropomorphic form} and avoid ``falling'' into this Uncanny Valley.
-Consequently, there is a considerable research effort to
-better understand the boundaries of anthropomorphic design and their effects
-on the interaction and experience. To date, findings have been however
-inconsistent \citep{cheetham_human_2011}.
-
-A phenomenon that is often studied related to the human-like design of objects and 
-artificial agents is \textbf{anthropomorphism}.
+%
+%However, at a certain point as the non-human agent
+%approaches but fails to closely resemble a human, the evoked valence in the
+%human user suddenly turns into a negative uncanny feeling of what
+%\cite{mori_uncanny_1970} describes as disgust and revulsion. This, in turn,
+%might lead to rejection of the non-human agent. The Uncanny
+%Valley hypothesis predicts that with further increasing the human-likeness of
+%the non-human agent such that it appears so realistic that it is not
+%distinguishable from a human but perceived to be human, the effect is again a
+%positive one, reflecting feelings and engagement that are similar as those
+%evoked by a human-human interaction. 
+%Of course, developers and designers of artificial agents
+%(\eg virtual characters, robots) try to exploit the positive effects of 
+%\textbf{anthropomorphic form} and avoid ``falling'' into this Uncanny Valley.
+%Consequently, there is a considerable research effort to
+%better understand the boundaries of anthropomorphic design and their effects
+%on the interaction and experience. To date, findings have been however
+%inconsistent \citep{cheetham_human_2011}.
+
+A phenomenon that is often studied related to this is \textbf{anthropomorphism}.
 Along this line, this article aims at fostering a better understanding of
@@
 
-\begin{figure}[h!]
+\begin{figure}[b]
         \centering
@@
         \end{subfigure}
-        \caption{Children`s interaction with Ranger, and their anthropomorphic projections onto the robot.
-Overall, large variations of both children`s behavior and their perception of the robot were found but seemed to be correlated to each other.}
+        \caption{Children's interaction with Ranger, and their anthropomorphic projections onto the robot.
+Overall, large variations of both children's behavior and their perception of the robot were found but seemed to be correlated to each other.}
     \label{fig:ranger}
@@
 These first remarks lead to the main question we attempt to address in this
-article: how can we understand \emph{anthropomorphism} as a whole, \hl{and in such a
-way that is support improved human-robot interactions?}\fixme{JF: something's wrong with this sentence}
+article: how can we understand \emph{anthropomorphism} as a whole, and in such a
+way that it supports or improves human-robot interaction?
 
@@
 \end{enumerate}
+
+Further, we would like to investigate the link between the variances in anthropomorphism and the correlating cognitive states.
 
@@
 Literature on anthropomorphism is quite diverse.
-We would like to point out that there exist different and partly conflicting definitions of the term anthropomorphism, and that in general, the \textit{terminology} is not clear.
-Probably as a result of this, there also exist different understandings of the \textit{phenomenon} that the term `anthropomorphism' describes.
+There exist different and partly conflicting definitions of the term anthropomorphism, and that in general, the \textit{terminology} is not clear.
+Probably as a result of this, there also exist different understandings of the \textit{phenomenon} that the term ``anthropomorphism'' describes.
  In this section we will first give an overview on the diversity of terms and
@@
 Originally, the term \textbf{anthropomorphism} comes from the Greek
-\textit{anthropos} for ``man'' (or ``human'') and \textit{morphe} for `form /
-structure' (or `shape'). Anthropomorphism is generally understood as people's
+\textit{anthropos} for ``man'' (or ``human'') and \textit{morphe} for ``form /
+structure'' (or ``shape''). Anthropomorphism is generally understood as people's
 tendency to perceive a non-human agent as if it had some human characteristics
@@
 anthropomorphism can alternatively be understood as \textbf{humanization} or
-\textbf{personification} of anything other than a human being\footnote{There
+\textbf{personification} of anything other than a human being.\footnote{There
 exist also the phenomenons inverse to anthropomorphism, which can be found
@@
 \citep{haslam_dehumanization:_2006}, or \textbf{mechanomorphism}
-\citep{caporael_anthropomorphism_1986}.}. Robots can
+\citep{caporael_anthropomorphism_1986}.} Robots can
 both be animized and anthropomorphized, but often the difference is not made.
@@
 \textit{animism}, as animate life is not a \textit{uniquely} human-like
-characteristic\footnote{For the whole list and more details, the reader may
-refer to the original work \citep{epley_when_2008}.}.
+characteristic.\footnote{For the whole list and more details, the reader may
+refer to the original work \citep{epley_when_2008}.}
 
@@
 
-In the following we will only briefly present the artifact-centered perspective to explain anthropomorphism\footnote{A review of anthropomorphic design of robots can also be found in \cite{fink_anthropomorphism_2012}}.
+In the following we will only briefly present the artifact-centered perspective to explain anthropomorphism.
+A review of anthropomorphic design of robots can also be found in \cite{fink_anthropomorphism_2012}.
 Then, we provide a more detailed review and synthesis of literature that applies a human-centered perspective to explain anthropomorphism.
@@
 and in turn apply human-human social schemas and norms to the occurring
-interactions.  \cite{takayama_perspectives_2012} propose to refer to this
+interactions.  \cite{takayama_perspectives_2012} proposes to refer to this
 immediate (sometimes visceral) sense in a situation as \textit{in-the-moment},
@@
 forces, religious agents, technological gadgets, or mechanical devices
-\citep{epley_when_2008}\footnote{According to \citet{epley_when_2008}, a
+\citep{epley_when_2008}.\footnote{According to \citet{epley_when_2008}, a
 non-human agent can be anything that acts -- or is believed to act -- with
-apparent independence.}. One common reason for anthropomorphism is that by
+apparent independence.} One common reason for anthropomorphism is that by
 perceiving some human-like characteristics in the non-human agent, this agent is
@@
 commonly anthropomorphize their pets, by ascribing mental states, intentions or
-feelings to them\footnote{Interestingly, pet-ownership seems to have a
+feelings to them.\footnote{Interestingly, pet-ownership seems to have a
 significant impact on human-robot interaction: several studies suggest that
 pet-owners are more likely to anthropomorphize technologies and robots than
-non pet-owners}. But how can these motivations behind anthropomorphism be
+non pet-owners} But how can these motivations behind anthropomorphism be
 explained from a human-centered point of view?
@@
 whether they are using anthropomorphism in a metaphoric sense (because their
-conceptions of the world and of the living are not yet fully formed). Later
-however, two famous experiments by \cite{heider_experimental_1944} and
+conceptions of the world and of the living are not yet fully formed). However, experiments by \cite{heider_experimental_1944} and
 \cite{michotte_perception_1963} showed that also adult participants attribute
@@
 elaborate stories, attributing motivations, emotions and relationships between
-the objects\footnote{For more details, the reader may refer to the ``attribution
-theory''.}.
+the objects.\footnote{For more details, the reader may refer to the ``attribution
+theory''.}
 
@@
 tend to hold richer mental models of anthropomorphic robots in contrast to
-mechanic ones \citep{kiesler_mental_2002}\footnote{Later in this article,
+mechanic ones \citep{kiesler_mental_2002}.\footnote{Later in this article,
 we may however come to question how far this result is based on
@@
 after continued interaction, and after the user gets acquainted with the
-robot's behavior.}. A similar finding is described in
+robot's behavior.} A similar finding is described in
 \cite{hegel_understanding_2008} and \cite{krach_can_2008}. In a user study using
@@
 associated with theory of mind  get activated \citep{krach_can_2008}.
-Implication of human brain area involved in the inference of others` mental
+Implication of human brain area involved in the inference of others' mental
 states has also been shown in response to viewing
@@
 mirror neurons and have been found in a wide range of modalities (motor,
-emotional etc.) \fixme{addref}. Seeing a robotic arm reaching for an object
+emotional \etc). Seeing a robotic arm reaching for an object
 activates the motor mirror neurons the same way as for seeing a human arm
@@
 mind but also the unpredictable feature of the agent behavior alone seems to be
-sufficient. Low-level mechanisms of the brain that allow humans to map others`
+sufficient. Low-level mechanisms of the brain that allow humans to map others'
 motor behaviors into their own repertoire are equally elicited when perceiving a
@@
 experience than the self and in turn people tend to make inferences about
-others' mental states by relying inordinately on their own mental state
+others' mental states by relying inordinately on their own mental state.
 \footnote{Using one's own mental states and characteristics as a guide when
@@
 non-human agents, this is called anthropomorphism. See
-\cite{epley_seeing_2007}}.  Also empirical findings suggest that knowledge about
+\cite{epley_seeing_2007}.} Also empirical findings suggest that knowledge about
 humans in general, or self-knowledge in particular, is likely to serve as a
@@
 In lack of social connections to other humans (\etc friends, family, colleagues), a person is more likely to compensate these social connections by anthropomorphizing non-human agents.
-In other words \textit{"[...] those who are chronically lonely should be more likely to anthropomorphize nonhuman agents than those who are more chronically connected"} \citep{epley_seeing_2007}.
-Importantly for anthropomorphism, this social connection often appears to be satisfied by connections with \textit{"two of the most commonly anthropomorphized non-human agents, namely pets and religious agents"} \citep{epley_seeing_2007}.
+In other words \textit{``[...] those who are chronically lonely should be more likely to anthropomorphize nonhuman agents than those who are more chronically connected"} \citep{epley_seeing_2007}.
+Importantly for anthropomorphism, this social connection often appears to be satisfied by connections with \textit{``two of the most commonly anthropomorphized non-human agents, namely pets and religious agents"} \citep{epley_seeing_2007}.
 Thus, the motivation of being socially connected increases the tendency to anthropomorphize non-human agents because first sociality motivation increases the tendency to perceive human-like characteristics and traits even in non-human agents, and second it increases the tendency to search for sources of social connection in one's environment.
@@
 More concretely, when seeking to understand why anthropomorphism in an interaction between a human and a non-human artifact happens, most attention is given to the artifact and/or to the human.
-We agree that these two are the essential `players' of anthropomorphism (see Figure \ref{fig:anthropofig}).
-Indeed and, as outlined before, research has shown that both the human and the artifact are not only the two players of anthropomorphism but also the two main `factors' that can promote or hinder anthropomorphism.
+We agree that these two are the essential ``players'' of anthropomorphism (see Figure \ref{fig:anthropofig}).
+Indeed and, as outlined before, research has shown that both the human and the artifact are not only the two players of anthropomorphism but also the two main ``factors'' that can promote or hinder anthropomorphism.
 
@@
 anthropomorphism is a function of a vector of robot's traits $R = \{r_0,...,r_n\}$, a vector human
-determinants $H = \{h_0,...,h_n\}$, a set of interaction situations that build
-an interaction context $C = \{s_0,...,s_n\}$, and the duration / history of the
+determinants $H = \{h_0,...,h_n\}$, characteristics of the interaction context $C = \{c_0,...,c_n\}$, and the duration / history of the
 interaction itself, $t$.
@@
 (Figure~\ref{fig:dynamics},~\citep{lemaignan2014dynamics}) represents how the
-level of `anthropomorphic effects'~\Ant[R,H,C,t] (\ie the observable
+level of ``anthropomorphic effects''~\Ant[R,H,C,t] (\ie the observable
 manifestations of anthropomorphism) evolves over a long-term human-robot
-interaction.\footnote{We cannot make a precise statement about how long `long-term' interaction has to be to be considered as such.
-It seems to be practical to not speak of `several days' or `weeks' but to rather consider the duration and frequency of the actual interactions with the artifact.
-One could probably call this the `interaction history'.}
+interaction.\footnote{We cannot make a precise statement about how long ``long-term'' interaction has to be to be considered as such.
+It seems to be practical to not speak of ``several days'' or ``weeks'' but to rather consider the duration and frequency of the actual interactions with the artifact.
+One could probably call this the ``interaction history''.}
 
@@
  The general
-\emph{shape} of the model remains however the same and depicts the evolution of
-anthropomorphism over time, \ie the general dynamics of anthropomorphism.\fixme{JF: Last sentence: Do you mean the shape of the curve?
-I would not agree that it remains the same ...
-but say that it shows a general tendency to decrease, however that there might be variations, mostly determined by the 4 factors.}
+\emph{shape} of the curve remains however the same and depicts the evolution of
+anthropomorphism over time, \ie the general dynamics of anthropomorphism.
 
@@
 The reason for this is that the message that design tries to make, always lies in the eye of the beholder.
-No matter how much effort a designer spends in making the `message' of the artifact's design clear, there is always some scope and creative freedom in how the design is interpreted by the beholder.}
+No matter how much effort a designer spends in making the ``message'' of the artifact's design clear, there is always some scope and creative freedom in how the design is interpreted by the beholder.}
 

### 2014-04-07 paper.tex
more refinements, mostly sections 4,5,6,7

@@
 
-\subsection{Our acception of anthropomorphism and related terminology}
+\subsection{Terminology used in this article}
 
@@
 
-\subsubsection{Initialization Phase\\}
-\label{sec:initialization}
-
-\paragraph{Pre-interaction phase\\}
-\hl{needs to be written, \eg people form expectations \etc and this leads to the ICA (\ICA).}
-
-\paragraph{Initial Capital of Anthropomorphism\\}
+\paragraph{Pre-interaction phase and Initial Capital of Anthropomorphism (ICA)\\}
 \label{sec:ica}
@@
 
-\paragraph{The Novelty Effect\\}
-\label{sec:noveltyeffect}
-
+\subsubsection{Initialization Phase\\}
+\label{sec:initialization}
+
+%\paragraph{The Novelty Effect\\}
+%\label{sec:noveltyeffect}
+
+We assume that the short phase of initialization is strongly affected by the so-called novelty effect.
 Novelty effects have been described with interactive technologies in general \citep{rogers_diffusion_1995} and also in several long-term HRI studies in workplaces \citep{huttenrauch_fetch-and-carry_2003,mutlu_robots_2008}, in schools and public places \citep{gockley_designing_2005,kanda_interactive_2004,kanda_communication_2005}, or elder care centers \citep{sabelli_conversational_2011}.
@@
 cleaning robots in households \citep{fink_living_2013}. The observed scenario describes how an elderly
-woman (71 years, living on her own with a little dog in a small row house) was
+woman (E., 71 years, living on her own with a little dog in a small row house) was
 setting up and using the robot for the first time during about 10 minutes.
 
-The woman (E.) is reading aloud parts of the ``quick start manual'': \emph{``When
-Roomba senses dirt, the blue dirt detect light is lit and Roomba cleans more
-intensely in that area.''} She laughs and turns to the robot, talking directly to
-it \emph{``Today you can light up darling!''}. E. carries the Roomba to the entrance
-door and puts it on the floor [floor type: tiles, partially covered with little
-Persian carpets], she explains \emph{``It has to start from here, this is where
-you enter the house!''}. After pressing the CLEAN button, the robot quickly gets
-stuck with the carpet in the entrance hall, consequently it reports error 1 [
-two-tone \textit{``uh-oh''} sound followed by a narrated voice that starts off with \textit{``error
-1''}]. E. is very surprised \emph{``What, it is even talking to me?''}, she lifts the
-robot off and puts it back for cleaning. At several occasions, while watching
+%The woman (E.) is reading aloud parts of the ``quick start manual'': \emph{``When
+%Roomba senses dirt, the blue dirt detect light is lit and Roomba cleans more
+%intensely in that area.''} She laughs and turns to the robot, talking directly to
+%it \emph{``Today you can light up darling!''}. E. carries the Roomba to the entrance
+%door and puts it on the floor [floor type: tiles, partially covered with little
+%Persian carpets], she explains \emph{``It has to start from here, this is where
+%you enter the house!''}. After pressing the CLEAN button, the robot quickly gets
+%stuck with the carpet in the entrance hall, consequently it reports error 1 [
+%two-tone \textit{``uh-oh''} sound followed by a narrated voice that starts off with \textit{``error
+%1''}]. E. is very surprised \emph{``What, it is even talking to me?''}, she lifts the
+%robot off and puts it back for cleaning.
+At several occasions, while watching
 how the robot moves around and cleans, E. makes compliments to the robot:
@@
 talking directly to the robot, or asking it questions (though it doesn't
-recognize speech); giving it nick-names or ascribing a gender (\emph{``darling''}
-/ \emph{``she''}); praising the robot (\emph{``Good job!''}); using pointing
-gestures toward the robot, or trying to direct it around with commands; attributing
+recognize speech); giving it nick-names or ascribing a gender, praising the robot, using pointing
+gestures toward the robot, or trying to direct it around with commands, and attributing
 a personal preference / intention to the robot (\emph{``she loves the hall!''}).
@@
 effects were likely due to the novelty of the robot, and the fact that E. was not familiar with the robot and its behavior.
-As \cite{persson_anthropomorphism_2000} names it: \textit{``Anthropomorphism is a way of making sense of complex behavior in the world around us.''}.
-Thus, as soon as this complexity is reduced, also anthropomorphism might be reduced.
+As \cite{persson_anthropomorphism_2000} names it: \textit{``Anthropomorphism is a way of making sense of complex behavior in the world around us.''} Thus, as soon as this complexity is reduced, also anthropomorphism might be reduced.
 
@@
 possibly \emph{deceptive} (for instance, it talks but does not understand when
-we talk ; it has eyes but does not recognize everyday objects we show ; etc.).
+we talk; it has eyes but does not recognize everyday objects we show; \etc).
 
@@
 By \emph{disruptive behaviors}, we mean any behavior exhibited by the robot that
-is unexpected by the user: for instance, a robot may usually follow always the
-same route to go to two different places in a house, and suddenly change the
+appears unexpected to the user: for instance, a robot may usually follow always the
+same route to go from one place in a house to the other, but suddenly it might change the
 route. The actual underlying reason may span from a bug to the detection of a
-new possible obstacle, but as long as this reason is not immediately
-intelligible to the user, the behavior counts as \emph{disruptive}.
+new obstacle, but as long as this reason is not immediately
+intelligible to the user, the behavior counts as \emph{disruptive}. (We will come back to the role of disruptive behaviors later, in Section \ref{sec:disruptive}.)
 
@@
 
-\fixme{JF: Severin, we should at some point mention what the ``expectation mismatch'' is ...
+%\fixme{JF: Severin, we should at some point mention what the ``expectation mismatch'' is ...
 I haven't found that so far ...
@@
 We also discuss two specific aspects: the cognitive impact of disruptive
-behaviors (section~\ref{sec:disruptive}) on mutual modelling, and how our models
-relate to the \emph{in-the-moment} versus \emph{reflective} perspectives on agency in HRI~\citet{takayama_perspectives_2012}.
+behaviors (section~\ref{sec:disruptive}) on mutual modeling, and how our models
+relate to the \emph{in-the-moment} versus \emph{reflective} perspectives on agency in HRI~\citep{takayama_perspectives_2012}.
 
@@
 
-We propose three different cognitive stages (Figure~\ref{fig:cognitivemodel}),
-which are related but do not directly match the three phases of
-the model of the dynamics of anthropomorphism. Note that these three stages are not mutually exclusive, they may overlap in time.
+We propose three different cognitive stages (Figure~\ref{fig:cognitivemodel}), which are not mutually exclusive but overlap over time.
+Note that these three cognitive stages are related but do not exactly match the
+\emph{Initialization}, \emph{Familiarization} and \emph{Stabilization} phases
+introduced in our model of the dynamics of anthropomorphism.
 
@@
 
-The \emph{stage 1} is the instinctive, pre-cognitive identification of living
+The \emph{Stage 1} is the instinctive, pre-cognitive identification of living
 peers. Studies conducted by~\citet{rosenthal-vonderputten_experimental_2013},
@@
 viewing the robots action and human automatic emotional responses are
-contributing at a lower level to the intuitive anthropomorphization (see Section
-2.2.2 \fixme{put ref}).
-
-The intuitive anthropomorphization in the cognitive stage 1 might be characteristic of what \cite{takayama_perspectives_2012} calls the \textit{in-the-moment} perspective on agency with a robot compared to the \textit{reflective} perspective (see paragraph ``artifact-centered perspective'' in Section \ref{sec:anthropomorphism}).
+contributing at a lower level to the intuitive anthropomorphization.
+
+The intuitive anthropomorphization in the cognitive Stage 1 might be characteristic of what \cite{takayama_perspectives_2012} calls the \textit{in-the-moment} perspective on agency with a robot compared to the \textit{reflective} perspective (see paragraph ``artifact-centered perspective'' in Section \ref{sec:anthropomorphism}).
 For instance, we reflectively
@@
 of the robot) or short interaction (touching, short talk like greetings), we
-suggest the human reaches the cognitive \emph{stage 2}: in this phase, the human
+suggest the human reaches the cognitive \emph{Stage 2}: in this phase, the human
 starts building a behavioral and cognitive model of the robot that would support
@@
 towards the robot, paying more attention to social cue than to low-level
-behaviour which may reinforce the resonnance mechanisms.
-
-The cognitive \emph{stage 3} is reached after a \emph{contextualized} interaction.
+behavior which may reinforce the resonance mechanisms.
+
+The cognitive \emph{Stage 3} is reached after a \emph{contextualized} interaction.
 A \emph{contextualized} interaction is \emph{explicitly purposeful} (the purpose
@@
 
-\subsection{Relation to the dynamics of anthropomorphism}
-
-These cognitive stages overlap over time but do not exactly match the
-\emph{Initialization}, \emph{Familiarization} and \emph{Stabilization} phases
-introduced in our model of the dynamics of anthropomorphism. In particular,
-the cognitive stages 1 and 2 are both included in the \emph{initialization} phase
+\paragraph{Relation to the dynamics of anthropomorphism\\}
+
+As mentioned before, the three cognitive stages proposed here do not match with the three phases in the \emph{Dynamics of Anthropomorphism}.
+In particular,
+the cognitive Stages 1 and 2 are both included in the \emph{initialization} phase
 of the anthropomorphism model. Sub-cognitive anthropomorphism typically
 \emph{initiates} the novelty effect by rapidly engaging the human in the
-interaction through an initial projected agency, whereas cognitive stage 2
+interaction through an initial projected agency, whereas cognitive Stage 2
 (projection of familiar mental models) supports the novelty effect by inducing
@@
 
-The cognitive stage 3 also overlaps with the \emph{Familiarization} phase: as
+The cognitive Stage 3 also overlaps with the \emph{Familiarization} phase: as
 the human gets used to the robot, he/she restates and adapts its
@@
 A \emph{stable level of anthropomorphism} is reached when the adaptation process
-depicted in the cognitive stage 3 reached a stable state, \ie the user's
+depicted in the cognitive Stage 3 reached a stable state, \ie the user's
 experience with the robot is correctly supported by the cognitive model he/she
 has built.
+
+Another way to think of the three proposed cognitive stages is to relate them to the \textbf{user experience} which is characteristic of these three stages.
+For instance, \cite{norman_emotional_2003} characterizes  three user experience dimensions (related to emotional attachment), which occur when people use or see a product for the first time: \emph{(1)} the \emph{visceral level}, which is the first impression of a product based on its experience; at this level people do not think about a product but make spontaneous judgments; \emph{(2)} the \emph{behavioral level}, in which people use and experience the product, appraise its functions, and consider aspects such as usefulness and usability; \emph{(3)} the \emph{reflective level}, in which consciousness takes part in the process, and past experiences are taken into account.
+In a study which was carried out in a shopping mall, \cite{weiss_i_2009} explored the emotional attachment during first time reactions of children and adults with the robotic dog AIBO.
+The authors also argue that it is important to understand the long-term development of people's social bonds to robots.
 
@@
 cases, the next occurrence of an expected behavior, if correctly interpreted
-(case I or II), is likely to lead to stronger effects due to a larger delta
+(case I or II), is likely to lead to stronger effects due to a larger $\delta$
 between expectations and actual observed behavior.
@@
 
-\fixme{Discuss here the general findings of the paper: the global shape of the
-model of the dynamics, ... // JF: yep, I agree, we should also come back to our initial hypotheses}
+Coming back to our two main hypotheses, on one hand we investigated how far anthropomorphism is based on multiple factors, namely, the design of the robot, the personal characteristics of the human user, and the context / situation in which the robot is used.
+We elaborated this hypothesis by reviewing literature from various related disciplines.
+Based on the outcomes of this, on the other hand, we proposed a model of the \emph{Dynamics of anthropomorphism}.
+We offered a cognitive interpretation of this model, as well as illustrations from our own previous work.
+However, our model has limitations, for instance, regarding the general effect of time and familiarization on anthropomorphism. We will discuss this in the following section.
 
@@
 to the robot.
-
-As outlined before, the tendency to anthropomorphize is motivated by
-a person's wish to make sense of an agent which might be difficult to understand
+Several studies described that after some time users interacted less with the robot or lost interest in it.
+Sustaining long-term interaction is one of the main challenges that robots with applications in daily life contexts face.
+Our question is that, if we would like overcome the novelty effect, how far does the robot's behavioral complexity play a role?
+Should the robot vary its behavior and behave unexpectedly from time to time?
+
+Most experiments, and even more when they investigate
+long-term interactions, are carried out with robots exhibiting relatively simple
+behaviors. In our model, the maximum level of anthropomorphism \AntMax is
+reached with the novelty effect, and then decreases. A natural question
+is whether we can design robots such that \AntMax remains high, possibly higher
+than $\ant[t_{novelty~peak}]$ (note that to know if sustaining strong
+anthropomorphic interaction is desirable is entirely another question, see Section \ref{sec:ethics}).
+
+Intuitively, the behavioral complexity of the robot, and in particular, the ability
+for the robot to evolve over time and \emph{adapt its behavior to the user} as the user
+familiarizes his/herself with the robot (\ie, \emph{co-familiarize}), seems to play a
+key role.
+
+Our model is based on the assumption that anthropomorphism tends to decrease with the user becoming more familiar to the robot.
+We explain this by the general motivation to anthropomorphize an agent which might be difficult to understand
 (in its functionality or behavior, for instance). In turn, a user might ascribe
 intentions or emotions to the system because the system's output was unexpected
-for the user. Based on this explanation, we estimate that when the user has
-familiarized herself / himself with the system, thus reached the point of when
+for the user, however he/she still wants to make sense of it. Consequently, we estimate that when the user has
+familiarized herself/himself with the system, thus reached the point of when
 the system is usable and explainable, the tendency to anthropomorphize
@@
 
-However, there exist views that suggest just the opposite, namely, that familiarization with an agent \textit{increases} the tendency to anthropomorphize \citep{eddy_attribution_1993}.
+However, there exist views that suggest just the opposite, namely, that familiarization and more interaction with an agent \textit{increase} the tendency to anthropomorphize \citep{eddy_attribution_1993}.
 Similarly, \cite{duffy_anthropomorphism_2003} reports that several psychological experiments and human-robot interaction experiments showed that familiarity may also ease social acceptance and even tend to \textit{increase} people's tendency to anthropomorphize.
@@
 We believe that as such, anthropomorphism can be better understood when studied and measured in a real, direct human-robot interaction compared to a mediated interaction.
-In a direct interaction scenario one could also take the human's behavior into account, as it seems to reflect an anthropomorphic interaction \citep{krach_can_2008,hegel_understanding_2008}.
-Of course, the scenario and measurements used depend on the research questions, so a direct human-robot interaction might not always be preferred.
+In a direct interaction scenario one could also take the human's behavior into account, as it seems to reflect an anthropomorphic interaction \citep{krach_can_2008,hegel_understanding_2008,weiss_i_2009}.
+Of course, the scenario and measurements one uses depend on the research questions, so a direct human-robot interaction might not always be preferred.
 
@@
 
-Regarding the second issue, how and with which means anthropomorphism is measured, the central point is that ``human-likeness'' itself is complex and manifold.
-It as a quite diverse and abstract concept, and instead of asking such a vague question, whether a robot is human-like or not, \cite{kahn_jr._robotic_2006} suggest to ask for more concrete constructs that are typical or unique of the concept of ``human-likeness''.
+Regarding the second issue, how and with which means anthropomorphism is measured, one of the view existing tools to do so is 5-item anthropomorphism part of the Godspeed questionnaire \citep{bartneck_measurement_2008}.
+On 5 point semantic differential scales, people are asked to rate the following constructs: fake - natural, machinelike - humanlike, unconscious - conscious, artificial - lifelike, moving rigidly - moving elegantly.
+The critical point that we see with this is that ``human-likeness'' itself is complex and manifold.
+Being such an abstract concept, instead of asking the vague question, whether a robot is human-like or not, \cite{kahn_jr._robotic_2006} suggest to ask for more concrete constructs that are typical or unique of the concept of ``human-likeness''.
 For instance, \cite{ruijten_introducing_2014} propose a 25-item questions to measure various concrete aspects of human-likeness.
@@
 Still, we also feel that measuring anthropomorphism (or social engagement with a robot) is challenging because the phenomenon is partially
-unconscious, its mediation is largely subject-dependent\fxnote{Should we put
-here different interaction profiles from the Ranger study?}, and we found the
+unconscious, its mediation is largely subject-dependent, and we found the
 phenomenon generally difficult to verbalize for users.
@@
 qualitative measurement of anthropomorphic effect are questionnaires and semi-structured interviews. We have
-explored both rating-scales in a questionnaire, and open questions in an interview (inspired from \citep{kahn_jr._robotic_2006,weiss_i_2009}).
+explored both rating-scales in a questionnaire, and open questions in an interview.
 In the Domino study, interviews were transcribed and participant's answers to the key questions that were assessing an anthropomorphic projection onto the robot, were analyzed.
@@
 
-\subsection{Sustaining long-term interaction}
-
-One main challenge that robots with applications in daily life contexts face is to sustain long-term interaction.
-
-\paragraph{Impact of the behavioral complexity of robots}
-
-To remain tractable, most experiments, and even more when they investigate
-long-term interactions, are carried out with robots exhibiting relatively simple
-behaviors. In our model, the maximum level of anthropomorphism \AntMax is
-reached at the end of the novelty effect, and then decreases. A natural question
-is whether we can design robots such as \AntMax remains high, possibly higher
-than $\ant[t_{novelty~peak}]$ (note that to know if sustaining strong
-anthropomorphic interaction is desirable is entirely another question).
-
-Intuitively, the behavioral complexity of the robot, and in particular, the ability
-for the robot to evolve over time and adapt its behavior to the user as the user
-familiarizes his/herself with the robot (\ie, \emph{co-familiarize}), seems to play a
-key role.
-
-\fixme{JF: Severin, I am not sure what you want to say here.}
+Some of these questions were taken from previous work done by \cite{kahn_jr._robotic_2006} an \cite{weiss_i_2009}.
+In both studies, both questionnaires and an analysis of behavior were used to assess children's and adult's engagement with, and perception of the robot.
+This seems to be a promising approach to investigate anthropomorphism, as it is also possible to combine quantitative and qualitative techniques.
 
 \subsection{Ethical aspects of anthropomorphism and human-like form of robots}
+\label{sec:ethics}
 
@@
 Can this be the reality we want to live in?
-What happens as soon as the artificial agent is considered a \textit{moral agent} \cite{sullins_when_2006}?
+What happens as soon as the artificial agent is considered a \textit{moral agent} \citep{sullins_when_2006}?
 Also, the use of \textit{socially interactive robots} in
@@
 \label{sec:conclusion}
-
-Our data suggest that there are qualitative differences and dynamics over time
-in how humans relate to different types of robots. More concretely, we found
-that people's perception of human-likeness in the robot and in turn their
-human-social engagement with the robot was not only based on how much the robot
-resembled a human (mostly in its behavioral cues) but that this was determined
-by multiple factors, including individual characteristics of the human user but
-also the context of use, for instance. Interestingly, our findings also suggest
-that how far people anthropomorphize a robot is likely to change over time with
-growing experience of the user with the system.
-
-Based on these observations and an extensive literature review, we would like to
-propose a model that accounts for variances and dynamics in anthropomorphism.
-This model of the \textit{``Dynamics of Anthropomorphism''} considers several
-impact factors, including the human user, the anthropomorphic design of the
-non-human agent, the context of use, and the interaction experience (time). With
-this initial model, we would like to extend the current understanding of
-anthropomorphism in robotics and human-robot interaction. This might in turn
-lead to a discussion about the short- and long-term benefits and other effects
-of the human-like (anthropomorphic) design of robots and other artificial
-agents.
 
@@
 
-While anthropomorphism is traditionally empirically understood as the
-interactions between the anthropomorphic design of a robot and the psychological
-determinants of the user, it appears that the duration and context of the
-interaction are also key factors, and that anthropomorphism needs to be
-understood as a dynamic phenomenon. In this article, we propose a new formal
-model of anthropomorphism that accounts for these three factors and also
-explicits the dynamics of anthropomorphism. We introduce the concepts of
-\emph{initial} and \emph{stabilized levels of anthropomorphism} as compound
-factors to characterize the profile of a given anthropomorphic interaction.
-
-The article also discusses the cognitive correlates of anthropomorphism. We
-proposes to identify three cognitive stages corresponding to successive
+Based on our previous (and on-going) work, we hypothesized that there are qualitative differences and dynamics over time
+in how humans relate to different types of robots. More concretely, we described
+that people's perception of human-likeness in a robot and in turn their
+human-social engagement with a robot is based on four main factors: (1) the (anthropomorphic) design of the robot, (2) individual characteristics of the human user, (3) the context of use / interaction, and (4) the interaction history (time factor).
+We further suggested
+that people's tendency to anthropomorphize a robot is likely to change over time with
+growing experience of the user with the system.
+
+To formalize the variances in anthropomorphism, we
+proposed a model that we call \textit{Dynamics of Anthropomorphism}.
+
+ We introduced the concepts of
+\emph{initial capital} and \emph{stabilized level of anthropomorphism} as compound
+factors to characterize the profile of a given anthropomorphic (long-term) interaction.
+
+The article also discussed the cognitive correlates of anthropomorphism. We
+proposed three cognitive stages corresponding to successive
 refinements of the mental models of the robot that the user builds during the
-interaction. We show how these stages relate to observable anthropomorphic
+interaction. We showed how these stages relate to observable anthropomorphic
 effects, and how they evolve over time.
@@
 
+%With
+%this initial model, we would like to extend the current understanding of
+%anthropomorphism in robotics and human-robot interaction. This might in turn
+%lead to a discussion about the short- and long-term benefits and other effects
+%of the anthropomorphic design of robots and other artificial
+%agents.
+
 \section*{Acknowledgments}

### 2014-04-07 paper.tex
new figure included

@@
 
-\begin{figure}\footnotesize
+%\begin{figure}\footnotesize
+%    \centering
+%    \begin{tabular}{  >{\centering\arraybackslash}m{2cm} | >{\centering\arraybackslash}m{2cm} | >{\centering\arraybackslash}m{2cm} }
+%     & Unplanned by the robot & Planned by the robot \\ \hline
+%    Perceived as non-intentional & case I  & case IIIa  \\ \hline
+%    Perceived as intentional &  case IIIb & case II 
+%    \end{tabular}
+%\caption{
+%    Behaviors of the robot that are unexpected by the user may be intentional
+%    (the robot has planned the behavior) or not (typically, a failure:
+%    misdetection, bug,...). Independently of that, the behavior may be
+%    \emph{perceived} by the user as intentional or not.}
+%\label{fig:perceptionUnexpectedBehavior}
+%\end{figure}
+
+\begin{figure}
     \centering
-    \begin{tabular}{  >{\centering\arraybackslash}m{2cm} | >{\centering\arraybackslash}m{2cm} | >{\centering\arraybackslash}m{2cm} }
-     & Unplanned by the robot & Planned by the robot \\ \hline
-    Perceived as non-intentional & case I  & case IIIa  \\ \hline
-    Perceived as intentional &  case IIIb & case II 
-    \end{tabular}
-\caption{
-    Behaviors of the robot that are unexpected by the user may be intentional
+    \includegraphics[width=0.75\columnwidth]{un-expected-behavior.pdf}
+    \caption{Behaviors of the robot that are unexpected by the user may be intentional
     (the robot has planned the behavior) or not (typically, a failure:
@@
     \emph{perceived} by the user as intentional or not.}
+
     \label{fig:perceptionUnexpectedBehavior}

### 2014-04-07 paper.tex
added alternative figure at bottom of the article
Moved alternate fig 'in our heads' next to the other one for easier comparison

@@
     \caption{Anthropomorphism is a psychological phenomenon which arises in a
-        social context, during an
-    interaction between a human agent and a non-human agent. One can take two main perspectives when trying to explain
-    anthropomorphism: a human-centered and an artifact-centered perspective (grey
-    triangles). Several external factors influence the anthropomorphism
-    phenomenon. Person- and artifact-related characteristics, but also related to the
-context of use as well as the actual time spent interacting with the robot (interaction history).}
+        social context, during an interaction between a human agent and a
+        non-human agent. One can take two main perspectives when trying to
+        explain anthropomorphism: a human-centered and an artifact-centered
+        perspective (grey triangles). Several external factors influence the
+        anthropomorphism phenomenon. Person- and artifact-related characteristics,
+        but also related to the context of use as well as the actual time spent
+        interacting with the robot (interaction history). [SEE
+        FIG~\ref{fig:anthropofig-alt} FOR AN ALTERNATIVE FIGURE]}
 
     \label{fig:anthropofig}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.75\columnwidth]{in_our_heads.pdf}
+    \caption{[ALTERNATIVE TO FIGURE \ref{fig:anthropofig}] Anthropomorphism is a
+        subjective, psychological phenomenon which arises in a social context, during an
+        interaction between a human agent and a non-human agent. One can take
+        two main perspectives when trying to explain anthropomorphism: a
+        human-centered and an artifact-centered perspective.
+        Several external factors influence the anthropomorphism phenomenon.
+        Person- and artifact-related characteristics, but also related to the
+        context of use as well as the actual time spent interacting with the
+        robot (interaction history).}
+
+    \label{fig:anthropofig-alt}
 \end{figure}

### 2014-04-07 paper.tex
New version of the abstract

@@
 
-A phenomenon that is often studied related to the human-like design of 
-robots is \textit{anthropomorphism} -- people's tendency to perceive human-like 
-characteristics in non-human agents. While this is a commonly discussed trait of 
-human-robot interaction (HRI), the phenomenon paradoxically appears to lack formal 
-grounds. Based on findings from several empirical studies and a 
-comprehensive synthesis of literature, this article attempts at extending 
-the current understanding of anthropomorphism. In accordance with theories 
-from social psychology, cognitive science, and neuroscience, we suggest to 
-formalize qualitative differences and dynamics over time in how 
-humans anthropomorphize non-human agents. We propose several key factors that determine anthropomorphism, 
-namely the 
-design of the non-human agent, the individual characteristics of the human 
-user, and the context of use. An initial model that we call 
-\textit{``Dynamics of Anthropomorphism''} tries to formalize the qualitative changes in anthropomorphism over time. To 
-account for these variances, our model describes the non-linear relationship between anthropomorphic effects of a human-robot interaction and the human user's growing experience with the system.
-We also present a cognitive interpretation that considers 
-these described dynamics. Further, we discuss scenarios and techniques to measure anthropomorphism. Finally, we make suggestions how others can 
-apply our model to better describe the complexity in human's 
-tendency to perceive human-like characteristics in non-human agents.
+\textit{Anthropomorphism} -- the people's tendency to perceive human-like
+characteristics in non-human agents -- is a phenomenon that is most often
+studied from the sole perspective of the human-like \emph{design} of robots.
+
+By building upon experimental results from several studies, a comprehensive
+synthesis of the literature, as well as insights from social psychology,
+cognitive science, and neuroscience, this article proposes to extend our current
+understanding of anthropomorphism into a \textbf{formal model} that defines a
+\textbf{clear terminology}, accounts for the \textbf{non-monotonic dynamics} of
+the phenomenon, and relate the observed \emph{effects} of anthropomorphism to
+their \textbf{underlying cognitive precursors}.
+
+We also examine the \textbf{factors} that determine anthropomorphism (the
+design of the non-human agent, the individual psychological determinants of the
+human user and the context of use) and we discuss several \textbf{episodes of
+interaction} that influence the anthropomorphic projections on the robot, like
+the \textbf{novelty effect}, the role of \textbf{familiarization} and the
+impact of \textbf{disruptive behaviors}.
+
+The article also discusses techniques and scenarios to measure anthropomorphism,
+and we conclude with a few suggestions on how others can apply our model to
+better describe our tendency to perceive human-like characteristics in non-human
+agents.
 

### 2014-04-07 paper.tex
abstract, now: really robust draft :)

@@
 
-\textit{Anthropomorphism} -- the people's tendency to perceive human-like
-characteristics in non-human agents -- is a phenomenon that is most often
+\textit{Anthropomorphism} -- people's tendency to perceive human-like
+characteristics in non-human agents -- is a phenomenon that is often
 studied from the sole perspective of the human-like \emph{design} of robots.
@@
 By building upon experimental results from several studies, a comprehensive
-synthesis of the literature, as well as insights from social psychology,
+synthesis of literature, as well as insights from social psychology,
 cognitive science, and neuroscience, this article proposes to extend our current
-understanding of anthropomorphism into a \textbf{formal model} that defines a
-\textbf{clear terminology}, accounts for the \textbf{non-monotonic dynamics} of
-the phenomenon, and relate the observed \emph{effects} of anthropomorphism to
+understanding of anthropomorphism. By doing so, we propose a \textbf{formal model} that defines a
+\textbf{clear terminology} and accounts for the \textbf{non-monotonic dynamics} of
+the phenomenon. We further relate the observed \emph{effects} of anthropomorphism to
 their \textbf{underlying cognitive precursors}.
 
-We also examine the \textbf{factors} that determine anthropomorphism (the
+We examine several \textbf{factors} that determine anthropomorphism, namely the
 design of the non-human agent, the individual psychological determinants of the
-human user and the context of use) and we discuss several \textbf{episodes of
+human user, and the context of use. Moreover, we discuss several \textbf{episodes of
 interaction} that influence the anthropomorphic projections on the robot, like
@@
 
-The article also discusses techniques and scenarios to measure anthropomorphism,
+Finally, the article also discusses techniques and scenarios to measure anthropomorphism,
 and we conclude with a few suggestions on how others can apply our model to
-better describe our tendency to perceive human-like characteristics in non-human
+better describe people's tendency to perceive human-like characteristics in non-human
 agents.

### 2014-06-24 paper.tex
my first commit from my mac system
i hope this works … i had to comment out the tikz figures because they
don't work here

@@
 \graphicspath{{figs/}}
-\usepackage{tikz}
-\usetikzlibrary{shapes}
-\usetikzlibrary{svg.path}
+%\usepackage{tikz}
+%\usetikzlibrary{shapes}
+%\usetikzlibrary{svg.path}
 %
@@
 
-\begin{figure*}[htb]
-\centering
-
-\begin{tikzpicture}[scale=1.4]
-
-% background shading
-\path[fill=green!20] (0,0) rectangle (0.6,5.5);
-\path[fill=blue!15] (0.6,0) rectangle (5.2,5.5);
-\path[fill=orange!20] (5.2,0) rectangle (9.8,5.5);
-\draw(0,5.5) node[anchor=south west, rotate=10] {\scriptsize \sc Initialization};
-\draw(2.5,5.5) node[anchor=south west, rotate=10] {\scriptsize \sc Familiarization};
-\draw(6.5,5.5) node[anchor=south west, rotate=10] {\scriptsize \sc Stabilization};
-% horizontal axis
-\draw[->] (0,0) -- (10,0) node[anchor=north] {$t$};
-\draw(5,-0.1) node[anchor=north] {\scriptsize Duration of interaction};
-
-% vertical axis
-\draw[->] (0,0) -- (0,6) node[anchor=east] {};
-\draw(-0.8,3) node[rotate=90,anchor=south] {\scriptsize Anthropomorphic effects};
-
-\draw (-0.05, 3) -- (0.05, 3) node[anchor=east] {\ICA};
-\draw (-0.05, 5) -- (0.05, 5) node[anchor=east] {\AntMax};
-
-% vertical axis - end
-\draw[->] (9.8,0) -- (9.8,2) node[anchor=east] {};
-\draw (9.8, 0.8) node[anchor=west] {\SLA};
-
-\draw[<-] (0.65,5) -- (0.8,5.2) node[anchor=east] {};
-\draw (0.9,5.3) node[anchor=west] {\tiny \it novelty peak};
-
-\draw[dashed] (0.6, 0) -- (0.6,5.1);
-\draw (0.6,0) node[anchor=north] {$t_{max}$};
-
-\draw[dotted] (0, 5) -- (6.2,5);
-\draw[dotted] (0, 3) -- (6.2,3);
-\draw[<->] (6.1,3) -- (6.1,5) node[sloped, above, midway] {$\Delta_{a}$};
-
-\draw[<-] (1.7,4.4) -- (3.2,4.1) node[anchor=east] {};
-\draw[<-] (2.85,2.6) -- (3.2,4.1) node[anchor=east] {};
-\draw (3.2,4.1) node[anchor=west, align=center] {\tiny \it disruptive\\ \tiny
-\it behaviors};
+%\begin{figure*}[htb]
+%\centering
+%
+%
+%\begin{tikzpicture}[scale=1.4]
+%
+%% background shading
+%\path[fill=green!20] (0,0) rectangle (0.6,5.5);
+%\path[fill=blue!15] (0.6,0) rectangle (5.2,5.5);
+%\path[fill=orange!20] (5.2,0) rectangle (9.8,5.5);
+%\draw(0,5.5) node[anchor=south west, rotate=10] {\scriptsize \sc Initialization};
+%\draw(2.5,5.5) node[anchor=south west, rotate=10] {\scriptsize \sc Familiarization};
+%\draw(6.5,5.5) node[anchor=south west, rotate=10] {\scriptsize \sc Stabilization};
+%% horizontal axis
+%\draw[->] (0,0) -- (10,0) node[anchor=north] {$t$};
+%\draw(5,-0.1) node[anchor=north] {\scriptsize Duration of interaction};
+%
+%
+%% vertical axis
+%\draw[->] (0,0) -- (0,6) node[anchor=east] {};
+%\draw(-0.8,3) node[rotate=90,anchor=south] {\scriptsize Anthropomorphic effects};
+%
+%\draw (-0.05, 3) -- (0.05, 3) node[anchor=east] {\ICA};
+%\draw (-0.05, 5) -- (0.05, 5) node[anchor=east] {\AntMax};
+%
+%% vertical axis - end
+%\draw[->] (9.8,0) -- (9.8,2) node[anchor=east] {};
+%\draw (9.8, 0.8) node[anchor=west] {\SLA};
+%
+%
+%\draw[<-] (0.65,5) -- (0.8,5.2) node[anchor=east] {};
+%\draw (0.9,5.3) node[anchor=west] {\tiny \it novelty peak};
+%
+%\draw[dashed] (0.6, 0) -- (0.6,5.1);
+%\draw (0.6,0) node[anchor=north] {$t_{max}$};
+%
+%\draw[dotted] (0, 5) -- (6.2,5);
+%\draw[dotted] (0, 3) -- (6.2,3);
+%\draw[<->] (6.1,3) -- (6.1,5) node[sloped, above, midway] {$\Delta_{a}$};
+%
+%\draw[<-] (1.7,4.4) -- (3.2,4.1) node[anchor=east] {};
+%\draw[<-] (2.85,2.6) -- (3.2,4.1) node[anchor=east] {};
+%\draw (3.2,4.1) node[anchor=west, align=center] {\tiny \it disruptive\\ \tiny
+%\it behaviors};
+%%%%%%
+%%% CURVES
 %%%%%
-%% CURVES
-%%%%
-\begin{scope}[yscale=-1,shift={(-0.125,-0.4)}]
-
-    \draw[ultra thick] svg[scale=1cm] "M 0.125,-2.5619582 c 0.0200733,-1.1573591
-    0.33954391,-1.9982333 0.57940683,-2.0013597 0.13691605,0 0.25550329,0.052908
-    0.37497897,0.1661788 0.119476,0.1130305 0.2396954,0.2786079
-    0.37944,0.4790565 0.069872,0.099803 0.1021612,-0.2231749
-    0.1792538,-0.2238964 0.099707,0 0.013454,0.4985362 0.3173383,0.9139831
-    0.1911917,0.2612926 0.3444354,0.2578391 0.6711932,0.4894291
-    0.2058265,0.1458798 0.1571532,0.9762306 0.2615031,0.9702183 0.097182,0
-    0.083295,-0.3336208 0.4330446,-0.1199242 0.4306401,0.2631203
-    0.216699,0.1355642 0.4296663,0.2647074 2.0858202,1.13836043
-    4.34683,1.41300027 6.3741749,1.43753027";
-
-    \draw[dashed] svg[scale=1cm] "M 0.125,-0.1952939 c 0.0553601,-3.1917862
-    0.33954391,-4.3648976 0.57940683,-4.368024 0.13691605,0 0.25550329,0.052908
-    0.37497897,0.1661788 m 2.6714393,2.7735737 C 4.7653984,-0.85050947
-    6.5955093,0.35382293 10.125,0.4062498";
-
-    \draw[dashed] svg[scale=1cm] "M 0.125,-3.6923825 C 0.1102888,-4.0297903
-    0.46454391,-4.5601915 0.70440683,-4.5633179 M 3.7508251,-1.6235654 C
-    4.9579368,-0.95548345 8.1358175,-0.82609971 10.125,-0.79459549";
-
-\end{scope}
-
-\end{tikzpicture}
-
-\caption{The dynamics of anthropomorphism. We distinguish three main phases:
-    \emph{initialization}, \emph{familiarization} and \emph{stabilization},
-    preceded by a \emph{pre-interaction} phase. The pre-interaction phase
-    is characterized through an \emph{initial capital of anthropomorphism} (ICA, noted \ICA).
-    Once the interaction starts, the level of anthropomorphism increases due to
-    the \emph{novelty effect}, and then decreases to reach a \emph{stabilized
-    level of anthropomorphism} (SLA, noted \SLA). \ICA and \SLA may vary
-    depending on the user (and his/her expectations), the robot and the context of interaction.  During the
-    interaction, unpredicted behaviors of the robot (\emph{disruptive
-    behaviors}) may lead to local increases or decreases of the level of
-    anthropomorphic effects.}
-
-\label{fig:dynamics}
-\end{figure*}
+%\begin{scope}[yscale=-1,shift={(-0.125,-0.4)}]
+%
+%    \draw[ultra thick] svg[scale=1cm] "M 0.125,-2.5619582 c 0.0200733,-1.1573591
+%    0.33954391,-1.9982333 0.57940683,-2.0013597 0.13691605,0 0.25550329,0.052908
+%    0.37497897,0.1661788 0.119476,0.1130305 0.2396954,0.2786079
+%    0.37944,0.4790565 0.069872,0.099803 0.1021612,-0.2231749
+%    0.1792538,-0.2238964 0.099707,0 0.013454,0.4985362 0.3173383,0.9139831
+%    0.1911917,0.2612926 0.3444354,0.2578391 0.6711932,0.4894291
+%    0.2058265,0.1458798 0.1571532,0.9762306 0.2615031,0.9702183 0.097182,0
+%    0.083295,-0.3336208 0.4330446,-0.1199242 0.4306401,0.2631203
+%    0.216699,0.1355642 0.4296663,0.2647074 2.0858202,1.13836043
+%    4.34683,1.41300027 6.3741749,1.43753027";
+%
+%    \draw[dashed] svg[scale=1cm] "M 0.125,-0.1952939 c 0.0553601,-3.1917862
+%    0.33954391,-4.3648976 0.57940683,-4.368024 0.13691605,0 0.25550329,0.052908
+%    0.37497897,0.1661788 m 2.6714393,2.7735737 C 4.7653984,-0.85050947
+%    6.5955093,0.35382293 10.125,0.4062498";
+%
+%    \draw[dashed] svg[scale=1cm] "M 0.125,-3.6923825 C 0.1102888,-4.0297903
+%    0.46454391,-4.5601915 0.70440683,-4.5633179 M 3.7508251,-1.6235654 C
+%    4.9579368,-0.95548345 8.1358175,-0.82609971 10.125,-0.79459549";
+%
+%
+%
+%\end{scope}
+%
+%\end{tikzpicture}
+%
+%\caption{The dynamics of anthropomorphism. We distinguish three main phases:
+%    \emph{initialization}, \emph{familiarization} and \emph{stabilization},
+%    preceded by a \emph{pre-interaction} phase. The pre-interaction phase
+%    is characterized through an \emph{initial capital of anthropomorphism} (ICA, noted \ICA).
+%    Once the interaction starts, the level of anthropomorphism increases due to
+%    the \emph{novelty effect}, and then decreases to reach a \emph{stabilized
+%    level of anthropomorphism} (SLA, noted \SLA). \ICA and \SLA may vary
+%    depending on the user (and his/her expectations), the robot and the context of interaction.  During the
+%    interaction, unpredicted behaviors of the robot (\emph{disruptive
+%    behaviors}) may lead to local increases or decreases of the level of
+%    anthropomorphic effects.}
+%
+%\label{fig:dynamics}
+%\end{figure*}
 
@@
 
-\begin{figure}[htb]
-\centering
-%\resizebox{\linewidth}{!}{
-\begin{tikzpicture}
-\baselineskip=8pt
-
-\path[fill=gray!20] (0,0) rectangle (10.5,2);
-\path[fill=gray!50] (0,2) rectangle (10.5,4);
-\path[fill=gray!20] (0,4) rectangle (10.5,6);
-
-\draw (-0.3,1) node[rotate=90] {Stage 1}
-      (-0.3,3) node[rotate=90] {Stage 2}
-      (-0.3,5) node[rotate=90] {Stage 3};
-
-\draw[->] (0,0) -- (11,0) node[anchor=north] {$t$};
-\draw[-|] (0,0) -- (0,6.5) node[anchor=east] {};
-% Us
-\draw[ultra thick, ->] (0,0) -- (1,2) -- (3,2) -- (4,4) -- (6,4) -- (7,6) --
-(9.5,6);
-\draw[ultra thick, dashed, ->] (3,2) -- (9.5,2);
-\draw[ultra thick, dashed, ->] (6,4) -- (9.5,4);
-
-\draw (11,1) node[align=left, anchor=west]{\scriptsize pre-cognitive\\\scriptsize anthropomorphism}; %label
-
-\draw (11,3) node[align=left, anchor=west] {\scriptsize{projection of existing}\\\scriptsize{mental models}\\\scriptsize{\it (familiarity)}}; %label
-
-\draw (11,5) node[align=left, anchor=west] {\scriptsize{adapted mental
-model} \\ $\to$ \scriptsize{adapted interaction}\\\scriptsize{\it (anthropomorphic or not)}}; %label
-
-\draw[dashed,->] (1,0.1) to[bend right] (2,1.9)  node at (4.5,1) {\tiny{\it observation (shape, motion, sound)}}; %label
-
-\draw[dashed,->] (4,2.1) to[bend right] (5,3.9)  node[align=left] at (7.5,3) {\tiny \it observation (interactive behavior) \\ \tiny \it or short interaction}; %label
-
-\draw[dashed,->] (7,4.1) to[bend right] (8,5.9)  node[align=left] at (9,5)
-{\tiny \it contextualized\\ \tiny \it interaction}; %label
-
-\end{tikzpicture}
-%}
-\caption{The three cognitive stages of anthropomorphism: Stage 1 is the instinctive,
-sub-cognitive identification of living peers. {\it Empathy} is characteristic
-of this stage. After longer observation or short, non-contextualized interaction
-(typically, a lab environment), the user reaches Stage 2: the user projects a
-mental model he/she is already familiar with onto the robot. After longer {\it
-contextualized} interaction (typically, at home), the user enters Stage 3 of
-anthropomorphism: the user composes a custom mental model of the robot,
-based on experience. This leads to adapted interaction modalities, that may
-still be anthropomorphic, or not.}
-\label{fig:cognitivemodel}
-\end{figure}
+%\begin{figure}[htb]
+%\centering
+%%\resizebox{\linewidth}{!}{
+%\begin{tikzpicture}
+%\baselineskip=8pt
+%
+%\path[fill=gray!20] (0,0) rectangle (10.5,2);
+%\path[fill=gray!50] (0,2) rectangle (10.5,4);
+%\path[fill=gray!20] (0,4) rectangle (10.5,6);
+%
+%\draw (-0.3,1) node[rotate=90] {Stage 1}
+%      (-0.3,3) node[rotate=90] {Stage 2}
+%      (-0.3,5) node[rotate=90] {Stage 3};
+%
+%\draw[->] (0,0) -- (11,0) node[anchor=north] {$t$};
+%\draw[-|] (0,0) -- (0,6.5) node[anchor=east] {};
+%% Us
+%\draw[ultra thick, ->] (0,0) -- (1,2) -- (3,2) -- (4,4) -- (6,4) -- (7,6) --
+%(9.5,6);
+%\draw[ultra thick, dashed, ->] (3,2) -- (9.5,2);
+%\draw[ultra thick, dashed, ->] (6,4) -- (9.5,4);
+%
+%\draw (11,1) node[align=left, anchor=west]{\scriptsize pre-cognitive\\\scriptsize anthropomorphism}; %label
+%
+%\draw (11,3) node[align=left, anchor=west] {\scriptsize{projection of existing}\\\scriptsize{mental models}\\\scriptsize{\it (familiarity)}}; %label
+%
+%\draw (11,5) node[align=left, anchor=west] {\scriptsize{adapted mental
+%model} \\ $\to$ \scriptsize{adapted interaction}\\\scriptsize{\it (anthropomorphic or not)}}; %label
+%
+%
+%\draw[dashed,->] (1,0.1) to[bend right] (2,1.9)  node at (4.5,1) {\tiny{\it observation (shape, motion, sound)}}; %label
+%
+%\draw[dashed,->] (4,2.1) to[bend right] (5,3.9)  node[align=left] at (7.5,3) {\tiny \it observation (interactive behavior) \\ \tiny \it or short interaction}; %label
+%
+%\draw[dashed,->] (7,4.1) to[bend right] (8,5.9)  node[align=left] at (9,5)
+%{\tiny \it contextualized\\ \tiny \it interaction}; %label
+%
+%\end{tikzpicture}
+%%}
+%\caption{The three cognitive stages of anthropomorphism: Stage 1 is the instinctive,
+%sub-cognitive identification of living peers. {\it Empathy} is characteristic
+%of this stage. After longer observation or short, non-contextualized interaction
+%(typically, a lab environment), the user reaches Stage 2: the user projects a
+%mental model he/she is already familiar with onto the robot. After longer {\it
+%contextualized} interaction (typically, at home), the user enters Stage 3 of
+%anthropomorphism: the user composes a custom mental model of the robot,
+%based on experience. This leads to adapted interaction modalities, that may
+%still be anthropomorphic, or not.}
+%\label{fig:cognitivemodel}
+%\end{figure}
 

### 2014-08-27 paper.tex
Full rewrite by Julia -- submitted version

--- 2014-04-07 paper.tex
@@
-%\documentclass{frontiersENG} % for Engineering articles
 \documentclass{frontiersSCNS} % for Science articles
-%\documentclass{frontiersMED} % for Medicine articles
-%\documentclass{frontiersFPHY} % for Physics articles
-
-%\usepackage[utf8x]{inputenc}
-%\usepackage[T1]{fontenc}
-
-%\usepackage[english]{babel}
-
+
+\usepackage[english]{babel}
+
+%\setcitestyle{square}
+\usepackage{url,lineno}
+\linenumbers
+
+\usepackage{datetime}
+\usepackage{fmtcount}
+\usepackage{etoolbox}
+
+\usepackage{amsmath} 
+\usepackage{mathptmx}
+
+\usepackage{array}
 \usepackage{graphicx}
+%\usepackage{caption}
+%\usepackage{subcaption}
 \graphicspath{{figs/}}
-\usepackage{tikz}
-\usetikzlibrary{shapes}
-\usetikzlibrary{svg.path}
-%
-\usepackage{amsmath} 
-\usepackage{mathptmx}      % use Times fonts if available on your TeX system
-%
+
 \usepackage{color, soul}
@@
 
-\usepackage{caption}
-\usepackage{subcaption}
-\usepackage{float}
-\floatstyle{plaintop}
-
-\usepackage{paralist} % inparaenum
-
-\usepackage[bookmarks]{hyperref}
-
-\usepackage[draft, nomargin, marginclue, footnote]{fixme}
-\fxsetup{targetlayout=color}
-
 \newcommand{\eg}{{\textit{e.g.~}}}
@@
 
-\usepackage{xifthen}% provides \isempty test
-
-% use either \Ant or \Ant[R,H,C,...]
-\newcommand{\Ant}[1][]{%
-      \ifthenelse{\isempty{#1}}%
-        {$\mathcal{A}$}
-        {$\mathcal{A}(#1)$}
-}
-
-\newcommand{\AntNorm}[1][]{%
-      \ifthenelse{\isempty{#1}}%
-      {$\widehat{\mathcal{A}}$}
-      {$\widehat{\mathcal{A}}(#1)$}
-}
-
-% for use inside a math environment
-\newcommand{\ant}[1][]{%
-      \ifthenelse{\isempty{#1}}%
-        {\mathcal{A}}
-        {\mathcal{A}(#1)}
-}
-
-\newcommand{\antNorm}[1][]{%
-      \ifthenelse{\isempty{#1}}%
-      {\widehat{\mathcal{A}}}
-      {\widehat{\mathcal{A}}(#1)}
-}
-
-\newcommand{\ICA}{{$\mathcal{A}_0$~}}
-\newcommand{\SLA}{{$\mathcal{A}_\infty$~}}
-\newcommand{\sla}{{\mathcal{A}_\infty}}
-\newcommand{\AntMax}{{$\mathcal{A}_{max}$~}}
-\newcommand{\antMax}{{\mathcal{A}_{max}}}
-
 \hyphenation{com-mon-ly}
@@
 \def\DOI{}
-\def\articleType{Research Article}
+\def\articleType{Hypothesis and Theory}
 \def\keyFont{\fontsize{8}{11}\helveticabold }
@@
 
-\textit{Anthropomorphism} -- the people's tendency to perceive human-like
-characteristics in non-human agents -- is a phenomenon that is most often
-studied from the sole perspective of the human-like \emph{design} of robots.
-
-By building upon experimental results from several studies, a comprehensive
-synthesis of the literature, as well as insights from social psychology,
-cognitive science, and neuroscience, this article proposes to extend our current
-understanding of anthropomorphism into a \textbf{formal model} that defines a
-\textbf{clear terminology}, accounts for the \textbf{non-monotonic dynamics} of
-the phenomenon, and relate the observed \emph{effects} of anthropomorphism to
-their \textbf{underlying cognitive precursors}.
-
-We also examine the \textbf{factors} that determine anthropomorphism (the
-design of the non-human agent, the individual psychological determinants of the
-human user and the context of use) and we discuss several \textbf{episodes of
-interaction} that influence the anthropomorphic projections on the robot, like
-the \textbf{novelty effect}, the role of \textbf{familiarization} and the
-impact of \textbf{disruptive behaviors}.
-
-The article also discusses techniques and scenarios to measure anthropomorphism,
-and we conclude with a few suggestions on how others can apply our model to
-better describe our tendency to perceive human-like characteristics in non-human
-agents.
+%As a primary goal, the abstract should render the general significance and conceptual advance of the work clearly accessible to a broad readership. References should not be cited in the abstract.
+
+\textit{Anthropomorphism} -- people's tendency to perceive human-like characteristics in non-human agents -- is a commonly observed phenomenon in Human-Robot Interaction (HRI).
+Though having been extensively studied, anthropomorphism is still not very well understood.
+Often, anthropomorphism is analyzed from the sole perspective of the human-like (anthropomorphic) design of a robot.
+%The question in focus is to what extent different types of anthropomorphic robot designs evoke affinity or uncanny feelings in the human user.
+%In this regard, the \textit{Uncanny Valley} hypothesis suggests that an anthropomorphic design can evoke both positive and negative feelings in human users, determined by the degree of human-likeness.
+We believe that we need to go beyond this, in order to gain a better awareness about the phenomenon as a whole.
+To this end, we make three suggestions toward extending our understanding of anthropomorphism in HRI.
+First, we suggest to comprehend anthropomorphism as a human-centered social phenomenon that arises in an interaction between a human and a robot in a specific context (partly determined by the purpose of the robot).
+Consequently, we propose that \textbf{multiple factors} need to be considered: the characteristics of the robot, of the human, and of the context.
+This holds implications for how anthropomorphism is studied and measured.
+%Real physical interaction is required.
+By applying a cognitive perspective, we further suggest that anthropomorphism is \textbf{multi-layered}, not being either \textit{there} or \textit{not there} but that there exist lower and higher levels of it, depending on the \textit{cognitive depth} that the attribution of a human-like characteristic to the robot implies, as well as on the specific mental model on which it is based.
+Finally, we hypothesize that anthropomorphism is \textbf{dynamic}.
+In other words, it evolves over time, with growing real or imagined interaction experience and familiarization of the human user with the robot.
+We formalize our ideas in a conceptual model that we call the \textit{Dynamics of Anthropomorphism}.
+Our hypotheses are based on results from our own empirical interaction studies, and informed on a review of related work in psychology, cognitive science and neuroscience as well as on previous research in HCI and HRI.
+%As a consequence of our hypotheses, we discuss the methods and measurement tools to study anthropomorphism and propose going toward long-term interaction studies to verify our conceptual model.
 
 \tiny
- \keyFont{ \section{Keywords:} Anthropomorphism, Design, Human-Robot Interaction, Social Issues in Robotics, Acceptance of Robots}
-
+\keyFont{ \section{Keywords:} Anthropomorphism, Design, Dynamics, Human-Robot 
+Interaction, Mental Models, Robot Acceptability, Social Robotics} 
 \end{abstract}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-%
-%
-%		INTRODUCTION & OVERVIEW
-%
-%
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+%
+%
+%		INTRODUCTION
+%
+%
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
 \section{Introduction}
-\label{sec:intro}
-
-The Uncanny Valley hypothesis \citep{mori_uncanny_1970} proposes that human-like
-designs of objects and non-human agents can evoke both positive and negative feelings in the human observer / user. A positive valence reflects the experience of 
-emotional engagement with and feelings of empathy for the non-human agent
-\citep{cheetham_human_2011}. This in turn may lead to an effective (human-like and 
-human-social) interaction with the non-human agent, and increase people's acceptance of
-it. 
-%
-%However, at a certain point as the non-human agent
-%approaches but fails to closely resemble a human, the evoked valence in the
-%human user suddenly turns into a negative uncanny feeling of what
-%\cite{mori_uncanny_1970} describes as disgust and revulsion. This, in turn,
-%might lead to rejection of the non-human agent. The Uncanny
-%Valley hypothesis predicts that with further increasing the human-likeness of
-%the non-human agent such that it appears so realistic that it is not
-%distinguishable from a human but perceived to be human, the effect is again a
-%positive one, reflecting feelings and engagement that are similar as those
-%evoked by a human-human interaction. 
-%Of course, developers and designers of artificial agents
-%(\eg virtual characters, robots) try to exploit the positive effects of 
-%\textbf{anthropomorphic form} and avoid ``falling'' into this Uncanny Valley.
-%Consequently, there is a considerable research effort to
-%better understand the boundaries of anthropomorphic design and their effects
-%on the interaction and experience. To date, findings have been however
-%inconsistent \citep{cheetham_human_2011}.
-
-A phenomenon that is often studied related to this is \textbf{anthropomorphism}.
-Along this line, this article aims at fostering a better understanding of
-anthropomorphism (noted \Ant in this paper) in human-robot interaction 
-by considering the phenomenon
-as a whole. Robotics researchers often tend to believe that
-anthropomorphism only describes a static set of human-like features of a robot
-(like shape, speech capabilities, facial expressions, etc.). We refer to these
-characteristics as the \emph{anthropomorphic design} of the
-robot~\citep{fink_anthropomorphism_2012}, and propose that \emph{anthropomorphism} in 
-general refers to a \emph{social phenomenon} that emerges from the (real or
-imagined) \emph{interaction} between a non-human agent (\eg a robot) and a 
-human~\citep{persson_anthropomorphism_2000}. According to~\cite{epley_when_2008},
-anthropomorphism includes that the human perceives, for instance, emotional states, motivations, or 
-intentions in the non-human agent, and tends to ascribe those qualities to it.
-As such, the dynamic and
-socio-cognitive dimensions of anthropomorphism are essential to understand the
-complex bonds that human users build with artificial agents such as robots.
-
-\subsection{A few results from the field}
-\label{sec:field-results}
-
-To support the reflection on variances and dimensions of anthropomorphism, it may be 
-useful to consider a few experimental
-results. We studied anthropomorphism in several short- and long-term
-human-robot interaction studies that we carried out with embodied robots, both
-in ecologically valid real-world environments and controlled lab settings. Those
-experiments are presented in details in previously published
-articles~\citep{fink_anthropomorphic_2012, fink_living_2013, fink2014which,
-lemaignan2014dynamics}. We only highlight here a few qualitative results that
-underline the complexity of the phenomenon.
-
-\begin{figure}[b]
-        \centering
-        \begin{subfigure}[t]{0.48\columnwidth}
-                \includegraphics[width=\textwidth]{roomba-activities.png}
-                \caption{Activities related to Roomba, n = 9 households}
-                \label{fig:roomba-activities}
-        \end{subfigure}%
-        \hspace{0.5cm} 
-        \begin{subfigure}[t]{0.48\columnwidth}
-                \includegraphics[width=\textwidth]{roomba-perception.pdf}
-                \caption{People's perception of Roomba, n = 15 participants}
-                \label{fig:roomba-perception}
-        \end{subfigure}
-    \caption{Usage and perception of the Roomba vacuum-cleaning robot over a 6 months period.
-Qualitative data suggest that people's activities related to the robot as well as their perception of the robot change over time.}
-    \label{fig:roomba}
+\label{sec:introduction}
+
+Anthropomorphism can be seen as a special type of
+social response that people commonly show when interacting with 
+robots.
+The phenomenon has been observed related to various types of technology, virtual agents, daily life objects, animals, and even simple geometric moving shapes.
+It seems that people have an almost natural tendency to \textit{``see human in the nonhuman''} -- and ascribe human-like characteristics to basically anything that acts or is believed to act with apparent independence \citep{epley_seeing_2007}.
+We focus here on anthropomorphism related to robots.
+In HRI it is commonly described that users tend to perceive and treat their robot as having some human-like characteristics, and hence attribute, for instance, emotional states, motivations, or intentions to it.
+Some Roomba (vacuum cleaning robot) owners even ascribe personality and gender to their robot and choose a name for it \citep{forlizzi_service_2006,forlizzi_how_2007,krumm_my_2007,sung_domestic_2010}.
+To what extent people anthropomorphize a robot has so far mostly been studied from the sole perspective of the design of a robot.
+In short, the general assumption is that the more human-like a robot looks like and behaves, the more people will anthropomorphize it.
+Not necessarily related to anthropomorphism but focusing on the uncanny aspect, Mori's \textit{Uncanny Valley} hypothesis suggests that the relation between the robot's degree of anthropomorphic form and people's feelings toward it is non-linear \citep{mori_uncanny_1970,mori_uncanny_2012}.
+Somewhat similar to this non-linear relation between a robot's design and people's feeling toward it, we suspect that also people's tendency to anthropomorphize a robot is of dynamic nature.
+Furthermore, we hypothesize that the robot's design (its degree of anthropomorphic form) is not the only factor that plays a role in how much the robot is anthropomorphized by a user.
+
+So far, the idea of multiple factors, as well as the dynamic nature of anthropomorphism have been mostly disregarded.
+There exists no research that investigated how anthropomorphism evolves over longer periods of time based on repeated physical interactions between the human and the robot.
+This is, however, a relevant aspect to investigate.
+Long-term interaction studies found that people's perception of a robot, their attitude toward it, how they use it, and how they experience it changes over time \citep{kanda_interactive_2004,karapanos_user_2009,sung_domestic_2010}.
+It is described that besides \textit{novelty effects} also the user's increasing \textit{familiarity} with the robot over time play a role and hence, we assume that this also impacts how much the robot will be anthropomorphized.
+We will shed light on this aspect by taking a (developmental / social) psychology and cognitive science perspective because these fields provide interesting explanations for people's tendency to anthropomorphize and we believe this can offer relevant extensions to our understanding of the phenomenon in HRI.
+Our general aim is to deepen our understanding of anthropomorphism, in order to advance research on this topic.
+We make three suggestions that can be addressed in future empirical research.
+Namely, we propose that anthropomorphism is based on multiple factors, that it is multi-layered, and that it is of dynamic nature.
+
+%This is mostly theoretical material, gathered by reviewing diverse literature, reflecting upon it and integrating it.
+Anthropomorphism has first not been our main research topic, however, what led us to investigate the phenomenon in more detail, were surprising findings from our own HRI studies in which we observed anthropomorphism as an emerging phenomenon.
+%We illustrate some of our empirical data and give concrete examples, so to stimulate the discussion about the current understanding of anthropomorphism, and guide the reader towards our ideas.
+One suggestion is, for instance, to measure anthropomorphism as being a characteristic of an interaction and not only of a user's perception of a robot.
+
+%The proposed dynamics of anthropomorphism also implicate that we need to find new methods and tools to measure anthropomorphism, and we would like to take an initial step toward this by introducing a so-called \textit{anthropomorphism index}.
+
+%
+%Another reason may be that most of the research that examines the \textit{Uncanny Valley} is conducted in absence of real interaction but uses photos or videos of different robots instead.
+Furthermore, to measure anthropomorphism, mostly rating scales and questionnaires are applied.
+Based on our understanding of anthropomorphism we see a limitation in this, which we would like to discuss later.
+
+%\footnote{To facilitate things, we use the terms \textit{`non-human 
+%agent'}, \textit{`system'} and \textit{`robot'}, as well as 
+%\textit{`artifact'} more or less interchangeably throughout this 
+%article. Similarly, the terms \textit{`users'}, 
+%\textit{`observers'}, \textit{`people'} and \textit{`humans'} are 
+%used as synonyms.} 
+%
+%
+
+%
+%This idea is supported by a child-robot interaction study that we carried out with twenty-six 4-5 year old children.\footnote{A publication about this study is in work.} In a playful task, each two children were collaborating with our robotic box ``Ranger'' \citep{fink_which_2014} to assemble a domino.
+From time to time, the robot showed some unexpected behavior and we assessed to what extent children anthropomorphized the robot, \textit{e.g.} by ascribing intention or emotional states to robot.
+%We found that children commonly attributed only some types of human-like characteristics, such as perceptual skills (which are not uniquely human), feeling, and moral standing.
+Also, children perceived the robot as a social entity and agreed it could be their friend.
+However, the majority of children did not ascribe intention to the robot ...
+
+%So far in human-robot interaction (HRI), the study of anthropomorphism has mostly centered on the anthropomorphic design of a robot and its influence on people's perception of the robot.
+For instance, a prominent question is how more and less anthropomorphic robots (\textit{e.g.}, humanoid robot \textit{vs.} mechanic robot) are perceived in terms of human-likeness and to what extent the different designs evoke feelings of closeness / affinity or reluctance / revulsion.
+The so-called \textit{Uncanny Valley} hypothesis \citep{mori_uncanny_1970} states a non-linear relationship between these two variables, which has provoked a lot of research, which produced partly controversial findings, however.
+
+%Not focusing on the uncanny aspect of a human-like robot design, a general question is whether people perceive and treat a human-like robot more readily as if it was a human.
+This is one of the major research topics in social robotics.
+
+\subsection{What is Anthropomorphism?}
+\label{sec:definitions}
+
+Literature on anthropomorphism is diverse and there exist different and partly conflicting definitions (across and within disciplines).
+As a result of this, there are also different understandings of what exactly (which phenomenon) `anthropomorphism' describes.
+%This may be due to the fact that anthropomorphism is studied in a variety of different domains that each integrate their own understanding and use the same terms to refer to different phenomena.
+The problem is that despite the lack of a commonly accepted definition, the terms `anthropomorphism' and `anthropomorphic' are often used as if their meanings were clear and agreed upon \citep{persson_anthropomorphism_2000}.
+Especially in a multi-disciplinary field like HRI this can lead to a conflict.
+Thus, we have to be clear and specific about what we mean when we talk about anthropomorphism.
+
+We propose to use the term `anthropomorphism' to refer to a specific \textit{human-centered social phenomenon} but to \textit{not} use the same term to refer to the amount of human-likeness in the \textit{design} of a robot (for latter one, we propose to use alternative formulations, such as `anthropomorphic design' or `human-like form'.) We believe that this differentiation is necessary and important.
+The point that we want to make is, that anthropomorphism arises in an interaction and as such, a robot does not \textit{``contain anthropomorphism''} or have a specific level of anthropomorphism in itself, but that it only gives rise to the process of being anthropomorphized by a given user.
+The ambiguity of terms has been previously discussed \citep{persson_anthropomorphism_2000,duffy_anthropomorphism_2002}.\footnote{Several attempts have been made to clarify what exactly anthropomorphism is.
+\cite{epley_when_2008} approached the issue from a psychological point of view give several examples of what anthropomorphism is \textit{not}.
+The reader may refer to the original work for more details.}
+
+More specifically, we use the term `anthropomorphism' to describe a social phenomenon that arises in a real or imagined interaction between a human and a robot in a given context (see Figure~\ref{fig:multiple-factors}).
+The active player (the one who anthropomorphizes) is the human, and therefore, the phenomenon itself is human-centered.
+(Explanations of anthropomorphism can apply both a human-centered and an artifact-centered perspective, depending on the direction of causality which is studied: Is the human himself motivated to anthropomorphize the robot or is the robot, which leads the human to anthropomorphize it?) In our understanding, anthropomorphism includes both people's tendency to \textit{perceive / image} human-like characteristics in a robot, as well as the action of verbally \textit{ascribing / attributing} these characteristics to the robot and \textit{reacting / behaving / treating} the robot alike.
+Consequently, we believe that anthropomorphism can not only be assessed as a variable of a person's perception of the robot but also be observed in how he/she interacts with the robot (this holds implications for how we measure anthropomorphism, see Section~\ref{sec:anthropomorphism-index}).
+For instance, the user establishing eye-contact with a robot, using facial expressions when reacting to the robot, applying direct speech and polite formulations, or using social gestures toward the robot, may be counted as forms of anthropomorphism.
+In other words, we see anthropomorphism as a special type of \textit{human-like social engagement} with the robot (and to which the human commits).
+
+\subsection{Overview}
+
+The remainder of this article is organized as follows.
+
+First, in Section~\ref{sec:material-methods} we give an overview of findings related to anthropomorphism from our own work.
+As several of our observations were rather surprising to us, we will use this to stimulate the reflection on the current understanding of anthropomorphism.
+Toward the end of this section, we propose a new concept towards measuring anthropomorphism, the so-called \textit{Anthropomorphism Index}, which renders a value that expresses a user's tendency to anthropomorphize a specific robot in a given context.
+
+Section~\ref{sec:our-ideas} builds the main part of the article, which consists of the three suggestions that we make toward extending our understanding of anthropomorphism.
+We first, in Subsection~\ref{sec:multiple-factors}) outline how and why we think that anthropomorphism is based on multiple factors and not only (or mostly) on how much the robot resembles a human.
+Our argumentation is mostly driven by relevant theories from developmental and social psychology, as well as research on user experience and design.
+As a second point, in Subsection~\ref{sec:multiple-layers}, we suggest that anthropomorphism is a multi-layered phenomenon, and for this we apply a cognitive perspective and further integrate relevant work from neuroscience.
+Thirdly, Subsection~\ref{sec:dynamics} introduces the idea of how anthropomorphism evolves over time, when novelty effects wear off, and the user gets familiar with the robot and with using it.
+This is formalized in a conceptual model that we call the \textit{Dynamics of Anthropomorphism}.
+
+(Section~\ref{sec:discussion}) discusses the role and effect of disruptive behaviors for anthropomorphism and in long-term HRI, and briefly presents ethical considerations.
+
+Finally, in Section~\ref{sec:conclusions} we conclude the article.
+We  first summarize our main ideas to extend the understanding of anthropomorphism in HRI.
+Then, we present implications and limitations of our work.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+%
+%
+%		MATERIAL & METHODS
+%
+%
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%\begin{methods}
+\section{Material \& Methods}
+\label{sec:material-methods}
+
+%How did our own research and literature review lead us to the idea of developing this conceptual model?
+
+In this section we give a brief overview of the studies that we carried out to
+investigate anthropomorphism in human-robot interaction. These studies did not necessarily have anthropomorphism is the main topic, bu were motivated also by other research
+questions, and we encourage the reader to refer to our other publications for more details about these studies.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+%
+%
+%		ROOMBA STUDY
+%
+%
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Roomba Study: changes in interaction and perception over time}
+\label{sec:roomba-study}
+
+We openly explored long-term interactions between human users and domestic
+service robots in a 6-months lasting ethnographic study~\citep{fink_living_2013}. 
+We gave commercially
+available vacuum cleaning robots (iRobot's Roomba) to nine households.
+There are two findings that are related to anthropomorphism.
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=10cm]{roomba-activities.pdf}% This is a *.jpg file
+\end{center}
+ \textbf{\refstepcounter{figure}\label{fig:roomba-activities} Figure \arabic{figure}.}{~~\small Over time there is a decrease of the social activities that households engaged in associated with the robot.
+Only 1 of the 9 households gave a name to their robot, and none of the households personalized their robot.}
 \end{figure}
 
-Figures~\ref{fig:roomba-activities} and~\ref{fig:roomba-perception} give a first
-perspective on how naive users interact and perceive robots over a long period
-of time. Here, \emph{Roomba} vacuum cleaning robots were given to nine
-households for a 6-months period. The aim was to explore how people use and
-perceive the robot over time, and how they generally live with the Roomba in
-their home. At various time points, users were asked to rate their perception of
-different features of the robot on a 7-point rating scale. As
-Figure~\ref{fig:roomba-perception} shows, some features remained stable over
-time (\emph{ease of use} and \emph{fun}), and others decreased: the perceived
-\emph{usefulness}, \emph{intelligence} and \emph{impact} on their household.
-\emph{intelligence} and \emph{impact} reflect the cognitive engagement of the
-user towards the machine: we can assume that one does not care to engage in a
-(cognitive) interaction with an artifact perceived as non-intelligent and with
-no impact on one's life (and the level of activity pictured in
-Figure~\ref{fig:roomba-activities} qualitatively confirms this intuition). Even
-if one can argue that the Roomba is not designed to foster interaction, it
-raises a first question: how to sustain engagement between a robot and a human
-over a long period of time? And, as a pre-requisite to answer, do we actually
-understand the psychological phenomenon, and can we effectively account for the
-dynamics of these interactions?
-
-Those questions are certainly not new, but paradoxically, while anthropomorphism
-is a commonly discussed trait of human-robot interaction, it appears
-that we lack formal grounds and models that would account for the long-term
-dynamics of these interactions.
-
-\begin{figure}[b]
-        \centering
-        \begin{subfigure}[b]{0.48\columnwidth}
-                \centering
-                \includegraphics[width=0.75\textwidth]{ranger}
-                \caption{Interaction scenario of the \emph{Ranger} domino study: the robot toy box Ranger transports domino tiles between the two children}
-                \label{fig:ranger-expe}
-        \end{subfigure}%
-        \hspace{0.5cm}
-        \begin{subfigure}[b]{0.48\columnwidth}
-            \includegraphics[width=\textwidth]{ranger-interactions-vs-qualitative-score}
-            \caption{We found a significant negative correlation ($p=0.048$) between the
-    number of interactions and the qualitative anthropomorphic projections. n = 13 groups}
-            \label{fig:qualitative-score}
-        \end{subfigure}
-        \caption{Children's interaction with Ranger, and their anthropomorphic projections onto the robot.
-Overall, large variations of both children's behavior and their perception of the robot were found but seemed to be correlated to each other.}
-    \label{fig:ranger}
+First, in terms of \textbf{anthropomorphic interactions} with the robot, we found that the effects were overall rather low and tended to fade out over time (first point is consistent with previous work by \cite{sung_housewives_2008}).
+Overall, we observed only few instances of people anthropomorphizing the robot or interacting with it in a human-social way.
+(Also, from the opposite point of view, the robot did not have a lasting social impact on the household, for instance, it did not lastingly change established cleaning roles.)
+Some of the initially observed anthropomorphic interactions associated with the robot include \textit{watching} the robot for fun, giving a \textit{demo} of the robot to guests / visitors, \textit{personalizing} the robot, giving a \textit{name} to the robot, \textit{talking} to the robot using direct speech, and \textit{playing} with the robot.
+The majority of these anthropomorphic interactions with the robot did not last but participants stopped doing them after some time.
+Figure~\ref{fig:roomba-activities} shows how many of the 9 households engaged
+in these activities during the 6 months when the study was conducted. We interpret that the nature of
+human-robot interaction and how users experience the robot changes over time. We suspect that this is one of the reasons for why also the amount of
+anthropomorphic / human-social interactions with the robot tends to decrease over
+time. It is however possible that with some particular users, anthropomorphic interactions sustain.
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=14cm]{roomba-ratings.pdf}% This is a *.jpg file
+\end{center}
+ \textbf{\refstepcounter{figure}\label{fig:roomba-ratings} Figure \arabic{figure}.}{~~\small People's perception of the robot evolved over time, with stronger variations in the beginning.
+\textit{T1} = expectations, \textit{T2} = first usage, \textit{T3} = after 2 weeks, \textit{T4} = after 2 months, \textit{T5} = after 6 months.}
 \end{figure}
 
-%\fixme{It was written as caption of fig:ranger: ``Level of interaction with a semi-anthropomorphic robot is \emph{not} a predictor of anthropomorphic projections.'' Comment JF: this statement does not make sense to me as we found a significant negative correlation between the two.}
-
-Figure~\ref{fig:qualitative-score} calls for other initial remarks. This diagram
-shows data from a (yet unpublished) study in which 13 pairs of children (4-5 years old)
-played for about 20 minutes a Domino game with a robot toy box (the robot was tasked to
-carry domino pieces from one child to the other, Figure~\ref{fig:ranger-expe}).
-The $x$-axis represents the number of social interactions between the children
-and the robot (like talking to the robot or showing objects), based on video annotations. On
-the $y$-axis, we have a synthetic qualitative measurement of anthropomorphic
-projections onto the robot, based on two interviews with the children. The correlation between both these
-values is significantly \emph{negative}: the more the children engaged into
-interaction, the less prone to anthropomorphic projections they were. This
-diagram also highlights an interesting cluster of children who did not interact
-much with the robot, and still reported a strong anthropomorphic perception of
-the robot.
-
-These results may seem counter-intuitive at first sight, and illustrate that the
-mechanisms that relate anthropomorphism to adoption and engagement are
-non-trivial. In section~\ref{sec:cognition-neuroscience}, we sketch a model of
-the cognitive correlates of anthropomorphism that partially account for these
-results.
-
-\subsection{Towards a formal understanding of anthropomorphism}
-
-These first remarks lead to the main question we attempt to address in this
-article: how can we understand \emph{anthropomorphism} as a whole, and in such a
-way that it supports or improves human-robot interaction?
-
-We propose to discuss anthropomorphism from three
-complementary perspectives:
-
-%Based on an extensive literature review~\citep{fink_anthropomorphism_2012},
-%several field and lab studies previously mentioned, and insights from the
-%cognitive neuroscience, we propose to discuss anthropomorphism from three
-%complementary perspectives.
-
-First, by reviewing what anthropomorphism actually \emph{means}:
-besides an \emph{artifact-centered} understanding that explains anthropomorphism from the human-like design of the non-human artifact, it seems important to explicit the social component, namely a \emph{human-centered} understanding, of anthropomorphism.
-
-Second, we propose a model, called the \textit{Dynamics of Anthropomorphism} to understand how anthropomorphism evolves over time ~\citep{lemaignan2014dynamics}.
-These dynamics are non-monotonic, and effects like the
-\emph{novelty effect} play here a key role.
-
-Finally, we adopt a third perspective on anthropomorphism by investigating its
-\emph{cognitive correlates}. Several studies previously showed that we build
-instinctive bonds with robots as soon as we attribute animacy, and we also know
-from social psychology some of the mechanisms that lead to
-\emph{familiarization}. We attempt here to ``connect the dots'', in order to
-build a practical model of the cognitive stages we encounter in human-robot
-interaction.
-
-%\paragraph{Two hypotheses}
-Our research question also translates to two
-hypotheses, which structure the reflections of this article:
+Second, in terms of people's \textbf{perception of human-like characteristics and social traits of the robot}, we obtained similar findings.
+The robot was overall not perceived as having human-like characteristics, and attributions of intelligence, for instance, decreased over time.
+At several time points during the 6-month lasting study, participants were asked to rate their perception and impression of the robot on 7-point Likert scales.
+Concerning anthropomorphism, we included
+\textit{perceived intelligence}, experienced \textit{fun} when using the
+robot, and \textit{perceived impact} of the robot on the household as indicators for the perception of human-likeness in the robot.
+Figure~\ref{fig:roomba-ratings} shows how people's perception of the robot evolves over time.
+Participants were generally not sure as how \textit{intelligent} they should rate the robot.
+Interestingly, at all five time points, male participants rated the robot as more intelligent (average 4.5) than females (average 3.4), however, this difference was not significant.
+Still, this suggests that gender, and probably other individual characteristics play a role.
+Also in terms of \textit{experienced fun} there was a non-significant but noteworthy gender difference.
+The rating for experienced fun remained quite stable for male participants, whereas it tended to decrease with time for female participants.
+The rating for \textit{perceived impact} reflects to what extent the robot is perceived to play a decisive role in the household.
+The average value remarkably increased after participants had used the robot the first time but then constantly decreased.
+This shows again, that people's perception of the robot changes over time, and that the initial moments using and interacting with a robot are special.
+Overall, Figure~\ref{fig:roomba-ratings} shows that after the first usage of
+the Roomba (T2), most of the perceived constructs slightly decrease (and hence
+are less positively rated) as time goes by. The course is different for the
+perceived \textit{ease of use} of the robot, as participants become more
+experienced with the robot over time.
+
+Summing it up, in accordance with previous work we also found relatively low rates of users
+treating and perceiving their vacuum cleaning robot as a living (or human-like)
+entity \citep{sung_housewives_2008}. We interpret that it might be the pure
+functional purpose and non human-like form of the Roomba that prevented people
+from anthropomorphizing it. Still, we observed some initial anthropomorphic
+effects, both reflected in interaction with and perception of the robot.
+However, most of the anthropomorphic effects did not last long. One fairly
+stable human-like interaction with the robot was \textit{talking to the robot},
+despite the fact that the robot was not able to recognize and respond to verbal
+statements.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+%
+%
+%		FORUM STUDY
+%
+%
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Forum Study: Anthropomorphism and the Purpose of Use of a Robot}
+\label{sec:forum-study}
+
+By carrying out a content analysis of 750 posts in three online discussion forums, we investigated the amount and context of anthropomorphic language that users apply when writing about their robotic dog AIBO, the vacuum cleaning robot
+Roomba, and the tablet computer iPad \citep{fink_anthropomorphic_2012}. These three devices were chosen as they show different designs and
+fulfill different purposes. We would describe (1) the AIBO as a zoomorphic /
+pet-like robot that does not have a clear purpose but engages people to play
+with it; (2) the Roomba as a mechanical / functional domestic service robot that has
+a practical main purpose (vacuum cleaning) but offers not much of interactivity;
+and (3) the iPad as a minimalistic designed interactive (touch-based) technology
+with multiple purposes (both entertainment, and professional / practical use).
+The general goal of this analysis was to compare the three devices in terms of how much they are anthropomorphized in general and regarding the topic of the post.
+Furthermore, we wanted to find out where on a hypothetical scale of anthropomorphism the Roomba would range compared to the AIBO and the iPad.
+There are two findings that are relevant here.
+
+First, in terms of how \textbf{anthropomorphic language is related to the device} (and most likely the overall design of it), we found a significant difference between how much the three devices are anthropomorphized.
+It was not a surprise that the highest amount of anthropomorphic
+language (56.6~\%) was found in the AIBO forum. In comparison, only 11.7~\% and
+respectively 2.2~\% of the segments in the Roomba and the iPad forum contained
+anthropomorphic expressions. These data suggest that on a hypothetical scale of
+perceived human-likeness (or rather life-likeness), Roomba is closer to the iPad
+than to the AIBO, at least in matters of how they are described with words. This
+was a surprised, as we had expected the Roomba would range closer to the AIBO, as both are autonomously moving robots.
+We interpret that the physical embodiment of the object and to what extent it resembles a life-like entity has a strong effect on how much it is anthropomorphized.
+This explains why a robotic dog is anthropomorphized more than more functionally designed devices.
+
+Second, in terms of how \textbf{anthropomorphic language is related to the topic of the conversation}, we found a significant difference between the three topics \textit{relation}, \textit{usage}, and \textit{technical aspects}.
+The analysis suggests that anthropomorphizing happens more when the topic of conversation is \textit{relation}, compared to \textit{usage}, and \textit{technical} aspects.
+This was true for the Roomba and the iPad forum.
+However, in the AIBO forum, the amount of anthropomorphic segments was found highest for the \textit{usage} topic.
+We interpret that it is the different type of interaction / context of use that makes the difference.
+Contrary to the iPad and the Roomba,
+the AIBO is made to encourage the user in a playful / social interaction, which
+in turn creates a specific use context. Further, AIBO has the ability to respond
+intelligently to its user and environment, which might also encourage people to
+ascribe human-like abilities to it while interacting with it.
+
+Overall, findings of the forum content analysis suggest that there are differences in
+people's tendency to use anthropomorphic language, originating form the design
+characteristics of the artifact. A pet-like robot encourages people to use more 
+anthropomorphic expressions when discussing about it in an online forum. However, 
+the difference might also be related to other factors that we did not analyze 
+here (\eg. author's characteristics). Our analysis further shows that the design 
+of the robot seems to more important than the topic of the discussion. 
+Interestingly, not only the physical embodiment
+of the robot but also its interaction complexity and purpose of use are likely to play a role in how much the robot is anthropomorphized.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+%
+%
+%		DOMINO STUDY
+%
+%
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Domino Study: Effects of Unexpected Robot Behavior}
+\label{sec:domino-study}
+
+The so-called ``Domino study'' describes a child-robot interaction study
+that we carried out in a controlled lab setting.
+13 pairs of 4-5 year old children (26 children in total) were playing a collaborative domino game, in which the robotic box ``Ranger'' \citep{fink_which_2014} was transporting domino tiles between the two children.
+The robot
+was operated by one of the experimenters using the wizard-of-oz technique.
+For the first 7 times a child called the robot to come over to fetch a domino tile, Ranger behaved correctly, coming straight over to the child.
+However, in a second phase Ranger would show some unexpected misbehavior.
+This misbehavior was pre-defined and executed by the human Wizard at given time points.
+One of the goals of this
+study was to investigate the effect of this unexpected robot behavior on (1) how much children ascribe
+human-like abilities (\eg intentions, cognitive abilities) to the robot, thus how much they anthropomorphize it; and (2) children's interaction in general and their active engagement with robot.
+Children's perception
+of the robot was assessed in a qualitative way using several short-interviews, in which we assessed, for instance, to what extent children believed Ranger has its own will, has feelings, is able to understand what they say, can be left alone at home (the questionnaire was adapted by \citep{kahn_jr._robotic_2006}).
+The interaction data was analyzed quantitatively after having annotated the video recordings of the interaction.
+We were especially interested in typical human-like actions, \eg do children talk to it directly, use gestures
+toward it or use polite formulations.
+
+First, regarding children's \textbf{perception} of the robot, we found that they commonly attributed hearing and seeing abilities to Ranger.
+However, though all children had interacted with a partly misbehaving robot, 12 of 26 children answered the robot would always obey to them, and the majority did not believe that the robot could do something silly.
+This suggests that they did not view the robot as having its own will or intentions itself.
+Most of the children attributed feelings to the robot and more than half of them could imagine Ranger as being their friend.
+This reflects that the robot is more perceived as a social agent but not necessarily having human-like qualities.
+In terms of what \citep{kahn_jr._robotic_2006} labels as ``moral standing'', we asked the 4-5 year-old's whether it would be ok to leave the robot alone at home while going on vacation.
+20 of 26 children replied negatively, however their justifications on this answer do not reflect an attribution of moral standing to the robot (\eg that the robot deserves care).
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=7cm]{correlation.pdf}% This is a *.jpg file
+\end{center}
+ \textbf{\refstepcounter{figure}\label{fig:correlation} Figure \arabic{figure}.}{~~\small Correlation between children's anthropomorphic perception of the robot and their amount of interactions with it ($n = 13$ groups).
+A scatter plot of the count of engagement actions (per group) and the anthropomorphic perception of the robot (per group) shows a significant negative correlation ($r(11)=-0.56, p=.05$).
+There appears a cluster of groups at the top left corner, which suggests that those groups of children that interacted less with the robot, anthropomorphized the robot more in their verbal statements.}
+\end{figure}
+
+Second, the statistical analysis of the interaction data was unfortunately not very conclusive in terms of anthropomorphism.
+(This may be due to the fact that children showed very different \textbf{interaction styles}, so that we were not able to identify common patterns.) However, when looking at the amount of some specific actions toward the robot that reflect engagement, data suggest that children were more engaged with Ranger during the second phase (when the robot misbehaved from time to time).
+These engagement reflecting actions were \textit{exploring} the robot, using \textit{gestures} toward it, \textit{misusing} it, \textit{touching} the robot, \textit{talking} directly to it, and \textit{looking} at the experimenter (this shows that children were surprised and confused about the robot's misbehavior).
+We found that the manipulation of Ranger's behavior was sufficient to sustain children's engagement with the robot.
+This result is not directly related to anthropomorphism.
+However, we wanted to see whether there is correlation between children's engagement with the robot and how much they anthropomorphize it (perceive the robot as human-like, and attribute human-like characteristics to it).
+Do children who perceive more human-like characteristics in the robot also interact with it in a more human-like engaged way?
+As Figure~\ref{fig:correlation} shows, the amount of children's anthropomorphic statements related to the robot (y-axis; qualitatively assessed from the interviews) and their interaction engagement with it (x-axis; quantitatively measured from the interaction videos) are negatively correlated $(r(11)=-0.56, p=.05)$.
+This was a main surprise.
+What had expected the opposite, namely children who engage more in the interaction would also perceive the robot as more human-like.
+However, the negative correlation suggests exactly the opposite: those children who interact more with the robot, treat and perceive it less as if it was a human.
+How can we interpret this finding?
+We think that those children who interacted more with Ranger, familiarized themselves better with it, and were better able to ``de-mystify'' the robot, thus being less in need of anthropomorphizing it.
+
+Summing it up, children in the Domino Study anthropomorphized the robot conditionally: they attributed perceptual skills, mental states (feelings), and social companionship to the robot.
+Contrary, children did not attribute intention or moral standing to the robot.
+Some children tended to anthropomorphize the robot in how they were interacting with it: by using social or pointing gestures to it and by using polite formulations.
+Interestingly, we found a negative correlation between children's quantified engagement with the robot and their tendency to anthropomorphize the robot, which suggests that less interaction comes along with increased anthropomorphism.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+%
+%
+%		ANTHROPOMORPHISM INDEX
+%
+%
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Anthropomorphism Index}
+\label{sec:anthropomorphism-index}
+
+It is not very clear how to operationalize and measure anthropomorphism.
+The phenomenon can be both subtle and complex at the same time, which poses challenges for finding appropriate study scenarios and metrics.
+So far, most studies on anthropomorphism involved showing pictures or videos of different types of robots to participants who are then asked to fill in a questionnaire (mostly using rating scales), in order to assess how much they perceived the different robots as human-like.
+We see two critical points here.
+First, the \textit{evaluation scenario}, in which anthropomorphism is studied appears limited.
+When showing pictures or videos of robots to participants, the robots are not physically present and one cannot directly interact with it.
+This is critical, as the user experience may be blurred.
+We have seen in our own research that from seeing pictures or a video of a robot, participants were not able to make detailed judgments about the robot, concerning its height / size, the materials used in the robot, and the sounds it produces -- in other words, the whole expression of the robot was limited.
+The point we want to make here is that nothing is as rich as direct non-mediated interaction.
+Especially, if we agree that anthropomorphism arises in an interaction, we need to study it in evaluation scenarios that include interaction.
+Furthermore, it would preferable to study anthropomorphism over extended periods of time or over several interaction sessions, as we hypothesize that anthropomorphism shows dynamics over time (see Section~\ref{sec:dynamics}).
+
+Second, we also see limitations concerning the \textit{measurement aspect}.
+So far, there exist mostly questionnaires that quantify anthropomorphism using rating scales, such as the ``Godspeed'' questionnaire developed by \cite{bartneck_measurement_2008}.
+We are not sure, however, whether this is sufficient.
+Anthropomorphism is a social phenomenon and we question ourselves whether it can really be measured solely as a post variable and quantified on a closed rating scale that does not allow the participant to elaborate on his/her answer.
+There may be more qualitative alternatives by using open-ended more descriptive techniques, in order to better understand how exactly and why the participant perceives the robot as human-like.
+Also, questions may be less abstract but ask more specifically about concrete aspects of human-likeness, \eg as suggested by \cite{kahn_jr._robotic_2006,ruijten_introducing_2014}.
+
+We propose that measurement tools of anthropomorphism should not only consider people's perception of the robot but also their interaction (how they behave) with the robot.
+Some previous work already suggests that there exists something like \textit{``anthropomorphic interaction''} \citep{krach_can_2008,hegel_understanding_2008,weiss_i_2009}.
+It would be interesting to formalize what this ``anthropomorphic interaction'' exactly is and how it can be evaluated and contribute to our understanding of anthropomorphism.
+Both quantitative and qualitative data could be combined for this, in order to reduce subjectivity.\footnote{In general, it is clear that the methods used need to be adapted to the specific research question.
+Large-scale surveys do usually not include in-depth interviews or physical interaction.
+However, for smaller sample sizes that one usually finds in empirical HRI studies, qualitative techniques allow for looking into details.}
+We would like to take an initial step toward developing such a measurement tool by proposing the so-called \textit{Anthropomorphism Index} ($AntX$).
+This is on one hand a proposed toolkit to measure anthropomorphism related to a person, based on his/her perception of the robot and his/her interaction with it; on the other hand, it also stands for a value that reflects how much a person anthropomorphized a robot in a given interaction scenario.
+The idea, which is new here, is to combine aspects of the perception with aspects of the interaction (in-situ measurement).
+This builds on the idea that anthropomorphism is a social phenomenon that arises in an interaction.
+
+Typically, \textbf{perception} would be measured both prior to the interaction (expectations of human-likeness of robots in general, for instance) and after the interaction with the robot (describing and viewing the robot as human-like).
+A list of concrete questions is not defined yet but examples could be taken from already existing questionnaires (\eg \cite{bartneck_measurement_2008,weiss_i_2009,kahn_jr._robotic_2006,ruijten_introducing_2014}).
+There can be yes/no type questions (\eg ``Can the robot be hungry?''; ``Can the robot feel ashamed?''), ratings using semantic differentials or Likert-type scales (\eg ``Playing with the robot is more like ...
+`playing with a toy' compared to `playing with a friend'.'' (semantic); ``The robot understands me'' (1-5 Likert-scale, for instance)), and open-ended questions (\eg ``Can you leave the robot alone at home while going on a 2-week holiday?
+Why (not)?'').
+The respective answers to these questions can be assigned with points reflecting the degree of anthropomorphic perception, and then summed up to obtain an overall estimate.
+
+The \textbf{interaction} scenario should be video-recorded to allow for later analysis.
+Specific types of anthropomorphic interaction (\eg use of polite formulations and direct speech, establishing eye-contact with the robot) can then be annotated in the videos.
+A list of such specific actions is not yet defined.
+Again, there can be yes/no items (\eg Did the participant use polite formulations or other forms of social desirability toward the robot?), and more quantified items (\eg How much did the participant talk directly to the robot?, How much did the participant establish eye-contact with the robot?).
+It would also be interesting to look more into details of the behavior aspects, for instance, How did the participant address the robot verbally?, How much was the participant using normal human-human like conversation as compared to typical interface-like conversation (more giving commands, adjusting speech rate, using monotonic speech).
+One could again think of assigning a specific number of points for items that reflect anthropomorphic interactions, and in the end build the sum to obtain an overall estimate.
+
+For both values, perception and interaction, there may be a pre-defined maximum value of $AntX$ or a fixed range of it that is seen as the desired degree of anthropomorphism (maximum anthropomorphism may not always be optimal or desired, sometimes a more machine-like treatment is preferred).
+In case of several interaction sessions or longitudinal interaction, several short interviews / questionnaires could be carried out to track how perception changes over time.
+Accordingly, the video analysis can be segmented and split into phases, which are then compared against, so to analyze how anthropomorphic interactions evolve over time.
+
+%\section{Related Work}
+%\label{sec:related-work}
+%
+%Findings from related work, maybe theoretical background.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+%
+%
+%		OUR IDEAS
+%
+%
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Extensions to the Understanding of Anthropomorphism in HRI}
+\label{sec:our-ideas}
+
+As presented in the previous section, some of our research on anthropomorphism in HRI produced unexpected results.
+We see it as our job to not hide surprising results but to offer a plausible interpretation to the scientific community.
+To allow doing so, we went through literature on anthropomorphism and reviewed articles from various disciplines, including HCI, philosophy, developmental and social psychology, cognitive sciences, artificial intelligence, and neurosciences.
+It is not trivial to synthesize and summarize such a diverse body of literature.
+Overall, we found that, on one hand anthropomorphism is an interesting research topic in a variety of disciplines.
+On the other hand, researchers agreed that anthropomorphism is of complex nature and that the phenomenon is still not very well understood as a whole \citep{duffy_anthropomorphism_2003,epley_seeing_2007}.
+The literature review helped us not only to better interpret our unexpected results on human-like engagement with robots but also to get an idea of the psychological motivations and underlying cognitive processes of anthropomorphism \citep{epley_seeing_2007}.
+We think that it is worth sharing the obtained insights with the broader HRI community (which is diverse itself).
+To do so in a structured way, we would like to make three suggestions toward extending the current understanding of anthropomorphism in HRI.
+We do not offer a perfect model or a complete framework here but share our conceptual ideas.
+This will hopefully lead to a constructive discussion among researchers and help generate more empirical work on why humans tend to perceive and interact with robots as if they were somewhat human.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+%
+%
+%		MULTIPLE FACTORS
+%
+%
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Anthropomorphism is based on Multiple Factors}
+\label{sec:multiple-factors}
+
+%\begin{figure}
+%\begin{center}
+%\includegraphics[width=13cm]{anthropo.pdf}% This is a *.jpg file
+%\end{center}
+% \textbf{\refstepcounter{figure}\label{fig:multiple-factors} Figure \arabic{figure}.}{~~\small Anthropomorphism arises in an interaction between a human ($H$) and a robot ($R$) in a specific context of use ($C$).
+These are the three main factors on which anthropomorphism is based.
+Further, to account for dynamics over time ($t$), the interaction history is taken into account.
+There are two main perspectives from which anthropomorphism can be studied, a human-centered one, focusing on variables related to the human; and an artifact-centered one, focusing on variables related to robot.}
+%\end{figure}
+
+Once considering anthropomorphism as a phenomenon that arises in an \textbf{interaction} between a robot and a human in a given context \citep{persson_anthropomorphism_2000}, it becomes apparent that the phenomenon is based on multiple factors.
+%(see Figure~\ref{fig:multiple-factors}).
+To account for both the human and the robot as the two main interaction partners, as well as for the context and other external variables that constitute the interaction, a comprehensive perspective is required.
+We suggest to apply the concept of \textbf{user experience} to interpret how anthropomorphism emerges.
+According to ISO 9241-210, user experience is defined as \textit{``a person's perceptions and responses resulting form the use and/or anticipated use of a product, system or service''}.
+User experience includes all the users' emotions, beliefs, preferences, perceptions, physical and psychological responses, behaviors and accomplishments that occur before, during and after use.
+The ISO also names three factors that influence user experience: system, user, and the context of use \citep{iso_ergonomics_2010}.
+Applying such a user-centered perspective, we take up the \textbf{human} (denoted as $H$), the \textbf{robot} ($R$), and the \textbf{context of use} ($C$), as the three main factors on which anthropomorphism (denoted as $A$) is based.
+
+\subsubsection{Characteristics of the Human\\}
+\label{sec:factor-human}
+
+The first main factor of anthropomorphism are characteristics of the human $H$.
+This includes several sub-factors $(h_0, ...
+, h_n)$, \eg psychological factors, demographic factors, and other traits of personality.
+It would theoretically be possible to compute a human-specific value $H=\{h_0, ...
+, h_n\}$ that indicates how much a person is likely to anthropomorphize, based on individual factors (in practice this looks different).
+Such value could for instance range between $0$ and $1$ to suggest something similar to a probability for a person to anthropomorphize.
+The point here is to account for individual differences of anthropomorphism and to acknowledge that each user is unique, having individual expectations, beliefs, emotions, and conceptions.
+This can be called a \textit{human-centered perspective} on anthropomorphism.
+%(see Figure~\ref{fig:multiple-factors})
+In the following paragraphs we present possible sub-factors. This list may not be complete, and we leave it open to other researchers to extend it.
+
+\paragraph{Psychological factors} can account for why some people are (intrinsically) more motivated to anthropomorphize than others.
+Irrespective of a robot's characteristics (which will be treated in the next Subsection, \ref{sec:factor-robot}) three main psychological determinants have been identified to explain a person's readiness to anthropomorphize.
+\cite{epley_seeing_2007} present those in their \textit{3-Factor Theory}, which suggests that some people are more likely to anthropomorphize when:
 
 \begin{enumerate}
-\item ~A person's tendency to anthropomorphize a robot
-    is based on several factors, including (but not limited to) (1) the
-    design of the robot, (2) the personal characteristics of the human user,
-    and (3) the context and situation of use. For instance, a social context
-    and purpose of the robot increase anthropomorphism: \textit{anthropomorphism
-    as a multi-factor phenomenon}.
-
-\item ~A person's tendency to anthropomorphize a robot
-    evolves in a non-linear way over time and with growing experience that the
-    person has with the robot. For instance, a more experienced user will
-    perceive the robot as more familiar and predictable, and in turn
-    anthropomorphizes the robot less: \textit{anthropomorphism as a dynamic
-    phenomenon}.
-
+\item anthropocentric knowledge is accessible and applicable to the artifact (\textit{elicited agent knowledge})
+\item they are motivated to explain and understand the behavior of other agents (\textit{effectance motivation}), and
+\item they have the desire for social contact and affiliation (\textit{social motivation}).
 \end{enumerate}
 
-Further, we would like to investigate the link between the variances in anthropomorphism and the correlating cognitive states.
-
-\subsection{Article overview}
-
-%\begin{inparaenum}[\itshape 1)\upshape]
-
-The remainder of this article is organized as follows.
-According to the three perspectives that we take, 
-we first (in Section
-%\ref{sec:overview-studies}, we give a brief overview on the various studies that
-%we conducted to investigate anthropomorphism, namely \item the Roomba study,
-%\item the Forum study, \item the Ranger domino study. Next, Section
-\ref{sec:anthropomorphism}) aim to establish a common ground in the
-understanding of anthropomorphism. We review literature from several relevant domains and integrate the different explanations into an understanding of
-anthropomorphism as a multi-factor phenomenon.
-Based on this, Section~\ref{sec:our-ideas} introduces our initial model of the
-\textit{Dynamics of Anthropomorphism}. This model describes the variances
-and dynamics of people's tendency to anthropomorphize an artificial agent,
-such as a robot. 
-Then Section \ref{sec:cognition-neuroscience} presents a
-cognitive and neuroscience perspective on anthropomorphism to consolidate
-our considerations and the proposed model.
-This is followed by a discussion
-about the limitations of our approach (Section \ref{sec:discussion}) and the
-existing and alternative ways to measure anthropomorphism in human-robot
-interactions.
-Finally, Section \ref{sec:conclusion} concludes this article
-and offers starting points for further research on anthropomorphism and the
-effect of the human-like design approach in robotics.
-
-%\end{inparaenum}
-
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%
-%%
-%%
-%%		OVERVIEW ON OUR STUDIES
-%%
-%%
-%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-%\section{Studying anthropomorphism in HRI}
-%\label{sec:overview-studies}
-%
-%In this section we give a brief overview of the studies that we conducted to
-%investigate anthropomorphism in human-robot interaction. Note that it was not
-%the main purpose of these studies to analyze in detail the effect of different
-%dimensions human-likeness of a robot on the user's perception of and interaction
-%with the robot. Each of these studies were motivated also by other research
-%questions, and we encourage the reader to refer to our other main publications
-%about these studies for more details.
-%
-%
-%\subsection{Roomba study: how people live with a vacuum cleaning robot}
-%
-%We openly explored long-term interactions between human users and a domestic
-%service robot in a 6-months lasting ethnographic study~\citep{fink_living_2013}. 
-%We gave a commercially
-%available vacuum cleaning robot (iRobot's Roomba, see Figure
-%\ref{fig:aibo-roomba-ipad} middle) to nine households. 
-%%in the French speaking
-%%part of Switzerland. 
-%%The fairly diverse sample of households consisted of 2
-%%single homes, 1 couple, and 6 families with children in their home. In total,
-%%this summed up to 30 participants: 15 adults (26-71 years old, mean age 43.6
-%%years), and 15 children (6 months to 18 years old). During the 6 months, each
-%%household was visited 5 times to conduct interviews and make field observations
-%%in the households. Moreover, during several weeks, households were asked to fill
-%%in a diary to report the usage of the robot and other cleaning activities.
-%Hereafter, we refer to this study as the ``Roomba study''. It is one of very few 
-%long-term human-robot interaction studies in the domestic environment. 
-%In the following, we present findings in respect of two aspects: First, we
-%qualitatively describe what kinds of anthropomorphic interactions between
-%participants and the robot were observed and outline how these interactions
-%evolved over time.  Second, we present people's perception of human-likeness and
-%social capabilities of the robot and how this perception changed over
-%time.
-%
-%%\footnote{\hl{note that these two different kinds of data
-%%(behavior/interaction and perception) already show that we try to measure
-%%anthropomorphism from these two angles!}}
-%
-%%The main goal of this study was to explore how households live with a vacuum
-%%cleaning robot over an extended period of time. We wanted to analyze how the
-%%usage of and interaction with the robot evolve over time, and to identify
-%%adoption phases as well as factors that impact on the long-term acceptance of
-%%service robots in homes.
-%
-%
-%\subsubsection{Anthropomorphic interactions with the robot\\}
-%
-%It has been described in several previous studies of the Roomba that users tend
-%to engage in a variety of non-cleaning activities associated with the robot,
-%including, but not limited to, naming, ascribing personality and gender
-%\citep{forlizzi_service_2006,forlizzi_how_2007,krumm_my_2007,sung_domestic_2010}.
-%\cite{sung_housewives_2008} carried out a survey among 379 Roomba users to
-%investigate how common these activities are. The authors concluded that overall,
-%respondents had relatively low rates of treating Roomba as a living entity.  
-%Similarly, in our long-term study of the Roomba in homes, we found that only few 
-%people tended to interact in an anthropomorphic or human-social way with their 
-%vacuum cleaning robot and that this effect did not sustain. Overall, our data 
-%suggest that the anthropomorphic effect and the social
-%impact of a functional robot on a household are rather marginal.
-%%There were just few instances of people anthropomorphizing the robot and
-%%interacting with it in a human-social way. More importantly, overall, these
-%%anthropomorphic interactions with the robot did not last but seemed to be
-%%somehow related to the novelty of the robot.
-%
-%We categorized several interactions and actions with the robot as
-%anthropomorphic or human-social (in a broader sense). 
-%%Examples of what we categorized as somehow social and anthropomorphic
-%%(human-like) interactions with the robot include \textit{watching} the robot
-%%for fun, giving a \textit{demo} of the robot to guests / visitors, taking a
-%%\textit{photo/video} of the robot, \textit{personalizing} the robot, giving a
-%%\textit{name} to the robot, \textit{talking} to the robot using direct speech,
-%%\textit{playing} with the robot, and making \textit{adjustments} to the home
-%%due to the robot. 
-%Figure \ref{fig:roomba-activities} shows how many of the 9 households engaged
-%in these activities during the 6 months when the study was conducted. 
-%
-%%\begin{figure}
-%%    \centering
-%%    \includegraphics[width=0.5\columnwidth]{roomba-activities.png}
-%%    \caption{Activities with the robot over time, n = 9 households. This bar
-%%        chart shows how many of the 9 households carried out different kinds of
-%%        anthropomorphic / social activities with and related to the robot at 3
-%%        time points during 6 months. Activities include \texttt{watching} the
-%%        robot for fun, giving a \texttt{demo} of the robot to guests / visitors,
-%%        \texttt{personalizing} the robot, giving a \texttt{name} to the robot,
-%%        \texttt{talking} to the robot, \texttt{playing} with the robot.
-%%        Participants were asked to report on these activities at 3 time points
-%%        after the robot was deployed in their home: after 2 weeks, after 2 months,
-%%        and after 6 months.} 
-%%
-%%\label{fig:roomba-activities}
-%%\end{figure}
-%
-%\begin{figure}
-%        \centering
-%        \begin{subfigure}[b]{0.48\columnwidth}
-%                \includegraphics[width=\textwidth]{roomba-activities.png}
-%                \caption{Roomba activities}
-%                \label{fig:roomba-activities}
-%        \end{subfigure}%
-%        ~ %add desired spacing between images, e. g. ~, \quad, \qquad etc.
-%          %(or a blank line to force the subfigure onto a new line)
-%        \begin{subfigure}[b]{0.48\columnwidth}
-%                \includegraphics[width=\textwidth]{roomba-perception.pdf}
-%                \caption{Roomba perception}
-%                \label{fig:roomba-perception}
-%        \end{subfigure}
-%        \caption{\textbf{The Roomba study: Long-term interaction with a robot.\\}
-%    \textbf{a)} Activities with the robot over time, n = 9 households. This bar
-%        chart shows how many of the 9 households carried out different kinds of
-%        anthropomorphic / social activities with and related to the robot at 3
-%        time points during 6 months. Activities include \texttt{watching} the
-%        robot for fun, giving a \texttt{demo} of the robot to guests / visitors,
-%        \texttt{personalizing} the robot, giving a \texttt{name} to the robot,
-%        \texttt{talking} to the robot, \texttt{playing} with the robot.
-%        Participants were asked to report on these activities at 3 time points
-%        after the robot was deployed in their home: after 2 weeks, after 2 months,
-%        and after 6 months.\\
-%	\textbf{b)} People's perception of the robot over time, n = 15 participants.
-%    		This line chart shows how people's perception of the robot evolves over
-%    		time. At 5 time points people were asked to rate the robot according to the
-%    		following aspects: the perceived \texttt{intelligence} of the robot, the
-%    		perceived \texttt{usefulness}, the perceived \texttt{ease of use}, how much
-%    		\texttt{fun} it was to use the robot, how far they found the robot had an
-%    		\texttt{impact} on their household, and their {overall} impression of it.}
-%    		\label{fig:roomba-study}
-%\end{figure}
-%
-%
-%\paragraph*{Watching the robot for fun.} We categorize watching a robot for fun
-%as an entertaining, emotional activity, reflecting a feeling of empathy for the
-%robot. In \cite{sung_housewives_2008} survey, 73~\% of the participants reported
-%to watch their Roomba running for fun. While in the beginning of our study, also
-%a quite high proportion (6 of 9 households) reported to watch the robot for fun,
-%after 2 and 6 months the number of households that engaged in this activity
-%decreased by half. 
-%
-%\paragraph*{Giving a robot demo to visitors.} It is somehow natural that owners
-%of innovative devices show the device to others and ask for their opinion about
-%it \citep{rogers_diffusion_1995}. However, this activity suggests that the robot
-%is presented as a new part of the household to visitors.
-%\cite{sung_domestic_2010} described that a vacuum cleaning robot can serve as a
-%mediator and encourage social interaction among people. We categorize giving a
-%demo of the robot to visitors / guests as such an activity. During the first 2
-%weeks with the robot 8 of 9 households in our study showed their robot to
-%others, and still after 2 and 6 months 5 of the households engaged in this
-%activity. This number is more or less in accordance with the 57~\% of survey
-%respondents who stated to give demonstrations to others
-%\citep{sung_housewives_2008}.
-%
-%%\paragraph*{Taking photos / videos of the robot.} How far taking a photo or
-%%video of a robot can be seen as an anthropomorphic interaction is questionable.
-%%However, it reflects the fact that the robot is observed by the user who for
-%%some reason is motivated to record the event. The number of households that
-%%took a photo or video of the robot decreased over time from 5 households in the
-%%beginning to 1 household after 6 months.
-%
-%\paragraph*{Personalizing the robot.} It has been found that people are
-%motivated to personalize technology as a form of self-expression (identity
-%projection) or when they use a technology a lot and know how to customize it
-%(technical identity projection) \citep{blom_personalization:_2000}. Though
-%\cite{sung_pimp_2009} found that some Roomba users who were given a
-%customization toolkit personalized their Roomba, none of the users in her study
-%who was \textit{not} given this toolkit personalized their Roomba. Also in our
-%study none of the 9 households engaged in a personalization activity.
-%
-%\paragraph*{Giving a name to the robot.} Giving a name to an artificial agent
-%reflects a certain kind of personal relationship to the agent. By naming a
-%robot, it is not anonymous anymore, and might be perceived as a moral agent. As
-%such, naming an artificial agent can be classified as anthropomorphizing this
-%agent. It further suggests that the agent is talked to directly. Though more
-%than 23~\% of the survey participants in \cite{sung_housewives_2008} study
-%reported to name their Roomba, only 1 of 9 households in our study did so. 
-%
-%\paragraph*{Talking directly to the robot.} Using direct speech toward an object
-%or artificial agent that does not have the ability to recognize and process
-%speech (such as verbal comments) or other sound cues, is an interesting
-%phenomenon which can be classified as an anthropomorphic interaction. Whereas
-%only 11~\% of the survey respondents in \cite{sung_housewives_2008} study
-%reported to talk to their robot, around half of the households engaged in this
-%activity and the proportion did not notably decrease over time. 
-%
-%\paragraph*{Playing with the robot.} In our study, it were mostly children who
-%engaged in playing with the robot, however, most of them stopped doing so after
-%some time. The number of household playing with their Roomba decreased from 8
-%when asked after 2 weeks with the robot, to 4 households after 2 months, and 1
-%household after 6 months. In \cite{sung_housewives_2008} survey, 37~\% of the
-%Roomba owners reported to play and experiment with their robot.\\ 
-%
-%%\paragraph*{Making adjustments to the home due to the robot.} To help Roomba
-%%clean, \cite{sung_housewives_2008} found in an online survey that about half of
-%%the 379 participants made physical modifications to their homes. This process
-%%is referred to as \textit{roombarization}, and it seems to be a unique aspect
-%%of adopting a domestic service robot. In our study, almost all the households
-%%made adjustments when they used the robot for the first time in front of us.
-%%However, during the first two weeks with the robot, only 3 households reported
-%%to have adjusted something due to the robot, and after 6 months it was only 1
-%%household that still engaged in this activity. This decrease is, however,
-%%logical since after some time most people had done all the necessary
-%%adjustments to enable the robot show a good performance.
-%
-%%\paragraph*{Emerging anthropomorphic interactions.} Another, from our side more
-%%unexpected interaction that we would describe as somehow anthropomorphic, is
-%%what we call \textit{``collaborative cleaning''} with the robot. In the initial
-%%phase of the study, some people spontaneously helped the robot to clean by
-%%either picking up crumbs from the floor themselves or pushing it right in front
-%%of the robot. Another way of collaborating with the robot we observed was to
-%%help it go everywhere by spontaneously putting up the trash bin or the carpet
-%%in the bathroom (things that are not just lying around and need to be cleaned
-%%up). However, the activity of collaborative cleaning faded out soon, and we
-%%suspect it was encouraged by the novelty of the robot.\\
-%
-%Overall, Figure \ref{fig:roomba-activities} shows that as time goes by, less
-%households engage in the before-mentioned non-cleaning activities with the
-%vacuum cleaning robot: after 2 weeks, on average, 4.67 of 9 households engage in
-%a human-like activity with the robot; after 2 months, the value decreases to
-%2.83, and after 6 months to 2.3. Our interpretation is that the nature of
-%human-robot interaction changes over time. More concretely, we suspect  that
-%anthropomorphic / human-social interactions with the robot become less over
-%time, and that only with some people these interactions sustain.
-%
-%
-%\subsubsection{Perception of anthropomorphic characteristics of the robot\\}
-%
-%We also studied people's perception of the robot, and how it evolved over time
-%(see Figure \ref{fig:roomba-perception}). The main idea was to find out which of
-%the perceived attributes could be related to how far the robot was integrated in
-%the household as a cleaning tool. Concerning anthropomorphism, we included
-%\textit{perceived intelligence} and experienced \textit{fun} when using the
-%robot as indicators for the perception of human-likeness in the robot.\fixme{JF: Severin, you also mentioned impact as one factor. Please include it here below as another paragraph.}
-%
-%%\begin{figure}
-%%    \centering
-%%    \includegraphics[width=0.5\columnwidth]{roomba-perception.pdf}
-%
-%%    \begin{tikzpicture}[scale=0.5, y = 2cm]
-%%    %axis
-%%    \draw (0,0) -- coordinate (x axis mid) (20,0);
-%%    \draw (0,0) -- coordinate (y axis mid) (0,7);
-%%    %ticks
-%%    \foreach \x in {0,4,...,20}
-%%        \draw (\x,1pt) -- (\x,-3pt);
-%%    \foreach \y in {1,...,7} 
-%%        \draw[black!20] (20,\y) -- (-3pt,\y);
-%%    \foreach \y in {1,...,7} 
-%%        \draw (-3pt, \y) node[anchor=east] {\y}; 
-%%    %labels
-%%    \node[below=0.8cm] at (x axis mid) {People's perception (n = 15)};
-%%    \node at (2, -0.4) {\tiny expectations};
-%%    \node[align=center] at (6, -0.4) {\tiny after\\ \tiny first usage};
-%%    \node[align=center] at (10, -0.4) {\tiny after\\ \tiny 2 weeks};
-%%    \node[align=center] at (14, -0.4) {\tiny after\\ \tiny 2 months};
-%%    \node[align=center] at (18, -0.4) {\tiny after\\ \tiny 6 months};
-%%
-%%    \draw[dashed, black!50] (6,0) -- (6,7) node[sloped, below, pos=0.25] {\tiny novelty effect};
-%%
-%%    \draw[ultra thick, red!50] (2,5.6) -- (6,6.1) -- (10,6.3) -- (14,6.3) -- (18,6.1) node at (15,6.5) {\tiny \it ease of use};
-%%    \draw[ultra thick, purple] (2,4.9) -- (6,5.2) -- (10,5.1) -- (14,4.5) -- (18,4.2) node at (3,4.7) {\tiny \it usefulness};
-%%    \draw[ultra thick, blue!50] (2,4) -- (6,4.1) -- (10,4.6) -- (14,4.1) -- (18,4.3) node at (16,4) {\tiny \it fun};
-%%    \draw[ultra thick, green!50] (2,3.9) -- (6,4.1) -- (10,4.2) -- (14,3.8) -- (18,3.3) node at (19,3.5) {\tiny \it intelligence};
-%%    \draw[ultra thick, orange] (2,3.5) -- (6,4.2) -- (10,4) -- (14,3.2) -- (18,2.8) node at (14,2.7) {\tiny \it impact};
-%%
-%%    \draw[ultra thick, dashed] (2,5.2) -- (6,5.2) -- (10,5) -- (14,4.9) -- (18,4.5) node at (14,5.3) {\tiny \it overall};
-%%
-%%    \end{tikzpicture}
-%
-%
-%%    \caption{People's perception of the robot over time, n = 15 participants.
-%%    This line chart shows how people's perception of the robot evolves over
-%%    time. At 5 time points people were asked to rate the robot according to the
-%%    following aspects: the perceived \texttt{intelligence} of the robot, the
-%%    perceived \texttt{usefulness}, the perceived \texttt{ease of use}, how much
-%%    \texttt{fun} it was to use the robot, how far they found the robot had an
-%%    \texttt{impact} on their household, and their {overall} impression of it.}
-%%
-%%    \label{fig:roomba-perception}
-%%\end{figure}
-%
-%\paragraph*{Perceived intelligence.} On a scale from 1-7, people were not sure
-%about how intelligent they should expect the robot to be (mean value 3.9). The
-%rating did not change much and not significantly over time (average ratings
-%between 3.3-4.2) \citep{fink_living_2013}. Interestingly, at all five time
-%points, male participants rated the robot as more intelligent (average 4.5) than
-%females (average 3.4), however, this difference was not significant. When asked
-%why they thought Roomba possesses intelligence, men more often referred to the
-%'robot side' of Roomba: its abilities to detect and avoid obstacles, stairs, and
-%being able to recharge itself. Contrary, women referred to its rather limited
-%vacuuming performance and found it was not as intelligent because \textit{``it
-%doesn't see where the dirt is, it sometimes leaves it, it can't be smart!''}.
-%This difference in the perception of intelligence of a robot suggests that
-%gender,and probably other individual characteristics need to be taken into
-%account.
-%
-%\paragraph*{Experienced fun.} Participants rated the robot as 'somewhat fun'
-%(values from 4.0-4.6). There was a qualitative gender difference (not
-%significant), in the sense that the experienced fun remained quite stable for
-%male participants, whereas it tended to decrease with time for female
-%participants. Men described the robot more as a 'fun gadget' than females, who
-%referred to it as \textit{``In the end, Roomba is a cleaning tool and it is not
-%really fun to use it''}. Again for this aspect, gender seems to play a role in
-%how the robot is perceived and experienced.\\
-%
-%Overall, Figure \ref{fig:roomba-perception} shows that after the first usage of
-%the Roomba (T2), most of the perceived constructs slightly decrease (and hence
-%are less positively rated) as time goes by. The course is different for the
-%perceived \textit{ease of use} of the robot, as participants become more
-%experienced with the robot over time. Also, the experienced \textit{fun} does
-%not decrease with time.
-% 
-%
-%\subsubsection{Summary Roomba study\\}
-%
-%In accordance with previous work we also found relatively low rates of users
-%treating and perceiving their vacuum cleaning robot as a living (or human-like)
-%entity \citep{sung_housewives_2008}. We interpret that it might be the pure
-%functional purpose and non human-like form of the Roomba that prevented people
-%from anthropomorphizing it. Still, we observed some initial anthropomorphic
-%effects, both reflected in interaction with and perception of the robot.
-%However, most of the anthropomorphic effects did not last long. One fairly
-%stable human-like interaction with the robot was \textit{talking to the robot},
-%despite the fact that the robot was not able to recognize and respond to verbal
-%statements.
-%
-%
-%\subsection{Forum study: using anthropomorphic expressions to describe a robot}
-%
-%We investigated the amount and context of anthropomorphic language in three
-%online discussion forums about the robotic dog AIBO, the vacuum cleaning robot
-%Roomba, and the tablet computer iPad. This was done by means of a content
-%analysis of 750 forum posts that were further partitioned in n = 1208 valid
-%segments \citep{fink_anthropomorphic_2012}. Hereafter, we refer to this study as
-%the "Forum study". The three devices, pictured in Figure
-%\ref{fig:aibo-roomba-ipad}, were chosen as they show different designs and
-%fulfill different purposes. We would describe (1) AIBO as a zoomorphic /
-%pet-like robot that does not have a clear purpose but engages people to play
-%with it; (2) Roomba as a mechanical / functional domestic service robot that has
-%a practical main purpose (vacuum cleaning) but offers not much of interactivity;
-%(3) the iPad as a minimalistic designed interactive (touch-based) technology
-%with multiple purposes (both entertainment, and professional / practical use).
-%Based on these different characteristics, we made the two following hypotheses
-%concerning anthropomorphism:
-%
-%\begin{enumerate}
-%    	\item People engage in a more social and human-like way with a robotic pet compared to a functional robot and a tablet computer, therefore there will be a higher amount of anthropomorphic language in the AIBO and Roomba forum, compared to the iPad forum.
-%    	\item As anthropomorphism can be seen as a certain kind of emotional / social relation to an artifact, there will be more anthropomorphic language in forum posts in which the author describes a relation to the device, compared to discussing technological aspects or how the device is used.
-%\end{enumerate}
-%
-%Similar to how \cite{friedman_hardware_2003} analyzed anthropomorphic language
-%in online forums, we coded a segment as anthropomorphic when the respective
-%device was described in terms of:
-%
-%\begin{itemize}
-%    \item \textit{Life-likeness}, such as being alive or having (parts of) a
-%        body, \eg \textit{``she can be reborn since you copied her memory
-%        stick''};
-%    \item \textit{Emotional states, empathy} or the technology having a
-%        \textit{feeling}, \eg \textit{``oh no, poor AIBO''};
-%    \item \textit{Gender, personality} or the technology having an
-%        \textit{intention}, \eg Roomba \textit{``seems to like to hang around
-%        under the sofa''};
-%    \item When the author gave the technology a \textit{name}, \eg
-%        \textit{``whenever I show Java his pink ball''};
-%    \item Being \textit{socially integrated}, such as being a family member, \eg
-%        \textit{``I'm considering adding a Roomba to the family''};
-%    \item \textit{Metaphorical ways}, \eg Roomba \textit{``sings its victory
-%        song when it finishes and docks''}.
-%\end{itemize}
-%
-%In the next paragraphs, we present findings in respect of our two hypotheses:
-%anthropomorphic language related to the device, and anthropomorphic language
-%related to the topic of the forum post.
-%
-%\begin{figure}[b]
-%    \centering
-%    \includegraphics[width=0.5\columnwidth]{aibo-roomba-ipad_2.jpg}
-%    \caption{The Sony AIBO robotic dog (left), the iRobot Roomba vacuum-cleaning robot (middle), and the Apple Inc.
-iPad tablet computer (right) were compared in terms of how far users of these devices use anthropomorphic expressions in online discussion forums about their technology / robot.}
-%    \label{fig:aibo-roomba-ipad}
-%\end{figure}
-%
-%%Overall, our analysis revealed that in all three forums, discussions about
-%%\textit{technical} aspects of the respective device were most frequent (67.7~\%
-%%of all 1208 categorized segments). However there were huge differences between
-%%the three devices: \textit{technical} aspects made up 79.9~\% of the discussion
-%%in the Roomba forum, compared to 69.9~\% in the AIBO forum, and 55.2~\% in the
-%%iPad forum. Another fairly frequently discussed topic concerned the
-%%\textit{usage} of the respective device, thus people describing how and for what
-%%they use their technology. This topic made up 21.8~\% of all posts, and was most
-%%frequent in the iPad forum (35.7~\%), followed by the Roomba forum (15.9~\%),
-%%and the AIBO forum (10.7~\%). Last but not least, we defined \textit{relation}
-%%as the third topic of interest. Discussions in which people described their
-%%relation to the respective device made up 10.5~\% of all posts, and was most
-%%frequent in the AIBO forum (19.4~\%), followed by the iPad forum (9.1~\%), and
-%%the Roomba forum (4.2~\%). \hl{(if it is getting too much we can leave out this
-%%paragraph, it's not crucial, and doesn't say anything about anthropomorphism
-%%directly)}
-%
-%
-%\subsubsection{Anthropomorphic language related to the device (design)\\}
-%
-%A statistical analysis revealed a significant difference for the use of
-%anthropomorphism across the three devices \citep{fink_anthropomorphic_2012}. In
-%accordance with our first hypothesis, the highest amount of anthropomorphic
-%language (56.6~\%) was found in the AIBO forum. In contrast, only 11.7~\% and
-%respectively 2.2~\% of the segments in the Roomba and the iPad forum contained
-%anthropomorphic expressions.  The data suggests that on a subjective scale of
-%perceived human-likeness (or rather life-likeness), Roomba is closer to the iPad
-%than to the AIBO, at least in matters of how they are described with words. This
-%was a bit against our expectation. Still, the Roomba is an autonomous robot that
-%can navigate around the house itself, and we expected this property to enhance
-%anthropomorphism. We interpret that here, the physical embodiment of the object
-%and how far it resembles a life-like entity determine how far the object is
-%anthropomorphized, and as such the robotic dog is anthropomorphized more than
-%the functionally designed devices.
-%
-%
-%\subsubsection{Anthropomorphic language related to the topic of conversation\\}
-%
-%Also in terms of anthropomorphic language related to the topic of conversation,
-%a statistical analysis revealed a significant difference
-%\citep{fink_anthropomorphic_2012}. The analysis suggests that anthropomorphizing
-%happens more when the topic of conversation is \textit{relation}, compared to
-%\textit{usage}, and \textit{technical} aspects. This finding is qualitatively
-%confirmed when looking at the distribution of anthropomorphic expressions across
-%the three topics in the Roomba and iPad forum (with both technologies the
-%highest amount of anthropomorphism is in the \textit{relation} topic). However,
-%in the AIBO the amount of anthropomorphic segments is highest for the
-%\textit{usage} topic.  We interpret that it is the different type of interaction
-%/ use context that makes the difference. Contrary to the iPad and the Roomba,
-%the AIBO is made to encourage its user in a playful / social interaction, which
-%in turn is a typical use context. Further, AIBO has the ability to respond
-%intelligently to its user and environment, which might also encourage people to
-%ascribe human-like abilities to it while interacting with it.
-%
-%
-%\subsubsection{Summary Forum study\\}
-%
-%Overall, findings of the content analysis suggest that there are differences in
-%people's tendency to use anthropomorphic language, originating form the design
-%characteristics of the artifact. A pet-like robot encourages people to use more 
-%anthropomorphic expressions when discussing about it in an online forum. However, 
-%the difference might also be related to other factors that we did not analyze 
-%here (\eg. author's characteristics). Our analysis further shows that the design 
-%of the robot seems to more important than the topic of the discussion. 
-%Interestingly, not only the physical embodiment
-%of the object but also the interaction complexity and purpose of use of the
-%object seems to play a role in how far the object is anthropomorphized.
-%
-%
-%\subsection{Ranger domino study: effect of unexpected robot behavior}
-%
-%The so-called "Ranger domino study" describes a child-robot interaction study
-%that we carried out in a fairly controlled lab setting. One of the goals of this
-%study was to investigate the effect of unexpected robot behavior on (1) the
-%interaction and engagement with robot, and (2) how far children would ascribe
-%human-like abilities (\eg intentions, cognitive abilities) to the robot.
-%
-%13 groups of each two children (n = 26) who were all between 4-5 years old and
-%knew each other, were invited to play with the Ranger
-%robot toy box \citep{fink2014which} to assemble a domino together. The robot
-%was operated by one of the experimenters using the wizard-of-oz technique.
-%Ranger was supposed to transport domino tiles between the two children and it
-%would do its job correctly for the first 7 runs, bringing each one domino tile to the child. Then, however, the
-%robot started misbehaving by not coming over to the child who was calling the 
-%robot. Three different experimental conditions were explored using three different 
-%types of misbehavior from the robot side:
-%Either the robot was \textit{disobeying} and did not come over at all, or 
-%the robot got \textit{lost} on its way to the child, or the robot did a 
-%\textit{mistake} by first going in another direction but then turning and 
-%coming over to the child who had called it.
-%According to these three different types of unexpected robot behavior, we 
-%expected to observe variations of how far the children perceived the 
-%robot in terms of intentionality, and cognitive abilities.
-%
-%In respect of anthropomorphism, we analyzed two types of data: children's 
-%\textit{interaction} with the robot (\eg do they talk to and use gestures 
-%toward the robot?, see Figure \ref{fig:interactions-per-run}), and 
-%children's \textit{perception} of the robot (\eg do they believe the 
-%robot has an own will, feelings, or is able to understand what they 
-%say?). The interaction data was analyzed quantitatively after having 
-%annotated the video recordings of the interaction. Children's perception 
-%of the robot was analyzed in a qualitative way and processed in a 
-%qualitative scale (higher values on that scale indicate more 
-%anthropomorphism), see Figure \ref{fig:qualitative-score}.
-%
-%\begin{figure}
-%        \centering
-%        \begin{subfigure}[b]{0.48\columnwidth}
-%                \includegraphics[width=\textwidth]{ranger-interactions-per-runs}
-%                \caption{Interactions per run}
-%                \label{fig:interactions-per-run}
-%        \end{subfigure}%
-%        ~ %add desired spacing between images, e. g. ~, \quad, \qquad etc.
-%          %(or a blank line to force the subfigure onto a new line)
-%        \begin{subfigure}[b]{0.48\columnwidth}
-%                \includegraphics[width=\textwidth]{ranger-interactions-vs-qualitative-score}
-%                \caption{Qualitative score by interactions}
-%                \label{fig:qualitative-score}
-%        \end{subfigure}
-%        \caption{\textbf{The Ranger domino study: Child-robot interaction.}\\
-%    \textbf{a)} Quantitative assessment: here, six interaction modalities have
-%        been selected: showing something to the robot ({\tt show}), talking to
-%        the robot ({\tt talk}), touching it ({\tt touch}), misbehaving (like
-%        shaking it, {\tt mis}), using gestures ({\tt ges}), and looking
-%        for help by glancing at the experimenter ({\tt look}). In each
-%        of the 13 experimental runs, we annotated and counted the number of
-%        occurrences of each of these interactions. Highlighted runs 2.3, 2.4,
-%        2.7 and 2.8 correspond to unexpected robot behaviors: we observe peaks
-%        of interactions every time the robot's behavior changes from expected to
-%        unexpected or from unexpected to expected. (n = 26 children)\\
-%	\textbf{b)} We found a significant negative correlation ($p=0.048$) between the
-%    number of interactions and the qualitative anthropomorphic projections. This 
-%    suggests that children who interacted more with the robot, anthropomorphized it 
-%	less, and \textit{vice versa}. (n = 13 groups)}
-%    		\label{fig:Ranger-domino}
-%\end{figure}
-%
-%
-%\subsubsection{Anthropomorphic interactions with the robot\\}
-%
-%The video recordings of the interaction session in which the children 
-%played domino with the partly misbehaving robot were annotated according 
-%to a coding scheme that we developed. Amongst others, six different types 
-%of active actions / active engagement that a child carried out with the 
-%robot were annotated. We understand some of these active engagement 
-%actions as anthropomorphic, such as talking directly to the robot or 
-%using gestures to the robot. The distribution of the interaction data per 
-%run (see Figure \ref{fig:interactions-per-run} suggests that after the 
-%robot started misbehaving (and thus became less predictable) children 
-%tended to use slightly more active engagement interactions: gestures toward the 
-%robot, and to talk more to the robot. Also, they were looking more often at the 
-%experimenter, seeking help. 
-%
-%%\begin{figure}
-%%    \centering
-%%    \includegraphics[width=0.5\columnwidth]{ranger-interactions-per-runs}
-%%    \caption{Quantitative assessment: here, six interaction modalities have
-%%        been selected: showing something to the robot ({\tt show}), talking to
-%%        the robot ({\tt talk}), touching it ({\tt touch}), misbehaving (like
-%%        shaking it, {\tt mis}), using gestures ({\tt ges}), and looking
-%%        for help by glancing at the experimenter ({\tt look}). In each
-%%        of the 13 experimental runs, we annotated and counted the number of
-%%        occurrences of each of these interactions. Highlighted runs 2.3, 2.4,
-%%        2.7 and 2.8 correspond to unexpected robot behaviors: we observe peaks
-%%        of interactions every time the robot's behavior changes from expected to
-%%        unexpected or from unexpected to expected. (n = 26 children)}
-%%
-%%    \label{fig:interactions-per-run}
-%%\end{figure}
-%
-%
-%\subsubsection{Perception of anthropomorphic characteristics of the robot\\}
-%
-%First of all, note that it is not at all easy to measure how far 4-5 year old's 
-%perceive a robot to have some human-like qualities. We interviewed children about 
-%various anthropomorphic traits of the robot, such as: Can the robot feel happy or 
-%sad? Some of these questions were inspired by \cite{kahn_jr._robotic_2006}. For 
-%each of these anthropomorphic traits questions, we gave a point if the child 
-%answered in a positive way (partly reversed, negative way), indicating that the 
-%child perceived the robot as somehow human-like. In the end, we summed up all 
-%points, to obtain a \textit{qualitative score} for a child's tendency to 
-%anthropomorphize the robot.
-%
-%
-%\subsubsection{Summary Ranger domino study\\}
-%
-%We were trying to bring both measurements together: the anthropomorphic 
-%interactions with the robot and the perception of anthropomorphic characteristics 
-%of the robot. By this, we wanted to find out whether both aspects are correlated to 
-%each other. A correlation would allow us to answer questions such as: Do children 
-%that perceive more human-like characteristics in the robot also interact with it in 
-%a more human-like way?
-%
-%
-%%\begin{figure}
-%%    \centering
-%%    \includegraphics[width=0.5\columnwidth]{ranger-interactions-vs-qualitative-score}
-%%    \caption{We found a significant negative correlation ($p=0.048$) between the
-%%    number of interactions and the qualitative anthropomorphic projections. This 
-%%    suggests that children who interacted more with the robot, anthropomorphized it 
-%%    less, and \textit{vice versa}. (n = 13 groups)}
-%%    \label{fig:qualitative-score}
-%%\end{figure}
-%
-%Figure~\ref{fig:qualitative-score} plots the qualitative against the quantitative assessment of
-%anthropomorphic effects during the Ranger domino study: the correlation is
-%negative. This was a surprise. The more the children interacted with the robot, the less they
-%projected anthropomorphic traits on the robot. We also note a remarkable cluster
-%of seven groups of children who did not interact much with the robot, but had a
-%strongly anthropomorphic perception of the robot. This may initially look
-%counter-intuitive (one could hypothesize that the more playful the children are
-%with the robot, the more likely they are to consider it as a friend/pet/lively
-%being). We discuss possible cognitive explanations of this in Section~\ref{sec:cognition-neuroscience}.
-%
-%
-%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-%
-%
-%		WHAT IS ANTHROPOMORPHISM
-%
-%
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Towards a unified understanding: What is anthropomorphism?}
-\label{sec:definitions}
-
-Literature on anthropomorphism is quite diverse.
-There exist different and partly conflicting definitions of the term anthropomorphism, and that in general, the \textit{terminology} is not clear.
-Probably as a result of this, there also exist different understandings of the \textit{phenomenon} that the term ``anthropomorphism'' describes.
- In this section we will first give an overview on the diversity of terms and
- then try to establish a common ground in the understanding of anthropomorphism
- as a psychological phenomenon.
-
- \subsection{The lexical field of anthropomorphism}
-
-Originally, the term \textbf{anthropomorphism} comes from the Greek
-\textit{anthropos} for ``man'' (or ``human'') and \textit{morphe} for ``form /
-structure'' (or ``shape''). Anthropomorphism is generally understood as people's
-tendency to perceive a non-human agent as if it had some human characteristics
-or traits. How a person perceives an agent is crucial, as it further determines
-how he/she relates to, and behaves towards the agent, or how he/she may behave in
-light of this agent \citep{epley_when_2008}. An anthropomorphic relationship is
-often characterized by the fact that the human attributes human-unique
-characteristics to the non-human agent. Since anthropomorphism becomes
-observable through these attributions, some definitions claim that
-anthropomorphism is not the \textit{perception} but rather the
-\textit{attribution} of human qualities to non-human agents.  Ascribing
-thoughts, emotions, and intentions are given as examples, and as the most
-prominently anthropomorphized non-human agents, animals and robots are mentioned
-\citep{duffy_anthropomorphism_2003,schmitz_concepts_2011}.
-
-Apart from anthropomorphism, there also exists the term \textbf{animism}, which
-can be defined as the attribution of life to the nonliving. The study of animism
-was pioneered by Piaget in the 1920s with his work on \textit{The Child's
-Conception of the  World}. He found that children tend to regard many inanimate
-objects as capable of sensations, emotions and intentions, and called this view
-``animism''. Since then, children's inferences about the world have been studied
-intensively, and there is an agreement that children's views and concepts of
-living, animal, and plant evolve as they grow up. Often synonymously used to
-animism is the term \textbf{zoomorphism}, which similarly applies to the cases
-when non-lifelike instances / artifacts are associated with animalistic
-attributes, excluding human-specific traits.  As ``being alive'' is not a
-human-unique property but applies to all living beings, the attribution of life
-may not be labeled as anthropomorphism (in a narrow understanding of it).
-Another possibility to illustrate how anthropomorphism differs from attributions
-of animacy is to look at paraphrases of anthropomorphism. That is to say,
-anthropomorphism can alternatively be understood as \textbf{humanization} or
-\textbf{personification} of anything other than a human being.\footnote{There
-exist also the phenomenons inverse to anthropomorphism, which can be found
-in the literature as \textbf{dehumanization}
-\citep{haslam_dehumanization:_2006}, or \textbf{mechanomorphism}
-\citep{caporael_anthropomorphism_1986}.} Robots can
-both be animized and anthropomorphized, but often the difference is not made.
-
-%\hl{can be cut from here ...}
-%
-%Thus, animism and anthropomorphism differ in two main aspects:
-%
-%First, the nature of the properties which can be ascribed to an agent differs.
-Life-likeness is not human-unique but applies to all living beings.
-Thus, \textit{animism} applies to attributions of life-like properties but excludes human-specific traits.
-Contrary, a narrow understanding of \textit{anthropomorphism} would exclude all attributions of life-likeness that are not human-unique, such as `being alive'.
-%  
-%Second, the range of agents to which life-likeness can be attributed differs.
-Naturally, only non-living agents can be animized.
-Thus, whereas non-human but \textit{living} beings (most importantly animals) can be anthropomorphized, they cannot be animized.
-Similarly, humans cannot neither be animized nor anthropomorphized as they are living beings and humans.
-%
-%\hl{... to here}
-
-%Personification has 
-%ancient roots, \eg in mythology but also in storytelling. For instance, anthropomorphism was also 
-%used to describe and be able to predict natural forces or anticipate great spirits.
-
-\subsection{Overview of the diverse understandings of anthropomorphism}
-
-Naturally, conflicts in how terms are used lead to a diversity of understandings
-of the phenomenon which is described.  One reason for this might be that
-anthropomorphism is a phenomenon that is studied in very different domains that
-might each integrate their own understanding, use the same term to refer to
-different things.  Despite the fact that there is no commonly accepted
-definition, the terms \textit{anthropomorphism}, \textit{anthropomorphic} or
-\textit{human-like} are often used as if their meanings were clear and agreed
-upon \citep{persson_anthropomorphism_2000}. It is even argued that these terms
-might be misused \citep{duffy_anthropomorphism_2002,epley_when_2008}.  For
-instance, some researchers refer to \textit{``the robot's level of
-anthropomorphism''} \citep{bartneck_is_2007,feil-seifer_human-robot_2008}, whereas others disagree to such a
-statement because they understand that a system or artifact itself does not
-\textit{``contain anthropomorphism''} but only gives rise to the process of
-anthropomorphizing in a given user and situation. Consequently,
-\cite{persson_anthropomorphism_2000} conclude that anthropomorphism emerges in
-the \textit{interaction} between the technology and the user, and has to be
-understood as such. We come back on this point in the next section.
-
-Another paradox is that, while human's tendency to anthropomorphize is commonly
-observed, the phenomenon is at the same time still rather poorly understood
-\citep{epley_seeing_2007}. The phenomenon itself has been found to be very
-complex, sometimes subtle and as such hard to study
-\citep{duffy_anthropomorphism_2002,epley_when_2008}. Besides, it is not clear
-how to operationalize and measure anthropomorphism (we discuss this question
-toward the end of this article, in Section \ref{sec:measuring}).
-
-%Anthropomorphism is used in different senses throughout different disciplines 
-%\citep{duffy_anthropomorphism_2003} which makes it difficult to synthesize findings. 
-Depending on which definition of anthropomorphism is applied, not everything 
-colloquially labeled as \emph{anthropomorphism} really is anthropomorphism.
-For example, it is not always clear whether a person (may it be an adult or 
-a child) who gives an anthropomorphic response, believes that the other agent really 
-thinks or acts like a human or whether he/she is using anthropomorphism in a metaphoric 
-sense \citep{leeds_childrens_1992}.
-This call for explicitely stating what we mean when talking about anthropomorphism.
-
-Several attempts have been made to clarify what the psychological phenomenon
-\emph{anthropomorphism} actually is.  From a psychology point of view,
-\citet{epley_when_2008} explain what anthropomorphism is \textit{not}. For
-instance, in their understanding, anthropomorphism does not include behavioral
-descriptions of observable actions but it requires going beyond what is directly
-observable. They also suggest that anthropomorphism does not merely entail
-\textit{animism}, as animate life is not a \textit{uniquely} human-like
-characteristic.\footnote{For the whole list and more details, the reader may
-refer to the original work \citep{epley_when_2008}.}
-
-%The authors list four effects that anthropomorphism does not include:
-%(1) First, anthropomorphism does not include behavioral descriptions of observable actions. Anthropomorphism requires going beyond what is directly observable.
-%(2) Second, anthropomorphism does not merely entail animism, as animate life is not a uniquely human-like characteristic.
-%(3) Third, anthropomorphism does not include any requirement of reasoned or reflective endorsement of an inference.\footnote{\hl{(the strength of anthropomorphic inferences can vary)}}
-%(4) Finally, anthropomorphism is not necessarily inaccurate.
-A psychological theory should take this (in)accuracy in anthropomorphism into account and predict variability in the tendency to perceive human-like traits in non-human agents.
-%% comment Julia: I commented this out because I think this is too complex and too much of detail here.
-
-As human-likeness itself is manifold and complex,
-some researchers argue that there might not just be one single type of
-anthropomorphism but different levels or gradations. For instance,
-\citet{persson_anthropomorphism_2000} proposes to understand anthropomorphism as
-a multi-layered phenomenon, namely \emph{primitive categorization},
-\emph{primitive psychology}, \emph{folk-psychology}, \emph{traits}, \emph{social
-roles}, and \emph{emotional anthropomorphism}. Correspondingly,
-\citet{ruijten_introducing_2014} propose to understand anthropomorphism as a
-continuum ranging from low to high human likeness, and to measure it as such.
-
-\subsection{Terminology used in this article}
-
-We use the term \textbf{anthropomorphism} to describe the \emph{psychological}
-phenomenon, which arises in the \emph{social context} of an interaction between
-a human agent and a non-human agent, in our case, a robot (see Figure
-\ref{fig:anthropofig}). We use this term to refer to both people's tendency to
-\textit{perceive} human-like characteristics, and to the tendency to
-\textit{ascribe} or \textit{attribute} such human-like characteristics to the
-agent or artifact. Besides, we call {\bf anthropomorphic effects} the
-\emph{observable manifestations} of anthropomorphism, \ie the human's behaviors
-and actions toward a non-human agent that reflect the underlying cognitive
-process of anthropomorphizing.
-
-However, despite the fact that ``anthropomorphism'' literally means ``human form'' we propose that the term should \textit{not} be used to refer to
-the \textit{form / design} of a non-human agent or artifact. To refer to an imitation of
-human-like \textit{form / design} of artificial agents, we propose to use the term
-\textbf{anthropomorphic design}. This explicit terminology prevents the commonly
-encountered confusion between anthropomorphism as a psychological, subjective
-phenomenon, and the external, objective factors that \emph{influence} the
-phenomenon itself.
-
-In the following, we might use the terms \emph{form} and \emph{design}
-interchangeably. Note that the terms \textit{form} or {\it design} do not only
-refer to the shape (how it looks like) but to the total expression of the
-artifact~\citep{bartneck_shaping_2004}. \citet{disalvo_hug:_2003} argues that
-\textit{form} includes the physical shape, materials, and behavioral qualities
-of the product. The behavioral aspect is of special importance for interactive
-systems that show some degree of autonomy (independence).  Several categories of
-anthropomorphic form exist, with no common agreement on the borders and
-transitions between those: anthropomorphic, zoomorphic, caricatured, functional
-\citep{fong_survey_2003}.
+The first factor, \textit{elicited agent knowledge}, is a \textit{cognitive determinant} of anthropomorphism and based on the idea that a person builds a mental model of the other agent (we treat this aspect in more detail in Section~\ref{sec:cognitive-viewpoint}).
+In short, the central point here is, that the person uses knowledge (a mental representation) about other humans (or him/herself) to make inferences on the (unfamiliar) robot.
+Anthropocentric knowledge is an easy source for us because as a human being we experience the world ourselves, as a human, and not as something or someone else.
+We have no other experience than the self, so in turn we tend to draw conclusions from ourselves on others' mental states.
+Attributing our own states to other humans is called ego-centrism.
+This mechanism is particularly formed in young children and decreases with cognitive development and the learning to distinguish the self from other humans, and non-human agents.
+
+The second factor, \textit{effectance}, as well as the third factor, \textit{sociality}, are \textit{motivational determinants} of anthropomorphism.
+\textit{Effectance} is understood as one's motivation to interact effectively within one's environment and the agents that inhabit it.
+In other words, we are motivated to make sense of our environment, and to be able to understand, predict and reduce uncertainty.
+According to \cite{epley_seeing_2007}, \textit{effectance motivation} can lead to anthropomorphize because this serves to reduce uncertainty and increase comprehension (especially about unfamiliar stimuli).
+It becomes apparent that people who feel more uncertain within their environment are likely to be more prone to anthropomorphize.
+
+The third factor, \textit{sociality} describes a person's motivation for social contact, social connection, and social approval from other agents.
+In lack of social connections to other humans (\eg friends, family, colleagues), a person is more likely to compensate these social connections by anthropomorphizing non-human agents.
+Interestingly, the two most commonly anthropomorphized non-human agents that serve to compensate for social connection to humans are pets and religious agents \citep{epley_seeing_2007}.
+In short, the motivation to be socially connected increases the tendency to anthropomorphize for two reasons.
+On one hand, sociality motivation increases the likelihood to perceive human-like characteristics in non-human agents; on the other hand, it also increases the tendency to search for sources of social connection in one's environment.
+
+\paragraph{Demographic factors} typically involve (but are not limited to) age, income aspects (often referred to as `social class'), cultural affiliation, and gender.
+Related work suggests that some of the demographic factors may impact to what extent a person is likely to anthropomoprhize.
+For instance, children tend to anthropomorphize especially robots more than adults.\footnote{It is not clear whether children really anthropomorphize more or whether they are just more prone to using metaphors within their conception of the world, or to projecting their own emotional states on any artifact that behaves with a certain independence.} Also, some cultures are notorious for their anthropomorphic religions and worldviews \citep{epley_when_2008}, and previous work suggests that anthropomorphism is a culture-sensitive phenomenon \citep{kaplan_who_2004,bartneck_cultural_2005}.
+
+\paragraph{Other person-related aspects} also play a role in shaping user experience, as well as probably for anthropomorphism.
+For instance, it has been found that expectations and attitudes toward using a robot can impact on how the robot is experienced and interacted with \citep{forlizzi_service_2006,forlizzi_how_2007}.
+In one of our studies, we also found that, those children who expected a robot to be very human-like, tended to be more disappointed as they discovered the limitations of the actual non human-like robot that we were using for the interaction study.\footnote{Due to a rather small sample size, we were unfortunately not able to identify the impact of the initial expectation on anthropomorphism.} Similarly, also previous experience with robots in general, knowledge about robots, and professional background is likely to play a role.
+Users who are better able to estimate the capabilities of the robot may be less likely to anthropomorphize the robot.
+
+\subsubsection{Characteristics of the Robot\\}
+\label{sec:factor-robot}
+
+The second main factor of anthropomorphism are characteristics of the robot $R$.
+Similar to before, this includes several sub-factors $(r_0, ...
+, r_n)$, \eg the robot's form, including its physical shape (how it looks like), materials, and other features of the design\footnote{Note that `design' may not only refer to the physical shape of a robot but to the total expression that it has as an artifact \citep{bartneck_shaping_2004}.
+Similarly, \cite{disalvo_hug:_2003} uses the term `form' to refer to both the physical shape, materials, and behavioral qualities of a product.
+In this article, we use `form' interchangeably to `physical shape' and `design' to embrace also behavioral and functional aspects.
+Thus, `form' is one aspect of the `design'.}, such as its interactions through expression, communication and behavioral qualities, and its functionality.
+If we are able to measure and evaluate these sub-factors regarding their similarity to human-likeness (or even applying a dyadic yes-or-no decision), we could obtain a robot-specific value $R=\{r_0, ...
+, r_n\}$ that indicates how much the robot is likely to be anthropomorphized by a user.
+Also this value may range between $0$ and $1$, with $1$ being a human.
+The point here is to account for differences between the given characteristics of different robots.
+As such, this main factor applies an \textit{artifact-centered} perspective on anthropomorphism
+%(see Figure~\ref{fig:multiple-factors})
+, as it argues that there are features of the artifact that suggest to the human to perceive it and treat it as if it had some human-like qualities.
+
+\paragraph{The Physical shape} of a robot refers to `how the robot looks like' and includes its general form, and other visible features, such as its size, the materials used, its color, and specific details.
+Generally, robots can be divided into human-like (anthropomorphic) and mechanical (non-anthropomorphic) robots.
+However, it makes sense to be slightly more specific about the form, and \cite{fong_survey_2003} suggest four categories: anthropomorphic, zoomorphic, caricatured, functional.
+The borders and transitions between these categories are not very well defined.
+Of particular importance seems to be the presence or absence of specific human body parts, such as arms and hands, legs, a torso or a head and face.
+Of those, the faces of robots have received remarkable attention concerning how they are perceived and accepted.
+\cite{disalvo_all_2002} studied what features and dimensions of a humanoid robot's face most dramatically contribute to people's perception of its humanness.
+The authors analyzed 48 humanoid robot heads and found that the presence of certain features, the dimensions of the head, and the total number of facial features heavily influence the perception of humanness in robot heads.
+
+Interestingly the authors found that despite the fact that all of the 48 evaluated robot were classified as humanoid, the majority of them was not rates as being very human-like by the participants.
+This result does not conflict with the robots being classified as humanoids, for that simply means that their form resembles a human more than it resembles any other form.
+It does, however, \textit{``raise the issue of how human-like a robot can be perceived by form alone''}.
+\citep{disalvo_all_2002} interpret that the `humanness' of a robot is defined not only by form but interactions through expression, communication, and behavior.
+We treat these aspects as a separate sub-factor of the robot's characteristics.
+
+\paragraph{Expression, communication, and behavior} refers to how the robot expresses its human qualities through interacting and behaving.
+In fact, many humanoid robots express their human-likeness not in physical shape but only through the \textit{suggestion} of features \citep{disalvo_all_2002}.
+Besides this, communication and interaction modalities of a robot are likely to play a role to what extent the robot will be anthropomorphized.
+Can the user interact with the robot through a touch interface, or using speech?
+Does the robot respond using linguistic utterances or non-linguistic sounds?
+Is the voice human-like or synthetic, on-board or coming from an external second device?
+A study by \cite{takayama_im_2009} found that this has an effect on people's perception of trust in the robot and how convincing the robot appears to them.
+Besides this, we expect that a robot's behavioral aspects concerning human-social interaction have an impact.
+Does the robot use polite formulations, etiquette, appropriate facial expressions?
+Are its responses and reactions timely?
+Usually, robots that directly interact with humans are slow, which appears not very human-like to most participants.
+
+\paragraph{The functionality, and purpose} are a robot-related characteristic that also partly determines the context of use.
+This aspect includes what kind of expectations the user may have of the robot, and how the user imagines using the robot.
+Is there only one user or a group of people interacting with the robot at the same time?
+Is the purpose of the robot a playful or a serious one?
+Does the robot have a purpose at all \citep{kaplan_free_2000}?
+We come back to this aspect in the next section, related to the context of use.
+
+\subsubsection{Characteristics of the Context of Use\\}
+\label{sec:factor-context}
+
+\textit{Context of use} is defined by the ISO as \textit{``users, tasks, equipment (hardware, software and materials), and the physical and social environments in which a product is used''}.
+Accordingly, there are various aspects that can impact how a robot is experienced.
+The real or imagined \textit{purpose} of a robot, including the application context in which it is typically used (\eg office environment, home, rehabilitation center, public space, \etc) as well as the task context (\eg serious or playful task; composition of human-robot team; number of users) and the (social) role in which the robot is used / experienced are taken into account.
+Generally, when the context of use of a robot is social, entertaining or playful, it will enhance anthropomorphism, compared to when the context is a routine or focused serious task (security, rescue, \etc).
+\cite{joosse_what_2013} showed, for instance, that when the same robot (NAO) was used in a different task context (cleaning task \vs tour guide), users ascribed different personalities to the robot.
+Also our content analysis of online discussion forums (see Section~\ref{sec:forum-study}) shows that the purpose of the robot has an impact on the amount of anthropomorphic descriptions.
+Also Goetz and Kiesler's work revealed a link between a robot's context of use and people's perception of the robot.
+The authors found that people prefer a serious robot for serious tasks and a less serious robot for more playful tasks \citep{goetz_cooperation_2002,goetz_matching_2003}.
+\cite{kaplan_free_2000} discussed the role of uselessness in the design of robots.
+The author argues that artificial pets like AIBO have no real purpose, in a sense that they do not provide any kind of service or, in other words, \textit{``they are not doing what you tell them to do''} and \textit{``they might refuse the order of its owner''}.
+It may be this very aspect that increases people's tendency to anthropomorphize the robot.
+According to Kaplan, it is in our daily use language that we tend to attribute intentions to devices that are not doing their job well.
+For instance, we do usually not develop a relationship with our computer, washing machine or TV set when they work just properly; however, when they start dis-functioning, when they show that they can act differently than what we ordered, then we are ready to ascribe to them so kind of \textit{intentionality}.
+This aspect lies somewhat in between the characteristics of the robot (its behavior) $R$ and the context of use $C$.
+
+The characteristics of the context can also impact on the user experience and in turn foster or hinder anthropomorphism indirectly.
+For instance, when there are several friends of the main user interacting simultaneously with the robot, the likelihood of anthropomorphism may be increased.
+The context here is already social when several people who know each other engage in social interaction among themselves, so the robot may be perceived as being somewhat part of the social interaction, and hence it may be attributed human-social qualities \citep{baxter2013do}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+%
+%
+%		MULTIPLE LAYERS / LEVELS
+%
+%
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Anthropomorphism has Multiple Layers (Levels)}
+\label{sec:multiple-layers}
+
+Despite a fairly huge body of literature on anthropomorphism, the phenomenon is still not very well understood.
+\cite{persson_anthropomorphism_2000} argued that one of the issues is the scientific community's lack of sufficient understanding of the wide range of phenomena that anthropomorphism encompasses.
+More specifically, the authors argued that anthropomorphism \textit{``is not one phenomenon''} but \textit{``means different things on different levels''}.
+This viewpoint appears to make sense, as also human-likeness itself is not `one big concept' but consists of a huge variety of details, it is multifaceted and complex itself, so there may also be not just one single type of anthropomorphism but different levels, layers or gradations.
+Accordingly, \cite{persson_anthropomorphism_2000} propose to understand anthropomorphism as a multi-layered phenomenon, that arises in different levels.
+The authors list six levels, that each have their own characteristics and involve specific types of user expectations.
+The suggested levels are \textit{primitive categorization}, \textit{primitive psychology}, \textit{folk psychology}, \textit{traits}, \textit{social roles} and \textit{emotional anthropomorphism}.
+They suggest to use this multi-layered schema as a tool for analyzing systems with respect to anthropomorphic effects.
+Similarly, also \cite{ruijten_introducing_2014} propose to not see anthropomorphism as one big phenomenon that is either \textit{their} or \textit{not their}.
+In contrast to \cite{persson_anthropomorphism_2000}, they suggest to understand anthropomorphism as a continuum, ranging from ow to high levels, depending on how much the attributed characteristic is typically or uniquely human (see Figure~\ref{fig:mental-model-overlap}).
 
 \begin{figure}
-    \centering
-    \includegraphics[width=0.75\columnwidth]{anthropo.pdf}
-    \caption{Anthropomorphism is a psychological phenomenon which arises in a
-        social context, during an interaction between a human agent and a
-        non-human agent. One can take two main perspectives when trying to
-        explain anthropomorphism: a human-centered and an artifact-centered
-        perspective (grey triangles). Several external factors influence the
-        anthropomorphism phenomenon. Person- and artifact-related characteristics,
-        but also related to the context of use as well as the actual time spent
-        interacting with the robot (interaction history). [SEE
-        FIG~\ref{fig:anthropofig-alt} FOR AN ALTERNATIVE FIGURE]}
-
-    \label{fig:anthropofig}
+\begin{center}
+\includegraphics[height=5cm]{mm-overlap.pdf}% This is a *.jpg file
+\end{center}
+ \textbf{\refstepcounter{figure}\label{fig:mental-model-overlap} Figure \arabic{figure}.}{~~\small When we anthropomorphize a robot, our mental model of the robot overlaps to some extent with our mental model of a human.
+This is to provide an explanation to ourselves for how the unfamiliar aspects of the robot work the way they do.
+The overlapping part may vary, depending on how similar the two mental models of the robot and the human are.
+Also, other mental models, \eg the one of a dog or a computer, may play a role (this is not displayed here).
+Note further that we may not have one general mental model of a human but that we may have several and more specific models of certain actions (how a human reaches and grasps a cup) and behaviors (how a dog conveys that he wants to play), for instance.}
 \end{figure}
 
-\begin{figure}
-    \centering
-    \includegraphics[width=0.75\columnwidth]{in_our_heads.pdf}
-    \caption{[ALTERNATIVE TO FIGURE \ref{fig:anthropofig}] Anthropomorphism is a
-        subjective, psychological phenomenon which arises in a social context, during an
-        interaction between a human agent and a non-human agent. One can take
-        two main perspectives when trying to explain anthropomorphism: a
-        human-centered and an artifact-centered perspective.
-        Several external factors influence the anthropomorphism phenomenon.
-        Person- and artifact-related characteristics, but also related to the
-        context of use as well as the actual time spent interacting with the
-        robot (interaction history).}
-
-    \label{fig:anthropofig-alt}
+\nocite{admoni_multi-category_2012}
+
+\subsubsection{A cognitive viewpoint on anthropomorphism\\}
+\label{sec:cognitive-viewpoint}
+
+Anthropomorphism has a fundamental `sense-making' function \citep{persson_anthropomorphism_2000}.
+It involves a cognitive process of induction whereby \textit{``people reason about an unknown stimulus based on a better-known representation of a related stimulus''} \citep{epley_when_2008}.
+This is important.
+The particular process of reasoning on which anthropomorphism is based includes two central aspects.
+First, it requires \textit{``an unknown stimulus''} and a \textit{``better known representation of a related stimulus''}.\footnote{We suspect that anthropomorphism can also occur in absence of such unknown stimuli.
+Then, rather individual psychological factors may play a role (instead of applying a cognitive explanation).
+For instance, individuals who lack social connection to other people \citep{epley_creating_2008} tend to anthropomorphize objects despite the fact that they may have an accurate mental model of the object.
+This may then be a more ``projection''-type of anthropomorphism, which does not necessarily serve to explain something unknown.} Humans generally tend to use the closest (most similar) better known mental representation in order to explain the unknown stimulus.
+(This better known available representation must not necessarily be the one of a human, however, it is often the case because what we understand best in this world is ourselves.)
+A second central aspect is a person's \textit{Theory of Mind} -- the ability to attribute mental states (\eg beliefs, intentions, knowledge, desire) to oneself and others, and to understand that others' states are different from one's own.
+
+\nocite{hegel_theory_2008}
+
+\begin{figure}[!b]
+\begin{center}
+\includegraphics[height=3.5cm]{low-high.pdf}
+\end{center}
+ \textbf{\refstepcounter{figure}\label{fig:low-high} Figure \arabic{figure}.}{~~\small Anthropomorphism is not discrete being either \textit{there} or \textit{not there} but may be a continuum, having lower and higher levels, based on how much the attributed characteristic is typically or uniquely human (illustration adapted by \cite{ruijten_introducing_2014}).}
 \end{figure}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-%
-%
-%		WHY DO HUMAN ANTHROPOMORPHIZE
-%
-%
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Why do humans anthropomorphize?}
-\label{sec:anthropomorphism}
-
-Anthropomorphism is an interesting phenomenon because it tells us something about 
-the relationship between the human who anthropomorphizes, and the non-human agent 
-which is anthropomorphized. Though commonly observed, it still appears controversial, at 
-the same time, that humans tend to \textit{``see human in the non-
-human''} \citep{epley_seeing_2007}.
-
-As anthropomorphism arises in an interaction between a human and a non-human agent
-\citep{persson_anthropomorphism_2000}, one can also
-take two main \textit{perspectives} when trying to explain why humans anthropomorphize \citep{lee_human_2005}: an artifact-centered perspective and a human-centered perspective (see grey triangles in Figure \ref{fig:anthropofig}).
-It has to be kept in mind that both perspectives are inseparable; they apply at the
-same time, and we would like to present them here just as two different viewpoints 
-on the same phenomenon.
-
-In the following we will only briefly present the artifact-centered perspective to explain anthropomorphism.
-A review of anthropomorphic design of robots can also be found in \cite{fink_anthropomorphism_2012}.
-Then, we provide a more detailed review and synthesis of literature that applies a human-centered perspective to explain anthropomorphism.
-Concretely, we integrate theories from developmental psychology, cognitive science / neuroscience, and social psychology to shed light on the question why humans anthropomorphize.
-
-\subsection{Artifact-centered perspective on anthropomorphism}
-
-The artifact-centered perspective explains anthropomorphism from the
-ascertainable parts of the non-human agent, namely the anthropomorphic form of
-it. This section deals with the question how far anthropomorphism can be
-explained from the design of the artifact.  One of the most prominent working
-hypothesis in this field is the Uncanny Valley hypothesis
-\citep{mori_uncanny_1970}. In general, it is proposed that human-like designs of
-robots can evoke both positive and negative feelings in a human user.
-
-The direction of causality in the artifact-centered view goes from the artifact
-to the humans: the artifact (or a certain feature of it) \emph{encourages} the
-human to anthropomorphize it.  This perspective assumes that humans directly
-(mindlessly) respond to life-like and social cues that the non-human agent or
-system emits \citep{nass_machines_2000}. Without thoughtful mental processing,
-humans tend to simply apply stereotypes and heuristics to the non-human agent,
-and in turn apply human-human social schemas and norms to the occurring
-interactions.  \cite{takayama_perspectives_2012} proposes to refer to this
-immediate (sometimes visceral) sense in a situation as \textit{in-the-moment},
-compared to a more distanced cogitation and consideration which she calls
-\textit{reflective}. As this distinction implies different cognitive processes,
-it is more approriate to apply a human-centered perspective and we will come
-back to it later, in section \ref{sec:cognitive-expl}.
-
-%\subsection{An artifact-centered perspective on anthropomorphism}
-%\label{sec:anthropomorphic-design}
-%
-%An artifact-centered perspective 
-%
-%The use of nature-inspired and in particular anthropomorphic (human-like) form in the 
-%design of non-human things is as old and manifold as people's tendency to anthropomorphize. 
-%Anthropomorphic (and life-like) forms have a long-standing tradition in design in general, and in the design of daily life things, in particular 
-%\citep{norman_design_1988,guthrie_bottles_2000}. Interestingly, from its very
-%beginning robots were resembling a human being in their appearance. Starting
-%from when the term \textit{robot} first appeared in a play by Karel \^{C}apek in the 1920ies, robots were man-made beings, created as the \textit{``shadow of man''} \citep{replicant_????}.
-
-%The view of people mindlessly reacting in a human-social manner to anthropomorphic forms
-%is based on the fact that humans naturally react to specific 
-%cues. From early childhood 
-%on, humans are inherently well-trained to perceive life \citep{epley_seeing_2007}, 
-%or to respond to social cues, such as facial expressions, social gestures or turn-taking.
-Humans have a propensity toward particular cues that seem to trigger automatic interpersonal social responses \citep{takayama_perspectives_2012}.
-%One has to keep in mind that in 
-%human-human interaction these cues are of various senses and modalities, 
-%and consequently human-like design is also realized addressing several senses. 
-%One of the most outstanding aspects is probably the outer appearance of an agent or 
-%artifact (in particular when it is unknown or unfamiliar). \cite{schmitz_concepts_2011} 
-%argues that an agent's outer appearance is likely to have an important impact on how 
-%the object is overall perceived. Consequently, if a robot's outer form resembles a 
-%human, the robot is likely to be treated similar to a human.
-Besides the physical shape of a robot, other more subtle anthropomorphic forms can be found in robots, including human-social behavioral cues (\eg eye-gaze), social gestures (\eg waving), or verbal politeness (\eg greeting, apologizing).
-%
-%People's natural reaction to these and other anthropomorphic design cues of
-%robots (in particular, social or also called \textit{sociable} robots 
-%\citep{breazeal_sociable_2000}) are extensively studied.
-This research is of particular interest in human-robot interaction as the consequences of anthropomorphic design can be both of positive and negative nature, and it is yet not clear what exactly it is that makes the difference.
-%
-%
-%\subsubsection{How people perceive and interact with human-like robots\\}
-%\label{sec:anthropomorphism-robotics}  
-% 
-%Most work that studies how far human users treat robots as social agents, builds on the 
-%famous work of \cite{reeves_media_1996} in HCI. In the so-called \textit{Media 
-%Equation}, the authors describe that people mindlessly react in a social way to their computer 
-%and that they tend to even attribute human (social) characteristics to it -- despite 
-%the fact that a computer does not have human-like characteristics. Apart from 
-%computers, anthropomorphism has also been observed with digital / virtual characters 
-%\citep{von_der_putten_it_2010}, and artificial embodied agents, 
-%such as robots \citep{rosenthal-vonderputten_experimental_2013}. 
-%In short, one can say that with robots, and human-like robots in 
-%particular, anthropomorphism is a commonly observed phenomenon. 
-%But what are the motivations which underlie the efforts of enhancing anthropomorphism 
-%through specific anthropomorphic design in robots? Why are anthropomorphic forms so 
-%distinct and at the same time controversial in robotics? There is no one single answer 
-%to these questions. 
-% 
-%The underlying central point about the human-like design of robots lies in the 
-%implications that this design holds, and the suggestions for interactions that
-%it makes to the human user. 
-%In other words, the appearance 
-%and function of a product, whether it is an appliance or a humanoid robot, affects how 
-%people perceive it, interact with it, and build long-term relationships with 
-%it \citep{bartneck_shaping_2004}. 
-%The principle of human-like form is probably most prominent in the design of robots, 
-%due to several reasons, such as to foster efficient interaction and increase 
-%acceptance. An anthropomorphic design of a robot encourages people to reason about this 
-%unfamiliar system \emph{as if} it was a human. To increase this tendency, robots are 
-%designed with anthropomorphic (or lifelike) forms, or are able to display and use 
-%human-social cues when interacting with humans.
-%However, anthropomorphic robot designs have been controversially discussed and received 
-%remarkable attention since the early 1970ies, related to Mori's
-%theory of the \textit{Uncanny Valley} \citep{mori_uncanny_1970}.
-%%see Figure \ref{fig:uncanny_valley}.
-%
-%%\begin{figure}\centering
-%%% Use the relevant command to insert your figure file.
-%%% For example, with the graphicx package use
-%%  \includegraphics[scale=0.75]{uncanny-valley.jpg}
-%%% figure caption is below the figure
-%% \caption{Mashiro Mori, illustration of the \textit{Uncanny Valley} hypothesis.
-The curve models the user's perceived affinity with the artifact, as its human likeness is increased.
-Up to a certain (not yet defined) point, a person perceives more affinity in a more human-like agent; however with an abrupt shift towards a negative perception as soon as the agent surpasses this point, of resembling a human too closely but not fully.
-Originally from 1970; picture from a manuscript version of \cite{mori_uncanny_2012}}
-%% \label{fig:uncanny_valley}       % Give a unique label
-%% \end{figure}
-%
-%Despite the fact that the Uncanny Valley theory was more a working hypothesis and not 
-%meant to be empirically examined \citep{cheetham_human_2011}, it has been studied quite 
-%extensively. However, results are inconsistent. We try to give a short overview (not 
-%exclusive) on work related to HRI and robotics in the following. 
-% 
-% 
-%\subsubsection{Anthropomorphic form can be advantageous for HRI\\}
-%
-%On one hand, developers and designers have discovered that human-like robots may better 
-%match the affordances that this to humans adapted world brings along. 
-%Apart from this, it is suggested that an increased human-likeness of a robot (up to a 
-%certain threshold) will generally lead to 
-%more perceived \textit{affinity} from the human side \citep{mori_uncanny_1970}.
-%% (see Figure \ref{fig:uncanny_valley}).
-%This further increases anthropomorphism, and as such
-%appears to be beneficial for human-robot relations, especially with socially 
-%interactive robots \citep{fong_survey_2003}. Consequently, the domain of (social) 
-%robotics tries to exploit this by using
-%anthropomorphic forms in robots.
-%Humans seem to readily accept and prefer the 
-%anthropomorphic form of a robot (up to a certain point), when compared to purely mechanical 
-%robots. A possible explanation for this is that perceiving a system as
-%human-like (or also pet-like) compared to machine-like changes the 
-%way how users try to understand and make sense of this system. The reason for this is 
-%that humans tend to project everyday 
-%expectations of human and animalistic life onto artificial agents that use 
-%anthropomorphic (or zoomorphic) forms \citep{schmitz_concepts_2011}. 
-%Both cognitive science 
-%and social psychology can provide explanations for this process of projection. The basic idea 
-%is that \textit{"the more similar in 
-%appearance, the more people are likely to use themselves as a source of induction 
-%and anthropomorphize these nonhuman agents"} \citep{epley_seeing_2007}. Studies have further 
-%shown that perceived similarity between the user and the robot influences the intensity of 
-%the participants' attributions towards the robot. Thus, the anthropomorphic design of a robot 
-%impacts the user's perception of the robot, and how far the user is likely to attribute and 
-%experience qualities such as intelligence, fun, or intentions in the robot. 
-%These experiences mark the transition between an immediate \textit{in-the-moment} and more thoughtful \textit{reflective} \citep{takayama_perspectives_2012} perception of, and interaction with the robot.
-As this distinction is also based on different cognitive processes, a more human-centered / cognitive perspective needs to be applied here, and we will treat this in Section \ref{sec:human-centered}.
-%
-%In short, the central point in using anthropomorphic design in sociable robots is that 
-%humans tend to apply the same communication references to anthropomorphic robots 
-%that they would use with other humans, which in turn enhances feeling familiar and 
-%comfortable when interacting with the otherwise unknown system.
-%This positive effect has been shown in various 
-%empirical studies. It has been found that robots with human-like forms can enhance social 
-%responses from humans which in turn can positively impact on acceptance 
-%\citep{duffy_anthropomorphism_2003,goetz_cooperation_2002,venkatesh_theoretical_2000}. 
-%People responded more positively to an artifact that displayed human-like 
-%behavioral characteristics (emotions, facial expression) in contrast to a purely 
-%functional design 
-%\citep{eyssel_anthropomorphic_2010,krach_can_2008,reeves_media_1996,riek_how_2009}. 
-%Overall, these results suggest that human-like features in robots enhance 
-%anthropomorphism, and in turn create a social view toward the robot.
-%
-% 
-%%Anthropomorphism represents just one of many examples of induction whereby "people reason about an unknown stimulus based on a better-known representation of a related stimulus" \cite{epley_when_2008}, in this case reasoning about a non-human agent based on representation of the self or other humans.
-%
-%
-%\subsubsection{Anthropomorphic form can be disadvantageous for HRI\\}
-%
-%The anthropomorphic form also 
-%increases people's expectations of the agent, and consequently, a very human-like 
-%appearing robot is not only perceived but also expected to act like a human. However, today's artificial systems are 
-%not able (yet) to mimic well human movements, or human social cues in an acceptable way. 
-%The case is that the artificial agent pretends to be human but fails, and this is 
-%more than just disappointing for the 
-%human -- it appears uncanny and evokes reluctance, the so-called 
-%\textit{"uncanny valley"}. The idea of naming this shift and drop from a positive to a negative reaction,
-%follows Freud's description of the so-called \textit{uncanny} (a translation from the German word 
-%\textit{``unheimlich''}). Controversially, something uncanny \textit{"derives its terror not from 
-%something externally alien or unknown but -- on the contrary -- from something 
-%strangely familiar which defeats our efforts to separate ourselves from it"} (v. Foerster, cited after \cite{hegel_understanding_2008}).
-%In other words, humans are very sensitive to the limits of what is familiar to them 
-%in a sense of being human. At the same time, humans are naturally very skilled when 
-%it comes to identifying what is acceptable as a human and what is an imitation 
-%of it. Even subtle differences can be crucial -- humans are inherently well trained 
-%in identifying if there is \hl{``something strange''} in the familiar.
-%Summing it up, a not yet very well defined thin line separates acceptable human-like forms in 
-%robots from creepy artificial \textit{almost} human-like appearing robots.
-%
-% 
-%Of course, there is no one good answer to the question how to not fall in the 
-%uncanny valley when designing an anthropomorphic system. Equipping a system with 
-%some anthropomorphic forms seems to be inevitable 
-%\cite{duffy_anthropomorphism_2002} in the advancement of human-machine interfaces 
-%and sociable robots \citep{breazeal_sociable_2000}. However, we agree that 
-%\textit{"the important criterion is to seek a balance between people's expectations 
-%and the machines capabilities"} \citep{duffy_anthropomorphism_2002}.
-
-% Simulation Theory
-
-%Findings that support anthropomorphic form in robots because they found people 
-%respond with anthropomorphizing these kind of robots, and in turn act more social 
-%toward them or accept them more easily:	empathy --> check Iolanda's paper
-
-%For instance, recent studies found that people tend to ascribe personality and 
-%intentions to robots \hl{(REFS)} and that they show empathetic behavior toward robots 
-%\citep{rosenthal-vonderputten_experimental_2013}.
-
-%Various studies have shown that people directly talk to their robot (even if it 
-%does not recognize speech), give it a name, greet it, or wonder about its 
-%intentions and actions as if it were a human 
-%\citep{eyssel_anthropomorphic_2010,fink_anthropomorphic_2012,forlizzi_how_2007,fussell_how_2008,kiesler_anthropomorphic_2008}.
-%It has frequently been described that people ascribe intentions or emotions to 
-%their domestic robot, such as to a Roomba vacuum-cleaning robot 
-%\citep{krumm_my_2007,sung_robots_2009} or the AIBO robotic dog 
-%\citep{friedman_hardware_2003}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-%
-%
-%		HUMAN-CENTERED PERSPECTIVE: SOCIAL PHENOMENON
-%
-%
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%\subsection{A human-centered perspective on anthropomorphism}
-%\label{sec:human-centered}
-
-\subsection{Human-centered perspective on anthropomorphism}
-
-In contrast to the artifact-centered perspective, in the human-centered
-perspective the argumentation is that the human is self-motivated to
-anthropomorphize the non-human artifact. As already mentioned, both these views
-go hand in hand.
-
-Humans tend to perceive human-like characteristics such as physical appearance,
-emotional states, or inner mental states and motivations in non-human agents
-that do not have these characteristics themselves, such as animals, natural
-forces, religious agents, technological gadgets, or mechanical devices
-\citep{epley_when_2008}.\footnote{According to \citet{epley_when_2008}, a
-non-human agent can be anything that acts -- or is believed to act -- with
-apparent independence.} One common reason for anthropomorphism is that by
-perceiving some human-like characteristics in the non-human agent, this agent is
-made more \emph{graspable}, \emph{understandable}, \emph{predictable}, and one
-can feel \emph{more empathetic} toward it, and possibly one can then anticipate
-the agent's behavior. These are central motivations when trying to explain
-anthropomorphism, and we will come back to them in more detail later on.
-\citet{eddy_attribution_1993} explain that, because of these reasons, people
-commonly anthropomorphize their pets, by ascribing mental states, intentions or
-feelings to them.\footnote{Interestingly, pet-ownership seems to have a
-significant impact on human-robot interaction: several studies suggest that
-pet-owners are more likely to anthropomorphize technologies and robots than
-non pet-owners} But how can these motivations behind anthropomorphism be
-explained from a human-centered point of view?
-
-In the following, we present what we found in reviewing literature that applies a human-centered perspective on anthropomorphism by building on:
-\textit{(1)} a line of research in developmental psychology that studies the attribution of animacy;
-\textit{(2)} a line of research in more cognitive sciences that studies the cognitive processes that underlie anthropomorphism, and
-\textit{(3)} a theory that explains anthropomorphism based on psychological factors.
-
-% \begin{figure}[b]\centering
-%% Use the relevant command to insert your figure file.
-%% For example, with the graphicx package use
-%  \includegraphics[scale=1]{north-wind.jpg}
-%  \includegraphics[scale=1]{sun.jpg}
-%% figure caption is below the figure
-% \caption{Milo Winter illustration of Aesop Fable \textit{The North Wind and the Sun}, 1919; both natural forces wind and sun are anthropomorphized with a human face; picture source: wikipedia}
-% \label{fig:north-wind-sun}       % Give a unique label
-% \end{figure}
-
-%An illustration of an anthropomorphism related to nature is shown in Figure 
-%\ref{fig:north-wind-sun}. In this Milo Winter (1919) drawing \textit{"The North Wind 
-%and the Sun"}, both north wind and sun are given a human face.
-
-%\subsubsection{Why do people anthropomorphize?\\}
-%\label{sec:explanations}
-
-%But why do people anthropomorphize?
-First and foremost, it needs to be mentioned that anthropomorphism is a fairly complex phenomenon.
-Paradoxically, there is a huge and diverse body of literature on it but nevertheless, it seems that anthropomorphism is still not very well understood (especially in a field as young as HRI).
-
-%Anthropomorphism as a social phenomenon arises in an interaction \citep{persson_anthropomorphism_2000}, and thus includes at least two interaction partners (the human and the real or imagined non-human agent).
-Therefore, one can take two main perspectives on explaining it \citep{lee_human_2005}: a human-centered, and an artifact-centered.
-We briefly outline both views in the following.
-It has to be kept in mind that both perspectives are inseparable; they apply at the same time, and we would like to present them here just as two different viewpoints on the same kind of phenomenon.
-
-\subsubsection{Developmental psychology research on the attribution of animacy and intention\\}
-\label{sec:developmental-expl}
-
-The phenomenon of attributing animacy and intentions to nonliving objects such
-as simple shapes has been intensively studied in developmental psychology. As
-mentioned earlier, Piaget found that children tend to ascribe life to the
-nonliving. They also tend to interpret physical phenomena in terms of intention
-on the part of the non-human subject. For instance children are likely to argue
-that \textit{``the sun is hot because it wants to make people warm''}
-\citep{leeds_childrens_1992}. In this example it is in fact questionable whether
-children really anthropomorphize the sun (believing that it has an intention) or
-whether they are using anthropomorphism in a metaphoric sense (because their
-conceptions of the world and of the living are not yet fully formed). However, experiments by \cite{heider_experimental_1944} and
-\cite{michotte_perception_1963} showed that also adult participants attribute
-animacy and intention to simple things and shapes based on motion. In both
-experiments, participants viewed animations of simple shapes, such as circles or
-triangles. Asked to describe what they observed, most people developed
-elaborate stories, attributing motivations, emotions and relationships between
-the objects.\footnote{For more details, the reader may refer to the ``attribution
-theory''.}
-
-%\begin{figure}[h]\centering
-%% Use the relevant command to insert your figure file.
-%% For example, with the graphicx package use
-%  \includegraphics[scale=0.6]{heider-simmel_animation.jpeg}
-%% figure caption is below the figure
-% \caption{Fritz Heider and Mary-Ann Simmel's animated film to study people's tendency to attribute animacy and intention to simple shapes; \textit{An experimental study of apparent behavior}, 1944}
-% \fxnote{wrap text around this figure?}
-% \label{fig:animacy_attribution}       % Give a unique label
-% \end{figure}
-
-As mentioned earlier, it seems that there is a natural, relatively spontaneous
-reaction that accounts for people's tendency to attribute animacy and intention
-to moving shapes, even when there is no similarity of the shape to a human. This
-tendency to animize / anthropomorphize is already developed (and even more
-distinct) in infants and children. Thus besides the anthropomorphic cues emitted
-by the design of the artifact, also developmental stages and people's natural
-reaction play a role how far we interpret movements (as one of the
-most basic ``life-like'' cues) for instance.
-
-\subsubsection{Cognitive science research, Theory of Mind, and neural correlates of anthropomorphism\\}
-\label{sec:cognitive-expl}
-
-Anthropomorphism and similar phenomenons can also be understood as a thoughtful
-process of induction whereby \textit{``people reason about an unknown stimulus
-based on a better-known representation of a related
-stimulus"}~\citep{epley_when_2008}. In the case of anthropomorphism this means a
-person's reasoning about a non-human agent based on the representation of the
-self or other humans. A central construct of this perspective is the so-called
-\textit{mental model} that a person has (and builds) of the agents he/she is
-reasoning about and interacting with. The specific mental model we have about an
-artifact / agent basically explains (in our individual way to ourselves) how
-this artifact / agent works the way it does.  There are two central aspects
-here, that derive from the above quote from Epley.
-
-\textit{(1)} One assumption is that the user is not familiar with the other
-agent. This is basically true for all other agents (and entities) but oneself
-because we can only be our self. This view is also consistent with the
-\emph{familiarity thesis}~\citep{hegel_understanding_2008} which claims that we
-understand the world based upon the mental model of the world that we are most
-familiar with (\ie our self). Thus, we can best use our self as source of induction
-when reasoning about other agents. However, in case we would like to understand
-the behavior of a spider, we would probably not use our mental model of a human
-(or our self) simply because we do not have many things in common with a spider.
-And this is the second central aspect here.
-
-\textit{(2)} One other assumption is based on the anthropomorphic design of the
-other agent: if the agent behaves, thus appears, much like a human being (\eg a
-robot that emits a human voice), people's mental model of the agent's behavior
-is likely to approach their mental model of humans (though the model may differ
-in some important aspects).
-
-This cognitive viewpoint on anthropomorphism is important because people's
+There are two possibilities how anthropomorphism can be multi-layered from a cognitive point of view.
+First, in the case of anthropomorphism, a person chooses their mental model (or parts of it) of a human (the `better known representation') in order to explain some aspect about the robot (the `unknown stimulus').
+In other words, the mental model that the person has of the robot is to some extent similar to the mental model that he/she has of a human (see Figure~\ref{fig:mental-model-overlap}).
+We suppose that regarding anthropomorphism, it matters to what extent the mental model of the robot is based on the mental model of a human (for instance, is it fully identical, only partly, not at all?).
+Thus, how much thus the overall mental model of the robot overlap with the mental model of a human?
+How many specific actions / traits of the robot are explained by resorting to a human-like representation of it?
+
+Second, the characteristic of being multi-layered is also based on how typically or uniquely human the attributed characteristic is (see Figure~\ref{fig:low-high}), how much `cognitive depth' it implicates.
+For instance, attributing animacy, perceptual skills, or primary emotions (\eg fear, anger, sadness, happiness) to a robot are an example for a lower level anthropomorphism.
+These attributions are not uniquely human and reflect a less deep cognitive process.
+In contrast, the attribution of intent, moral standing, or secondary emotions, such as desire, shame or guilt are an example for higher level anthropomorphism.
+These attributions come from more complex chains of thinking.
+We suggest three cognitive stages that are not mutually exclusive but overlap (also in terms of temporal dynamics of anthropomorphism, Section~\ref{sec:dynamics}).
+
+Based on this cognitive viewpoint, 
+we propose that anthropomorphism is multi-layered \citep{persson_anthropomorphism_2000}.
+This means that anthropomorphism is not either `there' or `not there' but that there exist multiple layers of it, to which we will refer to as \textit{lower and higher levels of anthropomorphism}.
+The different levels (it may also be a continuum) are based on different cognitive correlates.
+\textbf{Lower level anthropomorphism} is based on a less thorough mental processing of an interaction.
+It can be more spontaneous and unmindful.
+This type of superficial reasoning about the robot may be predicated on specific cognitive correlates.
+Contrary, \textbf{higher level anthropomorphism} typically involves a profound thoughtful mental processing of the interaction as well as deeper reasoning about the robot.
+We assume that also such deeper interactions are based on specific cognitive correlates (see Section~\ref{sec:cognitive-correlates}).
+
+\subsubsection{Cognitive Correlates of Anthropomorphism\\}
+\label{sec:cognitive-correlates}
+
+The following paragraphs provide an initial interpretation of anthropomorphism in terms of \textit{cognitive correlates}: How can human cognition explain the dynamic nature of our interactions with robots?
+What are the main cognitive stages upon which researchers can build to design `deeper' human-robot interactions?
+A cognitive viewpoint on anthropomorphism is important because people's
 estimation of an agent's knowledge model and its capabilities affects the way
@@
 tend to hold richer mental models of anthropomorphic robots in contrast to
-mechanic ones \citep{kiesler_mental_2002}.\footnote{Later in this article,
-we may however come to question how far this result is based on
-expectations from the human user side, which are likely to be refined
-after continued interaction, and after the user gets acquainted with the
-robot's behavior.} A similar finding is described in
+mechanic ones \citep{kiesler_mental_2002}.
+%\footnote{Later in this article,
+%we may however come to question how far this result is based on
+%expectations from the human user side, which are likely to be refined
+%after continued interaction, and after the user gets acquainted with the
+%robot's behavior.}
+A similar finding is described in
 \cite{hegel_understanding_2008} and \cite{krach_can_2008}. In a user study using
@@
 a tendency to explain one's own and others' actions in terms of beliefs, desires
-and goals,  called \textit{theory of mind}. The theory of mind allows the
+and goals, called \textit{Theory of Mind}. Theory of Mind allows the
 implicit attribution of intentions and other mental states to others
@@
 behavioral level as well as on the neuro-physiological level: the more the
-human-likeness of the artefactual partner increases, the more brain areas
-associated with theory of mind  get activated \citep{krach_can_2008}.
+human-likeness of the artifactual partner increases, the more brain areas
+associated with Theory of Mind get activated \citep{krach_can_2008}.
 Implication of human brain area involved in the inference of others' mental
 states has also been shown in response to viewing
-non-anthropomorphic/non-humanoid robotic gadgets whose behavior has been
+non-anthropomorphic / non-humanoid robotic gadgets whose behavior has been
 described as unpredictable -- but not in response to those whose behavior was
@@
 \citep{Waytz2010}. Interestingly, the grey matter volume of a brain area
-related to theory of mind has been correlated to individual's score of
+related to Theory of Mind has been correlated to individual's score of
 anthropomorphism \citep{cullen2013individual}.
 
-At lower, more automatic, level, robots have been shown to elicit resonance
+At a lower, more automatic, level, robots have been shown to elicit resonance
 behaviors in the human brain. Resonance behaviors \citep{Rizzolatti1999} are
@@
 activates the motor mirror neurons the same way as for seeing a human arm
-reaching for the same object \citep{Gazzola2007, oberman_eeg_2007}. However, a
-study of emotion perception on a robotic face found reduced activity in
+reaching for the same object \citep{Gazzola2007,oberman_eeg_2007}. However, a
+study of emotion perception on a robotic face, found reduced activity in
 emotional brain area known to have mirror properties in response to the robotic
-face compared to a human face \citep{Chaminade2010}. Nevertheless, these authors
-showed that when the participants were explicitly instructed to pay attention to
-the robot's emotional expression, motor mirror neurons get activated.
+face compared to a human face \citep{Chaminade2010}. Nevertheless, the authors
+showed that when participants were explicitly instructed to pay attention to
+the robot's emotional expression, motor mirror neurons got activated.
 Interestingly, using electroencephalography, it has also been shown that
@@
 that they make inferences about these agents based on what is familiar to them
--- themselves, humans and human behavior. This understanding builds on the
-theory of mind,  a
-person's ability to attribute mental states to oneself and others. 
+-- themselves, humans and human behavior.
+%This understanding builds on the
+%theory of mind,  a
+%person's ability to attribute mental states to oneself and others. 
 %A theory of mind for other agents enables us to attribute intentionality to those agents \citep{leslie_pretense_1987,admoni_multi-category_2012}. 
@@
 in the attribution of mental states to other humans. The human-likeness quality
-of the artefactual agent seems to play a role in the involvement of theory of
-mind but also the unpredictable feature of the agent behavior alone seems to be
+of the artifactual agent seems to play a role in the involvement of Theory of
+Mind but also the unpredictable feature of the agent behavior alone seems to be
 sufficient. Low-level mechanisms of the brain that allow humans to map others'
@@
 signals from a robot the same way as they do for human beings.
-%were recently demonstrated at the brain level~\citep{cullen2013individual}.
-
-\subsubsection{Social psychology research: a 3-factor theory of anthropomorphism\\}
-\label{sec:psychological-factors}
-
-Social psychology, finally, offers theories that apply well to understand
-people's motivation to anthropomorphize. Irrespective of the artifact's
-characteristics, several psychological determinants have been found to explain a
-person's tendency to anthropomorphize. \cite{epley_seeing_2007} present a
-\emph{3-factor theory} of when people are likely to anthropomorphize based on
-psychological determinants. Namely, the theory suggests that some people are
-more likely to anthropomorphize when:
-
-\begin{enumerate}
-	\item ~anthropocentric knowledge is accessible and applicable to the artifact (\textit{elicited agent knowledge}),
-	\item ~they are motivated to explain and understand the behavior of other agents (\textit{effectance motivation}), and
-	\item ~they have the desire for social contact and affiliation (\textit{social motivation}).
-\end{enumerate}
-
-The first factor (\textit{elicited agent knowledge}) is a \emph{cognitive
-determinant} of anthropomorphism and based on the idea that a person builds a
-mental model (theory of mind) of the other agent. \citet{epley_seeing_2007}
-suggest that the process of making inferences about non-human agents is based on
-the activation of knowledge about humans (or the self). As mentioned before,
-when a person builds a mental model of the other (unfamiliar) agent, the
-question here is why does she draw on knowledge about other humans / herself and
-not on something else? One basic reasons for this is a person's physical
-constraints of being a human and nothing else. Consequently, one has no other
-experience than the self and in turn people tend to make inferences about
-others' mental states by relying inordinately on their own mental state.
-\footnote{Using one's own mental states and characteristics as a guide when
-reasoning about other humans is called ego-centrism. In contrast, when using
-self-knowledge (or knowledge about humans in general) when reasoning about
-non-human agents, this is called anthropomorphism. See
-\cite{epley_seeing_2007}.} Also empirical findings suggest that knowledge about
-humans in general, or self-knowledge in particular, is likely to serve as a
-readily accessible base for induction when reasoning about non-human agents.
-This tendency is usually stronger in young children and decreases with cognitive
-development and the learning to distinguish the self from other humans, and
-non-human agents.
-
-Both the second factor \textit{effectance} and the third factor
-\textit{sociality} are \emph{motivational determinants} of anthropomorphism.
-\textit{Effectance} is understood a person's motivation to interact effectively
-in one's environment. That means, a person is motivated to be able to
-understand, predict, and reduce uncertainty about her environment and the agents
-that inhabit it. According to \cite{epley_seeing_2007}, \textit{effectance
-motivation} can lead to anthropomorphism, since anthropomorphism serves as one
-way to reduce uncertainty and to increase comprehension of events in one's
-environment. Again, also according this factor it can be argued that children
-are more likely to anthropomorphize than adults. As children are in their early
-stages of life, they are likely to feel more uncertain within their environment,
-and consequently tend to anthropomorphize more.
-
-The third factor \textit{sociality} describes a person's motivation for social contact, social connection, and social approval from other agents.
-In lack of social connections to other humans (\etc friends, family, colleagues), a person is more likely to compensate these social connections by anthropomorphizing non-human agents.
-In other words \textit{``[...] those who are chronically lonely should be more likely to anthropomorphize nonhuman agents than those who are more chronically connected"} \citep{epley_seeing_2007}.
-Importantly for anthropomorphism, this social connection often appears to be satisfied by connections with \textit{``two of the most commonly anthropomorphized non-human agents, namely pets and religious agents"} \citep{epley_seeing_2007}.
-Thus, the motivation of being socially connected increases the tendency to anthropomorphize non-human agents because first sociality motivation increases the tendency to perceive human-like characteristics and traits even in non-human agents, and second it increases the tendency to search for sources of social connection in one's environment.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-%
-%
-%		ANTHROPOMORPHISM AS A MULTI-FACTOR PHENOMENON
-%
-%
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Summary: Anthropomorphism as a multi-factor phenomenon}
-\label{sec:multi-factors}
-
-Summing it up, anthropomorphism is a commonly discussed and
-studied trait of human-robot interaction; however its current understanding seems to be stuck.
-More concretely, when seeking to understand why anthropomorphism in an interaction between a human and a non-human artifact happens, most attention is given to the artifact and/or to the human.
-We agree that these two are the essential ``players'' of anthropomorphism (see Figure \ref{fig:anthropofig}).
-Indeed and, as outlined before, research has shown that both the human and the artifact are not only the two players of anthropomorphism but also the two main ``factors'' that can promote or hinder anthropomorphism.
-
-However, we think that this is not the full story. When agreeing to understand anthropomorphism as a specific type of \textit{experience} that arises in an
-\textit{interaction} between a set of user expectations and the external reality \citep{persson_anthropomorphism_2000}, 
-%(see Figure~\ref{fig:anthropomorphism_and_interaction})
-it becomes clear that this interaction happens in a specific context, with a specific history.
-We think that the context and the history of the interaction (in Figure \ref{fig:factors} denoted as \textit{time}), are two more factors that determine anthropomorphism.
+
+\subsubsection{Cognitive Processes and Stages\\}
+
+Based on these lower and higher level cognitive correlates that lead to different levels of anthropomorphism, we would like to propose three main cognitive processes / stages that are relevant for interpreting the level (`depth') of anthropomorphism that is observed.
+
+%\hl{Infrahumanization theory}: people differentiate the ingroup from other groups by attributing uniquely human emotions.
+They consider secondary (uniquely human) emotions as being more characteristic of their own group than of the outgroup (Leyens, et al., 2000).\\
+%Typical \textbf{primary emotions} include fear, anger, sadness, and happiness (although these can also be felt as secondary emotions).
+\textbf{Secondary emotions} appear after primary emotions and may come from more complex chains of thinking.
+Examples: longing, affection, envy, shame, guilt).
+
+\textit{Stage 1} is the instinctive, pre-cognitive identification of living peers.
+Studies conducted by \cite{rosenthal-vonderputten_experimental_2013}, who investigated the neural correlates of emotional reactions of humans towards a robot, support the idea that humans tend to anthropomorphize robots intuitively in this pre-cognitive way.
+\textit{Empathy} is characteristic of this stage \citep{rosenthalvonderPutten2013neural}.
+At \textit{Stage 1}, intuitive anthropomorphism is likely at a lower level: so-called mirror neurons get automatically activated in response to the participant viewing the robots' actions and reacting emotionally toward it.
+This process may be similar to two previously described perspectives.
+First, relating this cognitive \textit{Stage 1} to a specific \textbf{user experience}, it may be similar to what \cite{norman_emotional_2003} characterizes as the \textit{visceral level}.
+By this, he means the first impression that a person has of a product, based on experience.
+At this level, people do not think about the product but make spontaneous judgments.
+Overall, Norman lists three different levels, that stand for different user experience dimensions, when analyzing     how people experience using a product for the first time and getting emotionally attached to it.
+Emotional attachment to a product is somewhat related to anthropomorphism.
+We come back to the other two levels of user experience later on.
+Secondly, our proposed cognitive \textit{Stage 1} may also be similar to what \cite{takayama_perspectives_2012} calls the \textit{in-the-moment} perspective on agency with a robot (in contrast to the \textit{reflective} perspective).
+For instance, when reflecting upon it, we may \textit{not} perceive agency in a social robot, however, this may feel quite differently right in the moment of interacting with the robot.
+Takayama argues that neglecting to separate reflective perspectives from in-the-moment perspectives of agency is one of the major sources of confusion when people talk and write about anthropomorphism.
+There appears to be a disconnection between what people consciously perceive and how they respond to stimuli that they may not consciously perceive.
+That means, in an initial phase of interacting with a novel device, people might not respond consciously but rather mindlessly \citep{nass_machines_2000}, and in turn anthropomorphize more easily.
+Only after some time of getting familiar with the robot, they might respond in a more reflective manner, and in turn the tendency to anthropomorphize may decrease (see Section~\ref{sec:dynamics}).
+This can be illustrated by the fact that when asked about it, people tend to deny interacting with computational systems as if they were people and yet they would respond to computers in many ways that are remarkably similar to how they respond to people \citep{reeves_media_1996}.
+\cite{takayama_perspectives_2012} also applies a cognitive viewpoint on the two different perspectives of \textit{in-the-moment} \textit{vs.} \textit{reflective}, to illustrate differences.
+She states that \textit{in-the-moment} perceptions of agency are largely shaped by bottom-up perceptual processes, evoking very immediate responses, for instance to the cues emitted by the robot's design.
+In contrast, \textit{reflective} perceptions are more often shaped by top-down processes because of the nature of reflective thought \citep{takayama_perspectives_2012}.
+
+The cognitive \textit{Stage 2} is typically reached after a longer observation period (including complete action sequences of the robot) or short interaction (touching the robot, short talk like greetings).
+At this stage, the human starts building a behavioral and cognitive model of the robot that supports both the observed and imagined capabilities of the robot.
+The \textit{familiarity thesis} \citep{hegel_understanding_2008} supports the idea that the human first projects onto the robot mental models of similar agents he/she is already familiar with (animals, human adults, children) (see Figure~\ref{fig:mental-model-overlap}).
+At this stage, the user might also change his/her attitude towards the robot, paying more attention to social cues than to low-level behavior which may reinforce the resonance mechanism.
+From a user-experience perspective, this cognitive stage may be similar to the \textit{behavioral level}, as proposed by \cite{norman_emotional_2003}.
+The author describes that at this level, people use and experience the product, appraise its functions, and consider aspects such as usefulness and usability.
+The product is experienced through interacting with it (behavior).
+
+\textit{Stage 3} is typically reached after a contextualized interaction, which is explicitly purposeful (the purpose of the interaction, be it purely entertainment, is explicit and conscious to the user), and takes place in an environment that fosters a stronger cognitive (and possibly affective / social) commitment from the human in the interaction (\eg at home).
+During this interaction, through experimenting with the robot, users iteratively restate  and reshape their behavioral and mental model of the robot (\textit{How does the robot react to such and such situation / input?
+What does the robot know about me?
+About itself?
+About our environment?
+What can the robot learn?
+etc.}).
+People assess the capabilities and limitations of the robot.
+This mental process depends on the human understanding of the robot's inner working, as well on the own tendency to anthropomorphize (characteristics of the human, Section~\ref{sec:factor-human}).
+Overall, as the mental model becomes more complete and detailed, there may be less `space' for anthropomorphism.
+At \textit{Stage 3}, the perception of the robot and its intended purpose appear to play a less important role than the personal characteristics.
+The process here is mostly driven by the user himself.
+The result of this \textit{Stage 3} would come along with a modified tendency to anthropomorphize because the user has built a full cognitive model of the robot, so that there is nothing left unknown about it.
+Consequently, the user is now able to attribute appropriate internal states to the robot.
+As previously mentioned, our proposes \textit{Stage 3} is similar to the \textit{reflective perspective} described by \cite{takayama_perspectives_2012}, and to what Norman calls equally the \textit{reflective level} of user experience \citep{norman_emotional_2003}.
+Here, consciousness takes part in the process, and past experiences are taken into account.
+
+%An alternative way to think of the three proposed cognitive stages is to relate them to the specific \textbf{user experience} which is characteristic of these three stages.
+For instance, \cite{norman_emotional_2003} characterizes three user experience dimensions (related to emotional attachment, which is somewhat similar to anthropomorphism), which occur when people use or see a product for the first time:
+%
+%\begin{enumerate}
+%\item the \textit{visceral level}, which is the first impression of a product based on its experience; at this level people do not think about a product but make spontaneous judgments;
+%\item \textit{behavioral level}, in which people use and experience the product, appraise its functions, and consider aspects such as usefulness and usability;
+%\item the \textit{reflective level}, in which consciousness takes part in the process, and past experiences are taken into account.
+%\end{enumerate}
+
+Such a cognitive / user experience view can be applied to analyze people's first reactions to robots, as it has been done by \cite{weiss_i_2009}.
+The authors explored emotional attachment during first time reactions of children and adults with the robotic dog AIBO.
+They also stressed the fact that it is important to understand the long-term development of people's social bonds to robot, since the first \textit{spontaneous} and \textit{in-the-moment} reactions are special.
+Keeping these aspects in mind, we suggest to regard anthropomorphism not as a constant but as a variable and to study how it evolves over time.
+Studies that investigate anthropomorphism should therefore preferably be span over extended periods of time or consist of several interaction sessions, so that a \textit{reflective level} can be reached.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+%
+%
+%		DYNAMICS
+%
+%
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Anthropomorphism is Dynamic}
+\label{sec:dynamics}
+
+So far, the HRI community has not investigated how anthropomorphism in interactions with robots evolve over time.
+There are several reasons for why it makes sense to consider temporal dynamics in anthropomorphism.
+
+One reason for why changes in anthropomorphism over time are likely, comes from the cognitive perspective, as outlined in the previous section.
+We are spontaneous but also reflect on our interactions with the robot.
+From the artifact-centered perspective on anthropomorphism (thus, looking at the characteristics of the robot) it is assumed that humans directly (more or less mindlessly) respond to life-like and social cues that a non-human agent (here: robot) emits \citep{reeves_media_1996,nass_machines_2000}.
+Without huge thoughtful mental processing, humans tend to apply stereotypes and heuristics to the robot, and in turn apply human-human social schemas and norms to the occurring interactions.
+However, this may only be some \textit{immediate} (sometimes visceral) experience, reflecting the first impression that the user has of the robot, based on its appearance \citep{norman_emotional_2003}.
+\cite{takayama_perspectives_2012} refers to this as the \textit{in-the-moment} perspective we have on the robot, compared to a more distanced cogitation and consideration, which the author calls \textit{reflective}.
+Further, we also become familiar with the robot as we continue interacting and dealing with it, we gain knowledge about it, and refine our mental model of the robot.
+
+Another reason for considering temporal dynamics are the changes in user experience \citep{karapanos_user_2009} and relationship to the robot.
+\cite{kanda_interactive_2004} pointed out that not only the relationships among people evolve over time but that, in a similar manner, one can expect that also people's relationship and their attitude toward robots evolve.
+The authors were among the first ones to describe empirically \textit{novelty effects} during a long-term study with an interactive robot in a school.
+
+Overall, we suggest that there is a process of familiarization between the human and the robot.
+Through this process, the user becomes on one hand more familiar with the robot and hence reduces uncertainty about it, and on the other hand the user gets more used to the robot in terms of how he/she experiences using and interacting with it.
+We hypothesize that through the process of familiarization a user's tendency to anthropomorphize generally decreases.
+This is an idea.
+There may be variances and exceptions based on person-related characteristics.
+The suspected relation between continued interaction over time (labeled as \textit{interaction history} ($t$)) and the observable \textit{anthropomorphic effects} ($A$) is visualized in Figure~\ref{fig:model-dynamics}.
+The initial idea of this phenomenological model was first proposed in \cite{lemaignan_dynamics_2014}.
+While the model primarily considers \textit{long-term interaction} of a human with the same robot, we do not make a precise statement about how long \textit{long-term} is.
+It appears more practical to not speak of a specific time interval (like two days or two weeks) but to rather consider the actual duration and frequency of the (imagined or real) interactions.
+Therefore, the time-axis is labeled \textit{interaction history}.
+On the y-axis anthropomorphism is quantified as a normalized value of \textit{anthropomorphic effects} $A_t(H,R,C)$.
+These are often qualitative and difficult to quantify on an absolute scale, so we present them as normalized value (denoted as $A$).
+If no anthropomorphic effects are observable, $A=0$.
+The maximum value of anthropomorphic effects is unique for each human user interacting with a specific robot in a given situation.
+Our conceptual model of the \textit{dynamics of anthropomorphism} is characterized by three phases.
 
 \begin{figure}
-    \centering
-    \includegraphics[width=0.7\columnwidth]{factors}
-    \caption{Anthropomorphism is a multi-factor phenomenon.
-How far people tend to anthropomorphize a robot is determined by four main factors: the design of the robot $(R)$, the personal characteristics of the human user $(H)$, the situation and context in which the interaction occurs $(C)$, and the amount of time (repeated interaction) that the user spends to familiarize herself with the robot $(t)$.}
-    \label{fig:factors}
+\begin{center}
+\includegraphics[width=13cm]{model-dynamics.pdf}% This is a *.jpg file
+\end{center}
+ \textbf{\refstepcounter{figure}\label{fig:model-dynamics} Figure \arabic{figure}.}{~~\small The conceptual model of the dynamics of anthropomorphism shows that the relationship between the \textit{anthropomorphic effects} ($A$) and the \textit{interaction history} ($t$) is non-linear.The curve starts with the \textit{Initial Capital of Anthropomorphism} ($ICA$).
+Then, there are three main phases: \textit{Initialization}, which is characterized by the \textit{novelty peak}; \textit{Familiarization}, in which \textit{disruptive behaviors} of the robot may lead to a peak or plunge of anthropomorphic effects; and \textit{Stabilization}, in which the curve balances over a longer period of time to obtain a \textit{Stabilized Level of Anthropomorphism} ($SLA$).
+The duration of these phases may vary and the overall shape of the curve is unique to each human interacting with a specific robot in a given context, as depicted by the alternative curves.}
 \end{figure}
 
-Consequently, we propose a holistic understanding of anthropomorphism as a phenomenon which is determined by multiple factors (see also Figure \ref{fig:factors}):
-
-\begin{enumerate}
-\item ~the characteristics of the \textbf{robot's design} (degree of anthropomorphic form),
-\item ~the psychological determinants in the \textbf{human user} (see
-\cite{epley_seeing_2007}),
-\item ~the characteristics of the \textbf{context / situation} in which the interaction occurs, and
-\item ~the fact of the user getting familiar with the robot \textbf{over time} (duration / history of interaction)
-\end{enumerate}
-
-%However, anthropomorphism is a complex process and we think that the current understanding of it does neither seem to fully take into account the wide range of phenomena that it encompasses, nor the multiplicity of factors which determine it.
-%This shortcoming and conflict in the understanding of anthropomorphism in HRI has already been denoted by others but we would like to take a first step towards moving forward in this dilemma, and encourage an open dialogue to solve this.
-
-%we suggest to understand anthropomorphism as a \emph{dynamic},
-%\emph{context-dependent} process. To this end, we apply Persson \textit{et
-%al.}'s six levels on anthropomorphism to HRI and introduce three
-%\emph{interaction phases}. These interaction phases of anthropomorphism reflect
-%also the results of a long-term study that we conducted in a real human
-%environment and provide an account of the so-called \textit{novelty effect}.
-
-%\begin{figure}[ht!]\centering
-%% Use the relevant command to insert your figure file.
-%% For example, with the graphicx package use
-%  \includegraphics[scale=0.42]{persson_anthropomorphism.png}
-%% figure caption is below the figure
-% \caption{Anthropomorphism emerges in the (real or imagined) interaction between
-% robot and user; illustration taken from \cite{persson_anthropomorphism_2000}
-% \hl{maybe we don't put the figure here, it was just to illustrate what I mean}}
-%
-% \label{fig:anthropomorphism_and_interaction}       % Give a unique label
-% \end{figure}
-
-When taking into account these multiple factors, a logical consequence seems to be that anthropomorphism is not either there or not there but that it arises in different levels, may they be distinct, having multiple layers \citep{persson_anthropomorphism_2000}.
-or a continuum being describes in low and high anthropomorphism \citep{ruijten_introducing_2014}.
-For instance,
-
-Moreover, we propose that anthropomorphism shows not only variances determined by these four main factors but that -- the fourth factor implies this -- anthropomorphism is likely to evolve over time with continued interaction between the human and the non-human agent.
-
-To facilitate things, we introduce the notation \Ant[R,H,C,t] to bring these multiple factors together. To take into account dynamics over time, we suggest that
-anthropomorphism is a function of a vector of robot's traits $R = \{r_0,...,r_n\}$, a vector human
-determinants $H = \{h_0,...,h_n\}$, characteristics of the interaction context $C = \{c_0,...,c_n\}$, and the duration / history of the
-interaction itself, $t$.
-
-%% -> Commented out the overview as it does not match what we actually present... maybe we need a new one?
-% We would further like to review and discuss research on anthropomorphism in
-% robotics and human-like design of robots. We first provide a comprehensive
-% understanding of the phenomenon drawing on theories from developmental
-% psychology and cognitive sciences. We then present the trends of different
-% kinds of anthropomorphic forms in robots and discuss their role in social
-% robotics. The article integrates related work from human-robot interaction
-% studies, reporting on findings from experiments with human subjects
-% interacting with and evaluating various types of systems. We try to give a
-% coherent view on the topic, outline similarities and antithetic findings, and
-% contribute to a better understanding of anthropomorphism in robotics, and the
-% acceptance of human-like characteristics in robots. We also aim to
-% constructively discuss anthropomorphic design of personal and socially
-% interactive robots.
-
-%In this article we will use the term \emph{anthropomorphic effect} to denote
-%observable correlates of anthropomorphism. With these we include, amongst
-%others, verbal utterances (such as direct speech or the use of pronouns
-%"he/she"), (social) gestures (such as a hug, waving, deictic gestures) or
-%\hl{anticipation of certain actions of an agent [what??]}.
-
-% Persson \textit{et al.}
-%suggest that the social phenomenon involves several levels, like primitive
-%psychology, folk-psychology, social stereotypes, and emotional anthropomorphism.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-%
-%
-%				PART 2: OUR IDEAS -- A DYNAMIC PHENOMENON
-%
-%
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-% SEVERIN & JULIA: there will be 2-3 subsections in which we present our ideas:
-% 	1) anthropomorphism is a multi-factor phenomenon (the figure with the several factors)
-%	2) anthropomorphism is dynamic (the dynamic curve model)
-%
-%
-
-\section{Anthropomorphism: a dynamic phenomenon}
-\label{sec:our-ideas}
-
-So far, the HRI community has not much investigated how anthropomorphism in
-human-robot interactions evolves over time (during the process of
-\emph{adopting} a robot, for instance). Though conflicts were
-found in the understanding of what anthropomorphism is, the HRI
-community more or less accepted viewing anthropomorphism as a static feature
-that once observed during a short-term interaction reflects a sustaining social
-effect. However, if we agree that anthropomorphism arises in an interaction, and thus reflects a specific relation, we cannot accept it as a static phenomenon.
-
-Similarly, \citet{kanda_interactive_2004} point out that relationships among
-people evolve over time and, in a similar manner, one can expect people's attitude toward
-technological artifacts and their relationship with them to evolve as well.
-In their study, \citet{kanda_interactive_2004} were among the first to
-describe empirically \emph{novelty effects} during a long-term study with an
-interactive robot in a school.
-
-From a theoretical perspective, we also expect anthropomorphism to change over
-time, with growing experience with a robot. As discussed in the previous
-sections, anthropomorphism means in essence \emph{reasoning about and perceiving
-something non-human (and unknown or unfamiliar) based on one's
-representation of the familiar and well-known concept of being human (or
-one-self)}. According to \citet{epley_when_2008}, the basic operations that
-underlie these inductive inferences are the \emph{acquisition of knowledge}, the
-\emph{activation or elicitation of knowledge}, and the \emph{application of
-activated knowledge at the time of the judgment}. By applying knowledge to a
-given situation or interaction, one also attempts to correct,
-adjust, or maybe integrate less accessible information into a more automatically
-activated default representation.
-%Epley argues that this process can be seen as
-%a process of correction, and thus, it is often insufficient leaving final
-%judgments biased in the direction of the initially activated representation.
-%Refinements to the initial representation mean something evolves.
-This process of refining the applied knowledge are natural because a person's knowledge base changes constantly with newly
-acquired things.
-For instance, a person can acquire new knowledge about a robot when interacting with it.
-With continued interaction with the unknown system also the user's expertise with the system grows, and it can be expected that in turn, the user will become able to better predict the previously unknown system.
-Consequently, as the robot becomes more predictable, there is less uncertainty, and the ``need to anthropomorphize'' the robot decreases (from the
-human-centered point of view).
-
-In other words, humans have a motivation to interact
-effectively in their environment \textit{(effectance)} \citep{epley_when_2008}.
-This means that humans are motivated to be able to understand and predict the
-environment and the agents around them.
-Thus, a person will seek to become familiar with what is unfamiliar.
-Anthropomorphism is encouraged when an agent is unfamiliar.
-Consequently, in the process of familiarizing oneself with an agent, the tendency to anthropomorphize this agent should decrease.
-
-We can not be sure about how exactly the process of familiarization to an unfamiliar agent (based on continued interaction with the robot) looks like.
-In turn, we can not make a precise statement about how continued interaction decreases anthropomorphism but we suspect there is a link between the two.
-
-In the introduction, we reported on a few selected experimental results that
-illustrate how the user tendency to anthropomorphize decreased over time.
-Combined with the extensive discussion on the nature and factors of
-anthropomorphism that we proposed in section~\ref{sec:anthropomorphism}, we
-introduce in the following section a novel qualitative model of the evolution
-of anthropomorphism over time, \ie a model of the \emph{dynamics of anthropomorphism}.
-
-\subsection{A Model of the Dynamics of Anthropomorphism}
-\label{sec:dynamics-model}
-
-The phenomenological model of anthropomorphism we propose
-(Figure~\ref{fig:dynamics},~\citep{lemaignan2014dynamics}) represents how the
-level of ``anthropomorphic effects''~\Ant[R,H,C,t] (\ie the observable
-manifestations of anthropomorphism) evolves over a long-term human-robot
-interaction.\footnote{We cannot make a precise statement about how long ``long-term'' interaction has to be to be considered as such.
-It seems to be practical to not speak of ``several days'' or ``weeks'' but to rather consider the duration and frequency of the actual interactions with the artifact.
-One could probably call this the ``interaction history''.}
-
-While the model primarily considers \emph{long-term interaction} -- direct
-(non-mediated), repeated interaction with the same robot, over an extended
-period of time (typically longer than a week), we also formally introduce a
-so-called \emph{novelty effect}~\citep{kanda_interactive_2004} that models the
-first phase of human-robot interaction, during which a specific increase of
-anthropomorphic interactions is observed.
-
-In the \emph{Dynamics of Anthropomorphism} model, anthropomorphism is quantified by a \emph{normalized level of
-anthropomorphic effects} $\antNorm[R,H,C,t] = \frac{\ant[R,H,C,t]}{\antMax}$:
-because anthropomorphic effects are often qualitative and difficult to quantify
-on an absolute scale, we present them as a normalized value, that spans from a
-minimum (no anthropomorphic effects: $\ant=0$) to a maximum (noted \AntMax, with
-$t_{max} = \operatorname{arg\,max}_t \, \ant[t]$). For the sake of readability,
-we will use \Ant in the following sections to refer to the normalized level of
-anthropomorphic effects. Note also that we discuss in
-Section~\ref{sec:measuring} possible methodologies for the quantitative and
-qualitative assessment of anthropomorphic effects.
-
-The actual maximum value of anthropomorphic effects depends on each unique
-combination of a human, a robot, a situation and several other factors we introduce below.
-Thus, the maximum value varies according to the specific characteristics of these factors.
-Figure~\ref{fig:dynamics} pictures this maximum value at
-$t_{max}$, which actually corresponds to what we call the novelty effect peak.\footnote{We assume that there is a peak in the human's experiences of the novelty effects of the unfamiliar system.
-Further, we suspect that this novelty peak comes along with the maximum value of anthropomorphic effects.}
- The general
-\emph{shape} of the curve remains however the same and depicts the evolution of
-anthropomorphism over time, \ie the general dynamics of anthropomorphism.
-
-\begin{figure*}[htb]
-\centering
-
-\begin{tikzpicture}[scale=1.4]
-
-% background shading
-\path[fill=green!20] (0,0) rectangle (0.6,5.5);
-\path[fill=blue!15] (0.6,0) rectangle (5.2,5.5);
-\path[fill=orange!20] (5.2,0) rectangle (9.8,5.5);
-\draw(0,5.5) node[anchor=south west, rotate=10] {\scriptsize \sc Initialization};
-\draw(2.5,5.5) node[anchor=south west, rotate=10] {\scriptsize \sc Familiarization};
-\draw(6.5,5.5) node[anchor=south west, rotate=10] {\scriptsize \sc Stabilization};
-% horizontal axis
-\draw[->] (0,0) -- (10,0) node[anchor=north] {$t$};
-\draw(5,-0.1) node[anchor=north] {\scriptsize Duration of interaction};
-
-% vertical axis
-\draw[->] (0,0) -- (0,6) node[anchor=east] {};
-\draw(-0.8,3) node[rotate=90,anchor=south] {\scriptsize Anthropomorphic effects};
-
-\draw (-0.05, 3) -- (0.05, 3) node[anchor=east] {\ICA};
-\draw (-0.05, 5) -- (0.05, 5) node[anchor=east] {\AntMax};
-
-% vertical axis - end
-\draw[->] (9.8,0) -- (9.8,2) node[anchor=east] {};
-\draw (9.8, 0.8) node[anchor=west] {\SLA};
-
-\draw[<-] (0.65,5) -- (0.8,5.2) node[anchor=east] {};
-\draw (0.9,5.3) node[anchor=west] {\tiny \it novelty peak};
-
-\draw[dashed] (0.6, 0) -- (0.6,5.1);
-\draw (0.6,0) node[anchor=north] {$t_{max}$};
-
-\draw[dotted] (0, 5) -- (6.2,5);
-\draw[dotted] (0, 3) -- (6.2,3);
-\draw[<->] (6.1,3) -- (6.1,5) node[sloped, above, midway] {$\Delta_{a}$};
-
-\draw[<-] (1.7,4.4) -- (3.2,4.1) node[anchor=east] {};
-\draw[<-] (2.85,2.6) -- (3.2,4.1) node[anchor=east] {};
-\draw (3.2,4.1) node[anchor=west, align=center] {\tiny \it disruptive\\ \tiny
-\it behaviors};
-%%%%%
-%% CURVES
-%%%%
-\begin{scope}[yscale=-1,shift={(-0.125,-0.4)}]
-
-    \draw[ultra thick] svg[scale=1cm] "M 0.125,-2.5619582 c 0.0200733,-1.1573591
-    0.33954391,-1.9982333 0.57940683,-2.0013597 0.13691605,0 0.25550329,0.052908
-    0.37497897,0.1661788 0.119476,0.1130305 0.2396954,0.2786079
-    0.37944,0.4790565 0.069872,0.099803 0.1021612,-0.2231749
-    0.1792538,-0.2238964 0.099707,0 0.013454,0.4985362 0.3173383,0.9139831
-    0.1911917,0.2612926 0.3444354,0.2578391 0.6711932,0.4894291
-    0.2058265,0.1458798 0.1571532,0.9762306 0.2615031,0.9702183 0.097182,0
-    0.083295,-0.3336208 0.4330446,-0.1199242 0.4306401,0.2631203
-    0.216699,0.1355642 0.4296663,0.2647074 2.0858202,1.13836043
-    4.34683,1.41300027 6.3741749,1.43753027";
-
-    \draw[dashed] svg[scale=1cm] "M 0.125,-0.1952939 c 0.0553601,-3.1917862
-    0.33954391,-4.3648976 0.57940683,-4.368024 0.13691605,0 0.25550329,0.052908
-    0.37497897,0.1661788 m 2.6714393,2.7735737 C 4.7653984,-0.85050947
-    6.5955093,0.35382293 10.125,0.4062498";
-
-    \draw[dashed] svg[scale=1cm] "M 0.125,-3.6923825 C 0.1102888,-4.0297903
-    0.46454391,-4.5601915 0.70440683,-4.5633179 M 3.7508251,-1.6235654 C
-    4.9579368,-0.95548345 8.1358175,-0.82609971 10.125,-0.79459549";
-
-\end{scope}
-
-\end{tikzpicture}
-
-\caption{The dynamics of anthropomorphism. We distinguish three main phases:
-    \emph{initialization}, \emph{familiarization} and \emph{stabilization},
-    preceded by a \emph{pre-interaction} phase. The pre-interaction phase
-    is characterized through an \emph{initial capital of anthropomorphism} (ICA, noted \ICA).
-    Once the interaction starts, the level of anthropomorphism increases due to
-    the \emph{novelty effect}, and then decreases to reach a \emph{stabilized
-    level of anthropomorphism} (SLA, noted \SLA). \ICA and \SLA may vary
-    depending on the user (and his/her expectations), the robot and the context of interaction.  During the
-    interaction, unpredicted behaviors of the robot (\emph{disruptive
-    behaviors}) may lead to local increases or decreases of the level of
-    anthropomorphic effects.}
-
-\label{fig:dynamics}
-\end{figure*}
-
-\subsection{Three phases}
-\label{sec:phases}
-
-We distinguish three main phases that describe the evolution of the
-anthropomorphic effects in a long-term human-robot interaction. They are
-depicted in different shades in Figure~\ref{fig:dynamics}.
-
-First, the \emph{initialization} phase. During this short phase (from a couple
-of seconds to a couple of hours), we observe an increased level of
-anthropomorphism, from an \emph{initial capital of anthropomorphism} \ICA
-(detailed in the next section) to a peak of anthropomorphic manifestations
-\AntMax that corresponds to the maximum of the \emph{novelty effect}.
-Section~\ref{sec:initialization} details this first phase.
-
-The second phase, \emph{familiarization}, lasts longer (up to several days) and
-models the process of the human getting acquainted to the robot: by observation
-and interaction, the human builds a model of the robot's behavior that allows
-him/her to predict the robot's actions. We observe a decrease of
-anthropomorphic effects during this phase, that we explain by the acquired
-ability to predict the behavior of the robot: the initial apparent behavioral
-complexity vanishes, and the robot is considered more and more as a tool.
-Section~\ref{sec:familiarization} discusses the second phase.
-
-The last phase is the \emph{stabilization} phase. The level of anthropomorphic
-effects tends to stabilize over a longer time, to reach a \emph{stabilized
-level of anthropomorphism} \SLA. \SLA may be null (no anthropomorphic
-effects observed anymore), but it may also remain at a higher level.  This
-third phase, as well as the \emph{stabilized level of anthropomorphism}, are
-discussed in section~\ref{sec:stabilization}.
-
-\paragraph{Pre-interaction phase and Initial Capital of Anthropomorphism (ICA)\\}
-\label{sec:ica}
-
-The \emph{initial capital of anthropomorphism} \ICA describes the initial potential
-for the robot to be anthropomorphized by the human user in a given situation.
-This potential depends on several factors, introduced in
-section~\ref{sec:multi-factors}, see also Figure \ref{fig:factors}. It has been shown, for instance, that
-some \textit{people} tend to anthropomorphize more than others, that some
-\textit{situations} induce anthropomorphism more than others, that
-\textit{children} tend to anthropomorphize more than adults, and that some
-\textit{cultures} are notorious for their anthropomorphic religions and
-worldviews~\citep{epley_when_2008}. Also the shape and design of the robot play a
-role, as well as the context in which the interaction takes place. Our model of
-anthropomorphism represents these factors as a compound metric \ICA. As such,
-\ICA describes the level of anthropomorphic projections just prior the first
-(real or imagined) interaction with a robot. In this stage of pre-interaction, people
-form \textbf{initial expectations} toward the robot and imagine how they will use it /
-interact with it.
-
-Taking up on our suggestion to have four main factors that impact on anthropomorphism, we propose that the initial capital of anthropomorphism can be build \emph{a priori}.
-As the \ICA marks the very moment before the first real or imagined contact of the human with the robot, the \textit{interaction history} between the two players is empty; consequently the time factor $t$ is not taken into account when building the \ICA.
-The specific \ICA value reflects how far a robot is likely to be anthropomorphized, based on the following three factors:
-
-\begin{enumerate}
-
-    \item ~\emph{Human factor} $S$: The \textbf{personality} and individual
-        traits of the human user: Psychological characteristics / determinants
-        that influence a person's tendency to anthropomorphize
-        artifacts~\citep{epley_seeing_2007}. Other individual traits and
-        demographic aspects are comprised (\eg age, gender, cultural background,
-        professional background).
-
-    \item ~\emph{Robot factor} $R$: The robot's \textbf{design} and how it
-        appears to the human user. Characteristics of the robot's form,
-        behavior, and interaction modalities (anthropomorphic
-        design)~\citep{fong_survey_2003}.
-
-    \item ~\emph{Context factor} $C$: The real or imagined
-        \textbf{purpose} of the robot, including the situational context in
-        which it is used, as well as the task context and role in which the
-        robot is used / experienced (environmental
-        context)~\citep{joosse_what_2013}.
-
-\end{enumerate}
-
-For \textbf{personality}, we suggest to apply the
-psychological \textit{3-factor theory} of anthropomorphism by \citet{epley_seeing_2007}. For instance,
-children generally tend to anthropomorphize objects more than adults. Also, a
-person who lacks social connection is said to be more likely to
-anthropomorphize. Both aspects would increase \ICA. This means that, one and the
-same robot used by a different user, can lead to a different \ICA.
-
-For \textbf{design}, we understand that a robot that follows an anthropomorphic
-design up to a certain acceptable level (\eg Nao) leads to a higher \ICA than a rather functional robot (\eg
-Roomba). Also, a robot that is able to display facial expressions would increase
-the \ICA. Quantifying the \emph{level} of anthropomorphic design in a robot, as
-suggested for instance by \citet{fong_survey_2003}, can be difficult.
-Nevertheless, the important aspect is how the robot appears to the user, \eg
-human-like or machine-like, acceptable or not-acceptable.\footnote{It becomes clear that the \textit{robot factor} can not be fully separated from the \textit{human factor}.
-The reason for this is that the message that design tries to make, always lies in the eye of the beholder.
-No matter how much effort a designer spends in making the ``message'' of the artifact's design clear, there is always some scope and creative freedom in how the design is interpreted by the beholder.}
-
-By taking the \textbf{purpose} of a robot into account, we suggest that the real
-or imagined application context of the robot, or in which situation the interaction occurs, impacts how far the robot will be attributed human-like
-characteristics. We draw on findings such as presented in \citet{joosse_what_2013}. The authors showed for instance that when the
-same robot (Nao) is used in a different task context (cleaning task \emph{vs.}
-tour guide), users ascribe different personalities to the robot. In general,
-a robot which is imagined in a social, entertaining or playful
-context leads to a higher \ICA than a robot which is used for a routine or
-focused task (security, rescue, etc.).
-This was also found in an analysis of anthropomorphic language in online forum discussions about the AIBO, Roomba, and iPad \citep{fink_anthropomorphic_2012}.
-Regardless of the conversation topic, more anthropomorphic language was found in the AIBO forum.
-However, this was not only due to the zoomorphic (pet-like) shape of AIBO but also due to its  playful purpose.
-The idea that the purpose of a robot are crucial factors, also receives support from
-Goetz \& Kiesler's work that revealed that people prefer a serious robot for
-serious tasks and a less serious robot for more playful
-tasks~\citep{goetz_cooperation_2002, goetz_matching_2003}.
-However, what about artificial agents that seem to have no purpose?
-\cite{kaplan_free_2000} discusses the role of uselessness in the design of robots.
-He argues that artificial pets such as the AIBO, have no real purpose, in a sense that they do not provide any kind of service, or, in other words \textit{``they are not doing what you tell them to do''} and \textit{``they might refuse the order of its owner''}.
-It is this very aspect that might increase people's tendency to anthropomorphize the robot.
-According to Kaplan, it is in our daily use language, that we tend to attribute intentions to devices that are not doing their job well.
-For instance, we do not develop any kind of relationship with our computer, washing machine or TV set when they work properly.
-The author argues that it is only when they start dis-functioning, when they show that they can act differently that what we ordered, that we are ready to give them some kind of ``intentionality''.
-
- Also, we suggest that
-the environmental context in which people experience and interact with the robot
-impacts the \ICA. For instance, several friends interacting simultaneously with
-the robot might lead to increased \ICA for each of the users, due to increased
-human-human social interactions (the robot might be perceived to be part of the
-social interaction, and in turn attributed human-like
-qualities~\citep{baxter2013do}).
-
 \subsubsection{Initialization Phase\\}
-\label{sec:initialization}
-
-%\paragraph{The Novelty Effect\\}
-%\label{sec:noveltyeffect}
-
-We assume that the short phase of initialization is strongly affected by the so-called novelty effect.
-Novelty effects have been described with interactive technologies in general \citep{rogers_diffusion_1995} and also in several long-term HRI studies in workplaces \citep{huttenrauch_fetch-and-carry_2003,mutlu_robots_2008}, in schools and public places \citep{gockley_designing_2005,kanda_interactive_2004,kanda_communication_2005}, or elder care centers \citep{sabelli_conversational_2011}.
-Further, also with domestic robots it has been found that people's interest, engagement, and fascination with the robot decreased over time \citep{fink_living_2013,fernaeus_how_2010,sung_robots_2009}.
-
-To illustrate how the novelty of a robot can evoke anthropomorphic effects, we
-present an example from our long-term ethnographic study with Roomba vacuum
-cleaning robots in households \citep{fink_living_2013}. The observed scenario describes how an elderly
-woman (E., 71 years, living on her own with a little dog in a small row house) was
-setting up and using the robot for the first time during about 10 minutes.
-
-%The woman (E.) is reading aloud parts of the ``quick start manual'': \emph{``When
-%Roomba senses dirt, the blue dirt detect light is lit and Roomba cleans more
-%intensely in that area.''} She laughs and turns to the robot, talking directly to
-%it \emph{``Today you can light up darling!''}. E. carries the Roomba to the entrance
-%door and puts it on the floor [floor type: tiles, partially covered with little
-%Persian carpets], she explains \emph{``It has to start from here, this is where
-%you enter the house!''}. After pressing the CLEAN button, the robot quickly gets
-%stuck with the carpet in the entrance hall, consequently it reports error 1 [
-%two-tone \textit{``uh-oh''} sound followed by a narrated voice that starts off with \textit{``error
-%1''}]. E. is very surprised \emph{``What, it is even talking to me?''}, she lifts the
-%robot off and puts it back for cleaning.
-At several occasions, while watching
-how the robot moves around and cleans, E. makes compliments to the robot:
-\emph{``Nice!''} or \emph{``Good job!''} or \emph{``Bravo!''}. Once, when the Roomba turns
-right in front of some crumbs on the kitchen floor and moves away without
-cleaning them up, E. says: \emph{``There you forgot something, what about over
-there? Look, there you still have something to clean up!''}, and she points at
-where she wants the Roomba to go. Further, she uses deictic gestures and tells the
-robot: \emph{``No, go this way! Come over here!''}. The woman keeps observing the
-robot and wonders about its intentions, asking it directly: \emph{``Why do you
-leave the kitchen? There is still something there on the fringe!''}. E. turns to
-the experimenter, and tells her: \emph{``She [the robot] loves the hall!''}.
-
-Besides this behavior of generally anthropomorphizing the robot, we observe the
-following concrete instances as anthropomorphic effects in this scenario:
-talking directly to the robot, or asking it questions (though it doesn't
-recognize speech); giving it nick-names or ascribing a gender, praising the robot, using pointing
-gestures toward the robot, or trying to direct it around with commands, and attributing
-a personal preference / intention to the robot (\emph{``she loves the hall!''}).
-
-During the following visits at the woman's place, E. did not talk to the robot
-anymore, and generally behaved in a less anthropomorphizing way. The observed
-effects were likely due to the novelty of the robot, and the fact that E. was not familiar with the robot and its behavior.
-As \cite{persson_anthropomorphism_2000} names it: \textit{``Anthropomorphism is a way of making sense of complex behavior in the world around us.''} Thus, as soon as this complexity is reduced, also anthropomorphism might be reduced.
+
+The \textit{Initialization Phase} starts with the so-called \textit{Initial Capital of Anthropomorphism} ($ICA$), which corresponds to $A_0$ (value of $A$ at time point $0$).
+This value considers the multiple factors presented in Section~\ref{sec:multiple-factors}, thus it is composed by factors of the human $H$, the robot $R$, and the context of use $C$.
+As such, $A_0$ describes the value of anthropomorphic effects that can be expected to occur during the first contact between the human and the robot in a given situation.
+During this first phase, pre-conceptions and initial expectations as well as previous experience of the user with other similar types of robots and similar contexts can have a strong impact and influence the general tendency to anthropomorphize.
+
+During the \textit{Initialization Phase} we expect an increasing value of $A$ that may be partly due to the so-called \textit{effects of novelty} of the robot.
+Such effects have been described with interactive technologies in general \citep{rogers_diffusion_1995}, and also in several long-term HRI studies in workplaces \citep{huttenrauch_fetch-and-carry_2003,mutlu_robots_2008}, in schools and public places \citep{gockley_designing_2005,kanda_communication_2005,kanda_interactive_2004}, and elder care centers \citep{sabelli_conversational_2011}.
+Also long-term studies of domestic robots have shown similar effects and found that after some time people's interest, engagement, and fascination of the robot decreased \citep{sung_robots_2009,sung_domestic_2010,fernaeus_how_2010,fink_living_2013}.
+
+What type of anthropomorphic effects are typical during the \textit{Initialization Phase}?
+In our own work, we observed that users spontaneously tend to talk directly to the robot (though the user knows that the system is not be able to recognize speech), for instance, by greeting the robot, asking questions to it, giving it nick-names or ascribing a gender, praising the robot, commenting on its performance in general, and giving commands.
+Also, the use of point gestures and waving at the robot were fairly common among participants of our studies, as well as ascribing gender and some personal preferences or intention to the robot.
+(Note that we did not even use an anthropomorphic robot but a Roomba vacuum cleaning robot.)
+
+In general, it appears that anthropomorphism during the \textit{Initialization Phase} is a commonly observed phenomenon.
+But we would like to stress again that most of these effects are likely to fade out over time.
 
 \subsubsection{Familiarization Phase\\}
-\label{sec:familiarization}
-
-In this context, \emph{familiarization} means \emph{to get acquainted with}.
-It is not to be confused with the \emph{familiarity thesis} that relates to the
-projection of already known cognitive models onto the robot. We discuss this other
-aspect in section~\ref{sec:cognition-neuroscience}.
-
-The \emph{familiarization phase} starts at the peak of the \emph{novelty
-effect}: anthropomorphic effects are at their maximum, the user thinks (s)he is
-potentially facing an agent aiming at ``human-level intelligence'' (to take
-McCarthy's words). This is a transient state that quickly vanishes, and the
-projected anthropomorphism then starts to decrease while the human observes and
-recognizes that the behavior of the robot is generally \emph{predictable} and
-possibly \emph{deceptive} (for instance, it talks but does not understand when
-we talk; it has eyes but does not recognize everyday objects we show; \etc).
-
-\paragraph{Disruptive behaviors\\}
-
-By \emph{disruptive behaviors}, we mean any behavior exhibited by the robot that
-appears unexpected to the user: for instance, a robot may usually follow always the
-same route to go from one place in a house to the other, but suddenly it might change the
-route. The actual underlying reason may span from a bug to the detection of a
-new obstacle, but as long as this reason is not immediately
-intelligible to the user, the behavior counts as \emph{disruptive}. (We will come back to the role of disruptive behaviors later, in Section \ref{sec:disruptive}.)
-
-As illustrated in Figure~\ref{fig:dynamics}, our model represents
-\emph{disruptive behaviors} as either local increases or local decreases of
-anthropomorphic effects in the familiarization phase (and at a lesser extend, in
-the stabilization phase): because such behaviors are unexpected, a human
-observer may interpret them either as the result of a richer deliberative
-process, which in turn leads to the supposition of complex cognitive skills, or
-conversely as a failure, reminding the human that the robot is ``just a
-machine''. Section~\ref{sec:disruptive} discusses more in depth the impact of
-the user's perception of disruptive behaviors, and their cognitive correlates.
-
-To illustrate how a disruptive behavior of a robot can evoke anthropomorphic effects, we present again an example from our long-term ethnographic study with Roomba vacuum cleaning robots in households \citep{fink_living_2013}.
-The observed scenario describes how a family (young parents, 26 and 28 years old, with 3 little children, 5 and 4 years, and 6 months old, living in a house with garden on the countryside) were using the robot during the first week.
-
-The father (M.) always lets Roomba clean up the ground floor after the family finishes dinner and they all go upstairs to put the children to bed.
-When the robot would have finished its cleaning cycle, the parents would later just find it docked at its charging station.
-It used to be like this every evening.
-However, one day when the father comes downstairs, Roomba is not at its station.
+
+In the \textit{Familiarization Phase} the user gets acquainted and familiar with the robot and with using the robot, and hence the tendency to anthropomorpize decreases.
+This phase typically starts as the local maximum value of anthropomorphic effects that are enhanced by the novelty of the robot start to wear off.
+The user may think that he/she faces an agent that aims at ``human-level intelligence'' (to take McCarthy's words).
+This is a transient state that quickly vanishes as the user recognized that the behavior of the robot is generally \textit{predictable} and possibly \textit{deceptive}.
+For instance, the robot produces verbal utterances (it ``talks'') but it does not understand when we talk; or the robot is endowed with eyes but does not recognize the objects we show it.
+
+\subsubsection{Stabilization Phase\\}
+
+During the \textit{Stabilization Phase} the value of $A$ tends to stabilize over a longer time, to reach a value that we call the \textit{Stabilized Level of Anthropomorphism} ($SLA$), which corresponds to $A_{\infty}$.
+The value that the $SLA$ approaches is unique for each user interacting with a specific robot in a given situation.
+$A_{\infty}$ may approach $0$, when no anthropomorphic effects are observed anymore, for instance, when the user is interacting with the robot in a routine way and he/she does not project any human-like traits unto the robot\footnote{The robot may have become \textit{``invisible in use''} \citep{takayama_toward_2011}.} As such, the $SLA$ stands for the long-term lasting value of anthropomorphism.
+We proposed that $A_0$ (the value corresponding to the $ICA$) is built on multiple factors (see Section~\ref{sec:multiple-factors}) and similar $A_{\infty}$ is based on these factors, however taking into account the \textit{interaction history} $t$ that the user has with the robot.
+Note that the $ICA$ and the $SLA$ are generally not correlated.
+A person may initially have a high potential of anthropomorphizing (high $A_0$), for instance a highly anthropomorphic robot, but subsequently get disappointed by the actual capabilities of it and stop explaining it in terms of human-like characteristics (low $A_{\infty}$).
+Another user may however create lasting affective bonds with the same robot and may continue to anthropomorphize the robot (high $A_{\infty}$).
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+%
+%
+%		DISCUSSION
+%
+%
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Discussion}
+\label{sec:discussion}
+
+We propose that anthropomorphism evolves over time.
+How this evolution looks like has not been studied yet and we can only make speculations based on our own previous work and the literature that we reviewed.
+However, the topic of how human-robot interaction, and anthropomorphism as a special form of it, evolve over time is important and certainly deserves further investigation.
+We observed that initially, users commonly anthropomorphized their Roomba vacuum cleaning robot but that the anthropomorphic effects generally became less over time.
+However, we found that some moments during using the robot seemed to particularly induce anthropomorphism more than others, and we would like to discuss this aspect in the next paragraphs.
+
+\subsection{Disruptive Behaviors}
+
+By \textit{disruptive behaviors}, we mean a behavior exhibited by the robot that appears unexpected to the user.
+For instance, Roomba may usually follow always the same (or similar) route to go from one spot in the apartment to another spot (\eg by following along the wall).
+But what if the robot suddenly changed its route?
+How does the user perceive and interpret this robot behavior?
+The user may assume that there is a bug or a technical problem that made the robot detect an obstacle where there is none, however, the actual `reason' for such behavior (even if there is no reason for it at all) is not immediately intelligible to the user, and is such the behavior counts as \textit{disruptive}.
+How do \textit{disruptive} robot behaviors relate to anthropomorphism?
+As these behaviors are unexpected by the user, they may surprise him/her and make him/her wonder about the reason for this.
+As the disruptive behavior of the robot is an \textit{unknown stimulus}, we assume that this will increase the tendency to anthropomorphize it.
+Hence, the disruptive behavior may trigger anthropomorphism, as a result of spontaneous response from the user side.
+This type of anthropomorphism is likely to emerge from \textit{Cognitive Stage 1}, as it is an immediate response, and the lasting effect may be rather short.
+We visualize such an effect of a \textit{disruptive} robot behavior as either a peak or a plunge (see Figure~\ref{fig:model-dynamics}), depending on how the user interprets the robot's behavior and whether an immediate increase or decrease of anthropomorphism can be observed.
+
+To illustrate how a disruptive behavior of a robot can evoke anthropomorphism, we present and example from our long-term ethnographic study with Roomba \citep{fink_living_2013}.
+The observed scenario describes how a family was using the robot during the first weeks.
+
+\begin{quote}
+For several days now, the father (M.) always lets Roomba clean up the ground floor after the family has finished dinner and they all go upstairs to put the children to bed.
+M.
+knows that when the robot has finished its cleaning cycle, it goes to its charging station.
+It used to be like this every evening and the father would find the robot docking at its station the next morning.
+However, one day when M.
+comes downstairs, Roomba is not at its station.
 He says: \emph{``Hey, Roomba, where are you?
 Why did you not want to got to sleep last night?''}.
-After some searching he found it stuck under the sofa and wondered why this had happened.
-
-What is the observed anthropomorphic effect in this scenario?
-Usually, the father did not talk to the robot or praise it.
-However, now that the robot did something unexpected (it was not at its usual place) he started wondering about its ``intention'' and directly asked the robot for its reasons to not \textit{``go to sleep''}.
-
-\subsubsection{Stabilization Phase\\}
-\label{sec:stabilization}
-
-The last phase is the \emph{stabilization} phase. The level of anthropomorphic
-effects tends to stabilize over a longer time, to reach a \emph{stabilized
-level of anthropomorphism}, noted \SLA.
-
-If, after the familiarization phase, no anthropomorphic effects are observed
-anymore, $\sla = 0$. This can be interpreted as the user interacting with the
-robot in a routine way, without projecting anymore human-like traits on the
-robot.
-
-\paragraph{Stabilized Level of Anthropomorphism\\}
-
-The \emph{Stabilized Level of Anthropomorphism} describes the long-term lasting level of
-anthropomorphism.
-We proposed that \ICA is built on three factors: user's \emph{personality},
-robot's \emph{design} and interaction \emph{purpose} (or \emph{interaction
-context}). The user's personality and the context of use do also influence \SLA.
-In particular, it appears that the user's level of acquaintance with
-technologies plays an important role in long-term tendency to
-anthropomorphize~\citep{fink_living_2013} (people more familiar with technology
-understand, and hence predict, better the behavior of the robot, which in turn
-leads them more frequently to ultimately consider the robot as a simple tool).
-
-The robot's design, on the other hand, plays a more subtle role, and strong
-initial anthropomorphic design does not mandate high \SLA: lasting
-anthropomorphic effects have been observed on non-anthropomorphic robots (like
-the iRobot Roomba~\citep{fink_living_2013} or the military iRobot
-PackBot\footnote{Rodney Brooks has reported in keynotes that occasionally
-soldiers would give a name to \emph{their} PackBot and require it to be repaired
-instead of being replaced by another one in case of incident.}), and on the
-contrary, anthropomorphic designs can lead to higher expectation deceptions,
-resulting in the robot not being used anymore.
-
-Note that the \emph{Initial Capital of Anthropomorphism} and the
-\emph{Stabilized Level of Anthropomorphism} are generally not correlated: one
-individual may have high potential of anthropomorphizing (high \ICA) at first
-sight of a good-looking humanoid robot, and get disappointed by the actual
-abilities of the robots, down to routine, non-anthropomorphic, interactions (low
-\SLA), while another user with the same high \ICA may, for instance, creates
-lasting affective bonds with the same robot, and keeps anthropomorphizing it
-(higher \SLA).
-
-%\fixme{JF: Severin, we should at some point mention what the ``expectation mismatch'' is ...
-I haven't found that so far ...
-but I am also not sure about how to explain this.
-I think that, the we already took into account the user's expectations in the human-factor.}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-%
-%
-%		PART 3: EXPLANATIONS -- COGNITIVE CORRELATES, NEUROSCIENCE VIEW
-%
-%
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{The Cognitive Correlates of Anthropomorphism}
-\label{sec:cognition-neuroscience}
-
-This section provides an initial interpretation of anthropomorphism in
-terms of \emph{cognitive correlates}: how human cognition can explain the
-dynamic nature of our interactions with robots, and what are the main cognitive
-stages upon which researchers can build to design better, deeper human-robot
-interactions.
-
-The next sections introduce a model of the cognitive stages involved in
-human-robot interaction, that can be interpreted in parallel to the model of the
-dynamics of anthropomorphism.
-
-We also discuss two specific aspects: the cognitive impact of disruptive
-behaviors (section~\ref{sec:disruptive}) on mutual modeling, and how our models
-relate to the \emph{in-the-moment} versus \emph{reflective} perspectives on agency in HRI~\citep{takayama_perspectives_2012}.
-
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%    Review of neuroscience work on robot-based 
-%    anthropomorphism..... may be moved somewhere 
-%    else or dispatched
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%From the human point of view, what are the brain mechanisms that could mediate anthropomorphism towards robots ?
-%\subsection{Neuroscience review of anthropomorphic brain mechanisms in human-robot interaction}
-%The neuroscientific study of human-robot interaction is still in its infancy.
-So far most studies have used robots as a way to investigate humans behaviour and brain responses to perception of an artefactual agent actions and emotional states but have not really tapped in the study of how a human behaviours and brain processes are influenced by its direct interaction with a robot (add ref, ref).
-%We briefly review below the neuroscientific literature relevant to understand
-%the neural mechanisms that may underly anthropomorphism. 
-%
-%
-%
-%\paragraph{Mirror neurons and resonnance behaviors \\}
-%
-%Resonnance behaviors \citep{Rizzolatti1999} are mechanisms by which the brain areas involved in the internal representations of an action, an emotion or a sensation are equally recruited during the perception of another individual performing the same action or experiencing the same emotion or sensation.
-%
-%Resonnance behaviors have first been shown in the motor mirror neurons system, that is a neural network in motor areas that fire both during the execution of specific goal-oriented action and during the viewing of action directed toward the same goal~\cite{Rizzolatti1996, Kilner2009}.
-%
-%Interestingly, there are good evidence showing that motor mirror neurons in the
-%human brain respond to both human and robotic motion \citet{Gazzola2007, oberman_eeg_2007}, stressing that perceiving the goal of an action is more important than the human-likeness of its kinematic to activate resonnance mechanisms.
-%%For example, fMRI study \citet{Gazzola2007} have found no significant difference in the activation of the mirror neurons system during the observation of an industrial robot or of a human performing the same action, suggesting that the goal of the action is more important than its kinematics to activate resonnance mechanisms.
-%mirror neurons
-%
-%%[At stage 1] We suggest that the human's mirror neuron system is contributing to anthropomorphism by  allowing for a mapping of the robot's goal-directed actions into the human own motor repertoire \cite{Gallese1998, Wolpert2003, cullen2013individual}.
-%
-%The response of the human brain to a social signal perceived on a robot, such as facial
-%emotional expression is less evident. 
-%
-%In studying emotional perception in a human or a robot face using functional
-%magnetic resonnance imagery (fMRI) \citet{Chaminade2010} found reduced activity
-%in response to the robot stimuli than to the human stimuli in emotional brain
-%areas known to have mirror properties. However if the subject was asked to
-%specifically attend to the emotional content of the stimuli, processing of the
-%robot facial expresion, but not of the human's, elicited a significant increase in the anterior part of the anterior frontal gyrus, a brain area considered as a marker of motor resonnance.
-%
-%Using electroencephalograpy another study have found that perception of emotions in a non-humanoid robot face affects the early brain processes of emotional expressions and the behavioral response of the participants the same way as did a human face \citep{Dubal2010}.
-%
-%
-%
-%Thus it seems that the display of resonance mechanisms for social behaviour when
-%viewing a robot is less straightforward than for motor behaviour and may dependent more on the internal attitude and cognitive conceptions the human has of the robot. 
-%%Brain areas involved when attributing mental states to other human seem to be involved also in anthropomorphism .
-Indeed, individual scores of anthropomorphisms have been found to correlate with the grey matter volume of the left temporoparietal junction, a brain area activared during mentalizing \citet{cullen2013individual}
-%However, the studies reviewed above show that the human brain can respond
-%equally to a human or a robot stimuli but they do not  directly address the
-%question of anthropomorphism. Indeed, although it can contribute to it, neither
-%activation of mirror neurons system simulating a perceived action nor influence
-%on early brain processies readily imply that the human confers a humanlike mental
-%state to the robot and thus can not be sufficient to infer anthropomorphism 
-%
-%
-%%\citet{Dubal2010}: using robots with anthropomorphic (eyes, nose, mouth) featres but not human-like (ie.
-wires and cables) the study show effect of emotional state of the robot on early brain processes of emotional expression using ERPs (enhanced P1 in happy vs neutral state).
-%
-%\paragraph{Neural correlates of theory of mind and antropomorphism\\}
-%
-%
-%%From an early age, humans develop a tendency to explain one's own and others'actions in terms of beliefs, desires and goals called theory of mind or mentalizing allowing the implicit attribution of intentions and other mental states to others \citep{Frith2003}.
-%%A system of brain areas have been linked to mentalizing that encompass an anterior region of the medial prefrontal cortex (MPFC), that may be the basis to distinguish between mental and physical states representation, the temporal lobes, that may allow access to social knowledge  and the posterior superior temporal sulctuc (STS), that might be involved in detection of agency \citep{Frith2003}.
-%In a more direct study of anthropomorphism, \citep{cullen2013individual} related
-%participant's scores of tendency to anthropomorphize to the grey matter
-%volume of the left temporal junction, a brain area involved in mentalizing,
-%that is the attribution of mental states to other human beings (theory of mind) \citep{Frith2003}. 
-%
-%Of note, \citet{Waytz2010} showed that the more an artifical agent behaved
-%unpredictably, the more subjects tend to attribute it a mind and the more the
-%ventro medial prefrontal cortex (VMPFC), key area for sociocognitve processes
-%and especially egocentric mentalizing about similar others, gets activated.
-%
-%
-%%\paragraph{Emotions/Empathy}
-%%Attitude of the human in a human-robot interaction might influence the anthropomorphic quality of the interaction: \citet{Chaminade2010} shows that directing attention towards emotional processing increases the responses to humanoid robot facial expression in the anteriror part of the left anterior frontal gyrus, a neural marker of motor resonnance.
-%
-% 
-%
-%
-%In the following section, we provide a tentative model of anthropomorphism in terms of cognitive correlates.
-We warmly welcome the feedback and comments from both the cognitive sciences and robotics communities to further
-%discuss these findings.
-%
-%
-
-\subsection{A Model of the Cognitive Stages of Human-Robot Interaction}
-\label{sec:cognitive-model}
-
-\begin{figure}[htb]
-\centering
-%\resizebox{\linewidth}{!}{
-\begin{tikzpicture}
-\baselineskip=8pt
-
-\path[fill=gray!20] (0,0) rectangle (10.5,2);
-\path[fill=gray!50] (0,2) rectangle (10.5,4);
-\path[fill=gray!20] (0,4) rectangle (10.5,6);
-
-\draw (-0.3,1) node[rotate=90] {Stage 1}
-      (-0.3,3) node[rotate=90] {Stage 2}
-      (-0.3,5) node[rotate=90] {Stage 3};
-
-\draw[->] (0,0) -- (11,0) node[anchor=north] {$t$};
-\draw[-|] (0,0) -- (0,6.5) node[anchor=east] {};
-% Us
-\draw[ultra thick, ->] (0,0) -- (1,2) -- (3,2) -- (4,4) -- (6,4) -- (7,6) --
-(9.5,6);
-\draw[ultra thick, dashed, ->] (3,2) -- (9.5,2);
-\draw[ultra thick, dashed, ->] (6,4) -- (9.5,4);
-
-\draw (11,1) node[align=left, anchor=west]{\scriptsize pre-cognitive\\\scriptsize anthropomorphism}; %label
-
-\draw (11,3) node[align=left, anchor=west] {\scriptsize{projection of existing}\\\scriptsize{mental models}\\\scriptsize{\it (familiarity)}}; %label
-
-\draw (11,5) node[align=left, anchor=west] {\scriptsize{adapted mental
-model} \\ $\to$ \scriptsize{adapted interaction}\\\scriptsize{\it (anthropomorphic or not)}}; %label
-
-\draw[dashed,->] (1,0.1) to[bend right] (2,1.9)  node at (4.5,1) {\tiny{\it observation (shape, motion, sound)}}; %label
-
-\draw[dashed,->] (4,2.1) to[bend right] (5,3.9)  node[align=left] at (7.5,3) {\tiny \it observation (interactive behavior) \\ \tiny \it or short interaction}; %label
-
-\draw[dashed,->] (7,4.1) to[bend right] (8,5.9)  node[align=left] at (9,5)
-{\tiny \it contextualized\\ \tiny \it interaction}; %label
-
-\end{tikzpicture}
-%}
-\caption{The three cognitive stages of anthropomorphism: Stage 1 is the instinctive,
-sub-cognitive identification of living peers. {\it Empathy} is characteristic
-of this stage. After longer observation or short, non-contextualized interaction
-(typically, a lab environment), the user reaches Stage 2: the user projects a
-mental model he/she is already familiar with onto the robot. After longer {\it
-contextualized} interaction (typically, at home), the user enters Stage 3 of
-anthropomorphism: the user composes a custom mental model of the robot,
-based on experience. This leads to adapted interaction modalities, that may
-still be anthropomorphic, or not.}
-\label{fig:cognitivemodel}
-\end{figure}
-
-We propose three different cognitive stages (Figure~\ref{fig:cognitivemodel}), which are not mutually exclusive but overlap over time.
-Note that these three cognitive stages are related but do not exactly match the
-\emph{Initialization}, \emph{Familiarization} and \emph{Stabilization} phases
-introduced in our model of the dynamics of anthropomorphism.
-
-\subsubsection{Cognitive Processes and Stages\\}
-
-The main underlying cognitive process in anthropomorphism is understood as
-perceiving and reasoning about something non-human and unfamiliar based on one's
-representation of the familiar and well-known concept of being
-human~\citep{epley_when_2008}. This led us to interpret the phases of
-anthropomorphic interactions as parallel cognitive phases
-(Figure~\ref{fig:cognitivemodel}).
-
-The \emph{Stage 1} is the instinctive, pre-cognitive identification of living
-peers. Studies conducted by~\citet{rosenthal-vonderputten_experimental_2013},
-who investigated the neural correlates of emotional reactions of humans towards
-a robot, supports the idea that humans tend to anthropomorphize robots
-intuitively in this pre-cognitive way. {\it Empathy} is characteristic of this
-stage~\citep{rosenthalvonderPutten2013neural}.  It is also at this stage that
-automatic activation of the human's mirror neurons system  in response to
-viewing the robots action and human automatic emotional responses are
-contributing at a lower level to the intuitive anthropomorphization.
-
-The intuitive anthropomorphization in the cognitive Stage 1 might be characteristic of what \cite{takayama_perspectives_2012} calls the \textit{in-the-moment} perspective on agency with a robot compared to the \textit{reflective} perspective (see paragraph ``artifact-centered perspective'' in Section \ref{sec:anthropomorphism}).
-For instance, we reflectively
-might \textit{not} perceive agency in a social robot, but it can feel quite differently
-in the moment of interaction. \cite{takayama_perspectives_2012}
-argues that neglecting to separate reflective perspectives from in-the-moment
-perspectives of agency is one of the major sources of confusion when people talk
-and write about anthropomorphism. There seems to be a disconnection between what
-people consciously perceive and how they respond to stimuli that they may not
-consciously perceive. That means, in the initial phase of interacting with a
-novel device \textit{(initialization)} (see Figure \ref{fig:dynamics}) people might not respond consciously but
-rather mindlessly \citep{nass_machines_2000}, and in turn anthropomorphize more.
-Only after some time of
-\textit{familiarization}, they might respond in a more reflective manner (in turn, the tendency to anthropomorphize might decrease). This
-can be illustrated by the fact that people tend to deny interacting with
-computational systems as if they were people and yet they respond to computers
-in many ways that are remarkably similar to how they respond to people
-\citep{reeves_media_1996}. \cite{takayama_perspectives_2012} also applies a
-cognitive viewpoint on the two different perspectives of in-the-moment \vs
-reflective to illustrate differences. She states that in-the-moment perceptions
-of agency are largely shaped by bottom-up perceptual processes, evoking very
-immediate responses (\eg to the cues emitted by the artifact's design (``artifact-centered perspective''). In contrast, according to Takayama,
-reflective perceptions are more often shaped by top-down processes because of
-the nature of reflective thought.
-
-%We suggest that the human's mirror neuron system is contributing to
-%anthropomorphism by  allowing for a mapping of the robot's goal-directed
-%actions into the human own motor repertoire \cite{Gallese1998, Wolpert2003,
-%cullen2013individual}.
-
-%mediated by the motor and emotional resonnance mechanisms at the neuronal level.
-
-After a longer observation period (typically including complete action sequences
-of the robot) or short interaction (touching, short talk like greetings), we
-suggest the human reaches the cognitive \emph{Stage 2}: in this phase, the human
-starts building a behavioral and cognitive model of the robot that would support
-both the observed and imagined capabilities of the robot.  The \emph{familiarity
-thesis}~\cite{hegel_understanding_2008} supports the idea that the human first
-projects onto the robot mental models of similar agents he/she is already
-familiar with (ranging from animals to human adults, to pets and children). We
-hypothesize that the nature of the projected mental model, as well as how deep
-the human engages in this projection, might be driven by the same parameters as
-we mentioned for the \emph{initial capital of anthropomorphism}
-(section~\ref{sec:ica}).  At this stage the human might also change his attitude
-towards the robot, paying more attention to social cue than to low-level
-behavior which may reinforce the resonance mechanisms.
-
-The cognitive \emph{Stage 3} is reached after a \emph{contextualized} interaction.
-A \emph{contextualized} interaction is \emph{explicitly purposeful} (the purpose
-of the interaction, be it purely entertainment, is explicit and conscious to the
-human), and takes place in an environment that fosters a stronger cognitive (and
-possibly affective/social) commitment from the human in the interaction
-(typically, at home). During this interaction, the human iteratively restates
-and reshapes his/her behavioral and mental model of the robot (\emph{How does
-the robot react to such and such situation/input?  What does the robot know
-about me? About itself? About our environment? What can the robot learn?}, etc.).
-
-This mental process depends on the human understanding of the robot's
-inner working, as well as his/her own tendency to anthropomorphize (the
-\emph{personality} in ICA factor), but at this
-stage, the \emph{perception} of the robot (its shape for instance) and its
-intended \emph{purpose} play a less important role. It is mostly a human-centric
-process.  The result of this third phase would be an iteratively adapted
-cognitive model of the robot. It is also at this last stage that the human might have a
-modified tendency to anthropomorphize, because he/she has built a full cognitive
-model of the robot. Consequently, the human would now be able to attribute appropriate internal states to the robot
-through his/her theory of mind.
-
-\paragraph{Relation to the dynamics of anthropomorphism\\}
-
-As mentioned before, the three cognitive stages proposed here do not match with the three phases in the \emph{Dynamics of Anthropomorphism}.
-In particular,
-the cognitive Stages 1 and 2 are both included in the \emph{initialization} phase
-of the anthropomorphism model. Sub-cognitive anthropomorphism typically
-\emph{initiates} the novelty effect by rapidly engaging the human in the
-interaction through an initial projected agency, whereas cognitive Stage 2
-(projection of familiar mental models) supports the novelty effect by inducing
-beliefs that the robot is set up with possibly complex cognitive abilities.
-
-The cognitive Stage 3 also overlaps with the \emph{Familiarization} phase: as
-the human gets used to the robot, he/she restates and adapts its
-cognitive model of the robot by iteratively reshaping pre-existent, familiar
-models until it provides a satisfying support to explain and justify the
-observed robot behavior.
-
-A \emph{stable level of anthropomorphism} is reached when the adaptation process
-depicted in the cognitive Stage 3 reached a stable state, \ie the user's
-experience with the robot is correctly supported by the cognitive model he/she
-has built.
-
-Another way to think of the three proposed cognitive stages is to relate them to the \textbf{user experience} which is characteristic of these three stages.
-For instance, \cite{norman_emotional_2003} characterizes  three user experience dimensions (related to emotional attachment), which occur when people use or see a product for the first time: \emph{(1)} the \emph{visceral level}, which is the first impression of a product based on its experience; at this level people do not think about a product but make spontaneous judgments; \emph{(2)} the \emph{behavioral level}, in which people use and experience the product, appraise its functions, and consider aspects such as usefulness and usability; \emph{(3)} the \emph{reflective level}, in which consciousness takes part in the process, and past experiences are taken into account.
-In a study which was carried out in a shopping mall, \cite{weiss_i_2009} explored the emotional attachment during first time reactions of children and adults with the robotic dog AIBO.
-The authors also argue that it is important to understand the long-term development of people's social bonds to robots.
-
-\subsection{Role of disruptive behaviors}
-\label{sec:disruptive}
-
-A cognitive interpretation of anthropomorphism also allows to better interpret
-the role of unexpected robot behaviors, that are \emph{disruptive} with respect
-to the cognitive process of building a mental model of the robot.
-
-Common observation of naive people (children or adults) interacting with robots
-shows that unexpected behaviors of the robot can have a notable impact on
-interaction. This is supported by the results from~\citet{Waytz2010}, mentioned in section
-\ref{sec:cognitive-expl}, that show that people attribute more easily
-anthropomorphic features to artifacts when they have unpredictable behaviors.
+After some searching, M.
+found the robot stuck under the sofa and wondered why this had happened.
+\end{quote}
+
+The special anthropomorphic effect in this scenario is that usually, the father did not talk to the robot or praise it.
+However, now that the robot did something unexpected (it was not at its usual place), he started wondering about its `intention' and directly asked Roomba for its reason to not \textit{``go to sleep''}.
+
+Disruptive robot behaviors can have a notable impact on how people interact with the robot (and trust it).
+Related to anthropomorphism, \cite{Waytz2010} showed that people attribute more easily anthropomorphic features to artifacts when they display some unpredictable behaviors.
 Also \cite{short_no_2010} found that variations in a robot's behavior (such that it is unexpected) influence people's attribution of mental states and intentionality to a robot.
@@
 
-During a normal interaction with the robot, the user iteratively refines his/her
-own model of the behavior of the robot. As explained in previous sections, as
-the user improves his/her model of the robot's actions, he/she also improves the
-ability to predict the actions and thus, the user tends to anthropomorphize
-less.
-
-We emit the hypothesis that an unexpected robot behavior might lead the user to
-suddenly restate his/her behavioral model of the robot and will temporarily lead
-to an increase or decrease of the level of anthropomorphism (depicted by the
-spikes in Figure~\ref{fig:dynamics}).
-
-%\begin{figure}\footnotesize
-%    \centering
-%    \begin{tabular}{  >{\centering\arraybackslash}m{2cm} | >{\centering\arraybackslash}m{2cm} | >{\centering\arraybackslash}m{2cm} }
-%     & Unplanned by the robot & Planned by the robot \\ \hline
-%    Perceived as non-intentional & case I  & case IIIa  \\ \hline
-%    Perceived as intentional &  case IIIb & case II 
-%    \end{tabular}
-%\caption{
-%    Behaviors of the robot that are unexpected by the user may be intentional
-%    (the robot has planned the behavior) or not (typically, a failure:
-%    misdetection, bug,...). Independently of that, the behavior may be
-%    \emph{perceived} by the user as intentional or not.}
-%\label{fig:perceptionUnexpectedBehavior}
+Related to this, the \textit{transparency} of the robot's actions to the user is crucial \citep{kim_who_2006}.
+The user may perceive the disruptive behavior as a failure of the system (and call the robot \textit{``stupid''} once or twice but subsequently stop using it at all).
+But what if the robot states the failure explicitly and tries mitigate it \citep{lee_gracefully_2010}?
+Then, the user may hypothesize that the robot has \textit{introspective} capabilities (it can reflect on its own internal state), which can promote anthropomorphism.
+Alternatively, the robot may also state something like \textit{``I do not want to go over there, I always get stuck on the carpet there.''} In such case, the disruptive behavior is perceived as intended by the robot, which will most likely increase anthropomorphism.
+
+On a more abstract level, a central question here is whether it is possible to sustain long-term interaction by making a robot more human-like or more social, so that people's tendency to anthropomorphize the robot is increased.
+We are rather critical regarding the anthropomorphic design of robots (and the overuse of it).
+Also, inducing anthropomorphism (especially on a higher level) may not always be good.
+
+\subsection{Ethical Considerations}
+
+Some higher levels of anthropomorphism can be similar to a user identifying him/herself with the robot or regarding it as a significant other.
+It is to some point up to the user to engage in such a lasting strong social relationship with a robot, however, we have to critically think about how much the design and the behavior of a robot should foster this.
+To what extent should the design of a robot encourage the user to lastingly attribute feelings or needs to it?
+Why should a machine even react to us as if it had emotions but only pretend and fake them?
+What happens as soon as a robot is considered a moral agent?
+\citep{sullins_when_2006}
+Engaging with a robot in a human-like / social way may be beneficial up to a certain point but there can be questionable implications, too.
+\cite{robins_robots_2005} discuss the use of socially interactive robots in contexts involving care, rehabilitation or therapy, and \cite{tanaka_care-receiving_2010} point to the up- and downsides of using social robots (and technology in general) in educational contexts.
+For instance, over reliance and dependence on robots are two critical aspects that the authors mention.
+We do not discuss these implications in detail here but we want to raise awareness that anthropomorphism holds ethical issues.
+Anthropomorphism including human-like interactions with a robot, may not be inherently good or desirable and should not automatically be seen as a solution to enhance long-term engagement between human users and robots.
+The message of our conceptual model of the dynamics of anthropomorphism is not that a sustained high level of anthropomorphic effects is good.
+It may not even be desired.
+After all, it remains questionable to what extent sustained anthropomorphic interactions between humans and robots can be favored.
+We need to rethink carefully the consequences that emotional and social bonds between humans and robots can have.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+%
+%
+%		CONCLUSIONS
+%
+%
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Conclusions}
+\label{sec:conclusions}
+
+In this paper, we presented a cognitive and psychological viewpoint on anthropomorphism, what we believe can offer relevant extensions to our understanding of anthropomorphism in HRI.
+Regarding anthropomorphism as a social phenomenon that arises in an interaction, we formulated the following three suggestions:
+\begin{enumerate}
+\item \textbf{Anthropomorphism is based on multiple factors.} The three main factors that constitute anthropomorphism, are characteristics of the human $H$, characteristics of the robot $R$, and characteristics of the context of use $C$.
+A temporal dimension is taken into account by the \textit{interaction history} $t$, which leads to anthropomorphism being also a dynamic phenomenon (see point 3).
+\item \textbf{Anthropomorphism is multi-layered.} Applying a cognitive viewpoint on anthropomorphism, there exist \textit{lower and higher levels} of the phenomenon.
+On one hand, the level (it may be a continuum rather than discrete levels) depends on one how typical or uniquely human the attributed characteristics are, and how much the mental model that the user build of the robot overlaps (or is inspired by) the mental model he/she has of another human.
+As an outcome of this, three different \textit{cognitive stages} have been identified.
+These stages reflect the implicated cognitive depth of the anthropomorphic effect.
+\item \textbf{Anthropomorphism is dynamic.} Looking at how experience and interaction evolve over time, we developed a conceptual model of the dynamics of anthropomorphism, which states that there is a non-linear relationship between the observable \textit{anthropomorphic effects} $A_t$ (a user's tendency to anthropomorphize a robot) and the \textit{interaction history} $t$ (taking into account the actual time the user has spent interacting with the robot for real or imagined).
+The shape of the hypothesized curve starts with the so-called \textit{Initial Capital of Anthropomorphism} ($ICA$) that can be measured as a pre-variable, based on the three main factors (see point 1).
+With a considerable interaction history, the curve approaches the so-called \textit{Stabilized Level of Antrhopomorphism} ($SLA$).
+How the curve evolves in between these two values is flexible and unique to each user, robot, and context.
+We generally assume an increase of \textit{anthropomorphic effects} driven by the \textit{novelty} of the robot, followed by a decrease of $A_t$ as the user \textit{familiarizes} him/herself with the robot and with using the robot.
+\end{enumerate}
+
+\subsection{Implications}
+
+Overall, if we agree that \textbf{anthropomorphism arises in an interaction}, this requires studying the phenomenon as such, both in terms of evaluation scenarios, and in terms of measurements.
+Regarding \textbf{evaluation scenarios}, we suggest to go beyond using videos and pictures of robots, but to use real interaction scenarios (possibly long-term, \eg one interaction spanning over an extended period of time, or several sessions so to have repeated interactions).
+In terms of \textbf{measurements}, we suggest to go beyond using rating scales, but to apply a more holistic approach that regards not only participants perception of the robot but also the way they interact with the robot.
+For this, we proposed a so-called \textit{Anthropomorphism Index} $AntX$ that can be used both as a measurement tool and as a value that reflects how much a user anthropomorphized a robot in a given situation.
+To take into account the dynamics over time, we propose to measure $AntX$ at several points, as a pre-variable (focusing on user expectations, previous experience, robot design), in-situ variables (focusing on behavioral aspects, interaction, variations of robot behavior) and post-variables (perception and acceptance rating of interaction).
+
+\subsection{Limitations}
+
+We have proposed that the user's familiarization with the robot is a significant factor that influences how anthropomorphism evolves over time.
+We assume a general \textit{decrease} of anthropomorphic effects as the user gets familiar with the robot, and we applied a cognitive viewpoint to legitimate this.
+However, there exist opposite interpretations.
+\cite{eddy_attribution_1993} state that familiarization and more interaction with an agent \textit{increase} the tendency to anthropomorphize.
+Similarly, \citep{duffy_anthropomorphism_2003} reports that several psychological experiments and HRI studies showed that familiarity with the system eases social acceptance and tends to \textit{increase} people's tendency to perceive human-like characteristics in the system.
+We acknowledge that our conceptual model is an idea that needs to be verified, so to see whether our hypotheses can hold.
+In particular, the effect of the user's familiarity with the robot, and the role of disruptive robot behaviors needs to be studied in more detail and over extended periods of time.
+
+While subject to discussion and further refinements and extensions, we hope that this contribution consolidates the scientific grounds of anthropomorphism and provides support for a better understanding of anthropomorphism and its role in long-term acceptance of robots in human environments.
+
+\section*{Acknowledgments}
+This research was supported by the Swiss National Science Foundation through the National Centre of Competence in Research Robotics.
+
+\bibliographystyle{frontiersinSCNS&ENG} % for Science and Engineering articles
+%\bibliographystyle{frontiersinHLTH&FPHY} % for Health and Physics articles
+\bibliography{dynamics-anthropomorphism}
+
+%\section*{Figures}
+
+%%% Use this if adding the figures directly in the mansucript, if so, please remember to also upload the files when submitting your article
+%%% There is no need for adding the file termination, as long as you indicate where the file is saved. In the examples below the files (logo1.jpg and logo2.eps) are in the Frontiers LaTeX folder
+%%% If using *.tif files convdynamics-anthropomorphismert them to .jpg or .png
+
+%\begin{figure}
+%\begin{center}
+%\includegraphics[width=3.5cm]{logo2}% This is an *.eps file
+%\end{center}
+% \textbf{\refstepcounter{figure}\label{fig:02} Figure \arabic{figure}.}{ Enter the caption for your figure here.  Repeat as  necessary for each of your figures }
 %\end{figure}
 
-\begin{figure}
-    \centering
-    \includegraphics[width=0.75\columnwidth]{un-expected-behavior.pdf}
-    \caption{Behaviors of the robot that are unexpected by the user may be intentional
-    (the robot has planned the behavior) or not (typically, a failure:
-    misdetection, bug,...). Independently of that, the behavior may be
-    \emph{perceived} by the user as intentional or not.}
-
-    \label{fig:perceptionUnexpectedBehavior}
-\end{figure}
-
-When talking about \emph{unexpected robot behaviors}, several distinct cases
-must however be considered, summarized in
-Table~\ref{fig:perceptionUnexpectedBehavior}.
-
-If the unexpected behavior is not planned, and perceived as such by the human
-(case I), the human can interpret that the robot is able to fail. If the robot
-explicitly states its failure (for instance, by saying ``I'm lost!''), the
-behavior is then called \emph{transparent} \citep{kim_who_2006}, and the user may hypothesize that the
-robot has \emph{introspective} capabilities (it can reflect on its own internal
-state), which may lead to higher anthropomorphic projections.  On the
-contrary, if the robot shows no sign of recognizing its own failure, the user
-may ascribe a lower level of anthropomorphism to the robot.
-
-In case II, the robot voluntary executes a behavior that is unexpected by the
-human, and the human perceives it rightfully as an \emph{intentional} behavior.
-For instance, the human asks the robot to go somewhere, and the robot refuses,
-saying ``I do not want to go there''. In that case, we expect to see an increase
-of attribution of anthropomorphism due to the human ascribing intentionality to the
-robot.
-
-Case IIIa and IIIb correspond to misinterpretations of the robot behavior. Case
-IIIb may actually lead to an increased level of anthropomorphism since the human
-will (wrongfully) attribute intentionality to the robot, while case IIIa is
-expected to lead to a lower anthropomorphism level.  However, in those two
-cases, the next occurrence of an expected behavior, if correctly interpreted
-(case I or II), is likely to lead to stronger effects due to a larger $\delta$
-between expectations and actual observed behavior.
-
-%% experience -> unexpected behavior should not impact the interaction child-robot BEFORE the theory of mind is established!
-
-%\subsection{\emph{In-the-moment} versus \emph{Reflective} perspectives}
-%
-%\fxwarning{SL: Bridge + integration in the section 4 TDB}
-%
-%\hl{(we actually assume that
-%anthropomorphism can be radically changing and be a very spontaneous
-%"reaction".)}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-%
-%
-%				DISCUSSION + FUTURE WORK
-%
-%
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% JULIA & SEVERIN: how to measure / quantify anthropomorphism ...
-% CLAIRE: FMRI study idea
-
-\section{Discussion}
-\label{sec:discussion}
-
-The model of anthropomorphism we propose is still a work in progress. In
-particular, its implications regarding the design of (social) robots and
-human-robot interaction are still to be refined but we hope this article helps encourage an open dialogue between those who do research of anthropomorphism.
-
-Coming back to our two main hypotheses, on one hand we investigated how far anthropomorphism is based on multiple factors, namely, the design of the robot, the personal characteristics of the human user, and the context / situation in which the robot is used.
-We elaborated this hypothesis by reviewing literature from various related disciplines.
-Based on the outcomes of this, on the other hand, we proposed a model of the \emph{Dynamics of anthropomorphism}.
-We offered a cognitive interpretation of this model, as well as illustrations from our own previous work.
-However, our model has limitations, for instance, regarding the general effect of time and familiarization on anthropomorphism. We will discuss this in the following section.
-
-\subsection{Effect of time / familiarization on anthropomorphism}
-
-We have proposed that time, or in other words, the user's familiarization with the non-human agent, models how anthropomorphism evolves over time.
-Our general assumption is that with continued interaction, and in turn growing user experience, the system becomes more predictable and consequently, the user's need to anthropomorphize the agent decreases.
-We would like to discuss this suggestion here.
-
-With \textit{time} as a factor, we
-referred to long-term interaction with the robot, which is related to what has been
-described as \textit{novelty effect} but also accounts for the user getting used
-to the robot.
-Several studies described that after some time users interacted less with the robot or lost interest in it.
-Sustaining long-term interaction is one of the main challenges that robots with applications in daily life contexts face.
-Our question is that, if we would like overcome the novelty effect, how far does the robot's behavioral complexity play a role?
-Should the robot vary its behavior and behave unexpectedly from time to time?
-
-Most experiments, and even more when they investigate
-long-term interactions, are carried out with robots exhibiting relatively simple
-behaviors. In our model, the maximum level of anthropomorphism \AntMax is
-reached with the novelty effect, and then decreases. A natural question
-is whether we can design robots such that \AntMax remains high, possibly higher
-than $\ant[t_{novelty~peak}]$ (note that to know if sustaining strong
-anthropomorphic interaction is desirable is entirely another question, see Section \ref{sec:ethics}).
-
-Intuitively, the behavioral complexity of the robot, and in particular, the ability
-for the robot to evolve over time and \emph{adapt its behavior to the user} as the user
-familiarizes his/herself with the robot (\ie, \emph{co-familiarize}), seems to play a
-key role.
-
-Our model is based on the assumption that anthropomorphism tends to decrease with the user becoming more familiar to the robot.
-We explain this by the general motivation to anthropomorphize an agent which might be difficult to understand
-(in its functionality or behavior, for instance). In turn, a user might ascribe
-intentions or emotions to the system because the system's output was unexpected
-for the user, however he/she still wants to make sense of it. Consequently, we estimate that when the user has
-familiarized herself/himself with the system, thus reached the point of when
-the system is usable and explainable, the tendency to anthropomorphize
-decreases.
-
-However, there exist views that suggest just the opposite, namely, that familiarization and more interaction with an agent \textit{increase} the tendency to anthropomorphize \citep{eddy_attribution_1993}.
-Similarly, \cite{duffy_anthropomorphism_2003} reports that several psychological experiments and human-robot interaction experiments showed that familiarity may also ease social acceptance and even tend to \textit{increase} people's tendency to anthropomorphize.
-
-Consequently, we have to accept that our model of the \emph{Dynamics of Anthropomorphism} needs to be verified, to see how far our hypotheses can hold.
-In particular, the effect of the user's familiarity with the system needs to be studied over a longer period of time.
-
-%\begin{enumerate} 
-%\item ~A person's tendency to anthropomorphize a robot
-%    is based on several factors, including (but not limited to) (1) the
-%    design of the robot, (2) the personal characteristics of the human user,
-%    and (3) the context and situation of use. For instance, a social context
-%    and purpose of the robot increase anthropomorphism: \textit{anthropomorphism
-%    as a multi-factor phenomenon}.
-%
-%\item ~A person's tendency to anthropomorphize a robot
-%    evolves in a non-linear way over time and with growing experience that the
-%    person has with the robot. For instance, a more experienced user will
-%    perceive the robot as more familiar and predictable, and in turn
-%    anthropomorphizes the robot less: \textit{anthropomorphism as a dynamic
-%    phenomenon}.
-%
-%\end{enumerate}
-
-%
-%Smart innovative devices, such as personal domestic robots, might demand from a
-%human user spontaneous usage of an unfamiliar system. Such situations will
-%require that a user should be able to build up a mental model quickly, which
-%particularly holds for novice users \cite{schmitz_concepts_2011}.
-
-\subsection{General observations}
-
-By adopting both a cognitive and a dynamic perspective on the anthropomorphic
-bonds that establish between a robot and a human during an interaction, some
-observations can be raised.
-
-For instance, we propose that the human \emph{adapts} iteratively to the robot
-by restating its cognitive model of the robot. Could our two models be
-conversely relied on to have the robot itself iteratively adapting its
-behavior? In particular, we hypothesize that the so-called novelty effect
-represents a peak in anthropomorphic manifestations, followed by mostly
-deception-driven refinements of the cognitive behavioral model of the robot.
-Could we imagine that the robot pro-actively \emph{verbalizes} its own limits,
-in a timely manner (likely before the end of the novelty effect). And how would
-this affect the cognitive models built by the human?
-
-One related question we plan to elaborate on is the effects of \emph{mutual
-explicitation of the mental model of the other agent}: a human and a robot
-interact on a given task, and after a while, we interrupt the task and ask each
-of the agents to explicit the mental model it has built of its partner
-(emotional state, beliefs, intentions, etc.). Depending on the cognitive stages
-the two agents are in, we may expect varying accuracy levels in the produced
-mental models.
-
-Another question raised by these models relates to their transposition to
-human-human interaction: while concepts like \emph{novelty effect} are not
-directly meaningful when analyzing human-human interaction, insights from
-cognitive sciences (and in particular social psychology) regarding how we, as
-humans, cope with unexpected behaviors from peers, or on the dynamics of mental
-model refinements, could bring interesting perspectives with possible
-applications to better manage long-term human-robot interactions.
-
-\subsection{Measuring anthropomorphism}
-\label{sec:measuring}
-
-%\fxwarning{To be completed/rephrased into a discussion}
-
-%Also, the methods and measurements applied to study anthropomorphism appear insufficient, when applying a holistic understanding of anthropomorphism emerging from an interaction between a human user and a robot, for instance.
-Our point here is that to study a phenomenon as complex as anthropomorphism, we believe that one needs to take into account many factors (see Section \ref{sec:multi-factors}), besides looking at the human-like design of the artifact.
-
-With this extended understanding of anthropomorphism being determined by multiple factors and showing dynamics over time, it also becomes questionable if the metrics and techniques that are currently used to measure anthropomorphism are sufficient.
-We would like to discuss two issues: the scenario in which anthropomorphism is measured, and how, with which means it is assessed.
-
-One needs to keep in mind that anthropomorphism arises in an interaction.
-We believe that as such, anthropomorphism can be better understood when studied and measured in a real, direct human-robot interaction compared to a mediated interaction.
-In a direct interaction scenario one could also take the human's behavior into account, as it seems to reflect an anthropomorphic interaction \citep{krach_can_2008,hegel_understanding_2008,weiss_i_2009}.
-Of course, the scenario and measurements one uses depend on the research questions, so a direct human-robot interaction might not always be preferred.
-
-However, most of the
-experiments that investigate anthropomorphism in HRI are conducted in
-controlled lab-settings during a short-term scenario.
-For instance, pictures or videos of different robots are shown to human subjects who subsequently fill in a questionnaire, to assess how far the different types of robots were perceived human-like.\footnote{It can already be critical to not indicate the height / size of a robot when it is pictured or presented in a video.
-We cannot assume that without any point of reference, lay people estimate correctly the height of ASIMO or Nao, for instance, they might think these humanoid robots are the same size as a Barbie doll.
-Also, when showing a picture, the movements, behaviors, materials of a robot, and so forth are totally disregarded.
-However, these aspects are also crucial features of a robot, impacting how human-like it appears.}
-We think that such
-experimental settings have limitations for studying a social phenomenon like
-anthropomorphism. The critical question is: can anthropomorphism really be measured in a post-interaction closed questionnaire or by rating scales?
-Findings might possibly lead to interpretations that would not be generalizable to natural settings or real interaction scenarios (which is always an issue in social science research).
-
-Regarding the second issue, how and with which means anthropomorphism is measured, one of the view existing tools to do so is 5-item anthropomorphism part of the Godspeed questionnaire \citep{bartneck_measurement_2008}.
-On 5 point semantic differential scales, people are asked to rate the following constructs: fake - natural, machinelike - humanlike, unconscious - conscious, artificial - lifelike, moving rigidly - moving elegantly.
-The critical point that we see with this is that ``human-likeness'' itself is complex and manifold.
-Being such an abstract concept, instead of asking the vague question, whether a robot is human-like or not, \cite{kahn_jr._robotic_2006} suggest to ask for more concrete constructs that are typical or unique of the concept of ``human-likeness''.
-For instance, \cite{ruijten_introducing_2014} propose a 25-item questions to measure various concrete aspects of human-likeness.
-Consequently, anthropomorphism can be modeled along a scale that accounts for lower and higher levels of it.
-
-Still, we also feel that measuring anthropomorphism (or social engagement with a robot) is challenging because the phenomenon is partially
-unconscious, its mediation is largely subject-dependent, and we found the
-phenomenon generally difficult to verbalize for users.
-
-To reduce subjectivity and still accurately account for psychological effects,
-it appears necessary to interleave quantitative and qualitative assessments of
-anthropomorphic effects.
-
-We present in this section the methodology and techniques that we used to
-assess anthropomorphic projections in the child-robot interaction study, called the Domino study (see Section \ref{sec:field-results}, and Figure \ref{fig:ranger}).
-
-\paragraph{Qualitative and quantitative assessment of anthropomorphism in human's behavior\\}
-
-Anthropomorphism can possibly be observed in how humans behave toward a non-human agent (social human-like engagement).
-Based on video recordings of the Domino experiment, we acquired both quantitative and qualitative behavioral data that reflects anthropomorphism.
-
-Quantitative data are
-acquired by systematic annotations of specific types of actions in the video records of the interaction. Six classes of interactions were identified as reflecting
-active commitment and/or an anthropomorphic interaction of the user: gestures toward the robot, touching the robot, direct talk to
-the robot, showing something to the robot, mistreating the robot (\eg kicking it), and looking at the experimenter because worried by the robot's behavior.
-
-By considering the number of occurrences, the duration, and consequently the frequency of these types of interaction, we can make statements of how far the robot is anthropomorphized in an interaction (based on quantitative data).
-
-We assessed anthropomorphic interactions qualitatively by looking at specific instances of human-social cues in the human's behavior, such as: facial expressions, observable emotional reactions (\eg surprised, high pitch voice or shouting to the robot), eye-contact with the robot, turn-taking gestures, greeting (waving) gestures.
-These are just suggestions of actions that might reflect anthropomorphism.
-These actions partly overlap with the quantitative assessment, however it is generally advisable to combine the two.
-
-\paragraph{Qualitative assessment of anthropomorphism when verbally referring to the robot (reflection)\\}
-
-The main tools for
-qualitative measurement of anthropomorphic effect are questionnaires and semi-structured interviews. We have
-explored both rating-scales in a questionnaire, and open questions in an interview.
-In the Domino study, interviews were transcribed and participant's answers to the key questions that were assessing an anthropomorphic projection onto the robot, were analyzed.
-For instance, one question to see how far children would ascribe moral standing to the robot was \emph{``If you had this robot at home, and you were to leave for 2 weeks of holidays, would it be ok to leave the robot alone at home?''}.
-A point for anthropomorphism was counted, when the participant's answer indicated an anthropomorphic view of the robot.
-This process led to a ``qualitative score'' that reflects how far the robot is anthropomorphized.
-We used the following constructs to measure how far the robot is perceived as a human-like agent:
-
-\begin{itemize}
-    \item ~Spontaneously ascribe inner states, {\it eg. robot is
-        hungry, tired}
-    \item ~Ascribe ``own will'', {\it eg. robot could leave room by itself, does not
-        always obey, could do a b\^{e}tise...}
-    \item ~Describe robot as friend
-    \item ~Ascribe cognitive abilities, {\it eg. robot is able to see,
-        able to hear}
-    \item ~Belief robot has feelings, {\it eg. robot can be happy or sad}
-    \item ~Give anthropomorphic explanation for
-        \begin{itemize}
-            \item ~Why robot can (not) leave room alone {\it eg. it would be sad when left alone}
-            \item ~Misbehavior {\it eg. robot wants to make a tour, doesn't
-                like to play any longer}
-        \end{itemize}
-\end{itemize}
-
-Some of these questions were taken from previous work done by \cite{kahn_jr._robotic_2006} an \cite{weiss_i_2009}.
-In both studies, both questionnaires and an analysis of behavior were used to assess children's and adult's engagement with, and perception of the robot.
-This seems to be a promising approach to investigate anthropomorphism, as it is also possible to combine quantitative and qualitative techniques.
-
-\subsection{Ethical aspects of anthropomorphism and human-like form of robots}
-\label{sec:ethics}
-
-% our message kind of is that it would be favorable to sustain anthropomorphism over 
-% extended periods of time ... however, this is ethically questionable, when thinking 
-% of emotional bonding with an artificial agent, etc. --> we sould elaborate on this a % bit
-
-After all discussion, there remains the question how far a sustained anthropomorphic (human social) interaction between a human and a non-human can be favored, regarding ethical aspects.
-We need to rethink carefully the consequences that emotional bonds between humans and robots can have.
-They might be beneficial on one hand but can also hold negative implications.
-How far should a robot's design encourage us to lastingly project feelings or intentions to it?
-Why should a machine even react to us as if it had emotions?
-Can this be the reality we want to live in?
-What happens as soon as the artificial agent is considered a \textit{moral agent} \citep{sullins_when_2006}?
-Also, the use of \textit{socially interactive robots} in
-contexts involving elderly care or in rehabilitation and with autistic children is a controversially discussed topic 
-\cite{robins_robots_2005}. Do we want robots to comfort us; robots that make us eventually even falling in love with them?
-The anthropomorphic design of robots is critical. Why do we even need this? The HRI / robotics community needs to discuss these and other questions.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-%
-%
-%				CONCLUSIONS
-%
-%
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% JULIA & SEVERIN
-
-\section{Conclusion}
-\label{sec:conclusion}
-
-Anthropomorphism is a social phenomenon which seems to be natural on one side
-and very complex on the other side. It is a mechanism within oneself that makes
-a human observer think and treat a non-human agent as if it would have some
-human (social) characteristics, and ascribe to it intentions, emotions, or
-thoughts, for instance. Understanding the reasons and modalities of
-anthropomorphism is thus of prime importance to build a successful and lasting
-human-robot interaction.
-
-Based on our previous (and on-going) work, we hypothesized that there are qualitative differences and dynamics over time
-in how humans relate to different types of robots. More concretely, we described
-that people's perception of human-likeness in a robot and in turn their
-human-social engagement with a robot is based on four main factors: (1) the (anthropomorphic) design of the robot, (2) individual characteristics of the human user, (3) the context of use / interaction, and (4) the interaction history (time factor).
-We further suggested
-that people's tendency to anthropomorphize a robot is likely to change over time with
-growing experience of the user with the system.
-
-To formalize the variances in anthropomorphism, we
-proposed a model that we call \textit{Dynamics of Anthropomorphism}.
-
- We introduced the concepts of
-\emph{initial capital} and \emph{stabilized level of anthropomorphism} as compound
-factors to characterize the profile of a given anthropomorphic (long-term) interaction.
-
-The article also discussed the cognitive correlates of anthropomorphism. We
-proposed three cognitive stages corresponding to successive
-refinements of the mental models of the robot that the user builds during the
-interaction. We showed how these stages relate to observable anthropomorphic
-effects, and how they evolve over time.
-
-While subject to discussion and further extensions, we hope that this
-contribution consolidates the scientific grounds of anthropomorphism, and
-provides support for a better understanding of long-term acceptance of robots in
-human environments.
-
-%With
-%this initial model, we would like to extend the current understanding of
-%anthropomorphism in robotics and human-robot interaction. This might in turn
-%lead to a discussion about the short- and long-term benefits and other effects
-%of the anthropomorphic design of robots and other artificial
-%agents.
-
-\section*{Acknowledgments}
-
-This research was supported by the Swiss National Science Foundation through the National Centre of Competence in Research Robotics.
-
-%\section{Bibliography}
-
-\bibliographystyle{frontiersinSCNS&ENG} % for Science and Engineering articles
-\bibliography{dynamics-anthropomorphism}   % name your BibTeX data base
+% \textbf{Figure 1.}{ Enter the caption for your figure here.
+Repeat as  necessary for each of your figures.}\label{fig:01}% If you don't add the figures in the LaTeX files, please upload them when submitting the article.
+
+%%% Frontiers will add the figures at the end of the provisional pdf automatically %%%
+
+%%% The use of LaTeX coding to draw Diagrams/Figures/Structures should be avoided. They should be external callouts including graphics.
 

### 2014-11-07 paper.tex
Cleaning up the source: wrapping + removed comments
No change in the content (hopefully)

--- 2014-04-07 paper.tex
@@
-%\documentclass{frontiersENG} % for Engineering articles
 \documentclass{frontiersSCNS} % for Science articles
-%\documentclass{frontiersMED} % for Medicine articles
-%\documentclass{frontiersFPHY} % for Physics articles
-
-%\usepackage[utf8x]{inputenc}
-%\usepackage[T1]{fontenc}
-
-%\usepackage[english]{babel}
 
@@
 
-% Leave a blank line between paragraphs in stead of using \\
-
 \copyrightyear{}
@@
 
-\def\journal{Cognitive Science}%%% write here for which journal %%%
+\def\journal{Cognitive Science}
 \def\DOI{}
@@
 \def\keyFont{\fontsize{8}{11}\helveticabold }
-\def\firstAuthorLast{Fink {et~al.}} %use et al only if is more than 1 author
+\def\firstAuthorLast{Fink {et~al.}} 
 \def\Authors{Julia Fink\,$^{1*}$, S\'{e}verin Lemaignan$^{1}$, Claire Braboszcz$^{2}$ and Pierre Dillenbourg$^{1}$}
@@
 \extraAuth{}
-\topic{The Uncanny Valley Hypothesis and Beyond}% If your article is part of a Research Topic, please indicate here which.
+\topic{The Uncanny Valley Hypothesis and Beyond}
 
@@
 The Uncanny Valley hypothesis \citep{mori_uncanny_1970} proposes that human-like
-designs of objects and non-human agents can evoke both positive and negative feelings in the human observer / user. A positive valence reflects the experience of 
-emotional engagement with and feelings of empathy for the non-human agent
-\citep{cheetham_human_2011}. This in turn may lead to an effective (human-like and 
-human-social) interaction with the non-human agent, and increase people's acceptance of
-it. 
-%
-%However, at a certain point as the non-human agent
-%approaches but fails to closely resemble a human, the evoked valence in the
-%human user suddenly turns into a negative uncanny feeling of what
-%\cite{mori_uncanny_1970} describes as disgust and revulsion. This, in turn,
-%might lead to rejection of the non-human agent. The Uncanny
-%Valley hypothesis predicts that with further increasing the human-likeness of
-%the non-human agent such that it appears so realistic that it is not
-%distinguishable from a human but perceived to be human, the effect is again a
-%positive one, reflecting feelings and engagement that are similar as those
-%evoked by a human-human interaction. 
-%Of course, developers and designers of artificial agents
-%(\eg virtual characters, robots) try to exploit the positive effects of 
-%\textbf{anthropomorphic form} and avoid ``falling'' into this Uncanny Valley.
-%Consequently, there is a considerable research effort to
-%better understand the boundaries of anthropomorphic design and their effects
-%on the interaction and experience. To date, findings have been however
-%inconsistent \citep{cheetham_human_2011}.
+designs of objects and non-human agents can evoke both positive and negative
+feelings in the human observer / user. A positive valence reflects the
+experience of emotional engagement with and feelings of empathy for the
+non-human agent \citep{cheetham_human_2011}. This in turn may lead to an
+effective (human-like and human-social) interaction with the non-human agent,
+and increase people's acceptance of it.
 
@@
 Along this line, this article aims at fostering a better understanding of
-anthropomorphism (noted \Ant in this paper) in human-robot interaction 
-by considering the phenomenon
-as a whole. Robotics researchers often tend to believe that
-anthropomorphism only describes a static set of human-like features of a robot
-(like shape, speech capabilities, facial expressions, etc.). We refer to these
-characteristics as the \emph{anthropomorphic design} of the
-robot~\citep{fink_anthropomorphism_2012}, and propose that \emph{anthropomorphism} in 
-general refers to a \emph{social phenomenon} that emerges from the (real or
-imagined) \emph{interaction} between a non-human agent (\eg a robot) and a 
-human~\citep{persson_anthropomorphism_2000}. According to~\cite{epley_when_2008},
-anthropomorphism includes that the human perceives, for instance, emotional states, motivations, or 
-intentions in the non-human agent, and tends to ascribe those qualities to it.
-As such, the dynamic and
+anthropomorphism (noted \Ant in this paper) in human-robot interaction by
+considering the phenomenon as a whole. Robotics researchers often tend to
+believe that anthropomorphism only describes a static set of human-like features
+of a robot (like shape, speech capabilities, facial expressions, etc.). We refer
+to these characteristics as the \emph{anthropomorphic design} of the
+robot~\citep{fink_anthropomorphism_2012}, and propose that
+\emph{anthropomorphism} in general refers to a \emph{social phenomenon} that
+emerges from the (real or imagined) \emph{interaction} between a non-human agent
+(\eg a robot) and a human~\citep{persson_anthropomorphism_2000}. According
+to~\cite{epley_when_2008}, anthropomorphism includes that the human perceives,
+for instance, emotional states, motivations, or intentions in the non-human
+agent, and tends to ascribe those qualities to it.  As such, the dynamic and
 socio-cognitive dimensions of anthropomorphism are essential to understand the
@@
         \end{subfigure}
-    \caption{Usage and perception of the Roomba vacuum-cleaning robot over a 6 months period.
-Qualitative data suggest that people's activities related to the robot as well as their perception of the robot change over time.}
+    \caption{Usage and perception of the Roomba vacuum-cleaning robot over a 6
+    months period. Qualitative data suggest that people's activities related to
+    the robot as well as their perception of the robot change over time.}
     \label{fig:roomba}
@@
                 \includegraphics[width=0.75\textwidth]{ranger}
-                \caption{Interaction scenario of the \emph{Ranger} domino study: the robot toy box Ranger transports domino tiles between the two children}
+                \caption{Interaction scenario of the \emph{Ranger} domino study:
+                the robot toy box Ranger transports domino tiles between the two
+                children}
                 \label{fig:ranger-expe}
@@
         \begin{subfigure}[b]{0.48\columnwidth}
-            \includegraphics[width=\textwidth]{ranger-interactions-vs-qualitative-score}
-            \caption{We found a significant negative correlation ($p=0.048$) between the
-    number of interactions and the qualitative anthropomorphic projections. n = 13 groups}
+            \includegraphics[width=\textwidth]{correlation}
+            \caption{\emph{Engagement actions} vs \textit{subjective anthropomorphic
+                perception} evidence one cluster of
+                high-anthropomorphizers/low-interactors and another group of children who
+                interact more with the robot and anthropomorphize it less.}
             \label{fig:qualitative-score}
         \end{subfigure}
-        \caption{Children's interaction with Ranger, and their anthropomorphic projections onto the robot.
-Overall, large variations of both children's behavior and their perception of the robot were found but seemed to be correlated to each other.}
+        \caption{Children's interaction with Ranger, and their anthropomorphic
+        projections onto the robot. Overall, large variations of both children's
+        behavior and their perception of the robot were found but seemed to be
+        correlated to each other.}
     \label{fig:ranger}
@@
 
-%Based on an extensive literature review~\citep{fink_anthropomorphism_2012},
-%several field and lab studies previously mentioned, and insights from the
-%cognitive neuroscience, we propose to discuss anthropomorphism from three
-%complementary perspectives.
-
-First, by reviewing what anthropomorphism actually \emph{means}:
-besides an \emph{artifact-centered} understanding that explains anthropomorphism from the human-like design of the non-human artifact, it seems important to explicit the social component, namely a \emph{human-centered} understanding, of anthropomorphism.
-
-Second, we propose a model, called the \textit{Dynamics of Anthropomorphism} to understand how anthropomorphism evolves over time ~\citep{lemaignan2014dynamics}.
-These dynamics are non-monotonic, and effects like the
-\emph{novelty effect} play here a key role.
+First, by reviewing what anthropomorphism actually \emph{means}: besides an
+\emph{artifact-centered} understanding that explains anthropomorphism from the
+human-like design of the non-human artifact, it seems important to explicit the
+social component, namely a \emph{human-centered} understanding, of
+anthropomorphism.
+
+Second, we propose a model, called the \textit{Dynamics of Anthropomorphism} to
+understand how anthropomorphism evolves over time
+~\citep{lemaignan2014dynamics}.  These dynamics are non-monotonic, and effects
+like the \emph{novelty effect} play here a key role.
 
@@
 
-Further, we would like to investigate the link between the variances in anthropomorphism and the correlating cognitive states.
+Further, we would like to investigate the link between the variances in
+anthropomorphism and the correlating cognitive states.
 
@@
 
-%\begin{inparaenum}[\itshape 1)\upshape]
-
-The remainder of this article is organized as follows.
-According to the three perspectives that we take, 
-we first (in Section
-%\ref{sec:overview-studies}, we give a brief overview on the various studies that
-%we conducted to investigate anthropomorphism, namely \item the Roomba study,
-%\item the Forum study, \item the Ranger domino study. Next, Section
-\ref{sec:anthropomorphism}) aim to establish a common ground in the
-understanding of anthropomorphism. We review literature from several relevant domains and integrate the different explanations into an understanding of
-anthropomorphism as a multi-factor phenomenon.
-Based on this, Section~\ref{sec:our-ideas} introduces our initial model of the
-\textit{Dynamics of Anthropomorphism}. This model describes the variances
-and dynamics of people's tendency to anthropomorphize an artificial agent,
-such as a robot. 
-Then Section \ref{sec:cognition-neuroscience} presents a
-cognitive and neuroscience perspective on anthropomorphism to consolidate
-our considerations and the proposed model.
-This is followed by a discussion
-about the limitations of our approach (Section \ref{sec:discussion}) and the
-existing and alternative ways to measure anthropomorphism in human-robot
-interactions.
-Finally, Section \ref{sec:conclusion} concludes this article
-and offers starting points for further research on anthropomorphism and the
-effect of the human-like design approach in robotics.
-
-%\end{inparaenum}
-
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%
-%%
-%%
-%%		OVERVIEW ON OUR STUDIES
-%%
-%%
-%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-%\section{Studying anthropomorphism in HRI}
-%\label{sec:overview-studies}
-%
-%In this section we give a brief overview of the studies that we conducted to
-%investigate anthropomorphism in human-robot interaction. Note that it was not
-%the main purpose of these studies to analyze in detail the effect of different
-%dimensions human-likeness of a robot on the user's perception of and interaction
-%with the robot. Each of these studies were motivated also by other research
-%questions, and we encourage the reader to refer to our other main publications
-%about these studies for more details.
-%
-%
-%\subsection{Roomba study: how people live with a vacuum cleaning robot}
-%
-%We openly explored long-term interactions between human users and a domestic
-%service robot in a 6-months lasting ethnographic study~\citep{fink_living_2013}. 
-%We gave a commercially
-%available vacuum cleaning robot (iRobot's Roomba, see Figure
-%\ref{fig:aibo-roomba-ipad} middle) to nine households. 
-%%in the French speaking
-%%part of Switzerland. 
-%%The fairly diverse sample of households consisted of 2
-%%single homes, 1 couple, and 6 families with children in their home. In total,
-%%this summed up to 30 participants: 15 adults (26-71 years old, mean age 43.6
-%%years), and 15 children (6 months to 18 years old). During the 6 months, each
-%%household was visited 5 times to conduct interviews and make field observations
-%%in the households. Moreover, during several weeks, households were asked to fill
-%%in a diary to report the usage of the robot and other cleaning activities.
-%Hereafter, we refer to this study as the ``Roomba study''. It is one of very few 
-%long-term human-robot interaction studies in the domestic environment. 
-%In the following, we present findings in respect of two aspects: First, we
-%qualitatively describe what kinds of anthropomorphic interactions between
-%participants and the robot were observed and outline how these interactions
-%evolved over time.  Second, we present people's perception of human-likeness and
-%social capabilities of the robot and how this perception changed over
-%time.
-%
-%%\footnote{\hl{note that these two different kinds of data
-%%(behavior/interaction and perception) already show that we try to measure
-%%anthropomorphism from these two angles!}}
-%
-%%The main goal of this study was to explore how households live with a vacuum
-%%cleaning robot over an extended period of time. We wanted to analyze how the
-%%usage of and interaction with the robot evolve over time, and to identify
-%%adoption phases as well as factors that impact on the long-term acceptance of
-%%service robots in homes.
-%
-%
-%\subsubsection{Anthropomorphic interactions with the robot\\}
-%
-%It has been described in several previous studies of the Roomba that users tend
-%to engage in a variety of non-cleaning activities associated with the robot,
-%including, but not limited to, naming, ascribing personality and gender
-%\citep{forlizzi_service_2006,forlizzi_how_2007,krumm_my_2007,sung_domestic_2010}.
-%\cite{sung_housewives_2008} carried out a survey among 379 Roomba users to
-%investigate how common these activities are. The authors concluded that overall,
-%respondents had relatively low rates of treating Roomba as a living entity.  
-%Similarly, in our long-term study of the Roomba in homes, we found that only few 
-%people tended to interact in an anthropomorphic or human-social way with their 
-%vacuum cleaning robot and that this effect did not sustain. Overall, our data 
-%suggest that the anthropomorphic effect and the social
-%impact of a functional robot on a household are rather marginal.
-%%There were just few instances of people anthropomorphizing the robot and
-%%interacting with it in a human-social way. More importantly, overall, these
-%%anthropomorphic interactions with the robot did not last but seemed to be
-%%somehow related to the novelty of the robot.
-%
-%We categorized several interactions and actions with the robot as
-%anthropomorphic or human-social (in a broader sense). 
-%%Examples of what we categorized as somehow social and anthropomorphic
-%%(human-like) interactions with the robot include \textit{watching} the robot
-%%for fun, giving a \textit{demo} of the robot to guests / visitors, taking a
-%%\textit{photo/video} of the robot, \textit{personalizing} the robot, giving a
-%%\textit{name} to the robot, \textit{talking} to the robot using direct speech,
-%%\textit{playing} with the robot, and making \textit{adjustments} to the home
-%%due to the robot. 
-%Figure \ref{fig:roomba-activities} shows how many of the 9 households engaged
-%in these activities during the 6 months when the study was conducted. 
-%
-%%\begin{figure}
-%%    \centering
-%%    \includegraphics[width=0.5\columnwidth]{roomba-activities.png}
-%%    \caption{Activities with the robot over time, n = 9 households. This bar
-%%        chart shows how many of the 9 households carried out different kinds of
-%%        anthropomorphic / social activities with and related to the robot at 3
-%%        time points during 6 months. Activities include \texttt{watching} the
-%%        robot for fun, giving a \texttt{demo} of the robot to guests / visitors,
-%%        \texttt{personalizing} the robot, giving a \texttt{name} to the robot,
-%%        \texttt{talking} to the robot, \texttt{playing} with the robot.
-%%        Participants were asked to report on these activities at 3 time points
-%%        after the robot was deployed in their home: after 2 weeks, after 2 months,
-%%        and after 6 months.} 
-%%
-%%\label{fig:roomba-activities}
-%%\end{figure}
-%
-%\begin{figure}
-%        \centering
-%        \begin{subfigure}[b]{0.48\columnwidth}
-%                \includegraphics[width=\textwidth]{roomba-activities.png}
-%                \caption{Roomba activities}
-%                \label{fig:roomba-activities}
-%        \end{subfigure}%
-%        ~ %add desired spacing between images, e. g. ~, \quad, \qquad etc.
-%          %(or a blank line to force the subfigure onto a new line)
-%        \begin{subfigure}[b]{0.48\columnwidth}
-%                \includegraphics[width=\textwidth]{roomba-perception.pdf}
-%                \caption{Roomba perception}
-%                \label{fig:roomba-perception}
-%        \end{subfigure}
-%        \caption{\textbf{The Roomba study: Long-term interaction with a robot.\\}
-%    \textbf{a)} Activities with the robot over time, n = 9 households. This bar
-%        chart shows how many of the 9 households carried out different kinds of
-%        anthropomorphic / social activities with and related to the robot at 3
-%        time points during 6 months. Activities include \texttt{watching} the
-%        robot for fun, giving a \texttt{demo} of the robot to guests / visitors,
-%        \texttt{personalizing} the robot, giving a \texttt{name} to the robot,
-%        \texttt{talking} to the robot, \texttt{playing} with the robot.
-%        Participants were asked to report on these activities at 3 time points
-%        after the robot was deployed in their home: after 2 weeks, after 2 months,
-%        and after 6 months.\\
-%	\textbf{b)} People's perception of the robot over time, n = 15 participants.
-%    		This line chart shows how people's perception of the robot evolves over
-%    		time. At 5 time points people were asked to rate the robot according to the
-%    		following aspects: the perceived \texttt{intelligence} of the robot, the
-%    		perceived \texttt{usefulness}, the perceived \texttt{ease of use}, how much
-%    		\texttt{fun} it was to use the robot, how far they found the robot had an
-%    		\texttt{impact} on their household, and their {overall} impression of it.}
-%    		\label{fig:roomba-study}
-%\end{figure}
-%
-%
-%\paragraph*{Watching the robot for fun.} We categorize watching a robot for fun
-%as an entertaining, emotional activity, reflecting a feeling of empathy for the
-%robot. In \cite{sung_housewives_2008} survey, 73~\% of the participants reported
-%to watch their Roomba running for fun. While in the beginning of our study, also
-%a quite high proportion (6 of 9 households) reported to watch the robot for fun,
-%after 2 and 6 months the number of households that engaged in this activity
-%decreased by half. 
-%
-%\paragraph*{Giving a robot demo to visitors.} It is somehow natural that owners
-%of innovative devices show the device to others and ask for their opinion about
-%it \citep{rogers_diffusion_1995}. However, this activity suggests that the robot
-%is presented as a new part of the household to visitors.
-%\cite{sung_domestic_2010} described that a vacuum cleaning robot can serve as a
-%mediator and encourage social interaction among people. We categorize giving a
-%demo of the robot to visitors / guests as such an activity. During the first 2
-%weeks with the robot 8 of 9 households in our study showed their robot to
-%others, and still after 2 and 6 months 5 of the households engaged in this
-%activity. This number is more or less in accordance with the 57~\% of survey
-%respondents who stated to give demonstrations to others
-%\citep{sung_housewives_2008}.
-%
-%%\paragraph*{Taking photos / videos of the robot.} How far taking a photo or
-%%video of a robot can be seen as an anthropomorphic interaction is questionable.
-%%However, it reflects the fact that the robot is observed by the user who for
-%%some reason is motivated to record the event. The number of households that
-%%took a photo or video of the robot decreased over time from 5 households in the
-%%beginning to 1 household after 6 months.
-%
-%\paragraph*{Personalizing the robot.} It has been found that people are
-%motivated to personalize technology as a form of self-expression (identity
-%projection) or when they use a technology a lot and know how to customize it
-%(technical identity projection) \citep{blom_personalization:_2000}. Though
-%\cite{sung_pimp_2009} found that some Roomba users who were given a
-%customization toolkit personalized their Roomba, none of the users in her study
-%who was \textit{not} given this toolkit personalized their Roomba. Also in our
-%study none of the 9 households engaged in a personalization activity.
-%
-%\paragraph*{Giving a name to the robot.} Giving a name to an artificial agent
-%reflects a certain kind of personal relationship to the agent. By naming a
-%robot, it is not anonymous anymore, and might be perceived as a moral agent. As
-%such, naming an artificial agent can be classified as anthropomorphizing this
-%agent. It further suggests that the agent is talked to directly. Though more
-%than 23~\% of the survey participants in \cite{sung_housewives_2008} study
-%reported to name their Roomba, only 1 of 9 households in our study did so. 
-%
-%\paragraph*{Talking directly to the robot.} Using direct speech toward an object
-%or artificial agent that does not have the ability to recognize and process
-%speech (such as verbal comments) or other sound cues, is an interesting
-%phenomenon which can be classified as an anthropomorphic interaction. Whereas
-%only 11~\% of the survey respondents in \cite{sung_housewives_2008} study
-%reported to talk to their robot, around half of the households engaged in this
-%activity and the proportion did not notably decrease over time. 
-%
-%\paragraph*{Playing with the robot.} In our study, it were mostly children who
-%engaged in playing with the robot, however, most of them stopped doing so after
-%some time. The number of household playing with their Roomba decreased from 8
-%when asked after 2 weeks with the robot, to 4 households after 2 months, and 1
-%household after 6 months. In \cite{sung_housewives_2008} survey, 37~\% of the
-%Roomba owners reported to play and experiment with their robot.\\ 
-%
-%%\paragraph*{Making adjustments to the home due to the robot.} To help Roomba
-%%clean, \cite{sung_housewives_2008} found in an online survey that about half of
-%%the 379 participants made physical modifications to their homes. This process
-%%is referred to as \textit{roombarization}, and it seems to be a unique aspect
-%%of adopting a domestic service robot. In our study, almost all the households
-%%made adjustments when they used the robot for the first time in front of us.
-%%However, during the first two weeks with the robot, only 3 households reported
-%%to have adjusted something due to the robot, and after 6 months it was only 1
-%%household that still engaged in this activity. This decrease is, however,
-%%logical since after some time most people had done all the necessary
-%%adjustments to enable the robot show a good performance.
-%
-%%\paragraph*{Emerging anthropomorphic interactions.} Another, from our side more
-%%unexpected interaction that we would describe as somehow anthropomorphic, is
-%%what we call \textit{``collaborative cleaning''} with the robot. In the initial
-%%phase of the study, some people spontaneously helped the robot to clean by
-%%either picking up crumbs from the floor themselves or pushing it right in front
-%%of the robot. Another way of collaborating with the robot we observed was to
-%%help it go everywhere by spontaneously putting up the trash bin or the carpet
-%%in the bathroom (things that are not just lying around and need to be cleaned
-%%up). However, the activity of collaborative cleaning faded out soon, and we
-%%suspect it was encouraged by the novelty of the robot.\\
-%
-%Overall, Figure \ref{fig:roomba-activities} shows that as time goes by, less
-%households engage in the before-mentioned non-cleaning activities with the
-%vacuum cleaning robot: after 2 weeks, on average, 4.67 of 9 households engage in
-%a human-like activity with the robot; after 2 months, the value decreases to
-%2.83, and after 6 months to 2.3. Our interpretation is that the nature of
-%human-robot interaction changes over time. More concretely, we suspect  that
-%anthropomorphic / human-social interactions with the robot become less over
-%time, and that only with some people these interactions sustain.
-%
-%
-%\subsubsection{Perception of anthropomorphic characteristics of the robot\\}
-%
-%We also studied people's perception of the robot, and how it evolved over time
-%(see Figure \ref{fig:roomba-perception}). The main idea was to find out which of
-%the perceived attributes could be related to how far the robot was integrated in
-%the household as a cleaning tool. Concerning anthropomorphism, we included
-%\textit{perceived intelligence} and experienced \textit{fun} when using the
-%robot as indicators for the perception of human-likeness in the robot.\fixme{JF: Severin, you also mentioned impact as one factor. Please include it here below as another paragraph.}
-%
-%%\begin{figure}
-%%    \centering
-%%    \includegraphics[width=0.5\columnwidth]{roomba-perception.pdf}
-%
-%%    \begin{tikzpicture}[scale=0.5, y = 2cm]
-%%    %axis
-%%    \draw (0,0) -- coordinate (x axis mid) (20,0);
-%%    \draw (0,0) -- coordinate (y axis mid) (0,7);
-%%    %ticks
-%%    \foreach \x in {0,4,...,20}
-%%        \draw (\x,1pt) -- (\x,-3pt);
-%%    \foreach \y in {1,...,7} 
-%%        \draw[black!20] (20,\y) -- (-3pt,\y);
-%%    \foreach \y in {1,...,7} 
-%%        \draw (-3pt, \y) node[anchor=east] {\y}; 
-%%    %labels
-%%    \node[below=0.8cm] at (x axis mid) {People's perception (n = 15)};
-%%    \node at (2, -0.4) {\tiny expectations};
-%%    \node[align=center] at (6, -0.4) {\tiny after\\ \tiny first usage};
-%%    \node[align=center] at (10, -0.4) {\tiny after\\ \tiny 2 weeks};
-%%    \node[align=center] at (14, -0.4) {\tiny after\\ \tiny 2 months};
-%%    \node[align=center] at (18, -0.4) {\tiny after\\ \tiny 6 months};
-%%
-%%    \draw[dashed, black!50] (6,0) -- (6,7) node[sloped, below, pos=0.25] {\tiny novelty effect};
-%%
-%%    \draw[ultra thick, red!50] (2,5.6) -- (6,6.1) -- (10,6.3) -- (14,6.3) -- (18,6.1) node at (15,6.5) {\tiny \it ease of use};
-%%    \draw[ultra thick, purple] (2,4.9) -- (6,5.2) -- (10,5.1) -- (14,4.5) -- (18,4.2) node at (3,4.7) {\tiny \it usefulness};
-%%    \draw[ultra thick, blue!50] (2,4) -- (6,4.1) -- (10,4.6) -- (14,4.1) -- (18,4.3) node at (16,4) {\tiny \it fun};
-%%    \draw[ultra thick, green!50] (2,3.9) -- (6,4.1) -- (10,4.2) -- (14,3.8) -- (18,3.3) node at (19,3.5) {\tiny \it intelligence};
-%%    \draw[ultra thick, orange] (2,3.5) -- (6,4.2) -- (10,4) -- (14,3.2) -- (18,2.8) node at (14,2.7) {\tiny \it impact};
-%%
-%%    \draw[ultra thick, dashed] (2,5.2) -- (6,5.2) -- (10,5) -- (14,4.9) -- (18,4.5) node at (14,5.3) {\tiny \it overall};
-%%
-%%    \end{tikzpicture}
-%
-%
-%%    \caption{People's perception of the robot over time, n = 15 participants.
-%%    This line chart shows how people's perception of the robot evolves over
-%%    time. At 5 time points people were asked to rate the robot according to the
-%%    following aspects: the perceived \texttt{intelligence} of the robot, the
-%%    perceived \texttt{usefulness}, the perceived \texttt{ease of use}, how much
-%%    \texttt{fun} it was to use the robot, how far they found the robot had an
-%%    \texttt{impact} on their household, and their {overall} impression of it.}
-%%
-%%    \label{fig:roomba-perception}
-%%\end{figure}
-%
-%\paragraph*{Perceived intelligence.} On a scale from 1-7, people were not sure
-%about how intelligent they should expect the robot to be (mean value 3.9). The
-%rating did not change much and not significantly over time (average ratings
-%between 3.3-4.2) \citep{fink_living_2013}. Interestingly, at all five time
-%points, male participants rated the robot as more intelligent (average 4.5) than
-%females (average 3.4), however, this difference was not significant. When asked
-%why they thought Roomba possesses intelligence, men more often referred to the
-%'robot side' of Roomba: its abilities to detect and avoid obstacles, stairs, and
-%being able to recharge itself. Contrary, women referred to its rather limited
-%vacuuming performance and found it was not as intelligent because \textit{``it
-%doesn't see where the dirt is, it sometimes leaves it, it can't be smart!''}.
-%This difference in the perception of intelligence of a robot suggests that
-%gender,and probably other individual characteristics need to be taken into
-%account.
-%
-%\paragraph*{Experienced fun.} Participants rated the robot as 'somewhat fun'
-%(values from 4.0-4.6). There was a qualitative gender difference (not
-%significant), in the sense that the experienced fun remained quite stable for
-%male participants, whereas it tended to decrease with time for female
-%participants. Men described the robot more as a 'fun gadget' than females, who
-%referred to it as \textit{``In the end, Roomba is a cleaning tool and it is not
-%really fun to use it''}. Again for this aspect, gender seems to play a role in
-%how the robot is perceived and experienced.\\
-%
-%Overall, Figure \ref{fig:roomba-perception} shows that after the first usage of
-%the Roomba (T2), most of the perceived constructs slightly decrease (and hence
-%are less positively rated) as time goes by. The course is different for the
-%perceived \textit{ease of use} of the robot, as participants become more
-%experienced with the robot over time. Also, the experienced \textit{fun} does
-%not decrease with time.
-% 
-%
-%\subsubsection{Summary Roomba study\\}
-%
-%In accordance with previous work we also found relatively low rates of users
-%treating and perceiving their vacuum cleaning robot as a living (or human-like)
-%entity \citep{sung_housewives_2008}. We interpret that it might be the pure
-%functional purpose and non human-like form of the Roomba that prevented people
-%from anthropomorphizing it. Still, we observed some initial anthropomorphic
-%effects, both reflected in interaction with and perception of the robot.
-%However, most of the anthropomorphic effects did not last long. One fairly
-%stable human-like interaction with the robot was \textit{talking to the robot},
-%despite the fact that the robot was not able to recognize and respond to verbal
-%statements.
-%
-%
-%\subsection{Forum study: using anthropomorphic expressions to describe a robot}
-%
-%We investigated the amount and context of anthropomorphic language in three
-%online discussion forums about the robotic dog AIBO, the vacuum cleaning robot
-%Roomba, and the tablet computer iPad. This was done by means of a content
-%analysis of 750 forum posts that were further partitioned in n = 1208 valid
-%segments \citep{fink_anthropomorphic_2012}. Hereafter, we refer to this study as
-%the "Forum study". The three devices, pictured in Figure
-%\ref{fig:aibo-roomba-ipad}, were chosen as they show different designs and
-%fulfill different purposes. We would describe (1) AIBO as a zoomorphic /
-%pet-like robot that does not have a clear purpose but engages people to play
-%with it; (2) Roomba as a mechanical / functional domestic service robot that has
-%a practical main purpose (vacuum cleaning) but offers not much of interactivity;
-%(3) the iPad as a minimalistic designed interactive (touch-based) technology
-%with multiple purposes (both entertainment, and professional / practical use).
-%Based on these different characteristics, we made the two following hypotheses
-%concerning anthropomorphism:
-%
-%\begin{enumerate}
-%    	\item People engage in a more social and human-like way with a robotic pet compared to a functional robot and a tablet computer, therefore there will be a higher amount of anthropomorphic language in the AIBO and Roomba forum, compared to the iPad forum.
-%    	\item As anthropomorphism can be seen as a certain kind of emotional / social relation to an artifact, there will be more anthropomorphic language in forum posts in which the author describes a relation to the device, compared to discussing technological aspects or how the device is used.
-%\end{enumerate}
-%
-%Similar to how \cite{friedman_hardware_2003} analyzed anthropomorphic language
-%in online forums, we coded a segment as anthropomorphic when the respective
-%device was described in terms of:
-%
-%\begin{itemize}
-%    \item \textit{Life-likeness}, such as being alive or having (parts of) a
-%        body, \eg \textit{``she can be reborn since you copied her memory
-%        stick''};
-%    \item \textit{Emotional states, empathy} or the technology having a
-%        \textit{feeling}, \eg \textit{``oh no, poor AIBO''};
-%    \item \textit{Gender, personality} or the technology having an
-%        \textit{intention}, \eg Roomba \textit{``seems to like to hang around
-%        under the sofa''};
-%    \item When the author gave the technology a \textit{name}, \eg
-%        \textit{``whenever I show Java his pink ball''};
-%    \item Being \textit{socially integrated}, such as being a family member, \eg
-%        \textit{``I'm considering adding a Roomba to the family''};
-%    \item \textit{Metaphorical ways}, \eg Roomba \textit{``sings its victory
-%        song when it finishes and docks''}.
-%\end{itemize}
-%
-%In the next paragraphs, we present findings in respect of our two hypotheses:
-%anthropomorphic language related to the device, and anthropomorphic language
-%related to the topic of the forum post.
-%
-%\begin{figure}[b]
-%    \centering
-%    \includegraphics[width=0.5\columnwidth]{aibo-roomba-ipad_2.jpg}
-%    \caption{The Sony AIBO robotic dog (left), the iRobot Roomba vacuum-cleaning robot (middle), and the Apple Inc.
-iPad tablet computer (right) were compared in terms of how far users of these devices use anthropomorphic expressions in online discussion forums about their technology / robot.}
-%    \label{fig:aibo-roomba-ipad}
-%\end{figure}
-%
-%%Overall, our analysis revealed that in all three forums, discussions about
-%%\textit{technical} aspects of the respective device were most frequent (67.7~\%
-%%of all 1208 categorized segments). However there were huge differences between
-%%the three devices: \textit{technical} aspects made up 79.9~\% of the discussion
-%%in the Roomba forum, compared to 69.9~\% in the AIBO forum, and 55.2~\% in the
-%%iPad forum. Another fairly frequently discussed topic concerned the
-%%\textit{usage} of the respective device, thus people describing how and for what
-%%they use their technology. This topic made up 21.8~\% of all posts, and was most
-%%frequent in the iPad forum (35.7~\%), followed by the Roomba forum (15.9~\%),
-%%and the AIBO forum (10.7~\%). Last but not least, we defined \textit{relation}
-%%as the third topic of interest. Discussions in which people described their
-%%relation to the respective device made up 10.5~\% of all posts, and was most
-%%frequent in the AIBO forum (19.4~\%), followed by the iPad forum (9.1~\%), and
-%%the Roomba forum (4.2~\%). \hl{(if it is getting too much we can leave out this
-%%paragraph, it's not crucial, and doesn't say anything about anthropomorphism
-%%directly)}
-%
-%
-%\subsubsection{Anthropomorphic language related to the device (design)\\}
-%
-%A statistical analysis revealed a significant difference for the use of
-%anthropomorphism across the three devices \citep{fink_anthropomorphic_2012}. In
-%accordance with our first hypothesis, the highest amount of anthropomorphic
-%language (56.6~\%) was found in the AIBO forum. In contrast, only 11.7~\% and
-%respectively 2.2~\% of the segments in the Roomba and the iPad forum contained
-%anthropomorphic expressions.  The data suggests that on a subjective scale of
-%perceived human-likeness (or rather life-likeness), Roomba is closer to the iPad
-%than to the AIBO, at least in matters of how they are described with words. This
-%was a bit against our expectation. Still, the Roomba is an autonomous robot that
-%can navigate around the house itself, and we expected this property to enhance
-%anthropomorphism. We interpret that here, the physical embodiment of the object
-%and how far it resembles a life-like entity determine how far the object is
-%anthropomorphized, and as such the robotic dog is anthropomorphized more than
-%the functionally designed devices.
-%
-%
-%\subsubsection{Anthropomorphic language related to the topic of conversation\\}
-%
-%Also in terms of anthropomorphic language related to the topic of conversation,
-%a statistical analysis revealed a significant difference
-%\citep{fink_anthropomorphic_2012}. The analysis suggests that anthropomorphizing
-%happens more when the topic of conversation is \textit{relation}, compared to
-%\textit{usage}, and \textit{technical} aspects. This finding is qualitatively
-%confirmed when looking at the distribution of anthropomorphic expressions across
-%the three topics in the Roomba and iPad forum (with both technologies the
-%highest amount of anthropomorphism is in the \textit{relation} topic). However,
-%in the AIBO the amount of anthropomorphic segments is highest for the
-%\textit{usage} topic.  We interpret that it is the different type of interaction
-%/ use context that makes the difference. Contrary to the iPad and the Roomba,
-%the AIBO is made to encourage its user in a playful / social interaction, which
-%in turn is a typical use context. Further, AIBO has the ability to respond
-%intelligently to its user and environment, which might also encourage people to
-%ascribe human-like abilities to it while interacting with it.
-%
-%
-%\subsubsection{Summary Forum study\\}
-%
-%Overall, findings of the content analysis suggest that there are differences in
-%people's tendency to use anthropomorphic language, originating form the design
-%characteristics of the artifact. A pet-like robot encourages people to use more 
-%anthropomorphic expressions when discussing about it in an online forum. However, 
-%the difference might also be related to other factors that we did not analyze 
-%here (\eg. author's characteristics). Our analysis further shows that the design 
-%of the robot seems to more important than the topic of the discussion. 
-%Interestingly, not only the physical embodiment
-%of the object but also the interaction complexity and purpose of use of the
-%object seems to play a role in how far the object is anthropomorphized.
-%
-%
-%\subsection{Ranger domino study: effect of unexpected robot behavior}
-%
-%The so-called "Ranger domino study" describes a child-robot interaction study
-%that we carried out in a fairly controlled lab setting. One of the goals of this
-%study was to investigate the effect of unexpected robot behavior on (1) the
-%interaction and engagement with robot, and (2) how far children would ascribe
-%human-like abilities (\eg intentions, cognitive abilities) to the robot.
-%
-%13 groups of each two children (n = 26) who were all between 4-5 years old and
-%knew each other, were invited to play with the Ranger
-%robot toy box \citep{fink2014which} to assemble a domino together. The robot
-%was operated by one of the experimenters using the wizard-of-oz technique.
-%Ranger was supposed to transport domino tiles between the two children and it
-%would do its job correctly for the first 7 runs, bringing each one domino tile to the child. Then, however, the
-%robot started misbehaving by not coming over to the child who was calling the 
-%robot. Three different experimental conditions were explored using three different 
-%types of misbehavior from the robot side:
-%Either the robot was \textit{disobeying} and did not come over at all, or 
-%the robot got \textit{lost} on its way to the child, or the robot did a 
-%\textit{mistake} by first going in another direction but then turning and 
-%coming over to the child who had called it.
-%According to these three different types of unexpected robot behavior, we 
-%expected to observe variations of how far the children perceived the 
-%robot in terms of intentionality, and cognitive abilities.
-%
-%In respect of anthropomorphism, we analyzed two types of data: children's 
-%\textit{interaction} with the robot (\eg do they talk to and use gestures 
-%toward the robot?, see Figure \ref{fig:interactions-per-run}), and 
-%children's \textit{perception} of the robot (\eg do they believe the 
-%robot has an own will, feelings, or is able to understand what they 
-%say?). The interaction data was analyzed quantitatively after having 
-%annotated the video recordings of the interaction. Children's perception 
-%of the robot was analyzed in a qualitative way and processed in a 
-%qualitative scale (higher values on that scale indicate more 
-%anthropomorphism), see Figure \ref{fig:qualitative-score}.
-%
-%\begin{figure}
-%        \centering
-%        \begin{subfigure}[b]{0.48\columnwidth}
-%                \includegraphics[width=\textwidth]{ranger-interactions-per-runs}
-%                \caption{Interactions per run}
-%                \label{fig:interactions-per-run}
-%        \end{subfigure}%
-%        ~ %add desired spacing between images, e. g. ~, \quad, \qquad etc.
-%          %(or a blank line to force the subfigure onto a new line)
-%        \begin{subfigure}[b]{0.48\columnwidth}
-%                \includegraphics[width=\textwidth]{ranger-interactions-vs-qualitative-score}
-%                \caption{Qualitative score by interactions}
-%                \label{fig:qualitative-score}
-%        \end{subfigure}
-%        \caption{\textbf{The Ranger domino study: Child-robot interaction.}\\
-%    \textbf{a)} Quantitative assessment: here, six interaction modalities have
-%        been selected: showing something to the robot ({\tt show}), talking to
-%        the robot ({\tt talk}), touching it ({\tt touch}), misbehaving (like
-%        shaking it, {\tt mis}), using gestures ({\tt ges}), and looking
-%        for help by glancing at the experimenter ({\tt look}). In each
-%        of the 13 experimental runs, we annotated and counted the number of
-%        occurrences of each of these interactions. Highlighted runs 2.3, 2.4,
-%        2.7 and 2.8 correspond to unexpected robot behaviors: we observe peaks
-%        of interactions every time the robot's behavior changes from expected to
-%        unexpected or from unexpected to expected. (n = 26 children)\\
-%	\textbf{b)} We found a significant negative correlation ($p=0.048$) between the
-%    number of interactions and the qualitative anthropomorphic projections. This 
-%    suggests that children who interacted more with the robot, anthropomorphized it 
-%	less, and \textit{vice versa}. (n = 13 groups)}
-%    		\label{fig:Ranger-domino}
-%\end{figure}
-%
-%
-%\subsubsection{Anthropomorphic interactions with the robot\\}
-%
-%The video recordings of the interaction session in which the children 
-%played domino with the partly misbehaving robot were annotated according 
-%to a coding scheme that we developed. Amongst others, six different types 
-%of active actions / active engagement that a child carried out with the 
-%robot were annotated. We understand some of these active engagement 
-%actions as anthropomorphic, such as talking directly to the robot or 
-%using gestures to the robot. The distribution of the interaction data per 
-%run (see Figure \ref{fig:interactions-per-run} suggests that after the 
-%robot started misbehaving (and thus became less predictable) children 
-%tended to use slightly more active engagement interactions: gestures toward the 
-%robot, and to talk more to the robot. Also, they were looking more often at the 
-%experimenter, seeking help. 
-%
-%%\begin{figure}
-%%    \centering
-%%    \includegraphics[width=0.5\columnwidth]{ranger-interactions-per-runs}
-%%    \caption{Quantitative assessment: here, six interaction modalities have
-%%        been selected: showing something to the robot ({\tt show}), talking to
-%%        the robot ({\tt talk}), touching it ({\tt touch}), misbehaving (like
-%%        shaking it, {\tt mis}), using gestures ({\tt ges}), and looking
-%%        for help by glancing at the experimenter ({\tt look}). In each
-%%        of the 13 experimental runs, we annotated and counted the number of
-%%        occurrences of each of these interactions. Highlighted runs 2.3, 2.4,
-%%        2.7 and 2.8 correspond to unexpected robot behaviors: we observe peaks
-%%        of interactions every time the robot's behavior changes from expected to
-%%        unexpected or from unexpected to expected. (n = 26 children)}
-%%
-%%    \label{fig:interactions-per-run}
-%%\end{figure}
-%
-%
-%\subsubsection{Perception of anthropomorphic characteristics of the robot\\}
-%
-%First of all, note that it is not at all easy to measure how far 4-5 year old's 
-%perceive a robot to have some human-like qualities. We interviewed children about 
-%various anthropomorphic traits of the robot, such as: Can the robot feel happy or 
-%sad? Some of these questions were inspired by \cite{kahn_jr._robotic_2006}. For 
-%each of these anthropomorphic traits questions, we gave a point if the child 
-%answered in a positive way (partly reversed, negative way), indicating that the 
-%child perceived the robot as somehow human-like. In the end, we summed up all 
-%points, to obtain a \textit{qualitative score} for a child's tendency to 
-%anthropomorphize the robot.
-%
-%
-%\subsubsection{Summary Ranger domino study\\}
-%
-%We were trying to bring both measurements together: the anthropomorphic 
-%interactions with the robot and the perception of anthropomorphic characteristics 
-%of the robot. By this, we wanted to find out whether both aspects are correlated to 
-%each other. A correlation would allow us to answer questions such as: Do children 
-%that perceive more human-like characteristics in the robot also interact with it in 
-%a more human-like way?
-%
-%
-%%\begin{figure}
-%%    \centering
-%%    \includegraphics[width=0.5\columnwidth]{ranger-interactions-vs-qualitative-score}
-%%    \caption{We found a significant negative correlation ($p=0.048$) between the
-%%    number of interactions and the qualitative anthropomorphic projections. This 
-%%    suggests that children who interacted more with the robot, anthropomorphized it 
-%%    less, and \textit{vice versa}. (n = 13 groups)}
-%%    \label{fig:qualitative-score}
-%%\end{figure}
-%
-%Figure~\ref{fig:qualitative-score} plots the qualitative against the quantitative assessment of
-%anthropomorphic effects during the Ranger domino study: the correlation is
-%negative. This was a surprise. The more the children interacted with the robot, the less they
-%projected anthropomorphic traits on the robot. We also note a remarkable cluster
-%of seven groups of children who did not interact much with the robot, but had a
-%strongly anthropomorphic perception of the robot. This may initially look
-%counter-intuitive (one could hypothesize that the more playful the children are
-%with the robot, the more likely they are to consider it as a friend/pet/lively
-%being). We discuss possible cognitive explanations of this in Section~\ref{sec:cognition-neuroscience}.
-%
-%
-%
+The remainder of this article is organized as follows.  According to the three
+perspectives that we take, we first (in Section \ref{sec:anthropomorphism}) aim
+to establish a common ground in the understanding of anthropomorphism. We review
+literature from several relevant domains and integrate the different
+explanations into an understanding of anthropomorphism as a multi-factor
+phenomenon.  Based on this, Section~\ref{sec:our-ideas} introduces our initial
+model of the \textit{Dynamics of Anthropomorphism}. This model describes the
+variances and dynamics of people's tendency to anthropomorphize an artificial
+agent, such as a robot.  Then Section \ref{sec:cognition-neuroscience} presents
+a cognitive and neuroscience perspective on anthropomorphism to consolidate our
+considerations and the proposed model.  This is followed by a discussion about
+the limitations of our approach (Section \ref{sec:discussion}) and the existing
+and alternative ways to measure anthropomorphism in human-robot interactions.
+Finally, Section \ref{sec:conclusion} concludes this article and offers starting
+points for further research on anthropomorphism and the effect of the human-like
+design approach in robotics.
 
@@
 
-Literature on anthropomorphism is quite diverse.
-There exist different and partly conflicting definitions of the term anthropomorphism, and that in general, the \textit{terminology} is not clear.
-Probably as a result of this, there also exist different understandings of the \textit{phenomenon} that the term ``anthropomorphism'' describes.
- In this section we will first give an overview on the diversity of terms and
- then try to establish a common ground in the understanding of anthropomorphism
- as a psychological phenomenon.
+Literature on anthropomorphism is quite diverse. There exist different and
+partly conflicting definitions of the term anthropomorphism, and that in
+general, the \textit{terminology} is not clear. Probably as a result of this,
+there also exist different understandings of the \textit{phenomenon} that the
+term ``anthropomorphism'' describes.  In this section we will first give an
+overview on the diversity of terms and then try to establish a common ground in
+the understanding of anthropomorphism as a psychological phenomenon.
 
@@
 
-%\hl{can be cut from here ...}
-%
-%Thus, animism and anthropomorphism differ in two main aspects:
-%
-%First, the nature of the properties which can be ascribed to an agent differs.
-Life-likeness is not human-unique but applies to all living beings.
-Thus, \textit{animism} applies to attributions of life-like properties but excludes human-specific traits.
-Contrary, a narrow understanding of \textit{anthropomorphism} would exclude all attributions of life-likeness that are not human-unique, such as `being alive'.
-%  
-%Second, the range of agents to which life-likeness can be attributed differs.
-Naturally, only non-living agents can be animized.
-Thus, whereas non-human but \textit{living} beings (most importantly animals) can be anthropomorphized, they cannot be animized.
-Similarly, humans cannot neither be animized nor anthropomorphized as they are living beings and humans.
-%
-%\hl{... to here}
-
-%Personification has 
-%ancient roots, \eg in mythology but also in storytelling. For instance, anthropomorphism was also 
-%used to describe and be able to predict natural forces or anticipate great spirits.
-
 \subsection{Overview of the diverse understandings of anthropomorphism}
@@
 instance, some researchers refer to \textit{``the robot's level of
-anthropomorphism''} \citep{bartneck_is_2007,feil-seifer_human-robot_2008}, whereas others disagree to such a
-statement because they understand that a system or artifact itself does not
-\textit{``contain anthropomorphism''} but only gives rise to the process of
-anthropomorphizing in a given user and situation. Consequently,
-\cite{persson_anthropomorphism_2000} conclude that anthropomorphism emerges in
-the \textit{interaction} between the technology and the user, and has to be
-understood as such. We come back on this point in the next section.
+anthropomorphism''} \citep{bartneck_is_2007,feil-seifer_human-robot_2008},
+whereas others disagree to such a statement because they understand that a
+system or artifact itself does not \textit{``contain anthropomorphism''} but
+only gives rise to the process of anthropomorphizing in a given user and
+situation. Consequently, \cite{persson_anthropomorphism_2000} conclude that
+anthropomorphism emerges in the \textit{interaction} between the technology and
+the user, and has to be understood as such. We come back on this point in the
+next section.
 
@@
 
-%Anthropomorphism is used in different senses throughout different disciplines 
-%\citep{duffy_anthropomorphism_2003} which makes it difficult to synthesize findings. 
 Depending on which definition of anthropomorphism is applied, not everything 
@@
 refer to the original work \citep{epley_when_2008}.}
-
-%The authors list four effects that anthropomorphism does not include:
-%(1) First, anthropomorphism does not include behavioral descriptions of observable actions. Anthropomorphism requires going beyond what is directly observable.
-%(2) Second, anthropomorphism does not merely entail animism, as animate life is not a uniquely human-like characteristic.
-%(3) Third, anthropomorphism does not include any requirement of reasoned or reflective endorsement of an inference.\footnote{\hl{(the strength of anthropomorphic inferences can vary)}}
-%(4) Finally, anthropomorphism is not necessarily inaccurate.
-A psychological theory should take this (in)accuracy in anthropomorphism into account and predict variability in the tendency to perceive human-like traits in non-human agents.
-%% comment Julia: I commented this out because I think this is too complex and too much of detail here.
 
@@
 
-However, despite the fact that ``anthropomorphism'' literally means ``human form'' we propose that the term should \textit{not} be used to refer to
-the \textit{form / design} of a non-human agent or artifact. To refer to an imitation of
-human-like \textit{form / design} of artificial agents, we propose to use the term
-\textbf{anthropomorphic design}. This explicit terminology prevents the commonly
-encountered confusion between anthropomorphism as a psychological, subjective
-phenomenon, and the external, objective factors that \emph{influence} the
-phenomenon itself.
+However, despite the fact that ``anthropomorphism'' literally means ``human
+form'' we propose that the term should \textit{not} be used to refer to the
+\textit{form / design} of a non-human agent or artifact. To refer to an
+imitation of human-like \textit{form / design} of artificial agents, we propose
+to use the term \textbf{anthropomorphic design}. This explicit terminology
+prevents the commonly encountered confusion between anthropomorphism as a
+psychological, subjective phenomenon, and the external, objective factors that
+\emph{influence} the phenomenon itself.
 
@@
 
-Anthropomorphism is an interesting phenomenon because it tells us something about 
-the relationship between the human who anthropomorphizes, and the non-human agent 
-which is anthropomorphized. Though commonly observed, it still appears controversial, at 
-the same time, that humans tend to \textit{``see human in the non-
-human''} \citep{epley_seeing_2007}.
-
-As anthropomorphism arises in an interaction between a human and a non-human agent
-\citep{persson_anthropomorphism_2000}, one can also
-take two main \textit{perspectives} when trying to explain why humans anthropomorphize \citep{lee_human_2005}: an artifact-centered perspective and a human-centered perspective (see grey triangles in Figure \ref{fig:anthropofig}).
-It has to be kept in mind that both perspectives are inseparable; they apply at the
-same time, and we would like to present them here just as two different viewpoints 
-on the same phenomenon.
-
-In the following we will only briefly present the artifact-centered perspective to explain anthropomorphism.
-A review of anthropomorphic design of robots can also be found in \cite{fink_anthropomorphism_2012}.
-Then, we provide a more detailed review and synthesis of literature that applies a human-centered perspective to explain anthropomorphism.
-Concretely, we integrate theories from developmental psychology, cognitive science / neuroscience, and social psychology to shed light on the question why humans anthropomorphize.
+Anthropomorphism is an interesting phenomenon because it tells us something
+about the relationship between the human who anthropomorphizes, and the
+non-human agent which is anthropomorphized. Though commonly observed, it still
+appears controversial, at the same time, that humans tend to \textit{``see human
+in the non- human''} \citep{epley_seeing_2007}.
+
+As anthropomorphism arises in an interaction between a human and a non-human
+agent \citep{persson_anthropomorphism_2000}, one can also take two main
+\textit{perspectives} when trying to explain why humans anthropomorphize
+\citep{lee_human_2005}: an artifact-centered perspective and a human-centered
+perspective (see grey triangles in Figure \ref{fig:anthropofig}). It has to be
+kept in mind that both perspectives are inseparable; they apply at the same
+time, and we would like to present them here just as two different viewpoints on
+the same phenomenon.
+
+In the following we will only briefly present the artifact-centered perspective
+to explain anthropomorphism. A review of anthropomorphic design of robots can
+also be found in \cite{fink_anthropomorphism_2012}. Then, we provide a more
+detailed review and synthesis of literature that applies a human-centered
+perspective to explain anthropomorphism. Concretely, we integrate theories from
+developmental psychology, cognitive science / neuroscience, and social
+psychology to shed light on the question why humans anthropomorphize.
 
@@
 
-%\subsection{An artifact-centered perspective on anthropomorphism}
-%\label{sec:anthropomorphic-design}
-%
-%An artifact-centered perspective 
-%
-%The use of nature-inspired and in particular anthropomorphic (human-like) form in the 
-%design of non-human things is as old and manifold as people's tendency to anthropomorphize. 
-%Anthropomorphic (and life-like) forms have a long-standing tradition in design in general, and in the design of daily life things, in particular 
-%\citep{norman_design_1988,guthrie_bottles_2000}. Interestingly, from its very
-%beginning robots were resembling a human being in their appearance. Starting
-%from when the term \textit{robot} first appeared in a play by Karel \^{C}apek in the 1920ies, robots were man-made beings, created as the \textit{``shadow of man''} \citep{replicant_????}.
-
-%The view of people mindlessly reacting in a human-social manner to anthropomorphic forms
-%is based on the fact that humans naturally react to specific 
-%cues. From early childhood 
-%on, humans are inherently well-trained to perceive life \citep{epley_seeing_2007}, 
-%or to respond to social cues, such as facial expressions, social gestures or turn-taking.
-Humans have a propensity toward particular cues that seem to trigger automatic interpersonal social responses \citep{takayama_perspectives_2012}.
-%One has to keep in mind that in 
-%human-human interaction these cues are of various senses and modalities, 
-%and consequently human-like design is also realized addressing several senses. 
-%One of the most outstanding aspects is probably the outer appearance of an agent or 
-%artifact (in particular when it is unknown or unfamiliar). \cite{schmitz_concepts_2011} 
-%argues that an agent's outer appearance is likely to have an important impact on how 
-%the object is overall perceived. Consequently, if a robot's outer form resembles a 
-%human, the robot is likely to be treated similar to a human.
-Besides the physical shape of a robot, other more subtle anthropomorphic forms can be found in robots, including human-social behavioral cues (\eg eye-gaze), social gestures (\eg waving), or verbal politeness (\eg greeting, apologizing).
-%
-%People's natural reaction to these and other anthropomorphic design cues of
-%robots (in particular, social or also called \textit{sociable} robots 
-%\citep{breazeal_sociable_2000}) are extensively studied.
-This research is of particular interest in human-robot interaction as the consequences of anthropomorphic design can be both of positive and negative nature, and it is yet not clear what exactly it is that makes the difference.
-%
-%
-%\subsubsection{How people perceive and interact with human-like robots\\}
-%\label{sec:anthropomorphism-robotics}  
-% 
-%Most work that studies how far human users treat robots as social agents, builds on the 
-%famous work of \cite{reeves_media_1996} in HCI. In the so-called \textit{Media 
-%Equation}, the authors describe that people mindlessly react in a social way to their computer 
-%and that they tend to even attribute human (social) characteristics to it -- despite 
-%the fact that a computer does not have human-like characteristics. Apart from 
-%computers, anthropomorphism has also been observed with digital / virtual characters 
-%\citep{von_der_putten_it_2010}, and artificial embodied agents, 
-%such as robots \citep{rosenthal-vonderputten_experimental_2013}. 
-%In short, one can say that with robots, and human-like robots in 
-%particular, anthropomorphism is a commonly observed phenomenon. 
-%But what are the motivations which underlie the efforts of enhancing anthropomorphism 
-%through specific anthropomorphic design in robots? Why are anthropomorphic forms so 
-%distinct and at the same time controversial in robotics? There is no one single answer 
-%to these questions. 
-% 
-%The underlying central point about the human-like design of robots lies in the 
-%implications that this design holds, and the suggestions for interactions that
-%it makes to the human user. 
-%In other words, the appearance 
-%and function of a product, whether it is an appliance or a humanoid robot, affects how 
-%people perceive it, interact with it, and build long-term relationships with 
-%it \citep{bartneck_shaping_2004}. 
-%The principle of human-like form is probably most prominent in the design of robots, 
-%due to several reasons, such as to foster efficient interaction and increase 
-%acceptance. An anthropomorphic design of a robot encourages people to reason about this 
-%unfamiliar system \emph{as if} it was a human. To increase this tendency, robots are 
-%designed with anthropomorphic (or lifelike) forms, or are able to display and use 
-%human-social cues when interacting with humans.
-%However, anthropomorphic robot designs have been controversially discussed and received 
-%remarkable attention since the early 1970ies, related to Mori's
-%theory of the \textit{Uncanny Valley} \citep{mori_uncanny_1970}.
-%%see Figure \ref{fig:uncanny_valley}.
-%
-%%\begin{figure}\centering
-%%% Use the relevant command to insert your figure file.
-%%% For example, with the graphicx package use
-%%  \includegraphics[scale=0.75]{uncanny-valley.jpg}
-%%% figure caption is below the figure
-%% \caption{Mashiro Mori, illustration of the \textit{Uncanny Valley} hypothesis.
-The curve models the user's perceived affinity with the artifact, as its human likeness is increased.
-Up to a certain (not yet defined) point, a person perceives more affinity in a more human-like agent; however with an abrupt shift towards a negative perception as soon as the agent surpasses this point, of resembling a human too closely but not fully.
-Originally from 1970; picture from a manuscript version of \cite{mori_uncanny_2012}}
-%% \label{fig:uncanny_valley}       % Give a unique label
-%% \end{figure}
-%
-%Despite the fact that the Uncanny Valley theory was more a working hypothesis and not 
-%meant to be empirically examined \citep{cheetham_human_2011}, it has been studied quite 
-%extensively. However, results are inconsistent. We try to give a short overview (not 
-%exclusive) on work related to HRI and robotics in the following. 
-% 
-% 
-%\subsubsection{Anthropomorphic form can be advantageous for HRI\\}
-%
-%On one hand, developers and designers have discovered that human-like robots may better 
-%match the affordances that this to humans adapted world brings along. 
-%Apart from this, it is suggested that an increased human-likeness of a robot (up to a 
-%certain threshold) will generally lead to 
-%more perceived \textit{affinity} from the human side \citep{mori_uncanny_1970}.
-%% (see Figure \ref{fig:uncanny_valley}).
-%This further increases anthropomorphism, and as such
-%appears to be beneficial for human-robot relations, especially with socially 
-%interactive robots \citep{fong_survey_2003}. Consequently, the domain of (social) 
-%robotics tries to exploit this by using
-%anthropomorphic forms in robots.
-%Humans seem to readily accept and prefer the 
-%anthropomorphic form of a robot (up to a certain point), when compared to purely mechanical 
-%robots. A possible explanation for this is that perceiving a system as
-%human-like (or also pet-like) compared to machine-like changes the 
-%way how users try to understand and make sense of this system. The reason for this is 
-%that humans tend to project everyday 
-%expectations of human and animalistic life onto artificial agents that use 
-%anthropomorphic (or zoomorphic) forms \citep{schmitz_concepts_2011}. 
-%Both cognitive science 
-%and social psychology can provide explanations for this process of projection. The basic idea 
-%is that \textit{"the more similar in 
-%appearance, the more people are likely to use themselves as a source of induction 
-%and anthropomorphize these nonhuman agents"} \citep{epley_seeing_2007}. Studies have further 
-%shown that perceived similarity between the user and the robot influences the intensity of 
-%the participants' attributions towards the robot. Thus, the anthropomorphic design of a robot 
-%impacts the user's perception of the robot, and how far the user is likely to attribute and 
-%experience qualities such as intelligence, fun, or intentions in the robot. 
-%These experiences mark the transition between an immediate \textit{in-the-moment} and more thoughtful \textit{reflective} \citep{takayama_perspectives_2012} perception of, and interaction with the robot.
-As this distinction is also based on different cognitive processes, a more human-centered / cognitive perspective needs to be applied here, and we will treat this in Section \ref{sec:human-centered}.
-%
-%In short, the central point in using anthropomorphic design in sociable robots is that 
-%humans tend to apply the same communication references to anthropomorphic robots 
-%that they would use with other humans, which in turn enhances feeling familiar and 
-%comfortable when interacting with the otherwise unknown system.
-%This positive effect has been shown in various 
-%empirical studies. It has been found that robots with human-like forms can enhance social 
-%responses from humans which in turn can positively impact on acceptance 
-%\citep{duffy_anthropomorphism_2003,goetz_cooperation_2002,venkatesh_theoretical_2000}. 
-%People responded more positively to an artifact that displayed human-like 
-%behavioral characteristics (emotions, facial expression) in contrast to a purely 
-%functional design 
-%\citep{eyssel_anthropomorphic_2010,krach_can_2008,reeves_media_1996,riek_how_2009}. 
-%Overall, these results suggest that human-like features in robots enhance 
-%anthropomorphism, and in turn create a social view toward the robot.
-%
-% 
-%%Anthropomorphism represents just one of many examples of induction whereby "people reason about an unknown stimulus based on a better-known representation of a related stimulus" \cite{epley_when_2008}, in this case reasoning about a non-human agent based on representation of the self or other humans.
-%
-%
-%\subsubsection{Anthropomorphic form can be disadvantageous for HRI\\}
-%
-%The anthropomorphic form also 
-%increases people's expectations of the agent, and consequently, a very human-like 
-%appearing robot is not only perceived but also expected to act like a human. However, today's artificial systems are 
-%not able (yet) to mimic well human movements, or human social cues in an acceptable way. 
-%The case is that the artificial agent pretends to be human but fails, and this is 
-%more than just disappointing for the 
-%human -- it appears uncanny and evokes reluctance, the so-called 
-%\textit{"uncanny valley"}. The idea of naming this shift and drop from a positive to a negative reaction,
-%follows Freud's description of the so-called \textit{uncanny} (a translation from the German word 
-%\textit{``unheimlich''}). Controversially, something uncanny \textit{"derives its terror not from 
-%something externally alien or unknown but -- on the contrary -- from something 
-%strangely familiar which defeats our efforts to separate ourselves from it"} (v. Foerster, cited after \cite{hegel_understanding_2008}).
-%In other words, humans are very sensitive to the limits of what is familiar to them 
-%in a sense of being human. At the same time, humans are naturally very skilled when 
-%it comes to identifying what is acceptable as a human and what is an imitation 
-%of it. Even subtle differences can be crucial -- humans are inherently well trained 
-%in identifying if there is \hl{``something strange''} in the familiar.
-%Summing it up, a not yet very well defined thin line separates acceptable human-like forms in 
-%robots from creepy artificial \textit{almost} human-like appearing robots.
-%
-% 
-%Of course, there is no one good answer to the question how to not fall in the 
-%uncanny valley when designing an anthropomorphic system. Equipping a system with 
-%some anthropomorphic forms seems to be inevitable 
-%\cite{duffy_anthropomorphism_2002} in the advancement of human-machine interfaces 
-%and sociable robots \citep{breazeal_sociable_2000}. However, we agree that 
-%\textit{"the important criterion is to seek a balance between people's expectations 
-%and the machines capabilities"} \citep{duffy_anthropomorphism_2002}.
-
-% Simulation Theory
-
-%Findings that support anthropomorphic form in robots because they found people 
-%respond with anthropomorphizing these kind of robots, and in turn act more social 
-%toward them or accept them more easily:	empathy --> check Iolanda's paper
-
-%For instance, recent studies found that people tend to ascribe personality and 
-%intentions to robots \hl{(REFS)} and that they show empathetic behavior toward robots 
-%\citep{rosenthal-vonderputten_experimental_2013}.
-
-%Various studies have shown that people directly talk to their robot (even if it 
-%does not recognize speech), give it a name, greet it, or wonder about its 
-%intentions and actions as if it were a human 
-%\citep{eyssel_anthropomorphic_2010,fink_anthropomorphic_2012,forlizzi_how_2007,fussell_how_2008,kiesler_anthropomorphic_2008}.
-%It has frequently been described that people ascribe intentions or emotions to 
-%their domestic robot, such as to a Roomba vacuum-cleaning robot 
-%\citep{krumm_my_2007,sung_robots_2009} or the AIBO robotic dog 
-%\citep{friedman_hardware_2003}.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%\subsection{A human-centered perspective on anthropomorphism}
-%\label{sec:human-centered}
 
@@
 
-In the following, we present what we found in reviewing literature that applies a human-centered perspective on anthropomorphism by building on:
-\textit{(1)} a line of research in developmental psychology that studies the attribution of animacy;
-\textit{(2)} a line of research in more cognitive sciences that studies the cognitive processes that underlie anthropomorphism, and
-\textit{(3)} a theory that explains anthropomorphism based on psychological factors.
-
-% \begin{figure}[b]\centering
-%% Use the relevant command to insert your figure file.
-%% For example, with the graphicx package use
-%  \includegraphics[scale=1]{north-wind.jpg}
-%  \includegraphics[scale=1]{sun.jpg}
-%% figure caption is below the figure
-% \caption{Milo Winter illustration of Aesop Fable \textit{The North Wind and the Sun}, 1919; both natural forces wind and sun are anthropomorphized with a human face; picture source: wikipedia}
-% \label{fig:north-wind-sun}       % Give a unique label
-% \end{figure}
-
-%An illustration of an anthropomorphism related to nature is shown in Figure 
-%\ref{fig:north-wind-sun}. In this Milo Winter (1919) drawing \textit{"The North Wind 
-%and the Sun"}, both north wind and sun are given a human face.
-
-%\subsubsection{Why do people anthropomorphize?\\}
-%\label{sec:explanations}
-
-%But why do people anthropomorphize?
-First and foremost, it needs to be mentioned that anthropomorphism is a fairly complex phenomenon.
-Paradoxically, there is a huge and diverse body of literature on it but nevertheless, it seems that anthropomorphism is still not very well understood (especially in a field as young as HRI).
-
-%Anthropomorphism as a social phenomenon arises in an interaction \citep{persson_anthropomorphism_2000}, and thus includes at least two interaction partners (the human and the real or imagined non-human agent).
-Therefore, one can take two main perspectives on explaining it \citep{lee_human_2005}: a human-centered, and an artifact-centered.
-We briefly outline both views in the following.
-It has to be kept in mind that both perspectives are inseparable; they apply at the same time, and we would like to present them here just as two different viewpoints on the same kind of phenomenon.
+In the following, we present what we found in reviewing literature that applies
+a human-centered perspective on anthropomorphism by building on: \textit{(1)} a
+line of research in developmental psychology that studies the attribution of
+animacy; \textit{(2)} a line of research in more cognitive sciences that studies
+the cognitive processes that underlie anthropomorphism, and \textit{(3)} a
+theory that explains anthropomorphism based on psychological factors.
 
@@
 whether they are using anthropomorphism in a metaphoric sense (because their
-conceptions of the world and of the living are not yet fully formed). However, experiments by \cite{heider_experimental_1944} and
+conceptions of the world and of the living are not yet fully formed). However,
+experiments by \cite{heider_experimental_1944} and
 \cite{michotte_perception_1963} showed that also adult participants attribute
@@
 experiments, participants viewed animations of simple shapes, such as circles or
-triangles. Asked to describe what they observed, most people developed
-elaborate stories, attributing motivations, emotions and relationships between
-the objects.\footnote{For more details, the reader may refer to the ``attribution
+triangles. Asked to describe what they observed, most people developed elaborate
+stories, attributing motivations, emotions and relationships between the
+objects.\footnote{For more details, the reader may refer to the ``attribution
 theory''.}
-
-%\begin{figure}[h]\centering
-%% Use the relevant command to insert your figure file.
-%% For example, with the graphicx package use
-%  \includegraphics[scale=0.6]{heider-simmel_animation.jpeg}
-%% figure caption is below the figure
-% \caption{Fritz Heider and Mary-Ann Simmel's animated film to study people's tendency to attribute animacy and intention to simple shapes; \textit{An experimental study of apparent behavior}, 1944}
-% \fxnote{wrap text around this figure?}
-% \label{fig:animacy_attribution}       % Give a unique label
-% \end{figure}
 
@@
 
-\subsubsection{Cognitive science research, Theory of Mind, and neural correlates of anthropomorphism\\}
+\subsubsection{Cognitive science research, Theory of Mind, and neural correlates
+of anthropomorphism\\}
+
 \label{sec:cognitive-expl}
@@
 person's ability to attribute mental states to oneself and others. 
-%A theory of mind for other agents enables us to attribute intentionality to those agents \citep{leslie_pretense_1987,admoni_multi-category_2012}. 
 We briefly reviewed  neuro-physiological evidence of a link between the tendency
@@
 signals from a robot the same way as they do for human beings.
-%were recently demonstrated at the brain level~\citep{cullen2013individual}.
 
@@
 \begin{enumerate}
-	\item ~anthropocentric knowledge is accessible and applicable to the artifact (\textit{elicited agent knowledge}),
-	\item ~they are motivated to explain and understand the behavior of other agents (\textit{effectance motivation}), and
-	\item ~they have the desire for social contact and affiliation (\textit{social motivation}).
+
+    \item ~anthropocentric knowledge is accessible and applicable to the
+        artifact (\textit{elicited agent knowledge}),
+
+    \item ~they are motivated to explain and understand the behavior of other
+        agents (\textit{effectance motivation}), and
+
+    \item ~they have the desire for social contact and affiliation
+        (\textit{social motivation}).
+
 \end{enumerate}
@@
 
-The third factor \textit{sociality} describes a person's motivation for social contact, social connection, and social approval from other agents.
-In lack of social connections to other humans (\etc friends, family, colleagues), a person is more likely to compensate these social connections by anthropomorphizing non-human agents.
-In other words \textit{``[...] those who are chronically lonely should be more likely to anthropomorphize nonhuman agents than those who are more chronically connected"} \citep{epley_seeing_2007}.
-Importantly for anthropomorphism, this social connection often appears to be satisfied by connections with \textit{``two of the most commonly anthropomorphized non-human agents, namely pets and religious agents"} \citep{epley_seeing_2007}.
-Thus, the motivation of being socially connected increases the tendency to anthropomorphize non-human agents because first sociality motivation increases the tendency to perceive human-like characteristics and traits even in non-human agents, and second it increases the tendency to search for sources of social connection in one's environment.
+The third factor \textit{sociality} describes a person's motivation for social
+contact, social connection, and social approval from other agents. In lack of
+social connections to other humans (\etc friends, family, colleagues), a person
+is more likely to compensate these social connections by anthropomorphizing
+non-human agents. In other words \textit{``[...] those who are chronically
+lonely should be more likely to anthropomorphize nonhuman agents than those who
+are more chronically connected"} \citep{epley_seeing_2007}. Importantly for
+anthropomorphism, this social connection often appears to be satisfied by
+connections with \textit{``two of the most commonly anthropomorphized non-human
+agents, namely pets and religious agents"} \citep{epley_seeing_2007}. Thus, the
+motivation of being socially connected increases the tendency to
+anthropomorphize non-human agents because first sociality motivation increases
+the tendency to perceive human-like characteristics and traits even in non-human
+agents, and second it increases the tendency to search for sources of social
+connection in one's environment.
 
@@
 
-Summing it up, anthropomorphism is a commonly discussed and
-studied trait of human-robot interaction; however its current understanding seems to be stuck.
-More concretely, when seeking to understand why anthropomorphism in an interaction between a human and a non-human artifact happens, most attention is given to the artifact and/or to the human.
-We agree that these two are the essential ``players'' of anthropomorphism (see Figure \ref{fig:anthropofig}).
-Indeed and, as outlined before, research has shown that both the human and the artifact are not only the two players of anthropomorphism but also the two main ``factors'' that can promote or hinder anthropomorphism.
-
-However, we think that this is not the full story. When agreeing to understand anthropomorphism as a specific type of \textit{experience} that arises in an
-\textit{interaction} between a set of user expectations and the external reality \citep{persson_anthropomorphism_2000}, 
+Summing it up, anthropomorphism is a commonly discussed and studied trait of
+human-robot interaction; however its current understanding seems to be stuck.
+More concretely, when seeking to understand why anthropomorphism in an
+interaction between a human and a non-human artifact happens, most attention is
+given to the artifact and/or to the human. We agree that these two are the
+essential ``players'' of anthropomorphism (see Figure \ref{fig:anthropofig}).
+Indeed and, as outlined before, research has shown that both the human and the
+artifact are not only the two players of anthropomorphism but also the two main
+``factors'' that can promote or hinder anthropomorphism.
+
+However, we think that this is not the full story. When agreeing to understand
+anthropomorphism as a specific type of \textit{experience} that arises in an
+\textit{interaction} between a set of user expectations and the external reality
+\citep{persson_anthropomorphism_2000}, 
 %(see Figure~\ref{fig:anthropomorphism_and_interaction})
-it becomes clear that this interaction happens in a specific context, with a specific history.
-We think that the context and the history of the interaction (in Figure \ref{fig:factors} denoted as \textit{time}), are two more factors that determine anthropomorphism.
+it becomes clear that this interaction happens in a specific context, with a
+specific history. We think that the context and the history of the interaction
+(in Figure \ref{fig:factors} denoted as \textit{time}), are two more factors
+that determine anthropomorphism.
 
@@
     \includegraphics[width=0.7\columnwidth]{factors}
-    \caption{Anthropomorphism is a multi-factor phenomenon.
-How far people tend to anthropomorphize a robot is determined by four main factors: the design of the robot $(R)$, the personal characteristics of the human user $(H)$, the situation and context in which the interaction occurs $(C)$, and the amount of time (repeated interaction) that the user spends to familiarize herself with the robot $(t)$.}
+    \caption{Anthropomorphism is a multi-factor phenomenon. How far people tend
+    to anthropomorphize a robot is determined by four main factors: the design
+    of the robot $(R)$, the personal characteristics of the human user $(H)$, the
+    situation and context in which the interaction occurs $(C)$, and the amount of
+    time (repeated interaction) that the user spends to familiarize herself with the
+    robot $(t)$.}
+
     \label{fig:factors}
@@
 
-Consequently, we propose a holistic understanding of anthropomorphism as a phenomenon which is determined by multiple factors (see also Figure \ref{fig:factors}):
+Consequently, we propose a holistic understanding of anthropomorphism as a
+phenomenon which is determined by multiple factors (see also Figure
+\ref{fig:factors}):
 
 \begin{enumerate}
-\item ~the characteristics of the \textbf{robot's design} (degree of anthropomorphic form),
-\item ~the psychological determinants in the \textbf{human user} (see
-\cite{epley_seeing_2007}),
-\item ~the characteristics of the \textbf{context / situation} in which the interaction occurs, and
-\item ~the fact of the user getting familiar with the robot \textbf{over time} (duration / history of interaction)
+
+\item ~the characteristics of the \textbf{robot's design} (degree of
+    anthropomorphic form),
+
+\item ~the psychological determinants in the \textbf{human user}
+    (see~\cite{epley_seeing_2007}),
+
+\item ~the characteristics of the \textbf{context / situation} in which the
+    interaction occurs, and
+
+\item ~the fact of the user getting familiar with the robot \textbf{over time}
+    (duration / history of interaction)
+
 \end{enumerate}
 
-%However, anthropomorphism is a complex process and we think that the current understanding of it does neither seem to fully take into account the wide range of phenomena that it encompasses, nor the multiplicity of factors which determine it.
-%This shortcoming and conflict in the understanding of anthropomorphism in HRI has already been denoted by others but we would like to take a first step towards moving forward in this dilemma, and encourage an open dialogue to solve this.
-
-%we suggest to understand anthropomorphism as a \emph{dynamic},
-%\emph{context-dependent} process. To this end, we apply Persson \textit{et
-%al.}'s six levels on anthropomorphism to HRI and introduce three
-%\emph{interaction phases}. These interaction phases of anthropomorphism reflect
-%also the results of a long-term study that we conducted in a real human
-%environment and provide an account of the so-called \textit{novelty effect}.
-
-%\begin{figure}[ht!]\centering
-%% Use the relevant command to insert your figure file.
-%% For example, with the graphicx package use
-%  \includegraphics[scale=0.42]{persson_anthropomorphism.png}
-%% figure caption is below the figure
-% \caption{Anthropomorphism emerges in the (real or imagined) interaction between
-% robot and user; illustration taken from \cite{persson_anthropomorphism_2000}
-% \hl{maybe we don't put the figure here, it was just to illustrate what I mean}}
-%
-% \label{fig:anthropomorphism_and_interaction}       % Give a unique label
-% \end{figure}
-
-When taking into account these multiple factors, a logical consequence seems to be that anthropomorphism is not either there or not there but that it arises in different levels, may they be distinct, having multiple layers \citep{persson_anthropomorphism_2000}.
-or a continuum being describes in low and high anthropomorphism \citep{ruijten_introducing_2014}.
-For instance,
-
-Moreover, we propose that anthropomorphism shows not only variances determined by these four main factors but that -- the fourth factor implies this -- anthropomorphism is likely to evolve over time with continued interaction between the human and the non-human agent.
-
-To facilitate things, we introduce the notation \Ant[R,H,C,t] to bring these multiple factors together. To take into account dynamics over time, we suggest that
-anthropomorphism is a function of a vector of robot's traits $R = \{r_0,...,r_n\}$, a vector human
-determinants $H = \{h_0,...,h_n\}$, characteristics of the interaction context $C = \{c_0,...,c_n\}$, and the duration / history of the
-interaction itself, $t$.
-
-%% -> Commented out the overview as it does not match what we actually present... maybe we need a new one?
-% We would further like to review and discuss research on anthropomorphism in
-% robotics and human-like design of robots. We first provide a comprehensive
-% understanding of the phenomenon drawing on theories from developmental
-% psychology and cognitive sciences. We then present the trends of different
-% kinds of anthropomorphic forms in robots and discuss their role in social
-% robotics. The article integrates related work from human-robot interaction
-% studies, reporting on findings from experiments with human subjects
-% interacting with and evaluating various types of systems. We try to give a
-% coherent view on the topic, outline similarities and antithetic findings, and
-% contribute to a better understanding of anthropomorphism in robotics, and the
-% acceptance of human-like characteristics in robots. We also aim to
-% constructively discuss anthropomorphic design of personal and socially
-% interactive robots.
-
-%In this article we will use the term \emph{anthropomorphic effect} to denote
-%observable correlates of anthropomorphism. With these we include, amongst
-%others, verbal utterances (such as direct speech or the use of pronouns
-%"he/she"), (social) gestures (such as a hug, waving, deictic gestures) or
-%\hl{anticipation of certain actions of an agent [what??]}.
-
-% Persson \textit{et al.}
-%suggest that the social phenomenon involves several levels, like primitive
-%psychology, folk-psychology, social stereotypes, and emotional anthropomorphism.
+When taking into account these multiple factors, a logical consequence seems to
+be that anthropomorphism is not either there or not there but that it arises in
+different levels, may they be distinct, having multiple layers
+\citep{persson_anthropomorphism_2000}. or a continuum being describes in low and
+high anthropomorphism \citep{ruijten_introducing_2014}. For instance,
+
+Moreover, we propose that anthropomorphism shows not only variances determined
+by these four main factors but that -- the fourth factor implies this --
+anthropomorphism is likely to evolve over time with continued interaction
+between the human and the non-human agent.
+
+To facilitate things, we introduce the notation \Ant[R,H,C,t] to bring these
+multiple factors together. To take into account dynamics over time, we suggest
+that anthropomorphism is a function of a vector of robot's traits $R =
+\{r_0,...,r_n\}$, a vector human determinants $H = \{h_0,...,h_n\}$,
+characteristics of the interaction context $C = \{c_0,...,c_n\}$, and the
+duration / history of the interaction itself, $t$.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-% SEVERIN & JULIA: there will be 2-3 subsections in which we present our ideas:
-% 	1) anthropomorphism is a multi-factor phenomenon (the figure with the several factors)
-%	2) anthropomorphism is dynamic (the dynamic curve model)
-%
-%
 
@@
 human-robot interactions evolves over time (during the process of
-\emph{adopting} a robot, for instance). Though conflicts were
-found in the understanding of what anthropomorphism is, the HRI
-community more or less accepted viewing anthropomorphism as a static feature
-that once observed during a short-term interaction reflects a sustaining social
-effect. However, if we agree that anthropomorphism arises in an interaction, and thus reflects a specific relation, we cannot accept it as a static phenomenon.
+\emph{adopting} a robot, for instance). Though conflicts were found in the
+understanding of what anthropomorphism is, the HRI community more or less
+accepted viewing anthropomorphism as a static feature that once observed during
+a short-term interaction reflects a sustaining social effect. However, if we
+agree that anthropomorphism arises in an interaction, and thus reflects a
+specific relation, we cannot accept it as a static phenomenon.
 
 Similarly, \citet{kanda_interactive_2004} point out that relationships among
-people evolve over time and, in a similar manner, one can expect people's attitude toward
-technological artifacts and their relationship with them to evolve as well.
-In their study, \citet{kanda_interactive_2004} were among the first to
-describe empirically \emph{novelty effects} during a long-term study with an
-interactive robot in a school.
+people evolve over time and, in a similar manner, one can expect people's
+attitude toward technological artifacts and their relationship with them to
+evolve as well.  In their study, \citet{kanda_interactive_2004} were among the
+first to describe empirically \emph{novelty effects} during a long-term study
+with an interactive robot in a school.
 
@@
 activated knowledge at the time of the judgment}. By applying knowledge to a
-given situation or interaction, one also attempts to correct,
-adjust, or maybe integrate less accessible information into a more automatically
-activated default representation.
-%Epley argues that this process can be seen as
-%a process of correction, and thus, it is often insufficient leaving final
-%judgments biased in the direction of the initially activated representation.
-%Refinements to the initial representation mean something evolves.
-This process of refining the applied knowledge are natural because a person's knowledge base changes constantly with newly
-acquired things.
-For instance, a person can acquire new knowledge about a robot when interacting with it.
-With continued interaction with the unknown system also the user's expertise with the system grows, and it can be expected that in turn, the user will become able to better predict the previously unknown system.
-Consequently, as the robot becomes more predictable, there is less uncertainty, and the ``need to anthropomorphize'' the robot decreases (from the
+given situation or interaction, one also attempts to correct, adjust, or maybe
+integrate less accessible information into a more automatically activated
+default representation.  This process of refining the applied knowledge are
+natural because a person's knowledge base changes constantly with newly acquired
+things. For instance, a person can acquire new knowledge about a robot when
+interacting with it. With continued interaction with the unknown system also the
+user's expertise with the system grows, and it can be expected that in turn, the
+user will become able to better predict the previously unknown system.
+Consequently, as the robot becomes more predictable, there is less uncertainty,
+and the ``need to anthropomorphize'' the robot decreases (from the
 human-centered point of view).
 
-In other words, humans have a motivation to interact
-effectively in their environment \textit{(effectance)} \citep{epley_when_2008}.
-This means that humans are motivated to be able to understand and predict the
-environment and the agents around them.
-Thus, a person will seek to become familiar with what is unfamiliar.
-Anthropomorphism is encouraged when an agent is unfamiliar.
-Consequently, in the process of familiarizing oneself with an agent, the tendency to anthropomorphize this agent should decrease.
-
-We can not be sure about how exactly the process of familiarization to an unfamiliar agent (based on continued interaction with the robot) looks like.
-In turn, we can not make a precise statement about how continued interaction decreases anthropomorphism but we suspect there is a link between the two.
+In other words, humans have a motivation to interact effectively in their
+environment \textit{(effectance)} \citep{epley_when_2008}.  This means that
+humans are motivated to be able to understand and predict the environment and
+the agents around them. Thus, a person will seek to become familiar with what is
+unfamiliar. Anthropomorphism is encouraged when an agent is unfamiliar.
+Consequently, in the process of familiarizing oneself with an agent, the
+tendency to anthropomorphize this agent should decrease.
+
+We can not be sure about how exactly the process of familiarization to an
+unfamiliar agent (based on continued interaction with the robot) looks like. In
+turn, we can not make a precise statement about how continued interaction
+decreases anthropomorphism but we suspect there is a link between the two.
 
@@
 anthropomorphism that we proposed in section~\ref{sec:anthropomorphism}, we
-introduce in the following section a novel qualitative model of the evolution
-of anthropomorphism over time, \ie a model of the \emph{dynamics of anthropomorphism}.
+introduce in the following section a novel qualitative model of the evolution of
+anthropomorphism over time, \ie a model of the \emph{dynamics of
+anthropomorphism}.
 
@@
 manifestations of anthropomorphism) evolves over a long-term human-robot
-interaction.\footnote{We cannot make a precise statement about how long ``long-term'' interaction has to be to be considered as such.
-It seems to be practical to not speak of ``several days'' or ``weeks'' but to rather consider the duration and frequency of the actual interactions with the artifact.
-One could probably call this the ``interaction history''.}
+interaction.\footnote{We cannot make a precise statement about how long
+``long-term'' interaction has to be to be considered as such. It seems to be
+practical to not speak of ``several days'' or ``weeks'' but to rather consider
+the duration and frequency of the actual interactions with the artifact. One
+could probably call this the ``interaction history''.}
 
@@
 
-In the \emph{Dynamics of Anthropomorphism} model, anthropomorphism is quantified by a \emph{normalized level of
-anthropomorphic effects} $\antNorm[R,H,C,t] = \frac{\ant[R,H,C,t]}{\antMax}$:
-because anthropomorphic effects are often qualitative and difficult to quantify
-on an absolute scale, we present them as a normalized value, that spans from a
-minimum (no anthropomorphic effects: $\ant=0$) to a maximum (noted \AntMax, with
-$t_{max} = \operatorname{arg\,max}_t \, \ant[t]$). For the sake of readability,
-we will use \Ant in the following sections to refer to the normalized level of
-anthropomorphic effects. Note also that we discuss in
-Section~\ref{sec:measuring} possible methodologies for the quantitative and
-qualitative assessment of anthropomorphic effects.
+In the \emph{Dynamics of Anthropomorphism} model, anthropomorphism is quantified
+by a \emph{normalized level of anthropomorphic effects} $\antNorm[R,H,C,t] =
+\frac{\ant[R,H,C,t]}{\antMax}$: because anthropomorphic effects are often
+qualitative and difficult to quantify on an absolute scale, we present them as a
+normalized value, that spans from a minimum (no anthropomorphic effects:
+$\ant=0$) to a maximum (noted \AntMax, with $t_{max} = \operatorname{arg\,max}_t
+\, \ant[t]$). For the sake of readability, we will use \Ant in the following
+sections to refer to the normalized level of anthropomorphic effects. Note also
+that we discuss in Section~\ref{sec:measuring} possible methodologies for the
+quantitative and qualitative assessment of anthropomorphic effects.
 
 The actual maximum value of anthropomorphic effects depends on each unique
-combination of a human, a robot, a situation and several other factors we introduce below.
-Thus, the maximum value varies according to the specific characteristics of these factors.
-Figure~\ref{fig:dynamics} pictures this maximum value at
-$t_{max}$, which actually corresponds to what we call the novelty effect peak.\footnote{We assume that there is a peak in the human's experiences of the novelty effects of the unfamiliar system.
-Further, we suspect that this novelty peak comes along with the maximum value of anthropomorphic effects.}
- The general
-\emph{shape} of the curve remains however the same and depicts the evolution of
-anthropomorphism over time, \ie the general dynamics of anthropomorphism.
+combination of a human, a robot, a situation and several other factors we
+introduce below. Thus, the maximum value varies according to the specific
+characteristics of these factors. Figure~\ref{fig:dynamics} pictures this
+maximum value at $t_{max}$, which actually corresponds to what we call the
+novelty effect peak.\footnote{We assume that there is a peak in the human's
+experiences of the novelty effects of the unfamiliar system. Further, we suspect
+that this novelty peak comes along with the maximum value of anthropomorphic
+effects.} The general \emph{shape} of the curve remains however the same and
+depicts the evolution of anthropomorphism over time, \ie the general dynamics of
+anthropomorphism.
 
@@
     level of anthropomorphism} (SLA, noted \SLA). \ICA and \SLA may vary
-    depending on the user (and his/her expectations), the robot and the context of interaction.  During the
-    interaction, unpredicted behaviors of the robot (\emph{disruptive
-    behaviors}) may lead to local increases or decreases of the level of
-    anthropomorphic effects.}
+    depending on the user (and his/her expectations), the robot and the context
+    of interaction.  During the interaction, unpredicted behaviors of the robot
+    (\emph{disruptive behaviors}) may lead to local increases or decreases of
+    the level of anthropomorphic effects.}
 
@@
 
-The \emph{initial capital of anthropomorphism} \ICA describes the initial potential
-for the robot to be anthropomorphized by the human user in a given situation.
-This potential depends on several factors, introduced in
-section~\ref{sec:multi-factors}, see also Figure \ref{fig:factors}. It has been shown, for instance, that
-some \textit{people} tend to anthropomorphize more than others, that some
-\textit{situations} induce anthropomorphism more than others, that
-\textit{children} tend to anthropomorphize more than adults, and that some
-\textit{cultures} are notorious for their anthropomorphic religions and
-worldviews~\citep{epley_when_2008}. Also the shape and design of the robot play a
-role, as well as the context in which the interaction takes place. Our model of
-anthropomorphism represents these factors as a compound metric \ICA. As such,
-\ICA describes the level of anthropomorphic projections just prior the first
-(real or imagined) interaction with a robot. In this stage of pre-interaction, people
-form \textbf{initial expectations} toward the robot and imagine how they will use it /
-interact with it.
-
-Taking up on our suggestion to have four main factors that impact on anthropomorphism, we propose that the initial capital of anthropomorphism can be build \emph{a priori}.
-As the \ICA marks the very moment before the first real or imagined contact of the human with the robot, the \textit{interaction history} between the two players is empty; consequently the time factor $t$ is not taken into account when building the \ICA.
-The specific \ICA value reflects how far a robot is likely to be anthropomorphized, based on the following three factors:
+The \emph{initial capital of anthropomorphism} \ICA describes the initial
+potential for the robot to be anthropomorphized by the human user in a given
+situation.  This potential depends on several factors, introduced in
+section~\ref{sec:multi-factors}, see also Figure \ref{fig:factors}. It has been
+shown, for instance, that some \textit{people} tend to anthropomorphize more
+than others, that some \textit{situations} induce anthropomorphism more than
+others, that \textit{children} tend to anthropomorphize more than adults, and
+that some \textit{cultures} are notorious for their anthropomorphic religions
+and worldviews~\citep{epley_when_2008}. Also the shape and design of the robot
+play a role, as well as the context in which the interaction takes place. Our
+model of anthropomorphism represents these factors as a compound metric \ICA. As
+such, \ICA describes the level of anthropomorphic projections just prior the
+first (real or imagined) interaction with a robot. In this stage of
+pre-interaction, people form \textbf{initial expectations} toward the robot and
+imagine how they will use it / interact with it.
+
+Taking up on our suggestion to have four main factors that impact on
+anthropomorphism, we propose that the initial capital of anthropomorphism can be
+build \emph{a priori}.  As the \ICA marks the very moment before the first real
+or imagined contact of the human with the robot, the \textit{interaction
+history} between the two players is empty; consequently the time factor $t$ is
+not taken into account when building the \ICA.  The specific \ICA value reflects
+how far a robot is likely to be anthropomorphized, based on the following three
+factors:
 
@@
 
-For \textbf{personality}, we suggest to apply the
-psychological \textit{3-factor theory} of anthropomorphism by \citet{epley_seeing_2007}. For instance,
-children generally tend to anthropomorphize objects more than adults. Also, a
-person who lacks social connection is said to be more likely to
-anthropomorphize. Both aspects would increase \ICA. This means that, one and the
-same robot used by a different user, can lead to a different \ICA.
+For \textbf{personality}, we suggest to apply the psychological \textit{3-factor
+theory} of anthropomorphism by \citet{epley_seeing_2007}. For instance, children
+generally tend to anthropomorphize objects more than adults. Also, a person who
+lacks social connection is said to be more likely to anthropomorphize. Both
+aspects would increase \ICA. This means that, one and the same robot used by a
+different user, can lead to a different \ICA.
 
 For \textbf{design}, we understand that a robot that follows an anthropomorphic
-design up to a certain acceptable level (\eg Nao) leads to a higher \ICA than a rather functional robot (\eg
-Roomba). Also, a robot that is able to display facial expressions would increase
-the \ICA. Quantifying the \emph{level} of anthropomorphic design in a robot, as
-suggested for instance by \citet{fong_survey_2003}, can be difficult.
-Nevertheless, the important aspect is how the robot appears to the user, \eg
-human-like or machine-like, acceptable or not-acceptable.\footnote{It becomes clear that the \textit{robot factor} can not be fully separated from the \textit{human factor}.
-The reason for this is that the message that design tries to make, always lies in the eye of the beholder.
-No matter how much effort a designer spends in making the ``message'' of the artifact's design clear, there is always some scope and creative freedom in how the design is interpreted by the beholder.}
+design up to a certain acceptable level (\eg Nao) leads to a higher \ICA than a
+rather functional robot (\eg Roomba). Also, a robot that is able to display
+facial expressions would increase the \ICA. Quantifying the \emph{level} of
+anthropomorphic design in a robot, as suggested for instance by
+\citet{fong_survey_2003}, can be difficult.  Nevertheless, the important aspect
+is how the robot appears to the user, \eg human-like or machine-like, acceptable
+or not-acceptable.\footnote{It becomes clear that the \textit{robot factor} can
+not be fully separated from the \textit{human factor}. The reason for this is
+that the message that design tries to make, always lies in the eye of the
+beholder. No matter how much effort a designer spends in making the ``message''
+of the artifact's design clear, there is always some scope and creative freedom
+in how the design is interpreted by the beholder.}
 
 By taking the \textbf{purpose} of a robot into account, we suggest that the real
-or imagined application context of the robot, or in which situation the interaction occurs, impacts how far the robot will be attributed human-like
-characteristics. We draw on findings such as presented in \citet{joosse_what_2013}. The authors showed for instance that when the
-same robot (Nao) is used in a different task context (cleaning task \emph{vs.}
-tour guide), users ascribe different personalities to the robot. In general,
-a robot which is imagined in a social, entertaining or playful
-context leads to a higher \ICA than a robot which is used for a routine or
-focused task (security, rescue, etc.).
-This was also found in an analysis of anthropomorphic language in online forum discussions about the AIBO, Roomba, and iPad \citep{fink_anthropomorphic_2012}.
-Regardless of the conversation topic, more anthropomorphic language was found in the AIBO forum.
-However, this was not only due to the zoomorphic (pet-like) shape of AIBO but also due to its  playful purpose.
-The idea that the purpose of a robot are crucial factors, also receives support from
-Goetz \& Kiesler's work that revealed that people prefer a serious robot for
-serious tasks and a less serious robot for more playful
-tasks~\citep{goetz_cooperation_2002, goetz_matching_2003}.
-However, what about artificial agents that seem to have no purpose?
-\cite{kaplan_free_2000} discusses the role of uselessness in the design of robots.
-He argues that artificial pets such as the AIBO, have no real purpose, in a sense that they do not provide any kind of service, or, in other words \textit{``they are not doing what you tell them to do''} and \textit{``they might refuse the order of its owner''}.
-It is this very aspect that might increase people's tendency to anthropomorphize the robot.
-According to Kaplan, it is in our daily use language, that we tend to attribute intentions to devices that are not doing their job well.
-For instance, we do not develop any kind of relationship with our computer, washing machine or TV set when they work properly.
-The author argues that it is only when they start dis-functioning, when they show that they can act differently that what we ordered, that we are ready to give them some kind of ``intentionality''.
-
- Also, we suggest that
-the environmental context in which people experience and interact with the robot
-impacts the \ICA. For instance, several friends interacting simultaneously with
-the robot might lead to increased \ICA for each of the users, due to increased
-human-human social interactions (the robot might be perceived to be part of the
-social interaction, and in turn attributed human-like
-qualities~\citep{baxter2013do}).
+or imagined application context of the robot, or in which situation the
+interaction occurs, impacts how far the robot will be attributed human-like
+characteristics. We draw on findings such as presented in
+\citet{joosse_what_2013}. The authors showed for instance that when the same
+robot (Nao) is used in a different task context (cleaning task \emph{vs.} tour
+guide), users ascribe different personalities to the robot. In general, a robot
+which is imagined in a social, entertaining or playful context leads to a higher
+\ICA than a robot which is used for a routine or focused task (security, rescue,
+etc.). This was also found in an analysis of anthropomorphic language in online
+forum discussions about the AIBO, Roomba, and iPad
+\citep{fink_anthropomorphic_2012}. Regardless of the conversation topic, more
+anthropomorphic language was found in the AIBO forum. However, this was not only
+due to the zoomorphic (pet-like) shape of AIBO but also due to its  playful
+purpose. The idea that the purpose of a robot are crucial factors, also receives
+support from Goetz \& Kiesler's work that revealed that people prefer a serious
+robot for serious tasks and a less serious robot for more playful
+tasks~\citep{goetz_cooperation_2002, goetz_matching_2003}.  However, what about
+artificial agents that seem to have no purpose? \cite{kaplan_free_2000}
+discusses the role of uselessness in the design of robots. He argues that
+artificial pets such as the AIBO, have no real purpose, in a sense that they do
+not provide any kind of service, or, in other words \textit{``they are not doing
+what you tell them to do''} and \textit{``they might refuse the order of its
+owner''}. It is this very aspect that might increase people's tendency to
+anthropomorphize the robot. According to Kaplan, it is in our daily use
+language, that we tend to attribute intentions to devices that are not doing
+their job well. For instance, we do not develop any kind of relationship with
+our computer, washing machine or TV set when they work properly. The author
+argues that it is only when they start dis-functioning, when they show that they
+can act differently that what we ordered, that we are ready to give them some
+kind of ``intentionality''.
+
+Also, we suggest that the environmental context in which people experience and
+interact with the robot impacts the \ICA. For instance, several friends
+interacting simultaneously with the robot might lead to increased \ICA for each
+of the users, due to increased human-human social interactions (the robot might
+be perceived to be part of the social interaction, and in turn attributed
+human-like qualities~\citep{baxter2013do}).
 
@@
 
-We assume that the short phase of initialization is strongly affected by the so-called novelty effect.
-Novelty effects have been described with interactive technologies in general \citep{rogers_diffusion_1995} and also in several long-term HRI studies in workplaces \citep{huttenrauch_fetch-and-carry_2003,mutlu_robots_2008}, in schools and public places \citep{gockley_designing_2005,kanda_interactive_2004,kanda_communication_2005}, or elder care centers \citep{sabelli_conversational_2011}.
-Further, also with domestic robots it has been found that people's interest, engagement, and fascination with the robot decreased over time \citep{fink_living_2013,fernaeus_how_2010,sung_robots_2009}.
+We assume that the short phase of initialization is strongly affected by the
+so-called novelty effect.  Novelty effects have been described with interactive
+technologies in general \citep{rogers_diffusion_1995} and also in several
+long-term HRI studies in workplaces
+\citep{huttenrauch_fetch-and-carry_2003,mutlu_robots_2008}, in schools and
+public places
+\citep{gockley_designing_2005,kanda_interactive_2004,kanda_communication_2005},
+or elder care centers \citep{sabelli_conversational_2011}. Further, also with
+domestic robots it has been found that people's interest, engagement, and
+fascination with the robot decreased over time
+\citep{fink_living_2013,fernaeus_how_2010,sung_robots_2009}.
 
@@
 present an example from our long-term ethnographic study with Roomba vacuum
-cleaning robots in households \citep{fink_living_2013}. The observed scenario describes how an elderly
-woman (E., 71 years, living on her own with a little dog in a small row house) was
-setting up and using the robot for the first time during about 10 minutes.
-
-%The woman (E.) is reading aloud parts of the ``quick start manual'': \emph{``When
-%Roomba senses dirt, the blue dirt detect light is lit and Roomba cleans more
-%intensely in that area.''} She laughs and turns to the robot, talking directly to
-%it \emph{``Today you can light up darling!''}. E. carries the Roomba to the entrance
-%door and puts it on the floor [floor type: tiles, partially covered with little
-%Persian carpets], she explains \emph{``It has to start from here, this is where
-%you enter the house!''}. After pressing the CLEAN button, the robot quickly gets
-%stuck with the carpet in the entrance hall, consequently it reports error 1 [
-%two-tone \textit{``uh-oh''} sound followed by a narrated voice that starts off with \textit{``error
-%1''}]. E. is very surprised \emph{``What, it is even talking to me?''}, she lifts the
-%robot off and puts it back for cleaning.
-At several occasions, while watching
-how the robot moves around and cleans, E. makes compliments to the robot:
-\emph{``Nice!''} or \emph{``Good job!''} or \emph{``Bravo!''}. Once, when the Roomba turns
-right in front of some crumbs on the kitchen floor and moves away without
-cleaning them up, E. says: \emph{``There you forgot something, what about over
-there? Look, there you still have something to clean up!''}, and she points at
-where she wants the Roomba to go. Further, she uses deictic gestures and tells the
-robot: \emph{``No, go this way! Come over here!''}. The woman keeps observing the
-robot and wonders about its intentions, asking it directly: \emph{``Why do you
-leave the kitchen? There is still something there on the fringe!''}. E. turns to
-the experimenter, and tells her: \emph{``She [the robot] loves the hall!''}.
+cleaning robots in households \citep{fink_living_2013}. The observed scenario
+describes how an elderly woman (E., 71 years, living on her own with a little
+dog in a small row house) was setting up and using the robot for the first time
+during about 10 minutes.
+
+At several occasions, while watching how the robot moves around and cleans, E.
+makes compliments to the robot: \emph{``Nice!''} or \emph{``Good job!''} or
+\emph{``Bravo!''}. Once, when the Roomba turns right in front of some crumbs on
+the kitchen floor and moves away without cleaning them up, E. says:
+\emph{``There you forgot something, what about over there? Look, there you still
+have something to clean up!''}, and she points at where she wants the Roomba to
+go. Further, she uses deictic gestures and tells the robot: \emph{``No, go this
+way! Come over here!''}. The woman keeps observing the robot and wonders about
+its intentions, asking it directly: \emph{``Why do you leave the kitchen? There
+is still something there on the fringe!''}. E. turns to the experimenter, and
+tells her: \emph{``She [the robot] loves the hall!''}.
 
@@
 talking directly to the robot, or asking it questions (though it doesn't
-recognize speech); giving it nick-names or ascribing a gender, praising the robot, using pointing
-gestures toward the robot, or trying to direct it around with commands, and attributing
-a personal preference / intention to the robot (\emph{``she loves the hall!''}).
+recognize speech); giving it nick-names or ascribing a gender, praising the
+robot, using pointing gestures toward the robot, or trying to direct it around
+with commands, and attributing a personal preference / intention to the robot
+(\emph{``she loves the hall!''}).
 
@@
 anymore, and generally behaved in a less anthropomorphizing way. The observed
-effects were likely due to the novelty of the robot, and the fact that E. was not familiar with the robot and its behavior.
-As \cite{persson_anthropomorphism_2000} names it: \textit{``Anthropomorphism is a way of making sense of complex behavior in the world around us.''} Thus, as soon as this complexity is reduced, also anthropomorphism might be reduced.
+effects were likely due to the novelty of the robot, and the fact that E. was
+not familiar with the robot and its behavior.  As
+\cite{persson_anthropomorphism_2000} names it: \textit{``Anthropomorphism is a
+way of making sense of complex behavior in the world around us.''} Thus, as soon
+as this complexity is reduced, also anthropomorphism might be reduced.
 
@@
 By \emph{disruptive behaviors}, we mean any behavior exhibited by the robot that
-appears unexpected to the user: for instance, a robot may usually follow always the
-same route to go from one place in a house to the other, but suddenly it might change the
-route. The actual underlying reason may span from a bug to the detection of a
-new obstacle, but as long as this reason is not immediately
-intelligible to the user, the behavior counts as \emph{disruptive}. (We will come back to the role of disruptive behaviors later, in Section \ref{sec:disruptive}.)
+appears unexpected to the user: for instance, a robot may usually follow always
+the same route to go from one place in a house to the other, but suddenly it
+might change the route. The actual underlying reason may span from a bug to the
+detection of a new obstacle, but as long as this reason is not immediately
+intelligible to the user, the behavior counts as \emph{disruptive}. (We will
+come back to the role of disruptive behaviors later, in Section
+\ref{sec:disruptive}.)
 
@@
 
-To illustrate how a disruptive behavior of a robot can evoke anthropomorphic effects, we present again an example from our long-term ethnographic study with Roomba vacuum cleaning robots in households \citep{fink_living_2013}.
-The observed scenario describes how a family (young parents, 26 and 28 years old, with 3 little children, 5 and 4 years, and 6 months old, living in a house with garden on the countryside) were using the robot during the first week.
-
-The father (M.) always lets Roomba clean up the ground floor after the family finishes dinner and they all go upstairs to put the children to bed.
-When the robot would have finished its cleaning cycle, the parents would later just find it docked at its charging station.
-It used to be like this every evening.
+To illustrate how a disruptive behavior of a robot can evoke anthropomorphic
+effects, we present again an example from our long-term ethnographic study with
+Roomba vacuum cleaning robots in households \citep{fink_living_2013}. The
+observed scenario describes how a family (young parents, 26 and 28 years old,
+with 3 little children, 5 and 4 years, and 6 months old, living in a house with
+garden on the countryside) were using the robot during the first week.
+
+The father (M.) always lets Roomba clean up the ground floor after the family
+finishes dinner and they all go upstairs to put the children to bed. When the
+robot would have finished its cleaning cycle, the parents would later just find
+it docked at its charging station. It used to be like this every evening.
 However, one day when the father comes downstairs, Roomba is not at its station.
-He says: \emph{``Hey, Roomba, where are you?
-Why did you not want to got to sleep last night?''}.
-After some searching he found it stuck under the sofa and wondered why this had happened.
-
-What is the observed anthropomorphic effect in this scenario?
-Usually, the father did not talk to the robot or praise it.
-However, now that the robot did something unexpected (it was not at its usual place) he started wondering about its ``intention'' and directly asked the robot for its reasons to not \textit{``go to sleep''}.
+He says: \emph{``Hey, Roomba, where are you? Why did you not want to got to
+sleep last night?''}. After some searching he found it stuck under the sofa and
+wondered why this had happened.
+
+What is the observed anthropomorphic effect in this scenario? Usually, the
+father did not talk to the robot or praise it. However, now that the robot did
+something unexpected (it was not at its usual place) he started wondering about
+its ``intention'' and directly asked the robot for its reasons to not
+\textit{``go to sleep''}.
 
@@
 
-The \emph{Stabilized Level of Anthropomorphism} describes the long-term lasting level of
-anthropomorphism.
-We proposed that \ICA is built on three factors: user's \emph{personality},
-robot's \emph{design} and interaction \emph{purpose} (or \emph{interaction
-context}). The user's personality and the context of use do also influence \SLA.
-In particular, it appears that the user's level of acquaintance with
-technologies plays an important role in long-term tendency to
+The \emph{Stabilized Level of Anthropomorphism} describes the long-term lasting
+level of anthropomorphism.  We proposed that \ICA is built on three factors:
+user's \emph{personality}, robot's \emph{design} and interaction \emph{purpose}
+(or \emph{interaction context}). The user's personality and the context of use
+do also influence \SLA.  In particular, it appears that the user's level of
+acquaintance with technologies plays an important role in long-term tendency to
 anthropomorphize~\citep{fink_living_2013} (people more familiar with technology
@@
 
-%\fixme{JF: Severin, we should at some point mention what the ``expectation mismatch'' is ...
-I haven't found that so far ...
-but I am also not sure about how to explain this.
-I think that, the we already took into account the user's expectations in the human-factor.}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 behaviors (section~\ref{sec:disruptive}) on mutual modeling, and how our models
-relate to the \emph{in-the-moment} versus \emph{reflective} perspectives on agency in HRI~\citep{takayama_perspectives_2012}.
-
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%    Review of neuroscience work on robot-based 
-%    anthropomorphism..... may be moved somewhere 
-%    else or dispatched
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%From the human point of view, what are the brain mechanisms that could mediate anthropomorphism towards robots ?
-%\subsection{Neuroscience review of anthropomorphic brain mechanisms in human-robot interaction}
-%The neuroscientific study of human-robot interaction is still in its infancy.
-So far most studies have used robots as a way to investigate humans behaviour and brain responses to perception of an artefactual agent actions and emotional states but have not really tapped in the study of how a human behaviours and brain processes are influenced by its direct interaction with a robot (add ref, ref).
-%We briefly review below the neuroscientific literature relevant to understand
-%the neural mechanisms that may underly anthropomorphism. 
-%
-%
-%
-%\paragraph{Mirror neurons and resonnance behaviors \\}
-%
-%Resonnance behaviors \citep{Rizzolatti1999} are mechanisms by which the brain areas involved in the internal representations of an action, an emotion or a sensation are equally recruited during the perception of another individual performing the same action or experiencing the same emotion or sensation.
-%
-%Resonnance behaviors have first been shown in the motor mirror neurons system, that is a neural network in motor areas that fire both during the execution of specific goal-oriented action and during the viewing of action directed toward the same goal~\cite{Rizzolatti1996, Kilner2009}.
-%
-%Interestingly, there are good evidence showing that motor mirror neurons in the
-%human brain respond to both human and robotic motion \citet{Gazzola2007, oberman_eeg_2007}, stressing that perceiving the goal of an action is more important than the human-likeness of its kinematic to activate resonnance mechanisms.
-%%For example, fMRI study \citet{Gazzola2007} have found no significant difference in the activation of the mirror neurons system during the observation of an industrial robot or of a human performing the same action, suggesting that the goal of the action is more important than its kinematics to activate resonnance mechanisms.
-%mirror neurons
-%
-%%[At stage 1] We suggest that the human's mirror neuron system is contributing to anthropomorphism by  allowing for a mapping of the robot's goal-directed actions into the human own motor repertoire \cite{Gallese1998, Wolpert2003, cullen2013individual}.
-%
-%The response of the human brain to a social signal perceived on a robot, such as facial
-%emotional expression is less evident. 
-%
-%In studying emotional perception in a human or a robot face using functional
-%magnetic resonnance imagery (fMRI) \citet{Chaminade2010} found reduced activity
-%in response to the robot stimuli than to the human stimuli in emotional brain
-%areas known to have mirror properties. However if the subject was asked to
-%specifically attend to the emotional content of the stimuli, processing of the
-%robot facial expresion, but not of the human's, elicited a significant increase in the anterior part of the anterior frontal gyrus, a brain area considered as a marker of motor resonnance.
-%
-%Using electroencephalograpy another study have found that perception of emotions in a non-humanoid robot face affects the early brain processes of emotional expressions and the behavioral response of the participants the same way as did a human face \citep{Dubal2010}.
-%
-%
-%
-%Thus it seems that the display of resonance mechanisms for social behaviour when
-%viewing a robot is less straightforward than for motor behaviour and may dependent more on the internal attitude and cognitive conceptions the human has of the robot. 
-%%Brain areas involved when attributing mental states to other human seem to be involved also in anthropomorphism .
-Indeed, individual scores of anthropomorphisms have been found to correlate with the grey matter volume of the left temporoparietal junction, a brain area activared during mentalizing \citet{cullen2013individual}
-%However, the studies reviewed above show that the human brain can respond
-%equally to a human or a robot stimuli but they do not  directly address the
-%question of anthropomorphism. Indeed, although it can contribute to it, neither
-%activation of mirror neurons system simulating a perceived action nor influence
-%on early brain processies readily imply that the human confers a humanlike mental
-%state to the robot and thus can not be sufficient to infer anthropomorphism 
-%
-%
-%%\citet{Dubal2010}: using robots with anthropomorphic (eyes, nose, mouth) featres but not human-like (ie.
-wires and cables) the study show effect of emotional state of the robot on early brain processes of emotional expression using ERPs (enhanced P1 in happy vs neutral state).
-%
-%\paragraph{Neural correlates of theory of mind and antropomorphism\\}
-%
-%
-%%From an early age, humans develop a tendency to explain one's own and others'actions in terms of beliefs, desires and goals called theory of mind or mentalizing allowing the implicit attribution of intentions and other mental states to others \citep{Frith2003}.
-%%A system of brain areas have been linked to mentalizing that encompass an anterior region of the medial prefrontal cortex (MPFC), that may be the basis to distinguish between mental and physical states representation, the temporal lobes, that may allow access to social knowledge  and the posterior superior temporal sulctuc (STS), that might be involved in detection of agency \citep{Frith2003}.
-%In a more direct study of anthropomorphism, \citep{cullen2013individual} related
-%participant's scores of tendency to anthropomorphize to the grey matter
-%volume of the left temporal junction, a brain area involved in mentalizing,
-%that is the attribution of mental states to other human beings (theory of mind) \citep{Frith2003}. 
-%
-%Of note, \citet{Waytz2010} showed that the more an artifical agent behaved
-%unpredictably, the more subjects tend to attribute it a mind and the more the
-%ventro medial prefrontal cortex (VMPFC), key area for sociocognitve processes
-%and especially egocentric mentalizing about similar others, gets activated.
-%
-%
-%%\paragraph{Emotions/Empathy}
-%%Attitude of the human in a human-robot interaction might influence the anthropomorphic quality of the interaction: \citet{Chaminade2010} shows that directing attention towards emotional processing increases the responses to humanoid robot facial expression in the anteriror part of the left anterior frontal gyrus, a neural marker of motor resonnance.
-%
-% 
-%
-%
-%In the following section, we provide a tentative model of anthropomorphism in terms of cognitive correlates.
-We warmly welcome the feedback and comments from both the cognitive sciences and robotics communities to further
-%discuss these findings.
-%
-%
+relate to the \emph{in-the-moment} versus \emph{reflective} perspectives on
+agency in HRI~\citep{takayama_perspectives_2012}.
 
@@
 
-We propose three different cognitive stages (Figure~\ref{fig:cognitivemodel}), which are not mutually exclusive but overlap over time.
-Note that these three cognitive stages are related but do not exactly match the
-\emph{Initialization}, \emph{Familiarization} and \emph{Stabilization} phases
-introduced in our model of the dynamics of anthropomorphism.
+We propose three different cognitive stages (Figure~\ref{fig:cognitivemodel}),
+which are not mutually exclusive but overlap over time. Note that these three
+cognitive stages are related but do not exactly match the \emph{Initialization},
+\emph{Familiarization} and \emph{Stabilization} phases introduced in our model
+of the dynamics of anthropomorphism.
 
@@
 
-The intuitive anthropomorphization in the cognitive Stage 1 might be characteristic of what \cite{takayama_perspectives_2012} calls the \textit{in-the-moment} perspective on agency with a robot compared to the \textit{reflective} perspective (see paragraph ``artifact-centered perspective'' in Section \ref{sec:anthropomorphism}).
-For instance, we reflectively
-might \textit{not} perceive agency in a social robot, but it can feel quite differently
-in the moment of interaction. \cite{takayama_perspectives_2012}
+The intuitive anthropomorphization in the cognitive Stage 1 might be
+characteristic of what \cite{takayama_perspectives_2012} calls the
+\textit{in-the-moment} perspective on agency with a robot compared to the
+\textit{reflective} perspective (see paragraph ``artifact-centered perspective''
+in Section \ref{sec:anthropomorphism}).  For instance, we reflectively might
+\textit{not} perceive agency in a social robot, but it can feel quite
+differently in the moment of interaction. \cite{takayama_perspectives_2012}
 argues that neglecting to separate reflective perspectives from in-the-moment
@@
 consciously perceive. That means, in the initial phase of interacting with a
-novel device \textit{(initialization)} (see Figure \ref{fig:dynamics}) people might not respond consciously but
-rather mindlessly \citep{nass_machines_2000}, and in turn anthropomorphize more.
-Only after some time of
-\textit{familiarization}, they might respond in a more reflective manner (in turn, the tendency to anthropomorphize might decrease). This
-can be illustrated by the fact that people tend to deny interacting with
-computational systems as if they were people and yet they respond to computers
-in many ways that are remarkably similar to how they respond to people
-\citep{reeves_media_1996}. \cite{takayama_perspectives_2012} also applies a
-cognitive viewpoint on the two different perspectives of in-the-moment \vs
-reflective to illustrate differences. She states that in-the-moment perceptions
-of agency are largely shaped by bottom-up perceptual processes, evoking very
-immediate responses (\eg to the cues emitted by the artifact's design (``artifact-centered perspective''). In contrast, according to Takayama,
-reflective perceptions are more often shaped by top-down processes because of
-the nature of reflective thought.
-
-%We suggest that the human's mirror neuron system is contributing to
-%anthropomorphism by  allowing for a mapping of the robot's goal-directed
-%actions into the human own motor repertoire \cite{Gallese1998, Wolpert2003,
-%cullen2013individual}.
-
-%mediated by the motor and emotional resonnance mechanisms at the neuronal level.
+novel device \textit{(initialization)} (see Figure \ref{fig:dynamics}) people
+might not respond consciously but rather mindlessly \citep{nass_machines_2000},
+and in turn anthropomorphize more.  Only after some time of
+\textit{familiarization}, they might respond in a more reflective manner (in
+turn, the tendency to anthropomorphize might decrease). This can be illustrated
+by the fact that people tend to deny interacting with computational systems as
+if they were people and yet they respond to computers in many ways that are
+remarkably similar to how they respond to people \citep{reeves_media_1996}.
+\cite{takayama_perspectives_2012} also applies a cognitive viewpoint on the two
+different perspectives of in-the-moment \vs reflective to illustrate
+differences. She states that in-the-moment perceptions of agency are largely
+shaped by bottom-up perceptual processes, evoking very immediate responses (\eg
+to the cues emitted by the artifact's design (``artifact-centered
+perspective''). In contrast, according to Takayama, reflective perceptions are
+more often shaped by top-down processes because of the nature of reflective
+thought.
 
@@
 
-This mental process depends on the human understanding of the robot's
-inner working, as well as his/her own tendency to anthropomorphize (the
-\emph{personality} in ICA factor), but at this
-stage, the \emph{perception} of the robot (its shape for instance) and its
-intended \emph{purpose} play a less important role. It is mostly a human-centric
-process.  The result of this third phase would be an iteratively adapted
-cognitive model of the robot. It is also at this last stage that the human might have a
-modified tendency to anthropomorphize, because he/she has built a full cognitive
-model of the robot. Consequently, the human would now be able to attribute appropriate internal states to the robot
-through his/her theory of mind.
+This mental process depends on the human understanding of the robot's inner
+working, as well as his/her own tendency to anthropomorphize (the
+\emph{personality} in ICA factor), but at this stage, the \emph{perception} of
+the robot (its shape for instance) and its intended \emph{purpose} play a less
+important role. It is mostly a human-centric process.  The result of this third
+phase would be an iteratively adapted cognitive model of the robot. It is also
+at this last stage that the human might have a modified tendency to
+anthropomorphize, because he/she has built a full cognitive model of the robot.
+Consequently, the human would now be able to attribute appropriate internal
+states to the robot through his/her theory of mind.
 
@@
 
-As mentioned before, the three cognitive stages proposed here do not match with the three phases in the \emph{Dynamics of Anthropomorphism}.
-In particular,
-the cognitive Stages 1 and 2 are both included in the \emph{initialization} phase
-of the anthropomorphism model. Sub-cognitive anthropomorphism typically
+As mentioned before, the three cognitive stages proposed here do not match with
+the three phases in the \emph{Dynamics of Anthropomorphism}.  In particular, the
+cognitive Stages 1 and 2 are both included in the \emph{initialization} phase of
+the anthropomorphism model. Sub-cognitive anthropomorphism typically
 \emph{initiates} the novelty effect by rapidly engaging the human in the
@@
 
-Another way to think of the three proposed cognitive stages is to relate them to the \textbf{user experience} which is characteristic of these three stages.
-For instance, \cite{norman_emotional_2003} characterizes  three user experience dimensions (related to emotional attachment), which occur when people use or see a product for the first time: \emph{(1)} the \emph{visceral level}, which is the first impression of a product based on its experience; at this level people do not think about a product but make spontaneous judgments; \emph{(2)} the \emph{behavioral level}, in which people use and experience the product, appraise its functions, and consider aspects such as usefulness and usability; \emph{(3)} the \emph{reflective level}, in which consciousness takes part in the process, and past experiences are taken into account.
-In a study which was carried out in a shopping mall, \cite{weiss_i_2009} explored the emotional attachment during first time reactions of children and adults with the robotic dog AIBO.
-The authors also argue that it is important to understand the long-term development of people's social bonds to robots.
+Another way to think of the three proposed cognitive stages is to relate them to
+the \textbf{user experience} which is characteristic of these three stages. For
+instance, \cite{norman_emotional_2003} characterizes  three user experience
+dimensions (related to emotional attachment), which occur when people use or see
+a product for the first time: \emph{(1)} the \emph{visceral level}, which is the
+first impression of a product based on its experience; at this level people do
+not think about a product but make spontaneous judgments; \emph{(2)} the
+\emph{behavioral level}, in which people use and experience the product,
+appraise its functions, and consider aspects such as usefulness and usability;
+\emph{(3)} the \emph{reflective level}, in which consciousness takes part in the
+process, and past experiences are taken into account.  In a study which was
+carried out in a shopping mall, \cite{weiss_i_2009} explored the emotional
+attachment during first time reactions of children and adults with the robotic
+dog AIBO. The authors also argue that it is important to understand the
+long-term development of people's social bonds to robots.
 
@@
 shows that unexpected behaviors of the robot can have a notable impact on
-interaction. This is supported by the results from~\citet{Waytz2010}, mentioned in section
-\ref{sec:cognitive-expl}, that show that people attribute more easily
+interaction. This is supported by the results from~\citet{Waytz2010}, mentioned
+in section \ref{sec:cognitive-expl}, that show that people attribute more easily
 anthropomorphic features to artifacts when they have unpredictable behaviors.
-Also \cite{short_no_2010} found that variations in a robot's behavior (such that it is unexpected) influence people's attribution of mental states and intentionality to a robot.
-Participants who were playing the ``rock-paper-scissors'' game with a robot that tried to cheat (either verbally or in its action), displayed a greater level of social engagement and made greater attributions of mental states.
-However, an unexpected (disruptive) robot behavior might also have a negative effect on user's engagement with the robot.
-For instance, when the user interprets the robot's behavior as a failure, he/she might lose trust in the robot.
-\cite{desai_impact_2013} found that in an interaction scenario, especially early failures of the robot can cause a dramatically lower real-time trust, compared to middle or late drops of reliability of the robot.
+Also \cite{short_no_2010} found that variations in a robot's behavior (such that
+it is unexpected) influence people's attribution of mental states and
+intentionality to a robot. Participants who were playing the
+``rock-paper-scissors'' game with a robot that tried to cheat (either verbally
+or in its action), displayed a greater level of social engagement and made
+greater attributions of mental states.  However, an unexpected (disruptive)
+robot behavior might also have a negative effect on user's engagement with the
+robot. For instance, when the user interprets the robot's behavior as a failure,
+he/she might lose trust in the robot. \cite{desai_impact_2013} found that in an
+interaction scenario, especially early failures of the robot can cause a
+dramatically lower real-time trust, compared to middle or late drops of
+reliability of the robot.
 
@@
 spikes in Figure~\ref{fig:dynamics}).
-
-%\begin{figure}\footnotesize
-%    \centering
-%    \begin{tabular}{  >{\centering\arraybackslash}m{2cm} | >{\centering\arraybackslash}m{2cm} | >{\centering\arraybackslash}m{2cm} }
-%     & Unplanned by the robot & Planned by the robot \\ \hline
-%    Perceived as non-intentional & case I  & case IIIa  \\ \hline
-%    Perceived as intentional &  case IIIb & case II 
-%    \end{tabular}
-%\caption{
-%    Behaviors of the robot that are unexpected by the user may be intentional
-%    (the robot has planned the behavior) or not (typically, a failure:
-%    misdetection, bug,...). Independently of that, the behavior may be
-%    \emph{perceived} by the user as intentional or not.}
-%\label{fig:perceptionUnexpectedBehavior}
-%\end{figure}
 
@@
 explicitly states its failure (for instance, by saying ``I'm lost!''), the
-behavior is then called \emph{transparent} \citep{kim_who_2006}, and the user may hypothesize that the
-robot has \emph{introspective} capabilities (it can reflect on its own internal
-state), which may lead to higher anthropomorphic projections.  On the
-contrary, if the robot shows no sign of recognizing its own failure, the user
-may ascribe a lower level of anthropomorphism to the robot.
+behavior is then called \emph{transparent} \citep{kim_who_2006}, and the user
+may hypothesize that the robot has \emph{introspective} capabilities (it can
+reflect on its own internal state), which may lead to higher anthropomorphic
+projections.  On the contrary, if the robot shows no sign of recognizing its own
+failure, the user may ascribe a lower level of anthropomorphism to the robot.
 
@@
 saying ``I do not want to go there''. In that case, we expect to see an increase
-of attribution of anthropomorphism due to the human ascribing intentionality to the
-robot.
+of attribution of anthropomorphism due to the human ascribing intentionality to
+the robot.
 
@@
 
-%% experience -> unexpected behavior should not impact the interaction child-robot BEFORE the theory of mind is established!
-
-%\subsection{\emph{In-the-moment} versus \emph{Reflective} perspectives}
-%
-%\fxwarning{SL: Bridge + integration in the section 4 TDB}
-%
-%\hl{(we actually assume that
-%anthropomorphism can be radically changing and be a very spontaneous
-%"reaction".)}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% JULIA & SEVERIN: how to measure / quantify anthropomorphism ...
-% CLAIRE: FMRI study idea
 
@@
 particular, its implications regarding the design of (social) robots and
-human-robot interaction are still to be refined but we hope this article helps encourage an open dialogue between those who do research of anthropomorphism.
-
-Coming back to our two main hypotheses, on one hand we investigated how far anthropomorphism is based on multiple factors, namely, the design of the robot, the personal characteristics of the human user, and the context / situation in which the robot is used.
-We elaborated this hypothesis by reviewing literature from various related disciplines.
-Based on the outcomes of this, on the other hand, we proposed a model of the \emph{Dynamics of anthropomorphism}.
-We offered a cognitive interpretation of this model, as well as illustrations from our own previous work.
-However, our model has limitations, for instance, regarding the general effect of time and familiarization on anthropomorphism. We will discuss this in the following section.
+human-robot interaction are still to be refined but we hope this article helps
+encourage an open dialogue between those who do research of anthropomorphism.
+
+Coming back to our two main hypotheses, on one hand we investigated how far
+anthropomorphism is based on multiple factors, namely, the design of the robot,
+the personal characteristics of the human user, and the context / situation in
+which the robot is used.  We elaborated this hypothesis by reviewing literature
+from various related disciplines. Based on the outcomes of this, on the other
+hand, we proposed a model of the \emph{Dynamics of anthropomorphism}. We offered
+a cognitive interpretation of this model, as well as illustrations from our own
+previous work.  However, our model has limitations, for instance, regarding the
+general effect of time and familiarization on anthropomorphism. We will discuss
+this in the following section.
 
@@
 
-We have proposed that time, or in other words, the user's familiarization with the non-human agent, models how anthropomorphism evolves over time.
-Our general assumption is that with continued interaction, and in turn growing user experience, the system becomes more predictable and consequently, the user's need to anthropomorphize the agent decreases.
-We would like to discuss this suggestion here.
-
-With \textit{time} as a factor, we
-referred to long-term interaction with the robot, which is related to what has been
-described as \textit{novelty effect} but also accounts for the user getting used
-to the robot.
-Several studies described that after some time users interacted less with the robot or lost interest in it.
-Sustaining long-term interaction is one of the main challenges that robots with applications in daily life contexts face.
-Our question is that, if we would like overcome the novelty effect, how far does the robot's behavioral complexity play a role?
-Should the robot vary its behavior and behave unexpectedly from time to time?
-
-Most experiments, and even more when they investigate
-long-term interactions, are carried out with robots exhibiting relatively simple
-behaviors. In our model, the maximum level of anthropomorphism \AntMax is
-reached with the novelty effect, and then decreases. A natural question
-is whether we can design robots such that \AntMax remains high, possibly higher
-than $\ant[t_{novelty~peak}]$ (note that to know if sustaining strong
-anthropomorphic interaction is desirable is entirely another question, see Section \ref{sec:ethics}).
-
-Intuitively, the behavioral complexity of the robot, and in particular, the ability
-for the robot to evolve over time and \emph{adapt its behavior to the user} as the user
-familiarizes his/herself with the robot (\ie, \emph{co-familiarize}), seems to play a
-key role.
-
-Our model is based on the assumption that anthropomorphism tends to decrease with the user becoming more familiar to the robot.
-We explain this by the general motivation to anthropomorphize an agent which might be difficult to understand
-(in its functionality or behavior, for instance). In turn, a user might ascribe
-intentions or emotions to the system because the system's output was unexpected
-for the user, however he/she still wants to make sense of it. Consequently, we estimate that when the user has
-familiarized herself/himself with the system, thus reached the point of when
-the system is usable and explainable, the tendency to anthropomorphize
-decreases.
-
-However, there exist views that suggest just the opposite, namely, that familiarization and more interaction with an agent \textit{increase} the tendency to anthropomorphize \citep{eddy_attribution_1993}.
-Similarly, \cite{duffy_anthropomorphism_2003} reports that several psychological experiments and human-robot interaction experiments showed that familiarity may also ease social acceptance and even tend to \textit{increase} people's tendency to anthropomorphize.
-
-Consequently, we have to accept that our model of the \emph{Dynamics of Anthropomorphism} needs to be verified, to see how far our hypotheses can hold.
-In particular, the effect of the user's familiarity with the system needs to be studied over a longer period of time.
-
-%\begin{enumerate} 
-%\item ~A person's tendency to anthropomorphize a robot
-%    is based on several factors, including (but not limited to) (1) the
-%    design of the robot, (2) the personal characteristics of the human user,
-%    and (3) the context and situation of use. For instance, a social context
-%    and purpose of the robot increase anthropomorphism: \textit{anthropomorphism
-%    as a multi-factor phenomenon}.
-%
-%\item ~A person's tendency to anthropomorphize a robot
-%    evolves in a non-linear way over time and with growing experience that the
-%    person has with the robot. For instance, a more experienced user will
-%    perceive the robot as more familiar and predictable, and in turn
-%    anthropomorphizes the robot less: \textit{anthropomorphism as a dynamic
-%    phenomenon}.
-%
-%\end{enumerate}
-
-%
-%Smart innovative devices, such as personal domestic robots, might demand from a
-%human user spontaneous usage of an unfamiliar system. Such situations will
-%require that a user should be able to build up a mental model quickly, which
-%particularly holds for novice users \cite{schmitz_concepts_2011}.
+We have proposed that time, or in other words, the user's familiarization with
+the non-human agent, models how anthropomorphism evolves over time. Our general
+assumption is that with continued interaction, and in turn growing user
+experience, the system becomes more predictable and consequently, the user's
+need to anthropomorphize the agent decreases. We would like to discuss this
+suggestion here.
+
+With \textit{time} as a factor, we referred to long-term interaction with the
+robot, which is related to what has been described as \textit{novelty effect}
+but also accounts for the user getting used to the robot. Several studies
+described that after some time users interacted less with the robot or lost
+interest in it. Sustaining long-term interaction is one of the main challenges
+that robots with applications in daily life contexts face. Our question is that,
+if we would like overcome the novelty effect, how far does the robot's
+behavioral complexity play a role? Should the robot vary its behavior and behave
+unexpectedly from time to time?
+
+Most experiments, and even more when they investigate long-term interactions,
+are carried out with robots exhibiting relatively simple behaviors. In our
+model, the maximum level of anthropomorphism \AntMax is reached with the novelty
+effect, and then decreases. A natural question is whether we can design robots
+such that \AntMax remains high, possibly higher than $\ant[t_{novelty~peak}]$
+(note that to know if sustaining strong anthropomorphic interaction is desirable
+is entirely another question, see Section \ref{sec:ethics}).
+
+Intuitively, the behavioral complexity of the robot, and in particular, the
+ability for the robot to evolve over time and \emph{adapt its behavior to the
+user} as the user familiarizes his/herself with the robot (\ie,
+\emph{co-familiarize}), seems to play a key role.
+
+Our model is based on the assumption that anthropomorphism tends to decrease
+with the user becoming more familiar to the robot.  We explain this by the
+general motivation to anthropomorphize an agent which might be difficult to
+understand (in its functionality or behavior, for instance). In turn, a user
+might ascribe intentions or emotions to the system because the system's output
+was unexpected for the user, however he/she still wants to make sense of it.
+Consequently, we estimate that when the user has familiarized herself/himself
+with the system, thus reached the point of when the system is usable and
+explainable, the tendency to anthropomorphize decreases.
+
+However, there exist views that suggest just the opposite, namely, that
+familiarization and more interaction with an agent \textit{increase} the
+tendency to anthropomorphize \citep{eddy_attribution_1993}. Similarly,
+\cite{duffy_anthropomorphism_2003} reports that several psychological
+experiments and human-robot interaction experiments showed that familiarity may
+also ease social acceptance and even tend to \textit{increase} people's tendency
+to anthropomorphize.
+
+Consequently, we have to accept that our model of the \emph{Dynamics of
+Anthropomorphism} needs to be verified, to see how far our hypotheses can hold.
+In particular, the effect of the user's familiarity with the system needs to be
+studied over a longer period of time.
 
@@
 by restating its cognitive model of the robot. Could our two models be
-conversely relied on to have the robot itself iteratively adapting its
-behavior? In particular, we hypothesize that the so-called novelty effect
-represents a peak in anthropomorphic manifestations, followed by mostly
-deception-driven refinements of the cognitive behavioral model of the robot.
-Could we imagine that the robot pro-actively \emph{verbalizes} its own limits,
-in a timely manner (likely before the end of the novelty effect). And how would
-this affect the cognitive models built by the human?
+conversely relied on to have the robot itself iteratively adapting its behavior?
+In particular, we hypothesize that the so-called novelty effect represents a
+peak in anthropomorphic manifestations, followed by mostly deception-driven
+refinements of the cognitive behavioral model of the robot.  Could we imagine
+that the robot pro-actively \emph{verbalizes} its own limits, in a timely manner
+(likely before the end of the novelty effect). And how would this affect the
+cognitive models built by the human?
 
@@
 
-%\fxwarning{To be completed/rephrased into a discussion}
-
-%Also, the methods and measurements applied to study anthropomorphism appear insufficient, when applying a holistic understanding of anthropomorphism emerging from an interaction between a human user and a robot, for instance.
-Our point here is that to study a phenomenon as complex as anthropomorphism, we believe that one needs to take into account many factors (see Section \ref{sec:multi-factors}), besides looking at the human-like design of the artifact.
-
-With this extended understanding of anthropomorphism being determined by multiple factors and showing dynamics over time, it also becomes questionable if the metrics and techniques that are currently used to measure anthropomorphism are sufficient.
-We would like to discuss two issues: the scenario in which anthropomorphism is measured, and how, with which means it is assessed.
-
-One needs to keep in mind that anthropomorphism arises in an interaction.
-We believe that as such, anthropomorphism can be better understood when studied and measured in a real, direct human-robot interaction compared to a mediated interaction.
-In a direct interaction scenario one could also take the human's behavior into account, as it seems to reflect an anthropomorphic interaction \citep{krach_can_2008,hegel_understanding_2008,weiss_i_2009}.
-Of course, the scenario and measurements one uses depend on the research questions, so a direct human-robot interaction might not always be preferred.
-
-However, most of the
-experiments that investigate anthropomorphism in HRI are conducted in
-controlled lab-settings during a short-term scenario.
-For instance, pictures or videos of different robots are shown to human subjects who subsequently fill in a questionnaire, to assess how far the different types of robots were perceived human-like.\footnote{It can already be critical to not indicate the height / size of a robot when it is pictured or presented in a video.
-We cannot assume that without any point of reference, lay people estimate correctly the height of ASIMO or Nao, for instance, they might think these humanoid robots are the same size as a Barbie doll.
-Also, when showing a picture, the movements, behaviors, materials of a robot, and so forth are totally disregarded.
-However, these aspects are also crucial features of a robot, impacting how human-like it appears.}
-We think that such
-experimental settings have limitations for studying a social phenomenon like
-anthropomorphism. The critical question is: can anthropomorphism really be measured in a post-interaction closed questionnaire or by rating scales?
-Findings might possibly lead to interpretations that would not be generalizable to natural settings or real interaction scenarios (which is always an issue in social science research).
-
-Regarding the second issue, how and with which means anthropomorphism is measured, one of the view existing tools to do so is 5-item anthropomorphism part of the Godspeed questionnaire \citep{bartneck_measurement_2008}.
-On 5 point semantic differential scales, people are asked to rate the following constructs: fake - natural, machinelike - humanlike, unconscious - conscious, artificial - lifelike, moving rigidly - moving elegantly.
-The critical point that we see with this is that ``human-likeness'' itself is complex and manifold.
-Being such an abstract concept, instead of asking the vague question, whether a robot is human-like or not, \cite{kahn_jr._robotic_2006} suggest to ask for more concrete constructs that are typical or unique of the concept of ``human-likeness''.
-For instance, \cite{ruijten_introducing_2014} propose a 25-item questions to measure various concrete aspects of human-likeness.
-Consequently, anthropomorphism can be modeled along a scale that accounts for lower and higher levels of it.
-
-Still, we also feel that measuring anthropomorphism (or social engagement with a robot) is challenging because the phenomenon is partially
-unconscious, its mediation is largely subject-dependent, and we found the
-phenomenon generally difficult to verbalize for users.
+With this extended understanding of anthropomorphism being determined by
+multiple factors and showing dynamics over time, it also becomes questionable if
+the metrics and techniques that are currently used to measure anthropomorphism
+are sufficient. We would like to discuss two issues: the scenario in which
+anthropomorphism is measured, and how, with which means it is assessed.
+
+One needs to keep in mind that anthropomorphism arises in an interaction. We
+believe that as such, anthropomorphism can be better understood when studied and
+measured in a real, direct human-robot interaction compared to a mediated
+interaction. In a direct interaction scenario one could also take the human's
+behavior into account, as it seems to reflect an anthropomorphic interaction
+\citep{krach_can_2008,hegel_understanding_2008,weiss_i_2009}.  Of course, the
+scenario and measurements one uses depend on the research questions, so a direct
+human-robot interaction might not always be preferred.
+
+However, most of the experiments that investigate anthropomorphism in HRI are
+conducted in controlled lab-settings during a short-term scenario. For instance,
+pictures or videos of different robots are shown to human subjects who
+subsequently fill in a questionnaire, to assess how far the different types of
+robots were perceived human-like.\footnote{It can already be critical to not
+indicate the height / size of a robot when it is pictured or presented in a
+video. We cannot assume that without any point of reference, lay people estimate
+correctly the height of ASIMO or Nao, for instance, they might think these
+humanoid robots are the same size as a Barbie doll. Also, when showing a
+picture, the movements, behaviors, materials of a robot, and so forth are
+totally disregarded. However, these aspects are also crucial features of a
+robot, impacting how human-like it appears.} We think that such experimental
+settings have limitations for studying a social phenomenon like
+anthropomorphism. The critical question is: can anthropomorphism really be
+measured in a post-interaction closed questionnaire or by rating scales?
+Findings might possibly lead to interpretations that would not be generalizable
+to natural settings or real interaction scenarios (which is always an issue in
+social science research).
+
+Regarding the second issue, how and with which means anthropomorphism is
+measured, one of the view existing tools to do so is 5-item anthropomorphism
+part of the Godspeed questionnaire \citep{bartneck_measurement_2008}. On 5 point
+semantic differential scales, people are asked to rate the following constructs:
+fake - natural, machinelike - humanlike, unconscious - conscious, artificial -
+lifelike, moving rigidly - moving elegantly. The critical point that we see with
+this is that ``human-likeness'' itself is complex and manifold. Being such an
+abstract concept, instead of asking the vague question, whether a robot is
+human-like or not, \cite{kahn_jr._robotic_2006} suggest to ask for more concrete
+constructs that are typical or unique of the concept of ``human-likeness''.  For
+instance, \cite{ruijten_introducing_2014} propose a 25-item questions to measure
+various concrete aspects of human-likeness. Consequently, anthropomorphism can
+be modeled along a scale that accounts for lower and higher levels of it.
+
+Still, we also feel that measuring anthropomorphism (or social engagement with a
+robot) is challenging because the phenomenon is partially unconscious, its
+mediation is largely subject-dependent, and we found the phenomenon generally
+difficult to verbalize for users.
 
@@
 
-We present in this section the methodology and techniques that we used to
-assess anthropomorphic projections in the child-robot interaction study, called the Domino study (see Section \ref{sec:field-results}, and Figure \ref{fig:ranger}).
-
-\paragraph{Qualitative and quantitative assessment of anthropomorphism in human's behavior\\}
-
-Anthropomorphism can possibly be observed in how humans behave toward a non-human agent (social human-like engagement).
-Based on video recordings of the Domino experiment, we acquired both quantitative and qualitative behavioral data that reflects anthropomorphism.
-
-Quantitative data are
-acquired by systematic annotations of specific types of actions in the video records of the interaction. Six classes of interactions were identified as reflecting
-active commitment and/or an anthropomorphic interaction of the user: gestures toward the robot, touching the robot, direct talk to
-the robot, showing something to the robot, mistreating the robot (\eg kicking it), and looking at the experimenter because worried by the robot's behavior.
-
-By considering the number of occurrences, the duration, and consequently the frequency of these types of interaction, we can make statements of how far the robot is anthropomorphized in an interaction (based on quantitative data).
-
-We assessed anthropomorphic interactions qualitatively by looking at specific instances of human-social cues in the human's behavior, such as: facial expressions, observable emotional reactions (\eg surprised, high pitch voice or shouting to the robot), eye-contact with the robot, turn-taking gestures, greeting (waving) gestures.
-These are just suggestions of actions that might reflect anthropomorphism.
-These actions partly overlap with the quantitative assessment, however it is generally advisable to combine the two.
-
-\paragraph{Qualitative assessment of anthropomorphism when verbally referring to the robot (reflection)\\}
-
-The main tools for
-qualitative measurement of anthropomorphic effect are questionnaires and semi-structured interviews. We have
-explored both rating-scales in a questionnaire, and open questions in an interview.
-In the Domino study, interviews were transcribed and participant's answers to the key questions that were assessing an anthropomorphic projection onto the robot, were analyzed.
-For instance, one question to see how far children would ascribe moral standing to the robot was \emph{``If you had this robot at home, and you were to leave for 2 weeks of holidays, would it be ok to leave the robot alone at home?''}.
-A point for anthropomorphism was counted, when the participant's answer indicated an anthropomorphic view of the robot.
-This process led to a ``qualitative score'' that reflects how far the robot is anthropomorphized.
-We used the following constructs to measure how far the robot is perceived as a human-like agent:
+We present in this section the methodology and techniques that we used to assess
+anthropomorphic projections in the child-robot interaction study, called the
+Domino study (see Section \ref{sec:field-results}, and Figure \ref{fig:ranger}).
+
+\paragraph{Qualitative and quantitative assessment of anthropomorphism in
+human's behavior\\}
+
+Anthropomorphism can possibly be observed in how humans behave toward a
+non-human agent (social human-like engagement). Based on video recordings of the
+Domino experiment, we acquired both quantitative and qualitative behavioral data
+that reflects anthropomorphism.
+
+Quantitative data are acquired by systematic annotations of specific types of
+actions in the video records of the interaction. Six classes of interactions
+were identified as reflecting active commitment and/or an anthropomorphic
+interaction of the user: gestures toward the robot, touching the robot, direct
+talk to the robot, showing something to the robot, mistreating the robot (\eg
+kicking it), and looking at the experimenter because worried by the robot's
+behavior.
+
+By considering the number of occurrences, the duration, and consequently the
+frequency of these types of interaction, we can make statements of how far the
+robot is anthropomorphized in an interaction (based on quantitative data).
+
+We assessed anthropomorphic interactions qualitatively by looking at specific
+instances of human-social cues in the human's behavior, such as: facial
+expressions, observable emotional reactions (\eg surprised, high pitch voice or
+shouting to the robot), eye-contact with the robot, turn-taking gestures,
+greeting (waving) gestures. These are just suggestions of actions that might
+reflect anthropomorphism. These actions partly overlap with the quantitative
+assessment, however it is generally advisable to combine the two.
+
+\paragraph{Qualitative assessment of anthropomorphism when verbally referring to
+the robot (reflection)\\}
+
+The main tools for qualitative measurement of anthropomorphic effect are
+questionnaires and semi-structured interviews. We have explored both
+rating-scales in a questionnaire, and open questions in an interview.  In the
+Domino study, interviews were transcribed and participant's answers to the key
+questions that were assessing an anthropomorphic projection onto the robot, were
+analyzed. For instance, one question to see how far children would ascribe moral
+standing to the robot was \emph{``If you had this robot at home, and you were to
+leave for 2 weeks of holidays, would it be ok to leave the robot alone at
+home?''}. A point for anthropomorphism was counted, when the participant's
+answer indicated an anthropomorphic view of the robot. This process led to a
+``qualitative score'' that reflects how far the robot is anthropomorphized. We
+used the following constructs to measure how far the robot is perceived as a
+human-like agent:
 
@@
 
-Some of these questions were taken from previous work done by \cite{kahn_jr._robotic_2006} an \cite{weiss_i_2009}.
-In both studies, both questionnaires and an analysis of behavior were used to assess children's and adult's engagement with, and perception of the robot.
-This seems to be a promising approach to investigate anthropomorphism, as it is also possible to combine quantitative and qualitative techniques.
+Some of these questions were taken from previous work done by
+\cite{kahn_jr._robotic_2006} an \cite{weiss_i_2009}. In both studies, both
+questionnaires and an analysis of behavior were used to assess children's and
+adult's engagement with, and perception of the robot. This seems to be a
+promising approach to investigate anthropomorphism, as it is also possible to
+combine quantitative and qualitative techniques.
 
@@
 
-% our message kind of is that it would be favorable to sustain anthropomorphism over 
-% extended periods of time ... however, this is ethically questionable, when thinking 
-% of emotional bonding with an artificial agent, etc. --> we sould elaborate on this a % bit
-
-After all discussion, there remains the question how far a sustained anthropomorphic (human social) interaction between a human and a non-human can be favored, regarding ethical aspects.
-We need to rethink carefully the consequences that emotional bonds between humans and robots can have.
-They might be beneficial on one hand but can also hold negative implications.
-How far should a robot's design encourage us to lastingly project feelings or intentions to it?
-Why should a machine even react to us as if it had emotions?
-Can this be the reality we want to live in?
-What happens as soon as the artificial agent is considered a \textit{moral agent} \citep{sullins_when_2006}?
-Also, the use of \textit{socially interactive robots} in
-contexts involving elderly care or in rehabilitation and with autistic children is a controversially discussed topic 
-\cite{robins_robots_2005}. Do we want robots to comfort us; robots that make us eventually even falling in love with them?
-The anthropomorphic design of robots is critical. Why do we even need this? The HRI / robotics community needs to discuss these and other questions.
+After all discussion, there remains the question how far a sustained
+anthropomorphic (human social) interaction between a human and a non-human can
+be favored, regarding ethical aspects. We need to rethink carefully the
+consequences that emotional bonds between humans and robots can have. They might
+be beneficial on one hand but can also hold negative implications. How far
+should a robot's design encourage us to lastingly project feelings or intentions
+to it? Why should a machine even react to us as if it had emotions? Can this be
+the reality we want to live in? What happens as soon as the artificial agent is
+considered a \textit{moral agent} \citep{sullins_when_2006}? Also, the use of
+\textit{socially interactive robots} in contexts involving elderly care or in
+rehabilitation and with autistic children is a controversially discussed topic
+\cite{robins_robots_2005}. Do we want robots to comfort us; robots that make us
+eventually even falling in love with them?  The anthropomorphic design of robots
+is critical. Why do we even need this? The HRI / robotics community needs to
+discuss these and other questions.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% JULIA & SEVERIN
 
@@
 
-Based on our previous (and on-going) work, we hypothesized that there are qualitative differences and dynamics over time
-in how humans relate to different types of robots. More concretely, we described
-that people's perception of human-likeness in a robot and in turn their
-human-social engagement with a robot is based on four main factors: (1) the (anthropomorphic) design of the robot, (2) individual characteristics of the human user, (3) the context of use / interaction, and (4) the interaction history (time factor).
-We further suggested
-that people's tendency to anthropomorphize a robot is likely to change over time with
-growing experience of the user with the system.
-
-To formalize the variances in anthropomorphism, we
-proposed a model that we call \textit{Dynamics of Anthropomorphism}.
-
- We introduced the concepts of
-\emph{initial capital} and \emph{stabilized level of anthropomorphism} as compound
-factors to characterize the profile of a given anthropomorphic (long-term) interaction.
+Based on our previous (and on-going) work, we hypothesized that there are
+qualitative differences and dynamics over time in how humans relate to different
+types of robots. More concretely, we described that people's perception of
+human-likeness in a robot and in turn their human-social engagement with a robot
+is based on four main factors: (1) the (anthropomorphic) design of the robot,
+(2) individual characteristics of the human user, (3) the context of use /
+interaction, and (4) the interaction history (time factor). We further suggested
+that people's tendency to anthropomorphize a robot is likely to change over time
+with growing experience of the user with the system.
+
+To formalize the variances in anthropomorphism, we proposed a model that we call
+\textit{Dynamics of Anthropomorphism}.
+
+We introduced the concepts of \emph{initial capital} and \emph{stabilized level
+of anthropomorphism} as compound factors to characterize the profile of a given
+anthropomorphic (long-term) interaction.
 
 The article also discussed the cognitive correlates of anthropomorphism. We
-proposed three cognitive stages corresponding to successive
-refinements of the mental models of the robot that the user builds during the
-interaction. We showed how these stages relate to observable anthropomorphic
-effects, and how they evolve over time.
+proposed three cognitive stages corresponding to successive refinements of the
+mental models of the robot that the user builds during the interaction. We
+showed how these stages relate to observable anthropomorphic effects, and how
+they evolve over time.
 
@@
 
-%With
-%this initial model, we would like to extend the current understanding of
-%anthropomorphism in robotics and human-robot interaction. This might in turn
-%lead to a discussion about the short- and long-term benefits and other effects
-%of the anthropomorphic design of robots and other artificial
-%agents.
-
 \section*{Acknowledgments}
 
-This research was supported by the Swiss National Science Foundation through the National Centre of Competence in Research Robotics.
-
-%\section{Bibliography}
+This research was supported by the Swiss National Science Foundation through the
+National Centre of Competence in Research Robotics.
 

### 2014-11-07 paper.tex
Start to shorten the paper, update the pictures

@@
 
-\newcommand{\eg}{{\textit{e.g.~}}}
-\newcommand{\etal}{{\textit{et al.~}}}
-\newcommand{\ie}{{\textit{i.e.~}}}
-\newcommand{\etc}{{\textit{etc.~}}}
-\newcommand{\vs}{{\textit{vs.~}}}
+\usepackage{xspace}
+\newcommand{\eg}{\textit{e.g.}\xspace}
+\newcommand{\etal}{\textit{et al.}\xspace}
+\newcommand{\ie}{\textit{i.e.}\xspace}
+\newcommand{\etc}{\textit{etc.}\xspace}
+\newcommand{\vs}{\textit{vs.}\xspace}
 
@@
         \begin{subfigure}[t]{0.48\columnwidth}
-                \includegraphics[width=\textwidth]{roomba-activities.png}
-                \caption{Activities related to Roomba, n = 9 households}
+                \includegraphics[height=7cm]{roomba-activities}
+                \caption{Activities related to Roomba, \textit{n = 9 households}}
                 \label{fig:roomba-activities}
@@
         \begin{subfigure}[t]{0.48\columnwidth}
-                \includegraphics[width=\textwidth]{roomba-perception.pdf}
-                \caption{People's perception of Roomba, n = 15 participants}
+                \includegraphics[height=7cm]{roomba-ratings}
+                \caption{People's perception of Roomba, \textit{n = 15
+                participants}}
                 \label{fig:roomba-perception}
@@
 
-Further, we would like to investigate the link between the variances in
-anthropomorphism and the correlating cognitive states.
-
 \subsection{Article overview}
@@
 the understanding of anthropomorphism as a psychological phenomenon.
-
- \subsection{The lexical field of anthropomorphism}
-
-Originally, the term \textbf{anthropomorphism} comes from the Greek
-\textit{anthropos} for ``man'' (or ``human'') and \textit{morphe} for ``form /
-structure'' (or ``shape''). Anthropomorphism is generally understood as people's
-tendency to perceive a non-human agent as if it had some human characteristics
-or traits. How a person perceives an agent is crucial, as it further determines
-how he/she relates to, and behaves towards the agent, or how he/she may behave in
-light of this agent \citep{epley_when_2008}. An anthropomorphic relationship is
-often characterized by the fact that the human attributes human-unique
-characteristics to the non-human agent. Since anthropomorphism becomes
-observable through these attributions, some definitions claim that
-anthropomorphism is not the \textit{perception} but rather the
-\textit{attribution} of human qualities to non-human agents.  Ascribing
-thoughts, emotions, and intentions are given as examples, and as the most
-prominently anthropomorphized non-human agents, animals and robots are mentioned
-\citep{duffy_anthropomorphism_2003,schmitz_concepts_2011}.
-
-Apart from anthropomorphism, there also exists the term \textbf{animism}, which
-can be defined as the attribution of life to the nonliving. The study of animism
-was pioneered by Piaget in the 1920s with his work on \textit{The Child's
-Conception of the  World}. He found that children tend to regard many inanimate
-objects as capable of sensations, emotions and intentions, and called this view
-``animism''. Since then, children's inferences about the world have been studied
-intensively, and there is an agreement that children's views and concepts of
-living, animal, and plant evolve as they grow up. Often synonymously used to
-animism is the term \textbf{zoomorphism}, which similarly applies to the cases
-when non-lifelike instances / artifacts are associated with animalistic
-attributes, excluding human-specific traits.  As ``being alive'' is not a
-human-unique property but applies to all living beings, the attribution of life
-may not be labeled as anthropomorphism (in a narrow understanding of it).
-Another possibility to illustrate how anthropomorphism differs from attributions
-of animacy is to look at paraphrases of anthropomorphism. That is to say,
-anthropomorphism can alternatively be understood as \textbf{humanization} or
-\textbf{personification} of anything other than a human being.\footnote{There
-exist also the phenomenons inverse to anthropomorphism, which can be found
-in the literature as \textbf{dehumanization}
-\citep{haslam_dehumanization:_2006}, or \textbf{mechanomorphism}
-\citep{caporael_anthropomorphism_1986}.} Robots can
-both be animized and anthropomorphized, but often the difference is not made.
 
@@
 
-\begin{figure}
-    \centering
-    \includegraphics[width=0.75\columnwidth]{in_our_heads.pdf}
-    \caption{[ALTERNATIVE TO FIGURE \ref{fig:anthropofig}] Anthropomorphism is a
-        subjective, psychological phenomenon which arises in a social context, during an
-        interaction between a human agent and a non-human agent. One can take
-        two main perspectives when trying to explain anthropomorphism: a
-        human-centered and an artifact-centered perspective.
-        Several external factors influence the anthropomorphism phenomenon.
-        Person- and artifact-related characteristics, but also related to the
-        context of use as well as the actual time spent interacting with the
-        robot (interaction history).}
-
-    \label{fig:anthropofig-alt}
-\end{figure}
+%
+%\begin{figure}
+%    \centering
+%    \includegraphics[width=0.75\columnwidth]{in_our_heads.pdf}
+%    \caption{[ALTERNATIVE TO FIGURE \ref{fig:anthropofig}] Anthropomorphism is a
+%        subjective, psychological phenomenon which arises in a social context, during an
+%        interaction between a human agent and a non-human agent. One can take
+%        two main perspectives when trying to explain anthropomorphism: a
+%        human-centered and an artifact-centered perspective.
+%        Several external factors influence the anthropomorphism phenomenon.
+%        Person- and artifact-related characteristics, but also related to the
+%        context of use as well as the actual time spent interacting with the
+%        robot (interaction history).}
+%
+%
+%    \label{fig:anthropofig-alt}
+%\end{figure}
+%
 
@@
 (note that to know if sustaining strong anthropomorphic interaction is desirable
-is entirely another question, see Section \ref{sec:ethics}).
+is entirely another question).
 
@@
 ability for the robot to evolve over time and \emph{adapt its behavior to the
-user} as the user familiarizes his/herself with the robot (\ie,
+user} as the user familiarizes his/herself with the robot (\ie
 \emph{co-familiarize}), seems to play a key role.
@@
 studied over a longer period of time.
-
-\subsection{General observations}
-
-By adopting both a cognitive and a dynamic perspective on the anthropomorphic
-bonds that establish between a robot and a human during an interaction, some
-observations can be raised.
-
-For instance, we propose that the human \emph{adapts} iteratively to the robot
-by restating its cognitive model of the robot. Could our two models be
-conversely relied on to have the robot itself iteratively adapting its behavior?
-In particular, we hypothesize that the so-called novelty effect represents a
-peak in anthropomorphic manifestations, followed by mostly deception-driven
-refinements of the cognitive behavioral model of the robot.  Could we imagine
-that the robot pro-actively \emph{verbalizes} its own limits, in a timely manner
-(likely before the end of the novelty effect). And how would this affect the
-cognitive models built by the human?
-
-One related question we plan to elaborate on is the effects of \emph{mutual
-explicitation of the mental model of the other agent}: a human and a robot
-interact on a given task, and after a while, we interrupt the task and ask each
-of the agents to explicit the mental model it has built of its partner
-(emotional state, beliefs, intentions, etc.). Depending on the cognitive stages
-the two agents are in, we may expect varying accuracy levels in the produced
-mental models.
-
-Another question raised by these models relates to their transposition to
-human-human interaction: while concepts like \emph{novelty effect} are not
-directly meaningful when analyzing human-human interaction, insights from
-cognitive sciences (and in particular social psychology) regarding how we, as
-humans, cope with unexpected behaviors from peers, or on the dynamics of mental
-model refinements, could bring interesting perspectives with possible
-applications to better manage long-term human-robot interactions.
 
@@
 
-\subsection{Ethical aspects of anthropomorphism and human-like form of robots}
-\label{sec:ethics}
-
-After all discussion, there remains the question how far a sustained
-anthropomorphic (human social) interaction between a human and a non-human can
-be favored, regarding ethical aspects. We need to rethink carefully the
-consequences that emotional bonds between humans and robots can have. They might
-be beneficial on one hand but can also hold negative implications. How far
-should a robot's design encourage us to lastingly project feelings or intentions
-to it? Why should a machine even react to us as if it had emotions? Can this be
-the reality we want to live in? What happens as soon as the artificial agent is
-considered a \textit{moral agent} \citep{sullins_when_2006}? Also, the use of
-\textit{socially interactive robots} in contexts involving elderly care or in
-rehabilitation and with autistic children is a controversially discussed topic
-\cite{robins_robots_2005}. Do we want robots to comfort us; robots that make us
-eventually even falling in love with them?  The anthropomorphic design of robots
-is critical. Why do we even need this? The HRI / robotics community needs to
-discuss these and other questions.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2014-11-07 paper.tex
Large simplification of the paper (now 23 pages)

@@
 \usepackage{textcomp}
+\usepackage{booktabs}
 
@@
 
-We propose to discuss anthropomorphism from three
-complementary perspectives:
+We propose to discuss anthropomorphism from three complementary perspectives:
 
@@
 
-%\paragraph{Two hypotheses}
-Our research question also translates to two
-hypotheses, which structure the reflections of this article:
-
-\begin{enumerate} 
-\item ~A person's tendency to anthropomorphize a robot
-    is based on several factors, including (but not limited to) (1) the
-    design of the robot, (2) the personal characteristics of the human user,
-    and (3) the context and situation of use. For instance, a social context
-    and purpose of the robot increase anthropomorphism: \textit{anthropomorphism
-    as a multi-factor phenomenon}.
-
-\item ~A person's tendency to anthropomorphize a robot
-    evolves in a non-linear way over time and with growing experience that the
-    person has with the robot. For instance, a more experienced user will
-    perceive the robot as more familiar and predictable, and in turn
-    anthropomorphizes the robot less: \textit{anthropomorphism as a dynamic
-    phenomenon}.
-
-\end{enumerate}
+\subsection{Terminology used in this article}
+
+We use the term \textbf{anthropomorphism} to describe the \emph{psychological}
+phenomenon, which arises in the \emph{social context} of an interaction between
+a human agent and a non-human agent, in our case, a robot (see Figure
+\ref{fig:anthropofig}). We use this term to refer to both people's tendency to
+\textit{perceive} human-like characteristics, and to the tendency to
+\textit{ascribe} or \textit{attribute} such human-like characteristics to the
+agent or artifact. Besides, we call {\bf anthropomorphic effects} the
+\emph{observable manifestations} of anthropomorphism, \ie the human's behaviors
+and actions toward a non-human agent that reflect the underlying cognitive
+process of anthropomorphizing.
+
+However, despite the fact that ``anthropomorphism'' literally means ``human
+form'' we propose that the term should \textit{not} be used to refer to the
+\textit{form / design} of a non-human agent or artifact. To refer to an
+imitation of human-like \textit{form / design} of artificial agents, we propose
+to use the term \textbf{anthropomorphic design}. This explicit terminology
+prevents the commonly encountered confusion between anthropomorphism as a
+psychological, subjective phenomenon, and the external, objective factors that
+\emph{influence} the phenomenon itself.
+
+In the following, we might use the terms \emph{form} and \emph{design}
+interchangeably. Note that the terms \textit{form} or {\it design} do not only
+refer to the shape (how it looks like) but to the total expression of the
+artifact~\citep{bartneck_shaping_2004}. \citet{disalvo_hug:_2003} argues that
+\textit{form} includes the physical shape, materials, and behavioral qualities
+of the product. The behavioral aspect is of special importance for interactive
+systems that show some degree of autonomy (independence).  Several categories of
+anthropomorphic form exist, with no common agreement on the borders and
+transitions between those: anthropomorphic, zoomorphic, caricatured, functional
+\citep{fong_survey_2003}.
 
@@
 explanations into an understanding of anthropomorphism as a multi-factor
-phenomenon.  Based on this, Section~\ref{sec:our-ideas} introduces our initial
-model of the \textit{Dynamics of Anthropomorphism}. This model describes the
-variances and dynamics of people's tendency to anthropomorphize an artificial
-agent, such as a robot.  Then Section \ref{sec:cognition-neuroscience} presents
-a cognitive and neuroscience perspective on anthropomorphism to consolidate our
-considerations and the proposed model.  This is followed by a discussion about
-the limitations of our approach (Section \ref{sec:discussion}) and the existing
-and alternative ways to measure anthropomorphism in human-robot interactions.
-Finally, Section \ref{sec:conclusion} concludes this article and offers starting
-points for further research on anthropomorphism and the effect of the human-like
-design approach in robotics.
+phenomenon.  Based on this, Section~\ref{sec:our-ideas} proposes a new
+conceptual model of the \textit{Dynamics of Anthropomorphism}. This model
+describes the variances and dynamics of people's tendency to anthropomorphize an
+artificial agent, such as a robot.  Then Section
+\ref{sec:cognition-neuroscience} presents a cognitive and neuroscience
+perspective on anthropomorphism to consolidate our considerations and the
+proposed model.  Section \ref{sec:measuring} looks at how these models can be
+operationalized, and in particular, what are the tools at hand to measure
+anthropomorphism. Finally, Section \ref{sec:conclusion} concludes this article
+and offers starting points for further research on anthropomorphism and the
+effect of the human-like design approach in robotics.
 
@@
 
-\section{Towards a unified understanding: What is anthropomorphism?}
-\label{sec:definitions}
+\section{The Dimensions of Anthropomorphism}
+\label{sec:anthropomorphism}
 
 Literature on anthropomorphism is quite diverse. There exist different and
-partly conflicting definitions of the term anthropomorphism, and that in
-general, the \textit{terminology} is not clear. Probably as a result of this,
-there also exist different understandings of the \textit{phenomenon} that the
-term ``anthropomorphism'' describes.  In this section we will first give an
-overview on the diversity of terms and then try to establish a common ground in
-the understanding of anthropomorphism as a psychological phenomenon.
+partly conflicting definitions of the term anthropomorphism, and it still
+appears controversial that humans tend to \textit{``see human
+in the non- human''} \citep{epley_seeing_2007}.
+
+As anthropomorphism arises in an interaction between a human and a non-human
+agent~\citep{persson_anthropomorphism_2000}, one can also take two main
+\textit{perspectives} when trying to explain why humans anthropomorphize~\citep{lee_human_2005}: an artifact-centered perspective and a human-centered
+perspective (the grey triangles in Figure \ref{fig:anthropofig}).
+
+In the following we will only briefly present the artifact-centered perspective
+to explain anthropomorphism. A review of anthropomorphic design of robots can
+also be found in~\cite{fink_anthropomorphism_2012}. Then, we provide a more
+detailed review and synthesis of literature that applies a human-centered
+perspective to explain anthropomorphism. We aim here at providing an exhaustive
+picture of this phenomenon, by summarizing theories from developmental
+psychology, cognitive science, neuroscience, and social psychology.
 
@@
 Depending on which definition of anthropomorphism is applied, not everything
-colloquially labeled as \emph{anthropomorphism} really is anthropomorphism.
-For example, it is not always clear whether a person (may it be an adult or 
-a child) who gives an anthropomorphic response, believes that the other agent really 
-thinks or acts like a human or whether he/she is using anthropomorphism in a metaphoric 
-sense \citep{leeds_childrens_1992}.
-This call for explicitely stating what we mean when talking about anthropomorphism.
+colloquially labeled as \emph{anthropomorphism} really is anthropomorphism.  For
+example, it is not always clear whether a person (may it be an adult or a child)
+who gives an anthropomorphic response, believes that the other agent really
+thinks or acts like a human or whether he/she is using anthropomorphism in a
+metaphoric sense \citep{leeds_childrens_1992}.  This call for explicitely
+stating what we mean when talking about anthropomorphism.
 
@@
 
-As human-likeness itself is manifold and complex,
-some researchers argue that there might not just be one single type of
-anthropomorphism but different levels or gradations. For instance,
-\citet{persson_anthropomorphism_2000} proposes to understand anthropomorphism as
-a multi-layered phenomenon, namely \emph{primitive categorization},
-\emph{primitive psychology}, \emph{folk-psychology}, \emph{traits}, \emph{social
-roles}, and \emph{emotional anthropomorphism}. Correspondingly,
-\citet{ruijten_introducing_2014} propose to understand anthropomorphism as a
-continuum ranging from low to high human likeness, and to measure it as such.
-
-\subsection{Terminology used in this article}
-
-We use the term \textbf{anthropomorphism} to describe the \emph{psychological}
-phenomenon, which arises in the \emph{social context} of an interaction between
-a human agent and a non-human agent, in our case, a robot (see Figure
-\ref{fig:anthropofig}). We use this term to refer to both people's tendency to
-\textit{perceive} human-like characteristics, and to the tendency to
-\textit{ascribe} or \textit{attribute} such human-like characteristics to the
-agent or artifact. Besides, we call {\bf anthropomorphic effects} the
-\emph{observable manifestations} of anthropomorphism, \ie the human's behaviors
-and actions toward a non-human agent that reflect the underlying cognitive
-process of anthropomorphizing.
-
-However, despite the fact that ``anthropomorphism'' literally means ``human
-form'' we propose that the term should \textit{not} be used to refer to the
-\textit{form / design} of a non-human agent or artifact. To refer to an
-imitation of human-like \textit{form / design} of artificial agents, we propose
-to use the term \textbf{anthropomorphic design}. This explicit terminology
-prevents the commonly encountered confusion between anthropomorphism as a
-psychological, subjective phenomenon, and the external, objective factors that
-\emph{influence} the phenomenon itself.
-
-In the following, we might use the terms \emph{form} and \emph{design}
-interchangeably. Note that the terms \textit{form} or {\it design} do not only
-refer to the shape (how it looks like) but to the total expression of the
-artifact~\citep{bartneck_shaping_2004}. \citet{disalvo_hug:_2003} argues that
-\textit{form} includes the physical shape, materials, and behavioral qualities
-of the product. The behavioral aspect is of special importance for interactive
-systems that show some degree of autonomy (independence).  Several categories of
-anthropomorphic form exist, with no common agreement on the borders and
-transitions between those: anthropomorphic, zoomorphic, caricatured, functional
-\citep{fong_survey_2003}.
+As human-likeness itself is manifold and complex, some researchers argue that
+there might not just be one single type of anthropomorphism but different levels
+or gradations. For instance, \citet{persson_anthropomorphism_2000} proposes to
+understand anthropomorphism as a multi-layered phenomenon, namely
+\emph{primitive categorization}, \emph{primitive psychology},
+\emph{folk-psychology}, \emph{traits}, \emph{social roles}, and \emph{emotional
+anthropomorphism}. Correspondingly, \citet{ruijten_introducing_2014} propose to
+understand anthropomorphism as a continuum ranging from low to high human
+likeness, and to measure it as such.
 
@@
         but also related to the context of use as well as the actual time spent
-        interacting with the robot (interaction history). [SEE
-        FIG~\ref{fig:anthropofig-alt} FOR AN ALTERNATIVE FIGURE]}
+        interacting with the robot (interaction history).}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Why do humans anthropomorphize?}
-\label{sec:anthropomorphism}
-
-Anthropomorphism is an interesting phenomenon because it tells us something
-about the relationship between the human who anthropomorphizes, and the
-non-human agent which is anthropomorphized. Though commonly observed, it still
-appears controversial, at the same time, that humans tend to \textit{``see human
-in the non- human''} \citep{epley_seeing_2007}.
-
-As anthropomorphism arises in an interaction between a human and a non-human
-agent \citep{persson_anthropomorphism_2000}, one can also take two main
-\textit{perspectives} when trying to explain why humans anthropomorphize
-\citep{lee_human_2005}: an artifact-centered perspective and a human-centered
-perspective (see grey triangles in Figure \ref{fig:anthropofig}). It has to be
-kept in mind that both perspectives are inseparable; they apply at the same
-time, and we would like to present them here just as two different viewpoints on
-the same phenomenon.
-
-In the following we will only briefly present the artifact-centered perspective
-to explain anthropomorphism. A review of anthropomorphic design of robots can
-also be found in \cite{fink_anthropomorphism_2012}. Then, we provide a more
-detailed review and synthesis of literature that applies a human-centered
-perspective to explain anthropomorphism. Concretely, we integrate theories from
-developmental psychology, cognitive science / neuroscience, and social
-psychology to shed light on the question why humans anthropomorphize.
 
@@
 
-\item ~the psychological determinants in the \textbf{human user}
-    (see~\cite{epley_seeing_2007}),
+\item ~the psychological determinants in the \textbf{human
+    user}~\citep{epley_seeing_2007},
 
@@
 
-When taking into account these multiple factors, a logical consequence seems to
-be that anthropomorphism is not either there or not there but that it arises in
-different levels, may they be distinct, having multiple layers
-\citep{persson_anthropomorphism_2000}. or a continuum being describes in low and
-high anthropomorphism \citep{ruijten_introducing_2014}. For instance,
-
-Moreover, we propose that anthropomorphism shows not only variances determined
-by these four main factors but that -- the fourth factor implies this --
-anthropomorphism is likely to evolve over time with continued interaction
-between the human and the non-human agent.
-
-To facilitate things, we introduce the notation \Ant[R,H,C,t] to bring these
-multiple factors together. To take into account dynamics over time, we suggest
-that anthropomorphism is a function of a vector of robot's traits $R =
-\{r_0,...,r_n\}$, a vector human determinants $H = \{h_0,...,h_n\}$,
-characteristics of the interaction context $C = \{c_0,...,c_n\}$, and the
-duration / history of the interaction itself, $t$.
+As such, we use in the remaining of the article the notation \Ant[R,H,C,t] to
+represent anthropomorphism as a function of the robot's traits $R$, the human
+determinants $H$, the characteristics of the interaction context $C$ and the
+history of the interaction itself, $t$. This last factor, time, is the focus of
+the next section.
 
@@
 % background shading
-\path[fill=green!20] (0,0) rectangle (0.6,5.5);
-\path[fill=blue!15] (0.6,0) rectangle (5.2,5.5);
+\path[fill=green!20] (0,0) rectangle (1.1,5.5);
+\path[fill=blue!15] (1.1,0) rectangle (5.2,5.5);
 \path[fill=orange!20] (5.2,0) rectangle (9.8,5.5);
-\draw(0,5.5) node[anchor=south west, rotate=10] {\scriptsize \sc Initialization};
-\draw(2.5,5.5) node[anchor=south west, rotate=10] {\scriptsize \sc Familiarization};
+\draw(0.5,5.5) node[anchor=south west, rotate=10] {\scriptsize \sc Initialization};
+\draw(3,5.5) node[anchor=south west, rotate=10] {\scriptsize \sc Familiarization};
 \draw(6.5,5.5) node[anchor=south west, rotate=10] {\scriptsize \sc Stabilization};
@@
 \draw[->] (0,0) -- (10,0) node[anchor=north] {$t$};
-\draw(5,-0.1) node[anchor=north] {\scriptsize Duration of interaction};
+\draw(5,-0.1) node[anchor=north] {\scriptsize Interaction history};
 
@@
 % vertical axis - end
-\draw[->] (9.8,0) -- (9.8,2) node[anchor=east] {};
+\draw[->] (9.8,0) -- (9.8,4) node[anchor=east] {};
 \draw (9.8, 0.8) node[anchor=west] {\SLA};
 
-\draw[<-] (0.65,5) -- (0.8,5.2) node[anchor=east] {};
-\draw (0.9,5.3) node[anchor=west] {\tiny \it novelty peak};
-
-\draw[dashed] (0.6, 0) -- (0.6,5.1);
-\draw (0.6,0) node[anchor=north] {$t_{max}$};
-
-\draw[dotted] (0, 5) -- (6.2,5);
-\draw[dotted] (0, 3) -- (6.2,3);
-\draw[<->] (6.1,3) -- (6.1,5) node[sloped, above, midway] {$\Delta_{a}$};
-
-\draw[<-] (1.7,4.4) -- (3.2,4.1) node[anchor=east] {};
-\draw[<-] (2.85,2.6) -- (3.2,4.1) node[anchor=east] {};
-\draw (3.2,4.1) node[anchor=west, align=center] {\tiny \it disruptive\\ \tiny
+\draw[<-] (1.15,5.1) -- (1.30,5.3) node[anchor=east] {};
+\draw (1.35,5.4) node[anchor=west] {\tiny \it novelty peak};
+
+\draw[dashed] (1.1, 0) -- (1.1,5.1);
+\draw (1.1,0) node[anchor=north] {$t_{max}$};
+
+%\draw[dotted] (0, 5) -- (6.2,5);
+%\draw[dotted] (0, 3) -- (6.2,3);
+%\draw[<->] (6.1,3) -- (6.1,5) node[sloped, above, midway] {$\Delta_{a}$};
+
+\draw[<-] (2.2,4.4) -- (3.7,4.1) node[anchor=east] {};
+\draw[<-] (3.3,2.6) -- (3.7,4.1) node[anchor=east] {};
+\draw (3.8,4.1) node[anchor=west, align=center] {\tiny \it disruptive\\ \tiny
 \it behaviors};
@@
 %%%%
-\begin{scope}[yscale=-1,shift={(-0.125,-0.4)}]
-
-    \draw[ultra thick] svg[scale=1cm] "M 0.125,-2.5619582 c 0.0200733,-1.1573591
-    0.33954391,-1.9982333 0.57940683,-2.0013597 0.13691605,0 0.25550329,0.052908
-    0.37497897,0.1661788 0.119476,0.1130305 0.2396954,0.2786079
-    0.37944,0.4790565 0.069872,0.099803 0.1021612,-0.2231749
-    0.1792538,-0.2238964 0.099707,0 0.013454,0.4985362 0.3173383,0.9139831
-    0.1911917,0.2612926 0.3444354,0.2578391 0.6711932,0.4894291
-    0.2058265,0.1458798 0.1571532,0.9762306 0.2615031,0.9702183 0.097182,0
-    0.083295,-0.3336208 0.4330446,-0.1199242 0.4306401,0.2631203
-    0.216699,0.1355642 0.4296663,0.2647074 2.0858202,1.13836043
-    4.34683,1.41300027 6.3741749,1.43753027";
-
-    \draw[dashed] svg[scale=1cm] "M 0.125,-0.1952939 c 0.0553601,-3.1917862
-    0.33954391,-4.3648976 0.57940683,-4.368024 0.13691605,0 0.25550329,0.052908
-    0.37497897,0.1661788 m 2.6714393,2.7735737 C 4.7653984,-0.85050947
-    6.5955093,0.35382293 10.125,0.4062498";
-
-    \draw[dashed] svg[scale=1cm] "M 0.125,-3.6923825 C 0.1102888,-4.0297903
-    0.46454391,-4.5601915 0.70440683,-4.5633179 M 3.7508251,-1.6235654 C
-    4.9579368,-0.95548345 8.1358175,-0.82609971 10.125,-0.79459549";
+\begin{scope}[yscale=-1,shift={(-0.125,-0.46)}]
+    \draw[ultra thick, green!70!red!50, dashed] svg[scale=1cm] "M 0.114,-1.1 C 0.733,-2.79 1.88,-2.23
+    2.51,-1.76 3.34,-1.14 3.94,0.02 10.1,0";
+
+    \draw[ultra thick, blue!70!red!50, dashed] svg[scale=1cm] "M 0.125,-3.21 C 0.549,-4.91 2.05,-4.42
+    2.59,-3.83 3.57,-2.74 5.93,-1.51 10.1,-1.53";
+
+    \draw[ultra thick, red!70, dashed] svg[scale=1cm] "M 0.12500001,-2.7222489 C 0.70533638,-5.3401235 1.9431386,-3.7307246 2.608741,-3.3299187 c 1.3619528,0.8201274 3.3166657,1.2251393 7.515191,1.2014756";
+
+    \draw[ultra thick] svg[scale=1cm] "M
+    0.125,-1.622832 c 0.19887378,-2.35086 0.74751962,-2.9373641 1.0765913,-2.9404859 0.3290717,-0.00312 0.5370891,0.383599 0.754419,0.6452353 0.069872,0.099803 0.1021612,-0.2231749 0.1792538,-0.2238964 0.099707,0 0.013454,0.4985362 0.3173383,0.9139831 0.1911917,0.2612926 0.3444354,0.2578391 0.6711932,0.4894291 0.2058265,0.1458798 0.1571532,0.9762306 0.2615031,0.9702183 0.097182,0 0.083295,-0.3336208 0.4330446,-0.1199242 0.4306401,0.2631203 0.216699,0.1355642 0.4296663,0.2647074 2.0858202,1.13836043 3.8496455,1.41300027 5.8769904,1.43753027";
 
@@
 
-\caption{The dynamics of anthropomorphism. We distinguish three main phases:
-    \emph{initialization}, \emph{familiarization} and \emph{stabilization},
-    preceded by a \emph{pre-interaction} phase. The pre-interaction phase
-    is characterized through an \emph{initial capital of anthropomorphism} (ICA, noted \ICA).
-    Once the interaction starts, the level of anthropomorphism increases due to
-    the \emph{novelty effect}, and then decreases to reach a \emph{stabilized
-    level of anthropomorphism} (SLA, noted \SLA). \ICA and \SLA may vary
-    depending on the user (and his/her expectations), the robot and the context
-    of interaction.  During the interaction, unpredicted behaviors of the robot
-    (\emph{disruptive behaviors}) may lead to local increases or decreases of
-    the level of anthropomorphic effects.}
+\caption{\textbf{Conceptual model of the dynamics of anthropomorphism}. We
+    distinguish three main phases: \emph{initialization}, \emph{familiarization}
+    and \emph{stabilization}, preceded by a \emph{pre-interaction} phase. The
+    pre-interaction phase is characterized through an \emph{initial capital of
+    anthropomorphism} (ICA, noted \ICA).  Once the interaction starts, the level
+    of anthropomorphism increases due to the \emph{novelty effect}, and then
+    decreases to reach a \emph{stabilized level of anthropomorphism} (SLA, noted
+    \SLA). \ICA and \SLA may vary depending on the user (and his/her
+    expectations), the robot and the context of interaction.  During the
+    interaction, unpredicted behaviors of the robot (\emph{disruptive
+    behaviors}) may lead to local increases or decreases of the level of
+    anthropomorphic effects. The duration of these phases may vary and the
+    overall shape of the curve is unique to each human interacting with a
+    specific robot in a given context, as depicted by the alternative curves.}
 
@@
 
-First, the \emph{initialization} phase. During this short phase (from a couple
-of seconds to a couple of hours), we observe an increased level of
-anthropomorphism, from an \emph{initial capital of anthropomorphism} \ICA
-(detailed in the next section) to a peak of anthropomorphic manifestations
-\AntMax that corresponds to the maximum of the \emph{novelty effect}.
-Section~\ref{sec:initialization} details this first phase.
-
-The second phase, \emph{familiarization}, lasts longer (up to several days) and
-models the process of the human getting acquainted to the robot: by observation
-and interaction, the human builds a model of the robot's behavior that allows
-him/her to predict the robot's actions. We observe a decrease of
-anthropomorphic effects during this phase, that we explain by the acquired
-ability to predict the behavior of the robot: the initial apparent behavioral
-complexity vanishes, and the robot is considered more and more as a tool.
-Section~\ref{sec:familiarization} discusses the second phase.
-
-The last phase is the \emph{stabilization} phase. The level of anthropomorphic
-effects tends to stabilize over a longer time, to reach a \emph{stabilized
-level of anthropomorphism} \SLA. \SLA may be null (no anthropomorphic
-effects observed anymore), but it may also remain at a higher level.  This
-third phase, as well as the \emph{stabilized level of anthropomorphism}, are
-discussed in section~\ref{sec:stabilization}.
-
-\paragraph{Pre-interaction phase and Initial Capital of Anthropomorphism (ICA)\\}
-\label{sec:ica}
-
-The \emph{initial capital of anthropomorphism} \ICA describes the initial
-potential for the robot to be anthropomorphized by the human user in a given
-situation.  This potential depends on several factors, introduced in
-section~\ref{sec:multi-factors}, see also Figure \ref{fig:factors}. It has been
-shown, for instance, that some \textit{people} tend to anthropomorphize more
-than others, that some \textit{situations} induce anthropomorphism more than
-others, that \textit{children} tend to anthropomorphize more than adults, and
-that some \textit{cultures} are notorious for their anthropomorphic religions
-and worldviews~\citep{epley_when_2008}. Also the shape and design of the robot
-play a role, as well as the context in which the interaction takes place. Our
-model of anthropomorphism represents these factors as a compound metric \ICA. As
-such, \ICA describes the level of anthropomorphic projections just prior the
-first (real or imagined) interaction with a robot. In this stage of
-pre-interaction, people form \textbf{initial expectations} toward the robot and
-imagine how they will use it / interact with it.
-
-Taking up on our suggestion to have four main factors that impact on
-anthropomorphism, we propose that the initial capital of anthropomorphism can be
-build \emph{a priori}.  As the \ICA marks the very moment before the first real
-or imagined contact of the human with the robot, the \textit{interaction
-history} between the two players is empty; consequently the time factor $t$ is
-not taken into account when building the \ICA.  The specific \ICA value reflects
-how far a robot is likely to be anthropomorphized, based on the following three
-factors:
-
-\begin{enumerate}
-
-    \item ~\emph{Human factor} $S$: The \textbf{personality} and individual
-        traits of the human user: Psychological characteristics / determinants
-        that influence a person's tendency to anthropomorphize
-        artifacts~\citep{epley_seeing_2007}. Other individual traits and
-        demographic aspects are comprised (\eg age, gender, cultural background,
-        professional background).
-
-    \item ~\emph{Robot factor} $R$: The robot's \textbf{design} and how it
-        appears to the human user. Characteristics of the robot's form,
-        behavior, and interaction modalities (anthropomorphic
-        design)~\citep{fong_survey_2003}.
-
-    \item ~\emph{Context factor} $C$: The real or imagined
-        \textbf{purpose} of the robot, including the situational context in
-        which it is used, as well as the task context and role in which the
-        robot is used / experienced (environmental
-        context)~\citep{joosse_what_2013}.
-
-\end{enumerate}
-
-For \textbf{personality}, we suggest to apply the psychological \textit{3-factor
-theory} of anthropomorphism by \citet{epley_seeing_2007}. For instance, children
-generally tend to anthropomorphize objects more than adults. Also, a person who
-lacks social connection is said to be more likely to anthropomorphize. Both
-aspects would increase \ICA. This means that, one and the same robot used by a
-different user, can lead to a different \ICA.
-
-For \textbf{design}, we understand that a robot that follows an anthropomorphic
-design up to a certain acceptable level (\eg Nao) leads to a higher \ICA than a
-rather functional robot (\eg Roomba). Also, a robot that is able to display
-facial expressions would increase the \ICA. Quantifying the \emph{level} of
-anthropomorphic design in a robot, as suggested for instance by
-\citet{fong_survey_2003}, can be difficult.  Nevertheless, the important aspect
-is how the robot appears to the user, \eg human-like or machine-like, acceptable
-or not-acceptable.\footnote{It becomes clear that the \textit{robot factor} can
-not be fully separated from the \textit{human factor}. The reason for this is
-that the message that design tries to make, always lies in the eye of the
-beholder. No matter how much effort a designer spends in making the ``message''
-of the artifact's design clear, there is always some scope and creative freedom
-in how the design is interpreted by the beholder.}
-
-By taking the \textbf{purpose} of a robot into account, we suggest that the real
-or imagined application context of the robot, or in which situation the
-interaction occurs, impacts how far the robot will be attributed human-like
-characteristics. We draw on findings such as presented in
-\citet{joosse_what_2013}. The authors showed for instance that when the same
-robot (Nao) is used in a different task context (cleaning task \emph{vs.} tour
-guide), users ascribe different personalities to the robot. In general, a robot
-which is imagined in a social, entertaining or playful context leads to a higher
-\ICA than a robot which is used for a routine or focused task (security, rescue,
-etc.). This was also found in an analysis of anthropomorphic language in online
-forum discussions about the AIBO, Roomba, and iPad
-\citep{fink_anthropomorphic_2012}. Regardless of the conversation topic, more
-anthropomorphic language was found in the AIBO forum. However, this was not only
-due to the zoomorphic (pet-like) shape of AIBO but also due to its  playful
-purpose. The idea that the purpose of a robot are crucial factors, also receives
-support from Goetz \& Kiesler's work that revealed that people prefer a serious
-robot for serious tasks and a less serious robot for more playful
-tasks~\citep{goetz_cooperation_2002, goetz_matching_2003}.  However, what about
-artificial agents that seem to have no purpose? \cite{kaplan_free_2000}
-discusses the role of uselessness in the design of robots. He argues that
-artificial pets such as the AIBO, have no real purpose, in a sense that they do
-not provide any kind of service, or, in other words \textit{``they are not doing
-what you tell them to do''} and \textit{``they might refuse the order of its
-owner''}. It is this very aspect that might increase people's tendency to
-anthropomorphize the robot. According to Kaplan, it is in our daily use
-language, that we tend to attribute intentions to devices that are not doing
-their job well. For instance, we do not develop any kind of relationship with
-our computer, washing machine or TV set when they work properly. The author
-argues that it is only when they start dis-functioning, when they show that they
-can act differently that what we ordered, that we are ready to give them some
-kind of ``intentionality''.
-
-Also, we suggest that the environmental context in which people experience and
-interact with the robot impacts the \ICA. For instance, several friends
-interacting simultaneously with the robot might lead to increased \ICA for each
-of the users, due to increased human-human social interactions (the robot might
-be perceived to be part of the social interaction, and in turn attributed
-human-like qualities~\citep{baxter2013do}).
-
 \subsubsection{Initialization Phase\\}
-\label{sec:initialization}
-
-%\paragraph{The Novelty Effect\\}
-%\label{sec:noveltyeffect}
-
-We assume that the short phase of initialization is strongly affected by the
-so-called novelty effect.  Novelty effects have been described with interactive
-technologies in general \citep{rogers_diffusion_1995} and also in several
-long-term HRI studies in workplaces
-\citep{huttenrauch_fetch-and-carry_2003,mutlu_robots_2008}, in schools and
-public places
-\citep{gockley_designing_2005,kanda_interactive_2004,kanda_communication_2005},
-or elder care centers \citep{sabelli_conversational_2011}. Further, also with
-domestic robots it has been found that people's interest, engagement, and
-fascination with the robot decreased over time
-\citep{fink_living_2013,fernaeus_how_2010,sung_robots_2009}.
-
-To illustrate how the novelty of a robot can evoke anthropomorphic effects, we
-present an example from our long-term ethnographic study with Roomba vacuum
-cleaning robots in households \citep{fink_living_2013}. The observed scenario
-describes how an elderly woman (E., 71 years, living on her own with a little
-dog in a small row house) was setting up and using the robot for the first time
-during about 10 minutes.
-
-At several occasions, while watching how the robot moves around and cleans, E.
-makes compliments to the robot: \emph{``Nice!''} or \emph{``Good job!''} or
-\emph{``Bravo!''}. Once, when the Roomba turns right in front of some crumbs on
-the kitchen floor and moves away without cleaning them up, E. says:
-\emph{``There you forgot something, what about over there? Look, there you still
-have something to clean up!''}, and she points at where she wants the Roomba to
-go. Further, she uses deictic gestures and tells the robot: \emph{``No, go this
-way! Come over here!''}. The woman keeps observing the robot and wonders about
-its intentions, asking it directly: \emph{``Why do you leave the kitchen? There
-is still something there on the fringe!''}. E. turns to the experimenter, and
-tells her: \emph{``She [the robot] loves the hall!''}.
-
-Besides this behavior of generally anthropomorphizing the robot, we observe the
-following concrete instances as anthropomorphic effects in this scenario:
-talking directly to the robot, or asking it questions (though it doesn't
-recognize speech); giving it nick-names or ascribing a gender, praising the
-robot, using pointing gestures toward the robot, or trying to direct it around
-with commands, and attributing a personal preference / intention to the robot
-(\emph{``she loves the hall!''}).
-
-During the following visits at the woman's place, E. did not talk to the robot
-anymore, and generally behaved in a less anthropomorphizing way. The observed
-effects were likely due to the novelty of the robot, and the fact that E. was
-not familiar with the robot and its behavior.  As
-\cite{persson_anthropomorphism_2000} names it: \textit{``Anthropomorphism is a
-way of making sense of complex behavior in the world around us.''} Thus, as soon
-as this complexity is reduced, also anthropomorphism might be reduced.
+
+The \textit{Initialization Phase} starts with the so-called \textit{Initial
+Capital of Anthropomorphism} ($ICA$), which corresponds to \ICA (value of \Ant
+at time point $0$). This value considers the multiple factors presented in
+Section~\ref{sec:multiple-factors}, thus it is composed by factors of the human
+$H$, the robot $R$, and the context of use $C$. As such, \ICA describes the
+value of anthropomorphic effects that can be expected to occur during the first
+contact between the human and the robot in a given situation. During this first
+phase, pre-conceptions and initial expectations as well as previous experience
+of the user with other similar types of robots and similar contexts can have a
+strong impact and influence the general tendency to anthropomorphize.
+
+During the \textit{Initialization Phase} we expect an increasing value of $A$
+that may be partly due to the so-called \textit{effects of novelty} of the
+robot. Such effects have been described with interactive technologies in general
+\citep{rogers_diffusion_1995}, and also in several long-term HRI studies in
+workplaces \citep{huttenrauch_fetch-and-carry_2003,mutlu_robots_2008}, in
+schools and public places
+\citep{gockley_designing_2005,kanda_communication_2005,kanda_interactive_2004},
+and elder care centers \citep{sabelli_conversational_2011}. Also long-term
+studies of domestic robots have shown similar effects and found that after some
+time people's interest, engagement, and fascination of the robot decreased
+\citep{sung_robots_2009,sung_domestic_2010,fernaeus_how_2010,fink_living_2013}.
+
+What type of anthropomorphic effects are typical during the
+\textit{Initialization Phase}? In our own work, we observed that users
+spontaneously tend to talk directly to the robot (though the user knows that the
+system is not be able to recognize speech), for instance, by greeting the robot,
+asking questions to it, giving it nick-names or ascribing a gender, praising the
+robot, commenting on its performance in general, and giving commands. Also, the
+use of point gestures and waving at the robot were fairly common among
+participants of our studies, as well as ascribing gender and some personal
+preferences or intention to the robot. (Note that we did not even use an
+anthropomorphic robot but a Roomba vacuum cleaning robot.)
+
+In general, it appears that anthropomorphism during the \textit{Initialization
+Phase} is a commonly observed phenomenon. But we would like to stress again that
+most of these effects are likely to fade out over time.
 
 \subsubsection{Familiarization Phase\\}
-\label{sec:familiarization}
-
-In this context, \emph{familiarization} means \emph{to get acquainted with}.
-It is not to be confused with the \emph{familiarity thesis} that relates to the
-projection of already known cognitive models onto the robot. We discuss this other
-aspect in section~\ref{sec:cognition-neuroscience}.
-
-The \emph{familiarization phase} starts at the peak of the \emph{novelty
-effect}: anthropomorphic effects are at their maximum, the user thinks (s)he is
-potentially facing an agent aiming at ``human-level intelligence'' (to take
-McCarthy's words). This is a transient state that quickly vanishes, and the
-projected anthropomorphism then starts to decrease while the human observes and
-recognizes that the behavior of the robot is generally \emph{predictable} and
-possibly \emph{deceptive} (for instance, it talks but does not understand when
-we talk; it has eyes but does not recognize everyday objects we show; \etc).
-
-\paragraph{Disruptive behaviors\\}
-
-By \emph{disruptive behaviors}, we mean any behavior exhibited by the robot that
+
+In the \textit{Familiarization Phase} the user gets acquainted and familiar with
+the robot and with using the robot, and hence the tendency to anthropomorpize
+decreases. This phase typically starts as the local maximum value of
+anthropomorphic effects that are enhanced by the novelty of the robot start to
+wear off. The user may think that he/she faces an agent that aims at
+``human-level intelligence'' (to take McCarthy's words). This is a transient
+state that quickly vanishes as the user recognized that the behavior of the
+robot is generally \textit{predictable} and possibly \textit{deceptive}. For
+instance, the robot produces verbal utterances (it ``talks'') but it does not
+understand when we talk; or the robot is endowed with eyes but does not
+recognize the objects we show it.
+
+\paragraph{Disruptive behaviors.}
+
+We call \emph{disruptive behaviors} any behavior exhibited by the robot hat
 appears unexpected to the user: for instance, a robot may usually follow always
@@
 detection of a new obstacle, but as long as this reason is not immediately
-intelligible to the user, the behavior counts as \emph{disruptive}. (We will
-come back to the role of disruptive behaviors later, in Section
-\ref{sec:disruptive}.)
-
-As illustrated in Figure~\ref{fig:dynamics}, our model represents
-\emph{disruptive behaviors} as either local increases or local decreases of
-anthropomorphic effects in the familiarization phase (and at a lesser extend, in
-the stabilization phase): because such behaviors are unexpected, a human
-observer may interpret them either as the result of a richer deliberative
-process, which in turn leads to the supposition of complex cognitive skills, or
-conversely as a failure, reminding the human that the robot is ``just a
-machine''. Section~\ref{sec:disruptive} discusses more in depth the impact of
-the user's perception of disruptive behaviors, and their cognitive correlates.
-
-To illustrate how a disruptive behavior of a robot can evoke anthropomorphic
-effects, we present again an example from our long-term ethnographic study with
-Roomba vacuum cleaning robots in households \citep{fink_living_2013}. The
-observed scenario describes how a family (young parents, 26 and 28 years old,
-with 3 little children, 5 and 4 years, and 6 months old, living in a house with
-garden on the countryside) were using the robot during the first week.
-
-The father (M.) always lets Roomba clean up the ground floor after the family
-finishes dinner and they all go upstairs to put the children to bed. When the
-robot would have finished its cleaning cycle, the parents would later just find
-it docked at its charging station. It used to be like this every evening.
-However, one day when the father comes downstairs, Roomba is not at its station.
-He says: \emph{``Hey, Roomba, where are you? Why did you not want to got to
-sleep last night?''}. After some searching he found it stuck under the sofa and
-wondered why this had happened.
-
-What is the observed anthropomorphic effect in this scenario? Usually, the
-father did not talk to the robot or praise it. However, now that the robot did
-something unexpected (it was not at its usual place) he started wondering about
-its ``intention'' and directly asked the robot for its reasons to not
-\textit{``go to sleep''}.
+intelligible to the user, the behavior counts as \emph{disruptive}. We further
+discuss the role of disruptive behaviors in cognitive terms in Section
+\ref{sec:disruptive}.
 
 \subsubsection{Stabilization Phase\\}
-\label{sec:stabilization}
-
-The last phase is the \emph{stabilization} phase. The level of anthropomorphic
-effects tends to stabilize over a longer time, to reach a \emph{stabilized
-level of anthropomorphism}, noted \SLA.
-
-If, after the familiarization phase, no anthropomorphic effects are observed
-anymore, $\sla = 0$. This can be interpreted as the user interacting with the
-robot in a routine way, without projecting anymore human-like traits on the
-robot.
-
-\paragraph{Stabilized Level of Anthropomorphism\\}
-
-The \emph{Stabilized Level of Anthropomorphism} describes the long-term lasting
-level of anthropomorphism.  We proposed that \ICA is built on three factors:
-user's \emph{personality}, robot's \emph{design} and interaction \emph{purpose}
-(or \emph{interaction context}). The user's personality and the context of use
-do also influence \SLA.  In particular, it appears that the user's level of
-acquaintance with technologies plays an important role in long-term tendency to
-anthropomorphize~\citep{fink_living_2013} (people more familiar with technology
-understand, and hence predict, better the behavior of the robot, which in turn
-leads them more frequently to ultimately consider the robot as a simple tool).
-
-The robot's design, on the other hand, plays a more subtle role, and strong
-initial anthropomorphic design does not mandate high \SLA: lasting
-anthropomorphic effects have been observed on non-anthropomorphic robots (like
-the iRobot Roomba~\citep{fink_living_2013} or the military iRobot
-PackBot\footnote{Rodney Brooks has reported in keynotes that occasionally
-soldiers would give a name to \emph{their} PackBot and require it to be repaired
-instead of being replaced by another one in case of incident.}), and on the
-contrary, anthropomorphic designs can lead to higher expectation deceptions,
-resulting in the robot not being used anymore.
-
-Note that the \emph{Initial Capital of Anthropomorphism} and the
-\emph{Stabilized Level of Anthropomorphism} are generally not correlated: one
-individual may have high potential of anthropomorphizing (high \ICA) at first
-sight of a good-looking humanoid robot, and get disappointed by the actual
-abilities of the robots, down to routine, non-anthropomorphic, interactions (low
-\SLA), while another user with the same high \ICA may, for instance, creates
-lasting affective bonds with the same robot, and keeps anthropomorphizing it
-(higher \SLA).
+
+During the \textit{Stabilization Phase} the value of $A$ tends to stabilize over
+a longer time, to reach a value that we call the \textit{Stabilized Level of
+Anthropomorphism} ($SLA$), which corresponds to \SLA. The value that the
+$SLA$ approaches is unique for each user interacting with a specific robot in a
+given situation. \SLA may approach $0$, when no anthropomorphic effects
+are observed anymore, for instance, when the user is interacting with the robot
+in a routine way and he/she does not project any human-like traits unto the
+robot\footnote{The robot may have become \textit{``invisible in use''}
+\citep{takayama_toward_2011}.} As such, the $SLA$ stands for the long-term
+lasting value of anthropomorphism.  We proposed that \SLA (the value
+corresponding to the $ICA$) is built on multiple factors (see
+Section~\ref{sec:multiple-factors}) and similar \SLA is based on these
+factors, however taking into account the \textit{interaction history} $t$ that
+the user has with the robot.  Note that the $ICA$ and the $SLA$ are generally
+not correlated. A person may initially have a high potential of
+anthropomorphizing (high \ICA), for instance a highly anthropomorphic robot,
+but subsequently get disappointed by the actual capabilities of it and stop
+explaining it in terms of human-like characteristics (low \SLA). Another
+user may however create lasting affective bonds with the same robot and may
+continue to anthropomorphize the robot (high \SLA).
 
@@
 
-\section{The Cognitive Correlates of Anthropomorphism}
+\section{Towards a Cognitive Interpretation}
 \label{sec:cognition-neuroscience}
 
-This section provides an initial interpretation of anthropomorphism in
-terms of \emph{cognitive correlates}: how human cognition can explain the
-dynamic nature of our interactions with robots, and what are the main cognitive
-stages upon which researchers can build to design better, deeper human-robot
-interactions.
-
-The next sections introduce a model of the cognitive stages involved in
-human-robot interaction, that can be interpreted in parallel to the model of the
-dynamics of anthropomorphism.
+The model that we have introduced so far helps to represent and organize the
+\emph{observations} of anthropomorphism. It does so at a conceptual level, and
+with a special emphasis on the evolution over time.
+
+This abstract model may contribute to a better understanding of the
+\emph{phenomenology} of anthropomorphism, but it does not help to \emph{explain}
+the phenomenon. This section proposes to look at the dynamics of
+anthropomorphism in terms of \emph{cognitive correlates}: how human cognition
+can explain the dynamic nature of our interactions with robots, and what are the
+main cognitive stages upon which researchers can build to design better, deeper
+human-robot interactions.
 
@@
 %}
-\caption{The three cognitive stages of anthropomorphism: Stage 1 is the instinctive,
+\caption{\textbf{The three cognitive stages of anthropomorphism}: Stage 1 is the instinctive,
 sub-cognitive identification of living peers. {\it Empathy} is characteristic
@@
 cases, the next occurrence of an expected behavior, if correctly interpreted
-(case I or II), is likely to lead to stronger effects due to a larger $\delta$
+(case I or II), is likely to lead to stronger effects due to a larger delta 
 between expectations and actual observed behavior.
@@
 
-\section{Discussion}
-\label{sec:discussion}
-
-The model of anthropomorphism we propose is still a work in progress. In
-particular, its implications regarding the design of (social) robots and
-human-robot interaction are still to be refined but we hope this article helps
-encourage an open dialogue between those who do research of anthropomorphism.
-
-Coming back to our two main hypotheses, on one hand we investigated how far
-anthropomorphism is based on multiple factors, namely, the design of the robot,
-the personal characteristics of the human user, and the context / situation in
-which the robot is used.  We elaborated this hypothesis by reviewing literature
-from various related disciplines. Based on the outcomes of this, on the other
-hand, we proposed a model of the \emph{Dynamics of anthropomorphism}. We offered
-a cognitive interpretation of this model, as well as illustrations from our own
-previous work.  However, our model has limitations, for instance, regarding the
-general effect of time and familiarization on anthropomorphism. We will discuss
-this in the following section.
-
-\subsection{Effect of time / familiarization on anthropomorphism}
-
-We have proposed that time, or in other words, the user's familiarization with
-the non-human agent, models how anthropomorphism evolves over time. Our general
-assumption is that with continued interaction, and in turn growing user
-experience, the system becomes more predictable and consequently, the user's
-need to anthropomorphize the agent decreases. We would like to discuss this
-suggestion here.
-
-With \textit{time} as a factor, we referred to long-term interaction with the
-robot, which is related to what has been described as \textit{novelty effect}
-but also accounts for the user getting used to the robot. Several studies
-described that after some time users interacted less with the robot or lost
-interest in it. Sustaining long-term interaction is one of the main challenges
-that robots with applications in daily life contexts face. Our question is that,
-if we would like overcome the novelty effect, how far does the robot's
-behavioral complexity play a role? Should the robot vary its behavior and behave
-unexpectedly from time to time?
-
-Most experiments, and even more when they investigate long-term interactions,
-are carried out with robots exhibiting relatively simple behaviors. In our
-model, the maximum level of anthropomorphism \AntMax is reached with the novelty
-effect, and then decreases. A natural question is whether we can design robots
-such that \AntMax remains high, possibly higher than $\ant[t_{novelty~peak}]$
-(note that to know if sustaining strong anthropomorphic interaction is desirable
-is entirely another question).
-
-Intuitively, the behavioral complexity of the robot, and in particular, the
-ability for the robot to evolve over time and \emph{adapt its behavior to the
-user} as the user familiarizes his/herself with the robot (\ie
-\emph{co-familiarize}), seems to play a key role.
-
-Our model is based on the assumption that anthropomorphism tends to decrease
-with the user becoming more familiar to the robot.  We explain this by the
-general motivation to anthropomorphize an agent which might be difficult to
-understand (in its functionality or behavior, for instance). In turn, a user
-might ascribe intentions or emotions to the system because the system's output
-was unexpected for the user, however he/she still wants to make sense of it.
-Consequently, we estimate that when the user has familiarized herself/himself
-with the system, thus reached the point of when the system is usable and
-explainable, the tendency to anthropomorphize decreases.
-
-However, there exist views that suggest just the opposite, namely, that
-familiarization and more interaction with an agent \textit{increase} the
-tendency to anthropomorphize \citep{eddy_attribution_1993}. Similarly,
-\cite{duffy_anthropomorphism_2003} reports that several psychological
-experiments and human-robot interaction experiments showed that familiarity may
-also ease social acceptance and even tend to \textit{increase} people's tendency
-to anthropomorphize.
-
-Consequently, we have to accept that our model of the \emph{Dynamics of
-Anthropomorphism} needs to be verified, to see how far our hypotheses can hold.
-In particular, the effect of the user's familiarity with the system needs to be
-studied over a longer period of time.
-
-\subsection{Measuring anthropomorphism}
+\section{Measuring anthropomorphism}
 \label{sec:measuring}
 
-With this extended understanding of anthropomorphism being determined by
-multiple factors and showing dynamics over time, it also becomes questionable if
-the metrics and techniques that are currently used to measure anthropomorphism
-are sufficient. We would like to discuss two issues: the scenario in which
-anthropomorphism is measured, and how, with which means it is assessed.
-
-One needs to keep in mind that anthropomorphism arises in an interaction. We
-believe that as such, anthropomorphism can be better understood when studied and
-measured in a real, direct human-robot interaction compared to a mediated
-interaction. In a direct interaction scenario one could also take the human's
-behavior into account, as it seems to reflect an anthropomorphic interaction
-\citep{krach_can_2008,hegel_understanding_2008,weiss_i_2009}.  Of course, the
-scenario and measurements one uses depend on the research questions, so a direct
-human-robot interaction might not always be preferred.
-
-However, most of the experiments that investigate anthropomorphism in HRI are
+Most of the experiments that investigate anthropomorphism in HRI are
 conducted in controlled lab-settings during a short-term scenario. For instance,
@@
 subsequently fill in a questionnaire, to assess how far the different types of
-robots were perceived human-like.\footnote{It can already be critical to not
-indicate the height / size of a robot when it is pictured or presented in a
-video. We cannot assume that without any point of reference, lay people estimate
-correctly the height of ASIMO or Nao, for instance, they might think these
-humanoid robots are the same size as a Barbie doll. Also, when showing a
-picture, the movements, behaviors, materials of a robot, and so forth are
-totally disregarded. However, these aspects are also crucial features of a
-robot, impacting how human-like it appears.} We think that such experimental
+robots were perceived human-like. We think that such experimental
 settings have limitations for studying a social phenomenon like
@@
 
-Regarding the second issue, how and with which means anthropomorphism is
-measured, one of the view existing tools to do so is 5-item anthropomorphism
-part of the Godspeed questionnaire \citep{bartneck_measurement_2008}. On 5 point
-semantic differential scales, people are asked to rate the following constructs:
-fake - natural, machinelike - humanlike, unconscious - conscious, artificial -
-lifelike, moving rigidly - moving elegantly. The critical point that we see with
-this is that ``human-likeness'' itself is complex and manifold. Being such an
-abstract concept, instead of asking the vague question, whether a robot is
-human-like or not, \cite{kahn_jr._robotic_2006} suggest to ask for more concrete
-constructs that are typical or unique of the concept of ``human-likeness''.  For
-instance, \cite{ruijten_introducing_2014} propose a 25-item questions to measure
-various concrete aspects of human-likeness. Consequently, anthropomorphism can
-be modeled along a scale that accounts for lower and higher levels of it.
-
-Still, we also feel that measuring anthropomorphism (or social engagement with a
-robot) is challenging because the phenomenon is partially unconscious, its
-mediation is largely subject-dependent, and we found the phenomenon generally
-difficult to verbalize for users.
-
-To reduce subjectivity and still accurately account for psychological effects,
-it appears necessary to interleave quantitative and qualitative assessments of
-anthropomorphic effects.
+The Godspeed questionnaire~\citep{bartneck_measurement_2008}, and in particular,
+its subpart focused on anthropomorphism, is the main validated questionnaire to
+assess anthropomorphism. On 5 point semantic differential scales, people are
+asked to rate the following constructs: fake \vs natural, machinelike \vs
+humanlike, unconscious \vs conscious, artificial \vs lifelike, moving rigidly
+\vs moving elegantly. Because the concept of ``human-likeness'' itself is
+complex and abstract, \cite{kahn_jr._robotic_2006} suggest to ask for more
+concrete constructs that are typical or unique of the concept of
+``human-likeness''.  For instance, \cite{ruijten_introducing_2014} propose a
+25-item questions to measure various concrete aspects of human-likeness.
+Consequently, anthropomorphism can be modeled along a scale that accounts for
+lower and higher levels of it.
+
+Still, measuring anthropomorphism (or social engagement with a robot) through
+subjective self-reporting remains challenging because the phenomenon is
+partially unconscious, its mediation is largely subject-dependent, and we found
+the phenomenon generally difficult to verbalize for users.
+
+As a consequence, to reduce subjectivity and still accurately account for
+psychological effects, it is necessary to interleave quantitative and
+qualitative assessments of anthropomorphic effects.
 
@@
 answer indicated an anthropomorphic view of the robot. This process led to a
-``qualitative score'' that reflects how far the robot is anthropomorphized. We
-used the following constructs to measure how far the robot is perceived as a
-human-like agent:
-
-\begin{itemize}
-    \item ~Spontaneously ascribe inner states, {\it eg. robot is
-        hungry, tired}
-    \item ~Ascribe ``own will'', {\it eg. robot could leave room by itself, does not
-        always obey, could do a b\^{e}tise...}
-    \item ~Describe robot as friend
-    \item ~Ascribe cognitive abilities, {\it eg. robot is able to see,
-        able to hear}
-    \item ~Belief robot has feelings, {\it eg. robot can be happy or sad}
-    \item ~Give anthropomorphic explanation for
-        \begin{itemize}
-            \item ~Why robot can (not) leave room alone {\it eg. it would be sad when left alone}
-            \item ~Misbehavior {\it eg. robot wants to make a tour, doesn't
-                like to play any longer}
-        \end{itemize}
-\end{itemize}
+``qualitative score'' that reflects how far the robot is anthropomorphized.
+Table~\ref{tab:domino-questions} summarizes the constructs that we used to
+measure how far the robot is perceived as a human-like agent, along with example
+questions.
+
+\begin{table}
+\centering
+\begin{tabular}{lp{10cm}}
+    \toprule
+    \textbf{Expectations}  &
+    \emph{How do you imagine a robot?} \newline
+    \emph{What could it look like?} \newline
+    \emph{Have you ever seen a robot before?}
+    \\
+    \midrule
+    \textbf{Impression} &
+
+    \emph{When you first saw R, what did you think?} \newline
+    \emph{Is R a robot? How do you know?} \newline
+    \emph{Did you expect R would come over to you when you call it?} \newline
+    \emph{What happened when you put the domino tile in the box?}
+    \\
+
+    \midrule
+    \textbf{Ascribe intention} &
+
+    \emph{Do you think R could go out the door all by itself?} \newline
+    \emph{Does R always obey / come over to you?} \newline
+    \emph{Could R do something silly?} \newline
+    \emph{Why did R not come over to you when you called it?}
+    \\
+    \midrule
+    \textbf{Ascribe cognitive connections} &
+
+    \emph{Here is a domino tile. Do you think R can see it?} \newline
+    \emph{When I say \textit{``Hello R!''}, do you think R can hear it?}
+    \\
+    \midrule
+    \textbf{Ascribe emotional state} &
+
+    \emph{Does R have feelings? Can R be happy or sad sometimes?}
+    \\
+    \midrule
+    \textbf{Social acceptance} &
+
+    \emph{Do you like R? Why (not)?} \newline
+    \emph{What do you (not) like about it?} \newline
+    \emph{Would you like to have R at home?}
+    \\
+    \midrule
+    \textbf{Companionship} &
+
+    \emph{Could R be your friend? Why (not)?}
+    \\
+    \midrule
+    \textbf{Ascribe moral standing} &
+
+    \emph{Assume you go on a holiday for two weeks. Is it alright to leave R
+    alone at home? Why (not)?}
+    \\
+    \bottomrule
+
+    \end{tabular}
+
+    \textbf{\refstepcounter{table}\label{tab:domino-questions}Table \arabic{table}.} Constructs and questions used during the semi-structured interviews
+    with children. The Ranger robot toy box is abbreviated with ``R''. Questions
+    related to the construct \emph{expectations} were asked during the
+    pre-interview.
+
+\end{table}
 

### 2014-11-12 paper.tex
In depth pass on the first part (section 1 and 2)

@@
 \def\firstAuthorLast{Fink {et~al.}} 
-\def\Authors{Julia Fink\,$^{1*}$, S\'{e}verin Lemaignan$^{1}$, Claire Braboszcz$^{2}$ and Pierre Dillenbourg$^{1}$}
+\def\Authors{Julia Fink\,$^{1*\dagger}$, S\'{e}verin Lemaignan$^{1\dagger}$, Claire Braboszcz$^{2}$ and Pierre Dillenbourg$^{1}$}
 \def\Address{$^{1}$Computer-Human Interaction in Learning and Instruction (CHILI) \\ Ecole Polytechnique F\'{e}d\'{e}rale de Lausanne (EPFL) \\ CH-1015 Lausanne, Switzerland \\
@@
 Universit\'{e} de Gen\`{e}ve \\ CH-1211 Gen\`{e}ve, Switzerland
+
+\vspace{0.5em}\tiny{$\dagger$ These authors have equally contributed to this article.}
 }
@@
 cognitive science, and neuroscience, this article proposes to extend our current
-understanding of anthropomorphism. By doing so, we propose a \textbf{formal model} that defines a
-\textbf{clear terminology} and accounts for the \textbf{non-monotonic dynamics} of
-the phenomenon. We further relate the observed \emph{effects} of anthropomorphism to
+understanding of anthropomorphism. We propose a \textbf{qualitative model} that defines a
+clear terminology and accounts for the \textbf{non-monotonic dynamics} of
+the phenomenon. We further relate the observed effects of anthropomorphism to
 their \textbf{underlying cognitive precursors}.
@@
 design of the non-human agent, the individual psychological determinants of the
-human user, and the context of use. Moreover, we discuss several \textbf{episodes of
-interaction} that influence the anthropomorphic projections on the robot, like
+human user, and the context of use. Moreover, we discuss several episodes of
+interaction that influence the anthropomorphic projections on the robot, like
 the \textbf{novelty effect}, the role of \textbf{familiarization} and the
@@
 
-Finally, the article also discusses techniques and scenarios to measure anthropomorphism,
+Finally, the article also discusses techniques to measure anthropomorphism,
 and we conclude with a few suggestions on how others can apply our model to
@@
 A phenomenon that is often studied related to this is \textbf{anthropomorphism}.
-Along this line, this article aims at fostering a better understanding of
+This article aims at fostering a better understanding of
 anthropomorphism (noted \Ant in this paper) in human-robot interaction by
@@
 emerges from the (real or imagined) \emph{interaction} between a non-human agent
-(\eg a robot) and a human~\citep{persson_anthropomorphism_2000}. According
+(a robot in our case) and a human~\citep{persson_anthropomorphism_2000}. According
 to~\cite{epley_when_2008}, anthropomorphism includes that the human perceives,
@@
 
-To support the reflection on variances and dimensions of anthropomorphism, it may be 
+To support the reflection on variances and dimensions of anthropomorphism, it is 
 useful to consider a few experimental
@@
                 \includegraphics[width=0.75\textwidth]{ranger}
-                \caption{Interaction scenario of the \emph{Ranger} domino study:
-                the robot toy box Ranger transports domino tiles between the two
+                \caption{Interaction scenario of the domino study:
+                    the robot toy box \emph{Ranger} transports domino tiles between the two
                 children}
@@
             \includegraphics[width=\textwidth]{correlation}
-            \caption{\emph{Engagement actions} vs \textit{subjective anthropomorphic
+            \caption{\emph{Actions reflecting engagement} vs \textit{subjective anthropomorphic
                 perception} evidence one cluster of
@@
         \end{subfigure}
-        \caption{Children's interaction with Ranger, and their anthropomorphic
-        projections onto the robot. Overall, large variations of both children's
-        behavior and their perception of the robot were found but seemed to be
-        correlated to each other.}
+        \caption{Investigating children's interactions with a robot in a playful
+            context: anthropomorphic perception does not necessarily positively
+            correlate with engagement.}
     \label{fig:ranger}
@@
 shows data from a (yet unpublished) study in which 13 pairs of children (4-5
-years old) played for about 20 minutes a Domino game with a robot toy box (the
+years old) played for about 20 minutes a domino game with a robot toy box (the
 robot was tasked to carry domino pieces from one child to the other,
@@
 showing objects), based on video annotations. On the $y$-axis, we have a
-synthetic qualitative measurement of anthropomorphic projections onto the robot,
-based on two interviews with the children. The correlation between both these
-values is significantly \emph{negative}: the more the children engaged into
-interaction, the less prone to anthropomorphic projections they were. This
-diagram also highlights an interesting cluster of children who did not interact
-much with the robot, and still reported a strong anthropomorphic perception of
-the robot.
+synthetic qualitative measurement of anthropomorphic perception of the the
+robot, based on two interviews with the children. The scatter plot evidences one
+cluster of high-anthropomorphizers/low-interactors and a another group of
+children who interact more with the robot and anthropomorphize it less: the
+more the children engaged into interaction, the less prone to an anthropomorphic
+perception they were.
 
@@
 article: how can we understand \emph{anthropomorphism} as a whole, and in such a
-way that it supports or improves human-robot interaction?
+way that it supports or improves the design of sustainable human-robot interaction?
 
@@
 
-First, by reviewing what anthropomorphism actually \emph{means}: besides an
+First, by reviewing what anthropomorphism actually means: besides an
 \emph{artifact-centered} understanding that explains anthropomorphism from the
@@
 
-Second, we propose a model, called the \textit{Dynamics of Anthropomorphism} to
-understand how anthropomorphism evolves over time
-~\citep{lemaignan2014dynamics}.  These dynamics are non-monotonic, and effects
-like the \emph{novelty effect} play here a key role.
-
-Finally, we adopt a third perspective on anthropomorphism by investigating its
-\emph{cognitive correlates}. Several studies previously showed that we build
-instinctive bonds with robots as soon as we attribute animacy, and we also know
-from social psychology some of the mechanisms that lead to
-\emph{familiarization}. We attempt here to ``connect the dots'', in order to
-build a practical model of the cognitive stages we encounter in human-robot
-interaction.
-
-\subsection{Terminology used in this article}
+Second, we propose a qualitative model of the \textit{dynamics of
+anthropomorphism} to understand how anthropomorphism evolves over time. These
+dynamics are typically non-monotonic, and effects like the \emph{novelty effect} play here
+a key role.
+
+Finally, we synthetize and integrate in an explanatory model the \emph{cognitive
+mechanisms} that underlie anthropomorphism. Several studies previously showed
+that we build instinctive bonds with robots as soon as we attribute animacy, and
+we also know from social psychology some of the mechanisms that lead to
+\emph{familiarization}. We attempt here to build a practical model of the
+cognitive stages we encounter in human-robot interaction.
+
+\paragraph{Terminology used in this article\\}
+
+While we discuss in section~\ref{meaning} the different meanings of
+anthropomorphism found in literature, it seems appropriate to already precisely
+define the terminology used in this article.
 
 We use the term \textbf{anthropomorphism} to describe the \emph{psychological}
-phenomenon, which arises in the \emph{social context} of an interaction between
-a human agent and a non-human agent, in our case, a robot (see Figure
+phenomenon which arises in the \emph{social context} of an interaction between a
+human agent and a non-human agent, in our case a robot (see Figure
 \ref{fig:anthropofig}). We use this term to refer to both people's tendency to
-\textit{perceive} human-like characteristics, and to the tendency to
-\textit{ascribe} or \textit{attribute} such human-like characteristics to the
-agent or artifact. Besides, we call {\bf anthropomorphic effects} the
-\emph{observable manifestations} of anthropomorphism, \ie the human's behaviors
-and actions toward a non-human agent that reflect the underlying cognitive
-process of anthropomorphizing.
-
-However, despite the fact that ``anthropomorphism'' literally means ``human
+\textit{perceive} (\textbf{anthropomorphic perceptions}) human-like
+characteristics, and to the tendency to \textit{ascribe} or \textit{attribute}
+such human-like characteristics to the agent or artifact
+(\textbf{anthropomorphic projections}). Besides, we call {\bf anthropomorphic
+effects} the \emph{observable manifestations} of anthropomorphism, \ie the
+human's behaviors and actions toward a non-human agent that reflect the
+underlying cognitive process of anthropomorphizing.
+
+Despite the fact that ``anthropomorphism'' literally means ``human
 form'' we propose that the term should \textit{not} be used to refer to the
@@
 of the product. The behavioral aspect is of special importance for interactive
-systems that show some degree of autonomy (independence).  Several categories of
-anthropomorphic form exist, with no common agreement on the borders and
-transitions between those: anthropomorphic, zoomorphic, caricatured, functional
-\citep{fong_survey_2003}.
+systems that show some degree of autonomy (independence).
 
@@
 The remainder of this article is organized as follows.  According to the three
-perspectives that we take, we first (in Section \ref{sec:anthropomorphism}) aim
-to establish a common ground in the understanding of anthropomorphism. We review
-literature from several relevant domains and integrate the different
-explanations into an understanding of anthropomorphism as a multi-factor
-phenomenon.  Based on this, Section~\ref{sec:our-ideas} proposes a new
-conceptual model of the \textit{Dynamics of Anthropomorphism}. This model
-describes the variances and dynamics of people's tendency to anthropomorphize an
-artificial agent, such as a robot.  Then Section
-\ref{sec:cognition-neuroscience} presents a cognitive and neuroscience
-perspective on anthropomorphism to consolidate our considerations and the
-proposed model.  Section \ref{sec:measuring} looks at how these models can be
-operationalized, and in particular, what are the tools at hand to measure
-anthropomorphism. Finally, Section \ref{sec:conclusion} concludes this article
-and offers starting points for further research on anthropomorphism and the
-effect of the human-like design approach in robotics.
+perspectives that we take, section \ref{sec:anthropomorphism} establishes a
+common ground in the understanding of anthropomorphism. We review literature
+from several relevant domains and integrate the different explanations into an
+understanding of anthropomorphism as a multi-factor phenomenon.  Based on this,
+section~\ref{sec:our-ideas} proposes a new qualitative model of the
+\textit{dynamics of anthropomorphism}. This model describes the variances and
+dynamics of people's tendency to anthropomorphize an artificial agent, such as a
+robot. Section \ref{sec:cognition-neuroscience} then investigates the cognitive
+and neuro-biological mechanisms of anthropomorphism to consolidate our
+considerations and the proposed model.  Section \ref{sec:measuring} looks at how
+these models can be operationalized, and in particular, what are the tools at
+hand to measure anthropomorphism. Finally, section \ref{sec:conclusion}
+concludes this article and offers starting points for further research on
+anthropomorphism and the effect of the human-like design approach in robotics.
 
@@
 partly conflicting definitions of the term anthropomorphism, and it still
-appears controversial that humans tend to \textit{``see human
-in the non- human''} \citep{epley_seeing_2007}.
-
-As anthropomorphism arises in an interaction between a human and a non-human
-agent~\citep{persson_anthropomorphism_2000}, one can also take two main
-\textit{perspectives} when trying to explain why humans anthropomorphize~\citep{lee_human_2005}: an artifact-centered perspective and a human-centered
-perspective (the grey triangles in Figure \ref{fig:anthropofig}).
-
-In the following we will only briefly present the artifact-centered perspective
-to explain anthropomorphism. A review of anthropomorphic design of robots can
-also be found in~\cite{fink_anthropomorphism_2012}. Then, we provide a more
-detailed review and synthesis of literature that applies a human-centered
-perspective to explain anthropomorphism. We aim here at providing an exhaustive
-picture of this phenomenon, by summarizing theories from developmental
+appears controversial that humans tend to \textit{``see human in the non-
+human''} \citep{epley_seeing_2007}. As anthropomorphism arises in an interaction
+between a human and a non-human agent~\citep{persson_anthropomorphism_2000}, one
+can also take two main \textit{perspectives} when trying to explain why humans
+anthropomorphize~\citep{lee_human_2005}: an artifact-centered perspective and a
+human-centered perspective.
+
+After discussing and clarifying the different meanings of anthropomorphism, we
+present the main aspects of an \emph{artifact-centered} perspective on
+anthropomorphism. We then provide a synthesis of literature that study
+ anthropomorphism from the perspective of the human: we aim here at providing a broad
+picture of this phenomenon by summarizing theories from developmental
 psychology, cognitive science, neuroscience, and social psychology.
 
+We then briefly discuss the impact of the interaction context on
+anthropomorphism, before restating anthropomorphism as a \emph{multi-factor
+phenomenon}.
+
 \subsection{Overview of the diverse understandings of anthropomorphism}
+\label{meaning}
 
 Naturally, conflicts in how terms are used lead to a diversity of understandings
-of the phenomenon which is described.  One reason for this might be that
-anthropomorphism is a phenomenon that is studied in very different domains that
-might each integrate their own understanding, use the same term to refer to
-different things.  Despite the fact that there is no commonly accepted
-definition, the terms \textit{anthropomorphism}, \textit{anthropomorphic} or
-\textit{human-like} are often used as if their meanings were clear and agreed
-upon \citep{persson_anthropomorphism_2000}. It is even argued that these terms
-might be misused \citep{duffy_anthropomorphism_2002,epley_when_2008}.  For
-instance, some researchers refer to \textit{``the robot's level of
-anthropomorphism''} \citep{bartneck_is_2007,feil-seifer_human-robot_2008},
-whereas others disagree to such a statement because they understand that a
-system or artifact itself does not \textit{``contain anthropomorphism''} but
-only gives rise to the process of anthropomorphizing in a given user and
-situation. Consequently, \cite{persson_anthropomorphism_2000} conclude that
-anthropomorphism emerges in the \textit{interaction} between the technology and
-the user, and has to be understood as such. We come back on this point in the
-next section.
+of the phenomenon which is described: anthropomorphism is a phenomenon that is
+studied in very different domains that each integrate their own understanding,
+use the same term to refer to different things.  Despite the fact that there is
+no commonly accepted definition, the terms \textit{anthropomorphism},
+\textit{anthropomorphic} or \textit{human-like} are often used as if their
+meanings were clear and agreed upon \citep{persson_anthropomorphism_2000}. It is
+however argued that these terms might be misused
+\citep{duffy_anthropomorphism_2002,epley_when_2008}.  For instance, some
+researchers refer to \textit{``the robot's level of anthropomorphism''}
+\citep{bartneck_is_2007,feil-seifer_human-robot_2008}, whereas others disagree
+to such a statement because they understand that a system or artifact itself
+does not \textit{``contain anthropomorphism''} (anthropomorphism is not
+intrinsic to the robot) but only gives rise to the process of anthropomorphizing
+in a given user and situation. Consequently,
+\cite{persson_anthropomorphism_2000} conclude that anthropomorphism emerges in
+the \textit{interaction} between the technology and the user, and has to be
+understood as such. We come back on this point in the next section.
 
@@
 \citep{duffy_anthropomorphism_2002,epley_when_2008}. Besides, it is not clear
-how to operationalize and measure anthropomorphism (we discuss this question
-toward the end of this article, in Section \ref{sec:measuring}).
+how to operationalize and measure anthropomorphism (we discuss this specific question
+in section \ref{sec:measuring}).
 
@@
 
-\begin{figure}
-    \centering
-    \includegraphics[width=0.75\columnwidth]{anthropo.pdf}
-    \caption{Anthropomorphism is a psychological phenomenon which arises in a
-        social context, during an interaction between a human agent and a
-        non-human agent. One can take two main perspectives when trying to
-        explain anthropomorphism: a human-centered and an artifact-centered
-        perspective (grey triangles). Several external factors influence the
-        anthropomorphism phenomenon. Person- and artifact-related characteristics,
-        but also related to the context of use as well as the actual time spent
-        interacting with the robot (interaction history).}
-
-    \label{fig:anthropofig}
-\end{figure}
-
-%
-%\begin{figure}
-%    \centering
-%    \includegraphics[width=0.75\columnwidth]{in_our_heads.pdf}
-%    \caption{[ALTERNATIVE TO FIGURE \ref{fig:anthropofig}] Anthropomorphism is a
-%        subjective, psychological phenomenon which arises in a social context, during an
-%        interaction between a human agent and a non-human agent. One can take
-%        two main perspectives when trying to explain anthropomorphism: a
-%        human-centered and an artifact-centered perspective.
-%        Several external factors influence the anthropomorphism phenomenon.
-%        Person- and artifact-related characteristics, but also related to the
-%        context of use as well as the actual time spent interacting with the
-%        robot (interaction history).}
-%
-%
-%    \label{fig:anthropofig-alt}
-%\end{figure}
-%
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-The artifact-centered perspective explains anthropomorphism from the
+The \emph{artifact-centered} perspective explains anthropomorphism from the
 ascertainable parts of the non-human agent, namely the anthropomorphic form of
@@
 back to it later, in section \ref{sec:cognitive-expl}.
+
+\paragraph{The Physical shape} of a robot refers to `how the robot looks like'
+and includes its general form, and other visible features, such as its size, the
+materials used, its color, and specific details. Generally, robots can be
+divided into human-like (anthropomorphic) and mechanical (non-anthropomorphic)
+robots. However, it makes sense to be slightly more specific about the form, and
+\cite{fong_survey_2003} suggest four categories: anthropomorphic, zoomorphic,
+caricatured, functional. The borders and transitions between these categories
+are not very well defined.  Of particular importance seems to be the presence or
+absence of specific human body parts, such as arms and hands, legs, a torso or a
+head and face. Of those, the faces of robots have received remarkable attention
+concerning how they are perceived and accepted. \cite{disalvo_all_2002} studied
+what features and dimensions of a humanoid robot's face most dramatically
+contribute to people's perception of its humanness. The authors analyzed 48
+humanoid robot heads and found that the presence of certain features, the
+dimensions of the head, and the total number of facial features heavily
+influence the perception of humanness in robot heads.
+
+\paragraph{Expression, communication, and behavior} refers to how the robot
+expresses its human qualities through interacting and behaving. In fact, many
+humanoid robots express their human-likeness not in physical shape but only
+through the \textit{suggestion} of features~\citep{disalvo_all_2002}. Besides
+this, communication and interaction modalities of a robot are likely to play a
+role to what extent the robot will be anthropomorphized. Can the user interact
+with the robot through a touch interface, or using speech? Does the robot
+respond using linguistic utterances or non-linguistic sounds? Is the voice
+human-like or synthetic, on-board or coming from an external second device? A
+study by~\cite{takayama_im_2009} found that this has an effect on people's
+perception of trust in the robot and how convincing the robot appears to them.
+Besides this, we expect that a robot's behavioral aspects concerning
+human-social interaction have an impact. Does the robot use polite formulations,
+etiquette, appropriate facial expressions? Are its responses and reactions
+timely? Usually, robots that directly interact with humans are slow, which
+appears not very human-like to most participants.
+
+\paragraph{The functionality, and purpose} are a robot-related characteristic
+that also partly determines the context of use. This aspect includes what kind
+of expectations the user may have of the robot, and how the user imagines using
+the robot. Is there only one user or a group of people interacting with the
+robot at the same time? Is the purpose of the robot a playful or a serious one?
+Does the robot have a purpose at all~\citep{kaplan_free_2000}? We further
+discuss this aspect in the section related to the context of use.
 
@@
 %
+% Context
+%
+%
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Role of the Context}
+
+\textit{Context of use} is defined by the ISO as \textit{``users, tasks,
+equipment (hardware, software and materials), and the physical and social
+environments in which a product is used''}. Accordingly, there are various
+aspects that can impact how a robot is experienced. The real or imagined
+\textit{purpose} of a robot, including the application context in which it is
+typically used (\eg office environment, home, rehabilitation center, public
+space, \etc) as well as the task context (\eg serious or playful task;
+composition of human-robot team; number of users) and the (social) role in which
+the robot is used / experienced are taken into account. Generally, when the
+context of use of a robot is social, entertaining or playful, it will enhance
+anthropomorphism, compared to when the context is a routine or focused serious
+task (security, rescue, \etc). \cite{joosse_what_2013} showed, for instance,
+that when the same robot ({\sc nao}) was used in a different task context (cleaning
+task \vs tour guide), users ascribed different personalities to the robot. \cite{goetz_cooperation_2002}
+revealed a link between a robot's context of use and people's perception of the
+robot. The authors found that people prefer a serious robot for serious tasks
+and a less serious robot for more playful tasks
+. \cite{kaplan_free_2000}
+discussed the role of uselessness in the design of robots. The author argues
+that artificial pets like AIBO have no real purpose, in a sense that they do not
+provide any kind of service or, in other words, \textit{``they are not doing
+what you tell them to do''} and \textit{``they might refuse the order of its
+owner''}. It may be this very aspect that increases people's tendency to
+anthropomorphize the robot. According to Kaplan, it is in our daily use language
+that we tend to attribute intentions to devices that are not doing their job
+well.
+
+The characteristics of the context can also impact on the user experience and in
+turn foster or hinder anthropomorphism indirectly. For instance, when there are
+several friends of the main user interacting simultaneously with the robot, the
+likelihood of anthropomorphism may be increased. The context here is already
+social when several people who know each other engage in social interaction
+among themselves, so the robot may be perceived as being somewhat part of the
+social interaction, and hence it may be attributed human-social qualities
+\citep{baxter2013do}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+%
+%
 %		ANTHROPOMORPHISM AS A MULTI-FACTOR PHENOMENON
@@
 \label{sec:multi-factors}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.75\columnwidth]{anthropo.pdf}
+    \caption{Anthropomorphism is a multi-factor phenomenon. How far people tend
+    to anthropomorphize a robot is determined by four main factors: the design
+    of the robot $(R)$, the personal characteristics of the human user $(H)$, the
+    situation and context in which the interaction occurs $(C)$, and the amount of
+    time (repeated interaction) that the user spends to familiarize herself with the
+    robot $(t)$.}
+
+    \label{fig:anthropofig}
+\end{figure}
 
@@
 specific history. We think that the context and the history of the interaction
-(in Figure \ref{fig:factors} denoted as \textit{time}), are two more factors
+(in Figure \ref{fig:anthropofig} denoted as \textit{time}), are two more factors
 that determine anthropomorphism.
-
-\begin{figure}
-    \centering
-    \includegraphics[width=0.7\columnwidth]{factors}
-    \caption{Anthropomorphism is a multi-factor phenomenon. How far people tend
-    to anthropomorphize a robot is determined by four main factors: the design
-    of the robot $(R)$, the personal characteristics of the human user $(H)$, the
-    situation and context in which the interaction occurs $(C)$, and the amount of
-    time (repeated interaction) that the user spends to familiarize herself with the
-    robot $(t)$.}
-
-    \label{fig:factors}
-\end{figure}
 
@@
 phenomenon which is determined by multiple factors (see also Figure
-\ref{fig:factors}):
+\ref{fig:anthropofig}):
 
@@
 sections to refer to the normalized level of anthropomorphic effects. Note also
-that we discuss in Section~\ref{sec:measuring} possible methodologies for the
+that we discuss in section~\ref{sec:measuring} possible methodologies for the
 quantitative and qualitative assessment of anthropomorphic effects.
@@
 at time point $0$). This value considers the multiple factors presented in
-Section~\ref{sec:multiple-factors}, thus it is composed by factors of the human
+section~\ref{sec:multiple-factors}, thus it is composed by factors of the human
 $H$, the robot $R$, and the context of use $C$. As such, \ICA describes the
@@
 intelligible to the user, the behavior counts as \emph{disruptive}. We further
-discuss the role of disruptive behaviors in cognitive terms in Section
+discuss the role of disruptive behaviors in cognitive terms in section
 \ref{sec:disruptive}.
@@
 corresponding to the $ICA$) is built on multiple factors (see
-Section~\ref{sec:multiple-factors}) and similar \SLA is based on these
+section~\ref{sec:multiple-factors}) and similar \SLA is based on these
 factors, however taking into account the \textit{interaction history} $t$ that
@@
 \textit{reflective} perspective (see paragraph ``artifact-centered perspective''
-in Section \ref{sec:anthropomorphism}).  For instance, we reflectively might
+in section \ref{sec:anthropomorphism}).  For instance, we reflectively might
 \textit{not} perceive agency in a social robot, but it can feel quite
@@
 anthropomorphic projections in the child-robot interaction study, called the
-Domino study (see Section \ref{sec:field-results}, and Figure \ref{fig:ranger}).
+Domino study (see section \ref{sec:field-results}, and Figure \ref{fig:ranger}).
 

### 2014-11-24 paper.tex
In depth pass on the second part (section 3 and 4)

@@
 
+\newcommand{\AntE}[1][]{%
+      \ifthenelse{\isempty{#1}}%
+      {$\mathcal{A}^{e}$}
+      {$\mathcal{A}^{e}(#1)$}
+}
+
 \newcommand{\AntNorm}[1][]{%
@@
 
-\newcommand{\antNorm}[1][]{%
+\newcommand{\antE}[1][]{%
       \ifthenelse{\isempty{#1}}%
-      {\widehat{\mathcal{A}}}
-      {\widehat{\mathcal{A}}(#1)}
+      {\mathcal{A}^{e}}
+      {\mathcal{A}^{e}(#1)}
 }
 
+\newcommand{\antENorm}[1][]{%
+      \ifthenelse{\isempty{#1}}%
+      {\widehat{\mathcal{A}^{e}}}
+      {\widehat{\mathcal{A}^{e}}(#1)}
+}
+
 \newcommand{\ICA}{{$\mathcal{A}_0$~}}
+\newcommand{\ICAe}{{$\mathcal{A}^{e}_0$~}}
 \newcommand{\SLA}{{$\mathcal{A}_\infty$~}}
+\newcommand{\SLAe}{{$\mathcal{A}^{e}_\infty$~}}
 \newcommand{\sla}{{\mathcal{A}_\infty}}
 \newcommand{\AntMax}{{$\mathcal{A}_{max}$~}}
-\newcommand{\antMax}{{\mathcal{A}_{max}}}
+\newcommand{\AntEMax}{{$\mathcal{A}^{e}_{max}$~}}
+\newcommand{\antEMax}{{\mathcal{A}^{e}_{max}}}
 
@@
 
-So far, the HRI community has not much investigated how anthropomorphism in
-human-robot interactions evolves over time (during the process of
-\emph{adopting} a robot, for instance). Though conflicts were found in the
-understanding of what anthropomorphism is, the HRI community more or less
-accepted viewing anthropomorphism as a static feature that once observed during
-a short-term interaction reflects a sustaining social effect. However, if we
-agree that anthropomorphism arises in an interaction, and thus reflects a
-specific relation, we cannot accept it as a static phenomenon.
-
-Similarly, \citet{kanda_interactive_2004} point out that relationships among
-people evolve over time and, in a similar manner, one can expect people's
-attitude toward technological artifacts and their relationship with them to
-evolve as well.  In their study, \citet{kanda_interactive_2004} were among the
-first to describe empirically \emph{novelty effects} during a long-term study
-with an interactive robot in a school.
-
-From a theoretical perspective, we also expect anthropomorphism to change over
-time, with growing experience with a robot. As discussed in the previous
-sections, anthropomorphism means in essence \emph{reasoning about and perceiving
-    something non-human (and unknown or unfamiliar) based on one's
-representation of the familiar and well-known concept of being human (or
-one-self)}. According to \citet{epley_when_2008}, the basic operations that
-underlie these inductive inferences are the \emph{acquisition of knowledge}, the
-\emph{activation or elicitation of knowledge}, and the \emph{application of
-activated knowledge at the time of the judgment}. By applying knowledge to a
-given situation or interaction, one also attempts to correct, adjust, or maybe
-integrate less accessible information into a more automatically activated
-default representation.  This process of refining the applied knowledge are
-natural because a person's knowledge base changes constantly with newly acquired
-things. For instance, a person can acquire new knowledge about a robot when
-interacting with it. With continued interaction with the unknown system also the
-user's expertise with the system grows, and it can be expected that in turn, the
-user will become able to better predict the previously unknown system.
-Consequently, as the robot becomes more predictable, there is less uncertainty,
-and the ``need to anthropomorphize'' the robot decreases (from the
-human-centered point of view).
-
-In other words, humans have a motivation to interact effectively in their
-environment \textit{(effectance)} \citep{epley_when_2008}.  This means that
-humans are motivated to be able to understand and predict the environment and
-the agents around them. Thus, a person will seek to become familiar with what is
-unfamiliar. Anthropomorphism is encouraged when an agent is unfamiliar.
-Consequently, in the process of familiarizing oneself with an agent, the
-tendency to anthropomorphize this agent should decrease.
-
-We can not be sure about how exactly the process of familiarization to an
-unfamiliar agent (based on continued interaction with the robot) looks like. In
-turn, we can not make a precise statement about how continued interaction
-decreases anthropomorphism but we suspect there is a link between the two.
+So far, the HRI community has not investigated how anthropomorphism in
+interactions with robots evolve over time. There are several reasons for why it
+makes sense to consider temporal dynamics in anthropomorphism.
+
+One reason for why changes in anthropomorphism over time are likely, comes from
+the cognitive perspective, as outlined in the previous section. We are
+spontaneous but also reflect on our interactions with the robot.  From the
+artifact-centered perspective on anthropomorphism (thus, looking at the
+characteristics of the robot) it is assumed that humans directly (more or less
+mindlessly) respond to life-like and social cues that a non-human agent (here:
+robot) emits~\citep{reeves_media_1996,nass_machines_2000}. Without huge
+thoughtful mental processing, humans tend to apply stereotypes and heuristics to
+the robot, and in turn apply human-human social schemas and norms to the
+occurring interactions. However, this may only be some \textit{immediate}
+(sometimes visceral) experience, reflecting the first impression that the user
+has of the robot, based on its appearance~\citep{norman_emotional_2003}.
+\cite{takayama_perspectives_2012} refers to this as the \textit{in-the-moment}
+perspective we have on the robot, compared to a more distanced cogitation and
+consideration, which the author calls \textit{reflective}.  Further, we also
+become familiar with the robot as we continue interacting and dealing with it,
+we gain knowledge about it, and refine our mental model of the robot.
+
+Another reason for considering temporal dynamics are the changes in user
+experience~\citep{karapanos_user_2009} and relationship to the robot.
+\cite{kanda_interactive_2004} pointed out that not only the relationships among
+people evolve over time but that, in a similar manner, one can expect that also
+people's relationship and their attitude toward robots evolve. The authors were
+among the first ones to describe empirically \textit{novelty effects} during a
+long-term study with an interactive robot in a school.
 
@@
 illustrate how the user tendency to anthropomorphize decreased over time.
-Combined with the extensive discussion on the nature and factors of
+Combined with the discussion on the nature and factors of
 anthropomorphism that we proposed in section~\ref{sec:anthropomorphism}, we
@@
 (Figure~\ref{fig:dynamics},~\citep{lemaignan2014dynamics}) represents how the
-level of ``anthropomorphic effects''~\Ant[R,H,C,t] (\ie the observable
-manifestations of anthropomorphism) evolves over a long-term human-robot
-interaction.\footnote{We cannot make a precise statement about how long
-``long-term'' interaction has to be to be considered as such. It seems to be
-practical to not speak of ``several days'' or ``weeks'' but to rather consider
-the duration and frequency of the actual interactions with the artifact. One
-could probably call this the ``interaction history''.}
+level of anthropomorphic \emph{effects}~\AntE[R,H,C,t] (\ie the observable
+manifestations of the anthropomorphism \Ant) evolves over a long-term human-robot
+interaction.
 
@@
 (non-mediated), repeated interaction with the same robot, over an extended
-period of time (typically longer than a week), we also formally introduce a
+period of time (typically longer than a week) --, we also formally introduce a
 so-called \emph{novelty effect}~\citep{kanda_interactive_2004} that models the
@@
 
-In the \emph{Dynamics of Anthropomorphism} model, anthropomorphism is quantified
-by a \emph{normalized level of anthropomorphic effects} $\antNorm[R,H,C,t] =
-\frac{\ant[R,H,C,t]}{\antMax}$: because anthropomorphic effects are often
+In this model, anthropomorphism is quantified
+by a \emph{normalized level of anthropomorphic effects} $\antENorm[R,H,C,t] =
+\frac{\antE[R,H,C,t]}{\antEMax}$: because anthropomorphic effects are often
 qualitative and difficult to quantify on an absolute scale, we present them as a
 normalized value, that spans from a minimum (no anthropomorphic effects:
-$\ant=0$) to a maximum (noted \AntMax, with $t_{max} = \operatorname{arg\,max}_t
-\, \ant[t]$). For the sake of readability, we will use \Ant in the following
+$\antE=0$) to a maximum (noted \AntEMax, with $t_{max} = \operatorname{arg\,max}_t
+\, \antE[t]$). For the sake of readability, we will use \Ant in the following
 sections to refer to the normalized level of anthropomorphic effects. Note also
@@
 combination of a human, a robot, a situation and several other factors we
-introduce below. Thus, the maximum value varies according to the specific
-characteristics of these factors. Figure~\ref{fig:dynamics} pictures this
-maximum value at $t_{max}$, which actually corresponds to what we call the
-novelty effect peak.\footnote{We assume that there is a peak in the human's
-experiences of the novelty effects of the unfamiliar system. Further, we suspect
-that this novelty peak comes along with the maximum value of anthropomorphic
-effects.} The general \emph{shape} of the curve remains however the same and
-depicts the evolution of anthropomorphism over time, \ie the general dynamics of
-anthropomorphism.
+introduce below. Figure~\ref{fig:dynamics} pictures this
+maximum value at $t_{max}$, which we hypothesize to correspond to the
+novelty effect ``peak''.
 
@@
 
-\draw (-0.05, 3) -- (0.05, 3) node[anchor=east] {\ICA};
-\draw (-0.05, 5) -- (0.05, 5) node[anchor=east] {\AntMax};
+\draw (-0.05, 2.1) -- (0.05, 2.1) node[anchor=east] {\ICAe};
+\draw (-0.05, 5) -- (0.05, 5) node[anchor=east] {\AntEMax};
 
@@
 \draw[->] (9.8,0) -- (9.8,4) node[anchor=east] {};
-\draw (9.8, 0.8) node[anchor=west] {\SLA};
+\draw (9.8, 0.8) node[anchor=west] {\SLAe};
 
@@
 
-\caption{\textbf{Conceptual model of the dynamics of anthropomorphism}. We
+\caption{\textbf{Qualitative model of the dynamics of anthropomorphism}. We
     distinguish three main phases: \emph{initialization}, \emph{familiarization}
@@
 
-\subsubsection{Initialization Phase\\}
-
-The \textit{Initialization Phase} starts with the so-called \textit{Initial
-Capital of Anthropomorphism} ($ICA$), which corresponds to \ICA (value of \Ant
-at time point $0$). This value considers the multiple factors presented in
-section~\ref{sec:multiple-factors}, thus it is composed by factors of the human
-$H$, the robot $R$, and the context of use $C$. As such, \ICA describes the
-value of anthropomorphic effects that can be expected to occur during the first
-contact between the human and the robot in a given situation. During this first
+\subsubsection{Pre-Interaction and Initialization Phase\\}
+
+The \emph{initial capital of anthropomorphism} \ICA describes the initial potential
+for the human user to anthropomorphize the robot in a given situation.
+This potential depends on several factors, introduced in
+section~\ref{sec:multi-factors}.
+It represents the level of anthropomorphic effects that can be expected to occur
+during the very first contacts between the human and the robot. During this first
 phase, pre-conceptions and initial expectations as well as previous experience
-of the user with other similar types of robots and similar contexts can have a
-strong impact and influence the general tendency to anthropomorphize.
-
-During the \textit{Initialization Phase} we expect an increasing value of $A$
-that may be partly due to the so-called \textit{effects of novelty} of the
+of the user with other similar types of robots and similar contexts are the
+primary source of influence.
+
+During the initialization phase, we expect an increasing value of \Ant
+that is due to the so-called \textit{effects of novelty} of the
 robot. Such effects have been described with interactive technologies in general
@@
 
-What type of anthropomorphic effects are typical during the
-\textit{Initialization Phase}? In our own work, we observed that users
-spontaneously tend to talk directly to the robot (though the user knows that the
-system is not be able to recognize speech), for instance, by greeting the robot,
-asking questions to it, giving it nick-names or ascribing a gender, praising the
-robot, commenting on its performance in general, and giving commands. Also, the
-use of point gestures and waving at the robot were fairly common among
-participants of our studies, as well as ascribing gender and some personal
-preferences or intention to the robot. (Note that we did not even use an
-anthropomorphic robot but a Roomba vacuum cleaning robot.)
-
-In general, it appears that anthropomorphism during the \textit{Initialization
-Phase} is a commonly observed phenomenon. But we would like to stress again that
-most of these effects are likely to fade out over time.
+The type of anthropomorphic effects typically observed during the initialization
+hpase include users who spontaneously tend to talk directly to the robot while
+they are aware that the system is not be able to recognize speech: greeting the
+robot, asking questions to it, giving it a nickname, praising the robot,
+commenting on its performances and giving commands. Also, the use of pointing
+gestures and waving at the robot are often found, as well as ascribing gender
+and some personal preferences or intention to the robot.
 
@@
 
-In the \textit{Familiarization Phase} the user gets acquainted and familiar with
-the robot and with using the robot, and hence the tendency to anthropomorpize
-decreases. This phase typically starts as the local maximum value of
-anthropomorphic effects that are enhanced by the novelty of the robot start to
-wear off. The user may think that he/she faces an agent that aims at
-``human-level intelligence'' (to take McCarthy's words). This is a transient
-state that quickly vanishes as the user recognized that the behavior of the
-robot is generally \textit{predictable} and possibly \textit{deceptive}. For
-instance, the robot produces verbal utterances (it ``talks'') but it does not
-understand when we talk; or the robot is endowed with eyes but does not
-recognize the objects we show it.
+In this context, \emph{familiarization} means \emph{to get acquainted with}.
+It is not to be confused with the \emph{familiarity thesis} that relates to the
+projection of already known cognitive models onto the robot. We discuss this other
+aspect in section~\ref{sec:cognition-neuroscience}.
+
+The \emph{familiarization phase} starts at the peak of the \emph{novelty
+effect}: anthropomorphic effects are at their maximum, the user thinks (s)he is
+potentially facing an agent aiming at ``human-level intelligence'' (to take
+McCarthy's words). This is a transient state that quickly vanishes, and the
+projected anthropomorphism then starts to decrease while the human observes and
+recognizes that the behavior of the robot is generally \emph{predictable} and
+possibly \emph{deceptive} (for instance, it talks but does not understand when
+we talk; it has eyes but does not recognize everyday objects we show; \etc).
 
@@
 
-We call \emph{disruptive behaviors} any behavior exhibited by the robot hat
+We call \emph{disruptive behaviors} any behavior exhibited by the robot that
 appears unexpected to the user: for instance, a robot may usually follow always
@@
 
-During the \textit{Stabilization Phase} the value of $A$ tends to stabilize over
+During the \textit{Stabilization Phase} the value of \Ant tends to stabilize over
 a longer time, to reach a value that we call the \textit{Stabilized Level of
-Anthropomorphism} ($SLA$), which corresponds to \SLA. The value that the
+Anthropomorphism} ($SLA$), noted \SLA. The value that the
 $SLA$ approaches is unique for each user interacting with a specific robot in a
 given situation. \SLA may approach $0$, when no anthropomorphic effects
-are observed anymore, for instance, when the user is interacting with the robot
+are observed anymore, for instance when the user is interacting with the robot
 in a routine way and he/she does not project any human-like traits unto the
-robot\footnote{The robot may have become \textit{``invisible in use''}
-\citep{takayama_toward_2011}.} As such, the $SLA$ stands for the long-term
-lasting value of anthropomorphism.  We proposed that \SLA (the value
-corresponding to the $ICA$) is built on multiple factors (see
-section~\ref{sec:multiple-factors}) and similar \SLA is based on these
-factors, however taking into account the \textit{interaction history} $t$ that
-the user has with the robot.  Note that the $ICA$ and the $SLA$ are generally
-not correlated. A person may initially have a high potential of
-anthropomorphizing (high \ICA), for instance a highly anthropomorphic robot,
-but subsequently get disappointed by the actual capabilities of it and stop
-explaining it in terms of human-like characteristics (low \SLA). Another
-user may however create lasting affective bonds with the same robot and may
-continue to anthropomorphize the robot (high \SLA).
+robot, what \cite{takayama_toward_2011} calls the robot being
+\textit{``invisible in use''}. \SLA may as well remains above 0 if the user
+continues to exhibit anthropomorphic behaviors when interacting with the robot
+on the long run.
+
+The level \SLA, like \ICA, is the result of a combination of multiple human,
+robotic and contextual factors, with the additional impact of the
+\emph{interaction history t} that the user experienced with the robot. Note that
+the $ICA$ and $SLA$ levels are generally not correlated: a person may initially
+have a high potential of anthropomorphizing (high \ICA), for instance a highly
+anthropomorphic robot, but subsequently get disappointed by the actual
+capabilities of it and stop explaining it in terms of human-like characteristics
+(low \SLA). Another user may however create lasting affective bonds with the
+same robot and may continue to anthropomorphize the robot (higher \SLA).
 
@@
 
-\path[fill=gray!20] (0,0) rectangle (10.5,2);
-\path[fill=gray!50] (0,2) rectangle (10.5,4);
-\path[fill=gray!20] (0,4) rectangle (10.5,6);
-
-\draw (-0.3,1) node[rotate=90] {Stage 1}
-      (-0.3,3) node[rotate=90] {Stage 2}
-      (-0.3,5) node[rotate=90] {Stage 3};
+%\path[fill=gray!20] (0,0) rectangle (10.5,2);
+%\path[fill=gray!50] (0,2) rectangle (10.5,4);
+%\path[fill=gray!20] (0,4) rectangle (10.5,6);
+
+\draw (-0.3,2) node[anchor=east] {Stage 1}
+      (-0.3,4) node[anchor=east] {Stage 2}
+      (-0.3,6) node[anchor=east] {Stage 3};
+
+\draw[thin,black!50,dotted] (-0.10,2) -- (1,2);
+\draw[thin,black!50,dotted] (-0.10,4) -- (4,4);
+\draw[thin,black!50,dotted] (-0.10,6) -- (7,6);
 
@@
 
-\draw (11,1) node[align=left, anchor=west]{\scriptsize pre-cognitive\\\scriptsize anthropomorphism}; %label
-
-\draw (11,3) node[align=left, anchor=west] {\scriptsize{projection of existing}\\\scriptsize{mental models}\\\scriptsize{\it (familiarity)}}; %label
-
-\draw (11,5) node[align=left, anchor=west] {\scriptsize{adapted mental
+\draw (11,2) node[align=left, anchor=west]{\scriptsize pre-cognitive\\\scriptsize anthropomorphism}; %label
+
+\draw (11,4) node[align=left, anchor=west] {\scriptsize{projection of existing}\\\scriptsize{mental models}\\\scriptsize{\it (familiarity)}}; %label
+
+\draw (11,6) node[align=left, anchor=west] {\scriptsize{adapted mental
 model} \\ $\to$ \scriptsize{adapted interaction}\\\scriptsize{\it (anthropomorphic or not)}}; %label
@@
 based on experience. This leads to adapted interaction modalities, that may
-still be anthropomorphic, or not.}
+still be anthropomorphic, or not. Note that the different stages coexist: Stage
+1 and 2 still affect the human perception of the robot in a Stage 3 interaction.}
 \label{fig:cognitivemodel}
@@
 \emph{Familiarization} and \emph{Stabilization} phases introduced in our model
-of the dynamics of anthropomorphism.
+of the dynamics of anthropomorphism. We discuss this relation hereafter.
 
@@
 people consciously perceive and how they respond to stimuli that they may not
-consciously perceive. That means, in the initial phase of interacting with a
+consciously perceive. This means that in the initial phase of interacting with a
 novel device \textit{(initialization)} (see Figure \ref{fig:dynamics}) people
 might not respond consciously but rather mindlessly \citep{nass_machines_2000},
-and in turn anthropomorphize more.  Only after some time of
-\textit{familiarization}, they might respond in a more reflective manner (in
-turn, the tendency to anthropomorphize might decrease). This can be illustrated
-by the fact that people tend to deny interacting with computational systems as
-if they were people and yet they respond to computers in many ways that are
-remarkably similar to how they respond to people \citep{reeves_media_1996}.
+and in turn anthropomorphize more. They start to respond in a more reflective
+manner only during the \textit{familiarization} (in turn, the tendency to
+anthropomorphize might decrease). This can be illustrated by the fact that
+people tend to deny interacting with computational systems as if they were
+people and yet they respond to computers in many ways that are remarkably
+similar to how they respond to people \citep{reeves_media_1996}.
 \cite{takayama_perspectives_2012} also applies a cognitive viewpoint on the two
@@
 both the observed and imagined capabilities of the robot.  The \emph{familiarity
-thesis}~\cite{hegel_understanding_2008} supports the idea that the human first
+thesis}~\citep{hegel_understanding_2008} supports the idea that the human first
 projects onto the robot mental models of similar agents he/she is already
@@
 the human engages in this projection, might be driven by the same parameters as
-we mentioned for the \emph{initial capital of anthropomorphism}
-(section~\ref{sec:ica}).  At this stage the human might also change his attitude
-towards the robot, paying more attention to social cue than to low-level
-behavior which may reinforce the resonance mechanisms.
+we mentioned for the \emph{initial capital of anthropomorphism}. We also believe
+that, at this stage, the human also changes his attitude towards the robot, by
+focusing his attention to social cue more than to low-level behaviors, which
+may in turn reinforce the resonance mechanisms.
 
@@
 working, as well as his/her own tendency to anthropomorphize (the
-\emph{personality} in ICA factor), but at this stage, the \emph{perception} of
-the robot (its shape for instance) and its intended \emph{purpose} play a less
-important role. It is mostly a human-centric process.  The result of this third
-phase would be an iteratively adapted cognitive model of the robot. It is also
-at this last stage that the human might have a modified tendency to
-anthropomorphize, because he/she has built a full cognitive model of the robot.
-Consequently, the human would now be able to attribute appropriate internal
-states to the robot through his/her theory of mind.
-
-\paragraph{Relation to the dynamics of anthropomorphism\\}
-
-As mentioned before, the three cognitive stages proposed here do not match with
-the three phases in the \emph{Dynamics of Anthropomorphism}.  In particular, the
-cognitive Stages 1 and 2 are both included in the \emph{initialization} phase of
-the anthropomorphism model. Sub-cognitive anthropomorphism typically
-\emph{initiates} the novelty effect by rapidly engaging the human in the
-interaction through an initial projected agency, whereas cognitive Stage 2
-(projection of familiar mental models) supports the novelty effect by inducing
-beliefs that the robot is set up with possibly complex cognitive abilities.
-
-The cognitive Stage 3 also overlaps with the \emph{Familiarization} phase: as
-the human gets used to the robot, he/she restates and adapts its
-cognitive model of the robot by iteratively reshaping pre-existent, familiar
-models until it provides a satisfying support to explain and justify the
-observed robot behavior.
-
-A \emph{stable level of anthropomorphism} is reached when the adaptation process
-depicted in the cognitive Stage 3 reached a stable state, \ie the user's
-experience with the robot is correctly supported by the cognitive model he/she
-has built.
+\emph{personality} in ICA factor). At this stage, the \emph{perception} of the
+robot (its shape for instance) and its original intended \emph{purpose} play
+less of an important role. It is mostly a human-centric process.  The result of
+this third phase is an iteratively adapted cognitive model of the robot.
 
@@
 \emph{(3)} the \emph{reflective level}, in which consciousness takes part in the
-process, and past experiences are taken into account.  In a study which was
-carried out in a shopping mall, \cite{weiss_i_2009} explored the emotional
-attachment during first time reactions of children and adults with the robotic
-dog AIBO. The authors also argue that it is important to understand the
-long-term development of people's social bonds to robots.
+process, and past experiences are taken into account.
+
+\paragraph{Relation to the dynamics of anthropomorphism\\}
+
+\begin{figure}[]
+\centering
+%\resizebox{\linewidth}{!}{
+\begin{tikzpicture}
+\baselineskip=8pt
+
+\draw[dotted, black!50, thin] (1.8, 6) -- (1.8, 0);
+\draw[dotted, black!50, thin] (6.5, 6) -- (6.5, 0);
+
+\draw(0.5,5.5) node[anchor=south west] {\scriptsize \sc Init.};
+\draw(2.5,5.5) node[anchor=south west] {\scriptsize \sc Familiarization};
+\draw(7,5.5) node[anchor=south west] {\scriptsize \sc Stabilization};
+
+\begin{scope}[yscale=-1,shift={(-0.125,-0.46)}]
+    \draw[ultra thick, black!50] svg[scale=1cm] "M 0.125,-1.622832 c 0.093536,-0.9062795
+    0.21996726,-1.9131565 0.9017912,-2.5842389 0.4277536,-0.3944265
+    1.1653486,-0.5108382 1.605386,-0.071103 1.1558512,0.9403904
+    1.9535208,2.2825896 3.2616057,3.0430907 0.871821,0.52801518
+    1.8461798,0.91299355 2.8702084,0.98695145 0.4522402,0.0444213
+    0.9069132,0.0552179 1.3610087,0.0620963";
+
+\end{scope}
+
+\draw (-0.3,1.5) node[anchor=east] {Stage 1}
+      (-0.3,3) node[anchor=east] {Stage 2}
+      (-0.3,4.5) node[anchor=east] {Stage 3};
+
+\draw[thin,black!50,dotted] (-0.10,1.5) -- (1,1.5);
+\draw[thin,black!50,dotted] (-0.10,3) -- (4,3);
+\draw[thin,black!50,dotted] (-0.10,4.5) -- (7,4.5);
+
+\draw[->] (0,0) -- (11,0) node[anchor=north] {$t$};
+\draw[-|] (0,0) -- (0,6.5) node[anchor=east] {};
+% Us
+\draw[ultra thick, ->] (0,0) -- (0.2,1.5) -- (1,1.5) -- (1.2,3) -- (3,3) -- (6,4.5) --
+(9.5,4.5);
+\draw[ultra thick, dashed, ->] (1,1.5) -- (9.5,1.5);
+\draw[ultra thick, dashed, ->] (3,3) -- (9.5,3);
+
+\end{tikzpicture}
+%}
+\caption{\textbf{Towards a cognitive interpretation of the dynamics of
+    anthropomorphism}: This diagram combines the figures~\ref{fig:dynamics}
+    and~\ref{fig:cognitivemodel} to evidence their interplay: we suggest that
+    the cognitive stages 1 and 2 (pre-cognitive anthropomorphism and projection
+    of known existing cognitive models) first play a key role in the early
+    perception of the robot, leading to high levels of anthropomorphic
+    behaviors. Then, the user smoothly transitions from projecting already known
+    models to building a new, specific cognitive model of the robot: this occurs
+    while the user familiarizes with the robot and leads over time to a
+    stabilized level of anthropomorphic behaviors. In the current state of
+    robotic technology, this stabilization mostly reads as a \emph{decrease} of
+    anthropomorphic perception, due to the user being able to explain and
+    accurately predict the robot behavior after enough interaction time, hence
+    perceiving the robot as a simple machine.}
+
+\label{fig:mix}
+\end{figure}
+
+As mentioned before, the three cognitive stages proposed here do not directly
+match with the three phases in the model of the dynamics of anthropomorphism,
+and Figure~\ref{fig:mix} attempts to depict their interplay.
+The cognitive Stages 1 and 2, in particular, are both active in the
+\emph{initialization} phase of the anthropomorphism model. Sub-cognitive
+anthropomorphism typically \emph{initiates} the novelty effect by rapidly
+engaging the human in the interaction through an initial projected agency,
+whereas cognitive Stage 2 (projection of familiar mental models) supports the
+novelty effect by inducing beliefs that the robot is set up with possibly
+complex cognitive abilities.
+
+The cognitive Stage 3 also overlaps with the \emph{Familiarization} phase: as
+the human gets used to the robot, he/she restates and adapts its
+cognitive model of the robot by iteratively reshaping pre-existent, familiar
+models until it provides a satisfying support to explain and justify the
+observed robot behavior.
+
+A \emph{stable level of anthropomorphism} is reached when the adaptation process
+depicted in the cognitive Stage 3 reached a stable state, \ie the user's
+experience with the robot is correctly supported by the cognitive model he/she
+has built.
 
@@
 or in its action), displayed a greater level of social engagement and made
-greater attributions of mental states.  However, an unexpected (disruptive)
-robot behavior might also have a negative effect on user's engagement with the
-robot. For instance, when the user interprets the robot's behavior as a failure,
-he/she might lose trust in the robot. \cite{desai_impact_2013} found that in an
-interaction scenario, especially early failures of the robot can cause a
-dramatically lower real-time trust, compared to middle or late drops of
-reliability of the robot.
-
-During a normal interaction with the robot, the user iteratively refines his/her
-own model of the behavior of the robot. As explained in previous sections, as
-the user improves his/her model of the robot's actions, he/she also improves the
-ability to predict the actions and thus, the user tends to anthropomorphize
-less.
-
-We emit the hypothesis that an unexpected robot behavior might lead the user to
-suddenly restate his/her behavioral model of the robot and will temporarily lead
-to an increase or decrease of the level of anthropomorphism (depicted by the
-spikes in Figure~\ref{fig:dynamics}).
+greater attributions of mental states, and conversely, unexpected robot
+behavior, when interpreted as a robot failure, has been observed to adversely
+affect cognitive engagement: \cite{desai_impact_2013}, for instance, found that
+in an interaction scenario, early failures of the robot can cause a dramatically
+lower real-time trust.
+
+Accordingly, we suggest that unexpected robot behaviors lead the user to restate
+his/her behavioral model, and hence, his/her cognitive model of the robot, which
+translates into an increase or decrease of the level of anthropomorphism
+(depicted by the spikes in Figure~\ref{fig:dynamics}, p.~\pageref{fig:dynamics}).
+
+When talking about \emph{unexpected robot behaviors}, several distinct cases can
+be considered, summarized in Table~\ref{fig:perceptionUnexpectedBehavior}.
 
@@
 
-When talking about \emph{unexpected robot behaviors}, several distinct cases
-must however be considered, summarized in
-Table~\ref{fig:perceptionUnexpectedBehavior}.
-
 If the unexpected behavior is not planned, and perceived as such by the human
-(case I), the human can interpret that the robot is able to fail. If the robot
-explicitly states its failure (for instance, by saying ``I'm lost!''), the
-behavior is then called \emph{transparent} \citep{kim_who_2006}, and the user
-may hypothesize that the robot has \emph{introspective} capabilities (it can
-reflect on its own internal state), which may lead to higher anthropomorphic
-projections.  On the contrary, if the robot shows no sign of recognizing its own
-failure, the user may ascribe a lower level of anthropomorphism to the robot.
+(case I, Table~\ref{fig:perceptionUnexpectedBehavior}), the human can interpret
+that the robot is able to fail. If the robot explicitly states its failure (for
+instance, by saying ``I'm lost!''), the behavior is then called
+\emph{transparent}~\citep{kim_who_2006}, and suggests that the
+robot has \emph{introspective} capabilities (it can reflect on its own internal
+state), which may lead to higher anthropomorphic projections.  On the contrary,
+if the robot shows no sign of recognizing its own failure, the user may ascribe
+a lower level of anthropomorphism to the robot.
 
@@
 will (wrongfully) attribute intentionality to the robot, while case IIIa is
-expected to lead to a lower anthropomorphism level.  However, in those two
-cases, the next occurrence of an expected behavior, if correctly interpreted
-(case I or II), is likely to lead to stronger effects due to a larger delta 
-between expectations and actual observed behavior.
+expected to lead to a lower anthropomorphism level.
 
@@
 
-Most of the experiments that investigate anthropomorphism in HRI are
-conducted in controlled lab-settings during a short-term scenario. For instance,
-pictures or videos of different robots are shown to human subjects who
-subsequently fill in a questionnaire, to assess how far the different types of
-robots were perceived human-like. We think that such experimental
-settings have limitations for studying a social phenomenon like
-anthropomorphism. The critical question is: can anthropomorphism really be
-measured in a post-interaction closed questionnaire or by rating scales?
-Findings might possibly lead to interpretations that would not be generalizable
-to natural settings or real interaction scenarios (which is always an issue in
-social science research).
+Most of the experiments that investigate anthropomorphism in HRI are conducted
+in controlled lab-settings during a short-term scenario. For instance, pictures
+or videos of different robots are shown to human subjects who subsequently fill
+in a questionnaire, to assess how far the different types of robots were
+perceived human-like. Such experimental settings have limitations for studying a
+social phenomenon like anthropomorphism, and one may wonder if anthropomorphism
+can really be measured in a post-interaction closed questionnaire or by rating
+scales. Findings might possibly lead to interpretations that would not be
+generalizable to natural settings or real interaction scenarios (which is always
+an issue in social science research).
 
@@
 25-item questions to measure various concrete aspects of human-likeness.
-Consequently, anthropomorphism can be modeled along a scale that accounts for
-lower and higher levels of it.
 

### 2014-11-25 paper.tex
New large pass on the sections up to 3.2.1 + merge Julia's conclusion
Section 5 (measuring anthro.) is now within the conclusion

@@
       \ifthenelse{\isempty{#1}}%
-      {$\mathcal{A}^{e}$}
-      {$\mathcal{A}^{e}(#1)$}
-}
-
-\newcommand{\AntNorm}[1][]{%
-      \ifthenelse{\isempty{#1}}%
-      {$\widehat{\mathcal{A}}$}
-      {$\widehat{\mathcal{A}}(#1)$}
+      {$\widetilde{\mathcal{A}}$}
+      {$\widetilde{\mathcal{A}}(#1)$}
 }
@@
       \ifthenelse{\isempty{#1}}%
-      {\mathcal{A}^{e}}
-      {\mathcal{A}^{e}(#1)}
+      {\widetilde{\mathcal{A}}}
+          {\widetilde{\mathcal{A}}(#1)}
 }
@@
       \ifthenelse{\isempty{#1}}%
-      {\widehat{\mathcal{A}^{e}}}
-      {\widehat{\mathcal{A}^{e}}(#1)}
+      {\widehat{\mathcal{A}}}
+      {\widehat{\mathcal{A}}(#1)}
 }
 
-\newcommand{\ICA}{{$\mathcal{A}_0$~}}
-\newcommand{\ICAe}{{$\mathcal{A}^{e}_0$~}}
+\newcommand{\IPA}{{$\mathcal{A}_0$~}}
+\newcommand{\IPAe}{{$\widetilde{\mathcal{A}_0}$~}}
 \newcommand{\SLA}{{$\mathcal{A}_\infty$~}}
-\newcommand{\SLAe}{{$\mathcal{A}^{e}_\infty$~}}
+\newcommand{\SLAe}{{$\widetilde{\mathcal{A}_\infty}$~}}
 \newcommand{\sla}{{\mathcal{A}_\infty}}
 \newcommand{\AntMax}{{$\mathcal{A}_{max}$~}}
-\newcommand{\AntEMax}{{$\mathcal{A}^{e}_{max}$~}}
-\newcommand{\antEMax}{{\mathcal{A}^{e}_{max}}}
+\newcommand{\AntEMax}{{$\widetilde{\mathcal{A}_{max}}$~}}
+\newcommand{\antEMax}{{\widetilde{\mathcal{A}_{max}}}}
 
@@
 \def\Authors{Julia Fink\,$^{1*\dagger}$, S\'{e}verin Lemaignan$^{1\dagger}$, Claire Braboszcz$^{2}$ and Pierre Dillenbourg$^{1}$}
-\def\Address{$^{1}$Computer-Human Interaction in Learning and Instruction (CHILI) \\ Ecole Polytechnique F\'{e}d\'{e}rale de Lausanne (EPFL) \\ CH-1015 Lausanne, Switzerland \\
+\def\Address{$^{1}$Computer-Human Interaction in Learning and Instruction
+    (CHILI) \\ \'{E}cole Polytechnique F\'{e}d\'{e}rale de Lausanne (EPFL) \\ CH-1015 Lausanne, Switzerland \\
 \vspace{0.25cm}
@@
 
-\title[Dynamics of Anthropomorphism]{Dynamics of Anthropomorphism in Human-Robot Interaction}
+\title[Dynamics of Anthropomorphism]{Anthropomorphism in Human-Robot
+Interaction: Nature, Dynamics and Underlying Cognitive Mechanisms}
 \author[\firstAuthorLast ]{\Authors}
@@
 By building upon experimental results from several studies, a comprehensive
-synthesis of literature, as well as insights from social psychology,
-cognitive science, and neuroscience, this article proposes to extend our current
-understanding of anthropomorphism. We propose a \textbf{qualitative model} that defines a
-clear terminology and accounts for the \textbf{non-monotonic dynamics} of
-the phenomenon. We further relate the observed effects of anthropomorphism to
-their \textbf{underlying cognitive precursors}.
-
-We examine several \textbf{factors} that determine anthropomorphism, namely the
-design of the non-human agent, the individual psychological determinants of the
-human user, and the context of use. Moreover, we discuss several episodes of
-interaction that influence the anthropomorphic projections on the robot, like
-the \textbf{novelty effect}, the role of \textbf{familiarization} and the
-impact of \textbf{disruptive behaviors}.
+synthesis of literature, as well as insights from social psychology, cognitive
+science, and neuroscience, this article proposes to extend our current
+understanding of anthropomorphism. We examine the several \textbf{factors} that
+determine anthropomorphism, namely the design of the non-human agent, the
+individual psychological determinants of the human user, and the context of use.
+Moreover, we discuss several episodes of interaction that influence the
+anthropomorphic projections on the robot, like the \textbf{novelty effect}, the
+role of \textbf{familiarization} and the impact of \textbf{unexpected
+behaviors}.
+
+We then propose a \textbf{qualitative model} that defines a clear terminology
+and accounts for the \textbf{non-monotonic dynamics} of the phenomenon. We
+further relate the observed effects of anthropomorphism to their
+\textbf{underlying cognitive precursors}.
 
@@
 A phenomenon that is often studied related to this is \textbf{anthropomorphism}.
-This article aims at fostering a better understanding of
-anthropomorphism (noted \Ant in this paper) in human-robot interaction by
-considering the phenomenon as a whole. Robotics researchers often tend to
-believe that anthropomorphism only describes a static set of human-like features
-of a robot (like shape, speech capabilities, facial expressions, etc.). We refer
-to these characteristics as the \emph{anthropomorphic design} of the
+This article aims at fostering a better understanding of anthropomorphism (noted
+\Ant in this paper) in human-robot interaction by considering the phenomenon as
+a whole. Robotics researchers often tend to consider that anthropomorphism only
+describes a static set of human-like features of a robot (like its shape, its
+speech capabilities, facial expressions, etc.). We refer to these
+characteristics as the \emph{anthropomorphic design} of the
 robot~\citep{fink_anthropomorphism_2012}, and propose that
 \emph{anthropomorphism} in general refers to a \emph{social phenomenon} that
-emerges from the (real or imagined) \emph{interaction} between a non-human agent
-(a robot in our case) and a human~\citep{persson_anthropomorphism_2000}. According
-to~\cite{epley_when_2008}, anthropomorphism includes that the human perceives,
-for instance, emotional states, motivations, or intentions in the non-human
-agent, and tends to ascribe those qualities to it.  As such, the dynamic and
-socio-cognitive dimensions of anthropomorphism are essential to understand the
-complex bonds that human users build with artificial agents such as robots.
+emerges from the (real or imagined) interaction between a non-human agent (a
+robot in our case) and a human~\citep{persson_anthropomorphism_2000}.  According
+to~\cite{epley_when_2008}, anthropomorphism includes the human perception of
+emotional states, motivations, intentions in the non-human agent, and tends to
+ascribe those qualities to it.  As such, the dynamic and socio-cognitive
+dimensions of anthropomorphism are essential to understand the complex bonds
+that human users build with artificial agents such as robots. This article aims
+at advancing our understanding of this phenomenon, both in term of an
+interdisciplinary literature synthesis, and in term of qualitative yet formal
+models that will support further research in this field.
 
@@
 \label{sec:field-results}
-
-To support the reflection on variances and dimensions of anthropomorphism, it is 
-useful to consider a few experimental
-results. We studied anthropomorphism in several short- and long-term
-human-robot interaction studies that we carried out with embodied robots, both
-in ecologically valid real-world environments and controlled lab settings. Those
-experiments are presented in details in previously published
-articles~\citep{fink_anthropomorphic_2012, fink_living_2013, fink2014which,
-lemaignan2014dynamics}. We only highlight here a few qualitative results that
-underline the complexity of the phenomenon.
 
@@
 
+To support the reflection on variances and dimensions of anthropomorphism, it is 
+useful to consider a few experimental
+results. We studied anthropomorphism in several short- and long-term
+human-robot interaction studies that we carried out with embodied robots, both
+in ecologically valid real-world environments and controlled lab settings. Those
+experiments are presented in details in previously published
+articles~\citep{fink_anthropomorphic_2012, fink_living_2013, fink2014which,
+lemaignan2014dynamics}. We only highlight here a few qualitative results that
+underline the complexity of the phenomenon.
+
 Figures~\ref{fig:roomba-activities} and~\ref{fig:roomba-perception} give a first
 perspective on how naive users interact and perceive robots over a long period
-of time. Here, \emph{Roomba} vacuum cleaning robots were given to nine
+of time. \emph{Roomba} vacuum cleaning robots were given to nine
 households for a 6-months period. The aim was to explore how people use and
@@
 shows data from a (yet unpublished) study in which 13 pairs of children (4-5
-years old) played for about 20 minutes a domino game with a robot toy box (the
-robot was tasked to carry domino pieces from one child to the other,
-Figure~\ref{fig:ranger-expe}).  The $x$-axis represents the number of social
+years old) played for about 20 minutes a domino game with a robot toy box. The
+robot was tasked to carry domino pieces from one child to the other
+(Figure~\ref{fig:ranger-expe}).  The $x$-axis represents the number of social
 interactions between the children and the robot (like talking to the robot or
@@
 cluster of high-anthropomorphizers/low-interactors and a another group of
-children who interact more with the robot and anthropomorphize it less: the
-more the children engaged into interaction, the less prone to an anthropomorphic
-perception they were.
+children who interact more with the robot and anthropomorphize it less: the more
+the children anthropomophized, the less engaged into the interaction they were.
 
@@
 mechanisms that relate anthropomorphism to adoption and engagement are
-non-trivial. In section~\ref{sec:cognition-neuroscience}, we sketch a model of
+non-trivial. In section~\ref{sec:cognition-neuroscience}, we will sketch a model of
 the cognitive correlates of anthropomorphism that partially account for these
@@
 First, by reviewing what anthropomorphism actually means: besides an
-\emph{artifact-centered} understanding that explains anthropomorphism from the
+\emph{artifact-centric} understanding that explains anthropomorphism from the
 human-like design of the non-human artifact, it seems important to explicit the
-social component, namely a \emph{human-centered} understanding, of
+social component, namely a \emph{human-centric} understanding, of
 anthropomorphism.
@@
 
-While we discuss in section~\ref{meaning} the different meanings of
-anthropomorphism found in literature, it seems appropriate to already precisely
-define the terminology used in this article.
-
-We use the term \textbf{anthropomorphism} to describe the \emph{psychological}
-phenomenon which arises in the \emph{social context} of an interaction between a
-human agent and a non-human agent, in our case a robot (see Figure
-\ref{fig:anthropofig}). We use this term to refer to both people's tendency to
+Despite the fact that there is no commonly accepted definition, the terms
+\textit{anthropomorphism}, \textit{anthropomorphic} or \textit{human-like} are
+often used as if their meanings were clear and agreed
+upon~\citep{persson_anthropomorphism_2000}. It is however argued that these
+terms might be misused~\citep{duffy_anthropomorphism_2002,epley_when_2008}, and
+while some researchers would refer for instance to \textit{``the robot's level
+of anthropomorphism''} \citep{bartneck_is_2007,feil-seifer_human-robot_2008},
+others disagree and argue that a system or artifact itself does not
+\emph{contain anthropomorphism} (anthropomorphism is not intrinsic to the robot)
+but only \emph{gives rise} to the process of anthropomorphizing in a given user
+and situation.
+
+In the frame of this article, we refer to the term \textbf{anthropomorphism} to
+describe the \emph{psychological} phenomenon which arises in the \emph{social
+context} of an interaction between a human agent and a non-human agent, in our
+case a robot. We use this term to refer to both people's tendency to
 \textit{perceive} (\textbf{anthropomorphic perceptions}) human-like
@@
 
-Despite the fact that ``anthropomorphism'' literally means ``human
-form'' we propose that the term should \textit{not} be used to refer to the
-\textit{form / design} of a non-human agent or artifact. To refer to an
-imitation of human-like \textit{form / design} of artificial agents, we propose
-to use the term \textbf{anthropomorphic design}. This explicit terminology
-prevents the commonly encountered confusion between anthropomorphism as a
-psychological, subjective phenomenon, and the external, objective factors that
-\emph{influence} the phenomenon itself.
+Despite the fact that ``anthropomorphism'' literally means ``human form'' we
+propose that the term should \textit{not} be used to refer to the \emph{form}
+and/or \emph{design} of a non-human agent or artifact. To refer to an imitation
+by an artificial agent of an human-like form, we propose to use the term
+\textbf{anthropomorphic design}. This explicit terminology prevents the commonly
+encountered confusion between anthropomorphism as a psychological, subjective
+phenomenon, and the external, objective factors that \emph{influence} the
+phenomenon itself.
 
@@
 
-The remainder of this article is organized as follows.  According to the three
+The remainder of this article is organized as follow.  According to the three
 perspectives that we take, section \ref{sec:anthropomorphism} establishes a
@@
 understanding of anthropomorphism as a multi-factor phenomenon.  Based on this,
-section~\ref{sec:our-ideas} proposes a new qualitative model of the
-\textit{dynamics of anthropomorphism}. This model describes the variances and
-dynamics of people's tendency to anthropomorphize an artificial agent, such as a
-robot. Section \ref{sec:cognition-neuroscience} then investigates the cognitive
-and neuro-biological mechanisms of anthropomorphism to consolidate our
+section~\ref{sec:our-ideas} proposes a new qualitative model of the dynamics of
+anthropomorphism. This model describes the variances and dynamics of people's
+tendency to anthropomorphize an artificial agent, such as a robot. Section
+\ref{sec:cognition-neuroscience} then investigates the cognitive and
+neuro-biological mechanisms of anthropomorphism to consolidate our
 considerations and the proposed model.  Section \ref{sec:measuring} looks at how
@@
 
-Literature on anthropomorphism is quite diverse. There exist different and
-partly conflicting definitions of the term anthropomorphism, and it still
-appears controversial that humans tend to \textit{``see human in the non-
-human''} \citep{epley_seeing_2007}. As anthropomorphism arises in an interaction
-between a human and a non-human agent~\citep{persson_anthropomorphism_2000}, one
-can also take two main \textit{perspectives} when trying to explain why humans
-anthropomorphize~\citep{lee_human_2005}: an artifact-centered perspective and a
-human-centered perspective.
-
-After discussing and clarifying the different meanings of anthropomorphism, we
-present the main aspects of an \emph{artifact-centered} perspective on
-anthropomorphism. We then provide a synthesis of literature that study
- anthropomorphism from the perspective of the human: we aim here at providing a broad
-picture of this phenomenon by summarizing theories from developmental
-psychology, cognitive science, neuroscience, and social psychology.
-
-We then briefly discuss the impact of the interaction context on
-anthropomorphism, before restating anthropomorphism as a \emph{multi-factor
-phenomenon}.
-
-\subsection{Overview of the diverse understandings of anthropomorphism}
-\label{meaning}
-
-Naturally, conflicts in how terms are used lead to a diversity of understandings
-of the phenomenon which is described: anthropomorphism is a phenomenon that is
-studied in very different domains that each integrate their own understanding,
-use the same term to refer to different things.  Despite the fact that there is
-no commonly accepted definition, the terms \textit{anthropomorphism},
-\textit{anthropomorphic} or \textit{human-like} are often used as if their
-meanings were clear and agreed upon \citep{persson_anthropomorphism_2000}. It is
-however argued that these terms might be misused
-\citep{duffy_anthropomorphism_2002,epley_when_2008}.  For instance, some
-researchers refer to \textit{``the robot's level of anthropomorphism''}
-\citep{bartneck_is_2007,feil-seifer_human-robot_2008}, whereas others disagree
-to such a statement because they understand that a system or artifact itself
-does not \textit{``contain anthropomorphism''} (anthropomorphism is not
-intrinsic to the robot) but only gives rise to the process of anthropomorphizing
-in a given user and situation. Consequently,
-\cite{persson_anthropomorphism_2000} conclude that anthropomorphism emerges in
-the \textit{interaction} between the technology and the user, and has to be
-understood as such. We come back on this point in the next section.
-
-Another paradox is that, while human's tendency to anthropomorphize is commonly
-observed, the phenomenon is at the same time still rather poorly understood
-\citep{epley_seeing_2007}. The phenomenon itself has been found to be very
-complex, sometimes subtle and as such hard to study
-\citep{duffy_anthropomorphism_2002,epley_when_2008}. Besides, it is not clear
-how to operationalize and measure anthropomorphism (we discuss this specific question
-in section \ref{sec:measuring}).
-
-Depending on which definition of anthropomorphism is applied, not everything
-colloquially labeled as \emph{anthropomorphism} really is anthropomorphism.  For
-example, it is not always clear whether a person (may it be an adult or a child)
-who gives an anthropomorphic response, believes that the other agent really
-thinks or acts like a human or whether he/she is using anthropomorphism in a
-metaphoric sense \citep{leeds_childrens_1992}.  This call for explicitely
-stating what we mean when talking about anthropomorphism.
-
-Several attempts have been made to clarify what the psychological phenomenon
-\emph{anthropomorphism} actually is.  From a psychology point of view,
-\citet{epley_when_2008} explain what anthropomorphism is \textit{not}. For
-instance, in their understanding, anthropomorphism does not include behavioral
-descriptions of observable actions but it requires going beyond what is directly
-observable. They also suggest that anthropomorphism does not merely entail
-\textit{animism}, as animate life is not a \textit{uniquely} human-like
-characteristic.\footnote{For the whole list and more details, the reader may
-refer to the original work \citep{epley_when_2008}.}
-
-As human-likeness itself is manifold and complex, some researchers argue that
-there might not just be one single type of anthropomorphism but different levels
-or gradations. For instance, \citet{persson_anthropomorphism_2000} proposes to
-understand anthropomorphism as a multi-layered phenomenon, namely
-\emph{primitive categorization}, \emph{primitive psychology},
-\emph{folk-psychology}, \emph{traits}, \emph{social roles}, and \emph{emotional
-anthropomorphism}. Correspondingly, \citet{ruijten_introducing_2014} propose to
-understand anthropomorphism as a continuum ranging from low to high human
-likeness, and to measure it as such.
+Anthropomorphism arises in an interaction between a human and a non-human agent,
+and one can consequently take two main perspectives when trying to explain why
+humans anthropomorphize~\citep{lee_human_2005}: an artifact-centric perspective
+and a human-centric perspective. We present these two perspectives, with a
+special focus on the complex human aspects: we attempt there to summarize the
+main approaches from developmental psychology, cognitive science, neuroscience,
+and social psychology. We then briefly discuss the impact of the interaction
+context on anthropomorphism, which will finally lead us to globally restate
+anthropomorphism as a \emph{multi-factor phenomenon}.
 
@@
 
-\subsection{Artifact-centered perspective on anthropomorphism}
-
-The \emph{artifact-centered} perspective explains anthropomorphism from the
+\subsection{Artifact-centric perspective on anthropomorphism}
+
+The \emph{artifact-centric} perspective explains anthropomorphism from the
 ascertainable parts of the non-human agent, namely the anthropomorphic form of
-it. This section deals with the question how far anthropomorphism can be
-explained from the design of the artifact.  One of the most prominent working
-hypothesis in this field is the Uncanny Valley hypothesis
-\citep{mori_uncanny_1970}. In general, it is proposed that human-like designs of
-robots can evoke both positive and negative feelings in a human user.
-
-The direction of causality in the artifact-centered view goes from the artifact
+it. One of the most prominent working hypothesis in this field is the Uncanny
+Valley hypothesis~\citep{mori_uncanny_1970}. It suggests that human-like designs
+of robots can evoke both positive and negative feelings in a human user.
+
+The direction of causality in the artifact-centric view goes from the artifact
 to the humans: the artifact (or a certain feature of it) \emph{encourages} the
@@
 \textit{reflective}. As this distinction implies different cognitive processes,
-it is more approriate to apply a human-centered perspective and we will come
+it is more approriate to apply a human-centric perspective and we will come
 back to it later, in section \ref{sec:cognitive-expl}.
 
-\paragraph{The Physical shape} of a robot refers to `how the robot looks like'
+\paragraph{The Physical shape} of a robot refers to ``how the robot looks like''
 and includes its general form, and other visible features, such as its size, the
-materials used, its color, and specific details. Generally, robots can be
-divided into human-like (anthropomorphic) and mechanical (non-anthropomorphic)
-robots. However, it makes sense to be slightly more specific about the form, and
+materials used, its color, and specific details. Specifically,
 \cite{fong_survey_2003} suggest four categories: anthropomorphic, zoomorphic,
 caricatured, functional. The borders and transitions between these categories
-are not very well defined.  Of particular importance seems to be the presence or
-absence of specific human body parts, such as arms and hands, legs, a torso or a
-head and face. Of those, the faces of robots have received remarkable attention
-concerning how they are perceived and accepted. \cite{disalvo_all_2002} studied
-what features and dimensions of a humanoid robot's face most dramatically
-contribute to people's perception of its humanness. The authors analyzed 48
-humanoid robot heads and found that the presence of certain features, the
-dimensions of the head, and the total number of facial features heavily
-influence the perception of humanness in robot heads.
+are not very well defined. The presence or absence of specific human body parts,
+such as arms and hands, legs, a torso or a head and face seems of particular
+importance. Of those, the faces of robots have received remarkable attention:
+\cite{disalvo_all_2002} studied for instance what features and dimensions of a humanoid
+robot's face most dramatically contribute to people's perception of its
+humanness. The authors analyzed 48 humanoid robot heads and found that the
+presence of certain features, the dimensions of the head, and the total number
+of facial features heavily influence the perception of humanness in robot heads.
 
 \paragraph{Expression, communication, and behavior} refers to how the robot
-expresses its human qualities through interacting and behaving. In fact, many
-humanoid robots express their human-likeness not in physical shape but only
-through the \textit{suggestion} of features~\citep{disalvo_all_2002}. Besides
-this, communication and interaction modalities of a robot are likely to play a
-role to what extent the robot will be anthropomorphized. Can the user interact
-with the robot through a touch interface, or using speech? Does the robot
-respond using linguistic utterances or non-linguistic sounds? Is the voice
-human-like or synthetic, on-board or coming from an external second device? A
-study by~\cite{takayama_im_2009} found that this has an effect on people's
-perception of trust in the robot and how convincing the robot appears to them.
-Besides this, we expect that a robot's behavioral aspects concerning
-human-social interaction have an impact. Does the robot use polite formulations,
-etiquette, appropriate facial expressions? Are its responses and reactions
-timely? Usually, robots that directly interact with humans are slow, which
-appears not very human-like to most participants.
+expresses its human qualities through interacting and behaving, and as a matter
+of fact, many humanoid robots primarily express their human-likeness through the
+\textit{suggestion} of features~\citep{disalvo_all_2002} instead of their
+physical shape. Interaction modalities also play a role to what extent the robot
+will be anthropomorphized. Can the user interact with the robot through a touch
+interface, or using speech? Does the robot respond using linguistic or
+non-linguistic utterances? Is the voice human-like or synthetic, on-board or
+coming from an external second device? A study by~\cite{takayama_im_2009} found
+that this has an effect on people's perception of trust in the robot and how
+convincing the robot appears to them.  Finally, the implementation of \emph{social
+rules} into the robot's behavior also impacts the tendency to anthropomorphize. Does the
+robot use polite formulations, etiquette, appropriate facial expressions? Are
+its responses and reactions timely? As it stands today, robots tend on the
+contrary to interact with humans at a slow pace, which does not elicit a
+human-like perception by the user.
 
@@
 %
-%		HUMAN-CENTERED PERSPECTIVE: SOCIAL PHENOMENON
-%
-%
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Human-centered perspective on anthropomorphism}
-
-In contrast to the artifact-centered perspective, in the human-centered
-perspective the argumentation is that the human is self-motivated to
-anthropomorphize the non-human artifact. As already mentioned, both these views
-go hand in hand.
+%		HUMAN-centric PERSPECTIVE: SOCIAL PHENOMENON
+%
+%
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Human-centric perspective on anthropomorphism}
 
@@
 non-human agent can be anything that acts -- or is believed to act -- with
-apparent independence.} One common reason for anthropomorphism is that by
+apparent independence.} One common explanation for anthropomorphism is that by
 perceiving some human-like characteristics in the non-human agent, this agent is
@@
 can feel \emph{more empathetic} toward it, and possibly one can then anticipate
-the agent's behavior. These are central motivations when trying to explain
-anthropomorphism, and we will come back to them in more detail later on.
-\citet{eddy_attribution_1993} explain that, because of these reasons, people
-commonly anthropomorphize their pets, by ascribing mental states, intentions or
-feelings to them.\footnote{Interestingly, pet-ownership seems to have a
-significant impact on human-robot interaction: several studies suggest that
-pet-owners are more likely to anthropomorphize technologies and robots than
-non pet-owners} But how can these motivations behind anthropomorphism be
-explained from a human-centered point of view?
+the agent's behavior. These are the typical reasons used for instance
+by~\citet{eddy_attribution_1993} to explain people's tendency to
+anthropomorphize their pets, by ascribing mental states, intentions or feelings
+to them.\footnote{Interestingly, pet-ownership seems to have a significant
+impact on human-robot interaction: several studies suggest that pet-owners
+are more likely to anthropomorphize technologies and robots than non
+pet-owners}
 
 In the following, we present what we found in reviewing literature that applies
-a human-centered perspective on anthropomorphism by building on: \textit{(1)} a
+a human-centric perspective on anthropomorphism by building on: \textit{(1)} a
 line of research in developmental psychology that studies the attribution of
@@
 The phenomenon of attributing animacy and intentions to nonliving objects such
-as simple shapes has been intensively studied in developmental psychology. As
-mentioned earlier, Piaget found that children tend to ascribe life to the
-nonliving. They also tend to interpret physical phenomena in terms of intention
-on the part of the non-human subject. For instance children are likely to argue
-that \textit{``the sun is hot because it wants to make people warm''}
-\citep{leeds_childrens_1992}. In this example it is in fact questionable whether
-children really anthropomorphize the sun (believing that it has an intention) or
-whether they are using anthropomorphism in a metaphoric sense (because their
-conceptions of the world and of the living are not yet fully formed). However,
-experiments by \cite{heider_experimental_1944} and
-\cite{michotte_perception_1963} showed that also adult participants attribute
-animacy and intention to simple things and shapes based on motion. In both
-experiments, participants viewed animations of simple shapes, such as circles or
-triangles. Asked to describe what they observed, most people developed elaborate
-stories, attributing motivations, emotions and relationships between the
-objects.\footnote{For more details, the reader may refer to the ``attribution
-theory''.}
-
-As mentioned earlier, it seems that there is a natural, relatively spontaneous
-reaction that accounts for people's tendency to attribute animacy and intention
+as simple shapes has been intensively studied in developmental psychology.
+Piaget found that children tend to ascribe life to the nonliving and they also
+tend to interpret physical phenomena in terms of intention on the part of the
+non-human subject. For instance children are likely to argue that \textit{``the
+sun is hot because it wants to make people warm''} \citep{leeds_childrens_1992}.
+It is questionable whether children really anthropomorphize the sun (believing
+that it has an intention) or whether they are using anthropomorphism in a
+metaphoric sense (because their conceptions of the world and of the living are
+not yet fully formed). However, experiments by \cite{heider_experimental_1944}
+and \cite{michotte_perception_1963} showed that also adult participants
+attribute animacy and intention to simple things and shapes based on motion. In
+both experiments, participants viewed animations of simple shapes, such as
+circles or triangles. Asked to describe what they observed, most people
+developed elaborate stories, attributing motivations, emotions and relationships
+between the objects.\footnote{For more details, the reader may refer to the
+\emph{attribution theory}.} People tend to attribute animacy and intention
 to moving shapes, even when there is no similarity of the shape to a human. This
@@
 familiar with (\ie our self). Thus, we can best use our self as source of induction
-when reasoning about other agents. However, in case we would like to understand
-the behavior of a spider, we would probably not use our mental model of a human
-(or our self) simply because we do not have many things in common with a spider.
-And this is the second central aspect here.
+when reasoning about other agents.
 
@@
 
-This cognitive viewpoint on anthropomorphism is important because people's
-estimation of an agent's knowledge model and its capabilities affects the way
-they relate to it. This holds implications for the resulting interaction with
-the system, the user experience, and the acceptance. Previous research examined
-the validity of the mental model concept with various kinds of robots
+People's estimation of an agent's knowledge model and its capabilities are of
+particular importance. This holds implications for the resulting interaction
+with the system, the user experience, and the acceptance. Previous research
+examined the validity of the mental model concept with various kinds of robots
 \citep{schmitz_concepts_2011,kiesler_mental_2002}. Findings suggest that people
 tend to hold richer mental models of anthropomorphic robots in contrast to
-mechanic ones \citep{kiesler_mental_2002}.\footnote{Later in this article,
-we may however come to question how far this result is based on
-expectations from the human user side, which are likely to be refined
-after continued interaction, and after the user gets acquainted with the
-robot's behavior.} A similar finding is described in
-\cite{hegel_understanding_2008} and \cite{krach_can_2008}. In a user study using
+mechanic ones \citep{kiesler_mental_2002}. A similar finding is described in
+\cite{hegel_understanding_2008} and \cite{krach_can_2008}: in a user study using
 functional magnetic resonance imagery (fMRI), the authors found that
@@
 \citep{premack1978does,leslie_pretense_1987,Frith2003}.  The finding of
-\cite{hegel_understanding_2008} and \cite{krach_can_2008} was evident at the
+Hegel and Krach was evident at the
 behavioral level as well as on the neuro-physiological level: the more the
@@
 -- themselves, humans and human behavior. This understanding builds on the
-theory of mind,  a
-person's ability to attribute mental states to oneself and others. 
-We briefly reviewed  neuro-physiological evidence of a link between the tendency
-to thoughtfully anthropomorphize and the engagement of brain processes involved
-in the attribution of mental states to other humans. The human-likeness quality
-of the artefactual agent seems to play a role in the involvement of theory of
-mind but also the unpredictable feature of the agent behavior alone seems to be
-sufficient. Low-level mechanisms of the brain that allow humans to map others'
-motor behaviors into their own repertoire are equally elicited when perceiving a
-robot's action. It is not yet clear whether humans are processing emotional
-signals from a robot the same way as they do for human beings.
+theory of mind,  a person's ability to attribute mental states to oneself and
+others.  There is also  neuro-physiological evidences of a link between the
+tendency to thoughtfully anthropomorphize and the engagement of brain processes
+involved in the attribution of mental states to other humans. The human-likeness
+quality of the artefactual agent seems to play a role in the involvement of
+theory of mind but also the unpredictable feature of the agent behavior alone
+seems to be sufficient. Low-level mechanisms of the brain that allow humans to
+map others' motor behaviors into their own repertoire are equally elicited when
+perceiving a robot's action. It is however not yet clear whether humans are processing
+emotional signals from a robot the same way as they do for human beings.
 
@@
 experience than the self and in turn people tend to make inferences about
-others' mental states by relying inordinately on their own mental state.
-\footnote{Using one's own mental states and characteristics as a guide when
-reasoning about other humans is called ego-centrism. In contrast, when using
-self-knowledge (or knowledge about humans in general) when reasoning about
-non-human agents, this is called anthropomorphism. See
-\cite{epley_seeing_2007}.} Also empirical findings suggest that knowledge about
-humans in general, or self-knowledge in particular, is likely to serve as a
-readily accessible base for induction when reasoning about non-human agents.
-This tendency is usually stronger in young children and decreases with cognitive
-development and the learning to distinguish the self from other humans, and
-non-human agents.
+others' mental states by relying inordinately on their own mental state.  Also
+empirical findings suggest that knowledge about humans in general, or
+self-knowledge in particular, is likely to serve as a readily accessible base
+for induction when reasoning about non-human agents.  This tendency is usually
+stronger in young children and decreases with cognitive development and the
+learning to distinguish the self from other humans, and non-human agents.
 
@@
 contact, social connection, and social approval from other agents. In lack of
-social connections to other humans (\etc friends, family, colleagues), a person
+social connections to other humans (friends, family, colleagues), a person
 is more likely to compensate these social connections by anthropomorphizing
@@
 task (security, rescue, \etc). \cite{joosse_what_2013} showed, for instance,
-that when the same robot ({\sc nao}) was used in a different task context (cleaning
-task \vs tour guide), users ascribed different personalities to the robot. \cite{goetz_cooperation_2002}
-revealed a link between a robot's context of use and people's perception of the
-robot. The authors found that people prefer a serious robot for serious tasks
-and a less serious robot for more playful tasks
-. \cite{kaplan_free_2000}
-discussed the role of uselessness in the design of robots. The author argues
-that artificial pets like AIBO have no real purpose, in a sense that they do not
-provide any kind of service or, in other words, \textit{``they are not doing
-what you tell them to do''} and \textit{``they might refuse the order of its
-owner''}. It may be this very aspect that increases people's tendency to
-anthropomorphize the robot. According to Kaplan, it is in our daily use language
-that we tend to attribute intentions to devices that are not doing their job
-well.
+that when the same robot ({\sc nao}) was used in a different task context
+(cleaning task \vs tour guide), users ascribed different personalities to the
+robot. \cite{goetz_cooperation_2002} revealed a link between a robot's context
+of use and people's perception of the robot: the authors found that people
+prefer a serious robot for serious tasks and a less serious robot for more
+playful tasks . \cite{kaplan_free_2000} discussed the role of uselessness in the
+design of robots. The author argues that artificial pets like AIBO have no real
+purpose, in a sense that they do not provide any kind of service or, in other
+words, \textit{``they are not doing what you tell them to do''} and
+\textit{``they might refuse the order of its owner''}. It may be this very
+aspect that increases people's tendency to anthropomorphize the robot. According
+to Kaplan, it is in our daily use language that we tend to attribute intentions
+to devices that are not doing their job well.
 
@@
 
-Summing it up, anthropomorphism is a commonly discussed and studied trait of
-human-robot interaction; however its current understanding seems to be stuck.
-More concretely, when seeking to understand why anthropomorphism in an
-interaction between a human and a non-human artifact happens, most attention is
-given to the artifact and/or to the human. We agree that these two are the
-essential ``players'' of anthropomorphism (see Figure \ref{fig:anthropofig}).
-Indeed and, as outlined before, research has shown that both the human and the
-artifact are not only the two players of anthropomorphism but also the two main
-``factors'' that can promote or hinder anthropomorphism.
-
-However, we think that this is not the full story. When agreeing to understand
+Summing it up, and while anthropomorphism is a commonly discussed and studied
+trait of human-robot interaction, its current understanding is somewhat limited:
+when looking at understanding why anthropomorphism arises in an interaction
+between a human and a non-human artifact, most attention is given to the
+artifact itself. This is however not the full story, and when considering
 anthropomorphism as a specific type of \textit{experience} that arises in an
-\textit{interaction} between a set of user expectations and the external reality
-\citep{persson_anthropomorphism_2000}, 
-%(see Figure~\ref{fig:anthropomorphism_and_interaction})
-it becomes clear that this interaction happens in a specific context, with a
-specific history. We think that the context and the history of the interaction
-(in Figure \ref{fig:anthropofig} denoted as \textit{time}), are two more factors
-that determine anthropomorphism.
-
-Consequently, we propose a holistic understanding of anthropomorphism as a
-phenomenon which is determined by multiple factors (see also Figure
-\ref{fig:anthropofig}):
+\textit{interaction} between a set of user expectations and the external
+reality~\citep{persson_anthropomorphism_2000}, it appears that complex human
+factors, the interaction context, and the interaction history do play key roles.
+
+It appears thus important to consider anthropomorphism as a phenomenon which is
+determined by multiple factors, depicted on Figure \ref{fig:anthropofig}:
 
@@
 
-\item ~the psychological determinants in the \textbf{human
+\item ~the complex cognitive and psychological determinants of the \textbf{human
     user}~\citep{epley_seeing_2007},
@@
 
-So far, the HRI community has not investigated how anthropomorphism in
-interactions with robots evolve over time. There are several reasons for why it
-makes sense to consider temporal dynamics in anthropomorphism.
-
-One reason for why changes in anthropomorphism over time are likely, comes from
-the cognitive perspective, as outlined in the previous section. We are
-spontaneous but also reflect on our interactions with the robot.  From the
-artifact-centered perspective on anthropomorphism (thus, looking at the
-characteristics of the robot) it is assumed that humans directly (more or less
-mindlessly) respond to life-like and social cues that a non-human agent (here:
-robot) emits~\citep{reeves_media_1996,nass_machines_2000}. Without huge
-thoughtful mental processing, humans tend to apply stereotypes and heuristics to
-the robot, and in turn apply human-human social schemas and norms to the
-occurring interactions. However, this may only be some \textit{immediate}
-(sometimes visceral) experience, reflecting the first impression that the user
-has of the robot, based on its appearance~\citep{norman_emotional_2003}.
-\cite{takayama_perspectives_2012} refers to this as the \textit{in-the-moment}
-perspective we have on the robot, compared to a more distanced cogitation and
-consideration, which the author calls \textit{reflective}.  Further, we also
-become familiar with the robot as we continue interacting and dealing with it,
-we gain knowledge about it, and refine our mental model of the robot.
-
-Another reason for considering temporal dynamics are the changes in user
-experience~\citep{karapanos_user_2009} and relationship to the robot.
-\cite{kanda_interactive_2004} pointed out that not only the relationships among
-people evolve over time but that, in a similar manner, one can expect that also
-people's relationship and their attitude toward robots evolve. The authors were
-among the first ones to describe empirically \textit{novelty effects} during a
-long-term study with an interactive robot in a school.
+The HRI community has yet to investigate in depth the impact of time on
+anthropomorphism. We already discussed how humans directly (more or less
+mindlessly) respond to life-like and social cues emitted by non-human agents:
+without thoughtful mental processing, humans tend to apply stereotypes and
+heuristics to the robot, and in turn apply human-human social schemas and norms
+to the occurring interactions. Following concepts introduced by
+\cite{takayama_perspectives_2012}, we also mentioned how \emph{reflective}
+interactions may succeed to \emph{in-the-moment} reactions, due to
+\emph{familiarization} effects.
+
+These dynamic modes of interactions reflect the changes in user
+experience~\citep{karapanos_user_2009} and relationship to the robot, and are
+given rhythm by specific interaction episodes like the \emph{novelty effect},
+first pointed out by~\cite{kanda_interactive_2004}.
 
@@
 illustrate how the user tendency to anthropomorphize decreased over time.
-Combined with the discussion on the nature and factors of
-anthropomorphism that we proposed in section~\ref{sec:anthropomorphism}, we
-introduce in the following section a novel qualitative model of the evolution of
-anthropomorphism over time, \ie a model of the \emph{dynamics of
-anthropomorphism}.
+Combined with the discussion on the nature and factors of anthropomorphism that
+we proposed in section~\ref{sec:anthropomorphism}, we introduce in the following
+section a novel qualitative model of the evolution of anthropomorphism over
+time, \ie a model of the \emph{dynamics of anthropomorphism}.
 
@@
 
-The phenomenological model of anthropomorphism we propose
-(Figure~\ref{fig:dynamics},~\citep{lemaignan2014dynamics}) represents how the
-level of anthropomorphic \emph{effects}~\AntE[R,H,C,t] (\ie the observable
-manifestations of the anthropomorphism \Ant) evolves over a long-term human-robot
-interaction.
+To better structure the reflection about the interplay between anthropomorphism
+and interaction history, we propose to introduce a phenomenological model of the
+dynamics of anthropomorphism.  (Figure~\ref{fig:dynamics}, first presented
+in~\citep{lemaignan2014dynamics}).  It represents how the level of
+anthropomorphic \emph{effects}~\AntE[R,H,C,t] (\ie the observable manifestations
+of the anthropomorphism \Ant) evolves over a long-term human-robot interaction.
 
@@
 (non-mediated), repeated interaction with the same robot, over an extended
-period of time (typically longer than a week) --, we also formally introduce a
+period of time (typically longer than a week) --, we also introduce the
 so-called \emph{novelty effect}~\citep{kanda_interactive_2004} that models the
@@
 
-In this model, anthropomorphism is quantified
-by a \emph{normalized level of anthropomorphic effects} $\antENorm[R,H,C,t] =
-\frac{\antE[R,H,C,t]}{\antEMax}$: because anthropomorphic effects are often
-qualitative and difficult to quantify on an absolute scale, we present them as a
-normalized value, that spans from a minimum (no anthropomorphic effects:
-$\antE=0$) to a maximum (noted \AntEMax, with $t_{max} = \operatorname{arg\,max}_t
-\, \antE[t]$). For the sake of readability, we will use \Ant in the following
-sections to refer to the normalized level of anthropomorphic effects. Note also
-that we discuss in section~\ref{sec:measuring} possible methodologies for the
-quantitative and qualitative assessment of anthropomorphic effects.
-
-The actual maximum value of anthropomorphic effects depends on each unique
-combination of a human, a robot, a situation and several other factors we
-introduce below. Figure~\ref{fig:dynamics} pictures this
-maximum value at $t_{max}$, which we hypothesize to correspond to the
-novelty effect ``peak''.
+In this model, anthropomorphism is quantified by a \emph{normalized level of
+anthropomorphic effects} $\antENorm[R,H,C,t] = \frac{\antE[R,H,C,t]}{\antEMax}$:
+because anthropomorphic effects are often qualitative and difficult to quantify
+on an absolute scale, the model represents them as a normalized value, that
+spans from a minimum (no anthropomorphic effects: $\antE=0$) to a maximum
+(\AntEMax, with $t_{max} = \operatorname{arg\,max}_t \, \antE[t]$, which we
+hypothesize to correspond to the novelty effect ``peak''). For the sake of
+readability, we will use \AntE in the following sections to refer to the
+normalized level of anthropomorphic effects.
+
+While not the focus of this article, we discuss in section~\ref{sec:measuring}
+some of the possible methodologies and techniques for the quantitative and
+qualitative assessment of anthropomorphic effects.
 
@@
 
-\draw (-0.05, 2.1) -- (0.05, 2.1) node[anchor=east] {\ICAe};
+\draw (-0.05, 2.1) -- (0.05, 2.1) node[anchor=east] {\IPAe};
 \draw (-0.05, 5) -- (0.05, 5) node[anchor=east] {\AntEMax};
@@
     and \emph{stabilization}, preceded by a \emph{pre-interaction} phase. The
-    pre-interaction phase is characterized through an \emph{initial capital of
-    anthropomorphism} (ICA, noted \ICA).  Once the interaction starts, the level
-    of anthropomorphism increases due to the \emph{novelty effect}, and then
+    pre-interaction phase is characterized through an \emph{initial potential to
+    anthropomorphize} (IPA, noted \IPAe).  Once the interaction starts, the level
+    of anthropomorphism increases, in part due to the \emph{novelty effect}, and then
     decreases to reach a \emph{stabilized level of anthropomorphism} (SLA, noted
-    \SLA). \ICA and \SLA may vary depending on the user (and his/her
+    \SLAe). \IPAe and \SLAe may vary depending on the user (and his/her
     expectations), the robot and the context of interaction.  During the
@@
     overall shape of the curve is unique to each human interacting with a
-    specific robot in a given context, as depicted by the alternative curves.}
+    specific robot in a given context, as emphasized by the alternative curves.}
 
@@
 
-The \emph{initial capital of anthropomorphism} \ICA describes the initial potential
-for the human user to anthropomorphize the robot in a given situation.
-This potential depends on several factors, introduced in
-section~\ref{sec:multi-factors}.
-It represents the level of anthropomorphic effects that can be expected to occur
-during the very first contacts between the human and the robot. During this first
-phase, pre-conceptions and initial expectations as well as previous experience
-of the user with other similar types of robots and similar contexts are the
-primary source of influence.
-
-During the initialization phase, we expect an increasing value of \Ant
-that is due to the so-called \textit{effects of novelty} of the
-robot. Such effects have been described with interactive technologies in general
-\citep{rogers_diffusion_1995}, and also in several long-term HRI studies in
-workplaces \citep{huttenrauch_fetch-and-carry_2003,mutlu_robots_2008}, in
-schools and public places
+The \emph{initial potential to anthropomorphize} \IPAe describes the initial
+potential for the human user to anthropomorphize the robot in a given situation.
+This potential depends on the several factors introduced in
+section~\ref{sec:multi-factors}.  It represents the level of anthropomorphic
+effects that can be expected to occur during the very first contacts between the
+human and the robot. During this first phase, pre-conceptions and initial
+expectations as well as previous experience of the user with other similar types
+of robots and similar contexts are of prime importance.
+
+During the initialization phase, we expect an increasing value of \Ant that is
+due to the effects of the novelty of the robot. Such effects have been described
+with interactive technologies in general \citep{rogers_diffusion_1995}, and also
+in several long-term HRI studies in workplaces
+\citep{huttenrauch_fetch-and-carry_2003,mutlu_robots_2008}, in schools and
+public places
 \citep{gockley_designing_2005,kanda_communication_2005,kanda_interactive_2004},
 and elder care centers \citep{sabelli_conversational_2011}. Also long-term
-studies of domestic robots have shown similar effects and found that after some
-time people's interest, engagement, and fascination of the robot decreased
+studies of domestic robots have shown similar effects -- and also found that
+after some time people's interest, engagement, and fascination of the robot
+decreased
 \citep{sung_robots_2009,sung_domestic_2010,fernaeus_how_2010,fink_living_2013}.
@@
 The type of anthropomorphic effects typically observed during the initialization
-hpase include users who spontaneously tend to talk directly to the robot while
-they are aware that the system is not be able to recognize speech: greeting the
+phase include users who spontaneously tend to talk directly to the robot while
+they are aware that the system is not be able to recognize speech (greeting the
 robot, asking questions to it, giving it a nickname, praising the robot,
-commenting on its performances and giving commands. Also, the use of pointing
-gestures and waving at the robot are often found, as well as ascribing gender
-and some personal preferences or intention to the robot.
+commenting on its performances, giving commands), the use of pointing gestures
+and waving at the robot, as well as ascribing gender and some personal
+preferences or intention to the robot.
 
@@
 a longer time, to reach a value that we call the \textit{Stabilized Level of
-Anthropomorphism} ($SLA$), noted \SLA. The value that the
-$SLA$ approaches is unique for each user interacting with a specific robot in a
-given situation. \SLA may approach $0$, when no anthropomorphic effects
+Anthropomorphism} (SLA), noted \SLAe. The value that the
+SLA approaches is unique for each user interacting with a specific robot in a
+given situation. \SLAe may approach $0$, when no anthropomorphic effects
 are observed anymore, for instance when the user is interacting with the robot
@@
 robot, what \cite{takayama_toward_2011} calls the robot being
-\textit{``invisible in use''}. \SLA may as well remains above 0 if the user
+\textit{``invisible in use''}. \SLAe may as well remains above 0 if the user
 continues to exhibit anthropomorphic behaviors when interacting with the robot
@@
 
-The level \SLA, like \ICA, is the result of a combination of multiple human,
+The level \SLAe, like \IPAe, is the result of a combination of multiple human,
 robotic and contextual factors, with the additional impact of the
 \emph{interaction history t} that the user experienced with the robot. Note that
-the $ICA$ and $SLA$ levels are generally not correlated: a person may initially
-have a high potential of anthropomorphizing (high \ICA), for instance a highly
+the IPA and SLA levels are generally not correlated: a person may initially
+have a high potential of anthropomorphizing (high \IPAe), for instance a highly
 anthropomorphic robot, but subsequently get disappointed by the actual
 capabilities of it and stop explaining it in terms of human-like characteristics
-(low \SLA). Another user may however create lasting affective bonds with the
-same robot and may continue to anthropomorphize the robot (higher \SLA).
+(low \SLAe). Another user may however create lasting affective bonds with the
+same robot and may continue to anthropomorphize the robot (higher \SLAe).
 
@@
 \textit{in-the-moment} perspective on agency with a robot compared to the
-\textit{reflective} perspective (see paragraph ``artifact-centered perspective''
+\textit{reflective} perspective (see paragraph ``artifact-centric perspective''
 in section \ref{sec:anthropomorphism}).  For instance, we reflectively might
@@
 shaped by bottom-up perceptual processes, evoking very immediate responses (\eg
-to the cues emitted by the artifact's design (``artifact-centered
+to the cues emitted by the artifact's design (``artifact-centric
 perspective''). In contrast, according to Takayama, reflective perceptions are
@@
 the human engages in this projection, might be driven by the same parameters as
-we mentioned for the \emph{initial capital of anthropomorphism}. We also believe
+we mentioned for the \emph{initial potential to anthropomorphize}. We also believe
 that, at this stage, the human also changes his attitude towards the robot, by
@@
 about me? About itself? About our environment? What can the robot learn?}, etc.).
-
-This mental process depends on the human understanding of the robot's inner
-working, as well as his/her own tendency to anthropomorphize (the
-\emph{personality} in ICA factor). At this stage, the \emph{perception} of the
-robot (its shape for instance) and its original intended \emph{purpose} play
-less of an important role. It is mostly a human-centric process.  The result of
-this third phase is an iteratively adapted cognitive model of the robot.
-
-Another way to think of the three proposed cognitive stages is to relate them to
-the \textbf{user experience} which is characteristic of these three stages. For
-instance, \cite{norman_emotional_2003} characterizes  three user experience
-dimensions (related to emotional attachment), which occur when people use or see
-a product for the first time: \emph{(1)} the \emph{visceral level}, which is the
-first impression of a product based on its experience; at this level people do
-not think about a product but make spontaneous judgments; \emph{(2)} the
-\emph{behavioral level}, in which people use and experience the product,
-appraise its functions, and consider aspects such as usefulness and usability;
-\emph{(3)} the \emph{reflective level}, in which consciousness takes part in the
-process, and past experiences are taken into account.
-
-\paragraph{Relation to the dynamics of anthropomorphism\\}
 
@@
 
+This mental process depends on the human understanding of the robot's inner
+working, as well as his/her own tendency to anthropomorphize (the
+\emph{personality} in IPA factor). At this stage, the \emph{perception} of the
+robot (its shape for instance) and its original intended \emph{purpose} play
+less of an important role. It is mostly a human-centric process.  The result of
+this third phase is an iteratively adapted cognitive model of the robot.
+
+Another way to think of the three proposed cognitive stages is to relate them to
+the \textbf{user experience} which is characteristic of these three stages. For
+instance, \cite{norman_emotional_2003} characterizes  three user experience
+dimensions (related to emotional attachment), which occur when people use or see
+a product for the first time: \emph{(1)} the \emph{visceral level}, which is the
+first impression of a product based on its experience; at this level people do
+not think about a product but make spontaneous judgments; \emph{(2)} the
+\emph{behavioral level}, in which people use and experience the product,
+appraise its functions, and consider aspects such as usefulness and usability;
+\emph{(3)} the \emph{reflective level}, in which consciousness takes part in the
+process, and past experiences are taken into account.
+
+\paragraph{Relation to the dynamics of anthropomorphism\\}
+
 As mentioned before, the three cognitive stages proposed here do not directly
@@
 
-\subsection{Role of disruptive behaviors}
+\subsection{Role of unexpected behaviors}
 \label{sec:disruptive}
@@
 %
-%				DISCUSSION + FUTURE WORK
-%
-%
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Measuring anthropomorphism}
+%				CONCLUSIONS
+%
+%
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Conclusion}
+\label{sec:conclusion}
+
+In this paper, we presented a cognitive and psychological viewpoint on anthropomorphism, what we believe can offer relevant extensions to our understanding of anthropomorphism in HRI.
+Regarding anthropomorphism as a social phenomenon that arises in an interaction, we formulated the following three suggestions:
+\begin{enumerate}
+\item \textbf{Anthropomorphism is based on multiple factors.} The three main factors that constitute anthropomorphism, are characteristics of the human $H$, characteristics of the robot $R$, and characteristics of the context of use $C$.
+A temporal dimension is taken into account by the \textit{interaction history} $t$, which leads to anthropomorphism being also a dynamic phenomenon (see point 3).
+\item \textbf{Anthropomorphism is multi-layered.} Applying a cognitive viewpoint on anthropomorphism, there exist \textit{lower and higher levels} of the phenomenon.
+On one hand, the level (it may be a continuum rather than discrete levels) depends on one how typical or uniquely human the attributed characteristics are, and how much the mental model that the user build of the robot overlaps (or is inspired by) the mental model he/she has of another human.
+As an outcome of this, three different \textit{cognitive stages} have been identified.
+These stages reflect the implicated cognitive depth of the anthropomorphic effect.
+\item \textbf{Anthropomorphism is dynamic.} Looking at how experience and interaction evolve over time, we developed a conceptual model of the dynamics of anthropomorphism, which states that there is a non-linear relationship between the observable \textit{anthropomorphic effects} $A_t$ (a user's tendency to anthropomorphize a robot) and the \textit{interaction history} $t$ (taking into account the actual time the user has spent interacting with the robot for real or imagined).
+The shape of the hypothesized curve starts with the so-called \textit{Initial Capital of Anthropomorphism} ($ICA$) that can be measured as a pre-variable, based on the three main factors (see point 1).
+With a considerable interaction history, the curve approaches the so-called \textit{Stabilized Level of Antrhopomorphism} ($SLA$).
+How the curve evolves in between these two values is flexible and unique to each user, robot, and context.
+We generally assume an increase of \textit{anthropomorphic effects} driven by the \textit{novelty} of the robot, followed by a decrease of $A_t$ as the user \textit{familiarizes} him/herself with the robot and with using the robot.
+\end{enumerate}
+
+\subsection{Measuring anthropomorphism}
 \label{sec:measuring}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-%
-%
-%				CONCLUSIONS
-%
-%
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Conclusion}
-\label{sec:conclusion}
-
-Anthropomorphism is a social phenomenon which seems to be natural on one side
-and very complex on the other side. It is a mechanism within oneself that makes
-a human observer think and treat a non-human agent as if it would have some
-human (social) characteristics, and ascribe to it intentions, emotions, or
-thoughts, for instance. Understanding the reasons and modalities of
-anthropomorphism is thus of prime importance to build a successful and lasting
-human-robot interaction.
-
-Based on our previous (and on-going) work, we hypothesized that there are
-qualitative differences and dynamics over time in how humans relate to different
-types of robots. More concretely, we described that people's perception of
-human-likeness in a robot and in turn their human-social engagement with a robot
-is based on four main factors: (1) the (anthropomorphic) design of the robot,
-(2) individual characteristics of the human user, (3) the context of use /
-interaction, and (4) the interaction history (time factor). We further suggested
-that people's tendency to anthropomorphize a robot is likely to change over time
-with growing experience of the user with the system.
-
-To formalize the variances in anthropomorphism, we proposed a model that we call
-\textit{Dynamics of Anthropomorphism}.
-
-We introduced the concepts of \emph{initial capital} and \emph{stabilized level
-of anthropomorphism} as compound factors to characterize the profile of a given
-anthropomorphic (long-term) interaction.
-
-The article also discussed the cognitive correlates of anthropomorphism. We
-proposed three cognitive stages corresponding to successive refinements of the
-mental models of the robot that the user builds during the interaction. We
-showed how these stages relate to observable anthropomorphic effects, and how
-they evolve over time.
-
-While subject to discussion and further extensions, we hope that this
-contribution consolidates the scientific grounds of anthropomorphism, and
-provides support for a better understanding of long-term acceptance of robots in
-human environments.
+\subsection{Implications}
+
+Overall, if we agree that \textbf{anthropomorphism arises in an interaction}, this requires studying the phenomenon as such, both in terms of evaluation scenarios, and in terms of measurements.
+Regarding \textbf{evaluation scenarios}, we suggest to go beyond using videos and pictures of robots, but to use real interaction scenarios (possibly long-term, \eg one interaction spanning over an extended period of time, or several sessions so to have repeated interactions).
+In terms of \textbf{measurements}, we suggest to go beyond using rating scales, but to apply a more holistic approach that regards not only participants perception of the robot but also the way they interact with the robot.
+For this, we proposed a so-called \textit{Anthropomorphism Index} $AntX$ that can be used both as a measurement tool and as a value that reflects how much a user anthropomorphized a robot in a given situation.
+To take into account the dynamics over time, we propose to measure $AntX$ at several points, as a pre-variable (focusing on user expectations, previous experience, robot design), in-situ variables (focusing on behavioral aspects, interaction, variations of robot behavior) and post-variables (perception and acceptance rating of interaction).
+
+\subsection{Limitations}
+
+We have proposed that the user's familiarization with the robot is a significant factor that influences how anthropomorphism evolves over time.
+We assume a general \textit{decrease} of anthropomorphic effects as the user gets familiar with the robot, and we applied a cognitive viewpoint to legitimate this.
+However, there exist opposite interpretations.
+\cite{eddy_attribution_1993} state that familiarization and more interaction with an agent \textit{increase} the tendency to anthropomorphize.
+Similarly, \citep{duffy_anthropomorphism_2003} reports that several psychological experiments and HRI studies showed that familiarity with the system eases social acceptance and tends to \textit{increase} people's tendency to perceive human-like characteristics in the system.
+We acknowledge that our conceptual model is an idea that needs to be verified, so to see whether our hypotheses can hold.
+In particular, the effect of the user's familiarity with the robot, and the role of disruptive robot behaviors needs to be studied in more detail and over extended periods of time.
+
+While subject to discussion and further refinements and extensions, we hope that this contribution consolidates the scientific grounds of anthropomorphism and provides support for a better understanding of anthropomorphism and its role in long-term acceptance of robots in human environments.
 

### 2014-11-25 paper.tex
Section 3: {stage->layer}

@@
 \emph{familiarization}. We attempt here to build a practical model of the
-cognitive stages we encounter in human-robot interaction.
+cognitive layers we encounter in human-robot interaction.
 
@@
 can explain the dynamic nature of our interactions with robots, and what are the
-main cognitive stages upon which researchers can build to design better, deeper
+main cognitive layers upon which researchers can build to design better, deeper
 human-robot interactions.
@@
 
-\subsection{A Model of the Cognitive Stages of Human-Robot Interaction}
+\subsection{A Model of the Cognitive Layers of Human-Robot Interaction}
 \label{sec:cognitive-model}
@@
 
-\draw (-0.3,2) node[anchor=east] {Stage 1}
-      (-0.3,4) node[anchor=east] {Stage 2}
-      (-0.3,6) node[anchor=east] {Stage 3};
+\draw (-0.3,2) node[anchor=east] {Layer 1}
+      (-0.3,4) node[anchor=east] {Layer 2}
+      (-0.3,6) node[anchor=east] {Layer 3};
 
@@
 %}
-\caption{\textbf{The three cognitive stages of anthropomorphism}: Stage 1 is the instinctive,
+\caption{\textbf{The three cognitive layers of anthropomorphism}: Layer 1 is the instinctive,
 sub-cognitive identification of living peers. {\it Empathy} is characteristic
 of this stage. After longer observation or short, non-contextualized interaction
-(typically, a lab environment), the user reaches Stage 2: the user projects a
+(typically, a lab environment), the user enters Layer 2: the user projects a
 mental model he/she is already familiar with onto the robot. After longer {\it
-contextualized} interaction (typically, at home), the user enters Stage 3 of
+contextualized} interaction (typically, at home), the user enters Layer 3 of
 anthropomorphism: the user composes a custom mental model of the robot,
 based on experience. This leads to adapted interaction modalities, that may
-still be anthropomorphic, or not. Note that the different stages coexist: Stage
-1 and 2 still affect the human perception of the robot in a Stage 3 interaction.}
+still be anthropomorphic, or not. Note that the different layers coexist: Layer
+1 and 2 still affect the human perception of the robot in a Layer 3 interaction.}
 \label{fig:cognitivemodel}
@@
 
-We propose three different cognitive stages (Figure~\ref{fig:cognitivemodel}),
+We propose three different cognitive layers (Figure~\ref{fig:cognitivemodel}),
 which are not mutually exclusive but overlap over time. Note that these three
@@
 
-\subsubsection{Cognitive Processes and Stages\\}
+\subsubsection{Cognitive Processes and Layers\\}
 
@@
 
-The \emph{Stage 1} is the instinctive, pre-cognitive identification of living
+The \emph{Layer 1} is the instinctive, pre-cognitive identification of living
 peers. Studies conducted by~\citet{rosenthal-vonderputten_experimental_2013},
@@
 intuitively in this pre-cognitive way. {\it Empathy} is characteristic of this
-stage~\citep{rosenthalvonderPutten2013neural}.  It is also at this stage that
+layer~\citep{rosenthalvonderPutten2013neural}.  It is also at this stage that
 automatic activation of the human's mirror neurons system  in response to
@@
 
-The intuitive anthropomorphization in the cognitive Stage 1 might be
+The intuitive anthropomorphization in the cognitive Layer 1 might be
 characteristic of what \cite{takayama_perspectives_2012} calls the
@@
 of the robot) or short interaction (touching, short talk like greetings), we
-suggest the human reaches the cognitive \emph{Stage 2}: in this phase, the human
+suggest the human activates the cognitive \emph{Layer 2}: in this phase, the human
 starts building a behavioral and cognitive model of the robot that would support
@@
 
-The cognitive \emph{Stage 3} is reached after a \emph{contextualized} interaction.
-A \emph{contextualized} interaction is \emph{explicitly purposeful} (the purpose
-of the interaction, be it purely entertainment, is explicit and conscious to the
-human), and takes place in an environment that fosters a stronger cognitive (and
-possibly affective/social) commitment from the human in the interaction
-(typically, at home). During this interaction, the human iteratively restates
-and reshapes his/her behavioral and mental model of the robot (\emph{How does
-the robot react to such and such situation/input?  What does the robot know
-about me? About itself? About our environment? What can the robot learn?}, etc.).
+The cognitive \emph{Layer 3} is gradually activated after a
+\emph{contextualized} interaction.  A \emph{contextualized} interaction is
+\emph{explicitly purposeful} (the purpose of the interaction, be it purely
+entertainment, is explicit and conscious to the human), and takes place in an
+environment that fosters a stronger cognitive (and possibly affective/social)
+commitment from the human in the interaction (typically, at home). During this
+interaction, the human iteratively restates and reshapes his/her behavioral and
+mental model of the robot (\emph{How does the robot react to such and such
+situation/input?  What does the robot know about me? About itself? About our
+environment? What can the robot learn?}, etc.).
 
@@
 
-\draw (-0.3,1.5) node[anchor=east] {Stage 1}
-      (-0.3,3) node[anchor=east] {Stage 2}
-      (-0.3,4.5) node[anchor=east] {Stage 3};
+\draw (-0.3,1.5) node[anchor=east] {Layer 1}
+      (-0.3,3) node[anchor=east] {Layer 2}
+      (-0.3,4.5) node[anchor=east] {Layer 3};
 
@@
 and Figure~\ref{fig:mix} attempts to depict their interplay.
-The cognitive Stages 1 and 2, in particular, are both active in the
+The cognitive Layers 1 and 2, in particular, are both active in the
 \emph{initialization} phase of the anthropomorphism model. Sub-cognitive
@@
 engaging the human in the interaction through an initial projected agency,
-whereas cognitive Stage 2 (projection of familiar mental models) supports the
+whereas cognitive Layer 2 (projection of familiar mental models) supports the
 novelty effect by inducing beliefs that the robot is set up with possibly
@@
 
-The cognitive Stage 3 also overlaps with the \emph{Familiarization} phase: as
+The cognitive Layer 3 also overlaps with the \emph{Familiarization} phase: as
 the human gets used to the robot, he/she restates and adapts its
@@
 A \emph{stable level of anthropomorphism} is reached when the adaptation process
-depicted in the cognitive Stage 3 reached a stable state, \ie the user's
+depicted in the cognitive Layer 3 reached a stable state, \ie the user's
 experience with the robot is correctly supported by the cognitive model he/she

### 2014-11-25 paper.tex
Polish conclusion and discussion on measuring anthrop.

@@
 
-In this paper, we presented a cognitive and psychological viewpoint on anthropomorphism, what we believe can offer relevant extensions to our understanding of anthropomorphism in HRI.
-Regarding anthropomorphism as a social phenomenon that arises in an interaction, we formulated the following three suggestions:
+In this paper, we have provided a broad account of the cognitive and
+psychological viewpoints on anthropomorphism, with a novel focus on the
+impact of time. Considering anthropomorphism as a social phenomenon that arises
+in an interaction, we formulated the following three suggestions:
+
 \begin{enumerate}
-\item \textbf{Anthropomorphism is based on multiple factors.} The three main factors that constitute anthropomorphism, are characteristics of the human $H$, characteristics of the robot $R$, and characteristics of the context of use $C$.
-A temporal dimension is taken into account by the \textit{interaction history} $t$, which leads to anthropomorphism being also a dynamic phenomenon (see point 3).
-\item \textbf{Anthropomorphism is multi-layered.} Applying a cognitive viewpoint on anthropomorphism, there exist \textit{lower and higher levels} of the phenomenon.
-On one hand, the level (it may be a continuum rather than discrete levels) depends on one how typical or uniquely human the attributed characteristics are, and how much the mental model that the user build of the robot overlaps (or is inspired by) the mental model he/she has of another human.
-As an outcome of this, three different \textit{cognitive stages} have been identified.
-These stages reflect the implicated cognitive depth of the anthropomorphic effect.
-\item \textbf{Anthropomorphism is dynamic.} Looking at how experience and interaction evolve over time, we developed a conceptual model of the dynamics of anthropomorphism, which states that there is a non-linear relationship between the observable \textit{anthropomorphic effects} $A_t$ (a user's tendency to anthropomorphize a robot) and the \textit{interaction history} $t$ (taking into account the actual time the user has spent interacting with the robot for real or imagined).
-The shape of the hypothesized curve starts with the so-called \textit{Initial Capital of Anthropomorphism} ($ICA$) that can be measured as a pre-variable, based on the three main factors (see point 1).
-With a considerable interaction history, the curve approaches the so-called \textit{Stabilized Level of Antrhopomorphism} ($SLA$).
-How the curve evolves in between these two values is flexible and unique to each user, robot, and context.
-We generally assume an increase of \textit{anthropomorphic effects} driven by the \textit{novelty} of the robot, followed by a decrease of $A_t$ as the user \textit{familiarizes} him/herself with the robot and with using the robot.
+
+\item \textbf{Anthropomorphism is based on multiple factors.} The three main
+    factors that constitute anthropomorphism are the characteristics of the
+    human, the characteristics of the robot, and the characteristics of the
+    context of use. A temporal dimension is taken into account by the
+    \textit{interaction history} $t$, which reflects the fact that
+    anthropomorphism is also a dynamic phenomenon.
+
+\item \textbf{Anthropomorphism is dynamic.} Looking at how experience and
+    interaction evolve over time, we developed a qualitative model of the
+    dynamics of anthropomorphism, which materializes a non-linear relationship
+    between the observable \textit{anthropomorphic effects} \AntE of the human
+    behavior and the \textit{interaction duration} $t$ (the actual time the user
+    has spent interacting with the robot for real or imagined). This qualitative
+    relationship starts at $t_{0}$ with the \textit{initial potential to
+    anthropomorphize} (IPA), a function of the three factors previously
+    discussed (point 1) that measures a pre-interaction form of
+    anthropomorphism. On the other end, at $t_{\infty}$, we suggest that the
+    interaction reaches a \textit{stabilized level of anthropomorphism} (SLA).
+    How the curve evolves in between these two values is flexible and unique to
+    each user, robot, and context. We however generally hypothesize an increase of
+    \textit{anthropomorphic effects} driven by the \textit{novelty} of the
+    robot, followed by a decrease of \AntE as the user \textit{familiarizes}
+    him/herself with the robot and with using the robot.
+
+\item \textbf{Anthropomorphism is multi-layered cognitive mechanism.} We have
+    identified three successive and overlapping cognitive layers that underlie
+    human-robot interaction and shape anthropomorphic behaviors.
+    These layers (that are likely continuum rather than discrete levels) depend
+    on one how typically human the robot is perceived, and how much the mental
+    model that the user builds of the robot overlaps (or is inspired by) the
+    mental model he/she has of another human. Each of the layers
+    reflect different depths of cognitive engagement between the human and the
+    robot.
+
 \end{enumerate}
+
+We believe that this systematic approach of anthropomorphism as a complex social
+and psychological phenomenon, along with the terminology clarification that we
+have proposed in the introduction of the article, can effectively support
+further research on the intricate interactions between humans and robots.
+
+We purposefully kept this work at a rather abstract level since our aim was to
+build and extend the theoretical grounds of anthropomorphism in HRI. The
+question of operationalizing these models is however also important, and the
+next section briefly sketch the state of the techniques and methods to
+concretely assess anthropomorphic attitudes in HRI.
 
@@
 concrete constructs that are typical or unique of the concept of
-``human-likeness''.  For instance, \cite{ruijten_introducing_2014} propose a
-25-item questions to measure various concrete aspects of human-likeness.
-
-Still, measuring anthropomorphism (or social engagement with a robot) through
-subjective self-reporting remains challenging because the phenomenon is
-partially unconscious, its mediation is largely subject-dependent, and we found
-the phenomenon generally difficult to verbalize for users.
-
-As a consequence, to reduce subjectivity and still accurately account for
-psychological effects, it is necessary to interleave quantitative and
-qualitative assessments of anthropomorphic effects.
-
-We present in this section the methodology and techniques that we used to assess
-anthropomorphic projections in the child-robot interaction study, called the
-Domino study (see section \ref{sec:field-results}, and Figure \ref{fig:ranger}).
-
-\paragraph{Qualitative and quantitative assessment of anthropomorphism in
-human's behavior\\}
-
-Anthropomorphism can possibly be observed in how humans behave toward a
-non-human agent (social human-like engagement). Based on video recordings of the
-Domino experiment, we acquired both quantitative and qualitative behavioral data
-that reflects anthropomorphism.
-
-Quantitative data are acquired by systematic annotations of specific types of
-actions in the video records of the interaction. Six classes of interactions
-were identified as reflecting active commitment and/or an anthropomorphic
-interaction of the user: gestures toward the robot, touching the robot, direct
-talk to the robot, showing something to the robot, mistreating the robot (\eg
-kicking it), and looking at the experimenter because worried by the robot's
-behavior.
-
-By considering the number of occurrences, the duration, and consequently the
-frequency of these types of interaction, we can make statements of how far the
-robot is anthropomorphized in an interaction (based on quantitative data).
-
-We assessed anthropomorphic interactions qualitatively by looking at specific
-instances of human-social cues in the human's behavior, such as: facial
-expressions, observable emotional reactions (\eg surprised, high pitch voice or
-shouting to the robot), eye-contact with the robot, turn-taking gestures,
-greeting (waving) gestures. These are just suggestions of actions that might
-reflect anthropomorphism. These actions partly overlap with the quantitative
-assessment, however it is generally advisable to combine the two.
-
-\paragraph{Qualitative assessment of anthropomorphism when verbally referring to
-the robot (reflection)\\}
-
-The main tools for qualitative measurement of anthropomorphic effect are
-questionnaires and semi-structured interviews. We have explored both
-rating-scales in a questionnaire, and open questions in an interview.  In the
-Domino study, interviews were transcribed and participant's answers to the key
-questions that were assessing an anthropomorphic projection onto the robot, were
-analyzed. For instance, one question to see how far children would ascribe moral
-standing to the robot was \emph{``If you had this robot at home, and you were to
-leave for 2 weeks of holidays, would it be ok to leave the robot alone at
-home?''}. A point for anthropomorphism was counted, when the participant's
-answer indicated an anthropomorphic view of the robot. This process led to a
-``qualitative score'' that reflects how far the robot is anthropomorphized.
-Table~\ref{tab:domino-questions} summarizes the constructs that we used to
-measure how far the robot is perceived as a human-like agent, along with example
-questions.
+``human-likeness'', and \cite{ruijten_introducing_2014} propose for instance a
+25-item questionnaire to measure various concrete aspects of human-likeness.
+
+We have explored both rating-scales in a questionnaire, and open questions in an
+interview.  In the ``dominos'' study depicted in Figure~\ref{fig:ranger}
+(page~\pageref{fig:ranger}), interviews with the young children were transcribed
+and participant's answers to key questions were analyzed. For instance, one
+question to see how far children would ascribe moral standing to the robot was
+\emph{``If you had this robot at home, and you were to leave for 2 weeks of
+holidays, would it be ok to leave the robot alone at home?''}. We then
+attributed points when the participant's answer indicated an anthropomorphic
+view of the robot. This process led to a ``qualitative score'' that reflects how
+far the robot is anthropomorphized. Table~\ref{tab:domino-questions} summarizes
+the constructs that we used to measure how far the robot is perceived as a
+human-like agent, along with example questions.
 
@@
 
-Some of these questions were taken from previous work done by
-\cite{kahn_jr._robotic_2006} an \cite{weiss_i_2009}. In both studies, both
-questionnaires and an analysis of behavior were used to assess children's and
-adult's engagement with, and perception of the robot. This seems to be a
-promising approach to investigate anthropomorphism, as it is also possible to
-combine quantitative and qualitative techniques.
+Still, measuring anthropomorphism (or social engagement with a robot) through
+subjective self-reporting remains challenging because the phenomenon is
+partially unconscious, it remains generally difficult to verbalize for users,
+and questionnaires, as post-hoc measurement, do not easily account for the
+dynamics of the phenomenon.  Some of the questions of the ``dominos'' study were
+taken from previous work done by~\cite{kahn_jr._robotic_2006}
+and~\cite{weiss_i_2009}, and in these two studies, questionnaires results were
+augmented with an analysis of behavior to assess children's and adult's
+engagement with the robot.
+
+We also explored the combination of interviews scoring with behavioral
+measurement in the ``dominos'' study: we acquired quantitative data by
+systematic annotations of specific types of actions in the video records of the
+interaction. Six classes of interactions were identified as reflecting active
+commitment and/or an anthropomorphic interaction of the user: gestures toward
+the robot, touching the robot, direct talk to the robot, showing something to
+the robot, mistreating the robot (\eg kicking it), and looking at the
+experimenter because worried by the robot's behavior.
+By considering the number of occurrences, the duration, and consequently the
+frequency of these types of interaction, we built a weighting scheme to rate
+the observed level of anthropomorphic behaviors in an interaction (\ie, \AntE).
+
+This approaches remain however fragile: in our experience, the weighting scheme
+of the annotated behaviors mostly relies on a subjective assessment by the
+experimenters, which makes it difficult to transfer to different experimental
+settings. And it remains to be seen how self-reported assessment of
+anthropomorphism (through questionnaires) can be meaningfully combined with
+behavioral measurements, in a way that account for the dynamic nature of
+anthropomorphism.
 
@@
 
-Overall, if we agree that \textbf{anthropomorphism arises in an interaction}, this requires studying the phenomenon as such, both in terms of evaluation scenarios, and in terms of measurements.
-Regarding \textbf{evaluation scenarios}, we suggest to go beyond using videos and pictures of robots, but to use real interaction scenarios (possibly long-term, \eg one interaction spanning over an extended period of time, or several sessions so to have repeated interactions).
-In terms of \textbf{measurements}, we suggest to go beyond using rating scales, but to apply a more holistic approach that regards not only participants perception of the robot but also the way they interact with the robot.
-For this, we proposed a so-called \textit{Anthropomorphism Index} $AntX$ that can be used both as a measurement tool and as a value that reflects how much a user anthropomorphized a robot in a given situation.
-To take into account the dynamics over time, we propose to measure $AntX$ at several points, as a pre-variable (focusing on user expectations, previous experience, robot design), in-situ variables (focusing on behavioral aspects, interaction, variations of robot behavior) and post-variables (perception and acceptance rating of interaction).
+Overall, if we agree that \textbf{anthropomorphism arises in an interaction},
+this requires studying the phenomenon as such, both in terms of evaluation
+scenarios, and in terms of measurements. Regarding \textbf{evaluation
+scenarios}, we suggest to go beyond using videos and pictures of robots, but to
+use real interaction scenarios (possibly long-term, \eg one interaction spanning
+over an extended period of time, or several sessions so to have repeated
+interactions). In terms of \textbf{measurements}, we suggest to go beyond using
+rating scales, but to apply a more holistic approach that regards not only
+participants perception of the robot but also the way they interact with the
+robot. To take into account the dynamics over time, it appears important to
+assess anthropomorphism at several points, as a
+pre-variable (focusing on user expectations, previous experience, robot design),
+in-situ variables (focusing on behavioral aspects, interaction, variations of
+robot behavior) and post-variables (perception and acceptance rating of
+interaction).
 
@@
 
-We have proposed that the user's familiarization with the robot is a significant factor that influences how anthropomorphism evolves over time.
-We assume a general \textit{decrease} of anthropomorphic effects as the user gets familiar with the robot, and we applied a cognitive viewpoint to legitimate this.
-However, there exist opposite interpretations.
-\cite{eddy_attribution_1993} state that familiarization and more interaction with an agent \textit{increase} the tendency to anthropomorphize.
-Similarly, \citep{duffy_anthropomorphism_2003} reports that several psychological experiments and HRI studies showed that familiarity with the system eases social acceptance and tends to \textit{increase} people's tendency to perceive human-like characteristics in the system.
-We acknowledge that our conceptual model is an idea that needs to be verified, so to see whether our hypotheses can hold.
-In particular, the effect of the user's familiarity with the robot, and the role of disruptive robot behaviors needs to be studied in more detail and over extended periods of time.
-
-While subject to discussion and further refinements and extensions, we hope that this contribution consolidates the scientific grounds of anthropomorphism and provides support for a better understanding of anthropomorphism and its role in long-term acceptance of robots in human environments.
+We have proposed that the user's familiarization with the robot is a significant
+factor that influences how anthropomorphism evolves over time. We assume a
+general \textit{decrease} of anthropomorphic effects as the user gets familiar
+with the robot, and we applied a cognitive viewpoint to legitimate this.
+However, there exist opposite interpretations. \cite{eddy_attribution_1993}
+state that familiarization and more interaction with an agent \textit{increase}
+the tendency to anthropomorphize. Similarly, \cite{duffy_anthropomorphism_2003}
+reports that several psychological experiments and HRI studies showed that
+familiarity with the system eases social acceptance and tends to
+\textit{increase} people's tendency to perceive human-like characteristics in
+the system.  We acknowledge that our conceptual model is an idea that needs to
+be verified, so to see whether our hypotheses can hold. In particular, the
+effect of the user's familiarity with the robot, and the role of disruptive
+robot behaviors needs to be studied in more detail and over extended periods of
+time.
+
+While subject to discussion and further refinements and extensions, we hope that
+this contribution consolidates the scientific grounds of anthropomorphism and
+provides support for a better understanding of anthropomorphism and its role in
+long-term acceptance of robots in human environments.
 

### 2014-11-28 paper.tex
Update section structure of part 4
Pass on the sections 3.2 -> 4

@@
 
-In this context, \emph{familiarization} means \emph{to get acquainted with}.
-It is not to be confused with the \emph{familiarity thesis} that relates to the
-projection of already known cognitive models onto the robot. We discuss this other
-aspect in section~\ref{sec:cognition-neuroscience}.
-
 The \emph{familiarization phase} starts at the peak of the \emph{novelty
-effect}: anthropomorphic effects are at their maximum, the user thinks (s)he is
+effect}: anthropomorphic effects are at their maximum, the user thinks he/she is
 potentially facing an agent aiming at ``human-level intelligence'' (to take
@@
 
-\paragraph{Disruptive behaviors.}
-
-We call \emph{disruptive behaviors} any behavior exhibited by the robot that
-appears unexpected to the user: for instance, a robot may usually follow always
-the same route to go from one place in a house to the other, but suddenly it
-might change the route. The actual underlying reason may span from a bug to the
-detection of a new obstacle, but as long as this reason is not immediately
-intelligible to the user, the behavior counts as \emph{disruptive}. We further
-discuss the role of disruptive behaviors in cognitive terms in section
-\ref{sec:disruptive}.
+During this phase, we call \emph{disruptive behaviors} any behavior exhibited by
+the robot that appears unexpected to the user: for instance, a robot usually
+always follows the same route to go from one place in a house to the other, and
+suddenly it changes the route. The actual underlying reason may span from a
+bug to the detection of a new obstacle, but as long as this reason is not
+immediately intelligible to the user, the behavior counts as \emph{disruptive}.
+We further discuss the role of disruptive behaviors in cognitive terms in
+section \ref{sec:disruptive}.
+
+Note that, in this context, \emph{familiarization} means \emph{to get acquainted with}.
+It is not to be confused with the \emph{familiarity thesis} that relates to the
+projection of already known cognitive models onto the robot. We discuss this other
+aspect in section~\ref{sec:cognition-neuroscience}.
 
@@
 
-During the \textit{Stabilization Phase} the value of \Ant tends to stabilize over
+During the \textit{Stabilization Phase} the level of \AntE tends to stabilize over
 a longer time, to reach a value that we call the \textit{Stabilized Level of
@@
 
+The model that we have introduced so far helps to represent and organize the
+\emph{observations} of anthropomorphism. It does so at a conceptual level, and
+with a special emphasis on the evolution over time.  This abstract model may
+contribute to a better understanding of the \emph{phenomenology} of
+anthropomorphism, but it does not help to \emph{explain} the phenomenon. To this
+end, we propose in the following section to explore the cognitive mechanisms at
+play that account for anthropomorphism.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-The model that we have introduced so far helps to represent and organize the
-\emph{observations} of anthropomorphism. It does so at a conceptual level, and
-with a special emphasis on the evolution over time.
-
-This abstract model may contribute to a better understanding of the
-\emph{phenomenology} of anthropomorphism, but it does not help to \emph{explain}
-the phenomenon. This section proposes to look at the dynamics of
-anthropomorphism in terms of \emph{cognitive correlates}: how human cognition
-can explain the dynamic nature of our interactions with robots, and what are the
-main cognitive layers upon which researchers can build to design better, deeper
-human-robot interactions.
+This section proposes to look at the dynamics of anthropomorphism in terms of
+their underlying cognitive mechanisms: how human cognition can explain the
+dynamic nature of our interactions with robots, and what are the main cognitive
+layers upon which researchers can build to design better, deeper human-robot
+interactions.
 
@@
 %}
-\caption{\textbf{The three cognitive layers of anthropomorphism}: Layer 1 is the instinctive,
-sub-cognitive identification of living peers. {\it Empathy} is characteristic
-of this stage. After longer observation or short, non-contextualized interaction
-(typically, a lab environment), the user enters Layer 2: the user projects a
-mental model he/she is already familiar with onto the robot. After longer {\it
-contextualized} interaction (typically, at home), the user enters Layer 3 of
-anthropomorphism: the user composes a custom mental model of the robot,
-based on experience. This leads to adapted interaction modalities, that may
-still be anthropomorphic, or not. Note that the different layers coexist: Layer
-1 and 2 still affect the human perception of the robot in a Layer 3 interaction.}
+\caption{\textbf{The three cognitive layers of anthropomorphism}: Layer 1 is the
+instinctive, sub-cognitive identification of living peers. {\it Empathy} is
+characteristic of this stage. The Layer 2 materializes after longer
+observation or short, non-contextualized interaction (typically, a lab
+environment): the user projects a mental model he/she is already familiar
+with onto the robot. After longer {\it contextualized} interaction
+(typically, at home), the user enters Layer 3 of anthropomorphism: the user
+composes a custom mental model of the robot, based on experience. This leads
+to adapted interaction modalities, that may still be anthropomorphic, or
+not. Note that the different layers coexist: Layer 1 and 2 continue to affect the
+human perception of the robot in a Layer 3 interaction.}
+
 \label{fig:cognitivemodel}
@@
 \emph{Familiarization} and \emph{Stabilization} phases introduced in our model
-of the dynamics of anthropomorphism. We discuss this relation hereafter.
-
-\subsubsection{Cognitive Processes and Layers\\}
+of the dynamics of anthropomorphism. We discuss this relation in
+section~\ref{sec:relations}.
 
@@
 
-The intuitive anthropomorphization in the cognitive Layer 1 might be
+This intuitive form of anthropomorphization in the cognitive Layer 1 might be
 characteristic of what \cite{takayama_perspectives_2012} calls the
 \textit{in-the-moment} perspective on agency with a robot compared to the
-\textit{reflective} perspective (see paragraph ``artifact-centric perspective''
-in section \ref{sec:anthropomorphism}).  For instance, we reflectively might
+\textit{reflective} perspective. For instance, we reflectively might
 \textit{not} perceive agency in a social robot, but it can feel quite
@@
 consciously perceive. This means that in the initial phase of interacting with a
-novel device \textit{(initialization)} (see Figure \ref{fig:dynamics}) people
+novel device (\textit{initialization} on Figure \ref{fig:dynamics}) people
 might not respond consciously but rather mindlessly \citep{nass_machines_2000},
 and in turn anthropomorphize more. They start to respond in a more reflective
-manner only during the \textit{familiarization} (in turn, the tendency to
-anthropomorphize might decrease). This can be illustrated by the fact that
-people tend to deny interacting with computational systems as if they were
-people and yet they respond to computers in many ways that are remarkably
+manner only during the \textit{familiarization}, and in turn, the tendency to
+anthropomorphize might decrease. This can be illustrated by the fact that
+people tend to deny interacting with computers as if they were
+people and yet they respond to them in many ways that are remarkably
 similar to how they respond to people \citep{reeves_media_1996}.
@@
 shaped by bottom-up perceptual processes, evoking very immediate responses (\eg
-to the cues emitted by the artifact's design (``artifact-centric
-perspective''). In contrast, according to Takayama, reflective perceptions are
+to the cues emitted by the artifact's design -- the artifact-centric
+perspective. In contrast, according to Takayama, reflective perceptions are
 more often shaped by top-down processes because of the nature of reflective
@@
 environment? What can the robot learn?}, etc.).
+This mental process depends on the human understanding of the robot's inner
+working, as well as his/her own tendency to anthropomorphize (the
+\emph{personality} in IPA factor). At this stage, the \emph{perception} of the
+robot (its shape for instance) and its original intended \emph{purpose} play
+less of an important role. It is mostly a human-centric process.  The result of
+this third phase is a custom cognitive model of the robot.
 
@@
 
-\draw(0.5,5.5) node[anchor=south west] {\scriptsize \sc Init.};
-\draw(2.5,5.5) node[anchor=south west] {\scriptsize \sc Familiarization};
-\draw(7,5.5) node[anchor=south west] {\scriptsize \sc Stabilization};
+\draw(0.5,6.0) node[anchor=south west] {\scriptsize \sc Init.};
+\draw(2.5,6.0) node[anchor=south west] {\scriptsize \sc Familiarization};
+\draw(7,6.0) node[anchor=south west] {\scriptsize \sc Stabilization};
 
@@
 
+\draw (-0.05, 2.1) -- (0.05, 2.1) node[anchor=east] {\IPAe};
+\draw (1.8, 4.9) -- (1.8, 5.1) node[anchor=south] {\scriptsize \AntEMax};
+\draw (10, 0.8) node[anchor=west] {\SLAe};
+
 \draw (-0.3,1.5) node[anchor=east] {Layer 1}
@@
     anthropomorphism}: This diagram combines the figures~\ref{fig:dynamics}
-    and~\ref{fig:cognitivemodel} to evidence their interplay: we suggest that
-    the cognitive stages 1 and 2 (pre-cognitive anthropomorphism and projection
-    of known existing cognitive models) first play a key role in the early
+    and~\ref{fig:cognitivemodel} to evidence their interplay: 
+    the cognitive layers 1 and 2 (pre-cognitive anthropomorphism and projection
+    of known existing cognitive models) play a key role in the early
     perception of the robot, leading to high levels of anthropomorphic
@@
 \end{figure}
-
-This mental process depends on the human understanding of the robot's inner
-working, as well as his/her own tendency to anthropomorphize (the
-\emph{personality} in IPA factor). At this stage, the \emph{perception} of the
-robot (its shape for instance) and its original intended \emph{purpose} play
-less of an important role. It is mostly a human-centric process.  The result of
-this third phase is an iteratively adapted cognitive model of the robot.
 
@@
 
-\paragraph{Relation to the dynamics of anthropomorphism\\}
+\subsection{Relation to the dynamics of anthropomorphism}
+\label{sec:relations}
 
@@
 instance, by saying ``I'm lost!''), the behavior is then called
-\emph{transparent}~\citep{kim_who_2006}, and suggests that the
-robot has \emph{introspective} capabilities (it can reflect on its own internal
-state), which may lead to higher anthropomorphic projections.  On the contrary,
-if the robot shows no sign of recognizing its own failure, the user may ascribe
-a lower level of anthropomorphism to the robot.
+\emph{transparent}~\citep{kim_who_2006}, and suggests that the robot has
+\emph{introspective} capabilities (it can reflect on its own internal state),
+which may lead to higher anthropomorphic projections.  On the contrary, if the
+robot shows no sign of recognizing its own failure (a ``plain'' bug), the user
+is likely to ascribe a lower level of anthropomorphism to the robot.
 
@@
 
-In this paper, we have provided a broad account of the cognitive and
+This article provides a broad account of the cognitive and
 psychological viewpoints on anthropomorphism, with a novel focus on the
@@
     human, the characteristics of the robot, and the characteristics of the
-    context of use. A temporal dimension is taken into account by the
+    context of use. Besides, a temporal dimension is taken into account by the
     \textit{interaction history} $t$, which reflects the fact that
@@
     has spent interacting with the robot for real or imagined). This qualitative
-    relationship starts at $t_{0}$ with the \textit{initial potential to
+    relationship starts at $t_{0}$ with what we propose to call an \textit{initial potential to
     anthropomorphize} (IPA), a function of the three factors previously
@@
 
-\item \textbf{Anthropomorphism is multi-layered cognitive mechanism.} We have
-    identified three successive and overlapping cognitive layers that underlie
+\item \textbf{Anthropomorphism is a multi-layered cognitive mechanism.} We 
+    identify three successive and overlapping cognitive layers that underlie
     human-robot interaction and shape anthropomorphic behaviors.
     These layers (that are likely continuum rather than discrete levels) depend
-    on one how typically human the robot is perceived, and how much the mental
+    on ``how typically human'' the robot is perceived, and how much the mental
     model that the user builds of the robot overlaps (or is inspired by) the
-    mental model he/she has of another human. Each of the layers
+    mental model he/she has of another human. Each of these layers
     reflect different depths of cognitive engagement between the human and the
@@
 
-This approaches remain however fragile: in our experience, the weighting scheme
+This approache remains however fragile: in our experience, the weighting scheme
 of the annotated behaviors mostly relies on a subjective assessment by the
